### 2020-01-23 S1_appendix.tex
Initial commit

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}

\usepackage{color,soul}
\usepackage{xcolor}
\usepackage{array}
\usepackage{mhchem}
\usepackage{mathtools}

\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}

\bibliographystyle{plos2015}

\begin{document}

\section*{S1 Appendix: Rate quantiles}

\section{Linear piecewise approximation}

In this article we introduced a linear piecewise approximation of the i-cdf to improve the \textit{quant} method. Let $\hat{F}^{-1}(\mathcal{R}_i)$ be the piecewise approximation of $F^{-1}(\mathcal{R}_i)$. The approximation is comprised of $n$ pieces (where $n$ is fixed).

%$\hat{F}(\mathcal{R}_i)$ be the piecewise approximation of $F(\mathcal{R}_i)$, and let  be its inverse function.

\begin{align}
\hat{F}^{-1}(\mathcal{R}_i) = F^{-1}(\floor{b_i}) + \begin{cases} \Big( F^{-1}(\floor{b_i} + 1) - F^{-1}(\floor{b_i}) \Big) \Big( b_i - \floor{b_i}  \Big) &\text{ if } \floor{b_i} < n-1  \\ 0 &\text{ if } \floor{b_i} = n-1 \end{cases}
\end{align}

where $b_i = \min \{ \max\{ \frac{n \times \mathcal{R}_i}{n-1}, \frac{n_0}{n-1} \}, \frac{n - 1 -n_0}{n-1} \}$ indexes $\mathcal{R}_i$ into one of the $n$ pieces $\floor{b_i}$. $n_0 = 0.1$ provides a lower and upper limits of the piecewise approximation, corresponding to $r_\text{min}$ and $r_\text{max}$ respectively. The lower and upper rate limits are equal to:

\begin{align}
r_\text{min} &= F^{-1}\Big( \frac{n_0}{n-1}\Big) = F^{-1}\Big( 0.001 \Big) \\
r_\text{max} &= F^{-1}\Big( \frac{n - 1 -n_0}{n-1}\Big) = F^{-1}\Big( 0.999 \Big),
\end{align}

when $n=101$ and $n_0=0.1$. It is important to ensure that any operators which act in rate space (as opposed to quantile space) respect these boundaries. The inverse of the approximation function (ie. the cdf $\hat{F}$) is

\begin{align}
\hat{F}(r_i) = \begin{cases} \max \big(0, \frac{1}{n-1} \times \Big( v_i + \frac{r_i -  F^{-1}(\floor{v_i})}{F^{-1}(\floor{v_i}+1) - F^{-1}(\floor{v_i})} \Big) \big) &\text{ if } \floor{v_i} < n-1  \\
	1 &\text{ if } \floor{v_i} = n-1 
\end{cases}
\end{align}

where $v_i \in (0, 1, \dotso, n-1)$ is the piece which $r_i$ corresponds to:

\begin{align}
v_i = \max\limits_{j = 0}^{n-1} \{ j : \hat{F}^{-1}\big(\frac{j}{n-1}\big) < r_i \}.
\end{align}

As the piecewise approximation is linear, computing the derivatives of these two functions (required for computing Hastings ratios) are trivial:

\begin{align}
\frac{\partial}{\partial \mathcal{R}_i} \hat{F}^{-1}(\mathcal{R}_i) =  D \hat{F}^{-1}(\mathcal{R}_i) &= \begin{cases}  \Big(\hat{F}^{-1}(\floor{b_i}+1) - \hat{F}^{-1}(\floor{b_i})\Big) \times(n-1)  & \text{ if } \floor{b_i} < n-1 \\
0 & \text{ if } \floor{b_i} = n-1 \end{cases} \label{eqn:derivFinv}  \\
\frac{\partial}{\partial r_i} \hat{F}(r_i) = D \hat{F}(r_i) &= \frac{1}{\hat{F}^{-1}\Big(\hat{F}(r_i)\Big)} \label{eqn:derivF}
\end{align}

\section{Tree operators for rate quantiles}

Zhang and Drummond 2020 introduced several tree operators for the \textit{real} parameterisation -- including Constant Distance, Simple Distance, and Small Pulley. In this appendix, these three operators are extended to the  the \textit{quant} parameterisation.

Following the notation presented in the main article, let $t_i$ be the time of node $i$, let $0 < q_i < 1$ be the rate quantile of node $i$, and let $r_i = \hat{F}^{-1}(q_i)$ be the natural rate of node $i$.

\subsection{Constant Distance}

Let $X$ be a uniformly-at-random sampled internal node on tree $\mathcal{T}$. Let $L$ and $R$ be the left and right child of $X$, respectively, and let $P$ be the parent of $X$. Under the \textit{quant} parameterisation, the Constant Distance operator works as follows: \\

\textul{\textit{Step 1}}. Propose a new height for $t_X$:

\begin{align}
	{t_X}^\prime \leftarrow t_X + \alpha
\end{align}

where $\alpha \sim \text{ Uniform}(-w, w)$, for some window size $w$. Ensure that $\max\{t_L, t_R \} < {t_X}^\prime < t_P$, and if the constrant is broken then reject the proposal.  \\

\textul{\textit{Step 2}}. Recalculate $q_X$ as:

\begin{align}
	{q_X}^\prime  \leftarrow & \hat{F}\Big({r_X}^\prime \Big) \nonumber\\
				\leftarrow & \hat{F}\Big(\frac{t_P - t_X}{t_P - {t_X}^\prime} r_X \Big)\nonumber \\
				\leftarrow & \hat{F}\Big(\frac{t_P - t_X}{t_P - {t_X}^\prime} \hat{F}^{-1}(q_X) \Big).
\end{align}

This ensures that the genetic distance between $X$ and $P$ remains constant after the operation by enforcing the constraint:

\begin{align}
	r_X (t_P - t_X) = {r_X}^\prime (t_P - {t_X}^\prime).
\end{align}

\textul{\textit{Step 3}}. Similarly, propose new rate quantiles for the two children $C \in \{L, R\}$:

\begin{align}
	{q_C}^\prime  \leftarrow & \hat{F}\Big({r_C}^\prime \Big) \nonumber\\
				\leftarrow & \hat{F}\Big(\frac{t_X - t_C}{{t_X}^\prime - t_C} \times r_C \Big) \nonumber\\
				\leftarrow & \hat{F}\Big(\frac{t_X - t_C}{{t_X}^\prime - t_C} \times \hat{F}^{-1}(q_C) \Big).
\end{align}

Ensure that $r_\text{min} < {r_i}^\prime < r_\text{max}$ for all proposed nodes $i \in \{X, L, R\}$, and if the constraint is broken then reject the proposal.

\textul{\textit{Step 4}}. Finally, compute the natural logarithm of the Hastings ratio as that of the determinant of the Jacobian matrix:

\begin{align}
	J &= \begin{bmatrix} \frac{\partial {t_X}^\prime}{\partial t_X} & \frac{\partial {t_X}^\prime}{\partial q_X} & \frac{\partial {t_X}^\prime}{\partial q_L} & \frac{\partial {t_X}^\prime}{\partial q_R} \\
			\frac{\partial {q_X}^\prime}{\partial t_X} & \frac{\partial {q_X}^\prime}{\partial q_X} & \frac{\partial {q_X}^\prime}{\partial q_L} & \frac{\partial {q_X}^\prime}{\partial q_R} \\
			\frac{\partial {q_L}^\prime}{\partial t_X} & \frac{\partial {q_L}^\prime}{\partial q_X} & \frac{\partial {q_L}^\prime}{\partial q_L} & \frac{\partial {q_L}^\prime}{\partial q_R} \\
			\frac{\partial {q_R}^\prime}{\partial t_X} & \frac{\partial {q_R}^\prime}{\partial q_X} & \frac{\partial {q_R}^\prime}{\partial q_L} & \frac{\partial {q_R}^\prime}{\partial q_R} \\ \end{bmatrix} \nonumber \\
			&= \begin{bmatrix} \frac{\partial {t_X}^\prime}{\partial t_X} & 0 & 0 & 0 \\
			\frac{\partial {q_X}^\prime}{\partial t_X} & \frac{\partial {q_X}^\prime}{\partial q_X} & 0 & 0 \\
			\frac{\partial {q_L}^\prime}{\partial t_X} & 0 & \frac{\partial {q_L}^\prime}{\partial q_L} & 0 \\
			\frac{\partial {q_R}^\prime}{\partial t_X} & 0 & 0 & \frac{\partial {q_R}^\prime}{\partial q_R} \\ \end{bmatrix}.
\end{align}

As $J$ is triangular, its determinant $|J|$ is equal to the product of diagonal elements:

\begin{align}
	\ln |J| =&  \ln \{ \frac{\partial {t_X}^\prime}{\partial t_X} \times \frac{\partial {q_X}^\prime}{\partial q_X} \times \frac{\partial {q_L}^\prime}{\partial q_L} \times \frac{\partial {q_R}^\prime}{\partial q_R} \} \nonumber\\
		=& \ln 1 + \ln \; D \hat{F}\Big( \frac{t_P - t_X}{t_P - {t_X}^\prime} \times \hat{F}^{-1}(q_X)  \Big) + \ln \frac{\partial}{\partial q_X}  \frac{t_P - t_X}{t_P - {t_X}^\prime} \hat{F}^{-1} \Big( q_X \Big) \nonumber\\
		& + \ln \; D\hat{F}\Big( \frac{t_X - t_L}{{t_X}^\prime - t_L} \times \hat{F}^{-1}(q_L) \Big) + \ln \frac{\partial}{\partial q_L} \frac{t_X - t_L}{{t_X}^\prime - t_L} \hat{F}^{-1} \Big( q_L \Big) \nonumber\\
		& + \ln \; D \hat{F}\Big( \frac{t_X - t_R}{{t_X}^\prime - t_R} \times \hat{F}^{-1}(q_R) \Big) + \ln \frac{\partial}{\partial q_R} \frac{t_X - t_R}{{t_X}^\prime - t_R} \hat{F}^{-1} \Big( q_R \Big) \nonumber\\
		=& \ln \; D \hat{F}\Big( \frac{t_P - t_X}{t_P - {t_X}^\prime} \times \hat{F}^{-1}(q_X)  \Big) + \ln \; D  \hat{F}^{-1} \Big( q_X \Big) + \ln \frac{t_P - t_X}{t_P - {t_X}^\prime} \nonumber\\
		& + \ln \; D\hat{F}\Big( \frac{t_X - t_L}{{t_X}^\prime - t_L} \times \hat{F}^{-1}(q_L) \Big) + \ln \; D \hat{F}^{-1} \Big( q_L \Big) + \ln  \frac{t_X - t_L}{{t_X}^\prime - t_L} \nonumber \\
		& + \ln \; D \hat{F}\Big( \frac{t_X - t_R}{{t_X}^\prime - t_R} \times \hat{F}^{-1}(q_R) \Big) + \ln \; D\hat{F}^{-1} \Big( q_R \Big) + \ln \frac{t_X - t_R}{{t_X}^\prime - t_R} .
\end{align}

The derivatives $D\hat{F}$ and $D\hat{F}^{-1}$ are readily computed under the linear piecewise approximation. As its final step, the operator returns $\ln |J|$.

\subsection{Simple Distance}

While Constant Distance proposes internal node heights, Simple Distance operates on the root. Let $X$ be the root node and let $L$ and $R$ be its two children.

\textul{\textit{Step 1}}. Propose a new height for $t_X$:

\begin{align}
	{t_X}^\prime \leftarrow t_X + \alpha
\end{align}

where $\alpha \sim \text{ Uniform}(-w, w)$, for some window size $w$. Ensure that $\max\{t_L, t_R \} < {t_X}^\prime$, and if the constraint is broken then reject the proposal.  \\

\textul{\textit{Step 2}}. Propose new rate quantiles for the two children $C \in \{L, R\}$:

\begin{align}
	{q_C}^\prime  \leftarrow & \hat{F}\Big({r_C}^\prime \Big)  \nonumber \\
				\leftarrow & \hat{F} \Big( \frac{t_X - t_C}{{t_X}^\prime - t_C} \times r_C \Big) \nonumber \\
				\leftarrow & \hat{F} \Big( \frac{t_X - t_C}{{t_X}^\prime - t_C} \times \hat{F}^{-1}(q_C) \Big).
\end{align}

These proposals ensure that the genetic distance between $X$ and its children $C$ remain constant after the operation by enforcing the constraint:

\begin{align}
	r_C (t_X - t_C) = {r_C}^\prime ({t_X}^\prime - t_C).
\end{align}

Ensure that $r_\text{min} < {r_C}^\prime < r_\text{max}$, and if the constraint is broken then reject the proposal.

\textul{\textit{Step 3}}. Return the natural logarithm of the Green ratio by calculating the determinant of the Jacobian matrix $J$.

\begin{align}
	J &= \begin{bmatrix} \frac{\partial {t_X}^\prime}{\partial t_X} & \frac{\partial {t_X}^\prime}{\partial q_L} & \frac{\partial {t_X}^\prime}{\partial q_R} \\
						\frac{\partial {q_L}^\prime}{\partial t_X} & \frac{\partial {q_L}^\prime}{\partial q_L} & \frac{\partial {q_L}^\prime}{\partial q_R} \\
						\frac{\partial {q_R}^\prime}{\partial t_X} & \frac{\partial {q_R}^\prime}{\partial q_L} & \frac{\partial {q_R}^\prime}{\partial q_R} \end{bmatrix} \nonumber \\
		&= \begin{bmatrix} \frac{\partial {t_X}^\prime}{\partial t_X} & 0 & 0 \\
						\frac{\partial {q_L}^\prime}{\partial t_X} & \frac{\partial {q_L}^\prime}{\partial q_L} & 0\\
						\frac{\partial {q_R}^\prime}{\partial t_X} & 0 & \frac{\partial {q_R}^\prime}{\partial q_R} \end{bmatrix}.
\end{align}

As $J$ is triangular, its determinant $|J|$ is equal to the product of diagonal elements:

\begin{align}
	\ln |J| =&  \ln \{ \frac{\partial {t_X}^\prime}{\partial t_X} \times \frac{\partial {q_L}^\prime}{\partial q_L} \times \frac{\partial {q_R}^\prime}{\partial q_R} \} \nonumber \\
			=& \ln \frac{\partial {t_X}^\prime}{\partial t_X} +  \ln \frac{\partial {q_L}^\prime}{\partial q_L} + \ln \frac{\partial {q_R}^\prime}{\partial q_R} \nonumber \\
			=& \ln 1  \nonumber\\
			&+ \ln \; D \hat{F}\Big( \frac{t_X - t_L}{{t_X}^\prime - t_L} \times \hat{F}^{-1}(q_L) \Big) + \ln \frac{\partial}{\partial q_L} \frac{t_X - t_L}{{t_X}^\prime - t_L} \hat{F}^{-1} \Big( q_L \Big) \nonumber\\
			&+ \ln \; D \hat{F}\Big( \frac{t_X - t_R}{{t_X}^\prime - t_R}\times \hat{F}^{-1}(q_R) \Big) + \ln \frac{\partial}{\partial q_R} \frac{t_X - t_R}{{t_X}^\prime - t_R} \hat{F}^{-1} \Big( q_R \Big) \nonumber\\
			=& \ln \; D \hat{F}\Big( \frac{t_X - t_L}{{t_X}^\prime - t_L} \times \hat{F}^{-1}(q_L) \Big) + \ln \; D \hat{F}^{-1} \Big( q_L \Big) + \ln \frac{t_X - t_L}{{t_X}^\prime - t_L}\nonumber \\
			&+ \ln \; D \hat{F}\Big( \frac{t_X - t_R}{{t_X}^\prime - t_R}\times \hat{F}^{-1}(q_R) \Big) + \ln \; D \hat{F}^{-1} \Big( q_R \Big) + \ln  \frac{t_X - t_R}{{t_X}^\prime - t_R}.
\end{align}

$D \hat{F}(x)$ and $D \hat{F}^{-1}(x)$ are readily computed from the linear piecewise approximation. As its final step, the operator returns $\ln |J|$.

\subsection{Small Pulley}

Just like the previous operator, Small Pulley operates on the root. Let $X$ be the root node and let $L$ and $R$ be its two children. However, unlike Simple Distance, this operator alters the two genetic distances $d_L = r_L (t_X - t_L) = \hat{F}^{-1} (q_L) (t_X - t_L)$ and $d_R = r_R (t_X - t_R) = \hat{F}^{-1} (q_R) (t_X - t_R)$, while conserving their sum $d_L + d_R$.

\textul{\textit{Step 1}}. Propose new genetic distances for $d_L$ and $d_R$:

\begin{align}
	{d_L}^\prime & \leftarrow d_L + \alpha \\
	{d_R}^\prime & \leftarrow d_R - \alpha
\end{align}

where $\alpha \sim \text{ Uniform}(-w, w)$, for some window size $w$. Ensure that $0 < {d_L}^\prime < d_L + d_R$ and that $r_\text{min} < {r_C}^\prime < r_\text{max}$ for $C \in \{ L, R \}$, and if either constrant is broken then reject the proposal.  \\

\textul{\textit{Step 2}}. Propose new rate quantiles for the two children $L$ and $R$:

\begin{align}
	{q_L}^\prime &\leftarrow \hat{F}\big( \frac{{d_L}^\prime}{t_X - t_L} \big) \nonumber\\
				 &\leftarrow \hat{F}\big( \frac{\hat{F}^{-1} (q_L) (t_X - t_L) + \alpha}{t_X - t_L} \big) \\
	{q_R}^\prime &\leftarrow \hat{F}\big( \frac{{d_R}^\prime}{t_X - t_R} \big) \nonumber \\
				 &\leftarrow \hat{F}\big( \frac{\hat{F}^{-1} (q_R) (t_X - t_R) - \alpha}{t_X - t_R} \big).
\end{align}

\textul{\textit{Step 3}}. Return the natural logarithm of the Green ratio by calculating the determinant of the Jacobian matrix $J$.

\begin{align}
	J &= \begin{bmatrix} \frac{\partial {q_L}^\prime}{\partial q_L} & \frac{\partial {q_L}^\prime}{\partial q_R} \\
						 \frac{\partial {q_R}^\prime}{\partial q_L} & \frac{\partial {q_R}^\prime}{\partial q_R} \end{bmatrix} \nonumber \\
	 &= \begin{bmatrix} \frac{\partial {q_L}^\prime}{\partial q_L} & 0 \\
						 0 & \frac{\partial {q_R}^\prime}{\partial q_R} \end{bmatrix}
\end{align}

As $J$ is triangular/diagonal, its determinant $|J|$ is equal to the product of diagonal elements:

\begin{align}
	\ln |J| =&  \ln \{ \frac{\partial {q_L}^\prime}{\partial q_L} \times \frac{\partial {q_R}^\prime}{\partial q_R} \} \nonumber \\
			=& \ln  \frac{\partial {q_L}^\prime}{\partial q_L} + \ln \frac{\partial {q_R}^\prime}{\partial q_R}\nonumber \\
			=& \ln \; D \hat{F}\big( \frac{\hat{F}^{-1} (q_L) (t_X - t_L) + \alpha}{t_X - t_L} \big) + \ln \frac{\partial {q_L}^\prime}{\partial q_L}  \frac{\hat{F}^{-1} (q_L) (t_X - t_L) + \alpha}{t_X - t_L} \nonumber\\
			&+ \ln \; D \hat{F}\big( \frac{\hat{F}^{-1} (q_R) (t_X - t_R) - \alpha}{t_X - t_R} \big) + \ln \frac{\partial {q_R}^\prime}{\partial q_R}  \frac{\hat{F}^{-1} (q_R) (t_X - t_R) - \alpha}{t_X - t_R} \nonumber\\
			=& \ln \; D \hat{F}\big( \frac{\hat{F}^{-1} (q_L) (t_X - t_L) + \alpha}{t_X - t_L} \big) + \ln \; D \hat{F}^{-1} (q_L) \nonumber \\
			&+ \ln \; D \hat{F}\big( \frac{\hat{F}^{-1} (q_R) (t_X - t_R) - \alpha}{t_X - t_R} \big) + \ln \; D\hat{F}^{-1} (q_R) .
\end{align}

Thus, as its final step, the operator returns $\ln |J|$.

\bibliography{references}

\end{document}

### 2020-01-23 S2_appendix.tex
Initial commit

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}

\usepackage{color,soul}
\usepackage{xcolor}
\usepackage{array}
\usepackage{mhchem}
\usepackage{mathtools}

\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}

\bibliographystyle{plos2015}

\begin{document}

\section*{S2 Appendix: Well-calibrated simulation studies}

Every method presented and tested in this paper was validated with a well-calibrated simulation study using the same model and operator set that which was benchmarked. This is achieved using 100 simulated datasets (each with $N=100$ taxa and a $L=5000$ nt alignment). The 95 \% highest posterior density (HPD) interval is calculated, and the `true' parameter values are compared with their values estimated from the simulated data.

The validation results are presented as plots. The number in the bottom right corner of each plot is the coverage; that is the percentage of simulations where the `true' parameter value is within the 95 \% HPD interval. If all parameters have coverage close to 95 \% coverage, then this suggests correctness of implementation.

The parameters presented in each plot are: the Yule model birth rate $\lambda$, rate heterogeneity gamma shape $\Gamma$, HKY substitution model parameter $\kappa$, log-normal clock standard deviation $\sigma$, the frequency of the A nucleotide $f_A$, and the rate of the first taxon $r_1$. The remaining 3 frequencies and 99 taxa rates are omitted from the figures.

\begin{figure}[!htb]
\includegraphics[width=0.85\textwidth]{Figures/CalSim_cat.pdf}
\caption{\textbf{The \textit{cat} parameterisation.} Blue and red vertical lines are 95 \% HPD intervals, where blue intervals contain the true value and red intervals do not.}
\label{fig:rateparams}
\end{figure}

\begin{figure}[!htb]
\includegraphics[width=0.85\textwidth]{Figures/CalSim_real.pdf}
\caption{\textbf{The \textit{real} parameterisation,} with the operators decribed by Zhang and Drummond 2020.}
\label{fig:rateparams}
\end{figure}

\begin{figure}[!htb]
\includegraphics[width=0.85\textwidth]{Figures/CalSim_quant.pdf}
\caption{\textbf{The \textit{quant} parameterisation,} with the operators decribed by Zhang and Drummond 2020, and adapted for \textit{quant} as described in \textbf{S1 Appendix}.}
\label{fig:rateparams}
\end{figure}

\bibliography{references}

\end{document}

### 2020-01-23 manuscript.tex
Initial commit

% Template for PLoS
% Version 3.5 March 2018
%
% % % % % % % % % % % % % % % % % % % % % %
%
% -- IMPORTANT NOTE
%
% This template contains comments intended
% to minimize problems and delays during our production
% process. Please follow the template instructions
% whenever possible.
%
% % % % % % % % % % % % % % % % % % % % % % %
%
% Once your paper is accepted for publication,
% PLEASE REMOVE ALL TRACKED CHANGES in this file
% and leave only the final text of your manuscript.
% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
%
%
% There are no restrictions on package use within the LaTeX files except that
% no packages listed in the template may be deleted.
%
% Please do not include colors or graphics in the text.
%
% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
%
% % % % % % % % % % % % % % % % % % % % % % %
%
% -- FIGURES AND TABLES
%
% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
%
% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
% - Figures should be uploaded separately from your manuscript file.
% - Figures generated using LaTeX should be extracted and removed from the PDF before submission.
% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
% For figure citations, please use "Fig" instead of "Figure".
% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
%
% Tables should be cell-based and may not contain:
% - spacing/line breaks within cells to alter layout or alignment
% - do not nest tabular environments (no tabular environments within tabular environments)
% - no graphics or colored text (cell background color/shading OK)
% See http://journals.plos.org/plosone/s/tables for table guidelines.
%
% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
%
% % % % % % % % % % % % % % % % % % % % % % % %
%
% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
%
% IMPORTANT
% Below are a few tips to help format your equations and other special characters according to our specifications. For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
%
% For inline equations, please be sure to include all portions of an equation in the math environment.  For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
%
% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
%
% Please add line breaks to long display equations when possible in order to fit size of the column.
%
% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
%
% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2".
%
% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
%
% % % % % % % % % % % % % % % % % % % % % % % %
%
% Please contact latex@plos.org with any questions.
%
% % % % % % % % % % % % % % % % % % % % % % % %

\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}

% amsmath and amssymb packages, useful for mathematical formulas and symbols
\usepackage{amsmath,amssymb}

% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{changepage}

% Use Unicode characters when possible
\usepackage[utf8x]{inputenc}

% textcomp package and marvosym package for additional characters
\usepackage{textcomp,marvosym}

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

% Use nameref to cite supporting information files (see Supporting Information section for more info)
\usepackage{nameref,hyperref}

% line numbers
\usepackage[right]{lineno}

% ligatures disabled
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }

% color can be used to apply background shading to table cells only
\usepackage[table]{xcolor}

% array package and thick rules for tables
\usepackage{array}

\usepackage{color,soul}
\usepackage[normalem]{ulem}

\usepackage{mhchem}
\usepackage{mathtools}

\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}

% create "+" rule type for thick vertical lines
\newcolumntype{+}{!{\vrule width 2pt}}

% create \thickcline for thick horizontal lines of variable length
\newlength\savedwidth
\newcommand\thickcline[1]{%
  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
  \cline{#1}%
  \noalign{\vskip\arrayrulewidth}%
  \noalign{\global\arrayrulewidth\savedwidth}%
}

% \thickhline command for thick horizontal lines that span the table
\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
\hline
\noalign{\global\arrayrulewidth\savedwidth}}

% Remove comment for double spacing
%\usepackage{setspace}
%\doublespacing

% Text layout
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in
\textheight 8.75in

% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
% Captions will be left justified
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
\renewcommand{\figurename}{Fig}

% Use the PLoS provided BiBTeX style
\bibliographystyle{plos2015}

% Remove brackets from numbering in List of References
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
%\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
%\setlength{\headheight}{27.023pt}
%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\today}

\usepackage{makecell}
\usepackage{gensymb}
\usepackage{rotating}
\usepackage{pdflscape}
\usepackage{multirow}

%% Include all macros below
\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}
\newcommand{\angstrom}{\mbox{\normalfont\AA}}

\newenvironment{changemargin}[2]{%
\begin{list}{}{%
\setlength{\topsep}{0pt}%
\setlength{\leftmargin}{#1}%
\setlength{\rightmargin}{#2}%
\setlength{\listparindent}{\parindent}%
\setlength\textit{emindent}{\parindent}%
\setlength{\parsep}{\parskip}%
}%
\item[]}{\end{list}}

%% END MACROS SECTION

\begin{document}
\vspace*{0.2in}

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Smarter dating moves and faster proposals: revisiting the phylogenetic relaxed clock model} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Jordan Douglas\textsuperscript{1*},
Rong Zhang\textsuperscript{1},
Alexei J. Drummond\textsuperscript{1,2},
Remco Bouckaert\textsuperscript{1}
\\
\bigskip
\textbf{1} Centre for Computational Evolution, School of Computer Science, University of Auckland, Auckland, New Zealand\\
\textbf{2} School of Biological Sciences, University of Auckland, Auckland, New Zealand
\\
\bigskip

% Use the asterisk to denote corresponding authorship and provide email address in note below.
* jordan.douglas@auckland.ac.nz

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step.
% Author Summary not valid for PLOS ONE submissions.   
\section*{Author summary}

\linenumbers

% Use "Eq" instead of "Equation" for equation citations.
\section*{Introduction}

% Results and Discussion can be combined.
\section*{Models} \label{sect:models}

\subsection*{Preliminaries}

% Define tau

Let $\mathcal{T}$ be a binary rooted time tree with $N$ taxa (and $2N-2$ branches). Let $L$ be the number of sites within the multiple sequence alignment $D$, and let $L_\text{eff}$ be the \textit{effective} number of sites in the alignment (ie. the number of site patterns). The posterior density of a phylogenetic model is described by

\begin{eqnarray}
\label{eq:bayesian}
p(\mathcal{T}, \vec{\mathcal{R}}^{\,}, \sigma, \theta|D) \propto  p(D|\mathcal{T}, r(\vec{\mathcal{R}}^{\,}), \theta) \; p(\mathcal{T}|\theta) \;  p(\vec{\mathcal{R}}^{\,} | \sigma) \; p(\sigma) \; p(\theta),
\end{eqnarray}

for rate standard deviation $\sigma$ and other model parameters $\theta$. $\vec{\mathcal{R}}^{\,}$ is a vector of abstracted substitution rates, which is transformed into real rates by $r(\vec{\mathcal{R}}^{\,})$. Three methods of representing rates as $\vec{\mathcal{R}}^{\,}$ are presented in \textbf{\nameref{sect:rateparams}}.

Under the \textit{relaxed clock model}, each internal and leaf node is assigned a substitution rate $r_i = r(\mathcal{R}_i)$, which corresponds to its parent branch. There are a total of $|\vec{\mathcal{R}}^{\,}| = 2N-2$ rates, which are independently distributed under the relaxed clock model prior  \cite{drummond2006relaxed}.

%The substitution rate on branch $i$

\subsection*{Rate parameterisations}
\label{sect:rateparams}

In Bayesian inference, the way parameters are represented in the model can affect the mixing ability of the model and the meaning of the model itself. Three methods for parameterising substitution rates are described below, and are later evaluated in \textbf{\nameref{sect:results}}. Each parameterisation technique is associated with i) an abstraction of the rates $\vec{\mathcal{R}}^{\,}$, ii) some function for transforming this parameter into real rates $r(\vec{\mathcal{R}}^{\,})$, and iii) a prior density function of the abstraction $p(\vec{\mathcal{R}}^{\,} | \sigma) $. The three methods are summarised in \textbf{Fig \ref{fig:rateparams}}.

\begin{figure}[!h]
\includegraphics[width=\textwidth]{Figures/rateparameterisation.pdf}
\caption{\textbf{Methods of rate parameterisation.} The \textit{cat} and \textit{quant} approximations are plotted on top of the true underlying rate prior distribution (\textit{real}). In this example, rates are drawn from a $\text{LogNormal}(\mu = -0.045, \sigma = 0.3)$ distribution. The probability density function (pdf) and cumulative density function (cdf) of this distribution are shown.}
\label{fig:rateparams}
\end{figure}

\subsubsection*{1. Real rates}
The natural (and unabstracted) parameterisation of a substitution rate is a real number $\mathcal{R}_i \in \mathbb{R}, \mathcal{R}_i > 0$ which is equal to the rate itself. Thus, under the \textit{real} parameterisation:

% \vec{\mathcal{R}}^{\,} =& \; \vec{r}^{\,} \\
\begin{align}
r(\vec{\mathcal{R}}^{\,}) =& \; \vec{\mathcal{R}}^{\,}.
\end{align}

Under the prior distribution $p(\vec{\mathcal{R}}^{\,} | \sigma)$, rates are often log-normally or exponentially distributed with a mean of 1:

\begin{align}
p(\mathcal{R}_i | \sigma) = \frac{1}{\mathcal{R}_i \sigma \sqrt{2\pi}} \exp \big( -\frac{(\ln \mathcal{R}_i - \mu)^2}{2\sigma^2} \big) \quad &(\text{ LogNormal}(\mu, \sigma)\;) \text{, or}  \\
p(\mathcal{R}_i | \sigma) = p(\mathcal{R}_i) = e^{-\mathcal{R}_i} \quad &(\text{ Exponential}(\lambda=1)\;)
\end{align}

where $\mu = -0.5\sigma^2$ is set such that the expected value of the log-normal distribution is 1.

Zhang and Drummond 2020 present a series of tree operators which propose internal/root node heights, and then recompute the rates of incident branches such that their genetic distances ($r_i \times \tau_i$) remain constant after the proposal. By maintaining genetic distances the likelihood can also be maintained. These operators account for the correlation which exists between branch rates and branch times -- a correlation which is induced by the likelihood function.

%the correlation between rates and times, as imposed by likelihood function, is r after the proposal , and thus lowers the risk of ``falling o

% Such operators are incompatible with the \textit{cat} parameterisation.  The \textit{real} parameterisation and its associated operators yield a mixing rate up to an order of magnitude faster than that of \textit{cat}. \\

\subsubsection*{2. Categories}
The category parameterisation (\textit{cat}) is an abstraction of the \textit{real} parameterisation. Each branch is assigned an integer from $0$ to $n-1$:

\begin{align}
\vec{\mathcal{R}}^{\,} \in& \{ 0, 1, \dotso, n-1 \}^{2N-2}.
\end{align}

The domain of $\vec{\mathcal{R}}^{\,}$ is uniformly distributed:

\begin{align}
p(\mathcal{R}_i | \sigma) = p(\mathcal{R}_i) = \frac{1}{n}.
\end{align}

Let $f(x|\sigma)$ be the probability density function (pdf) and let $F(x|\sigma) = \int\limits_{0}^{x} f(t|\sigma) \; dt$ be the cumulative distribution function (cdf) of the prior distribution used by the underlying \textit{real} clock model. Then, in the \textit{cat} parameterisation, $f(x|\sigma)$ is discretised into $n$ bins and the elements of $\vec{\mathcal{R}}^{\,}$ each point to one of these bins. Each bin contains uniform probability density $1/n$. The rate of each bin is equal to the median value within the bin

\begin{align}
r(\mathcal{R}_i) =& \; F^{-1}\big(\frac{\mathcal{R}_i + 0.5}{n}\big),
\end{align}

where $F^{-1}$ is the inverse cumulative distribution function (i-cdf).

The key advantage of the \textit{cat} parameterisation is the removal of a term from the posterior density (Equation \ref{eq:bayesian}), or more accurately the replacement of a non-trivial $p(\vec{\mathcal{R}}^{\,} | \sigma)$ term with that of a uniform prior. Thus, one fewer term needs to be estimated per rate.

This method was suggested in the original BEAST2 relaxed clock paper \cite{drummond2006relaxed} and has been widely used. However, the constant distance operators since introduced by Zhang and Drummond 2020 -- which are incompatible with the \textit{cat} parameterisation -- yield an increase in mixing rate under \textit{real} by up to an order of magnitude over that of \textit{cat}.

\subsubsection*{3. Quantiles}

Finally, rates can be parameterised as real numbers $0 < \mathcal{R}_i < 1$ which describe the rate's quantile with respect to some underlying clock model distribution. Under the  \textit{quant} parameterisation, each element in $\vec{\mathcal{R}}^{\,}$ is uniformly distributed.

\begin{align}
\vec{\mathcal{R}}^{\,} \in & \; \mathbb{R}^{2N-2}, 0 < \mathcal{R}_i < 1  \\
p(\mathcal{R}_i | \sigma) = & \; p(\mathcal{R}_i) = 1
\end{align}

Transforming these quantiles into rates invokes the i-cdf of the underlying \textit{real} clock model distribution. Thus, while this approach has clear similarities with \textit{cat}, the domain of rates here is continuous (as opposed to being confined to a discrete number of bins) and is therefore compatible with the class of operators described by Zhang and Drummond 2020.

A potential disadvantage of the \textit{quant} method would be the computational requirements of continuously evaluating the i-cdf, especially for trees with large $N$. Hence, rather than evaluating the exact i-cdf $F^{-1}$, an approximation $\hat{F}^{-1}$ will be used instead:

\begin{align}
r(\mathcal{R}_i) =& \; \hat{F}^{-1}(\mathcal{R}_i).
\end{align}

In this article we have extended \textit{quant} through a linear piecewise approximation of the i-cdf. As the piecewise approximation is linear, evaluating the derivatives $\frac{\partial}{\partial \mathcal{R}_i} \hat{F}^{-1}(\mathcal{R}_i) =  D \hat{F}^{-1}(\mathcal{R}_i)$ and $\frac{\partial}{\partial r_i} \hat{F}(r_i) = D \hat{F}(r_i)$  -- which are required for computing Hastings ratios -- is trivial. The approximation is comprised of $n$ pieces (where $n$ is fixed) and upper and lower rate boundaries $r_\text{min}$ and $r_\text{max}$. The approximation is displayed in \textbf{Fig \ref{fig:rateparams}} and further detailed in \textbf{\nameref{sect:S1Appendix}}.

Zhang and Drummond 2020 introduced several tree operators for the \textit{real} parameterisation -- including \textbf{Constant Distance}, \textbf{Simple Distance}, and \textbf{Small Pulley}. In this project, we extended these three operators so that they are compatible with the \textit{quant} parameterisation. These are presented in \textbf{\nameref{sect:S1Appendix}}.

% REMEMBER to define NNI and SPR acronyms in introduction preferably
\subsection*{Narrow Exchange Rate} \label{sect:NER}

The \textbf{Narrow Exchange} operator \cite{drummond2002estimating}, widely used in BEAST \cite{drummond2012bayesian} and BEAST2 \cite{bouckaert2019beast}, is similar to NNI, and works as follows (\textbf{Fig. \ref{fig:narrowexchange}}):

\textul{\textit{Step 1}}. Sample an internal/root node $E$ from tree $\mathcal{T}$, where $E$ has grandchildren.

\textul{\textit{Step 2}}. Identify the child of $E$ with the greater height. Denote this child as $D$ and its sibling as $C$ (ie. $t_D > t_C$).

\textul{\textit{Step 3}}. Randomly identify the two children of $D$ as $A$ and $B$.

\textul{\textit{Step 4}}. Relocate the $B-D$ branch onto the $C-E$ branch, so that $B$ and $C$ become siblings and their parent is $D$. All node heights are unchanged.

\begin{figure}[!h]
\includegraphics[width=\textwidth]{Figures/NarrowExchange.pdf}
\caption{\textbf{Depiction of Narrow Exchange and Narrow Exchange Rate operators.} Proposals are denoted by $\mathcal{T} \rightarrow \mathcal{T}^\prime$. The vertical axis corresponds to node height $t$. In the bottom figure, branch rates $r$ are indicated by line thickness. In this example, the $\mathcal{D}_{AE}$ and $\mathcal{D}_{CE}$ constraints are satisfied.}
\label{fig:narrowexchange}
\end{figure}

Lakner et al. 2008 \cite{lakner2008efficiency} found that tree operators which perterb topology (such as NNI and SPR) consistently perform better than those which also change branch lengths (such as LOCAL \cite{simon1998local} and Continuous Change \cite{jow2002bayesian}). If Narrow Exchange was adapted to the relaxed clock model by ensuring that genetic distances remain constant after the proposal, its performance may be improved even further.

%Therefore, it seems reasonable to adapt the Narrow Exchange operator for use with the relaxed clock model, such that genetic distances remain constant after performing the proposal $\mathcal{T} \rightarrow \mathcal{T}^\prime$.

Here, we present the \textbf{Narrow Exchange Rate} (NER) operator. Let $r_A$, $r_B$, $r_C$, and $r_D$ be the clock rates of nodes $A$, $B$, $C$, and $D$, respectively. In addition to the modest topological change applied by Narrow Exchange, NER also proposes new clock rates ${r_A}^\prime$, ${r_B}^\prime$, ${r_C}^\prime$, and ${r_D}^\prime$. NER is compatible with both the \textit{real} and \textit{quant} parameterisations. Analagous to the Constant Distance operator, these rates are proposed such that genetic distances between nodes $A$, $B$, $C$, and $E$ are maintained. Thus, there are $\binom{4}{2} = 6$ pairwise distance constraints.

\begin{align}
	\mathcal{D}_{AB}: \quad & r_A  (t_D - t_A) + r_B  (t_D - t_B) = \nonumber \\
					 & {r_A}^\prime  (t_E - t_A) + {r_D}^\prime  (t_E - t_D) + {r_B}^\prime (t_D - t_B) \\
	\mathcal{D}_{AC}: \quad & r_A  (t_D - t_A) + r_D  (t_E - t_D) + r_C  (t_E - t_C) = \nonumber \\
				 	  & {r_A}^\prime  (t_E - t_A) + {r_D}^\prime  (t_E - t_D) + {r_C}^\prime (t_D - t_C) \\
 	\mathcal{D}_{AE}: \quad & r_A  (t_D - t_A) + r_D  (t_E - t_D)= \nonumber \\
					  & {r_A}^\prime  (t_E - t_A) \\
  	\mathcal{D}_{BC}: \quad & r_B  (t_D - t_B) + r_D  (t_E - t_D) + r_C  (t_E - t_D)= \nonumber \\
					  & {r_B}^\prime (t_D - t_B) + {r_C}^\prime (t_D - t_C) \\
   	\mathcal{D}_{BE}: \quad & r_B  (t_D - t_B) + r_D  (t_E - t_D)= \nonumber \\
					  & {r_B}^\prime (t_D - t_B) + {r_D}^\prime (t_E - t_D) \\
	\mathcal{D}_{CE}: \quad & r_C  (t_E - t_C)= \nonumber \\
					  & {r_C}^\prime (t_D - t_C) + {r_D}^\prime (t_E - t_D) 
\end{align}

Further constraints are imposed by the model itself:

\begin{align}
	r_i > 0 \text{ and } {r_i}^\prime > 0 \text { for } i \in \{A,B,C,D\}.
\end{align}

Unfortunately, it is not possible to solve all six $\mathcal{D}_{ij}$ constraints without permitting non-positive rates. Therefore rather than conserving all six pairwise distances, NER conserves a \textit{subset} of distances. It is not immediately clear which distances should be conserved.

\subsubsection*{Automated generation of operators and constraint satisfaction}

The total space of NER operators is comprised of all possible subsets of distance constraints (ie. $\{\},\{\mathcal{D}_{AB}\}, \{\mathcal{D}_{AC}\}, \dotso , \{\mathcal{D}_{AB}, \mathcal{D}_{AC}, \mathcal{D}_{AE}, \mathcal{D}_{BC}, \mathcal{D}_{BE}, \mathcal{D}_{CE} \}$) which are solvable. The simplest NER -- the null operator denoted by NER$\{\}$ -- does not satisfy any distance constraints. This is equivalent to Narrow Exchange.

As it is unclear which NER variants would perform the best, we developed an automated pipeline for generating and testing these operators.

\paragraph{1. Solution finding.} Using standard analytical linear-system solving libraries in MATLAB, the $2^6=64$ subsets of distance constraints are solved. 54 out of the 64 subsets were found to be solvable, and the unsolvables were discarded.

\paragraph{2. Solving Jacobian determinants.} The determinant of the Jacobian matrix $J$ is required for computng the Hastings ratio of the proposal. $J$ is defined as

\begin{align}
	J &= \begin{bmatrix} \frac{\partial {r_A}^\prime}{\partial r_A} & \frac{\partial {r_A}^\prime}{\partial r_B} & \frac{\partial {r_A}^\prime}{\partial r_C} & \frac{\partial {r_A}^\prime}{\partial r_D} \\
	\frac{\partial {r_B}^\prime}{\partial r_A} & \frac{\partial {r_B}^\prime}{\partial r_B} & \frac{\partial {r_B}^\prime}{\partial r_C} & \frac{\partial {r_B}^\prime}{\partial r_D} \\
	\frac{\partial {r_C}^\prime}{\partial r_A} & \frac{\partial {r_C}^\prime}{\partial r_B} & \frac{\partial {r_C}^\prime}{\partial r_C} & \frac{\partial {r_C}^\prime}{\partial r_D} \\
	\frac{\partial {r_D}^\prime}{\partial r_A} & \frac{\partial {r_D}^\prime}{\partial r_B} & \frac{\partial {r_D}^\prime}{\partial r_C} & \frac{\partial {r_D}^\prime}{\partial r_D} \end{bmatrix}.  \nonumber  \\
\end{align}

Computing the determinant $|J|$ invokes standard analytical differentiation and linear algebra libraries of MATLAB. 6 of the 54 operators were found to have $|J|=0$, corresponding to irreversible proposals, and were discarded.

\paragraph{3. Automated generation of BEAST2 operators.} Java class files are generated using string processing. Each class corresponds to a single operator, extends the class of a meta-NER-operator, and is comprised of the solutions found in \textbf{1} and the Jacobian determinant found in \textbf{2}. $|J|$ is further augmented if the \textit{quant} parameterisation is employed.

The 48 operators generated by this pipeline are evaluated and compared in \textbf{\nameref{sect:results}}.

%Each NER variant differs by its a) proposals, which are the solutions found in step \textbf{1}, and b) its Jacobian $|J|$.

%On top of topological changes, NER is comprised of proposals for ${r_A}^\prime$, ${r_B}^\prime$, ${r_C}^\prime$, and ${r_D}^\prime$.

\subsection*{Bactrian proposal kernel} \label{sect:randomwalks}

%The proposal kernel $q(x^\prime|x)$ defines the conditional probability of proposing state $x^\prime$ given state $x$.

The step size of a proposal kernal $q(x^\prime|x)$ should be such that the proposed state $x^\prime$ is sufficiently far from the current state $x$ to explore vast areas of parameter space, but not so large that the proposal is rejected too often. Yang et al. have challenged the widely used uniform proposal kernel in place of the Bactrian kernel \cite{yang2013searching, thawornwattana2018designing}.
The $\text{Bactrian}(m)$ distribution is defined as the sum of two Normal distributions:

\begin{align}
	\alpha \sim \text{Bactrian}(m) \equiv \frac{1}{2}\text{Normal}(-m, 1-m^2) + \frac{1}{2}\text{Normal}(m, 1-m^2)
\end{align}

where $0 \leq m < 1$ describes the modality of the Bactrian distribution. When $m=0$, the Bactrian distribution is equivalent to a $\text{Normal}(0, 1)$ distribution. As $m \rightarrow 1$, the distribution becomes increasingly bimodal (\textbf{Fig. XXX}). Yang et al. 2013 \cite{yang2013searching} suggest that $\text{Bactrian}(m=0.95)$ yields a proposal kernel superior to the uniform kernel by placing minimal probability on step which are too small or too large.

 %The bimodally shaped Bactrian distribution ensures that most step sizes are of an intermediate magnitude.

%In this article we compare the performance the uniform and Bactrian proposal kernels in the clock model.

% Give the equation of the Uniform + Bactrian kernals
% Fig: Bactrian m=0, 0.92, 0.95, 0.98, + Uniform(-1,1)
% In this article we compare the Uniform + Bactrian proposals in the clock model

% BRIEFLY describe three operators: random walk, scale, uniform + where the proposal kernal comes in + which parameters in the clock model it applies to

\begin{table}[h!]
\centering
\begin{tabular}{|l| l l l|} 
 \hline
  &&& \\
 & Operator & Proposal & Parameters  \\
 &&& \\
 1 & \textbf{Random walk operator} & $x^\prime \leftarrow x + w\alpha$ & $t, \sigma, r, q$ \\
 2 & \textbf{Scale operator} & $x^\prime \leftarrow $ & $\sigma, r$  \\
 %3 & \textbf{Uniform operator} & \begin{align} a \\ b \end{align} & $t, q$  \\
 4 & \textbf{Constant distance operators} & $x^\prime \leftarrow x + w\alpha$ & $t$ \\
 5 & \textbf{NER operator} & $x^\prime \leftarrow x + w\alpha$ & $t$ \\
 \hline
\end{tabular}
\caption{Proposal kernels}
\label{table:kernels}
\end{table}

% $x^\prime \leftarrow w \times \frac{u - x}{x - l}$

\subsection*{Clock model averaging}

\section*{Results and Discussion} \label{sect:results}

\subsection*{Assessment criteria and datasets}

To avoid a cross-product explosion, the three targets for clock model improvement (\textbf{\nameref{sect:rateparams}}, \textbf{\nameref{sect:NER}}, and \textbf{\nameref{sect:randomwalks}}) are evaluated sequentially, in the order presented in this paper. The setting(s) which are considered to be the best in each step are then incorporated into the following step. This protocol and its outcomes are summarised in \textbf{Fig. \ref{fig:tournament}}.

\begin{figure}[!h]
\includegraphics[width=\textwidth]{Figures/tournament.pdf}
\caption{\textbf{Protocol for optimising methodology settings.} The three areas (detailed in \textbf{\nameref{sect:models}}) are optimised sequentially, where the best setting from each step is used when optimising the following step.}
\label{fig:tournament}
\end{figure}

Methodologies are assessed according to the following criteria.

\textbf{1. Validation}. This is assessed by measuring the coverage of all estimated parameters in a well-calibrated simulation study, using 100 simulated datasets (with $N=100$ taxa and $L=5000$ nucleotide alignments). These are presented in \textbf{\nameref{sect:WCSS_appendix}}. \\

\textbf{2. Time to convergence}. Two independent MCMC chains are run and the time is measured until: a) the absolute difference in clade posterior probability between the two chains is less than 0.05 for all clades, b) the Rubin-Gelman statistic $\hat{R}$ \cite{gelman1992inference} of every estimated parameter is less than 1.05, and c) the effective sample size \cite{rambaut2013tracer} of every estimated parameter is greater than 100 in each chain. \\

\textbf{3. Mixing of parameters}. Key parameters are evaluated for the number of effective samples generated per hour (ESS/hr). \\

For the latter two criteria, methodologies are benchmarked using 30 empirical datasets compiled and partitioned \cite{lanfear2016partitionfinder} by Lanfear \cite{lanfear2019Github} In order to explore the effects of sequence length, the partitions of each empirical dataset are randomly subsampled at varying sample sizes (\textbf{Table \ref{table:datasets}}). Datasets and BEAST2 .xml templates are provided in the GitHub repository accompanying this article.

Methodologies are benchmarked using an Intel(R) Xeon(R) Gold 6138 CPU (2.00 GHz), with one two-threaded processing unit per pair of MCMC chains.

% https://github.com/roblanf/BenchmarkAlignments
\begin{table}[h!]
\centering
\begin{tabular}{|l| l l l l l|} 
 \hline
  &&&&& \\
 ID & $N$ & $P$ & $L$ (kb) & $L_\text{eff}$ (kb) & Reference \\
 &&&&& \\

 1  &  6  &  1/4/8/16  &  0.4/2.1/10.2/13.7  &  0.1/0.5/1/1.1  &  Richart 2015 \cite{Richart_2016} \\

2  &  10  &  1/4/8/16  &  0.4/1.5/3.1/6.7  &  0.1/0.3/0.5/0.9  &  Crawford 2012 \cite{Crawford_2012} \\

3  &  11  &  1/4/8/16  &  0.5/2.2/4.9/10.1  &  0.1/0.4/0.7/1.3  &  Leache 2015 \cite{Leache_2015} \\

4  &  18  &  1/4/8/16  &  0.4/1.8/2.9/6.7  &  0.1/0.3/0.4/0.9  &  Meiklejohn 2016 \cite{Meiklejohn_2016} \\

5  &  27  &  1/4/8/16  &  0.8/1.4/2/4.3  &  0.3/0.6/1/1.7  &  Faircloth 2013 \cite{Faircloth_2013} \\

6  &  33  &  1/4/8/16  &  0.4/1.7/2.6/5.1  &  0.1/0.5/0.7/1.5  &  McCormack 2013 \cite{McCormack_2013} \\

7  &  38  &  1/4  &  0.4/2.1  &  0.2/0.6  &  Bergsten 2013 \cite{Bergsten_2013} \\

8  &  38  &  1/4/8/16  &  1/2.4/8.1/14.9  &  0.7/1.8/5.6/10.1  &  Ran 2018 \cite{Ran_2018} \\

9  &  41  &  1/3  &  0.4/1.7  &  0.3/1.1  &  Brown 2012 \cite{Brown_2012} \\

10  &  44  &  1/3  &  0.6/1.9  &  0.2/0.8  &  Cognato 2001 \cite{Cognato_2001} \\

11  &  44  &  1/4/7  &  0.8/2.9/5.9  &  0.3/0.8/1.8  &  Dornburg 2012 \cite{Dornburg_2012} \\

12  &  51  &  1/4/6  &  0.6/3.5/5.4  &  0.1/0.9/1.8  &  Sauquet 2011 \cite{Sauquet_2011} \\

13  &  61  &  1/4/8/16  &  0.9/4.2/7.5/15  &  0.7/2.8/4.6/9.6  &  Broughton 2013 \cite{Broughton_2013} \\

14  &  69  &  1/2  &  0.7/0.8  &  0.1/0.1  &  Devitt 2013 \cite{Devitt_2013} \\

15  &  70  &  1/3  &  0.7/2.2  &  0.3/0.9  &  Kawahara 2013 \cite{Kawahara_2013} \\

16  &  78  &  1/4/8/16  &  0.4/1.9/4.1/7.2  &  0.3/1.7/3.6/6.2  &  Cannon 2016 \cite{Cannon_2016} \\

17  &  78  &  1/4/8/16  &  1/2.6/8/14.1  &  0.6/1.7/6.4/10.4  &  Lartillot 2012 \cite{Lartillot_2012} \\

18  &  79  &  1/4/8/16  &  0.1/1.3/0.8/4.5  &  0/0.1/0.1/0.8  &  Oaks 2011 \cite{Oaks_2011} \\

19  &  94  &  1/4/8/11  &  0.1/1.8/3/3.7  &  0.1/0.8/1.3/1.7  &  Rightmyer 2013 \cite{Rightmyer_2013} \\

20  &  106  &  1/4/8/16  &  0.6/3.1/5.1/11.6  &  0.3/1.2/2/4.5  &  Moyle 2016 \cite{Moyle_2016} \\

21  &  110  &  1/4/8/16  &  0.5/2.1/3.8/7.1  &  0.3/1.4/2.5/4.3  &  Fong 2012 \cite{Fong_2012} \\

22  &  145  &  1/2  &  1.6/3  &  0.5/1  &  Anderson 2013 \cite{Anderson_2013} \\

23  &  152  &  1/4/5  &  1/3.5/3.6  &  0.6/1.6/1.6  &  Day 2013 \cite{Day_2013} \\

24  &  187  &  1/4/8/16  &  0.3/0.9/1.4/3.5  &  0.2/0.7/1.1/2.9  &  Branstetter 2017 \cite{Branstetter_2017} \\

25  &  197  &  1/4/8/14  &  0.9/3.1/6.1/11.6  &  0.3/1.6/3.5/6.3  &  Horn 2014 \cite{Horn_2014} \\

26  &  235  &  1/4/8/16  &  2.3/6.4/8.5/25.7  &  0.9/2.3/3.2/12.2  &  Reddy 2017 \cite{Reddy_2017} \\

27  &  237  &  1/4/5  &  0.8/2.4/3.1  &  0.2/1.2/1.5  &  Murray 2013 \cite{Murray_2013} \\

28  &  608  &  1/4/8/10  &  0.9/3.7/7.1/8.6  &  0.7/2.8/5.4/6.4  &  Near 2013 \cite{Near_2013} \\

29  &  1171  &  1/4  &  0.8/3.9  &  0.8/2.4  &  Looney 2016 \cite{Looney_2016} \\

 &&&&& \\
 \hline
\end{tabular}
\caption{Empirical datasets used during benchmarking. Number of taxa $N$, number of partitions $P$, total alignment length $L$, and number of patterns $L_\text{eff}$ are specified. Where a dataset is sampled more than once, the dimensions of its multiple samples are separated by `/'.  }
\label{table:datasets}
\end{table}

\subsection*{Comparison of rate parameterisations}

\subsection*{Comparison of NER variants}

\subsubsection*{Initial screening by acceptance rate}

\subsubsection*{Advanced screening by congergence time}

\subsection*{Comparison of random walk proposals}

\section*{Conclusion}

\section*{Supporting information}

\paragraph*{S1 Appendix.}
\label{sect:S1Appendix}
{\textbf{Rate quantiles.} The linear piecewise approximation used in the \textit{quant} parameterisation is described. Tree operators presented by Zhang and Drummond 2020 are extended to the \textit{quant} parameterisation.

\paragraph*{S2 Appendix.}
\label{sect:WCSS_appendix}
{\textbf{Well-calibated simulation studies.} Methodologies are validated using well-calibated simulation studies.

\nolinenumbers

% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}
%
% or
%
% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here. See http://journals.plos.org/plosone/s/latex for
% step-by-step instructions.
%

\newpage
\bibliography{references}

\end{document}

### 2020-01-23 lognormal.R

@@ -1,0 +1,362 @@
+
+library(tikzDevice)
+
+S = 0.3
+M = -0.5 * S * S
+xmax = 2.5
+
+
+setwd("/home/jdou557/Documents/Marsden2019/Months/January2020/ClockModelPaper/Figures")
+
+
+par(mfrow = c(2,3))
+
+
+
+
+# Categories pdf
+ypts = dlnorm(x, M, S)
+plot(x, ypts , ylim = c(0, max(ypts)*1.2), type = "n", xaxs = "i", yaxs = "i", axes = F, xlab = expression("r"[i]), ylab = "Density",
+main = "cats pdf (10 bins)")
+
+nbins = 10
+cats = 0:(nbins-1)
+bin.cols = "#d3d3d3"
+for (i in cats){
+	
+
+	x0 = qlnorm((i)/nbins, M, S)
+	x1 = qlnorm((i+1)/nbins, M, S)
+	if (i == nbins-1) {
+		x1 = xmax
+	}
+	xmid = qlnorm((i+0.5)/nbins, M, S)
+	y = dlnorm(xmid, M, S)
+
+	rect(x0, 0, x1, y, col = bin.cols, border = "white", lwd = 2) 
+	points(xmid, y, pch = 16, col = cols, cex = 1.5)
+
+
+	text(xmid, y + 0.08, i)
+
+
+}
+
+lines(x, ypts , col = cols, lwd = 3)
+axis(1)
+
+
+
+# Rates pdf
+
+x = seq(from = 0, to = xmax, by = 0.01)
+
+cols = "#008cba"
+plot(x, dlnorm(x, M, S), type = "l", xaxs = "i", col = cols, lwd = 3, yaxs = "i", axes = F, xlab = expression("r"[i]), ylab = "Density",
+main = "real pdf")
+axis(1)
+
+
+
+# Quantiles pdf
+nquant = 10
+qrates = numeric(0)
+for (i in 1:(nquant)){
+
+
+	if (i == 1) {
+		qrates[i] = qlnorm(0.1 / (nquant -1), M, S)
+	}else if (i < nquant) {
+		qrates[i] = qlnorm((i-1) / (nquant -1), M, S)
+	}else{
+		qrates[i] = qlnorm((nquant - 1 - 0.1) / (nquant - 1), M, S)
+	}
+
+}
+
+
+
+quantToRate = function(q) {
+
+	v = q * (nquant-1)
+        i = floor(v)
+	index = i + 1
+	r = qrates[index]
[…]

### 2020-01-23 bactrian.R
Bactrian

@@ -1,0 +1,91 @@
+
+library(tikzDevice)
+
+
+
+setwd("/home/jdou557/Documents/Marsden2019/papers/ClockModelPaper/Figures")
+
+
+filename = "bactrian"
+cols = 1
+rows = 1
+basewidth = 2.5
+
+
+
+options(tikzMetricPackages = c("\\usepackage[utf8]{inputenc}",
+    "\\usepackage[T1]{fontenc}", "\\usetikzlibrary{calc}",
+    "\\usepackage{amssymb}"))
+## I need the amssymb package because I use \mathcal and \mathbb
+	tikz(paste0(filename, ".tex"), width = 1.61*basewidth*cols, height = basewidth*rows, standAlone = TRUE,
+    	packages = c("\\usepackage{tikz}",
+	         "\\usepackage[active,tightpage,psfixbb]{preview}",
+	         "\\PreviewEnvironment{pgfpicture}",
+	         "\\setlength\\PreviewBorder{0pt}",
+	         "\\usepackage{amssymb}"))
+
+
+
+par(mfrow = c(rows, cols), mar = c(4,1,2,1))
+par(las=1)
+#par(cex = 1.0)
+
+
+
+dbactrian = function(x, m){
+
+	
+	s = 1
+	dens = 1 / (2*s*sqrt(2*pi*(1-m^2)))
+	dens = dens * (exp( -(x + m*s)^2 / (2 * (1-m^2)) * s^2 ) + exp( -(x - m*s)^2 / (2 * (1-m^2)) * s^2 ))
+	dens
+}
+
+
+x = seq(from = -3, to = 3, by = 0.001)
+plot(0, 1, xlim = range(x), ylim = c(0,1.1), type = "n", xlab = "$\\alpha$", ylab = "", main = "Bactrian distribution", xaxs = "i", yaxs = "i", axes = F)
+
+
+mvals = c(0.92, 0.95, 0.98)
+
+cols = c("#008cba", "#8cba00", "#ba008c")
+cols = c("#001922", "#006588", "#08c0ff")
+lwds = c(2,2,2)
+ltys = c("solid", "dashed", "dotted")
+ltys = c("solid", "solid", "solid")
+
+
+
+for (i in 1:length(mvals)){
+	m = mvals[i]
+	col = cols[i]
+	lwd = lwds[i]
+	lty = ltys[i]
[…]

### 2020-01-23 lognormal.R

@@ -6,7 +6,7 @@ M = -0.5 * S * S
 xmax = 2.5
 
 
-setwd("/home/jdou557/Documents/Marsden2019/Months/January2020/ClockModelPaper/Figures")
+#setwd("/home/jdou557/Documents/Marsden2019/papers/ClockModelPaper/Figures")
 
 
 par(mfrow = c(2,3))

### 2020-01-27 manuscript.tex
Protocol order rearrangement

@@
 
+\renewcommand{\arraystretch}{1.3}
+
 %% END MACROS SECTION
@@
 
+\subsection*{Bactrian proposal kernel} \label{sect:randomwalks}
+
+%The proposal kernel $q(x^\prime|x)$ defines the conditional probability of proposing state $x^\prime$ given state $x$.
+
+The step size of a proposal kernal $q(x^\prime|x)$ should be such that the proposed state $x^\prime$ is sufficiently far from the current state $x$ to explore vast areas of parameter space, but not so large that the proposal is rejected too often.
+Yang et al.
+have challenged the widely used uniform proposal kernel in place of the Bactrian kernel \cite{yang2013searching, thawornwattana2018designing}.
+The $\text{Bactrian}(m)$ distribution is defined as the sum of two Normal distributions:
+
+\begin{align}
+	\Sigma \sim \text{Bactrian}(m) \equiv \frac{1}{2}\text{Normal}(-m, 1-m^2) + \frac{1}{2}\text{Normal}(m, 1-m^2)
+\end{align}
+
+where $0 \leq m < 1$ describes the modality of the Bactrian distribution.
+When $m=0$, the Bactrian distribution is equivalent to a $\text{Normal}(0, 1)$ distribution.
+As $m \rightarrow 1$, the distribution becomes increasingly bimodal (\textbf{Fig.
+\ref{fig:bactrian}}).
+Yang et al.
+2013 \cite{yang2013searching} suggest that $\text{Bactrian}(m=0.95)$ yields a proposal kernel superior to the uniform kernel, by placing minimal probability on steps which are too small or too large.
+
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{Figures/bactrian.pdf}
+\caption{\textbf{The Bactrian proposal kernel.} Y-axis corresponds to probability density $f(\Sigma|m)$.  }
+\label{fig:bactrian}
+\end{figure}
+
+In this article we compare the performance the uniform and Bactrian proposal kernels in the clock model.
+Three Bactrian distributions are compared($m=0.92$, $m=0.95$, and $m=0.98$).
+The clock model operators which are augmented by the Bactrian distribution are described in \textbf{Table \ref{table:kernels}}.
+
+% Give the equation of the Uniform + Bactrian kernals
+% Fig: Bactrian m=0, 0.92, 0.95, 0.98, + Uniform(-1,1)
+% In this article we compare the Uniform + Bactrian proposals in the clock model
+
+% BRIEFLY describe three operators: random walk, scale, uniform + where the proposal kernal comes in + which parameters in the clock model it applies to
+
+\begin{table}[h!]
+\centering
+\begin{tabular}{|l| l l l|} 
+ \hline
+ & Operator & Proposal & Parameters  \\
+ 1 & \textbf{Random walk operator} & $x^\prime \leftarrow x + s\Sigma$ & $t, \sigma, r, q$ \\
+ 2 & \textbf{Scale operator} & $x^\prime \leftarrow x \times e^{s\Sigma}$ & $\sigma, r$  \\
+ %3 & \textbf{Uniform operator} & $\begin{array} {rl} y &\leftarrow s\Sigma \times \frac{u - x}{x - l} \\ x^\prime &\leftarrow \frac{u + l * y}{y + 1}  \end{array}$ & $t, q$  \\
+ 3 & \textbf{Constant distance operators} & $x^\prime \leftarrow x + s\Sigma$ & $t$ \\
+ \hline
+\end{tabular}
+\caption{Summary of proposal kernels $q(x^\prime|x)$ of clock model operators.
+In each operator, $\Sigma$ is drawn from either a $\text{Noramlised-Bactrian}(m)$ or $\text{Uniform}(-\sqrt{3},\sqrt{3})$ distribution.
+The scale size $s$ is tunable.
+The proposal kernel may apply to node heights $t$, clock standard deviation $\sigma$, clock rates $r$ (\textit{real} only), and clock rate quantiles $q$ (\textit{quant} only).
+The Scale operator acts on parameters with non-negative domains.
+}
+\label{table:kernels}
+\end{table}
+
+% $x^\prime \leftarrow w \times \frac{u - x}{x - l}$
+
+\newpage
 % REMEMBER to define NNI and SPR acronyms in introduction preferably
@@
 2008 \cite{lakner2008efficiency} found that tree operators which perterb topology (such as NNI and SPR) consistently perform better than those which also change branch lengths (such as LOCAL \cite{simon1998local} and Continuous Change \cite{jow2002bayesian}).
-If Narrow Exchange was adapted to the relaxed clock model by ensuring that genetic distances remain constant after the proposal, its performance may be improved even further.
+If Narrow Exchange was adapted to the relaxed clock model by ensuring that genetic distances remain constant after the proposal, its performance may be improved even further, which may in turn permit proposing a new node height $t_D$ and therefore changing branch time lengths (without affecting branch distance lengths).
 
@@
 In addition to the modest topological change applied by Narrow Exchange, NER also proposes new clock rates ${r_A}^\prime$, ${r_B}^\prime$, ${r_C}^\prime$, and ${r_D}^\prime$.
+We also consider a case of the NER operator which proposes a new node height:
+
+\begin{align}
+	{t_D}^\prime \leftarrow t_D + \Sigma
+\end{align}
+
+for random walk step size $\Sigma$ drawn from a uniform or \textbf{\nameref{sect:randomwalks}}.
 NER is compatible with both the \textit{real} and \textit{quant} parameterisations.
@@
 The 48 operators generated by this pipeline are evaluated and compared in \textbf{\nameref{sect:results}}.
+Each operator is considered with and without a random walk on $t_D$ and thus there are 96 total settings.
 
@@
 %On top of topological changes, NER is comprised of proposals for ${r_A}^\prime$, ${r_B}^\prime$, ${r_C}^\prime$, and ${r_D}^\prime$.
-
-\subsection*{Bactrian proposal kernel} \label{sect:randomwalks}
-
-%The proposal kernel $q(x^\prime|x)$ defines the conditional probability of proposing state $x^\prime$ given state $x$.
-
-The step size of a proposal kernal $q(x^\prime|x)$ should be such that the proposed state $x^\prime$ is sufficiently far from the current state $x$ to explore vast areas of parameter space, but not so large that the proposal is rejected too often.
-Yang et al.
-have challenged the widely used uniform proposal kernel in place of the Bactrian kernel \cite{yang2013searching, thawornwattana2018designing}.
-The $\text{Bactrian}(m)$ distribution is defined as the sum of two Normal distributions:
-
-\begin{align}
-	\alpha \sim \text{Bactrian}(m) \equiv \frac{1}{2}\text{Normal}(-m, 1-m^2) + \frac{1}{2}\text{Normal}(m, 1-m^2)
-\end{align}
-
-where $0 \leq m < 1$ describes the modality of the Bactrian distribution.
-When $m=0$, the Bactrian distribution is equivalent to a $\text{Normal}(0, 1)$ distribution.
-As $m \rightarrow 1$, the distribution becomes increasingly bimodal (\textbf{Fig.
-XXX}).
-Yang et al.
-2013 \cite{yang2013searching} suggest that $\text{Bactrian}(m=0.95)$ yields a proposal kernel superior to the uniform kernel by placing minimal probability on step which are too small or too large.
-
- %The bimodally shaped Bactrian distribution ensures that most step sizes are of an intermediate magnitude.
-
-%In this article we compare the performance the uniform and Bactrian proposal kernels in the clock model.
-
-% Give the equation of the Uniform + Bactrian kernals
-% Fig: Bactrian m=0, 0.92, 0.95, 0.98, + Uniform(-1,1)
-% In this article we compare the Uniform + Bactrian proposals in the clock model
-
-% BRIEFLY describe three operators: random walk, scale, uniform + where the proposal kernal comes in + which parameters in the clock model it applies to
-
-\begin{table}[h!]
-\centering
-\begin{tabular}{|l| l l l|} 
- \hline
-  &&& \\
- & Operator & Proposal & Parameters  \\
- &&& \\
- 1 & \textbf{Random walk operator} & $x^\prime \leftarrow x + w\alpha$ & $t, \sigma, r, q$ \\
- 2 & \textbf{Scale operator} & $x^\prime \leftarrow $ & $\sigma, r$  \\
- %3 & \textbf{Uniform operator} & \begin{align} a \\ b \end{align} & $t, q$  \\
- 4 & \textbf{Constant distance operators} & $x^\prime \leftarrow x + w\alpha$ & $t$ \\
- 5 & \textbf{NER operator} & $x^\prime \leftarrow x + w\alpha$ & $t$ \\
- \hline
-\end{tabular}
-\caption{Proposal kernels}
-\label{table:kernels}
-\end{table}
-
-% $x^\prime \leftarrow w \times \frac{u - x}{x - l}$
 
@@
 
-To avoid a cross-product explosion, the three targets for clock model improvement (\textbf{\nameref{sect:rateparams}}, \textbf{\nameref{sect:NER}}, and \textbf{\nameref{sect:randomwalks}}) are evaluated sequentially, in the order presented in this paper.
+To avoid a cross-product explosion, the three targets for clock model improvement (\textbf{\nameref{sect:rateparams}}, \textbf{\nameref{sect:randomwalks}}, and \textbf{\nameref{sect:NER}}) are evaluated sequentially, in the order presented in this paper.
 The setting(s) which are considered to be the best in each step are then incorporated into the following step.
@@
 
-17  &  78  &  1/4/8/16  &  1/2.6/8/14.1  &  0.6/1.7/6.4/10.4  &  Lartillot 2012 \cite{Lartillot_2012} \\
+17  &  79  &  1/4/8/16  &  0.1/1.3/0.8/4.5  &  0/0.1/0.1/0.8  &  Oaks 2011 \cite{Oaks_2011} \\
 
-18  &  79  &  1/4/8/16  &  0.1/1.3/0.8/4.5  &  0/0.1/0.1/0.8  &  Oaks 2011 \cite{Oaks_2011} \\
+18  &  94  &  1/4/8/11  &  0.1/1.8/3/3.7  &  0.1/0.8/1.3/1.7  &  Rightmyer 2013 \cite{Rightmyer_2013} \\
 
-19  &  94  &  1/4/8/11  &  0.1/1.8/3/3.7  &  0.1/0.8/1.3/1.7  &  Rightmyer 2013 \cite{Rightmyer_2013} \\
+19  &  106  &  1/4/8/16  &  0.6/3.1/5.1/11.6  &  0.3/1.2/2/4.5  &  Moyle 2016 \cite{Moyle_2016} \\
 
-20  &  106  &  1/4/8/16  &  0.6/3.1/5.1/11.6  &  0.3/1.2/2/4.5  &  Moyle 2016 \cite{Moyle_2016} \\
+20  &  110  &  1/4/8/16  &  0.5/2.1/3.8/7.1  &  0.3/1.4/2.5/4.3  &  Fong 2012 \cite{Fong_2012} \\
 
-21  &  110  &  1/4/8/16  &  0.5/2.1/3.8/7.1  &  0.3/1.4/2.5/4.3  &  Fong 2012 \cite{Fong_2012} \\
+21  &  152  &  1/4/5  &  1/3.5/3.6  &  0.6/1.6/1.6  &  Day 2013 \cite{Day_2013} \\
 
-22  &  145  &  1/2  &  1.6/3  &  0.5/1  &  Anderson 2013 \cite{Anderson_2013} \\
+22  &  187  &  1/4/8/16  &  0.3/0.9/1.4/3.5  &  0.2/0.7/1.1/2.9  &  Branstetter 2017 \cite{Branstetter_2017} \\
 
-23  &  152  &  1/4/5  &  1/3.5/3.6  &  0.6/1.6/1.6  &  Day 2013 \cite{Day_2013} \\
+23  &  197  &  1/4/8/14  &  0.9/3.1/6.1/11.6  &  0.3/1.6/3.5/6.3  &  Horn 2014 \cite{Horn_2014} \\
 
-24  &  187  &  1/4/8/16  &  0.3/0.9/1.4/3.5  &  0.2/0.7/1.1/2.9  &  Branstetter 2017 \cite{Branstetter_2017} \\
+24  &  235  &  1/4/8/16  &  2.3/6.4/8.5/25.7  &  0.9/2.3/3.2/12.2  &  Reddy 2017 \cite{Reddy_2017} \\
 
-25  &  197  &  1/4/8/14  &  0.9/3.1/6.1/11.6  &  0.3/1.6/3.5/6.3  &  Horn 2014 \cite{Horn_2014} \\
+25  &  237  &  1/4/5  &  0.8/2.4/3.1  &  0.2/1.2/1.5  &  Murray 2013 \cite{Murray_2013} \\
 
-26  &  235  &  1/4/8/16  &  2.3/6.4/8.5/25.7  &  0.9/2.3/3.2/12.2  &  Reddy 2017 \cite{Reddy_2017} \\
-
-27  &  237  &  1/4/5  &  0.8/2.4/3.1  &  0.2/1.2/1.5  &  Murray 2013 \cite{Murray_2013} \\
-
-28  &  608  &  1/4/8/10  &  0.9/3.7/7.1/8.6  &  0.7/2.8/5.4/6.4  &  Near 2013 \cite{Near_2013} \\
-
-29  &  1171  &  1/4  &  0.8/3.9  &  0.8/2.4  &  Looney 2016 \cite{Looney_2016} \\
+26  &  608  &  1/4/8/10  &  0.9/3.7/7.1/8.6  &  0.7/2.8/5.4/6.4  &  Near 2013 \cite{Near_2013} \\
 
@@
 \subsection*{Comparison of rate parameterisations}
+
+We compared the three rate parameterisations described in \textbf{\nameref{sect:rateparams}}.
+All three settings use the standard BEAST2 clock model operators from Drummond et al.
+2006 \cite{drummond2006relaxed}.
+\textit{real} and \textit{quant} additionally use the constant-distance tree operators described by Zhang and Drummond 2020.
+To determine whether the difference in performance between \textit{real}/\textit{quant} versus \textit{cat} is because of the constant-distance tree operators or the parameterisation itself, we also included benchmarked two additional settings: \textit{real 2006} and \textit{quant 2006}, which do not used the constant-distance operators.
+These five settings are validated in \textbf{\nameref{sect:WCSS_appendix}}.
+
+\textbf{Fig.
+\ref{fig:parameterisationResults}} shows that the \textit{real 2006} performs considerably worse than any of the other settings.
+This is due to the poor sampling of the prior under this setting (ie.
+low ESS of $p(\theta)$).
+The failure of \textit{real 2006} thus highlights the appeal of 1) the \textit{cat} or \textit{quant} parameterisations, both of which have trivial contributions to the prior density (ie.
+uniform priors), and 2) the smarter operators used by \textit{real} (Zhang and Drummond 2020).
+Due to its computational burden, \textit{real 2006} was not benchmarked for all of the datasets in \textbf{Table \ref{table:datasets}}.
+
+\begin{figure}[!h]
+%\includegraphics[width=\textwidth]{Figures/tournament.pdf}
+\caption{\textbf{Rate parameterisation evaluation.} }
+\label{fig:parameterisationResults}
+\end{figure}
+
+% 1-3) the \textit{cat}, \textit{real}, and \textit{quant} parameterisations using the operators described by Drummond et al. 2006 \cite{drummond2006relaxed}; 3) the \textit{quant} parameteristion
 

### 2020-01-28 bactrian.R
Tidying paper

@@ -7,7 +7,7 @@ setwd("/home/jdou557/Documents/Marsden2019/papers/ClockModelPaper/Figures")
 
 
 filename = "bactrian"
-cols = 1
+cols = 2
 rows = 1
 basewidth = 2.5
 
@@ -43,7 +43,10 @@ dbactrian = function(x, m){
 
 
 x = seq(from = -3, to = 3, by = 0.001)
-plot(0, 1, xlim = range(x), ylim = c(0,1.1), type = "n", xlab = "$\\alpha$", ylab = "", main = "Bactrian distribution", xaxs = "i", yaxs = "i", axes = F)
+
+
+# Bactrian
+plot(0, 1, xlim = range(x), ylim = c(0,1.1), type = "n", xlab = "$\\Sigma$", ylab = "", main = "Bactrian distribution", xaxs = "i", yaxs = "i", axes = F)
 
 
 mvals = c(0.92, 0.95, 0.98)
@@ -70,6 +73,9 @@ legend("topleft", paste0("$m=", mvals, "$"), col = cols, lwd = lwds, lty = ltys,
 axis(1)
 
 
+
+# Normalised Bactrian
+plot(0, 1, xlim = range(x), ylim = c(0,1.1), type = "n", xlab = "$\\Sigma$", ylab = "", main = "Proposal kernels", xaxs = "i", yaxs = "i", axes = F)
 
 
 

### 2020-01-30 S2_appendix.tex
Interval operator

@@
 \includegraphics[width=0.85\textwidth]{Figures/CalSim_real.pdf}
-\caption{\textbf{The \textit{real} parameterisation,} with the operators decribed by Zhang and Drummond 2020.}
+\caption{\textbf{The \textit{real} parameterisation,} with the operators decribed by Zhang and Drummond 2020. The \textit{real 2006} setting uses a subset of the operators tested in this validation. }
 \label{fig:rateparams}
@@
 \includegraphics[width=0.85\textwidth]{Figures/CalSim_quant.pdf}
-\caption{\textbf{The \textit{quant} parameterisation,} with the operators decribed by Zhang and Drummond 2020, and adapted for \textit{quant} as described in \textbf{S1 Appendix}.}
+\caption{\textbf{The \textit{quant} parameterisation,} with the operators decribed by Zhang and Drummond 2020, and adapted for \textit{quant} as described in \textbf{S1 Appendix}.
+The \textit{quant 2006} setting uses a subset of the operators tested in this validation.}
 \label{fig:rateparams}
+\end{figure}
+
+\begin{figure}[!htb]
+\includegraphics[width=0.85\textwidth]{Figures/CalSim_NER_real.pdf}
+\caption{\textbf{The Narrow Exchange Rate operators under the \textit{real} parameterisation.} The 48 NER and 48 NERw operators, including the null Narrow Exchange operator, are tested in the same MCMC session.}
+\label{fig:rateparams}
+\end{figure}
+
+\begin{figure}[!htb]
+\includegraphics[width=0.85\textwidth]{Figures/CalSim_NER_quant.pdf}
+\caption{\textbf{The Narrow Exchange Rate operators under the \textit{quant} parameterisation.} The 48 NER and 48 NERw operators are tested simultaneously.}
+\label{fig:rateparams}
+\end{figure}
+
+\begin{figure}[!htb]
+%\includegraphics[width=0.85\textwidth]{Figures/CalSim_quant.pdf}
+\caption{\textbf{Bactrian proposal kernel.} A $\text{Bactrian}(0.95)$ proposal kernel is used for all clock model operators, as described in main article.}
 \end{figure}

### 2020-01-30 manuscript.tex
Interval operator

@@
 
-The step size of a proposal kernal $q(x^\prime|x)$ should be such that the proposed state $x^\prime$ is sufficiently far from the current state $x$ to explore vast areas of parameter space, but not so large that the proposal is rejected too often.
+The step size of a proposal kernal $q(x^\prime|x)$ should be such that the proposed state $x^\prime$ is sufficiently far from the current state $x$ to explore vast areas of parameter space, but not so large that the proposal is rejected too often \cite{roberts1997weak}.
 Yang et al.
@@
 
-In this article we compare the performance the uniform and Bactrian proposal kernels in the clock model.
-Three Bactrian distributions are compared($m=0.92$, $m=0.95$, and $m=0.98$).
-The clock model operators which are augmented by the Bactrian distribution are described in \textbf{Table \ref{table:kernels}}.
+In this article we compare the performance of uniform and Bactrian proposal kernels in the clock model.
+Two Bactrian distributions are compared($m=0.95$ and $m=0.98$).
+The clock model operators which these proposal kernels apply to are described in \textbf{Table \ref{table:kernels}}.
 
@@
  & Operator & Proposal & Parameters  \\
- 1 & \textbf{Random walk operator} & $x^\prime \leftarrow x + s\Sigma$ & $t, \sigma, r, q$ \\
+ 1 & \textbf{Random walk operator} & $x^\prime \leftarrow x + s\Sigma$ & $\sigma, r, q$ \\
  2 & \textbf{Scale operator} & $x^\prime \leftarrow x \times e^{s\Sigma}$ & $\sigma, r$  \\
- %3 & \textbf{Uniform operator} & $\begin{array} {rl} y &\leftarrow s\Sigma \times \frac{u - x}{x - l} \\ x^\prime &\leftarrow \frac{u + l * y}{y + 1}  \end{array}$ & $t, q$  \\
- 3 & \textbf{Constant distance operators} & $x^\prime \leftarrow x + s\Sigma$ & $t$ \\
+ 3 & \textbf{Interval operator} & $\begin{array} {rl} y &\leftarrow \frac{u - x}{x - l} \times e^{s\Sigma} \\ x^\prime &\leftarrow \frac{u + l * y}{y + 1}  \end{array}$ & $q \;\; (l=0,u=1)$  \\
+ 4 & \textbf{Constant distance operators} & $x^\prime \leftarrow x + s\Sigma$ & $t$ \\
+
  \hline
@@
 \caption{Summary of proposal kernels $q(x^\prime|x)$ of clock model operators.
-In each operator, $\Sigma$ is drawn from either a $\text{Noramlised-Bactrian}(m)$ or $\text{Uniform}(-\sqrt{3},\sqrt{3})$ distribution.
+In each operator, $\Sigma$ is drawn from either a $\text{Bactrian}(m)$ or $\text{Uniform}$ distribution (distributions are normalised so that they have a mean of 0 and a variance of 1).
 The scale size $s$ is tunable.
@@
 The Scale operator acts on parameters with non-negative domains.
+The Interval operator proposes values which respect its domain ie.
+$l < x^\prime < u$.
 }
@@
 2008 \cite{lakner2008efficiency} found that tree operators which perterb topology (such as NNI and SPR) consistently perform better than those which also change branch lengths (such as LOCAL \cite{simon1998local} and Continuous Change \cite{jow2002bayesian}).
-If Narrow Exchange was adapted to the relaxed clock model by ensuring that genetic distances remain constant after the proposal, its performance may be improved even further, which may in turn permit proposing a new node height $t_D$ and therefore changing branch time lengths (without affecting branch distance lengths).
+If Narrow Exchange was adapted to the relaxed clock model by ensuring that genetic distances remain constant after the proposal, its performance may be improved even further.
+This may in turn permit proposing a new node height $t_D$ and therefore changing branch (time) lengths.
 
@@
 In addition to the modest topological change applied by Narrow Exchange, NER also proposes new clock rates ${r_A}^\prime$, ${r_B}^\prime$, ${r_C}^\prime$, and ${r_D}^\prime$.
-We also consider a case of the NER operator which proposes a new node height:
+While NER does not alter $t_D$ (ie.
+${t_D}^\prime \leftarrow t_D$), we also consider NERw - a special case of the NER operator which embarks $t_D$ on a random walk:
 
 \begin{align}
-	{t_D}^\prime \leftarrow t_D + \Sigma
+	{t_D}^\prime \leftarrow t_D + s\Sigma
 \end{align}
 
-for random walk step size $\Sigma$ drawn from a uniform or \textbf{\nameref{sect:randomwalks}}.
-NER is compatible with both the \textit{real} and \textit{quant} parameterisations.
-Analagous to the Constant Distance operator, these rates are proposed such that genetic distances between nodes $A$, $B$, $C$, and $E$ are maintained.
+for random walk step size $s\Sigma$ where $s$ is a tunable scaler parameter and $\Sigma$ is drawn from a uniform or \textbf{\nameref{sect:randomwalks}}.
+NER (and NERw) are compatible with both the \textit{real} and \textit{quant} parameterisations.
+Analagous to the Constant Distance operator, new rates are proposed such that genetic distances between nodes $A$, $B$, $C$, and $E$ are maintained.
 Thus, there are $\binom{4}{2} = 6$ pairwise distance constraints.
@@
 	\mathcal{D}_{AB}: \quad & r_A  (t_D - t_A) + r_B  (t_D - t_B) = \nonumber \\
-					 & {r_A}^\prime  (t_E - t_A) + {r_D}^\prime  (t_E - t_D) + {r_B}^\prime (t_D - t_B) \\
+					 & {r_A}^\prime  (t_E - t_A) + {r_D}^\prime  (t_E - {t_D}^\prime) + {r_B}^\prime ({t_D}^\prime - t_B) \\
 	\mathcal{D}_{AC}: \quad & r_A  (t_D - t_A) + r_D  (t_E - t_D) + r_C  (t_E - t_C) = \nonumber \\
-				 	  & {r_A}^\prime  (t_E - t_A) + {r_D}^\prime  (t_E - t_D) + {r_C}^\prime (t_D - t_C) \\
+				 	  & {r_A}^\prime  (t_E - t_A) + {r_D}^\prime  (t_E - {t_D}^\prime) + {r_C}^\prime ({t_D}^\prime - t_C) \\
  	\mathcal{D}_{AE}: \quad & r_A  (t_D - t_A) + r_D  (t_E - t_D)= \nonumber \\
@@
   	\mathcal{D}_{BC}: \quad & r_B  (t_D - t_B) + r_D  (t_E - t_D) + r_C  (t_E - t_D)= \nonumber \\
-					  & {r_B}^\prime (t_D - t_B) + {r_C}^\prime (t_D - t_C) \\
+					  & {r_B}^\prime ({t_D}^\prime - t_B) + {r_C}^\prime ({t_D}^\prime - t_C) \\
    	\mathcal{D}_{BE}: \quad & r_B  (t_D - t_B) + r_D  (t_E - t_D)= \nonumber \\
-					  & {r_B}^\prime (t_D - t_B) + {r_D}^\prime (t_E - t_D) \\
+					  & {r_B}^\prime ({t_D}^\prime - t_B) + {r_D}^\prime (t_E - {t_D}^\prime) \\
 	\mathcal{D}_{CE}: \quad & r_C  (t_E - t_C)= \nonumber \\
-					  & {r_C}^\prime (t_D - t_C) + {r_D}^\prime (t_E - t_D) 
+					  & {r_C}^\prime ({t_D}^\prime - t_C) + {r_D}^\prime (t_E - {t_D}^\prime) 
 \end{align}
@@
 \begin{align}
-	r_i > 0 \text{ and } {r_i}^\prime > 0 \text { for } i \in \{A,B,C,D\}.
+	r_i > 0 \text{ and } {r_i}^\prime > 0 \text { for } i \in \{A,B,C,D\} \\
+	\max\{t_B, t_C \} < {t_D}^\prime < t_E.
 \end{align}
 
-Unfortunately, it is not possible to solve all six $\mathcal{D}_{ij}$ constraints without permitting non-positive rates.
+Unfortunately, it is not possible to solve all six $\mathcal{D}_{ij}$ constraints without permitting non-positive rates or illegal trees.
 Therefore rather than conserving all six pairwise distances, NER conserves a \textit{subset} of distances.
@@
 
+% Cite HKY somewhere hasegawa1985dating
+
 To avoid a cross-product explosion, the three targets for clock model improvement (\textbf{\nameref{sect:rateparams}}, \textbf{\nameref{sect:randomwalks}}, and \textbf{\nameref{sect:NER}}) are evaluated sequentially, in the order presented in this paper.
@@
 
-For the latter two criteria, methodologies are benchmarked using 30 empirical datasets compiled and partitioned \cite{lanfear2016partitionfinder} by Lanfear \cite{lanfear2019Github} In order to explore the effects of sequence length, the partitions of each empirical dataset are randomly subsampled at varying sample sizes (\textbf{Table \ref{table:datasets}}).
+For the latter two criteria, methodologies are benchmarked using 25 empirical datasets compiled and partitioned \cite{lanfear2016partitionfinder} by Lanfear \cite{lanfear2019Github} In order to explore the effects of sequence length, the partitions of each empirical dataset are randomly subsampled at varying sample sizes (\textbf{Table \ref{table:datasets}}).
 Datasets and BEAST2 .xml templates are provided in the GitHub repository accompanying this article.
@@
  \hline
-  &&&&& \\
- ID & $N$ & $P$ & $L$ (kb) & $L_\text{eff}$ (kb) & Reference \\
- &&&&& \\
+  & $N$ & $P$ & $L$ (kb) & $L_\text{eff}$ (kb) & Ref. \\
 
@@
 
-26  &  608  &  1/4/8/10  &  0.9/3.7/7.1/8.6  &  0.7/2.8/5.4/6.4  &  Near 2013 \cite{Near_2013} \\
-
- &&&&& \\
  \hline

### 2020-01-31 S2_appendix.tex
Benchmarking

@@
 \begin{figure}[!htb]
+\includegraphics[width=0.85\textwidth]{Figures/CalSim_bactrian95.pdf}
+\caption{\textbf{Bactrian proposal kernel.} A $\text{Bactrian}(0.95)$ proposal kernel is used for all clock model operators (under \textit{quant}), as described in main article.}
+\end{figure}
+
+\begin{figure}[!htb]
 \includegraphics[width=0.85\textwidth]{Figures/CalSim_NER_real.pdf}
@@
 
-\begin{figure}[!htb]
-%\includegraphics[width=0.85\textwidth]{Figures/CalSim_quant.pdf}
-\caption{\textbf{Bactrian proposal kernel.} A $\text{Bactrian}(0.95)$ proposal kernel is used for all clock model operators, as described in main article.}
-\end{figure}
-
 \bibliography{references}

### 2020-02-04 manuscript.tex
NER results

@@
 
-For the latter two criteria, methodologies are benchmarked using 25 empirical datasets compiled and partitioned \cite{lanfear2016partitionfinder} by Lanfear \cite{lanfear2019Github} In order to explore the effects of sequence length, the partitions of each empirical dataset are randomly subsampled at varying sample sizes (\textbf{Table \ref{table:datasets}}).
+For the latter two criteria, methodologies are benchmarked using the empirical datasets compiled and partitioned \cite{lanfear2016partitionfinder} by Lanfear \cite{lanfear2019Github}.
+Two datasets (the turtle data by Crawford et al.
+2012 \cite{Crawford_2012}; and the songbird data by Moyle et al.
+2016 \cite{Moyle_2016}) are used during the optimisation stage, where each setting is run $15 \times$ and the average statistics across the $15 \times 2 = 30$ chains are reported.
+All 25 datasets presented in \textbf{Table \ref{table:datasets}} are benchmarked together $1 \times$ each at the end of the protocol.
 Datasets and BEAST2 .xml templates are provided in the GitHub repository accompanying this article.
 
-Methodologies are benchmarked using an Intel(R) Xeon(R) Gold 6138 CPU (2.00 GHz), with one two-threaded processing unit per pair of MCMC chains.
+Methodologies are benchmarked using the Intel(R) Xeon(R) Gold 6138 CPU (2.00 GHz), with two processing units per pair of MCMC chains.
 
@@
 
-2  &  10  &  1/4/8/16  &  0.4/1.5/3.1/6.7  &  0.1/0.3/0.5/0.9  &  Crawford 2012 \cite{Crawford_2012} \\
+\textbf{2}  &  \textbf{10}  &  1/4/8/\textbf{16}  &  0.4/1.5/3.1/\textbf{6.7}  &  0.1/0.3/0.5/\textbf{0.9}  &  \textbf{Crawford 2012} \cite{Crawford_2012} \\
 
@@
 
-19  &  106  &  1/4/8/16  &  0.6/3.1/5.1/11.6  &  0.3/1.2/2/4.5  &  Moyle 2016 \cite{Moyle_2016} \\
+\textbf{19}  &  \textbf{106}  &  1/\textbf{4}/8/16  &  0.6/\textbf{3.1}/5.1/11.6  &  0.3/\textbf{1.2}/2/4.5  &  \textbf{Moyle 2016} \cite{Moyle_2016} \\
 
@@
 \end{tabular}
-\caption{Empirical datasets used during benchmarking.
-Number of taxa $N$, number of partitions $P$, total alignment length $L$, and number of patterns $L_\text{eff}$ are specified.
+\caption{Empirical datasets used during benchmarking, sorted in increasing order of taxa count $N$.
+Number of partitions $P$, total alignment length $L$, and number of patterns $L_\text{eff}$ are also specified.
 Where a dataset is sampled more than once, the dimensions of its multiple samples are separated by `/'.
+The datasets in bold (Crawford \cite{Crawford_2012} and Moyle \cite{Moyle_2016}) are used during the optimisation protocol.
 }
@@
 
+%Our results are also consistent with Zhang and Drummond 2020, who found that \textit{real} (with constant distance operators) gives superior mixing of rates compared with \textit{cat}.
+
+Our results show that the \textit{quant} parameterisation yields the best performance with respect to effective samples per hour.
+\textit{quant} outperforms \textit{quant 2006}, suggesting that the constant distance operators are effective.
+Furthermore, \textit{quant} outperforms \textit{real} especially at sampling from the posterior and prior distributions (ie.
+high ESS/hr for $p(\theta|D)$ and $p(\theta)$).
+This is most likely because of the uniform prior distribution of rate quantiles.
+
+Overall, \textit{quant} yields a median ESS/hr approximately 150 \% faster with respect to sampling the posterior probability, and approximately 30 \% faster with respect to sampling branch rates $r$ and clock standard deviation $\sigma$, compared with \textit{real}.
+
+%\text{cat} and \textit{quant 2006} parameterisations yield similar effective samples per hour for all parameters (including posterior, likelihood, and prior probabilities).
+
 \begin{figure}[!h]
-%\includegraphics[width=\textwidth]{Figures/tournament.pdf}
-\caption{\textbf{Rate parameterisation evaluation.} }
+\includegraphics[width=\textwidth]{Figures/ESS.pdf}
+\caption{\textbf{Rate parameterisation evaluation.} Comparison of ESS/hr (averaged across two independent MCMC chains) with respect to relevant terms -- $L$: likelihood, $p$: prior density, $r$: clock rate averaged across all leaves, $\sigma$: clock standard deviation.
+Each point is from one partition sample of the empirical data in \textbf{Table \ref{table:datasets}}.
+}
 \label{fig:parameterisationResults}
@@
 
+\subsection*{Comparison of Bactrian and uniform proposal kernels on the clock model}
+
 \subsection*{Comparison of NER variants}
+
+We compared the Narrrow Exchange Rate (NER) operators described in \textbf{\nameref{sect:NER}}.
+This protocol selects the best among 48 NER (no random walk) and 48 NERw ($\text{Bactrian}(0.95)$ random walk) operators, and has two phases.
+First, the best of the 96 is selected by comparing operator acceptance rates on simulated data.
+Second, the selected operator is benchmarked with respect to convergence time and sampling rate on real data (\textbf{Table \ref{table:datasets}}).
+All the analyses in this section invoke the \textit{quant} parameterisation and $\text{Bactrian}(0.95)$ proposal kernels on clock model parameters.
 
@@
 
+We selected the best operator variant by performing MCMC on 100 simulated datasets, where each MCMC employed all 96 NER/NERw variants.
+The acceptance rate of each operator is compared to that of the null operator $\text{NER}\{\}$ (ie.
+Narrow Exchange).
+
+\textbf{Fig.
+\ref{fig:acceptanceRateScreening}} shows that NER variants which satisfy the genetic distances between nodes $B$ and $A$ (ie.
+$\mathcal{D}_{AB}$) or between $B$ and $C$ (ie.
+$\mathcal{D}_{BC}$) consistently perform worse than the standard Narrow Exchange operator, where $B$ is the node being interchanged from the $A$ branch to the $C$ branch (\textbf{Fig.
+\ref{fig:narrowexchange}}).
+This is an intuitive result.
+If the posterior distribution is relatively flat, and the data presents high uncertainty in the positioning of $B$, with respect to $A$ and $C$, then the topological rearrangement performed by Narrow Exchange will be favoured.
+However, this uncertainty in the \textit{topology} is likely coupled with uncertainty in the \textit{distance} between $B$ and $A$ or between $B$ and $C$.
+Thus, in this case, respecting the $\mathcal{D}_{AB}$ and $\mathcal{D}_{BC}$ constraints (by proposing branch rates) makes too many unnecessary changes to the state and the operator performs worse.
+
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{Figures/acceptanceRates.pdf}
+\caption{\textbf{Screening of NER and NERw variants by acceptance rate.} Left: comparison of NER variants with the null operator $\text{NER}\{\}$ (ie.
+Narrow Exchange).
+Each of the 48 operators are represented by a single point, uniquely encoded by the point stylings.
+The number of times each operator is proposed and accepted is compared with that of $\text{NER}\{\}$, and a Z-test is performed to determine whether there is a significant difference in the two acceptance rates.
+This process is repeated for each of $100$ simulated datasets.
+The axes of each plot are the proportion of these $100$ simulations for which there is significant evidence that the operator is better than $\text{NER}\{\}$ (x-axis) or worse than $\text{NER}\{\}$ (y-axis).
+Right: comparison of NER with NERw.
+Each point is one NER/NERw variant from a single simulation.
+This plot shows that the random walk hinders the acceptance rates of all NER variants, including $\text{NER}\{\}$.
+}
+\label{fig:acceptanceRateScreening}
+\end{figure}
+
+\textbf{Fig.
+\ref{fig:acceptanceRateScreening}} also reveals a cluster of NER variants which -- under the conditions of the simulation --  performed better than the null operator $\text{NER}\{\}$ around 10\% of the time and performed worse around 40\% of the time.
+One such operator is  $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$.
+This variant conserves the genetic distance between all child nodes $A$, $B$, and $C$, and the grandparent node $E$.
+This is performed by proposing rates for $r_A$, $r_B$, and $r_C$ while obeying the distance constraints imposed by the operator.
+Exploring this operator further, we can see that $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ is at its best when there is a large variance in branch rate ie.
+when clock standard deviation $\sigma$ is high ($\sigma \gtrsim 0.3$), corresponding to data which is not clock-like.
+On the other hand, $\text{NER}\{\}$ is much preferred when the operator's acceptance rate is high ($\gtrsim 0.15$), which corresponds to poorer signal in the data.
+Overall, $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ outperforms the standard Narrow Exchange operator provided that the data is not clock-like and contains strong signal.
+
+Finally, \textbf{Fig.
+\ref{fig:acceptanceRateScreening}} shows that by applying a (Bactrian) random walk to $t_D$ -- the height of internal node $D$ -- the acceptance rate of NER plummets dramatically.
+This effect is most dominant for the NER variants which satisfy distance constraints (ie.
+the operators which are not $\text{NER}\{\}$).
+This result is unfortunate however not unexpected, and is consistent with Lakner et al.
+2008 \cite{lakner2008efficiency}, who observed that tree operators perform best when they change either topology, or branch lengths, but not both.
+
+Although there are several operators tying for first place, we selected the $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ operator to proceed to the next round of optimisation.
+
 \subsubsection*{Advanced screening by congergence time}
-
-\subsection*{Comparison of random walk proposals}
 
@@
 
+\newpage
 \section*{Supporting information}

### 2020-02-11 manuscript.tex
Benchmark new set

@@
 Time to convergence}.
-Two independent MCMC chains are run and the time is measured until: a) the absolute difference in clade posterior probability between the two chains is less than 0.05 for all clades, b) the Rubin-Gelman statistic $\hat{R}$ \cite{gelman1992inference} of every estimated parameter is less than 1.05, and c) the effective sample size \cite{rambaut2013tracer} of every estimated parameter is greater than 100 in each chain.
+Two independent MCMC chains are run and the time is measured until: a) the absolute difference in clade posterior probability between the two chains is less than 0.05 for all clades, b) the Rubin-Gelman statistic $\hat{R}$ \cite{gelman1992inference} of every estimated parameter is less than 1.05, and c) the effective sample size \cite{rambaut2018posterior} of every estimated parameter is greater than 100 in each chain.
 \\
@@
 For the latter two criteria, methodologies are benchmarked using the empirical datasets compiled and partitioned \cite{lanfear2016partitionfinder} by Lanfear \cite{lanfear2019Github}.
-Two datasets (the turtle data by Crawford et al.
-2012 \cite{Crawford_2012}; and the songbird data by Moyle et al.
-2016 \cite{Moyle_2016}) are used during the optimisation stage, where each setting is run $15 \times$ and the average statistics across the $15 \times 2 = 30$ chains are reported.
+Four datasets (the spider data by Richart et al.
+2015 \cite{Richart_2016}; the turtle data by Crawford et al.
+2012 \cite{Crawford_2012}; the caterpillar dataset by Kawahara et al.
+2013 \cite{Kawahara_2013}; and the songbird data by Moyle et al.
+2016 \cite{Moyle_2016}) are used during the optimisation stage, where each setting is run $10 \times$ and the average statistics across the $10 \times 2 = 20$ chains are reported.
 All 25 datasets presented in \textbf{Table \ref{table:datasets}} are benchmarked together $1 \times$ each at the end of the protocol.
@@
 
- 1  &  6  &  1/4/8/16  &  0.4/2.1/10.2/13.7  &  0.1/0.5/1/1.1  &  Richart 2015 \cite{Richart_2016} \\
+\textbf{1}  &  \textbf{6}  &  1/4/8/\textbf{16}  &  0.4/2.1/10.2/\textbf{13.7}  &  0.1/0.5/1/\textbf{1.1}  &  \textbf{Richart 2015} \cite{Richart_2016} \\
 
@@
 
-15  &  70  &  1/3  &  0.7/2.2  &  0.3/0.9  &  Kawahara 2013 \cite{Kawahara_2013} \\
+\textbf{15}  &  \textbf{70}  &  1/\textbf{3}  &  0.7/\textbf{2.2}  &  0.3/\textbf{0.9}  &  \textbf{Kawahara 2013} \cite{Kawahara_2013} \\
 
@@
 
-\textbf{19}  &  \textbf{106}  &  1/\textbf{4}/8/16  &  0.6/\textbf{3.1}/5.1/11.6  &  0.3/\textbf{1.2}/2/4.5  &  \textbf{Moyle 2016} \cite{Moyle_2016} \\
+\textbf{19}  &  \textbf{106}  &  \textbf{1}/4/8/16  &  \textbf{0.6}/3.1/5.1/11.6  &  \textbf{0.3}/1.2/2/4.5  &  \textbf{Moyle 2016} \cite{Moyle_2016} \\
 
@@
 Where a dataset is sampled more than once, the dimensions of its multiple samples are separated by `/'.
-The datasets in bold (Crawford \cite{Crawford_2012} and Moyle \cite{Moyle_2016}) are used during the optimisation protocol.
+The datasets in bold (Richart 2015 \cite{Richart_2016}, Crawford \cite{Crawford_2012}, Kawahara \cite{Kawahara_2013}, and Moyle \cite{Moyle_2016}) are used during the optimisation protocol.
 }
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{Figures/ESS.pdf}
+%\includegraphics[width=\textwidth]{Figures/ESS.pdf}
 \caption{\textbf{Rate parameterisation evaluation.} Comparison of ESS/hr (averaged across two independent MCMC chains) with respect to relevant terms -- $L$: likelihood, $p$: prior density, $r$: clock rate averaged across all leaves, $\sigma$: clock standard deviation.
@@
 
-We selected the best operator variant by performing MCMC on 100 simulated datasets, where each MCMC employed all 96 NER/NERw variants.
+We selected the best operator variant by performing MCMC on 300 simulated datasets, where each MCMC employed all 96 NER/NERw variants.
+Simulated datasets have $N=30$ taxa and an alignment with $L \sim \text{Uniform}(10^2, 10^4)$ sites.
 The acceptance rate of each operator is compared to that of the null operator $\text{NER}\{\}$ (ie.
@@
 $\mathcal{D}_{AB}$) or between $B$ and $C$ (ie.
-$\mathcal{D}_{BC}$) consistently perform worse than the standard Narrow Exchange operator, where $B$ is the node being interchanged from the $A$ branch to the $C$ branch (\textbf{Fig.
+$\mathcal{D}_{BC}$) usually perform worse than the standard Narrow Exchange operator, where $B$ is the node being interchanged from the $A$ branch to the $C$ branch (\textbf{Fig.
 \ref{fig:narrowexchange}}).
@@
 \includegraphics[width=\textwidth]{Figures/acceptanceRates.pdf}
-\caption{\textbf{Screening of NER and NERw variants by acceptance rate.} Left: comparison of NER variants with the null operator $\text{NER}\{\}$ (ie.
+\caption{\textbf{Screening of NER and NERw variants by acceptance rate.} Top left: comparison of NER variants with the null operator $\text{NER}\{\}$ (ie.
 Narrow Exchange).
 Each of the 48 operators are represented by a single point, uniquely encoded by the point stylings.
-The number of times each operator is proposed and accepted is compared with that of $\text{NER}\{\}$, and a Z-test is performed to determine whether there is a significant difference in the two acceptance rates.
-This process is repeated for each of $100$ simulated datasets.
-The axes of each plot are the proportion of these $100$ simulations for which there is significant evidence that the operator is better than $\text{NER}\{\}$ (x-axis) or worse than $\text{NER}\{\}$ (y-axis).
-Right: comparison of NER with NERw.
+The number of times each operator is proposed and accepted is compared with that of $\text{NER}\{\}$, and one-sided z-tests are performed to assess the statistical significance between the two acceptance rates ($p = 0.001$).
+This process is repeated for each of $300$ simulated datasets.
+The axes of each plot are the proportion of these $300$ simulations for which there is evidence that the operator is better than $\text{NER}\{\}$ (x-axis) or worse than $\text{NER}\{\}$ (y-axis).
+Top right: comparison of NER and NERw acceptance rates.
 Each point is one NER/NERw variant from a single simulation.
-This plot shows that the random walk hinders the acceptance rates of all NER variants, including $\text{NER}\{\}$.
+Bottom: relationship between the acceptance rates $\alpha$ of $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ and $\text{NER}\{ \}$ with the clock model standard deviation $\sigma$ and the number of patterns $L_\textit{eff}$.
+Each point is a single simulation.
 }
@@
 \textbf{Fig.
-\ref{fig:acceptanceRateScreening}} also reveals a cluster of NER variants which -- under the conditions of the simulation --  performed better than the null operator $\text{NER}\{\}$ around 10\% of the time and performed worse around 40\% of the time.
+\ref{fig:acceptanceRateScreening}} also reveals a cluster of NER variants which -- under the conditions of the simulation --  performed better than the null operator $\text{NER}\{\}$ around 25\% of the time and performed worse around 10\% of the time.
 One such operator is  $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$.
@@
 Exploring this operator further, we can see that $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ is at its best when there is a large variance in branch rate ie.
-when clock standard deviation $\sigma$ is high ($\sigma \gtrsim 0.3$), corresponding to data which is not clock-like.
-On the other hand, $\text{NER}\{\}$ is much preferred when the operator's acceptance rate is high ($\gtrsim 0.15$), which corresponds to poorer signal in the data.
-Overall, $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ outperforms the standard Narrow Exchange operator provided that the data is not clock-like and contains strong signal.
+when clock standard deviation $\sigma$ is high ($\sigma \gtrsim 0.5$ for $N=30$), corresponding to data which is not clock-like.
+On the other hand, $\text{NER}\{\}$ is much preferred when the operator's acceptance rate is high ($\gtrsim 0.15$) -- corresponding with datasets with a small number of site patterns ($L_\textit{eff} \lesssim 500$ for $N=30$) and thus poor signal.
+Overall, $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ outperforms the standard Narrow Exchange operator when the data is not clock-like and contains enough signal.
 
@@
 
-\subsubsection*{Advanced screening by congergence time}
+\subsubsection*{Benchmarking convergence time}
 

### 2020-02-13 lognormal.R
Updated benchmark table

@@ -1,7 +1,7 @@
 
 library(tikzDevice)
 
-S = 0.3
+S = 0.01
 M = -0.5 * S * S
 xmax = 2.5
 
@@ -352,6 +352,82 @@ dev.off()
 
 tools::texi2pdf(paste0(filename, ".tex"))
 system(paste(getOption("pdfviewer"), paste0(filename, ".pdf")))
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+plot(0, 0, type = "n", xlim = c(0, 1000), ylim = c(0, 5), xlab = "n pieces", ylab = "range of rates")
+
+
+for (S in c(0.01, 0.1, 0.5)) {
+
+
+	x = numeric(0)
+	yl = numeric(0)
+	yu = numeric(0)
+	for (nn in seq(from = 10, to = 1000, by = 10)) {
+
+		#
+		nquant = nn
+		qrates = numeric(0)
+		for (i in 1:(nquant)){
+
+
+			if (i == 1) {
+				qrates[i] = qlnorm(0.1 / (nquant -1), M, S)
+			}else if (i < nquant) {
+				qrates[i] = qlnorm((i-1) / (nquant -1), M, S)
+			}else{
+				qrates[i] = qlnorm((nquant - 1 - 0.1) / (nquant - 1), M, S)
+			}
+
+		}
+
+
+		rmin_y = 0.09 / (nquant-1)
+		rmax_y = (nquant-1-0.09) / (nquant-1)
+		rmin_x = quantToRate(rmin_y)
+		rmax_x = quantToRate(rmax_y)
+
+		#print(paste0(nn, ": (", round(rmin_x, 3), ", ", round(rmax_x, 3), ")"))
+		x = c(x, nquant)
+		yu = c(yu, rmax_x)
+		yl = c(yl, rmin_x)
+
+
+	}
+
+
+	polygon( c(0, x, rev(x), 0), c(1, yu, rev(yl), 1))
+
+
+
+}
+
+abline(1, 0)
+grid()
+
+
+
+
+
+
+
+
+
 
 
 

### 2020-03-02 manuscript.tex
AVMVN

@@
 
-In Bayesian inference, the way parameters are represented in the model can affect the mixing ability of the model and the meaning of the model itself.
+In Bayesian inference, the way parameters are represented in the model can affect the mixing ability of the model and the meaning of the model itself \cite{gelman2004parameterization}.
 Three methods for parameterising substitution rates are described below, and are later evaluated in \textbf{\nameref{sect:results}}.
@@
 
+\subsection*{A guided adaptive leaf rate operator}
+
+A \textit{guided} operator incorporates knowledge about neighbouring states, while an \textit{adaptive} operator undergoes a training process to improve its efficiency over time \cite{roberts2007coupling}.
+In previous work, parsimony scores and conditional clade probabilities of neighbouring trees have been employed by guided tree operators \cite{hohna2012guided,zhang2019using,meyer2019adaptive} and the latter has also been explored as the basis of  adaptive tree operators \cite{hohna2012guided,meyer2019adaptive}.
+The (adaptive) mirror kernel \cite{thawornwattana2018designing} learns a target distribution which acts as a `mirror image' of the current point $x$.
+The adaptable variance multivariate normal (AVMVN) kernel \cite{baele2017adaptive,suchard2018bayesian} learns correlations between parameters during MCMC.
+Baele et al.
+2017  observed a large increase ($\approx 5-10 \times$) in sampling efficiency from using the AVMVN kernel on clock rates and substitution model parameters across partitions \cite{baele2017adaptive}.
+
+In this article we consider application of the AVMVN kernel to the branch rates of leaf nodes.
+This operator is not readily applicable to internal node branch rates due to their dependency on the topology of the tree.
+
+\subsubsection*{AVMVN kernel}
+\label{AVMVN_sect}
+
+The AVMVN kernel assumes its parameters live in $x \in \mathbb{R}^N$ and that these parameters follow a multivariate normal distribution with covariance matrix $\Sigma_N$.
+Hence, the kernel operates on the logarithmic or logistic transformation of the $N$ leaf branch rates, depending on the rate parameterisation:
+
+\begin{align}
+	x_i = \begin{cases} \log r_i \text{ for } \textit{real} \\
+						\log \frac{q_i}{1 - q_i} \text{ for } \textit{quant}  \end{cases}
+\end{align}
+
+where $r_i$ is a real rate and $q_i$ is a rate quantile. The AVMVN probability density is defined by
+
+\begin{align}
+	\mathcal{AVMVN}(x) = (1-\beta) \mathcal{MVN}\big(x, \frac{\Sigma_N}{N} \big) + \beta \mathcal{MVN}\big(x, \frac{\mathbb{I}_N}{N} \big),
+\end{align}
+
+where $\mathcal{MVN}$ is the multivariate normal probability density.
+$\beta \; (= 0.05)$ is a constant which determines the fraction of the proposal determined by the identity matrix ${I}_N$, as opposed to the covariance matrix $\Sigma_D$ which is trained during MCMC.
+
+The AVMVN proposal kernel is computed as
+
+\begin{align}
+	& x^\prime \leftarrow x + \sum\limits_{i=1}^N \sum\limits_{j=i}^N c_{i,j} \times s\Sigma \\
+	\text {where } & c = \texttt{cholesky} \{ (1-\beta) \frac{\Sigma_N}{N} + \beta \frac{\mathbb{I}_N}{N} \}.
+\end{align}
+
+The \texttt{cholesky}$\{Y\}$ decomposition returns a lower diagonal matrix $L$, with positive real diagonal entries, such that $Y = LL^\prime$ \cite{lindstrom1988newton, pourahmadi2007cholesky}.
+$s$ is a tunable step size parameter and $\Sigma$ is a random variable drawn from a proposal kernel (uniform or Bactrian for instance).
+Our BEAST2 implementation of the AVMVN kernel is adapted from that of BEAST \cite{suchard2018bayesian}.
+
+In \nameref{sect:results}, we evaluate this operator for its ability to estimate leaf rates.
+As the size of the covariance matrix $\Sigma_N$ grows with the number of taxa $N$, AVMVN is hypothesised to work well on small trees but become less efficient with larger taxon sets.
+
 \subsection*{Clock model averaging}
@@
 Time to convergence}.
-Two independent MCMC chains are run and the time is measured until: a) the absolute difference in clade posterior probability between the two chains is less than 0.05 for all clades, b) the Rubin-Gelman statistic $\hat{R}$ \cite{gelman1992inference} of every estimated parameter is less than 1.05, and c) the effective sample size \cite{rambaut2018posterior} of every estimated parameter is greater than 100 in each chain.
+Two independent MCMC chains are run and the time is measured until: a) the absolute difference in clade posterior probability between the two chains is less than 0.05 for all clades, b) the Rubin-Gelman statistic $\hat{R}$ \cite{gelman1992inference} of every estimated parameter is less than 1.05, and c) the effective sample size \cite{rambaut2018posterior} of every estimated parameter is greater than 200 in each chain.
 \\
@@
 
-For the latter two criteria, methodologies are benchmarked using the empirical datasets compiled and partitioned \cite{lanfear2016partitionfinder} by Lanfear \cite{lanfear2019Github}.
-Four datasets (the spider data by Richart et al.
-2015 \cite{Richart_2016}; the turtle data by Crawford et al.
-2012 \cite{Crawford_2012}; the caterpillar dataset by Kawahara et al.
-2013 \cite{Kawahara_2013}; and the songbird data by Moyle et al.
-2016 \cite{Moyle_2016}) are used during the optimisation stage, where each setting is run $10 \times$ and the average statistics across the $10 \times 2 = 20$ chains are reported.
-All 25 datasets presented in \textbf{Table \ref{table:datasets}} are benchmarked together $1 \times$ each at the end of the protocol.
+For the latter two criteria, methodologies are benchmarked using both simulated and empirical datasets -- the latter were compiled \cite{lanfear2019Github} and partitioned \cite{lanfear2016partitionfinder} by Lanfear et al.
+as `benchmark alignments' (\textbf{Table \ref{table:datasets}}).
+Each setting is run $10 \times$ per dataset and the average statistics across the $10 \times 2 = 20$ chains are reported.
+.
+
+%All 25 datasets presented in \textbf{Table \ref{table:datasets}} are benchmarked together $1 \times$ each at the end of the protocol.
 Datasets and BEAST2 .xml templates are provided in the GitHub repository accompanying this article.
@@
  \hline
-  & $N$ & $P$ & $L$ (kb) & $L_\text{eff}$ (kb) & Ref. \\
+  & $N$ & $P$ & $L$ (kb) & $L_\text{eff}$ (kb) & \textbf{Description} \\
 
-\textbf{1}  &  \textbf{6}  &  1/4/8/\textbf{16}  &  0.4/2.1/10.2/\textbf{13.7}  &  0.1/0.5/1/\textbf{1.1}  &  \textbf{Richart 2015} \cite{Richart_2016} \\
+1  &  6  &  16  &  13.7  &  1.1  &  Spiders (Richart 2015 \cite{Richart_2016}) \\
 
-\textbf{2}  &  \textbf{10}  &  1/4/8/\textbf{16}  &  0.4/1.5/3.1/\textbf{6.7}  &  0.1/0.3/0.5/\textbf{0.9}  &  \textbf{Crawford 2012} \cite{Crawford_2012} \\
+2  &  18  &  16  &  6.7  &  0.9  &  Gallopheasants (Meiklejohn 2016 \cite{Meiklejohn_2016}) \\
 
-3  &  11  &  1/4/8/16  &  0.5/2.2/4.9/10.1  &  0.1/0.4/0.7/1.3  &  Leache 2015 \cite{Leache_2015} \\
+3  &  33  &  16  &  5.1  &  1.5  &  Birds (McCormack 2013 \cite{McCormack_2013}) \\
 
-4  &  18  &  1/4/8/16  &  0.4/1.8/2.9/6.7  &  0.1/0.3/0.4/0.9  &  Meiklejohn 2016 \cite{Meiklejohn_2016} \\
+4  &  40  &  1 &  3.0  &  0.6-1.8  &  \textit{Simulated data} $\times 10$ \\
 
-5  &  27  &  1/4/8/16  &  0.8/1.4/2/4.3  &  0.3/0.6/1/1.7  &  Faircloth 2013 \cite{Faircloth_2013} \\
+5  &  44  &  3  &  1.9  &  0.8  &  Bark beetles (Cognato 2001 \cite{Cognato_2001}) \\
 
-6  &  33  &  1/4/8/16  &  0.4/1.7/2.6/5.1  &  0.1/0.5/0.7/1.5  &  McCormack 2013 \cite{McCormack_2013} \\
+6  &  51  &  6  &  5.4  &  1.8  &  Southern beeches (Sauquet 2011 \cite{Sauquet_2011}) \\
 
-7  &  38  &  1/4  &  0.4/2.1  &  0.2/0.6  &  Bergsten 2013 \cite{Bergsten_2013} \\
+7  &  70  &  3  &  2.2  &  0.9  &  Caterpillars (Kawahara 2013 \cite{Kawahara_2013}) \\
 
-8  &  38  &  1/4/8/16  &  1/2.4/8.1/14.9  &  0.7/1.8/5.6/10.1  &  Ran 2018 \cite{Ran_2018} \\
+8  &  94  &  4  &  1.8  &  0.8  &  Bees (Rightmyer 2013 \cite{Rightmyer_2013}) \\
 
-9  &  41  &  1/3  &  0.4/1.7  &  0.3/1.1  &  Brown 2012 \cite{Brown_2012} \\
+9  &  106  &  1  &  0.6  &  0.3  & Songbirds (Moyle 2016 \cite{Moyle_2016}) \\
 
-10  &  44  &  1/3  &  0.6/1.9  &  0.2/0.8  &  Cognato 2001 \cite{Cognato_2001} \\
-
-11  &  44  &  1/4/7  &  0.8/2.9/5.9  &  0.3/0.8/1.8  &  Dornburg 2012 \cite{Dornburg_2012} \\
-
-12  &  51  &  1/4/6  &  0.6/3.5/5.4  &  0.1/0.9/1.8  &  Sauquet 2011 \cite{Sauquet_2011} \\
-
-13  &  61  &  1/4/8/16  &  0.9/4.2/7.5/15  &  0.7/2.8/4.6/9.6  &  Broughton 2013 \cite{Broughton_2013} \\
-
-14  &  69  &  1/2  &  0.7/0.8  &  0.1/0.1  &  Devitt 2013 \cite{Devitt_2013} \\
-
-\textbf{15}  &  \textbf{70}  &  1/\textbf{3}  &  0.7/\textbf{2.2}  &  0.3/\textbf{0.9}  &  \textbf{Kawahara 2013} \cite{Kawahara_2013} \\
-
-16  &  78  &  1/4/8/16  &  0.4/1.9/4.1/7.2  &  0.3/1.7/3.6/6.2  &  Cannon 2016 \cite{Cannon_2016} \\
-
-17  &  79  &  1/4/8/16  &  0.1/1.3/0.8/4.5  &  0/0.1/0.1/0.8  &  Oaks 2011 \cite{Oaks_2011} \\
-
-18  &  94  &  1/4/8/11  &  0.1/1.8/3/3.7  &  0.1/0.8/1.3/1.7  &  Rightmyer 2013 \cite{Rightmyer_2013} \\
-
-\textbf{19}  &  \textbf{106}  &  \textbf{1}/4/8/16  &  \textbf{0.6}/3.1/5.1/11.6  &  \textbf{0.3}/1.2/2/4.5  &  \textbf{Moyle 2016} \cite{Moyle_2016} \\
-
-20  &  110  &  1/4/8/16  &  0.5/2.1/3.8/7.1  &  0.3/1.4/2.5/4.3  &  Fong 2012 \cite{Fong_2012} \\
-
-21  &  152  &  1/4/5  &  1/3.5/3.6  &  0.6/1.6/1.6  &  Day 2013 \cite{Day_2013} \\
-
-22  &  187  &  1/4/8/16  &  0.3/0.9/1.4/3.5  &  0.2/0.7/1.1/2.9  &  Branstetter 2017 \cite{Branstetter_2017} \\
-
-23  &  197  &  1/4/8/14  &  0.9/3.1/6.1/11.6  &  0.3/1.6/3.5/6.3  &  Horn 2014 \cite{Horn_2014} \\
-
-24  &  235  &  1/4/8/16  &  2.3/6.4/8.5/25.7  &  0.9/2.3/3.2/12.2  &  Reddy 2017 \cite{Reddy_2017} \\
-
-25  &  237  &  1/4/5  &  0.8/2.4/3.1  &  0.2/1.2/1.5  &  Murray 2013 \cite{Murray_2013} \\
+10  &  110  &  1  &  0.5  &  0.3  &  Vertebrates (Fong 2012 \cite{Fong_2012}) \\
 
@@
 \end{tabular}
-\caption{Empirical datasets used during benchmarking, sorted in increasing order of taxa count $N$.
+\caption{Datasets used during benchmarking, sorted in increasing order of taxa count $N$.
 Number of partitions $P$, total alignment length $L$, and number of patterns $L_\text{eff}$ are also specified.
-Where a dataset is sampled more than once, the dimensions of its multiple samples are separated by `/'.
-The datasets in bold (Richart 2015 \cite{Richart_2016}, Crawford \cite{Crawford_2012}, Kawahara \cite{Kawahara_2013}, and Moyle \cite{Moyle_2016}) are used during the optimisation protocol.
-}
+The 9 empirical datasets are benchmarked $10 \times$ per setting, whereas each of the 10 simulated datasets are benchmarked once per setting.}
 \label{table:datasets}
@@
 
-We compared the Narrrow Exchange Rate (NER) operators described in \textbf{\nameref{sect:NER}}.
+The \textbf{\nameref{sect:NER}} (NER) operators are evaluated.
 This protocol selects the best among 48 NER (no random walk) and 48 NERw ($\text{Bactrian}(0.95)$ random walk) operators, and has two phases.
@@
 Second, the selected operator is benchmarked with respect to convergence time and sampling rate on real data (\textbf{Table \ref{table:datasets}}).
-All the analyses in this section invoke the \textit{quant} parameterisation and $\text{Bactrian}(0.95)$ proposal kernels on clock model parameters.
+The analyses in this section invoke the \textit{quant} parameterisation and $\text{Bactrian}(0.95)$ proposal kernels on clock model parameters.
 

### 2020-03-04 manuscript.tex
Clock model averaging

@@
 However, the constant distance operators since introduced by Zhang and Drummond 2020 -- which are incompatible with the \textit{cat} parameterisation -- yield an increase in mixing rate under \textit{real} by up to an order of magnitude over that of \textit{cat}.
+Moreover, the implementation of the \textit{cat} model has come under criticism \cite{rannala2007inferring}.
 
@@
 
-The \textbf{Narrow Exchange} operator \cite{drummond2002estimating}, widely used in BEAST \cite{drummond2012bayesian} and BEAST2 \cite{bouckaert2019beast}, is similar to NNI, and works as follows (\textbf{Fig.
+The \textbf{Narrow Exchange} operator \cite{drummond2002estimating}, widely used in BEAST \cite{drummond2012bayesian,suchard2018bayesian} and BEAST2 \cite{bouckaert2019beast}, is similar to NNI, and works as follows (\textbf{Fig.
 \ref{fig:narrowexchange}}):
@@
 \begin{align}
-	& x^\prime \leftarrow x + \sum\limits_{i=1}^N \sum\limits_{j=i}^N c_{i,j} \times s\Sigma \\
-	\text {where } & c = \texttt{cholesky} \{ (1-\beta) \frac{\Sigma_N}{N} + \beta \frac{\mathbb{I}_N}{N} \}.
+	x^\prime &\leftarrow x + \sum\limits_{i=1}^N \sum\limits_{j=i}^N c_{i,j} \times s\Sigma \\
+	\text {where }  c &= \texttt{cholesky} \{ (1-\beta) \frac{\Sigma_N}{N} + \beta \frac{\mathbb{I}_N}{N} \}.
 \end{align}
@@
 
-\section*{Results and Discussion} \label{sect:results}
+In Bayesian model averaging (BMA), competing models are estimated in the posterior distribution alongside other parameters and are thus directly selected through usual Bayesian inference methods  \cite{fragoso2018bayesian}.
+This is in contrast to other methods -- such as path sampling \cite{lartillot2006computing} and stepping-stone sampling \cite{xie2011improving} -- which operate outside of this central Bayesian inference process (in this case the MCMC algorithm).
+BMA has been applied to many domains \cite{fragoso2018bayesian} -- including astrophysics \cite{parkinson2013bayesian}, geographical information systems \cite{barber2006modelling}, and molecular biology \cite{douglas2020bayesian} -- and in phylogenetics  has been applied to selection of substitution models \cite{beier2004phylogenetic,posada2008jmodeltest,bouckaert2017bmodeltest}, rate heterogeneity models \cite{bouckaert2017bmodeltest}, and clock models \cite{li2012model,baele2012accurate}.
+
+Li and Drummond 2012 used Bayesian model averaging to select clock model prior distributions -- LogNormal, Exponential, and Inverse Gaussian \cite{li2012model}.
+This was achieved by a model indicator that points to the applicable clock model.
+However, due to its discrete nature, sampling the model indicator can be inefficient.
+
+As a preliminary non-phylogenetic analysis, we explored the statistical power of distinguishing between log-normally and exponentially distributed data, and how this depends on sample size $2N-2$ (for $N$ taxa) and standard deviation $\sigma$ (for log-normally distributed data).
+Models are distinguished using the Bayesian information criterion (BIC):
+
+\begin{align}
+	BIC = \begin{cases} \log(2N-2) - 2 \log \big( \hat{L} \; P(\hat{\sigma}) \big) & \text{for LogNormal}(-0.5\sigma^2, \sigma) \\ 
+	- 2 \log \big( \hat{L} \big) & \text{for Exponential}(1) \end{cases}
+\end{align}
+
+where $\hat{L}$ is the maximim likelihood and $P(\hat{\sigma})$ is the prior density of $\sigma$.
+This analysis reveals that when there are a small number of rates, data simulated from a lognormal distribution is often best modelled with an exponential distribution, especially when $\sigma$ is close to 1 (\text{Fig.
+\ref{fig:ClockModelAverging}}).
+However, for larger trees $N > 30$, clock model averaging should be a viable approach.
+
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{Figures/ClockModelAverging.pdf}
+\caption{\textbf{Ability to resolve LogNormal and Exponential distributed data.} \textit{Left:} at each grid point, $2N-2$ random variables are sampled from a $\text{LogNormal}(-0.5\sigma^2, \sigma)$ distribution.
+The point is assessed for its fit to i) a $\text{LogNormal}(-0.5\hat{\sigma}^2, \hat{\sigma})$ distributon, and ii) an $\text{Exponential}(1)$ disribution using the Bayesian information criterion (BIC).
+This is repeated 1000 $\times$ at each grid point and the two sets of BIC scores are compared using a paired t-test ($p=0.001$), which determines the colour of the point on the plot.
+\textit{Right:} points are instead sampled from an $\text{Exponential}(1)$ disribution.
+These simulations show that clock model averaging is most applicable for trees with more than 30 taxa.
+}
+\label{fig:ClockModelAverging}
+\end{figure}
+
+\section*{Results} \label{sect:results}
 
@@
 
+\subsubsection*{Clock model averaging}
+
+\section*{Discussion} \label{sect:discussion}
+
 \section*{Conclusion}

### 2020-03-04 manuscript.tex
Clock model averaging

@@
 In this article we consider application of the AVMVN kernel to the branch rates of leaf nodes.
-This operator is not readily applicable to internal node branch rates due to their dependency on the topology of the tree.
+This operator is not readily applicable to internal node branch rates due to their dependencies on tree topology.
 
@@
 \begin{align}
-	\mathcal{AVMVN}(x) = (1-\beta) \mathcal{MVN}\big(x, \frac{\Sigma_N}{N} \big) + \beta \mathcal{MVN}\big(x, \frac{\mathbb{I}_N}{N} \big),
+	\mathcal{AVMVN}(x) =  \mathcal{MVN}\big(x, (1-\beta) \frac{\Sigma_N}{N} + \beta \frac{\mathbb{I}_N}{N} \big) ,
 \end{align}
@@
 where $\mathcal{MVN}$ is the multivariate normal probability density.
-$\beta \; (= 0.05)$ is a constant which determines the fraction of the proposal determined by the identity matrix ${I}_N$, as opposed to the covariance matrix $\Sigma_D$ which is trained during MCMC.
+$\beta \; (= 0.05)$ is a constant which determines the fraction of the proposal determined by the identity matrix $\mathbb{I}_N$, as opposed to the covariance matrix $\Sigma_D$ which is trained during MCMC.
 
@@
 \subsection*{Clock model averaging}
+\label{sect:clockModelAveraging}
 
@@
 
-where $\hat{L}$ is the maximim likelihood and $P(\hat{\sigma})$ is the prior density of $\sigma$.
+where $\hat{L}$ is the maximim likelihood and $P(\hat{\sigma})$ is the prior density of maximum likelihood estimate $\hat{\sigma}$.
 This analysis reveals that when there are a small number of rates, data simulated from a lognormal distribution is often best modelled with an exponential distribution, especially when $\sigma$ is close to 1 (\text{Fig.
@@
 \caption{\textbf{Ability to resolve LogNormal and Exponential distributed data.} \textit{Left:} at each grid point, $2N-2$ random variables are sampled from a $\text{LogNormal}(-0.5\sigma^2, \sigma)$ distribution.
-The point is assessed for its fit to i) a $\text{LogNormal}(-0.5\hat{\sigma}^2, \hat{\sigma})$ distributon, and ii) an $\text{Exponential}(1)$ disribution using the Bayesian information criterion (BIC).
+The samples are assessed for their fit to i) a $\text{LogNormal}(-0.5\hat{\sigma}^2, \hat{\sigma})$ distributon, and ii) an $\text{Exponential}(1)$ disribution, using the Bayesian information criterion (BIC).
 This is repeated 1000 $\times$ at each grid point and the two sets of BIC scores are compared using a paired t-test ($p=0.001$), which determines the colour of the point on the plot.
@@
 
-To avoid a cross-product explosion, the three targets for clock model improvement (\textbf{\nameref{sect:rateparams}}, \textbf{\nameref{sect:randomwalks}}, and \textbf{\nameref{sect:NER}}) are evaluated sequentially, in the order presented in this paper.
-The setting(s) which are considered to be the best in each step are then incorporated into the following step.
+To avoid a cross-product explosion, the four targets for clock model improvement (\textbf{\nameref{sect:rateparams}}, \textbf{\nameref{sect:randomwalks}}, \textbf{\nameref{sect:NER}}, and \textbf{\nameref{AVMVN_sect}}) are evaluated sequentially, in the order presented in this paper.
+The setting which is considered to be the best in each step is then incorporated into the following step.
 This protocol and its outcomes are summarised in \textbf{Fig.
@@
 
-\textbf{Fig.
+%\textbf{Fig.
 \ref{fig:parameterisationResults}} shows that the \textit{real 2006} performs considerably worse than any of the other settings.
@@
 
-%Our results are also consistent with Zhang and Drummond 2020, who found that \textit{real} (with constant distance operators) gives superior mixing of rates compared with \textit{cat}.
-
-Our results show that the \textit{quant} parameterisation yields the best performance with respect to effective samples per hour.
+%Our results show that the \textit{quant} parameterisation yields the best performance with respect to effective samples per hour.
 \textit{quant} outperforms \textit{quant 2006}, suggesting that the constant distance operators are effective.
@@
 
-Overall, \textit{quant} yields a median ESS/hr approximately 150 \% faster with respect to sampling the posterior probability, and approximately 30 \% faster with respect to sampling branch rates $r$ and clock standard deviation $\sigma$, compared with \textit{real}.
-
-%\text{cat} and \textit{quant 2006} parameterisations yield similar effective samples per hour for all parameters (including posterior, likelihood, and prior probabilities).
+%Overall, \textit{quant} yields a median ESS/hr approximately 150 \% faster with respect to sampling the posterior probability, and approximately 30 \% faster with respect to sampling branch rates $r$ and clock standard deviation $\sigma$, compared with \textit{real}.
 
@@
 
-\subsubsection*{Clock model averaging}
+\subsection*{Evaluating the AVMVN leaf rate operator}
+
+\subsection*{Clock model averaging}
 

### 2020-07-01 manuscript.tex
Update
fixes

@@
 \\
-Jordan Douglas\textsuperscript{1*},
-Rong Zhang\textsuperscript{1},
-Alexei J. Drummond\textsuperscript{1,2},
-Remco Bouckaert\textsuperscript{1}
+Jordan Douglas\textsuperscript{1,2*},
+Rong Zhang\textsuperscript{1,2},
+Alexei J. Drummond\textsuperscript{1,2,3},
+Remco Bouckaert\textsuperscript{1,2}
 \\
 \bigskip
-\textbf{1} Centre for Computational Evolution, School of Computer Science, University of Auckland, Auckland, New Zealand\\
-\textbf{2} School of Biological Sciences, University of Auckland, Auckland, New Zealand
+\textbf{1} Centre for Computational Evolution,  University of Auckland, Auckland, New Zealand\\
+\textbf{2} School of Computer Science, University of Auckland, Auckland, New Zealand\\
+\textbf{3} School of Biological Sciences, University of Auckland, Auckland, New Zealand
 \\
@@
 \subsection*{A guided adaptive leaf rate operator}
+\label{AVMVN_sect}
 
@@
 \subsubsection*{AVMVN kernel}
-\label{AVMVN_sect}
 
@@
 As the size of the covariance matrix $\Sigma_N$ grows with the number of taxa $N$, AVMVN is hypothesised to work well on small trees but become less efficient with larger taxon sets.
-
-\subsection*{Clock model averaging}
-\label{sect:clockModelAveraging}
-
-In Bayesian model averaging (BMA), competing models are estimated in the posterior distribution alongside other parameters and are thus directly selected through usual Bayesian inference methods  \cite{fragoso2018bayesian}.
-This is in contrast to other methods -- such as path sampling \cite{lartillot2006computing} and stepping-stone sampling \cite{xie2011improving} -- which operate outside of this central Bayesian inference process (in this case the MCMC algorithm).
-BMA has been applied to many domains \cite{fragoso2018bayesian} -- including astrophysics \cite{parkinson2013bayesian}, geographical information systems \cite{barber2006modelling}, and molecular biology \cite{douglas2020bayesian} -- and in phylogenetics  has been applied to selection of substitution models \cite{beier2004phylogenetic,posada2008jmodeltest,bouckaert2017bmodeltest}, rate heterogeneity models \cite{bouckaert2017bmodeltest}, and clock models \cite{li2012model,baele2012accurate}.
-
-Li and Drummond 2012 used Bayesian model averaging to select clock model prior distributions -- LogNormal, Exponential, and Inverse Gaussian \cite{li2012model}.
-This was achieved by a model indicator that points to the applicable clock model.
-However, due to its discrete nature, sampling the model indicator can be inefficient.
-
-As a preliminary non-phylogenetic analysis, we explored the statistical power of distinguishing between log-normally and exponentially distributed data, and how this depends on sample size $2N-2$ (for $N$ taxa) and standard deviation $\sigma$ (for log-normally distributed data).
-Models are distinguished using the Bayesian information criterion (BIC):
-
-\begin{align}
-	BIC = \begin{cases} \log(2N-2) - 2 \log \big( \hat{L} \; P(\hat{\sigma}) \big) & \text{for LogNormal}(-0.5\sigma^2, \sigma) \\ 
-	- 2 \log \big( \hat{L} \big) & \text{for Exponential}(1) \end{cases}
-\end{align}
-
-where $\hat{L}$ is the maximim likelihood and $P(\hat{\sigma})$ is the prior density of maximum likelihood estimate $\hat{\sigma}$.
-This analysis reveals that when there are a small number of rates, data simulated from a lognormal distribution is often best modelled with an exponential distribution, especially when $\sigma$ is close to 1 (\text{Fig.
-\ref{fig:ClockModelAverging}}).
-However, for larger trees $N > 30$, clock model averaging should be a viable approach.
-
-\begin{figure}[!h]
-\includegraphics[width=\textwidth]{Figures/ClockModelAverging.pdf}
-\caption{\textbf{Ability to resolve LogNormal and Exponential distributed data.} \textit{Left:} at each grid point, $2N-2$ random variables are sampled from a $\text{LogNormal}(-0.5\sigma^2, \sigma)$ distribution.
-The samples are assessed for their fit to i) a $\text{LogNormal}(-0.5\hat{\sigma}^2, \hat{\sigma})$ distributon, and ii) an $\text{Exponential}(1)$ disribution, using the Bayesian information criterion (BIC).
-This is repeated 1000 $\times$ at each grid point and the two sets of BIC scores are compared using a paired t-test ($p=0.001$), which determines the colour of the point on the plot.
-\textit{Right:} points are instead sampled from an $\text{Exponential}(1)$ disribution.
-These simulations show that clock model averaging is most applicable for trees with more than 30 taxa.
-}
-\label{fig:ClockModelAverging}
-\end{figure}
 
@@
 
-1  &  6  &  16  &  13.7  &  1.1  &  Spiders (Richart 2015 \cite{Richart_2016}) \\
+ 1  &  38  &  8  &  9.1  &  6.45  &  Seed plants (Ran 2018 \cite{Ran_2018}) \\
 
-2  &  18  &  16  &  6.7  &  0.9  &  Gallopheasants (Meiklejohn 2016 \cite{Meiklejohn_2016}) \\
+2  &  44  &  7  &  5.9  &  1.8  &  Squirrel Fishes (Dornburg 2012 \cite{Dornburg_2012}) \\
 
-3  &  33  &  16  &  5.1  &  1.5  &  Birds (McCormack 2013 \cite{McCormack_2013}) \\
+3  &  44  &  3  &  1.9  &  0.8  &  Bark beetles (Cognato 2001 \cite{Cognato_2001}) \\
 
-4  &  40  &  1 &  3.0  &  0.6-1.8  &  \textit{Simulated data} $\times 10$ \\
+4  &  51  &  6  &  5.4  &  1.8  &  Southern beeches (Sauquet 2011 \cite{Sauquet_2011}) \\
 
-5  &  44  &  3  &  1.9  &  0.8  &  Bark beetles (Cognato 2001 \cite{Cognato_2001}) \\
+5  &  61  &  8  &  6.9  &  4.3  &  Bony fishes (Broughton 2013 \cite{Broughton_2013}) \\
 
-6  &  51  &  6  &  5.4  &  1.8  &  Southern beeches (Sauquet 2011 \cite{Sauquet_2011}) \\
+6  &  70  &  3  &  2.2  &  0.9  &  Caterpillars (Kawahara 2013 \cite{Kawahara_2013}) \\
 
-7  &  70  &  3  &  2.2  &  0.9  &  Caterpillars (Kawahara 2013 \cite{Kawahara_2013}) \\
+7  &  78  &  8  &  3.4  &  3.1  &  Animals (Cannon 2016 \cite{Cannon_2016}) \\
 
-8  &  94  &  4  &  1.8  &  0.8  &  Bees (Rightmyer 2013 \cite{Rightmyer_2013}) \\
+8  &  80  &  1 &  10.0  &  4.2  &  \textit{Simulated data}  \\
 
-9  &  106  &  1  &  0.6  &  0.3  & Songbirds (Moyle 2016 \cite{Moyle_2016}) \\
+9  &  94  &  4  &  2.2  &  1  &  Bees (Rightmyer 2013 \cite{Rightmyer_2013}) \\
 
-10  &  110  &  1  &  0.5  &  0.3  &  Vertebrates (Fong 2012 \cite{Fong_2012}) \\
+10  &  106  &  1  &  0.8  &  0.5  &  Songbirds (Moyle 2016 \cite{Moyle_2016}) \\
 
@@
 \caption{Datasets used during benchmarking, sorted in increasing order of taxa count $N$.
-Number of partitions $P$, total alignment length $L$, and number of patterns $L_\text{eff}$ are also specified.
-The 9 empirical datasets are benchmarked $10 \times$ per setting, whereas each of the 10 simulated datasets are benchmarked once per setting.}
+Number of partitions $P$, total alignment length $L$, and number of patterns $L_\text{eff}$ are also specified.}
 \label{table:datasets}

### 2020-07-17 manuscript.tex
tidies

@@
 {\Large
-\textbf\newline{Smarter dating moves and faster proposals: revisiting the phylogenetic relaxed clock model} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
+\textbf\newline{Smarter dating and faster proposals: revisiting the phylogenetic relaxed clock model} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
 }
@@
 
+The molecular clock hypothesis states that the evolutionary rates of biological sequences are approximately constant throughout time \cite{zuckerkandl1962molecular}.
+This assumption forms the basis of phylogenetics, under which evolutionary trees and divergence dates of life forms are inferred from biological sequences, such as nucleotides and amino acids \cite{douzery2003local, drummond2006relaxed}.
+In Bayesian phylogenetics, these trees and their associated parameters are estimated as probabilitiy distributions \cite{kuhner1995estimating, larget1999markov, mau1999bayesian}. 
+Statistical inference is typically performed by sampling under the Metropolis-Hastings Markov chain Monte Carlo (MCMC) algorithm \cite{metropolis53, hastings70}.
+Bayesian phylogenetic clock models have been implemented in many platforms including BEAST \cite{drummond2012bayesian}, BEAST2 \cite{bouckaert2019beast}, MrBayes \cite{ronquist2012mrbayes}, and RevBayes \cite{hohna2016revbayes}.
+
+The simplest phylogenetic clock model -- the strick clock -- makes the convenient assumption that the evolutionary rate is constant across all lineages \cite{zuckerkandl1965evolutionary, kuhner1995estimating, larget1999markov}.
+% Early examples?
+However, molecular substitution rates are known to vary over time, over population sizes, over evolutionary pressures, and over DNA replicative machineries \cite{gillespie1994causes, woolfit2009effective, loh2010optimization}.
+Moreover, any given dataset may be clock-like (where the substitution rate has a small variance across lineages) or non clock-like (a large variance). 
+In the latter case, a strict clock is probably not suitable.
+
+This led to the development of relaxed (uncorrelated) clock models, under which each branch in the phylogenetic tree has its own substitution rate  \cite{drummond2006relaxed}.
+Branch rates can be drawn from a range of probability distributions including log-normal, exponential, gamma, and inverse-gamma distributions \cite{drummond2006relaxed, lepage2007general, li2012model}.
+This class of models is widely used, and has aided insight into many recent biological problems, including the 2016 Zika virus outbreak \cite{faria2017establishment} and the COVID-19 pandemic \cite{giovanetti2020first}.
+% is compatible with increasingly prominent multispecies coalescent models \cite{ogilvie2017starbeast2},
+
+Finally, although not the focus of this article, the class of correlated clock models assumes some form of auto-correlation between rates over time. 
+The correlation itself can invoke a range of stochastic models, including compound Poisson \cite{huelsenbeck2000compound} and CIR processes \cite{lepage2007general}, or it can exist as a series of local relaxed clocks \cite{drummond2010bayesian}.
+However, due to the correlated and discrete nature of such models, the time until MCMC convergence may be cumbersome, particularly for larger datasets \cite{drummond2010bayesian}.
+
+With the increasing availabilty of biological sequence data, the development of efficient Bayesian phylogenetic methods is more important than ever. 
+The performance of MCMC is dependent not only on computational runtime but also the efficacy of an
+MCMC setup to achieve its convergence.
+A critical task therein lies the further advancement of MCMC operators.
+Recent developments in this area include the advancement of guided tree proposals \cite{zhang2020using, meyer2019adaptive, hohna2012guided}, coupled MCMC \cite{altekar2004parallel, muller2019coupled},
+adaptive multivariate transition kernels \cite{baele2017adaptive},
+and other explorative proposal kernels \cite{yang2013searching, thawornwattana2018designing}.
+In the case of clock models, smart tree proposals can account for correlations between substitution rates and divergence times \cite{zhang2020improving}. 
+The rate parameterisation itself can also affect the ability to ``mix'' during MCMC \cite{drummond2006relaxed, li2012model, zhang2020improving}.
+
+While a range of advanced operators and other MCMC optimisation methods have arisen over the years, there has yet to be a widescale performance benchmarking of such methods as applied to the relaxed clock model.
+In this article, we systematically evaluate how the relaxed clock model can benefit from i) different substitution rate parameterisations,  ii) the use of Bactrian proposal kernels \cite{yang2013searching}, iii) tree operators which account for correlations between substitution rates and times, and iv) adaptive multivariate operators \cite{baele2017adaptive}.
+The discussed methods are implemented in and compared using BEAST2 \cite{bouckaert2019beast}.
+
+% phylogenetic model -- and the operators used during MCMC -- to achieve convergence. 
+%A great body of research of MCMC performance
+
+% With increasing sequence availability, it is desirable to have faster MCMC
+% This can be achieved through faster mixing and better performance (beagle)
+% Address modern optimisation speedups - bactrian, AVMVN, + 2 others not covered in this paper including GUIDED tree proposals
+% Address various attempts made to optimise clock models (Rong's paper, different parameterisations + 1 other not covered)
+% While many ideas have come up over the years, a large scale systematic comparison of which methods yield faster mixing (if there is one) has not been applied
+
+% In this article, benchmark a range of approaches including...
+
 % Results and Discussion can be combined.
@@
 
-Let $\mathcal{T}$ be a binary rooted time tree with $N$ taxa (and $2N-2$ branches).
-Let $L$ be the number of sites within the multiple sequence alignment $D$, and let $L_\text{eff}$ be the \textit{effective} number of sites in the alignment (ie.
-the number of site patterns).
+Let $\mathcal{T}$ be a binary rooted time tree with $N$ taxa.
+Let $L$ be the number of sites within the multiple sequence alignment $D$, and let $L_\text{eff}$ be the effective number of sites in the alignment (i.e.
+the number of unique patterns across all sites in the alignment).
 The posterior density of a phylogenetic model is described by
@@
 
-for rate standard deviation $\sigma$ and other model parameters $\theta$.
+for substitution rate standard deviation $\sigma$ and other model parameters $\theta$.
 $\vec{\mathcal{R}}^{\,}$ is a vector of abstracted substitution rates, which is transformed into real rates by $r(\vec{\mathcal{R}}^{\,})$.
@@
 
-Under the \textit{relaxed clock model}, each internal and leaf node is assigned a substitution rate $r_i = r(\mathcal{R}_i)$, which corresponds to its parent branch.
-There are a total of $|\vec{\mathcal{R}}^{\,}| = 2N-2$ rates, which are independently distributed under the relaxed clock model prior  \cite{drummond2006relaxed}.
+Let $t_i$ be the height (time) of node $i$.
+Every internal and leaf node $i$ in $\mathcal{T}$ is associated with a parental branch length (the height difference between $i$ and its parent) $\tau_i$ and a parental branch substitution rate $r_i = r(\mathcal{R}_i)$.
+There are a total of $2N-2$ internal and leaf nodes. 
+Under the relaxed clock model, each $\mathcal{R}_i$ is independently distributed under the prior.
 
-%The substitution rate on branch $i$
+The posterior distribution is sampled by MCMC.
+The probability of accepting proposed state $x^\prime$ from state $x$ is calculated using the Metropolis-Hastings ratio \cite{metropolis53, hastings70}:
 
-\subsection*{Rate parameterisations}
+\begin{eqnarray}
+\label{eq:MCMC}
+\alpha(x^\prime|x) =  \min\left( 1, \frac{p(x^\prime|D)}{p(x|D)} \frac{q(x|x^\prime)}{q(x^\prime|x)} \right).
+\end{eqnarray}
+
+$q(a|b)$ is the transition kernel: the probability of proposing state $b$ from state $a$.
+The ratio between the two $\frac{q(x|x^\prime)}{q(x^\prime|x)}$ is known as the Hastings ratio \cite{hastings70}.
+
+\subsection*{Substitution rate parameterisations}
 \label{sect:rateparams}
@@
 
+\clearpage
 \subsubsection*{1. Real rates}
@@
 
-Under the prior distribution $p(\vec{\mathcal{R}}^{\,} | \sigma)$, rates are often log-normally or exponentially distributed with a mean of 1:
+Under the prior distribution $p(\vec{\mathcal{R}}^{\,} | \sigma)$, rates are log-normally distributed with a mean of 1:
 
 \begin{align}
-p(\mathcal{R}_i | \sigma) = \frac{1}{\mathcal{R}_i \sigma \sqrt{2\pi}} \exp \big( -\frac{(\ln \mathcal{R}_i - \mu)^2}{2\sigma^2} \big) \quad &(\text{ LogNormal}(\mu, \sigma)\;) \text{, or}  \\
-p(\mathcal{R}_i | \sigma) = p(\mathcal{R}_i) = e^{-\mathcal{R}_i} \quad &(\text{ Exponential}(\lambda=1)\;)
+p(\mathcal{R}_i | \sigma) = \frac{1}{\mathcal{R}_i \sigma \sqrt{2\pi}} \exp \big( -\frac{(\ln \mathcal{R}_i - \mu)^2}{2\sigma^2} \big) 
 \end{align}
@@
 where $\mu = -0.5\sigma^2$ is set such that the expected value of the log-normal distribution is 1.
+In this article we only consider log-normal clock priors, however the methods discussed are general.
 
-Zhang and Drummond 2020 present a series of tree operators which propose internal/root node heights, and then recompute the rates of incident branches such that their genetic distances ($r_i \times \tau_i$) remain constant after the proposal.
-By maintaining genetic distances the likelihood can also be maintained.
-These operators account for the correlation which exists between branch rates and branch times -- a correlation which is induced by the likelihood function.
+Zhang and Drummond 2020 present a series of tree operators which propose internal/root node heights, and then recompute the rates of incident branches such that their genetic distances ($r_i \times \tau_i$) remain constant after the proposal \cite{zhang2020improving}.
+These operators account for the correlation which exists between branch rates and branch times.
+By keeping the genetic distance of each branch constant, the likelihood is unaltered by the proposal.
 
@@
 
+These integers correspond to $n$ rate categories.
  The domain of $\vec{\mathcal{R}}^{\,}$ is uniformly distributed:
@@
 
-This method was suggested in the original BEAST2 relaxed clock paper \cite{drummond2006relaxed} and has been widely used.
-However, the constant distance operators since introduced by Zhang and Drummond 2020 -- which are incompatible with the \textit{cat} parameterisation -- yield an increase in mixing rate under \textit{real} by up to an order of magnitude over that of \textit{cat}.
-Moreover, the implementation of the \textit{cat} model has come under criticism \cite{rannala2007inferring}.
+This method has been widely used in BEAST and BEAST2 analyses \cite{drummond2006relaxed}. 
+However, the recently developed constant distance operators  -- which are incompatible with the \textit{cat} parameterisation -- yield an increase in mixing rate under \textit{real} by up to an order of magnitude over that of \textit{cat} \cite{zhang2020improving}.
 
@@
 Transforming these quantiles into rates invokes the i-cdf of the underlying \textit{real} clock model distribution.
-Thus, while this approach has clear similarities with \textit{cat}, the domain of rates here is continuous (as opposed to being confined to a discrete number of bins) and is therefore compatible with the class of operators described by Zhang and Drummond 2020.
+Thus, while this approach has clear similarities with \textit{cat}, the domain of rates here is continuous (as opposed to being confined to a discrete number of bins) and is therefore compatible with constant distance operators \cite{zhang2020improving}.
 
-A potential disadvantage of the \textit{quant} method would be the computational requirements of continuously evaluating the i-cdf, especially for trees with large $N$.
+A potential disadvantage of the \textit{quant} method would be the computational requirements of continuously evaluating the i-cdf.
+As the number of quantiles grows with the taxon count $N$, this drawback would be at its worst on large trees.
 Hence, rather than evaluating the exact i-cdf $F^{-1}$, an approximation $\hat{F}^{-1}$ will be used instead:
@@
 In this article we have extended \textit{quant} through a linear piecewise approximation of the i-cdf.
-As the piecewise approximation is linear, evaluating the derivatives $\frac{\partial}{\partial \mathcal{R}_i} \hat{F}^{-1}(\mathcal{R}_i) =  D \hat{F}^{-1}(\mathcal{R}_i)$ and $\frac{\partial}{\partial r_i} \hat{F}(r_i) = D \hat{F}(r_i)$  -- which are required for computing Hastings ratios -- is trivial.
+As the piecewise approximation is linear, evaluating the derivatives $\frac{\partial}{\partial \mathcal{R}_i} \hat{F}^{-1}(\mathcal{R}_i) =  D \hat{F}^{-1}(\mathcal{R}_i)$ and $\frac{\partial}{\partial r_i} \hat{F}(r_i) = D \hat{F}(r_i)$  -- which are required for computing the Hastings ratios -- is trivial.
 The approximation is comprised of $n$ pieces (where $n$ is fixed) and upper and lower rate boundaries $r_\text{min}$ and $r_\text{max}$.
@@
 
-Zhang and Drummond 2020 introduced several tree operators for the \textit{real} parameterisation -- including \textbf{Constant Distance}, \textbf{Simple Distance}, and \textbf{Small Pulley}.
+Zhang and Drummond 2020 introduced several tree operators for the \textit{real} parameterisation -- including \texttt{Constant Distance}, \texttt{Simple Distance}, and \texttt{Small Pulley}.
 In this project, we extended these three operators so that they are compatible with the \textit{quant} parameterisation.
@@
  & Operator & Proposal & Parameters  \\
- 1 & \textbf{Random walk operator} & $x^\prime \leftarrow x + s\Sigma$ & $\sigma, r, q$ \\
- 2 & \textbf{Scale operator} & $x^\prime \leftarrow x \times e^{s\Sigma}$ & $\sigma, r$  \\
- 3 & \textbf{Interval operator} & $\begin{array} {rl} y &\leftarrow \frac{u - x}{x - l} \times e^{s\Sigma} \\ x^\prime &\leftarrow \frac{u + l * y}{y + 1}  \end{array}$ & $q \;\; (l=0,u=1)$  \\
- 4 & \textbf{Constant distance operators} & $x^\prime \leftarrow x + s\Sigma$ & $t$ \\
+ 1 & \texttt{Random walk} operator & $x^\prime \leftarrow x + s\Sigma$ & $\sigma, r, q$ \\
+ 2 & \texttt{Scale} operator & $x^\prime \leftarrow x \times e^{s\Sigma}$ & $\sigma, r$  \\
+ 3 & \texttt{Interval} operator & $\begin{array} {rl} y &\leftarrow \frac{u - x}{x - l} \times e^{s\Sigma} \\ x^\prime &\leftarrow \frac{u + l * y}{y + 1}  \end{array}$ & $q \;\; (l=0,u=1)$  \\
+ 4 & \texttt{Constant distance} operator & $x^\prime \leftarrow x + s\Sigma$ & $t$ \\
 
@@
 \caption{Summary of proposal kernels $q(x^\prime|x)$ of clock model operators.
+\texttt{Random walk}, \texttt{Scale}, and \texttt{Interval} are standard BEAST2 operators.
  In each operator, $\Sigma$ is drawn from either a $\text{Bactrian}(m)$ or $\text{Uniform}$ distribution (distributions are normalised so that they have a mean of 0 and a variance of 1).
@@
 The Scale operator acts on parameters with non-negative domains.
-The Interval operator proposes values which respect its domain ie.
-$l < x^\prime < u$.
+The Interval operator proposes values which respect the domain of the parameter i.e.
+$l < x, x^\prime < u$.
 }
@@
 
-The \textbf{Narrow Exchange} operator \cite{drummond2002estimating}, widely used in BEAST \cite{drummond2012bayesian,suchard2018bayesian} and BEAST2 \cite{bouckaert2019beast}, is similar to NNI, and works as follows (\textbf{Fig.
+The \texttt{Narrow Exchange} operator \cite{drummond2002estimating}, widely used in BEAST \cite{drummond2012bayesian,suchard2018bayesian} and BEAST2 \cite{bouckaert2019beast}, is similar to NNI, and works as follows (\textbf{Fig.
 \ref{fig:narrowexchange}}):
@@
 
-\textul{\textit{Step 2}}. Identify the child of $E$ with the greater height. Denote this child as $D$ and its sibling as $C$ (ie. $t_D > t_C$).
+\textul{\textit{Step 2}}. Identify the child of $E$ with the greater height. Denote this child as $D$ and its sibling as $C$ (i.e. $t_D > t_C$).
 
@@
 \includegraphics[width=\textwidth]{Figures/NarrowExchange.pdf}
-\caption{\textbf{Depiction of Narrow Exchange and Narrow Exchange Rate operators.} Proposals are denoted by $\mathcal{T} \rightarrow \mathcal{T}^\prime$.
+\caption{\textbf{Depiction of \texttt{Narrow Exchange} and \texttt{Narrow Exchange Rate} operators.} Proposals are denoted by $\mathcal{T} \rightarrow \mathcal{T}^\prime$.
 The vertical axis corresponds to node height $t$.
@@
 2008 \cite{lakner2008efficiency} found that tree operators which perterb topology (such as NNI and SPR) consistently perform better than those which also change branch lengths (such as LOCAL \cite{simon1998local} and Continuous Change \cite{jow2002bayesian}).
-If Narrow Exchange was adapted to the relaxed clock model by ensuring that genetic distances remain constant after the proposal, its performance may be improved even further.
+If \texttt{Narrow Exchange} was adapted to the relaxed clock model by ensuring that genetic distances remain constant after the proposal, its performance may be improved even further.
 This may in turn permit proposing a new node height $t_D$ and therefore changing branch (time) lengths.
@@
 
-Here, we present the \textbf{Narrow Exchange Rate} (NER) operator.
+Here, we present the \texttt{Narrow Exchange Rate} (NER) operator.
 Let $r_A$, $r_B$, $r_C$, and $r_D$ be the clock rates of nodes $A$, $B$, $C$, and $D$, respectively.
-In addition to the modest topological change applied by Narrow Exchange, NER also proposes new clock rates ${r_A}^\prime$, ${r_B}^\prime$, ${r_C}^\prime$, and ${r_D}^\prime$.
-While NER does not alter $t_D$ (ie.
+In addition to the modest topological change applied by \texttt{Narrow Exchange}, NER also proposes new clock rates ${r_A}^\prime$, ${r_B}^\prime$, ${r_C}^\prime$, and ${r_D}^\prime$.
+While NER does not alter $t_D$ (i.e.
 ${t_D}^\prime \leftarrow t_D$), we also consider NERw - a special case of the NER operator which embarks $t_D$ on a random walk:
@@
 NER (and NERw) are compatible with both the \textit{real} and \textit{quant} parameterisations.
-Analagous to the Constant Distance operator, new rates are proposed such that genetic distances between nodes $A$, $B$, $C$, and $E$ are maintained.
+Analagous to the \texttt{Constant Distance} operator, new rates are proposed such that genetic distances between nodes $A$, $B$, $C$, and $E$ are maintained.
 Thus, there are $\binom{4}{2} = 6$ pairwise distance constraints.
@@
 
-The total space of NER operators is comprised of all possible subsets of distance constraints (ie.
+The total space of NER operators is comprised of all possible subsets of distance constraints (i.e.
 $\{\},\{\mathcal{D}_{AB}\}, \{\mathcal{D}_{AC}\}, \dotso , \{\mathcal{D}_{AB}, \mathcal{D}_{AC}, \mathcal{D}_{AE}, \mathcal{D}_{BC}, \mathcal{D}_{BE}, \mathcal{D}_{CE} \}$) which are solvable.
 The simplest NER -- the null operator denoted by NER$\{\}$ -- does not satisfy any distance constraints.
-This is equivalent to Narrow Exchange.
+This is equivalent to \texttt{Narrow Exchange}.
 
@@
 Computing the determinant $|J|$ invokes standard analytical differentiation and linear algebra libraries of MATLAB. 
-6 of the 54 operators were found to have $|J|=0$, corresponding to irreversible proposals, and were discarded.
+6 of the 54 solvable operators were found to have $|J|=0$, corresponding to irreversible proposals, and were discarded.
 
@@
 Each class corresponds to a single operator, extends the class of a meta-NER-operator, and is comprised of the solutions found in \textbf{1} and the Jacobian determinant found in \textbf{2}.
-$|J|$ is further augmented if the \textit{quant} parameterisation is employed.
+$|J|$ is further augmented if the \textit{quant} parameterisation is employed (\textbf{\nameref{sect:S1Appendix}}).
 
@@
 A \textit{guided} operator incorporates knowledge about neighbouring states, while an \textit{adaptive} operator undergoes a training process to improve its efficiency over time \cite{roberts2007coupling}.
-In previous work, parsimony scores and conditional clade probabilities of neighbouring trees have been employed by guided tree operators \cite{hohna2012guided,zhang2019using,meyer2019adaptive} and the latter has also been explored as the basis of  adaptive tree operators \cite{hohna2012guided,meyer2019adaptive}.
+In previous work, parsimony scores and conditional clade probabilities of neighbouring trees have been employed by guided tree operators \cite{hohna2012guided,zhang2020using,meyer2019adaptive} and the latter has also been explored as the basis of  adaptive tree operators \cite{hohna2012guided,meyer2019adaptive}.
 The (adaptive) mirror kernel \cite{thawornwattana2018designing} learns a target distribution which acts as a `mirror image' of the current point $x$.
@@
 	x^\prime &\leftarrow x + \sum\limits_{i=1}^N \sum\limits_{j=i}^N c_{i,j} \times s\Sigma \\
-	\text {where }  c &= \texttt{cholesky} \{ (1-\beta) \frac{\Sigma_N}{N} + \beta \frac{\mathbb{I}_N}{N} \}.
+	\text {where }  c &= \text{cholesky} \left( (1-\beta) \frac{\Sigma_N}{N} + \beta \frac{\mathbb{I}_N}{N} \right).
 \end{align}
 
-The \texttt{cholesky}$\{Y\}$ decomposition returns a lower diagonal matrix $L$, with positive real diagonal entries, such that $Y = LL^\prime$ \cite{lindstrom1988newton, pourahmadi2007cholesky}.
+The cholesky$(Y)$ decomposition returns a lower diagonal matrix $L$, with positive real diagonal entries, such that $Y = LL^\prime$ \cite{lindstrom1988newton, pourahmadi2007cholesky}.
 $s$ is a tunable step size parameter and $\Sigma$ is a random variable drawn from a proposal kernel (uniform or Bactrian for instance).
@@
 
-\textbf{2.
+\textbf{2. Mixing of parameters}. Key parameters are evaluated for the number of effective samples generated per hour (ESS/hr). This calculation is performed by BEAST2 \cite{bouckaert2019beast}. \\
+
+%\textbf{3.
 Time to convergence}.
@@
 
-\textbf{3. Mixing of parameters}. Key parameters are evaluated for the number of effective samples generated per hour (ESS/hr). \\
-
-For the latter two criteria, methodologies are benchmarked using both simulated and empirical datasets -- the latter were compiled \cite{lanfear2019Github} and partitioned \cite{lanfear2016partitionfinder} by Lanfear et al.
+Methodologies are benchmarked using one simulated and nine empirical datasets -- the latter were compiled \cite{lanfear2019Github} and partitioned \cite{lanfear2016partitionfinder} by Lanfear et al.
 as `benchmark alignments' (\textbf{Table \ref{table:datasets}}).
-Each setting is run $10 \times$ per dataset and the average statistics across the $10 \times 2 = 20$ chains are reported.
-.
+To facilitate convergence on complex datasets, each posterior distribution is sampled using coupled MCMC (MC$^3$) with 4 chains \cite{muller2019coupled}.
+Each methodology is benchmarked across 5 replicates on each dataset, using an the Intel Xeon Gold 6138 CPU (2.00 GHz).
 
@@
 Datasets and BEAST2 .xml templates are provided in the GitHub repository accompanying this article.
-
-Methodologies are benchmarked using the Intel(R) Xeon(R) Gold 6138 CPU (2.00 GHz), with two processing units per pair of MCMC chains.
 
@@
 
+\subsection*{Evaluating constant distance operators}
+
 \subsection*{Comparison of rate parameterisations}
@@
 2006 \cite{drummond2006relaxed}.
-\textit{real} and \textit{quant} additionally use the constant-distance tree operators described by Zhang and Drummond 2020.
+\textit{real} and \textit{quant} additionally use the constant-distance tree operators \cite{zhang2020improving}.
 To determine whether the difference in performance between \textit{real}/\textit{quant} versus \textit{cat} is because of the constant-distance tree operators or the parameterisation itself, we also included benchmarked two additional settings: \textit{real 2006} and \textit{quant 2006}, which do not used the constant-distance operators.
@@
 \ref{fig:parameterisationResults}} shows that the \textit{real 2006} performs considerably worse than any of the other settings.
-This is due to the poor sampling of the prior under this setting (ie.
+This is due to the poor sampling of the prior under this setting (i.e.
 low ESS of $p(\theta)$).
-The failure of \textit{real 2006} thus highlights the appeal of 1) the \textit{cat} or \textit{quant} parameterisations, both of which have trivial contributions to the prior density (ie.
+The failure of \textit{real 2006} thus highlights the appeal of 1) the \textit{cat} or \textit{quant} parameterisations, both of which have trivial contributions to the prior density (i.e.
 uniform priors), and 2) the smarter operators used by \textit{real} (Zhang and Drummond 2020).
@@
 \textit{quant} outperforms \textit{quant 2006}, suggesting that the constant distance operators are effective.
-Furthermore, \textit{quant} outperforms \textit{real} especially at sampling from the posterior and prior distributions (ie.
+Furthermore, \textit{quant} outperforms \textit{real} especially at sampling from the posterior and prior distributions (i.e.
 high ESS/hr for $p(\theta|D)$ and $p(\theta)$).
@@
 \begin{figure}[!h]
-%\includegraphics[width=\textwidth]{Figures/ESS.pdf}
-\caption{\textbf{Rate parameterisation evaluation.} Comparison of ESS/hr (averaged across two independent MCMC chains) with respect to relevant terms -- $L$: likelihood, $p$: prior density, $r$: clock rate averaged across all leaves, $\sigma$: clock standard deviation.
-Each point is from one partition sample of the empirical data in \textbf{Table \ref{table:datasets}}.
+\includegraphics[width=\textwidth]{/home/jdou557/Documents/Marsden2019/Months/July2020/fromVM/benchmarkingVM/ESS_round1.pdf}
+\caption{\textbf{Rate parameterisation performance evaluation.} Comparison of ESS/hr (averaged across five independent MC3 analyses) with respect to relevant terms -- $P$: posterior density; $L$: likelihood, $p$: prior density, $r$: clock rate ESS averaged across all leaves, $\hat{r}$: branch rate mean, $v$: branch rate variance, $\sigma$: clock standard deviation, $\kappa$: HKY model transition-transversion ratio, $\lambda$: Yule model birth rate.
+$h$: tree height.
+Datasets are displayed in \textbf{Table \ref{table:datasets}}.
 }
@@
 Simulated datasets have $N=30$ taxa and an alignment with $L \sim \text{Uniform}(10^2, 10^4)$ sites.
-The acceptance rate of each operator is compared to that of the null operator $\text{NER}\{\}$ (ie.
-Narrow Exchange).
+The acceptance rate of each operator is compared to that of the null operator $\text{NER}\{\}$ (i.e.
+\texttt{Narrow Exchange}).
 
 \textbf{Fig.
-\ref{fig:acceptanceRateScreening}} shows that NER variants which satisfy the genetic distances between nodes $B$ and $A$ (ie.
-$\mathcal{D}_{AB}$) or between $B$ and $C$ (ie.
-$\mathcal{D}_{BC}$) usually perform worse than the standard Narrow Exchange operator, where $B$ is the node being interchanged from the $A$ branch to the $C$ branch (\textbf{Fig.
+\ref{fig:acceptanceRateScreening}} shows that NER variants which satisfy the genetic distances between nodes $B$ and $A$ (i.e.
+$\mathcal{D}_{AB}$) or between $B$ and $C$ (i.e.
+$\mathcal{D}_{BC}$) usually perform worse than the standard \texttt{Narrow Exchange} operator, where $B$ is the node being interchanged from the $A$ branch to the $C$ branch (\textbf{Fig.
 \ref{fig:narrowexchange}}).
 This is an intuitive result.
-If the posterior distribution is relatively flat, and the data presents high uncertainty in the positioning of $B$, with respect to $A$ and $C$, then the topological rearrangement performed by Narrow Exchange will be favoured.
+If the posterior distribution is relatively flat, and the data presents high uncertainty in the positioning of $B$, with respect to $A$ and $C$, then the topological rearrangement performed by \texttt{Narrow Exchange} will be favoured.
 However, this uncertainty in the \textit{topology} is likely coupled with uncertainty in the \textit{distance} between $B$ and $A$ or between $B$ and $C$.
@@
 \includegraphics[width=\textwidth]{Figures/acceptanceRates.pdf}
-\caption{\textbf{Screening of NER and NERw variants by acceptance rate.} Top left: comparison of NER variants with the null operator $\text{NER}\{\}$ (ie.
-Narrow Exchange).
+\caption{\textbf{Screening of NER and NERw variants by acceptance rate.} Top left: comparison of NER variants with the null operator $\text{NER}\{\}$ (i.e.
+\texttt{Narrow Exchange}).
 Each of the 48 operators are represented by a single point, uniquely encoded by the point stylings.
@@
 This is performed by proposing rates for $r_A$, $r_B$, and $r_C$ while obeying the distance constraints imposed by the operator.
-Exploring this operator further, we can see that $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ is at its best when there is a large variance in branch rate ie.
+Exploring this operator further, we can see that $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ is at its best when there is a large variance in branch rate i.e.
 when clock standard deviation $\sigma$ is high ($\sigma \gtrsim 0.5$ for $N=30$), corresponding to data which is not clock-like.
 On the other hand, $\text{NER}\{\}$ is much preferred when the operator's acceptance rate is high ($\gtrsim 0.15$) -- corresponding with datasets with a small number of site patterns ($L_\textit{eff} \lesssim 500$ for $N=30$) and thus poor signal.
-Overall, $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ outperforms the standard Narrow Exchange operator when the data is not clock-like and contains enough signal.
+Overall, $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ outperforms the standard \texttt{Narrow Exchange} operator when the data is not clock-like and contains enough signal.
 
@@
 \ref{fig:acceptanceRateScreening}} shows that by applying a (Bactrian) random walk to $t_D$ -- the height of internal node $D$ -- the acceptance rate of NER plummets dramatically.
-This effect is most dominant for the NER variants which satisfy distance constraints (ie.
+This effect is most dominant for the NER variants which satisfy distance constraints (i.e.
 the operators which are not $\text{NER}\{\}$).
@@
 {\textbf{Rate quantiles.} The linear piecewise approximation used in the \textit{quant} parameterisation is described.
-Tree operators presented by Zhang and Drummond 2020 are extended to the \textit{quant} parameterisation.
+\texttt{Constant distance} tree operators \cite{zhang2020improving} are extended to the \textit{quant} parameterisation.
 

### 2020-07-27 manuscript.tex
Refactor

@@
 {\Large
-\textbf\newline{Smarter dating and faster proposals: revisiting the phylogenetic relaxed clock model} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
+\textbf\newline{Adaptive dating and faster proposals: revisiting the phylogenetic relaxed clock model} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
 }
@@
 adaptive multivariate transition kernels \cite{baele2017adaptive},
-and other explorative proposal kernels \cite{yang2013searching, thawornwattana2018designing}.
+and other explorative proposal kernels including the Bactrian and mirror kernels \cite{yang2013searching, thawornwattana2018designing}.
 In the case of clock models, smart tree proposals can account for correlations between substitution rates and divergence times \cite{zhang2020improving}. 
@@
 While a range of advanced operators and other MCMC optimisation methods have arisen over the years, there has yet to be a widescale performance benchmarking of such methods as applied to the relaxed clock model.
-In this article, we systematically evaluate how the relaxed clock model can benefit from i) different substitution rate parameterisations,  ii) the use of Bactrian proposal kernels \cite{yang2013searching}, iii) tree operators which account for correlations between substitution rates and times, and iv) adaptive multivariate operators \cite{baele2017adaptive}.
+In this article, we systematically evaluate how the relaxed clock model can benefit from i) adaptive operator weighting, ii) different substitution rate parameterisations,  iii) the use of Bactrian proposal kernels \cite{yang2013searching}, iv) tree operators which account for correlations between substitution rates and times, and v) adaptive multivariate operators \cite{baele2017adaptive}.
 The discussed methods are implemented in and compared using BEAST2 \cite{bouckaert2019beast}.
@@
 
-% Define tau
-
 Let $\mathcal{T}$ be a binary rooted time tree with $N$ taxa.
@@
 
-for substitution rate standard deviation $\sigma$ and other model parameters $\theta$.
-$\vec{\mathcal{R}}^{\,}$ is a vector of abstracted substitution rates, which is transformed into real rates by $r(\vec{\mathcal{R}}^{\,})$.
+where $\sigma$ is the clock model standard deviation, $p(\mathcal{T}|\theta)$ is the tree prior, and $\theta$ describes other unspecified parameters. 
+The tree likelihood $p(D|\mathcal{T}, r(\vec{\mathcal{R}}^{\,}), \theta)$ is computed using Felsenstein's tree-peeling algorithm \cite{felsenstein1981evolutionary}, where
+$\vec{\mathcal{R}}^{\,}$ is a vector of abstracted substitution rates and transformed into real rates by function $r(\vec{\mathcal{R}}^{\,})$.
 Three methods of representing rates as $\vec{\mathcal{R}}^{\,}$ are presented in \textbf{\nameref{sect:rateparams}}.
@@
 
+\clearpage
 \subsection*{Substitution rate parameterisations}
@@
 
-This method has been widely used in BEAST and BEAST2 analyses \cite{drummond2006relaxed}. 
-However, the recently developed constant distance operators  -- which are incompatible with the \textit{cat} parameterisation -- yield an increase in mixing rate under \textit{real} by up to an order of magnitude over that of \textit{cat} \cite{zhang2020improving}.
+This parameterisation has been widely used in BEAST and BEAST2 analyses \cite{drummond2006relaxed}. 
+However, the recently developed constant distance operators  -- which are incompatible with the \textit{cat} parameterisation -- can yield an increase in mixing rate under \textit{real} by up to an order of magnitude over that of \textit{cat}, depending on the dataset \cite{zhang2020improving}.
 
@@
 
-Transforming these quantiles into rates invokes the i-cdf of the underlying \textit{real} clock model distribution.
-Thus, while this approach has clear similarities with \textit{cat}, the domain of rates here is continuous (as opposed to being confined to a discrete number of bins) and is therefore compatible with constant distance operators \cite{zhang2020improving}.
-
-A potential disadvantage of the \textit{quant} method would be the computational requirements of continuously evaluating the i-cdf.
-As the number of quantiles grows with the taxon count $N$, this drawback would be at its worst on large trees.
-Hence, rather than evaluating the exact i-cdf $F^{-1}$, an approximation $\hat{F}^{-1}$ will be used instead:
+Transforming these quantiles into rates invokes the i-cdf of the underlying \textit{real} clock model distribution:
 
 \begin{align}
-r(\mathcal{R}_i) =& \; \hat{F}^{-1}(\mathcal{R}_i).
+r(\mathcal{R}_i) =& \; F^{-1}(\mathcal{R}_i).
 \end{align}
 
-In this article we have extended \textit{quant} through a linear piecewise approximation of the i-cdf.
+While this approach has clear similarities with \textit{cat}, the domain of rates here is continuous (as opposed to being confined to a discrete number of bins).
+In this project we extended the family of constant distance operators  \cite{zhang2020improving} so they are compatible with \textit{quant}.
+These are presented in \textbf{\nameref{sect:S1Appendix}}.
+
+%A potential disadvantage of the \textit{quant} method would be the computational requirements of continuously evaluating the i-cdf.
+%As the number of quantiles grows with the taxon count $N$, this drawback would be at its worst on large trees.
+%Hence, rather than evaluating the exact i-cdf $F^{-1}$, an approximation $\hat{F}^{-1}$ will be used instead:
+
+%\begin{align}
+%r(\mathcal{R}_i) =& \; \hat{F}^{-1}(\mathcal{R}_i).
+%\end{align}
+
+%In this article we have extended \textit{quant} through a linear piecewise approximation of the i-cdf.
 As the piecewise approximation is linear, evaluating the derivatives $\frac{\partial}{\partial \mathcal{R}_i} \hat{F}^{-1}(\mathcal{R}_i) =  D \hat{F}^{-1}(\mathcal{R}_i)$ and $\frac{\partial}{\partial r_i} \hat{F}(r_i) = D \hat{F}(r_i)$  -- which are required for computing the Hastings ratios -- is trivial.
@@
 
-Zhang and Drummond 2020 introduced several tree operators for the \textit{real} parameterisation -- including \texttt{Constant Distance}, \texttt{Simple Distance}, and \texttt{Small Pulley}.
+%Zhang and Drummond 2020 introduced several tree operators for the \textit{real} parameterisation -- including \texttt{Constant Distance}, \texttt{Simple Distance}, and \texttt{Small Pulley}.
 In this project, we extended these three operators so that they are compatible with the \textit{quant} parameterisation.
@@
 
+\clearpage
+\subsection*{Adaptive operator weighting}
+\label{sect:adaptiveSampling}
+
+The weight of an operator determines the probability of the operator being selected at each step during MCMC.
+In BEAST2, operators can have a tunable parameter $s$ which determines the step size of the operator \cite{bouckaert2019beast}. 
+Although $s$ is learned throughout the MCMC chain, the operator weights themselves are typically held constant.
+Pre-existing BEAST2 clock model operators (i.e.
+those which generate proposals for either $\mathcal{R}$ or $\sigma$) are summarised in \textbf{Table \ref{table:kernels}}, and further operators are introduced throughout the paper.
+
+% Section intro
+% Give some examples of this operator working better on this dataset but not that one, where both operators apply to the same parameter eg. Constant Distance? Any others?
+% Bring up theme that this can be related to signal.
+Sampling from the prior may give better results when there is poor signal, whereas random-walk based operators may do better in the other case.
+Any general theoretical examples of this?
+
+\begin{table}[h!]
+\centering
+\begin{tabular}{|l| l p{4cm} l l|} 
+ \hline
+ & Operator & Description & Parameters & Parameterisations  \\
+  \hline
+ 1 & \texttt{RandomWalk} & Moves a single element by a tunable amount. & $\mathcal{R}, \sigma$ & \textit{cat}, \textit{real}, \textit{quant} \\
+  \hline
+ 2 & \texttt{Scale} & Applies \texttt{RandomWalk} on the log-transformation (suitable for parameters with positive domains). & $\mathcal{R}, \sigma$ & \textit{real}, \textit{quant}  \\
+  \hline
+ 3 & \texttt{Interval} & Applies \texttt{RandomWalk} on the logit-transformation (suitable for parameters with upper and lower limits). & $\mathcal{R}$ & \textit{quant}  \\
+  \hline
+   4 & \texttt{Swap} & Swaps two random elements in the vector \cite{drummond2006relaxed}. & $\mathcal{R}$  & \textit{cat}, \textit{real}, \textit{quant}  \\
+ \hline
+  5 & \texttt{Uniform} & Resamples one element in the vector from a uniform distribution. & $\mathcal{R}$  & \textit{cat}, \textit{quant}  \\
+ \hline
+ 6 & \texttt{ConstantDistance} & Adjusts an internal node and recalculates all incident branch rates such that the genetic distances remain constant \cite{zhang2020improving}.
+& $\mathcal{R}, \mathcal{T}$ & \textit{real}, \textit{quant} \\
+ \hline
+ 7 & \texttt{SimpleDistance} & Applies \texttt{SimpleDistance} to the root node \cite{zhang2020improving}.  & $\mathcal{R}, \mathcal{T}$ & \textit{real}, \textit{quant} \\
+ \hline
+ 8 & \texttt{SmallPulley} & Proposes new branch rates incident to the root such that their combined genetic distance is constant  \cite{zhang2020improving}.
+& $\mathcal{R}$ & \textit{real}, \textit{quant} \\
+ \hline
+ 9 & \texttt{FastClockScale} & Applies \texttt{Scale} to $\sigma$ and then recomputes all rates $\mathcal{R}$ such that their quantiles under the prior $p(\mathcal{R}|\sigma)$ are constant \cite{zhang2020improving}.
+& $\mathcal{R}$ & \textit{real} \\
+ \hline
+\end{tabular}
+\caption{Summary of pre-existing BEAST2 operators which apply to either branch rates $\mathcal{R}$ or the clock standard deviation $\sigma$, and the substitution rate parameterisation they apply to.
+ \texttt{ConstantDistance} and \texttt{SimpleDistance} also adjust tree node heights. }
+\label{table:kernels}
+\end{table}
+
+It is not always clear which mixture of operators is best for a given dataset.
+In this article we introduce \texttt{AdaptiveOperatorSampler} -- a meta-operator which learns operator weights during MCMC and samples operators according to these weights.
+The meta-operator undergoes three phases.
+In the first phase (burn-in), \texttt{AdaptiveOperatorSampler} samples from its set of sub-operators uniformly at random.
+In the second phase (learn-in), the meta-operator continues to sample operators uniformly at random however it begins learning several terms detailed below.
+In its final phase, \texttt{AdaptiveOperatorSampler} samples operators (denoted by $\omega$) using the following distribution:
+
+\begin{align}
+\label{eqn:adaptiveSampler}
+	p(\omega_i) \propto \begin{cases} 1 & \text{ with probability } \Omega \\ \frac{1}{\mathbb{T}(\omega_i)} \sum\limits_{p \in \text{parameters}} \frac{1}{\sigma^2_p} \Big[ \sum\limits_{x \in \text{accepts}_i}  (x_p - x_p^\prime)^2 \Big] & \text{ with probability } 1-\Omega \end{cases}.
+\end{align}
+
+where $\Omega = 0.01$ allows any sub-operator to be sampled regardless of its performance.
+The remaining terms are trained during the second and third phases: the cumulative computational runtime spent on each operator $\mathbb{T}(\omega_i)$, the sample variance $\sigma^2_p$ of each parameter $p$, and the sum-of-squares $\sum\limits_{x \in \text{accepts}_i} (x_p - x_p^\prime)^2$, where $x_p$ and $x_p^\prime$ are the values of $p$ before and after each acceptance of a proposal made by $\omega_i$.
+
+%The terms which are learned during the second and third phases are: ,
+
+Under Equation \ref{eqn:adaptiveSampler}, operators which effect larger changes on the parameters of interest, in shorter runtime, are sampled with greater probabilities. 
+Division of the sum-of-squares term by the parameter variance $\sigma^2_p$ enables comparison between different parameters.
+
+We also introduce the \texttt{SampleFromPrior($\vec{x}^{\,}$)} operator.
+This operator resamples $\psi$ randomly selected elements within vector $\vec{x}^{\,}$ from their prior distributions, where $\psi \sim \text{Binomial}(n=|\vec{x}^{\,}|, p=\frac{s}{|\vec{x}^{\,}|})$ for tunable parameter $s$.
+
+We hypothesis that datasets with strong signal (or large $L$) will mix best when the more precise and meticulous kind of operator is employed, such as those informed by correlations within the posterior distribution e.g.
+the family of constant distance operators \cite{zhang2020improving}.
+Whereas, datasets which contain very poor signal (or small $L$) are likely to mix best when there is more weight placed on bold operators such as \texttt{SampleFromPrior}, \texttt{Swap}, or \texttt{Uniform} which sample each branch rate independently of its current estimate.
+\texttt{AdaptiveOperatorSampler} should learn the combination of weights behind these classes of operators best suited for the dataset.
+
+In this article we apply three instances of the \texttt{AdaptiveOperatorSampler} meta-operator to the \textit{real} and \textit{quant} parameterisations. 
+These are summarised in \textbf{Table \ref{table:adaptiveSampling}}.
+
+\begin{table}[h!]
+\centering
+\begin{tabular}{|l p{4cm}|} 
+ \hline
+ Meta-operator & Operators \\
+\hline
+ \multirow{4}{*}{\texttt{AdaptiveOperatorSampler($\sigma$)}} & \texttt{FastClockScale($\sigma, \mathcal{R}$)}$^{*}$ \\ 
+ & \texttt{RandomWalk($\sigma$)} \\
+ & \texttt{Scale($\sigma$)} \\
+ & \texttt{SampleFromPrior($\sigma$)} \\
+ \hline
+  \multirow{6}{*}{\texttt{AdaptiveOperatorSampler($\mathcal{R}$)}} & \texttt{ConstantDistance($\mathcal{R}, \mathcal{T}$)} \\ 
+& \texttt{RandomWalk($\mathcal{R}$)} \\
+& \texttt{Scale($\mathcal{R}$)}$^{*}$ \\
+& \texttt{Interval($\mathcal{R}$)}$^{**}$  \\
+& \texttt{Swap($\mathcal{R}$)} \\
+& \texttt{SampleFromPrior($\mathcal{R}$)} \\
+ \hline
+   \multirow{2}{*}{\texttt{AdaptiveOperatorSampler(root)}} & \texttt{SimpleDistance($\mathcal{R}, \mathcal{T}$)} \\ 
+&  \texttt{SmallPulley($\mathcal{R}, t$)}\\
+ \hline
+\end{tabular}
+\caption{Summary of the three instances of \texttt{AdaptiveOperatorSampler} used under the \textit{real} and \textit{quant} parameterisations.  $^{*}$\textit{real} only. $^{**}$\textit{quant} only. }
+\label{table:adaptiveSampling}
+\end{table}
+
+%\texttt{AdaptiveOperatorSampler($\sigma$)} samples the clock standard deviation, 
+%\texttt{AdaptiveOperatorSampler($\mathcal{R}$)} samples branch rates and internal node heights,
+%and \texttt{AdaptiveOperatorSampler(root)} samples
+
+\clearpage
 \subsection*{Bactrian proposal kernel} \label{sect:randomwalks}
@@
 Two Bactrian distributions are compared($m=0.95$ and $m=0.98$).
-The clock model operators which these proposal kernels apply to are described in \textbf{Table \ref{table:kernels}}.
+The clock model operators which these proposal kernels apply to are described in \textbf{Table \ref{table:bactriankernels}}.
+
+\begin{table}[h!]
+\centering
+\begin{tabular}{|l| p{3cm} l l|} 
+ \hline
+ & Operator(s) & Proposal & Parameter $x$   \\
+  \hline
+ 1 & \texttt{RandomWalk}  & $x^\prime \leftarrow x + s\Sigma$ & $\mathcal{R}, \sigma$  \\
+  \hline
+ 2 & \texttt{Scale} & $x^\prime \leftarrow x \times e^{s\Sigma}$ & $\mathcal{R}, \sigma$   \\
+  \hline
+ 3 & \texttt{Interval} & $\begin{array} {rl} &y \leftarrow \frac{1 - x}{x} \times e^{s\Sigma} \\ &x^\prime \leftarrow \frac{y}{y + 1}  \end{array}$ & $\mathcal{R}$  \\
+  \hline
+ 4 & \texttt{ConstantDistance} \texttt{SimpleDistance} & $x^\prime \leftarrow x + s\Sigma$ & $t$ \\
+ \hline
+ 5 & \texttt{SmallPulley} & $x^\prime \leftarrow x + s\Sigma$ & $\mathcal{R}$  \\
+ \hline
+6 & \texttt{FastClockScale}  & $x^\prime \leftarrow x \times e^{s\Sigma}$ & $\sigma$   \\
+ \hline
+\end{tabular}
+\caption{Proposal kernels $q(x^\prime|x)$ of clock model operators.
+ In each operator, $\Sigma$ is drawn from either a $\text{Bactrian}(m)$ or $\text{Uniform}$ distribution (distributions are normalised so that they have a mean of 0 and a variance of 1). 
+ The scale size $s$ is tunable.
+ \texttt{ConstantDistance} and \texttt{SimpleDistance} propose tree heights $t$.
+  The \texttt{Interval} operator applies to rate quantiles and respects its domain i.e. $0 < x, x^\prime < 1$. }
+\label{table:bactriankernels}
+\end{table}
 
@@
 
-\begin{table}[h!]
-\centering
-\begin{tabular}{|l| l l l|} 
- \hline
- & Operator & Proposal & Parameters  \\
- 1 & \texttt{Random walk} operator & $x^\prime \leftarrow x + s\Sigma$ & $\sigma, r, q$ \\
- 2 & \texttt{Scale} operator & $x^\prime \leftarrow x \times e^{s\Sigma}$ & $\sigma, r$  \\
- 3 & \texttt{Interval} operator & $\begin{array} {rl} y &\leftarrow \frac{u - x}{x - l} \times e^{s\Sigma} \\ x^\prime &\leftarrow \frac{u + l * y}{y + 1}  \end{array}$ & $q \;\; (l=0,u=1)$  \\
- 4 & \texttt{Constant distance} operator & $x^\prime \leftarrow x + s\Sigma$ & $t$ \\
-
- \hline
-\end{tabular}
-\caption{Summary of proposal kernels $q(x^\prime|x)$ of clock model operators.
-\texttt{Random walk}, \texttt{Scale}, and \texttt{Interval} are standard BEAST2 operators.
- In each operator, $\Sigma$ is drawn from either a $\text{Bactrian}(m)$ or $\text{Uniform}$ distribution (distributions are normalised so that they have a mean of 0 and a variance of 1).
-The scale size $s$ is tunable.
-The proposal kernel may apply to node heights $t$, clock standard deviation $\sigma$, clock rates $r$ (\textit{real} only), and clock rate quantiles $q$ (\textit{quant} only).
-The Scale operator acts on parameters with non-negative domains.
-The Interval operator proposes values which respect the domain of the parameter i.e.
-$l < x, x^\prime < u$.
-}
-\label{table:kernels}
-\end{table}
-
 % $x^\prime \leftarrow w \times \frac{u - x}{x - l}$
 
-\newpage
+\clearpage
 % REMEMBER to define NNI and SPR acronyms in introduction preferably
@@
 
-The \texttt{Narrow Exchange} operator \cite{drummond2002estimating}, widely used in BEAST \cite{drummond2012bayesian,suchard2018bayesian} and BEAST2 \cite{bouckaert2019beast}, is similar to NNI, and works as follows (\textbf{Fig.
+The \texttt{NarrowExchange} operator \cite{drummond2002estimating}, used widely in BEAST \cite{drummond2012bayesian,suchard2018bayesian} and BEAST2 \cite{bouckaert2019beast}, is similar to nearest neighbour interchange (NNI), and works as follows (\textbf{Fig.
 \ref{fig:narrowexchange}}):
@@
 \includegraphics[width=\textwidth]{Figures/NarrowExchange.pdf}
-\caption{\textbf{Depiction of \texttt{Narrow Exchange} and \texttt{Narrow Exchange Rate} operators.} Proposals are denoted by $\mathcal{T} \rightarrow \mathcal{T}^\prime$.
+\caption{\textbf{Depiction of \texttt{NarrowExchange} and \texttt{NarrowExchangeRate} operators.} Proposals are denoted by $\mathcal{T} \rightarrow \mathcal{T}^\prime$.
 The vertical axis corresponds to node height $t$.
@@
 Lakner et al.
-2008 \cite{lakner2008efficiency} found that tree operators which perterb topology (such as NNI and SPR) consistently perform better than those which also change branch lengths (such as LOCAL \cite{simon1998local} and Continuous Change \cite{jow2002bayesian}).
-If \texttt{Narrow Exchange} was adapted to the relaxed clock model by ensuring that genetic distances remain constant after the proposal, its performance may be improved even further.
+2008 \cite{lakner2008efficiency} found that tree operators which perterb topology (such as NNI) consistently perform better than those which also change branch lengths (such as LOCAL \cite{simon1998local} and Continuous Change \cite{jow2002bayesian}).
+If \texttt{NarrowExchange} could be adapted to the relaxed clock model by ensuring that genetic distances remain constant after the proposal, its performance may be improved even further. 
 This may in turn permit proposing a new node height $t_D$ and therefore changing branch (time) lengths.
@@
 
-Here, we present the \texttt{Narrow Exchange Rate} (NER) operator.
+Here, we present the \texttt{NarrowExchangeRate} (NER) operator. 
 Let $r_A$, $r_B$, $r_C$, and $r_D$ be the clock rates of nodes $A$, $B$, $C$, and $D$, respectively. 
-In addition to the modest topological change applied by \texttt{Narrow Exchange}, NER also proposes new clock rates ${r_A}^\prime$, ${r_B}^\prime$, ${r_C}^\prime$, and ${r_D}^\prime$.
+In addition to the modest topological change applied by \texttt{NarrowExchange}, NER also proposes new clock rates ${r_A}^\prime$, ${r_B}^\prime$, ${r_C}^\prime$, and ${r_D}^\prime$.
 While NER does not alter $t_D$ (i.e.
@@
 NER (and NERw) are compatible with both the \textit{real} and \textit{quant} parameterisations.
-Analagous to the \texttt{Constant Distance} operator, new rates are proposed such that genetic distances between nodes $A$, $B$, $C$, and $E$ are maintained.
+Analagous to the \texttt{ConstantDistance} operator, new rates are proposed such that genetic distances between nodes $A$, $B$, $C$, and $E$ are maintained.
 Thus, there are $\binom{4}{2} = 6$ pairwise distance constraints.
@@
 The simplest NER -- the null operator denoted by NER$\{\}$ -- does not satisfy any distance constraints. 
-This is equivalent to \texttt{Narrow Exchange}.
+This is equivalent to \texttt{NarrowExchange}.
 
@@
 
+\clearpage
 \subsection*{A guided adaptive leaf rate operator}
@@
 In this article we consider application of the AVMVN kernel to the branch rates of leaf nodes. 
-This operator is not readily applicable to internal node branch rates due to their dependencies on tree topology.
+This operator, referred to as \texttt{LeafAVMVN}, is not readily applicable to internal node branch rates due to their dependencies on tree topology.
 
@@
 
-In \nameref{sect:results}, we evaluate this operator for its ability to estimate leaf rates.
+In \nameref{sect:results}, we evaluate the \texttt{LeafAVMVN} operator for its ability to estimate leaf rates. 
 As the size of the covariance matrix $\Sigma_N$ grows with the number of taxa $N$, AVMVN is hypothesised to work well on small trees but become less efficient with larger taxon sets.
 
+\clearpage
 \section*{Results} \label{sect:results}
+
+Throughout \nameref{sect:models}, we introduced four new operators which are applied to the relaxed clock. 
+These operators are summarised in \textbf{Table \ref{table:newOperators}} and are applied in conjunction with the pre-existing clock model operators presented in \textbf{Table \ref{table:kernels}}.
+
+\begin{table}[h!]
+\centering
+\begin{tabular}{|l| l p{4cm} l|} 
+ \hline
+ & Operator & Description & Parameters  \\
+  \hline
+1 & \texttt{AdaptiveOperatorSampler} & Samples sub-operators proportionally to their weights, which are learned (see \nameref{sect:adaptiveSampling}). & $\mathcal{R}, \sigma, \mathcal{T}$ \\
+  \hline
+2 & \texttt{SampleFromPrior} & Resamples a random number of elements from their prior (see \nameref{sect:adaptiveSampling}). & $\mathcal{R}, \sigma$ \\
+  \hline
+3 & \texttt{NarrowExchangeRate} & Moves a branch and recomputes branch rates so that genetic distances are constant (see \nameref{sect:NER}). & $\mathcal{R}, \mathcal{T}$\\
+  \hline
+4 & \texttt{LeafAVMVN}  & Proposals new rates for all leaves in one move (see \nameref{AVMVN_sect}) \cite{baele2017adaptive}. & $\mathcal{R}$ \\
+  \hline
+\end{tabular}
+\caption{Summary of clock model operators introduced throughout this article.}
+\label{table:newOperators}
+\end{table}
 
@@
 
-To avoid a cross-product explosion, the four targets for clock model improvement (\textbf{\nameref{sect:rateparams}}, \textbf{\nameref{sect:randomwalks}}, \textbf{\nameref{sect:NER}}, and \textbf{\nameref{AVMVN_sect}}) are evaluated sequentially, in the order presented in this paper.
-The setting which is considered to be the best in each step is then incorporated into the following step.
-This protocol and its outcomes are summarised in \textbf{Fig.
-\ref{fig:tournament}}.
+To avoid a cross-product explosion, the five targets for clock model improvement are evaluated sequentially in the following order: \textbf{\nameref{sect:adaptiveSampling}} \textbf{\nameref{sect:rateparams}}, \textbf{\nameref{sect:randomwalks}}, \textbf{\nameref{sect:NER}}, and \textbf{\nameref{AVMVN_sect}}.
+
+ The setting which is considered to be the best in each step is then incorporated into the following step. This protocol and its outcomes are summarised in \textbf{Fig. \ref{fig:tournament}}.
 
@@
 
-\subsection*{Evaluating constant distance operators}
+\clearpage
+\subsection*{Round 1: A simple operator weight learning algorithm can improve performance}
 
-\subsection*{Comparison of rate parameterisations}
+We compared the cons, nocons, and adapt operator configurations for the \textit{real} and \textit{quant} parameterisations (\textbf{Table \ref{table:round1Results}}).
+The nocons configuration contained the standard BEAST2 operator mix, while cons contained the operator mix used by Zhang and Drummond 2020 \cite{zhang2020improving}. 
+The adapt mix combines the above operators, as well as the rudimentary \texttt{SampleFromPrior} operator, and learns the weights of each operator using  \texttt{AdaptiveOperatorSampler}.
+
+\begin{table}[h!]
+\centering
+\begin{tabular}{|l l l l|} 
+ \hline
+Configuration & Operator & Weight & Parameterisations  \\
+  \hline
+ \multirow{6}{*}{nocons} & \texttt{RandomWalk($\mathcal{R}$)} & $10$ & \textit{real}  \\
+ 	& \texttt{Scale($\mathcal{R}$)} & $10$ & \textit{real} \\ 
+ 	& \texttt{Uniform($\mathcal{R}$)} & $10$ & \textit{quant} \\ 
+ 	& \texttt{Interval($\mathcal{R}$)} & $10$ & \textit{quant} \\ 
+ 	& \texttt{Swap($\mathcal{R}$)} & $10$ & \textit{real}, \textit{quant} \\ 
+ 	& \texttt{Scale($\sigma$)} & $10$ & \textit{real}, \textit{quant} \\ 
+  \hline
+   \multirow{10}{*}{cons} 
+   & \texttt{ConstantDistance($\mathcal{R}, \mathcal{T}$)} & $20 \times \frac{2N-2}{2N-1}$ & \textit{real}, \textit{quant}  \\
+   & \texttt{SimpleDistance($\mathcal{R}, \mathcal{T}$)} & $10 \times \frac{2N-2}{2N-1}$ & \textit{real}, \textit{quant}  \\
+   & \texttt{SmallPulley($\mathcal{R}$)} & $10 \times \frac{2N-2}{2N-1}$ & \textit{real}, \textit{quant}  \\
+   & \texttt{RandomWalk($\mathcal{R}$)} & $5$ & \textit{real}  \\
+ 	& \texttt{Scale($\mathcal{R}$)} & $2.5$ & \textit{real} \\ 
+ 	& \texttt{Uniform($\mathcal{R}$)} & $5$ & \textit{quant} \\ 
+ 	& \texttt{Interval($\mathcal{R}$)} & $2.5$ & \textit{quant} \\ 
+ 	& \texttt{Swap($\mathcal{R}$)} & $2.5$ & \textit{real}, \textit{quant} \\ 
+ 	& \texttt{FastClockScale($\sigma$)} & $10$ & \textit{real}  \\ 
+ 	& \texttt{Scale($\sigma$)} & $10$ &  \textit{quant} \\ 
+  \hline
+     \multirow{3}{*}{adapt} & \texttt{AdaptiveOperatorSampler($\sigma$)} & $10$ & \textit{real}, \textit{quant} \\
+ 	& \texttt{AdaptiveOperatorSampler($\mathcal{R}$)} & $30 \times \frac{2N-2}{2N-1}$ & \textit{real}, \textit{quant} \\
+ 	& \texttt{AdaptiveOperatorSampler(root)} & $30 \times \frac{1}{2N-1}$ & \textit{real}, \textit{quant} \\
+  \hline
+
+\end{tabular}
+\caption{Operator configurations for Round 1.
+In each configuration, the weight behind $\mathcal{R}$ sums to 30 and for $\sigma$ is equal to 10 within any one rate parameterisation.
+Operators which apply to either internal nodes or the root (but not both) weighted according to leaf count $N$.}
+\label{table:round1Results}
+\end{table}
+
+These results show that, while nocons gives better performance than cons on smaller datasets (corresponding to low signal), and cons performs better on larger datasets (high signal), the adapt configuration gives the best performance overall.
+This trend is observed for both the \textit{real} and the \textit{quant} parameterisations.
+Therefore, the \texttt{AdaptiveOperatorSampler} operator will be included in all subsequent rounds in the tournament.
+
+\clearpage
+\subsection*{Round 2: The three rate parameterisations yield similar mixing ability }
 
 We compared the three rate parameterisations described in \textbf{\nameref{sect:rateparams}}. 
-All three settings use the standard BEAST2 clock model operators from Drummond et al.
-2006 \cite{drummond2006relaxed}.
-\textit{real} and \textit{quant} additionally use the constant-distance tree operators \cite{zhang2020improving}.
-To determine whether the difference in performance between \textit{real}/\textit{quant} versus \textit{cat} is because of the constant-distance tree operators or the parameterisation itself, we also included benchmarked two additional settings: \textit{real 2006} and \textit{quant 2006}, which do not used the constant-distance operators.
-These five settings are validated in \textbf{\nameref{sect:WCSS_appendix}}.
+The \textit{cat} operator configuration is described in \textbf{Table \ref{table:round2Results}}.
+\textit{real} and \textit{quant} make use of constant distance tree operators \cite{zhang2020improving} and both use the \texttt{AdaptiveOperatorSampler} operator to learn clock model operator weights.
+The three settings are validated in \textbf{\nameref{sect:WCSS_appendix}}.
+
+\begin{table}[h!]
+\centering
+\begin{tabular}{|l l l|} 
+ \hline
+Configuration & Operator & Weight  \\
+  \hline
+ \multirow{4}{*}{\textit{cat}} 
+ 	& \texttt{RandomWalk($\mathcal{R}$)} & $10$ \\
+ 	& \texttt{Uniform($\mathcal{R}$)} & $10$  \\ 
+ 	& \texttt{Swap($\mathcal{R}$)} & $10$ \\ 
+ 	& \texttt{Scale($\sigma$)} & $10$ \\ 
+  \hline
+\end{tabular}
+\caption{Operator configurations for \textit{cat} in Round 2. The configurations of \textit{real} (adapt) and \textit{quant} (adapt) are shown in \textbf{Table \ref{table:round1Results}}.}
+\label{table:round2Results}
+\end{table}
 
@@
 
-\subsection*{Comparison of Bactrian and uniform proposal kernels on the clock model}
+\subsection*{Round 3: The Bactrian proposal kernel is the best for the clock model}
 
-\subsection*{Comparison of NER variants}
+\subsection*{Round 4: Finding the best NER operator variant}
 

### 2020-07-28 manuscript.tex
fig1 update

@@
 In Bayesian phylogenetics, these trees and their associated parameters are estimated as probabilitiy distributions \cite{kuhner1995estimating, larget1999markov, mau1999bayesian}. 
-Statistical inference is typically performed by sampling under the Metropolis-Hastings Markov chain Monte Carlo (MCMC) algorithm \cite{metropolis53, hastings70}.
+Statistical inference is typically performed by sampling using the Markov chain Monte Carlo (MCMC) algorithm \cite{metropolis53, hastings70}.
 Bayesian phylogenetic clock models have been implemented in many platforms including BEAST \cite{drummond2012bayesian}, BEAST2 \cite{bouckaert2019beast}, MrBayes \cite{ronquist2012mrbayes}, and RevBayes \cite{hohna2016revbayes}.
@@
 adaptive multivariate transition kernels \cite{baele2017adaptive},
-and other explorative proposal kernels including the Bactrian and mirror kernels \cite{yang2013searching, thawornwattana2018designing}.
-In the case of clock models, smart tree proposals can account for correlations between substitution rates and divergence times \cite{zhang2020improving}. 
+and other explorative proposal kernels such as the Bactrian and mirror kernels \cite{yang2013searching, thawornwattana2018designing}.
+In the case of clock models, informed tree proposals can account for correlations between substitution rates and divergence times \cite{zhang2020improving}. 
 The rate parameterisation itself can also affect the ability to ``mix'' during MCMC \cite{drummond2006relaxed, li2012model, zhang2020improving}.
@@
 \label{eq:bayesian}
-p(\mathcal{T}, \vec{\mathcal{R}}^{\,}, \sigma, \theta|D) \propto  p(D|\mathcal{T}, r(\vec{\mathcal{R}}^{\,}), \theta) \; p(\mathcal{T}|\theta) \;  p(\vec{\mathcal{R}}^{\,} | \sigma) \; p(\sigma) \; p(\theta),
+p(\mathcal{T}, \vec{\mathcal{R}}^{\,}, \sigma, \theta|D) \propto  p(D|\mathcal{T}, r(\vec{\mathcal{R}}^{\,}), \theta) \; p(\mathcal{T}|\theta) \;  p(\vec{\mathcal{R}}^{\,} | \sigma) \; p(\sigma) \; p(\theta).
 \end{eqnarray}
 
-where $\sigma$ is the clock model standard deviation, $p(\mathcal{T}|\theta)$ is the tree prior, and $\theta$ describes other unspecified parameters. 
-The tree likelihood $p(D|\mathcal{T}, r(\vec{\mathcal{R}}^{\,}), \theta)$ is computed using Felsenstein's tree-peeling algorithm \cite{felsenstein1981evolutionary}, where
+$\sigma$ represents clock model related parameters, and $p(\mathcal{T}|\theta)$ is the tree prior where $\theta$ describes further unspecified parameters. 
+The tree likelihood $p(D|\mathcal{T}, r(\vec{\mathcal{R}}^{\,}), \theta)$ is computed using the tree-peeling algorithm \cite{felsenstein1981evolutionary}, where
 $\vec{\mathcal{R}}^{\,}$ is a vector of abstracted substitution rates and transformed into real rates by function $r(\vec{\mathcal{R}}^{\,})$.
@@
 Let $t_i$ be the height (time) of node $i$.
-Every internal and leaf node $i$ in $\mathcal{T}$ is associated with a parental branch length (the height difference between $i$ and its parent) $\tau_i$ and a parental branch substitution rate $r_i = r(\mathcal{R}_i)$.
-There are a total of $2N-2$ internal and leaf nodes. 
-Under the relaxed clock model, each $\mathcal{R}_i$ is independently distributed under the prior.
-
-The posterior distribution is sampled by MCMC.
-The probability of accepting proposed state $x^\prime$ from state $x$ is calculated using the Metropolis-Hastings ratio \cite{metropolis53, hastings70}:
+Each node $i$ in $\mathcal{T}$, except for the root, is associated with a parental branch length $\tau_i$ (the height difference between $i$ and its parent)  and a parental branch substitution rate $r_i = r(\mathcal{R}_i)$.
+In a relaxed clock model, each of the $2N-2$ elements in $\mathcal{R}_i$ are independently distributed under the prior $p(\vec{\mathcal{R}}^{\,} | \sigma)$.
+
+The posterior distribution is sampled by the Metropolis-Hastings-Green MCMC algorithm \cite{metropolis53, hastings70, green1995reversible},
+under which the probability of accepting proposed state $x^\prime$ from state $x$ is equal to:
 
@@
 \label{eq:MCMC}
-\alpha(x^\prime|x) =  \min\left( 1, \frac{p(x^\prime|D)}{p(x|D)} \frac{q(x|x^\prime)}{q(x^\prime|x)} \right).
+\alpha(x^\prime|x) =  \min\left( 1, \frac{p(x^\prime|D)}{p(x|D)} \; \frac{q(x|x^\prime)}{q(x^\prime|x)} \; |J| \right).
 \end{eqnarray}
@@
 $q(a|b)$ is the transition kernel: the probability of proposing state $b$ from state $a$.
-The ratio between the two $\frac{q(x|x^\prime)}{q(x^\prime|x)}$ is known as the Hastings ratio \cite{hastings70}.
+The ratio between the two $\frac{q(x|x^\prime)}{q(x^\prime|x)}$ is also known as the Hastings ratio \cite{hastings70}.
+The determinant of the Jacobian matrix $|J|$ solves the dimension-matching problem for proposals which operate on multiple terms across one or more spaces \cite{green1995reversible, geyer2003metropolis}.
+This term is known as the Green ratio.
 
@@
 In Bayesian inference, the way parameters are represented in the model can affect the mixing ability of the model and the meaning of the model itself \cite{gelman2004parameterization}.
-Three methods for parameterising substitution rates are described below, and are later evaluated in \textbf{\nameref{sect:results}}.
-Each parameterisation technique is associated with i) an abstraction of the rates $\vec{\mathcal{R}}^{\,}$, ii) some function for transforming this parameter into real rates $r(\vec{\mathcal{R}}^{\,})$, and iii) a prior density function of the abstraction $p(\vec{\mathcal{R}}^{\,} | \sigma) $.
+Three methods for parameterising substitution rates are described below.
+ Each parameterisation is associated with i) an abstraction of the branch rate vector $\vec{\mathcal{R}}^{\,}$, ii) some function for transforming this parameter into unabstracted branch rates $r(\vec{\mathcal{R}}^{\,})$, and iii) a prior density function of the abstraction $p(\vec{\mathcal{R}}^{\,} | \sigma) $.
  The three methods are summarised in \textbf{Fig \ref{fig:rateparams}}.
@@
 \includegraphics[width=\textwidth]{Figures/rateparameterisation.pdf}
-\caption{\textbf{Methods of rate parameterisation.} The \textit{cat} and \textit{quant} approximations are plotted on top of the true underlying rate prior distribution (\textit{real}).
-In this example, rates are drawn from a $\text{LogNormal}(\mu = -0.045, \sigma = 0.3)$ distribution.
-The probability density function (pdf) and cumulative density function (cdf) of this distribution are shown.}
+\caption{\textbf{Branch rate parameterisations.} Top left: the branch rate prior under a log-normal($-0.5\sigma^2, \sigma$) distribution (with a mean of 1). 
+The function for transforming $\mathcal{R}$ into branch rates $r(\mathcal{R})$ is depicted for \textit{real} (top right), \textit{cat} (bottom left), and \textit{quant} (bottom right).
+For simplicity there are 10 \textit{cat} bins displayed, however in practice there are $2N-2$ bins. }
 \label{fig:rateparams}
@@
 
-We hypothesis that datasets with strong signal (or large $L$) will mix best when the more precise and meticulous kind of operator is employed, such as those informed by correlations within the posterior distribution e.g.
+We hypothesise that datasets with strong signal (or large $L$) will mix best when the more precise and meticulous kind of operator is employed, such as those informed by correlations within the posterior distribution e.g.
 the family of constant distance operators \cite{zhang2020improving}.
@@
 To facilitate convergence on complex datasets, each posterior distribution is sampled using coupled MCMC (MC$^3$) with 4 chains \cite{muller2019coupled}.
-Each methodology is benchmarked across 5 replicates on each dataset, using an the Intel Xeon Gold 6138 CPU (2.00 GHz).
+Each methodology is benchmarked across 5 replicates on each dataset, using an the Intel Xeon Gold 6138 CPU (2.00 GHz) and all methodologies use identical models and operator configurations, except where a difference is specified.
 
@@
   & $N$ & $P$ & $L$ (kb) & $L_\text{eff}$ (kb) & \textbf{Description} \\
+  \hline
 
@@
 \clearpage
-\subsection*{Round 1: A simple operator weight learning algorithm can improve performance}
+\subsection*{Round 1: A simple operator-weight learning algorithm can improve performance}
 
@@
 In each configuration, the weight behind $\mathcal{R}$ sums to 30 and for $\sigma$ is equal to 10 within any one rate parameterisation.
-Operators which apply to either internal nodes or the root (but not both) weighted according to leaf count $N$.}
+Operators which apply to either internal nodes or the root (but not both) weighted according to leaf count $N$.
+The adapt operators are further broken down in \textbf{Table \ref{table:adaptiveSampling}}.}
 \label{table:round1Results}

### 2020-07-28 lognormal.R

@@ -1,160 +1,24 @@
 
 library(tikzDevice)
 
-S = 0.01
-M = -0.5 * S * S
-xmax = 2.5
+#S = 0.5
+#M = -0.5 * S * S
+xmax = 2
 
 
-#setwd("/home/jdou557/Documents/Marsden2019/papers/ClockModelPaper/Figures")
+Svals = c(0.1, 0.5, 1.0)
+Mvals = -0.5 * Svals * Svals
+Scols = c("#c91f37", "#36e0c8", "#747474")
 
 
-par(mfrow = c(2,3))
-
-
-
-
-# Categories pdf
-ypts = dlnorm(x, M, S)
-plot(x, ypts , ylim = c(0, max(ypts)*1.2), type = "n", xaxs = "i", yaxs = "i", axes = F, xlab = expression("r"[i]), ylab = "Density",
-main = "cats pdf (10 bins)")
-
-nbins = 10
-cats = 0:(nbins-1)
-bin.cols = "#d3d3d3"
-for (i in cats){
-	
-
-	x0 = qlnorm((i)/nbins, M, S)
-	x1 = qlnorm((i+1)/nbins, M, S)
-	if (i == nbins-1) {
-		x1 = xmax
-	}
-	xmid = qlnorm((i+0.5)/nbins, M, S)
-	y = dlnorm(xmid, M, S)
-
-	rect(x0, 0, x1, y, col = bin.cols, border = "white", lwd = 2) 
-	points(xmid, y, pch = 16, col = cols, cex = 1.5)
-
-
-	text(xmid, y + 0.08, i)
-
-
-}
-
-lines(x, ypts , col = cols, lwd = 3)
-axis(1)
-
-
-
-# Rates pdf
-
-x = seq(from = 0, to = xmax, by = 0.01)
-
-cols = "#008cba"
-plot(x, dlnorm(x, M, S), type = "l", xaxs = "i", col = cols, lwd = 3, yaxs = "i", axes = F, xlab = expression("r"[i]), ylab = "Density",
-main = "real pdf")
-axis(1)
-
-
-
-# Quantiles pdf
-nquant = 10
-qrates = numeric(0)
-for (i in 1:(nquant)){
-
-
-	if (i == 1) {
-		qrates[i] = qlnorm(0.1 / (nquant -1), M, S)
-	}else if (i < nquant) {
-		qrates[i] = qlnorm((i-1) / (nquant -1), M, S)
-	}else{
[…]

### 2020-07-29 correlations.R
likelihood ridge

@@ -1,0 +1,145 @@
+library(graphics)
+library(tikzDevice)
+library(shape)
+#library(plotly)
+
+set.seed(1234566)
+
+
+basewidth = 5
+baseheight = basewidth 
+filename = "correlations.tex"
+options(tikzMetricPackages = c("\\usepackage[utf8]{inputenc}",
+    "\\usepackage[T1]{fontenc}", "\\usetikzlibrary{calc}",
+    "\\usepackage{amssymb}"))
+## I need the amssymb package because I use \mathcal and \mathbb
+	tikz(filename, width = basewidth*2, height = baseheight*1, standAlone = TRUE,
+    	packages = c("\\usepackage{tikz}",
+	         "\\usepackage[active,tightpage,psfixbb]{preview}",
+	         "\\PreviewEnvironment{pgfpicture}",
+	         "\\setlength\\PreviewBorder{0pt}",
+	         "\\usepackage{amssymb}"))
+
+
+
+par(mfrow = c(1,2))
+par(mar = c(5,5,5,5))
+par(cex.lab = 1.4)
+par(cex.main = 1.4)
+
+
+
+
+
+
+likelihood = function(seq1, seq2, len, rate){
+
+
+	d = len*rate
+
+	sum(log(ifelse(seq1 == seq2, 1/4 + 3/4*exp(-4*d/3), 1/4 - 1/4*exp(-4*d/3))))
+
+
+}
+
+xmax = 1.5
+mu = 1 * 4/3
+t = 0.1
+grid.len = 100
+x = seq(from = 0.01, to = xmax, length = grid.len)
+y = seq(from = 0.01, to = xmax, length = grid.len)
+for (L in c(100, 500)){
+	#plot(0, 0, xlim=c(0, 2), ylim = c(0, 1), type = "n", xlab="Branch rate $r$", ylab="Branch length $\\tau$", axes = F, main = paste("Branch likelihood when L =", L, "sites"))
+
+
+
+	seq1 = sample(1:4, L, replace = T)
+	nmut = rpois(1, L*mu*t)
+	mut.loc = sample(1:L, nmut)
+	seq2 = seq1
+	seq2[mut.loc] = sample(1:4, nmut,  replace = T)
+
+
+	lnL = matrix(0, nrow = grid.len, ncol = grid.len)
+	for (i in 1:length(x)){
+
[…]

### 2020-07-29 lognormal.R

@@ -62,7 +62,7 @@ axis(2, las=2)
 
 
 # 2) real
-plot(0, 1, type = "n", xaxs = "i", yaxs = "i", axes = F, xlab = "Abstraction $\\mathcal{R}$ [rate]", ylab = "Branch rate $r(\\mathcal{R})$",
+plot(0, 1, type = "n", xaxs = "i", yaxs = "i", axes = F, xlab = "Abstraction $\\vec{\\mathcal{R}}^{\\,}$ [rate]", ylab = "Branch rate $r(\\vec{\\mathcal{R}}^{\\,})$",
 main = "\\textit{real}", xlim =c(0, xmax), ylim=c(0, xmax))
 
 lines(c(0, xmax), c(0, xmax), lwd = 3)
@@ -73,7 +73,7 @@ axis(2, at = seq(from = 0, to = xmax, by = 0.5), las=2)
 
 # 3) categories
 nbins = 10
-plot(0, 1, type = "n",  yaxs = "i", axes = F, xlab = "Abstraction $\\mathcal{R}$ [category number]", ylab = "Branch rate $r(\\mathcal{R})$",
+plot(0, 1, type = "n",  yaxs = "i", axes = F, xlab = "Abstraction $\\vec{\\mathcal{R}}^{\\,}$ [category number]", ylab = "Branch rate $r(\\vec{\\mathcal{R}}^{\\,})$",
 main = paste0("\\textit{cat} with ", nbins, " bins"), xlim =c(0, nbins-1), ylim=c(0, xmax))
 
 
@@ -100,7 +100,7 @@ axis(2, at = seq(from = 0, to = xmax, by = 0.5), las=2)
 
 
 # 4) quantiles
-plot(0, 1, type = "n", yaxs = "i", axes = F, xlab = "Abstraction $\\mathcal{R}$ [quantile]", ylab = "Branch rate $r(\\mathcal{R})$",
+plot(0, 1, type = "n", yaxs = "i", axes = F, xlab = "Abstraction $\\vec{\\mathcal{R}}^{\\,}$ [quantile]", ylab = "Branch rate $r(\\vec{\\mathcal{R}}^{\\,})$",
 main = paste0("\\textit{quant}"), xlim =c(0, 1), ylim=c(0, xmax))
 
 

### 2020-07-29 manuscript.tex
tidy ups

@@
 The molecular clock hypothesis states that the evolutionary rates of biological sequences are approximately constant throughout time \cite{zuckerkandl1962molecular}.
-This assumption forms the basis of phylogenetics, under which evolutionary trees and divergence dates of life forms are inferred from biological sequences, such as nucleotides and amino acids \cite{douzery2003local, drummond2006relaxed}.
+This assumption forms the basis of phylogenetics, under which the evolutionary trees and divergence dates of life forms are inferred from biological sequences, such as nucleotides and amino acids \cite{douzery2003local, drummond2006relaxed}.
 In Bayesian phylogenetics, these trees and their associated parameters are estimated as probabilitiy distributions \cite{kuhner1995estimating, larget1999markov, mau1999bayesian}. 
@@
 % Early examples?
-However, molecular substitution rates are known to vary over time, over population sizes, over evolutionary pressures, and over DNA replicative machineries \cite{gillespie1994causes, woolfit2009effective, loh2010optimization}.
+However, molecular substitution rates are known to vary over time, over population sizes, over evolutionary pressures, and over nucleic acid replicative machineries \cite{gillespie1994causes, woolfit2009effective, loh2010optimization}.
 Moreover, any given dataset may be clock-like (where the substitution rate has a small variance across lineages) or non clock-like (a large variance). 
@@
 
-This led to the development of relaxed (uncorrelated) clock models, under which each branch in the phylogenetic tree has its own substitution rate  \cite{drummond2006relaxed}.
-Branch rates can be drawn from a range of probability distributions including log-normal, exponential, gamma, and inverse-gamma distributions \cite{drummond2006relaxed, lepage2007general, li2012model}.
+This led to the development of relaxed (uncorrelated) clock models, under which each branch in the phylogenetic tree has its own molecular substitution rate  \cite{drummond2006relaxed}.
+Branch rates can be drawn from a range of probability distributions including Log-Normal, Exponential, Gamma, and Inverse-Gamma distributions \cite{drummond2006relaxed, lepage2007general, li2012model}.
 This class of models is widely used, and has aided insight into many recent biological problems, including the 2016 Zika virus outbreak \cite{faria2017establishment} and the COVID-19 pandemic \cite{giovanetti2020first}.
@@
 Each node $i$ in $\mathcal{T}$, except for the root, is associated with a parental branch length $\tau_i$ (the height difference between $i$ and its parent)  and a parental branch substitution rate $r_i = r(\mathcal{R}_i)$.
-In a relaxed clock model, each of the $2N-2$ elements in $\mathcal{R}_i$ are independently distributed under the prior $p(\vec{\mathcal{R}}^{\,} | \sigma)$.
+In a relaxed clock model, each of the $2N-2$ elements in $\vec{\mathcal{R}}^{\,}$ are independently distributed under the prior $p(\vec{\mathcal{R}}^{\,} | \sigma)$.
 
@@
 \includegraphics[width=\textwidth]{Figures/rateparameterisation.pdf}
-\caption{\textbf{Branch rate parameterisations.} Top left: the branch rate prior under a log-normal($-0.5\sigma^2, \sigma$) distribution (with a mean of 1). 
+\caption{\textbf{Branch rate parameterisations.} Top left: the prior density of a branch rate $r$ under a Log-Normal($-0.5\sigma^2, \sigma$) distribution (with its mean fixed at 1). 
 The function for transforming $\mathcal{R}$ into branch rates $r(\mathcal{R})$ is depicted for \textit{real} (top right), \textit{cat} (bottom left), and \textit{quant} (bottom right).
@@
 
-Under the prior distribution $p(\vec{\mathcal{R}}^{\,} | \sigma)$, rates are log-normally distributed with a mean of 1:
+Under the prior distribution $p(\vec{\mathcal{R}}^{\,} | \sigma)$, rates are Log-Normally distributed with a mean of 1:
 
@@
 
-where $\mu = -0.5\sigma^2$ is set such that the expected value of the log-normal distribution is 1.
-In this article we only consider log-normal clock priors, however the methods discussed are general.
-
-Zhang and Drummond 2020 present a series of tree operators which propose internal/root node heights, and then recompute the rates of incident branches such that their genetic distances ($r_i \times \tau_i$) remain constant after the proposal \cite{zhang2020improving}.
-These operators account for the correlation which exists between branch rates and branch times.
+where $\mu = -0.5\sigma^2$ is set such that the expected value of the Log-Normal distribution is 1.
+In this article we only consider Log-Normal clock priors, however the methods discussed are general.
+
+Zhang and Drummond 2020 introduced a series of tree operators which propose node heights and branch rates, such that the resulting genetic distances ($r_i \times \tau_i$) remain constant \cite{zhang2020improving}.
+These operators account for correlations between branch rates and branch times.
 By keeping the genetic distance of each branch constant, the likelihood is unaltered by the proposal.
@@
 \subsubsection*{2. Categories}
-The category parameterisation (\textit{cat}) is an abstraction of the \textit{real} parameterisation. Each branch is assigned an integer from $0$ to $n-1$:
+The category parameterisation (\textit{cat}) is an abstraction of the \textit{real} parameterisation. 
+Each of the $2N-2$ branches are assigned an integer from $0$ to $n-1$:
 
@@
 
-These integers correspond to $n$ rate categories.
- The domain of $\vec{\mathcal{R}}^{\,}$ is uniformly distributed:
+These integers correspond to $n$ rate categories (\textbf{Fig. \ref{fig:rateparams}}).
+The domain of $\vec{\mathcal{R}}^{\,}$ is uniformly distributed under thr prior:
 
@@
 
-Let $f(x|\sigma)$ be the probability density function (pdf) and let $F(x|\sigma) = \int\limits_{0}^{x} f(t|\sigma) \; dt$ be the cumulative distribution function (cdf) of the prior distribution used by the underlying \textit{real} clock model.
-Then, in the \textit{cat} parameterisation, $f(x|\sigma)$ is discretised into $n$ bins and the elements of $\vec{\mathcal{R}}^{\,}$ each point to one of these bins.
-Each bin contains uniform probability density $1/n$.
+Let $f(x|\sigma)$ be the probability density function (PDF) and let $F(x|\sigma) = \int\limits_{0}^{x} f(t|\sigma) \; dt$ be the cumulative distribution function (CDF) of the prior distribution used by the underlying \textit{real} clock model.
+Then, in the \textit{cat} parameterisation, $f(x|\sigma)$ is discretised into $n$ bins and each element within $\vec{\mathcal{R}}^{\,}$ points to one such bin,
+where each bin has uniform prior density.
  The rate of each bin is equal to the median value within the bin
@@
 
-where $F^{-1}$ is the inverse cumulative distribution function (i-cdf).
+where $F^{-1}$ is the inverse cumulative distribution function (i-CDF).
 
 The key advantage of the \textit{cat} parameterisation is the removal of a term from the posterior density (Equation \ref{eq:bayesian}), or more accurately the replacement of a non-trivial $p(\vec{\mathcal{R}}^{\,} | \sigma)$ term with that of a uniform prior.
-Thus, one fewer term needs to be estimated per rate.
+This may facilitate efficient traversal of the parameter space by MCMC.
 
@@
 Finally, rates can be parameterised as real numbers $0 < \mathcal{R}_i < 1$ which describe the rate's quantile with respect to some underlying clock model distribution.
-Under the  \textit{quant} parameterisation, each element in $\vec{\mathcal{R}}^{\,}$ is uniformly distributed.
+Under the  \textit{quant} parameterisation, each of the $2N-2$ elements in $\vec{\mathcal{R}}^{\,}$ are uniformly distributed.
 
@@
 
-Transforming these quantiles into rates invokes the i-cdf of the underlying \textit{real} clock model distribution:
+Transforming these quantiles into rates invokes the i-CDF of the underlying \textit{real} clock model distribution:
 
@@
 In this project we extended the family of constant distance operators  \cite{zhang2020improving} so they are compatible with \textit{quant}.
-These are presented in \textbf{\nameref{sect:S1Appendix}}.
+These operators are presented in \textbf{\nameref{sect:S1Appendix}}.
+
+The computational requirements of i-CDF evaluation may hinder the performance of the \textit{quant} parameterisation.
 
@@
 Pre-existing BEAST2 clock model operators (i.e.
-those which generate proposals for either $\mathcal{R}$ or $\sigma$) are summarised in \textbf{Table \ref{table:kernels}}, and further operators are introduced throughout the paper.
+those which generate proposals for either $\vec{\mathcal{R}}^{\,}$ or $\sigma$) are summarised in \textbf{Table \ref{table:kernels}}, and further operators are introduced throughout the paper.
 
@@
 \centering
-\begin{tabular}{|l| l p{4cm} l l|} 
- \hline
- & Operator & Description & Parameters & Parameterisations  \\
-  \hline
- 1 & \texttt{RandomWalk} & Moves a single element by a tunable amount. & $\mathcal{R}, \sigma$ & \textit{cat}, \textit{real}, \textit{quant} \\
-  \hline
- 2 & \texttt{Scale} & Applies \texttt{RandomWalk} on the log-transformation (suitable for parameters with positive domains). & $\mathcal{R}, \sigma$ & \textit{real}, \textit{quant}  \\
-  \hline
- 3 & \texttt{Interval} & Applies \texttt{RandomWalk} on the logit-transformation (suitable for parameters with upper and lower limits). & $\mathcal{R}$ & \textit{quant}  \\
-  \hline
-   4 & \texttt{Swap} & Swaps two random elements in the vector \cite{drummond2006relaxed}. & $\mathcal{R}$  & \textit{cat}, \textit{real}, \textit{quant}  \\
- \hline
-  5 & \texttt{Uniform} & Resamples one element in the vector from a uniform distribution. & $\mathcal{R}$  & \textit{cat}, \textit{quant}  \\
- \hline
- 6 & \texttt{ConstantDistance} & Adjusts an internal node and recalculates all incident branch rates such that the genetic distances remain constant \cite{zhang2020improving}.
-& $\mathcal{R}, \mathcal{T}$ & \textit{real}, \textit{quant} \\
- \hline
- 7 & \texttt{SimpleDistance} & Applies \texttt{SimpleDistance} to the root node \cite{zhang2020improving}.  & $\mathcal{R}, \mathcal{T}$ & \textit{real}, \textit{quant} \\
- \hline
- 8 & \texttt{SmallPulley} & Proposes new branch rates incident to the root such that their combined genetic distance is constant  \cite{zhang2020improving}.
-& $\mathcal{R}$ & \textit{real}, \textit{quant} \\
- \hline
- 9 & \texttt{FastClockScale} & Applies \texttt{Scale} to $\sigma$ and then recomputes all rates $\mathcal{R}$ such that their quantiles under the prior $p(\mathcal{R}|\sigma)$ are constant \cite{zhang2020improving}.
+\begin{tabular}{|l p{4.2cm} l l|} 
+ \hline
+ Operator & Description & Parameters & Parameterisations  \\
+  \hline
+ \texttt{RandomWalk} & Moves a single element by a tunable amount. & $\vec{\mathcal{R}}^{\,}, \sigma$ & \textit{cat}, \textit{real}, \textit{quant} \\
+  \hline
+\texttt{Scale} & Applies \texttt{RandomWalk} on the log-transformation (suitable for parameters with positive domains). & $\vec{\mathcal{R}}^{\,}, \sigma$ & \textit{real}, \textit{quant}  \\
+  \hline
+ \texttt{Interval} & Applies \texttt{RandomWalk} on the logit-transformation (suitable for parameters with upper and lower limits). & $\vec{\mathcal{R}}^{\,}$ & \textit{quant}  \\
+  \hline
+ \texttt{Swap} & Swaps two random elements in the vector \cite{drummond2006relaxed}. & $\vec{\mathcal{R}}^{\,}$  & \textit{cat}, \textit{real}, \textit{quant}  \\
+ \hline
+\texttt{Uniform} & Resamples one element in the vector from a uniform distribution. & $\vec{\mathcal{R}}^{\,}$  & \textit{cat}, \textit{quant}  \\
+ \hline
+\texttt{ConstantDistance} & Adjusts an internal node and recalculates all incident branch rates such that the genetic distances remain constant \cite{zhang2020improving}.
+& $\vec{\mathcal{R}}^{\,}, \mathcal{T}$ & \textit{real}, \textit{quant} \\
+ \hline
+\texttt{SimpleDistance} & Applies \texttt{ConstantDistance} to the root node \cite{zhang2020improving}.  & $\vec{\mathcal{R}}^{\,}, \mathcal{T}$ & \textit{real}, \textit{quant} \\
+ \hline
+\texttt{SmallPulley} & Proposes new branch rates incident to the root such that their combined genetic distance is constant  \cite{zhang2020improving}.
+& $\vec{\mathcal{R}}^{\,}$ & \textit{real}, \textit{quant} \\
+ \hline
+\texttt{FastClockScale} & Applies \texttt{Scale} to $\sigma$ and then recomputes all rates $\vec{\mathcal{R}}^{\,}$ such that their quantiles under the prior $p(\vec{\mathcal{R}}^{\,}|\sigma)$ are constant \cite{zhang2020improving}.
 & $\mathcal{R}$ & \textit{real} \\
@@
 \end{tabular}
-\caption{Summary of pre-existing BEAST2 operators which apply to either branch rates $\mathcal{R}$ or the clock standard deviation $\sigma$, and the substitution rate parameterisation they apply to.
- \texttt{ConstantDistance} and \texttt{SimpleDistance} also adjust tree node heights. }
+\caption{Summary of pre-existing BEAST2 operators, which apply to either branch rates $\vec{\mathcal{R}}^{\,}$ or the clock standard deviation $\sigma$, and the substitution rate parameterisation they apply to.
+ \texttt{ConstantDistance} and \texttt{SimpleDistance} also adjust node heights in the tree $\mathcal{T}$. }
 \label{table:kernels}
@@
 We hypothesise that datasets with strong signal (or large $L$) will mix best when the more precise and meticulous kind of operator is employed, such as those informed by correlations within the posterior distribution e.g.
-the family of constant distance operators \cite{zhang2020improving}.
+the family of constant distance operators \cite{zhang2020improving} (\textbf{Fig.
+\ref{fig:rateparams}}).
 Whereas, datasets which contain very poor signal (or small $L$) are likely to mix best when there is more weight placed on bold operators such as \texttt{SampleFromPrior}, \texttt{Swap}, or \texttt{Uniform} which sample each branch rate independently of its current estimate.
-\texttt{AdaptiveOperatorSampler} should learn the combination of weights behind these classes of operators best suited for the dataset.
+\texttt{AdaptiveOperatorSampler} should learn the combination of weights behind these classes of operators best suited for any given dataset.
+
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{Figures/correlations.pdf}
+\caption{\textbf{Traversing likelihood space.}
+The z-axes above are the log-likelihoods of the genetic distance $r \times \tau$ between two simulated nucleic acid sequences of length $L$, under the Jukes-Cantor substitution model \cite{jukes1969evolution}.
+Two possible proposals from the current state (red circle) are depicted.
+These proposals are generated by the \texttt{RandomWalk} (\texttt{RW}) and \texttt{ConstantDistance} (\texttt{CD}) operators.
+In the low signal dataset ($L=0.1$kb), both operators can traverse the likelihood space effectively.
+ However, the same exact same proposal by \texttt{RandomWalk} incurs a much larger likelihood penalty in the $L=0.5$kb dataset by ``falling off the ridge'', in contrast to \texttt{ConstantDistance} which ``walks along the ridge''.
+ This discrepancy is even stronger for larger datasets and thus necessitates the use of operators such as \texttt{ConstantDistance} which account for correlations between branch lengths and rates. }
+\label{fig:rateparams}
+\end{figure}
 
@@
 \hline
- \multirow{4}{*}{\texttt{AdaptiveOperatorSampler($\sigma$)}} & \texttt{FastClockScale($\sigma, \mathcal{R}$)}$^{*}$ \\ 
+ \multirow{4}{*}{\texttt{AdaptiveOperatorSampler($\sigma$)}} & \texttt{FastClockScale($\sigma, \vec{\mathcal{R}}^{\,}$)}$^{*}$ \\ 
  & \texttt{RandomWalk($\sigma$)} \\
@@
  \hline
-  \multirow{6}{*}{\texttt{AdaptiveOperatorSampler($\mathcal{R}$)}} & \texttt{ConstantDistance($\mathcal{R}, \mathcal{T}$)} \\ 
-& \texttt{RandomWalk($\mathcal{R}$)} \\
-& \texttt{Scale($\mathcal{R}$)}$^{*}$ \\
-& \texttt{Interval($\mathcal{R}$)}$^{**}$  \\
-& \texttt{Swap($\mathcal{R}$)} \\
-& \texttt{SampleFromPrior($\mathcal{R}$)} \\
- \hline
-   \multirow{2}{*}{\texttt{AdaptiveOperatorSampler(root)}} & \texttt{SimpleDistance($\mathcal{R}, \mathcal{T}$)} \\ 
-&  \texttt{SmallPulley($\mathcal{R}, t$)}\\
+  \multirow{6}{*}{\texttt{AdaptiveOperatorSampler($\vec{\mathcal{R}}^{\,}$)}} & \texttt{ConstantDistance($\vec{\mathcal{R}}^{\,}, \mathcal{T}$)} \\ 
+& \texttt{RandomWalk($\vec{\mathcal{R}}^{\,}$)} \\
+& \texttt{Scale($\vec{\mathcal{R}}^{\,}$)}$^{*}$ \\
+& \texttt{Interval($\vec{\mathcal{R}}^{\,}$)}$^{**}$  \\
+& \texttt{Swap($\vec{\mathcal{R}}^{\,}$)} \\
+& \texttt{SampleFromPrior($\vec{\mathcal{R}}^{\,}$)} \\
+ \hline
+   \multirow{2}{*}{\texttt{AdaptiveOperatorSampler(root)}} & \texttt{SimpleDistance($\vec{\mathcal{R}}^{\,}, \mathcal{T}$)} \\ 
+&  \texttt{SmallPulley($\vec{\mathcal{R}}^{\,}, t$)}\\
  \hline
@@
 \includegraphics[width=\textwidth]{Figures/bactrian.pdf}
-\caption{\textbf{The Bactrian proposal kernel.} Y-axis corresponds to probability density $f(\Sigma|m)$.  }
+\caption{\textbf{The Bactrian proposal kernel.} The step size made under a Bactrian proposal kernel is equal to $s \Sigma$ where $\Sigma$ is drawn from the above distribution and $s$ is tunable.   }
 \label{fig:bactrian}
@@
   \hline
- 1 & \texttt{RandomWalk}  & $x^\prime \leftarrow x + s\Sigma$ & $\mathcal{R}, \sigma$  \\
-  \hline
- 2 & \texttt{Scale} & $x^\prime \leftarrow x \times e^{s\Sigma}$ & $\mathcal{R}, \sigma$   \\
-  \hline
- 3 & \texttt{Interval} & $\begin{array} {rl} &y \leftarrow \frac{1 - x}{x} \times e^{s\Sigma} \\ &x^\prime \leftarrow \frac{y}{y + 1}  \end{array}$ & $\mathcal{R}$  \\
+ 1 & \texttt{RandomWalk}  & $x^\prime \leftarrow x + s\Sigma$ & $\vec{\mathcal{R}}^{\,}, \sigma$  \\
+  \hline
+ 2 & \texttt{Scale} & $x^\prime \leftarrow x \times e^{s\Sigma}$ & $\vec{\mathcal{R}}^{\,}, \sigma$   \\
+  \hline
+ 3 & \texttt{Interval} & $\begin{array} {rl} &y \leftarrow \frac{1 - x}{x} \times e^{s\Sigma} \\ &x^\prime \leftarrow \frac{y}{y + 1}  \end{array}$ & $\vec{\mathcal{R}}^{\,}$  \\
   \hline
@@
  \hline
- 5 & \texttt{SmallPulley} & $x^\prime \leftarrow x + s\Sigma$ & $\mathcal{R}$  \\
+ 5 & \texttt{SmallPulley} & $x^\prime \leftarrow x + s\Sigma$ & $\vec{\mathcal{R}}^{\,}$  \\
  \hline
@@
 \caption{Proposal kernels $q(x^\prime|x)$ of clock model operators.
- In each operator, $\Sigma$ is drawn from either a $\text{Bactrian}(m)$ or $\text{Uniform}$ distribution (distributions are normalised so that they have a mean of 0 and a variance of 1). 
+ In each operator, $\Sigma$ is drawn from either a $\text{Bactrian}(m)$ or $\text{Uniform}$ distribution. 
  The scale size $s$ is tunable.
@@
 
-The AVMVN kernel assumes its parameters live in $x \in \mathbb{R}^N$ and that these parameters follow a multivariate normal distribution with covariance matrix $\Sigma_N$.
+The AVMVN kernel assumes its parameters live in $x \in \mathbb{R}^N$ and that these parameters follow a Multivariate Normal distribution with covariance matrix $\Sigma_N$.
 Hence, the kernel operates on the logarithmic or logistic transformation of the $N$ leaf branch rates, depending on the rate parameterisation:
@@
 
-where $\mathcal{MVN}$ is the multivariate normal probability density.
+where $\mathcal{MVN}$ is the Multivariate Normal probability density.
 $\beta \; (= 0.05)$ is a constant which determines the fraction of the proposal determined by the identity matrix $\mathbb{I}_N$, as opposed to the covariance matrix $\Sigma_D$ which is trained during MCMC.
@@
 
-Throughout \nameref{sect:models}, we introduced four new operators which are applied to the relaxed clock. 
+In this article we have introduced four new clock model operators. 
 These operators are summarised in \textbf{Table \ref{table:newOperators}} and are applied in conjunction with the pre-existing clock model operators presented in \textbf{Table \ref{table:kernels}}.
@@
 \centering
-\begin{tabular}{|l| l p{4cm} l|} 
- \hline
- & Operator & Description & Parameters  \\
-  \hline
-1 & \texttt{AdaptiveOperatorSampler} & Samples sub-operators proportionally to their weights, which are learned (see \nameref{sect:adaptiveSampling}). & $\mathcal{R}, \sigma, \mathcal{T}$ \\
-  \hline
-2 & \texttt{SampleFromPrior} & Resamples a random number of elements from their prior (see \nameref{sect:adaptiveSampling}). & $\mathcal{R}, \sigma$ \\
-  \hline
-3 & \texttt{NarrowExchangeRate} & Moves a branch and recomputes branch rates so that genetic distances are constant (see \nameref{sect:NER}). & $\mathcal{R}, \mathcal{T}$\\
-  \hline
-4 & \texttt{LeafAVMVN}  & Proposals new rates for all leaves in one move (see \nameref{AVMVN_sect}) \cite{baele2017adaptive}. & $\mathcal{R}$ \\
+\begin{tabular}{|l p{4cm} l|} 
+ \hline
+ Operator & Description & Parameters  \\
+  \hline
+ \texttt{AdaptiveOperatorSampler} & Samples sub-operators proportionally to their weights, which are learned (see \nameref{sect:adaptiveSampling}). & $\vec{\mathcal{R}}^{\,}, \sigma, \mathcal{T}$ \\
+  \hline
+ \texttt{SampleFromPrior} & Resamples a random number of elements from their prior (see \nameref{sect:adaptiveSampling}). & $\vec{\mathcal{R}}^{\,}, \sigma$ \\
+  \hline
+ \texttt{NarrowExchangeRate} & Moves a branch and recomputes branch rates so that genetic distances are constant (see \nameref{sect:NER}). & $\vec{\mathcal{R}}^{\,}, \mathcal{T}$\\
+  \hline
+ \texttt{LeafAVMVN}  & Proposals new rates for all leaves in one move (see \nameref{AVMVN_sect}) \cite{baele2017adaptive}. & $\vec{\mathcal{R}}^{\,}$ \\
   \hline
@@
  \multirow{6}{*}{nocons} & \texttt{RandomWalk($\mathcal{R}$)} & $10$ & \textit{real}  \\
- 	& \texttt{Scale($\mathcal{R}$)} & $10$ & \textit{real} \\ 
- 	& \texttt{Uniform($\mathcal{R}$)} & $10$ & \textit{quant} \\ 
- 	& \texttt{Interval($\mathcal{R}$)} & $10$ & \textit{quant} \\ 
- 	& \texttt{Swap($\mathcal{R}$)} & $10$ & \textit{real}, \textit{quant} \\ 
+ 	& \texttt{Scale($\vec{\mathcal{R}}^{\,}$)} & $10$ & \textit{real} \\ 
+ 	& \texttt{Uniform($\vec{\mathcal{R}}^{\,}$)} & $10$ & \textit{quant} \\ 
+ 	& \texttt{Interval($\vec{\mathcal{R}}^{\,}$)} & $10$ & \textit{quant} \\ 
+ 	& \texttt{Swap($\vec{\mathcal{R}}^{\,}$)} & $10$ & \textit{real}, \textit{quant} \\ 
  	& \texttt{Scale($\sigma$)} & $10$ & \textit{real}, \textit{quant} \\ 
@@
    \multirow{10}{*}{cons} 
-   & \texttt{ConstantDistance($\mathcal{R}, \mathcal{T}$)} & $20 \times \frac{2N-2}{2N-1}$ & \textit{real}, \textit{quant}  \\
-   & \texttt{SimpleDistance($\mathcal{R}, \mathcal{T}$)} & $10 \times \frac{2N-2}{2N-1}$ & \textit{real}, \textit{quant}  \\
-   & \texttt{SmallPulley($\mathcal{R}$)} & $10 \times \frac{2N-2}{2N-1}$ & \textit{real}, \textit{quant}  \\
-   & \texttt{RandomWalk($\mathcal{R}$)} & $5$ & \textit{real}  \\
- 	& \texttt{Scale($\mathcal{R}$)} & $2.5$ & \textit{real} \\ 
- 	& \texttt{Uniform($\mathcal{R}$)} & $5$ & \textit{quant} \\ 
- 	& \texttt{Interval($\mathcal{R}$)} & $2.5$ & \textit{quant} \\ 
- 	& \texttt{Swap($\mathcal{R}$)} & $2.5$ & \textit{real}, \textit{quant} \\ 
- 	& \texttt{FastClockScale($\sigma$)} & $10$ & \textit{real}  \\ 
+   & \texttt{ConstantDistance($\vec{\mathcal{R}}^{\,}, \mathcal{T}$)} & $20 \times \frac{2N-2}{2N-1}$ & \textit{real}, \textit{quant}  \\
+   & \texttt{SimpleDistance($\vec{\mathcal{R}}^{\,}, \mathcal{T}$)} & $10 \times \frac{2N-2}{2N-1}$ & \textit{real}, \textit{quant}  \\
+   & \texttt{SmallPulley($\vec{\mathcal{R}}^{\,}$)} & $10 \times \frac{2N-2}{2N-1}$ & \textit{real}, \textit{quant}  \\
+   & \texttt{RandomWalk($\vec{\mathcal{R}}^{\,}$)} & $5$ & \textit{real}  \\
+ 	& \texttt{Scale($\vec{\mathcal{R}}^{\,}$)} & $2.5$ & \textit{real} \\ 
+ 	& \texttt{Uniform($\vec{\mathcal{R}}^{\,}$)} & $5$ & \textit{quant} \\ 
+ 	& \texttt{Interval($\vec{\mathcal{R}}^{\,}$)} & $2.5$ & \textit{quant} \\ 
+ 	& \texttt{Swap($\vec{\mathcal{R}}^{\,}$)} & $2.5$ & \textit{real}, \textit{quant} \\ 
+ 	& \texttt{FastClockScale($\sigma, \vec{\mathcal{R}}^{\,}$)} & $10$ & \textit{real}  \\ 
  	& \texttt{Scale($\sigma$)} & $10$ &  \textit{quant} \\ 
@@
      \multirow{3}{*}{adapt} & \texttt{AdaptiveOperatorSampler($\sigma$)} & $10$ & \textit{real}, \textit{quant} \\
- 	& \texttt{AdaptiveOperatorSampler($\mathcal{R}$)} & $30 \times \frac{2N-2}{2N-1}$ & \textit{real}, \textit{quant} \\
+ 	& \texttt{AdaptiveOperatorSampler($\vec{\mathcal{R}}^{\,}$)} & $30 \times \frac{2N-2}{2N-1}$ & \textit{real}, \textit{quant} \\
  	& \texttt{AdaptiveOperatorSampler(root)} & $30 \times \frac{1}{2N-1}$ & \textit{real}, \textit{quant} \\
@@
 \end{tabular}
-\caption{Operator configurations for Round 1.
-In each configuration, the weight behind $\mathcal{R}$ sums to 30 and for $\sigma$ is equal to 10 within any one rate parameterisation.
-Operators which apply to either internal nodes or the root (but not both) weighted according to leaf count $N$.
-The adapt operators are further broken down in \textbf{Table \ref{table:adaptiveSampling}}.}
+\caption{Operator configurations for Round 1. In each configuration, the weight behind $\mathcal{R}$ sums to 30 and for $\sigma$ is equal to 10 within any one rate parameterisation. 
+Operators which apply to either internal nodes or the root (but not both) are weighted according to leaf count $N$.
+The adapt operators are further broken down in \textbf{Table \ref{table:adaptiveSampling}}.
+The total weight of all operators across all parameters was 116 in each MCMC setup.
+Therefore a weight of 10 corresponds to sampling probability of 0.086, for example.}
 \label{table:round1Results}
@@
  \multirow{4}{*}{\textit{cat}} 
- 	& \texttt{RandomWalk($\mathcal{R}$)} & $10$ \\
- 	& \texttt{Uniform($\mathcal{R}$)} & $10$  \\ 
- 	& \texttt{Swap($\mathcal{R}$)} & $10$ \\ 
+ 	& \texttt{RandomWalk($\vec{\mathcal{R}}^{\,}$)} & $10$ \\
+ 	& \texttt{Uniform($\vec{\mathcal{R}}^{\,}$)} & $10$  \\ 
+ 	& \texttt{Swap($\vec{\mathcal{R}}^{\,}$)} & $10$ \\ 
  	& \texttt{Scale($\sigma$)} & $10$ \\ 

### 2020-07-29 bactrian.R

@@ -3,13 +3,11 @@ library(tikzDevice)
 
 
 
-setwd("/home/jdou557/Documents/Marsden2019/papers/ClockModelPaper/Figures")
-
 
 filename = "bactrian"
-cols = 2
+cols = 1
 rows = 1
-basewidth = 2.5
+basewidth = 3.5
 
 
 
@@ -26,9 +24,10 @@ options(tikzMetricPackages = c("\\usepackage[utf8]{inputenc}",
 
 
 
-par(mfrow = c(rows, cols), mar = c(4,1,2,1))
+par(mfrow = c(rows, cols), mar = c(5,5,5,2))
 par(las=1)
-#par(cex = 1.0)
+par(cex.main = 1.3)
+par(cex.lab = 1.3)
 
 
 
@@ -39,6 +38,7 @@ dbactrian = function(x, m){
 	dens = 1 / (2*s*sqrt(2*pi*(1-m^2)))
 	dens = dens * (exp( -(x + m*s)^2 / (2 * (1-m^2)) * s^2 ) + exp( -(x - m*s)^2 / (2 * (1-m^2)) * s^2 ))
 	dens
+
 }
 
 
@@ -46,14 +46,14 @@ x = seq(from = -3, to = 3, by = 0.001)
 
 
 # Bactrian
-plot(0, 1, xlim = range(x), ylim = c(0,1.1), type = "n", xlab = "$\\Sigma$", ylab = "", main = "Bactrian distribution", xaxs = "i", yaxs = "i", axes = F)
+plot(0, 1, xlim = range(x), ylim = c(0,1.1), type = "n", xlab = "$\\Sigma$", ylab = "Probability density function $p(\\Sigma|m)$", main = "Bactrian distribution", xaxs = "i", yaxs = "i", axes = F)
 
 
-mvals = c(0.92, 0.95, 0.98)
+mvals = c(0, 0.95, 0.98)
 
 cols = c("#008cba", "#8cba00", "#ba008c")
-cols = c("#001922", "#006588", "#08c0ff")
-lwds = c(2,2,2)
+cols = c("#00000077", "#00658877", "#08c0ff77")
+lwds = c(1,1,1)
 ltys = c("solid", "dashed", "dotted")
 ltys = c("solid", "solid", "solid")
 
@@ -64,18 +64,15 @@ for (i in 1:length(mvals)){
 	col = cols[i]
 	lwd = lwds[i]
 	lty = ltys[i]
[…]

### 2020-07-29 correlations.R

@@ -45,7 +45,7 @@ likelihood = function(seq1, seq2, len, rate){
 xmax = 1.5
 mu = 1 * 4/3
 t = 0.1
-grid.len = 100
+grid.len = 500
 x = seq(from = 0.01, to = xmax, length = grid.len)
 y = seq(from = 0.01, to = xmax, length = grid.len)
 for (L in c(100, 500)){
@@ -83,7 +83,7 @@ for (L in c(100, 500)){
 	breaks  =signif(breaks, 2)
 	breaks = round(breaks / 10, 0) * 10
 	#seq(from = min(lnL.vec), to = max(lnL.vec), length = nbins+1)
-	image(x, y, lnL, xlab="Branch rate $r$", ylab="Branch length $\\tau$", axes=F,  main = paste0("Branch log-likelihood when L = ", L/1000, "kb"), col = cols,
+	image(x, y, lnL, xlab="Branch rate $r$", ylab="Branch length $\\tau$", axes=F,  main = paste0("log-likelihood when L = ", L/1000, "kb"), col = cols,
 			 breaks = breaks, useRaster = TRUE, xaxs = "i", yaxs = "i")
 
 
@@ -108,16 +108,17 @@ for (L in c(100, 500)){
 	
 
 
-	dr = 0.3
+	dr = 0.5
 
 	# Randomwalk
 	Arrows(r0, t0, r0 + dr, t0, lcol = arrow.col,  arr.type="curved")
 	#text(r0 + dr + 0.05, t0, "$x^\\prime$", adj = c(0, 0.3), col = font.col)
-	text(r0 + dr/2, t0 - 0.02, "\\texttt{RW}", adj = c(0.5, 1), cex = 1.2)
+	text(r0 + dr/2, t0 + 0.02, "\\texttt{RW}", adj = c(0.5, 0), cex = 1.2)
 
 
 
 	# Constant distance
+	dr = 0.3
 	r1 = r0 - dr
 	t1 = r0/r1 * t0
 	#r1 = r0*t0/t1

### 2020-07-29 lognormal.R

@@ -37,7 +37,7 @@ par(cex.main = 1.5)
 x = seq(from = 0, to = xmax, by = 0.01)
 
 plot(0, 0, type = "n", xaxs = "i", lwd = 3, yaxs = "i", axes = F, xlab = "Branch rate $r$", ylab = "$p(r|\\sigma)$",
-main = "Probability density function (log-normal)", xlim = c(0, xmax), ylim=c(0, 5))
+main = "Probability density function (Log-Normal)", xlim = c(0, xmax), ylim=c(0, 5))
 
 
 
@@ -62,7 +62,7 @@ axis(2, las=2)
 
 
 # 2) real
-plot(0, 1, type = "n", xaxs = "i", yaxs = "i", axes = F, xlab = "Abstraction $\\vec{\\mathcal{R}}^{\\,}$ [rate]", ylab = "Branch rate $r(\\vec{\\mathcal{R}}^{\\,})$",
+plot(0, 1, type = "n", xaxs = "i", yaxs = "i", axes = F, xlab = "Abstraction $\\mathcal{R}$ [rate]", ylab = "Branch rate $r(\\mathcal{R})$",
 main = "\\textit{real}", xlim =c(0, xmax), ylim=c(0, xmax))
 
 lines(c(0, xmax), c(0, xmax), lwd = 3)
@@ -73,7 +73,7 @@ axis(2, at = seq(from = 0, to = xmax, by = 0.5), las=2)
 
 # 3) categories
 nbins = 10
-plot(0, 1, type = "n",  yaxs = "i", axes = F, xlab = "Abstraction $\\vec{\\mathcal{R}}^{\\,}$ [category number]", ylab = "Branch rate $r(\\vec{\\mathcal{R}}^{\\,})$",
+plot(0, 1, type = "n",  yaxs = "i", axes = F, xlab = "Abstraction $\\mathcal{R}$ [category number]", ylab = "Branch rate $r(\\mathcal{R})$",
 main = paste0("\\textit{cat} with ", nbins, " bins"), xlim =c(0, nbins-1), ylim=c(0, xmax))
 
 
@@ -100,7 +100,7 @@ axis(2, at = seq(from = 0, to = xmax, by = 0.5), las=2)
 
 
 # 4) quantiles
[…]

### 2020-07-30 manuscript.tex
general tidyups

@@
 \usepackage[normalem]{ulem}
+\usepackage{algorithm}
+\usepackage[noend]{algpseudocode}
 
@@
 {\Large
-\textbf\newline{Adaptive dating and faster proposals: revisiting the phylogenetic relaxed clock model} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
+\textbf\newline{Adaptive dating and fast proposals: revisiting the phylogenetic relaxed clock model} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
 }
@@
 
-The molecular clock hypothesis states that the evolutionary rates of biological sequences are approximately constant throughout time \cite{zuckerkandl1962molecular}.
-This assumption forms the basis of phylogenetics, under which the evolutionary trees and divergence dates of life forms are inferred from biological sequences, such as nucleotides and amino acids \cite{douzery2003local, drummond2006relaxed}.
+The molecular clock hypothesis states that the evolutionary rates of biological sequences, such as nucleotides and amino acids, are approximately constant through time \cite{zuckerkandl1962molecular}.
+This assumption forms the basis of phylogenetics, under which the evolutionary trees and divergence dates of life forms are inferred from biological sequences \cite{douzery2003local, drummond2006relaxed}.
 In Bayesian phylogenetics, these trees and their associated parameters are estimated as probabilitiy distributions \cite{kuhner1995estimating, larget1999markov, mau1999bayesian}. 
-Statistical inference is typically performed by sampling using the Markov chain Monte Carlo (MCMC) algorithm \cite{metropolis53, hastings70}.
-Bayesian phylogenetic clock models have been implemented in many platforms including BEAST \cite{drummond2012bayesian}, BEAST2 \cite{bouckaert2019beast}, MrBayes \cite{ronquist2012mrbayes}, and RevBayes \cite{hohna2016revbayes}.
+Statistical inference can be performed by the Markov chain Monte Carlo (MCMC) algorithm \cite{metropolis53, hastings70} using platforms such as BEAST \cite{drummond2012bayesian}, BEAST2 \cite{bouckaert2019beast}, MrBayes \cite{ronquist2012mrbayes}, and RevBayes \cite{hohna2016revbayes}.
 
@@
 
-With the increasing availabilty of biological sequence data, the development of efficient Bayesian phylogenetic methods is more important than ever. 
+With the overwhelming availabilty of biological sequence data, the development of efficient Bayesian phylogenetic methods is more important than ever. 
 The performance of MCMC is dependent not only on computational runtime but also the efficacy of an
@@
 \label{eq:bayesian}
-p(\mathcal{T}, \vec{\mathcal{R}}^{\,}, \sigma, \theta|D) \propto  p(D|\mathcal{T}, r(\vec{\mathcal{R}}^{\,}), \theta) \; p(\mathcal{T}|\theta) \;  p(\vec{\mathcal{R}}^{\,} | \sigma) \; p(\sigma) \; p(\theta).
+p(\mathcal{T}, \vec{\mathcal{R}}^{\,}, \sigma, \mu_C, \theta|D) \propto  p(D|\mathcal{T}, r(\vec{\mathcal{R}}^{\,}), \mu_C) \; p(\mathcal{T}|\theta) \;  p(\vec{\mathcal{R}}^{\,} | \sigma) \; p(\sigma) \; p(\mu_C) \; p(\theta).
 \end{eqnarray}
@@
 $\sigma$ represents clock model related parameters, and $p(\mathcal{T}|\theta)$ is the tree prior where $\theta$ describes further unspecified parameters. 
-The tree likelihood $p(D|\mathcal{T}, r(\vec{\mathcal{R}}^{\,}), \theta)$ is computed using the tree-peeling algorithm \cite{felsenstein1981evolutionary}, where
-$\vec{\mathcal{R}}^{\,}$ is a vector of abstracted substitution rates and transformed into real rates by function $r(\vec{\mathcal{R}}^{\,})$.
+The tree likelihood $p(D|\mathcal{T}, r(\vec{\mathcal{R}}^{\,}), \mu_C)$ is computed using the tree-peeling algorithm \cite{felsenstein1981evolutionary}, where $\mu_C$ is the overall clock rate and
+$\vec{\mathcal{R}}^{\,}$ is a vector of abstracted branch rates which is transformed into real rates by function $r(\vec{\mathcal{R}}^{\,})$. 
+Branch rates have a mean of 1 under the prior to avoid non-identifiability with node heights and the clock rate $\mu_C$.
 Three methods of representing rates as $\vec{\mathcal{R}}^{\,}$ are presented in \textbf{\nameref{sect:rateparams}}.
@@
 
-Under the prior distribution $p(\vec{\mathcal{R}}^{\,} | \sigma)$, rates are Log-Normally distributed with a mean of 1:
+Under the Log-Normal clock prior $p(\vec{\mathcal{R}}^{\,} | \sigma)$, rates are distributed with a mean of 1:
 
@@
 These integers correspond to $n$ rate categories (\textbf{Fig. \ref{fig:rateparams}}).
-The domain of $\vec{\mathcal{R}}^{\,}$ is uniformly distributed under thr prior:
+The domain of $\vec{\mathcal{R}}^{\,}$ is uniformly distributed under the prior:
 
@@
 
-Let $f(x|\sigma)$ be the probability density function (PDF) and let $F(x|\sigma) = \int\limits_{0}^{x} f(t|\sigma) \; dt$ be the cumulative distribution function (CDF) of the prior distribution used by the underlying \textit{real} clock model.
+Let $f(x|\sigma)$ be the probability density function (PDF) and let $F(x|\sigma) = \int\limits_{0}^{x} f(t|\sigma) \; dt$ be the cumulative distribution function (CDF) of the prior distribution used by the underlying \textit{real} clock model (a Log-Normal distribution in this project).
 Then, in the \textit{cat} parameterisation, $f(x|\sigma)$ is discretised into $n$ bins and each element within $\vec{\mathcal{R}}^{\,}$ points to one such bin,
@@
 
+However, evaluation of the i-CDF is computationally demanding and this may hinder the performance of the \textit{quant} parameterisation.
+
 While this approach has clear similarities with \textit{cat}, the domain of rates here is continuous (as opposed to being confined to a discrete number of bins).
-In this project we extended the family of constant distance operators  \cite{zhang2020improving} so they are compatible with \textit{quant}.
-These operators are presented in \textbf{\nameref{sect:S1Appendix}}.
-
-The computational requirements of i-CDF evaluation may hinder the performance of the \textit{quant} parameterisation.
+In this project we extended the family of constant distance operators  \cite{zhang2020improving} so they are compatible with \textit{quant} (\textbf{\nameref{sect:S1Appendix}}).
+
+When $\sigma$ is proposed under either \textit{quant} or \textit{cat}, all of the rates $r(\vec{\mathcal{R}}^{\,})$ are proposed along with it, thus enabling large changes to the state space with a single proposal.
+Whereas, this is not the case for \textit{real}, which led to the development of the \texttt{FastClockScale} operator \cite{zhang2020improving}.
 
@@
  \hline
-\texttt{ConstantDistance} & Adjusts an internal node and recalculates all incident branch rates such that the genetic distances remain constant \cite{zhang2020improving}.
+\texttt{ConstantDistance} & Adjusts an internal node height and recalculates all incident branch rates such that the genetic distances remain constant \cite{zhang2020improving}.
 & $\vec{\mathcal{R}}^{\,}, \mathcal{T}$ & \textit{real}, \textit{quant} \\
@@
 \texttt{FastClockScale} & Applies \texttt{Scale} to $\sigma$ and then recomputes all rates $\vec{\mathcal{R}}^{\,}$ such that their quantiles under the prior $p(\vec{\mathcal{R}}^{\,}|\sigma)$ are constant \cite{zhang2020improving}.
-& $\mathcal{R}$ & \textit{real} \\
+& $\vec{\mathcal{R}}^{\,}, \sigma$ & \textit{real} \\
  \hline
@@
 \label{eqn:adaptiveSampler}
-	p(\omega_i) \propto \begin{cases} 1 & \text{ with probability } \Omega \\ \frac{1}{\mathbb{T}(\omega_i)} \sum\limits_{p \in \text{parameters}} \frac{1}{\sigma^2_p} \Big[ \sum\limits_{x \in \text{accepts}_i}  (x_p - x_p^\prime)^2 \Big] & \text{ with probability } 1-\Omega \end{cases}.
+	p(\omega_i) \propto \begin{cases} 1 & \text{ with probability } \Omega \\ \frac{1}{\mathbb{T}(\omega_i)} \sum\limits_{p \in \text{parameters}} \frac{1}{\sigma^2_p}  \sum\limits_{x \in \text{accepts}_i}  || x_p - x_p^\prime ||^2 & \text{ with probability } 1-\Omega \end{cases}
 \end{align}
@@
 where $\Omega = 0.01$ allows any sub-operator to be sampled regardless of its performance.
-The remaining terms are trained during the second and third phases: the cumulative computational runtime spent on each operator $\mathbb{T}(\omega_i)$, the sample variance $\sigma^2_p$ of each parameter $p$, and the sum-of-squares $\sum\limits_{x \in \text{accepts}_i} (x_p - x_p^\prime)^2$, where $x_p$ and $x_p^\prime$ are the values of $p$ before and after each acceptance of a proposal made by $\omega_i$.
+The remaining terms are trained during the second and third phases: the cumulative computational runtime spent on each operator $\mathbb{T}(\omega_i)$, the sample variance $\sigma^2_p$ of each parameter $p$, and the sum-of-squares $\sum\limits_{x \in \text{accepts}_i} ||x_p - x_p^\prime||^2$, where $x_p$ and $x_p^\prime$ are the values of $p$ before and after each acceptance of a proposal made by $\omega_i$.
 
@@
 
-Under Equation \ref{eqn:adaptiveSampler}, operators which effect larger changes on the parameters of interest, in shorter runtime, are sampled with greater probabilities. 
+Under \textbf{Equation \ref{eqn:adaptiveSampler}}, operators which effect larger changes on the parameters of interest, in shorter runtime, are sampled with greater probabilities. 
 Division of the sum-of-squares term by the parameter variance $\sigma^2_p$ enables comparison between different parameters.
@@
 We also introduce the \texttt{SampleFromPrior($\vec{x}^{\,}$)} operator.
-This operator resamples $\psi$ randomly selected elements within vector $\vec{x}^{\,}$ from their prior distributions, where $\psi \sim \text{Binomial}(n=|\vec{x}^{\,}|, p=\frac{s}{|\vec{x}^{\,}|})$ for tunable parameter $s$.
+This operator resamples $\psi$ randomly selected elements within vector $\vec{x}^{\,}$ from their prior distributions, where $\psi \sim \text{Binomial}(n=|\vec{x}^{\,}|, p=\frac{s}{|\vec{x}^{\,}|})$ for tunable term $s$.
 
@@
 Whereas, datasets which contain very poor signal (or small $L$) are likely to mix best when there is more weight placed on bold operators such as \texttt{SampleFromPrior}, \texttt{Swap}, or \texttt{Uniform} which sample each branch rate independently of its current estimate.
-\texttt{AdaptiveOperatorSampler} should learn the combination of weights behind these classes of operators best suited for any given dataset.
+Ideally, an operator to the likes of \texttt{AdaptiveOperatorSampler} would learn the combination of weights behind these classes of operators best suited for any given dataset.
 
@@
 In the low signal dataset ($L=0.1$kb), both operators can traverse the likelihood space effectively.
- However, the same exact same proposal by \texttt{RandomWalk} incurs a much larger likelihood penalty in the $L=0.5$kb dataset by ``falling off the ridge'', in contrast to \texttt{ConstantDistance} which ``walks along the ridge''.
+ However, the exact same proposal by \texttt{RandomWalk} incurs a much larger likelihood penalty in the $L=0.5$kb dataset by ``falling off the ridge'', in contrast to \texttt{ConstantDistance} which ``walks along the ridge''.
  This discrepancy is even stronger for larger datasets and thus necessitates the use of operators such as \texttt{ConstantDistance} which account for correlations between branch lengths and rates. }
@@
 \end{tabular}
-\caption{Summary of the three instances of \texttt{AdaptiveOperatorSampler} used under the \textit{real} and \textit{quant} parameterisations.  $^{*}$\textit{real} only. $^{**}$\textit{quant} only. }
+\caption{Summary of the three instances of \texttt{AdaptiveOperatorSampler} used under the \textit{real} and \textit{quant} parameterisations.
+\texttt{AdaptiveOperatorSampler(root)} applies the root-targetting constant distance operators only \cite{zhang2020improving} while \texttt{AdaptiveOperatorSampler($\vec{\mathcal{R}}^{\,}$)} targets all rates and all nodes.
+The two meta-operators are weighted proportionally to the contribution of the root node to the total node count. 
+  $^{*}$\textit{real} only. $^{**}$\textit{quant} only. }
 \label{table:adaptiveSampling}
@@
 The step size of a proposal kernal $q(x^\prime|x)$ should be such that the proposed state $x^\prime$ is sufficiently far from the current state $x$ to explore vast areas of parameter space, but not so large that the proposal is rejected too often \cite{roberts1997weak}.
-Yang et al.
-have challenged the widely used uniform proposal kernel in place of the Bactrian kernel \cite{yang2013searching, thawornwattana2018designing}.
+Operators which attain an acceptance probability of 0.234 are often considered to have arrived at a suitable midpoint between these two extremes \cite{bouckaert2019beast, roberts1997weak}.
+The standard uniform distribution kernel has recently been challenged by the Bactrian kernel \cite{yang2013searching, thawornwattana2018designing}.
 The $\text{Bactrian}(m)$ distribution is defined as the sum of two Normal distributions:
@@
 Yang et al.
-2013 \cite{yang2013searching} suggest that $\text{Bactrian}(m=0.95)$ yields a proposal kernel superior to the uniform kernel, by placing minimal probability on steps which are too small or too large.
+2013 \cite{yang2013searching} suggest that $\text{Bactrian}(m=0.95)$ yields a proposal kernel which traverses the posterior distribution more efficiently that the standard uniform kernel, by placing minimal probability on steps which are too small or too large.
+In this case, a target acceptance probability of around 0.3 is optimal.
 
@@
 
-In this article we compare the performance of uniform and Bactrian proposal kernels in the clock model.
-Two Bactrian distributions are compared($m=0.95$ and $m=0.98$).
+In this article we compare the performance of uniform and Bactrian proposal kernels with respect to estimating clock model parameters $\vec{\mathcal{R}}^{\,}$ and $\sigma$.
+Two Bactrian distributions are compared ($m=0.95$ and $m=0.98$).
 The clock model operators which these proposal kernels apply to are described in \textbf{Table \ref{table:bactriankernels}}.
@@
 
-The \texttt{NarrowExchange} operator \cite{drummond2002estimating}, used widely in BEAST \cite{drummond2012bayesian,suchard2018bayesian} and BEAST2 \cite{bouckaert2019beast}, is similar to nearest neighbour interchange (NNI), and works as follows (\textbf{Fig.
+The \texttt{NarrowExchange} operator \cite{drummond2002estimating}, used widely in BEAST \cite{drummond2012bayesian,suchard2018bayesian} and BEAST2 \cite{bouckaert2019beast}, is similar to nearest-neighbour-interchange \cite{semple2003phylogenetics}, and works as follows (\textbf{Fig.
 \ref{fig:narrowexchange}}):
@@
 Lakner et al.
-2008 \cite{lakner2008efficiency} found that tree operators which perterb topology (such as NNI) consistently perform better than those which also change branch lengths (such as LOCAL \cite{simon1998local} and Continuous Change \cite{jow2002bayesian}).
-If \texttt{NarrowExchange} could be adapted to the relaxed clock model by ensuring that genetic distances remain constant after the proposal, its performance may be improved even further. 
-This may in turn permit proposing a new node height $t_D$ and therefore changing branch (time) lengths.
+2008 \cite{lakner2008efficiency} found that tree operators which perterb topology (such as nearest-neighbour-interchange and subtree-prune-and-regraft \cite{semple2003phylogenetics}) consistently perform better than those which also change branch lengths (such as LOCAL \cite{simon1998local} and Continuous Change \cite{jow2002bayesian}).
+If \texttt{NarrowExchange} was adapted the relaxed clock model by ensuring that genetic distances remain constant after the proposal (akin to the constant distance operators \cite{zhang2020improving}), then its ability to traverse the state space may improve.
+This may in turn permit proposing a new node height $t_D$ and therefore changing branch lengths.
 
@@
 NER (and NERw) are compatible with both the \textit{real} and \textit{quant} parameterisations.
-Analagous to the \texttt{ConstantDistance} operator, new rates are proposed such that genetic distances between nodes $A$, $B$, $C$, and $E$ are maintained.
-Thus, there are $\binom{4}{2} = 6$ pairwise distance constraints.
+Analagous to the \texttt{ConstantDistance} operator, the proposed rates ensure that the genetic distances between nodes $A$, $B$, $C$, and $E$ are constant. 
+There are six pairwise distance between these four nodes and therefore six constraints:
 
@@
 
-Unfortunately, it is not possible to solve all six $\mathcal{D}_{ij}$ constraints without permitting non-positive rates or illegal trees.
-Therefore rather than conserving all six pairwise distances, NER conserves a \textit{subset} of distances.
-It is not immediately clear which distances should be conserved.
+Unfortunately, there is no solution to all six $\mathcal{D}_{ij}$ constraints unless non-positive rates or illegal trees are permitted.
+ Therefore rather than conserving all six pairwise distances, NER conserves a \textit{subset} of distances. It is not immediately clear which subset should be conserved.
 
@@
 This is equivalent to \texttt{NarrowExchange}. 
-
-As it is unclear which NER variants would perform the best, we developed an automated pipeline for generating and testing these operators.
+To determine which NER variants have the best performance, we developed an automated pipeline for generating and testing these operators.
 
 \paragraph{1.
-Solution finding.} Using standard analytical linear-system solving libraries in MATLAB, the $2^6=64$ subsets of distance constraints are solved.
-54 out of the 64 subsets were found to be solvable, and the unsolvables were discarded.
-
-\paragraph{2. Solving Jacobian determinants.} The determinant of the Jacobian matrix $J$ is required for computng the Hastings ratio of the proposal. $J$ is defined as
+Solution finding.} Using standard analytical linear-system solving libraries in MATLAB \cite{higham2016matlab}, the $2^6=64$ subsets of distance constraints were solved.
+54 of the 64 subsets were found to be solvable, and the unsolvables were discarded.
+
+\paragraph{2. Solving Jacobian determinants.} The determinant of the Jacobian matrix $J$ is required for computng the Green ratio of the proposal. $J$ is defined as
 
@@
 $|J|$ is further augmented if the \textit{quant} parameterisation is employed (\textbf{\nameref{sect:S1Appendix}}).
+Two such operators are expressed in \textbf{Algorithms \ref{alg:NER1} and \ref{alg:NER2}}.
+
+\begin{algorithm}
+\caption{The NER$\{ \mathcal{D}_{BC}, \mathcal{D}_{CE} \}$ operator.}
+\begin{algorithmic}[1]
+
+\Procedure{proposal}{$t_A$, $t_B$, $t_C$, $t_D$, $t_E$, $r_A$, $r_B$, $r_C$, $r_D$}
+
+	\State
+    \State $s\Sigma \leftarrow $ getRandomWalkSize() \Comment{Random walk size is 0 unless this is NERw}
+    \State $t_D^\prime \leftarrow t_D + s\Sigma$ \Comment{Propose new node height for $D$}
+    \State
+    \State $r_A^\prime \leftarrow r_A$ \Comment{Propose new rates}
+    \State $r_B^\prime \leftarrow \frac{r_B(t_D - t_B) + r_D(t_E - t_D) + r_D(t_E - t_D^\prime)}{t_D^\prime - t_B}$
+    \State $r_C^\prime \leftarrow \frac{r_C(t_E - t_C) - r_D(t_E - t_D^\prime)}{t_D^\prime - t_C}$
+    \State $r_D^\prime \leftarrow r_D$
+    \State
+    \State $|J| \leftarrow \frac{(t_D - t_B)(t_E - t_C)}{(t_D^\prime - t_B)(t_D^\prime - t_C)}$ \Comment{Calculate Jacobian determinant}
+    \State \Return $(r_A^\prime, r_B^\prime, r_C^\prime, r_D^\prime, t_D^\prime, |J|)$
+
+\EndProcedure
+
+\end{algorithmic}
+\label{alg:NER1}
+\end{algorithm}
+
+\begin{algorithm}
+\caption{The NER$\{ \mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE} \}$ operator.}
+\begin{algorithmic}[1]
+
+\Procedure{proposal}{$t_A$, $t_B$, $t_C$, $t_D$, $t_E$, $r_A$, $r_B$, $r_C$, $r_D$}
+
+	\State
+    \State $s\Sigma \leftarrow $ getRandomWalkSize() \Comment{Random walk size is 0 unless this is NERw}
+    \State $t_D^\prime \leftarrow t_D + s\Sigma$ \Comment{Propose new node height for $D$}
+    \State
+    \State $r_A^\prime \leftarrow \frac{r_A(t_D - t_A) + r_D(t_E - t_D)}{t_E - t_A}$ \Comment{Propose new rates}
+    \State $r_B^\prime \leftarrow \frac{r_B(t_D - t_B) + r_D(t_D^\prime - t_D)}{t_D^\prime - t_B}$
+    \State $r_C^\prime \leftarrow \frac{r_C(t_E - t_C) - r_D(t_E - t_D^\prime)}{t_D^\prime - t_C}$
+    \State $r_D^\prime \leftarrow r_D$
+    \State
+    \State $|J| \leftarrow \frac{(t_D - t_A)(t_D - t_B)(t_E - t_C)}{(t_E - t_A)(t_D^\prime - t_B)(t_D^\prime - t_C)}$ \Comment{Calculate Jacobian determinant}
+    \State \Return $(r_A^\prime, r_B^\prime, r_C^\prime, r_D^\prime, t_D^\prime, |J|)$
+
+\EndProcedure
+
+\end{algorithmic}
+\label{alg:NER2}
+\end{algorithm}
 
@@
 Each operator is considered with and without a random walk on $t_D$ and thus there are 96 total settings.
-
-%Each NER variant differs by its a) proposals, which are the solutions found in step \textbf{1}, and b) its Jacobian $|J|$.
-
-%On top of topological changes, NER is comprised of proposals for ${r_A}^\prime$, ${r_B}^\prime$, ${r_C}^\prime$, and ${r_D}^\prime$.
 
@@
 \clearpage
+\subsection*{Model specification and MCMC settings} \label{sect:methods}
+
+In all phylogenetic analyses presented here, we use a Yule \cite{yule1925ii} tree prior $p(\mathcal{T}|\lambda)$ with birth rate $\lambda \sim \text{Log-Normal}(1,1.25)$.
+The clock standard deviation has a $\sigma \sim \text{Gamma}(0.5396,0.3819)$ prior.
+Datasets are partitioned into subsequences, where each partition is associated with a distinct HKY substitution model \cite{hasegawa1985dating}.
+The transition-transversion ratio $\kappa \sim \text{Log-Normal}(1, 1.25)$, the four nucleotide frequencies $(f_A, f_C, f_G, f_T) \sim \text{Dirichlet}(10,10,10,10)$, and the relative clock rate $\mu_C \sim \text{Log-Normal}(1, 0.6)$ are estimated independently for each partition.
+The operator scheme ensures that the clock rates $\mu_C$ have a mean of 1 across all partitions. 
+To enable the rapid benchmarking of larger datasets we use BEAGLE for high-performance tree likelihood calculations \cite{ayres2012beagle} and coupled MCMC with four chains for efficient mixing \cite{muller2019coupled}.
+The neighbour joining tree \cite{saitou1987neighbor} is used as the initial state in each MCMC chain.
+
+\clearpage
 \section*{Results} \label{sect:results}
@@
 
-Methodologies are benchmarked using one simulated and nine empirical datasets -- the latter were compiled \cite{lanfear2019Github} and partitioned \cite{lanfear2016partitionfinder} by Lanfear et al.
-as `benchmark alignments' (\textbf{Table \ref{table:datasets}}).
-To facilitate convergence on complex datasets, each posterior distribution is sampled using coupled MCMC (MC$^3$) with 4 chains \cite{muller2019coupled}.
-Each methodology is benchmarked across 5 replicates on each dataset, using an the Intel Xeon Gold 6138 CPU (2.00 GHz) and all methodologies use identical models and operator configurations, except where a difference is specified.
+Methodologies are benchmarked using one simulated and nine empirical datasets.
+The latter were compiled \cite{lanfear2019Github} and partitioned \cite{lanfear2016partitionfinder} by Lanfear et al. as `benchmark alignments' (\textbf{Table \ref{table:datasets}}).
+Each methodology is benchmarked across 5 replicates on each dataset, using an the Intel Xeon Gold 6138 CPU (2.00 GHz).
+All methodologies use identical models and operator configurations, except where a difference is specified.
 
@@
 Operators which apply to either internal nodes or the root (but not both) are weighted according to leaf count $N$.
-The adapt operators are further broken down in \textbf{Table \ref{table:adaptiveSampling}}.
-The total weight of all operators across all parameters was 116 in each MCMC setup.
-Therefore a weight of 10 corresponds to sampling probability of 0.086, for example.}
+The adapt operators are further broken down in \textbf{Table \ref{table:adaptiveSampling}}.}
+%The total weight of all operators across all parameters was 116 in each MCMC setup.
+T%herefore a weight of 10 corresponds to sampling probability of 0.086, for example.
 \label{table:round1Results}
@@
 \clearpage
-\subsection*{Round 2: The three rate parameterisations yield similar mixing ability }
+\subsection*{Round 2: The \textit{real} parameterisation yields the fastest mixing }
 
@@
 
-\subsection*{Round 3: The Bactrian proposal kernel is the best for the clock model}
+\subsection*{Round 3: Bactrian proposal kernels are 10\% more efficient than uniform kernels}
 
@@
 
-\subsubsection*{Initial screening by acceptance rate}
+\subsubsection*{Initial screening by acceptance rate on simulated data}
 
@@
 \caption{\textbf{Screening of NER and NERw variants by acceptance rate.} Top left: comparison of NER variants with the null operator $\text{NER}\{\}$ (i.e.
-\texttt{Narrow Exchange}).
+\texttt{NarrowExchange}).
 Each of the 48 operators are represented by a single point, uniquely encoded by the point stylings.
@@
 This process is repeated for each of $300$ simulated datasets.
-The axes of each plot are the proportion of these $300$ simulations for which there is evidence that the operator is better than $\text{NER}\{\}$ (x-axis) or worse than $\text{NER}\{\}$ (y-axis).
+The axes of each plot are the proportion of these $300$ simulations for which there is evidence that the operator is significantly better than $\text{NER}\{\}$ (x-axis) or worse than $\text{NER}\{\}$ (y-axis).
 Top right: comparison of NER and NERw acceptance rates.
 Each point is one NER/NERw variant from a single simulation.
-Bottom: relationship between the acceptance rates $\alpha$ of $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ and $\text{NER}\{ \}$ with the clock model standard deviation $\sigma$ and the number of patterns $L_\textit{eff}$.
+Bottom: relationship between the acceptance rates $\alpha$ of $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ and $\text{NER}\{ \}$ with the clock model standard deviation $\sigma$ and the number of sites $L$.
 Each point is a single simulation.
@@
 \ref{fig:acceptanceRateScreening}} also reveals a cluster of NER variants which -- under the conditions of the simulation --  performed better than the null operator $\text{NER}\{\}$ around 25\% of the time and performed worse around 10\% of the time.
-One such operator is  $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$.
-This variant conserves the genetic distance between all child nodes $A$, $B$, and $C$, and the grandparent node $E$.
+One such operator is  $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ and is presented in \textbf{Algorithm \ref{alg:NER2}}. 
+This variant conserves the genetic distance between the child nodes ($A, B, C$) and the grandparent node $E$.
 This is performed by proposing rates for $r_A$, $r_B$, and $r_C$ while obeying the distance constraints imposed by the operator.
@@
 when clock standard deviation $\sigma$ is high ($\sigma \gtrsim 0.5$ for $N=30$), corresponding to data which is not clock-like.
-On the other hand, $\text{NER}\{\}$ is much preferred when the operator's acceptance rate is high ($\gtrsim 0.15$) -- corresponding with datasets with a small number of site patterns ($L_\textit{eff} \lesssim 500$ for $N=30$) and thus poor signal.
-Overall, $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ outperforms the standard \texttt{Narrow Exchange} operator when the data is not clock-like and contains enough signal.
+On the other hand, $\text{NER}\{\}$ is much preferred when the operator's acceptance rate is high ($\gtrsim 0.15$) -- corresponding to datasets with short sequences ($L < 1$kb for $N=30$) and thus poor signal.
+Overall, $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ outperforms the standard \texttt{NarrowExchange} operator when the data is not clock-like and contains enough signal.
 
@@
 
-Although there are several operators tying for first place, we selected the $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ operator to proceed to the next round of optimisation.
+Although there are several operators which are tying for first place and behave equivalently, we selected the $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ operator to proceed to the next round of optimisation.
 
@@
 
-\subsection*{Evaluating the AVMVN leaf rate operator}
-
-\subsection*{Clock model averaging}
+\subsection*{Round 5: The AVMVN leaf rate operator works well for small taxon sets}
 

### 2020-07-30 correlations.R

@@ -83,13 +83,13 @@ for (L in c(100, 500)){
 	breaks  =signif(breaks, 2)
 	breaks = round(breaks / 10, 0) * 10
 	#seq(from = min(lnL.vec), to = max(lnL.vec), length = nbins+1)
-	image(x, y, lnL, xlab="Branch rate $r$", ylab="Branch length $\\tau$", axes=F,  main = paste0("log-likelihood when L = ", L/1000, "kb"), col = cols,
+	image(x, y, xlim = c(0, xmax), ylim = c(0, xmax), lnL, xlab="Branch rate $r$", ylab="Branch length $\\tau$", axes=F,  main = paste0("log-likelihood when L = ", L/1000, "kb"), col = cols,
 			 breaks = breaks, useRaster = TRUE, xaxs = "i", yaxs = "i")
 
 
 
 	par(new=TRUE)
-	contour(x, y, lnL, xlab="", ylab="", axes=F,  main = "", nlevels = nbins, levels = breaks, xaxs = "i", yaxs = "i", col = "black", lwd = 2, labcex = 1.0)
+	contour(x, y, lnL, xlab="", ylab="", axes=F,  main = "", nlevels = nbins, levels = breaks, xaxs = "i", yaxs = "i", col = "black", lwd = 2, labcex = 1.0, xlim = c(0, xmax), ylim = c(0, xmax))
 
 	axis(1, at = seq(from = 0, to = xmax, by = 0.5))
 	axis(2, at = seq(from = 0, to = xmax, by = 0.5), las=2)

### 2020-07-30 lognormal.R

@@ -108,7 +108,7 @@ for (i in 1:length(Svals)){
 	S = Svals[i]
 	M = Mvals[i]
 	x = seq(from = 0, to = 1, by = 0.001)
-	y = qlnorm (x, M, S)
+	y = c(qlnorm (x[-length(x)], M, S), xmax*2)
 	lines(x, y, pch = 16, col = Scols[i], lwd = 3)
 }
 

### 2020-07-31 S1_appendix.tex
tree figs

@@
 
-\section*{S1 Appendix: Rate quantiles}
+\section*{S1 Appendix: Tree operators for rate quantiles}
 
-\section{Linear piecewise approximation}
+Zhang and Drummond 2020 introduced several tree operators for the \textit{real} parameterisation -- including Constant Distance, Simple Distance, and Small Pulley \cite{zhang2020improving}.
+In this appendix, these three operators are extended to the  the \textit{quant} parameterisation.
+Following the notation presented in the main article, let $t_i$ be the time of node $i$, let $0 < q_i < 1$ be the rate quantile of node $i$, and let $r_i = F^{-1}(q_i)$ be the real rate of node $i$ where $F^{-1}$ is the inverse cumulative density function (i-CDF).
 
-In this article we introduced a linear piecewise approximation of the i-cdf to improve the \textit{quant} method.
-Let $\hat{F}^{-1}(\mathcal{R}_i)$ be the piecewise approximation of $F^{-1}(\mathcal{R}_i)$.
-The approximation is comprised of $n$ pieces (where $n$ is fixed).
+\subsection*{Constant Distance}
 
-%$\hat{F}(\mathcal{R}_i)$ be the piecewise approximation of $F(\mathcal{R}_i)$, and let  be its inverse function.
+Let $\mathcal{X}$ be a uniformly-at-random sampled internal node on tree $\mathcal{T}$.
+Let $\mathcal{L}$ and $\mathcal{R}$ be the left and right child of $\mathcal{X}$, respectively, and let $\mathcal{P}$ be the parent of $\mathcal{X}$.
+Under the \textit{quant} parameterisation, the \texttt{ConstantDistance} operator works as follows: \\
+
+\textul{\textit{Step 1}}. Propose a new height for $t_\mathcal{X}$:
 
 \begin{align}
-\hat{F}^{-1}(\mathcal{R}_i) = F^{-1}(\floor{b_i}) + \begin{cases} \Big( F^{-1}(\floor{b_i} + 1) - F^{-1}(\floor{b_i}) \Big) \Big( b_i - \floor{b_i}  \Big) &\text{ if } \floor{b_i} < n-1  \\ 0 &\text{ if } \floor{b_i} = n-1 \end{cases}
+	{t_\mathcal{X}}^\prime \leftarrow t_\mathcal{X} + s\Sigma
 \end{align}
 
-where $b_i = \min \{ \max\{ \frac{n \times \mathcal{R}_i}{n-1}, \frac{n_0}{n-1} \}, \frac{n - 1 -n_0}{n-1} \}$ indexes $\mathcal{R}_i$ into one of the $n$ pieces $\floor{b_i}$.
-$n_0 = 0.1$ provides a lower and upper limits of the piecewise approximation, corresponding to $r_\text{min}$ and $r_\text{max}$ respectively.
-The lower and upper rate limits are equal to:
+where $\Sigma$ is drawn from a proposal transition distribution (Uniform or Bactrian), and $s$ is a tunable step size.
+Ensure that $\max\{t_\mathcal{L}, t_\mathcal{R} \} < {t_\mathcal{X}}^\prime < t_\mathcal{P}$, and if the constraint is broken then reject the proposal.
+\\
+
+\textul{\textit{Step 2}}. Recalculate $q_\mathcal{X}$ as:
 
 \begin{align}
-r_\text{min} &= F^{-1}\Big( \frac{n_0}{n-1}\Big) = F^{-1}\Big( 0.001 \Big) \\
-r_\text{max} &= F^{-1}\Big( \frac{n - 1 -n_0}{n-1}\Big) = F^{-1}\Big( 0.999 \Big),
+	{q_\mathcal{X}}^\prime  \leftarrow & F\Big({r_\mathcal{X}}^\prime \Big) \nonumber\\
+				\leftarrow & F\Big(\frac{t_\mathcal{P} - t_\mathcal{X}}{t_\mathcal{P} - {t_\mathcal{X}}^\prime} r_X \Big)\nonumber \\
+				\leftarrow & F\Big(\frac{t_\mathcal{P} - t_\mathcal{X}}{t_\mathcal{P} - {t_\mathcal{X}}^\prime} F^{-1}(q_\mathcal{X}) \Big).
 \end{align}
 
-when $n=101$ and $n_0=0.1$.
-It is important to ensure that any operators which act in rate space (as opposed to quantile space) respect these boundaries.
-The inverse of the approximation function (ie.
-the cdf $\hat{F}$) is
+This ensures that the genetic distance between $\mathcal{X}$ and $P$ remains constant after the operation by enforcing the constraint:
 
 \begin{align}
-\hat{F}(r_i) = \begin{cases} \max \big(0, \frac{1}{n-1} \times \Big( v_i + \frac{r_i -  F^{-1}(\floor{v_i})}{F^{-1}(\floor{v_i}+1) - F^{-1}(\floor{v_i})} \Big) \big) &\text{ if } \floor{v_i} < n-1  \\
-	1 &\text{ if } \floor{v_i} = n-1 
-\end{cases}
+	r_\mathcal{X} (t_\mathcal{P} - t_\mathcal{X}) = {r_\mathcal{X}}^\prime (t_\mathcal{P} - {t_\mathcal{X}}^\prime).
 \end{align}
 
-where $v_i \in (0, 1, \dotso, n-1)$ is the piece which $r_i$ corresponds to:
+\textul{\textit{Step 3}}. Similarly, propose new rate quantiles for the two children $\mathcal{C} \in \{\mathcal{L}, \mathcal{R}\}$:
 
 \begin{align}
-v_i = \max\limits_{j = 0}^{n-1} \{ j : \hat{F}^{-1}\big(\frac{j}{n-1}\big) < r_i \}.
+	{q_\mathcal{C}}^\prime  \leftarrow & F\Big({r_\mathcal{C}}^\prime \Big) \nonumber\\
+				\leftarrow & F\Big(\frac{t_\mathcal{X} - t_\mathcal{C}}{{t_\mathcal{X}}^\prime - t_\mathcal{C}} \times r_\mathcal{C} \Big) \nonumber\\
+				\leftarrow & F\Big(\frac{t_\mathcal{X} - t_\mathcal{C}}{{t_\mathcal{X}}^\prime - t_\mathcal{C}} \times F^{-1}(q_\mathcal{C}) \Big).
 \end{align}
 
-As the piecewise approximation is linear, computing the derivatives of these two functions (required for computing Hastings ratios) are trivial:
+Ensure that $0 < {q_i}^\prime < 1$ for all proposed nodes $i \in \{\mathcal{X}, L, R\}$, and if the constraint is broken then reject the proposal. 
+This constraint can only be broken from numerical issues.
+
+\textul{\textit{Step 4}}. Finally, in order to calculate the Metropolis-Hastings-Green ratio, return the determinant of the Jacobian matrix:
 
 \begin{align}
-\frac{\partial}{\partial \mathcal{R}_i} \hat{F}^{-1}(\mathcal{R}_i) =  D \hat{F}^{-1}(\mathcal{R}_i) &= \begin{cases}  \Big(\hat{F}^{-1}(\floor{b_i}+1) - \hat{F}^{-1}(\floor{b_i})\Big) \times(n-1)  & \text{ if } \floor{b_i} < n-1 \\
-0 & \text{ if } \floor{b_i} = n-1 \end{cases} \label{eqn:derivFinv}  \\
-\frac{\partial}{\partial r_i} \hat{F}(r_i) = D \hat{F}(r_i) &= \frac{1}{\hat{F}^{-1}\Big(\hat{F}(r_i)\Big)} \label{eqn:derivF}
-\end{align}
-
-\section{Tree operators for rate quantiles}
-
-Zhang and Drummond 2020 introduced several tree operators for the \textit{real} parameterisation -- including Constant Distance, Simple Distance, and Small Pulley.
-In this appendix, these three operators are extended to the  the \textit{quant} parameterisation.
-
-Following the notation presented in the main article, let $t_i$ be the time of node $i$, let $0 < q_i < 1$ be the rate quantile of node $i$, and let $r_i = \hat{F}^{-1}(q_i)$ be the natural rate of node $i$.
-
-\subsection{Constant Distance}
-
-Let $X$ be a uniformly-at-random sampled internal node on tree $\mathcal{T}$.
-Let $L$ and $R$ be the left and right child of $X$, respectively, and let $P$ be the parent of $X$.
-Under the \textit{quant} parameterisation, the Constant Distance operator works as follows: \\
-
-\textul{\textit{Step 1}}. Propose a new height for $t_X$:
-
-\begin{align}
-	{t_X}^\prime \leftarrow t_X + \alpha
-\end{align}
-
-where $\alpha \sim \text{ Uniform}(-w, w)$, for some window size $w$. Ensure that $\max\{t_L, t_R \} < {t_X}^\prime < t_P$, and if the constrant is broken then reject the proposal.  \\
-
-\textul{\textit{Step 2}}. Recalculate $q_X$ as:
-
-\begin{align}
-	{q_X}^\prime  \leftarrow & \hat{F}\Big({r_X}^\prime \Big) \nonumber\\
-				\leftarrow & \hat{F}\Big(\frac{t_P - t_X}{t_P - {t_X}^\prime} r_X \Big)\nonumber \\
-				\leftarrow & \hat{F}\Big(\frac{t_P - t_X}{t_P - {t_X}^\prime} \hat{F}^{-1}(q_X) \Big).
-\end{align}
-
-This ensures that the genetic distance between $X$ and $P$ remains constant after the operation by enforcing the constraint:
-
-\begin{align}
-	r_X (t_P - t_X) = {r_X}^\prime (t_P - {t_X}^\prime).
-\end{align}
-
-\textul{\textit{Step 3}}. Similarly, propose new rate quantiles for the two children $C \in \{L, R\}$:
-
-\begin{align}
-	{q_C}^\prime  \leftarrow & \hat{F}\Big({r_C}^\prime \Big) \nonumber\\
-				\leftarrow & \hat{F}\Big(\frac{t_X - t_C}{{t_X}^\prime - t_C} \times r_C \Big) \nonumber\\
-				\leftarrow & \hat{F}\Big(\frac{t_X - t_C}{{t_X}^\prime - t_C} \times \hat{F}^{-1}(q_C) \Big).
-\end{align}
-
-Ensure that $r_\text{min} < {r_i}^\prime < r_\text{max}$ for all proposed nodes $i \in \{X, L, R\}$, and if the constraint is broken then reject the proposal.
-
-\textul{\textit{Step 4}}. Finally, compute the natural logarithm of the Hastings ratio as that of the determinant of the Jacobian matrix:
-
-\begin{align}
-	J &= \begin{bmatrix} \frac{\partial {t_X}^\prime}{\partial t_X} & \frac{\partial {t_X}^\prime}{\partial q_X} & \frac{\partial {t_X}^\prime}{\partial q_L} & \frac{\partial {t_X}^\prime}{\partial q_R} \\
-			\frac{\partial {q_X}^\prime}{\partial t_X} & \frac{\partial {q_X}^\prime}{\partial q_X} & \frac{\partial {q_X}^\prime}{\partial q_L} & \frac{\partial {q_X}^\prime}{\partial q_R} \\
-			\frac{\partial {q_L}^\prime}{\partial t_X} & \frac{\partial {q_L}^\prime}{\partial q_X} & \frac{\partial {q_L}^\prime}{\partial q_L} & \frac{\partial {q_L}^\prime}{\partial q_R} \\
-			\frac{\partial {q_R}^\prime}{\partial t_X} & \frac{\partial {q_R}^\prime}{\partial q_X} & \frac{\partial {q_R}^\prime}{\partial q_L} & \frac{\partial {q_R}^\prime}{\partial q_R} \\ \end{bmatrix} \nonumber \\
-			&= \begin{bmatrix} \frac{\partial {t_X}^\prime}{\partial t_X} & 0 & 0 & 0 \\
-			\frac{\partial {q_X}^\prime}{\partial t_X} & \frac{\partial {q_X}^\prime}{\partial q_X} & 0 & 0 \\
-			\frac{\partial {q_L}^\prime}{\partial t_X} & 0 & \frac{\partial {q_L}^\prime}{\partial q_L} & 0 \\
-			\frac{\partial {q_R}^\prime}{\partial t_X} & 0 & 0 & \frac{\partial {q_R}^\prime}{\partial q_R} \\ \end{bmatrix}.
+	J &= \begin{bmatrix} \frac{\partial {t_\mathcal{X}}^\prime}{\partial t_\mathcal{X}} & \frac{\partial {t_\mathcal{X}}^\prime}{\partial q_\mathcal{X}} & \frac{\partial {t_\mathcal{X}}^\prime}{\partial q_\mathcal{L}} & \frac{\partial {t_\mathcal{X}}^\prime}{\partial q_\mathcal{R}} \\
+			\frac{\partial {q_\mathcal{X}}^\prime}{\partial t_\mathcal{X}} & \frac{\partial {q_\mathcal{X}}^\prime}{\partial q_\mathcal{X}} & \frac{\partial {q_\mathcal{X}}^\prime}{\partial q_\mathcal{L}} & \frac{\partial {q_\mathcal{X}}^\prime}{\partial q_\mathcal{R}} \\
+			\frac{\partial {q_\mathcal{L}}^\prime}{\partial t_\mathcal{X}} & \frac{\partial {q_\mathcal{L}}^\prime}{\partial q_\mathcal{X}} & \frac{\partial {q_\mathcal{L}}^\prime}{\partial q_\mathcal{L}} & \frac{\partial {q_\mathcal{L}}^\prime}{\partial q_\mathcal{R}} \\
+			\frac{\partial {q_\mathcal{R}}^\prime}{\partial t_\mathcal{X}} & \frac{\partial {q_\mathcal{R}}^\prime}{\partial q_\mathcal{X}} & \frac{\partial {q_\mathcal{R}}^\prime}{\partial q_\mathcal{L}} & \frac{\partial {q_\mathcal{R}}^\prime}{\partial q_\mathcal{R}} \\ \end{bmatrix} \nonumber \\
+			&= \begin{bmatrix} \frac{\partial {t_\mathcal{X}}^\prime}{\partial t_\mathcal{X}} & 0 & 0 & 0 \\
+			\frac{\partial {q_\mathcal{X}}^\prime}{\partial t_\mathcal{X}} & \frac{\partial {q_\mathcal{X}}^\prime}{\partial q_\mathcal{X}} & 0 & 0 \\
+			\frac{\partial {q_\mathcal{L}}^\prime}{\partial t_\mathcal{X}} & 0 & \frac{\partial {q_\mathcal{L}}^\prime}{\partial q_\mathcal{L}} & 0 \\
+			\frac{\partial {q_\mathcal{R}}^\prime}{\partial t_\mathcal{X}} & 0 & 0 & \frac{\partial {q_\mathcal{R}}^\prime}{\partial q_\mathcal{R}} \\ \end{bmatrix}.
 \end{align}
@@
 \begin{align}
-	\ln |J| =&  \ln \{ \frac{\partial {t_X}^\prime}{\partial t_X} \times \frac{\partial {q_X}^\prime}{\partial q_X} \times \frac{\partial {q_L}^\prime}{\partial q_L} \times \frac{\partial {q_R}^\prime}{\partial q_R} \} \nonumber\\
-		=& \ln 1 + \ln \; D \hat{F}\Big( \frac{t_P - t_X}{t_P - {t_X}^\prime} \times \hat{F}^{-1}(q_X)  \Big) + \ln \frac{\partial}{\partial q_X}  \frac{t_P - t_X}{t_P - {t_X}^\prime} \hat{F}^{-1} \Big( q_X \Big) \nonumber\\
-		& + \ln \; D\hat{F}\Big( \frac{t_X - t_L}{{t_X}^\prime - t_L} \times \hat{F}^{-1}(q_L) \Big) + \ln \frac{\partial}{\partial q_L} \frac{t_X - t_L}{{t_X}^\prime - t_L} \hat{F}^{-1} \Big( q_L \Big) \nonumber\\
-		& + \ln \; D \hat{F}\Big( \frac{t_X - t_R}{{t_X}^\prime - t_R} \times \hat{F}^{-1}(q_R) \Big) + \ln \frac{\partial}{\partial q_R} \frac{t_X - t_R}{{t_X}^\prime - t_R} \hat{F}^{-1} \Big( q_R \Big) \nonumber\\
-		=& \ln \; D \hat{F}\Big( \frac{t_P - t_X}{t_P - {t_X}^\prime} \times \hat{F}^{-1}(q_X)  \Big) + \ln \; D  \hat{F}^{-1} \Big( q_X \Big) + \ln \frac{t_P - t_X}{t_P - {t_X}^\prime} \nonumber\\
-		& + \ln \; D\hat{F}\Big( \frac{t_X - t_L}{{t_X}^\prime - t_L} \times \hat{F}^{-1}(q_L) \Big) + \ln \; D \hat{F}^{-1} \Big( q_L \Big) + \ln  \frac{t_X - t_L}{{t_X}^\prime - t_L} \nonumber \\
-		& + \ln \; D \hat{F}\Big( \frac{t_X - t_R}{{t_X}^\prime - t_R} \times \hat{F}^{-1}(q_R) \Big) + \ln \; D\hat{F}^{-1} \Big( q_R \Big) + \ln \frac{t_X - t_R}{{t_X}^\prime - t_R} .
+	\ln |J| =&  \ln \{ \frac{\partial {t_\mathcal{X}}^\prime}{\partial t_\mathcal{X}} \times \frac{\partial {q_\mathcal{X}}^\prime}{\partial q_\mathcal{X}} \times \frac{\partial {q_\mathcal{L}}^\prime}{\partial q_\mathcal{L}} \times \frac{\partial {q_\mathcal{R}}^\prime}{\partial q_\mathcal{R}} \} \nonumber\\
+		=& \ln 1 + \ln \; D F\Big( \frac{t_\mathcal{P} - t_\mathcal{X}}{t_\mathcal{P} - {t_\mathcal{X}}^\prime} \times F^{-1}(q_\mathcal{X})  \Big) + \ln \frac{\partial}{\partial q_\mathcal{X}}  \frac{t_\mathcal{P} - t_\mathcal{X}}{t_\mathcal{P} - {t_\mathcal{X}}^\prime} F^{-1} \Big( q_\mathcal{X} \Big) \nonumber\\
+		& + \ln \; DF\Big( \frac{t_X - t_\mathcal{L}}{{t_\mathcal{X}}^\prime - t_\mathcal{L}} \times F^{-1}(q_\mathcal{L}) \Big) + \ln \frac{\partial}{\partial q_\mathcal{L}} \frac{t_\mathcal{X} - t_\mathcal{L}}{{t_\mathcal{X}}^\prime - t_\mathcal{L}} F^{-1} \Big( q_\mathcal{L} \Big) \nonumber\\
+		& + \ln \; D F\Big( \frac{t_\mathcal{X} - t_\mathcal{R}}{{t_\mathcal{X}}^\prime - t_\mathcal{R}} \times F^{-1}(q_\mathcal{R}) \Big) + \ln \frac{\partial}{\partial q_\mathcal{R}} \frac{t_\mathcal{X} - t_\mathcal{R}}{{t_\mathcal{X}}^\prime - t_\mathcal{R}} F^{-1} \Big( q_\mathcal{R} \Big) \nonumber\\
+		=& \ln \; D F\Big( \frac{t_\mathcal{P} - t_\mathcal{X}}{t_\mathcal{P} - {t_\mathcal{X}}^\prime} \times F^{-1}(q_\mathcal{X})  \Big) + \ln \; D  F^{-1} \Big( q_\mathcal{X} \Big) + \ln \frac{t_\mathcal{P} - t_\mathcal{X}}{t_\mathcal{P} - {t_\mathcal{X}}^\prime} \nonumber\\
+		& + \ln \; DF\Big( \frac{t_\mathcal{X} - t_\mathcal{L}}{{t_\mathcal{X}}^\prime - t_\mathcal{L}} \times F^{-1}(q_\mathcal{L}) \Big) + \ln \; D F^{-1} \Big( q_\mathcal{L} \Big) + \ln  \frac{t_\mathcal{X} - t_\mathcal{L}}{{t_\mathcal{X}}^\prime - t_\mathcal{L}} \nonumber \\
+		& + \ln \; D F\Big( \frac{t_\mathcal{X} - t_\mathcal{R}}{{t_\mathcal{X}}^\prime - t_\mathcal{R}} \times F^{-1}(q_\mathcal{R}) \Big) + \ln \; DF^{-1} \Big( q_\mathcal{R} \Big) + \ln \frac{t_\mathcal{X} - t_\mathcal{R}}{{t_\mathcal{X}}^\prime - t_\mathcal{R}} .
 \end{align}
 
-The derivatives $D\hat{F}$ and $D\hat{F}^{-1}$ are readily computed under the linear piecewise approximation. As its final step, the operator returns $\ln |J|$.
+The derivatives $DF$ and $DF^{-1}$ can be computed using numerical approximations.
+ As its final step, the operator returns $\ln |J|$.
 
-\subsection{Simple Distance}
+\subsection*{Simple Distance}
 
-While Constant Distance proposes internal node heights, Simple Distance operates on the root. Let $X$ be the root node and let $L$ and $R$ be its two children.
+While \texttt{ConstantDistance} proposes internal node heights, \texttt{SimpleDistance} operates on the root.
+Let $\mathcal{X}$ be the root node and let $\mathcal{L}$ and $\mathcal{R}$ be its two children.
 
-\textul{\textit{Step 1}}. Propose a new height for $t_X$:
+\textul{\textit{Step 1}}. Propose a new height for $t_\mathcal{X}$:
 
 \begin{align}
-	{t_X}^\prime \leftarrow t_X + \alpha
+	{t_\mathcal{X}}^\prime \leftarrow t_\mathcal{X} + s\Sigma
 \end{align}
 
-where $\alpha \sim \text{ Uniform}(-w, w)$, for some window size $w$. Ensure that $\max\{t_L, t_R \} < {t_X}^\prime$, and if the constraint is broken then reject the proposal.  \\
+Ensure that $\max\{t_\mathcal{L}, t_\mathcal{R} \} < {t_\mathcal{X}}^\prime$, and if the constraint is broken then reject the proposal.  \\
 
-\textul{\textit{Step 2}}. Propose new rate quantiles for the two children $C \in \{L, R\}$:
+\textul{\textit{Step 2}}. Propose new rate quantiles for the two children $\mathcal{C} \in \{\mathcal{L}, \mathcal{R}\}$:
 
 \begin{align}
-	{q_C}^\prime  \leftarrow & \hat{F}\Big({r_C}^\prime \Big)  \nonumber \\
-				\leftarrow & \hat{F} \Big( \frac{t_X - t_C}{{t_X}^\prime - t_C} \times r_C \Big) \nonumber \\
-				\leftarrow & \hat{F} \Big( \frac{t_X - t_C}{{t_X}^\prime - t_C} \times \hat{F}^{-1}(q_C) \Big).
+	{q_\mathcal{C}}^\prime  \leftarrow & F\Big({r_\mathcal{C}}^\prime \Big)  \nonumber \\
+				\leftarrow & F \Big( \frac{t_\mathcal{X} - t_\mathcal{C}}{{t_\mathcal{X}}^\prime - t_\mathcal{C}} \times r_\mathcal{C} \Big) \nonumber \\
+				\leftarrow & F \Big( \frac{t_\mathcal{X} - t_\mathcal{C}}{{t_\mathcal{X}}^\prime - t_\mathcal{C}} \times F^{-1}(q_\mathcal{C}) \Big).
 \end{align}
 
-These proposals ensure that the genetic distance between $X$ and its children $C$ remain constant after the operation by enforcing the constraint:
+These proposals ensure that the genetic distance between $\mathcal{X}$ and its children $\mathcal{C}$ remain constant after the operation by enforcing the constraint:
 
 \begin{align}
-	r_C (t_X - t_C) = {r_C}^\prime ({t_X}^\prime - t_C).
+	r_\mathcal{C} (t_\mathcal{X} - t_\mathcal{C}) = {r_\mathcal{C}}^\prime ({t_\mathcal{X}}^\prime - t_\mathcal{C}).
 \end{align}
 
-Ensure that $r_\text{min} < {r_C}^\prime < r_\text{max}$, and if the constraint is broken then reject the proposal.
+Ensure that $0 < {q_C}^\prime < 1$, and if the constraint is broken then reject the proposal.
 
-\textul{\textit{Step 3}}. Return the natural logarithm of the Green ratio by calculating the determinant of the Jacobian matrix $J$.
+\textul{\textit{Step 3}}. Finally, in order to calculate the Metropolis-Hastings-Green ratio, return the determinant of the Jacobian matrix:
 
 \begin{align}
-	J &= \begin{bmatrix} \frac{\partial {t_X}^\prime}{\partial t_X} & \frac{\partial {t_X}^\prime}{\partial q_L} & \frac{\partial {t_X}^\prime}{\partial q_R} \\
-						\frac{\partial {q_L}^\prime}{\partial t_X} & \frac{\partial {q_L}^\prime}{\partial q_L} & \frac{\partial {q_L}^\prime}{\partial q_R} \\
-						\frac{\partial {q_R}^\prime}{\partial t_X} & \frac{\partial {q_R}^\prime}{\partial q_L} & \frac{\partial {q_R}^\prime}{\partial q_R} \end{bmatrix} \nonumber \\
-		&= \begin{bmatrix} \frac{\partial {t_X}^\prime}{\partial t_X} & 0 & 0 \\
-						\frac{\partial {q_L}^\prime}{\partial t_X} & \frac{\partial {q_L}^\prime}{\partial q_L} & 0\\
-						\frac{\partial {q_R}^\prime}{\partial t_X} & 0 & \frac{\partial {q_R}^\prime}{\partial q_R} \end{bmatrix}.
+	J &= \begin{bmatrix} \frac{\partial {t_\mathcal{X}}^\prime}{\partial t_\mathcal{X}} & \frac{\partial {t_\mathcal{X}}^\prime}{\partial q_\mathcal{L}} & \frac{\partial {t_\mathcal{X}}^\prime}{\partial q_\mathcal{R}} \\
+						\frac{\partial {q_\mathcal{L}}^\prime}{\partial t_\mathcal{X}} & \frac{\partial {q_\mathcal{L}}^\prime}{\partial q_\mathcal{L}} & \frac{\partial {q_\mathcal{L}}^\prime}{\partial q_\mathcal{R}} \\
+						\frac{\partial {q_\mathcal{R}}^\prime}{\partial t_\mathcal{X}} & \frac{\partial {q_\mathcal{R}}^\prime}{\partial q_\mathcal{L}} & \frac{\partial {q_\mathcal{R}}^\prime}{\partial q_\mathcal{R}} \end{bmatrix} \nonumber \\
+		&= \begin{bmatrix} \frac{\partial {t_\mathcal{X}}^\prime}{\partial t_\mathcal{X}} & 0 & 0 \\
+						\frac{\partial {q_\mathcal{L}}^\prime}{\partial t_\mathcal{X}} & \frac{\partial {q_\mathcal{L}}^\prime}{\partial q_\mathcal{L}} & 0\\
+						\frac{\partial {q_\mathcal{R}}^\prime}{\partial t_\mathcal{X}} & 0 & \frac{\partial {q_\mathcal{R}}^\prime}{\partial q_\mathcal{R}} \end{bmatrix}.
 \end{align}
@@
 \begin{align}
-	\ln |J| =&  \ln \{ \frac{\partial {t_X}^\prime}{\partial t_X} \times \frac{\partial {q_L}^\prime}{\partial q_L} \times \frac{\partial {q_R}^\prime}{\partial q_R} \} \nonumber \\
-			=& \ln \frac{\partial {t_X}^\prime}{\partial t_X} +  \ln \frac{\partial {q_L}^\prime}{\partial q_L} + \ln \frac{\partial {q_R}^\prime}{\partial q_R} \nonumber \\
+	\ln |J| =&  \ln \{ \frac{\partial {t_\mathcal{X}}^\prime}{\partial t_\mathcal{X}} \times \frac{\partial {q_\mathcal{L}}^\prime}{\partial q_\mathcal{L}} \times \frac{\partial {q_\mathcal{R}}^\prime}{\partial q_\mathcal{R}} \} \nonumber \\
+			=& \ln \frac{\partial {t_\mathcal{X}}^\prime}{\partial t_\mathcal{X}} +  \ln \frac{\partial {q_\mathcal{L}}^\prime}{\partial q_\mathcal{L}} + \ln \frac{\partial {q_\mathcal{R}}^\prime}{\partial q_\mathcal{R}} \nonumber \\
 			=& \ln 1  \nonumber\\
-			&+ \ln \; D \hat{F}\Big( \frac{t_X - t_L}{{t_X}^\prime - t_L} \times \hat{F}^{-1}(q_L) \Big) + \ln \frac{\partial}{\partial q_L} \frac{t_X - t_L}{{t_X}^\prime - t_L} \hat{F}^{-1} \Big( q_L \Big) \nonumber\\
-			&+ \ln \; D \hat{F}\Big( \frac{t_X - t_R}{{t_X}^\prime - t_R}\times \hat{F}^{-1}(q_R) \Big) + \ln \frac{\partial}{\partial q_R} \frac{t_X - t_R}{{t_X}^\prime - t_R} \hat{F}^{-1} \Big( q_R \Big) \nonumber\\
-			=& \ln \; D \hat{F}\Big( \frac{t_X - t_L}{{t_X}^\prime - t_L} \times \hat{F}^{-1}(q_L) \Big) + \ln \; D \hat{F}^{-1} \Big( q_L \Big) + \ln \frac{t_X - t_L}{{t_X}^\prime - t_L}\nonumber \\
-			&+ \ln \; D \hat{F}\Big( \frac{t_X - t_R}{{t_X}^\prime - t_R}\times \hat{F}^{-1}(q_R) \Big) + \ln \; D \hat{F}^{-1} \Big( q_R \Big) + \ln  \frac{t_X - t_R}{{t_X}^\prime - t_R}.
+			&+ \ln \; D F\Big( \frac{t_\mathcal{X} - t_\mathcal{L}}{{t_\mathcal{X}}^\prime - t_\mathcal{L}} \times F^{-1}(q_\mathcal{L}) \Big) + \ln \frac{\partial}{\partial q_\mathcal{L}} \frac{t_\mathcal{X} - t_\mathcal{L}}{{t_\mathcal{X}}^\prime - t_\mathcal{L}} F^{-1} \Big( q_\mathcal{L} \Big) \nonumber\\
+			&+ \ln \; D F\Big( \frac{t_\mathcal{X} - t_\mathcal{R}}{{t_\mathcal{X}}^\prime - t_\mathcal{R}}\times F^{-1}(q_\mathcal{R}) \Big) + \ln \frac{\partial}{\partial q_\mathcal{R}} \frac{t_\mathcal{X} - t_\mathcal{R}}{{t_\mathcal{X}}^\prime - t_\mathcal{R}} F^{-1} \Big( q_\mathcal{R} \Big) \nonumber\\
+			=& \ln \; D F\Big( \frac{t_\mathcal{X} - t_\mathcal{L}}{{t_\mathcal{X}}^\prime - t_\mathcal{L}} \times F^{-1}(q_\mathcal{L}) \Big) + \ln \; D F^{-1} \Big( q_\mathcal{L} \Big) + \ln \frac{t_\mathcal{X} - t_\mathcal{L}}{{t_\mathcal{X}}^\prime - t_\mathcal{L}}\nonumber \\
+			&+ \ln \; D F\Big( \frac{t_\mathcal{X} - t_\mathcal{R}}{{t_\mathcal{X}}^\prime - t_\mathcal{R}}\times F^{-1}(q_\mathcal{R}) \Big) + \ln \; D F^{-1} \Big( q_\mathcal{R} \Big) + \ln  \frac{t_\mathcal{X} - t_\mathcal{R}}{{t_\mathcal{X}}^\prime - t_\mathcal{R}}.
 \end{align}
 
-$D \hat{F}(x)$ and $D \hat{F}^{-1}(x)$ are readily computed from the linear piecewise approximation. As its final step, the operator returns $\ln |J|$.
+As its final step, the operator returns $\ln |J|$.
 
-\subsection{Small Pulley}
+\subsection*{Small Pulley}
 
-Just like the previous operator, Small Pulley operates on the root.
-Let $X$ be the root node and let $L$ and $R$ be its two children.
-However, unlike Simple Distance, this operator alters the two genetic distances $d_L = r_L (t_X - t_L) = \hat{F}^{-1} (q_L) (t_X - t_L)$ and $d_R = r_R (t_X - t_R) = \hat{F}^{-1} (q_R) (t_X - t_R)$, while conserving their sum $d_L + d_R$.
+Just like the previous operator, \texttt{SmallPulley} operates on the root. 
+Let $\mathcal{X}$ be the root node and let $\mathcal{L}$ and $\mathcal{R}$ be its two children.
+However, unlike \texttt{SimpleDistance}, this operator alters the two genetic distances $d_\mathcal{L} = r_\mathcal{L} (t_\mathcal{X} - t_\mathcal{L}) = F^{-1} (q_\mathcal{L}) (t_\mathcal{X} - t_\mathcal{L})$ and $d_\mathcal{R} = r_\mathcal{R} (t_\mathcal{X} - t_\mathcal{R}) = F^{-1} (q_\mathcal{R}) (t_\mathcal{X} - t_\mathcal{R})$, while conserving their sum $d_\mathcal{L} + d_\mathcal{R}$.
 
-\textul{\textit{Step 1}}. Propose new genetic distances for $d_L$ and $d_R$:
+\textul{\textit{Step 1}}. Propose new genetic distances for $d_\mathcal{L}$ and $d_\mathcal{R}$:
 
 \begin{align}
-	{d_L}^\prime & \leftarrow d_L + \alpha \\
-	{d_R}^\prime & \leftarrow d_R - \alpha
+	{d_\mathcal{L}}^\prime & \leftarrow d_\mathcal{L} + s\Sigma \\
+	{d_\mathcal{R}}^\prime & \leftarrow d_\mathcal{R} - s\Sigma
 \end{align}
 
-where $\alpha \sim \text{ Uniform}(-w, w)$, for some window size $w$.
-Ensure that $0 < {d_L}^\prime < d_L + d_R$ and that $r_\text{min} < {r_C}^\prime < r_\text{max}$ for $C \in \{ L, R \}$, and if either constrant is broken then reject the proposal.
-\\
+Ensure that $0 < {d_\mathcal{L}}^\prime < d_\mathcal{L} + d_\mathcal{R}$, and if the constraint is broken then reject the proposal.  \\
 
-\textul{\textit{Step 2}}. Propose new rate quantiles for the two children $L$ and $R$:
+\textul{\textit{Step 2}}. Propose new rate quantiles for the two children $\mathcal{L}$ and $\mathcal{R}$:
 
 \begin{align}
-	{q_L}^\prime &\leftarrow \hat{F}\big( \frac{{d_L}^\prime}{t_X - t_L} \big) \nonumber\\
-				 &\leftarrow \hat{F}\big( \frac{\hat{F}^{-1} (q_L) (t_X - t_L) + \alpha}{t_X - t_L} \big) \\
-	{q_R}^\prime &\leftarrow \hat{F}\big( \frac{{d_R}^\prime}{t_X - t_R} \big) \nonumber \\
-				 &\leftarrow \hat{F}\big( \frac{\hat{F}^{-1} (q_R) (t_X - t_R) - \alpha}{t_X - t_R} \big).
+	{q_\mathcal{L}}^\prime &\leftarrow F\big( \frac{{d_\mathcal{L}}^\prime}{t_\mathcal{X} - t_\mathcal{L}} \big) \nonumber\\
+				 &\leftarrow F\big( \frac{F^{-1} (q_\mathcal{L}) (t_\mathcal{X} - t_\mathcal{L}) + \Sigma}{t_\mathcal{X} - t_\mathcal{L}} \big) \\
+	{q_\mathcal{R}}^\prime &\leftarrow F\big( \frac{{d_\mathcal{R}}^\prime}{t_\mathcal{X} - t_\mathcal{R}} \big) \nonumber \\
+				 &\leftarrow F\big( \frac{F^{-1} (q_\mathcal{R}) (t_\mathcal{X} - t_\mathcal{R}) - \Sigma}{t_\mathcal{X} - t_\mathcal{R}} \big).
 \end{align}
 
-\textul{\textit{Step 3}}. Return the natural logarithm of the Green ratio by calculating the determinant of the Jacobian matrix $J$.
+\textul{\textit{Step 3}}. Return the determinant of the Jacobian matrix:
 
 \begin{align}
-	J &= \begin{bmatrix} \frac{\partial {q_L}^\prime}{\partial q_L} & \frac{\partial {q_L}^\prime}{\partial q_R} \\
-						 \frac{\partial {q_R}^\prime}{\partial q_L} & \frac{\partial {q_R}^\prime}{\partial q_R} \end{bmatrix} \nonumber \\
-	 &= \begin{bmatrix} \frac{\partial {q_L}^\prime}{\partial q_L} & 0 \\
-						 0 & \frac{\partial {q_R}^\prime}{\partial q_R} \end{bmatrix}
+	J &= \begin{bmatrix} \frac{\partial {q_\mathcal{L}}^\prime}{\partial q_\mathcal{L}} & \frac{\partial {q_\mathcal{L}}^\prime}{\partial q_\mathcal{R}} \\
+						 \frac{\partial {q_\mathcal{R}}^\prime}{\partial q_\mathcal{L}} & \frac{\partial {q_\mathcal{R}}^\prime}{\partial q_\mathcal{R}} \end{bmatrix} \nonumber \\
+	 &= \begin{bmatrix} \frac{\partial {q_\mathcal{L}}^\prime}{\partial q_\mathcal{L}} & 0 \\
+						 0 & \frac{\partial {q_\mathcal{R}}^\prime}{\partial q_\mathcal{R}} \end{bmatrix}
 \end{align}
@@
 \begin{align}
-	\ln |J| =&  \ln \{ \frac{\partial {q_L}^\prime}{\partial q_L} \times \frac{\partial {q_R}^\prime}{\partial q_R} \} \nonumber \\
-			=& \ln  \frac{\partial {q_L}^\prime}{\partial q_L} + \ln \frac{\partial {q_R}^\prime}{\partial q_R}\nonumber \\
-			=& \ln \; D \hat{F}\big( \frac{\hat{F}^{-1} (q_L) (t_X - t_L) + \alpha}{t_X - t_L} \big) + \ln \frac{\partial {q_L}^\prime}{\partial q_L}  \frac{\hat{F}^{-1} (q_L) (t_X - t_L) + \alpha}{t_X - t_L} \nonumber\\
-			&+ \ln \; D \hat{F}\big( \frac{\hat{F}^{-1} (q_R) (t_X - t_R) - \alpha}{t_X - t_R} \big) + \ln \frac{\partial {q_R}^\prime}{\partial q_R}  \frac{\hat{F}^{-1} (q_R) (t_X - t_R) - \alpha}{t_X - t_R} \nonumber\\
-			=& \ln \; D \hat{F}\big( \frac{\hat{F}^{-1} (q_L) (t_X - t_L) + \alpha}{t_X - t_L} \big) + \ln \; D \hat{F}^{-1} (q_L) \nonumber \\
-			&+ \ln \; D \hat{F}\big( \frac{\hat{F}^{-1} (q_R) (t_X - t_R) - \alpha}{t_X - t_R} \big) + \ln \; D\hat{F}^{-1} (q_R) .
+	\ln |J| =&  \ln \{ \frac{\partial {q_\mathcal{L}}^\prime}{\partial q_\mathcal{L}} \times \frac{\partial {q_\mathcal{R}}^\prime}{\partial q_\mathcal{R}} \} \nonumber \\
+			=& \ln  \frac{\partial {q_\mathcal{L}}^\prime}{\partial q_\mathcal{L}} + \ln \frac{\partial {q_\mathcal{R}}^\prime}{\partial q_\mathcal{R}}\nonumber \\
+			=& \ln \; D F\big( \frac{F^{-1} (q_\mathcal{L}) (t_\mathcal{X} - t_\mathcal{L}) + \Sigma}{t_\mathcal{X} - t_\mathcal{L}} \big) + \ln \frac{\partial {q_\mathcal{L}}^\prime}{\partial q_\mathcal{L}}  \frac{F^{-1} (q_\mathcal{L}) (t_\mathcal{X} - t_\mathcal{L}) + \Sigma}{t_\mathcal{X} - t_\mathcal{L}} \nonumber\\
+			&+ \ln \; D F\big( \frac{F^{-1} (q_\mathcal{R}) (t_\mathcal{X} - t_\mathcal{R}) - \Sigma}{t_\mathcal{X} - t_\mathcal{R}} \big) + \ln \frac{\partial {q_\mathcal{R}}^\prime}{\partial q_\mathcal{R}}  \frac{F^{-1} (q_\mathcal{R}) (t_\mathcal{X} - t_\mathcal{R}) - \Sigma}{t_\mathcal{X} - t_\mathcal{R}} \nonumber\\
+			=& \ln \; D F\big( \frac{F^{-1} (q_\mathcal{L}) (t_\mathcal{X} - t_\mathcal{L}) + \Sigma}{t_\mathcal{X} - t_\mathcal{L}} \big) + \ln \; D F^{-1} (q_\mathcal{L}) \nonumber \\
+			&+ \ln \; D F\big( \frac{F^{-1} (q_\mathcal{R}) (t_\mathcal{X} - t_\mathcal{R}) - \Sigma}{t_\mathcal{X} - t_\mathcal{R}} \big) + \ln \; DF^{-1} (q_\mathcal{R}) .
 \end{align}

### 2020-07-31 manuscript.tex
tree figs

@@
 
-The molecular clock hypothesis states that the evolutionary rates of biological sequences, such as nucleotides and amino acids, are approximately constant through time \cite{zuckerkandl1962molecular}.
-This assumption forms the basis of phylogenetics, under which the evolutionary trees and divergence dates of life forms are inferred from biological sequences \cite{douzery2003local, drummond2006relaxed}.
+The molecular clock hypothesis states that the evolutionary rates of biological sequences are approximately constant through time \cite{zuckerkandl1962molecular}.
+This assumption forms the basis of phylogenetics, under which the evolutionary trees and divergence dates of life forms are inferred from biological sequences, such as nucleic and amino acids \cite{douzery2003local, drummond2006relaxed}.
 In Bayesian phylogenetics, these trees and their associated parameters are estimated as probabilitiy distributions \cite{kuhner1995estimating, larget1999markov, mau1999bayesian}. 
@@
 
-In this article we compare the performance of uniform and Bactrian proposal kernels with respect to estimating clock model parameters $\vec{\mathcal{R}}^{\,}$ and $\sigma$.
-Two Bactrian distributions are compared ($m=0.95$ and $m=0.98$).
+In this article we compare the performance of uniform and Bactrian(0.95) proposal kernels with respect to estimating clock model parameters $\vec{\mathcal{R}}^{\,}$ and $\sigma$. 
 The clock model operators which these proposal kernels apply to are described in \textbf{Table \ref{table:bactriankernels}}.
@@
 
-In this article we have introduced four new clock model operators. 
-These operators are summarised in \textbf{Table \ref{table:newOperators}} and are applied in conjunction with the pre-existing clock model operators presented in \textbf{Table \ref{table:kernels}}.
+\subsection*{Assessment criteria and datasets}
+
+% Cite HKY somewhere hasegawa1985dating
+
+To avoid a cross-product explosion, the five targets for clock model improvement are evaluated sequentially in the following order: \textbf{\nameref{sect:adaptiveSampling}} \textbf{\nameref{sect:rateparams}}, \textbf{\nameref{sect:randomwalks}}, \textbf{\nameref{sect:NER}}, and \textbf{\nameref{AVMVN_sect}}.
+The four operators introduced in these sections are summarised in \textbf{Table \ref{table:newOperators}}.
+The setting which is considered to be the best in each step is then incorporated into the following step. This protocol and its outcomes are summarised in \textbf{Fig. \ref{fig:tournament}}.
 
@@
 \end{tabular}
-\caption{Summary of clock model operators introduced throughout this article.}
+\caption{Summary of clock model operators introduced throughout this article. Pre-existing clock model operators are summarised in \textbf{Table \ref{table:kernels}}}
 \label{table:newOperators}
 \end{table}
-
-\subsection*{Assessment criteria and datasets}
-
-% Cite HKY somewhere hasegawa1985dating
-
-To avoid a cross-product explosion, the five targets for clock model improvement are evaluated sequentially in the following order: \textbf{\nameref{sect:adaptiveSampling}} \textbf{\nameref{sect:rateparams}}, \textbf{\nameref{sect:randomwalks}}, \textbf{\nameref{sect:NER}}, and \textbf{\nameref{AVMVN_sect}}.
-
- The setting which is considered to be the best in each step is then incorporated into the following step. This protocol and its outcomes are summarised in \textbf{Fig. \ref{fig:tournament}}.
 
@@
 
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{Figures/cognato.pdf}
+\includegraphics[width=\textwidth]{Figures/broughton.pdf}
+\caption{\textbf{Maximum clade credibility trees.} Trees from the bark beetle data by Cognato et al.
+2001 \cite{Cognato_2001} (top) and the bony fish data by Broughton et al.
+2013 \cite{Broughton_2013} (bottom) are presented above.
+Branches are coloured by substitution rate (units: substitutions per site per unit of time) and the y-axis shows arbitrary units of time.
+Internal nodes are labelled with posterior clade support.
+Figures generated by UglyTrees \cite{uglytrees}.
+}
+\label{fig:parameterisationResults}
+\end{figure}
+
 \section*{Conclusion}

### 2020-07-31 manuscript.tex
tidy ups

@@
 \includegraphics[width=\textwidth]{Figures/tournament.pdf}
-\caption{\textbf{Protocol for optimising methodology settings.} The three areas (detailed in \textbf{\nameref{sect:models}}) are optimised sequentially, where the best setting from each step is used when optimising the following step.}
+\caption{\textbf{Protocol for optimising clock model methodologies.} Each area (detailed in \textbf{\nameref{sect:models}}) is optimised sequentially, and the best setting from each step is used when optimising the following step.}
 \label{fig:tournament}

### 2020-08-03 manuscript.tex
benchmarking xml sessions

@@
 However, molecular substitution rates are known to vary over time, over population sizes, over evolutionary pressures, and over nucleic acid replicative machineries \cite{gillespie1994causes, woolfit2009effective, loh2010optimization}.
-Moreover, any given dataset may be clock-like (where the substitution rate has a small variance across lineages) or non clock-like (a large variance). 
+Moreover, any given dataset may be clock-like (where the substitution rates have a small variance across lineages) or non clock-like (a large variance). 
 In the latter case, a strict clock is probably not suitable.
@@
 
-8  &  80  &  1 &  10.0  &  4.2  &  \textit{Simulated data}  \\
+8  &  80  &  1 &  10.0  &  0.9  &  \textit{Simulated data}  \\
 
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{/home/jdou557/Documents/Marsden2019/Months/July2020/fromVM/benchmarkingVM/ESS_round1.pdf}
+\includegraphics[width=\textwidth]{benchmarking/benchmarkingVM/ESS_round1.pdf}
 \caption{\textbf{Rate parameterisation performance evaluation.} Comparison of ESS/hr (averaged across five independent MC3 analyses) with respect to relevant terms -- $P$: posterior density; $L$: likelihood, $p$: prior density, $r$: clock rate ESS averaged across all leaves, $\hat{r}$: branch rate mean, $v$: branch rate variance, $\sigma$: clock standard deviation, $\kappa$: HKY model transition-transversion ratio, $\lambda$: Yule model birth rate.

### 2020-08-03 benchmarking/clear.sh

@@ -1,0 +1,53 @@
+#!/bin/sh
+
+
+
+
+
+#settings=("real" "cat" "quant" "AVMN" "bactrian98" "bactrian95" "NER" "real_06" "quant_06")
+datasets=("Sauquet_2011" "Moyle_2016" "simulated" "Dornburg_2012" "Broughton_2013" "Ran_2018_dna" "Cannon_2016_dna" "Rightmyer_2013" "Kawahara_2013" "Cognato_2001")
+
+
+
+
+
+ echo "Removing log and tree files"
+              
+# Real data   
+for batch in {1..5}
+do
+
+	echo "Batch${batch}"
+	cd "Batch${batch}"
+
+	for d in ${datasets[@]} ; do
+	    echo "Dataset $d"
+	    cd $d
+
+	    for e in */ ; do
+	        echo "Partition $e"
+	        cd $e
+
+
+
+	         rm *.log
+	         rm *.trees
+
+
+
+	        cd ../
+	    done
+	    
+
+    	#sleep 1
+
+   	 	cd ../
+	done
+
+	cd ../
+
+done
+
+
+
+

### 2020-08-03 benchmarking/plotBenchmark.R

@@ -1,0 +1,914 @@
+
+library(tikzDevice)
+library(HDInterval)
+library(lubridate)
+
+
+
+
+#settings = c("cat",  "real_06", "quant_06", "real", "quant", "bactrian95", "bactrian98", "NER", "AVMN")
+settings = c("real", "real_adaptive", "real_06")
+
+benchmark = data.frame(batch = numeric(0), param = character(0), dataset = character(0), partition = numeric(0), setting = character(0), nstates = numeric(0), finalESS = numeric(0), finalMCD = numeric(0), done = logical(0),  error = logical(0))
+
+
+latex.table = read.table("/home/jdou557/Documents/Marsden2019/Months/January2020/fromVM/latex.table", sep = "&")
+colnames(latex.table) = c("ID", "N", "P", "L", "Leff", "ref")
+latex.table$ref = gsub(" ", "", gsub("[0-9].+", "", latex.table$ref))
+
+
+
+latex.table$completion = ""
+
+progress.df = read.csv("progress.csv", header = T)
+progress.df$batch = ifelse(progress.df$batch == 4, 5, ifelse(progress.df$batch == 5, 4, progress.df$batch))
+
+
+parameters = c("posterior", "likelihood", "prior", "treeLength", "height", "birthRate", "kappa",  "freqParameter", "ucldStdev", "clockRate", "TipRates", "RateStatLogger.mean", "RateStatLogger.variance")
+
+
+parameters.latex = lapply(parameters, function(x) x)
+names(parameters.latex) = parameters
+parameters.latex["posterior"] = "Posterior $P(\\theta|D)$"
+parameters.latex["likelihood"] = "Likelihood $P(D|\\theta)$"
+parameters.latex["prior"] = "Prior $P(\\theta)$"
+parameters.latex["birthRate"] = "Yule birth rate $\\lambda$"
+parameters.latex["gammaShape"] = "$\\Gamma$ shape"
+parameters.latex["kappa"] = "$\\kappa$"
+parameters.latex["freqParameter"] = "Nucleotide frequency $f$"
+parameters.latex["ucldStdev"] = "Clock SD $\\sigma$"
+parameters.latex["TipRates"] = "Mean tip rate $r$"
+parameters.latex["treeLength"] = "Tree length $l$"
+parameters.latex["height"] = "Tree height $h$"
+
+
+getDateTime = function(str){
+
[…]

### 2020-08-03 benchmarking/render.R

@@ -1,0 +1,558 @@
+
+library(tikzDevice)
+library(HDInterval)
+library(lubridate)
+library(colorspace)
+
+
+PER_CHAIN = TRUE
+
+#settings = c("cat", "real", "quant", "bactrian95", "bactrian98")
+settings = c("cat",  "real_06", "quant_06", "real", "quant", "bactrian95", "bactrian98", "NER", "AVMN")
+settings = c("cat",  "real_06", "real", "real_adaptive", "quant_06_cached", "quant_cached_adaptive", "quant_cached")
+
+benchmark = data.frame(batch = numeric(0), param = character(0), dataset = character(0), partition = numeric(0), setting = character(0), nstates = numeric(0), finalESS = numeric(0), finalMCD = numeric(0), done = logical(0),  error = logical(0))
+
+
+
+
+settings.names = lapply(settings, function(x) x)
+settings.names["cat"] = "\\textit{cat}"
+
+settings.names["real"] = "cons (\\textit{real})"
+settings.names["real_06"] = "nocons (\\textit{real})"
+settings.names["real_adaptive"] = "adapt (\\textit{real})"
+
+settings.names["quant_cached"] = "cons (\\textit{quant})"
+settings.names["quant_06_cached"] = "nocons (\\textit{quant})"
+settings.names["quant_cached_adaptive"] = "adapt (\\textit{quant})"
+settings.names["bactrian95"] = "Bactrian (\\textit{real})"
+settings.names["NER"] = "NER (\\textit{real})"
+
+
+latex.table = read.table("../../Benchmarking/latex.table", sep = "&")
+colnames(latex.table) = c("ID", "N", "P", "L", "Leff", "ref")
+latex.table$ref = gsub(" ", "", gsub("[0-9].+", "", latex.table$ref))
+
+
+
+latex.table$completion = ""
+
+progress.df = read.csv("progress.csv", header = T)
+progress.df$batch = ifelse(progress.df$batch == 4, 5, ifelse(progress.df$batch == 5, 4, progress.df$batch))
+
+
+#parameters = c("posterior", "likelihood", "prior", "height", "birthRate", "kappa",  "ucldStdev", "clockRate", "TipRates", "RateStatLogger.mean", "RateStatLogger.variance")
[…]

### 2020-08-07 benchmarking/benchmarkingVM/ESS_round1_quant.tex
update

% Created by tikzDevice version 0.12.3 on 2020-08-07 14:28:34
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (578.16,578.16);
\begin{scope}
\path[clip] (  0.00,289.08) rectangle (289.08,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,548.96) {\bfseries Comparison of cons (\textit{quant}) and nocons (\textit{quant})};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,301.03) {ESS/chain [nocons (\textit{quant})]};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,433.62) {ESS/chain [cons (\textit{quant})]};
\end{scope}
\begin{scope}
\path[clip] ( 49.80,338.88) rectangle (239.28,528.36);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{gray}{0.91}

\path[draw=drawColor,line width= 0.1pt,line join=round,line cap=round,fill=fillColor] (  0.00,370.43) --
	(207.73,578.16) --
	(284.32,578.16) --
	(284.32,492.05) --
	(  0.00,207.73) --
	cycle;
\definecolor{fillColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] (  0.00,343.31) --
	(234.85,578.16) --
	(284.32,578.16) --
	(284.32,519.17) --
	(  0.00,234.85) --
	cycle;
\definecolor{fillColor}{RGB}{169,169,169}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (  0.00,316.20) --
	(261.96,578.16) --
	(284.32,578.16) --
	(284.32,546.28) --
	(  0.00,261.96) --
	cycle;

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (138.68,342.31) {$\frac{1}{64} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,431.66) {$64\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (111.56,342.31) {$\frac{1}{16} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,404.54) {$16\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 82.79,342.31) {$\frac{1}{4} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92,377.43) {$4\times$};

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,528.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (154.78,458.84) --
	(163.04,458.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.35,457.22) --
	(159.35,460.34);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (159.35,455.61) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (224.94,510.20) --
	(228.38,510.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.73,506.80) --
	(226.73,513.10);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (226.73,506.17) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.40,510.73) --
	(197.94,510.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.67,509.26) --
	(197.67,512.10);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.67,506.70) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (150.10,455.56) --
	(157.51,455.56);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (154.15,454.17) --
	(154.15,456.86);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (154.15,451.53) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.84,449.55) --
	(170.33,449.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (166.15,447.40) --
	(166.15,451.49);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (166.15,446.64) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.37,520.33) --
	(233.01,520.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.69,519.95) --
	(232.69,520.70);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (232.69,517.43) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (224.96,506.23) --
	(230.80,506.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.10,504.49) --
	(228.10,507.82);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (228.10,503.00) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.75,524.40) --
	(212.92,524.40);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.95,522.92) --
	(210.95,525.77);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.95,520.36) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.29,515.90) --
	(230.63,515.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.46,515.51) --
	(230.46,516.29);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (230.46,511.87) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.29,493.62) --
	(212.37,493.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.89,492.26) --
	(210.89,494.89);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.89,489.59) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (207.98,501.27) --
	(226.00,501.27);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (219.00,498.36) --
	(219.00,503.79);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (219.00,498.36) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (132.74,453.24) --
	(141.29,453.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (137.48,446.20) --
	(137.48,458.41);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (137.48,450.02) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (219.83,509.99) --
	(224.29,509.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.19,509.30) --
	(222.19,510.65);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (222.19,505.95) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.03,507.85) --
	(141.88,507.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.05,507.28) --
	(140.05,508.40);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (140.05,503.81) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (133.17,452.60) --
	(141.38,452.60);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (137.70,447.13) --
	(137.70,456.87);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (137.70,448.56) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (127.75,425.78) --
	(152.95,425.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (144.15,422.66) --
	(144.15,428.46);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (144.15,422.87) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.00,524.46) --
	(235.41,524.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.21,524.31) --
	(235.21,524.60);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (235.21,521.55) {$\mu$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.43,494.98) --
	(214.98,494.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (213.29,491.43) --
	(213.29,497.98);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (213.29,491.75) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.67,519.49) --
	(218.04,519.49);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.40,515.97) --
	(210.40,522.47);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.40,515.46) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.24,515.43) --
	(230.27,515.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.76,514.84) --
	(229.76,516.00);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (229.76,511.39) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.64,476.76) --
	(195.83,476.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.56,472.41) --
	(192.56,480.32);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.56,472.73) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.95,497.88) --
	(217.97,497.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.62,493.68) --
	(215.62,501.33);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (215.62,494.97) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (233.90,525.40) --
	(237.76,525.40);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.92,523.47) --
	(235.92,527.15);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (235.92,522.49) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.84,487.70) --
	(186.74,487.70);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.01,486.39) --
	(184.01,488.93);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.01,484.48) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.22,512.65) --
	(230.84,512.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.04,510.97) --
	(230.04,514.20);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (230.04,508.62) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.88,516.90) --
	(222.04,516.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.47,516.68) --
	(221.47,517.11);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (221.47,512.86) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.74,484.64) --
	(178.27,484.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.58,483.10) --
	(176.58,486.08);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.58,480.61) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.90,483.44) --
	(187.90,483.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.71,482.22) --
	(184.71,484.58);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.71,480.53) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.75,518.95) --
	(230.85,518.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.31,518.70) --
	(230.31,519.19);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (230.31,516.04) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (166.13,467.76) --
	(176.11,467.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.75,465.03) --
	(171.75,470.15);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.75,464.53) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.94,516.52) --
	(233.57,516.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.77,513.95) --
	(232.77,518.79);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (232.77,512.49) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.38,515.49) --
	(211.58,515.49);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.48,515.32) --
	(211.48,515.67);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.48,511.46) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.31,486.46) --
	(183.35,486.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.56,484.65) --
	(177.56,488.12);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.56,482.43) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.76,473.27) --
	(183.08,473.27);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (178.59,470.39) --
	(178.59,475.77);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (178.59,470.36) {$\sigma$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,338.88) -- (229.95,338.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,338.88) -- ( 49.80,333.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 94.84,338.88) -- ( 94.84,333.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (139.88,338.88) -- (139.88,333.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.92,338.88) -- (184.92,333.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.95,338.88) -- (229.95,333.90);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 49.80,320.95) {1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 94.84,320.95) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (139.88,320.95) {100};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (184.92,320.95) {1000};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (229.95,320.95) {10000};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,338.88) -- ( 49.80,519.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,338.88) -- ( 44.82,338.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,383.92) -- ( 44.82,383.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,428.96) -- ( 44.82,428.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,474.00) -- ( 44.82,474.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,519.03) -- ( 44.82,519.03);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,336.02) {1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,381.06) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,426.10) {100};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,471.14) {1000};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,516.18) {10000};
\end{scope}
\begin{scope}
\path[clip] ( 49.80,338.88) rectangle (239.28,528.36);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{255,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,431.01) rectangle (189.67,426.03);
\definecolor{fillColor}{RGB}{0,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,421.05) rectangle (189.67,416.07);
\definecolor{fillColor}{RGB}{0,255,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,411.09) rectangle (189.67,406.11);
\definecolor{fillColor}{RGB}{255,255,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,401.13) rectangle (189.67,396.15);
\definecolor{fillColor}{RGB}{255,165,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,391.17) rectangle (189.67,386.19);
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,381.21) rectangle (189.67,376.23);
\definecolor{fillColor}{RGB}{160,32,240}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,371.25) rectangle (189.67,366.27);
\definecolor{fillColor}{RGB}{0,100,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,361.29) rectangle (189.67,356.31);
\definecolor{fillColor}{RGB}{0,255,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,351.33) rectangle (189.67,346.35);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,425.66) {Broughton};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,415.70) {Cognato};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,405.74) {Dornburg};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,395.78) {Kawahara};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,385.82) {Moyle};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,375.86) {Ran};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,365.90) {Rightmyer};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,355.94) {Sauquet};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,345.98) {simulated};
\end{scope}
\begin{scope}
\path[clip] (289.08,289.08) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,548.96) {\bfseries Comparison of adapt (\textit{quant}) and nocons (\textit{quant})};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,301.03) {ESS/chain [nocons (\textit{quant})]};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (307.01,433.62) {ESS/chain [adapt (\textit{quant})]};
\end{scope}
\begin{scope}
\path[clip] (338.88,338.88) rectangle (528.36,528.36);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{gray}{0.91}

\path[draw=drawColor,line width= 0.1pt,line join=round,line cap=round,fill=fillColor] (157.53,239.42) --
	(496.27,578.16) --
	(573.70,578.16) --
	(573.70,491.81) --
	(157.53, 75.64) --
	cycle;
\definecolor{fillColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] (157.53,212.12) --
	(523.57,578.16) --
	(573.70,578.16) --
	(573.70,519.11) --
	(157.53,102.93) --
	cycle;
\definecolor{fillColor}{RGB}{169,169,169}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (157.53,184.82) --
	(550.86,578.16) --
	(573.70,578.16) --
	(573.70,546.40) --
	(157.53,130.23) --
	cycle;

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (428.30,342.31) {$\frac{1}{64} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,432.20) {$64\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (401.01,342.31) {$\frac{1}{16} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,404.91) {$16\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (372.05,342.31) {$\frac{1}{4} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.00,377.61) {$4\times$};

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (338.88,338.88) -- (528.36,528.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (444.56,460.15) --
	(452.88,460.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (449.16,451.26) --
	(449.16,466.25);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (449.16,456.92) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (515.19,511.43) --
	(518.65,511.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (516.99,509.17) --
	(516.99,513.46);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (516.99,507.40) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (487.47,511.23) --
	(488.01,511.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (487.74,509.90) --
	(487.74,512.47);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (487.74,507.20) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (439.85,456.76) --
	(447.30,456.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.93,442.37) --
	(443.93,464.99);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (443.93,452.73) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (450.66,445.02) --
	(460.21,445.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (456.01,433.72) --
	(456.01,452.15);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (456.01,442.11) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (522.67,521.39) --
	(523.32,521.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (522.99,521.26) --
	(522.99,521.51);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (522.99,518.48) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (515.20,518.74) --
	(521.09,518.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (518.37,517.15) --
	(518.37,520.21);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (518.37,515.51) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (498.89,524.94) --
	(503.09,524.94);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (501.10,524.79) --
	(501.10,525.10);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (501.10,520.91) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (520.58,523.16) --
	(520.92,523.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (520.75,522.01) --
	(520.75,524.25);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (520.75,519.13) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.44,502.28) --
	(502.53,502.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (501.05,497.87) --
	(501.05,505.88);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (501.05,498.25) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (498.12,509.95) --
	(516.25,509.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (509.20,506.14) --
	(509.20,513.14);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (509.20,507.05) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (422.38,436.05) --
	(430.98,436.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.15,420.84) --
	(427.15,444.52);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (427.15,432.82) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (510.04,510.60) --
	(514.54,510.60);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (512.42,509.80) --
	(512.42,511.38);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (512.42,506.57) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.70,507.74) --
	(431.58,507.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (429.73,503.94) --
	(429.73,510.93);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (429.73,503.71) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (422.81,435.78) --
	(431.07,435.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.37,416.30) --
	(427.37,445.38);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (427.37,431.75) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.35,405.59) --
	(442.71,405.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.86,396.96) --
	(433.86,411.56);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (433.86,402.68) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (525.32,525.14) --
	(525.72,525.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (525.52,524.81) --
	(525.52,525.46);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (525.52,522.23) {$\mu$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (501.59,504.01) --
	(505.16,504.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (503.46,501.14) --
	(503.46,506.51);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (503.46,500.78) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (487.73,516.99) --
	(508.25,516.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (500.55,514.10) --
	(500.55,519.51);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (500.55,512.95) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (519.52,521.82) --
	(520.55,521.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (520.04,521.15) --
	(520.04,522.46);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (520.04,517.78) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (478.65,484.41) --
	(485.88,484.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.59,480.26) --
	(482.59,487.83);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (482.59,480.37) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (503.11,505.33) --
	(508.17,505.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (505.81,502.96) --
	(505.81,507.44);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (505.81,502.42) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (524.20,526.64) --
	(528.09,526.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (526.24,525.57) --
	(526.24,527.65);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (526.24,523.73) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (470.79,487.52) --
	(476.73,487.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (473.99,482.71) --
	(473.99,491.39);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (473.99,484.30) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (519.49,514.36) --
	(521.12,514.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (520.32,512.66) --
	(520.32,515.93);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (520.32,510.33) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (511.10,518.21) --
	(512.27,518.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (511.70,516.35) --
	(511.70,519.91);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (511.70,514.18) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.66,484.99) --
	(468.20,484.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (466.51,478.51) --
	(466.51,489.86);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (466.51,480.96) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (470.85,484.00) --
	(477.90,484.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.69,481.54) --
	(474.69,486.20);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.69,481.10) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (520.03,520.25) --
	(521.13,520.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (520.59,519.78) --
	(520.59,520.70);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (520.59,517.34) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (455.99,472.35) --
	(466.03,472.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.64,469.91) --
	(461.64,474.53);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (461.64,469.13) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (522.24,517.24) --
	(523.87,517.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (523.07,515.10) --
	(523.07,519.18);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (523.07,513.21) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (501.54,517.24) --
	(501.74,517.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (501.64,517.01) --
	(501.64,517.47);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (501.64,513.21) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (459.19,486.19) --
	(473.32,486.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (467.49,483.53) --
	(467.49,488.53);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (467.49,482.16) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.66,476.31) --
	(473.05,476.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (468.53,474.09) --
	(468.53,478.31);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.53,473.41) {$\sigma$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,338.88) -- (520.23,338.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,338.88) -- (338.88,333.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (384.22,338.88) -- (384.22,333.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (429.56,338.88) -- (429.56,333.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.90,338.88) -- (474.90,333.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (520.23,338.88) -- (520.23,333.90);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (338.88,320.95) {1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (384.22,320.95) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (429.56,320.95) {100};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (474.90,320.95) {1000};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (520.23,320.95) {10000};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,338.88) -- (338.88,520.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,338.88) -- (333.90,338.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,384.22) -- (333.90,384.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,429.56) -- (333.90,429.56);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,474.90) -- (333.90,474.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,520.23) -- (333.90,520.23);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,336.02) {1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,381.36) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,426.70) {100};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,472.04) {1000};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,517.38) {10000};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,259.88) {\bfseries Comparison of adapt (\textit{quant}) and cons (\textit{quant})};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54, 11.95) {ESS/chain [cons (\textit{quant})]};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,144.54) {ESS/chain [adapt (\textit{quant})]};
\end{scope}
\begin{scope}
\path[clip] ( 49.80, 49.80) rectangle (239.28,239.28);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{gray}{0.91}

\path[draw=drawColor,line width= 0.1pt,line join=round,line cap=round,fill=fillColor] (  0.00, 81.35) --
	(284.32,365.67) --
	(284.32,202.97) --
	( 81.35,  0.00) --
	(  0.00,  0.00) --
	cycle;
\definecolor{fillColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] (  0.00, 54.23) --
	(284.32,338.55) --
	(284.32,230.09) --
	( 54.23,  0.00) --
	(  0.00,  0.00) --
	cycle;
\definecolor{fillColor}{RGB}{169,169,169}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (  0.00, 27.12) --
	(284.32,311.43) --
	(284.32,257.20) --
	( 27.12,  0.00) --
	(  0.00,  0.00) --
	cycle;

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (138.68, 53.23) {$\frac{1}{64} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,142.58) {$64\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (111.56, 53.23) {$\frac{1}{16} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,115.46) {$16\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 82.79, 53.23) {$\frac{1}{4} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92, 88.35) {$4\times$};

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 49.80, 49.80) -- (239.28,239.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.14,170.26) --
	(171.26,170.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.76,161.43) --
	(169.76,176.32);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.76,167.04) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.72,221.21) --
	(224.02,221.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.12,218.96) --
	(221.12,223.22);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (221.12,217.17) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.18,221.01) --
	(223.02,221.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.65,219.69) --
	(221.65,222.24);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (221.65,216.97) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (165.09,166.90) --
	(167.78,166.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (166.48,152.60) --
	(166.48,175.07);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (166.48,162.87) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.32,155.24) --
	(162.41,155.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.47,144.01) --
	(160.47,162.32);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (160.47,152.33) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.87,231.10) --
	(231.62,231.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.25,230.97) --
	(231.25,231.22);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (231.25,228.19) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.41,228.47) --
	(218.74,228.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.15,226.88) --
	(217.15,229.93);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (217.15,225.24) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (233.84,234.63) --
	(236.69,234.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.32,234.47) --
	(235.32,234.79);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (235.32,230.60) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.43,232.86) --
	(227.21,232.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.82,231.71) --
	(226.82,233.94);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (226.82,228.83) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.18,212.12) --
	(205.81,212.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.54,207.74) --
	(204.54,215.70);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (204.54,208.09) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.28,219.74) --
	(214.71,219.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.19,215.95) --
	(212.19,222.91);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.19,216.83) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (157.12,146.32) --
	(169.33,146.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (164.16,131.22) --
	(164.16,154.74);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (164.16,143.10) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.22,220.39) --
	(221.57,220.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.91,219.58) --
	(220.91,221.16);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.91,216.35) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.20,217.55) --
	(219.32,217.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.77,213.77) --
	(218.77,220.71);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (218.77,213.51) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.05,146.06) --
	(167.79,146.06);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.52,126.71) --
	(163.52,155.60);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (163.52,142.03) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (133.58,116.07) --
	(139.38,116.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (136.70,107.50) --
	(136.70,122.00);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (136.70,113.16) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.23,234.82) --
	(235.52,234.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.38,234.50) --
	(235.38,235.14);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (235.38,231.92) {$\mu$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (202.35,213.84) --
	(208.90,213.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (205.90,210.98) --
	(205.90,216.32);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.90,210.61) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.89,226.73) --
	(233.39,226.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.41,223.86) --
	(230.41,229.23);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (230.41,222.70) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.76,231.53) --
	(226.92,231.53);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.35,230.87) --
	(226.35,232.16);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (226.35,227.49) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (183.33,194.36) --
	(191.24,194.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.68,190.24) --
	(187.68,197.76);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.68,190.33) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.60,215.14) --
	(212.25,215.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.80,212.80) --
	(208.80,217.24);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (208.80,212.24) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.39,236.31) --
	(238.07,236.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (236.32,235.26) --
	(236.32,237.32);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (236.32,233.41) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.31,197.46) --
	(199.85,197.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.62,192.67) --
	(198.62,201.30);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.62,194.23) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.89,224.12) --
	(225.12,224.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.57,222.43) --
	(223.57,225.68);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (223.57,220.09) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.60,227.94) --
	(228.03,227.94);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.82,226.10) --
	(227.82,229.63);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (227.82,223.91) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.02,194.94) --
	(197.00,194.94);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.56,188.51) --
	(195.56,199.78);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.56,190.91) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.14,193.96) --
	(195.50,193.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.36,191.51) --
	(194.36,196.14);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.36,191.06) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.62,229.97) --
	(230.11,229.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.87,229.50) --
	(229.87,230.42);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (229.87,227.06) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.95,182.39) --
	(181.07,182.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (178.68,179.96) --
	(178.68,184.55);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (178.68,179.16) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (224.87,226.98) --
	(229.71,226.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.44,224.85) --
	(227.44,228.90);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (227.44,222.95) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.24,226.98) --
	(226.59,226.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.41,226.76) --
	(226.41,227.21);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (226.41,222.95) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.57,196.14) --
	(199.04,196.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.38,193.50) --
	(197.38,198.46);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.38,192.10) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.31,186.32) --
	(186.69,186.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.19,184.11) --
	(184.19,188.31);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.19,183.42) {$\sigma$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 49.80) -- (229.95, 49.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 49.80) -- ( 49.80, 44.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 94.84, 49.80) -- ( 94.84, 44.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (139.88, 49.80) -- (139.88, 44.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.92, 49.80) -- (184.92, 44.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.95, 49.80) -- (229.95, 44.82);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 49.80, 31.87) {1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 94.84, 31.87) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (139.88, 31.87) {100};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (184.92, 31.87) {1000};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (229.95, 31.87) {10000};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 49.80) -- ( 49.80,229.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 49.80) -- ( 44.82, 49.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 94.84) -- ( 44.82, 94.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,139.88) -- ( 44.82,139.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,184.92) -- ( 44.82,184.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,229.95) -- ( 44.82,229.95);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84, 46.94) {1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84, 91.98) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,137.02) {100};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,182.06) {1000};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,227.10) {10000};
\end{scope}
\begin{scope}
\path[clip] (289.08,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.66] at (433.62,258.45) {\bfseries Speed comparison};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.66] at (433.62, 11.95) {Setting};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.66] at (307.01,144.54) {Speed ($10^6$ states/hr)};
\end{scope}
\begin{scope}
\path[clip] (338.88, 49.80) rectangle (528.36,239.28);
\definecolor{drawColor}{RGB}{255,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.88, 78.53) -- (428.64, 77.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.60, 77.16) -- (516.36, 77.22);
\definecolor{fillColor}{RGB}{255,0,0}

\path[fill=fillColor] (345.90, 81.52) --
	(348.41, 77.16) --
	(343.38, 77.16) --
	cycle;

\path[fill=fillColor] (433.62, 77.16) circle (  1.87);

\path[fill=fillColor] (521.34, 77.23) circle (  1.87);
\definecolor{drawColor}{RGB}{255,165,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.86,117.42) -- (428.65,111.69);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.60,111.30) -- (516.36,110.92);
\definecolor{fillColor}{RGB}{255,165,0}

\path[fill=fillColor] (345.90,120.70) --
	(348.41,116.34) --
	(343.38,116.34) --
	cycle;

\path[fill=fillColor] (433.62,111.32) circle (  1.87);

\path[fill=fillColor] (521.34,110.89) circle (  1.87);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.88, 68.40) -- (428.64, 68.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.60, 68.43) -- (516.36, 68.52);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] (345.90, 68.39) circle (  1.87);

\path[fill=fillColor] (433.62, 68.42) circle (  1.87);

\path[fill=fillColor] (521.34, 71.43) --
	(523.86, 67.07) --
	(518.83, 67.07) --
	cycle;
\definecolor{drawColor}{RGB}{160,32,240}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.88, 99.16) -- (428.64, 98.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.60, 98.01) -- (516.36, 96.50);
\definecolor{fillColor}{RGB}{160,32,240}

\path[fill=fillColor] (345.90,102.12) --
	(348.41, 97.77) --
	(343.38, 97.77) --
	cycle;

\path[fill=fillColor] (433.62, 98.11) circle (  1.87);

\path[fill=fillColor] (521.34, 96.40) circle (  1.87);
\definecolor{drawColor}{RGB}{0,100,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.88,103.24) -- (428.64,101.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.60,101.14) -- (516.36,100.31);
\definecolor{fillColor}{RGB}{0,100,0}

\path[fill=fillColor] (345.90,106.27) --
	(348.41,101.92) --
	(343.38,101.92) --
	cycle;

\path[fill=fillColor] (433.62,101.20) circle (  1.87);

\path[fill=fillColor] (521.34,100.26) circle (  1.87);
\definecolor{drawColor}{RGB}{0,255,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.88,109.78) -- (428.64,111.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.60,111.46) -- (516.36,111.39);
\definecolor{fillColor}{RGB}{0,255,255}

\path[fill=fillColor] (345.90,109.68) circle (  1.87);

\path[fill=fillColor] (433.62,114.37) --
	(436.14,110.02) --
	(431.10,110.02) --
	cycle;

\path[fill=fillColor] (521.34,111.38) circle (  1.87);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (345.90, 49.80) -- (521.34, 49.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (345.90, 49.80) -- (345.90, 44.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.62, 49.80) -- (433.62, 44.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (521.34, 49.80) -- (521.34, 44.82);

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (348.76, 39.84) {nocons (\textit{quant})};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (436.48, 39.84) {cons (\textit{quant})};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (524.20, 39.84) {adapt (\textit{quant})};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 56.82) -- (338.88,216.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 56.82) -- (333.90, 56.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 96.66) -- (333.90, 96.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,136.50) -- (333.90,136.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,176.33) -- (333.90,176.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,216.17) -- (333.90,216.17);

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (326.93, 56.82) {0};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (326.93, 96.66) {10};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (326.93,136.50) {20};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (326.93,176.33) {30};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (326.93,216.17) {40};
\end{scope}
\end{tikzpicture}

\end{document}

### 2020-08-07 benchmarking/benchmarkingVM/ESS_round1_real.tex
update

% Created by tikzDevice version 0.12.3 on 2020-08-07 14:28:24
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (578.16,578.16);
\begin{scope}
\path[clip] (  0.00,289.08) rectangle (289.08,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,548.96) {\bfseries Comparison of cons (\textit{real}) and nocons (\textit{real})};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,301.03) {ESS/chain [nocons (\textit{real})]};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,433.62) {ESS/chain [cons (\textit{real})]};
\end{scope}
\begin{scope}
\path[clip] ( 49.80,338.88) rectangle (239.28,528.36);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{gray}{0.91}

\path[draw=drawColor,line width= 0.1pt,line join=round,line cap=round,fill=fillColor] (  0.00,365.38) --
	(212.78,578.16) --
	(281.53,578.16) --
	(281.53,494.30) --
	(  0.00,212.78) --
	cycle;
\definecolor{fillColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] (  0.00,339.95) --
	(238.21,578.16) --
	(281.53,578.16) --
	(281.53,519.74) --
	(  0.00,238.21) --
	cycle;
\definecolor{fillColor}{RGB}{169,169,169}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (  0.00,314.51) --
	(263.65,578.16) --
	(281.53,578.16) --
	(281.53,545.17) --
	(  0.00,263.65) --
	cycle;

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (133.64,342.31) {$\frac{1}{64} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,426.62) {$64\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (108.20,342.31) {$\frac{1}{16} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,401.18) {$16\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 81.11,342.31) {$\frac{1}{4} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92,375.75) {$4\times$};

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,528.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.14,457.67) --
	(163.00,457.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.72,454.14) --
	(158.72,460.63);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.72,454.44) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.97,498.27) --
	(218.78,498.27);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.83,495.92) --
	(212.83,500.36);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.83,494.24) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (178.45,498.59) --
	(180.15,498.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.32,497.51) --
	(179.32,499.62);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.32,494.56) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (146.49,453.46) --
	(152.86,453.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (149.95,449.76) --
	(149.95,456.55);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (149.95,449.43) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (156.64,437.17) --
	(165.01,437.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.30,434.91) --
	(161.30,439.18);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (161.30,434.26) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.32,508.76) --
	(221.15,508.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.74,507.98) --
	(220.74,509.51);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.74,505.85) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.30,494.32) --
	(194.81,494.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.60,491.54) --
	(193.60,496.74);
\definecolor{drawColor}{RGB}{0,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.60,491.10) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (205.85,498.07) --
	(214.19,498.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.49,494.17) --
	(210.49,501.29);
\definecolor{drawColor}{RGB}{0,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.49,494.04) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.48,503.25) --
	(210.75,503.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.13,501.60) --
	(210.13,504.76);
\definecolor{drawColor}{RGB}{0,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.13,499.21) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.18,482.71) --
	(198.08,482.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.79,479.66) --
	(195.79,485.33);
\definecolor{drawColor}{RGB}{0,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.79,478.68) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.48,485.22) --
	(198.60,485.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.57,481.89) --
	(197.57,488.04);
\definecolor{drawColor}{RGB}{0,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.57,482.32) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.10,512.25) --
	(223.18,512.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.65,510.74) --
	(222.65,513.65);
\definecolor{drawColor}{RGB}{0,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (222.65,509.35) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.17,469.31) --
	(197.17,474.08);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.17,468.62) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (214.45,504.24) --
	(220.93,504.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.97,503.56) --
	(217.97,504.90);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (217.97,500.21) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.42,505.36) --
	(222.61,505.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (216.85,505.09) --
	(216.85,505.62);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (216.85,501.33) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.48,442.96) --
	(169.48,453.47);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.48,444.93) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.56,462.82) --
	(196.56,467.56);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.56,462.44) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.70,512.26) --
	(223.15,512.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.93,512.04) --
	(222.93,512.48);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (222.93,509.36) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.68,478.88) --
	(192.68,485.07);
\definecolor{drawColor}{RGB}{255,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.68,479.01) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.72,496.18) --
	(218.04,496.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (205.74,494.03) --
	(205.74,498.10);
\definecolor{drawColor}{RGB}{255,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.74,492.14) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.70,503.25) --
	(229.53,503.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (224.55,502.95) --
	(224.55,503.55);
\definecolor{drawColor}{RGB}{255,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (224.55,499.22) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.85,475.04) --
	(211.32,475.04);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.84,472.97) --
	(200.84,476.90);
\definecolor{drawColor}{RGB}{255,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (200.84,471.00) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.62,480.49) --
	(206.62,483.96);
\definecolor{drawColor}{RGB}{255,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (206.62,479.40) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.33,511.89) --
	(223.37,511.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.86,511.27) --
	(222.86,512.49);
\definecolor{drawColor}{RGB}{255,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (222.86,508.99) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.91,482.52) --
	(221.91,491.18);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (221.91,484.13) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (202.65,482.61) --
	(202.65,488.22);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.65,481.59) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (199.21,500.97) --
	(230.61,500.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.94,500.31) --
	(220.94,501.61);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.94,496.94) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.32,486.64) --
	(193.67,486.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.26,482.99) --
	(185.26,489.69);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.26,482.61) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (207.68,479.70) --
	(207.68,488.91);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.68,481.98) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (119.95,439.54) --
	(137.90,439.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (131.04,432.27) --
	(131.04,444.73);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (131.04,436.31) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.56,498.07) --
	(210.93,498.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.02,496.36) --
	(208.02,499.62);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (208.02,494.03) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (125.81,497.45) --
	(135.01,497.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (130.98,494.97) --
	(130.98,499.64);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (130.98,493.42) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (119.66,452.88) --
	(130.48,452.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (125.86,445.61) --
	(125.86,458.08);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (125.86,448.85) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (119.40,419.55) --
	(144.64,419.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (136.05,411.70) --
	(136.05,425.03);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (136.05,416.65) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.17,512.87) --
	(223.63,512.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.40,512.58) --
	(223.40,513.16);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (223.40,509.97) {$\mu$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (165.32,492.59) --
	(187.22,492.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.36,490.80) --
	(179.36,494.22);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.36,489.37) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.77,494.95) --
	(207.58,494.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (199.98,487.86) --
	(199.98,500.06);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.98,490.92) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.10,499.92) --
	(216.56,499.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.11,499.81) --
	(210.11,500.04);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.11,495.89) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (156.75,463.31) --
	(179.56,463.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.50,460.78) --
	(171.50,465.53);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.50,459.27) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (165.37,483.34) --
	(188.77,483.34);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.57,482.71) --
	(180.57,483.94);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.57,480.43) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (216.41,512.30) --
	(225.65,512.30);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.61,509.43) --
	(221.61,514.78);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (221.61,509.40) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (164.18,476.03) --
	(174.33,476.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.95,474.65) --
	(169.95,477.32);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.95,472.81) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (213.06,503.10) --
	(218.28,503.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.85,502.50) --
	(215.85,503.67);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (215.85,499.06) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (202.88,502.51) --
	(207.31,502.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (205.23,502.21) --
	(205.23,502.80);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.23,498.47) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.71,468.73) --
	(170.74,468.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (166.40,467.18) --
	(166.40,470.16);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (166.40,464.70) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.55,467.47) --
	(172.33,467.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (167.72,466.51) --
	(167.72,468.39);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (167.72,464.57) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.84,507.62) --
	(218.89,507.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.38,507.22) --
	(218.38,508.01);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (218.38,504.71) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (137.20,493.15) --
	(182.80,493.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.55,492.20) --
	(171.55,494.06);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.55,489.93) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.57,502.64) --
	(218.61,502.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (207.57,501.88) --
	(207.57,503.37);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.57,498.61) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.92,502.35) --
	(194.96,502.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.81,502.20) --
	(187.81,502.49);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.81,498.31) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (165.35,472.33) --
	(173.05,472.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.60,471.58) --
	(169.60,473.05);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.60,468.29) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (134.07,470.24) --
	(176.07,470.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (165.12,469.07) --
	(165.12,471.33);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (165.12,467.33) {$\sigma$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,338.88) -- (218.78,338.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,338.88) -- ( 49.80,333.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.05,338.88) -- ( 92.05,333.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (134.29,338.88) -- (134.29,333.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.54,338.88) -- (176.54,333.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.78,338.88) -- (218.78,333.90);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 49.80,320.95) {1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 92.05,320.95) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (134.29,320.95) {100};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (176.54,320.95) {1000};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (218.78,320.95) {10000};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,338.88) -- ( 49.80,507.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,338.88) -- ( 44.82,338.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,381.13) -- ( 44.82,381.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,423.37) -- ( 44.82,423.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,465.62) -- ( 44.82,465.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,507.86) -- ( 44.82,507.86);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,336.02) {1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,378.27) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,420.51) {100};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,462.76) {1000};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,505.00) {10000};
\end{scope}
\begin{scope}
\path[clip] ( 49.80,338.88) rectangle (239.28,528.36);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{255,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,431.01) rectangle (189.67,426.03);
\definecolor{fillColor}{RGB}{0,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,421.05) rectangle (189.67,416.07);
\definecolor{fillColor}{RGB}{0,255,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,411.09) rectangle (189.67,406.11);
\definecolor{fillColor}{RGB}{255,255,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,401.13) rectangle (189.67,396.15);
\definecolor{fillColor}{RGB}{255,165,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,391.17) rectangle (189.67,386.19);
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,381.21) rectangle (189.67,376.23);
\definecolor{fillColor}{RGB}{160,32,240}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,371.25) rectangle (189.67,366.27);
\definecolor{fillColor}{RGB}{0,100,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,361.29) rectangle (189.67,356.31);
\definecolor{fillColor}{RGB}{0,255,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,351.33) rectangle (189.67,346.35);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,425.66) {Broughton};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,415.70) {Cognato};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,405.74) {Dornburg};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,395.78) {Kawahara};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,385.82) {Moyle};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,375.86) {Ran};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,365.90) {Rightmyer};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,355.94) {Sauquet};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,345.98) {simulated};
\end{scope}
\begin{scope}
\path[clip] (289.08,289.08) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,548.96) {\bfseries Comparison of adapt (\textit{real}) and nocons (\textit{real})};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,301.03) {ESS/chain [nocons (\textit{real})]};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (307.01,433.62) {ESS/chain [adapt (\textit{real})]};
\end{scope}
\begin{scope}
\path[clip] (338.88,338.88) rectangle (528.36,528.36);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{gray}{0.91}

\path[draw=drawColor,line width= 0.1pt,line join=round,line cap=round,fill=fillColor] (169.90,246.20) --
	(501.86,578.16) --
	(570.61,578.16) --
	(570.61,494.30) --
	(169.90, 93.59) --
	cycle;
\definecolor{fillColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] (169.90,220.77) --
	(527.29,578.16) --
	(570.61,578.16) --
	(570.61,519.74) --
	(169.90,119.03) --
	cycle;
\definecolor{fillColor}{RGB}{169,169,169}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.90,195.33) --
	(552.73,578.16) --
	(570.61,578.16) --
	(570.61,545.17) --
	(169.90,144.46) --
	cycle;

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (422.72,342.31) {$\frac{1}{64} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,426.62) {$64\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (397.28,342.31) {$\frac{1}{16} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,401.18) {$16\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (370.19,342.31) {$\frac{1}{4} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.00,375.75) {$4\times$};

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (338.88,338.88) -- (528.36,528.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (442.22,490.95) --
	(452.08,490.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (447.80,488.50) --
	(447.80,493.11);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (447.80,487.72) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (493.05,494.57) --
	(507.86,494.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (501.91,492.61) --
	(501.91,496.33);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (501.91,490.53) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (467.53,499.63) --
	(469.23,499.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (468.40,499.53) --
	(468.40,499.72);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.40,495.59) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (435.57,457.21) --
	(441.94,457.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (439.03,453.71) --
	(439.03,460.15);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (439.03,453.18) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (445.72,477.46) --
	(454.09,477.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (450.38,473.15) --
	(450.38,480.94);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (450.38,474.55) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (509.40,508.34) --
	(510.23,508.34);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (509.82,507.96) --
	(509.82,508.71);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (509.82,505.44) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.25,470.08) --
	(486.25,474.05);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (486.25,468.95) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (503.53,505.74) --
	(510.01,505.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (507.05,504.33) --
	(507.05,507.05);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (507.05,501.71) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (497.50,509.15) --
	(511.69,509.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (505.93,509.01) --
	(505.93,509.30);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (505.93,505.12) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (458.56,441.48) --
	(458.56,447.41);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (458.56,440.65) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.64,465.29) --
	(485.64,470.85);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (485.64,465.37) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (511.78,512.39) --
	(512.23,512.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (512.01,512.01) --
	(512.01,512.77);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (512.01,509.49) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (510.99,489.74) --
	(510.99,496.16);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (510.99,490.01) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (491.73,482.43) --
	(491.73,487.46);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (491.73,481.08) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (488.29,509.74) --
	(519.69,509.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (510.02,509.40) --
	(510.02,510.06);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (510.02,505.70) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (458.40,493.13) --
	(482.75,493.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.34,492.97) --
	(474.34,493.29);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.34,489.10) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (496.76,491.95) --
	(496.76,497.87);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (496.76,492.25) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (409.03,486.63) --
	(426.98,486.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.12,480.59) --
	(420.12,491.17);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (420.12,483.41) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (493.64,486.94) --
	(500.01,486.94);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (497.10,484.78) --
	(497.10,488.87);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (497.10,482.90) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (414.89,499.46) --
	(424.09,499.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.06,498.34) --
	(420.06,500.52);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (420.06,495.43) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (408.74,462.06) --
	(419.56,462.06);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (414.94,452.46) --
	(414.94,468.33);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (414.94,458.03) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (408.48,488.92) --
	(433.72,488.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (425.13,483.95) --
	(425.13,492.83);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (425.13,486.02) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (512.25,512.90) --
	(512.71,512.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (512.48,512.69) --
	(512.48,513.11);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (512.48,509.99) {$\mu$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.40,497.82) --
	(476.30,497.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (468.44,494.86) --
	(468.44,500.36);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.44,494.59) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (475.85,498.71) --
	(496.66,498.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (489.06,489.13) --
	(489.06,504.97);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (489.06,494.67) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (489.18,507.02) --
	(505.64,507.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.19,506.47) --
	(499.19,507.55);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (499.19,502.98) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (445.83,469.60) --
	(468.64,469.60);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (460.58,463.71) --
	(460.58,474.05);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (460.58,465.56) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.45,496.70) --
	(477.85,496.70);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (469.65,491.56) --
	(469.65,500.72);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (469.65,493.80) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (505.49,512.98) --
	(514.73,512.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (510.69,511.49) --
	(510.69,514.37);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (510.69,510.08) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (453.26,482.10) --
	(463.41,482.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (459.03,480.23) --
	(459.03,483.80);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (459.03,478.87) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (502.14,502.07) --
	(507.36,502.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (504.93,500.38) --
	(504.93,503.61);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (504.93,498.03) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (491.96,503.97) --
	(496.39,503.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (494.31,503.61) --
	(494.31,504.33);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (494.31,499.94) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (449.79,473.17) --
	(459.82,473.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (455.48,470.48) --
	(455.48,475.52);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (455.48,469.14) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (450.63,478.15) --
	(461.41,478.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (456.80,476.59) --
	(456.80,479.58);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (456.80,475.24) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (506.92,507.74) --
	(507.97,507.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (507.46,507.42) --
	(507.46,508.04);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (507.46,504.83) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.28,495.30) --
	(471.88,495.30);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (460.63,494.52) --
	(460.63,496.04);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (460.63,492.07) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.65,495.60) --
	(507.69,495.60);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (496.65,494.08) --
	(496.65,497.00);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (496.65,491.57) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (465.00,500.38) --
	(484.04,500.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.89,500.12) --
	(476.89,500.63);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (476.89,496.34) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.43,473.27) --
	(462.13,473.27);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (458.68,472.16) --
	(458.68,474.32);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (458.68,469.24) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.15,473.74) --
	(465.15,473.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.20,471.09) --
	(454.20,476.05);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (454.20,470.83) {$\sigma$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,338.88) -- (507.86,338.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,338.88) -- (338.88,333.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (381.13,338.88) -- (381.13,333.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.37,338.88) -- (423.37,333.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (465.62,338.88) -- (465.62,333.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (507.86,338.88) -- (507.86,333.90);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (338.88,320.95) {1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (381.13,320.95) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (423.37,320.95) {100};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (465.62,320.95) {1000};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (507.86,320.95) {10000};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,338.88) -- (338.88,507.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,338.88) -- (333.90,338.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,381.13) -- (333.90,381.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,423.37) -- (333.90,423.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,465.62) -- (333.90,465.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,507.86) -- (333.90,507.86);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,336.02) {1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,378.27) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,420.51) {100};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,462.76) {1000};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,505.00) {10000};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,259.88) {\bfseries Comparison of adapt (\textit{real}) and cons (\textit{real})};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54, 11.95) {ESS/chain [cons (\textit{real})]};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,144.54) {ESS/chain [adapt (\textit{real})]};
\end{scope}
\begin{scope}
\path[clip] ( 49.80, 49.80) rectangle (239.28,239.28);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{gray}{0.91}

\path[draw=drawColor,line width= 0.1pt,line join=round,line cap=round,fill=fillColor] (  0.00, 82.04) --
	(284.70,366.75) --
	(284.70,202.66) --
	( 82.04,  0.00) --
	(  0.00,  0.00) --
	cycle;
\definecolor{fillColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] (  0.00, 54.70) --
	(284.70,339.40) --
	(284.70,230.01) --
	( 54.70,  0.00) --
	(  0.00,  0.00) --
	cycle;
\definecolor{fillColor}{RGB}{169,169,169}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (  0.00, 27.35) --
	(284.70,312.05) --
	(284.70,257.36) --
	( 27.35,  0.00) --
	(  0.00,  0.00) --
	cycle;

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (139.38, 53.23) {$\frac{1}{64} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,143.28) {$64\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (112.03, 53.23) {$\frac{1}{16} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,115.93) {$16\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 83.03, 53.23) {$\frac{1}{4} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92, 88.58) {$4\times$};

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 49.80, 49.80) -- (239.28,239.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.73,213.31) --
	(180.71,213.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.53,210.67) --
	(177.53,215.64);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.53,210.08) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.65,217.20) --
	(223.43,217.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.18,215.09) --
	(221.18,219.10);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (221.18,213.16) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.36,222.64) --
	(222.63,222.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.53,222.53) --
	(221.53,222.74);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (221.53,218.60) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.02,177.03) --
	(176.32,177.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.00,173.27) --
	(173.00,180.19);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.00,173.00) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.05,198.80) --
	(157.65,198.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (155.48,194.17) --
	(155.48,202.55);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (155.48,195.89) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.61,232.01) --
	(233.26,232.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.46,231.60) --
	(232.46,232.40);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (232.46,229.10) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.04,193.12) --
	(195.17,193.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.77,190.87) --
	(192.77,195.14);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.77,189.89) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.87,229.21) --
	(228.31,229.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.60,227.70) --
	(227.60,230.62);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (227.60,225.18) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.52,232.88) --
	(229.09,232.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.80,232.72) --
	(228.80,233.04);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (228.80,228.85) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.71,163.56) --
	(173.01,163.56);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.16,160.12) --
	(168.16,166.49);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (168.16,159.53) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (183.06,188.93) --
	(188.16,188.93);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.77,185.72) --
	(185.77,191.69);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.77,186.03) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.98,236.37) --
	(236.46,236.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (236.22,235.95) --
	(236.22,236.77);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (236.22,233.46) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.24,215.76) --
	(213.56,215.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.45,212.01) --
	(209.45,218.92);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.45,212.54) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.34,207.04) --
	(210.37,207.04);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (207.59,204.14) --
	(207.59,209.56);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.59,203.00) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.38,233.51) --
	(224.77,233.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (224.09,233.15) --
	(224.09,233.86);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (224.09,229.47) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.76,215.65) --
	(211.95,215.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.68,215.48) --
	(208.68,215.82);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (208.68,211.62) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (201.21,217.83) --
	(211.12,217.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.78,214.39) --
	(206.78,220.75);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (206.78,214.92) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (150.22,208.67) --
	(163.61,208.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.03,202.16) --
	(158.03,213.55);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.03,205.44) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (219.13,208.99) --
	(222.64,208.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.96,206.67) --
	(220.96,211.07);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.96,204.96) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.63,222.46) --
	(222.65,222.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.30,221.26) --
	(220.30,223.59);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.30,218.43) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (164.55,182.25) --
	(177.96,182.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.38,171.93) --
	(172.38,188.99);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.38,178.21) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (128.10,211.13) --
	(142.44,211.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (136.54,205.79) --
	(136.54,215.33);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (136.54,208.22) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (236.56,236.91) --
	(237.19,236.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (236.88,236.68) --
	(236.88,237.13);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (236.88,234.00) {$\mu$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (213.15,220.69) --
	(216.83,220.69);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.07,217.51) --
	(215.07,223.43);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (215.07,217.47) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.98,221.65) --
	(223.10,221.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.61,211.36) --
	(217.61,228.38);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (217.61,217.62) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.83,230.59) --
	(223.08,230.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.96,230.00) --
	(222.96,231.16);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (222.96,226.55) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.87,190.35) --
	(185.98,190.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (183.59,184.02) --
	(183.59,195.13);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.59,186.31) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.45,219.50) --
	(205.78,219.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (205.12,213.97) --
	(205.12,223.81);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.12,216.59) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (233.18,237.00) --
	(238.93,237.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (236.27,235.39) --
	(236.27,238.49);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (236.27,234.10) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.79,203.79) --
	(198.65,203.79);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.27,201.78) --
	(197.27,205.62);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.27,200.56) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.73,225.26) --
	(226.99,225.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.37,223.45) --
	(226.37,226.92);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (226.37,221.23) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.42,227.31) --
	(226.05,227.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.74,226.93) --
	(225.74,227.69);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (225.74,223.28) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.75,194.19) --
	(190.95,194.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.42,191.29) --
	(189.42,196.72);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (189.42,190.16) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.03,199.54) --
	(189.05,199.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.07,197.87) --
	(188.07,201.08);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.07,196.64) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.81,231.36) --
	(231.65,231.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.23,231.02) --
	(231.23,231.69);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (231.23,228.45) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (214.65,217.98) --
	(216.65,217.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.68,217.15) --
	(215.68,218.78);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (215.68,214.76) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.06,218.31) --
	(226.66,218.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.88,216.68) --
	(225.88,219.81);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (225.88,214.28) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.41,223.44) --
	(225.72,223.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.56,223.17) --
	(225.56,223.71);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (225.56,219.41) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.48,194.30) --
	(194.06,194.30);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.28,193.10) --
	(193.28,195.43);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.28,190.27) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.79,194.80) --
	(192.21,194.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.04,191.95) --
	(191.04,197.29);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.04,191.90) {$\sigma$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 49.80) -- (231.49, 49.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 49.80) -- ( 49.80, 44.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.22, 49.80) -- ( 95.22, 44.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.65, 49.80) -- (140.65, 44.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.07, 49.80) -- (186.07, 44.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.49, 49.80) -- (231.49, 44.82);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 49.80, 31.87) {1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 95.22, 31.87) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (140.65, 31.87) {100};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (186.07, 31.87) {1000};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (231.49, 31.87) {10000};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 49.80) -- ( 49.80,231.49);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 49.80) -- ( 44.82, 49.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 95.22) -- ( 44.82, 95.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,140.65) -- ( 44.82,140.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,186.07) -- ( 44.82,186.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,231.49) -- ( 44.82,231.49);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84, 46.94) {1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84, 92.37) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,137.79) {100};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,183.21) {1000};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,228.64) {10000};
\end{scope}
\begin{scope}
\path[clip] (289.08,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.66] at (433.62,258.45) {\bfseries Speed comparison};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.66] at (433.62, 11.95) {Setting};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.66] at (307.01,144.54) {Speed ($10^6$ states/hr)};
\end{scope}
\begin{scope}
\path[clip] (338.88, 49.80) rectangle (528.36,239.28);
\definecolor{drawColor}{RGB}{255,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.85, 89.35) -- (428.67, 81.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.57, 81.09) -- (516.39, 89.09);
\definecolor{fillColor}{RGB}{255,0,0}

\path[fill=fillColor] (345.90, 92.78) --
	(348.41, 88.43) --
	(343.38, 88.43) --
	cycle;

\path[fill=fillColor] (433.62, 80.59) circle (  1.87);

\path[fill=fillColor] (521.34, 89.60) circle (  1.87);
\definecolor{drawColor}{RGB}{0,255,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.72,134.93) -- (428.80,114.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.48,114.58) -- (516.48,132.20);
\definecolor{fillColor}{RGB}{0,255,0}

\path[fill=fillColor] (345.90,139.09) --
	(348.41,134.73) --
	(343.38,134.73) --
	cycle;

\path[fill=fillColor] (433.62,113.49) circle (  1.87);

\path[fill=fillColor] (521.34,133.30) circle (  1.87);
\definecolor{drawColor}{RGB}{255,165,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (349.23,225.52) -- (430.29,135.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.56,132.54) -- (516.40,142.76);
\definecolor{fillColor}{RGB}{255,165,0}

\path[fill=fillColor] (345.90,232.13) --
	(348.41,227.77) --
	(343.38,227.77) --
	cycle;

\path[fill=fillColor] (433.62,131.89) circle (  1.87);

\path[fill=fillColor] (521.34,143.41) circle (  1.87);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.88, 71.53) -- (428.64, 69.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.60, 69.22) -- (516.36, 71.77);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] (345.90, 71.68) circle (  1.87);

\path[fill=fillColor] (433.62, 69.06) circle (  1.87);

\path[fill=fillColor] (521.34, 74.84) --
	(523.86, 70.48) --
	(518.83, 70.48) --
	cycle;
\definecolor{drawColor}{RGB}{160,32,240}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.48,143.02) -- (429.04,109.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.26,109.56) -- (516.70,139.97);
\definecolor{fillColor}{RGB}{160,32,240}

\path[fill=fillColor] (345.90,147.87) --
	(348.41,143.51) --
	(343.38,143.51) --
	cycle;

\path[fill=fillColor] (433.62,107.76) circle (  1.87);

\path[fill=fillColor] (521.34,141.77) circle (  1.87);
\definecolor{drawColor}{RGB}{0,100,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.70,132.99) -- (428.82,111.40);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.60,110.21) -- (516.36,112.45);
\definecolor{fillColor}{RGB}{0,100,0}

\path[fill=fillColor] (345.90,137.22) --
	(348.41,132.86) --
	(343.38,132.86) --
	cycle;

\path[fill=fillColor] (433.62,110.07) circle (  1.87);

\path[fill=fillColor] (521.34,112.59) circle (  1.87);
\definecolor{drawColor}{RGB}{0,255,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (349.79,196.49) -- (429.73,132.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (437.55,132.47) -- (517.41,194.71);
\definecolor{fillColor}{RGB}{0,255,255}

\path[fill=fillColor] (345.90,202.50) --
	(348.41,198.15) --
	(343.38,198.15) --
	cycle;

\path[fill=fillColor] (433.62,129.40) circle (  1.87);

\path[fill=fillColor] (521.34,197.77) circle (  1.87);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (345.90, 49.80) -- (521.34, 49.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (345.90, 49.80) -- (345.90, 44.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.62, 49.80) -- (433.62, 44.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (521.34, 49.80) -- (521.34, 44.82);

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (348.76, 39.84) {nocons (\textit{real})};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (436.48, 39.84) {cons (\textit{real})};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (524.20, 39.84) {adapt (\textit{real})};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 56.82) -- (338.88,216.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 56.82) -- (333.90, 56.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 96.66) -- (333.90, 96.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,136.50) -- (333.90,136.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,176.33) -- (333.90,176.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,216.17) -- (333.90,216.17);

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (326.93, 56.82) {0};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (326.93, 96.66) {10};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (326.93,136.50) {20};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (326.93,176.33) {30};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (326.93,216.17) {40};
\end{scope}
\end{tikzpicture}

\end{document}

### 2020-08-07 benchmarking/benchmarkingVM/ESS_round2.tex
update

% Created by tikzDevice version 0.12.3 on 2020-08-07 14:28:37
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (578.16,578.16);
\begin{scope}
\path[clip] (  0.00,289.08) rectangle (289.08,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,548.96) {\bfseries Comparison of adapt (\textit{real}) and \textit{cat}};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,301.03) {ESS/chain [\textit{cat}]};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,433.62) {ESS/chain [adapt (\textit{real})]};
\end{scope}
\begin{scope}
\path[clip] ( 49.80,338.88) rectangle (239.28,528.36);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{gray}{0.91}

\path[draw=drawColor,line width= 0.1pt,line join=round,line cap=round,fill=fillColor] (  0.00,370.60) --
	(207.56,578.16) --
	(284.41,578.16) --
	(284.41,491.97) --
	(  0.00,207.56) --
	cycle;
\definecolor{fillColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] (  0.00,343.43) --
	(234.73,578.16) --
	(284.41,578.16) --
	(284.41,519.15) --
	(  0.00,234.73) --
	cycle;
\definecolor{fillColor}{RGB}{169,169,169}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (  0.00,316.25) --
	(261.91,578.16) --
	(284.41,578.16) --
	(284.41,546.32) --
	(  0.00,261.91) --
	cycle;

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (138.85,342.31) {$\frac{1}{64} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,431.83) {$64\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (111.68,342.31) {$\frac{1}{16} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,404.66) {$16\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 82.85,342.31) {$\frac{1}{4} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92,377.49) {$4\times$};

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,528.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.85,501.35) --
	(160.70,501.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (156.77,498.73) --
	(156.77,503.66);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (156.77,498.12) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.10,505.21) --
	(226.15,505.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (224.23,503.12) --
	(224.23,507.10);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (224.23,501.18) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.91,510.62) --
	(195.69,510.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.30,510.51) --
	(195.30,510.72);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.30,506.58) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (150.45,465.30) --
	(158.07,465.30);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (154.63,461.56) --
	(154.63,468.44);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (154.63,461.27) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (143.37,486.93) --
	(159.52,486.93);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.06,482.33) --
	(153.06,490.65);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (153.06,484.03) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.81,519.93) --
	(232.76,519.93);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.29,519.53) --
	(232.29,520.32);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (232.29,517.02) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.38,481.29) --
	(197.55,481.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.14,479.06) --
	(195.14,483.29);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.14,478.06) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.44,517.15) --
	(231.91,517.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.19,515.64) --
	(231.19,518.55);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (231.19,513.12) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.86,520.80) --
	(226.63,520.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.25,520.64) --
	(226.25,520.95);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (226.25,516.76) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.50,451.92) --
	(178.74,451.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.28,448.49) --
	(174.28,454.83);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.28,447.88) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.34,477.13) --
	(194.89,477.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.89,473.94) --
	(191.89,479.87);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.89,474.22) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.29,524.26) --
	(235.63,524.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.46,523.85) --
	(235.46,524.66);
\definecolor{drawColor}{RGB}{0,255,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (235.46,521.35) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (219.41,503.79) --
	(222.44,503.79);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.99,500.06) --
	(220.99,506.92);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.99,500.56) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.74,495.12) --
	(212.21,495.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.55,492.24) --
	(210.55,497.62);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.55,491.08) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.33,521.42) --
	(228.35,521.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.85,521.06) --
	(227.85,521.77);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (227.85,517.38) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.31,503.68) --
	(212.31,503.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.41,503.51) --
	(210.41,503.85);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.41,499.64) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.56,505.84) --
	(217.05,505.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (214.93,502.42) --
	(214.93,508.74);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (214.93,502.93) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.33,496.74) --
	(152.55,496.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (141.01,490.27) --
	(141.01,501.59);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (141.01,493.51) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.17,497.06) --
	(223.98,497.06);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.95,494.75) --
	(218.95,499.12);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (218.95,493.03) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (127.87,510.44) --
	(136.69,510.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (132.77,509.25) --
	(132.77,511.57);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (132.77,506.41) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (122.43,470.48) --
	(153.27,470.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (143.38,460.23) --
	(143.38,477.18);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (143.38,466.45) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.53,499.18) --
	(134.19,499.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (128.53,493.87) --
	(128.53,503.35);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (128.53,496.28) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.21,524.80) --
	(235.92,524.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.57,524.57) --
	(235.57,525.02);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (235.57,521.89) {$\mu$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.15,508.68) --
	(210.57,508.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.05,505.52) --
	(206.05,511.41);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (206.05,505.46) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (167.79,509.64) --
	(219.64,509.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (207.40,499.41) --
	(207.40,516.32);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.40,505.60) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.29,518.51) --
	(227.21,518.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.27,517.93) --
	(226.27,519.08);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (226.27,514.48) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.98,478.53) --
	(195.19,478.53);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.02,472.24) --
	(190.02,483.29);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.02,474.50) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.02,507.50) --
	(212.05,507.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.06,502.00) --
	(211.06,511.78);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.06,504.59) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.89,524.89) --
	(238.66,524.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (236.87,523.29) --
	(236.87,526.36);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (236.87,521.98) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.69,491.89) --
	(181.70,491.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (178.93,489.89) --
	(178.93,493.70);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (178.93,488.66) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.17,513.22) --
	(230.44,513.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.82,511.43) --
	(229.82,514.87);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (229.82,509.19) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.44,515.26) --
	(219.18,515.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.81,514.88) --
	(218.81,515.64);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (218.81,511.23) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.99,482.35) --
	(176.42,482.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.05,479.47) --
	(173.05,484.86);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.05,478.32) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.60,487.67) --
	(185.47,487.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (183.18,486.01) --
	(183.18,489.20);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.18,484.76) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.29,519.28) --
	(230.98,519.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.64,518.95) --
	(230.64,519.61);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (230.64,516.38) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.39,505.99) --
	(174.41,505.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.66,505.16) --
	(169.66,506.79);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.66,502.77) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.75,506.32) --
	(230.90,506.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.39,504.70) --
	(229.39,507.81);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (229.39,502.28) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.03,511.42) --
	(206.39,511.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.21,511.15) --
	(206.21,511.69);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (206.21,507.39) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.24,482.46) --
	(177.13,482.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.28,481.27) --
	(175.28,483.58);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (175.28,478.43) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.62,482.96) --
	(187.77,482.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.37,480.13) --
	(185.37,485.43);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.37,480.05) {$\sigma$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,338.88) -- (230.34,338.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,338.88) -- ( 49.80,333.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 94.93,338.88) -- ( 94.93,333.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.07,338.88) -- (140.07,333.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.20,338.88) -- (185.20,333.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.34,338.88) -- (230.34,333.90);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 49.80,320.95) {1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 94.93,320.95) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (140.07,320.95) {100};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (185.20,320.95) {1000};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (230.34,320.95) {10000};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,338.88) -- ( 49.80,519.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,338.88) -- ( 44.82,338.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,384.01) -- ( 44.82,384.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,429.15) -- ( 44.82,429.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,474.28) -- ( 44.82,474.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,519.42) -- ( 44.82,519.42);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,336.02) {1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,381.16) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,426.29) {100};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,471.42) {1000};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,516.56) {10000};
\end{scope}
\begin{scope}
\path[clip] ( 49.80,338.88) rectangle (239.28,528.36);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{255,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,431.01) rectangle (189.67,426.03);
\definecolor{fillColor}{RGB}{0,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,421.05) rectangle (189.67,416.07);
\definecolor{fillColor}{RGB}{0,255,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,411.09) rectangle (189.67,406.11);
\definecolor{fillColor}{RGB}{255,255,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,401.13) rectangle (189.67,396.15);
\definecolor{fillColor}{RGB}{255,165,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,391.17) rectangle (189.67,386.19);
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,381.21) rectangle (189.67,376.23);
\definecolor{fillColor}{RGB}{160,32,240}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,371.25) rectangle (189.67,366.27);
\definecolor{fillColor}{RGB}{0,100,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,361.29) rectangle (189.67,356.31);
\definecolor{fillColor}{RGB}{0,255,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,351.33) rectangle (189.67,346.35);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,425.66) {Broughton};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,415.70) {Cognato};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,405.74) {Dornburg};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,395.78) {Kawahara};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,385.82) {Moyle};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,375.86) {Ran};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,365.90) {Rightmyer};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,355.94) {Sauquet};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,345.98) {simulated};
\end{scope}
\begin{scope}
\path[clip] (289.08,289.08) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,548.96) {\bfseries Comparison of adapt (\textit{quant}) and \textit{cat}};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,301.03) {ESS/chain [\textit{cat}]};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (307.01,433.62) {ESS/chain [adapt (\textit{quant})]};
\end{scope}
\begin{scope}
\path[clip] (338.88,338.88) rectangle (528.36,528.36);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{gray}{0.91}

\path[draw=drawColor,line width= 0.1pt,line join=round,line cap=round,fill=fillColor] (158.34,239.86) --
	(496.64,578.16) --
	(573.49,578.16) --
	(573.49,491.97) --
	(158.34, 76.82) --
	cycle;
\definecolor{fillColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] (158.34,212.69) --
	(523.81,578.16) --
	(573.49,578.16) --
	(573.49,519.15) --
	(158.34,104.00) --
	cycle;
\definecolor{fillColor}{RGB}{169,169,169}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.34,185.52) --
	(550.99,578.16) --
	(573.49,578.16) --
	(573.49,546.32) --
	(158.34,131.17) --
	cycle;

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (427.93,342.31) {$\frac{1}{64} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,431.83) {$64\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (400.76,342.31) {$\frac{1}{16} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,404.66) {$16\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (371.93,342.31) {$\frac{1}{4} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.00,377.49) {$4\times$};

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (338.88,338.88) -- (528.36,528.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (440.93,459.60) --
	(449.78,459.60);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (445.85,450.75) --
	(445.85,465.67);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (445.85,456.37) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (511.18,510.65) --
	(515.23,510.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (513.31,508.40) --
	(513.31,512.67);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (513.31,506.62) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.99,510.45) --
	(484.77,510.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (484.38,509.13) --
	(484.38,511.69);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (484.38,506.42) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (439.53,456.23) --
	(447.15,456.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.71,441.90) --
	(443.71,464.42);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (443.71,452.20) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (432.45,444.54) --
	(448.60,444.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (442.14,433.29) --
	(442.14,451.64);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (442.14,441.64) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (520.89,520.56) --
	(521.84,520.56);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (521.37,520.43) --
	(521.37,520.69);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (521.37,517.66) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (508.49,517.93) --
	(511.52,517.93);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (510.07,516.34) --
	(510.07,519.39);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (510.07,514.70) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (497.82,524.11) --
	(501.29,524.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.63,523.95) --
	(499.63,524.26);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (499.63,520.07) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (516.41,522.33) --
	(517.43,522.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (516.93,521.18) --
	(516.93,523.42);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (516.93,518.30) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (497.39,501.55) --
	(501.39,501.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.49,497.15) --
	(499.49,505.13);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (499.49,497.51) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (501.64,509.18) --
	(506.13,509.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (504.01,505.39) --
	(504.01,512.36);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (504.01,506.28) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (398.41,435.61) --
	(441.63,435.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (430.09,420.47) --
	(430.09,444.05);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (430.09,432.38) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (501.25,509.83) --
	(513.06,509.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (508.03,509.03) --
	(508.03,510.60);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (508.03,505.80) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (416.95,506.98) --
	(425.77,506.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.85,503.20) --
	(421.85,510.16);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (421.85,502.95) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (411.51,435.35) --
	(442.35,435.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (432.46,415.96) --
	(432.46,444.90);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (432.46,431.31) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (409.61,405.29) --
	(423.27,405.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.61,396.70) --
	(417.61,411.24);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (417.61,402.38) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (524.29,524.30) --
	(525.00,524.30);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (524.65,523.97) --
	(524.65,524.62);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (524.65,521.39) {$\mu$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (489.23,503.26) --
	(499.65,503.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.13,500.41) --
	(495.13,505.76);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (495.13,500.04) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (456.87,516.19) --
	(508.72,516.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (496.48,513.31) --
	(496.48,518.70);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (496.48,512.15) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (514.37,520.99) --
	(516.29,520.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (515.35,520.33) --
	(515.35,521.63);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (515.35,516.96) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (472.06,483.75) --
	(484.27,483.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.10,479.62) --
	(479.10,487.16);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (479.10,479.72) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.10,504.58) --
	(501.13,504.58);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (500.14,502.22) --
	(500.14,506.68);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (500.14,501.67) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (523.97,525.79) --
	(527.74,525.79);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (525.95,524.73) --
	(525.95,526.80);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (525.95,522.89) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.77,486.85) --
	(470.78,486.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (468.01,482.06) --
	(468.01,490.70);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.01,483.63) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (518.25,513.57) --
	(519.52,513.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (518.90,511.88) --
	(518.90,515.13);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (518.90,509.54) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (507.52,517.40) --
	(508.26,517.40);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (507.89,515.55) --
	(507.89,519.09);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (507.89,513.37) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (458.07,484.33) --
	(465.50,484.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.13,477.88) --
	(462.13,489.18);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (462.13,480.30) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (469.68,483.35) --
	(474.55,483.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (472.26,480.89) --
	(472.26,485.53);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (472.26,480.45) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (519.37,519.43) --
	(520.06,519.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (519.72,518.97) --
	(519.72,519.89);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (519.72,516.53) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (452.47,471.75) --
	(463.49,471.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (458.74,469.32) --
	(458.74,473.92);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (458.74,468.53) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (516.83,516.44) --
	(519.98,516.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (518.47,514.31) --
	(518.47,518.36);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (518.47,512.41) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.11,516.44) --
	(495.47,516.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.29,516.21) --
	(495.29,516.67);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (495.29,512.41) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.32,485.53) --
	(466.21,485.53);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.36,482.88) --
	(464.36,487.86);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (464.36,481.49) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (471.70,475.69) --
	(476.85,475.69);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.45,473.48) --
	(474.45,477.68);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.45,472.79) {$\sigma$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,338.88) -- (519.42,338.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,338.88) -- (338.88,333.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (384.01,338.88) -- (384.01,333.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (429.15,338.88) -- (429.15,333.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.28,338.88) -- (474.28,333.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (519.42,338.88) -- (519.42,333.90);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (338.88,320.95) {1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (384.01,320.95) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (429.15,320.95) {100};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (474.28,320.95) {1000};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (519.42,320.95) {10000};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,338.88) -- (338.88,519.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,338.88) -- (333.90,338.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,384.01) -- (333.90,384.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,429.15) -- (333.90,429.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,474.28) -- (333.90,474.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,519.42) -- (333.90,519.42);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,336.02) {1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,381.16) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,426.29) {100};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,471.42) {1000};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,516.56) {10000};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,259.88) {\bfseries Comparison of adapt (\textit{quant}) and adapt (\textit{real})};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54, 11.95) {ESS/chain [adapt (\textit{real})]};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,144.54) {ESS/chain [adapt (\textit{quant})]};
\end{scope}
\begin{scope}
\path[clip] ( 49.80, 49.80) rectangle (239.28,239.28);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{gray}{0.91}

\path[draw=drawColor,line width= 0.1pt,line join=round,line cap=round,fill=fillColor] (  0.00, 82.29) --
	(284.84,367.13) --
	(284.84,202.55) --
	( 82.29,  0.00) --
	(  0.00,  0.00) --
	cycle;
\definecolor{fillColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] (  0.00, 54.86) --
	(284.84,339.70) --
	(284.84,229.98) --
	( 54.86,  0.00) --
	(  0.00,  0.00) --
	cycle;
\definecolor{fillColor}{RGB}{169,169,169}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (  0.00, 27.43) --
	(284.84,312.27) --
	(284.84,257.41) --
	( 27.43,  0.00) --
	(  0.00,  0.00) --
	cycle;

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (139.62, 53.23) {$\frac{1}{64} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,143.53) {$64\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (112.19, 53.23) {$\frac{1}{16} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,116.09) {$16\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 83.11, 53.23) {$\frac{1}{4} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92, 88.66) {$4\times$};

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 49.80, 49.80) -- (239.28,239.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.16,171.66) --
	(216.14,171.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (213.81,162.73) --
	(213.81,177.79);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (213.81,168.44) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.60,223.20) --
	(219.61,223.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.71,220.93) --
	(217.71,225.24);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (217.71,219.17) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.06,223.00) --
	(223.27,223.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.16,221.67) --
	(223.16,224.24);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (223.16,218.96) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.64,168.26) --
	(180.59,168.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.42,153.80) --
	(177.42,176.53);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.42,164.23) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.61,156.46) --
	(203.01,156.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (199.25,145.11) --
	(199.25,163.63);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.25,153.56) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.16,233.20) --
	(232.96,233.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.56,233.07) --
	(232.56,233.33);
\definecolor{drawColor}{RGB}{255,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (232.56,230.30) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.51,230.54) --
	(219.43,230.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (216.27,228.94) --
	(216.27,232.02);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (216.27,227.31) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.61,236.78) --
	(210.05,236.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (207.52,236.62) --
	(207.52,236.94);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.52,232.75) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (233.70,234.99) --
	(234.42,234.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.07,233.83) --
	(234.07,236.08);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (234.07,230.95) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.98,214.01) --
	(216.33,214.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (216.16,209.57) --
	(216.16,217.63);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (216.16,209.97) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (214.89,221.71) --
	(221.27,221.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.34,217.88) --
	(218.34,224.92);
\definecolor{drawColor}{RGB}{255,165,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (218.34,218.81) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (202.63,147.44) --
	(214.05,147.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.15,132.17) --
	(209.15,155.96);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.15,144.22) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (207.15,222.37) --
	(211.56,222.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.48,221.56) --
	(209.48,223.15);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.48,218.33) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.78,219.50) --
	(224.12,219.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.99,215.67) --
	(222.99,222.70);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (222.99,215.46) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.30,147.18) --
	(189.41,147.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.65,127.61) --
	(182.65,156.83);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.65,143.15) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.26,116.84) --
	(215.83,116.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.62,108.17) --
	(211.62,122.84);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.62,113.93) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.25,236.97) --
	(237.70,236.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.48,236.65) --
	(237.48,237.30);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (237.48,234.07) {$\mu$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.02,215.74) --
	(223.96,215.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.21,212.86) --
	(221.21,218.26);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (221.21,212.51) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.85,228.78) --
	(228.92,228.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.17,225.88) --
	(222.17,231.32);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (222.17,224.75) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.55,233.64) --
	(231.71,233.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.14,232.97) --
	(231.14,234.28);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (231.14,229.60) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.43,196.04) --
	(195.58,196.04);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.78,191.87) --
	(190.78,199.48);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.78,192.01) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (214.47,217.06) --
	(224.34,217.06);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.01,214.69) --
	(220.01,219.19);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.01,214.16) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.96,238.48) --
	(239.06,238.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.57,237.41) --
	(237.57,239.50);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (237.57,235.58) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (202.24,199.17) --
	(206.09,199.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.26,194.33) --
	(204.26,203.06);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (204.26,195.95) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.98,226.15) --
	(227.46,226.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.80,224.44) --
	(225.80,227.72);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (225.80,222.11) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.47,230.01) --
	(228.23,230.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.85,228.14) --
	(227.85,231.72);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (227.85,225.98) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.72,196.63) --
	(197.16,196.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.63,190.12) --
	(194.63,201.52);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.63,192.60) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.32,195.64) --
	(201.54,195.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.00,193.16) --
	(200.00,197.84);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (200.00,192.73) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.57,232.06) --
	(232.24,232.06);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.91,231.59) --
	(231.91,232.52);
\definecolor{drawColor}{RGB}{0,100,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (231.91,229.16) {$\mu$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.66,183.93) --
	(219.30,183.93);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.50,181.48) --
	(218.50,186.11);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (218.50,180.70) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.19,229.04) --
	(220.33,229.04);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.82,226.89) --
	(218.82,230.98);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (218.82,225.01) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.70,229.04) --
	(224.24,229.04);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.97,228.81) --
	(223.97,229.27);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (223.97,225.01) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.54,197.84) --
	(195.87,197.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.74,195.17) --
	(194.74,200.19);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.74,193.80) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.39,187.91) --
	(197.73,187.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.24,185.67) --
	(195.24,189.92);
\definecolor{drawColor}{RGB}{0,255,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.24,185.00) {$\sigma$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 49.80) -- (232.05, 49.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 49.80) -- ( 49.80, 44.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.36, 49.80) -- ( 95.36, 44.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.92, 49.80) -- (140.92, 44.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.49, 49.80) -- (186.49, 44.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.05, 49.80) -- (232.05, 44.82);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 49.80, 31.87) {1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 95.36, 31.87) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (140.92, 31.87) {100};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (186.49, 31.87) {1000};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (232.05, 31.87) {10000};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 49.80) -- ( 49.80,232.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 49.80) -- ( 44.82, 49.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 95.36) -- ( 44.82, 95.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,140.92) -- ( 44.82,140.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,186.49) -- ( 44.82,186.49);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,232.05) -- ( 44.82,232.05);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84, 46.94) {1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84, 92.50) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,138.07) {100};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,183.63) {1000};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,229.19) {10000};
\end{scope}
\begin{scope}
\path[clip] (289.08,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.66] at (433.62,258.45) {\bfseries Speed comparison};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.66] at (433.62, 11.95) {Setting};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.66] at (307.01,144.54) {Speed ($10^6$ states/hr)};
\end{scope}
\begin{scope}
\path[clip] (338.88, 49.80) rectangle (528.36,239.28);
\definecolor{drawColor}{RGB}{255,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.86, 82.50) -- (428.66, 89.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.55, 88.90) -- (516.41, 77.92);
\definecolor{fillColor}{RGB}{255,0,0}

\path[fill=fillColor] (345.90, 82.07) circle (  1.87);

\path[fill=fillColor] (433.62, 92.50) --
	(436.14, 88.14) --
	(431.10, 88.14) --
	cycle;

\path[fill=fillColor] (521.34, 77.23) circle (  1.87);
\definecolor{drawColor}{RGB}{255,165,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.84,153.76) -- (428.68,144.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.29,141.68) -- (516.67,112.63);
\definecolor{fillColor}{RGB}{255,165,0}

\path[fill=fillColor] (345.90,157.28) --
	(348.41,152.93) --
	(343.38,152.93) --
	cycle;

\path[fill=fillColor] (433.62,143.41) circle (  1.87);

\path[fill=fillColor] (521.34,110.89) circle (  1.87);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.88, 69.57) -- (428.64, 71.79);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.60, 71.74) -- (516.37, 68.72);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] (345.90, 69.42) circle (  1.87);

\path[fill=fillColor] (433.62, 74.84) --
	(436.14, 70.48) --
	(431.10, 70.48) --
	cycle;

\path[fill=fillColor] (521.34, 68.52) circle (  1.87);
\definecolor{drawColor}{RGB}{160,32,240}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.68,117.44) -- (428.84,140.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.04,139.48) -- (516.92, 98.69);
\definecolor{fillColor}{RGB}{160,32,240}

\path[fill=fillColor] (345.90,116.04) circle (  1.87);

\path[fill=fillColor] (433.62,144.68) --
	(436.14,140.32) --
	(431.10,140.32) --
	cycle;

\path[fill=fillColor] (521.34, 96.40) circle (  1.87);
\definecolor{drawColor}{RGB}{0,100,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.88,115.29) -- (428.64,112.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.55,111.90) -- (516.41,100.95);
\definecolor{fillColor}{RGB}{0,100,0}

\path[fill=fillColor] (345.90,118.36) --
	(348.41,114.00) --
	(343.38,114.00) --
	cycle;

\path[fill=fillColor] (433.62,112.59) circle (  1.87);

\path[fill=fillColor] (521.34,100.26) circle (  1.87);
\definecolor{drawColor}{RGB}{0,255,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.16,147.49) -- (429.35,195.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (437.17,194.28) -- (517.79,114.87);
\definecolor{fillColor}{RGB}{0,255,255}

\path[fill=fillColor] (345.90,144.92) circle (  1.87);

\path[fill=fillColor] (433.62,200.68) --
	(436.14,196.32) --
	(431.10,196.32) --
	cycle;

\path[fill=fillColor] (521.34,111.38) circle (  1.87);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (345.90, 49.80) -- (521.34, 49.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (345.90, 49.80) -- (345.90, 44.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.62, 49.80) -- (433.62, 44.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (521.34, 49.80) -- (521.34, 44.82);

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (348.76, 39.84) {\textit{cat}};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (436.48, 39.84) {adapt (\textit{real})};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (524.20, 39.84) {adapt (\textit{quant})};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 56.82) -- (338.88,216.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 56.82) -- (333.90, 56.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 96.66) -- (333.90, 96.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,136.50) -- (333.90,136.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,176.33) -- (333.90,176.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,216.17) -- (333.90,216.17);

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (326.93, 56.82) {0};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (326.93, 96.66) {10};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (326.93,136.50) {20};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (326.93,176.33) {30};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (326.93,216.17) {40};
\end{scope}
\end{tikzpicture}

\end{document}

### 2020-08-07 benchmarking/benchmarkingVM/ESS_round3.tex
update

% Created by tikzDevice version 0.12.3 on 2020-08-07 14:28:39
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (289.08,289.08);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at (144.54,253.90) {\bfseries Comparison of Bactrian (\textit{real}) and adapt (\textit{real})};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at (144.54, 14.40) {ESS/chain [adapt (\textit{real})]};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at ( 21.60,144.54) {ESS/chain [Bactrian (\textit{real})]};
\end{scope}
\begin{scope}
\path[clip] ( 60.00, 60.00) rectangle (229.08,229.08);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{gray}{0.91}

\path[draw=drawColor,line width= 0.1pt,line join=round,line cap=round,fill=fillColor] (  0.00, 73.08) --
	(216.00,289.08) --
	(269.54,289.08) --
	(269.54,196.46) --
	( 73.08,  0.00) --
	(  0.00,  0.00) --
	cycle;
\definecolor{fillColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] (  0.00, 48.72) --
	(240.36,289.08) --
	(269.54,289.08) --
	(269.54,220.82) --
	( 48.72,  0.00) --
	(  0.00,  0.00) --
	cycle;
\definecolor{fillColor}{RGB}{169,169,169}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (  0.00, 24.36) --
	(264.72,289.08) --
	(269.54,289.08) --
	(269.54,245.18) --
	( 24.36,  0.00) --
	(  0.00,  0.00) --
	cycle;

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (142.16, 64.13) {$\frac{1}{64} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,146.85) {$64\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (117.80, 64.13) {$\frac{1}{16} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,122.49) {$16\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 91.44, 64.13) {$\frac{1}{4} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 62.56, 98.13) {$4\times$};

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 60.00, 60.00) -- (229.08,229.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.39,202.25) --
	(214.66,202.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.22,200.65) --
	(212.22,203.71);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (212.22,198.36) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.91,206.44) --
	(219.07,206.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (213.08,191.17) --
	(213.08,214.48);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (213.08,201.58) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.51,221.34) --
	(221.54,221.34);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.04,220.39) --
	(221.04,222.25);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (221.04,216.48) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.55,185.90) --
	(189.46,185.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.19,182.34) --
	(185.19,188.86);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (185.19,181.04) {$h$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.24,201.88) --
	(215.00,201.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.16,198.88) --
	(211.16,204.43);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (211.16,198.38) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.32,225.51) --
	(228.07,225.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.75,222.77) --
	(226.75,227.87);
\definecolor{drawColor}{RGB}{160,32,240}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (226.75,222.01) {$\mu$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- (221.85, 60.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- ( 60.00, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.46, 60.00) -- (100.46, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.92, 60.00) -- (140.92, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.38, 60.00) -- (181.38, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.85, 60.00) -- (221.85, 54.00);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 60.00, 38.40) {1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (100.46, 38.40) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (140.92, 38.40) {100};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (181.38, 38.40) {1000};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (221.85, 38.40) {10000};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- ( 60.00,221.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- ( 54.00, 60.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,100.46) -- ( 54.00,100.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,140.92) -- ( 54.00,140.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,181.38) -- ( 54.00,181.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,221.85) -- ( 54.00,221.85);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00, 56.56) {1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00, 97.02) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,137.48) {100};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,177.94) {1000};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,218.40) {10000};
\end{scope}
\begin{scope}
\path[clip] ( 60.00, 60.00) rectangle (229.08,229.08);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{255,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,171.00) rectangle (169.31,165.00);
\definecolor{fillColor}{RGB}{0,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,159.00) rectangle (169.31,153.00);
\definecolor{fillColor}{RGB}{0,255,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,147.00) rectangle (169.31,141.00);
\definecolor{fillColor}{RGB}{255,255,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,135.00) rectangle (169.31,129.00);
\definecolor{fillColor}{RGB}{255,165,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,123.00) rectangle (169.31,117.00);
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,111.00) rectangle (169.31,105.00);
\definecolor{fillColor}{RGB}{160,32,240}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11, 99.00) rectangle (169.31, 93.00);
\definecolor{fillColor}{RGB}{0,100,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11, 87.00) rectangle (169.31, 81.00);
\definecolor{fillColor}{RGB}{0,255,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11, 75.00) rectangle (169.31, 69.00);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,164.56) {Broughton};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,152.56) {Cognato};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,140.56) {Dornburg};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,128.56) {Kawahara};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,116.56) {Moyle};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,104.56) {Ran};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31, 92.56) {Rightmyer};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31, 80.56) {Sauquet};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31, 68.56) {simulated};
\end{scope}
\end{tikzpicture}
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (289.08,289.08);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.00] at (144.54,252.18) {\bfseries Speed comparison};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.00] at (144.54, 14.40) {Setting};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.00] at ( 21.60,144.54) {Speed ($10^6$ states/hr)};
\end{scope}
\begin{scope}
\path[clip] ( 60.00, 60.00) rectangle (229.08,229.08);
\definecolor{drawColor}{RGB}{160,32,240}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 72.26,142.15) -- (216.82,144.02);
\definecolor{fillColor}{RGB}{160,32,240}

\path[fill=fillColor] ( 66.26,142.07) circle (  2.25);

\path[fill=fillColor] (222.82,147.60) --
	(225.85,142.35) --
	(219.79,142.35) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.26, 60.00) -- (222.82, 60.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.26, 60.00) -- ( 66.26, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.82, 60.00) -- (222.82, 54.00);

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 69.71, 48.00) {adapt (\textit{real})};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at (226.26, 48.00) {Bactrian (\textit{real})};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 66.26) -- ( 60.00,208.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 66.26) -- ( 54.00, 66.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,101.81) -- ( 54.00,101.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,137.36) -- ( 54.00,137.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,172.91) -- ( 54.00,172.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,208.46) -- ( 54.00,208.46);

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 45.60, 66.26) {0};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 45.60,101.81) {10};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 45.60,137.36) {20};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 45.60,172.91) {30};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 45.60,208.46) {40};
\end{scope}
\end{tikzpicture}

\end{document}

### 2020-08-07 benchmarking/benchmarkingVM/init.sh

@@ -1,0 +1,4 @@
+#!/bin/sh
+
+
+echo "batch,dataset,setting,date,status" > progress.csv

### 2020-08-07 benchmarking/benchmarkingVM/submit_CSjob.sh

@@ -1,0 +1,60 @@
+#!/bin/sh
+
+
+# Dummy job for ~5 min to give the other batche times to start
+#~/beast/bin/beast  -overwrite -beagle_SSE ../datasets/startdummy.xml
+
+#settings=("real" "real_adaptive" "cat" "quant" "AVMN" "bactrian98" "bactrian95" "NER" "real_06" "quant_06")
+settings=("cat" "cat_adaptive" "real" "real_06" "real_adaptive" "quant_cached" "quant_cached_adaptive" "quant_06_cached" "bactrian95")
+
+datasets=("Rightmyer_2013" "Ran_2018_dna" "Broughton_2013" "simulated" "Sauquet_2011" "Moyle_2016" "Dornburg_2012" "Kawahara_2013" "Cognato_2001")
+
+
+
+
+# Randomly shuffle the datasets
+#datasets_shuffled=( $(shuf -e "${datasets[@]}") )
+
+for d in ${datasets[@]} ; do
+    echo "$d"
+    cd $d
+
+    for e in */ ; do
+        echo "$e"
+        cd $e
+
+
+          # Randomly shuffle the settings
+          settings_shuffled=( $(shuf -e "${settings[@]}") )
+          for s in "${settings_shuffled[@]}"
+          do
+              
+             if [ ! -f "output_${s}.out" ]; then
+                echo "Beginning ../../../datasets/$d/$e/benchmark_${s}.xml"
+                echo "$1,$d,$s,$(date),start" >> ../../../progress.csv
+                ~/beast/bin/beast -overwrite -beagle_SSE ../../../datasets/$d/$e/benchmark_${s}.xml > "output_${s}.out" >> "error_${s}.err"
+                echo "$1,$d,$s,$(date),finish" >> ../../../progress.csv
+             fi
+          done
+
+          
+
+        cd ../
+    done
+
+
+    #sleep 1
+
+    cd ../
+
+
+    # Dummy job for ~5 min to give the other batches time to finish
+    #~/beast/bin/beast  -overwrite -beagle_SSE ../datasets/startdummy.xml
+
+done
+
+
+
+# Dummy job to ensure that the other jobs are not benefitting from free CPUs
+#~/beast/bin/beast  -overwrite -beagle_SSE ../datasets/endless_dummy.xml
+

### 2020-08-07 benchmarking/render.R

@@ -9,7 +9,7 @@ PER_CHAIN = TRUE
 
 #settings = c("cat", "real", "quant", "bactrian95", "bactrian98")
 settings = c("cat",  "real_06", "quant_06", "real", "quant", "bactrian95", "bactrian98", "NER", "AVMN")
-settings = c("cat",  "real_06", "real", "real_adaptive", "quant_06_cached", "quant_cached_adaptive", "quant_cached")
+settings = c("cat",  "real_06", "real", "real_adaptive", "quant_06_cached", "quant_cached_adaptive", "quant_cached", "bactrian95")
 
 benchmark = data.frame(batch = numeric(0), param = character(0), dataset = character(0), partition = numeric(0), setting = character(0), nstates = numeric(0), finalESS = numeric(0), finalMCD = numeric(0), done = logical(0),  error = logical(0))
 
@@ -30,7 +30,7 @@ settings.names["bactrian95"] = "Bactrian (\\textit{real})"
 settings.names["NER"] = "NER (\\textit{real})"
 
 
-latex.table = read.table("../../Benchmarking/latex.table", sep = "&")
+latex.table = read.table("../latex.table", sep = "&")
 colnames(latex.table) = c("ID", "N", "P", "L", "Leff", "ref")
 latex.table$ref = gsub(" ", "", gsub("[0-9].+", "", latex.table$ref))
 
@@ -384,7 +384,7 @@ plot.grid = function(filename, settings, grid.like = TRUE, main = "") {
 			lwd_base = 1.6
 			for (i in length(times):1){
 				t = times[i]
-				polygon(c(0.0001, xymax*10, xymax*10, 0.0001), c(0.0001*t, xymax*10*t, xymax*10/t, 0.0001/t), col = bg.cols[i], lwd =lwd_base * 0.8^i, border="black")
+				polygon(c(0.0001, xymax*10, xymax*10, 0.0001), c(0.0001*t, xymax*10*t, xymax*10/t, 0.0001/t), col = bg.cols[i], lwd =lwd_base * 0.6^i, border="black")
 			}
 
 
@@ -522,18 +522,19 @@ plot.grid = function(filename, settings, grid.like = TRUE, main = "") {
 
 
 
-plot.grid("ESS_real", c("real_06", "real", "real_adaptive"), TRUE, "Round 1")
[…]

### 2020-08-07 correlationsbimodal.R

@@ -1,0 +1,170 @@
+library(graphics)
+library(tikzDevice)
+library(shape)
+#library(plotly)
+
+set.seed(1234566)
+
+
+basewidth = 5
+baseheight = basewidth 
+filename = "bimodal.tex"
+options(tikzMetricPackages = c("\\usepackage[utf8]{inputenc}",
+    "\\usepackage[T1]{fontenc}", "\\usetikzlibrary{calc}",
+    "\\usepackage{amssymb}"))
+## I need the amssymb package because I use \mathcal and \mathbb
+	tikz(filename, width = basewidth*2, height = baseheight*1, standAlone = TRUE,
+    	packages = c("\\usepackage{tikz}",
+	         "\\usepackage[active,tightpage,psfixbb]{preview}",
+	         "\\PreviewEnvironment{pgfpicture}",
+	         "\\setlength\\PreviewBorder{0pt}",
+	         "\\usepackage{amssymb}"))
+
+
+
+par(mfrow = c(1,2))
+par(mar = c(5,5,5,5))
+par(cex.lab = 1.4)
+par(cex.main = 1.4)
+
+
+
+
+yule.rate = 1/5
+sigma = 0.2
+
+
+t.prior = function(t){
+	dexp(t, yule.rate, log = T)
+	#dlnorm(t, -0.5*sigma*sigma, sigma, log = T)
+}
+
+r.prior = function(r){
+	dlnorm(r/5, -0.5*sigma*sigma, sigma, log = T)
+}
+
+
+prior = function(rate, len){
+	t.prior(len) + r.prior(rate)
+}
+
+
+likelihood = function(seq1, seq2, rate, len){
+
+
+	d = len*rate
+
+	sum(log(ifelse(seq1 == seq2, 1/4 + 3/4*exp(-4*d/3), 1/4 - 1/4*exp(-4*d/3)))) 
+
+}
+
+xmax = 10
+mu = 1 * 4/3
+t = 0.1
+grid.len = 500
+dL = 20000
+x = seq(from = 0.01, to = xmax, length = grid.len)
+y = seq(from = 0.01, to = xmax, length = grid.len)
+
+for (L in c(80, 90)){
[…]

### 2020-08-07 S1_appendix.tex
well calibrated simulation studies

@@
 \usepackage[utf8]{inputenc}
+
+\usepackage[margin=1in]{geometry}
 
@@
 \begin{document}
+
+\vspace*{0.2in}
+
+% Title must be 250 characters or less.
+\begin{flushleft}
+{\Large
+\textbf\newline{Adaptive dating and fast proposals: revisiting the phylogenetic relaxed clock model} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
+}
+\newline
+% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
+\\
+Jordan Douglas\textsuperscript{1,2*},
+Rong Zhang\textsuperscript{1,2},
+Alexei J. Drummond\textsuperscript{1,2,3},
+Remco Bouckaert\textsuperscript{1,2}
+\\
+\bigskip
+\textbf{1} Centre for Computational Evolution,  University of Auckland, Auckland, New Zealand\\
+\textbf{2} School of Computer Science, University of Auckland, Auckland, New Zealand\\
+\textbf{3} School of Biological Sciences, University of Auckland, Auckland, New Zealand
+\\
+\bigskip
+
+% Use the asterisk to denote corresponding authorship and provide email address in note below.
+* jordan.douglas@auckland.ac.nz
+
+\end{flushleft}
 

### 2020-08-10 S2_appendix.tex
results update

--- 2020-01-23 S2_appendix.tex
@@
 
+\usepackage[margin=1in]{geometry}
 \usepackage{color,soul}
@@
 
+\vspace*{0.2in}
+
+% Title must be 250 characters or less.
+\begin{flushleft}
+{\Large
+\textbf\newline{Adaptive dating and fast proposals: revisiting the phylogenetic relaxed clock model} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
+}
+\newline
+% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
+\\
+Jordan Douglas\textsuperscript{1,2*},
+Rong Zhang\textsuperscript{1,2},
+Alexei J. Drummond\textsuperscript{1,2,3},
+Remco Bouckaert\textsuperscript{1,2}
+\\
+\bigskip
+\textbf{1} Centre for Computational Evolution,  University of Auckland, Auckland, New Zealand\\
+\textbf{2} School of Computer Science, University of Auckland, Auckland, New Zealand\\
+\textbf{3} School of Biological Sciences, University of Auckland, Auckland, New Zealand
+\\
+\bigskip
+
+% Use the asterisk to denote corresponding authorship and provide email address in note below.
+* jordan.douglas@auckland.ac.nz
+
+\end{flushleft}
+
 \section*{S2 Appendix: Well-calibrated simulation studies}
 
-Every method presented and tested in this paper was validated with a well-calibrated simulation study using the same model and operator set that which was benchmarked.
-This is achieved using 100 simulated datasets (each with $N=100$ taxa and a $L=5000$ nt alignment).
-The 95 \% highest posterior density (HPD) interval is calculated, and the `true' parameter values are compared with their values estimated from the simulated data.
+The methods presented and benchmarked in this paper were validated with well-calibrated simulation studies using the same model and operator scheme that was benchmarked. 
+This was achieved using 100 simulated datasets (each with $N=30$ taxa and a $L=2000$ nt alignment).
+The 95\% highest posterior density (HPD) intervals of each parameter during MCMC were calculated, and these intervals were compared with the `true' parameter values which the data was simulated under.
 
-The validation results are presented as plots.
-The number in the bottom right corner of each plot is the coverage; that is the percentage of simulations where the `true' parameter value is within the 95 \% HPD interval.
-If all parameters have coverage close to 95 \% coverage, then this suggests correctness of implementation.
+The validation results are presented as plots (below). 
+In each plot, blue and red vertical lines are 95\% HPD intervals, where blue intervals contain the true value and red intervals do not.
+The number in the bottom right corner of each plot is the coverage; that is the percentage of simulations where the `true' parameter value is within the 95\% HPD interval. 
+If all parameters have coverage close to 95\%, then this suggests correctness of both methodology and implementation.
 
-The parameters presented in each plot are: the Yule model birth rate $\lambda$, rate heterogeneity gamma shape $\Gamma$, HKY substitution model parameter $\kappa$, log-normal clock standard deviation $\sigma$, the frequency of the A nucleotide $f_A$, and the rate of the first taxon $r_1$.
-The remaining 3 frequencies and 99 taxa rates are omitted from the figures.
+Overall, these experiments suggest that the operators presented in the main paper were correctly implemented.
 
 \begin{figure}[!htb]
-\includegraphics[width=0.85\textwidth]{Figures/CalSim_cat.pdf}
-\caption{\textbf{The \textit{cat} parameterisation.} Blue and red vertical lines are 95 \% HPD intervals, where blue intervals contain the true value and red intervals do not.}
-\label{fig:rateparams}
+\includegraphics[width=\textwidth]{Figures/N30_cat_adaptive.pdf}
+\caption{\textbf{The adapt (\textit{cat}) configuration.} }
 \end{figure}
@@
 \begin{figure}[!htb]
-\includegraphics[width=0.85\textwidth]{Figures/CalSim_real.pdf}
-\caption{\textbf{The \textit{real} parameterisation,} with the operators decribed by Zhang and Drummond 2020.}
-\label{fig:rateparams}
+\includegraphics[width=\textwidth]{Figures/N30_real_adaptive.pdf}
+\caption{\textbf{The adapt (\textit{real}) configuration.} }
 \end{figure}
@@
 \begin{figure}[!htb]
-\includegraphics[width=0.85\textwidth]{Figures/CalSim_quant.pdf}
-\caption{\textbf{The \textit{quant} parameterisation,} with the operators decribed by Zhang and Drummond 2020, and adapted for \textit{quant} as described in \textbf{S1 Appendix}.}
-\label{fig:rateparams}
+\includegraphics[width=\textwidth]{Figures/N30_quant_cached_adaptive.pdf}
+\caption{\textbf{The adapt (\textit{quant}) configuration.} The constant distance operators were extended from \emph{real} to \emph{quant} as described in \textbf{S1 Appendix}.}
 \end{figure}
 
-\bibliography{references}
+\begin{figure}[!htb]
+%\includegraphics[width=\textwidth]{Figures/CalSim_NER_real.pdf}
+\caption{\textbf{The Narrow Exchange Rate operators under the \textit{real} parameterisation.} The 48 NER and 48 NERw operators, including \texttt{NarrowExchange}, are tested in the same MCMC session.}
+\end{figure}
+
+\begin{figure}[!htb]
+%\includegraphics[width=\textwidth]{Figures/CalSim_NER_quant.pdf}
+\caption{\textbf{The \texttt{LeafAVMVN} configuration.} The adaptive NER operator, Bactrian proposals, and the \emph{real} configuration are included.}
+\end{figure}
+
+%\bibliography{references}
 

### 2020-08-10 S3_appendix.tex
results update

--- 2020-08-10 S2_appendix.tex
@@
 
-\section*{S2 Appendix: Well-calibrated simulation studies}
-
-The methods presented and benchmarked in this paper were validated with well-calibrated simulation studies using the same model and operator scheme that was benchmarked. 
-This was achieved using 100 simulated datasets (each with $N=30$ taxa and a $L=2000$ nt alignment).
-The 95\% highest posterior density (HPD) intervals of each parameter during MCMC were calculated, and these intervals were compared with the `true' parameter values which the data was simulated under.
-
-The validation results are presented as plots (below). 
-In each plot, blue and red vertical lines are 95\% HPD intervals, where blue intervals contain the true value and red intervals do not.
-The number in the bottom right corner of each plot is the coverage; that is the percentage of simulations where the `true' parameter value is within the 95\% HPD interval. 
-If all parameters have coverage close to 95\%, then this suggests correctness of both methodology and implementation.
-
-Overall, these experiments suggest that the operators presented in the main paper were correctly implemented.
+\section*{S3 Appendix: Supplementary results}
 
 \begin{figure}[!htb]
-\includegraphics[width=\textwidth]{Figures/N30_cat_adaptive.pdf}
-\caption{\textbf{The adapt (\textit{cat}) configuration.} }
-\end{figure}
-
-\begin{figure}[!htb]
-\includegraphics[width=\textwidth]{Figures/N30_real_adaptive.pdf}
-\caption{\textbf{The adapt (\textit{real}) configuration.} }
-\end{figure}
-
-\begin{figure}[!htb]
-\includegraphics[width=\textwidth]{Figures/N30_quant_cached_adaptive.pdf}
-\caption{\textbf{The adapt (\textit{quant}) configuration.} The constant distance operators were extended from \emph{real} to \emph{quant} as described in \textbf{S1 Appendix}.}
-\end{figure}
-
-\begin{figure}[!htb]
-%\includegraphics[width=\textwidth]{Figures/CalSim_NER_real.pdf}
-\caption{\textbf{The Narrow Exchange Rate operators under the \textit{real} parameterisation.} The 48 NER and 48 NERw operators, including \texttt{NarrowExchange}, are tested in the same MCMC session.}
-\end{figure}
-
-\begin{figure}[!htb]
-%\includegraphics[width=\textwidth]{Figures/CalSim_NER_quant.pdf}
-\caption{\textbf{The \texttt{LeafAVMVN} configuration.} The adaptive NER operator, Bactrian proposals, and the \emph{real} configuration are included.}
+\includegraphics[width=\textwidth]{benchmarking/benchmarkingVM/ESS_round1_catquant.pdf}
+\caption{\textbf{Round 1: Performance evaluation of \texttt{AdaptiveOperatorSampler} under the \emph{quant} and \emph{cat} parameterisations.}
+These results show that neither \emph{cat} nor \emph{quant} benefit strongly from adaptive weight sampling.
+The constant distance operators (cons) greatly improves the \emph{quant} parameterisation for most datasets, as expected.
+}
 \end{figure}

### 2020-08-10 benchmarking/benchmarkingVM/ESS_round1_catquant.tex
results update

% Created by tikzDevice version 0.12.3 on 2020-08-10 13:51:28
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (578.16,578.16);
\begin{scope}
\path[clip] (  0.00,289.08) rectangle (289.08,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,548.96) {\bfseries cons (\textit{quant}) vs. nocons (\textit{quant})};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,301.03) {ESS/hr [nocons (\textit{quant})]};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,433.62) {ESS/hr [cons (\textit{quant})]};
\end{scope}
\begin{scope}
\path[clip] ( 49.80,338.88) rectangle (239.28,528.36);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,374.64) --
	(203.52,578.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (286.65,578.16) --
	(286.65,490.17) --
	(  0.00,203.52);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (  0.00,346.12) --
	(232.04,578.16);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (286.65,578.16) --
	(286.65,518.69) --
	(  0.00,232.04);

\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (  0.00,317.60) --
	(260.56,578.16);

\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (286.65,578.16) --
	(286.65,547.21) --
	(  0.00,260.56);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (142.89,342.31) {$\frac{1}{64} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,435.87) {$64\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (114.37,342.31) {$\frac{1}{16} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,407.35) {$16\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 84.20,342.31) {$\frac{1}{4} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92,378.83) {$4\times$};

\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,528.36);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 94.65,416.78) --
	(103.65,416.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.64,409.37) --
	( 99.64,422.22);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 99.64,413.56) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.25,476.46) --
	(190.95,476.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.73,475.74) --
	(188.73,477.16);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.73,472.43) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.21,474.21) --
	(104.27,474.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (102.34,473.61) --
	(102.34,474.79);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (102.34,470.18) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.11,416.10) --
	(103.73,416.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.87,410.35) --
	( 99.87,420.59);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 99.87,412.07) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.40,387.89) --
	(115.90,387.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (106.65,384.62) --
	(106.65,390.72);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (106.65,384.99) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.54,483.66) --
	(195.01,483.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.29,483.25) --
	(194.29,484.06);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.29,480.76) {$\kappa$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.24,453.03) --
	(151.45,453.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.58,451.65) --
	(148.58,454.32);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (148.58,449.80) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.12,479.26) --
	(197.83,479.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.99,477.50) --
	(196.99,480.89);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.99,475.23) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.36,483.73) --
	(188.58,483.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.98,483.50) --
	(187.98,483.96);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.98,479.70) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.83,449.81) --
	(142.53,449.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.76,448.18) --
	(140.76,451.31);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (140.76,445.77) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.30,448.54) --
	(152.66,448.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (149.31,447.26) --
	(149.31,449.74);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (149.31,445.63) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.59,488.02) --
	(199.40,488.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (199.00,487.58) --
	(199.00,488.46);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.00,485.12) {$\kappa$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.84,422.09) --
	(126.52,422.09);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (122.64,409.09) --
	(122.64,429.99);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (122.64,418.86) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.62,458.97) --
	(195.24,458.97);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.51,454.93) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.66,477.15) --
	(163.23,477.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.95,476.14) --
	(162.95,478.11);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (162.95,473.11) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.91,421.56) --
	(120.70,421.56);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.17,406.76) --
	(117.17,430.08);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (117.17,417.53) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (124.20,409.98) --
	(134.18,409.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.79,405.95) --
	(129.79,413.35);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (129.79,407.07) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.21,485.10) --
	(197.03,485.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.62,484.28) --
	(196.62,485.89);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.62,482.19) {$\kappa$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.77,432.05) --
	(140.26,432.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (135.68,429.18) --
	(135.68,434.57);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (135.68,428.82) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.99,483.34) --
	(200.70,483.34);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (199.86,480.63) --
	(199.86,485.72);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.86,479.30) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.36,482.25) --
	(177.58,482.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.47,482.07) --
	(177.47,482.44);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.47,478.22) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (133.12,451.72) --
	(147.88,451.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (141.79,449.82) --
	(141.79,453.46);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (141.79,447.69) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (136.74,437.84) --
	(147.60,437.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (142.88,434.82) --
	(142.88,440.47);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (142.88,434.94) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.27,487.58) --
	(198.98,487.58);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.14,487.05) --
	(198.14,488.10);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.14,484.68) {$\kappa$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.42,460.68) --
	(181.15,460.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.37,456.94) --
	(179.37,463.84);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.37,457.45) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.94,486.46) --
	(184.37,486.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.33,482.75) --
	(176.33,489.60);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.33,482.42) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.15,482.18) --
	(197.23,482.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.69,481.57) --
	(196.69,482.78);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.69,478.15) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.45,441.52) --
	(161.00,441.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (157.57,436.94) --
	(157.57,445.26);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (157.57,437.48) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.01,463.73) --
	(184.30,463.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.82,459.32) --
	(181.82,467.36);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.82,460.82) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.90,498.16) --
	(211.56,498.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.27,495.77) --
	(210.27,500.30);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.27,495.25) {$\kappa$};
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.64,472.51) --
	(197.79,472.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.95,470.68) --
	(194.95,474.19);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.95,469.28) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.60,491.62) --
	(178.99,491.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.91,490.07) --
	(176.91,493.06);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.91,487.58) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.25,482.68) --
	(197.61,482.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.43,482.27) --
	(197.43,483.09);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.43,478.65) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.17,459.25) --
	(178.40,459.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.85,457.81) --
	(176.85,460.59);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.85,455.21) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.79,467.29) --
	(192.74,467.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.37,464.24) --
	(185.37,469.95);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.37,464.39) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.72,501.36) --
	(212.84,501.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.78,500.78) --
	(212.78,501.94);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.78,498.46) {$\kappa$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,338.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,338.88) -- ( 49.80,333.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 97.17,338.88) -- ( 97.17,333.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (144.54,338.88) -- (144.54,333.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.91,338.88) -- (191.91,333.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.28,338.88) -- (239.28,333.90);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 49.80,320.95) {1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 97.17,320.95) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (144.54,320.95) {100};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (191.91,320.95) {1000};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (239.28,320.95) {10000};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,338.88) -- ( 49.80,528.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,338.88) -- ( 44.82,338.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,386.25) -- ( 44.82,386.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,433.62) -- ( 44.82,433.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,480.99) -- ( 44.82,480.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,528.36) -- ( 44.82,528.36);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,336.02) {1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,383.39) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,430.76) {100};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,478.13) {1000};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,525.50) {10000};
\end{scope}
\begin{scope}
\path[clip] ( 49.80,338.88) rectangle (239.28,528.36);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,431.01) rectangle (189.67,426.03);
\definecolor{fillColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,421.05) rectangle (189.67,416.07);
\definecolor{fillColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,411.09) rectangle (189.67,406.11);
\definecolor{fillColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,401.13) rectangle (189.67,396.15);
\definecolor{fillColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,391.17) rectangle (189.67,386.19);
\definecolor{fillColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,381.21) rectangle (189.67,376.23);
\definecolor{fillColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,371.25) rectangle (189.67,366.27);
\definecolor{fillColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,361.29) rectangle (189.67,356.31);
\definecolor{fillColor}{RGB}{68,68,68}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,351.33) rectangle (189.67,346.35);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,425.66) {Ran};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,415.70) {Cognato};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,405.74) {Dornburg};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,395.78) {Sauquet};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,385.82) {Broughton};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,375.86) {Kawahara};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,365.90) {simulated};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,355.94) {Rightmyer};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,345.98) {Moyle};
\end{scope}
\begin{scope}
\path[clip] (289.08,289.08) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,548.96) {\bfseries adapt (\textit{quant}) vs. nocons (\textit{quant})};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,301.03) {ESS/hr [nocons (\textit{quant})]};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (307.01,433.62) {ESS/hr [adapt (\textit{quant})]};
\end{scope}
\begin{scope}
\path[clip] (338.88,338.88) rectangle (528.36,528.36);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (149.40,234.96) --
	(492.60,578.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (575.73,578.16) --
	(575.73,490.17) --
	(149.40, 63.84) --
	(149.40,234.96);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (149.40,206.44) --
	(521.12,578.16);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (575.73,578.16) --
	(575.73,518.69) --
	(149.40, 92.36) --
	(149.40,206.44);

\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (149.40,177.92) --
	(549.64,578.16);

\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (575.73,578.16) --
	(575.73,547.21) --
	(149.40,120.88) --
	(149.40,177.92);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (431.97,342.31) {$\frac{1}{64} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,435.87) {$64\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (403.45,342.31) {$\frac{1}{16} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,407.35) {$16\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (373.28,342.31) {$\frac{1}{4} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.00,378.83) {$4\times$};

\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (338.88,338.88) -- (528.36,528.36);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (383.73,398.02) --
	(392.73,398.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (388.72,382.13) --
	(388.72,406.87);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (388.72,394.79) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (475.33,475.91) --
	(480.03,475.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.81,475.07) --
	(477.81,476.72);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (477.81,471.88) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.29,472.93) --
	(393.35,472.93);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (391.42,468.95) --
	(391.42,476.26);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (391.42,468.89) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (384.19,397.74) --
	(392.81,397.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (388.95,377.39) --
	(388.95,407.77);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (388.95,393.71) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (378.48,366.19) --
	(404.98,366.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (395.73,357.18) --
	(395.73,372.44);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (395.73,363.29) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.62,483.32) --
	(484.09,483.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.37,483.08) --
	(483.37,483.56);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.37,480.42) {$\kappa$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (434.32,451.80) --
	(440.53,451.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (437.66,446.77) --
	(437.66,455.84);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (437.66,448.57) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.20,479.84) --
	(486.91,479.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.07,478.07) --
	(486.07,481.48);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (486.07,475.81) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.44,483.86) --
	(477.66,483.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.06,481.92) --
	(477.06,485.64);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (477.06,479.83) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.91,449.16) --
	(431.61,449.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (429.84,442.38) --
	(429.84,454.24);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (429.84,445.12) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (434.38,448.12) --
	(441.74,448.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.39,445.55) --
	(438.39,450.42);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (438.39,445.22) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (487.67,488.03) --
	(488.48,488.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (488.08,487.64) --
	(488.08,488.41);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (488.08,485.12) {$\kappa$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (406.92,424.00) --
	(415.60,424.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (411.72,420.41) --
	(411.72,427.05);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (411.72,420.77) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (480.70,478.83) --
	(484.32,478.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.59,474.57) --
	(482.59,482.36);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (482.59,474.80) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (451.74,476.83) --
	(452.31,476.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (452.03,476.28) --
	(452.03,477.36);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (452.03,472.79) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (401.99,423.32) --
	(409.78,423.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (406.25,420.99) --
	(406.25,425.41);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (406.25,419.28) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (413.28,406.71) --
	(423.26,406.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.87,404.60) --
	(418.87,408.64);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (418.87,403.81) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.29,485.22) --
	(486.11,485.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.70,485.09) --
	(485.70,485.35);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (485.70,482.32) {$\kappa$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.85,435.95) --
	(429.34,435.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (424.76,433.40) --
	(424.76,438.22);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (424.76,432.72) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (488.07,482.85) --
	(489.78,482.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (488.94,480.61) --
	(488.94,484.87);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (488.94,478.82) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (466.44,482.85) --
	(466.66,482.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (466.55,482.61) --
	(466.55,483.09);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (466.55,478.82) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (422.20,450.41) --
	(436.96,450.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (430.87,447.63) --
	(430.87,452.86);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (430.87,446.38) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (425.82,440.09) --
	(436.68,440.09);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (431.96,437.76) --
	(431.96,442.18);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (431.96,437.18) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.35,487.61) --
	(488.06,487.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (487.22,485.91) --
	(487.22,489.18);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (487.22,484.71) {$\kappa$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (466.50,469.66) --
	(470.23,469.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (468.45,467.06) --
	(468.45,471.96);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.45,466.43) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (452.02,481.52) --
	(473.45,481.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (465.41,478.07) --
	(465.41,484.47);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (465.41,477.48) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.23,487.79) --
	(486.31,487.79);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.77,487.17) --
	(485.77,488.40);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (485.77,483.76) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (442.53,448.83) --
	(450.08,448.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (446.65,445.54) --
	(446.65,451.66);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (446.65,444.80) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (468.09,470.37) --
	(473.38,470.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (470.90,468.48) --
	(470.90,472.10);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (470.90,467.47) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (497.98,499.91) --
	(500.64,499.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.35,499.32) --
	(499.35,500.49);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (499.35,497.01) {$\kappa$};
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (480.72,484.41) --
	(486.87,484.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (484.03,482.75) --
	(484.03,485.95);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (484.03,481.19) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.68,490.90) --
	(468.07,490.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (465.99,490.73) --
	(465.99,491.06);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (465.99,486.86) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.33,489.03) --
	(486.69,489.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.51,487.83) --
	(486.51,490.17);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (486.51,485.00) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.25,467.22) --
	(467.48,467.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (465.93,462.61) --
	(465.93,470.98);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (465.93,463.19) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.87,475.23) --
	(481.82,475.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.45,471.25) --
	(474.45,478.57);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.45,472.33) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (501.80,501.33) --
	(501.92,501.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (501.86,500.87) --
	(501.86,501.77);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (501.86,498.42) {$\kappa$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,338.88) -- (528.36,338.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,338.88) -- (338.88,333.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (386.25,338.88) -- (386.25,333.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.62,338.88) -- (433.62,333.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (480.99,338.88) -- (480.99,333.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (528.36,338.88) -- (528.36,333.90);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (338.88,320.95) {1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (386.25,320.95) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (433.62,320.95) {100};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (480.99,320.95) {1000};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (528.36,320.95) {10000};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,338.88) -- (338.88,528.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,338.88) -- (333.90,338.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,386.25) -- (333.90,386.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,433.62) -- (333.90,433.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,480.99) -- (333.90,480.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,528.36) -- (333.90,528.36);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,336.02) {1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,383.39) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,430.76) {100};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,478.13) {1000};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,525.50) {10000};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,259.88) {\bfseries adapt (\textit{quant}) vs. cons (\textit{quant})};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54, 11.95) {ESS/hr [cons (\textit{quant})]};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,144.54) {ESS/hr [adapt (\textit{quant})]};
\end{scope}
\begin{scope}
\path[clip] ( 49.80, 49.80) rectangle (239.28,239.28);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00, 85.56) --
	(286.65,372.21) --
	(286.65,201.09) --
	( 85.56,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (  0.00, 57.04) --
	(286.65,343.69) --
	(286.65,229.61) --
	( 57.04,  0.00);

\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (  0.00, 28.52) --
	(286.65,315.17) --
	(286.65,258.13) --
	( 28.52,  0.00);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (142.89, 53.23) {$\frac{1}{64} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,146.79) {$64\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (114.37, 53.23) {$\frac{1}{16} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,118.27) {$16\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 84.20, 53.23) {$\frac{1}{4} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92, 89.75) {$4\times$};

\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] ( 49.80, 49.80) -- (239.28,239.28);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.29,108.94) --
	(133.14,108.94);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (127.70, 93.05) --
	(127.70,117.79);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (127.70,105.71) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.66,186.83) --
	(188.08,186.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.38,185.99) --
	(187.38,187.64);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.38,182.80) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.53,183.85) --
	(185.71,183.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.13,179.87) --
	(185.13,187.18);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.13,179.81) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.27,108.66) --
	(131.51,108.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (127.02, 88.31) --
	(127.02,118.69);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (127.02,104.63) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.54, 77.11) --
	(101.64, 77.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 98.81, 68.10) --
	( 98.81, 83.36);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 98.81, 74.21) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.17,194.24) --
	(194.98,194.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.58,194.00) --
	(194.58,194.48);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.58,191.34) {$\kappa$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.57,162.72) --
	(165.24,162.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.95,157.69) --
	(163.95,166.76);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (163.95,159.49) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.42,190.76) --
	(191.81,190.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.18,188.99) --
	(190.18,192.40);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.18,186.73) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.42,194.78) --
	(194.88,194.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.65,192.84) --
	(194.65,196.56);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.65,190.75) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.10,160.08) --
	(162.23,160.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.73,153.30) --
	(160.73,165.16);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (160.73,156.04) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.18,159.04) --
	(160.66,159.04);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.46,156.47) --
	(159.46,161.34);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (159.46,156.14) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.50,198.95) --
	(199.38,198.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.94,198.56) --
	(198.94,199.33);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.94,196.04) {$\kappa$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.01,134.92) --
	(140.91,134.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (133.01,131.33) --
	(133.01,137.97);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (133.01,131.69) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.89,185.49) --
	(169.89,193.28);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.89,185.72) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.06,187.75) --
	(189.03,187.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.07,187.20) --
	(188.07,188.28);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.07,183.71) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.68,134.24) --
	(141.00,134.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (132.48,131.91) --
	(132.48,136.33);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (132.48,130.20) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (116.87,117.63) --
	(124.27,117.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.90,115.52) --
	(120.90,119.56);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (120.90,114.73) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.20,196.14) --
	(196.81,196.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.02,196.01) --
	(196.02,196.27);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.02,193.24) {$\kappa$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.10,146.87) --
	(145.49,146.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (142.97,144.32) --
	(142.97,149.14);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (142.97,143.64) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.55,193.77) --
	(196.64,193.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.26,191.53) --
	(194.26,195.79);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.26,189.74) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.99,193.77) --
	(193.36,193.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.17,193.53) --
	(193.17,194.01);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.17,189.74) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.74,161.33) --
	(164.38,161.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.64,158.55) --
	(162.64,163.78);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (162.64,157.30) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.74,151.01) --
	(151.39,151.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.76,148.68) --
	(148.76,153.10);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (148.76,148.10) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.97,198.53) --
	(199.02,198.53);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.50,196.83) --
	(198.50,200.10);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.50,195.63) {$\kappa$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (167.86,180.58) --
	(174.76,180.58);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.60,177.98) --
	(171.60,182.88);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.60,177.35) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.67,192.44) --
	(200.52,192.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.38,188.99) --
	(197.38,195.39);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.38,188.40) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.49,198.71) --
	(193.70,198.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.10,198.09) --
	(193.10,199.32);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.10,194.68) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (147.86,159.75) --
	(156.18,159.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (152.44,156.46) --
	(152.44,162.58);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (152.44,155.72) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (170.24,181.29) --
	(178.28,181.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.65,179.40) --
	(174.65,183.02);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.65,178.39) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.69,210.83) --
	(211.22,210.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.08,210.24) --
	(209.08,211.41);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.08,207.93) {$\kappa$};
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.60,195.33) --
	(185.11,195.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (183.43,193.67) --
	(183.43,196.87);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.43,192.11) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.99,201.82) --
	(203.98,201.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (202.54,201.65) --
	(202.54,201.98);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.54,197.78) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.19,199.95) --
	(194.01,199.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.60,198.75) --
	(193.60,201.09);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.60,195.92) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.73,178.14) --
	(171.51,178.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (170.17,173.53) --
	(170.17,181.90);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (170.17,174.11) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.16,186.15) --
	(180.87,186.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (178.21,182.17) --
	(178.21,189.49);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (178.21,183.25) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.70,212.25) --
	(212.86,212.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.28,211.79) --
	(212.28,212.69);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.28,209.34) {$\kappa$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 49.80) -- (239.28, 49.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 49.80) -- ( 49.80, 44.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 97.17, 49.80) -- ( 97.17, 44.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (144.54, 49.80) -- (144.54, 44.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.91, 49.80) -- (191.91, 44.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.28, 49.80) -- (239.28, 44.82);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 49.80, 31.87) {1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 97.17, 31.87) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (144.54, 31.87) {100};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (191.91, 31.87) {1000};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (239.28, 31.87) {10000};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 49.80) -- ( 49.80,239.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 49.80) -- ( 44.82, 49.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 97.17) -- ( 44.82, 97.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,144.54) -- ( 44.82,144.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,191.91) -- ( 44.82,191.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,239.28) -- ( 44.82,239.28);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84, 46.94) {1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84, 94.31) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,141.68) {100};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,189.05) {1000};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,236.42) {10000};
\end{scope}
\begin{scope}
\path[clip] (289.08,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,259.88) {\bfseries adapt (\textit{cat}) vs. \textit{cat}};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62, 11.95) {ESS/hr [\textit{cat}]};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (307.01,144.54) {ESS/hr [adapt (\textit{cat})]};
\end{scope}
\begin{scope}
\path[clip] (338.88, 49.80) rectangle (528.36,239.28);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.52,  0.00) --
	(575.73,372.21) --
	(575.73,201.09) --
	(374.64,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (232.04,  0.00) --
	(575.73,343.69) --
	(575.73,229.61) --
	(346.12,  0.00);

\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (260.56,  0.00) --
	(575.73,315.17) --
	(575.73,258.13) --
	(317.60,  0.00);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (431.97, 53.23) {$\frac{1}{64} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,146.79) {$64\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (403.45, 53.23) {$\frac{1}{16} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,118.27) {$16\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (373.28, 53.23) {$\frac{1}{4} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.00, 89.75) {$4\times$};

\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (338.88, 49.80) -- (528.36,239.28);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (369.53,100.95) --
	(401.69,100.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (391.34, 96.83) --
	(391.34,104.39);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (391.34, 97.73) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (469.11,180.21) --
	(478.54,180.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.36,157.25) --
	(474.36,190.79);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.36,176.18) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (378.71, 99.41) --
	(392.60, 99.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (386.80, 95.00) --
	(386.80,103.04);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (386.80, 95.37) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (379.87,102.83) --
	(403.10,102.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (394.60,100.19) --
	(394.60,105.17);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (394.60, 98.80) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (373.83, 90.46) --
	(386.33, 90.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (381.02, 83.73) --
	(381.02, 95.52);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (381.02, 87.56) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.33,194.78) --
	(484.25,194.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.79,194.57) --
	(483.79,194.99);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.79,191.87) {$\kappa$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (403.60,109.49) --
	(412.89,109.49);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (408.76, 99.61) --
	(408.76,116.13);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (408.76,106.26) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.33,191.83) --
	(481.58,191.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.56,190.07) --
	(479.56,193.44);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (479.56,187.79) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (448.80,164.69) --
	(449.61,164.69);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (449.21,164.54) --
	(449.21,164.84);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (449.21,160.65) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (402.13,107.26) --
	(410.13,107.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (406.52,100.97) --
	(406.52,112.07);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (406.52,103.23) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (394.71,110.51) --
	(411.65,110.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (404.88,103.25) --
	(404.88,115.87);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (404.88,107.61) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.25,196.27) --
	(485.92,196.27);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.59,196.12) --
	(485.59,196.43);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (485.59,193.37) {$\kappa$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.30,177.43) --
	(465.23,177.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (460.48,172.15) --
	(460.48,181.63);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (460.48,174.20) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.33,174.98) --
	(474.75,174.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.90,158.21) --
	(461.90,184.09);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (461.90,170.94) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (480.68,197.38) --
	(482.70,197.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (481.71,196.98) --
	(481.71,197.78);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (481.71,193.35) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (436.28,158.71) --
	(449.09,158.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.66,150.24) --
	(443.66,164.70);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (443.66,154.68) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.65,180.86) --
	(466.79,180.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (465.75,178.58) --
	(465.75,182.90);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (465.75,177.95) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.10,210.49) --
	(500.73,210.49);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.93,208.48) --
	(499.93,212.33);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (499.93,207.59) {$\kappa$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 49.80) -- (528.36, 49.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 49.80) -- (338.88, 44.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (386.25, 49.80) -- (386.25, 44.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.62, 49.80) -- (433.62, 44.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (480.99, 49.80) -- (480.99, 44.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (528.36, 49.80) -- (528.36, 44.82);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (338.88, 31.87) {1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (386.25, 31.87) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (433.62, 31.87) {100};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (480.99, 31.87) {1000};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (528.36, 31.87) {10000};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 49.80) -- (338.88,239.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 49.80) -- (333.90, 49.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 97.17) -- (333.90, 97.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,144.54) -- (333.90,144.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,191.91) -- (333.90,191.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,239.28) -- (333.90,239.28);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92, 46.94) {1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92, 94.31) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,141.68) {100};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,189.05) {1000};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,236.42) {10000};
\end{scope}
\end{tikzpicture}

\end{document}

### 2020-08-10 benchmarking/benchmarkingVM/ESS_round1_real.tex
results update

@@
-% Created by tikzDevice version 0.12.3 on 2020-08-07 14:28:24
+% Created by tikzDevice version 0.12.3 on 2020-08-10 16:04:15
 % !TEX encoding = UTF-8 Unicode
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,548.96) {\bfseries Comparison of cons (\textit{real}) and nocons (\textit{real})};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,301.03) {ESS/chain [nocons (\textit{real})]};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,433.62) {ESS/chain [cons (\textit{real})]};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,548.96) {\bfseries cons (\textit{real}) vs. nocons (\textit{real})};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,301.03) {ESS/hr [nocons (\textit{real})]};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,433.62) {ESS/hr [cons (\textit{real})]};
 \end{scope}
@@
 \definecolor{drawColor}{RGB}{0,0,0}
-\definecolor{fillColor}{gray}{0.91}
-
-\path[draw=drawColor,line width= 0.1pt,line join=round,line cap=round,fill=fillColor] (  0.00,365.38) --
-	(212.78,578.16) --
-	(281.53,578.16) --
-	(281.53,494.30) --
-	(  0.00,212.78) --
-	cycle;
-\definecolor{fillColor}{RGB}{190,190,190}
-
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] (  0.00,339.95) --
-	(238.21,578.16) --
-	(281.53,578.16) --
-	(281.53,519.74) --
-	(  0.00,238.21) --
-	cycle;
-\definecolor{fillColor}{RGB}{169,169,169}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (  0.00,314.51) --
-	(263.65,578.16) --
-	(281.53,578.16) --
-	(281.53,545.17) --
-	(  0.00,263.65) --
-	cycle;
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (133.64,342.31) {$\frac{1}{64} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,426.62) {$64\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (108.20,342.31) {$\frac{1}{16} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,401.18) {$16\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 81.11,342.31) {$\frac{1}{4} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92,375.75) {$4\times$};
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,528.36);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.14,457.67) --
-	(163.00,457.67);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.72,454.14) --
-	(158.72,460.63);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.72,454.44) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.97,498.27) --
-	(218.78,498.27);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.83,495.92) --
-	(212.83,500.36);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.83,494.24) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (178.45,498.59) --
-	(180.15,498.59);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.32,497.51) --
-	(179.32,499.62);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.32,494.56) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (146.49,453.46) --
-	(152.86,453.46);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (149.95,449.76) --
-	(149.95,456.55);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (149.95,449.43) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (156.64,437.17) --
-	(165.01,437.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.30,434.91) --
-	(161.30,439.18);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (161.30,434.26) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.32,508.76) --
-	(221.15,508.76);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.74,507.98) --
-	(220.74,509.51);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.74,505.85) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.30,494.32) --
-	(194.81,494.32);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.60,491.54) --
-	(193.60,496.74);
-\definecolor{drawColor}{RGB}{0,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.60,491.10) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (205.85,498.07) --
-	(214.19,498.07);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.49,494.17) --
-	(210.49,501.29);
-\definecolor{drawColor}{RGB}{0,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.49,494.04) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.48,503.25) --
-	(210.75,503.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.13,501.60) --
-	(210.13,504.76);
-\definecolor{drawColor}{RGB}{0,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.13,499.21) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.18,482.71) --
-	(198.08,482.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.79,479.66) --
-	(195.79,485.33);
-\definecolor{drawColor}{RGB}{0,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.79,478.68) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.48,485.22) --
-	(198.60,485.22);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.57,481.89) --
-	(197.57,488.04);
-\definecolor{drawColor}{RGB}{0,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.57,482.32) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.10,512.25) --
-	(223.18,512.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.65,510.74) --
-	(222.65,513.65);
-\definecolor{drawColor}{RGB}{0,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (222.65,509.35) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.17,469.31) --
-	(197.17,474.08);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.17,468.62) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (214.45,504.24) --
-	(220.93,504.24);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.97,503.56) --
-	(217.97,504.90);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (217.97,500.21) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.42,505.36) --
-	(222.61,505.36);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (216.85,505.09) --
-	(216.85,505.62);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (216.85,501.33) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.48,442.96) --
-	(169.48,453.47);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.48,444.93) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.56,462.82) --
-	(196.56,467.56);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.56,462.44) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.70,512.26) --
-	(223.15,512.26);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.93,512.04) --
-	(222.93,512.48);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (222.93,509.36) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.68,478.88) --
-	(192.68,485.07);
-\definecolor{drawColor}{RGB}{255,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.68,479.01) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.72,496.18) --
-	(218.04,496.18);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (205.74,494.03) --
-	(205.74,498.10);
-\definecolor{drawColor}{RGB}{255,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.74,492.14) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.70,503.25) --
-	(229.53,503.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (224.55,502.95) --
-	(224.55,503.55);
-\definecolor{drawColor}{RGB}{255,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (224.55,499.22) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.85,475.04) --
-	(211.32,475.04);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.84,472.97) --
-	(200.84,476.90);
-\definecolor{drawColor}{RGB}{255,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (200.84,471.00) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.62,480.49) --
-	(206.62,483.96);
-\definecolor{drawColor}{RGB}{255,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (206.62,479.40) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.33,511.89) --
-	(223.37,511.89);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.86,511.27) --
-	(222.86,512.49);
-\definecolor{drawColor}{RGB}{255,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (222.86,508.99) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.91,482.52) --
-	(221.91,491.18);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (221.91,484.13) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (202.65,482.61) --
-	(202.65,488.22);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.65,481.59) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (199.21,500.97) --
-	(230.61,500.97);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.94,500.31) --
-	(220.94,501.61);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.94,496.94) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.32,486.64) --
-	(193.67,486.64);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.26,482.99) --
-	(185.26,489.69);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.26,482.61) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (207.68,479.70) --
-	(207.68,488.91);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.68,481.98) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (119.95,439.54) --
-	(137.90,439.54);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (131.04,432.27) --
-	(131.04,444.73);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (131.04,436.31) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.56,498.07) --
-	(210.93,498.07);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.02,496.36) --
-	(208.02,499.62);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (208.02,494.03) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (125.81,497.45) --
-	(135.01,497.45);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (130.98,494.97) --
-	(130.98,499.64);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (130.98,493.42) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (119.66,452.88) --
-	(130.48,452.88);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (125.86,445.61) --
-	(125.86,458.08);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (125.86,448.85) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (119.40,419.55) --
-	(144.64,419.55);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (136.05,411.70) --
-	(136.05,425.03);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (136.05,416.65) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.17,512.87) --
-	(223.63,512.87);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.40,512.58) --
-	(223.40,513.16);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (223.40,509.97) {$\mu$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (165.32,492.59) --
-	(187.22,492.59);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.36,490.80) --
-	(179.36,494.22);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.36,489.37) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.77,494.95) --
-	(207.58,494.95);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (199.98,487.86) --
-	(199.98,500.06);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.98,490.92) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.10,499.92) --
-	(216.56,499.92);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.11,499.81) --
-	(210.11,500.04);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.11,495.89) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (156.75,463.31) --
-	(179.56,463.31);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.50,460.78) --
-	(171.50,465.53);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.50,459.27) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (165.37,483.34) --
-	(188.77,483.34);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.57,482.71) --
-	(180.57,483.94);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.57,480.43) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (216.41,512.30) --
-	(225.65,512.30);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.61,509.43) --
-	(221.61,514.78);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (221.61,509.40) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (164.18,476.03) --
-	(174.33,476.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.95,474.65) --
-	(169.95,477.32);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.95,472.81) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (213.06,503.10) --
-	(218.28,503.10);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.85,502.50) --
-	(215.85,503.67);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (215.85,499.06) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (202.88,502.51) --
-	(207.31,502.51);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (205.23,502.21) --
-	(205.23,502.80);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.23,498.47) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.71,468.73) --
-	(170.74,468.73);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (166.40,467.18) --
-	(166.40,470.16);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (166.40,464.70) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.55,467.47) --
-	(172.33,467.47);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (167.72,466.51) --
-	(167.72,468.39);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (167.72,464.57) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.84,507.62) --
-	(218.89,507.62);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.38,507.22) --
-	(218.38,508.01);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (218.38,504.71) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (137.20,493.15) --
-	(182.80,493.15);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.55,492.20) --
-	(171.55,494.06);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.55,489.93) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.57,502.64) --
-	(218.61,502.64);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (207.57,501.88) --
-	(207.57,503.37);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.57,498.61) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.92,502.35) --
-	(194.96,502.35);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.81,502.20) --
-	(187.81,502.49);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.81,498.31) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (165.35,472.33) --
-	(173.05,472.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.60,471.58) --
-	(169.60,473.05);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.60,468.29) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (134.07,470.24) --
-	(176.07,470.24);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (165.12,469.07) --
-	(165.12,471.33);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (165.12,467.33) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,374.64) --
+	(203.52,578.16);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (286.65,578.16) --
+	(286.65,490.17) --
+	(  0.00,203.52);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (  0.00,346.12) --
+	(232.04,578.16);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (286.65,578.16) --
+	(286.65,518.69) --
+	(  0.00,232.04);
+
+\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (  0.00,317.60) --
+	(260.56,578.16);
+
+\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (286.65,578.16) --
+	(286.65,547.21) --
+	(  0.00,260.56);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (142.89,342.31) {$\frac{1}{64} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,435.87) {$64\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (114.37,342.31) {$\frac{1}{16} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,407.35) {$16\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 84.20,342.31) {$\frac{1}{4} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92,378.83) {$4\times$};
+
+\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,528.36);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 86.08,409.37) --
+	(106.21,409.37);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 98.51,401.22) --
+	( 98.51,415.19);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 98.51,406.14) {$p$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.95,474.99) --
+	(188.09,474.99);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.83,473.08) --
+	(184.83,476.74);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.83,470.96) {$L$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.65,474.30) --
+	(102.96,474.30);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 98.44,471.52) --
+	( 98.44,476.75);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 98.44,470.27) {$r$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 85.75,424.33) --
+	( 97.88,424.33);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.70,416.17) --
+	( 92.70,430.15);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 92.70,420.29) {$h$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 85.46,386.96) --
+	(113.76,386.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (104.13,378.15) --
+	(104.13,393.10);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (104.13,384.05) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.32,483.57) --
+	(194.53,483.57);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.94,482.97) --
+	(193.94,484.15);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.94,480.66) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (167.20,470.80) --
+	(170.02,470.80);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.66,467.68) --
+	(168.66,473.50);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (168.66,467.57) {$p$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.39,475.00) --
+	(191.75,475.00);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.60,470.62) --
+	(187.60,478.61);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.60,470.96) {$L$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.47,480.80) --
+	(187.89,480.80);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.19,478.95) --
+	(187.19,482.50);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.19,476.77) {$r$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.19,457.78) --
+	(173.69,457.78);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.12,454.35) --
+	(171.12,460.71);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.12,453.74) {$h$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.89,460.59) --
+	(174.27,460.59);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.11,456.85) --
+	(173.11,463.75);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.11,457.69) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.58,485.03) --
+	(197.77,485.03);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.24,483.39) --
+	(196.24,486.55);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.24,482.13) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.67,442.74) --
+	(172.67,448.10);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.67,442.37) {$p$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.04,481.91) --
+	(199.30,481.91);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.99,481.15) --
+	(195.99,482.65);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.99,477.88) {$L$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.28,483.17) --
+	(201.19,483.17);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.73,482.87) --
+	(194.73,483.47);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.73,479.14) {$r$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (141.61,413.21) --
+	(141.61,424.99);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (141.61,415.90) {$h$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.98,435.47) --
+	(171.98,440.78);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.98,435.39) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.52,487.53) --
+	(197.96,487.53);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.74,487.09) --
+	(197.74,487.96);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.74,484.63) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (135.67,450.29) --
+	(147.06,450.29);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (142.14,448.74) --
+	(142.14,451.73);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (142.14,447.06) {$p$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.48,480.63) --
+	(196.33,480.63);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.61,479.97) --
+	(193.61,481.28);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.61,476.60) {$L$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.06,479.97) --
+	(184.03,479.97);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.70,479.64) --
+	(181.70,480.30);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.70,475.94) {$r$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (131.78,442.10) --
+	(143.02,442.10);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.16,440.36) --
+	(138.16,443.70);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (138.16,438.06) {$h$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (132.72,440.69) --
+	(144.81,440.69);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (139.64,439.60) --
+	(139.64,441.72);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (139.64,437.78) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.55,488.06) --
+	(198.21,488.06);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.88,487.69) --
+	(197.88,488.42);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.88,485.15) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (123.29,429.70) --
+	(134.35,429.70);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.55,425.74) --
+	(129.55,433.02);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (129.55,426.47) {$p$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.28,475.22) --
+	(196.89,475.22);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.22,472.58) --
+	(190.22,477.56);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.22,471.19) {$L$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.67,475.58) --
+	(153.58,475.58);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (152.65,474.36) --
+	(152.65,476.74);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (152.65,471.55) {$r$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (115.83,424.98) --
+	(122.98,424.98);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (119.72,420.83) --
+	(119.72,428.44);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (119.72,420.95) {$h$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (127.22,406.71) --
+	(136.61,406.71);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (132.44,404.17) --
+	(132.44,408.97);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (132.44,403.80) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.61,485.43) --
+	(196.23,485.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.92,484.44) --
+	(195.92,486.37);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.92,482.52) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (167.63,453.48) --
+	(167.63,460.42);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (167.63,454.02) {$p$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (118.33,472.88) --
+	(196.07,472.88);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.27,470.47) --
+	(182.27,475.03);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.27,468.84) {$L$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.68,480.81) --
+	(208.94,480.81);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.36,480.47) --
+	(203.36,481.14);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (203.36,476.77) {$r$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (146.51,449.17) --
+	(188.52,449.17);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.77,446.85) --
+	(176.77,451.26);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.77,445.14) {$h$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (183.26,455.28) --
+	(183.26,459.17);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.26,454.41) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.59,486.76) --
+	(197.77,486.76);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.19,486.27) --
+	(197.19,487.23);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.19,483.85) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (105.42,469.49) --
+	(156.55,469.49);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (143.93,468.42) --
+	(143.93,470.50);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (143.93,466.26) {$p$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.45,480.12) --
+	(196.70,480.12);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.33,479.27) --
+	(184.33,480.94);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.33,476.09) {$L$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.84,479.79) --
+	(170.18,479.79);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.16,479.63) --
+	(162.16,479.96);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (162.16,475.76) {$r$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (136.98,446.13) --
+	(145.62,446.13);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (141.75,445.29) --
+	(141.75,446.94);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (141.75,442.10) {$h$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (101.91,443.79) --
+	(149.00,443.79);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (136.72,442.48) --
+	(136.72,445.01);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (136.72,440.88) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.72,487.93) --
+	(199.43,487.93);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.12,487.45) --
+	(198.12,488.39);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.12,485.02) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (136.95,468.82) --
+	(161.50,468.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (152.69,467.28) --
+	(152.69,470.26);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (152.69,465.59) {$p$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.00,470.14) --
+	(184.33,470.14);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.81,462.83) --
+	(175.81,475.52);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (175.81,466.10) {$L$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.94,477.02) --
+	(194.40,477.02);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.18,476.87) --
+	(187.18,477.17);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.18,472.99) {$r$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (127.34,436.53) --
+	(152.92,436.53);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (143.88,434.15) --
+	(143.88,438.66);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (143.88,432.50) {$h$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (137.00,458.99) --
+	(163.24,458.99);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (154.05,457.82) --
+	(154.05,460.09);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (154.05,456.08) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.68,499.03) --
+	(209.42,499.03);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.05,497.42) --
+	(209.05,500.52);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.05,496.12) {$\kappa$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.40,457.56) --
+	(200.40,467.28);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (200.40,459.76) {$p$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (178.81,457.66) --
+	(178.81,463.95);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (178.81,457.01) {$L$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.96,478.25) --
+	(210.16,478.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (199.32,477.51) --
+	(199.32,478.96);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.32,474.22) {$r$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (141.43,462.19) --
+	(168.73,462.19);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.31,458.09) --
+	(159.31,465.60);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (159.31,458.15) {$h$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.44,454.40) --
+	(184.44,464.73);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.44,457.30) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.41,501.46) --
+	(213.31,501.46);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.38,500.63) --
+	(212.38,502.26);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.38,498.56) {$\kappa$};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,338.88) -- (218.78,338.88);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,338.88);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.05,338.88) -- ( 92.05,333.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (134.29,338.88) -- (134.29,333.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.54,338.88) -- (176.54,333.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.78,338.88) -- (218.78,333.90);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 97.17,338.88) -- ( 97.17,333.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (144.54,338.88) -- (144.54,333.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.91,338.88) -- (191.91,333.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.28,338.88) -- (239.28,333.90);
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 92.05,320.95) {10};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (134.29,320.95) {100};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (176.54,320.95) {1000};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (218.78,320.95) {10000};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,338.88) -- ( 49.80,507.86);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 97.17,320.95) {10};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (144.54,320.95) {100};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (191.91,320.95) {1000};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (239.28,320.95) {10000};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,338.88) -- ( 49.80,528.36);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,381.13) -- ( 44.82,381.13);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,423.37) -- ( 44.82,423.37);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,465.62) -- ( 44.82,465.62);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,507.86) -- ( 44.82,507.86);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,386.25) -- ( 44.82,386.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,433.62) -- ( 44.82,433.62);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,480.99) -- ( 44.82,480.99);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,528.36) -- ( 44.82,528.36);
 
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,378.27) {10};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,420.51) {100};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,462.76) {1000};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,505.00) {10000};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,383.39) {10};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,430.76) {100};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,478.13) {1000};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,525.50) {10000};
 \end{scope}
@@
 \definecolor{drawColor}{RGB}{0,0,0}
-\definecolor{fillColor}{RGB}{255,0,0}
+\definecolor{fillColor}{RGB}{255,0,109}
 
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,431.01) rectangle (189.67,426.03);
-\definecolor{fillColor}{RGB}{0,0,255}
+\definecolor{fillColor}{RGB}{253,104,0}
 
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,421.05) rectangle (189.67,416.07);
-\definecolor{fillColor}{RGB}{0,255,0}
+\definecolor{fillColor}{RGB}{143,161,0}
 
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,411.09) rectangle (189.67,406.11);
-\definecolor{fillColor}{RGB}{255,255,0}
+\definecolor{fillColor}{RGB}{0,195,0}
 
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,401.13) rectangle (189.67,396.15);
-\definecolor{fillColor}{RGB}{255,165,0}
+\definecolor{fillColor}{RGB}{0,219,171}
 
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,391.17) rectangle (189.67,386.19);
-\definecolor{fillColor}{RGB}{0,0,0}
+\definecolor{fillColor}{RGB}{0,216,255}
 
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,381.21) rectangle (189.67,376.23);
-\definecolor{fillColor}{RGB}{160,32,240}
+\definecolor{fillColor}{RGB}{151,0,255}
 
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,371.25) rectangle (189.67,366.27);
-\definecolor{fillColor}{RGB}{0,100,0}
+\definecolor{fillColor}{RGB}{255,0,255}
 
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,361.29) rectangle (189.67,356.31);
-\definecolor{fillColor}{RGB}{0,255,255}
+\definecolor{fillColor}{RGB}{68,68,68}
 
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,425.66) {Broughton};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,425.66) {Ran};
 
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,395.78) {Kawahara};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,385.82) {Moyle};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,375.86) {Ran};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,365.90) {Rightmyer};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,355.94) {Sauquet};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,345.98) {simulated};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,395.78) {Sauquet};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,385.82) {Broughton};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,375.86) {Kawahara};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,365.90) {simulated};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,355.94) {Rightmyer};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,345.98) {Moyle};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,548.96) {\bfseries Comparison of adapt (\textit{real}) and nocons (\textit{real})};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,301.03) {ESS/chain [nocons (\textit{real})]};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (307.01,433.62) {ESS/chain [adapt (\textit{real})]};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,548.96) {\bfseries adapt (\textit{real}) vs. nocons (\textit{real})};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,301.03) {ESS/hr [nocons (\textit{real})]};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (307.01,433.62) {ESS/hr [adapt (\textit{real})]};
 \end{scope}
@@
 \definecolor{drawColor}{RGB}{0,0,0}
-\definecolor{fillColor}{gray}{0.91}
-
-\path[draw=drawColor,line width= 0.1pt,line join=round,line cap=round,fill=fillColor] (169.90,246.20) --
-	(501.86,578.16) --
-	(570.61,578.16) --
-	(570.61,494.30) --
-	(169.90, 93.59) --
-	cycle;
-\definecolor{fillColor}{RGB}{190,190,190}
-
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] (169.90,220.77) --
-	(527.29,578.16) --
-	(570.61,578.16) --
-	(570.61,519.74) --
-	(169.90,119.03) --
-	cycle;
-\definecolor{fillColor}{RGB}{169,169,169}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.90,195.33) --
-	(552.73,578.16) --
-	(570.61,578.16) --
-	(570.61,545.17) --
-	(169.90,144.46) --
-	cycle;
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (422.72,342.31) {$\frac{1}{64} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,426.62) {$64\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (397.28,342.31) {$\frac{1}{16} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,401.18) {$16\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (370.19,342.31) {$\frac{1}{4} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.00,375.75) {$4\times$};
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (338.88,338.88) -- (528.36,528.36);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (442.22,490.95) --
-	(452.08,490.95);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (447.80,488.50) --
-	(447.80,493.11);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (447.80,487.72) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (493.05,494.57) --
-	(507.86,494.57);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (501.91,492.61) --
-	(501.91,496.33);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (501.91,490.53) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (467.53,499.63) --
-	(469.23,499.63);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (468.40,499.53) --
-	(468.40,499.72);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.40,495.59) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (435.57,457.21) --
-	(441.94,457.21);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (439.03,453.71) --
-	(439.03,460.15);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (439.03,453.18) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (445.72,477.46) --
-	(454.09,477.46);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (450.38,473.15) --
-	(450.38,480.94);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (450.38,474.55) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (509.40,508.34) --
-	(510.23,508.34);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (509.82,507.96) --
-	(509.82,508.71);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (509.82,505.44) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.25,470.08) --
-	(486.25,474.05);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (486.25,468.95) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (503.53,505.74) --
-	(510.01,505.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (507.05,504.33) --
-	(507.05,507.05);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (507.05,501.71) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (497.50,509.15) --
-	(511.69,509.15);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (505.93,509.01) --
-	(505.93,509.30);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (505.93,505.12) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (458.56,441.48) --
-	(458.56,447.41);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (458.56,440.65) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.64,465.29) --
-	(485.64,470.85);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (485.64,465.37) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (511.78,512.39) --
-	(512.23,512.39);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (512.01,512.01) --
-	(512.01,512.77);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (512.01,509.49) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (510.99,489.74) --
-	(510.99,496.16);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (510.99,490.01) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (491.73,482.43) --
-	(491.73,487.46);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (491.73,481.08) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (488.29,509.74) --
-	(519.69,509.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (510.02,509.40) --
-	(510.02,510.06);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (510.02,505.70) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (458.40,493.13) --
-	(482.75,493.13);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.34,492.97) --
-	(474.34,493.29);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.34,489.10) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (496.76,491.95) --
-	(496.76,497.87);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (496.76,492.25) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (409.03,486.63) --
-	(426.98,486.63);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.12,480.59) --
-	(420.12,491.17);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (420.12,483.41) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (493.64,486.94) --
-	(500.01,486.94);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (497.10,484.78) --
-	(497.10,488.87);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (497.10,482.90) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (414.89,499.46) --
-	(424.09,499.46);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.06,498.34) --
-	(420.06,500.52);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (420.06,495.43) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (408.74,462.06) --
-	(419.56,462.06);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (414.94,452.46) --
-	(414.94,468.33);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (414.94,458.03) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (408.48,488.92) --
-	(433.72,488.92);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (425.13,483.95) --
-	(425.13,492.83);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (425.13,486.02) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (512.25,512.90) --
-	(512.71,512.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (512.48,512.69) --
-	(512.48,513.11);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (512.48,509.99) {$\mu$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.40,497.82) --
-	(476.30,497.82);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (468.44,494.86) --
-	(468.44,500.36);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.44,494.59) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (475.85,498.71) --
-	(496.66,498.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (489.06,489.13) --
-	(489.06,504.97);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (489.06,494.67) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (489.18,507.02) --
-	(505.64,507.02);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.19,506.47) --
-	(499.19,507.55);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (499.19,502.98) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (445.83,469.60) --
-	(468.64,469.60);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (460.58,463.71) --
-	(460.58,474.05);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (460.58,465.56) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.45,496.70) --
-	(477.85,496.70);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (469.65,491.56) --
-	(469.65,500.72);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (469.65,493.80) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (505.49,512.98) --
-	(514.73,512.98);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (510.69,511.49) --
-	(510.69,514.37);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (510.69,510.08) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (453.26,482.10) --
-	(463.41,482.10);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (459.03,480.23) --
-	(459.03,483.80);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (459.03,478.87) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (502.14,502.07) --
-	(507.36,502.07);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (504.93,500.38) --
-	(504.93,503.61);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (504.93,498.03) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (491.96,503.97) --
-	(496.39,503.97);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (494.31,503.61) --
-	(494.31,504.33);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (494.31,499.94) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (449.79,473.17) --
-	(459.82,473.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (455.48,470.48) --
-	(455.48,475.52);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (455.48,469.14) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (450.63,478.15) --
-	(461.41,478.15);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (456.80,476.59) --
-	(456.80,479.58);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (456.80,475.24) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (506.92,507.74) --
-	(507.97,507.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (507.46,507.42) --
-	(507.46,508.04);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (507.46,504.83) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.28,495.30) --
-	(471.88,495.30);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (460.63,494.52) --
-	(460.63,496.04);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (460.63,492.07) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.65,495.60) --
-	(507.69,495.60);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (496.65,494.08) --
-	(496.65,497.00);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (496.65,491.57) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (465.00,500.38) --
-	(484.04,500.38);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.89,500.12) --
-	(476.89,500.63);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (476.89,496.34) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.43,473.27) --
-	(462.13,473.27);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (458.68,472.16) --
-	(458.68,474.32);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (458.68,469.24) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.15,473.74) --
-	(465.15,473.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.20,471.09) --
-	(454.20,476.05);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (454.20,470.83) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (149.40,234.96) --
+	(492.60,578.16);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (575.73,578.16) --
+	(575.73,490.17) --
+	(149.40, 63.84) --
+	(149.40,234.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (149.40,206.44) --
+	(521.12,578.16);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (575.73,578.16) --
+	(575.73,518.69) --
+	(149.40, 92.36) --
+	(149.40,206.44);
+
+\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (149.40,177.92) --
+	(549.64,578.16);
+
+\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (575.73,578.16) --
+	(575.73,547.21) --
+	(149.40,120.88) --
+	(149.40,177.92);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (431.97,342.31) {$\frac{1}{64} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,435.87) {$64\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (403.45,342.31) {$\frac{1}{16} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,407.35) {$16\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (373.28,342.31) {$\frac{1}{4} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.00,378.83) {$4\times$};
+
+\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (338.88,338.88) -- (528.36,528.36);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (375.16,462.17) --
+	(395.29,462.17);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (387.59,455.39) --
+	(387.59,467.26);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (387.59,458.94) {$p$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (470.03,462.51) --
+	(477.17,462.51);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (473.91,460.09) --
+	(473.91,464.68);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (473.91,458.48) {$L$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (381.73,476.56) --
+	(392.04,476.56);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (387.52,475.30) --
+	(387.52,477.74);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (387.52,472.52) {$r$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (374.83,434.62) --
+	(386.96,434.62);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (381.78,423.86) --
+	(381.78,441.65);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (381.78,430.59) {$h$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (374.54,464.74) --
+	(402.84,464.74);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (393.21,459.17) --
+	(393.21,469.12);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (393.21,461.83) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.40,483.53) --
+	(483.61,483.53);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.02,482.91) --
+	(483.02,484.13);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.02,480.62) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.75,443.62) --
+	(461.75,448.06);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (461.75,442.73) {$p$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (481.12,483.60) --
+	(488.38,483.60);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.07,482.02) --
+	(485.07,485.07);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (485.07,479.57) {$L$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.36,487.42) --
+	(490.27,487.42);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.81,487.26) --
+	(483.81,487.59);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.81,483.39) {$r$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (430.69,411.54) --
+	(430.69,418.19);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (430.69,411.10) {$h$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.06,438.24) --
+	(461.06,444.47);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (461.06,438.69) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.60,487.66) --
+	(487.04,487.66);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.82,487.45) --
+	(486.82,487.86);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (486.82,484.75) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (424.75,457.09) --
+	(436.14,457.09);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (431.22,454.99) --
+	(431.22,458.99);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (431.22,453.86) {$p$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.56,479.48) --
+	(485.41,479.48);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.69,477.59) --
+	(482.69,481.21);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (482.69,475.44) {$L$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (468.14,481.62) --
+	(473.11,481.62);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (470.78,481.21) --
+	(470.78,482.01);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (470.78,477.58) {$r$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.86,447.08) --
+	(432.10,447.08);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.24,444.06) --
+	(427.24,449.71);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (427.24,443.04) {$h$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,452.65) --
+	(433.89,452.65);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (428.72,450.91) --
+	(428.72,454.26);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (428.72,449.75) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.63,487.71) --
+	(487.29,487.71);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.96,487.18) --
+	(486.96,488.23);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (486.96,484.81) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.37,467.01) --
+	(423.43,467.01);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.63,464.26) --
+	(418.63,469.44);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (418.63,463.79) {$p$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (469.36,471.07) --
+	(485.97,471.07);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.30,468.87) --
+	(479.30,473.05);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (479.30,467.03) {$L$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (440.75,476.74) --
+	(442.66,476.74);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (441.73,476.63) --
+	(441.73,476.85);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (441.73,472.71) {$r$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (404.91,429.18) --
+	(412.06,429.18);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (408.80,425.26) --
+	(408.80,432.48);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (408.80,425.15) {$h$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (416.30,451.88) --
+	(425.69,451.88);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.52,447.05) --
+	(421.52,455.79);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (421.52,448.98) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (484.69,485.74) --
+	(485.31,485.74);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.00,485.16) --
+	(485.00,486.31);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (485.00,482.84) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (394.50,471.89) --
+	(445.63,471.89);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.01,471.02) --
+	(433.01,472.72);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (433.01,468.66) {$p$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (437.53,472.23) --
+	(485.78,472.23);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (473.41,470.53) --
+	(473.41,473.80);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (473.41,468.19) {$L$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (437.92,477.58) --
+	(459.26,477.58);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (451.24,477.30) --
+	(451.24,477.86);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (451.24,473.55) {$r$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.06,447.19) --
+	(434.70,447.19);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (430.83,445.94) --
+	(430.83,448.37);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (430.83,443.16) {$h$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (390.99,447.71) --
+	(438.08,447.71);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (425.80,444.74) --
+	(425.80,450.30);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (425.80,444.81) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.80,487.32) --
+	(488.51,487.32);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (487.20,486.11) --
+	(487.20,488.46);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (487.20,484.42) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.03,474.71) --
+	(450.58,474.71);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (441.77,471.39) --
+	(441.77,477.57);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (441.77,471.49) {$p$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (450.08,475.71) --
+	(473.41,475.71);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.89,464.98) --
+	(464.89,482.73);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (464.89,471.68) {$L$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (465.02,485.03) --
+	(483.48,485.03);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.26,484.42) --
+	(476.26,485.62);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (476.26,481.00) {$r$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (416.42,443.07) --
+	(442.00,443.07);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (432.96,436.47) --
+	(432.96,448.06);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (432.96,439.03) {$h$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.08,473.47) --
+	(452.32,473.47);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.13,467.70) --
+	(443.13,477.96);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (443.13,470.56) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (497.76,498.31) --
+	(498.50,498.31);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (498.13,497.03) --
+	(498.13,499.52);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (498.13,495.41) {$\kappa$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (489.48,465.66) --
+	(489.48,472.86);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (489.48,466.35) {$p$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (467.89,457.46) --
+	(467.89,463.10);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (467.89,456.44) {$L$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.04,488.08) --
+	(499.24,488.08);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (488.40,487.70) --
+	(488.40,488.45);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (488.40,484.04) {$r$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (430.51,469.46) --
+	(457.81,469.46);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (448.39,469.28) --
+	(448.39,469.64);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (448.39,465.42) {$h$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (473.52,468.14) --
+	(473.52,474.77);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (473.52,468.82) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (500.49,501.82) --
+	(502.39,501.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (501.46,500.70) --
+	(501.46,502.87);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (501.46,498.91) {$\kappa$};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,338.88) -- (507.86,338.88);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,338.88) -- (528.36,338.88);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (381.13,338.88) -- (381.13,333.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.37,338.88) -- (423.37,333.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (465.62,338.88) -- (465.62,333.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (507.86,338.88) -- (507.86,333.90);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (386.25,338.88) -- (386.25,333.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.62,338.88) -- (433.62,333.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (480.99,338.88) -- (480.99,333.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (528.36,338.88) -- (528.36,333.90);
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (381.13,320.95) {10};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (423.37,320.95) {100};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (465.62,320.95) {1000};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (507.86,320.95) {10000};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,338.88) -- (338.88,507.86);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (386.25,320.95) {10};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (433.62,320.95) {100};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (480.99,320.95) {1000};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (528.36,320.95) {10000};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,338.88) -- (338.88,528.36);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,381.13) -- (333.90,381.13);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,423.37) -- (333.90,423.37);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,465.62) -- (333.90,465.62);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,507.86) -- (333.90,507.86);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,386.25) -- (333.90,386.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,433.62) -- (333.90,433.62);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,480.99) -- (333.90,480.99);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,528.36) -- (333.90,528.36);
 
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,378.27) {10};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,420.51) {100};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,462.76) {1000};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,505.00) {10000};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,383.39) {10};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,430.76) {100};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,478.13) {1000};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,525.50) {10000};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,259.88) {\bfseries Comparison of adapt (\textit{real}) and cons (\textit{real})};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54, 11.95) {ESS/chain [cons (\textit{real})]};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,144.54) {ESS/chain [adapt (\textit{real})]};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,259.88) {\bfseries adapt (\textit{real}) vs. cons (\textit{real})};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54, 11.95) {ESS/hr [cons (\textit{real})]};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,144.54) {ESS/hr [adapt (\textit{real})]};
 \end{scope}
@@
 \definecolor{drawColor}{RGB}{0,0,0}
-\definecolor{fillColor}{gray}{0.91}
-
-\path[draw=drawColor,line width= 0.1pt,line join=round,line cap=round,fill=fillColor] (  0.00, 82.04) --
-	(284.70,366.75) --
-	(284.70,202.66) --
-	( 82.04,  0.00) --
-	(  0.00,  0.00) --
-	cycle;
-\definecolor{fillColor}{RGB}{190,190,190}
-
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] (  0.00, 54.70) --
-	(284.70,339.40) --
-	(284.70,230.01) --
-	( 54.70,  0.00) --
-	(  0.00,  0.00) --
-	cycle;
-\definecolor{fillColor}{RGB}{169,169,169}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (  0.00, 27.35) --
-	(284.70,312.05) --
-	(284.70,257.36) --
-	( 27.35,  0.00) --
-	(  0.00,  0.00) --
-	cycle;
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (139.38, 53.23) {$\frac{1}{64} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,143.28) {$64\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (112.03, 53.23) {$\frac{1}{16} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,115.93) {$16\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 83.03, 53.23) {$\frac{1}{4} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92, 88.58) {$4\times$};
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 49.80, 49.80) -- (239.28,239.28);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.73,213.31) --
-	(180.71,213.31);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.53,210.67) --
-	(177.53,215.64);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.53,210.08) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.65,217.20) --
-	(223.43,217.20);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.18,215.09) --
-	(221.18,219.10);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (221.18,213.16) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.36,222.64) --
-	(222.63,222.64);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.53,222.53) --
-	(221.53,222.74);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (221.53,218.60) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.02,177.03) --
-	(176.32,177.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.00,173.27) --
-	(173.00,180.19);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.00,173.00) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.05,198.80) --
-	(157.65,198.80);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (155.48,194.17) --
-	(155.48,202.55);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (155.48,195.89) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.61,232.01) --
-	(233.26,232.01);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.46,231.60) --
-	(232.46,232.40);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (232.46,229.10) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.04,193.12) --
-	(195.17,193.12);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.77,190.87) --
-	(192.77,195.14);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.77,189.89) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.87,229.21) --
-	(228.31,229.21);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.60,227.70) --
-	(227.60,230.62);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (227.60,225.18) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.52,232.88) --
-	(229.09,232.88);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.80,232.72) --
-	(228.80,233.04);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (228.80,228.85) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.71,163.56) --
-	(173.01,163.56);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.16,160.12) --
-	(168.16,166.49);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (168.16,159.53) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (183.06,188.93) --
-	(188.16,188.93);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.77,185.72) --
-	(185.77,191.69);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.77,186.03) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.98,236.37) --
-	(236.46,236.37);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (236.22,235.95) --
-	(236.22,236.77);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (236.22,233.46) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.24,215.76) --
-	(213.56,215.76);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.45,212.01) --
-	(209.45,218.92);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.45,212.54) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.34,207.04) --
-	(210.37,207.04);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (207.59,204.14) --
-	(207.59,209.56);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.59,203.00) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.38,233.51) --
-	(224.77,233.51);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (224.09,233.15) --
-	(224.09,233.86);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (224.09,229.47) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.76,215.65) --
-	(211.95,215.65);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.68,215.48) --
-	(208.68,215.82);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (208.68,211.62) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (201.21,217.83) --
-	(211.12,217.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.78,214.39) --
-	(206.78,220.75);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (206.78,214.92) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (150.22,208.67) --
-	(163.61,208.67);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.03,202.16) --
-	(158.03,213.55);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.03,205.44) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (219.13,208.99) --
-	(222.64,208.99);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.96,206.67) --
-	(220.96,211.07);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.96,204.96) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.63,222.46) --
-	(222.65,222.46);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.30,221.26) --
-	(220.30,223.59);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.30,218.43) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (164.55,182.25) --
-	(177.96,182.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.38,171.93) --
-	(172.38,188.99);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.38,178.21) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (128.10,211.13) --
-	(142.44,211.13);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (136.54,205.79) --
-	(136.54,215.33);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (136.54,208.22) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (236.56,236.91) --
-	(237.19,236.91);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (236.88,236.68) --
-	(236.88,237.13);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (236.88,234.00) {$\mu$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (213.15,220.69) --
-	(216.83,220.69);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.07,217.51) --
-	(215.07,223.43);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (215.07,217.47) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.98,221.65) --
-	(223.10,221.65);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.61,211.36) --
-	(217.61,228.38);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (217.61,217.62) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.83,230.59) --
-	(223.08,230.59);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.96,230.00) --
-	(222.96,231.16);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (222.96,226.55) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.87,190.35) --
-	(185.98,190.35);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (183.59,184.02) --
-	(183.59,195.13);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.59,186.31) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.45,219.50) --
-	(205.78,219.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (205.12,213.97) --
-	(205.12,223.81);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.12,216.59) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (233.18,237.00) --
-	(238.93,237.00);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (236.27,235.39) --
-	(236.27,238.49);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (236.27,234.10) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.79,203.79) --
-	(198.65,203.79);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.27,201.78) --
-	(197.27,205.62);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.27,200.56) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.73,225.26) --
-	(226.99,225.26);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.37,223.45) --
-	(226.37,226.92);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (226.37,221.23) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.42,227.31) --
-	(226.05,227.31);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.74,226.93) --
-	(225.74,227.69);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (225.74,223.28) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.75,194.19) --
-	(190.95,194.19);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.42,191.29) --
-	(189.42,196.72);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (189.42,190.16) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.03,199.54) --
-	(189.05,199.54);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.07,197.87) --
-	(188.07,201.08);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.07,196.64) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.81,231.36) --
-	(231.65,231.36);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.23,231.02) --
-	(231.23,231.69);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (231.23,228.45) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (214.65,217.98) --
-	(216.65,217.98);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.68,217.15) --
-	(215.68,218.78);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (215.68,214.76) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.06,218.31) --
-	(226.66,218.31);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.88,216.68) --
-	(225.88,219.81);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (225.88,214.28) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.41,223.44) --
-	(225.72,223.44);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.56,223.17) --
-	(225.56,223.71);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (225.56,219.41) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.48,194.30) --
-	(194.06,194.30);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.28,193.10) --
-	(193.28,195.43);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.28,190.27) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.79,194.80) --
-	(192.21,194.80);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.04,191.95) --
-	(191.04,197.29);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.04,191.90) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00, 85.56) --
+	(286.65,372.21) --
+	(286.65,201.09) --
+	( 85.56,  0.00);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (  0.00, 57.04) --
+	(286.65,343.69) --
+	(286.65,229.61) --
+	( 57.04,  0.00);
+
+\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (  0.00, 28.52) --
+	(286.65,315.17) --
+	(286.65,258.13) --
+	( 28.52,  0.00);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (142.89, 53.23) {$\frac{1}{64} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,146.79) {$64\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (114.37, 53.23) {$\frac{1}{16} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,118.27) {$16\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 84.20, 53.23) {$\frac{1}{4} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92, 89.75) {$4\times$};
+
+\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] ( 49.80, 49.80) -- (239.28,239.28);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.14,173.09) --
+	(126.11,173.09);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.29,166.31) --
+	(120.29,178.18);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (120.29,169.86) {$p$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.00,173.43) --
+	(187.66,173.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.91,171.01) --
+	(185.91,175.60);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.91,169.40) {$L$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.44,187.48) --
+	(187.67,187.48);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.22,186.22) --
+	(185.22,188.66);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.22,183.44) {$r$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (127.09,145.54) --
+	(141.07,145.54);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (135.25,134.78) --
+	(135.25,152.57);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (135.25,141.51) {$h$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.07,175.66) --
+	(104.02,175.66);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 97.88,170.09) --
+	( 97.88,180.04);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 97.88,172.75) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.89,194.45) --
+	(195.07,194.45);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.49,193.83) --
+	(194.49,195.05);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.49,191.54) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.66,156.88) --
+	(159.02,156.88);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (156.52,154.54) --
+	(156.52,158.98);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (156.52,153.65) {$p$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.07,194.52) --
+	(193.57,194.52);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.83,192.94) --
+	(192.83,195.99);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.83,190.49) {$L$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.79,198.34) --
+	(194.39,198.34);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.09,198.18) --
+	(194.09,198.51);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.09,194.31) {$r$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (124.13,126.05) --
+	(135.91,126.05);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (130.85,122.46) --
+	(130.85,129.11);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (130.85,122.02) {$h$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (146.39,152.51) --
+	(151.70,152.51);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (149.22,149.16) --
+	(149.22,155.39);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (149.22,149.61) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.01,198.58) --
+	(198.88,198.58);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.45,198.37) --
+	(198.45,198.78);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.45,195.67) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.66,168.01) --
+	(162.65,168.01);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.21,165.91) --
+	(161.21,169.91);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (161.21,164.78) {$p$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.89,190.40) --
+	(192.20,190.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.55,188.51) --
+	(191.55,192.13);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.55,186.36) {$L$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.56,192.54) --
+	(191.22,192.54);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.89,192.13) --
+	(190.89,192.93);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.89,188.50) {$r$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.28,158.00) --
+	(154.62,158.00);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.02,154.98) --
+	(153.02,160.63);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (153.02,153.96) {$h$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (150.52,163.57) --
+	(152.64,163.57);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.61,161.83) --
+	(151.61,165.18);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (151.61,160.67) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.61,198.63) --
+	(199.34,198.63);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.98,198.10) --
+	(198.98,199.15);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.98,195.73) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (136.66,177.93) --
+	(143.94,177.93);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.62,175.18) --
+	(140.62,180.36);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (140.62,174.71) {$p$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (183.50,181.99) --
+	(188.48,181.99);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.14,179.79) --
+	(186.14,183.97);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (186.14,177.95) {$L$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.28,187.66) --
+	(187.66,187.66);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.50,187.55) --
+	(186.50,187.77);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (186.50,183.63) {$r$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (131.75,140.10) --
+	(139.36,140.10);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (135.90,136.18) --
+	(135.90,143.40);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (135.90,136.07) {$h$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (115.09,162.80) --
+	(119.89,162.80);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.63,157.97) --
+	(117.63,166.71);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (117.63,159.90) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.36,196.66) --
+	(197.29,196.66);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.35,196.08) --
+	(196.35,197.23);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.35,193.76) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.34,182.81) --
+	(181.42,182.81);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.41,181.94) --
+	(180.41,183.64);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.41,179.58) {$p$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.19,183.15) --
+	(191.86,183.15);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.04,181.45) --
+	(191.04,184.72);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.04,179.11) {$L$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.55,188.50) --
+	(190.88,188.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.71,188.22) --
+	(190.71,188.78);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.71,184.47) {$r$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (156.21,158.11) --
+	(157.86,158.11);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (157.05,156.86) --
+	(157.05,159.29);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (157.05,154.08) {$h$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.40,158.63) --
+	(155.93,158.63);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (154.71,155.66) --
+	(154.71,161.22);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (154.71,155.73) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.37,198.24) --
+	(199.31,198.24);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.85,197.03) --
+	(198.85,199.38);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.85,195.34) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (178.20,185.63) --
+	(181.18,185.63);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.74,182.31) --
+	(179.74,188.49);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.74,182.41) {$p$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.75,186.63) --
+	(186.44,186.63);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.06,175.90) --
+	(181.06,193.65);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.06,182.60) {$L$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.79,195.95) --
+	(188.09,195.95);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.94,195.34) --
+	(187.94,196.54);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.94,191.92) {$r$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.07,153.99) --
+	(149.58,153.99);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (147.45,147.39) --
+	(147.45,158.98);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (147.45,149.95) {$h$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.74,184.39) --
+	(171.01,184.39);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.91,178.62) --
+	(169.91,188.88);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.91,181.48) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.34,209.23) --
+	(211.44,209.23);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.95,207.95) --
+	(209.95,210.44);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.95,206.33) {$\kappa$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.48,180.49) --
+	(178.20,180.49);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.91,176.58) --
+	(173.91,183.78);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.91,177.27) {$p$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.58,171.39) --
+	(174.87,171.39);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.97,168.38) --
+	(171.97,174.02);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.97,167.36) {$L$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.43,199.00) --
+	(189.88,199.00);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.17,198.62) --
+	(189.17,199.37);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (189.17,194.96) {$r$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.01,180.38) --
+	(176.52,180.38);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.11,180.20) --
+	(173.11,180.56);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.11,176.34) {$h$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (165.32,182.64) --
+	(175.65,182.64);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.13,179.06) --
+	(171.13,185.69);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.13,179.74) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.55,212.74) --
+	(213.18,212.74);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.38,211.62) --
+	(212.38,213.79);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.38,209.83) {$\kappa$};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 49.80) -- (231.49, 49.80);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 49.80) -- (239.28, 49.80);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.22, 49.80) -- ( 95.22, 44.82);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.65, 49.80) -- (140.65, 44.82);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.07, 49.80) -- (186.07, 44.82);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.49, 49.80) -- (231.49, 44.82);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 97.17, 49.80) -- ( 97.17, 44.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (144.54, 49.80) -- (144.54, 44.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.91, 49.80) -- (191.91, 44.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.28, 49.80) -- (239.28, 44.82);
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 95.22, 31.87) {10};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (140.65, 31.87) {100};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (186.07, 31.87) {1000};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (231.49, 31.87) {10000};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 49.80) -- ( 49.80,231.49);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 97.17, 31.87) {10};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (144.54, 31.87) {100};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (191.91, 31.87) {1000};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (239.28, 31.87) {10000};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 49.80) -- ( 49.80,239.28);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 95.22) -- ( 44.82, 95.22);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,140.65) -- ( 44.82,140.65);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,186.07) -- ( 44.82,186.07);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,231.49) -- ( 44.82,231.49);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 97.17) -- ( 44.82, 97.17);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,144.54) -- ( 44.82,144.54);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,191.91) -- ( 44.82,191.91);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,239.28) -- ( 44.82,239.28);
 
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84, 92.37) {10};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,137.79) {100};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,183.21) {1000};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,228.64) {10000};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84, 94.31) {10};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,141.68) {100};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,189.05) {1000};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,236.42) {10000};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.66] at (433.62,258.45) {\bfseries Speed comparison};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.66] at (433.62, 11.95) {Setting};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.66] at (307.01,144.54) {Speed ($10^6$ states/hr)};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,259.88) {\bfseries \texttt{AdaptiveOperatorSampler} weights};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62, 11.95) {Sequence length $L$ (kb)};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (307.01,144.54) {Learned operator weight};
 \end{scope}
@@
 \path[clip] (338.88, 49.80) rectangle (528.36,239.28);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.85, 89.35) -- (428.67, 81.11);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.57, 81.09) -- (516.39, 89.09);
-\definecolor{fillColor}{RGB}{255,0,0}
-
-\path[fill=fillColor] (345.90, 92.78) --
-	(348.41, 88.43) --
-	(343.38, 88.43) --
+\definecolor{fillColor}{RGB}{255,0,109}
+
+\path[fill=fillColor] (485.73,232.77) circle (  1.87);
+
+\path[fill=fillColor] (485.73, 55.06) --
+	(488.24, 50.70) --
+	(483.21, 50.70) --
 	cycle;
-
-\path[fill=fillColor] (433.62, 80.59) circle (  1.87);
-
-\path[fill=fillColor] (521.34, 89.60) circle (  1.87);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.72,134.93) -- (428.80,114.73);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.48,114.58) -- (516.48,132.20);
-\definecolor{fillColor}{RGB}{0,255,0}
-
-\path[fill=fillColor] (345.90,139.09) --
-	(348.41,134.73) --
-	(343.38,134.73) --
+\definecolor{fillColor}{RGB}{0,0,0}
+
+\path[fill=fillColor] (435.32,150.27) circle (  2.15);
+
+\path[fill=fillColor] (435.32,142.15) --
+	(438.21,137.14) --
+	(432.42,137.14) --
 	cycle;
-
-\path[fill=fillColor] (433.62,113.49) circle (  1.87);
-
-\path[fill=fillColor] (521.34,133.30) circle (  1.87);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (349.23,225.52) -- (430.29,135.59);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.56,132.54) -- (516.40,142.76);
-\definecolor{fillColor}{RGB}{255,165,0}
-
-\path[fill=fillColor] (345.90,232.13) --
-	(348.41,227.77) --
-	(343.38,227.77) --
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,146.98) {\texttt{ConstantDistance}};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
+\definecolor{fillColor}{RGB}{143,161,0}
+
+\path[fill=fillColor] (394.78,149.36) circle (  1.87);
+
+\path[fill=fillColor] (394.78, 80.07) --
+	(397.29, 75.72) --
+	(392.26, 75.72) --
 	cycle;
-
-\path[fill=fillColor] (433.62,131.89) circle (  1.87);
-
-\path[fill=fillColor] (521.34,143.41) circle (  1.87);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.88, 71.53) -- (428.64, 69.21);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.60, 69.22) -- (516.36, 71.77);
 \definecolor{fillColor}{RGB}{0,0,0}
 
-\path[fill=fillColor] (345.90, 71.68) circle (  1.87);
-
-\path[fill=fillColor] (433.62, 69.06) circle (  1.87);
-
-\path[fill=fillColor] (521.34, 74.84) --
-	(523.86, 70.48) --
-	(518.83, 70.48) --
+\path[fill=fillColor] (435.32,150.27) circle (  2.15);
+
+\path[fill=fillColor] (435.32,142.15) --
+	(438.21,137.14) --
+	(432.42,137.14) --
 	cycle;
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.48,143.02) -- (429.04,109.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.26,109.56) -- (516.70,139.97);
-\definecolor{fillColor}{RGB}{160,32,240}
-
-\path[fill=fillColor] (345.90,147.87) --
-	(348.41,143.51) --
-	(343.38,143.51) --
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,146.98) {\texttt{ConstantDistance}};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
+\definecolor{fillColor}{RGB}{0,195,0}
+
+\path[fill=fillColor] (390.04,184.14) circle (  1.87);
+
+\path[fill=fillColor] (390.04, 69.81) --
+	(392.55, 65.46) --
+	(387.52, 65.46) --
 	cycle;
-
-\path[fill=fillColor] (433.62,107.76) circle (  1.87);
-
-\path[fill=fillColor] (521.34,141.77) circle (  1.87);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.70,132.99) -- (428.82,111.40);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.60,110.21) -- (516.36,112.45);
-\definecolor{fillColor}{RGB}{0,100,0}
-
-\path[fill=fillColor] (345.90,137.22) --
-	(348.41,132.86) --
-	(343.38,132.86) --
+\definecolor{fillColor}{RGB}{0,0,0}
+
+\path[fill=fillColor] (435.32,150.27) circle (  2.15);
+
+\path[fill=fillColor] (435.32,142.15) --
+	(438.21,137.14) --
+	(432.42,137.14) --
 	cycle;
 
-\path[fill=fillColor] (433.62,110.07) circle (  1.87);
-
-\path[fill=fillColor] (521.34,112.59) circle (  1.87);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (349.79,196.49) -- (429.73,132.52);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (437.55,132.47) -- (517.41,194.71);
-\definecolor{fillColor}{RGB}{0,255,255}
-
-\path[fill=fillColor] (345.90,202.50) --
-	(348.41,198.15) --
-	(343.38,198.15) --
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,146.98) {\texttt{ConstantDistance}};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
+\definecolor{fillColor}{RGB}{0,219,171}
+
+\path[fill=fillColor] (404.25,211.12) circle (  1.87);
+
+\path[fill=fillColor] (404.25, 60.31) --
+	(406.77, 55.95) --
+	(401.74, 55.95) --
 	cycle;
-
-\path[fill=fillColor] (433.62,129.40) circle (  1.87);
-
-\path[fill=fillColor] (521.34,197.77) circle (  1.87);
+\definecolor{fillColor}{RGB}{0,0,0}
+
+\path[fill=fillColor] (435.32,150.27) circle (  2.15);
+
+\path[fill=fillColor] (435.32,142.15) --
+	(438.21,137.14) --
+	(432.42,137.14) --
+	cycle;
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,146.98) {\texttt{ConstantDistance}};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
+\definecolor{fillColor}{RGB}{151,0,255}
+
+\path[fill=fillColor] (433.62,198.59) circle (  1.87);
+
+\path[fill=fillColor] (433.62, 71.59) --
+	(436.14, 67.23) --
+	(431.10, 67.23) --
+	cycle;
+\definecolor{fillColor}{RGB}{0,0,0}
+
+\path[fill=fillColor] (435.32,150.27) circle (  2.15);
+
+\path[fill=fillColor] (435.32,142.15) --
+	(438.21,137.14) --
+	(432.42,137.14) --
+	cycle;
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,146.98) {\texttt{ConstantDistance}};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
+\definecolor{fillColor}{RGB}{255,0,255}
+
+\path[fill=fillColor] (359.72,131.32) circle (  1.87);
+
+\path[fill=fillColor] (359.72, 82.69) --
+	(362.24, 78.34) --
+	(357.21, 78.34) --
+	cycle;
+\definecolor{fillColor}{RGB}{0,0,0}
+
+\path[fill=fillColor] (435.32,150.27) circle (  2.15);
+
+\path[fill=fillColor] (435.32,142.15) --
+	(438.21,137.14) --
+	(432.42,137.14) --
+	cycle;
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,146.98) {\texttt{ConstantDistance}};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
+\definecolor{fillColor}{RGB}{68,68,68}
+
+\path[fill=fillColor] (346.46,125.02) circle (  1.87);
+
+\path[fill=fillColor] (346.46, 77.24) --
+	(348.97, 72.89) --
+	(343.94, 72.89) --
+	cycle;
+\definecolor{fillColor}{RGB}{0,0,0}
+
+\path[fill=fillColor] (435.32,150.27) circle (  2.15);
+
+\path[fill=fillColor] (435.32,142.15) --
+	(438.21,137.14) --
+	(432.42,137.14) --
+	cycle;
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,146.98) {\texttt{ConstantDistance}};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,113.13) --
+	(339.26,113.54) --
+	(339.64,113.94) --
+	(340.02,114.34) --
+	(340.40,114.75) --
+	(340.78,115.15) --
+	(341.16,115.56) --
+	(341.54,115.97) --
+	(341.92,116.38) --
+	(342.30,116.79) --
+	(342.68,117.20) --
+	(343.06,117.61) --
+	(343.44,118.03) --
+	(343.82,118.44) --
+	(344.20,118.86) --
+	(344.58,119.27) --
+	(344.96,119.69) --
+	(345.34,120.11) --
+	(345.71,120.53) --
+	(346.09,120.95) --
+	(346.47,121.37) --
+	(346.85,121.80) --
+	(347.23,122.22) --
+	(347.61,122.65) --
+	(347.99,123.07) --
+	(348.37,123.50) --
+	(348.75,123.93) --
+	(349.13,124.36) --
+	(349.51,124.79) --
+	(349.89,125.22) --
+	(350.27,125.65) --
+	(350.65,126.08) --
+	(351.03,126.51) --
+	(351.41,126.95) --
+	(351.79,127.38) --
+	(352.17,127.82) --
+	(352.55,128.25) --
+	(352.93,128.69) --
+	(353.31,129.13) --
+	(353.69,129.57) --
+	(354.07,130.01) --
+	(354.45,130.44) --
+	(354.83,130.88) --
+	(355.21,131.33) --
+	(355.59,131.77) --
+	(355.97,132.21) --
+	(356.35,132.65) --
+	(356.73,133.09) --
+	(357.11,133.54) --
+	(357.49,133.98) --
+	(357.87,134.43) --
+	(358.25,134.87) --
+	(358.63,135.32) --
+	(359.01,135.76) --
+	(359.38,136.21) --
+	(359.76,136.65) --
+	(360.14,137.10) --
+	(360.52,137.55) --
+	(360.90,137.99) --
+	(361.28,138.44) --
+	(361.66,138.89) --
+	(362.04,139.34) --
+	(362.42,139.79) --
+	(362.80,140.24) --
+	(363.18,140.68) --
+	(363.56,141.13) --
+	(363.94,141.58) --
+	(364.32,142.03) --
+	(364.70,142.48) --
+	(365.08,142.93) --
+	(365.46,143.38) --
+	(365.84,143.83) --
+	(366.22,144.28) --
+	(366.60,144.73) --
+	(366.98,145.18) --
+	(367.36,145.63) --
+	(367.74,146.08) --
+	(368.12,146.53) --
+	(368.50,146.98) --
+	(368.88,147.43) --
+	(369.26,147.88) --
+	(369.64,148.32) --
+	(370.02,148.77) --
+	(370.40,149.22) --
+	(370.78,149.67) --
+	(371.16,150.12) --
+	(371.54,150.57) --
+	(371.92,151.01) --
+	(372.30,151.46) --
+	(372.68,151.91) --
+	(373.05,152.36) --
+	(373.43,152.80) --
+	(373.81,153.25) --
+	(374.19,153.69) --
+	(374.57,154.14) --
+	(374.95,154.58) --
+	(375.33,155.03) --
+	(375.71,155.47) --
+	(376.09,155.92) --
+	(376.47,156.36) --
+	(376.85,156.80) --
+	(377.23,157.24) --
+	(377.61,157.68) --
+	(377.99,158.13) --
+	(378.37,158.57) --
+	(378.75,159.01) --
+	(379.13,159.44) --
+	(379.51,159.88) --
+	(379.89,160.32) --
+	(380.27,160.76) --
+	(380.65,161.19) --
+	(381.03,161.63) --
+	(381.41,162.06) --
+	(381.79,162.50) --
+	(382.17,162.93) --
+	(382.55,163.36) --
+	(382.93,163.79) --
+	(383.31,164.22) --
+	(383.69,164.65) --
+	(384.07,165.08) --
+	(384.45,165.51) --
+	(384.83,165.94) --
+	(385.21,166.36) --
+	(385.59,166.79) --
+	(385.97,167.21) --
+	(386.34,167.64) --
+	(386.72,168.06) --
+	(387.10,168.48) --
+	(387.48,168.90) --
+	(387.86,169.32) --
+	(388.24,169.74) --
+	(388.62,170.16) --
+	(389.00,170.57) --
+	(389.38,170.99) --
+	(389.76,171.40) --
+	(390.14,171.82) --
+	(390.52,172.23) --
+	(390.90,172.64) --
+	(391.28,173.05) --
+	(391.66,173.46) --
+	(392.04,173.86) --
+	(392.42,174.27) --
+	(392.80,174.67) --
+	(393.18,175.08) --
+	(393.56,175.48) --
+	(393.94,175.88) --
+	(394.32,176.28) --
+	(394.70,176.68) --
+	(395.08,177.08) --
+	(395.46,177.47) --
+	(395.84,177.87) --
+	(396.22,178.26) --
+	(396.60,178.65) --
+	(396.98,179.04) --
+	(397.36,179.43) --
+	(397.74,179.82) --
+	(398.12,180.21) --
+	(398.50,180.59) --
+	(398.88,180.98) --
+	(399.26,181.36) --
+	(399.64,181.74) --
+	(400.01,182.12) --
+	(400.39,182.50) --
+	(400.77,182.88) --
+	(401.15,183.25) --
+	(401.53,183.62) --
+	(401.91,184.00) --
+	(402.29,184.37) --
+	(402.67,184.74) --
+	(403.05,185.11) --
+	(403.43,185.47) --
+	(403.81,185.84) --
+	(404.19,186.20) --
+	(404.57,186.56) --
+	(404.95,186.92) --
+	(405.33,187.28) --
+	(405.71,187.64) --
+	(406.09,188.00) --
+	(406.47,188.35) --
+	(406.85,188.70) --
+	(407.23,189.05) --
+	(407.61,189.40) --
+	(407.99,189.75) --
+	(408.37,190.10) --
+	(408.75,190.44) --
+	(409.13,190.79) --
+	(409.51,191.13) --
+	(409.89,191.47) --
+	(410.27,191.81) --
+	(410.65,192.14) --
+	(411.03,192.48) --
+	(411.41,192.81) --
+	(411.79,193.14) --
+	(412.17,193.48) --
+	(412.55,193.80) --
+	(412.93,194.13) --
+	(413.31,194.46) --
+	(413.68,194.78) --
+	(414.06,195.10) --
+	(414.44,195.42) --
+	(414.82,195.74) --
+	(415.20,196.06) --
+	(415.58,196.38) --
+	(415.96,196.69) --
+	(416.34,197.00) --
+	(416.72,197.31) --
+	(417.10,197.62) --
+	(417.48,197.93) --
+	(417.86,198.24) --
+	(418.24,198.54) --
+	(418.62,198.84) --
+	(419.00,199.15) --
+	(419.38,199.45) --
+	(419.76,199.74) --
+	(420.14,200.04) --
+	(420.52,200.33) --
+	(420.90,200.63) --
+	(421.28,200.92) --
+	(421.66,201.21) --
+	(422.04,201.50) --
+	(422.42,201.78) --
+	(422.80,202.07) --
+	(423.18,202.35) --
+	(423.56,202.63) --
+	(423.94,202.91) --
+	(424.32,203.19) --
+	(424.70,203.47) --
+	(425.08,203.74) --
+	(425.46,204.01) --
+	(425.84,204.29) --
+	(426.22,204.56) --
+	(426.60,204.82) --
+	(426.97,205.09) --
+	(427.35,205.36) --
+	(427.73,205.62) --
+	(428.11,205.88) --
+	(428.49,206.14) --
+	(428.87,206.40) --
+	(429.25,206.66) --
+	(429.63,206.91) --
+	(430.01,207.17) --
+	(430.39,207.42) --
+	(430.77,207.67) --
+	(431.15,207.92) --
+	(431.53,208.17) --
+	(431.91,208.41) --
+	(432.29,208.66) --
+	(432.67,208.90) --
+	(433.05,209.14) --
+	(433.43,209.38) --
+	(433.81,209.62) --
+	(434.19,209.86) --
+	(434.57,210.09) --
+	(434.95,210.33) --
+	(435.33,210.56) --
+	(435.71,210.79) --
+	(436.09,211.02) --
+	(436.47,211.25) --
+	(436.85,211.47) --
+	(437.23,211.70) --
+	(437.61,211.92) --
+	(437.99,212.14) --
+	(438.37,212.36) --
+	(438.75,212.58) --
+	(439.13,212.80) --
+	(439.51,213.01) --
+	(439.89,213.23) --
+	(440.27,213.44) --
+	(440.64,213.65) --
+	(441.02,213.86) --
+	(441.40,214.07) --
+	(441.78,214.27) --
+	(442.16,214.48) --
+	(442.54,214.68) --
+	(442.92,214.89) --
+	(443.30,215.09) --
+	(443.68,215.29) --
+	(444.06,215.48) --
+	(444.44,215.68) --
+	(444.82,215.88) --
+	(445.20,216.07) --
+	(445.58,216.26) --
+	(445.96,216.45) --
+	(446.34,216.64) --
+	(446.72,216.83) --
+	(447.10,217.02) --
+	(447.48,217.21) --
+	(447.86,217.39) --
+	(448.24,217.57) --
+	(448.62,217.76) --
+	(449.00,217.94) --
+	(449.38,218.11) --
+	(449.76,218.29) --
+	(450.14,218.47) --
+	(450.52,218.64) --
+	(450.90,218.82) --
+	(451.28,218.99) --
+	(451.66,219.16) --
+	(452.04,219.33) --
+	(452.42,219.50) --
+	(452.80,219.67) --
+	(453.18,219.84) --
+	(453.56,220.00) --
+	(453.93,220.16) --
+	(454.31,220.33) --
+	(454.69,220.49) --
+	(455.07,220.65) --
+	(455.45,220.81) --
+	(455.83,220.96) --
+	(456.21,221.12) --
+	(456.59,221.28) --
+	(456.97,221.43) --
+	(457.35,221.58) --
+	(457.73,221.73) --
+	(458.11,221.89) --
+	(458.49,222.03) --
+	(458.87,222.18) --
+	(459.25,222.33) --
+	(459.63,222.48) --
+	(460.01,222.62) --
+	(460.39,222.76) --
+	(460.77,222.91) --
+	(461.15,223.05) --
+	(461.53,223.19) --
+	(461.91,223.33) --
+	(462.29,223.47) --
+	(462.67,223.60) --
+	(463.05,223.74) --
+	(463.43,223.87) --
+	(463.81,224.01) --
+	(464.19,224.14) --
+	(464.57,224.27) --
+	(464.95,224.40) --
+	(465.33,224.53) --
+	(465.71,224.66) --
+	(466.09,224.79) --
+	(466.47,224.92) --
+	(466.85,225.04) --
+	(467.23,225.17) --
+	(467.60,225.29) --
+	(467.98,225.41) --
+	(468.36,225.53) --
+	(468.74,225.65) --
+	(469.12,225.77) --
+	(469.50,225.89) --
+	(469.88,226.01) --
+	(470.26,226.13) --
+	(470.64,226.24) --
+	(471.02,226.36) --
+	(471.40,226.47) --
+	(471.78,226.58) --
+	(472.16,226.70) --
+	(472.54,226.81) --
+	(472.92,226.92) --
+	(473.30,227.03) --
+	(473.68,227.13) --
+	(474.06,227.24) --
+	(474.44,227.35) --
+	(474.82,227.45) --
+	(475.20,227.56) --
+	(475.58,227.66) --
+	(475.96,227.77) --
+	(476.34,227.87) --
+	(476.72,227.97) --
+	(477.10,228.07) --
+	(477.48,228.17) --
+	(477.86,228.27) --
+	(478.24,228.37) --
+	(478.62,228.46) --
+	(479.00,228.56) --
+	(479.38,228.66) --
+	(479.76,228.75) --
+	(480.14,228.84) --
+	(480.52,228.94) --
+	(480.90,229.03) --
+	(481.27,229.12) --
+	(481.65,229.21) --
+	(482.03,229.30) --
+	(482.41,229.39) --
+	(482.79,229.48) --
+	(483.17,229.57) --
+	(483.55,229.66) --
+	(483.93,229.74) --
+	(484.31,229.83) --
+	(484.69,229.91) --
+	(485.07,230.00) --
+	(485.45,230.08) --
+	(485.83,230.16) --
+	(486.21,230.24) --
+	(486.59,230.33) --
+	(486.97,230.41) --
+	(487.35,230.49) --
+	(487.73,230.57) --
+	(488.11,230.64) --
+	(488.49,230.72) --
+	(488.87,230.80) --
+	(489.25,230.88) --
+	(489.63,230.95) --
+	(490.01,231.03) --
+	(490.39,231.10) --
+	(490.77,231.18) --
+	(491.15,231.25) --
+	(491.53,231.32) --
+	(491.91,231.39) --
+	(492.29,231.47) --
+	(492.67,231.54) --
+	(493.05,231.61) --
+	(493.43,231.68) --
+	(493.81,231.75) --
+	(494.19,231.81) --
+	(494.56,231.88) --
+	(494.94,231.95) --
+	(495.32,232.02) --
+	(495.70,232.08) --
+	(496.08,232.15) --
+	(496.46,232.21) --
+	(496.84,232.28) --
+	(497.22,232.34) --
+	(497.60,232.40) --
+	(497.98,232.47) --
+	(498.36,232.53) --
+	(498.74,232.59) --
+	(499.12,232.65) --
+	(499.50,232.71) --
+	(499.88,232.77) --
+	(500.26,232.83) --
+	(500.64,232.89) --
+	(501.02,232.95) --
+	(501.40,233.01) --
+	(501.78,233.06) --
+	(502.16,233.12) --
+	(502.54,233.18) --
+	(502.92,233.23) --
+	(503.30,233.29) --
+	(503.68,233.34) --
+	(504.06,233.40) --
+	(504.44,233.45) --
+	(504.82,233.50) --
+	(505.20,233.56) --
+	(505.58,233.61) --
+	(505.96,233.66) --
+	(506.34,233.71) --
+	(506.72,233.76) --
+	(507.10,233.81) --
+	(507.48,233.86) --
+	(507.86,233.91) --
+	(508.23,233.96) --
+	(508.61,234.01) --
+	(508.99,234.06) --
+	(509.37,234.11) --
+	(509.75,234.16) --
+	(510.13,234.20) --
+	(510.51,234.25) --
+	(510.89,234.30) --
+	(511.27,234.34) --
+	(511.65,234.39) --
+	(512.03,234.43) --
+	(512.41,234.48) --
+	(512.79,234.52) --
+	(513.17,234.56) --
+	(513.55,234.61) --
+	(513.93,234.65) --
+	(514.31,234.69) --
+	(514.69,234.74) --
+	(515.07,234.78) --
+	(515.45,234.82) --
+	(515.83,234.86) --
+	(516.21,234.90) --
+	(516.59,234.94) --
+	(516.97,234.98) --
+	(517.35,235.02) --
+	(517.73,235.06) --
+	(518.11,235.10) --
+	(518.49,235.14) --
+	(518.87,235.18) --
+	(519.25,235.22) --
+	(519.63,235.25) --
+	(520.01,235.29) --
+	(520.39,235.33) --
+	(520.77,235.36) --
+	(521.15,235.40) --
+	(521.53,235.44) --
+	(521.90,235.47) --
+	(522.28,235.51) --
+	(522.66,235.54) --
+	(523.04,235.58) --
+	(523.42,235.61) --
+	(523.80,235.64) --
+	(524.18,235.68) --
+	(524.56,235.71) --
+	(524.94,235.74) --
+	(525.32,235.78) --
+	(525.70,235.81) --
+	(526.08,235.84) --
+	(526.46,235.87) --
+	(526.84,235.91) --
+	(527.22,235.94) --
+	(527.60,235.97) --
+	(527.98,236.00) --
+	(528.36,236.03);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 82.52) --
+	(339.26, 82.40) --
+	(339.64, 82.27) --
+	(340.02, 82.15) --
+	(340.40, 82.02) --
+	(340.78, 81.90) --
+	(341.16, 81.77) --
+	(341.54, 81.65) --
+	(341.92, 81.53) --
+	(342.30, 81.40) --
+	(342.68, 81.28) --
+	(343.06, 81.16) --
+	(343.44, 81.04) --
+	(343.82, 80.92) --
+	(344.20, 80.80) --
+	(344.58, 80.68) --
+	(344.96, 80.56) --
+	(345.34, 80.44) --
+	(345.71, 80.32) --
+	(346.09, 80.20) --
+	(346.47, 80.08) --
+	(346.85, 79.96) --
+	(347.23, 79.84) --
+	(347.61, 79.73) --
+	(347.99, 79.61) --
+	(348.37, 79.49) --
+	(348.75, 79.37) --
+	(349.13, 79.26) --
+	(349.51, 79.14) --
+	(349.89, 79.03) --
+	(350.27, 78.91) --
+	(350.65, 78.80) --
+	(351.03, 78.68) --
+	(351.41, 78.57) --
+	(351.79, 78.46) --
+	(352.17, 78.34) --
+	(352.55, 78.23) --
+	(352.93, 78.12) --
+	(353.31, 78.01) --
+	(353.69, 77.90) --
+	(354.07, 77.78) --
+	(354.45, 77.67) --
+	(354.83, 77.56) --
+	(355.21, 77.45) --
+	(355.59, 77.34) --
+	(355.97, 77.23) --
+	(356.35, 77.12) --
+	(356.73, 77.02) --
+	(357.11, 76.91) --
+	(357.49, 76.80) --
+	(357.87, 76.69) --
+	(358.25, 76.58) --
+	(358.63, 76.48) --
+	(359.01, 76.37) --
+	(359.38, 76.26) --
+	(359.76, 76.16) --
+	(360.14, 76.05) --
+	(360.52, 75.95) --
+	(360.90, 75.84) --
+	(361.28, 75.74) --
+	(361.66, 75.63) --
+	(362.04, 75.53) --
+	(362.42, 75.43) --
+	(362.80, 75.32) --
+	(363.18, 75.22) --
+	(363.56, 75.12) --
+	(363.94, 75.02) --
+	(364.32, 74.92) --
+	(364.70, 74.81) --
+	(365.08, 74.71) --
+	(365.46, 74.61) --
+	(365.84, 74.51) --
+	(366.22, 74.41) --
+	(366.60, 74.31) --
+	(366.98, 74.21) --
+	(367.36, 74.12) --
+	(367.74, 74.02) --
+	(368.12, 73.92) --
+	(368.50, 73.82) --
+	(368.88, 73.72) --
+	(369.26, 73.63) --
+	(369.64, 73.53) --
+	(370.02, 73.43) --
+	(370.40, 73.34) --
+	(370.78, 73.24) --
+	(371.16, 73.15) --
+	(371.54, 73.05) --
+	(371.92, 72.96) --
+	(372.30, 72.86) --
+	(372.68, 72.77) --
+	(373.05, 72.67) --
+	(373.43, 72.58) --
+	(373.81, 72.49) --
+	(374.19, 72.39) --
+	(374.57, 72.30) --
+	(374.95, 72.21) --
+	(375.33, 72.12) --
+	(375.71, 72.03) --
+	(376.09, 71.93) --
+	(376.47, 71.84) --
+	(376.85, 71.75) --
+	(377.23, 71.66) --
+	(377.61, 71.57) --
+	(377.99, 71.48) --
+	(378.37, 71.39) --
+	(378.75, 71.30) --
+	(379.13, 71.22) --
+	(379.51, 71.13) --
+	(379.89, 71.04) --
+	(380.27, 70.95) --
+	(380.65, 70.86) --
+	(381.03, 70.78) --
+	(381.41, 70.69) --
+	(381.79, 70.60) --
+	(382.17, 70.52) --
+	(382.55, 70.43) --
+	(382.93, 70.35) --
+	(383.31, 70.26) --
+	(383.69, 70.18) --
+	(384.07, 70.09) --
+	(384.45, 70.01) --
+	(384.83, 69.92) --
+	(385.21, 69.84) --
+	(385.59, 69.76) --
+	(385.97, 69.67) --
+	(386.34, 69.59) --
+	(386.72, 69.51) --
+	(387.10, 69.43) --
+	(387.48, 69.35) --
+	(387.86, 69.26) --
+	(388.24, 69.18) --
+	(388.62, 69.10) --
+	(389.00, 69.02) --
+	(389.38, 68.94) --
+	(389.76, 68.86) --
+	(390.14, 68.78) --
+	(390.52, 68.70) --
+	(390.90, 68.62) --
+	(391.28, 68.54) --
+	(391.66, 68.47) --
+	(392.04, 68.39) --
+	(392.42, 68.31) --
+	(392.80, 68.23) --
+	(393.18, 68.15) --
+	(393.56, 68.08) --
+	(393.94, 68.00) --
+	(394.32, 67.92) --
+	(394.70, 67.85) --
+	(395.08, 67.77) --
+	(395.46, 67.70) --
+	(395.84, 67.62) --
+	(396.22, 67.55) --
+	(396.60, 67.47) --
+	(396.98, 67.40) --
+	(397.36, 67.32) --
+	(397.74, 67.25) --
+	(398.12, 67.18) --
+	(398.50, 67.10) --
+	(398.88, 67.03) --
+	(399.26, 66.96) --
+	(399.64, 66.88) --
+	(400.01, 66.81) --
+	(400.39, 66.74) --
+	(400.77, 66.67) --
+	(401.15, 66.60) --
+	(401.53, 66.53) --
+	(401.91, 66.45) --
+	(402.29, 66.38) --
+	(402.67, 66.31) --
+	(403.05, 66.24) --
+	(403.43, 66.17) --
+	(403.81, 66.10) --
+	(404.19, 66.03) --
+	(404.57, 65.97) --
+	(404.95, 65.90) --
+	(405.33, 65.83) --
+	(405.71, 65.76) --
+	(406.09, 65.69) --
+	(406.47, 65.62) --
+	(406.85, 65.56) --
+	(407.23, 65.49) --
+	(407.61, 65.42) --
+	(407.99, 65.36) --
+	(408.37, 65.29) --
+	(408.75, 65.22) --
+	(409.13, 65.16) --
+	(409.51, 65.09) --
+	(409.89, 65.03) --
+	(410.27, 64.96) --
+	(410.65, 64.90) --
+	(411.03, 64.83) --
+	(411.41, 64.77) --
+	(411.79, 64.70) --
+	(412.17, 64.64) --
+	(412.55, 64.58) --
+	(412.93, 64.51) --
+	(413.31, 64.45) --
+	(413.68, 64.39) --
+	(414.06, 64.33) --
+	(414.44, 64.26) --
+	(414.82, 64.20) --
+	(415.20, 64.14) --
+	(415.58, 64.08) --
+	(415.96, 64.02) --
+	(416.34, 63.96) --
+	(416.72, 63.89) --
+	(417.10, 63.83) --
+	(417.48, 63.77) --
+	(417.86, 63.71) --
+	(418.24, 63.65) --
+	(418.62, 63.59) --
+	(419.00, 63.53) --
+	(419.38, 63.47) --
+	(419.76, 63.42) --
+	(420.14, 63.36) --
+	(420.52, 63.30) --
+	(420.90, 63.24) --
+	(421.28, 63.18) --
+	(421.66, 63.12) --
+	(422.04, 63.07) --
+	(422.42, 63.01) --
+	(422.80, 62.95) --
+	(423.18, 62.90) --
+	(423.56, 62.84) --
+	(423.94, 62.78) --
+	(424.32, 62.73) --
+	(424.70, 62.67) --
+	(425.08, 62.61) --
+	(425.46, 62.56) --
+	(425.84, 62.50) --
+	(426.22, 62.45) --
+	(426.60, 62.39) --
+	(426.97, 62.34) --
+	(427.35, 62.28) --
+	(427.73, 62.23) --
+	(428.11, 62.18) --
+	(428.49, 62.12) --
+	(428.87, 62.07) --
+	(429.25, 62.02) --
+	(429.63, 61.96) --
+	(430.01, 61.91) --
+	(430.39, 61.86) --
+	(430.77, 61.80) --
+	(431.15, 61.75) --
+	(431.53, 61.70) --
+	(431.91, 61.65) --
+	(432.29, 61.60) --
+	(432.67, 61.55) --
+	(433.05, 61.49) --
+	(433.43, 61.44) --
+	(433.81, 61.39) --
+	(434.19, 61.34) --
+	(434.57, 61.29) --
+	(434.95, 61.24) --
+	(435.33, 61.19) --
+	(435.71, 61.14) --
+	(436.09, 61.09) --
+	(436.47, 61.04) --
+	(436.85, 60.99) --
+	(437.23, 60.94) --
+	(437.61, 60.90) --
+	(437.99, 60.85) --
+	(438.37, 60.80) --
+	(438.75, 60.75) --
+	(439.13, 60.70) --
+	(439.51, 60.66) --
+	(439.89, 60.61) --
+	(440.27, 60.56) --
+	(440.64, 60.51) --
+	(441.02, 60.47) --
+	(441.40, 60.42) --
+	(441.78, 60.37) --
+	(442.16, 60.33) --
+	(442.54, 60.28) --
+	(442.92, 60.23) --
+	(443.30, 60.19) --
+	(443.68, 60.14) --
+	(444.06, 60.10) --
+	(444.44, 60.05) --
+	(444.82, 60.01) --
+	(445.20, 59.96) --
+	(445.58, 59.92) --
+	(445.96, 59.87) --
+	(446.34, 59.83) --
+	(446.72, 59.78) --
+	(447.10, 59.74) --
+	(447.48, 59.70) --
+	(447.86, 59.65) --
+	(448.24, 59.61) --
+	(448.62, 59.57) --
+	(449.00, 59.52) --
+	(449.38, 59.48) --
+	(449.76, 59.44) --
+	(450.14, 59.40) --
+	(450.52, 59.35) --
+	(450.90, 59.31) --
+	(451.28, 59.27) --
+	(451.66, 59.23) --
+	(452.04, 59.19) --
+	(452.42, 59.14) --
+	(452.80, 59.10) --
+	(453.18, 59.06) --
+	(453.56, 59.02) --
+	(453.93, 58.98) --
+	(454.31, 58.94) --
+	(454.69, 58.90) --
+	(455.07, 58.86) --
+	(455.45, 58.82) --
+	(455.83, 58.78) --
+	(456.21, 58.74) --
+	(456.59, 58.70) --
+	(456.97, 58.66) --
+	(457.35, 58.62) --
+	(457.73, 58.58) --
+	(458.11, 58.54) --
+	(458.49, 58.50) --
+	(458.87, 58.47) --
+	(459.25, 58.43) --
+	(459.63, 58.39) --
+	(460.01, 58.35) --
+	(460.39, 58.31) --
+	(460.77, 58.27) --
+	(461.15, 58.24) --
+	(461.53, 58.20) --
+	(461.91, 58.16) --
+	(462.29, 58.13) --
+	(462.67, 58.09) --
+	(463.05, 58.05) --
+	(463.43, 58.01) --
+	(463.81, 57.98) --
+	(464.19, 57.94) --
+	(464.57, 57.91) --
+	(464.95, 57.87) --
+	(465.33, 57.83) --
+	(465.71, 57.80) --
+	(466.09, 57.76) --
+	(466.47, 57.73) --
+	(466.85, 57.69) --
+	(467.23, 57.66) --
+	(467.60, 57.62) --
+	(467.98, 57.59) --
+	(468.36, 57.55) --
+	(468.74, 57.52) --
+	(469.12, 57.48) --
+	(469.50, 57.45) --
+	(469.88, 57.41) --
+	(470.26, 57.38) --
+	(470.64, 57.35) --
+	(471.02, 57.31) --
+	(471.40, 57.28) --
+	(471.78, 57.25) --
+	(472.16, 57.21) --
+	(472.54, 57.18) --
+	(472.92, 57.15) --
+	(473.30, 57.11) --
+	(473.68, 57.08) --
+	(474.06, 57.05) --
+	(474.44, 57.02) --
+	(474.82, 56.98) --
+	(475.20, 56.95) --
+	(475.58, 56.92) --
+	(475.96, 56.89) --
+	(476.34, 56.86) --
+	(476.72, 56.83) --
+	(477.10, 56.79) --
+	(477.48, 56.76) --
+	(477.86, 56.73) --
+	(478.24, 56.70) --
+	(478.62, 56.67) --
+	(479.00, 56.64) --
+	(479.38, 56.61) --
+	(479.76, 56.58) --
+	(480.14, 56.55) --
+	(480.52, 56.52) --
+	(480.90, 56.49) --
+	(481.27, 56.46) --
+	(481.65, 56.43) --
+	(482.03, 56.40) --
+	(482.41, 56.37) --
+	(482.79, 56.34) --
+	(483.17, 56.31) --
+	(483.55, 56.28) --
+	(483.93, 56.25) --
+	(484.31, 56.22) --
+	(484.69, 56.19) --
+	(485.07, 56.16) --
+	(485.45, 56.14) --
+	(485.83, 56.11) --
+	(486.21, 56.08) --
+	(486.59, 56.05) --
+	(486.97, 56.02) --
+	(487.35, 55.99) --
+	(487.73, 55.97) --
+	(488.11, 55.94) --
+	(488.49, 55.91) --
+	(488.87, 55.88) --
+	(489.25, 55.86) --
+	(489.63, 55.83) --
+	(490.01, 55.80) --
+	(490.39, 55.78) --
+	(490.77, 55.75) --
+	(491.15, 55.72) --
+	(491.53, 55.69) --
+	(491.91, 55.67) --
+	(492.29, 55.64) --
+	(492.67, 55.62) --
+	(493.05, 55.59) --
+	(493.43, 55.56) --
+	(493.81, 55.54) --
+	(494.19, 55.51) --
+	(494.56, 55.49) --
+	(494.94, 55.46) --
+	(495.32, 55.43) --
+	(495.70, 55.41) --
+	(496.08, 55.38) --
+	(496.46, 55.36) --
+	(496.84, 55.33) --
+	(497.22, 55.31) --
+	(497.60, 55.28) --
+	(497.98, 55.26) --
+	(498.36, 55.23) --
+	(498.74, 55.21) --
+	(499.12, 55.19) --
+	(499.50, 55.16) --
+	(499.88, 55.14) --
+	(500.26, 55.11) --
+	(500.64, 55.09) --
+	(501.02, 55.06) --
+	(501.40, 55.04) --
+	(501.78, 55.02) --
+	(502.16, 54.99) --
+	(502.54, 54.97) --
+	(502.92, 54.95) --
+	(503.30, 54.92) --
+	(503.68, 54.90) --
+	(504.06, 54.88) --
+	(504.44, 54.85) --
+	(504.82, 54.83) --
+	(505.20, 54.81) --
+	(505.58, 54.79) --
+	(505.96, 54.76) --
+	(506.34, 54.74) --
+	(506.72, 54.72) --
+	(507.10, 54.70) --
+	(507.48, 54.67) --
+	(507.86, 54.65) --
+	(508.23, 54.63) --
+	(508.61, 54.61) --
+	(508.99, 54.59) --
+	(509.37, 54.57) --
+	(509.75, 54.54) --
+	(510.13, 54.52) --
+	(510.51, 54.50) --
+	(510.89, 54.48) --
+	(511.27, 54.46) --
+	(511.65, 54.44) --
+	(512.03, 54.42) --
+	(512.41, 54.40) --
+	(512.79, 54.37) --
+	(513.17, 54.35) --
+	(513.55, 54.33) --
+	(513.93, 54.31) --
+	(514.31, 54.29) --
+	(514.69, 54.27) --
+	(515.07, 54.25) --
+	(515.45, 54.23) --
+	(515.83, 54.21) --
+	(516.21, 54.19) --
+	(516.59, 54.17) --
+	(516.97, 54.15) --
+	(517.35, 54.13) --
+	(517.73, 54.11) --
+	(518.11, 54.09) --
+	(518.49, 54.07) --
+	(518.87, 54.05) --
+	(519.25, 54.03) --
+	(519.63, 54.01) --
+	(520.01, 54.00) --
+	(520.39, 53.98) --
+	(520.77, 53.96) --
+	(521.15, 53.94) --
+	(521.53, 53.92) --
+	(521.90, 53.90) --
+	(522.28, 53.88) --
+	(522.66, 53.86) --
+	(523.04, 53.85) --
+	(523.42, 53.83) --
+	(523.80, 53.81) --
+	(524.18, 53.79) --
+	(524.56, 53.77) --
+	(524.94, 53.75) --
+	(525.32, 53.74) --
+	(525.70, 53.72) --
+	(526.08, 53.70) --
+	(526.46, 53.68) --
+	(526.84, 53.67) --
+	(527.22, 53.65) --
+	(527.60, 53.63) --
+	(527.98, 53.61) --
+	(528.36, 53.60);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (345.90, 49.80) -- (521.34, 49.80);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (345.90, 49.80) -- (345.90, 44.82);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 49.80) -- (528.36, 49.80);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 49.80) -- (338.88, 44.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (386.25, 49.80) -- (386.25, 44.82);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (521.34, 49.80) -- (521.34, 44.82);
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (348.76, 39.84) {nocons (\textit{real})};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (436.48, 39.84) {cons (\textit{real})};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (524.20, 39.84) {adapt (\textit{real})};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 56.82) -- (338.88,216.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 56.82) -- (333.90, 56.82);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 96.66) -- (333.90, 96.66);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,136.50) -- (333.90,136.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,176.33) -- (333.90,176.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,216.17) -- (333.90,216.17);
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (326.93, 56.82) {0};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (326.93, 96.66) {10};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (326.93,136.50) {20};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (326.93,176.33) {30};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (326.93,216.17) {40};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (480.99, 49.80) -- (480.99, 44.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (528.36, 49.80) -- (528.36, 44.82);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (338.88, 31.87) {0};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (386.25, 31.87) {5};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (433.62, 31.87) {10};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (480.99, 31.87) {15};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (528.36, 31.87) {20};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 49.80) -- (338.88,239.28);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 49.80) -- (333.90, 49.80);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 87.70) -- (333.90, 87.70);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,125.59) -- (333.90,125.59);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,163.49) -- (333.90,163.49);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,201.38) -- (333.90,201.38);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,239.28) -- (333.90,239.28);
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92, 46.94) {0.0};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92, 84.84) {0.2};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,122.73) {0.4};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,160.63) {0.6};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,198.53) {0.8};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,236.42) {1.0};
 \end{scope}

### 2020-08-10 benchmarking/benchmarkingVM/ESS_round2.tex
results update

@@
-% Created by tikzDevice version 0.12.3 on 2020-08-07 14:28:37
+% Created by tikzDevice version 0.12.3 on 2020-08-10 16:04:21
 % !TEX encoding = UTF-8 Unicode
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,548.96) {\bfseries Comparison of adapt (\textit{real}) and \textit{cat}};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,301.03) {ESS/chain [\textit{cat}]};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,433.62) {ESS/chain [adapt (\textit{real})]};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,548.96) {\bfseries adapt (\textit{real}) vs. adapt (\textit{cat})};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,301.03) {ESS/hr [adapt (\textit{cat})]};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,433.62) {ESS/hr [adapt (\textit{real})]};
 \end{scope}
@@
 \definecolor{drawColor}{RGB}{0,0,0}
-\definecolor{fillColor}{gray}{0.91}
-
-\path[draw=drawColor,line width= 0.1pt,line join=round,line cap=round,fill=fillColor] (  0.00,370.60) --
-	(207.56,578.16) --
-	(284.41,578.16) --
-	(284.41,491.97) --
-	(  0.00,207.56) --
-	cycle;
-\definecolor{fillColor}{RGB}{190,190,190}
-
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] (  0.00,343.43) --
-	(234.73,578.16) --
-	(284.41,578.16) --
-	(284.41,519.15) --
-	(  0.00,234.73) --
-	cycle;
-\definecolor{fillColor}{RGB}{169,169,169}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (  0.00,316.25) --
-	(261.91,578.16) --
-	(284.41,578.16) --
-	(284.41,546.32) --
-	(  0.00,261.91) --
-	cycle;
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (138.85,342.31) {$\frac{1}{64} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,431.83) {$64\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (111.68,342.31) {$\frac{1}{16} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,404.66) {$16\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 82.85,342.31) {$\frac{1}{4} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92,377.49) {$4\times$};
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,528.36);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.85,501.35) --
-	(160.70,501.35);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (156.77,498.73) --
-	(156.77,503.66);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (156.77,498.12) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.10,505.21) --
-	(226.15,505.21);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (224.23,503.12) --
-	(224.23,507.10);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (224.23,501.18) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.91,510.62) --
-	(195.69,510.62);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.30,510.51) --
-	(195.30,510.72);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.30,506.58) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (150.45,465.30) --
-	(158.07,465.30);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (154.63,461.56) --
-	(154.63,468.44);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (154.63,461.27) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (143.37,486.93) --
-	(159.52,486.93);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.06,482.33) --
-	(153.06,490.65);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (153.06,484.03) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.81,519.93) --
-	(232.76,519.93);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.29,519.53) --
-	(232.29,520.32);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (232.29,517.02) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.38,481.29) --
-	(197.55,481.29);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.14,479.06) --
-	(195.14,483.29);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.14,478.06) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.44,517.15) --
-	(231.91,517.15);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.19,515.64) --
-	(231.19,518.55);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (231.19,513.12) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.86,520.80) --
-	(226.63,520.80);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.25,520.64) --
-	(226.25,520.95);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (226.25,516.76) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.50,451.92) --
-	(178.74,451.92);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.28,448.49) --
-	(174.28,454.83);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.28,447.88) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.34,477.13) --
-	(194.89,477.13);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.89,473.94) --
-	(191.89,479.87);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.89,474.22) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.29,524.26) --
-	(235.63,524.26);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.46,523.85) --
-	(235.46,524.66);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (235.46,521.35) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (219.41,503.79) --
-	(222.44,503.79);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.99,500.06) --
-	(220.99,506.92);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.99,500.56) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.74,495.12) --
-	(212.21,495.12);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.55,492.24) --
-	(210.55,497.62);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.55,491.08) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.33,521.42) --
-	(228.35,521.42);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.85,521.06) --
-	(227.85,521.77);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (227.85,517.38) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.31,503.68) --
-	(212.31,503.68);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.41,503.51) --
-	(210.41,503.85);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.41,499.64) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.56,505.84) --
-	(217.05,505.84);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (214.93,502.42) --
-	(214.93,508.74);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (214.93,502.93) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.33,496.74) --
-	(152.55,496.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (141.01,490.27) --
-	(141.01,501.59);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (141.01,493.51) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.17,497.06) --
-	(223.98,497.06);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.95,494.75) --
-	(218.95,499.12);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (218.95,493.03) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (127.87,510.44) --
-	(136.69,510.44);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (132.77,509.25) --
-	(132.77,511.57);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (132.77,506.41) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (122.43,470.48) --
-	(153.27,470.48);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (143.38,460.23) --
-	(143.38,477.18);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (143.38,466.45) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.53,499.18) --
-	(134.19,499.18);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (128.53,493.87) --
-	(128.53,503.35);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (128.53,496.28) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.21,524.80) --
-	(235.92,524.80);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.57,524.57) --
-	(235.57,525.02);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (235.57,521.89) {$\mu$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.15,508.68) --
-	(210.57,508.68);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.05,505.52) --
-	(206.05,511.41);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (206.05,505.46) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (167.79,509.64) --
-	(219.64,509.64);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (207.40,499.41) --
-	(207.40,516.32);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.40,505.60) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.29,518.51) --
-	(227.21,518.51);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.27,517.93) --
-	(226.27,519.08);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (226.27,514.48) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.98,478.53) --
-	(195.19,478.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.02,472.24) --
-	(190.02,483.29);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.02,474.50) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.02,507.50) --
-	(212.05,507.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.06,502.00) --
-	(211.06,511.78);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.06,504.59) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.89,524.89) --
-	(238.66,524.89);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (236.87,523.29) --
-	(236.87,526.36);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (236.87,521.98) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.69,491.89) --
-	(181.70,491.89);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (178.93,489.89) --
-	(178.93,493.70);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (178.93,488.66) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.17,513.22) --
-	(230.44,513.22);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.82,511.43) --
-	(229.82,514.87);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (229.82,509.19) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.44,515.26) --
-	(219.18,515.26);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.81,514.88) --
-	(218.81,515.64);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (218.81,511.23) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.99,482.35) --
-	(176.42,482.35);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.05,479.47) --
-	(173.05,484.86);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.05,478.32) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.60,487.67) --
-	(185.47,487.67);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (183.18,486.01) --
-	(183.18,489.20);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.18,484.76) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.29,519.28) --
-	(230.98,519.28);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.64,518.95) --
-	(230.64,519.61);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (230.64,516.38) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.39,505.99) --
-	(174.41,505.99);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.66,505.16) --
-	(169.66,506.79);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.66,502.77) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.75,506.32) --
-	(230.90,506.32);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.39,504.70) --
-	(229.39,507.81);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (229.39,502.28) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.03,511.42) --
-	(206.39,511.42);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.21,511.15) --
-	(206.21,511.69);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (206.21,507.39) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.24,482.46) --
-	(177.13,482.46);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.28,481.27) --
-	(175.28,483.58);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (175.28,478.43) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.62,482.96) --
-	(187.77,482.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.37,480.13) --
-	(185.37,485.43);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.37,480.05) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,374.64) --
+	(203.52,578.16);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (286.65,578.16) --
+	(286.65,490.17) --
+	(  0.00,203.52);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (  0.00,346.12) --
+	(232.04,578.16);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (286.65,578.16) --
+	(286.65,518.69) --
+	(  0.00,232.04);
+
+\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (  0.00,317.60) --
+	(260.56,578.16);
+
+\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (286.65,578.16) --
+	(286.65,547.21) --
+	(  0.00,260.56);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (142.89,342.31) {$\frac{1}{64} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,435.87) {$64\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (114.37,342.31) {$\frac{1}{16} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,407.35) {$16\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 84.20,342.31) {$\frac{1}{4} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92,378.83) {$4\times$};
+
+\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,528.36);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 96.83,462.17) --
+	(104.39,462.17);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.95,455.39) --
+	(100.95,467.26);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (100.95,458.94) {$p$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (157.25,462.51) --
+	(190.79,462.51);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.21,460.09) --
+	(180.21,464.68);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.21,458.48) {$L$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.00,476.56) --
+	(103.04,476.56);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.41,475.30) --
+	( 99.41,477.74);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 99.41,472.52) {$r$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.19,434.62) --
+	(105.17,434.62);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (102.83,423.86) --
+	(102.83,441.65);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (102.83,430.59) {$h$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.73,464.74) --
+	( 95.52,464.74);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 90.46,459.17) --
+	( 90.46,469.12);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 90.46,461.83) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.57,483.53) --
+	(194.99,483.53);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.78,482.91) --
+	(194.78,484.13);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.78,480.62) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.61,467.01) --
+	(116.13,467.01);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.49,464.26) --
+	(109.49,469.44);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (109.49,463.79) {$p$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.07,471.07) --
+	(193.44,471.07);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.83,468.87) --
+	(191.83,473.05);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.83,467.03) {$L$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (164.54,476.74) --
+	(164.84,476.74);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (164.69,476.63) --
+	(164.69,476.85);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (164.69,472.71) {$r$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.97,429.18) --
+	(112.07,429.18);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (107.26,425.26) --
+	(107.26,432.48);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (107.26,425.15) {$h$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (103.25,451.88) --
+	(115.87,451.88);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (110.51,447.05) --
+	(110.51,455.79);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (110.51,448.98) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.12,485.74) --
+	(196.43,485.74);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.27,485.16) --
+	(196.27,486.31);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.27,482.84) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.15,474.71) --
+	(181.63,474.71);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.43,471.39) --
+	(177.43,477.57);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.43,471.49) {$p$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.21,475.71) --
+	(184.09,475.71);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.98,464.98) --
+	(174.98,482.73);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.98,471.68) {$L$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.98,485.03) --
+	(197.78,485.03);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.38,484.42) --
+	(197.38,485.62);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.38,481.00) {$r$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (150.24,443.07) --
+	(164.70,443.07);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.71,436.47) --
+	(158.71,448.06);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.71,439.03) {$h$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (178.58,473.47) --
+	(182.90,473.47);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.86,467.70) --
+	(180.86,477.96);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.86,470.56) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.48,498.31) --
+	(212.33,498.31);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.49,497.03) --
+	(210.49,499.52);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.49,495.41) {$\kappa$};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,338.88) -- (230.34,338.88);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,338.88);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 94.93,338.88) -- ( 94.93,333.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.07,338.88) -- (140.07,333.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.20,338.88) -- (185.20,333.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.34,338.88) -- (230.34,333.90);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 97.17,338.88) -- ( 97.17,333.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (144.54,338.88) -- (144.54,333.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.91,338.88) -- (191.91,333.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.28,338.88) -- (239.28,333.90);
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 94.93,320.95) {10};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (140.07,320.95) {100};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (185.20,320.95) {1000};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (230.34,320.95) {10000};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,338.88) -- ( 49.80,519.42);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 97.17,320.95) {10};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (144.54,320.95) {100};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (191.91,320.95) {1000};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (239.28,320.95) {10000};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,338.88) -- ( 49.80,528.36);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,384.01) -- ( 44.82,384.01);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,429.15) -- ( 44.82,429.15);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,474.28) -- ( 44.82,474.28);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,519.42) -- ( 44.82,519.42);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,386.25) -- ( 44.82,386.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,433.62) -- ( 44.82,433.62);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,480.99) -- ( 44.82,480.99);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,528.36) -- ( 44.82,528.36);
 
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,381.16) {10};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,426.29) {100};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,471.42) {1000};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,516.56) {10000};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,383.39) {10};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,430.76) {100};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,478.13) {1000};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,525.50) {10000};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,548.96) {\bfseries Comparison of adapt (\textit{quant}) and \textit{cat}};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,301.03) {ESS/chain [\textit{cat}]};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (307.01,433.62) {ESS/chain [adapt (\textit{quant})]};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,548.96) {\bfseries adapt (\textit{quant}) vs. adapt (\textit{cat})};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,301.03) {ESS/hr [adapt (\textit{cat})]};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (307.01,433.62) {ESS/hr [adapt (\textit{quant})]};
 \end{scope}
@@
 \definecolor{drawColor}{RGB}{0,0,0}
-\definecolor{fillColor}{gray}{0.91}
-
-\path[draw=drawColor,line width= 0.1pt,line join=round,line cap=round,fill=fillColor] (158.34,239.86) --
-	(496.64,578.16) --
-	(573.49,578.16) --
-	(573.49,491.97) --
-	(158.34, 76.82) --
-	cycle;
-\definecolor{fillColor}{RGB}{190,190,190}
-
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] (158.34,212.69) --
-	(523.81,578.16) --
-	(573.49,578.16) --
-	(573.49,519.15) --
-	(158.34,104.00) --
-	cycle;
-\definecolor{fillColor}{RGB}{169,169,169}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.34,185.52) --
-	(550.99,578.16) --
-	(573.49,578.16) --
-	(573.49,546.32) --
-	(158.34,131.17) --
-	cycle;
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (427.93,342.31) {$\frac{1}{64} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,431.83) {$64\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (400.76,342.31) {$\frac{1}{16} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,404.66) {$16\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (371.93,342.31) {$\frac{1}{4} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.00,377.49) {$4\times$};
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (338.88,338.88) -- (528.36,528.36);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (440.93,459.60) --
-	(449.78,459.60);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (445.85,450.75) --
-	(445.85,465.67);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (445.85,456.37) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (511.18,510.65) --
-	(515.23,510.65);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (513.31,508.40) --
-	(513.31,512.67);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (513.31,506.62) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.99,510.45) --
-	(484.77,510.45);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (484.38,509.13) --
-	(484.38,511.69);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (484.38,506.42) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (439.53,456.23) --
-	(447.15,456.23);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.71,441.90) --
-	(443.71,464.42);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (443.71,452.20) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (432.45,444.54) --
-	(448.60,444.54);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (442.14,433.29) --
-	(442.14,451.64);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (442.14,441.64) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (520.89,520.56) --
-	(521.84,520.56);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (521.37,520.43) --
-	(521.37,520.69);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (521.37,517.66) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (508.49,517.93) --
-	(511.52,517.93);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (510.07,516.34) --
-	(510.07,519.39);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (510.07,514.70) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (497.82,524.11) --
-	(501.29,524.11);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.63,523.95) --
-	(499.63,524.26);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (499.63,520.07) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (516.41,522.33) --
-	(517.43,522.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (516.93,521.18) --
-	(516.93,523.42);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (516.93,518.30) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (497.39,501.55) --
-	(501.39,501.55);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.49,497.15) --
-	(499.49,505.13);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (499.49,497.51) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (501.64,509.18) --
-	(506.13,509.18);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (504.01,505.39) --
-	(504.01,512.36);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (504.01,506.28) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (398.41,435.61) --
-	(441.63,435.61);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (430.09,420.47) --
-	(430.09,444.05);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (430.09,432.38) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (501.25,509.83) --
-	(513.06,509.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (508.03,509.03) --
-	(508.03,510.60);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (508.03,505.80) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (416.95,506.98) --
-	(425.77,506.98);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.85,503.20) --
-	(421.85,510.16);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (421.85,502.95) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (411.51,435.35) --
-	(442.35,435.35);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (432.46,415.96) --
-	(432.46,444.90);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (432.46,431.31) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (409.61,405.29) --
-	(423.27,405.29);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.61,396.70) --
-	(417.61,411.24);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (417.61,402.38) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (524.29,524.30) --
-	(525.00,524.30);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (524.65,523.97) --
-	(524.65,524.62);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (524.65,521.39) {$\mu$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (489.23,503.26) --
-	(499.65,503.26);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.13,500.41) --
-	(495.13,505.76);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (495.13,500.04) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (456.87,516.19) --
-	(508.72,516.19);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (496.48,513.31) --
-	(496.48,518.70);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (496.48,512.15) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (514.37,520.99) --
-	(516.29,520.99);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (515.35,520.33) --
-	(515.35,521.63);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (515.35,516.96) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (472.06,483.75) --
-	(484.27,483.75);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.10,479.62) --
-	(479.10,487.16);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (479.10,479.72) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.10,504.58) --
-	(501.13,504.58);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (500.14,502.22) --
-	(500.14,506.68);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (500.14,501.67) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (523.97,525.79) --
-	(527.74,525.79);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (525.95,524.73) --
-	(525.95,526.80);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (525.95,522.89) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.77,486.85) --
-	(470.78,486.85);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (468.01,482.06) --
-	(468.01,490.70);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.01,483.63) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (518.25,513.57) --
-	(519.52,513.57);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (518.90,511.88) --
-	(518.90,515.13);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (518.90,509.54) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (507.52,517.40) --
-	(508.26,517.40);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (507.89,515.55) --
-	(507.89,519.09);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (507.89,513.37) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (458.07,484.33) --
-	(465.50,484.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.13,477.88) --
-	(462.13,489.18);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (462.13,480.30) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (469.68,483.35) --
-	(474.55,483.35);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (472.26,480.89) --
-	(472.26,485.53);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (472.26,480.45) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (519.37,519.43) --
-	(520.06,519.43);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (519.72,518.97) --
-	(519.72,519.89);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (519.72,516.53) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (452.47,471.75) --
-	(463.49,471.75);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (458.74,469.32) --
-	(458.74,473.92);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (458.74,468.53) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (516.83,516.44) --
-	(519.98,516.44);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (518.47,514.31) --
-	(518.47,518.36);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (518.47,512.41) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.11,516.44) --
-	(495.47,516.44);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.29,516.21) --
-	(495.29,516.67);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (495.29,512.41) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.32,485.53) --
-	(466.21,485.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.36,482.88) --
-	(464.36,487.86);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (464.36,481.49) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (471.70,475.69) --
-	(476.85,475.69);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.45,473.48) --
-	(474.45,477.68);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.45,472.79) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (149.40,234.96) --
+	(492.60,578.16);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (575.73,578.16) --
+	(575.73,490.17) --
+	(149.40, 63.84) --
+	(149.40,234.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (149.40,206.44) --
+	(521.12,578.16);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (575.73,578.16) --
+	(575.73,518.69) --
+	(149.40, 92.36) --
+	(149.40,206.44);
+
+\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (149.40,177.92) --
+	(549.64,578.16);
+
+\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (575.73,578.16) --
+	(575.73,547.21) --
+	(149.40,120.88) --
+	(149.40,177.92);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (431.97,342.31) {$\frac{1}{64} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,435.87) {$64\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (403.45,342.31) {$\frac{1}{16} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,407.35) {$16\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (373.28,342.31) {$\frac{1}{4} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.00,378.83) {$4\times$};
+
+\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (338.88,338.88) -- (528.36,528.36);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (385.91,398.02) --
+	(393.47,398.02);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (390.03,382.13) --
+	(390.03,406.87);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (390.03,394.79) {$p$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (446.33,475.91) --
+	(479.87,475.91);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (469.29,475.07) --
+	(469.29,476.72);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (469.29,471.88) {$L$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (384.08,472.93) --
+	(392.12,472.93);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (388.49,468.95) --
+	(388.49,476.26);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (388.49,468.89) {$r$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.27,397.74) --
+	(394.25,397.74);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (391.91,377.39) --
+	(391.91,407.77);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (391.91,393.71) {$h$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (372.81,366.19) --
+	(384.60,366.19);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (379.54,357.18) --
+	(379.54,372.44);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (379.54,363.29) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.65,483.32) --
+	(484.07,483.32);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.86,483.08) --
+	(483.86,483.56);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.86,480.42) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (388.69,424.26) --
+	(405.21,424.26);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (398.57,421.10) --
+	(398.57,427.01);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (398.57,421.04) {$p$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.15,476.34) --
+	(482.52,476.34);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (480.91,473.72) --
+	(480.91,478.65);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (480.91,472.30) {$L$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (453.62,477.11) --
+	(453.92,477.11);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (453.77,476.35) --
+	(453.77,477.84);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (453.77,473.07) {$r$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (390.05,422.63) --
+	(401.15,422.63);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (396.34,419.69) --
+	(396.34,425.20);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (396.34,418.60) {$h$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (392.33,405.99) --
+	(404.95,405.99);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (399.59,404.44) --
+	(399.59,407.42);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (399.59,403.08) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.20,485.27) --
+	(485.51,485.27);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.35,485.11) --
+	(485.35,485.43);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (485.35,482.37) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.23,469.66) --
+	(470.71,469.66);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (466.51,467.06) --
+	(466.51,471.96);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (466.51,466.43) {$p$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (447.29,481.52) --
+	(473.17,481.52);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.06,478.07) --
+	(464.06,484.47);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (464.06,477.48) {$L$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.06,487.79) --
+	(486.86,487.79);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.46,487.17) --
+	(486.46,488.40);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (486.46,483.76) {$r$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (439.32,448.83) --
+	(453.78,448.83);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (447.79,445.54) --
+	(447.79,451.66);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (447.79,444.80) {$h$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (467.66,470.37) --
+	(471.98,470.37);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (469.94,468.48) --
+	(469.94,472.10);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (469.94,467.47) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (497.56,499.91) --
+	(501.41,499.91);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.57,499.32) --
+	(499.57,500.49);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (499.57,497.01) {$\kappa$};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,338.88) -- (519.42,338.88);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,338.88) -- (528.36,338.88);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (384.01,338.88) -- (384.01,333.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (429.15,338.88) -- (429.15,333.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.28,338.88) -- (474.28,333.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (519.42,338.88) -- (519.42,333.90);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (386.25,338.88) -- (386.25,333.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.62,338.88) -- (433.62,333.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (480.99,338.88) -- (480.99,333.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (528.36,338.88) -- (528.36,333.90);
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (384.01,320.95) {10};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (429.15,320.95) {100};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (474.28,320.95) {1000};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (519.42,320.95) {10000};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,338.88) -- (338.88,519.42);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (386.25,320.95) {10};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (433.62,320.95) {100};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (480.99,320.95) {1000};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (528.36,320.95) {10000};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,338.88) -- (338.88,528.36);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,384.01) -- (333.90,384.01);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,429.15) -- (333.90,429.15);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,474.28) -- (333.90,474.28);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,519.42) -- (333.90,519.42);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,386.25) -- (333.90,386.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,433.62) -- (333.90,433.62);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,480.99) -- (333.90,480.99);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,528.36) -- (333.90,528.36);
 
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,381.16) {10};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,426.29) {100};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,471.42) {1000};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,516.56) {10000};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,383.39) {10};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,430.76) {100};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,478.13) {1000};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,525.50) {10000};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,259.88) {\bfseries Comparison of adapt (\textit{quant}) and adapt (\textit{real})};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54, 11.95) {ESS/chain [adapt (\textit{real})]};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,144.54) {ESS/chain [adapt (\textit{quant})]};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,259.88) {\bfseries adapt (\textit{quant}) vs. adapt (\textit{real})};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54, 11.95) {ESS/hr [adapt (\textit{real})]};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,144.54) {ESS/hr [adapt (\textit{quant})]};
 \end{scope}
@@
 \definecolor{drawColor}{RGB}{0,0,0}
-\definecolor{fillColor}{gray}{0.91}
-
-\path[draw=drawColor,line width= 0.1pt,line join=round,line cap=round,fill=fillColor] (  0.00, 82.29) --
-	(284.84,367.13) --
-	(284.84,202.55) --
-	( 82.29,  0.00) --
-	(  0.00,  0.00) --
-	cycle;
-\definecolor{fillColor}{RGB}{190,190,190}
-
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] (  0.00, 54.86) --
-	(284.84,339.70) --
-	(284.84,229.98) --
-	( 54.86,  0.00) --
-	(  0.00,  0.00) --
-	cycle;
-\definecolor{fillColor}{RGB}{169,169,169}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (  0.00, 27.43) --
-	(284.84,312.27) --
-	(284.84,257.41) --
-	( 27.43,  0.00) --
-	(  0.00,  0.00) --
-	cycle;
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (139.62, 53.23) {$\frac{1}{64} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,143.53) {$64\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (112.19, 53.23) {$\frac{1}{16} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,116.09) {$16\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 83.11, 53.23) {$\frac{1}{4} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92, 88.66) {$4\times$};
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 49.80, 49.80) -- (239.28,239.28);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.16,171.66) --
-	(216.14,171.66);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (213.81,162.73) --
-	(213.81,177.79);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (213.81,168.44) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.60,223.20) --
-	(219.61,223.20);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.71,220.93) --
-	(217.71,225.24);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (217.71,219.17) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.06,223.00) --
-	(223.27,223.00);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.16,221.67) --
-	(223.16,224.24);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (223.16,218.96) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.64,168.26) --
-	(180.59,168.26);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.42,153.80) --
-	(177.42,176.53);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.42,164.23) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.61,156.46) --
-	(203.01,156.46);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (199.25,145.11) --
-	(199.25,163.63);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.25,153.56) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.16,233.20) --
-	(232.96,233.20);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.56,233.07) --
-	(232.56,233.33);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (232.56,230.30) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.51,230.54) --
-	(219.43,230.54);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (216.27,228.94) --
-	(216.27,232.02);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (216.27,227.31) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.61,236.78) --
-	(210.05,236.78);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (207.52,236.62) --
-	(207.52,236.94);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.52,232.75) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (233.70,234.99) --
-	(234.42,234.99);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.07,233.83) --
-	(234.07,236.08);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (234.07,230.95) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.98,214.01) --
-	(216.33,214.01);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (216.16,209.57) --
-	(216.16,217.63);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (216.16,209.97) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (214.89,221.71) --
-	(221.27,221.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.34,217.88) --
-	(218.34,224.92);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (218.34,218.81) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (202.63,147.44) --
-	(214.05,147.44);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.15,132.17) --
-	(209.15,155.96);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.15,144.22) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (207.15,222.37) --
-	(211.56,222.37);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.48,221.56) --
-	(209.48,223.15);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.48,218.33) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.78,219.50) --
-	(224.12,219.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.99,215.67) --
-	(222.99,222.70);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (222.99,215.46) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.30,147.18) --
-	(189.41,147.18);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.65,127.61) --
-	(182.65,156.83);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.65,143.15) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.26,116.84) --
-	(215.83,116.84);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.62,108.17) --
-	(211.62,122.84);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.62,113.93) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.25,236.97) --
-	(237.70,236.97);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.48,236.65) --
-	(237.48,237.30);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (237.48,234.07) {$\mu$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.02,215.74) --
-	(223.96,215.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.21,212.86) --
-	(221.21,218.26);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (221.21,212.51) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.85,228.78) --
-	(228.92,228.78);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.17,225.88) --
-	(222.17,231.32);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (222.17,224.75) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.55,233.64) --
-	(231.71,233.64);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.14,232.97) --
-	(231.14,234.28);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (231.14,229.60) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.43,196.04) --
-	(195.58,196.04);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.78,191.87) --
-	(190.78,199.48);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.78,192.01) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (214.47,217.06) --
-	(224.34,217.06);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.01,214.69) --
-	(220.01,219.19);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.01,214.16) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.96,238.48) --
-	(239.06,238.48);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.57,237.41) --
-	(237.57,239.50);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (237.57,235.58) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (202.24,199.17) --
-	(206.09,199.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.26,194.33) --
-	(204.26,203.06);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (204.26,195.95) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.98,226.15) --
-	(227.46,226.15);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.80,224.44) --
-	(225.80,227.72);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (225.80,222.11) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.47,230.01) --
-	(228.23,230.01);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.85,228.14) --
-	(227.85,231.72);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (227.85,225.98) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.72,196.63) --
-	(197.16,196.63);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.63,190.12) --
-	(194.63,201.52);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.63,192.60) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.32,195.64) --
-	(201.54,195.64);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.00,193.16) --
-	(200.00,197.84);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (200.00,192.73) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.57,232.06) --
-	(232.24,232.06);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.91,231.59) --
-	(231.91,232.52);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (231.91,229.16) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.66,183.93) --
-	(219.30,183.93);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.50,181.48) --
-	(218.50,186.11);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (218.50,180.70) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.19,229.04) --
-	(220.33,229.04);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.82,226.89) --
-	(218.82,230.98);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (218.82,225.01) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.70,229.04) --
-	(224.24,229.04);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.97,228.81) --
-	(223.97,229.27);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (223.97,225.01) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.54,197.84) --
-	(195.87,197.84);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.74,195.17) --
-	(194.74,200.19);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.74,193.80) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.39,187.91) --
-	(197.73,187.91);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.24,185.67) --
-	(195.24,189.92);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.24,185.00) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00, 85.56) --
+	(286.65,372.21) --
+	(286.65,201.09) --
+	( 85.56,  0.00);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (  0.00, 57.04) --
+	(286.65,343.69) --
+	(286.65,229.61) --
+	( 57.04,  0.00);
+
+\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (  0.00, 28.52) --
+	(286.65,315.17) --
+	(286.65,258.13) --
+	( 28.52,  0.00);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (142.89, 53.23) {$\frac{1}{64} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,146.79) {$64\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (114.37, 53.23) {$\frac{1}{16} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,118.27) {$16\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 84.20, 53.23) {$\frac{1}{4} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92, 89.75) {$4\times$};
+
+\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] ( 49.80, 49.80) -- (239.28,239.28);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (166.31,108.94) --
+	(178.18,108.94);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.09, 93.05) --
+	(173.09,117.79);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.09,105.71) {$p$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.01,186.83) --
+	(175.60,186.83);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.43,185.99) --
+	(173.43,187.64);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.43,182.80) {$L$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.22,183.85) --
+	(188.66,183.85);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.48,179.87) --
+	(187.48,187.18);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.48,179.81) {$r$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (134.78,108.66) --
+	(152.57,108.66);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.54, 88.31) --
+	(145.54,118.69);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (145.54,104.63) {$h$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (170.09, 77.11) --
+	(180.04, 77.11);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.66, 68.10) --
+	(175.66, 83.36);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (175.66, 74.21) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.83,194.24) --
+	(195.05,194.24);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.45,194.00) --
+	(194.45,194.48);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.45,191.34) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (165.91,162.72) --
+	(169.91,162.72);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.01,157.69) --
+	(168.01,166.76);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (168.01,159.49) {$p$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.51,190.76) --
+	(192.13,190.76);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.40,188.99) --
+	(190.40,192.40);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.40,186.73) {$L$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.13,194.78) --
+	(192.93,194.78);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.54,192.84) --
+	(192.54,196.56);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.54,190.75) {$r$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (154.98,160.08) --
+	(160.63,160.08);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.00,153.30) --
+	(158.00,165.16);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.00,156.04) {$h$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.83,159.04) --
+	(165.18,159.04);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.57,156.47) --
+	(163.57,161.34);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (163.57,156.14) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.10,198.95) --
+	(199.15,198.95);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.63,198.56) --
+	(198.63,199.33);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.63,196.04) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.18,135.18) --
+	(180.36,135.18);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.93,132.02) --
+	(177.93,137.93);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.93,131.96) {$p$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.79,187.26) --
+	(183.97,187.26);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.99,184.64) --
+	(181.99,189.57);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.99,183.22) {$L$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.55,188.03) --
+	(187.77,188.03);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.66,187.27) --
+	(187.66,188.76);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.66,183.99) {$r$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (136.18,133.55) --
+	(143.40,133.55);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.10,130.61) --
+	(140.10,136.12);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (140.10,129.52) {$h$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (157.97,116.91) --
+	(166.71,116.91);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.80,115.36) --
+	(162.80,118.34);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (162.80,114.00) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.08,196.19) --
+	(197.23,196.19);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.66,196.03) --
+	(196.66,196.35);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.66,193.29) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.94,146.87) --
+	(183.64,146.87);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.81,144.32) --
+	(182.81,149.14);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.81,143.64) {$p$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.45,193.77) --
+	(184.72,193.77);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (183.15,191.53) --
+	(183.15,195.79);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.15,189.74) {$L$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.22,193.77) --
+	(188.78,193.77);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.50,193.53) --
+	(188.50,194.01);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.50,189.74) {$r$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (156.86,161.33) --
+	(159.29,161.33);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.11,158.55) --
+	(158.11,163.78);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.11,157.30) {$h$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (155.66,151.01) --
+	(161.22,151.01);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.63,148.68) --
+	(158.63,153.10);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.63,148.10) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.03,198.53) --
+	(199.38,198.53);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.24,196.83) --
+	(198.24,200.10);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.24,195.63) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.31,180.58) --
+	(188.49,180.58);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.63,177.98) --
+	(185.63,182.88);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.63,177.35) {$p$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.90,192.44) --
+	(193.65,192.44);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.63,188.99) --
+	(186.63,195.39);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (186.63,188.40) {$L$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.34,198.71) --
+	(196.54,198.71);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.95,198.09) --
+	(195.95,199.32);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.95,194.68) {$r$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (147.39,159.75) --
+	(158.98,159.75);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.99,156.46) --
+	(153.99,162.58);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (153.99,155.72) {$h$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (178.62,181.29) --
+	(188.88,181.29);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.39,179.40) --
+	(184.39,183.02);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.39,178.39) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (207.95,210.83) --
+	(210.44,210.83);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.23,210.24) --
+	(209.23,211.41);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.23,207.93) {$\kappa$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.58,195.33) --
+	(183.78,195.33);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.49,193.67) --
+	(180.49,196.87);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.49,192.11) {$p$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.38,201.82) --
+	(174.02,201.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.39,201.65) --
+	(171.39,201.98);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.39,197.78) {$L$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.62,199.95) --
+	(199.37,199.95);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (199.00,198.75) --
+	(199.00,201.09);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.00,195.92) {$r$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.20,178.14) --
+	(180.56,178.14);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.38,173.53) --
+	(180.38,181.90);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.38,174.11) {$h$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.06,186.15) --
+	(185.69,186.15);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.64,182.17) --
+	(182.64,189.49);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.64,183.25) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.62,212.25) --
+	(213.79,212.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.74,211.79) --
+	(212.74,212.69);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.74,209.34) {$\kappa$};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 49.80) -- (232.05, 49.80);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 49.80) -- (239.28, 49.80);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.36, 49.80) -- ( 95.36, 44.82);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.92, 49.80) -- (140.92, 44.82);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.49, 49.80) -- (186.49, 44.82);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.05, 49.80) -- (232.05, 44.82);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 97.17, 49.80) -- ( 97.17, 44.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (144.54, 49.80) -- (144.54, 44.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.91, 49.80) -- (191.91, 44.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.28, 49.80) -- (239.28, 44.82);
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 95.36, 31.87) {10};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (140.92, 31.87) {100};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (186.49, 31.87) {1000};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (232.05, 31.87) {10000};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 49.80) -- ( 49.80,232.05);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 97.17, 31.87) {10};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (144.54, 31.87) {100};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (191.91, 31.87) {1000};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (239.28, 31.87) {10000};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 49.80) -- ( 49.80,239.28);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 95.36) -- ( 44.82, 95.36);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,140.92) -- ( 44.82,140.92);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,186.49) -- ( 44.82,186.49);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,232.05) -- ( 44.82,232.05);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 97.17) -- ( 44.82, 97.17);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,144.54) -- ( 44.82,144.54);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,191.91) -- ( 44.82,191.91);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,239.28) -- ( 44.82,239.28);
 
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84, 92.50) {10};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,138.07) {100};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,183.63) {1000};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,229.19) {10000};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84, 94.31) {10};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,141.68) {100};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,189.05) {1000};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,236.42) {10000};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.66] at (433.62,258.45) {\bfseries Speed comparison};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.66] at (433.62, 11.95) {Setting};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.66] at (307.01,144.54) {Speed ($10^6$ states/hr)};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,259.88) {\bfseries Disparity as a function of sequence length};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62, 11.95) {Sequence length $L$ (kb)};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (307.01,144.54) {ESS/hr of tip rates $r$};
 \end{scope}
@@
 \path[clip] (338.88, 49.80) rectangle (528.36,239.28);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.86, 82.50) -- (428.66, 89.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.55, 88.90) -- (516.41, 77.92);
-\definecolor{fillColor}{RGB}{255,0,0}
-
-\path[fill=fillColor] (345.90, 82.07) circle (  1.87);
-
-\path[fill=fillColor] (433.62, 92.50) --
-	(436.14, 88.14) --
-	(431.10, 88.14) --
-	cycle;
-
-\path[fill=fillColor] (521.34, 77.23) circle (  1.87);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.84,153.76) -- (428.68,144.02);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.29,141.68) -- (516.67,112.63);
-\definecolor{fillColor}{RGB}{255,165,0}
-
-\path[fill=fillColor] (345.90,157.28) --
-	(348.41,152.93) --
-	(343.38,152.93) --
-	cycle;
-
-\path[fill=fillColor] (433.62,143.41) circle (  1.87);
-
-\path[fill=fillColor] (521.34,110.89) circle (  1.87);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.88, 69.57) -- (428.64, 71.79);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.60, 71.74) -- (516.37, 68.72);
-\definecolor{fillColor}{RGB}{0,0,0}
-
-\path[fill=fillColor] (345.90, 69.42) circle (  1.87);
-
-\path[fill=fillColor] (433.62, 74.84) --
-	(436.14, 70.48) --
-	(431.10, 70.48) --
-	cycle;
-
-\path[fill=fillColor] (521.34, 68.52) circle (  1.87);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.68,117.44) -- (428.84,140.37);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.04,139.48) -- (516.92, 98.69);
-\definecolor{fillColor}{RGB}{160,32,240}
-
-\path[fill=fillColor] (345.90,116.04) circle (  1.87);
-
-\path[fill=fillColor] (433.62,144.68) --
-	(436.14,140.32) --
-	(431.10,140.32) --
-	cycle;
-
-\path[fill=fillColor] (521.34, 96.40) circle (  1.87);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.88,115.29) -- (428.64,112.75);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.55,111.90) -- (516.41,100.95);
-\definecolor{fillColor}{RGB}{0,100,0}
-
-\path[fill=fillColor] (345.90,118.36) --
-	(348.41,114.00) --
-	(343.38,114.00) --
-	cycle;
-
-\path[fill=fillColor] (433.62,112.59) circle (  1.87);
-
-\path[fill=fillColor] (521.34,100.26) circle (  1.87);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.16,147.49) -- (429.35,195.20);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (437.17,194.28) -- (517.79,114.87);
-\definecolor{fillColor}{RGB}{0,255,255}
-
-\path[fill=fillColor] (345.90,144.92) circle (  1.87);
-
-\path[fill=fillColor] (433.62,200.68) --
-	(436.14,196.32) --
-	(431.10,196.32) --
-	cycle;
-
-\path[fill=fillColor] (521.34,111.38) circle (  1.87);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (485.73,205.86) --
+	(485.73, 51.84);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (485.73,126.77) {$77\times $};
+\definecolor{fillColor}{RGB}{0,140,186}
+
+\path[fill=fillColor] (485.73,205.86) circle (  1.87);
+\definecolor{fillColor}{RGB}{105,105,105}
+
+\path[fill=fillColor] (485.73, 51.84) circle (  1.87);
+\definecolor{fillColor}{gray}{0.64}
+
+\path[fill=fillColor] (485.73,199.70) circle (  1.87);
+\definecolor{fillColor}{RGB}{0,140,186}
+
+\path[fill=fillColor] (347.47, 84.16) circle (  2.15);
+\definecolor{fillColor}{RGB}{105,105,105}
+
+\path[fill=fillColor] (347.47, 72.71) circle (  2.15);
+\definecolor{fillColor}{gray}{0.64}
+
+\path[fill=fillColor] (347.47, 61.25) circle (  2.15);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 80.88) {adapt (\textit{real})};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 69.42) {adapt (\textit{cat})};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 57.97) {adapt (\textit{quant})};
+\definecolor{fillColor}{RGB}{0,140,186}
+
+\path[fill=fillColor] (347.47, 84.16) circle (  2.15);
+\definecolor{fillColor}{RGB}{105,105,105}
+
+\path[fill=fillColor] (347.47, 72.71) circle (  2.15);
+\definecolor{fillColor}{gray}{0.64}
+
+\path[fill=fillColor] (347.47, 61.25) circle (  2.15);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 80.88) {adapt (\textit{real})};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 69.42) {adapt (\textit{cat})};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 57.97) {adapt (\textit{quant})};
+\definecolor{fillColor}{RGB}{0,140,186}
+
+\path[fill=fillColor] (394.78,308.65) circle (  1.87);
+
+\path[fill=fillColor] (347.47, 84.16) circle (  2.15);
+\definecolor{fillColor}{RGB}{105,105,105}
+
+\path[fill=fillColor] (347.47, 72.71) circle (  2.15);
+\definecolor{fillColor}{gray}{0.64}
+
+\path[fill=fillColor] (347.47, 61.25) circle (  2.15);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 80.88) {adapt (\textit{real})};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 69.42) {adapt (\textit{cat})};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 57.97) {adapt (\textit{quant})};
+\definecolor{fillColor}{RGB}{0,140,186}
+
+\path[fill=fillColor] (390.04,246.75) circle (  1.87);
+\definecolor{fillColor}{gray}{0.64}
+
+\path[fill=fillColor] (390.04,277.75) circle (  1.87);
+\definecolor{fillColor}{RGB}{0,140,186}
+
+\path[fill=fillColor] (347.47, 84.16) circle (  2.15);
+\definecolor{fillColor}{RGB}{105,105,105}
+
+\path[fill=fillColor] (347.47, 72.71) circle (  2.15);
+\definecolor{fillColor}{gray}{0.64}
+
+\path[fill=fillColor] (347.47, 61.25) circle (  2.15);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 80.88) {adapt (\textit{real})};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 69.42) {adapt (\textit{cat})};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 57.97) {adapt (\textit{quant})};
+
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (404.25,204.65) --
+	(404.25,100.19);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (404.25,150.34) {$3.1\times $};
+\definecolor{fillColor}{RGB}{0,140,186}
+
+\path[fill=fillColor] (404.25,204.65) circle (  1.87);
+\definecolor{fillColor}{RGB}{105,105,105}
+
+\path[fill=fillColor] (404.25,100.19) circle (  1.87);
+\definecolor{fillColor}{gray}{0.64}
+
+\path[fill=fillColor] (404.25,210.63) circle (  1.87);
+\definecolor{fillColor}{RGB}{0,140,186}
+
+\path[fill=fillColor] (347.47, 84.16) circle (  2.15);
+\definecolor{fillColor}{RGB}{105,105,105}
+
+\path[fill=fillColor] (347.47, 72.71) circle (  2.15);
+\definecolor{fillColor}{gray}{0.64}
+
+\path[fill=fillColor] (347.47, 61.25) circle (  2.15);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 80.88) {adapt (\textit{real})};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 69.42) {adapt (\textit{cat})};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 57.97) {adapt (\textit{quant})};
+\definecolor{fillColor}{RGB}{0,140,186}
+
+\path[fill=fillColor] (347.47, 84.16) circle (  2.15);
+\definecolor{fillColor}{RGB}{105,105,105}
+
+\path[fill=fillColor] (347.47, 72.71) circle (  2.15);
+\definecolor{fillColor}{gray}{0.64}
+
+\path[fill=fillColor] (347.47, 61.25) circle (  2.15);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 80.88) {adapt (\textit{real})};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 69.42) {adapt (\textit{cat})};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 57.97) {adapt (\textit{quant})};
+\definecolor{fillColor}{RGB}{0,140,186}
+
+\path[fill=fillColor] (433.62,210.36) circle (  1.87);
+\definecolor{fillColor}{gray}{0.64}
+
+\path[fill=fillColor] (433.62,258.51) circle (  1.87);
+\definecolor{fillColor}{RGB}{0,140,186}
+
+\path[fill=fillColor] (347.47, 84.16) circle (  2.15);
+\definecolor{fillColor}{RGB}{105,105,105}
+
+\path[fill=fillColor] (347.47, 72.71) circle (  2.15);
+\definecolor{fillColor}{gray}{0.64}
+
+\path[fill=fillColor] (347.47, 61.25) circle (  2.15);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 80.88) {adapt (\textit{real})};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 69.42) {adapt (\textit{cat})};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 57.97) {adapt (\textit{quant})};
+
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (359.72,284.96) --
+	(359.72,295.15);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (359.72,287.98) {$0.96\times $};
+\definecolor{fillColor}{RGB}{0,140,186}
+
+\path[fill=fillColor] (359.72,284.96) circle (  1.87);
+\definecolor{fillColor}{RGB}{105,105,105}
+
+\path[fill=fillColor] (359.72,295.15) circle (  1.87);
+\definecolor{fillColor}{gray}{0.64}
+
+\path[fill=fillColor] (359.72,315.21) circle (  1.87);
+\definecolor{fillColor}{RGB}{0,140,186}
+
+\path[fill=fillColor] (347.47, 84.16) circle (  2.15);
+\definecolor{fillColor}{RGB}{105,105,105}
+
+\path[fill=fillColor] (347.47, 72.71) circle (  2.15);
+\definecolor{fillColor}{gray}{0.64}
+
+\path[fill=fillColor] (347.47, 61.25) circle (  2.15);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 80.88) {adapt (\textit{real})};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 69.42) {adapt (\textit{cat})};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 57.97) {adapt (\textit{quant})};
+\definecolor{fillColor}{RGB}{0,140,186}
+
+\path[fill=fillColor] (346.46,317.20) circle (  1.87);
+\definecolor{fillColor}{gray}{0.64}
+
+\path[fill=fillColor] (346.46,337.93) circle (  1.87);
+\definecolor{fillColor}{RGB}{0,140,186}
+
+\path[fill=fillColor] (347.47, 84.16) circle (  2.15);
+\definecolor{fillColor}{RGB}{105,105,105}
+
+\path[fill=fillColor] (347.47, 72.71) circle (  2.15);
+\definecolor{fillColor}{gray}{0.64}
+
+\path[fill=fillColor] (347.47, 61.25) circle (  2.15);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 80.88) {adapt (\textit{real})};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 69.42) {adapt (\textit{cat})};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 57.97) {adapt (\textit{quant})};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (521.34, 49.80) -- (521.34, 44.82);
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (348.76, 39.84) {\textit{cat}};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (436.48, 39.84) {adapt (\textit{real})};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (524.20, 39.84) {adapt (\textit{quant})};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 56.82) -- (338.88,216.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 56.82) -- (333.90, 56.82);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 96.66) -- (333.90, 96.66);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,136.50) -- (333.90,136.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,176.33) -- (333.90,176.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,216.17) -- (333.90,216.17);
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (326.93, 56.82) {0};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (326.93, 96.66) {10};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (326.93,136.50) {20};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (326.93,176.33) {30};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (326.93,216.17) {40};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (480.99, 49.80) -- (480.99, 44.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (528.36, 49.80) -- (528.36, 44.82);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (338.88, 31.87) {0};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (386.25, 31.87) {5};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (433.62, 31.87) {10};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (480.99, 31.87) {15};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (528.36, 31.87) {20};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 49.80) -- (338.88,239.28);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 49.80) -- (333.90, 49.80);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 87.70) -- (333.90, 87.70);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,125.59) -- (333.90,125.59);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,163.49) -- (333.90,163.49);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,201.38) -- (333.90,201.38);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,239.28) -- (333.90,239.28);
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92, 46.94) {0};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92, 84.84) {200};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,122.73) {400};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,160.63) {600};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,198.53) {800};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,236.42) {1000};
 \end{scope}

### 2020-08-10 benchmarking/benchmarkingVM/ESS_round3.tex
results update

@@
-% Created by tikzDevice version 0.12.3 on 2020-08-07 14:28:39
+% Created by tikzDevice version 0.12.3 on 2020-08-10 15:55:24
 % !TEX encoding = UTF-8 Unicode
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at (144.54,253.90) {\bfseries Comparison of Bactrian (\textit{real}) and adapt (\textit{real})};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at (144.54,253.90) {\bfseries Bactrian (\textit{real}) vs. adapt (\textit{real})};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at (144.54, 14.40) {ESS/chain [adapt (\textit{real})]};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at (144.54, 14.40) {ESS/hr [adapt (\textit{real})]};
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at ( 21.60,144.54) {ESS/chain [Bactrian (\textit{real})]};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at ( 21.60,144.54) {ESS/hr [Bactrian (\textit{real})]};
 \end{scope}
@@
 \definecolor{drawColor}{RGB}{0,0,0}
-\definecolor{fillColor}{gray}{0.91}
 
-\path[draw=drawColor,line width= 0.1pt,line join=round,line cap=round,fill=fillColor] (  0.00, 73.08) --
-	(216.00,289.08) --
-	(269.54,289.08) --
-	(269.54,196.46) --
-	( 73.08,  0.00) --
-	(  0.00,  0.00) --
-	cycle;
-\definecolor{fillColor}{RGB}{190,190,190}
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00, 76.35) --
+	(212.73,289.08);
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] (  0.00, 48.72) --
-	(240.36,289.08) --
-	(269.54,289.08) --
-	(269.54,220.82) --
-	( 48.72,  0.00) --
-	(  0.00,  0.00) --
-	cycle;
-\definecolor{fillColor}{RGB}{169,169,169}
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.35,289.08) --
+	(271.35,195.00) --
+	( 76.35,  0.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (  0.00, 24.36) --
-	(264.72,289.08) --
-	(269.54,289.08) --
-	(269.54,245.18) --
-	( 24.36,  0.00) --
-	(  0.00,  0.00) --
-	cycle;
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (  0.00, 50.90) --
+	(238.18,289.08);
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (142.16, 64.13) {$\frac{1}{64} \times$};
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (271.35,289.08) --
+	(271.35,220.45) --
+	( 50.90,  0.00);
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,146.85) {$64\times$};
+\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (  0.00, 25.45) --
+	(263.63,289.08);
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (117.80, 64.13) {$\frac{1}{16} \times$};
+\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (271.35,289.08) --
+	(271.35,245.90) --
+	( 25.45,  0.00);
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,122.49) {$16\times$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (145.42, 64.13) {$\frac{1}{64} \times$};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 91.44, 64.13) {$\frac{1}{4} \times$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,150.12) {$64\times$};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 62.56, 98.13) {$4\times$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (119.97, 64.13) {$\frac{1}{16} \times$};
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 60.00, 60.00) -- (229.08,229.08);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,124.67) {$16\times$};
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.39,202.25) --
-	(214.66,202.25);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 92.53, 64.13) {$\frac{1}{4} \times$};
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.22,200.65) --
-	(212.22,203.71);
-\definecolor{drawColor}{RGB}{160,32,240}
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 62.56, 99.22) {$4\times$};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (212.22,198.36) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
+\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] ( 60.00, 60.00) -- (229.08,229.08);
+\definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.91,206.44) --
-	(219.07,206.44);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.97,173.04) --
+	(174.56,173.04);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (213.08,191.17) --
-	(213.08,214.48);
-\definecolor{drawColor}{RGB}{160,32,240}
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (170.02,163.26) --
+	(170.02,179.39);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (213.08,201.58) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (170.02,169.15) {$p$};
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.51,221.34) --
-	(221.54,221.34);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.16,172.12) --
+	(172.25,172.12);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.04,220.39) --
-	(221.04,222.25);
-\definecolor{drawColor}{RGB}{160,32,240}
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (170.32,170.07) --
+	(170.32,173.96);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (221.04,216.48) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (170.32,167.26) {$L$};
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.55,185.90) --
-	(189.46,185.90);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.73,184.48) --
+	(183.91,184.48);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.19,182.34) --
-	(185.19,188.86);
-\definecolor{drawColor}{RGB}{160,32,240}
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.85,183.02) --
+	(182.85,185.84);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (185.19,181.04) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (182.85,179.62) {$r$};
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.24,201.88) --
-	(215.00,201.88);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (135.83,152.06) --
+	(151.70,152.06);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.16,198.88) --
-	(211.16,204.43);
-\definecolor{drawColor}{RGB}{160,32,240}
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.43,146.58) --
+	(145.43,156.28);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (211.16,198.38) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (145.43,147.20) {$h$};
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.32,225.51) --
-	(228.07,225.51);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (167.34,176.95) --
+	(176.22,176.95);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.75,222.77) --
-	(226.75,227.87);
-\definecolor{drawColor}{RGB}{160,32,240}
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.31,171.72) --
+	(172.31,181.01);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (226.75,222.01) {$\mu$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (172.31,173.45) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.52,189.61) --
+	(189.61,189.61);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.07,189.39) --
+	(189.07,189.83);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (189.07,186.11) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.89,177.49) --
+	(176.50,177.49);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.34,177.31) --
+	(174.34,177.66);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (174.34,173.60) {$p$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.00,179.60) --
+	(179.72,179.60);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.96,177.03) --
+	(177.96,181.87);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (177.96,174.74) {$L$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.92,182.73) --
+	(183.11,182.73);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (183.02,182.56) --
+	(183.02,182.90);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (183.02,177.87) {$r$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (137.08,144.73) --
+	(143.52,144.73);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.58,137.44) --
+	(140.58,149.93);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (140.58,139.87) {$h$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (156.53,157.68) --
+	(164.32,157.68);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.84,139.80) --
+	(160.84,166.56);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (160.84,154.18) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.53,191.09) --
+	(191.56,191.09);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.05,190.40) --
+	(191.05,191.75);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (191.05,187.59) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (178.25,170.79) --
+	(183.76,170.79);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.21,169.12) --
+	(181.21,172.32);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (181.21,166.90) {$p$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.52,175.16) --
+	(188.36,175.16);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.10,159.21) --
+	(182.10,183.57);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (182.10,170.30) {$L$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.87,190.74) --
+	(190.95,190.74);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.41,189.74) --
+	(190.41,191.69);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (190.41,185.88) {$r$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (147.08,153.71) --
+	(157.42,153.71);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (152.97,149.99) --
+	(152.97,156.80);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (152.97,148.85) {$h$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.95,170.40) --
+	(184.11,170.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.10,167.27) --
+	(180.10,173.07);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (180.10,166.90) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (201.12,201.71) --
+	(203.34,201.71);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (202.27,200.95) --
+	(202.27,202.44);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (202.27,198.21) {$\kappa$};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- (221.85, 60.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- (229.08, 60.00);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.46, 60.00) -- (100.46, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (102.27, 60.00) -- (102.27, 54.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.92, 60.00) -- (140.92, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (144.54, 60.00) -- (144.54, 54.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.38, 60.00) -- (181.38, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.81, 60.00) -- (186.81, 54.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.85, 60.00) -- (221.85, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.08, 60.00) -- (229.08, 54.00);
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (100.46, 38.40) {10};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (102.27, 38.40) {10};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (140.92, 38.40) {100};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (144.54, 38.40) {100};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (181.38, 38.40) {1000};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (186.81, 38.40) {1000};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (221.85, 38.40) {10000};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (229.08, 38.40) {10000};
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- ( 60.00,221.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- ( 60.00,229.08);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,100.46) -- ( 54.00,100.46);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,102.27) -- ( 54.00,102.27);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,140.92) -- ( 54.00,140.92);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,144.54) -- ( 54.00,144.54);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,181.38) -- ( 54.00,181.38);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,186.81) -- ( 54.00,186.81);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,221.85) -- ( 54.00,221.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,229.08) -- ( 54.00,229.08);
 
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00, 97.02) {10};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00, 98.83) {10};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,137.48) {100};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,141.10) {100};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,177.94) {1000};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,183.37) {1000};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,218.40) {10000};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,225.64) {10000};
 \end{scope}
@@
 \definecolor{drawColor}{RGB}{0,0,0}
-\definecolor{fillColor}{RGB}{255,0,0}
+\definecolor{fillColor}{RGB}{255,0,109}
 
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,171.00) rectangle (169.31,165.00);
-\definecolor{fillColor}{RGB}{0,0,255}
+\definecolor{fillColor}{RGB}{253,104,0}
 
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,159.00) rectangle (169.31,153.00);
-\definecolor{fillColor}{RGB}{0,255,0}
+\definecolor{fillColor}{RGB}{143,161,0}
 
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,147.00) rectangle (169.31,141.00);
-\definecolor{fillColor}{RGB}{255,255,0}
+\definecolor{fillColor}{RGB}{0,195,0}
 
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,135.00) rectangle (169.31,129.00);
-\definecolor{fillColor}{RGB}{255,165,0}
+\definecolor{fillColor}{RGB}{0,219,171}
 
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,123.00) rectangle (169.31,117.00);
-\definecolor{fillColor}{RGB}{0,0,0}
+\definecolor{fillColor}{RGB}{0,216,255}
 
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,111.00) rectangle (169.31,105.00);
-\definecolor{fillColor}{RGB}{160,32,240}
+\definecolor{fillColor}{RGB}{151,0,255}
 
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11, 99.00) rectangle (169.31, 93.00);
-\definecolor{fillColor}{RGB}{0,100,0}
+\definecolor{fillColor}{RGB}{255,0,255}
 
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11, 87.00) rectangle (169.31, 81.00);
-\definecolor{fillColor}{RGB}{0,255,255}
+\definecolor{fillColor}{RGB}{68,68,68}
 
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,164.56) {Broughton};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,164.56) {Ran};
 
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,128.56) {Kawahara};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,128.56) {Sauquet};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,116.56) {Moyle};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,116.56) {Broughton};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,104.56) {Ran};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,104.56) {Kawahara};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31, 92.56) {Rightmyer};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31, 92.56) {simulated};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31, 80.56) {Sauquet};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31, 80.56) {Rightmyer};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31, 68.56) {simulated};
-\end{scope}
-\end{tikzpicture}
-\begin{tikzpicture}[x=1pt,y=1pt]
-\definecolor{fillColor}{RGB}{255,255,255}
-\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (289.08,289.08);
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.00] at (144.54,252.18) {\bfseries Speed comparison};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.00] at (144.54, 14.40) {Setting};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.00] at ( 21.60,144.54) {Speed ($10^6$ states/hr)};
-\end{scope}
-\begin{scope}
-\path[clip] ( 60.00, 60.00) rectangle (229.08,229.08);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 72.26,142.15) -- (216.82,144.02);
-\definecolor{fillColor}{RGB}{160,32,240}
-
-\path[fill=fillColor] ( 66.26,142.07) circle (  2.25);
-
-\path[fill=fillColor] (222.82,147.60) --
-	(225.85,142.35) --
-	(219.79,142.35) --
-	cycle;
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.26, 60.00) -- (222.82, 60.00);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.26, 60.00) -- ( 66.26, 54.00);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.82, 60.00) -- (222.82, 54.00);
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 69.71, 48.00) {adapt (\textit{real})};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at (226.26, 48.00) {Bactrian (\textit{real})};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 66.26) -- ( 60.00,208.46);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 66.26) -- ( 54.00, 66.26);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,101.81) -- ( 54.00,101.81);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,137.36) -- ( 54.00,137.36);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,172.91) -- ( 54.00,172.91);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,208.46) -- ( 54.00,208.46);
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 45.60, 66.26) {0};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 45.60,101.81) {10};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 45.60,137.36) {20};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 45.60,172.91) {30};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 45.60,208.46) {40};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31, 68.56) {Moyle};
 \end{scope}

### 2020-08-10 manuscript.tex
results update

@@
 
+\usepackage{commath}
+
 \usepackage{mhchem}
+\usepackage{tikz}
 \usepackage{mathtools}
@@
 \item[]}{\end{list}}
+
+\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;}
 
@@
 % Results and Discussion can be combined.
-\section*{Models} \label{sect:models}
+\section*{Models and Methods} \label{sect:models}
 
@@
 
-Let $\mathcal{T}$ be a binary rooted time tree with $N$ taxa.
-Let $L$ be the number of sites within the multiple sequence alignment $D$, and let $L_\text{eff}$ be the effective number of sites in the alignment (i.e.
-the number of unique patterns across all sites in the alignment).
+Let $\mathcal{T}$ be a binary rooted time tree with $N$ taxa. Let $L$ be the number of sites within the multiple sequence alignment $D$. 
 The posterior density of a phylogenetic model is described by
@@
 \label{eqn:adaptiveSampler}
-	p(\omega_i) \propto \begin{cases} 1 & \text{ with probability } \Omega \\ \frac{1}{\mathbb{T}(\omega_i)} \sum\limits_{p \in \text{parameters}} \frac{1}{\sigma^2_p}  \sum\limits_{x \in \text{accepts}_i}  || x_p - x_p^\prime ||^2 & \text{ with probability } 1-\Omega \end{cases}
+	p(\omega_i) \propto \begin{cases} 1 & \text{ with probability } \Omega \\ \frac{1}{\mathbb{T}(\omega_i)} \sum\limits_{p \in \text{POI}}  \sum\limits_{x \in \text{accepts}(\omega_i)}  \mathbb{D}(x_p, x_p^\prime) & \text{ with probability } 1-\Omega \end{cases}
 \end{align}
@@
 where $\Omega = 0.01$ allows any sub-operator to be sampled regardless of its performance.
-The remaining terms are trained during the second and third phases: the cumulative computational runtime spent on each operator $\mathbb{T}(\omega_i)$, the sample variance $\sigma^2_p$ of each parameter $p$, and the sum-of-squares $\sum\limits_{x \in \text{accepts}_i} ||x_p - x_p^\prime||^2$, where $x_p$ and $x_p^\prime$ are the values of $p$ before and after each acceptance of a proposal made by $\omega_i$.
+The parameters of interest (POI) may be either a set of numerical parameters (such as branch rates or node heights), or it may be the tree itself, but it cannot be both.
+The distance between states $x_p$ and its (accepted) proposal $x_p^\prime$ with respect to parameter $p$ is determined by
+
+\begin{align}
+\label{eqn:distanceFunctions} 
+	\mathbb{D}(x_p, x_p^\prime) = \begin{cases} \texttt{RF}(x_p, x_p^\prime)^2 & \text{ if } p \text{ is a tree} \\ 
+	\frac{1}{|p|} \Big[ \frac{\norm{x_p - x_p^\prime}}{\sigma_p} \Big]^2    & \text{ if } p \text{ is numerical}  \end{cases}
+\end{align}
+
+where \texttt{RF} is the Robinson-Foulds tree distance \cite{robinson1981comparison}, and $|p|$ is the number of dimensions of numerical parameter $p$ (1 for $\sigma$, $2N-2$ for $\vec{\mathcal{R}}^{\,}$, and $2N-1$ for node heights $t$).
+The remaining terms are trained during the second and third phases: the cumulative computational runtime spent on each operator $\mathbb{T}(\omega_i)$, the sample standard deviation $\sigma_p$ of each numerical parameter $p$, and the sum distances $\sum_x \mathbb{D}(x_p, x_p^\prime)$.
 
@@
 
-Under \textbf{Equation \ref{eqn:adaptiveSampler}}, operators which effect larger changes on the parameters of interest, in shorter runtime, are sampled with greater probabilities. 
-Division of the sum-of-squares term by the parameter variance $\sigma^2_p$ enables comparison between different parameters.
+Under \textbf{Equations \ref{eqn:adaptiveSampler} and \ref{eqn:distanceFunctions}}, operators which effect larger changes on the parameters of interest, in shorter runtime, are sampled with greater probabilities.
+Division of the squared distance by a parameters variance $\sigma^2_p$ enables comparison between different numerical parameters.
 
@@
 \centering
-\begin{tabular}{|l p{4cm}|} 
- \hline
- Meta-operator & Operators \\
-\hline
- \multirow{4}{*}{\texttt{AdaptiveOperatorSampler($\sigma$)}} & \texttt{FastClockScale($\sigma, \vec{\mathcal{R}}^{\,}$)}$^{*}$ \\ 
- & \texttt{RandomWalk($\sigma$)} \\
- & \texttt{Scale($\sigma$)} \\
- & \texttt{SampleFromPrior($\sigma$)} \\
- \hline
-  \multirow{6}{*}{\texttt{AdaptiveOperatorSampler($\vec{\mathcal{R}}^{\,}$)}} & \texttt{ConstantDistance($\vec{\mathcal{R}}^{\,}, \mathcal{T}$)} \\ 
-& \texttt{RandomWalk($\vec{\mathcal{R}}^{\,}$)} \\
-& \texttt{Scale($\vec{\mathcal{R}}^{\,}$)}$^{*}$ \\
-& \texttt{Interval($\vec{\mathcal{R}}^{\,}$)}$^{**}$  \\
-& \texttt{Swap($\vec{\mathcal{R}}^{\,}$)} \\
-& \texttt{SampleFromPrior($\vec{\mathcal{R}}^{\,}$)} \\
- \hline
-   \multirow{2}{*}{\texttt{AdaptiveOperatorSampler(root)}} & \texttt{SimpleDistance($\vec{\mathcal{R}}^{\,}, \mathcal{T}$)} \\ 
-&  \texttt{SmallPulley($\vec{\mathcal{R}}^{\,}, t$)}\\
+\begin{tabular}{|l l l|} 
+ \hline
+ Meta-operator & POI & Operators \\
+\hline
+ \multirow{4}{*}{\texttt{AdaptiveOperatorSampler($\sigma$)}} & \multirow{4}{*}{$\sigma$} & \texttt{FastClockScale($\sigma, \vec{\mathcal{R}}^{\,}$)} \\ 
+ && \texttt{RandomWalk($\sigma$)}  \\
+ && \texttt{Scale($\sigma$)}  \\
+ && \texttt{SampleFromPrior($\sigma$)}  \\
+ \hline
+  \multirow{6}{*}{\texttt{AdaptiveOperatorSampler($\vec{\mathcal{R}}^{\,}$)}} & \multirow{6}{*}{$\vec{\mathcal{R}}^{\,}, t$} & \texttt{ConstantDistance($\vec{\mathcal{R}}^{\,}, \mathcal{T}$)}   \\ 
+&& \texttt{RandomWalk($\vec{\mathcal{R}}^{\,}$)}  \\
+&& \texttt{Scale($\vec{\mathcal{R}}^{\,}$)}   \\
+&& \texttt{Interval($\vec{\mathcal{R}}^{\,}$)}   \\
+&& \texttt{Swap($\vec{\mathcal{R}}^{\,}$)}  \\
+&& \texttt{SampleFromPrior($\vec{\mathcal{R}}^{\,}$)} \\
+ \hline
+   \multirow{2}{*}{\texttt{AdaptiveOperatorSampler(root)}} & \multirow{2}{*}{$\vec{\mathcal{R}}^{\,}, t$} & \texttt{SimpleDistance($\vec{\mathcal{R}}^{\,}, \mathcal{T}$)}  \\ 
+&&  \texttt{SmallPulley($\vec{\mathcal{R}}^{\,}, t$)}  \\
  \hline
 \end{tabular}
-\caption{Summary of the three instances of \texttt{AdaptiveOperatorSampler} used under the \textit{real} and \textit{quant} parameterisations.
-\texttt{AdaptiveOperatorSampler(root)} applies the root-targetting constant distance operators only \cite{zhang2020improving} while \texttt{AdaptiveOperatorSampler($\vec{\mathcal{R}}^{\,}$)} targets all rates and all nodes.
-The two meta-operators are weighted proportionally to the contribution of the root node to the total node count. 
-  $^{*}$\textit{real} only. $^{**}$\textit{quant} only. }
+\caption{Summary of the three instances of \texttt{AdaptiveOperatorSampler} and their parameters of interest (POI).
+Note that different operators are applicable to different substitution rate parameterisations (\textbf{Table \ref{table:kernels}}). 
+\texttt{AdaptiveOperatorSampler(root)} applies the root-targeting constant distance operators only \cite{zhang2020improving} while \texttt{AdaptiveOperatorSampler($\vec{\mathcal{R}}^{\,}$)} targets all rates and all nodes heights $t$.
+The two meta-operators are weighted proportionally to the contribution of the root node to the total node count. }
 \label{table:adaptiveSampling}
@@
 
-The 48 operators generated by this pipeline are evaluated and compared in \textbf{\nameref{sect:results}}.
-Each operator is considered with and without a random walk on $t_D$ and thus there are 96 total settings.
-
-\clearpage
-\subsection*{A guided adaptive leaf rate operator}
-\label{AVMVN_sect}
-
-A \textit{guided} operator incorporates knowledge about neighbouring states, while an \textit{adaptive} operator undergoes a training process to improve its efficiency over time \cite{roberts2007coupling}.
-In previous work, parsimony scores and conditional clade probabilities of neighbouring trees have been employed by guided tree operators \cite{hohna2012guided,zhang2020using,meyer2019adaptive} and the latter has also been explored as the basis of  adaptive tree operators \cite{hohna2012guided,meyer2019adaptive}.
-The (adaptive) mirror kernel \cite{thawornwattana2018designing} learns a target distribution which acts as a `mirror image' of the current point $x$.
-The adaptable variance multivariate normal (AVMVN) kernel \cite{baele2017adaptive,suchard2018bayesian} learns correlations between parameters during MCMC.
-Baele et al.
-2017  observed a large increase ($\approx 5-10 \times$) in sampling efficiency from using the AVMVN kernel on clock rates and substitution model parameters across partitions \cite{baele2017adaptive}.
-
-In this article we consider application of the AVMVN kernel to the branch rates of leaf nodes. 
-This operator, referred to as \texttt{LeafAVMVN}, is not readily applicable to internal node branch rates due to their dependencies on tree topology.
-
-\subsubsection*{AVMVN kernel}
-
-The AVMVN kernel assumes its parameters live in $x \in \mathbb{R}^N$ and that these parameters follow a Multivariate Normal distribution with covariance matrix $\Sigma_N$.
-Hence, the kernel operates on the logarithmic or logistic transformation of the $N$ leaf branch rates, depending on the rate parameterisation:
-
-\begin{align}
-	x_i = \begin{cases} \log r_i \text{ for } \textit{real} \\
-						\log \frac{q_i}{1 - q_i} \text{ for } \textit{quant}  \end{cases}
-\end{align}
-
-where $r_i$ is a real rate and $q_i$ is a rate quantile. The AVMVN probability density is defined by
-
-\begin{align}
-	\mathcal{AVMVN}(x) =  \mathcal{MVN}\big(x, (1-\beta) \frac{\Sigma_N}{N} + \beta \frac{\mathbb{I}_N}{N} \big) ,
-\end{align}
-
-where $\mathcal{MVN}$ is the Multivariate Normal probability density.
-$\beta \; (= 0.05)$ is a constant which determines the fraction of the proposal determined by the identity matrix $\mathbb{I}_N$, as opposed to the covariance matrix $\Sigma_D$ which is trained during MCMC.
-
-The AVMVN proposal kernel is computed as
-
-\begin{align}
-	x^\prime &\leftarrow x + \sum\limits_{i=1}^N \sum\limits_{j=i}^N c_{i,j} \times s\Sigma \\
-	\text {where }  c &= \text{cholesky} \left( (1-\beta) \frac{\Sigma_N}{N} + \beta \frac{\mathbb{I}_N}{N} \right).
-\end{align}
-
-The cholesky$(Y)$ decomposition returns a lower diagonal matrix $L$, with positive real diagonal entries, such that $Y = LL^\prime$ \cite{lindstrom1988newton, pourahmadi2007cholesky}.
-$s$ is a tunable step size parameter and $\Sigma$ is a random variable drawn from a proposal kernel (uniform or Bactrian for instance).
-Our BEAST2 implementation of the AVMVN kernel is adapted from that of BEAST \cite{suchard2018bayesian}.
-
-In \nameref{sect:results}, we evaluate the \texttt{LeafAVMVN} operator for its ability to estimate leaf rates. 
-As the size of the covariance matrix $\Sigma_N$ grows with the number of taxa $N$, AVMVN is hypothesised to work well on small trees but become less efficient with larger taxon sets.
-
-\clearpage
-\subsection*{Model specification and MCMC settings} \label{sect:methods}
-
-In all phylogenetic analyses presented here, we use a Yule \cite{yule1925ii} tree prior $p(\mathcal{T}|\lambda)$ with birth rate $\lambda \sim \text{Log-Normal}(1,1.25)$.
-The clock standard deviation has a $\sigma \sim \text{Gamma}(0.5396,0.3819)$ prior.
-Datasets are partitioned into subsequences, where each partition is associated with a distinct HKY substitution model \cite{hasegawa1985dating}.
-The transition-transversion ratio $\kappa \sim \text{Log-Normal}(1, 1.25)$, the four nucleotide frequencies $(f_A, f_C, f_G, f_T) \sim \text{Dirichlet}(10,10,10,10)$, and the relative clock rate $\mu_C \sim \text{Log-Normal}(1, 0.6)$ are estimated independently for each partition.
-The operator scheme ensures that the clock rates $\mu_C$ have a mean of 1 across all partitions. 
-To enable the rapid benchmarking of larger datasets we use BEAGLE for high-performance tree likelihood calculations \cite{ayres2012beagle} and coupled MCMC with four chains for efficient mixing \cite{muller2019coupled}.
-The neighbour joining tree \cite{saitou1987neighbor} is used as the initial state in each MCMC chain.
-
-\clearpage
-\section*{Results} \label{sect:results}
-
-\subsection*{Assessment criteria and datasets}
-
-% Cite HKY somewhere hasegawa1985dating
-
-To avoid a cross-product explosion, the five targets for clock model improvement are evaluated sequentially in the following order: \textbf{\nameref{sect:adaptiveSampling}} \textbf{\nameref{sect:rateparams}}, \textbf{\nameref{sect:randomwalks}}, \textbf{\nameref{sect:NER}}, and \textbf{\nameref{AVMVN_sect}}.
-The four operators introduced in these sections are summarised in \textbf{Table \ref{table:newOperators}}.
-The setting which is considered to be the best in each step is then incorporated into the following step. This protocol and its outcomes are summarised in \textbf{Fig. \ref{fig:tournament}}.
-
-\begin{table}[h!]
-\centering
-\begin{tabular}{|l p{4cm} l|} 
- \hline
- Operator & Description & Parameters  \\
-  \hline
- \texttt{AdaptiveOperatorSampler} & Samples sub-operators proportionally to their weights, which are learned (see \nameref{sect:adaptiveSampling}). & $\vec{\mathcal{R}}^{\,}, \sigma, \mathcal{T}$ \\
-  \hline
- \texttt{SampleFromPrior} & Resamples a random number of elements from their prior (see \nameref{sect:adaptiveSampling}). & $\vec{\mathcal{R}}^{\,}, \sigma$ \\
-  \hline
- \texttt{NarrowExchangeRate} & Moves a branch and recomputes branch rates so that genetic distances are constant (see \nameref{sect:NER}). & $\vec{\mathcal{R}}^{\,}, \mathcal{T}$\\
-  \hline
- \texttt{LeafAVMVN}  & Proposals new rates for all leaves in one move (see \nameref{AVMVN_sect}) \cite{baele2017adaptive}. & $\vec{\mathcal{R}}^{\,}$ \\
-  \hline
-\end{tabular}
-\caption{Summary of clock model operators introduced throughout this article. Pre-existing clock model operators are summarised in \textbf{Table \ref{table:kernels}}}
-\label{table:newOperators}
-\end{table}
-
-\begin{figure}[!h]
-\includegraphics[width=\textwidth]{Figures/tournament.pdf}
-\caption{\textbf{Protocol for optimising clock model methodologies.} Each area (detailed in \textbf{\nameref{sect:models}}) is optimised sequentially, and the best setting from each step is used when optimising the following step.}
-\label{fig:tournament}
-\end{figure}
-
-Methodologies are assessed according to the following criteria.
-
-\textbf{1.
-Validation}.
-This is assessed by measuring the coverage of all estimated parameters in a well-calibrated simulation study, using 100 simulated datasets (with $N=100$ taxa and $L=5000$ nucleotide alignments).
-These are presented in \textbf{\nameref{sect:WCSS_appendix}}.
-\\
-
-\textbf{2. Mixing of parameters}. Key parameters are evaluated for the number of effective samples generated per hour (ESS/hr). This calculation is performed by BEAST2 \cite{bouckaert2019beast}. \\
-
-%\textbf{3.
-Time to convergence}.
-Two independent MCMC chains are run and the time is measured until: a) the absolute difference in clade posterior probability between the two chains is less than 0.05 for all clades, b) the Rubin-Gelman statistic $\hat{R}$ \cite{gelman1992inference} of every estimated parameter is less than 1.05, and c) the effective sample size \cite{rambaut2018posterior} of every estimated parameter is greater than 200 in each chain.
-\\
-
-Methodologies are benchmarked using one simulated and nine empirical datasets.
-The latter were compiled \cite{lanfear2019Github} and partitioned \cite{lanfear2016partitionfinder} by Lanfear et al. as `benchmark alignments' (\textbf{Table \ref{table:datasets}}).
-Each methodology is benchmarked across 5 replicates on each dataset, using an the Intel Xeon Gold 6138 CPU (2.00 GHz).
-All methodologies use identical models and operator configurations, except where a difference is specified.
-
-%All 25 datasets presented in \textbf{Table \ref{table:datasets}} are benchmarked together $1 \times$ each at the end of the protocol.
-Datasets and BEAST2 .xml templates are provided in the GitHub repository accompanying this article.
-
-% https://github.com/roblanf/BenchmarkAlignments
-\begin{table}[h!]
-\centering
-\begin{tabular}{|l| l l l l l|} 
- \hline
-  & $N$ & $P$ & $L$ (kb) & $L_\text{eff}$ (kb) & \textbf{Description} \\
-  \hline
-
- 1  &  38  &  8  &  9.1  &  6.45  &  Seed plants (Ran 2018 \cite{Ran_2018}) \\
-
-2  &  44  &  7  &  5.9  &  1.8  &  Squirrel Fishes (Dornburg 2012 \cite{Dornburg_2012}) \\
-
-3  &  44  &  3  &  1.9  &  0.8  &  Bark beetles (Cognato 2001 \cite{Cognato_2001}) \\
-
-4  &  51  &  6  &  5.4  &  1.8  &  Southern beeches (Sauquet 2011 \cite{Sauquet_2011}) \\
-
-5  &  61  &  8  &  6.9  &  4.3  &  Bony fishes (Broughton 2013 \cite{Broughton_2013}) \\
-
-6  &  70  &  3  &  2.2  &  0.9  &  Caterpillars (Kawahara 2013 \cite{Kawahara_2013}) \\
-
-7  &  78  &  8  &  3.4  &  3.1  &  Animals (Cannon 2016 \cite{Cannon_2016}) \\
-
-8  &  80  &  1 &  10.0  &  0.9  &  \textit{Simulated data}  \\
-
-9  &  94  &  4  &  2.2  &  1  &  Bees (Rightmyer 2013 \cite{Rightmyer_2013}) \\
-
-10  &  106  &  1  &  0.8  &  0.5  &  Songbirds (Moyle 2016 \cite{Moyle_2016}) \\
-
- \hline
-\end{tabular}
-\caption{Datasets used during benchmarking, sorted in increasing order of taxa count $N$.
-Number of partitions $P$, total alignment length $L$, and number of patterns $L_\text{eff}$ are also specified.}
-\label{table:datasets}
-\end{table}
-
-\clearpage
-\subsection*{Round 1: A simple operator-weight learning algorithm can improve performance}
-
-We compared the cons, nocons, and adapt operator configurations for the \textit{real} and \textit{quant} parameterisations (\textbf{Table \ref{table:round1Results}}).
-The nocons configuration contained the standard BEAST2 operator mix, while cons contained the operator mix used by Zhang and Drummond 2020 \cite{zhang2020improving}. 
-The adapt mix combines the above operators, as well as the rudimentary \texttt{SampleFromPrior} operator, and learns the weights of each operator using  \texttt{AdaptiveOperatorSampler}.
-
-\begin{table}[h!]
-\centering
-\begin{tabular}{|l l l l|} 
- \hline
-Configuration & Operator & Weight & Parameterisations  \\
-  \hline
- \multirow{6}{*}{nocons} & \texttt{RandomWalk($\mathcal{R}$)} & $10$ & \textit{real}  \\
- 	& \texttt{Scale($\vec{\mathcal{R}}^{\,}$)} & $10$ & \textit{real} \\ 
- 	& \texttt{Uniform($\vec{\mathcal{R}}^{\,}$)} & $10$ & \textit{quant} \\ 
- 	& \texttt{Interval($\vec{\mathcal{R}}^{\,}$)} & $10$ & \textit{quant} \\ 
- 	& \texttt{Swap($\vec{\mathcal{R}}^{\,}$)} & $10$ & \textit{real}, \textit{quant} \\ 
- 	& \texttt{Scale($\sigma$)} & $10$ & \textit{real}, \textit{quant} \\ 
-  \hline
-   \multirow{10}{*}{cons} 
-   & \texttt{ConstantDistance($\vec{\mathcal{R}}^{\,}, \mathcal{T}$)} & $20 \times \frac{2N-2}{2N-1}$ & \textit{real}, \textit{quant}  \\
-   & \texttt{SimpleDistance($\vec{\mathcal{R}}^{\,}, \mathcal{T}$)} & $10 \times \frac{2N-2}{2N-1}$ & \textit{real}, \textit{quant}  \\
-   & \texttt{SmallPulley($\vec{\mathcal{R}}^{\,}$)} & $10 \times \frac{2N-2}{2N-1}$ & \textit{real}, \textit{quant}  \\
-   & \texttt{RandomWalk($\vec{\mathcal{R}}^{\,}$)} & $5$ & \textit{real}  \\
- 	& \texttt{Scale($\vec{\mathcal{R}}^{\,}$)} & $2.5$ & \textit{real} \\ 
- 	& \texttt{Uniform($\vec{\mathcal{R}}^{\,}$)} & $5$ & \textit{quant} \\ 
- 	& \texttt{Interval($\vec{\mathcal{R}}^{\,}$)} & $2.5$ & \textit{quant} \\ 
- 	& \texttt{Swap($\vec{\mathcal{R}}^{\,}$)} & $2.5$ & \textit{real}, \textit{quant} \\ 
- 	& \texttt{FastClockScale($\sigma, \vec{\mathcal{R}}^{\,}$)} & $10$ & \textit{real}  \\ 
- 	& \texttt{Scale($\sigma$)} & $10$ &  \textit{quant} \\ 
-  \hline
-     \multirow{3}{*}{adapt} & \texttt{AdaptiveOperatorSampler($\sigma$)} & $10$ & \textit{real}, \textit{quant} \\
- 	& \texttt{AdaptiveOperatorSampler($\vec{\mathcal{R}}^{\,}$)} & $30 \times \frac{2N-2}{2N-1}$ & \textit{real}, \textit{quant} \\
- 	& \texttt{AdaptiveOperatorSampler(root)} & $30 \times \frac{1}{2N-1}$ & \textit{real}, \textit{quant} \\
-  \hline
-
-\end{tabular}
-\caption{Operator configurations for Round 1. In each configuration, the weight behind $\mathcal{R}$ sums to 30 and for $\sigma$ is equal to 10 within any one rate parameterisation. 
-Operators which apply to either internal nodes or the root (but not both) are weighted according to leaf count $N$.
-The adapt operators are further broken down in \textbf{Table \ref{table:adaptiveSampling}}.}
-%The total weight of all operators across all parameters was 116 in each MCMC setup.
-T%herefore a weight of 10 corresponds to sampling probability of 0.086, for example.
-\label{table:round1Results}
-\end{table}
-
-These results show that, while nocons gives better performance than cons on smaller datasets (corresponding to low signal), and cons performs better on larger datasets (high signal), the adapt configuration gives the best performance overall.
-This trend is observed for both the \textit{real} and the \textit{quant} parameterisations.
-Therefore, the \texttt{AdaptiveOperatorSampler} operator will be included in all subsequent rounds in the tournament.
-
-\clearpage
-\subsection*{Round 2: The \textit{real} parameterisation yields the fastest mixing }
-
-We compared the three rate parameterisations described in \textbf{\nameref{sect:rateparams}}. 
-The \textit{cat} operator configuration is described in \textbf{Table \ref{table:round2Results}}.
-\textit{real} and \textit{quant} make use of constant distance tree operators \cite{zhang2020improving} and both use the \texttt{AdaptiveOperatorSampler} operator to learn clock model operator weights.
-The three settings are validated in \textbf{\nameref{sect:WCSS_appendix}}.
-
-\begin{table}[h!]
-\centering
-\begin{tabular}{|l l l|} 
- \hline
-Configuration & Operator & Weight  \\
-  \hline
- \multirow{4}{*}{\textit{cat}} 
- 	& \texttt{RandomWalk($\vec{\mathcal{R}}^{\,}$)} & $10$ \\
- 	& \texttt{Uniform($\vec{\mathcal{R}}^{\,}$)} & $10$  \\ 
- 	& \texttt{Swap($\vec{\mathcal{R}}^{\,}$)} & $10$ \\ 
- 	& \texttt{Scale($\sigma$)} & $10$ \\ 
-  \hline
-\end{tabular}
-\caption{Operator configurations for \textit{cat} in Round 2. The configurations of \textit{real} (adapt) and \textit{quant} (adapt) are shown in \textbf{Table \ref{table:round1Results}}.}
-\label{table:round2Results}
-\end{table}
-
-%\textbf{Fig.
-\ref{fig:parameterisationResults}} shows that the \textit{real 2006} performs considerably worse than any of the other settings.
-This is due to the poor sampling of the prior under this setting (i.e.
-low ESS of $p(\theta)$).
-The failure of \textit{real 2006} thus highlights the appeal of 1) the \textit{cat} or \textit{quant} parameterisations, both of which have trivial contributions to the prior density (i.e.
-uniform priors), and 2) the smarter operators used by \textit{real} (Zhang and Drummond 2020).
-Due to its computational burden, \textit{real 2006} was not benchmarked for all of the datasets in \textbf{Table \ref{table:datasets}}.
-
-%Our results show that the \textit{quant} parameterisation yields the best performance with respect to effective samples per hour.
-\textit{quant} outperforms \textit{quant 2006}, suggesting that the constant distance operators are effective.
-Furthermore, \textit{quant} outperforms \textit{real} especially at sampling from the posterior and prior distributions (i.e.
-high ESS/hr for $p(\theta|D)$ and $p(\theta)$).
-This is most likely because of the uniform prior distribution of rate quantiles.
-
-%Overall, \textit{quant} yields a median ESS/hr approximately 150 \% faster with respect to sampling the posterior probability, and approximately 30 \% faster with respect to sampling branch rates $r$ and clock standard deviation $\sigma$, compared with \textit{real}.
-
-\begin{figure}[!h]
-\includegraphics[width=\textwidth]{benchmarking/benchmarkingVM/ESS_round1.pdf}
-\caption{\textbf{Rate parameterisation performance evaluation.} Comparison of ESS/hr (averaged across five independent MC3 analyses) with respect to relevant terms -- $P$: posterior density; $L$: likelihood, $p$: prior density, $r$: clock rate ESS averaged across all leaves, $\hat{r}$: branch rate mean, $v$: branch rate variance, $\sigma$: clock standard deviation, $\kappa$: HKY model transition-transversion ratio, $\lambda$: Yule model birth rate.
-$h$: tree height.
-Datasets are displayed in \textbf{Table \ref{table:datasets}}.
-}
-\label{fig:parameterisationResults}
-\end{figure}
-
-% 1-3) the \textit{cat}, \textit{real}, and \textit{quant} parameterisations using the operators described by Drummond et al. 2006 \cite{drummond2006relaxed}; 3) the \textit{quant} parameteristion
-
-\subsection*{Round 3: Bactrian proposal kernels are 10\% more efficient than uniform kernels}
-
-\subsection*{Round 4: Finding the best NER operator variant}
-
-The \textbf{\nameref{sect:NER}} (NER) operators are evaluated.
-This protocol selects the best among 48 NER (no random walk) and 48 NERw ($\text{Bactrian}(0.95)$ random walk) operators, and has two phases.
-First, the best of the 96 is selected by comparing operator acceptance rates on simulated data.
-Second, the selected operator is benchmarked with respect to convergence time and sampling rate on real data (\textbf{Table \ref{table:datasets}}).
-The analyses in this section invoke the \textit{quant} parameterisation and $\text{Bactrian}(0.95)$ proposal kernels on clock model parameters.
-
-\subsubsection*{Initial screening by acceptance rate on simulated data}
-
-We selected the best operator variant by performing MCMC on 300 simulated datasets, where each MCMC employed all 96 NER/NERw variants.
+\subsubsection*{Screening operators by acceptance rate on simulated data}
+
+We selected the best NER operator variant by performing MCMC on 300 simulated datasets, where each MCMC employed all 96 NER/NERw variants. 
 Simulated datasets have $N=30$ taxa and an alignment with $L \sim \text{Uniform}(10^2, 10^4)$ sites. 
-The acceptance rate of each operator is compared to that of the null operator $\text{NER}\{\}$ (i.e.
-\texttt{Narrow Exchange}).
+The acceptance rate of each operator (which in this case is equivalent to the average \texttt{RF} distance) is compared to that of the null operator $\text{NER}\{\}$ (i.e. \texttt{NarrowExchange}).
 
@@
 
-Although there are several operators which are tying for first place and behave equivalently, we selected the $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ operator to proceed to the next round of optimisation.
+Although there are several operators which behaved equivalently during this initial screening process, we selected $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ to proceed to benchmarking (\textbf{\nameref{sect:results}}).
+Due to the apparent sensitivity of NER operators to the dataset, we introduce the adaptive operator \texttt{AdaptiveOperatorSampler(NER)} which allows the operator scheme to fall back on the standard \texttt{NarrowExchange} in the event of $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ performing poorly (\textbf{Table \ref{table:adaptiveNER}}).
+
+\begin{table}[h!]
+\centering
+\begin{tabular}{|l l l|} 
+ \hline
+ Meta-operator & POI & Operators \\
+\hline
+ \multirow{2}{*}{\texttt{AdaptiveOperatorSampler(NER)}} & \multirow{2}{*}{$\mathcal{T}$} & NER$\{  \}$ \\ 
+ && NER$\{ \mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE} \}$ \\
+ \hline
+\end{tabular}
+\caption{The adaptive NER operator. 
+The Robinson-Foulds distance between trees before and after every proposal accept is used to train the operator weights.
+In the special case of NER proposals, the \texttt{RF} distance is always equal to 1.
+}
+\label{table:adaptiveNER}
+\end{table}
+
+\clearpage
+\subsection*{A guided adaptive leaf rate operator}
+\label{AVMVN_sect}
+
+A \textit{guided} operator incorporates knowledge about neighbouring states, while an \textit{adaptive} operator undergoes a training process to improve its efficiency over time \cite{roberts2007coupling}.
+In previous work, parsimony scores and conditional clade probabilities of neighbouring trees have been employed by guided tree operators \cite{hohna2012guided,zhang2020using,meyer2019adaptive} and the latter has also been explored as the basis of  adaptive tree operators \cite{hohna2012guided,meyer2019adaptive}.
+The (adaptive) mirror kernel \cite{thawornwattana2018designing} learns a target distribution which acts as a `mirror image' of the current point $x$.
+The adaptable variance multivariate normal (AVMVN) kernel \cite{baele2017adaptive,suchard2018bayesian} learns correlations between parameters during MCMC.
+Baele et al.
+2017  observed a large increase ($\approx 5-10 \times$) in sampling efficiency from using the AVMVN kernel on clock rates and substitution model parameters across partitions \cite{baele2017adaptive}.
+
+In this article we consider application of the AVMVN kernel to the branch rates of leaf nodes. 
+This operator, referred to as \texttt{LeafAVMVN}, is not readily applicable to internal node branch rates due to their dependencies on tree topology.
+
+\subsubsection*{AVMVN kernel}
+
+The AVMVN kernel assumes its parameters live in $x \in \mathbb{R}^N$ and that these parameters follow a Multivariate Normal distribution with covariance matrix $\Sigma_N$.
+Hence, the kernel operates on the logarithmic or logistic transformation of the $N$ leaf branch rates, depending on the rate parameterisation:
+
+\begin{align}
+	x_i = \begin{cases} \log r_i \text{ for } \textit{real} \\
+						\log \frac{q_i}{1 - q_i} \text{ for } \textit{quant}  \end{cases}
+\end{align}
+
+where $r_i$ is a real rate and $q_i$ is a rate quantile. The AVMVN probability density is defined by
+
+\begin{align}
+	\mathcal{AVMVN}(x) =  \mathcal{MVN}\big(x, (1-\beta) \frac{\Sigma_N}{N} + \beta \frac{\mathbb{I}_N}{N} \big) ,
+\end{align}
+
+where $\mathcal{MVN}$ is the Multivariate Normal probability density.
+$\beta \; (= 0.05)$ is a constant which determines the fraction of the proposal determined by the identity matrix $\mathbb{I}_N$, as opposed to the covariance matrix $\Sigma_D$ which is trained during MCMC.
+
+The AVMVN proposal kernel is computed as
+
+\begin{align}
+	x^\prime &\leftarrow x + \sum\limits_{i=1}^N \sum\limits_{j=i}^N c_{i,j} \times s\Sigma \\
+	\text {where }  c &= \text{cholesky} \left( (1-\beta) \frac{\Sigma_N}{N} + \beta \frac{\mathbb{I}_N}{N} \right).
+\end{align}
+
+The cholesky$(Y)$ decomposition returns a lower diagonal matrix $L$, with positive real diagonal entries, such that $Y = LL^\prime$ \cite{lindstrom1988newton, pourahmadi2007cholesky}.
+$s$ is a tunable step size parameter and $\Sigma$ is a random variable drawn from a proposal kernel (uniform or Bactrian for instance).
+Our BEAST2 implementation of the AVMVN kernel is adapted from that of BEAST \cite{suchard2018bayesian}.
+
+In \nameref{sect:results}, we evaluate the \texttt{LeafAVMVN} operator for its ability to estimate leaf rates. 
+As the size of the covariance matrix $\Sigma_N$ grows with the number of taxa $N$, AVMVN is hypothesised to work well on small trees but become less efficient with larger taxon sets.
+
+\clearpage
+\subsection*{Model specification and MCMC settings} \label{sect:methods}
+
+In all phylogenetic analyses presented here, we use a Yule \cite{yule1925ii} tree prior $p(\mathcal{T}|\lambda)$ with birth rate $\lambda \sim \text{Log-Normal}(1,1.25)$.
+The clock standard deviation has a $\sigma \sim \text{Gamma}(0.5396,0.3819)$ prior.
+Datasets are partitioned into subsequences, where each partition is associated with a distinct HKY substitution model \cite{hasegawa1985dating}.
+The transition-transversion ratio $\kappa \sim \text{Log-Normal}(1, 1.25)$, the four nucleotide frequencies $(f_A, f_C, f_G, f_T) \sim \text{Dirichlet}(10,10,10,10)$, and the relative clock rate $\mu_C \sim \text{Log-Normal}(1, 0.6)$ are estimated independently for each partition.
+The operator scheme ensures that the clock rates $\mu_C$ have a mean of 1 across all partitions. 
+To enable the rapid benchmarking of larger datasets we use BEAGLE for high-performance tree likelihood calculations \cite{ayres2012beagle} and coupled MCMC with four chains for efficient mixing \cite{muller2019coupled}.
+The neighbour joining tree \cite{saitou1987neighbor} is used as the initial state in each MCMC chain.
+
+\subsection*{Operator configurations} \label{sect:operatorSchemes}
+
+Throughout the article, we have introduced four new operators. 
+These are summarised in \textbf{Table \ref{table:newOperators}}.
+
+\begin{table}[h!]
+\centering
+\begin{tabular}{|l p{4cm} l|} 
+ \hline
+ Operator & Description & Parameters  \\
+  \hline
+ \texttt{AdaptiveOperatorSampler} & Samples sub-operators proportionally to their weights, which are learned (see \nameref{sect:adaptiveSampling}). & $\vec{\mathcal{R}}^{\,}, \sigma, \mathcal{T}$ \\
+  \hline
+ \texttt{SampleFromPrior} & Resamples a random number of elements from their prior (see \nameref{sect:adaptiveSampling}). & $\vec{\mathcal{R}}^{\,}, \sigma$ \\
+  \hline
+ \texttt{NarrowExchangeRate} & Moves a branch and recomputes branch rates so that genetic distances are constant (see \nameref{sect:NER}). & $\vec{\mathcal{R}}^{\,}, \mathcal{T}$\\
+  \hline
+ \texttt{LeafAVMVN}  & Proposals new rates for all leaves in one move (see \nameref{AVMVN_sect}) \cite{baele2017adaptive}. & $\vec{\mathcal{R}}^{\,}$ \\
+  \hline
+\end{tabular}
+\caption{Summary of clock model operators introduced throughout this article. Pre-existing clock model operators are summarised in \textbf{Table \ref{table:kernels}}}
+\label{table:newOperators}
+\end{table}
+
+In \textbf{Table \ref{table:operatorSchemes}}, we define all operator configurations which are benchmarked throughout \textbf{\nameref{sect:results}}.
+
+\begin{table}[h!]
+\centering
+\begin{tabular}{|l l l l l l|} 
+ \hline
+Configuration & Operator & Weight & \textit{real} & \textit{cat} & \textit{quant}  \\
+  \hline
+ \multirow{6}{*}{nocons} & \texttt{RandomWalk($\mathcal{R}$)} & $10$ & \checkmark &&  \\
+ 	& \texttt{Scale($\vec{\mathcal{R}}^{\,}$)} & $10$ & \checkmark && \\ 
+ 	& \texttt{Uniform($\vec{\mathcal{R}}^{\,}$)} & $10$ & & \checkmark & \checkmark \\ 
+ 	& \texttt{Interval($\vec{\mathcal{R}}^{\,}$)} & $10$ &  & & \checkmark \\ 
+ 	& \texttt{Swap($\vec{\mathcal{R}}^{\,}$)} & $10$ & \checkmark & \checkmark & \checkmark \\ 
+ 	& \texttt{Scale($\sigma$)} & $10$ & \checkmark & \checkmark & \checkmark \\ 
+  \hline
+   \multirow{10}{*}{cons} 
+   & \texttt{ConstantDistance($\vec{\mathcal{R}}^{\,}, \mathcal{T}$)} & $20 \times \frac{2N-2}{2N-1}$ & \checkmark & & \checkmark  \\
+   & \texttt{SimpleDistance($\vec{\mathcal{R}}^{\,}, \mathcal{T}$)} & $10 \times \frac{2N-2}{2N-1}$ & \checkmark & & \checkmark  \\
+   & \texttt{SmallPulley($\vec{\mathcal{R}}^{\,}$)} & $10 \times \frac{2N-2}{2N-1}$ & \checkmark & & \checkmark  \\
+   & \texttt{RandomWalk($\vec{\mathcal{R}}^{\,}$)} & $5$ & \checkmark &&  \\
+ 	& \texttt{Scale($\vec{\mathcal{R}}^{\,}$)} & $2.5$ & \checkmark && \\ 
+ 	& \texttt{Uniform($\vec{\mathcal{R}}^{\,}$)} & $5$ & &&\checkmark \\ 
+ 	& \texttt{Interval($\vec{\mathcal{R}}^{\,}$)} & $2.5$ & &&\checkmark\\ 
+ 	& \texttt{Swap($\vec{\mathcal{R}}^{\,}$)} & $2.5$ & \checkmark & & \checkmark  \\ 
+ 	& \texttt{FastClockScale($\sigma, \vec{\mathcal{R}}^{\,}$)} & $10$ & \checkmark  && \\ 
+ 	& \texttt{Scale($\sigma$)} & $10$ &  &&\checkmark \\ 
+  \hline
+     \multirow{3}{*}{adapt} & \texttt{AdaptiveOperatorSampler($\sigma$)} & $10$ & \checkmark & \checkmark & \checkmark  \\
+ 	& \texttt{AdaptiveOperatorSampler($\vec{\mathcal{R}}^{\,}$)} & $30 \times \frac{2N-2}{2N-1}$ & \checkmark & & \checkmark  \\
+ 	& \texttt{AdaptiveOperatorSampler($\vec{\mathcal{R}}^{\,}$)} & $30$ &  & \checkmark & \\
+ 	& \texttt{AdaptiveOperatorSampler(root)} & $30 \times \frac{1}{2N-1}$ & \checkmark & & \checkmark  \\
+
+  \hline
+
+\end{tabular}
+\caption{Operator configurations and the substitution rate parameterisations which each operator are applicable to.
+Within each configuration (and substitution rate parameterisation), the weight behind $\mathcal{R}$ sums to 30 and the weight of $\sigma$ is equal to 10.
+There is no cons (\textit{cat}) configuration because the parameterisation is not compatible the constant distance operators.
+Operators which apply to either internal nodes or the root (but not both) are weighted according to leaf count $N$.
+The adapt operators are further broken down in \textbf{Table \ref{table:adaptiveSampling}}.}
+%The total weight of all operators across all parameters was 116 in each MCMC setup.
+T%herefore a weight of 10 corresponds to sampling probability of 0.086, for example.
+\label{table:operatorSchemes}
+\end{table}
+
+\clearpage
+\section*{Results} \label{sect:results}
+
+\subsection*{Assessment criteria and datasets}
+
+% Cite HKY somewhere hasegawa1985dating
+
+To avoid a cross-product explosion, the five targets for clock model improvement are evaluated sequentially in the following order: \textbf{\nameref{sect:adaptiveSampling}} \textbf{\nameref{sect:rateparams}}, \textbf{\nameref{sect:randomwalks}}, \textbf{\nameref{sect:NER}}, and \textbf{\nameref{AVMVN_sect}}.
+The four operators introduced in these sections are summarised in \textbf{Table \ref{table:newOperators}}.
+The setting which is considered to be the best in each step is then incorporated into the following step. This protocol and its outcomes are summarised in \textbf{Fig. \ref{fig:tournament}}.
+
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{Figures/tournament.pdf}
+\caption{\textbf{Protocol for optimising clock model methodologies.} Each area (detailed in \textbf{\nameref{sect:models}}) is optimised sequentially, and the best setting from each step is used when optimising the following step.}
+\label{fig:tournament}
+\end{figure}
+
+Methodologies are assessed according to the following criteria.
+
+\textbf{1.
+Validation}.
+This is assessed by measuring the coverage of all estimated parameters in a well-calibrated simulation study, using 100 simulated datasets (with $N=100$ taxa and $L=5000$ nucleotide alignments).
+These are presented in \textbf{\nameref{sect:WCSS_appendix}}.
+\\
+
+\textbf{2. Mixing of parameters}. Key parameters are evaluated for the number of effective samples generated per hour (ESS/hr). This calculation is performed by BEAST2 \cite{bouckaert2019beast}. \\
+
+%\textbf{3.
+Time to convergence}.
+Two independent MCMC chains are run and the time is measured until: a) the absolute difference in clade posterior probability between the two chains is less than 0.05 for all clades, b) the Rubin-Gelman statistic $\hat{R}$ \cite{gelman1992inference} of every estimated parameter is less than 1.05, and c) the effective sample size \cite{rambaut2018posterior} of every estimated parameter is greater than 200 in each chain.
+\\
+
+Methodologies are benchmarked using one simulated and eight empirical datasets.
+The latter were compiled \cite{lanfear2019Github} and partitioned \cite{lanfear2016partitionfinder} by Lanfear et al. as `benchmark alignments' (\textbf{Table \ref{table:datasets}}).
+Each methodology is benchmarked across 5 replicates on each dataset, using an the Intel Xeon Gold 6138 CPU (2.00 GHz).
+All methodologies use identical models and operator configurations, except where a difference is specified.
+
+%All 25 datasets presented in \textbf{Table \ref{table:datasets}} are benchmarked together $1 \times$ each at the end of the protocol.
+Datasets and BEAST2 .xml templates are provided in the GitHub repository accompanying this article.
+
+% https://github.com/roblanf/BenchmarkAlignments
+\begin{table}[h!]
+\centering
+\begin{tabular}{|l| l l l l l|} 
+ \hline
+  & $N$ & $P$ & $L$ (kb) & $L_\text{eff}$ (kb) & \textbf{Description} \\
+  \hline
+
+ 1  &  38  &  16  &  15.5  &  10.5  &  Seed plants (Ran 2018 \cite{Ran_2018}) \\
+
+2  &  44  &  7  &  5.9  &  1.8  &  Squirrel Fishes (Dornburg 2012 \cite{Dornburg_2012}) \\
+
+3  &  44  &  3  &  1.9  &  0.8  &  Bark beetles (Cognato 2001 \cite{Cognato_2001}) \\
+
+4  &  51  &  6  &  5.4  &  1.8  &  Southern beeches (Sauquet 2011 \cite{Sauquet_2011}) \\
+
+5  &  61  &  8  &  6.9  &  4.3  &  Bony fishes (Broughton 2013 \cite{Broughton_2013}) \\
+
+6  &  70  &  3  &  2.2  &  0.9  &  Caterpillars (Kawahara 2013 \cite{Kawahara_2013}) \\
+
+7  &  80  &  1 &  10.0  &  0.9  &  \textit{Simulated data}  \\
+
+8  &  94  &  4  &  2.2  &  1  &  Bees (Rightmyer 2013 \cite{Rightmyer_2013}) \\
+
+9  &  106  &  1  &  0.8  &  0.5  &  Songbirds (Moyle 2016 \cite{Moyle_2016}) \\
+
+ \hline
+\end{tabular}
+\caption{Datasets used during benchmarking, sorted in increasing order of taxa count $N$.
+Number of partitions $P$, total alignment length $L$, and number of site patterns $L_\text{eff}$ in the alignment are also specified.}
+\label{table:datasets}
+\end{table}
+
+\clearpage
+\subsection*{Round 1: A simple operator-weight learning algorithm can improve performance}
+
+We compared the cons, nocons, and adapt operator configurations for the \textit{real} and \textit{quant} parameterisations (\textbf{Table \ref{table:operatorSchemes}}). 
+The nocons configuration contained the standard BEAST2 operator mix, while cons contained the operator mix used by Zhang and Drummond 2020 \cite{zhang2020improving}. 
+The adapt mix combines the above operators, as well as the simple-but-bold \texttt{SampleFromPrior} operator, and learns the weights of each operator using  \texttt{AdaptiveOperatorSampler}.
+We also tested the adapt (\textit{cat}) configuration to determine whether \textit{cat} can be further improved by learning the underlying weights behind \texttt{RandomWalk}, \texttt{Swap}, and \texttt{SampleFromPrior}.
+
+These results show that nocons performs better than cons on small datasets while cons performs better on large datasets (\textbf{Fig.
+\ref{fig:round1Results}} and \textbf{\nameref{sect:SR_appendix}}).
+This is an expected result and is true for both the \textit{real} and the \textit{quant} parameterisations.
+The adapt configuration dramatically improved mixing for \textit{real}, by finding the right balance between these two extremes.
+However the \texttt{AdaptiveOperatorSampler} operator did not benefit for either \textit{cat} or \textit{quant}, suggesting that the default operator weighting scheme was sufficient in either case.
+Overall, the \texttt{AdaptiveOperatorSampler} operator will be included in all subsequent rounds in the tournament.
+
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{benchmarking/benchmarkingVM/ESS_round1_real.pdf}
+\caption{\textbf{Round 1: benchmarking the \texttt{AdaptiveOperatorSampler} operator.} Top left, top right, bottom left: each plot compares the ESS/hr ($\pm 2$ standard errors) across two operator configurations with respect to relevant terms -- $L$: likelihood, $p$: prior density, $r$: clock rate ESS averaged across all leaves, $\sigma$: clock standard deviation, $h$: tree height, and $\kappa$: HKY model transition-transversion ratio.
+Bottom right: the effect of sequence length $L$ on operator weights learned by \texttt{AdaptiveOperatorSampler}. Both sets of results are fit by a logistic regression curve.
+ The benchmark datasets are displayed in \textbf{Table \ref{table:datasets}}. The \emph{cat} and \emph{quant} evaluations are presented in \nameref{sect:SR_appendix}.  }
+\label{fig:round1Results}
+\end{figure}
+
+\clearpage
+\subsection*{Round 2: The \textit{real} parameterisation yields the fastest mixing }
+
+We compared the three rate parameterisations described in \textbf{\nameref{sect:rateparams}}. 
+adapt (\textit{real}) and adapt (\textit{quant}) both employ constant distance tree operators \cite{zhang2020improving} and both use the \texttt{AdaptiveOperatorSampler} operator to learn clock model operator weights.
+Clock model operators weights are also learned in the adapt (\textit{cat}) configuration.
+
+This experiment revealed that the \textit{real} parameterisation greatly outperforms both \textit{cat} and \textit{quant} on most datasets (\textbf{Fig. \ref{fig:round2Results}}).
+This disparity is strongest for large datasets.
+In the most extreme case, $r$ and $\sigma$ both mixed around $70 \times$ faster on the 15.5 kb Seed plant dataset by \cite{Ran_2018} for \textit{real} than they did for \textit{cat}.
+The advantages in using constant distance operators would likely be even stronger for larger $L$.
+Overall, we have determined that \textit{real}, and its associated operators, makes the best parameterisation covered here and will proceed to the next rounds of the benchmarking.
+
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{benchmarking/benchmarkingVM/ESS_round2.pdf}
+\caption{\textbf{Round 2: benchmarking substitution rate parameterisations.} Top left, top right, bottom left: the adapt (\textit{real}), adapt (\textit{cat}), and adapt (\textit{quant}) configurations were compared.
+See \textbf{Fig.
+\ref{fig:round1Results}} caption for figure notation.
+Bottom right: comparison of the mean tip rate ESS/hr as a function of sequence length.
+}
+\label{fig:round2Results}
+\end{figure}
+
+% 1-3) the \textit{cat}, \textit{real}, and \textit{quant} parameterisations using the operators described by Drummond et al. 2006 \cite{drummond2006relaxed}; 3) the \textit{quant} parameteristion
+
+\subsection*{Round 3: Bactrian proposal kernels are 10\% more efficient than uniform kernels}
+
+\subsection*{Round 4: Finding the best NER operator variant}
+
+The \textbf{\nameref{sect:NER}} (NER) operators are evaluated.
+This protocol selects the best among 48 NER (no random walk) and 48 NERw ($\text{Bactrian}(0.95)$ random walk) operators, and has two phases.
+First, the best of the 96 is selected by comparing operator acceptance rates on simulated data.
+Second, the selected operator is benchmarked with respect to convergence time and sampling rate on real data (\textbf{Table \ref{table:datasets}}).
+The analyses in this section invoke the \textit{quant} parameterisation and $\text{Bactrian}(0.95)$ proposal kernels on clock model parameters.
 
@@
 
+\paragraph*{S3 Appendix.}
+\label{sect:SR_appendix}
+{\textbf{Supplementary results.} Presentation and interpretation of further benchmarking results.
+
 \nolinenumbers

### 2020-08-10 benchmarking/benchmarkingVM/submit_CSjob.sh

@@ -5,9 +5,9 @@
 #~/beast/bin/beast  -overwrite -beagle_SSE ../datasets/startdummy.xml
 
 #settings=("real" "real_adaptive" "cat" "quant" "AVMN" "bactrian98" "bactrian95" "NER" "real_06" "quant_06")
-settings=("cat" "cat_adaptive" "real" "real_06" "real_adaptive" "quant_cached" "quant_cached_adaptive" "quant_06_cached" "bactrian95")
+settings=("cat" "cat_adaptive" "real" "real_06" "real_adaptive" "quant_cached" "quant_cached_adaptive" "quant_06_cached" "bactrian95" "NER")
 
-datasets=("Rightmyer_2013" "Ran_2018_dna" "Broughton_2013" "simulated" "Sauquet_2011" "Moyle_2016" "Dornburg_2012" "Kawahara_2013" "Cognato_2001")
+datasets=("Ran_2018_dna" "Rightmyer_2013" "Broughton_2013" "simulated" "Sauquet_2011" "Moyle_2016" "Dornburg_2012" "Kawahara_2013" "Cognato_2001")
 
 
 

### 2020-08-10 benchmarking/render.R

@@ -3,13 +3,15 @@ library(tikzDevice)
 library(HDInterval)
 library(lubridate)
 library(colorspace)
+library(rjson)
 
 
-PER_CHAIN = TRUE
+
+PER_CHAIN = FALSE
 
 #settings = c("cat", "real", "quant", "bactrian95", "bactrian98")
 settings = c("cat",  "real_06", "quant_06", "real", "quant", "bactrian95", "bactrian98", "NER", "AVMN")
-settings = c("cat",  "real_06", "real", "real_adaptive", "quant_06_cached", "quant_cached_adaptive", "quant_cached", "bactrian95")
+settings = c("cat", "cat_adaptive",  "real_06", "real", "real_adaptive", "quant_06_cached", "quant_cached_adaptive", "quant_cached", "bactrian95", "NER")
 
 benchmark = data.frame(batch = numeric(0), param = character(0), dataset = character(0), partition = numeric(0), setting = character(0), nstates = numeric(0), finalESS = numeric(0), finalMCD = numeric(0), done = logical(0),  error = logical(0))
 
@@ -18,6 +20,7 @@ benchmark = data.frame(batch = numeric(0), param = character(0), dataset = chara
 
 settings.names = lapply(settings, function(x) x)
 settings.names["cat"] = "\\textit{cat}"
+settings.names["cat_adaptive"] = "adapt (\\textit{cat})"
 
 settings.names["real"] = "cons (\\textit{real})"
 settings.names["real_06"] = "nocons (\\textit{real})"
@@ -43,7 +46,7 @@ progress.df$batch = ifelse(progress.df$batch == 4, 5, ifelse(progress.df$batch =
 
 
 #parameters = c("posterior", "likelihood", "prior", "height", "birthRate", "kappa",  "ucldStdev", "clockRate", "TipRates", "RateStatLogger.mean", "RateStatLogger.variance")
-parameters = c("prior", "likelihood", "TipRates", "height", "ucldStdev", "clockRate")
+parameters = c("prior", "likelihood", "TipRates", "height", "ucldStdev", "kappa")
 
 
 parameters.latex = lapply(parameters, function(x) x)
[…]

### 2020-08-20 clockSD.R
clock sd operators

@@ -1,0 +1,92 @@
+
+library(tikzDevice)
+
+
+
+basewidth = 7
+baseheight = basewidth * 0.618
+filename = "clockSD.tex"
+options(tikzMetricPackages = c("\\usepackage[utf8]{inputenc}",
+    "\\usepackage[T1]{fontenc}", "\\usetikzlibrary{calc}",
+    "\\usepackage{amssymb}"))
+## I need the amssymb package because I use \mathcal and \mathbb
+	tikz(filename, width = basewidth, height = baseheight*1, standAlone = TRUE,
+    	packages = c("\\usepackage{tikz}",
+	         "\\usepackage[active,tightpage,psfixbb]{preview}",
+	         "\\PreviewEnvironment{pgfpicture}",
+	         "\\setlength\\PreviewBorder{0pt}",
+	         "\\usepackage{amssymb}"))
+
+
+
+par(mfrow = c(1,1))
+par(mar = c(5,5,5,5))
+par(cex.lab = 1.4)
+par(cex.main = 1.4)
+
+
+
+sigma = 0.4
+mu = -0.5*sigma^2
+sigma2 = 0.8
+mu2 = -0.5*sigma2^2
+
+r = seq(from = 0.001, to = 2, length = 500)
+q1 = plnorm(r, mu, sigma)
+q2 = plnorm(r, mu2, sigma2)
+
+
+# $\\vec{\\mathcal{R}}$
+plot(r, q1, type = "l", xlab = "Rate", ylab = "Quantile", main = "$\\sigma$ scale operators", xaxs = "i", yaxs = "i", axes = F, lwd=2, xlim = c(0, 2), ylim = c(0,1))
+points(r, q2, type = "l", col = "red", lwd=2)
+
+legend("topleft", c(paste0("$\\sigma=", sigma, "$"), paste0("$\\sigma^\\prime=", sigma2, "$")), col = c("black", "red"), lwd = 2, bty = "n")
+
+
+# Scale
+s_r0 = 0.7
+s_q0 = plnorm(s_r0, mu, sigma)
+s_q1 = plnorm(s_r0, mu2, sigma2)
+lines(c(s_r0, s_r0), c(0, max(s_q0, s_q1)), lwd = 2, col = "#696969", lty = "1515")
+
[…]

### 2020-08-20 manuscript.tex
tidy

@@
 
-The simplest phylogenetic clock model -- the strick clock -- makes the convenient assumption that the evolutionary rate is constant across all lineages \cite{zuckerkandl1965evolutionary, kuhner1995estimating, larget1999markov}.
+The simplest phylogenetic clock model -- the strick clock -- makes the mathematically convenient assumption that the evolutionary rate is constant across all lineages \cite{zuckerkandl1965evolutionary, kuhner1995estimating, larget1999markov}.
 % Early examples?
@@
 
-When $\sigma$ is proposed under either \textit{quant} or \textit{cat}, all of the rates $r(\vec{\mathcal{R}}^{\,})$ are proposed along with it, thus enabling large changes to the state space with a single proposal.
-Whereas, this is not the case for \textit{real}, which led to the development of the \texttt{FastClockScale} operator \cite{zhang2020improving}.
-
 %A potential disadvantage of the \textit{quant} method would be the computational requirements of continuously evaluating the i-cdf.
@@
 \clearpage
-\subsection*{Adaptive operator weighting}
-\label{sect:adaptiveSampling}
+\subsection*{Clock model operators}
+\label{sect:clockModelOperators}
 
@@
 
+\begin{table}[h!]
+\centering
+\begin{tabular}{|l p{4.2cm} l l|} 
+ \hline
+ Operator & Description & Parameters & Parameterisations  \\
+  \hline
+ \texttt{RandomWalk} & Moves a single element by a tunable amount. & $\vec{\mathcal{R}}^{\,}, \sigma$ & \textit{cat}, \textit{real}, \textit{quant} \\
+  \hline
+\texttt{Scale} & Applies \texttt{RandomWalk} on the log-transformation (suitable for parameters with positive domains). & $\vec{\mathcal{R}}^{\,}, \sigma$ & \textit{real}, \textit{quant}  \\
+  \hline
+ \texttt{Interval} & Applies \texttt{RandomWalk} on the logit-transformation (suitable for parameters with upper and lower limits). & $\vec{\mathcal{R}}^{\,}$ & \textit{quant}  \\
+  \hline
+ \texttt{Swap} & Swaps two random elements in the vector \cite{drummond2006relaxed}. & $\vec{\mathcal{R}}^{\,}$  & \textit{cat}, \textit{real}, \textit{quant}  \\
+ \hline
+\texttt{Uniform} & Resamples one element in the vector from a uniform distribution. & $\vec{\mathcal{R}}^{\,}$  & \textit{cat}, \textit{quant}  \\
+ \hline
+\texttt{ConstantDistance} & Adjusts an internal node height and recalculates all incident branch rates such that the genetic distances remain constant \cite{zhang2020improving}.
+& $\vec{\mathcal{R}}^{\,}, \mathcal{T}$ & \textit{real}, \textit{quant} \\
+ \hline
+\texttt{SimpleDistance} & Applies \texttt{ConstantDistance} to the root node \cite{zhang2020improving}.  & $\vec{\mathcal{R}}^{\,}, \mathcal{T}$ & \textit{real}, \textit{quant} \\
+ \hline
+\texttt{SmallPulley} & Proposes new branch rates incident to the root such that their combined genetic distance is constant  \cite{zhang2020improving}.
+& $\vec{\mathcal{R}}^{\,}$ & \textit{real}, \textit{quant} \\
+ \hline
+\texttt{CisScale} & Applies \texttt{Scale} to $\sigma$.
+Then recomputes all rates such that their quantiles are constant (for \textit{real} \cite{zhang2020improving}) or recomputes all quantiles such that their rates are constant (\textit{quant}).
+& $\vec{\mathcal{R}}^{\,}, \sigma$ & \textit{real}, \textit{quant} \\
+ \hline
+\end{tabular}
+\caption{Summary of pre-existing BEAST2 operators, which apply to either branch rates $\vec{\mathcal{R}}^{\,}$ or the clock standard deviation $\sigma$, and the substitution rate parameterisation they apply to.
+ \texttt{ConstantDistance} and \texttt{SimpleDistance} also adjust node heights in the tree $\mathcal{T}$. }
+\label{table:kernels}
+\end{table}
+
+The family of constant distance operators (\texttt{ConstantDistance}, \texttt{SimpleDistance}, and \texttt{SmallPulley} \cite{zhang2020improving}) are best suited for larger datasets (or datasets with strong signal) where the likelihood distribution is peaked (\textbf{Fig.
+\ref{fig:rateparams}}).
+While simple one dimensional operators such as \texttt{RandomWalk} or \texttt{Scale} must make small steps in order to stay ``on the ridge'' of the likelihood function, the constant distance operators ``wander along the ridge''  by ensuring that genetic distances are constant after the proposal.
+
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{Figures/correlations.pdf}
+\caption{\textbf{Traversing likelihood space.}
+The z-axes above are the log-likelihoods of the genetic distance $r \times \tau$ between two simulated nucleic acid sequences of length $L$, under the Jukes-Cantor substitution model \cite{jukes1969evolution}.
+Two possible proposals from the current state (white circle) are depicted.
+These proposals are generated by the \texttt{RandomWalk} (\texttt{RW}) and \texttt{ConstantDistance} (\texttt{CD}) operators.
+In the low signal dataset ($L=0.1$kb), both operators can traverse the likelihood space effectively.
+ However, the exact same proposal by \texttt{RandomWalk} incurs a much larger likelihood penalty in the $L=0.5$kb dataset by ``falling off the ridge'', in contrast to \texttt{ConstantDistance} which ``walks along the ridge''.
+ This discrepancy is even stronger for larger datasets and thus necessitates the use of operators such as \texttt{ConstantDistance} which account for correlations between branch lengths and rates. }
+\label{fig:rateparams}
+\end{figure}
+
+ \texttt{Scale} and \texttt{CisScale} both operate on the clock model standard deviation $\sigma$ however they behave differently in the \textit{real} and \textit{quant} parameterisations (\textbf{Fig.
+\ref{fig:clockSDoperators}}).
+In \textit{real}, large proposals of $\sigma \rightarrow \sigma^\prime$ made by  \texttt{Scale} are likely to be rejected due to large penalties in clock model prior $p(\vec{\mathcal{R}}^{\,}|\sigma^\prime)$.
+This led to the development of the fast clock scaler \cite{zhang2020improving} (herein referred to as \texttt{CisScale}), which recomputes all branch rates $\vec{\mathcal{R}}^{\,} \rightarrow \vec{\mathcal{R}}^{\, \prime}$ such that their quantiles under the new clock model prior remain constant $p(\vec{\mathcal{R}}^{\,}|\sigma) = p(\vec{\mathcal{R}}^{\, \prime}|\sigma^\prime)$.
+In contrast, a proposal made by \texttt{Scale} $\sigma \rightarrow \sigma^\prime$ under the \textit{quant} parameterisation implicitly alters all branch rates $r(\vec{\mathcal{R}}^{\,})$ while leaving the quantiles $\vec{\mathcal{R}}^{\,}$ themselves constant.
+But by applying \texttt{CisScale} under \textit{quant},
+all quantiles are recomputed $\vec{\mathcal{R}} \rightarrow \vec{\mathcal{R}}^\prime$  such that the respective branch rates are constant i.e.
+$r(\vec{\mathcal{R}}^{\,}) = r(\vec{\mathcal{R}}^{\,\prime})$.
+Overall, \texttt{Scale} and \texttt{CisScale} propose rates/quantiles in the opposite (trans) or same (cis) space that the clock model is parameterised under (\textbf{Fig.
+\ref{fig:clockSDoperators}}).
+
+\begin{figure}[!h]
+\centering
+\includegraphics[width=\textwidth]{Figures/clockSD.pdf}
+\caption{\textbf{Clock standard deviation scale operators.}
+The two operators above propose a clock standard deviation $\sigma^\prime \leftarrow \sigma \times e^{s\Sigma}$ for some step size $s \Sigma$. 
+Then, either the new quantiles are such that the rates remain constant (``New quantiles'', above) or the new rates are  such that the quantiles remain constant (``New rates''). 
+In the \textit{real} parameterisation, these two operators are known as \texttt{Scale} and \texttt{CisScale}, respectively.
+Whereas, in \textit{quant}, they are known as \texttt{CisScale} and \texttt{Scale}.    }
+\label{fig:clockSDoperators}
+\end{figure}
+
+\clearpage
+\subsection*{Adaptive operator weighting}
+\label{sect:adaptiveSampling}
+
 % Section intro
@@
 Any general theoretical examples of this?
-
-\begin{table}[h!]
-\centering
-\begin{tabular}{|l p{4.2cm} l l|} 
- \hline
- Operator & Description & Parameters & Parameterisations  \\
-  \hline
- \texttt{RandomWalk} & Moves a single element by a tunable amount. & $\vec{\mathcal{R}}^{\,}, \sigma$ & \textit{cat}, \textit{real}, \textit{quant} \\
-  \hline
-\texttt{Scale} & Applies \texttt{RandomWalk} on the log-transformation (suitable for parameters with positive domains). & $\vec{\mathcal{R}}^{\,}, \sigma$ & \textit{real}, \textit{quant}  \\
-  \hline
- \texttt{Interval} & Applies \texttt{RandomWalk} on the logit-transformation (suitable for parameters with upper and lower limits). & $\vec{\mathcal{R}}^{\,}$ & \textit{quant}  \\
-  \hline
- \texttt{Swap} & Swaps two random elements in the vector \cite{drummond2006relaxed}. & $\vec{\mathcal{R}}^{\,}$  & \textit{cat}, \textit{real}, \textit{quant}  \\
- \hline
-\texttt{Uniform} & Resamples one element in the vector from a uniform distribution. & $\vec{\mathcal{R}}^{\,}$  & \textit{cat}, \textit{quant}  \\
- \hline
-\texttt{ConstantDistance} & Adjusts an internal node height and recalculates all incident branch rates such that the genetic distances remain constant \cite{zhang2020improving}.
-& $\vec{\mathcal{R}}^{\,}, \mathcal{T}$ & \textit{real}, \textit{quant} \\
- \hline
-\texttt{SimpleDistance} & Applies \texttt{ConstantDistance} to the root node \cite{zhang2020improving}.  & $\vec{\mathcal{R}}^{\,}, \mathcal{T}$ & \textit{real}, \textit{quant} \\
- \hline
-\texttt{SmallPulley} & Proposes new branch rates incident to the root such that their combined genetic distance is constant  \cite{zhang2020improving}.
-& $\vec{\mathcal{R}}^{\,}$ & \textit{real}, \textit{quant} \\
- \hline
-\texttt{FastClockScale} & Applies \texttt{Scale} to $\sigma$ and then recomputes all rates $\vec{\mathcal{R}}^{\,}$ such that their quantiles under the prior $p(\vec{\mathcal{R}}^{\,}|\sigma)$ are constant \cite{zhang2020improving}.
-& $\vec{\mathcal{R}}^{\,}, \sigma$ & \textit{real} \\
- \hline
-\end{tabular}
-\caption{Summary of pre-existing BEAST2 operators, which apply to either branch rates $\vec{\mathcal{R}}^{\,}$ or the clock standard deviation $\sigma$, and the substitution rate parameterisation they apply to.
- \texttt{ConstantDistance} and \texttt{SimpleDistance} also adjust node heights in the tree $\mathcal{T}$. }
-\label{table:kernels}
-\end{table}
 
@@
 
-We also introduce the \texttt{SampleFromPrior($\vec{x}^{\,}$)} operator.
+Datasets with strong signal (or large $L$) are likely to achieve faster convergence when the more precise and meticulous kinds of operators are employed, such as those informed by correlations within the posterior distribution (\textbf{Fig.
+\ref{fig:rateparams}}).
+Whereas, datasets which contain very poor signal (or small $L$) are likely to mix faster when more weight is placed on bold operators. 
+We therefore introduce the \texttt{SampleFromPrior($\vec{x}^{\,}$)} operator.
 This operator resamples $\psi$ randomly selected elements within vector $\vec{x}^{\,}$ from their prior distributions, where $\psi \sim \text{Binomial}(n=|\vec{x}^{\,}|, p=\frac{s}{|\vec{x}^{\,}|})$ for tunable term $s$.
-
-We hypothesise that datasets with strong signal (or large $L$) will mix best when the more precise and meticulous kind of operator is employed, such as those informed by correlations within the posterior distribution e.g.
-the family of constant distance operators \cite{zhang2020improving} (\textbf{Fig.
-\ref{fig:rateparams}}).
-Whereas, datasets which contain very poor signal (or small $L$) are likely to mix best when there is more weight placed on bold operators such as \texttt{SampleFromPrior}, \texttt{Swap}, or \texttt{Uniform} which sample each branch rate independently of its current estimate.
+%The \texttt{Uniform} operator is a special case of \texttt{SampleFromPrior}.
+\texttt{SampleFromPrior} is always included among the mixture of operators under \texttt{AdaptiveOperatorSampler} and serves to make the boldest proposals for datasets with poor signal.
 Ideally, an operator to the likes of \texttt{AdaptiveOperatorSampler} would learn the combination of weights behind these classes of operators best suited for any given dataset.
 
-\begin{figure}[!h]
-\includegraphics[width=\textwidth]{Figures/correlations.pdf}
-\caption{\textbf{Traversing likelihood space.}
-The z-axes above are the log-likelihoods of the genetic distance $r \times \tau$ between two simulated nucleic acid sequences of length $L$, under the Jukes-Cantor substitution model \cite{jukes1969evolution}.
-Two possible proposals from the current state (red circle) are depicted.
-These proposals are generated by the \texttt{RandomWalk} (\texttt{RW}) and \texttt{ConstantDistance} (\texttt{CD}) operators.
-In the low signal dataset ($L=0.1$kb), both operators can traverse the likelihood space effectively.
- However, the exact same proposal by \texttt{RandomWalk} incurs a much larger likelihood penalty in the $L=0.5$kb dataset by ``falling off the ridge'', in contrast to \texttt{ConstantDistance} which ``walks along the ridge''.
- This discrepancy is even stronger for larger datasets and thus necessitates the use of operators such as \texttt{ConstantDistance} which account for correlations between branch lengths and rates. }
-\label{fig:rateparams}
-\end{figure}
-
-In this article we apply three instances of the \texttt{AdaptiveOperatorSampler} meta-operator to the \textit{real} and \textit{quant} parameterisations. 
+In this article we apply three instances of the \texttt{AdaptiveOperatorSampler} meta-operator to the \textit{real}, \textit{cat}, and \textit{quant} parameterisations. 
 These are summarised in \textbf{Table \ref{table:adaptiveSampling}}.
@@
 \hline
- \multirow{4}{*}{\texttt{AdaptiveOperatorSampler($\sigma$)}} & \multirow{4}{*}{$\sigma$} & \texttt{FastClockScale($\sigma, \vec{\mathcal{R}}^{\,}$)} \\ 
+ \multirow{4}{*}{\texttt{AdaptiveOperatorSampler($\sigma$)}} & \multirow{4}{*}{$\sigma$} & \texttt{CisScale($\sigma, \vec{\mathcal{R}}^{\,}$)} \\ 
  && \texttt{RandomWalk($\sigma$)}  \\
@@
 \end{tabular}
-\caption{Summary of the three instances of \texttt{AdaptiveOperatorSampler} and their parameters of interest (POI).
-Note that different operators are applicable to different substitution rate parameterisations (\textbf{Table \ref{table:kernels}}). 
+\caption{Summary of \texttt{AdaptiveOperatorSampler} operators and their parameters of interest (POI).
+Different operators are applicable to different substitution rate parameterisations (\textbf{Table \ref{table:kernels}}). 
 \texttt{AdaptiveOperatorSampler(root)} applies the root-targeting constant distance operators only \cite{zhang2020improving} while \texttt{AdaptiveOperatorSampler($\vec{\mathcal{R}}^{\,}$)} targets all rates and all nodes heights $t$.
-The two meta-operators are weighted proportionally to the contribution of the root node to the total node count. }
+These two operators are weighted proportionally to the contribution of the root node to the total node count. }
 \label{table:adaptiveSampling}
@@
  \hline
-6 & \texttt{FastClockScale}  & $x^\prime \leftarrow x \times e^{s\Sigma}$ & $\sigma$   \\
+6 & \texttt{CisScale}  & $x^\prime \leftarrow x \times e^{s\Sigma}$ & $\sigma$   \\
  \hline
@@
 
-\subsubsection*{Screening operators by acceptance rate on simulated data}
-
-We selected the best NER operator variant by performing MCMC on 300 simulated datasets, where each MCMC employed all 96 NER/NERw variants. 
-Simulated datasets have $N=30$ taxa and an alignment with $L \sim \text{Uniform}(10^2, 10^4)$ sites. 
-The acceptance rate of each operator (which in this case is equivalent to the average \texttt{RF} distance) is compared to that of the null operator $\text{NER}\{\}$ (i.e. \texttt{NarrowExchange}).
-
-\textbf{Fig.
-\ref{fig:acceptanceRateScreening}} shows that NER variants which satisfy the genetic distances between nodes $B$ and $A$ (i.e.
+\paragraph{4. Screening operators for acceptance rate using simulated data.}
+
+The best NER operator variant to proceed to benchmarking on empirical data (\textbf{\nameref{sect:results}}) was selected by  performing MCMC on simulated data, measuring the acceptance rates of each of the 96 NER/NERw variants, and comparing them with the null operator $\text{NER}\{\}$ / \texttt{NarrowExchange}.
+In total, there were 300 simulated datasets each with $N=30$ taxa and varying alignment lengths.
+
+%The acceptance rate of each operator (which in this case is equivalent to the average \texttt{RF} distance) was compared to that of the null operator $\text{NER}\{\}$ (i.e. \texttt{NarrowExchange}).
+
+These experiments showed that NER variants which satisfy the genetic distances between nodes $B$ and $A$ (i.e.
 $\mathcal{D}_{AB}$) or between $B$ and $C$ (i.e.
-$\mathcal{D}_{BC}$) usually perform worse than the standard \texttt{Narrow Exchange} operator, where $B$ is the node being interchanged from the $A$ branch to the $C$ branch (\textbf{Fig.
-\ref{fig:narrowexchange}}).
+$\mathcal{D}_{BC}$) usually performed worse than the standard \texttt{NarrowExchange} operator (\textbf{Fig.
+\ref{fig:acceptanceRateScreening}}).
 This is an intuitive result. 
-If the posterior distribution is relatively flat, and the data presents high uncertainty in the positioning of $B$, with respect to $A$ and $C$, then the topological rearrangement performed by \texttt{Narrow Exchange} will be favoured.
-However, this uncertainty in the \textit{topology} is likely coupled with uncertainty in the \textit{distance} between $B$ and $A$ or between $B$ and $C$.
-Thus, in this case, respecting the $\mathcal{D}_{AB}$ and $\mathcal{D}_{BC}$ constraints (by proposing branch rates) makes too many unnecessary changes to the state and the operator performs worse.
+If there is high uncertainty in the positioning of $B$ with respect to $A$ and $C$, then there is no value in respecting either of these distance constraints, and the proposals made to the rates may often be too bold or the Green ratio $|J|$ too small for the proposal to be accepted.
 
@@
 \ref{fig:acceptanceRateScreening}} also reveals a cluster of NER variants which -- under the conditions of the simulation --  performed better than the null operator $\text{NER}\{\}$ around 25\% of the time and performed worse around 10\% of the time.
-One such operator is  $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ and is presented in \textbf{Algorithm \ref{alg:NER2}}. 
-This variant conserves the genetic distance between the child nodes ($A, B, C$) and the grandparent node $E$.
-This is performed by proposing rates for $r_A$, $r_B$, and $r_C$ while obeying the distance constraints imposed by the operator.
-Exploring this operator further, we can see that $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ is at its best when there is a large variance in branch rate i.e.
-when clock standard deviation $\sigma$ is high ($\sigma \gtrsim 0.5$ for $N=30$), corresponding to data which is not clock-like.
-On the other hand, $\text{NER}\{\}$ is much preferred when the operator's acceptance rate is high ($\gtrsim 0.15$) -- corresponding to datasets with short sequences ($L < 1$kb for $N=30$) and thus poor signal.
+One such operator is  $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$  (\textbf{Algorithm \ref{alg:NER2}}). 
+This variant conserves the genetic distance between nodes $A$, $B$, $C$ and their grandparent $E$. 
+Moreover, this operator performs well when branch rates have a large variance ($\sigma > 0.5$), corresponding to data which is not clock-like. 
+On the other hand, the null operator $\text{NER}\{\}$ performs better on shorter sequences ($L < 1$kb) and therefore weaker signal.  
 Overall, $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ outperforms the standard \texttt{NarrowExchange} operator when the data is not clock-like and contains enough signal.
 
-Finally, \textbf{Fig.
-\ref{fig:acceptanceRateScreening}} shows that by applying a (Bactrian) random walk to $t_D$ -- the height of internal node $D$ -- the acceptance rate of NER plummets dramatically.
-This effect is most dominant for the NER variants which satisfy distance constraints (i.e.
-the operators which are not $\text{NER}\{\}$).
-This result is unfortunate however not unexpected, and is consistent with Lakner et al.
-2008 \cite{lakner2008efficiency}, who observed that tree operators perform best when they change either topology, or branch lengths, but not both.
-
-Although there are several operators which behaved equivalently during this initial screening process, we selected $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ to proceed to benchmarking (\textbf{\nameref{sect:results}}).
-Due to the apparent sensitivity of NER operators to the dataset, we introduce the adaptive operator \texttt{AdaptiveOperatorSampler(NER)} which allows the operator scheme to fall back on the standard \texttt{NarrowExchange} in the event of $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ performing poorly (\textbf{Table \ref{table:adaptiveNER}}).
+Finally, this initial screening showed that applying a (Bactrian) random walk to the node height $t_D$ made the operator worse.
+This effect was most dominant for the NER variants which satisfy distance constraints (i.e. the operators which are not $\text{NER}\{\}$).
+
+Although there were several operators which behaved equivalently during this initial screening process, we selected $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ to proceed to benchmarking (\textbf{\nameref{sect:results}}).
+Due to the apparent sensitivity of NER operators to the data, we introduce the adaptive operator \texttt{AdaptiveOperatorSampler(NER)} which allows the operator scheme to fall back on the standard \texttt{NarrowExchange} in the event of $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ performing poorly (\textbf{Table \ref{table:adaptiveNER}}).
 
@@
  	& \texttt{Swap($\vec{\mathcal{R}}^{\,}$)} & $2.5$ & \checkmark & & \checkmark  \\ 
- 	& \texttt{FastClockScale($\sigma, \vec{\mathcal{R}}^{\,}$)} & $10$ & \checkmark  && \\ 
+ 	& \texttt{CisScale($\sigma, \vec{\mathcal{R}}^{\,}$)} & $10$ & \checkmark  && \checkmark \\ 
  	& \texttt{Scale($\sigma$)} & $10$ &  &&\checkmark \\ 
@@
  	& \texttt{AdaptiveOperatorSampler(root)} & $30 \times \frac{1}{2N-1}$ & \checkmark & & \checkmark  \\
+ 	 \hline
+ 	 \hline
+ 	\multirow{1}{*}{NER\{\}} & \texttt{NarrowExchange} & $15$ & \checkmark & \checkmark  & \checkmark  \\
+ 	\hline
+ 	\multirow{1}{*}{NER} & \texttt{AdaptiveOperatorSampler(NER)} & $15$ & \checkmark &  & \checkmark  \\
 
@@
 \caption{Operator configurations and the substitution rate parameterisations which each operator are applicable to.
-Within each configuration (and substitution rate parameterisation), the weight behind $\mathcal{R}$ sums to 30 and the weight of $\sigma$ is equal to 10.
+Within each configuration (and substitution rate parameterisation), the weight behind $\mathcal{R}$ sums to 30, the weight of $\sigma$ is equal to 10, and the weight of NER is equal to 15.
 There is no cons (\textit{cat}) configuration because the parameterisation is not compatible the constant distance operators.
@@
 
-To avoid a cross-product explosion, the five targets for clock model improvement are evaluated sequentially in the following order: \textbf{\nameref{sect:adaptiveSampling}} \textbf{\nameref{sect:rateparams}}, \textbf{\nameref{sect:randomwalks}}, \textbf{\nameref{sect:NER}}, and \textbf{\nameref{AVMVN_sect}}.
+To avoid a cross-product explosion, the five targets for clock model improvement are evaluated sequentially in the following order: \textbf{\nameref{sect:adaptiveSampling}}, \textbf{\nameref{sect:rateparams}}, \textbf{\nameref{sect:randomwalks}}, \textbf{\nameref{sect:NER}}, and \textbf{\nameref{AVMVN_sect}}.
 The four operators introduced in these sections are summarised in \textbf{Table \ref{table:newOperators}}.
@@
 
-\textbf{1.
-Validation}.
-This is assessed by measuring the coverage of all estimated parameters in a well-calibrated simulation study, using 100 simulated datasets (with $N=100$ taxa and $L=5000$ nucleotide alignments).
-These are presented in \textbf{\nameref{sect:WCSS_appendix}}.
-\\
-
-\textbf{2. Mixing of parameters}. Key parameters are evaluated for the number of effective samples generated per hour (ESS/hr). This calculation is performed by BEAST2 \cite{bouckaert2019beast}. \\
+\textbf{1. Validation}. This is assessed by measuring the coverage of all estimated parameters in well-calibrated simulation studies. These are presented in \textbf{\nameref{sect:WCSS_appendix}}. \\
+
+\textbf{2. Mixing of parameters}. Key parameters are evaluated for the number of effective samples generated per hour (ESS/hr). 
+This calculation is performed by BEAST2 \cite{bouckaert2019beast}. \\
 
@@
 Methodologies are benchmarked using one simulated and eight empirical datasets.
-The latter were compiled \cite{lanfear2019Github} and partitioned \cite{lanfear2016partitionfinder} by Lanfear et al. as `benchmark alignments' (\textbf{Table \ref{table:datasets}}).
-Each methodology is benchmarked across 5 replicates on each dataset, using an the Intel Xeon Gold 6138 CPU (2.00 GHz).
+The latter were compiled \cite{lanfear2019Github} and partitioned \cite{lanfear2016partitionfinder} by Lanfear et al. as ``benchmark alignments'' (\textbf{Table \ref{table:datasets}}).
+Each methodology is benchmarked across 5 replicates on each dataset, using the Intel Xeon Gold 6138 CPU (2.00 GHz).
 All methodologies use identical models and operator configurations, except where a difference is specified.
@@
  \hline
-  & $N$ & $P$ & $L$ (kb) & $L_\text{eff}$ (kb) & \textbf{Description} \\
+  & $N$ & $P$ & $L$ (kb) & $L_\text{unq}$ (kb) & \textbf{Description} \\
   \hline
@@
 \caption{Datasets used during benchmarking, sorted in increasing order of taxa count $N$.
-Number of partitions $P$, total alignment length $L$, and number of site patterns $L_\text{eff}$ in the alignment are also specified.}
+Number of partitions $P$, total alignment length $L$, and number of unique site patterns $L_\text{unq}$ in the alignment are also specified.
+}
 \label{table:datasets}
@@
 
-We compared the cons, nocons, and adapt operator configurations for the \textit{real} and \textit{quant} parameterisations (\textbf{Table \ref{table:operatorSchemes}}). 
-The nocons configuration contained the standard BEAST2 operator mix, while cons contained the operator mix used by Zhang and Drummond 2020 \cite{zhang2020improving}. 
-The adapt mix combines the above operators, as well as the simple-but-bold \texttt{SampleFromPrior} operator, and learns the weights of each operator using  \texttt{AdaptiveOperatorSampler}.
-We also tested the adapt (\textit{cat}) configuration to determine whether \textit{cat} can be further improved by learning the underlying weights behind \texttt{RandomWalk}, \texttt{Swap}, and \texttt{SampleFromPrior}.
-
-These results show that nocons performs better than cons on small datasets while cons performs better on large datasets (\textbf{Fig.
+We compared the nocons, cons, and and adapt operator configurations (\textbf{Table \ref{table:operatorSchemes}}).
+nocons contained all of the standard BEAST2 operator configurations for \textit{real}, \textit{cat}, and \textit{quant}.
+cons additionally contained (cons)tant distance operators and employed the same operator weighting scheme used previously \cite{zhang2020improving} (\textit{real} and \textit{quant} only). 
+Finally, the adapt configuration combined all of the above applicable operators, as well as the simple-but-bold \texttt{SampleFromPrior} operator, and learned the weights of each operator using  \texttt{AdaptiveOperatorSampler}.
+
+This experiment revealed that nocons performed better than cons on datasets with small $L$ while cons performed better on larger datasets (\textbf{Fig.
 \ref{fig:round1Results}} and \textbf{\nameref{sect:SR_appendix}}).
-This is an expected result and is true for both the \textit{real} and the \textit{quant} parameterisations.
-The adapt configuration dramatically improved mixing for \textit{real}, by finding the right balance between these two extremes.
-However the \texttt{AdaptiveOperatorSampler} operator did not benefit for either \textit{cat} or \textit{quant}, suggesting that the default operator weighting scheme was sufficient in either case.
+This result is unsurprising (\textbf{Fig. \ref{fig:rateparams}}).
+Furthermore, the adapt setup dramatically improved mixing for \textit{real} by finding the right balance between cons and nocons.
+This yielded an average ESS/hr of XXX times that of cons and YYY times that of nocons, with respect to leaf branch rates.   
+However adapt did not improve \textit{cat} or \textit{quant}, suggesting that the default operator weighting scheme was sufficient in either case.
 Overall, the \texttt{AdaptiveOperatorSampler} operator will be included in all subsequent rounds in the tournament.
@@
 \includegraphics[width=\textwidth]{benchmarking/benchmarkingVM/ESS_round1_real.pdf}
-\caption{\textbf{Round 1: benchmarking the \texttt{AdaptiveOperatorSampler} operator.} Top left, top right, bottom left: each plot compares the ESS/hr ($\pm 2$ standard errors) across two operator configurations with respect to relevant terms -- $L$: likelihood, $p$: prior density, $r$: clock rate ESS averaged across all leaves, $\sigma$: clock standard deviation, $h$: tree height, and $\kappa$: HKY model transition-transversion ratio.
+\caption{\textbf{Round 1: benchmarking the \texttt{AdaptiveOperatorSampler} operator.} Top left, top right, bottom left: each plot compares the ESS/hr ($\pm 2$ standard errors) across two operator configurations with respect to relevant terms -- $L$: log likelihood, $p$: log prior density, $r$: substitution rate ESS averaged across all leaves, $\sigma$: clock standard deviation, $h$: tree height, and $\kappa$: HKY model transition-transversion ratio.
 Bottom right: the effect of sequence length $L$ on operator weights learned by \texttt{AdaptiveOperatorSampler}. Both sets of results are fit by a logistic regression curve.
- The benchmark datasets are displayed in \textbf{Table \ref{table:datasets}}. The \emph{cat} and \emph{quant} evaluations are presented in \nameref{sect:SR_appendix}.  }
+ The benchmark datasets are displayed in \textbf{Table \ref{table:datasets}}. The \emph{cat} and \emph{quant} settings are evaluated in \nameref{sect:SR_appendix}.  }
 \label{fig:round1Results}
@@
 We compared the three rate parameterisations described in \textbf{\nameref{sect:rateparams}}. 
-adapt (\textit{real}) and adapt (\textit{quant}) both employ constant distance tree operators \cite{zhang2020improving} and both use the \texttt{AdaptiveOperatorSampler} operator to learn clock model operator weights.
-Clock model operators weights are also learned in the adapt (\textit{cat}) configuration.
-
-This experiment revealed that the \textit{real} parameterisation greatly outperforms both \textit{cat} and \textit{quant} on most datasets (\textbf{Fig. \ref{fig:round2Results}}).
+adapt (\textit{real}) and adapt (\textit{quant}) both employed constant distance tree operators \cite{zhang2020improving} and both used the \texttt{AdaptiveOperatorSampler} operator to learn clock model operator weights.
+Clock model operators weights were also learned in the adapt (\textit{cat}) configuration.
+
+This experiment showed that the \textit{real} parameterisation greatly outperformed both \textit{cat} and \textit{quant} on most datasets (\textbf{Fig. \ref{fig:round2Results}}).
 This disparity is strongest for large datasets.
-In the most extreme case, $r$ and $\sigma$ both mixed around $70 \times$ faster on the 15.5 kb Seed plant dataset by \cite{Ran_2018} for \textit{real} than they did for \textit{cat}.
+In the most extreme case, leaf substitution rates $r$ and clock standard deviation $\sigma$ both mixed around $70 \times$ faster on the 15.5 kb seed plant dataset \cite{Ran_2018} for \textit{real} than they did for \textit{cat}.
 The advantages in using constant distance operators would likely be even stronger for larger $L$.
@@
 \ref{fig:round1Results}} caption for figure notation.
-Bottom right: comparison of the mean tip rate ESS/hr as a function of sequence length.
+Bottom right: comparison of the mean tip substitution rate ESS/hr as a function of sequence length.
 }
@@
 
+% Points to cover
+
+% - Dont change branch lengths and topology at the same time.
+This result is unfortunate however not unexpected, and is consistent with Lakner et al.
+2008 \cite{lakner2008efficiency}, who observed that tree operators perform best when they change either topology, or branch lengths, but not both.
+
 \begin{figure}[!h]
@@
 \includegraphics[width=\textwidth]{Figures/broughton.pdf}
-\caption{\textbf{Maximum clade credibility trees.} Trees from the bark beetle data by Cognato et al.
-2001 \cite{Cognato_2001} (top) and the bony fish data by Broughton et al.
-2013 \cite{Broughton_2013} (bottom) are presented above.
-Branches are coloured by substitution rate (units: substitutions per site per unit of time) and the y-axis shows arbitrary units of time.
-Internal nodes are labelled with posterior clade support.
-Figures generated by UglyTrees \cite{uglytrees}.
-}
+\caption{\textbf{Maximum clade credibility trees.} 
+Phylogenetic trees of bark beetles (Cognato et al. 2001 \cite{Cognato_2001}; top) and bony fishes (Broughton et al. 2013 \cite{Broughton_2013}; bottom) are presented. 
+Branches are coloured by substitution rate (units: substitutions per site per unit of time) and the y-axis shows time, such that there is on average 1 substitution per unit of time.
+ Internal nodes are labelled with posterior clade support. Figures generated by UglyTrees \cite{uglytrees}.  }
 \label{fig:parameterisationResults}

### 2020-08-20 correlations.R

@@ -99,8 +99,8 @@ for (L in c(100, 500)){
 
 
 	# Draw an arrow
-	arrow.col = "#FF4500" #"black" #"#FF4500"
-	font.col = arrow.col
+	arrow.col = "white" # "#FF4500" "black"
+	font.col = "black" # arrow.col
 	#points(0.3, 0.3, pch = 16, col = arrow.col)
 
 	r0 = 0.5
@@ -113,7 +113,7 @@ for (L in c(100, 500)){
 	# Randomwalk
 	Arrows(r0, t0, r0 + dr, t0, lcol = arrow.col,  arr.type="curved")
 	#text(r0 + dr + 0.05, t0, "$x^\\prime$", adj = c(0, 0.3), col = font.col)
-	text(r0 + dr/2, t0 + 0.02, "\\texttt{RW}", adj = c(0.5, 0), cex = 1.2)
+	text(r0 + dr/2, t0 + 0.02, "\\texttt{RW}", adj = c(0.5, 0), cex = 1.2, col = font.col)
 
 
 
@@ -124,7 +124,7 @@ for (L in c(100, 500)){
 	#r1 = r0*t0/t1
 	Arrows(r0, t0, r1, t1, lcol = arrow.col,  arr.type="curved")
 	#text(r1, t1 + 0.05, "$x^\\prime$", adj = c(0.5, 0), col = font.col)
-	text((r0 + r1)/2 - 0.01, (t0 + t1)/2, "\\texttt{CD}", adj = c(1, 0.5), cex = 1.2)
+	text((r0 + r1)/2 - 0.01, (t0 + t1)/2, "\\texttt{CD}", adj = c(1, 0.5), cex = 1.2, col = font.col)
 
 	points(r0, t0, pch = 21, col = "black", bg=arrow.col, cex = 2, lwd = 2)
 	#text(r0, t0, "$x$", adj = c(0, 0), col = font.col)
@@ -132,10 +132,6 @@ for (L in c(100, 500)){
 
 
 }
-
-
-
-
 
 
 

### 2020-08-20 manuscript.tex
quantiles linear

@@
 The function for transforming $\mathcal{R}$ into branch rates $r(\mathcal{R})$ is depicted for \textit{real} (top right), \textit{cat} (bottom left), and \textit{quant} (bottom right).
-For simplicity there are 10 \textit{cat} bins displayed, however in practice there are $2N-2$ bins. }
+For visualisation purposes, there are only 10 bins/pieces displayed, however in practice there are $2N-2$ bins for \textit{cat} and 100 pieces for \textit{quant}.
+The first and final \textit{quant} pieces are equal to the underlying function however the pieces in between use linear approximations of this function. }
 \label{fig:rateparams}
@@
 
-Transforming these quantiles into rates invokes the i-CDF of the underlying \textit{real} clock model distribution:
-
-\begin{align}
-r(\mathcal{R}_i) =& \; F^{-1}(\mathcal{R}_i).
-\end{align}
-
-However, evaluation of the i-CDF is computationally demanding and this may hinder the performance of the \textit{quant} parameterisation.
-
-While this approach has clear similarities with \textit{cat}, the domain of rates here is continuous (as opposed to being confined to a discrete number of bins).
-In this project we extended the family of constant distance operators  \cite{zhang2020improving} so they are compatible with \textit{quant} (\textbf{\nameref{sect:S1Appendix}}).
+Transforming these quantiles into rates invokes the i-CDF of the underlying \textit{real} clock model distribution.
+However, this function is computationally demanding to evaluate and therefore an approximation of the i-CDF is used:
+
+\begin{align}
+r(\mathcal{R}_i) =& \; \hat{F}^{-1}(\mathcal{R}_i)
+\end{align}
+
+where $\hat{F}^{-1}$ is a linear piecewise approximation with 100 pieces.
+While this approach has clear similarities with \textit{cat}, the domain of rates here is continuous instead of discrete.
+In this project we extended the family of constant distance operators  \cite{zhang2020improving} so that they are compatible with \textit{quant}.
+Further details on the \textit{quant} piecewise approximation and constant distance operators can be found in \textbf{\nameref{sect:S1Appendix}}.
 

### 2020-08-20 lognormal.R

@@ -36,7 +36,7 @@ par(cex.main = 1.5)
 # 1) pdf
 x = seq(from = 0, to = xmax, by = 0.01)
 
-plot(0, 0, type = "n", xaxs = "i", lwd = 3, yaxs = "i", axes = F, xlab = "Branch rate $r$", ylab = "$p(r|\\sigma)$",
+plot(0, 0, type = "n", lwd = 3, yaxs = "i", axes = F, xlab = "Branch rate $r$", ylab = "$p(r|\\sigma)$",
 main = "Probability density function (Log-Normal)", xlim = c(0, xmax), ylim=c(0, 5))
 
 
@@ -62,7 +62,7 @@ axis(2, las=2)
 
 
 # 2) real
-plot(0, 1, type = "n", xaxs = "i", yaxs = "i", axes = F, xlab = "Abstraction $\\mathcal{R}$ [rate]", ylab = "Branch rate $r(\\mathcal{R})$",
+plot(0, 1, type = "n", yaxs = "i", axes = F, xlab = "Abstraction $\\mathcal{R}$ [rate]", ylab = "Branch rate $r(\\mathcal{R})$",
 main = "\\textit{real}", xlim =c(0, xmax), ylim=c(0, xmax))
 
 lines(c(0, xmax), c(0, xmax), lwd = 3)
@@ -100,16 +100,45 @@ axis(2, at = seq(from = 0, to = xmax, by = 0.5), las=2)
 
 
 # 4) quantiles
+nquant = 10
 plot(0, 1, type = "n", yaxs = "i", axes = F, xlab = "Abstraction $\\mathcal{R}$ [quantile]", ylab = "Branch rate $r(\\mathcal{R})$",
-main = paste0("\\textit{quant}"), xlim =c(0, 1), ylim=c(0, xmax))
+main = paste0("\\textit{quant} with ", nquant, " pieces"), xlim =c(0, 1), ylim=c(0, xmax))
 
 
 for (i in 1:length(Svals)){
 	S = Svals[i]
 	M = Mvals[i]
-	x = seq(from = 0, to = 1, by = 0.001)
-	y = c(qlnorm (x[-length(x)], M, S), xmax*2)
-	lines(x, y, pch = 16, col = Scols[i], lwd = 3)
+	
+
+	for (b in 0:(nquant-1)){
+		
+		q0 = b / nquant
+		q1 = (b+1) / nquant
+		
[…]

### 2020-08-21 manuscript.tex
tidy ups

@@
 
-The weight of an operator determines the probability of the operator being selected at each step during MCMC.
-In BEAST2, operators can have a tunable parameter $s$ which determines the step size of the operator \cite{bouckaert2019beast}. 
-Although $s$ is learned throughout the MCMC chain, the operator weights themselves are typically held constant.
-Pre-existing BEAST2 clock model operators (i.e.
-those which generate proposals for either $\vec{\mathcal{R}}^{\,}$ or $\sigma$) are summarised in \textbf{Table \ref{table:kernels}}, and further operators are introduced throughout the paper.
+The weight of an operator determines the probability of the operator being selected and is typically fixed throughout MCMC.
+In BEAST2, operators can have its own tunable parameter $s$ which determines the step size of the operator, and this term is learned over the course of the MCMC \cite{bouckaert2019beast}. 
+Here, we define clock model operators as those which generate proposals for either $\vec{\mathcal{R}}^{\,}$ or $\sigma$.
+Pre-existing BEAST2 clock model operators are summarised in \textbf{Table \ref{table:kernels}}, and further operators are introduced throughout the paper.
 
@@
 \centering
-\begin{tabular}{|l p{4.2cm} l l|} 
+\begin{tabular}{l p{4.2cm} l l} 
  \hline
@@
 \centering
-\begin{tabular}{|l l l|} 
- \hline
+\begin{tabular}{l l l} 
  Meta-operator & POI & Operators \\
@@
 &&  \texttt{SmallPulley($\vec{\mathcal{R}}^{\,}, t$)}  \\
- \hline
 \end{tabular}
@@
 \centering
-\begin{tabular}{|l| p{3cm} l l|} 
- \hline
+\begin{tabular}{l p{3cm} l l}
+
  & Operator(s) & Proposal & Parameter $x$   \\
@@
 6 & \texttt{CisScale}  & $x^\prime \leftarrow x \times e^{s\Sigma}$ & $\sigma$   \\
- \hline
 \end{tabular}
@@
 \includegraphics[width=\textwidth]{Figures/acceptanceRates.pdf}
-\caption{\textbf{Screening of NER and NERw variants by acceptance rate.} Top left: comparison of NER variants with the null operator $\text{NER}\{\}$ (i.e.
-\texttt{NarrowExchange}).
-Each of the 48 operators are represented by a single point, uniquely encoded by the point stylings.
+\caption{\textbf{Screening of NER and NERw variants by acceptance rate.} Top left: comparison of NER variants with the null operator $\text{NER}\{\}$ / \texttt{NarrowExchange}. 
+Each operator is represented by a single point, uniquely encoded by the point stylings. 
 The number of times each operator is proposed and accepted is compared with that of $\text{NER}\{\}$, and one-sided z-tests are performed to assess the statistical significance between the two acceptance rates ($p = 0.001$).
-This process is repeated for each of $300$ simulated datasets.
+This process is repeated across $300$ simulated datasets.
 The axes of each plot are the proportion of these $300$ simulations for which there is evidence that the operator is significantly better than $\text{NER}\{\}$ (x-axis) or worse than $\text{NER}\{\}$ (y-axis).
@@
  && NER$\{ \mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE} \}$ \\
- \hline
 \end{tabular}
@@
 \centering
-\begin{tabular}{|l p{4cm} l|} 
- \hline
+\begin{tabular}{l p{4cm} l} 
  Operator & Description & Parameters  \\
@@
  \texttt{LeafAVMVN}  & Proposals new rates for all leaves in one move (see \nameref{AVMVN_sect}) \cite{baele2017adaptive}. & $\vec{\mathcal{R}}^{\,}$ \\
-  \hline
 \end{tabular}
@@
 \centering
-\begin{tabular}{|l l l l l l|} 
- \hline
+\begin{tabular}{l l l l l l} 
 Configuration & Operator & Weight & \textit{real} & \textit{cat} & \textit{quant}  \\
@@
  	\multirow{1}{*}{NER} & \texttt{AdaptiveOperatorSampler(NER)} & $15$ & \checkmark &  & \checkmark  \\
-
-  \hline
-
 \end{tabular}
@@
 Within each configuration (and substitution rate parameterisation), the weight behind $\mathcal{R}$ sums to 30, the weight of $\sigma$ is equal to 10, and the weight of NER is equal to 15.
-There is no cons (\textit{cat}) configuration because the parameterisation is not compatible the constant distance operators.
+%There is no cons (\textit{cat}) configuration because the parameterisation is not compatible the constant distance operators.
 Operators which apply to either internal nodes or the root (but not both) are weighted according to leaf count $N$.
-The adapt operators are further broken down in \textbf{Table \ref{table:adaptiveSampling}}.}
+The adapt operators are further broken down in \textbf{Table \ref{table:adaptiveSampling}}.
+All other operators (i.e. those which apply to which apply to other terms in the state such as the nucleotide substitution model) are held constant within each dataset.
+}
+
 %The total weight of all operators across all parameters was 116 in each MCMC setup.
-T%herefore a weight of 10 corresponds to sampling probability of 0.086, for example.
+%%herefore a weight of 10 corresponds to sampling probability of 0.086, for example.
 \label{table:operatorSchemes}
@@
 \centering
-\begin{tabular}{|l| l l l l l|} 
- \hline
+\begin{tabular}{l l l l l l} 
   & $N$ & $P$ & $L$ (kb) & $L_\text{unq}$ (kb) & \textbf{Description} \\
@@
 
- \hline
 \end{tabular}
-\caption{Datasets used during benchmarking, sorted in increasing order of taxa count $N$.
+\caption{Benchmark datasets, sorted in increasing order of taxa count $N$.
 Number of partitions $P$, total alignment length $L$, and number of unique site patterns $L_\text{unq}$ in the alignment are also specified.
@@
 
-We compared the nocons, cons, and and adapt operator configurations (\textbf{Table \ref{table:operatorSchemes}}).
-nocons contained all of the standard BEAST2 operator configurations for \textit{real}, \textit{cat}, and \textit{quant}.
+We compared the nocons, cons, and adapt operator configurations (\textbf{Table \ref{table:operatorSchemes}}).
+nocons contained all of the standard BEAST2 operator configurations and weightings for \textit{real}, \textit{cat}, and \textit{quant}.
 cons additionally contained (cons)tant distance operators and employed the same operator weighting scheme used previously \cite{zhang2020improving} (\textit{real} and \textit{quant} only). 
-Finally, the adapt configuration combined all of the above applicable operators, as well as the simple-but-bold \texttt{SampleFromPrior} operator, and learned the weights of each operator using  \texttt{AdaptiveOperatorSampler}.
+Finally, the adapt configuration combined all of the above applicable operators, as well as the simple-but-bold \texttt{SampleFromPrior} operator, and learned the weights of each operator using the  \texttt{AdaptiveOperatorSampler}.
 
@@
 Bottom right: the effect of sequence length $L$ on operator weights learned by \texttt{AdaptiveOperatorSampler}. Both sets of results are fit by a logistic regression curve.
- The benchmark datasets are displayed in \textbf{Table \ref{table:datasets}}. The \emph{cat} and \emph{quant} settings are evaluated in \nameref{sect:SR_appendix}.  }
+ The benchmark datasets are displayed in \textbf{Table \ref{table:datasets}}. The \emph{cat} and \emph{quant} settings are evaluated in \textbf{\nameref{sect:SR_appendix}}.  }
 \label{fig:round1Results}
@@
 This experiment showed that the \textit{real} parameterisation greatly outperformed both \textit{cat} and \textit{quant} on most datasets (\textbf{Fig. \ref{fig:round2Results}}).
-This disparity is strongest for large datasets.
+This disparity is strongest for long alignments.
 In the most extreme case, leaf substitution rates $r$ and clock standard deviation $\sigma$ both mixed around $70 \times$ faster on the 15.5 kb seed plant dataset \cite{Ran_2018} for \textit{real} than they did for \textit{cat}.
@@
 
-\subsection*{Round 4: Finding the best NER operator variant}
-
-The \textbf{\nameref{sect:NER}} (NER) operators are evaluated.
-This protocol selects the best among 48 NER (no random walk) and 48 NERw ($\text{Bactrian}(0.95)$ random walk) operators, and has two phases.
-First, the best of the 96 is selected by comparing operator acceptance rates on simulated data.
-Second, the selected operator is benchmarked with respect to convergence time and sampling rate on real data (\textbf{Table \ref{table:datasets}}).
-The analyses in this section invoke the \textit{quant} parameterisation and $\text{Bactrian}(0.95)$ proposal kernels on clock model parameters.
-
-\subsubsection*{Benchmarking convergence time}
+We benchmarked the adapt (\textit{real}) configuration with a) standard uniform proposal kernels, and b) Bactrian(0.95) kernels.
+These kernels applied to all clock rate related operators (\textbf{Table \ref{table:bactriankernels}}).
+
+\subsection*{Round 4: Evaluating adaptive NER}
+
+Our initial screening of the \texttt{NarrowExchangeRate} (NER) operators revealed that the $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ operator outperformed the standard $\text{NER} \{\}$ / \texttt{NarrowExchange} operator about 25\% of the time on simulated data, however it was also very sensitive to the dataset.
+Therefore we wrapped up the two operators ($\text{NER} \{\}$ and $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$) within an \texttt{AdaptiveOperatorSampler} operator so that the appropriate weights can be learned, using the Robinson-Foulds metric.
+In this round we benchmarked the adapt + Bactrian(0.95) (\textit{real})  setting with a) $\text{NER} \{\}$ only, and b) adaptive $\text{NER}$ (\textbf{Table \ref{table:operatorSchemes}}).
 

### 2020-08-24 benchmarking/benchmarkingVM/ESS_round1_catquant.tex
results update

@@
-% Created by tikzDevice version 0.12.3 on 2020-08-10 13:51:28
+% Created by tikzDevice version 0.12.3.1 on 2020-08-24 19:04:32
 % !TEX encoding = UTF-8 Unicode
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,301.03) {ESS/hr [nocons (\textit{quant})]};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,433.62) {ESS/hr [cons (\textit{quant})]};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,301.03) {ESS/chain [nocons (\textit{quant})]};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,433.62) {ESS/chain [cons (\textit{quant})]};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,374.64) --
-	(203.52,578.16);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (286.65,578.16) --
-	(286.65,490.17) --
-	(  0.00,203.52);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (  0.00,346.12) --
-	(232.04,578.16);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (286.65,578.16) --
-	(286.65,518.69) --
-	(  0.00,232.04);
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (  0.00,317.60) --
-	(260.56,578.16);
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (286.65,578.16) --
-	(286.65,547.21) --
-	(  0.00,260.56);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (142.89,342.31) {$\frac{1}{64} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,435.87) {$64\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (114.37,342.31) {$\frac{1}{16} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,407.35) {$16\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 84.20,342.31) {$\frac{1}{4} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92,378.83) {$4\times$};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,368.65) --
+	(209.51,578.16);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (283.33,578.16) --
+	(283.33,492.84) --
+	(  0.00,209.51);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (  0.00,342.13) --
+	(236.03,578.16);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (283.33,578.16) --
+	(283.33,519.37) --
+	(  0.00,236.03);
+
+\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (  0.00,315.60) --
+	(262.56,578.16);
+
+\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (283.33,578.16) --
+	(283.33,545.89) --
+	(  0.00,262.56);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (136.90,342.31) {$\frac{1}{64} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,429.88) {$64\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (110.38,342.31) {$\frac{1}{16} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,403.36) {$16\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 82.20,342.31) {$\frac{1}{4} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92,376.84) {$4\times$};
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 94.65,416.78) --
-	(103.65,416.78);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.64,409.37) --
-	( 99.64,422.22);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 99.64,413.56) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.25,476.46) --
-	(190.95,476.46);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.73,475.74) --
-	(188.73,477.16);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.73,472.43) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.21,474.21) --
-	(104.27,474.21);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (102.34,473.61) --
-	(102.34,474.79);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (102.34,470.18) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.11,416.10) --
-	(103.73,416.10);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.87,410.35) --
-	( 99.87,420.59);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 99.87,412.07) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.40,387.89) --
-	(115.90,387.89);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (106.65,384.62) --
-	(106.65,390.72);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (106.65,384.99) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.54,483.66) --
-	(195.01,483.66);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.29,483.25) --
-	(194.29,484.06);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.29,480.76) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.24,453.03) --
-	(151.45,453.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.58,451.65) --
-	(148.58,454.32);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (148.58,449.80) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.12,479.26) --
-	(197.83,479.26);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.99,477.50) --
-	(196.99,480.89);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.99,475.23) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.36,483.73) --
-	(188.58,483.73);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.98,483.50) --
-	(187.98,483.96);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.98,479.70) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.83,449.81) --
-	(142.53,449.81);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.76,448.18) --
-	(140.76,451.31);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (140.76,445.77) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.30,448.54) --
-	(152.66,448.54);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (149.31,447.26) --
-	(149.31,449.74);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (149.31,445.63) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.59,488.02) --
-	(199.40,488.02);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (199.00,487.58) --
-	(199.00,488.46);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.00,485.12) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.84,422.09) --
-	(126.52,422.09);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (122.64,409.09) --
-	(122.64,429.99);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (122.64,418.86) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.62,458.97) --
-	(195.24,458.97);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.51,454.93) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.66,477.15) --
-	(163.23,477.15);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.95,476.14) --
-	(162.95,478.11);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (162.95,473.11) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.91,421.56) --
-	(120.70,421.56);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.17,406.76) --
-	(117.17,430.08);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (117.17,417.53) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (124.20,409.98) --
-	(134.18,409.98);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.79,405.95) --
-	(129.79,413.35);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (129.79,407.07) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.21,485.10) --
-	(197.03,485.10);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.62,484.28) --
-	(196.62,485.89);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.62,482.19) {$\kappa$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.77,432.05) --
-	(140.26,432.05);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (135.68,429.18) --
-	(135.68,434.57);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (135.68,428.82) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.99,483.34) --
-	(200.70,483.34);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (199.86,480.63) --
-	(199.86,485.72);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.86,479.30) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.36,482.25) --
-	(177.58,482.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.47,482.07) --
-	(177.47,482.44);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.47,478.22) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (133.12,451.72) --
-	(147.88,451.72);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (141.79,449.82) --
-	(141.79,453.46);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (141.79,447.69) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (136.74,437.84) --
-	(147.60,437.84);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (142.88,434.82) --
-	(142.88,440.47);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (142.88,434.94) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.27,487.58) --
-	(198.98,487.58);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.14,487.05) --
-	(198.14,488.10);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.14,484.68) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.42,460.68) --
-	(181.15,460.68);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.37,456.94) --
-	(179.37,463.84);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.37,457.45) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.94,486.46) --
-	(184.37,486.46);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.33,482.75) --
-	(176.33,489.60);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.33,482.42) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.15,482.18) --
-	(197.23,482.18);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.69,481.57) --
-	(196.69,482.78);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.69,478.15) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.45,441.52) --
-	(161.00,441.52);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (157.57,436.94) --
-	(157.57,445.26);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (157.57,437.48) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.01,463.73) --
-	(184.30,463.73);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.82,459.32) --
-	(181.82,467.36);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.82,460.82) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.90,498.16) --
-	(211.56,498.16);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.27,495.77) --
-	(210.27,500.30);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.27,495.25) {$\kappa$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.64,472.51) --
-	(197.79,472.51);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.95,470.68) --
-	(194.95,474.19);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.95,469.28) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.60,491.62) --
-	(178.99,491.62);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.91,490.07) --
-	(176.91,493.06);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.91,487.58) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.25,482.68) --
-	(197.61,482.68);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.43,482.27) --
-	(197.43,483.09);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.43,478.65) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.17,459.25) --
-	(178.40,459.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.85,457.81) --
-	(176.85,460.59);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.85,455.21) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.79,467.29) --
-	(192.74,467.29);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.37,464.24) --
-	(185.37,469.95);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.37,464.39) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.72,501.36) --
-	(212.84,501.36);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.78,500.78) --
-	(212.78,501.94);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.78,498.46) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (146.55,466.16) --
+	(158.29,466.16);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (153.31,462.75) --
+	(153.31,469.06);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (153.31,462.93) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.24,515.97) --
+	(190.72,515.97);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.95,514.61) --
+	(186.95,517.24);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (186.95,511.94) {$L$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (141.27,507.51) --
+	(146.34,507.51);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (143.97,507.30) --
+	(143.97,507.72);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (143.97,503.48) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (141.32,461.89) --
+	(150.41,461.89);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (146.40,454.67) --
+	(146.40,467.11);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (146.40,457.85) {$h$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (107.73,439.48) --
+	(121.71,439.48);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (115.97,429.54) --
+	(115.97,445.99);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (115.97,436.58) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (224.56,513.60) --
+	(225.34,513.60);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (224.96,513.22) --
+	(224.96,513.97);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (224.96,510.69) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (212.80,499.16) --
+	(214.49,499.16);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (213.66,497.99) --
+	(213.66,500.27);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (213.66,495.94) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.38,483.91) --
+	(193.63,483.91);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.01,482.28) --
+	(193.01,485.40);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.01,479.87) {$L$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (219.89,514.97) --
+	(220.35,514.97);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (220.12,514.79) --
+	(220.12,515.14);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.12,510.93) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (203.60,494.30) --
+	(207.53,494.30);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (205.67,493.23) --
+	(205.67,495.31);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.67,490.27) {$h$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (214.64,497.73) --
+	(216.55,497.73);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (215.62,496.54) --
+	(215.62,498.85);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (215.62,494.83) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (224.49,514.56) --
+	(225.65,514.56);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (225.08,514.02) --
+	(225.08,515.09);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (225.08,511.66) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (170.28,470.40) --
+	(175.14,470.40);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.86,468.37) --
+	(172.86,472.24);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.86,467.18) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (201.34,496.33) --
+	(204.09,496.33);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (202.76,494.98) --
+	(202.76,497.58);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.76,492.29) {$L$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (223.55,516.52) --
+	(224.53,516.52);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (224.05,516.26) --
+	(224.05,516.77);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (224.05,512.48) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (159.45,457.17) --
+	(165.46,457.17);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (162.69,454.81) --
+	(162.69,459.28);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (162.69,453.14) {$h$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.00,474.69) --
+	(190.72,474.69);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.11,471.18) --
+	(186.11,477.64);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (186.11,471.78) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (227.77,516.29) --
+	(228.21,516.29);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (227.99,515.94) --
+	(227.99,516.64);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (227.99,513.39) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.06,489.34) --
+	(190.32,489.34);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.76,488.63) --
+	(188.76,490.02);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.76,486.11) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.99,489.04) --
+	(194.37,489.04);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.31,486.77) --
+	(192.31,491.07);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.31,485.01) {$L$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (218.80,514.30) --
+	(219.31,514.30);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (219.06,514.16) --
+	(219.06,514.43);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (219.06,510.26) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.50,485.31) --
+	(182.06,485.31);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.06,483.39) --
+	(179.06,487.05);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.06,481.27) {$h$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.00,481.50) --
+	(186.35,481.50);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.63,479.81) --
+	(182.63,483.06);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.63,478.60) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (227.74,516.74) --
+	(228.17,516.74);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (227.96,516.39) --
+	(227.96,517.08);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (227.96,513.84) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (162.10,466.73) --
+	(168.36,466.73);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (165.49,463.57) --
+	(165.49,469.44);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (165.49,463.50) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.81,509.25) --
+	(205.39,509.25);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (202.39,507.51) --
+	(202.39,510.84);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.39,505.21) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (197.30,509.61) --
+	(198.11,509.61);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (197.71,509.14) --
+	(197.71,510.08);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.71,505.58) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (153.88,467.30) --
+	(166.55,467.30);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.25,464.25) --
+	(161.25,469.93);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (161.25,463.27) {$h$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.45,456.76) --
+	(175.22,456.76);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.13,453.03) --
+	(172.13,459.89);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.13,453.86) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (225.42,514.50) --
+	(226.46,514.50);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (225.95,514.10) --
+	(225.95,514.89);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (225.95,511.59) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (223.12,507.57) --
+	(225.42,507.57);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (224.30,506.14) --
+	(224.30,508.89);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (224.30,504.34) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (206.07,496.58) --
+	(208.33,496.58);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (207.23,495.41) --
+	(207.23,497.68);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.23,492.54) {$L$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (235.17,517.38) --
+	(235.44,517.38);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (235.30,517.27) --
+	(235.30,517.48);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (235.30,513.34) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (197.08,487.47) --
+	(198.88,487.47);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.00,485.85) --
+	(198.00,488.96);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.00,483.44) {$h$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (207.94,497.31) --
+	(210.40,497.31);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (209.21,494.40) --
+	(209.21,499.82);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.21,494.40) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (226.56,516.29) --
+	(227.64,516.29);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (227.11,515.86) --
+	(227.11,516.70);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (227.11,513.38) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.20,477.66) --
+	(185.95,477.66);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.29,474.79) --
+	(183.29,480.15);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.29,474.43) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (224.14,506.92) --
+	(226.44,506.92);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (225.33,505.18) --
+	(225.33,508.51);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (225.33,502.88) {$L$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.48,515.51) --
+	(213.95,515.51);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (212.75,515.17) --
+	(212.75,515.84);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.75,511.47) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.69,490.11) --
+	(189.00,490.11);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.70,488.43) --
+	(185.70,491.66);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.70,486.08) {$h$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.19,479.36) --
+	(189.91,479.36);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.26,477.87) --
+	(187.26,480.75);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.26,476.46) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (228.82,517.74) --
+	(230.68,517.74);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (229.77,516.59) --
+	(229.77,518.83);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (229.77,514.84) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (215.58,501.69) --
+	(218.44,501.69);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (217.06,500.72) --
+	(217.06,502.62);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (217.06,498.46) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.05,492.78) --
+	(195.08,492.78);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.63,489.01) --
+	(193.63,495.94);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.63,488.75) {$L$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (227.29,514.73) --
+	(228.68,514.73);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (228.00,514.55) --
+	(228.00,514.90);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (228.00,510.70) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.17,489.32) --
+	(202.86,489.32);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.40,483.15) --
+	(199.40,493.99);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.40,485.29) {$h$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.54,499.38) --
+	(205.81,499.38);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (200.64,496.95) --
+	(200.64,501.54);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (200.64,496.47) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (238.32,528.60) --
+	(239.74,528.60);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (239.05,527.61) --
+	(239.05,529.55);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (239.05,525.70) {$\kappa$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (225.31,507.29) --
+	(227.66,507.29);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (226.52,506.61) --
+	(226.52,507.94);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (226.52,504.06) {$p$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (215.46,502.68) --
+	(216.79,502.68);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (216.13,500.67) --
+	(216.13,504.49);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (216.13,498.64) {$L$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (230.05,515.15) --
+	(230.28,515.15);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (230.16,514.85) --
+	(230.16,515.45);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (230.16,511.12) {$r$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (212.27,497.33) --
+	(214.57,497.33);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (213.45,496.08) --
+	(213.45,498.51);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (213.45,493.30) {$h$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (218.24,500.49) --
+	(221.78,500.49);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (220.09,499.55) --
+	(220.09,501.39);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.09,497.59) {$\sigma$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (239.91,530.16) --
+	(241.03,530.16);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (240.48,529.47) --
+	(240.48,530.82);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (240.48,527.25) {$\kappa$};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,338.88);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,338.88) -- (226.02,338.88);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 97.17,338.88) -- ( 97.17,333.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (144.54,338.88) -- (144.54,333.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.91,338.88) -- (191.91,333.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.28,338.88) -- (239.28,333.90);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 93.85,338.88) -- ( 93.85,333.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (137.91,338.88) -- (137.91,333.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.96,338.88) -- (181.96,333.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.02,338.88) -- (226.02,333.90);
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 97.17,320.95) {10};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (144.54,320.95) {100};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (191.91,320.95) {1000};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (239.28,320.95) {10000};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,338.88) -- ( 49.80,528.36);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 93.85,320.95) {10};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (137.91,320.95) {100};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (181.96,320.95) {1000};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (226.02,320.95) {10000};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,338.88) -- ( 49.80,515.10);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,386.25) -- ( 44.82,386.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,433.62) -- ( 44.82,433.62);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,480.99) -- ( 44.82,480.99);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,528.36) -- ( 44.82,528.36);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,382.93) -- ( 44.82,382.93);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,426.99) -- ( 44.82,426.99);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,471.04) -- ( 44.82,471.04);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,515.10) -- ( 44.82,515.10);
 
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,383.39) {10};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,430.76) {100};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,478.13) {1000};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,525.50) {10000};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,380.08) {10};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,424.13) {100};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,468.19) {1000};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,512.24) {10000};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,301.03) {ESS/hr [nocons (\textit{quant})]};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (307.01,433.62) {ESS/hr [adapt (\textit{quant})]};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,301.03) {ESS/chain [nocons (\textit{quant})]};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (307.01,433.62) {ESS/chain [adapt (\textit{quant})]};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (149.40,234.96) --
-	(492.60,578.16);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (575.73,578.16) --
-	(575.73,490.17) --
-	(149.40, 63.84) --
-	(149.40,234.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (149.40,206.44) --
-	(521.12,578.16);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (575.73,578.16) --
-	(575.73,518.69) --
-	(149.40, 92.36) --
-	(149.40,206.44);
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (149.40,177.92) --
-	(549.64,578.16);
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (575.73,578.16) --
-	(575.73,547.21) --
-	(149.40,120.88) --
-	(149.40,177.92);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (431.97,342.31) {$\frac{1}{64} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,435.87) {$64\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (403.45,342.31) {$\frac{1}{16} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,407.35) {$16\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (373.28,342.31) {$\frac{1}{4} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.00,378.83) {$4\times$};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.66,242.23) --
+	(498.59,578.16);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (572.41,578.16) --
+	(572.41,492.84) --
+	(162.66, 83.09) --
+	(162.66,242.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (162.66,215.71) --
+	(525.11,578.16);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (572.41,578.16) --
+	(572.41,519.37) --
+	(162.66,109.61) --
+	(162.66,215.71);
+
+\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (162.66,189.19) --
+	(551.64,578.16);
+
+\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (572.41,578.16) --
+	(572.41,545.89) --
+	(162.66,136.14) --
+	(162.66,189.19);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (425.98,342.31) {$\frac{1}{64} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,429.88) {$64\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (399.46,342.31) {$\frac{1}{16} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,403.36) {$16\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (371.28,342.31) {$\frac{1}{4} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.00,376.84) {$4\times$};
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (383.73,398.02) --
-	(392.73,398.02);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (388.72,382.13) --
-	(388.72,406.87);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (388.72,394.79) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (475.33,475.91) --
-	(480.03,475.91);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.81,475.07) --
-	(477.81,476.72);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (477.81,471.88) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.29,472.93) --
-	(393.35,472.93);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (391.42,468.95) --
-	(391.42,476.26);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (391.42,468.89) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (384.19,397.74) --
-	(392.81,397.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (388.95,377.39) --
-	(388.95,407.77);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (388.95,393.71) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (378.48,366.19) --
-	(404.98,366.19);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (395.73,357.18) --
-	(395.73,372.44);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (395.73,363.29) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.62,483.32) --
-	(484.09,483.32);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.37,483.08) --
-	(483.37,483.56);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.37,480.42) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (434.32,451.80) --
-	(440.53,451.80);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (437.66,446.77) --
-	(437.66,455.84);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (437.66,448.57) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.20,479.84) --
-	(486.91,479.84);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.07,478.07) --
-	(486.07,481.48);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (486.07,475.81) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.44,483.86) --
-	(477.66,483.86);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.06,481.92) --
-	(477.06,485.64);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (477.06,479.83) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.91,449.16) --
-	(431.61,449.16);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (429.84,442.38) --
-	(429.84,454.24);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (429.84,445.12) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (434.38,448.12) --
-	(441.74,448.12);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.39,445.55) --
-	(438.39,450.42);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (438.39,445.22) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (487.67,488.03) --
-	(488.48,488.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (488.08,487.64) --
-	(488.08,488.41);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (488.08,485.12) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (406.92,424.00) --
-	(415.60,424.00);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (411.72,420.41) --
-	(411.72,427.05);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (411.72,420.77) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (480.70,478.83) --
-	(484.32,478.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.59,474.57) --
-	(482.59,482.36);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (482.59,474.80) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (451.74,476.83) --
-	(452.31,476.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (452.03,476.28) --
-	(452.03,477.36);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (452.03,472.79) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (401.99,423.32) --
-	(409.78,423.32);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (406.25,420.99) --
-	(406.25,425.41);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (406.25,419.28) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (413.28,406.71) --
-	(423.26,406.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.87,404.60) --
-	(418.87,408.64);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (418.87,403.81) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.29,485.22) --
-	(486.11,485.22);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.70,485.09) --
-	(485.70,485.35);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (485.70,482.32) {$\kappa$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.85,435.95) --
-	(429.34,435.95);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (424.76,433.40) --
-	(424.76,438.22);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (424.76,432.72) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (488.07,482.85) --
-	(489.78,482.85);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (488.94,480.61) --
-	(488.94,484.87);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (488.94,478.82) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (466.44,482.85) --
-	(466.66,482.85);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (466.55,482.61) --
-	(466.55,483.09);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (466.55,478.82) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (422.20,450.41) --
-	(436.96,450.41);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (430.87,447.63) --
-	(430.87,452.86);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (430.87,446.38) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (425.82,440.09) --
-	(436.68,440.09);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (431.96,437.76) --
-	(431.96,442.18);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (431.96,437.18) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.35,487.61) --
-	(488.06,487.61);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (487.22,485.91) --
-	(487.22,489.18);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (487.22,484.71) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (466.50,469.66) --
-	(470.23,469.66);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (468.45,467.06) --
-	(468.45,471.96);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.45,466.43) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (452.02,481.52) --
-	(473.45,481.52);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (465.41,478.07) --
-	(465.41,484.47);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (465.41,477.48) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.23,487.79) --
-	(486.31,487.79);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.77,487.17) --
-	(485.77,488.40);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (485.77,483.76) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (442.53,448.83) --
-	(450.08,448.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (446.65,445.54) --
-	(446.65,451.66);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (446.65,444.80) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (468.09,470.37) --
-	(473.38,470.37);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (470.90,468.48) --
-	(470.90,472.10);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (470.90,467.47) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (497.98,499.91) --
-	(500.64,499.91);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.35,499.32) --
-	(499.35,500.49);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (499.35,497.01) {$\kappa$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (480.72,484.41) --
-	(486.87,484.41);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (484.03,482.75) --
-	(484.03,485.95);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (484.03,481.19) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.68,490.90) --
-	(468.07,490.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (465.99,490.73) --
-	(465.99,491.06);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (465.99,486.86) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.33,489.03) --
-	(486.69,489.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.51,487.83) --
-	(486.51,490.17);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (486.51,485.00) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.25,467.22) --
-	(467.48,467.22);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (465.93,462.61) --
-	(465.93,470.98);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (465.93,463.19) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.87,475.23) --
-	(481.82,475.23);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.45,471.25) --
-	(474.45,478.57);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.45,472.33) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (501.80,501.33) --
-	(501.92,501.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (501.86,500.87) --
-	(501.86,501.77);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (501.86,498.42) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (435.63,486.24) --
+	(447.37,486.24);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (442.39,483.71) --
+	(442.39,488.48);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (442.39,483.01) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (471.32,515.98) --
+	(479.80,515.98);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (476.03,515.21) --
+	(476.03,516.73);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (476.03,511.95) {$L$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (430.35,510.08) --
+	(435.42,510.08);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (433.05,508.58) --
+	(433.05,511.48);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (433.05,506.05) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (430.40,481.95) --
+	(439.49,481.95);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (435.48,475.06) --
+	(435.48,487.01);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (435.48,477.92) {$h$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (396.81,494.23) --
+	(410.79,494.23);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (405.05,489.73) --
+	(405.05,497.87);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (405.05,491.33) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (513.64,514.61) --
+	(514.42,514.61);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (514.04,513.26) --
+	(514.04,515.87);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (514.04,511.71) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (501.88,502.88) --
+	(503.57,502.88);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (502.74,501.44) --
+	(502.74,504.21);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (502.74,499.65) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.46,484.45) --
+	(482.71,484.45);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (482.09,483.64) --
+	(482.09,485.23);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (482.09,480.42) {$L$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (508.97,515.82) --
+	(509.43,515.82);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (509.20,515.68) --
+	(509.20,515.96);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (509.20,511.79) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (492.68,496.95) --
+	(496.61,496.95);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (494.75,495.13) --
+	(494.75,498.62);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (494.75,492.92) {$h$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (503.72,512.60) --
+	(505.63,512.60);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (504.70,511.28) --
+	(504.70,513.84);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (504.70,509.70) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (513.57,514.28) --
+	(514.73,514.28);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (514.16,513.85) --
+	(514.16,514.70);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (514.16,511.38) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (459.36,476.21) --
+	(464.22,476.21);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (461.94,471.55) --
+	(461.94,479.95);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (461.94,472.98) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (490.42,496.44) --
+	(493.17,496.44);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (491.84,495.62) --
+	(491.84,497.22);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (491.84,492.41) {$L$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (512.63,518.61) --
+	(513.61,518.61);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (513.13,518.39) --
+	(513.13,518.83);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (513.13,514.58) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (448.53,462.00) --
+	(454.54,462.00);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (451.77,456.27) --
+	(451.77,466.41);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (451.77,457.97) {$h$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (469.08,485.00) --
+	(479.80,485.00);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (475.19,480.84) --
+	(475.19,488.42);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (475.19,482.10) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (516.85,516.49) --
+	(517.29,516.49);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (517.07,516.20) --
+	(517.07,516.78);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (517.07,513.59) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (476.14,489.90) --
+	(479.40,489.90);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (477.84,488.38) --
+	(477.84,491.32);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (477.84,486.68) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (479.07,490.25) --
+	(483.45,490.25);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.39,488.30) --
+	(481.39,492.02);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (481.39,486.22) {$L$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (507.88,515.74) --
+	(508.39,515.74);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (508.14,515.62) --
+	(508.14,515.85);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (508.14,511.70) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (464.58,489.96) --
+	(471.14,489.96);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (468.14,488.02) --
+	(468.14,491.72);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.14,485.93) {$h$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (467.08,493.91) --
+	(475.43,493.91);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (471.71,491.52) --
+	(471.71,496.04);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (471.71,491.01) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (516.82,517.00) --
+	(517.25,517.00);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (517.04,516.92) --
+	(517.04,517.07);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (517.04,514.09) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (451.18,471.62) --
+	(457.44,471.62);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (454.57,470.11) --
+	(454.57,473.01);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (454.57,468.39) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (487.89,510.00) --
+	(494.47,510.00);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (491.47,507.87) --
+	(491.47,511.92);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (491.47,505.97) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (486.38,508.84) --
+	(487.19,508.84);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (486.79,508.29) --
+	(486.79,509.38);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (486.79,504.81) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (442.96,470.99) --
+	(455.63,470.99);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (450.33,469.17) --
+	(450.33,472.65);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (450.33,466.96) {$h$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (457.53,483.25) --
+	(464.30,483.25);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (461.21,480.13) --
+	(461.21,485.92);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (461.21,480.34) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (514.50,514.97) --
+	(515.54,514.97);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (515.03,514.65) --
+	(515.03,515.28);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (515.03,512.07) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (512.20,516.70) --
+	(514.50,516.70);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (513.38,515.91) --
+	(513.38,517.46);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (513.38,513.48) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (495.15,498.61) --
+	(497.41,498.61);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (496.31,495.49) --
+	(496.31,501.29);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (496.31,494.57) {$L$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (524.25,525.98) --
+	(524.52,525.98);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (524.38,525.81) --
+	(524.38,526.15);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (524.38,521.95) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (486.16,488.18) --
+	(487.96,488.18);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (487.08,486.37) --
+	(487.08,489.84);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (487.08,484.15) {$h$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (497.02,502.47) --
+	(499.48,502.47);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (498.29,501.02) --
+	(498.29,503.81);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (498.29,499.56) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (515.64,516.37) --
+	(516.72,516.37);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (516.19,516.06) --
+	(516.19,516.68);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (516.19,513.47) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (469.28,480.49) --
+	(475.03,480.49);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (472.37,476.54) --
+	(472.37,483.75);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (472.37,477.26) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (513.22,512.09) --
+	(515.52,512.09);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (514.41,510.16) --
+	(514.41,513.84);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (514.41,508.05) {$L$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (500.56,516.42) --
+	(503.03,516.42);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (501.83,516.22) --
+	(501.83,516.60);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (501.83,512.38) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (470.77,488.99) --
+	(478.08,488.99);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (474.78,483.50) --
+	(474.78,493.25);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.78,484.95) {$h$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (473.27,494.00) --
+	(478.99,494.00);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (476.34,490.82) --
+	(476.34,496.72);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (476.34,491.09) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (517.90,518.35) --
+	(519.76,518.35);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (518.85,517.20) --
+	(518.85,519.44);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (518.85,515.45) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (504.66,505.50) --
+	(507.52,505.50);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (506.14,502.97) --
+	(506.14,507.73);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (506.14,502.27) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.13,487.87) --
+	(484.16,487.87);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (482.71,484.86) --
+	(482.71,490.48);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (482.71,483.84) {$L$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (516.37,519.55) --
+	(517.76,519.55);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (517.08,519.31) --
+	(517.08,519.79);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (517.08,515.52) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (484.25,490.54) --
+	(491.94,490.54);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (488.48,486.19) --
+	(488.48,494.09);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (488.48,486.51) {$h$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (482.62,504.83) --
+	(494.89,504.83);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (489.72,500.57) --
+	(489.72,508.31);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (489.72,501.92) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (527.40,528.64) --
+	(528.82,528.64);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (528.13,528.52) --
+	(528.13,528.76);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (528.13,525.74) {$\kappa$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (514.39,514.92) --
+	(516.74,514.92);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (515.60,507.67) --
+	(515.60,520.16);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (515.60,511.69) {$p$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (504.54,501.52) --
+	(505.87,501.52);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (505.21,494.65) --
+	(505.21,506.56);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (505.21,497.48) {$L$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (519.13,518.27) --
+	(519.36,518.27);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (519.24,510.35) --
+	(519.24,523.85);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (519.24,514.23) {$r$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (501.35,500.17) --
+	(503.65,500.17);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (502.53,491.51) --
+	(502.53,506.10);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (502.53,496.13) {$h$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (507.32,509.87) --
+	(510.86,509.87);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (509.17,501.95) --
+	(509.17,515.45);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (509.17,506.96) {$\sigma$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (528.99,527.10) --
+	(530.11,527.10);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (529.56,518.90) --
+	(529.56,532.82);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (529.56,524.20) {$\kappa$};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,338.88) -- (528.36,338.88);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,338.88) -- (515.10,338.88);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (386.25,338.88) -- (386.25,333.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.62,338.88) -- (433.62,333.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (480.99,338.88) -- (480.99,333.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (528.36,338.88) -- (528.36,333.90);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (382.93,338.88) -- (382.93,333.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.99,338.88) -- (426.99,333.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (471.04,338.88) -- (471.04,333.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (515.10,338.88) -- (515.10,333.90);
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (386.25,320.95) {10};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (433.62,320.95) {100};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (480.99,320.95) {1000};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (528.36,320.95) {10000};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,338.88) -- (338.88,528.36);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (382.93,320.95) {10};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (426.99,320.95) {100};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (471.04,320.95) {1000};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (515.10,320.95) {10000};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,338.88) -- (338.88,515.10);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,386.25) -- (333.90,386.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,433.62) -- (333.90,433.62);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,480.99) -- (333.90,480.99);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,528.36) -- (333.90,528.36);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,382.93) -- (333.90,382.93);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,426.99) -- (333.90,426.99);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,471.04) -- (333.90,471.04);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,515.10) -- (333.90,515.10);
 
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,383.39) {10};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,430.76) {100};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,478.13) {1000};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,525.50) {10000};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,380.08) {10};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,424.13) {100};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,468.19) {1000};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,512.24) {10000};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54, 11.95) {ESS/hr [cons (\textit{quant})]};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,144.54) {ESS/hr [adapt (\textit{quant})]};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54, 11.95) {ESS/chain [cons (\textit{quant})]};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,144.54) {ESS/chain [adapt (\textit{quant})]};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00, 85.56) --
-	(286.65,372.21) --
-	(286.65,201.09) --
-	( 85.56,  0.00);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (  0.00, 57.04) --
-	(286.65,343.69) --
-	(286.65,229.61) --
-	( 57.04,  0.00);
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (  0.00, 28.52) --
-	(286.65,315.17) --
-	(286.65,258.13) --
-	( 28.52,  0.00);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (142.89, 53.23) {$\frac{1}{64} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,146.79) {$64\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (114.37, 53.23) {$\frac{1}{16} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,118.27) {$16\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 84.20, 53.23) {$\frac{1}{4} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92, 89.75) {$4\times$};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00, 79.57) --
+	(283.33,362.91) --
+	(283.33,203.76) --
+	( 79.57,  0.00);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (  0.00, 53.05) --
+	(283.33,336.38) --
+	(283.33,230.29) --
+	( 53.05,  0.00);
+
+\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (  0.00, 26.52) --
+	(283.33,309.86) --
+	(283.33,256.81) --
+	( 26.52,  0.00);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (136.90, 53.23) {$\frac{1}{64} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,140.80) {$64\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (110.38, 53.23) {$\frac{1}{16} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,114.28) {$16\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 82.20, 53.23) {$\frac{1}{4} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92, 87.76) {$4\times$};
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.29,108.94) --
-	(133.14,108.94);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (127.70, 93.05) --
-	(127.70,117.79);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (127.70,105.71) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.66,186.83) --
-	(188.08,186.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.38,185.99) --
-	(187.38,187.64);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.38,182.80) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.53,183.85) --
-	(185.71,183.85);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.13,179.87) --
-	(185.13,187.18);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.13,179.81) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.27,108.66) --
-	(131.51,108.66);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (127.02, 88.31) --
-	(127.02,118.69);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (127.02,104.63) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.54, 77.11) --
-	(101.64, 77.11);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 98.81, 68.10) --
-	( 98.81, 83.36);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 98.81, 74.21) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.17,194.24) --
-	(194.98,194.24);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.58,194.00) --
-	(194.58,194.48);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.58,191.34) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.57,162.72) --
-	(165.24,162.72);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.95,157.69) --
-	(163.95,166.76);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (163.95,159.49) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.42,190.76) --
-	(191.81,190.76);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.18,188.99) --
-	(190.18,192.40);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.18,186.73) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.42,194.78) --
-	(194.88,194.78);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.65,192.84) --
-	(194.65,196.56);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.65,190.75) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.10,160.08) --
-	(162.23,160.08);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.73,153.30) --
-	(160.73,165.16);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (160.73,156.04) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.18,159.04) --
-	(160.66,159.04);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.46,156.47) --
-	(159.46,161.34);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (159.46,156.14) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.50,198.95) --
-	(199.38,198.95);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.94,198.56) --
-	(198.94,199.33);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.94,196.04) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.01,134.92) --
-	(140.91,134.92);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (133.01,131.33) --
-	(133.01,137.97);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (133.01,131.69) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.89,185.49) --
-	(169.89,193.28);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.89,185.72) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.06,187.75) --
-	(189.03,187.75);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.07,187.20) --
-	(188.07,188.28);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.07,183.71) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.68,134.24) --
-	(141.00,134.24);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (132.48,131.91) --
-	(132.48,136.33);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (132.48,130.20) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (116.87,117.63) --
-	(124.27,117.63);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.90,115.52) --
-	(120.90,119.56);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (120.90,114.73) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.20,196.14) --
-	(196.81,196.14);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.02,196.01) --
-	(196.02,196.27);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.02,193.24) {$\kappa$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.10,146.87) --
-	(145.49,146.87);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (142.97,144.32) --
-	(142.97,149.14);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (142.97,143.64) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.55,193.77) --
-	(196.64,193.77);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.26,191.53) --
-	(194.26,195.79);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.26,189.74) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.99,193.77) --
-	(193.36,193.77);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.17,193.53) --
-	(193.17,194.01);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.17,189.74) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.74,161.33) --
-	(164.38,161.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.64,158.55) --
-	(162.64,163.78);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (162.64,157.30) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.74,151.01) --
-	(151.39,151.01);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.76,148.68) --
-	(148.76,153.10);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (148.76,148.10) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.97,198.53) --
-	(199.02,198.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.50,196.83) --
-	(198.50,200.10);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.50,195.63) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (167.86,180.58) --
-	(174.76,180.58);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.60,177.98) --
-	(171.60,182.88);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.60,177.35) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.67,192.44) --
-	(200.52,192.44);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.38,188.99) --
-	(197.38,195.39);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.38,188.40) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.49,198.71) --
-	(193.70,198.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.10,198.09) --
-	(193.10,199.32);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.10,194.68) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (147.86,159.75) --
-	(156.18,159.75);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (152.44,156.46) --
-	(152.44,162.58);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (152.44,155.72) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (170.24,181.29) --
-	(178.28,181.29);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.65,179.40) --
-	(174.65,183.02);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.65,178.39) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.69,210.83) --
-	(211.22,210.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.08,210.24) --
-	(209.08,211.41);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.08,207.93) {$\kappa$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.60,195.33) --
-	(185.11,195.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (183.43,193.67) --
-	(183.43,196.87);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.43,192.11) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.99,201.82) --
-	(203.98,201.82);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (202.54,201.65) --
-	(202.54,201.98);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.54,197.78) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.19,199.95) --
-	(194.01,199.95);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.60,198.75) --
-	(193.60,201.09);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.60,195.92) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.73,178.14) --
-	(171.51,178.14);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (170.17,173.53) --
-	(170.17,181.90);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (170.17,174.11) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.16,186.15) --
-	(180.87,186.15);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (178.21,182.17) --
-	(178.21,189.49);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (178.21,183.25) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.70,212.25) --
-	(212.86,212.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.28,211.79) --
-	(212.28,212.69);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.28,209.34) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.67,197.16) --
+	(179.98,197.16);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (177.08,194.63) --
+	(177.08,199.40);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.08,193.93) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (225.53,226.90) --
+	(228.16,226.90);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (226.89,226.13) --
+	(226.89,227.65);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (226.89,222.87) {$L$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (218.22,221.00) --
+	(218.64,221.00);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (218.43,219.50) --
+	(218.43,222.40);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (218.43,216.97) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (165.59,192.87) --
+	(178.03,192.87);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.81,185.98) --
+	(172.81,197.93);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.81,188.84) {$h$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (140.46,205.15) --
+	(156.91,205.15);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.40,200.65) --
+	(150.40,208.79);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (150.40,202.25) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (224.14,225.53) --
+	(224.89,225.53);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (224.52,224.18) --
+	(224.52,226.79);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (224.52,222.63) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (208.91,213.80) --
+	(211.19,213.80);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (210.08,212.36) --
+	(210.08,215.13);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.08,210.57) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.20,195.37) --
+	(196.32,195.37);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.83,194.56) --
+	(194.83,196.15);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.83,191.34) {$L$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (225.71,226.74) --
+	(226.06,226.74);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (225.89,226.60) --
+	(225.89,226.88);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (225.89,222.71) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (204.15,207.87) --
+	(206.23,207.87);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (205.22,206.05) --
+	(205.22,209.54);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.22,203.84) {$h$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (207.46,223.52) --
+	(209.77,223.52);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (208.65,222.20) --
+	(208.65,224.76);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (208.65,220.62) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (224.94,225.20) --
+	(226.01,225.20);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (225.48,224.77) --
+	(225.48,225.62);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (225.48,222.30) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.29,187.13) --
+	(183.16,187.13);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.32,182.47) --
+	(181.32,190.87);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.32,183.90) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (205.90,207.36) --
+	(208.50,207.36);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (207.25,206.54) --
+	(207.25,208.14);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.25,203.33) {$L$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (227.18,229.53) --
+	(227.69,229.53);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (227.44,229.31) --
+	(227.44,229.75);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (227.44,225.50) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (165.73,172.92) --
+	(170.20,172.92);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.09,167.19) --
+	(168.09,177.33);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (168.09,168.89) {$h$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.10,195.92) --
+	(188.56,195.92);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.61,191.76) --
+	(185.61,199.34);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.61,193.02) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (226.86,227.41) --
+	(227.56,227.41);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (227.21,227.12) --
+	(227.21,227.70);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (227.21,224.51) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.55,200.82) --
+	(200.94,200.82);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (200.26,199.30) --
+	(200.26,202.24);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (200.26,197.60) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (197.69,201.17) --
+	(201.99,201.17);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.96,199.22) --
+	(199.96,202.94);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.96,197.14) {$L$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (225.08,226.66) --
+	(225.35,226.66);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (225.22,226.54) --
+	(225.22,226.77);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (225.22,222.62) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.31,200.88) --
+	(197.97,200.88);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.23,198.94) --
+	(196.23,202.64);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.23,196.85) {$h$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.73,204.83) --
+	(193.98,204.83);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.42,202.44) --
+	(192.42,206.96);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.42,201.93) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (227.31,227.92) --
+	(228.00,227.92);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (227.66,227.84) --
+	(227.66,227.99);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (227.66,225.01) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.49,182.54) --
+	(180.36,182.54);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (177.65,181.03) --
+	(177.65,183.93);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.65,179.31) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (218.43,220.92) --
+	(221.76,220.92);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (220.17,218.79) --
+	(220.17,222.84);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.17,216.89) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (220.06,219.76) --
+	(221.00,219.76);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (220.53,219.21) --
+	(220.53,220.30);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.53,215.73) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.17,181.91) --
+	(180.85,181.91);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.22,180.09) --
+	(178.22,183.57);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (178.22,177.88) {$h$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (163.95,194.17) --
+	(170.81,194.17);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (167.68,191.05) --
+	(167.68,196.84);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (167.68,191.26) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (225.02,225.89) --
+	(225.81,225.89);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (225.42,225.57) --
+	(225.42,226.20);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (225.42,222.99) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (217.06,227.62) --
+	(219.81,227.62);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (218.49,226.83) --
+	(218.49,228.38);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (218.49,224.40) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (206.33,209.53) --
+	(208.60,209.53);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (207.50,206.41) --
+	(207.50,212.21);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.50,205.49) {$L$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (228.19,236.90) --
+	(228.40,236.90);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (228.30,236.73) --
+	(228.30,237.07);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (228.30,232.87) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.77,199.10) --
+	(199.88,199.10);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.39,197.29) --
+	(198.39,200.76);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.39,195.07) {$h$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (205.32,213.39) --
+	(210.74,213.39);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (208.23,211.94) --
+	(208.23,214.73);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (208.23,210.48) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (226.78,227.29) --
+	(227.62,227.29);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (227.21,226.98) --
+	(227.21,227.60);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (227.21,224.39) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.71,191.41) --
+	(191.07,191.41);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.58,187.46) --
+	(188.58,194.67);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.58,188.18) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (216.10,223.01) --
+	(219.43,223.01);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (217.84,221.08) --
+	(217.84,224.76);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (217.84,218.97) {$L$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (226.09,227.34) --
+	(226.76,227.34);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (226.43,227.14) --
+	(226.43,227.52);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (226.43,223.30) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.35,199.91) --
+	(202.58,199.91);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (201.03,194.42) --
+	(201.03,204.17);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (201.03,195.87) {$h$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.79,204.92) --
+	(191.67,204.92);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.28,201.74) --
+	(190.28,207.64);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.28,202.01) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (227.51,229.27) --
+	(229.75,229.27);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (228.66,228.12) --
+	(228.66,230.36);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (228.66,226.37) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.64,216.42) --
+	(213.54,216.42);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (212.61,213.89) --
+	(212.61,218.65);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.61,213.19) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.93,198.79) --
+	(206.86,198.79);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (203.70,195.78) --
+	(203.70,201.40);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (203.70,194.76) {$L$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (225.47,230.47) --
+	(225.82,230.47);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (225.65,230.23) --
+	(225.65,230.71);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (225.65,226.44) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.07,201.46) --
+	(204.91,201.46);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (200.24,197.11) --
+	(200.24,205.01);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (200.24,197.43) {$h$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (207.87,215.75) --
+	(212.46,215.75);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (210.30,211.49) --
+	(210.30,219.23);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.30,212.84) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (238.53,239.56) --
+	(240.47,239.56);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (239.52,239.44) --
+	(239.52,239.68);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (239.52,236.66) {$\kappa$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (217.53,225.84) --
+	(218.86,225.84);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (218.21,218.59) --
+	(218.21,231.08);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (218.21,222.61) {$p$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.59,212.44) --
+	(215.41,212.44);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (213.60,205.57) --
+	(213.60,217.48);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (213.60,208.40) {$L$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (225.77,229.19) --
+	(226.37,229.19);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (226.07,221.27) --
+	(226.07,234.77);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (226.07,225.15) {$r$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (207.00,211.09) --
+	(209.43,211.09);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (208.25,202.43) --
+	(208.25,217.02);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (208.25,207.05) {$h$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (210.47,220.79) --
+	(212.31,220.79);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.41,212.87) --
+	(211.41,226.37);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.41,217.88) {$\sigma$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (240.39,238.02) --
+	(241.74,238.02);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (241.08,229.82) --
+	(241.08,243.74);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (241.08,235.12) {$\kappa$};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 49.80) -- (239.28, 49.80);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 49.80) -- (226.02, 49.80);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 97.17, 49.80) -- ( 97.17, 44.82);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (144.54, 49.80) -- (144.54, 44.82);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.91, 49.80) -- (191.91, 44.82);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.28, 49.80) -- (239.28, 44.82);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 93.85, 49.80) -- ( 93.85, 44.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (137.91, 49.80) -- (137.91, 44.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.96, 49.80) -- (181.96, 44.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.02, 49.80) -- (226.02, 44.82);
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 97.17, 31.87) {10};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (144.54, 31.87) {100};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (191.91, 31.87) {1000};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (239.28, 31.87) {10000};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 49.80) -- ( 49.80,239.28);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 93.85, 31.87) {10};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (137.91, 31.87) {100};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (181.96, 31.87) {1000};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (226.02, 31.87) {10000};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 49.80) -- ( 49.80,226.02);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 97.17) -- ( 44.82, 97.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,144.54) -- ( 44.82,144.54);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,191.91) -- ( 44.82,191.91);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,239.28) -- ( 44.82,239.28);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 93.85) -- ( 44.82, 93.85);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,137.91) -- ( 44.82,137.91);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,181.96) -- ( 44.82,181.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,226.02) -- ( 44.82,226.02);
 
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84, 94.31) {10};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,141.68) {100};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,189.05) {1000};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,236.42) {10000};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84, 91.00) {10};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,135.05) {100};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,179.11) {1000};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,223.16) {10000};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62, 11.95) {ESS/hr [\textit{cat}]};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (307.01,144.54) {ESS/hr [adapt (\textit{cat})]};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62, 11.95) {ESS/chain [\textit{cat}]};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (307.01,144.54) {ESS/chain [adapt (\textit{cat})]};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.52,  0.00) --
-	(575.73,372.21) --
-	(575.73,201.09) --
-	(374.64,  0.00);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (232.04,  0.00) --
-	(575.73,343.69) --
-	(575.73,229.61) --
-	(346.12,  0.00);
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (260.56,  0.00) --
-	(575.73,315.17) --
-	(575.73,258.13) --
-	(317.60,  0.00);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (431.97, 53.23) {$\frac{1}{64} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,146.79) {$64\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (403.45, 53.23) {$\frac{1}{16} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,118.27) {$16\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (373.28, 53.23) {$\frac{1}{4} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.00, 89.75) {$4\times$};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.51,  0.00) --
+	(572.41,362.91) --
+	(572.41,203.76) --
+	(368.65,  0.00);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (236.03,  0.00) --
+	(572.41,336.38) --
+	(572.41,230.29) --
+	(342.13,  0.00);
+
+\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (262.56,  0.00) --
+	(572.41,309.86) --
+	(572.41,256.81) --
+	(315.60,  0.00);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (425.98, 53.23) {$\frac{1}{64} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,140.80) {$64\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (399.46, 53.23) {$\frac{1}{16} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,114.28) {$16\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (371.28, 53.23) {$\frac{1}{4} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.00, 87.76) {$4\times$};
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (369.53,100.95) --
-	(401.69,100.95);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (391.34, 96.83) --
-	(391.34,104.39);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (391.34, 97.73) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (469.11,180.21) --
-	(478.54,180.21);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.36,157.25) --
-	(474.36,190.79);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.36,176.18) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (378.71, 99.41) --
-	(392.60, 99.41);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (386.80, 95.00) --
-	(386.80,103.04);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (386.80, 95.37) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (379.87,102.83) --
-	(403.10,102.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (394.60,100.19) --
-	(394.60,105.17);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (394.60, 98.80) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (373.83, 90.46) --
-	(386.33, 90.46);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (381.02, 83.73) --
-	(381.02, 95.52);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (381.02, 87.56) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.33,194.78) --
-	(484.25,194.78);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.79,194.57) --
-	(483.79,194.99);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.79,191.87) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (403.60,109.49) --
-	(412.89,109.49);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (408.76, 99.61) --
-	(408.76,116.13);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (408.76,106.26) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.33,191.83) --
-	(481.58,191.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.56,190.07) --
-	(479.56,193.44);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (479.56,187.79) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (448.80,164.69) --
-	(449.61,164.69);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (449.21,164.54) --
-	(449.21,164.84);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (449.21,160.65) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (402.13,107.26) --
-	(410.13,107.26);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (406.52,100.97) --
-	(406.52,112.07);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (406.52,103.23) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (394.71,110.51) --
-	(411.65,110.51);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (404.88,103.25) --
-	(404.88,115.87);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (404.88,107.61) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.25,196.27) --
-	(485.92,196.27);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.59,196.12) --
-	(485.59,196.43);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (485.59,193.37) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.30,177.43) --
-	(465.23,177.43);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (460.48,172.15) --
-	(460.48,181.63);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (460.48,174.20) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.33,174.98) --
-	(474.75,174.98);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.90,158.21) --
-	(461.90,184.09);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (461.90,170.94) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (480.68,197.38) --
-	(482.70,197.38);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (481.71,196.98) --
-	(481.71,197.78);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (481.71,193.35) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (436.28,158.71) --
-	(449.09,158.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.66,150.24) --
-	(443.66,164.70);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (443.66,154.68) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.65,180.86) --
-	(466.79,180.86);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (465.75,178.58) --
-	(465.75,182.90);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (465.75,177.95) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.10,210.49) --
-	(500.73,210.49);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.93,208.48) --
-	(499.93,212.33);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (499.93,207.59) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (402.48,133.81) --
+	(427.20,133.81);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (418.58,122.95) --
+	(418.58,140.70);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (418.58,130.59) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (463.96,183.86) --
+	(498.40,183.86);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (488.07,166.42) --
+	(488.07,192.82);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (488.07,179.82) {$L$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (412.32,131.41) --
+	(425.95,131.41);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (420.32,125.62) --
+	(420.32,135.84);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (420.32,127.37) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (412.59,133.07) --
+	(432.70,133.07);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (425.17,121.05) --
+	(425.17,140.40);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (425.17,129.04) {$h$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (386.96,106.84) --
+	(412.97,106.84);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (404.08, 99.96) --
+	(404.08,111.88);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (404.08,103.93) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (514.29,225.53) --
+	(514.97,225.53);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (514.63,225.34) --
+	(514.63,225.72);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (514.63,222.63) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (497.79,213.90) --
+	(503.46,213.90);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (500.83,212.35) --
+	(500.83,215.34);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (500.83,210.68) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (478.90,193.69) --
+	(482.27,193.69);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.66,192.49) --
+	(480.66,194.82);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (480.66,189.66) {$L$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (507.93,220.22) --
+	(508.43,220.22);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (508.18,220.02) --
+	(508.18,220.41);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (508.18,216.18) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (491.57,205.97) --
+	(495.12,205.97);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (493.43,203.33) --
+	(493.43,208.29);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (493.43,201.94) {$h$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (503.22,214.26) --
+	(504.66,214.26);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (503.95,213.02) --
+	(503.95,215.41);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (503.95,211.35) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (515.97,224.96) --
+	(517.47,224.96);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (516.73,224.23) --
+	(516.73,225.66);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (516.73,222.06) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.25,189.86) --
+	(484.33,189.86);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (482.85,187.61) --
+	(482.85,191.86);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (482.85,186.63) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (485.11,203.25) --
+	(489.02,203.25);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (487.16,201.42) --
+	(487.16,204.91);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (487.16,199.21) {$L$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (511.92,224.51) --
+	(513.09,224.51);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (512.51,223.97) --
+	(512.51,225.03);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (512.51,220.48) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (456.53,174.40) --
+	(465.54,174.40);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (461.56,168.49) --
+	(461.56,178.92);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (461.56,170.37) {$h$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (471.24,182.70) --
+	(477.85,182.70);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (474.83,179.96) --
+	(474.83,185.10);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.83,179.80) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (519.16,227.69) --
+	(519.69,227.69);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (519.43,227.51) --
+	(519.43,227.87);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (519.43,224.79) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (465.86,186.69) --
+	(466.93,186.69);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (466.40,185.13) --
+	(466.40,188.14);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (466.40,183.47) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (476.81,194.33) --
+	(481.05,194.33);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (479.05,192.40) --
+	(479.05,196.08);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (479.05,190.29) {$L$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (503.73,219.06) --
+	(506.09,219.06);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (504.95,218.53) --
+	(504.95,219.58);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (504.95,215.03) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (457.61,179.76) --
+	(463.97,179.76);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (461.06,175.67) --
+	(461.06,183.13);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (461.06,175.73) {$h$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (461.22,186.48) --
+	(469.53,186.48);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (465.82,164.01) --
+	(465.82,196.53);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (465.82,183.58) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (518.70,228.09) --
+	(519.30,228.09);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (519.00,227.61) --
+	(519.00,228.56);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (519.00,225.19) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (440.05,149.07) --
+	(446.60,149.07);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (443.61,140.42) --
+	(443.61,155.00);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (443.61,145.84) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (482.66,197.96) --
+	(497.10,197.96);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (491.21,193.52) --
+	(491.21,201.57);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (491.21,193.93) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (482.31,198.48) --
+	(483.02,198.48);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (482.67,197.65) --
+	(482.67,199.28);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (482.67,194.45) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (435.88,141.67) --
+	(444.13,141.67);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (440.45,137.70) --
+	(440.45,144.96);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (440.45,137.63) {$h$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (430.12,152.12) --
+	(446.95,152.12);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (440.33,138.07) --
+	(440.33,160.13);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (440.33,149.21) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (515.31,226.85) --
+	(516.96,226.85);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (516.15,226.06) --
+	(516.15,227.60);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (516.15,223.94) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (511.01,226.91) --
+	(512.84,226.91);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (511.95,226.11) --
+	(511.95,227.68);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (511.95,223.69) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (491.35,207.58) --
+	(497.18,207.58);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (494.48,206.11) --
+	(494.48,208.95);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (494.48,203.55) {$L$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (523.54,236.94) --
+	(523.81,236.94);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (523.67,236.77) --
+	(523.67,237.11);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (523.67,232.91) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (482.77,199.05) --
+	(485.89,199.05);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (484.39,196.91) --
+	(484.39,200.98);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (484.39,195.02) {$h$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (497.32,213.65) --
+	(500.98,213.65);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (499.24,211.50) --
+	(499.24,215.58);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (499.24,210.75) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (517.89,227.34) --
+	(518.87,227.34);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (518.38,227.05) --
+	(518.38,227.63);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (518.38,224.44) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (455.83,171.67) --
+	(462.39,171.67);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (459.39,168.44) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (511.24,226.95) --
+	(515.97,226.95);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (513.75,222.92) {$L$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (493.31,212.27) --
+	(493.57,212.27);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (493.44,208.24) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (461.13,178.96) --
+	(463.91,178.96);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (462.57,174.93) {$h$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (468.52,174.11) --
+	(474.54,174.11);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (471.77,171.20) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (516.74,230.25) --
+	(519.35,230.25);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (518.09,227.35) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (487.89,210.95) --
+	(497.51,210.95);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (493.30,206.38) --
+	(493.30,214.63);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (493.30,207.72) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (464.41,188.45) --
+	(478.88,188.45);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (472.98,185.46) --
+	(472.98,191.04);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (472.98,184.42) {$L$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (510.18,227.14) --
+	(512.82,227.14);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (511.55,226.45) --
+	(511.55,227.79);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (511.55,223.10) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (472.41,191.50) --
+	(476.82,191.50);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (474.74,184.11) --
+	(474.74,196.81);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.74,187.46) {$h$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (474.64,199.45) --
+	(482.47,199.45);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (478.95,190.32) --
+	(478.95,205.61);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (478.95,196.55) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (528.55,239.61) --
+	(529.80,239.61);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (529.19,236.91) --
+	(529.19,241.97);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (529.19,236.70) {$\kappa$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (507.92,228.14) --
+	(510.30,228.14);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (509.15,227.35) --
+	(509.15,228.89);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (509.15,224.91) {$p$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (498.70,215.49) --
+	(502.10,215.49);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (500.48,214.12) --
+	(500.48,216.77);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (500.48,211.46) {$L$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (514.09,231.37) --
+	(515.01,231.37);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (514.56,231.18) --
+	(514.56,231.57);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (514.56,227.34) {$r$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (495.91,214.59) --
+	(499.36,214.59);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (497.71,213.26) --
+	(497.71,215.83);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (497.71,210.56) {$h$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (500.08,220.23) --
+	(503.50,220.23);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (501.87,219.79) --
+	(501.87,220.66);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (501.87,217.32) {$\sigma$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (530.30,241.17) --
+	(532.04,241.17);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (531.19,240.33) --
+	(531.19,241.98);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (531.19,238.27) {$\kappa$};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 49.80) -- (528.36, 49.80);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 49.80) -- (515.10, 49.80);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (386.25, 49.80) -- (386.25, 44.82);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.62, 49.80) -- (433.62, 44.82);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (480.99, 49.80) -- (480.99, 44.82);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (528.36, 49.80) -- (528.36, 44.82);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (382.93, 49.80) -- (382.93, 44.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.99, 49.80) -- (426.99, 44.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (471.04, 49.80) -- (471.04, 44.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (515.10, 49.80) -- (515.10, 44.82);
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (386.25, 31.87) {10};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (433.62, 31.87) {100};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (480.99, 31.87) {1000};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (528.36, 31.87) {10000};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 49.80) -- (338.88,239.28);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (382.93, 31.87) {10};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (426.99, 31.87) {100};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (471.04, 31.87) {1000};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (515.10, 31.87) {10000};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 49.80) -- (338.88,226.02);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 97.17) -- (333.90, 97.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,144.54) -- (333.90,144.54);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,191.91) -- (333.90,191.91);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,239.28) -- (333.90,239.28);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 93.85) -- (333.90, 93.85);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,137.91) -- (333.90,137.91);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,181.96) -- (333.90,181.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,226.02) -- (333.90,226.02);
 
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92, 94.31) {10};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,141.68) {100};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,189.05) {1000};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,236.42) {10000};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92, 91.00) {10};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,135.05) {100};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,179.11) {1000};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,223.16) {10000};
 \end{scope}

### 2020-08-24 benchmarking/benchmarkingVM/ESS_round1_real.tex
results update

--- 2020-08-07 benchmarking/benchmarkingVM/ESS_round1_real.tex
@@
-% Created by tikzDevice version 0.12.3 on 2020-08-07 14:28:24
+% Created by tikzDevice version 0.12.3.1 on 2020-08-24 19:04:05
 % !TEX encoding = UTF-8 Unicode
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,548.96) {\bfseries Comparison of cons (\textit{real}) and nocons (\textit{real})};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,548.96) {\bfseries cons (\textit{real}) vs. nocons (\textit{real})};
 
@@
 \definecolor{drawColor}{RGB}{0,0,0}
-\definecolor{fillColor}{gray}{0.91}
-
-\path[draw=drawColor,line width= 0.1pt,line join=round,line cap=round,fill=fillColor] (  0.00,365.38) --
-	(212.78,578.16) --
-	(281.53,578.16) --
-	(281.53,494.30) --
-	(  0.00,212.78) --
-	cycle;
-\definecolor{fillColor}{RGB}{190,190,190}
-
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] (  0.00,339.95) --
-	(238.21,578.16) --
-	(281.53,578.16) --
-	(281.53,519.74) --
-	(  0.00,238.21) --
-	cycle;
-\definecolor{fillColor}{RGB}{169,169,169}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (  0.00,314.51) --
-	(263.65,578.16) --
-	(281.53,578.16) --
-	(281.53,545.17) --
-	(  0.00,263.65) --
-	cycle;
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (133.64,342.31) {$\frac{1}{64} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,426.62) {$64\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (108.20,342.31) {$\frac{1}{16} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,401.18) {$16\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 81.11,342.31) {$\frac{1}{4} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92,375.75) {$4\times$};
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,528.36);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.14,457.67) --
-	(163.00,457.67);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.72,454.14) --
-	(158.72,460.63);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.72,454.44) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.97,498.27) --
-	(218.78,498.27);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.83,495.92) --
-	(212.83,500.36);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.83,494.24) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (178.45,498.59) --
-	(180.15,498.59);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.32,497.51) --
-	(179.32,499.62);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.32,494.56) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (146.49,453.46) --
-	(152.86,453.46);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (149.95,449.76) --
-	(149.95,456.55);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (149.95,449.43) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (156.64,437.17) --
-	(165.01,437.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.30,434.91) --
-	(161.30,439.18);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (161.30,434.26) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.32,508.76) --
-	(221.15,508.76);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.74,507.98) --
-	(220.74,509.51);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.74,505.85) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.30,494.32) --
-	(194.81,494.32);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.60,491.54) --
-	(193.60,496.74);
-\definecolor{drawColor}{RGB}{0,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.60,491.10) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (205.85,498.07) --
-	(214.19,498.07);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.49,494.17) --
-	(210.49,501.29);
-\definecolor{drawColor}{RGB}{0,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.49,494.04) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.48,503.25) --
-	(210.75,503.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.13,501.60) --
-	(210.13,504.76);
-\definecolor{drawColor}{RGB}{0,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.13,499.21) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.18,482.71) --
-	(198.08,482.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.79,479.66) --
-	(195.79,485.33);
-\definecolor{drawColor}{RGB}{0,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.79,478.68) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.48,485.22) --
-	(198.60,485.22);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.57,481.89) --
-	(197.57,488.04);
-\definecolor{drawColor}{RGB}{0,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.57,482.32) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.10,512.25) --
-	(223.18,512.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.65,510.74) --
-	(222.65,513.65);
-\definecolor{drawColor}{RGB}{0,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (222.65,509.35) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.17,469.31) --
-	(197.17,474.08);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.17,468.62) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (214.45,504.24) --
-	(220.93,504.24);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.97,503.56) --
-	(217.97,504.90);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (217.97,500.21) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.42,505.36) --
-	(222.61,505.36);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (216.85,505.09) --
-	(216.85,505.62);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (216.85,501.33) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.48,442.96) --
-	(169.48,453.47);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.48,444.93) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.56,462.82) --
-	(196.56,467.56);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.56,462.44) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.70,512.26) --
-	(223.15,512.26);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.93,512.04) --
-	(222.93,512.48);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (222.93,509.36) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.68,478.88) --
-	(192.68,485.07);
-\definecolor{drawColor}{RGB}{255,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.68,479.01) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.72,496.18) --
-	(218.04,496.18);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (205.74,494.03) --
-	(205.74,498.10);
-\definecolor{drawColor}{RGB}{255,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.74,492.14) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.70,503.25) --
-	(229.53,503.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (224.55,502.95) --
-	(224.55,503.55);
-\definecolor{drawColor}{RGB}{255,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (224.55,499.22) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.85,475.04) --
-	(211.32,475.04);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.84,472.97) --
-	(200.84,476.90);
-\definecolor{drawColor}{RGB}{255,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (200.84,471.00) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.62,480.49) --
-	(206.62,483.96);
-\definecolor{drawColor}{RGB}{255,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (206.62,479.40) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.33,511.89) --
-	(223.37,511.89);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.86,511.27) --
-	(222.86,512.49);
-\definecolor{drawColor}{RGB}{255,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (222.86,508.99) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.91,482.52) --
-	(221.91,491.18);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (221.91,484.13) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (202.65,482.61) --
-	(202.65,488.22);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.65,481.59) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (199.21,500.97) --
-	(230.61,500.97);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.94,500.31) --
-	(220.94,501.61);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.94,496.94) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.32,486.64) --
-	(193.67,486.64);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.26,482.99) --
-	(185.26,489.69);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.26,482.61) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (207.68,479.70) --
-	(207.68,488.91);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.68,481.98) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (119.95,439.54) --
-	(137.90,439.54);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (131.04,432.27) --
-	(131.04,444.73);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (131.04,436.31) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.56,498.07) --
-	(210.93,498.07);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.02,496.36) --
-	(208.02,499.62);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (208.02,494.03) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (125.81,497.45) --
-	(135.01,497.45);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (130.98,494.97) --
-	(130.98,499.64);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (130.98,493.42) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (119.66,452.88) --
-	(130.48,452.88);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (125.86,445.61) --
-	(125.86,458.08);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (125.86,448.85) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (119.40,419.55) --
-	(144.64,419.55);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (136.05,411.70) --
-	(136.05,425.03);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (136.05,416.65) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.17,512.87) --
-	(223.63,512.87);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.40,512.58) --
-	(223.40,513.16);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (223.40,509.97) {$\mu$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (165.32,492.59) --
-	(187.22,492.59);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.36,490.80) --
-	(179.36,494.22);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.36,489.37) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.77,494.95) --
-	(207.58,494.95);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (199.98,487.86) --
-	(199.98,500.06);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.98,490.92) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.10,499.92) --
-	(216.56,499.92);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.11,499.81) --
-	(210.11,500.04);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.11,495.89) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (156.75,463.31) --
-	(179.56,463.31);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.50,460.78) --
-	(171.50,465.53);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.50,459.27) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (165.37,483.34) --
-	(188.77,483.34);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.57,482.71) --
-	(180.57,483.94);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.57,480.43) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (216.41,512.30) --
-	(225.65,512.30);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.61,509.43) --
-	(221.61,514.78);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (221.61,509.40) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (164.18,476.03) --
-	(174.33,476.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.95,474.65) --
-	(169.95,477.32);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.95,472.81) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (213.06,503.10) --
-	(218.28,503.10);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.85,502.50) --
-	(215.85,503.67);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (215.85,499.06) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (202.88,502.51) --
-	(207.31,502.51);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (205.23,502.21) --
-	(205.23,502.80);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.23,498.47) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.71,468.73) --
-	(170.74,468.73);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (166.40,467.18) --
-	(166.40,470.16);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (166.40,464.70) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.55,467.47) --
-	(172.33,467.47);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (167.72,466.51) --
-	(167.72,468.39);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (167.72,464.57) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.84,507.62) --
-	(218.89,507.62);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.38,507.22) --
-	(218.38,508.01);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (218.38,504.71) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (137.20,493.15) --
-	(182.80,493.15);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.55,492.20) --
-	(171.55,494.06);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.55,489.93) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.57,502.64) --
-	(218.61,502.64);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (207.57,501.88) --
-	(207.57,503.37);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.57,498.61) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.92,502.35) --
-	(194.96,502.35);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.81,502.20) --
-	(187.81,502.49);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.81,498.31) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (165.35,472.33) --
-	(173.05,472.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.60,471.58) --
-	(169.60,473.05);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.60,468.29) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (134.07,470.24) --
-	(176.07,470.24);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (165.12,469.07) --
-	(165.12,471.33);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (165.12,467.33) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,368.65) --
+	(209.51,578.16);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (283.33,578.16) --
+	(283.33,492.84) --
+	(  0.00,209.51);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (  0.00,342.13) --
+	(236.03,578.16);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (283.33,578.16) --
+	(283.33,519.37) --
+	(  0.00,236.03);
+
+\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (  0.00,315.60) --
+	(262.56,578.16);
+
+\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (283.33,578.16) --
+	(283.33,545.89) --
+	(  0.00,262.56);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (136.90,342.31) {$\frac{1}{64} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,429.88) {$64\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (110.38,342.31) {$\frac{1}{16} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,403.36) {$16\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 82.20,342.31) {$\frac{1}{4} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92,376.84) {$4\times$};
+
+\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,528.36);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (107.51,439.94) --
+	(127.68,439.94);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (120.14,425.21) --
+	(120.14,448.17);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (120.14,436.72) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.31,513.97) --
+	(196.31,515.47);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.31,510.70) {$L$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (130.03,502.83) --
+	(138.08,502.83);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (134.47,497.15) --
+	(134.47,507.20);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (134.47,498.80) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (120.13,454.10) --
+	(131.49,454.10);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (126.64,438.20) --
+	(126.64,462.66);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (126.64,450.07) {$h$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (107.78,424.74) --
+	(134.23,424.74);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (125.25,412.85) --
+	(125.25,432.02);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (125.25,421.84) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (224.32,514.62) --
+	(225.43,514.62);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (224.88,514.04) --
+	(224.88,515.18);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (224.88,511.71) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (124.52,503.87) --
+	(156.63,503.87);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (146.64,501.94) --
+	(146.64,505.62);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (146.64,500.64) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (153.28,483.23) --
+	(178.74,483.23);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.96,480.38) --
+	(169.96,485.72);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.96,479.20) {$L$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (209.53,512.98) --
+	(219.08,512.98);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (214.89,512.67) --
+	(214.89,513.28);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (214.89,508.94) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.79,492.00) --
+	(201.34,492.00);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.21,490.01) --
+	(193.21,493.80);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.21,487.96) {$h$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (138.03,494.31) --
+	(180.52,494.31);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.23,492.07) --
+	(169.23,496.31);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.23,491.41) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (225.55,516.60) --
+	(227.26,516.60);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (226.43,516.10) --
+	(226.43,517.09);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (226.43,513.70) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.40,474.45) --
+	(198.40,481.06);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.40,474.81) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (145.24,495.45) --
+	(203.65,495.45);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.27,494.96) --
+	(191.27,495.92);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.27,491.42) {$L$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (209.83,514.09) --
+	(229.21,514.09);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (221.87,513.75) --
+	(221.87,514.43);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (221.87,510.05) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.36,451.14) --
+	(176.36,460.33);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.36,452.25) {$h$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.91,466.15) --
+	(198.91,474.11);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.91,467.64) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (228.60,518.50) --
+	(229.08,518.50);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (228.84,518.10) --
+	(228.84,518.89);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (228.84,515.59) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (129.72,483.83) --
+	(169.90,483.83);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (158.85,482.60) --
+	(158.85,484.98);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.85,480.60) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (153.47,490.36) --
+	(195.70,490.36);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.44,489.61) --
+	(184.44,491.09);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.44,486.33) {$L$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (202.50,511.41) --
+	(216.09,511.41);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (210.48,511.05) --
+	(210.48,511.76);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.48,507.38) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.11,476.52) --
+	(176.28,476.52);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (167.16,475.30) --
+	(167.16,477.68);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (167.16,472.49) {$h$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (136.04,473.71) --
+	(175.13,473.71);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.20,470.57) --
+	(164.20,476.41);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (164.20,470.81) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (228.57,519.04) --
+	(229.27,519.04);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (228.92,518.76) --
+	(228.92,519.31);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (228.92,516.13) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (157.99,465.14) --
+	(165.18,465.14);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.92,462.06) --
+	(161.92,467.80);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (161.92,461.92) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.71,508.79) --
+	(203.68,508.79);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.45,506.03) --
+	(195.45,511.19);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.45,504.75) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.01,507.17) --
+	(187.33,507.17);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.68,506.03) --
+	(186.68,508.25);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (186.68,503.14) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (143.93,460.26) --
+	(151.84,460.26);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (148.29,455.77) --
+	(148.29,463.90);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (148.29,456.23) {$h$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (158.24,444.03) --
+	(170.29,444.03);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (165.20,442.71) --
+	(165.20,445.27);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (165.20,441.13) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (226.21,516.34) --
+	(226.84,516.34);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (226.53,515.49) --
+	(226.53,517.16);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (226.53,513.44) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.07,486.04) --
+	(195.07,492.68);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.07,486.42) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.22,495.86) --
+	(188.22,500.05);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.22,494.04) {$L$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (224.90,512.15) --
+	(238.51,512.15);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (232.89,511.77) --
+	(232.89,512.53);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (232.89,508.12) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.48,482.21) --
+	(219.73,482.21);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (208.90,479.90) --
+	(208.90,484.27);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (208.90,478.18) {$h$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (212.90,487.36) --
+	(212.90,491.02);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.90,486.37) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (227.61,517.72) --
+	(228.72,517.72);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (228.17,517.16) --
+	(228.17,518.25);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (228.17,514.81) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (134.31,501.18) --
+	(134.31,502.87);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (134.31,498.82) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (140.07,506.91) --
+	(140.07,511.00);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (140.07,505.03) {$L$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (163.84,511.28) --
+	(197.54,511.28);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.31,511.18) --
+	(187.31,511.39);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.31,507.25) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.23,479.47) --
+	(178.50,479.47);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.04,477.70) --
+	(176.04,481.09);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.04,475.44) {$h$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (145.91,475.98) --
+	(145.91,477.70);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (145.91,473.95) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (225.98,518.28) --
+	(229.70,518.28);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (227.93,517.72) --
+	(227.93,518.83);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (227.93,515.38) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (106.47,493.53) --
+	(119.17,493.53);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (113.85,490.64) --
+	(113.85,496.03);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (113.85,490.30) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (121.32,481.57) --
+	(142.29,481.57);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (134.54,464.93) --
+	(134.54,490.33);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (134.54,477.53) {$L$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (197.73,508.06) --
+	(213.81,508.06);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (207.41,507.86) --
+	(207.41,508.26);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.41,504.03) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (147.10,471.65) --
+	(168.39,471.65);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (160.56,469.20) --
+	(160.56,473.83);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (160.56,467.62) {$h$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (109.28,482.67) --
+	(125.12,482.67);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (118.79,477.71) --
+	(118.79,486.60);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (118.79,479.76) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (236.93,528.42) --
+	(238.96,528.42);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (237.97,526.53) --
+	(237.97,530.13);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (237.97,525.51) {$\kappa$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (227.40,493.98) --
+	(227.40,500.05);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (227.40,494.03) {$p$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.33,489.37) --
+	(175.33,499.62);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (175.33,491.14) {$L$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.06,509.80) --
+	(237.03,509.80);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (225.26,509.43) --
+	(225.26,510.17);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (225.26,505.77) {$r$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.04,492.43) --
+	(200.67,492.43);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.66,487.19) --
+	(191.66,496.54);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.66,488.40) {$h$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (207.78,491.01) --
+	(207.78,496.89);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.78,491.27) {$\sigma$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (241.40,531.56) --
+	(243.18,531.56);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (242.31,530.87) --
+	(242.31,532.22);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (242.31,528.65) {$\kappa$};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,338.88) -- (218.78,338.88);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,338.88) -- (226.02,338.88);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.05,338.88) -- ( 92.05,333.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (134.29,338.88) -- (134.29,333.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.54,338.88) -- (176.54,333.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.78,338.88) -- (218.78,333.90);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 93.85,338.88) -- ( 93.85,333.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (137.91,338.88) -- (137.91,333.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.96,338.88) -- (181.96,333.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.02,338.88) -- (226.02,333.90);
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 92.05,320.95) {10};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (134.29,320.95) {100};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (176.54,320.95) {1000};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (218.78,320.95) {10000};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,338.88) -- ( 49.80,507.86);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 93.85,320.95) {10};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (137.91,320.95) {100};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (181.96,320.95) {1000};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (226.02,320.95) {10000};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,338.88) -- ( 49.80,515.10);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,381.13) -- ( 44.82,381.13);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,423.37) -- ( 44.82,423.37);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,465.62) -- ( 44.82,465.62);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,507.86) -- ( 44.82,507.86);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,382.93) -- ( 44.82,382.93);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,426.99) -- ( 44.82,426.99);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,471.04) -- ( 44.82,471.04);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,515.10) -- ( 44.82,515.10);
 
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,378.27) {10};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,420.51) {100};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,462.76) {1000};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,505.00) {10000};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,380.08) {10};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,424.13) {100};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,468.19) {1000};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,512.24) {10000};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,548.96) {\bfseries Comparison of adapt (\textit{real}) and nocons (\textit{real})};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,548.96) {\bfseries adapt (\textit{real}) vs. nocons (\textit{real})};
 
@@
 \definecolor{drawColor}{RGB}{0,0,0}
-\definecolor{fillColor}{gray}{0.91}
-
-\path[draw=drawColor,line width= 0.1pt,line join=round,line cap=round,fill=fillColor] (169.90,246.20) --
-	(501.86,578.16) --
-	(570.61,578.16) --
-	(570.61,494.30) --
-	(169.90, 93.59) --
-	cycle;
-\definecolor{fillColor}{RGB}{190,190,190}
-
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] (169.90,220.77) --
-	(527.29,578.16) --
-	(570.61,578.16) --
-	(570.61,519.74) --
-	(169.90,119.03) --
-	cycle;
-\definecolor{fillColor}{RGB}{169,169,169}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.90,195.33) --
-	(552.73,578.16) --
-	(570.61,578.16) --
-	(570.61,545.17) --
-	(169.90,144.46) --
-	cycle;
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (422.72,342.31) {$\frac{1}{64} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,426.62) {$64\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (397.28,342.31) {$\frac{1}{16} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,401.18) {$16\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (370.19,342.31) {$\frac{1}{4} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.00,375.75) {$4\times$};
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (338.88,338.88) -- (528.36,528.36);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (442.22,490.95) --
-	(452.08,490.95);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (447.80,488.50) --
-	(447.80,493.11);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (447.80,487.72) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (493.05,494.57) --
-	(507.86,494.57);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (501.91,492.61) --
-	(501.91,496.33);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (501.91,490.53) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (467.53,499.63) --
-	(469.23,499.63);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (468.40,499.53) --
-	(468.40,499.72);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.40,495.59) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (435.57,457.21) --
-	(441.94,457.21);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (439.03,453.71) --
-	(439.03,460.15);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (439.03,453.18) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (445.72,477.46) --
-	(454.09,477.46);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (450.38,473.15) --
-	(450.38,480.94);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (450.38,474.55) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (509.40,508.34) --
-	(510.23,508.34);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (509.82,507.96) --
-	(509.82,508.71);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (509.82,505.44) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.25,470.08) --
-	(486.25,474.05);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (486.25,468.95) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (503.53,505.74) --
-	(510.01,505.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (507.05,504.33) --
-	(507.05,507.05);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (507.05,501.71) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (497.50,509.15) --
-	(511.69,509.15);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (505.93,509.01) --
-	(505.93,509.30);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (505.93,505.12) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (458.56,441.48) --
-	(458.56,447.41);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (458.56,440.65) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.64,465.29) --
-	(485.64,470.85);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (485.64,465.37) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (511.78,512.39) --
-	(512.23,512.39);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (512.01,512.01) --
-	(512.01,512.77);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (512.01,509.49) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (510.99,489.74) --
-	(510.99,496.16);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (510.99,490.01) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (491.73,482.43) --
-	(491.73,487.46);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (491.73,481.08) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (488.29,509.74) --
-	(519.69,509.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (510.02,509.40) --
-	(510.02,510.06);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (510.02,505.70) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (458.40,493.13) --
-	(482.75,493.13);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.34,492.97) --
-	(474.34,493.29);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.34,489.10) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (496.76,491.95) --
-	(496.76,497.87);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (496.76,492.25) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (409.03,486.63) --
-	(426.98,486.63);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.12,480.59) --
-	(420.12,491.17);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (420.12,483.41) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (493.64,486.94) --
-	(500.01,486.94);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (497.10,484.78) --
-	(497.10,488.87);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (497.10,482.90) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (414.89,499.46) --
-	(424.09,499.46);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.06,498.34) --
-	(420.06,500.52);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (420.06,495.43) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (408.74,462.06) --
-	(419.56,462.06);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (414.94,452.46) --
-	(414.94,468.33);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (414.94,458.03) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (408.48,488.92) --
-	(433.72,488.92);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (425.13,483.95) --
-	(425.13,492.83);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (425.13,486.02) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (512.25,512.90) --
-	(512.71,512.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (512.48,512.69) --
-	(512.48,513.11);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (512.48,509.99) {$\mu$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.40,497.82) --
-	(476.30,497.82);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (468.44,494.86) --
-	(468.44,500.36);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.44,494.59) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (475.85,498.71) --
-	(496.66,498.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (489.06,489.13) --
-	(489.06,504.97);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (489.06,494.67) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (489.18,507.02) --
-	(505.64,507.02);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.19,506.47) --
-	(499.19,507.55);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (499.19,502.98) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (445.83,469.60) --
-	(468.64,469.60);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (460.58,463.71) --
-	(460.58,474.05);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (460.58,465.56) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.45,496.70) --
-	(477.85,496.70);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (469.65,491.56) --
-	(469.65,500.72);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (469.65,493.80) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (505.49,512.98) --
-	(514.73,512.98);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (510.69,511.49) --
-	(510.69,514.37);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (510.69,510.08) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (453.26,482.10) --
-	(463.41,482.10);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (459.03,480.23) --
-	(459.03,483.80);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (459.03,478.87) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (502.14,502.07) --
-	(507.36,502.07);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (504.93,500.38) --
-	(504.93,503.61);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (504.93,498.03) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (491.96,503.97) --
-	(496.39,503.97);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (494.31,503.61) --
-	(494.31,504.33);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (494.31,499.94) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (449.79,473.17) --
-	(459.82,473.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (455.48,470.48) --
-	(455.48,475.52);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (455.48,469.14) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (450.63,478.15) --
-	(461.41,478.15);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (456.80,476.59) --
-	(456.80,479.58);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (456.80,475.24) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (506.92,507.74) --
-	(507.97,507.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (507.46,507.42) --
-	(507.46,508.04);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (507.46,504.83) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.28,495.30) --
-	(471.88,495.30);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (460.63,494.52) --
-	(460.63,496.04);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (460.63,492.07) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.65,495.60) --
-	(507.69,495.60);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (496.65,494.08) --
-	(496.65,497.00);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (496.65,491.57) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (465.00,500.38) --
-	(484.04,500.38);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.89,500.12) --
-	(476.89,500.63);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (476.89,496.34) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.43,473.27) --
-	(462.13,473.27);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (458.68,472.16) --
-	(458.68,474.32);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (458.68,469.24) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.15,473.74) --
-	(465.15,473.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.20,471.09) --
-	(454.20,476.05);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (454.20,470.83) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.66,242.23) --
+	(498.59,578.16);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (572.41,578.16) --
+	(572.41,492.84) --
+	(162.66, 83.09) --
+	(162.66,242.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (162.66,215.71) --
+	(525.11,578.16);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (572.41,578.16) --
+	(572.41,519.37) --
+	(162.66,109.61) --
+	(162.66,215.71);
+
+\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (162.66,189.19) --
+	(551.64,578.16);
+
+\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (572.41,578.16) --
+	(572.41,545.89) --
+	(162.66,136.14) --
+	(162.66,189.19);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (425.98,342.31) {$\frac{1}{64} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,429.88) {$64\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (399.46,342.31) {$\frac{1}{16} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,403.36) {$16\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (371.28,342.31) {$\frac{1}{4} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.00,376.84) {$4\times$};
+
+\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (338.88,338.88) -- (528.36,528.36);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (396.59,491.83) --
+	(416.76,491.83);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (409.22,484.91) --
+	(409.22,496.90);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (409.22,488.60) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (485.39,513.46) --
+	(485.39,517.31);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (485.39,511.45) {$L$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (419.11,508.15) --
+	(427.16,508.15);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (423.55,507.02) --
+	(423.55,509.22);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (423.55,504.12) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (409.21,469.50) --
+	(420.57,469.50);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (415.72,459.30) --
+	(415.72,476.12);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (415.72,465.47) {$h$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (396.86,494.88) --
+	(423.31,494.88);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (414.33,490.31) --
+	(414.33,498.58);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (414.33,491.98) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (513.40,514.73) --
+	(514.51,514.73);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (513.96,514.21) --
+	(513.96,515.24);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (513.96,511.83) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (413.60,504.78) --
+	(445.71,504.78);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (435.72,504.07) --
+	(435.72,505.47);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (435.72,501.56) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (442.36,483.32) --
+	(467.82,483.32);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (459.04,482.10) --
+	(459.04,484.46);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (459.04,479.28) {$L$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (498.61,513.50) --
+	(508.16,513.50);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (503.97,513.33) --
+	(503.97,513.67);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (503.97,509.47) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (467.87,494.70) --
+	(490.42,494.70);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (482.29,493.28) --
+	(482.29,496.02);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (482.29,490.67) {$h$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (427.11,506.61) --
+	(469.60,506.61);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (458.31,505.81) --
+	(458.31,507.37);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (458.31,503.70) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (514.63,514.56) --
+	(516.34,514.56);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (515.51,514.31) --
+	(515.51,514.81);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (515.51,511.66) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (487.48,477.75) --
+	(487.48,481.67);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (487.48,476.59) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (434.32,492.07) --
+	(492.73,492.07);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.35,485.78) --
+	(480.35,496.80);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (480.35,488.04) {$L$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (498.91,518.14) --
+	(518.29,518.14);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (510.95,517.82) --
+	(510.95,518.45);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (510.95,514.11) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (465.44,449.07) --
+	(465.44,453.85);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (465.44,447.57) {$h$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (487.99,472.24) --
+	(487.99,478.57);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (487.99,472.76) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (517.68,518.59) --
+	(518.16,518.59);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (517.92,518.46) --
+	(517.92,518.71);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (517.92,515.68) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (418.80,491.01) --
+	(458.98,491.01);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (447.93,487.64) --
+	(447.93,493.87);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (447.93,487.78) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (442.55,488.00) --
+	(484.78,488.00);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (473.52,486.78) --
+	(473.52,489.16);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (473.52,483.97) {$L$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (491.58,512.98) --
+	(505.17,512.98);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (499.56,512.68) --
+	(499.56,513.27);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (499.56,508.95) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (438.19,480.43) --
+	(465.36,480.43);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (456.24,476.92) --
+	(456.24,483.40);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (456.24,476.40) {$h$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (425.12,485.33) --
+	(464.21,485.33);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (453.28,483.22) --
+	(453.28,487.22);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (453.28,482.42) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (517.65,518.72) --
+	(518.35,518.72);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (518.00,518.22) --
+	(518.00,519.21);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (518.00,515.82) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (447.07,496.45) --
+	(454.26,496.45);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (451.00,492.63) --
+	(451.00,499.63);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (451.00,493.22) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (469.79,506.28) --
+	(492.76,506.28);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (484.53,502.48) --
+	(484.53,509.46);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (484.53,502.25) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (475.09,508.23) --
+	(476.41,508.23);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (475.76,508.03) --
+	(475.76,508.43);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (475.76,504.20) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (433.01,463.38) --
+	(440.92,463.38);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (437.37,458.93) --
+	(437.37,466.99);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (437.37,459.35) {$h$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (447.32,485.70) --
+	(459.37,485.70);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (454.28,478.90) --
+	(454.28,490.71);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (454.28,482.80) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (515.29,516.73) --
+	(515.92,516.73);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (515.61,516.31) --
+	(515.61,517.14);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (515.61,513.83) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (484.15,483.94) --
+	(484.15,500.04);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (484.15,490.41) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (477.30,495.56) --
+	(477.30,497.59);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (477.30,492.57) {$L$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (513.98,524.67) --
+	(527.59,524.67);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (521.97,524.50) --
+	(521.97,524.84);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (521.97,520.63) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (470.56,488.81) --
+	(508.81,488.81);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (497.98,487.21) --
+	(497.98,490.29);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (497.98,484.78) {$h$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (501.98,495.18) --
+	(501.98,499.74);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (501.98,494.69) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (516.69,516.36) --
+	(517.80,516.36);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (517.25,515.62) --
+	(517.25,517.07);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (517.25,513.45) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (423.39,502.71) --
+	(423.39,504.41);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (423.39,500.35) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (429.15,508.11) --
+	(429.15,511.22);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (429.15,505.70) {$L$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (452.92,509.24) --
+	(486.62,509.24);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (476.39,508.98) --
+	(476.39,509.50);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (476.39,505.21) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (462.31,479.99) --
+	(467.58,479.99);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (465.12,478.93) --
+	(465.12,481.00);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (465.12,475.96) {$h$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (434.99,478.69) --
+	(434.99,483.82);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (434.99,478.52) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (515.06,517.17) --
+	(518.78,517.17);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (517.01,516.17) --
+	(517.01,518.13);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (517.01,514.27) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (395.55,504.25) --
+	(408.25,504.25);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (402.93,499.69) --
+	(402.93,507.93);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (402.93,501.02) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (410.40,482.55) --
+	(431.37,482.55);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (423.62,478.83) --
+	(423.62,485.66);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (423.62,478.52) {$L$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (486.81,515.35) --
+	(502.89,515.35);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (496.49,514.89) --
+	(496.49,515.80);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (496.49,511.32) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (436.18,476.20) --
+	(457.47,476.20);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (449.64,470.52) --
+	(449.64,480.58);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (449.64,472.17) {$h$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (398.36,502.37) --
+	(414.20,502.37);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (407.87,497.47) --
+	(407.87,506.27);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (407.87,499.46) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (526.01,528.12) --
+	(528.04,528.12);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (527.05,526.74) --
+	(527.05,529.42);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (527.05,525.22) {$\kappa$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (516.48,497.06) --
+	(516.48,503.10);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (516.48,497.09) {$p$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (464.41,493.38) --
+	(464.41,499.78);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (464.41,492.81) {$L$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (478.14,518.98) --
+	(526.11,518.98);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (514.34,518.81) --
+	(514.34,519.15);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (514.34,514.95) {$r$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (463.12,499.46) --
+	(489.75,499.46);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.74,497.44) --
+	(480.74,501.29);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (480.74,495.42) {$h$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (496.86,502.88) --
+	(496.86,505.02);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (496.86,501.07) {$\sigma$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (530.48,531.24) --
+	(532.26,531.24);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (531.39,530.62) --
+	(531.39,531.84);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (531.39,528.33) {$\kappa$};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,338.88) -- (507.86,338.88);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,338.88) -- (515.10,338.88);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (381.13,338.88) -- (381.13,333.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.37,338.88) -- (423.37,333.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (465.62,338.88) -- (465.62,333.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (507.86,338.88) -- (507.86,333.90);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (382.93,338.88) -- (382.93,333.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.99,338.88) -- (426.99,333.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (471.04,338.88) -- (471.04,333.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (515.10,338.88) -- (515.10,333.90);
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (381.13,320.95) {10};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (423.37,320.95) {100};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (465.62,320.95) {1000};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (507.86,320.95) {10000};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,338.88) -- (338.88,507.86);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (382.93,320.95) {10};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (426.99,320.95) {100};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (471.04,320.95) {1000};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (515.10,320.95) {10000};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,338.88) -- (338.88,515.10);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,381.13) -- (333.90,381.13);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,423.37) -- (333.90,423.37);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,465.62) -- (333.90,465.62);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,507.86) -- (333.90,507.86);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,382.93) -- (333.90,382.93);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,426.99) -- (333.90,426.99);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,471.04) -- (333.90,471.04);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,515.10) -- (333.90,515.10);
 
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,378.27) {10};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,420.51) {100};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,462.76) {1000};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,505.00) {10000};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,380.08) {10};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,424.13) {100};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,468.19) {1000};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,512.24) {10000};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,259.88) {\bfseries Comparison of adapt (\textit{real}) and cons (\textit{real})};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,259.88) {\bfseries adapt (\textit{real}) vs. cons (\textit{real})};
 
@@
 \definecolor{drawColor}{RGB}{0,0,0}
-\definecolor{fillColor}{gray}{0.91}
-
-\path[draw=drawColor,line width= 0.1pt,line join=round,line cap=round,fill=fillColor] (  0.00, 82.04) --
-	(284.70,366.75) --
-	(284.70,202.66) --
-	( 82.04,  0.00) --
-	(  0.00,  0.00) --
-	cycle;
-\definecolor{fillColor}{RGB}{190,190,190}
-
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] (  0.00, 54.70) --
-	(284.70,339.40) --
-	(284.70,230.01) --
-	( 54.70,  0.00) --
-	(  0.00,  0.00) --
-	cycle;
-\definecolor{fillColor}{RGB}{169,169,169}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (  0.00, 27.35) --
-	(284.70,312.05) --
-	(284.70,257.36) --
-	( 27.35,  0.00) --
-	(  0.00,  0.00) --
-	cycle;
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (139.38, 53.23) {$\frac{1}{64} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,143.28) {$64\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (112.03, 53.23) {$\frac{1}{16} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,115.93) {$16\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 83.03, 53.23) {$\frac{1}{4} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92, 88.58) {$4\times$};
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 49.80, 49.80) -- (239.28,239.28);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.73,213.31) --
-	(180.71,213.31);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.53,210.67) --
-	(177.53,215.64);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.53,210.08) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.65,217.20) --
-	(223.43,217.20);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.18,215.09) --
-	(221.18,219.10);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (221.18,213.16) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.36,222.64) --
-	(222.63,222.64);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.53,222.53) --
-	(221.53,222.74);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (221.53,218.60) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.02,177.03) --
-	(176.32,177.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.00,173.27) --
-	(173.00,180.19);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.00,173.00) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.05,198.80) --
-	(157.65,198.80);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (155.48,194.17) --
-	(155.48,202.55);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (155.48,195.89) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.61,232.01) --
-	(233.26,232.01);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.46,231.60) --
-	(232.46,232.40);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (232.46,229.10) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.04,193.12) --
-	(195.17,193.12);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.77,190.87) --
-	(192.77,195.14);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.77,189.89) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.87,229.21) --
-	(228.31,229.21);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.60,227.70) --
-	(227.60,230.62);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (227.60,225.18) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.52,232.88) --
-	(229.09,232.88);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.80,232.72) --
-	(228.80,233.04);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (228.80,228.85) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.71,163.56) --
-	(173.01,163.56);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.16,160.12) --
-	(168.16,166.49);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (168.16,159.53) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (183.06,188.93) --
-	(188.16,188.93);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.77,185.72) --
-	(185.77,191.69);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.77,186.03) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.98,236.37) --
-	(236.46,236.37);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (236.22,235.95) --
-	(236.22,236.77);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (236.22,233.46) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.24,215.76) --
-	(213.56,215.76);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.45,212.01) --
-	(209.45,218.92);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.45,212.54) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.34,207.04) --
-	(210.37,207.04);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (207.59,204.14) --
-	(207.59,209.56);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.59,203.00) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.38,233.51) --
-	(224.77,233.51);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (224.09,233.15) --
-	(224.09,233.86);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (224.09,229.47) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.76,215.65) --
-	(211.95,215.65);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.68,215.48) --
-	(208.68,215.82);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (208.68,211.62) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (201.21,217.83) --
-	(211.12,217.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.78,214.39) --
-	(206.78,220.75);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (206.78,214.92) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (150.22,208.67) --
-	(163.61,208.67);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.03,202.16) --
-	(158.03,213.55);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.03,205.44) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (219.13,208.99) --
-	(222.64,208.99);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.96,206.67) --
-	(220.96,211.07);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.96,204.96) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.63,222.46) --
-	(222.65,222.46);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.30,221.26) --
-	(220.30,223.59);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.30,218.43) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (164.55,182.25) --
-	(177.96,182.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.38,171.93) --
-	(172.38,188.99);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.38,178.21) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (128.10,211.13) --
-	(142.44,211.13);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (136.54,205.79) --
-	(136.54,215.33);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (136.54,208.22) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (236.56,236.91) --
-	(237.19,236.91);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (236.88,236.68) --
-	(236.88,237.13);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (236.88,234.00) {$\mu$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (213.15,220.69) --
-	(216.83,220.69);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.07,217.51) --
-	(215.07,223.43);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (215.07,217.47) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.98,221.65) --
-	(223.10,221.65);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.61,211.36) --
-	(217.61,228.38);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (217.61,217.62) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.83,230.59) --
-	(223.08,230.59);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.96,230.00) --
-	(222.96,231.16);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (222.96,226.55) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.87,190.35) --
-	(185.98,190.35);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (183.59,184.02) --
-	(183.59,195.13);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.59,186.31) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.45,219.50) --
-	(205.78,219.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (205.12,213.97) --
-	(205.12,223.81);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.12,216.59) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (233.18,237.00) --
-	(238.93,237.00);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (236.27,235.39) --
-	(236.27,238.49);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (236.27,234.10) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.79,203.79) --
-	(198.65,203.79);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.27,201.78) --
-	(197.27,205.62);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.27,200.56) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.73,225.26) --
-	(226.99,225.26);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.37,223.45) --
-	(226.37,226.92);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (226.37,221.23) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.42,227.31) --
-	(226.05,227.31);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.74,226.93) --
-	(225.74,227.69);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (225.74,223.28) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.75,194.19) --
-	(190.95,194.19);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.42,191.29) --
-	(189.42,196.72);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (189.42,190.16) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.03,199.54) --
-	(189.05,199.54);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.07,197.87) --
-	(188.07,201.08);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.07,196.64) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.81,231.36) --
-	(231.65,231.36);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.23,231.02) --
-	(231.23,231.69);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (231.23,228.45) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (214.65,217.98) --
-	(216.65,217.98);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.68,217.15) --
-	(215.68,218.78);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (215.68,214.76) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.06,218.31) --
-	(226.66,218.31);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.88,216.68) --
-	(225.88,219.81);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (225.88,214.28) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.41,223.44) --
-	(225.72,223.44);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.56,223.17) --
-	(225.56,223.71);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (225.56,219.41) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.48,194.30) --
-	(194.06,194.30);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.28,193.10) --
-	(193.28,195.43);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.28,190.27) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.79,194.80) --
-	(192.21,194.80);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.04,191.95) --
-	(191.04,197.29);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.04,191.90) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00, 79.57) --
+	(283.33,362.91) --
+	(283.33,203.76) --
+	( 79.57,  0.00);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (  0.00, 53.05) --
+	(283.33,336.38) --
+	(283.33,230.29) --
+	( 53.05,  0.00);
+
+\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (  0.00, 26.52) --
+	(283.33,309.86) --
+	(283.33,256.81) --
+	( 26.52,  0.00);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (136.90, 53.23) {$\frac{1}{64} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,140.80) {$64\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (110.38, 53.23) {$\frac{1}{16} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,114.28) {$16\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 82.20, 53.23) {$\frac{1}{4} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92, 87.76) {$4\times$};
+
+\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] ( 49.80, 49.80) -- (239.28,239.28);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (136.13,202.75) --
+	(159.09,202.75);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.86,195.83) --
+	(150.86,207.82);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (150.86,199.52) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (224.89,226.40) --
+	(226.39,226.40);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (225.65,224.38) --
+	(225.65,228.23);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (225.65,222.37) {$L$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (208.07,219.07) --
+	(218.12,219.07);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (213.75,217.94) --
+	(213.75,220.14);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (213.75,215.04) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.12,180.42) --
+	(173.58,180.42);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (165.02,170.22) --
+	(165.02,187.04);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (165.02,176.39) {$h$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (123.77,205.80) --
+	(142.94,205.80);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (135.66,201.23) --
+	(135.66,209.50);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (135.66,202.90) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (224.96,225.65) --
+	(226.10,225.65);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (225.54,225.13) --
+	(225.54,226.16);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (225.54,222.75) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (212.86,215.70) --
+	(216.54,215.70);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (214.79,214.99) --
+	(214.79,216.39);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (214.79,212.48) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.30,194.24) --
+	(196.64,194.24);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.15,193.02) --
+	(194.15,195.38);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.15,190.20) {$L$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (223.59,224.42) --
+	(224.20,224.42);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (223.90,224.25) --
+	(223.90,224.59);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (223.90,220.39) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (200.93,205.62) --
+	(204.72,205.62);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (202.92,204.20) --
+	(202.92,206.94);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.92,201.59) {$h$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (202.99,217.53) --
+	(207.23,217.53);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (205.23,216.73) --
+	(205.23,218.29);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.23,214.62) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (227.02,225.48) --
+	(228.01,225.48);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (227.52,225.23) --
+	(227.52,225.73);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (227.52,222.58) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.37,190.73) --
+	(191.98,190.73);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.96,188.67) --
+	(188.96,192.59);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.96,187.51) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (205.88,202.99) --
+	(206.84,202.99);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (206.37,196.70) --
+	(206.37,207.72);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (206.37,198.96) {$L$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (224.67,229.06) --
+	(225.35,229.06);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (225.01,228.74) --
+	(225.01,229.37);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (225.01,225.03) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (162.06,162.53) --
+	(171.25,162.53);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (167.20,159.99) --
+	(167.20,164.77);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (167.20,158.49) {$h$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (177.07,186.59) --
+	(185.03,186.59);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.46,183.16) --
+	(181.46,189.49);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.46,183.68) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (229.02,229.51) --
+	(229.81,229.51);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (229.42,229.38) --
+	(229.42,229.63);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (229.42,226.60) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.52,201.93) --
+	(195.90,201.93);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.75,198.56) --
+	(194.75,204.79);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.75,198.70) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (200.53,198.92) --
+	(202.01,198.92);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (201.28,197.70) --
+	(201.28,200.08);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (201.28,194.89) {$L$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (221.97,223.90) --
+	(222.68,223.90);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (222.33,223.60) --
+	(222.33,224.19);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (222.33,219.87) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.22,191.35) --
+	(188.60,191.35);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.44,187.84) --
+	(187.44,194.32);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.44,187.32) {$h$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.49,196.25) --
+	(187.33,196.25);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.63,194.14) --
+	(184.63,198.14);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.63,193.34) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (229.68,229.64) --
+	(230.23,229.64);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (229.96,229.14) --
+	(229.96,230.13);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (229.96,226.74) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.98,207.37) --
+	(178.72,207.37);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.06,203.55) --
+	(176.06,210.55);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.06,204.14) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (216.95,217.20) --
+	(222.11,217.20);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (219.71,213.40) --
+	(219.71,220.38);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (219.71,213.17) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (216.95,219.15) --
+	(219.17,219.15);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (218.09,218.95) --
+	(218.09,219.35);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (218.09,215.12) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (166.69,174.30) --
+	(174.82,174.30);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.18,169.85) --
+	(171.18,177.91);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.18,170.27) {$h$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (153.63,196.62) --
+	(156.19,196.62);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (154.95,189.82) --
+	(154.95,201.63);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (154.95,193.72) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (226.41,227.65) --
+	(228.08,227.65);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (227.26,227.23) --
+	(227.26,228.06);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (227.26,224.75) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.96,204.56) --
+	(203.60,204.56);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (200.57,194.86) --
+	(200.57,210.96);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (200.57,201.33) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (206.78,207.52) --
+	(210.97,207.52);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (208.99,206.48) --
+	(208.99,208.51);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (208.99,203.49) {$L$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (222.69,235.59) --
+	(223.45,235.59);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (223.07,235.42) --
+	(223.07,235.76);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (223.07,231.55) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.82,199.73) --
+	(195.19,199.73);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.13,198.13) --
+	(193.13,201.21);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.13,195.70) {$h$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.28,208.52) --
+	(201.94,208.52);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (200.19,206.10) --
+	(200.19,210.66);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (200.19,205.61) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (228.08,227.28) --
+	(229.17,227.28);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (228.64,226.54) --
+	(228.64,227.99);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (228.64,224.37) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (212.10,214.50) --
+	(213.79,214.50);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (212.97,213.63) --
+	(212.97,215.33);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.97,211.27) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (217.83,220.65) --
+	(221.92,220.65);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (219.98,219.03) --
+	(219.98,222.14);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (219.98,216.62) {$L$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (222.10,220.16) --
+	(222.31,220.16);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (222.20,219.90) --
+	(222.20,220.42);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (222.20,216.13) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.62,190.91) --
+	(192.01,190.91);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.39,189.85) --
+	(190.39,191.92);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.39,186.88) {$h$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.90,192.35) --
+	(188.62,192.35);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.78,189.61) --
+	(187.78,194.74);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.78,189.44) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (228.64,228.09) --
+	(229.75,228.09);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (229.20,227.09) --
+	(229.20,229.05);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (229.20,225.19) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (201.56,215.17) --
+	(206.95,215.17);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (204.45,210.61) --
+	(204.45,218.85);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (204.45,211.94) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.85,193.47) --
+	(201.25,193.47);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.49,189.75) --
+	(192.49,196.58);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.49,189.44) {$L$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (218.78,226.27) --
+	(219.18,226.27);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (218.98,225.81) --
+	(218.98,226.72);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (218.98,222.24) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.12,187.12) --
+	(184.75,187.12);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.57,181.44) --
+	(182.57,191.50);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.57,183.09) {$h$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.63,213.29) --
+	(197.52,213.29);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.59,208.39) --
+	(193.59,217.19);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.59,210.38) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (237.45,239.04) --
+	(241.05,239.04);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (239.34,237.66) --
+	(239.34,240.34);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (239.34,236.14) {$\kappa$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (204.90,211.23) --
+	(210.97,211.23);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (208.18,207.98) --
+	(208.18,214.02);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (208.18,208.01) {$p$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (200.29,207.77) --
+	(210.54,207.77);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (206.09,204.30) --
+	(206.09,210.70);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (206.09,203.73) {$L$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (220.35,229.90) --
+	(221.09,229.90);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (220.72,229.73) --
+	(220.72,230.07);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.72,225.87) {$r$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.11,210.38) --
+	(207.46,210.38);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (203.35,208.36) --
+	(203.35,212.21);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (203.35,206.34) {$h$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (201.93,214.90) --
+	(207.81,214.90);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (205.10,213.80) --
+	(205.10,215.94);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.10,211.99) {$\sigma$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (241.79,242.16) --
+	(243.14,242.16);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (242.48,241.54) --
+	(242.48,242.76);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (242.48,239.25) {$\kappa$};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 49.80) -- (231.49, 49.80);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 49.80) -- (226.02, 49.80);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.22, 49.80) -- ( 95.22, 44.82);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.65, 49.80) -- (140.65, 44.82);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.07, 49.80) -- (186.07, 44.82);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.49, 49.80) -- (231.49, 44.82);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 93.85, 49.80) -- ( 93.85, 44.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (137.91, 49.80) -- (137.91, 44.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.96, 49.80) -- (181.96, 44.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.02, 49.80) -- (226.02, 44.82);
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 95.22, 31.87) {10};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (140.65, 31.87) {100};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (186.07, 31.87) {1000};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (231.49, 31.87) {10000};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 49.80) -- ( 49.80,231.49);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 93.85, 31.87) {10};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (137.91, 31.87) {100};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (181.96, 31.87) {1000};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (226.02, 31.87) {10000};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 49.80) -- ( 49.80,226.02);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 95.22) -- ( 44.82, 95.22);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,140.65) -- ( 44.82,140.65);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,186.07) -- ( 44.82,186.07);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,231.49) -- ( 44.82,231.49);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 93.85) -- ( 44.82, 93.85);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,137.91) -- ( 44.82,137.91);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,181.96) -- ( 44.82,181.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,226.02) -- ( 44.82,226.02);
 
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84, 92.37) {10};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,137.79) {100};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,183.21) {1000};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,228.64) {10000};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84, 91.00) {10};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,135.05) {100};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,179.11) {1000};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,223.16) {10000};
 \end{scope}
@@
 \path[clip] (338.88, 49.80) rectangle (528.36,239.28);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.85, 89.35) -- (428.67, 81.11);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.57, 81.09) -- (516.39, 89.09);
-\definecolor{fillColor}{RGB}{255,0,0}
-
-\path[fill=fillColor] (345.90, 92.78) --
-	(348.41, 88.43) --
-	(343.38, 88.43) --
+\definecolor{fillColor}{RGB}{255,0,109}
+
+\path[fill=fillColor] (485.73,232.77) circle (  1.87);
+
+\path[fill=fillColor] (485.73, 55.06) --
+	(488.24, 50.70) --
+	(483.21, 50.70) --
 	cycle;
-
-\path[fill=fillColor] (433.62, 80.59) circle (  1.87);
-
-\path[fill=fillColor] (521.34, 89.60) circle (  1.87);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.72,134.93) -- (428.80,114.73);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.48,114.58) -- (516.48,132.20);
-\definecolor{fillColor}{RGB}{0,255,0}
-
-\path[fill=fillColor] (345.90,139.09) --
-	(348.41,134.73) --
-	(343.38,134.73) --
+\definecolor{fillColor}{RGB}{0,0,0}
+
+\path[fill=fillColor] (435.32,150.27) circle (  2.15);
+
+\path[fill=fillColor] (435.32,142.15) --
+	(438.21,137.14) --
+	(432.42,137.14) --
 	cycle;
-
-\path[fill=fillColor] (433.62,113.49) circle (  1.87);
-
-\path[fill=fillColor] (521.34,133.30) circle (  1.87);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (349.23,225.52) -- (430.29,135.59);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.56,132.54) -- (516.40,142.76);
-\definecolor{fillColor}{RGB}{255,165,0}
-
-\path[fill=fillColor] (345.90,232.13) --
-	(348.41,227.77) --
-	(343.38,227.77) --
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,146.98) {\texttt{ConstantDistance}};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
+\definecolor{fillColor}{RGB}{143,161,0}
+
+\path[fill=fillColor] (394.78,149.36) circle (  1.87);
+
+\path[fill=fillColor] (394.78, 80.07) --
+	(397.29, 75.72) --
+	(392.26, 75.72) --
 	cycle;
-
-\path[fill=fillColor] (433.62,131.89) circle (  1.87);
-
-\path[fill=fillColor] (521.34,143.41) circle (  1.87);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.88, 71.53) -- (428.64, 69.21);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.60, 69.22) -- (516.36, 71.77);
 \definecolor{fillColor}{RGB}{0,0,0}
 
-\path[fill=fillColor] (345.90, 71.68) circle (  1.87);
-
-\path[fill=fillColor] (433.62, 69.06) circle (  1.87);
-
-\path[fill=fillColor] (521.34, 74.84) --
-	(523.86, 70.48) --
-	(518.83, 70.48) --
+\path[fill=fillColor] (435.32,150.27) circle (  2.15);
+
+\path[fill=fillColor] (435.32,142.15) --
+	(438.21,137.14) --
+	(432.42,137.14) --
 	cycle;
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.48,143.02) -- (429.04,109.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.26,109.56) -- (516.70,139.97);
-\definecolor{fillColor}{RGB}{160,32,240}
-
-\path[fill=fillColor] (345.90,147.87) --
-	(348.41,143.51) --
-	(343.38,143.51) --
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,146.98) {\texttt{ConstantDistance}};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
+\definecolor{fillColor}{RGB}{0,195,0}
+
+\path[fill=fillColor] (390.04,184.14) circle (  1.87);
+
+\path[fill=fillColor] (390.04, 69.81) --
+	(392.55, 65.46) --
+	(387.52, 65.46) --
 	cycle;
-
-\path[fill=fillColor] (433.62,107.76) circle (  1.87);
-
-\path[fill=fillColor] (521.34,141.77) circle (  1.87);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.70,132.99) -- (428.82,111.40);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.60,110.21) -- (516.36,112.45);
-\definecolor{fillColor}{RGB}{0,100,0}
-
-\path[fill=fillColor] (345.90,137.22) --
-	(348.41,132.86) --
-	(343.38,132.86) --
+\definecolor{fillColor}{RGB}{0,0,0}
+
+\path[fill=fillColor] (435.32,150.27) circle (  2.15);
+
+\path[fill=fillColor] (435.32,142.15) --
+	(438.21,137.14) --
+	(432.42,137.14) --
 	cycle;
 
-\path[fill=fillColor] (433.62,110.07) circle (  1.87);
-
-\path[fill=fillColor] (521.34,112.59) circle (  1.87);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (349.79,196.49) -- (429.73,132.52);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (437.55,132.47) -- (517.41,194.71);
-\definecolor{fillColor}{RGB}{0,255,255}
-
-\path[fill=fillColor] (345.90,202.50) --
-	(348.41,198.15) --
-	(343.38,198.15) --
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,146.98) {\texttt{ConstantDistance}};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
+\definecolor{fillColor}{RGB}{0,219,171}
+
+\path[fill=fillColor] (404.25,211.12) circle (  1.87);
+
+\path[fill=fillColor] (404.25, 60.31) --
+	(406.77, 55.95) --
+	(401.74, 55.95) --
 	cycle;
-
-\path[fill=fillColor] (433.62,129.40) circle (  1.87);
-
-\path[fill=fillColor] (521.34,197.77) circle (  1.87);
+\definecolor{fillColor}{RGB}{0,0,0}
+
+\path[fill=fillColor] (435.32,150.27) circle (  2.15);
+
+\path[fill=fillColor] (435.32,142.15) --
+	(438.21,137.14) --
+	(432.42,137.14) --
+	cycle;
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,146.98) {\texttt{ConstantDistance}};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
+\definecolor{fillColor}{RGB}{151,0,255}
+
+\path[fill=fillColor] (433.62,198.59) circle (  1.87);
+
+\path[fill=fillColor] (433.62, 71.59) --
+	(436.14, 67.23) --
+	(431.10, 67.23) --
+	cycle;
+\definecolor{fillColor}{RGB}{0,0,0}
+
+\path[fill=fillColor] (435.32,150.27) circle (  2.15);
+
+\path[fill=fillColor] (435.32,142.15) --
+	(438.21,137.14) --
+	(432.42,137.14) --
+	cycle;
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,146.98) {\texttt{ConstantDistance}};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
+\definecolor{fillColor}{RGB}{255,0,255}
+
+\path[fill=fillColor] (359.72,131.32) circle (  1.87);
+
+\path[fill=fillColor] (359.72, 82.69) --
+	(362.24, 78.34) --
+	(357.21, 78.34) --
+	cycle;
+\definecolor{fillColor}{RGB}{0,0,0}
+
+\path[fill=fillColor] (435.32,150.27) circle (  2.15);
+
+\path[fill=fillColor] (435.32,142.15) --
+	(438.21,137.14) --
+	(432.42,137.14) --
+	cycle;
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,146.98) {\texttt{ConstantDistance}};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
+\definecolor{fillColor}{RGB}{68,68,68}
+
+\path[fill=fillColor] (346.46,125.73) circle (  1.87);
+
+\path[fill=fillColor] (346.46, 76.98) --
+	(348.97, 72.63) --
+	(343.94, 72.63) --
+	cycle;
+\definecolor{fillColor}{RGB}{0,0,0}
+
+\path[fill=fillColor] (435.32,150.27) circle (  2.15);
+
+\path[fill=fillColor] (435.32,142.15) --
+	(438.21,137.14) --
+	(432.42,137.14) --
+	cycle;
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,146.98) {\texttt{ConstantDistance}};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,113.48) --
+	(339.26,113.88) --
+	(339.64,114.28) --
+	(340.02,114.68) --
+	(340.40,115.09) --
+	(340.78,115.49) --
+	(341.16,115.90) --
+	(341.54,116.31) --
+	(341.92,116.71) --
+	(342.30,117.12) --
+	(342.68,117.53) --
+	(343.06,117.95) --
+	(343.44,118.36) --
+	(343.82,118.77) --
+	(344.20,119.19) --
+	(344.58,119.60) --
+	(344.96,120.02) --
+	(345.34,120.44) --
+	(345.71,120.86) --
+	(346.09,121.28) --
+	(346.47,121.70) --
+	(346.85,122.12) --
+	(347.23,122.55) --
+	(347.61,122.97) --
+	(347.99,123.39) --
+	(348.37,123.82) --
+	(348.75,124.25) --
+	(349.13,124.67) --
+	(349.51,125.10) --
+	(349.89,125.53) --
+	(350.27,125.96) --
+	(350.65,126.39) --
+	(351.03,126.83) --
+	(351.41,127.26) --
+	(351.79,127.69) --
+	(352.17,128.12) --
+	(352.55,128.56) --
+	(352.93,128.99) --
+	(353.31,129.43) --
+	(353.69,129.87) --
+	(354.07,130.30) --
+	(354.45,130.74) --
+	(354.83,131.18) --
+	(355.21,131.62) --
+	(355.59,132.06) --
+	(355.97,132.50) --
+	(356.35,132.94) --
+	(356.73,133.38) --
+	(357.11,133.82) --
+	(357.49,134.27) --
+	(357.87,134.71) --
+	(358.25,135.15) --
+	(358.63,135.60) --
+	(359.01,136.04) --
+	(359.38,136.48) --
+	(359.76,136.93) --
+	(360.14,137.37) --
+	(360.52,137.82) --
+	(360.90,138.26) --
+	(361.28,138.71) --
+	(361.66,139.16) --
+	(362.04,139.60) --
+	(362.42,140.05) --
+	(362.80,140.50) --
+	(363.18,140.94) --
+	(363.56,141.39) --
+	(363.94,141.84) --
+	(364.32,142.28) --
+	(364.70,142.73) --
+	(365.08,143.18) --
+	(365.46,143.63) --
+	(365.84,144.08) --
+	(366.22,144.52) --
+	(366.60,144.97) --
+	(366.98,145.42) --
+	(367.36,145.87) --
+	(367.74,146.31) --
+	(368.12,146.76) --
+	(368.50,147.21) --
+	(368.88,147.66) --
+	(369.26,148.10) --
+	(369.64,148.55) --
+	(370.02,149.00) --
+	(370.40,149.44) --
+	(370.78,149.89) --
+	(371.16,150.34) --
+	(371.54,150.78) --
+	(371.92,151.23) --
+	(372.30,151.67) --
+	(372.68,152.12) --
+	(373.05,152.56) --
+	(373.43,153.01) --
+	(373.81,153.45) --
+	(374.19,153.89) --
+	(374.57,154.34) --
+	(374.95,154.78) --
+	(375.33,155.22) --
+	(375.71,155.66) --
+	(376.09,156.11) --
+	(376.47,156.55) --
+	(376.85,156.99) --
+	(377.23,157.43) --
+	(377.61,157.87) --
+	(377.99,158.30) --
+	(378.37,158.74) --
+	(378.75,159.18) --
+	(379.13,159.62) --
+	(379.51,160.05) --
+	(379.89,160.49) --
+	(380.27,160.92) --
+	(380.65,161.36) --
+	(381.03,161.79) --
+	(381.41,162.22) --
+	(381.79,162.65) --
+	(382.17,163.08) --
+	(382.55,163.51) --
+	(382.93,163.94) --
+	(383.31,164.37) --
+	(383.69,164.80) --
+	(384.07,165.23) --
+	(384.45,165.65) --
+	(384.83,166.08) --
+	(385.21,166.50) --
+	(385.59,166.93) --
+	(385.97,167.35) --
+	(386.34,167.77) --
+	(386.72,168.19) --
+	(387.10,168.61) --
+	(387.48,169.03) --
+	(387.86,169.44) --
+	(388.24,169.86) --
+	(388.62,170.28) --
+	(389.00,170.69) --
+	(389.38,171.10) --
+	(389.76,171.51) --
+	(390.14,171.93) --
+	(390.52,172.34) --
+	(390.90,172.74) --
+	(391.28,173.15) --
+	(391.66,173.56) --
+	(392.04,173.96) --
+	(392.42,174.37) --
+	(392.80,174.77) --
+	(393.18,175.17) --
+	(393.56,175.57) --
+	(393.94,175.97) --
+	(394.32,176.37) --
+	(394.70,176.76) --
+	(395.08,177.16) --
+	(395.46,177.55) --
+	(395.84,177.95) --
+	(396.22,178.34) --
+	(396.60,178.73) --
+	(396.98,179.12) --
+	(397.36,179.50) --
+	(397.74,179.89) --
+	(398.12,180.27) --
+	(398.50,180.66) --
+	(398.88,181.04) --
+	(399.26,181.42) --
+	(399.64,181.80) --
+	(400.01,182.18) --
+	(400.39,182.55) --
+	(400.77,182.93) --
+	(401.15,183.30) --
+	(401.53,183.67) --
+	(401.91,184.05) --
+	(402.29,184.41) --
+	(402.67,184.78) --
+	(403.05,185.15) --
+	(403.43,185.51) --
+	(403.81,185.88) --
+	(404.19,186.24) --
+	(404.57,186.60) --
+	(404.95,186.96) --
+	(405.33,187.31) --
+	(405.71,187.67) --
+	(406.09,188.02) --
+	(406.47,188.38) --
+	(406.85,188.73) --
+	(407.23,189.08) --
+	(407.61,189.43) --
+	(407.99,189.77) --
+	(408.37,190.12) --
+	(408.75,190.46) --
+	(409.13,190.80) --
+	(409.51,191.14) --
+	(409.89,191.48) --
+	(410.27,191.82) --
+	(410.65,192.15) --
+	(411.03,192.49) --
+	(411.41,192.82) --
+	(411.79,193.15) --
+	(412.17,193.48) --
+	(412.55,193.81) --
+	(412.93,194.13) --
+	(413.31,194.46) --
+	(413.68,194.78) --
+	(414.06,195.10) --
+	(414.44,195.42) --
+	(414.82,195.74) --
+	(415.20,196.05) --
+	(415.58,196.37) --
+	(415.96,196.68) --
+	(416.34,196.99) --
+	(416.72,197.30) --
+	(417.10,197.61) --
+	(417.48,197.92) --
+	(417.86,198.22) --
+	(418.24,198.52) --
+	(418.62,198.83) --
+	(419.00,199.13) --
+	(419.38,199.42) --
+	(419.76,199.72) --
+	(420.14,200.02) --
+	(420.52,200.31) --
+	(420.90,200.60) --
+	(421.28,200.89) --
+	(421.66,201.18) --
+	(422.04,201.47) --
+	(422.42,201.75) --
+	(422.80,202.03) --
+	(423.18,202.32) --
+	(423.56,202.60) --
+	(423.94,202.88) --
+	(424.32,203.15) --
+	(424.70,203.43) --
+	(425.08,203.70) --
+	(425.46,203.97) --
+	(425.84,204.25) --
+	(426.22,204.51) --
+	(426.60,204.78) --
+	(426.97,205.05) --
+	(427.35,205.31) --
+	(427.73,205.58) --
+	(428.11,205.84) --
+	(428.49,206.10) --
+	(428.87,206.35) --
+	(429.25,206.61) --
+	(429.63,206.86) --
+	(430.01,207.12) --
+	(430.39,207.37) --
+	(430.77,207.62) --
+	(431.15,207.87) --
+	(431.53,208.11) --
+	(431.91,208.36) --
+	(432.29,208.60) --
+	(432.67,208.85) --
+	(433.05,209.09) --
+	(433.43,209.33) --
+	(433.81,209.56) --
+	(434.19,209.80) --
+	(434.57,210.03) --
+	(434.95,210.27) --
+	(435.33,210.50) --
+	(435.71,210.73) --
+	(436.09,210.96) --
+	(436.47,211.18) --
+	(436.85,211.41) --
+	(437.23,211.63) --
+	(437.61,211.86) --
+	(437.99,212.08) --
+	(438.37,212.30) --
+	(438.75,212.51) --
+	(439.13,212.73) --
+	(439.51,212.95) --
+	(439.89,213.16) --
+	(440.27,213.37) --
+	(440.64,213.58) --
+	(441.02,213.79) --
+	(441.40,214.00) --
+	(441.78,214.21) --
+	(442.16,214.41) --
+	(442.54,214.61) --
+	(442.92,214.82) --
+	(443.30,215.02) --
+	(443.68,215.22) --
+	(444.06,215.41) --
+	(444.44,215.61) --
+	(444.82,215.81) --
+	(445.20,216.00) --
+	(445.58,216.19) --
+	(445.96,216.38) --
+	(446.34,216.57) --
+	(446.72,216.76) --
+	(447.10,216.95) --
+	(447.48,217.13) --
+	(447.86,217.32) --
+	(448.24,217.50) --
+	(448.62,217.68) --
+	(449.00,217.86) --
+	(449.38,218.04) --
+	(449.76,218.22) --
+	(450.14,218.39) --
+	(450.52,218.57) --
+	(450.90,218.74) --
+	(451.28,218.91) --
+	(451.66,219.09) --
+	(452.04,219.26) --
+	(452.42,219.42) --
+	(452.80,219.59) --
+	(453.18,219.76) --
+	(453.56,219.92) --
+	(453.93,220.09) --
+	(454.31,220.25) --
+	(454.69,220.41) --
+	(455.07,220.57) --
+	(455.45,220.73) --
+	(455.83,220.89) --
+	(456.21,221.04) --
+	(456.59,221.20) --
+	(456.97,221.35) --
+	(457.35,221.50) --
+	(457.73,221.66) --
+	(458.11,221.81) --
+	(458.49,221.96) --
+	(458.87,222.10) --
+	(459.25,222.25) --
+	(459.63,222.40) --
+	(460.01,222.54) --
+	(460.39,222.69) --
+	(460.77,222.83) --
+	(461.15,222.97) --
+	(461.53,223.11) --
+	(461.91,223.25) --
+	(462.29,223.39) --
+	(462.67,223.52) --
+	(463.05,223.66) --
+	(463.43,223.80) --
+	(463.81,223.93) --
+	(464.19,224.06) --
+	(464.57,224.19) --
+	(464.95,224.32) --
+	(465.33,224.45) --
+	(465.71,224.58) --
+	(466.09,224.71) --
+	(466.47,224.84) --
+	(466.85,224.96) --
+	(467.23,225.09) --
+	(467.60,225.21) --
+	(467.98,225.33) --
+	(468.36,225.46) --
+	(468.74,225.58) --
+	(469.12,225.70) --
+	(469.50,225.81) --
+	(469.88,225.93) --
+	(470.26,226.05) --
+	(470.64,226.16) --
+	(471.02,226.28) --
+	(471.40,226.39) --
+	(471.78,226.51) --
+	(472.16,226.62) --
+	(472.54,226.73) --
+	(472.92,226.84) --
+	(473.30,226.95) --
+	(473.68,227.06) --
+	(474.06,227.17) --
+	(474.44,227.27) --
+	(474.82,227.38) --
+	(475.20,227.48) --
+	(475.58,227.59) --
+	(475.96,227.69) --
+	(476.34,227.79) --
+	(476.72,227.89) --
+	(477.10,228.00) --
+	(477.48,228.10) --
+	(477.86,228.19) --
+	(478.24,228.29) --
+	(478.62,228.39) --
+	(479.00,228.49) --
+	(479.38,228.58) --
+	(479.76,228.68) --
+	(480.14,228.77) --
+	(480.52,228.87) --
+	(480.90,228.96) --
+	(481.27,229.05) --
+	(481.65,229.14) --
+	(482.03,229.23) --
+	(482.41,229.32) --
+	(482.79,229.41) --
+	(483.17,229.50) --
+	(483.55,229.58) --
+	(483.93,229.67) --
+	(484.31,229.76) --
+	(484.69,229.84) --
+	(485.07,229.93) --
+	(485.45,230.01) --
+	(485.83,230.09) --
+	(486.21,230.18) --
+	(486.59,230.26) --
+	(486.97,230.34) --
+	(487.35,230.42) --
+	(487.73,230.50) --
+	(488.11,230.58) --
+	(488.49,230.65) --
+	(488.87,230.73) --
+	(489.25,230.81) --
+	(489.63,230.89) --
+	(490.01,230.96) --
+	(490.39,231.04) --
+	(490.77,231.11) --
+	(491.15,231.18) --
+	(491.53,231.26) --
+	(491.91,231.33) --
+	(492.29,231.40) --
+	(492.67,231.47) --
+	(493.05,231.54) --
+	(493.43,231.61) --
+	(493.81,231.68) --
+	(494.19,231.75) --
+	(494.56,231.82) --
+	(494.94,231.89) --
+	(495.32,231.95) --
+	(495.70,232.02) --
+	(496.08,232.08) --
+	(496.46,232.15) --
+	(496.84,232.21) --
+	(497.22,232.28) --
+	(497.60,232.34) --
+	(497.98,232.40) --
+	(498.36,232.47) --
+	(498.74,232.53) --
+	(499.12,232.59) --
+	(499.50,232.65) --
+	(499.88,232.71) --
+	(500.26,232.77) --
+	(500.64,232.83) --
+	(501.02,232.89) --
+	(501.40,232.95) --
+	(501.78,233.00) --
+	(502.16,233.06) --
+	(502.54,233.12) --
+	(502.92,233.17) --
+	(503.30,233.23) --
+	(503.68,233.28) --
+	(504.06,233.34) --
+	(504.44,233.39) --
+	(504.82,233.45) --
+	(505.20,233.50) --
+	(505.58,233.55) --
+	(505.96,233.60) --
+	(506.34,233.66) --
+	(506.72,233.71) --
+	(507.10,233.76) --
+	(507.48,233.81) --
+	(507.86,233.86) --
+	(508.23,233.91) --
+	(508.61,233.96) --
+	(508.99,234.01) --
+	(509.37,234.05) --
+	(509.75,234.10) --
+	(510.13,234.15) --
+	(510.51,234.20) --
+	(510.89,234.24) --
+	(511.27,234.29) --
+	(511.65,234.34) --
+	(512.03,234.38) --
+	(512.41,234.43) --
+	(512.79,234.47) --
+	(513.17,234.51) --
+	(513.55,234.56) --
+	(513.93,234.60) --
+	(514.31,234.64) --
+	(514.69,234.69) --
+	(515.07,234.73) --
+	(515.45,234.77) --
+	(515.83,234.81) --
+	(516.21,234.85) --
+	(516.59,234.89) --
+	(516.97,234.93) --
+	(517.35,234.97) --
+	(517.73,235.01) --
+	(518.11,235.05) --
+	(518.49,235.09) --
+	(518.87,235.13) --
+	(519.25,235.17) --
+	(519.63,235.21) --
+	(520.01,235.24) --
+	(520.39,235.28) --
+	(520.77,235.32) --
+	(521.15,235.35) --
+	(521.53,235.39) --
+	(521.90,235.43) --
+	(522.28,235.46) --
+	(522.66,235.50) --
+	(523.04,235.53) --
+	(523.42,235.57) --
+	(523.80,235.60) --
+	(524.18,235.63) --
+	(524.56,235.67) --
+	(524.94,235.70) --
+	(525.32,235.73) --
+	(525.70,235.77) --
+	(526.08,235.80) --
+	(526.46,235.83) --
+	(526.84,235.86) --
+	(527.22,235.90) --
+	(527.60,235.93) --
+	(527.98,235.96) --
+	(528.36,235.99);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 82.37) --
+	(339.26, 82.25) --
+	(339.64, 82.13) --
+	(340.02, 82.00) --
+	(340.40, 81.88) --
+	(340.78, 81.75) --
+	(341.16, 81.63) --
+	(341.54, 81.51) --
+	(341.92, 81.39) --
+	(342.30, 81.27) --
+	(342.68, 81.14) --
+	(343.06, 81.02) --
+	(343.44, 80.90) --
+	(343.82, 80.78) --
+	(344.20, 80.66) --
+	(344.58, 80.54) --
+	(344.96, 80.42) --
+	(345.34, 80.31) --
+	(345.71, 80.19) --
+	(346.09, 80.07) --
+	(346.47, 79.95) --
+	(346.85, 79.83) --
+	(347.23, 79.72) --
+	(347.61, 79.60) --
+	(347.99, 79.48) --
+	(348.37, 79.37) --
+	(348.75, 79.25) --
+	(349.13, 79.14) --
+	(349.51, 79.02) --
+	(349.89, 78.91) --
+	(350.27, 78.80) --
+	(350.65, 78.68) --
+	(351.03, 78.57) --
+	(351.41, 78.46) --
+	(351.79, 78.34) --
+	(352.17, 78.23) --
+	(352.55, 78.12) --
+	(352.93, 78.01) --
+	(353.31, 77.90) --
+	(353.69, 77.79) --
+	(354.07, 77.68) --
+	(354.45, 77.57) --
+	(354.83, 77.46) --
+	(355.21, 77.35) --
+	(355.59, 77.24) --
+	(355.97, 77.13) --
+	(356.35, 77.02) --
+	(356.73, 76.91) --
+	(357.11, 76.81) --
+	(357.49, 76.70) --
+	(357.87, 76.59) --
+	(358.25, 76.49) --
+	(358.63, 76.38) --
+	(359.01, 76.28) --
+	(359.38, 76.17) --
+	(359.76, 76.07) --
+	(360.14, 75.96) --
+	(360.52, 75.86) --
+	(360.90, 75.75) --
+	(361.28, 75.65) --
+	(361.66, 75.55) --
+	(362.04, 75.44) --
+	(362.42, 75.34) --
+	(362.80, 75.24) --
+	(363.18, 75.14) --
+	(363.56, 75.04) --
+	(363.94, 74.93) --
+	(364.32, 74.83) --
+	(364.70, 74.73) --
+	(365.08, 74.63) --
+	(365.46, 74.53) --
+	(365.84, 74.43) --
+	(366.22, 74.33) --
+	(366.60, 74.24) --
+	(366.98, 74.14) --
+	(367.36, 74.04) --
+	(367.74, 73.94) --
+	(368.12, 73.84) --
+	(368.50, 73.75) --
+	(368.88, 73.65) --
+	(369.26, 73.55) --
+	(369.64, 73.46) --
+	(370.02, 73.36) --
+	(370.40, 73.27) --
+	(370.78, 73.17) --
+	(371.16, 73.08) --
+	(371.54, 72.98) --
+	(371.92, 72.89) --
+	(372.30, 72.80) --
+	(372.68, 72.70) --
+	(373.05, 72.61) --
+	(373.43, 72.52) --
+	(373.81, 72.42) --
+	(374.19, 72.33) --
+	(374.57, 72.24) --
+	(374.95, 72.15) --
+	(375.33, 72.06) --
+	(375.71, 71.97) --
+	(376.09, 71.88) --
+	(376.47, 71.79) --
+	(376.85, 71.70) --
+	(377.23, 71.61) --
+	(377.61, 71.52) --
+	(377.99, 71.43) --
+	(378.37, 71.34) --
+	(378.75, 71.25) --
+	(379.13, 71.16) --
+	(379.51, 71.08) --
+	(379.89, 70.99) --
+	(380.27, 70.90) --
+	(380.65, 70.82) --
+	(381.03, 70.73) --
+	(381.41, 70.64) --
+	(381.79, 70.56) --
+	(382.17, 70.47) --
+	(382.55, 70.39) --
+	(382.93, 70.30) --
+	(383.31, 70.22) --
+	(383.69, 70.13) --
+	(384.07, 70.05) --
+	(384.45, 69.97) --
+	(384.83, 69.88) --
+	(385.21, 69.80) --
+	(385.59, 69.72) --
+	(385.97, 69.63) --
+	(386.34, 69.55) --
+	(386.72, 69.47) --
+	(387.10, 69.39) --
+	(387.48, 69.31) --
+	(387.86, 69.23) --
+	(388.24, 69.15) --
+	(388.62, 69.07) --
+	(389.00, 68.99) --
+	(389.38, 68.91) --
+	(389.76, 68.83) --
+	(390.14, 68.75) --
+	(390.52, 68.67) --
+	(390.90, 68.59) --
+	(391.28, 68.51) --
+	(391.66, 68.43) --
+	(392.04, 68.36) --
+	(392.42, 68.28) --
+	(392.80, 68.20) --
+	(393.18, 68.13) --
+	(393.56, 68.05) --
+	(393.94, 67.97) --
+	(394.32, 67.90) --
+	(394.70, 67.82) --
+	(395.08, 67.75) --
+	(395.46, 67.67) --
+	(395.84, 67.60) --
+	(396.22, 67.52) --
+	(396.60, 67.45) --
+	(396.98, 67.37) --
+	(397.36, 67.30) --
+	(397.74, 67.23) --
+	(398.12, 67.15) --
+	(398.50, 67.08) --
+	(398.88, 67.01) --
+	(399.26, 66.94) --
+	(399.64, 66.86) --
+	(400.01, 66.79) --
+	(400.39, 66.72) --
+	(400.77, 66.65) --
+	(401.15, 66.58) --
+	(401.53, 66.51) --
+	(401.91, 66.44) --
+	(402.29, 66.37) --
+	(402.67, 66.30) --
+	(403.05, 66.23) --
+	(403.43, 66.16) --
+	(403.81, 66.09) --
+	(404.19, 66.02) --
+	(404.57, 65.95) --
+	(404.95, 65.88) --
+	(405.33, 65.81) --
+	(405.71, 65.75) --
+	(406.09, 65.68) --
+	(406.47, 65.61) --
+	(406.85, 65.55) --
+	(407.23, 65.48) --
+	(407.61, 65.41) --
+	(407.99, 65.35) --
+	(408.37, 65.28) --
+	(408.75, 65.21) --
+	(409.13, 65.15) --
+	(409.51, 65.08) --
+	(409.89, 65.02) --
+	(410.27, 64.95) --
+	(410.65, 64.89) --
+	(411.03, 64.83) --
+	(411.41, 64.76) --
+	(411.79, 64.70) --
+	(412.17, 64.63) --
+	(412.55, 64.57) --
+	(412.93, 64.51) --
+	(413.31, 64.45) --
+	(413.68, 64.38) --
+	(414.06, 64.32) --
+	(414.44, 64.26) --
+	(414.82, 64.20) --
+	(415.20, 64.14) --
+	(415.58, 64.07) --
+	(415.96, 64.01) --
+	(416.34, 63.95) --
+	(416.72, 63.89) --
+	(417.10, 63.83) --
+	(417.48, 63.77) --
+	(417.86, 63.71) --
+	(418.24, 63.65) --
+	(418.62, 63.59) --
+	(419.00, 63.53) --
+	(419.38, 63.48) --
+	(419.76, 63.42) --
+	(420.14, 63.36) --
+	(420.52, 63.30) --
+	(420.90, 63.24) --
+	(421.28, 63.18) --
+	(421.66, 63.13) --
+	(422.04, 63.07) --
+	(422.42, 63.01) --
+	(422.80, 62.96) --
+	(423.18, 62.90) --
+	(423.56, 62.84) --
+	(423.94, 62.79) --
+	(424.32, 62.73) --
+	(424.70, 62.68) --
+	(425.08, 62.62) --
+	(425.46, 62.56) --
+	(425.84, 62.51) --
+	(426.22, 62.45) --
+	(426.60, 62.40) --
+	(426.97, 62.35) --
+	(427.35, 62.29) --
+	(427.73, 62.24) --
+	(428.11, 62.18) --
+	(428.49, 62.13) --
+	(428.87, 62.08) --
+	(429.25, 62.02) --
+	(429.63, 61.97) --
+	(430.01, 61.92) --
+	(430.39, 61.87) --
+	(430.77, 61.81) --
+	(431.15, 61.76) --
+	(431.53, 61.71) --
+	(431.91, 61.66) --
+	(432.29, 61.61) --
+	(432.67, 61.56) --
+	(433.05, 61.51) --
+	(433.43, 61.45) --
+	(433.81, 61.40) --
+	(434.19, 61.35) --
+	(434.57, 61.30) --
+	(434.95, 61.25) --
+	(435.33, 61.20) --
+	(435.71, 61.15) --
+	(436.09, 61.10) --
+	(436.47, 61.06) --
+	(436.85, 61.01) --
+	(437.23, 60.96) --
+	(437.61, 60.91) --
+	(437.99, 60.86) --
+	(438.37, 60.81) --
+	(438.75, 60.77) --
+	(439.13, 60.72) --
+	(439.51, 60.67) --
+	(439.89, 60.62) --
+	(440.27, 60.58) --
+	(440.64, 60.53) --
+	(441.02, 60.48) --
+	(441.40, 60.44) --
+	(441.78, 60.39) --
+	(442.16, 60.34) --
+	(442.54, 60.30) --
+	(442.92, 60.25) --
+	(443.30, 60.21) --
+	(443.68, 60.16) --
+	(444.06, 60.11) --
+	(444.44, 60.07) --
+	(444.82, 60.02) --
+	(445.20, 59.98) --
+	(445.58, 59.94) --
+	(445.96, 59.89) --
+	(446.34, 59.85) --
+	(446.72, 59.80) --
+	(447.10, 59.76) --
+	(447.48, 59.72) --
+	(447.86, 59.67) --
+	(448.24, 59.63) --
+	(448.62, 59.59) --
+	(449.00, 59.54) --
+	(449.38, 59.50) --
+	(449.76, 59.46) --
+	(450.14, 59.42) --
+	(450.52, 59.37) --
+	(450.90, 59.33) --
+	(451.28, 59.29) --
+	(451.66, 59.25) --
+	(452.04, 59.21) --
+	(452.42, 59.16) --
+	(452.80, 59.12) --
+	(453.18, 59.08) --
+	(453.56, 59.04) --
+	(453.93, 59.00) --
+	(454.31, 58.96) --
+	(454.69, 58.92) --
+	(455.07, 58.88) --
+	(455.45, 58.84) --
+	(455.83, 58.80) --
+	(456.21, 58.76) --
+	(456.59, 58.72) --
+	(456.97, 58.68) --
+	(457.35, 58.64) --
+	(457.73, 58.60) --
+	(458.11, 58.57) --
+	(458.49, 58.53) --
+	(458.87, 58.49) --
+	(459.25, 58.45) --
+	(459.63, 58.41) --
+	(460.01, 58.37) --
+	(460.39, 58.34) --
+	(460.77, 58.30) --
+	(461.15, 58.26) --
+	(461.53, 58.22) --
+	(461.91, 58.19) --
+	(462.29, 58.15) --
+	(462.67, 58.11) --
+	(463.05, 58.08) --
+	(463.43, 58.04) --
+	(463.81, 58.00) --
+	(464.19, 57.97) --
+	(464.57, 57.93) --
+	(464.95, 57.89) --
+	(465.33, 57.86) --
+	(465.71, 57.82) --
+	(466.09, 57.79) --
+	(466.47, 57.75) --
+	(466.85, 57.72) --
+	(467.23, 57.68) --
+	(467.60, 57.65) --
+	(467.98, 57.61) --
+	(468.36, 57.58) --
+	(468.74, 57.54) --
+	(469.12, 57.51) --
+	(469.50, 57.47) --
+	(469.88, 57.44) --
+	(470.26, 57.41) --
+	(470.64, 57.37) --
+	(471.02, 57.34) --
+	(471.40, 57.31) --
+	(471.78, 57.27) --
+	(472.16, 57.24) --
+	(472.54, 57.21) --
+	(472.92, 57.17) --
+	(473.30, 57.14) --
+	(473.68, 57.11) --
+	(474.06, 57.08) --
+	(474.44, 57.04) --
+	(474.82, 57.01) --
+	(475.20, 56.98) --
+	(475.58, 56.95) --
+	(475.96, 56.92) --
+	(476.34, 56.88) --
+	(476.72, 56.85) --
+	(477.10, 56.82) --
+	(477.48, 56.79) --
+	(477.86, 56.76) --
+	(478.24, 56.73) --
+	(478.62, 56.70) --
+	(479.00, 56.67) --
+	(479.38, 56.64) --
+	(479.76, 56.61) --
+	(480.14, 56.57) --
+	(480.52, 56.54) --
+	(480.90, 56.51) --
+	(481.27, 56.48) --
+	(481.65, 56.45) --
+	(482.03, 56.43) --
+	(482.41, 56.40) --
+	(482.79, 56.37) --
+	(483.17, 56.34) --
+	(483.55, 56.31) --
+	(483.93, 56.28) --
+	(484.31, 56.25) --
+	(484.69, 56.22) --
+	(485.07, 56.19) --
+	(485.45, 56.16) --
+	(485.83, 56.14) --
+	(486.21, 56.11) --
+	(486.59, 56.08) --
+	(486.97, 56.05) --
+	(487.35, 56.02) --
+	(487.73, 56.00) --
+	(488.11, 55.97) --
+	(488.49, 55.94) --
+	(488.87, 55.91) --
+	(489.25, 55.89) --
+	(489.63, 55.86) --
+	(490.01, 55.83) --
+	(490.39, 55.80) --
+	(490.77, 55.78) --
+	(491.15, 55.75) --
+	(491.53, 55.72) --
+	(491.91, 55.70) --
+	(492.29, 55.67) --
+	(492.67, 55.64) --
+	(493.05, 55.62) --
+	(493.43, 55.59) --
+	(493.81, 55.57) --
+	(494.19, 55.54) --
+	(494.56, 55.51) --
+	(494.94, 55.49) --
+	(495.32, 55.46) --
+	(495.70, 55.44) --
+	(496.08, 55.41) --
+	(496.46, 55.39) --
+	(496.84, 55.36) --
+	(497.22, 55.34) --
+	(497.60, 55.31) --
+	(497.98, 55.29) --
+	(498.36, 55.26) --
+	(498.74, 55.24) --
+	(499.12, 55.21) --
+	(499.50, 55.19) --
+	(499.88, 55.17) --
+	(500.26, 55.14) --
+	(500.64, 55.12) --
+	(501.02, 55.09) --
+	(501.40, 55.07) --
+	(501.78, 55.05) --
+	(502.16, 55.02) --
+	(502.54, 55.00) --
+	(502.92, 54.98) --
+	(503.30, 54.95) --
+	(503.68, 54.93) --
+	(504.06, 54.91) --
+	(504.44, 54.88) --
+	(504.82, 54.86) --
+	(505.20, 54.84) --
+	(505.58, 54.82) --
+	(505.96, 54.79) --
+	(506.34, 54.77) --
+	(506.72, 54.75) --
+	(507.10, 54.73) --
+	(507.48, 54.70) --
+	(507.86, 54.68) --
+	(508.23, 54.66) --
+	(508.61, 54.64) --
+	(508.99, 54.62) --
+	(509.37, 54.59) --
+	(509.75, 54.57) --
+	(510.13, 54.55) --
+	(510.51, 54.53) --
+	(510.89, 54.51) --
+	(511.27, 54.49) --
+	(511.65, 54.47) --
+	(512.03, 54.45) --
+	(512.41, 54.42) --
+	(512.79, 54.40) --
+	(513.17, 54.38) --
+	(513.55, 54.36) --
+	(513.93, 54.34) --
+	(514.31, 54.32) --
+	(514.69, 54.30) --
+	(515.07, 54.28) --
+	(515.45, 54.26) --
+	(515.83, 54.24) --
+	(516.21, 54.22) --
+	(516.59, 54.20) --
+	(516.97, 54.18) --
+	(517.35, 54.16) --
+	(517.73, 54.14) --
+	(518.11, 54.12) --
+	(518.49, 54.10) --
+	(518.87, 54.08) --
+	(519.25, 54.06) --
+	(519.63, 54.04) --
+	(520.01, 54.02) --
+	(520.39, 54.01) --
+	(520.77, 53.99) --
+	(521.15, 53.97) --
+	(521.53, 53.95) --
+	(521.90, 53.93) --
+	(522.28, 53.91) --
+	(522.66, 53.89) --
+	(523.04, 53.87) --
+	(523.42, 53.86) --
+	(523.80, 53.84) --
+	(524.18, 53.82) --
+	(524.56, 53.80) --
+	(524.94, 53.78) --
+	(525.32, 53.76) --
+	(525.70, 53.75) --
+	(526.08, 53.73) --
+	(526.46, 53.71) --
+	(526.84, 53.69) --
+	(527.22, 53.68) --
+	(527.60, 53.66) --
+	(527.98, 53.64) --
+	(528.36, 53.62);
 \end{scope}

### 2020-08-24 benchmarking/benchmarkingVM/ESS_round2.tex
results update

@@
-% Created by tikzDevice version 0.12.3 on 2020-08-10 16:04:21
+% Created by tikzDevice version 0.12.3.1 on 2020-08-24 19:04:48
 % !TEX encoding = UTF-8 Unicode
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,301.03) {ESS/hr [adapt (\textit{cat})]};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,433.62) {ESS/hr [adapt (\textit{real})]};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,301.03) {ESS/chain [adapt (\textit{cat})]};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,433.62) {ESS/chain [adapt (\textit{real})]};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 96.83,462.17) --
-	(104.39,462.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.95,455.39) --
-	(100.95,467.26);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (100.95,458.94) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (157.25,462.51) --
-	(190.79,462.51);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.21,460.09) --
-	(180.21,464.68);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.21,458.48) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.00,476.56) --
-	(103.04,476.56);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.41,475.30) --
-	( 99.41,477.74);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 99.41,472.52) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.19,434.62) --
-	(105.17,434.62);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (102.83,423.86) --
-	(102.83,441.65);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (102.83,430.59) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.73,464.74) --
-	( 95.52,464.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 90.46,459.17) --
-	( 90.46,469.12);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 90.46,461.83) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.57,483.53) --
-	(194.99,483.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.78,482.91) --
-	(194.78,484.13);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.78,480.62) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.61,467.01) --
-	(116.13,467.01);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.49,464.26) --
-	(109.49,469.44);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (109.49,463.79) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.07,471.07) --
-	(193.44,471.07);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.83,468.87) --
-	(191.83,473.05);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.83,467.03) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (164.54,476.74) --
-	(164.84,476.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (164.69,476.63) --
-	(164.69,476.85);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (164.69,472.71) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.97,429.18) --
-	(112.07,429.18);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (107.26,425.26) --
-	(107.26,432.48);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (107.26,425.15) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (103.25,451.88) --
-	(115.87,451.88);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (110.51,447.05) --
-	(110.51,455.79);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (110.51,448.98) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.12,485.74) --
-	(196.43,485.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.27,485.16) --
-	(196.27,486.31);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.27,482.84) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.15,474.71) --
-	(181.63,474.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.43,471.39) --
-	(177.43,477.57);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.43,471.49) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.21,475.71) --
-	(184.09,475.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.98,464.98) --
-	(174.98,482.73);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.98,471.68) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.98,485.03) --
-	(197.78,485.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.38,484.42) --
-	(197.38,485.62);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.38,481.00) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (150.24,443.07) --
-	(164.70,443.07);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.71,436.47) --
-	(158.71,448.06);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.71,439.03) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (178.58,473.47) --
-	(182.90,473.47);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.86,467.70) --
-	(180.86,477.96);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.86,470.56) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.48,498.31) --
-	(212.33,498.31);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.49,497.03) --
-	(210.49,499.52);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.49,495.41) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (122.95,491.83) --
+	(140.70,491.83);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (133.81,484.91) --
+	(133.81,496.90);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (133.81,488.60) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (166.42,515.48) --
+	(192.82,515.48);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.86,513.46) --
+	(183.86,517.31);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.86,511.45) {$L$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (125.62,508.15) --
+	(135.84,508.15);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (131.41,507.02) --
+	(131.41,509.22);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (131.41,504.12) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (121.05,469.50) --
+	(140.40,469.50);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (133.07,459.30) --
+	(133.07,476.12);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (133.07,465.47) {$h$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 99.96,494.88) --
+	(111.88,494.88);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (106.84,490.31) --
+	(106.84,498.58);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (106.84,491.98) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (225.34,514.73) --
+	(225.72,514.73);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (225.53,514.21) --
+	(225.53,515.24);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (225.53,511.83) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (212.35,504.78) --
+	(215.34,504.78);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (213.90,504.07) --
+	(213.90,505.47);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (213.90,501.56) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.49,483.32) --
+	(194.82,483.32);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.69,482.10) --
+	(193.69,484.46);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.69,479.28) {$L$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (220.02,513.50) --
+	(220.41,513.50);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (220.22,513.33) --
+	(220.22,513.67);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.22,509.47) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (203.33,494.70) --
+	(208.29,494.70);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (205.97,493.28) --
+	(205.97,496.02);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.97,490.67) {$h$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (213.02,506.61) --
+	(215.41,506.61);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (214.26,505.81) --
+	(214.26,507.37);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (214.26,503.70) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (224.23,514.56) --
+	(225.66,514.56);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (224.96,514.31) --
+	(224.96,514.81);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (224.96,511.66) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.61,479.81) --
+	(191.86,479.81);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.86,477.75) --
+	(189.86,481.67);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (189.86,476.59) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (201.42,492.07) --
+	(204.91,492.07);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (203.25,485.78) --
+	(203.25,496.80);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (203.25,488.04) {$L$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (223.97,518.14) --
+	(225.03,518.14);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (224.51,517.82) --
+	(224.51,518.45);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (224.51,514.11) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.49,451.61) --
+	(178.92,451.61);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.40,449.07) --
+	(174.40,453.85);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.40,447.57) {$h$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.96,475.67) --
+	(185.10,475.67);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.70,472.24) --
+	(182.70,478.57);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.70,472.76) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (227.51,518.59) --
+	(227.87,518.59);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (227.69,518.46) --
+	(227.69,518.71);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (227.69,515.68) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.13,491.01) --
+	(188.14,491.01);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.69,487.64) --
+	(186.69,493.87);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (186.69,487.78) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.40,488.00) --
+	(196.08,488.00);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.33,486.78) --
+	(194.33,489.16);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.33,483.97) {$L$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (218.53,512.98) --
+	(219.58,512.98);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (219.06,512.68) --
+	(219.06,513.27);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (219.06,508.95) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.67,480.43) --
+	(183.13,480.43);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.76,476.92) --
+	(179.76,483.40);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.76,476.40) {$h$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.01,485.33) --
+	(196.53,485.33);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.48,483.22) --
+	(186.48,487.22);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (186.48,482.42) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (227.61,518.72) --
+	(228.56,518.72);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (228.09,518.22) --
+	(228.09,519.21);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (228.09,515.82) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (140.42,496.45) --
+	(155.00,496.45);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.07,492.63) --
+	(149.07,499.63);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (149.07,493.22) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.52,506.28) --
+	(201.57,506.28);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (197.96,502.48) --
+	(197.96,509.46);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.96,502.25) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (197.65,508.23) --
+	(199.28,508.23);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.48,508.03) --
+	(198.48,508.43);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.48,504.20) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (137.70,463.38) --
+	(144.96,463.38);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (141.67,458.93) --
+	(141.67,466.99);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (141.67,459.35) {$h$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (138.07,485.70) --
+	(160.13,485.70);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.12,478.90) --
+	(152.12,490.71);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (152.12,482.80) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (226.06,516.73) --
+	(227.60,516.73);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (226.85,516.31) --
+	(226.85,517.14);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (226.85,513.83) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (226.11,493.64) --
+	(227.68,493.64);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (226.91,483.94) --
+	(226.91,500.04);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (226.91,490.41) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (206.11,496.60) --
+	(208.95,496.60);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (207.58,495.56) --
+	(207.58,497.59);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.58,492.57) {$L$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (236.77,524.67) --
+	(237.11,524.67);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (236.94,524.50) --
+	(236.94,524.84);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (236.94,520.63) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.91,488.81) --
+	(200.98,488.81);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.05,487.21) --
+	(199.05,490.29);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.05,484.78) {$h$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.50,497.60) --
+	(215.58,497.60);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (213.65,495.18) --
+	(213.65,499.74);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (213.65,494.69) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (227.05,516.36) --
+	(227.63,516.36);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (227.34,515.62) --
+	(227.34,517.07);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (227.34,513.45) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.67,502.71) --
+	(171.67,504.41);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.67,500.35) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (226.95,508.11) --
+	(226.95,511.22);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (226.95,505.70) {$L$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (212.27,508.98) --
+	(212.27,509.50);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.27,505.21) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.96,478.93) --
+	(178.96,481.00);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (178.96,475.96) {$h$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.11,478.69) --
+	(174.11,483.82);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.11,478.52) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (230.25,516.17) --
+	(230.25,518.13);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (230.25,514.27) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (206.38,504.25) --
+	(214.63,504.25);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (210.95,499.69) --
+	(210.95,507.93);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.95,501.02) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.46,482.55) --
+	(191.04,482.55);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.45,478.83) --
+	(188.45,485.66);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.45,478.52) {$L$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (226.45,515.35) --
+	(227.79,515.35);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (227.14,514.89) --
+	(227.14,515.80);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (227.14,511.32) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.11,476.20) --
+	(196.81,476.20);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.50,470.52) --
+	(191.50,480.58);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.50,472.17) {$h$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.32,502.37) --
+	(205.61,502.37);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.45,497.47) --
+	(199.45,506.27);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.45,499.46) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (236.91,528.12) --
+	(241.97,528.12);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (239.61,526.74) --
+	(239.61,529.42);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (239.61,525.22) {$\kappa$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (227.35,500.31) --
+	(228.89,500.31);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (228.14,497.06) --
+	(228.14,503.10);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (228.14,497.09) {$p$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (214.12,496.85) --
+	(216.77,496.85);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (215.49,493.38) --
+	(215.49,499.78);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (215.49,492.81) {$L$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (231.18,518.98) --
+	(231.57,518.98);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (231.37,518.81) --
+	(231.37,519.15);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (231.37,514.95) {$r$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (213.26,499.46) --
+	(215.83,499.46);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (214.59,497.44) --
+	(214.59,501.29);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (214.59,495.42) {$h$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (219.79,503.98) --
+	(220.66,503.98);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (220.23,502.88) --
+	(220.23,505.02);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.23,501.07) {$\sigma$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (240.33,531.24) --
+	(241.98,531.24);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (241.17,530.62) --
+	(241.17,531.84);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (241.17,528.33) {$\kappa$};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,301.03) {ESS/hr [adapt (\textit{cat})]};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (307.01,433.62) {ESS/hr [adapt (\textit{quant})]};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,301.03) {ESS/chain [adapt (\textit{cat})]};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (307.01,433.62) {ESS/chain [adapt (\textit{quant})]};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (385.91,398.02) --
-	(393.47,398.02);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (390.03,382.13) --
-	(390.03,406.87);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (390.03,394.79) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (446.33,475.91) --
-	(479.87,475.91);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (469.29,475.07) --
-	(469.29,476.72);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (469.29,471.88) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (384.08,472.93) --
-	(392.12,472.93);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (388.49,468.95) --
-	(388.49,476.26);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (388.49,468.89) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.27,397.74) --
-	(394.25,397.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (391.91,377.39) --
-	(391.91,407.77);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (391.91,393.71) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (372.81,366.19) --
-	(384.60,366.19);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (379.54,357.18) --
-	(379.54,372.44);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (379.54,363.29) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.65,483.32) --
-	(484.07,483.32);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.86,483.08) --
-	(483.86,483.56);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.86,480.42) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (388.69,424.26) --
-	(405.21,424.26);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (398.57,421.10) --
-	(398.57,427.01);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (398.57,421.04) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.15,476.34) --
-	(482.52,476.34);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (480.91,473.72) --
-	(480.91,478.65);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (480.91,472.30) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (453.62,477.11) --
-	(453.92,477.11);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (453.77,476.35) --
-	(453.77,477.84);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (453.77,473.07) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (390.05,422.63) --
-	(401.15,422.63);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (396.34,419.69) --
-	(396.34,425.20);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (396.34,418.60) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (392.33,405.99) --
-	(404.95,405.99);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (399.59,404.44) --
-	(399.59,407.42);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (399.59,403.08) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.20,485.27) --
-	(485.51,485.27);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.35,485.11) --
-	(485.35,485.43);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (485.35,482.37) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.23,469.66) --
-	(470.71,469.66);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (466.51,467.06) --
-	(466.51,471.96);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (466.51,466.43) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (447.29,481.52) --
-	(473.17,481.52);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.06,478.07) --
-	(464.06,484.47);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (464.06,477.48) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.06,487.79) --
-	(486.86,487.79);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.46,487.17) --
-	(486.46,488.40);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (486.46,483.76) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (439.32,448.83) --
-	(453.78,448.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (447.79,445.54) --
-	(447.79,451.66);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (447.79,444.80) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (467.66,470.37) --
-	(471.98,470.37);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (469.94,468.48) --
-	(469.94,472.10);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (469.94,467.47) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (497.56,499.91) --
-	(501.41,499.91);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.57,499.32) --
-	(499.57,500.49);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (499.57,497.01) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (412.03,486.24) --
+	(429.78,486.24);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (422.89,483.71) --
+	(422.89,488.48);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (422.89,483.01) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (455.50,515.98) --
+	(481.90,515.98);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (472.94,515.21) --
+	(472.94,516.73);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (472.94,511.95) {$L$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (414.70,510.08) --
+	(424.92,510.08);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (420.49,508.58) --
+	(420.49,511.48);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (420.49,506.05) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (410.13,481.95) --
+	(429.48,481.95);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (422.15,475.06) --
+	(422.15,487.01);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (422.15,477.92) {$h$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (389.04,494.23) --
+	(400.96,494.23);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (395.92,489.73) --
+	(395.92,497.87);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (395.92,491.33) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (514.42,514.61) --
+	(514.80,514.61);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (514.61,513.26) --
+	(514.61,515.87);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (514.61,511.71) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (501.43,502.88) --
+	(504.42,502.88);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (502.98,501.44) --
+	(502.98,504.21);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (502.98,499.65) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.57,484.45) --
+	(483.90,484.45);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (482.77,483.64) --
+	(482.77,485.23);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (482.77,480.42) {$L$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (509.10,515.82) --
+	(509.49,515.82);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (509.30,515.68) --
+	(509.30,515.96);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (509.30,511.79) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (492.41,496.95) --
+	(497.37,496.95);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (495.05,495.13) --
+	(495.05,498.62);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (495.05,492.92) {$h$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (502.10,512.60) --
+	(504.49,512.60);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (503.34,511.28) --
+	(503.34,513.84);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (503.34,509.70) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (513.31,514.28) --
+	(514.74,514.28);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (514.04,513.85) --
+	(514.04,514.70);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (514.04,511.38) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (476.69,476.21) --
+	(480.94,476.21);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (478.94,471.55) --
+	(478.94,479.95);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (478.94,472.98) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (490.50,496.44) --
+	(493.99,496.44);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (492.33,495.62) --
+	(492.33,497.22);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (492.33,492.41) {$L$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (513.05,518.61) --
+	(514.11,518.61);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (513.59,518.39) --
+	(513.59,518.83);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (513.59,514.58) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (457.57,462.00) --
+	(468.00,462.00);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (463.48,456.27) --
+	(463.48,466.41);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (463.48,457.97) {$h$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (469.04,485.00) --
+	(474.18,485.00);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (471.78,480.84) --
+	(471.78,488.42);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (471.78,482.10) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (516.59,516.49) --
+	(516.95,516.49);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (516.77,516.20) --
+	(516.77,516.78);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (516.77,513.59) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (474.21,489.90) --
+	(477.22,489.90);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (475.77,488.38) --
+	(475.77,491.32);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (475.77,486.68) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.48,490.25) --
+	(485.16,490.25);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.41,488.30) --
+	(483.41,492.02);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.41,486.22) {$L$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (507.61,515.74) --
+	(508.66,515.74);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (508.14,515.62) --
+	(508.14,515.85);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (508.14,511.70) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (464.75,489.96) --
+	(472.21,489.96);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (468.84,488.02) --
+	(468.84,491.72);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.84,485.93) {$h$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (453.09,493.91) --
+	(485.61,493.91);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (475.56,491.52) --
+	(475.56,496.04);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (475.56,491.01) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (516.69,517.00) --
+	(517.64,517.00);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (517.17,516.92) --
+	(517.17,517.07);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (517.17,514.09) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (429.50,471.62) --
+	(444.08,471.62);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (438.15,470.11) --
+	(438.15,473.01);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (438.15,468.39) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (482.60,510.00) --
+	(490.65,510.00);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (487.04,507.87) --
+	(487.04,511.92);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (487.04,505.97) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (486.73,508.84) --
+	(488.36,508.84);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (487.56,508.29) --
+	(487.56,509.38);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (487.56,504.81) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (426.78,470.99) --
+	(434.04,470.99);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (430.75,469.17) --
+	(430.75,472.65);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (430.75,466.96) {$h$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (427.15,483.25) --
+	(449.21,483.25);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (441.20,480.13) --
+	(441.20,485.92);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (441.20,480.34) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (515.14,514.97) --
+	(516.68,514.97);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (515.93,514.65) --
+	(515.93,515.28);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (515.93,512.07) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (515.19,516.70) --
+	(516.76,516.70);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (515.99,515.91) --
+	(515.99,517.46);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (515.99,513.48) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (495.19,498.61) --
+	(498.03,498.61);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (496.66,495.49) --
+	(496.66,501.29);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (496.66,494.57) {$L$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (525.85,525.98) --
+	(526.19,525.98);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (526.02,525.81) --
+	(526.02,526.15);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (526.02,521.95) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (485.99,488.18) --
+	(490.06,488.18);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (488.13,486.37) --
+	(488.13,489.84);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (488.13,484.15) {$h$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (500.58,502.47) --
+	(504.66,502.47);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (502.73,501.02) --
+	(502.73,503.81);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (502.73,499.56) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (516.13,516.37) --
+	(516.71,516.37);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (516.42,516.06) --
+	(516.42,516.68);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (516.42,513.47) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (460.75,476.54) --
+	(460.75,483.75);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (460.75,477.26) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (516.03,510.16) --
+	(516.03,513.84);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (516.03,508.05) {$L$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (501.35,516.22) --
+	(501.35,516.60);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (501.35,512.38) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (468.04,483.50) --
+	(468.04,493.25);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.04,484.95) {$h$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (463.19,490.82) --
+	(463.19,496.72);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (463.19,491.09) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (519.33,517.20) --
+	(519.33,519.44);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (519.33,515.45) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (495.46,505.50) --
+	(503.71,505.50);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (500.03,502.97) --
+	(500.03,507.73);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (500.03,502.27) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (474.54,487.87) --
+	(480.12,487.87);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (477.53,484.86) --
+	(477.53,490.48);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (477.53,483.84) {$L$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (515.53,519.55) --
+	(516.87,519.55);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (516.22,519.31) --
+	(516.22,519.79);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (516.22,515.52) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (473.19,490.54) --
+	(485.89,490.54);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.58,486.19) --
+	(480.58,494.09);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (480.58,486.51) {$h$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (479.40,504.83) --
+	(494.69,504.83);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (488.53,500.57) --
+	(488.53,508.31);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (488.53,501.92) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (525.99,528.64) --
+	(531.05,528.64);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (528.69,528.52) --
+	(528.69,528.76);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (528.69,525.74) {$\kappa$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (516.43,514.92) --
+	(517.97,514.92);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (517.22,507.67) --
+	(517.22,520.16);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (517.22,511.69) {$p$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (503.20,501.52) --
+	(505.85,501.52);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (504.57,494.65) --
+	(504.57,506.56);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (504.57,497.48) {$L$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (520.26,518.27) --
+	(520.65,518.27);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (520.45,510.35) --
+	(520.45,523.85);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (520.45,514.23) {$r$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (502.34,500.17) --
+	(504.91,500.17);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (503.67,491.51) --
+	(503.67,506.10);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (503.67,496.13) {$h$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (508.87,509.87) --
+	(509.74,509.87);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (509.31,501.95) --
+	(509.31,515.45);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (509.31,506.96) {$\sigma$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (529.41,527.10) --
+	(531.06,527.10);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (530.25,518.90) --
+	(530.25,532.82);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (530.25,524.20) {$\kappa$};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54, 11.95) {ESS/hr [adapt (\textit{real})]};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,144.54) {ESS/hr [adapt (\textit{quant})]};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54, 11.95) {ESS/chain [adapt (\textit{real})]};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,144.54) {ESS/chain [adapt (\textit{quant})]};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (166.31,108.94) --
-	(178.18,108.94);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.09, 93.05) --
-	(173.09,117.79);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.09,105.71) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.01,186.83) --
-	(175.60,186.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.43,185.99) --
-	(173.43,187.64);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.43,182.80) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.22,183.85) --
-	(188.66,183.85);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.48,179.87) --
-	(187.48,187.18);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.48,179.81) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (134.78,108.66) --
-	(152.57,108.66);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.54, 88.31) --
-	(145.54,118.69);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (145.54,104.63) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (170.09, 77.11) --
-	(180.04, 77.11);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.66, 68.10) --
-	(175.66, 83.36);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (175.66, 74.21) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.83,194.24) --
-	(195.05,194.24);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.45,194.00) --
-	(194.45,194.48);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.45,191.34) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (165.91,162.72) --
-	(169.91,162.72);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.01,157.69) --
-	(168.01,166.76);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (168.01,159.49) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.51,190.76) --
-	(192.13,190.76);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.40,188.99) --
-	(190.40,192.40);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.40,186.73) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.13,194.78) --
-	(192.93,194.78);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.54,192.84) --
-	(192.54,196.56);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.54,190.75) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (154.98,160.08) --
-	(160.63,160.08);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.00,153.30) --
-	(158.00,165.16);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.00,156.04) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.83,159.04) --
-	(165.18,159.04);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.57,156.47) --
-	(163.57,161.34);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (163.57,156.14) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.10,198.95) --
-	(199.15,198.95);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.63,198.56) --
-	(198.63,199.33);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.63,196.04) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.18,135.18) --
-	(180.36,135.18);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.93,132.02) --
-	(177.93,137.93);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.93,131.96) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.79,187.26) --
-	(183.97,187.26);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.99,184.64) --
-	(181.99,189.57);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.99,183.22) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.55,188.03) --
-	(187.77,188.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.66,187.27) --
-	(187.66,188.76);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.66,183.99) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (136.18,133.55) --
-	(143.40,133.55);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.10,130.61) --
-	(140.10,136.12);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (140.10,129.52) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (157.97,116.91) --
-	(166.71,116.91);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.80,115.36) --
-	(162.80,118.34);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (162.80,114.00) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.08,196.19) --
-	(197.23,196.19);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.66,196.03) --
-	(196.66,196.35);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.66,193.29) {$\kappa$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.94,146.87) --
-	(183.64,146.87);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.81,144.32) --
-	(182.81,149.14);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.81,143.64) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.45,193.77) --
-	(184.72,193.77);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (183.15,191.53) --
-	(183.15,195.79);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.15,189.74) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.22,193.77) --
-	(188.78,193.77);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.50,193.53) --
-	(188.50,194.01);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.50,189.74) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (156.86,161.33) --
-	(159.29,161.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.11,158.55) --
-	(158.11,163.78);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.11,157.30) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (155.66,151.01) --
-	(161.22,151.01);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.63,148.68) --
-	(158.63,153.10);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.63,148.10) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.03,198.53) --
-	(199.38,198.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.24,196.83) --
-	(198.24,200.10);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.24,195.63) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.31,180.58) --
-	(188.49,180.58);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.63,177.98) --
-	(185.63,182.88);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.63,177.35) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.90,192.44) --
-	(193.65,192.44);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.63,188.99) --
-	(186.63,195.39);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (186.63,188.40) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.34,198.71) --
-	(196.54,198.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.95,198.09) --
-	(195.95,199.32);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.95,194.68) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (147.39,159.75) --
-	(158.98,159.75);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.99,156.46) --
-	(153.99,162.58);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (153.99,155.72) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (178.62,181.29) --
-	(188.88,181.29);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.39,179.40) --
-	(184.39,183.02);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.39,178.39) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (207.95,210.83) --
-	(210.44,210.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.23,210.24) --
-	(209.23,211.41);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.23,207.93) {$\kappa$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.58,195.33) --
-	(183.78,195.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.49,193.67) --
-	(180.49,196.87);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.49,192.11) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.38,201.82) --
-	(174.02,201.82);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.39,201.65) --
-	(171.39,201.98);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.39,197.78) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.62,199.95) --
-	(199.37,199.95);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (199.00,198.75) --
-	(199.00,201.09);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.00,195.92) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.20,178.14) --
-	(180.56,178.14);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.38,173.53) --
-	(180.38,181.90);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.38,174.11) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.06,186.15) --
-	(185.69,186.15);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.64,182.17) --
-	(182.64,189.49);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.64,183.25) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.62,212.25) --
-	(213.79,212.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.74,211.79) --
-	(212.74,212.69);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.74,209.34) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.83,197.16) --
+	(207.82,197.16);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (202.75,194.63) --
+	(202.75,199.40);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.75,193.93) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (224.38,226.90) --
+	(228.23,226.90);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (226.40,226.13) --
+	(226.40,227.65);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (226.40,222.87) {$L$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (217.94,221.00) --
+	(220.14,221.00);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (219.07,219.50) --
+	(219.07,222.40);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (219.07,216.97) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (170.22,192.87) --
+	(187.04,192.87);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.42,185.98) --
+	(180.42,197.93);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.42,188.84) {$h$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (201.23,205.15) --
+	(209.50,205.15);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (205.80,200.65) --
+	(205.80,208.79);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.80,202.25) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (225.13,225.53) --
+	(226.16,225.53);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (225.65,224.18) --
+	(225.65,226.79);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (225.65,222.63) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (214.99,213.80) --
+	(216.39,213.80);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (215.70,212.36) --
+	(215.70,215.13);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (215.70,210.57) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.02,195.37) --
+	(195.38,195.37);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.24,194.56) --
+	(194.24,196.15);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.24,191.34) {$L$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (224.25,226.74) --
+	(224.59,226.74);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (224.42,226.60) --
+	(224.42,226.88);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (224.42,222.71) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (204.20,207.87) --
+	(206.94,207.87);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (205.62,206.05) --
+	(205.62,209.54);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.62,203.84) {$h$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (216.73,223.52) --
+	(218.29,223.52);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (217.53,222.20) --
+	(217.53,224.76);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (217.53,220.62) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (225.23,225.20) --
+	(225.73,225.20);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (225.48,224.77) --
+	(225.48,225.62);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (225.48,222.30) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.67,187.13) --
+	(192.59,187.13);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.73,182.47) --
+	(190.73,190.87);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.73,183.90) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.70,207.36) --
+	(207.72,207.36);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (202.99,206.54) --
+	(202.99,208.14);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.99,203.33) {$L$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (228.74,229.53) --
+	(229.37,229.53);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (229.06,229.31) --
+	(229.06,229.75);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (229.06,225.50) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (159.99,172.92) --
+	(164.77,172.92);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (162.53,167.19) --
+	(162.53,177.33);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (162.53,168.89) {$h$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.16,195.92) --
+	(189.49,195.92);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.59,191.76) --
+	(186.59,199.34);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (186.59,193.02) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (229.38,227.41) --
+	(229.63,227.41);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (229.51,227.12) --
+	(229.51,227.70);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (229.51,224.51) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.56,200.82) --
+	(204.79,200.82);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (201.93,199.30) --
+	(201.93,202.24);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (201.93,197.60) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (197.70,201.17) --
+	(200.08,201.17);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.92,199.22) --
+	(198.92,202.94);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.92,197.14) {$L$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (223.60,226.66) --
+	(224.19,226.66);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (223.90,226.54) --
+	(223.90,226.77);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (223.90,222.62) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.84,200.88) --
+	(194.32,200.88);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.35,198.94) --
+	(191.35,202.64);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.35,196.85) {$h$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.14,204.83) --
+	(198.14,204.83);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.25,202.44) --
+	(196.25,206.96);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.25,201.93) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (229.14,227.92) --
+	(230.13,227.92);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (229.64,227.84) --
+	(229.64,227.99);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (229.64,225.01) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (203.55,182.54) --
+	(210.55,182.54);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (207.37,181.03) --
+	(207.37,183.93);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.37,179.31) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (213.40,220.92) --
+	(220.38,220.92);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (217.20,218.79) --
+	(217.20,222.84);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (217.20,216.89) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (218.95,219.76) --
+	(219.35,219.76);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (219.15,219.21) --
+	(219.15,220.30);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (219.15,215.73) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.85,181.91) --
+	(177.91,181.91);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.30,180.09) --
+	(174.30,183.57);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.30,177.88) {$h$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.82,194.17) --
+	(201.63,194.17);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.62,191.05) --
+	(196.62,196.84);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.62,191.26) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (227.23,225.89) --
+	(228.06,225.89);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (227.65,225.57) --
+	(227.65,226.20);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (227.65,222.99) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.86,227.62) --
+	(210.96,227.62);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (204.56,226.83) --
+	(204.56,228.38);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (204.56,224.40) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (206.48,209.53) --
+	(208.51,209.53);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (207.52,206.41) --
+	(207.52,212.21);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.52,205.49) {$L$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (235.42,236.90) --
+	(235.76,236.90);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (235.59,236.73) --
+	(235.59,237.07);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (235.59,232.87) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.13,199.10) --
+	(201.21,199.10);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.73,197.29) --
+	(199.73,200.76);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.73,195.07) {$h$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (206.10,213.39) --
+	(210.66,213.39);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (208.52,211.94) --
+	(208.52,214.73);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (208.52,210.48) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (226.54,227.29) --
+	(227.99,227.29);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (227.28,226.98) --
+	(227.28,227.60);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (227.28,224.39) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (213.63,191.41) --
+	(215.33,191.41);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (214.50,187.46) --
+	(214.50,194.67);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (214.50,188.18) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (219.03,223.01) --
+	(222.14,223.01);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (220.65,221.08) --
+	(220.65,224.76);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.65,218.97) {$L$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (219.90,227.34) --
+	(220.42,227.34);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (220.16,227.14) --
+	(220.16,227.52);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.16,223.30) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.85,199.91) --
+	(191.92,199.91);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.91,194.42) --
+	(190.91,204.17);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.91,195.87) {$h$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.61,204.92) --
+	(194.74,204.92);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.35,201.74) --
+	(192.35,207.64);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.35,202.01) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (227.09,229.27) --
+	(229.05,229.27);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (228.09,228.12) --
+	(228.09,230.36);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (228.09,226.37) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (210.61,216.42) --
+	(218.85,216.42);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (215.17,213.89) --
+	(215.17,218.65);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (215.17,213.19) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.75,198.79) --
+	(196.58,198.79);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.47,195.78) --
+	(193.47,201.40);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.47,194.76) {$L$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (225.81,230.47) --
+	(226.72,230.47);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (226.27,230.23) --
+	(226.27,230.71);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (226.27,226.44) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.44,201.46) --
+	(191.50,201.46);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.12,197.11) --
+	(187.12,205.01);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.12,197.43) {$h$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (208.39,215.75) --
+	(217.19,215.75);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (213.29,211.49) --
+	(213.29,219.23);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (213.29,212.84) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (237.66,239.56) --
+	(240.34,239.56);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (239.04,239.44) --
+	(239.04,239.68);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (239.04,236.66) {$\kappa$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (207.98,225.84) --
+	(214.02,225.84);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.23,218.59) --
+	(211.23,231.08);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.23,222.61) {$p$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (204.30,212.44) --
+	(210.70,212.44);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (207.77,205.57) --
+	(207.77,217.48);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.77,208.40) {$L$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (229.73,229.19) --
+	(230.07,229.19);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (229.90,221.27) --
+	(229.90,234.77);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (229.90,225.15) {$r$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (208.36,211.09) --
+	(212.21,211.09);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (210.38,202.43) --
+	(210.38,217.02);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.38,207.05) {$h$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (213.80,220.79) --
+	(215.94,220.79);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (214.90,212.87) --
+	(214.90,226.37);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (214.90,217.88) {$\sigma$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (241.54,238.02) --
+	(242.76,238.02);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (242.16,229.82) --
+	(242.16,243.74);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (242.16,235.12) {$\kappa$};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (485.73,205.86) --
-	(485.73, 51.84);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (485.73,126.77) {$77\times $};
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (485.73,274.05) --
+	(485.73, 51.96);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (485.73,160.93) {$100\times $};
 \definecolor{fillColor}{RGB}{0,140,186}
 
-\path[fill=fillColor] (485.73,205.86) circle (  1.87);
+\path[fill=fillColor] (485.73,274.05) circle (  1.87);
 \definecolor{fillColor}{RGB}{105,105,105}
 
-\path[fill=fillColor] (485.73, 51.84) circle (  1.87);
+\path[fill=fillColor] (485.73, 51.96) circle (  1.87);
 \definecolor{fillColor}{gray}{0.64}
 
-\path[fill=fillColor] (485.73,199.70) circle (  1.87);
+\path[fill=fillColor] (485.73,278.61) circle (  1.87);
 \definecolor{fillColor}{RGB}{0,140,186}
@@
 
-\path[fill=fillColor] (394.78,308.65) circle (  1.87);
+\path[fill=fillColor] (394.78,420.47) circle (  1.87);
 
@@
 
-\path[fill=fillColor] (390.04,246.75) circle (  1.87);
+\path[fill=fillColor] (390.04,334.64) circle (  1.87);
 \definecolor{fillColor}{gray}{0.64}
 
-\path[fill=fillColor] (390.04,277.75) circle (  1.87);
+\path[fill=fillColor] (390.04,376.63) circle (  1.87);
 \definecolor{fillColor}{RGB}{0,140,186}
@@
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (404.25,204.65) --
-	(404.25,100.19);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (404.25,150.34) {$3.1\times $};
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (404.25,272.59) --
+	(404.25,124.41);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (404.25,196.42) {$3\times $};
 \definecolor{fillColor}{RGB}{0,140,186}
 
-\path[fill=fillColor] (404.25,204.65) circle (  1.87);
+\path[fill=fillColor] (404.25,272.59) circle (  1.87);
 \definecolor{fillColor}{RGB}{105,105,105}
 
-\path[fill=fillColor] (404.25,100.19) circle (  1.87);
+\path[fill=fillColor] (404.25,124.41) circle (  1.87);
 \definecolor{fillColor}{gray}{0.64}
 
-\path[fill=fillColor] (404.25,210.63) circle (  1.87);
+\path[fill=fillColor] (404.25,276.59) circle (  1.87);
 \definecolor{fillColor}{RGB}{0,140,186}
@@
 
-\path[fill=fillColor] (433.62,210.36) circle (  1.87);
+\path[fill=fillColor] (433.62,282.32) circle (  1.87);
 \definecolor{fillColor}{gray}{0.64}
 
-\path[fill=fillColor] (433.62,258.51) circle (  1.87);
+\path[fill=fillColor] (433.62,387.81) circle (  1.87);
 \definecolor{fillColor}{RGB}{0,140,186}
@@
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (359.72,284.96) --
-	(359.72,295.15);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (359.72,287.98) {$0.96\times $};
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (359.72,374.45) --
+	(359.72,381.62);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (359.72,375.96) {$0.98\times $};
 \definecolor{fillColor}{RGB}{0,140,186}
 
-\path[fill=fillColor] (359.72,284.96) circle (  1.87);
+\path[fill=fillColor] (359.72,374.45) circle (  1.87);
 \definecolor{fillColor}{RGB}{105,105,105}
 
-\path[fill=fillColor] (359.72,295.15) circle (  1.87);
+\path[fill=fillColor] (359.72,381.62) circle (  1.87);
 \definecolor{fillColor}{gray}{0.64}
 
-\path[fill=fillColor] (359.72,315.21) circle (  1.87);
+\path[fill=fillColor] (359.72,444.47) circle (  1.87);
 \definecolor{fillColor}{RGB}{0,140,186}
@@
 
-\path[fill=fillColor] (346.46,317.20) circle (  1.87);
+\path[fill=fillColor] (346.46,438.74) circle (  1.87);
 \definecolor{fillColor}{gray}{0.64}
 
-\path[fill=fillColor] (346.46,337.93) circle (  1.87);
+\path[fill=fillColor] (346.46,381.39) circle (  1.87);
 \definecolor{fillColor}{RGB}{0,140,186}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 87.70) -- (333.90, 87.70);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,125.59) -- (333.90,125.59);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,163.49) -- (333.90,163.49);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,201.38) -- (333.90,201.38);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 81.38) -- (333.90, 81.38);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,112.96) -- (333.90,112.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,144.54) -- (333.90,144.54);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,176.12) -- (333.90,176.12);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,207.70) -- (333.90,207.70);
 
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92, 84.84) {200};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,122.73) {400};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,160.63) {600};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,198.53) {800};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,236.42) {1000};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92, 78.52) {1000};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,110.10) {2000};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,141.68) {3000};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,173.26) {4000};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,204.84) {5000};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,236.42) {6000};
 \end{scope}

### 2020-08-24 benchmarking/benchmarkingVM/ESS_round3.tex
results update

@@
-% Created by tikzDevice version 0.12.3 on 2020-08-10 15:55:24
+% Created by tikzDevice version 0.12.3.1 on 2020-08-24 19:05:08
 % !TEX encoding = UTF-8 Unicode
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at (144.54, 14.40) {ESS/hr [adapt (\textit{real})]};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at (144.54, 14.40) {ESS/chain [adapt (\textit{real})]};
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at ( 21.60,144.54) {ESS/hr [Bactrian (\textit{real})]};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at ( 21.60,144.54) {ESS/chain [Bactrian (\textit{real})]};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00, 76.35) --
-	(212.73,289.08);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00, 71.00) --
+	(218.08,289.08);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.35,289.08) --
-	(271.35,195.00) --
-	( 76.35,  0.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (268.39,289.08) --
+	(268.39,197.39) --
+	( 71.00,  0.00);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (  0.00, 50.90) --
-	(238.18,289.08);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (  0.00, 47.34) --
+	(241.74,289.08);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (271.35,289.08) --
-	(271.35,220.45) --
-	( 50.90,  0.00);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (268.39,289.08) --
+	(268.39,221.06) --
+	( 47.34,  0.00);
 
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (  0.00, 25.45) --
-	(263.63,289.08);
+\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (  0.00, 23.67) --
+	(265.41,289.08);
 
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (271.35,289.08) --
-	(271.35,245.90) --
-	( 25.45,  0.00);
+\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (268.39,289.08) --
+	(268.39,244.72) --
+	( 23.67,  0.00);
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (145.42, 64.13) {$\frac{1}{64} \times$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (140.08, 64.13) {$\frac{1}{64} \times$};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,150.12) {$64\times$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,144.78) {$64\times$};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (119.97, 64.13) {$\frac{1}{16} \times$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (116.41, 64.13) {$\frac{1}{16} \times$};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,124.67) {$16\times$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,121.11) {$16\times$};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 92.53, 64.13) {$\frac{1}{4} \times$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 90.75, 64.13) {$\frac{1}{4} \times$};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 62.56, 99.22) {$4\times$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 62.56, 97.44) {$4\times$};
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.97,173.04) --
-	(174.56,173.04);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.31,201.61) --
+	(201.01,201.61);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (170.02,163.26) --
-	(170.02,179.39);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.48,192.53) --
+	(196.48,207.50);
+\definecolor{drawColor}{RGB}{255,0,109}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (170.02,169.15) {$p$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (196.48,197.72) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.16,172.12) --
-	(172.25,172.12);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (215.79,219.42) --
+	(219.22,219.42);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (170.32,170.07) --
-	(170.32,173.96);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (217.59,218.48) --
+	(217.59,220.32);
+\definecolor{drawColor}{RGB}{255,0,109}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (170.32,167.26) {$L$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (217.59,214.56) {$L$};
+\definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.73,184.48) --
-	(183.91,184.48);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (210.04,212.68) --
+	(212.00,212.68);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.85,183.02) --
-	(182.85,185.84);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.05,211.52) --
+	(211.05,213.76);
+\definecolor{drawColor}{RGB}{255,0,109}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (182.85,179.62) {$r$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (211.05,207.82) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (135.83,152.06) --
-	(151.70,152.06);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (167.45,182.57) --
+	(182.46,182.57);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.43,146.58) --
-	(145.43,156.28);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.56,176.26) --
+	(176.56,187.17);
+\definecolor{drawColor}{RGB}{255,0,109}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (145.43,147.20) {$h$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (176.56,177.71) {$h$};
+\definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (167.34,176.95) --
-	(176.22,176.95);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.12,205.91) --
+	(202.50,205.91);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.31,171.72) --
-	(172.31,181.01);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.21,201.26) --
+	(199.21,209.56);
+\definecolor{drawColor}{RGB}{255,0,109}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (172.31,173.45) {$\sigma$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (199.21,202.41) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.52,189.61) --
-	(189.61,189.61);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (216.46,217.34) --
+	(217.37,217.34);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.07,189.39) --
-	(189.07,189.83);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (216.92,217.08) --
+	(216.92,217.59);
+\definecolor{drawColor}{RGB}{255,0,109}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (189.07,186.11) {$\kappa$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (216.92,213.84) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (207.40,193.34) --
+	(208.66,193.34);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (208.04,186.76) --
+	(208.04,198.08);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (208.04,189.45) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.80,188.26) --
+	(189.91,188.26);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.89,186.60) --
+	(188.89,189.77);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (188.89,183.40) {$L$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (215.67,218.00) --
+	(215.97,218.00);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (215.82,217.74) --
+	(215.82,218.26);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (215.82,213.14) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (197.78,199.74) --
+	(200.22,199.74);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.04,198.72) --
+	(199.04,200.70);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (199.04,194.88) {$h$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (208.96,201.61) --
+	(210.35,201.61);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (209.67,200.11) --
+	(209.67,202.99);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (209.67,198.11) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (216.54,216.76) --
+	(216.99,216.76);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (216.77,216.10) --
+	(216.77,217.39);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (216.77,213.26) {$\kappa$};
 \definecolor{drawColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.89,177.49) --
-	(176.50,177.49);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (197.20,193.91) --
+	(203.44,193.91);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.34,177.31) --
-	(174.34,177.66);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (200.61,191.58) --
+	(200.61,195.96);
+\definecolor{drawColor}{RGB}{0,219,171}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (174.34,173.60) {$p$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (200.61,190.02) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.00,179.60) --
-	(179.72,179.60);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (205.98,209.31) --
+	(212.21,209.31);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.96,177.03) --
-	(177.96,181.87);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (209.38,208.84) --
+	(209.38,209.77);
+\definecolor{drawColor}{RGB}{0,219,171}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (177.96,174.74) {$L$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (209.38,204.45) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.92,182.73) --
-	(183.11,182.73);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (210.94,210.71) --
+	(211.30,210.71);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (183.02,182.56) --
-	(183.02,182.90);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.12,210.10) --
+	(211.12,211.29);
+\definecolor{drawColor}{RGB}{0,219,171}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (183.02,177.87) {$r$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (211.12,205.85) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (137.08,144.73) --
-	(143.52,144.73);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (167.13,177.83) --
+	(174.32,177.83);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.58,137.44) --
-	(140.58,149.93);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.10,173.05) --
+	(171.10,181.55);
+\definecolor{drawColor}{RGB}{0,219,171}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (140.58,139.87) {$h$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (171.10,172.97) {$h$};
+\definecolor{drawColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (156.53,157.68) --
-	(164.32,157.68);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.94,189.00) --
+	(195.48,189.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.84,139.80) --
-	(160.84,166.56);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.01,181.20) --
+	(191.01,194.33);
+\definecolor{drawColor}{RGB}{0,219,171}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (160.84,154.18) {$\sigma$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (191.01,185.50) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.53,191.09) --
-	(191.56,191.09);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (218.33,218.47) --
+	(219.07,218.47);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.05,190.40) --
-	(191.05,191.75);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (218.70,217.85) --
+	(218.70,219.07);
+\definecolor{drawColor}{RGB}{0,219,171}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (191.05,187.59) {$\kappa$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (218.70,214.97) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.44,174.86) --
+	(203.81,174.86);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.09,167.36) --
+	(198.09,180.05);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (198.09,170.97) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.81,195.50) --
+	(201.63,195.50);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (200.74,190.50) --
+	(200.74,199.36);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (200.74,190.64) {$L$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (225.63,221.84) --
+	(225.94,221.84);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (225.79,220.41) --
+	(225.79,223.15);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (225.79,216.98) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.36,192.17) --
+	(195.11,192.17);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.79,190.64) --
+	(193.79,193.58);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (193.79,187.31) {$h$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.47,178.14) --
+	(203.54,178.14);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (201.63,172.95) --
+	(201.63,182.11);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (201.63,174.64) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (217.71,218.09) --
+	(219.01,218.09);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (218.37,217.44) --
+	(218.37,218.71);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (218.37,214.59) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (206.19,185.19) --
+	(207.71,185.19);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (206.97,176.99) --
+	(206.97,190.71);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (206.97,181.30) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.01,189.58) --
+	(213.79,189.58);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (212.46,182.79) --
+	(212.46,194.43);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (212.46,184.72) {$L$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.79,213.27) --
+	(212.25,213.27);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (212.02,212.31) --
+	(212.02,214.18);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (212.02,208.41) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.97,195.85) --
+	(186.82,195.85);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.92,193.43) --
+	(185.92,197.98);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (185.92,190.99) {$h$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.76,187.74) --
+	(189.34,187.74);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.20,186.56) --
+	(187.20,188.84);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (187.20,184.24) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (218.20,218.21) --
+	(219.95,218.21);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (219.10,214.91) --
+	(219.10,220.97);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (219.10,214.71) {$\kappa$};
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (178.25,170.79) --
-	(183.76,170.79);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (203.49,195.91) --
+	(210.85,195.91);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.21,169.12) --
-	(181.21,172.32);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (207.56,188.71) --
+	(207.56,200.95);
+\definecolor{drawColor}{RGB}{255,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (181.21,166.90) {$p$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (207.56,192.02) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.52,175.16) --
-	(188.36,175.16);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.88,186.94) --
+	(190.98,186.94);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.10,159.21) --
-	(182.10,183.57);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.20,179.46) --
+	(188.20,192.12);
+\definecolor{drawColor}{RGB}{255,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (182.10,170.30) {$L$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (188.20,182.08) {$L$};
+\definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.87,190.74) --
-	(190.95,190.74);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (217.06,217.95) --
+	(217.87,217.95);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.41,189.74) --
-	(190.41,191.69);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (217.47,217.06) --
+	(217.47,218.80);
+\definecolor{drawColor}{RGB}{255,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (190.41,185.88) {$r$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (217.47,213.09) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (147.08,153.71) --
-	(157.42,153.71);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (177.47,184.35) --
+	(186.44,184.35);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (152.97,149.99) --
-	(152.97,156.80);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.54,181.55) --
+	(182.54,186.76);
+\definecolor{drawColor}{RGB}{255,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (152.97,148.85) {$h$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (182.54,179.49) {$h$};
+\definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.95,170.40) --
-	(184.11,170.40);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (201.51,198.78) --
+	(209.36,198.78);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.10,167.27) --
-	(180.10,173.07);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (205.89,194.94) --
+	(205.89,201.91);
+\definecolor{drawColor}{RGB}{255,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (180.10,166.90) {$\sigma$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (205.89,195.28) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (201.12,201.71) --
-	(203.34,201.71);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (227.63,228.33) --
+	(230.02,228.33);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (202.27,200.95) --
-	(202.27,202.44);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (228.87,227.50) --
+	(228.87,229.12);
+\definecolor{drawColor}{RGB}{255,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (202.27,198.21) {$\kappa$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (228.87,224.83) {$\kappa$};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- (229.08, 60.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- (217.25, 60.00);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (102.27, 60.00) -- (102.27, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.31, 60.00) -- ( 99.31, 54.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (144.54, 60.00) -- (144.54, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.62, 60.00) -- (138.62, 54.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.81, 60.00) -- (186.81, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.93, 60.00) -- (177.93, 54.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.08, 60.00) -- (229.08, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.25, 60.00) -- (217.25, 54.00);
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (102.27, 38.40) {10};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 99.31, 38.40) {10};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (144.54, 38.40) {100};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (138.62, 38.40) {100};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (186.81, 38.40) {1000};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (177.93, 38.40) {1000};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (229.08, 38.40) {10000};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (217.25, 38.40) {10000};
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- ( 60.00,229.08);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- ( 60.00,217.25);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,102.27) -- ( 54.00,102.27);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 99.31) -- ( 54.00, 99.31);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,144.54) -- ( 54.00,144.54);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,138.62) -- ( 54.00,138.62);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,186.81) -- ( 54.00,186.81);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,177.93) -- ( 54.00,177.93);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,229.08) -- ( 54.00,229.08);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,217.25) -- ( 54.00,217.25);
 
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00, 98.83) {10};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00, 95.87) {10};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,141.10) {100};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,135.18) {100};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,183.37) {1000};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,174.49) {1000};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,225.64) {10000};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,213.80) {10000};
 \end{scope}

### 2020-08-24 benchmarking/pull.sh

@@ -1,0 +1,54 @@
+#!/bin/sh
+
+
+
+scp -r jdou557@login02.fos.auckland.ac.nz/benchmarkingVM.zip .
+
+#settings=("real" "cat" "quant" "AVMN" "bactrian98" "bactrian95" "NER" "real_06" "quant_06")
+datasets=("Sauquet_2011" "Moyle_2016" "simulated" "Dornburg_2012" "Broughton_2013" "Ran_2018_dna" "Rightmyer_2013" "Kawahara_2013" "Cognato_2001")
+
+
+
+
+
+ echo "Removing log and tree files"
+              
+# Real data   
+for batch in {1..5}
+do
+
+	echo "Batch${batch}"
+	cd "Batch${batch}"
+
+	for d in ${datasets[@]} ; do
+	    echo "Dataset $d"
+	    cd $d
+
+	    for e in */ ; do
+	        echo "Partition $e"
+	        cd $e
+
+
+			for logfile in *.log; do
+				echo $logfile
+				#/mnt/e/STOREDFILES/BEAST2/linux/beast/bin/loganalyser -oneline ${logfile}.log -burnin 0 > ${logfile}.ess
+			 done
+
+
+
+	        cd ../
+	    done
+	    
+
+    	#sleep 1
+
+   	 	cd ../
+	done
+
+	cd ../
+
+done
+
+
+
+

### 2020-08-24 benchmarking/render.R

@@ -7,7 +7,7 @@ library(rjson)
 
 
 
-PER_CHAIN = FALSE
+PER_CHAIN = TRUE
 
 #settings = c("cat", "real", "quant", "bactrian95", "bactrian98")
 settings = c("cat",  "real_06", "quant_06", "real", "quant", "bactrian95", "bactrian98", "NER", "AVMN")
@@ -87,7 +87,7 @@ parameters.latex.small["RateStatLogger.mean"] = "$\\bar{r}$"
 getDateTime = function(str){
 
 	year = as.numeric(strsplit(str, " +")[[1]][6])
-	month =strsplit(str, " +")[[1]][2]
+	month = strsplit(str, " +")[[1]][2]
 	day = strsplit(str, " +")[[1]][3]
 	if (nchar(day) == 1) day = paste0("0", day)
 	time = strsplit(str, " +")[[1]][4]
@@ -99,7 +99,8 @@ getDateTime = function(str){
 
 
 ESS.df = data.frame(batch = numeric(0), param = character(0), dataset = character(0), partition = numeric(0), setting = character(0), nstates = numeric(0),
- ESS = numeric(0), hr = numeric(0), ESS.hr = numeric(0), Leff = numeric(0), L = numeric(0), N = numeric(0), mean.speed = numeric(0), CD_weight = numeric(0), RW_weight = numeric(0), SPP_weight = numeric(0))
+		ESS = numeric(0), hr = numeric(0), ESS.hr = numeric(0), Leff = numeric(0), L = numeric(0), N = numeric(0), mean.speed = numeric(0), 
+		CD_weight = numeric(0), RW_weight = numeric(0), SPP_weight = numeric(0), NER_weight = numeric(0), NER_acc = numeric(0), NE_acc = numeric(0))
 
 
 
@@ -173,9 +174,9 @@ for (f in batchfolders){
 					fileName = paste0("error_", s, ".err")
 					if (!file.exists(fileName)) {
 						#print("Error cannot file file")
-						next
+						#next
 					}
-					output_in = readLines(fileName)
+					#output_in = readLines(fileName)
 
 
 					# Is it done?
@@ -195,23 +196,31 @@ for (f in batchfolders){
 						next
 					}
 					finish.date = getDateTime(finish.date)
-					runtime.hr = as.numeric(finish.date - start.date)
+					
+					
[…]

### 2020-08-26 benchmarking/benchmarkingVM/ESS_round1_catquant.tex
results update

--- 2020-08-10 benchmarking/benchmarkingVM/ESS_round1_catquant.tex
@@
-% Created by tikzDevice version 0.12.3 on 2020-08-10 13:51:28
+% Created by tikzDevice version 0.12.3.1 on 2020-08-25 15:33:04
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,374.64) --
-	(203.52,578.16);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (286.65,578.16) --
-	(286.65,490.17) --
-	(  0.00,203.52);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (  0.00,346.12) --
-	(232.04,578.16);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (286.65,578.16) --
-	(286.65,518.69) --
-	(  0.00,232.04);
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (  0.00,317.60) --
-	(260.56,578.16);
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (286.65,578.16) --
-	(286.65,547.21) --
-	(  0.00,260.56);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (142.89,342.31) {$\frac{1}{64} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,435.87) {$64\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (114.37,342.31) {$\frac{1}{16} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,407.35) {$16\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 84.20,342.31) {$\frac{1}{4} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92,378.83) {$4\times$};
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,528.36);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 94.65,416.78) --
-	(103.65,416.78);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.64,409.37) --
-	( 99.64,422.22);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 99.64,413.56) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.25,476.46) --
-	(190.95,476.46);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.73,475.74) --
-	(188.73,477.16);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.73,472.43) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.21,474.21) --
-	(104.27,474.21);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (102.34,473.61) --
-	(102.34,474.79);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (102.34,470.18) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.11,416.10) --
-	(103.73,416.10);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.87,410.35) --
-	( 99.87,420.59);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 99.87,412.07) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.40,387.89) --
-	(115.90,387.89);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (106.65,384.62) --
-	(106.65,390.72);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (106.65,384.99) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.54,483.66) --
-	(195.01,483.66);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.29,483.25) --
-	(194.29,484.06);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.29,480.76) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.24,453.03) --
-	(151.45,453.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.58,451.65) --
-	(148.58,454.32);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (148.58,449.80) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.12,479.26) --
-	(197.83,479.26);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.99,477.50) --
-	(196.99,480.89);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.99,475.23) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.36,483.73) --
-	(188.58,483.73);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.98,483.50) --
-	(187.98,483.96);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.98,479.70) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.83,449.81) --
-	(142.53,449.81);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.76,448.18) --
-	(140.76,451.31);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (140.76,445.77) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.30,448.54) --
-	(152.66,448.54);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (149.31,447.26) --
-	(149.31,449.74);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (149.31,445.63) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.59,488.02) --
-	(199.40,488.02);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (199.00,487.58) --
-	(199.00,488.46);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.00,485.12) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.84,422.09) --
-	(126.52,422.09);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (122.64,409.09) --
-	(122.64,429.99);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (122.64,418.86) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.62,458.97) --
-	(195.24,458.97);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.51,454.93) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.66,477.15) --
-	(163.23,477.15);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.95,476.14) --
-	(162.95,478.11);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (162.95,473.11) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.91,421.56) --
-	(120.70,421.56);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.17,406.76) --
-	(117.17,430.08);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (117.17,417.53) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (124.20,409.98) --
-	(134.18,409.98);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.79,405.95) --
-	(129.79,413.35);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (129.79,407.07) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.21,485.10) --
-	(197.03,485.10);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.62,484.28) --
-	(196.62,485.89);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.62,482.19) {$\kappa$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.77,432.05) --
-	(140.26,432.05);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (135.68,429.18) --
-	(135.68,434.57);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (135.68,428.82) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.99,483.34) --
-	(200.70,483.34);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (199.86,480.63) --
-	(199.86,485.72);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.86,479.30) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.36,482.25) --
-	(177.58,482.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.47,482.07) --
-	(177.47,482.44);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.47,478.22) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (133.12,451.72) --
-	(147.88,451.72);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (141.79,449.82) --
-	(141.79,453.46);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (141.79,447.69) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (136.74,437.84) --
-	(147.60,437.84);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (142.88,434.82) --
-	(142.88,440.47);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (142.88,434.94) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.27,487.58) --
-	(198.98,487.58);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.14,487.05) --
-	(198.14,488.10);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.14,484.68) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.42,460.68) --
-	(181.15,460.68);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.37,456.94) --
-	(179.37,463.84);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.37,457.45) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.94,486.46) --
-	(184.37,486.46);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.33,482.75) --
-	(176.33,489.60);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.33,482.42) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.15,482.18) --
-	(197.23,482.18);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.69,481.57) --
-	(196.69,482.78);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.69,478.15) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.45,441.52) --
-	(161.00,441.52);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (157.57,436.94) --
-	(157.57,445.26);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (157.57,437.48) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.01,463.73) --
-	(184.30,463.73);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.82,459.32) --
-	(181.82,467.36);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.82,460.82) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.90,498.16) --
-	(211.56,498.16);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.27,495.77) --
-	(210.27,500.30);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.27,495.25) {$\kappa$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.64,472.51) --
-	(197.79,472.51);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.95,470.68) --
-	(194.95,474.19);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.95,469.28) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.60,491.62) --
-	(178.99,491.62);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.91,490.07) --
-	(176.91,493.06);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.91,487.58) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.25,482.68) --
-	(197.61,482.68);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.43,482.27) --
-	(197.43,483.09);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.43,478.65) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.17,459.25) --
-	(178.40,459.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.85,457.81) --
-	(176.85,460.59);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.85,455.21) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.79,467.29) --
-	(192.74,467.29);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.37,464.24) --
-	(185.37,469.95);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.37,464.39) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.72,501.36) --
-	(212.84,501.36);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.78,500.78) --
-	(212.78,501.94);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.78,498.46) {$\kappa$};
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (  0.00,368.65) --
+	(209.51,578.16);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (283.33,578.16) --
+	(283.33,492.84) --
+	(  0.00,209.51);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,342.13) --
+	(236.03,578.16);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (283.33,578.16) --
+	(283.33,519.37) --
+	(  0.00,236.03);
+
+\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round] (  0.00,315.60) --
+	(262.56,578.16);
+
+\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round] (283.33,578.16) --
+	(283.33,545.89) --
+	(  0.00,262.56);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (136.90,342.31) {$\frac{1}{64} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,429.88) {$64\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (110.38,342.31) {$\frac{1}{16} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,403.36) {$16\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 82.20,342.31) {$\frac{1}{4} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92,376.84) {$4\times$};
+
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,528.36);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 92.06,411.70) --
+	(103.71,411.70);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 98.76,408.30) --
+	( 98.76,414.58);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 98.76,408.47) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (127.75,461.51) --
+	(136.14,461.51);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (132.40,460.16) --
+	(132.40,462.77);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (132.40,457.48) {$L$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 86.72,453.05) --
+	( 91.82,453.05);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 89.44,452.87) --
+	( 89.44,453.23);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 89.44,449.02) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 86.78,407.42) --
+	( 95.88,407.42);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 91.87,400.23) --
+	( 91.87,412.63);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 91.87,403.39) {$h$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 53.22,385.02) --
+	( 67.16,385.02);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 61.43,375.09) --
+	( 61.43,391.53);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 61.43,382.12) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (170.05,459.14) --
+	(170.79,459.14);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (170.42,458.74) --
+	(170.42,459.52);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (170.42,456.23) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.41,484.07) --
+	(203.29,484.07);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.75,480.26) --
+	(199.75,487.25);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.75,480.85) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.32,468.85) --
+	(182.12,468.85);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.02,464.40) --
+	(179.02,472.46);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.02,464.82) {$L$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (202.56,499.80) --
+	(209.12,499.80);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (206.12,496.65) --
+	(206.12,502.51);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (206.12,495.77) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.18,479.04) --
+	(195.29,479.04);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.66,476.43) --
+	(191.66,481.33);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.66,475.00) {$h$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (197.75,482.46) --
+	(204.87,482.46);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (201.64,479.93) --
+	(201.64,484.70);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (201.64,479.56) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (207.07,499.42) --
+	(214.51,499.42);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.15,496.11) --
+	(211.15,502.24);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.15,496.51) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (141.42,439.64) --
+	(145.39,439.64);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (143.51,437.79) --
+	(143.51,441.33);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (143.51,436.42) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.24,465.61) --
+	(175.56,465.61);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.52,463.95) --
+	(173.52,467.13);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.52,461.57) {$L$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.84,485.78) --
+	(195.64,485.78);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.76,485.39) --
+	(194.76,486.16);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.76,481.74) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (130.58,426.42) --
+	(135.71,426.42);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (133.32,424.17) --
+	(133.32,428.43);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (133.32,422.38) {$h$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.34,443.92) --
+	(161.79,443.92);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (156.91,440.58) --
+	(156.91,446.77);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (156.91,441.02) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (197.72,485.55) --
+	(199.65,485.55);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.71,485.16) --
+	(198.71,485.94);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.71,482.65) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (159.25,461.02) --
+	(162.39,461.02);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (160.88,460.40) --
+	(160.88,461.62);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (160.88,457.79) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (162.17,460.73) --
+	(166.45,460.73);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.43,458.38) --
+	(164.43,462.82);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (164.43,456.70) {$L$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.93,485.98) --
+	(191.45,485.98);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.19,485.77) --
+	(191.19,486.19);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.19,481.95) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (147.67,456.98) --
+	(154.15,456.98);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.19,455.19) --
+	(151.19,458.61);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (151.19,452.94) {$h$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.17,453.18) --
+	(158.44,453.18);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (154.75,451.58) --
+	(154.75,454.65);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (154.75,450.27) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.83,488.43) --
+	(200.35,488.43);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (200.09,487.96) --
+	(200.09,488.88);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (200.09,485.52) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (119.54,419.45) --
+	(125.87,419.45);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (122.97,413.25) --
+	(122.97,424.13);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (122.97,416.23) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (156.29,461.77) --
+	(162.87,461.77);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (159.86,457.79) --
+	(159.86,465.07);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (159.86,457.74) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (154.77,462.26) --
+	(155.59,462.26);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (155.19,457.82) --
+	(155.19,465.86);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (155.19,458.22) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (111.36,420.07) --
+	(124.02,420.07);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (118.72,413.64) --
+	(118.72,424.87);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (118.72,416.04) {$h$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (125.89,409.29) --
+	(132.73,409.29);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (129.61,403.87) --
+	(129.61,413.52);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (129.61,406.39) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.91,467.12) --
+	(183.92,467.12);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.42,462.81) --
+	(183.42,470.64);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.42,464.22) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.12,483.47) --
+	(204.02,483.47);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (201.73,479.04) --
+	(201.73,487.06);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (201.73,480.24) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.89,472.43) --
+	(186.13,472.43);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.58,468.48) --
+	(184.58,475.70);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.58,468.39) {$L$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (210.72,493.14) --
+	(214.50,493.14);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (212.70,490.14) --
+	(212.70,495.73);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.70,489.11) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.99,463.39) --
+	(177.57,463.39);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.42,458.68) --
+	(175.42,467.17);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (175.42,459.36) {$h$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.79,473.24) --
+	(188.18,473.24);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.56,467.69) --
+	(186.56,477.54);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (186.56,470.34) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (202.34,492.07) --
+	(206.48,492.07);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (204.52,488.90) --
+	(204.52,494.79);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (204.52,489.16) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (154.78,452.89) --
+	(160.59,452.89);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (157.90,450.01) --
+	(157.90,455.39);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (157.90,449.66) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.87,482.15) --
+	(200.95,482.15);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.93,480.40) --
+	(199.93,483.76);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.93,478.12) {$L$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.09,490.74) --
+	(188.57,490.74);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.37,490.40) --
+	(187.37,491.07);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.37,486.70) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (156.27,465.34) --
+	(163.66,465.34);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (160.32,463.67) --
+	(160.32,466.88);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (160.32,461.31) {$h$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (158.86,454.59) --
+	(164.47,454.59);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.87,453.07) --
+	(161.87,456.01);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (161.87,451.69) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (203.38,492.98) --
+	(205.35,492.98);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (204.39,491.80) --
+	(204.39,494.09);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (204.39,490.07) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.62,458.20) --
+	(175.50,458.20);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.11,457.24) --
+	(174.11,459.12);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.11,454.97) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.11,449.29) --
+	(152.12,449.29);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.67,445.56) --
+	(150.67,452.41);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (150.67,445.26) {$L$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.33,471.24) --
+	(185.73,471.24);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.05,471.11) --
+	(185.05,471.37);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.05,467.21) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.22,445.85) --
+	(159.90,445.85);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (156.45,439.59) --
+	(156.45,450.57);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (156.45,441.82) {$h$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.57,455.90) --
+	(162.87,455.90);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (157.69,453.42) --
+	(157.69,458.09);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (157.69,452.99) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.38,485.12) --
+	(196.78,485.12);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.09,484.12) --
+	(196.09,486.06);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.09,482.21) {$\kappa$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.91,469.41) --
+	(194.38,469.41);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.19,468.77) --
+	(193.19,470.02);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.19,466.18) {$p$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.83,464.80) --
+	(184.74,464.80);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.88,462.76) --
+	(182.88,466.64);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.88,460.77) {$L$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.66,477.27) --
+	(198.99,477.27);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.95,477.03) --
+	(196.95,477.51);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.95,473.24) {$r$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (177.86,459.46) --
+	(182.29,459.46);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.20,458.11) --
+	(180.20,460.72);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.20,455.43) {$h$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.44,462.61) --
+	(188.89,462.61);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.79,461.80) --
+	(186.79,463.38);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (186.79,459.70) {$\sigma$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (205.09,492.28) --
+	(209.17,492.28);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (207.24,491.61) --
+	(207.24,492.93);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.24,489.37) {$\kappa$};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (149.40,234.96) --
-	(492.60,578.16);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (575.73,578.16) --
-	(575.73,490.17) --
-	(149.40, 63.84) --
-	(149.40,234.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (149.40,206.44) --
-	(521.12,578.16);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (575.73,578.16) --
-	(575.73,518.69) --
-	(149.40, 92.36) --
-	(149.40,206.44);
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (149.40,177.92) --
-	(549.64,578.16);
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (575.73,578.16) --
-	(575.73,547.21) --
-	(149.40,120.88) --
-	(149.40,177.92);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (431.97,342.31) {$\frac{1}{64} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,435.87) {$64\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (403.45,342.31) {$\frac{1}{16} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,407.35) {$16\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (373.28,342.31) {$\frac{1}{4} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.00,378.83) {$4\times$};
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (338.88,338.88) -- (528.36,528.36);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (383.73,398.02) --
-	(392.73,398.02);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (388.72,382.13) --
-	(388.72,406.87);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (388.72,394.79) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (475.33,475.91) --
-	(480.03,475.91);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.81,475.07) --
-	(477.81,476.72);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (477.81,471.88) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.29,472.93) --
-	(393.35,472.93);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (391.42,468.95) --
-	(391.42,476.26);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (391.42,468.89) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (384.19,397.74) --
-	(392.81,397.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (388.95,377.39) --
-	(388.95,407.77);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (388.95,393.71) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (378.48,366.19) --
-	(404.98,366.19);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (395.73,357.18) --
-	(395.73,372.44);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (395.73,363.29) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.62,483.32) --
-	(484.09,483.32);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.37,483.08) --
-	(483.37,483.56);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.37,480.42) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (434.32,451.80) --
-	(440.53,451.80);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (437.66,446.77) --
-	(437.66,455.84);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (437.66,448.57) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.20,479.84) --
-	(486.91,479.84);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.07,478.07) --
-	(486.07,481.48);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (486.07,475.81) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.44,483.86) --
-	(477.66,483.86);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.06,481.92) --
-	(477.06,485.64);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (477.06,479.83) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.91,449.16) --
-	(431.61,449.16);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (429.84,442.38) --
-	(429.84,454.24);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (429.84,445.12) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (434.38,448.12) --
-	(441.74,448.12);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.39,445.55) --
-	(438.39,450.42);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (438.39,445.22) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (487.67,488.03) --
-	(488.48,488.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (488.08,487.64) --
-	(488.08,488.41);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (488.08,485.12) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (406.92,424.00) --
-	(415.60,424.00);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (411.72,420.41) --
-	(411.72,427.05);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (411.72,420.77) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (480.70,478.83) --
-	(484.32,478.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.59,474.57) --
-	(482.59,482.36);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (482.59,474.80) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (451.74,476.83) --
-	(452.31,476.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (452.03,476.28) --
-	(452.03,477.36);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (452.03,472.79) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (401.99,423.32) --
-	(409.78,423.32);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (406.25,420.99) --
-	(406.25,425.41);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (406.25,419.28) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (413.28,406.71) --
-	(423.26,406.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.87,404.60) --
-	(418.87,408.64);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (418.87,403.81) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.29,485.22) --
-	(486.11,485.22);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.70,485.09) --
-	(485.70,485.35);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (485.70,482.32) {$\kappa$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.85,435.95) --
-	(429.34,435.95);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (424.76,433.40) --
-	(424.76,438.22);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (424.76,432.72) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (488.07,482.85) --
-	(489.78,482.85);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (488.94,480.61) --
-	(488.94,484.87);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (488.94,478.82) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (466.44,482.85) --
-	(466.66,482.85);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (466.55,482.61) --
-	(466.55,483.09);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (466.55,478.82) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (422.20,450.41) --
-	(436.96,450.41);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (430.87,447.63) --
-	(430.87,452.86);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (430.87,446.38) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (425.82,440.09) --
-	(436.68,440.09);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (431.96,437.76) --
-	(431.96,442.18);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (431.96,437.18) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.35,487.61) --
-	(488.06,487.61);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (487.22,485.91) --
-	(487.22,489.18);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (487.22,484.71) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (466.50,469.66) --
-	(470.23,469.66);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (468.45,467.06) --
-	(468.45,471.96);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.45,466.43) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (452.02,481.52) --
-	(473.45,481.52);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (465.41,478.07) --
-	(465.41,484.47);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (465.41,477.48) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.23,487.79) --
-	(486.31,487.79);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.77,487.17) --
-	(485.77,488.40);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (485.77,483.76) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (442.53,448.83) --
-	(450.08,448.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (446.65,445.54) --
-	(446.65,451.66);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (446.65,444.80) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (468.09,470.37) --
-	(473.38,470.37);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (470.90,468.48) --
-	(470.90,472.10);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (470.90,467.47) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (497.98,499.91) --
-	(500.64,499.91);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.35,499.32) --
-	(499.35,500.49);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (499.35,497.01) {$\kappa$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (480.72,484.41) --
-	(486.87,484.41);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (484.03,482.75) --
-	(484.03,485.95);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (484.03,481.19) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.68,490.90) --
-	(468.07,490.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (465.99,490.73) --
-	(465.99,491.06);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (465.99,486.86) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.33,489.03) --
-	(486.69,489.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.51,487.83) --
-	(486.51,490.17);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (486.51,485.00) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.25,467.22) --
-	(467.48,467.22);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (465.93,462.61) --
-	(465.93,470.98);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (465.93,463.19) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.87,475.23) --
-	(481.82,475.23);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.45,471.25) --
-	(474.45,478.57);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.45,472.33) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (501.80,501.33) --
-	(501.92,501.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (501.86,500.87) --
-	(501.86,501.77);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (501.86,498.42) {$\kappa$};
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (162.66,242.23) --
+	(498.59,578.16);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (572.41,578.16) --
+	(572.41,492.84) --
+	(162.66, 83.09) --
+	(162.66,242.23);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.66,215.71) --
+	(525.11,578.16);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (572.41,578.16) --
+	(572.41,519.37) --
+	(162.66,109.61) --
+	(162.66,215.71);
+
+\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round] (162.66,189.19) --
+	(551.64,578.16);
+
+\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round] (572.41,578.16) --
+	(572.41,545.89) --
+	(162.66,136.14) --
+	(162.66,189.19);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (425.98,342.31) {$\frac{1}{64} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,429.88) {$64\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (399.46,342.31) {$\frac{1}{16} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,403.36) {$16\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (371.28,342.31) {$\frac{1}{4} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.00,376.84) {$4\times$};
+
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (338.88,338.88) -- (528.36,528.36);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (381.14,422.82) --
+	(392.79,422.82);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (387.84,420.40) --
+	(387.84,424.97);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (387.84,419.59) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (416.83,452.57) --
+	(425.22,452.57);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (421.48,451.90) --
+	(421.48,453.22);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (421.48,448.54) {$L$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (375.80,446.67) --
+	(380.90,446.67);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (378.52,445.22) --
+	(378.52,448.02);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (378.52,442.64) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (375.86,418.52) --
+	(384.96,418.52);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (380.95,411.75) --
+	(380.95,423.52);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (380.95,414.49) {$h$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (342.30,430.80) --
+	(356.24,430.80);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (350.51,426.42) --
+	(350.51,434.36);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (350.51,427.90) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (459.13,451.20) --
+	(459.87,451.20);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (459.50,449.83) --
+	(459.50,452.49);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (459.50,448.30) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (484.49,486.05) --
+	(492.37,486.05);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (488.83,480.97) --
+	(488.83,490.06);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (488.83,482.83) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (464.40,467.41) --
+	(471.20,467.41);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (468.10,463.99) --
+	(468.10,470.31);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.10,463.37) {$L$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (491.64,498.84) --
+	(498.20,498.84);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (495.20,495.08) --
+	(495.20,501.97);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (495.20,494.80) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (476.26,480.02) --
+	(484.37,480.02);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.74,475.53) --
+	(480.74,483.64);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (480.74,475.98) {$h$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (486.83,495.85) --
+	(493.95,495.85);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (490.72,490.38) --
+	(490.72,500.09);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (490.72,492.94) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (496.15,497.26) --
+	(503.59,497.26);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (500.23,493.73) --
+	(500.23,500.23);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (500.23,494.35) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (430.50,444.25) --
+	(434.47,444.25);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (432.59,439.52) --
+	(432.59,448.04);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (432.59,441.02) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (460.32,464.46) --
+	(464.64,464.46);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (462.60,463.55) --
+	(462.60,465.34);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (462.60,460.43) {$L$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (482.92,486.64) --
+	(484.72,486.64);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.84,486.09) --
+	(483.84,487.17);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.84,482.60) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (419.66,430.01) --
+	(424.79,430.01);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (422.40,424.45) --
+	(422.40,434.32);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (422.40,425.98) {$h$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (439.42,453.02) --
+	(450.87,453.02);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (445.99,448.90) --
+	(445.99,456.41);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (445.99,450.12) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (486.80,484.52) --
+	(488.73,484.52);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (487.79,483.75) --
+	(487.79,485.27);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (487.79,481.62) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (448.33,455.28) --
+	(451.47,455.28);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (449.96,453.50) --
+	(449.96,456.90);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (449.96,452.05) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (451.25,455.59) --
+	(455.53,455.59);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (453.51,453.77) --
+	(453.51,457.25);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (453.51,451.56) {$L$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.01,481.09) --
+	(480.53,481.09);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.27,480.69) --
+	(480.27,481.49);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (480.27,477.06) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (436.75,455.34) --
+	(443.23,455.34);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (440.27,453.12) --
+	(440.27,457.33);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (440.27,451.30) {$h$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (439.25,459.26) --
+	(447.52,459.26);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (443.83,456.93) --
+	(443.83,461.33);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (443.83,456.35) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (488.91,482.35) --
+	(489.43,482.35);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (489.17,481.98) --
+	(489.17,482.72);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (489.17,479.45) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (408.62,419.90) --
+	(414.95,419.90);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (412.05,418.40) --
+	(412.05,421.29);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (412.05,416.67) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (445.37,458.29) --
+	(451.95,458.29);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (448.94,456.11) --
+	(448.94,460.25);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (448.94,454.26) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (443.85,457.12) --
+	(444.67,457.12);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (444.27,456.64) --
+	(444.27,457.60);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (444.27,453.09) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (400.44,419.27) --
+	(413.10,419.27);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (407.80,417.46) --
+	(407.80,420.93);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (407.80,415.24) {$h$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (414.97,431.53) --
+	(421.81,431.53);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (418.69,428.40) --
+	(418.69,434.22);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (418.69,428.63) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (471.99,463.25) --
+	(473.00,463.25);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (472.50,463.00) --
+	(472.50,463.51);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (472.50,460.35) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (488.20,491.43) --
+	(493.10,491.43);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (490.81,488.34) --
+	(490.81,494.10);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (490.81,488.21) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (471.97,473.26) --
+	(475.21,473.26);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (473.66,469.46) --
+	(473.66,476.43);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (473.66,469.23) {$L$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (499.80,500.72) --
+	(503.58,500.72);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (501.78,497.68) --
+	(501.78,503.35);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (501.78,496.69) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (462.07,462.90) --
+	(466.65,462.90);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (464.50,459.58) --
+	(464.50,465.73);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (464.50,458.87) {$h$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (473.87,477.19) --
+	(477.26,477.19);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (475.64,474.02) --
+	(475.64,479.91);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (475.64,474.29) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (491.42,491.09) --
+	(495.56,491.09);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (493.60,488.28) --
+	(493.60,493.53);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (493.60,488.18) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (443.86,453.47) --
+	(449.67,453.47);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (446.98,449.31) --
+	(446.98,456.88);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (446.98,450.24) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (487.95,485.02) --
+	(490.03,485.02);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (489.01,483.20) --
+	(489.01,486.68);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (489.01,480.99) {$L$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (475.17,489.36) --
+	(477.65,489.36);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (476.45,488.95) --
+	(476.45,489.76);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (476.45,485.33) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (445.35,461.95) --
+	(452.74,461.95);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (449.40,456.35) --
+	(449.40,466.27);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (449.40,457.91) {$h$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (447.94,466.97) --
+	(453.55,466.97);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (450.95,463.63) --
+	(450.95,469.80);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (450.95,464.06) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (492.46,491.31) --
+	(494.43,491.31);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (493.47,489.94) --
+	(493.47,492.58);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (493.47,488.40) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (461.70,458.77) --
+	(464.58,458.77);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (463.19,456.24) --
+	(463.19,461.00);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (463.19,455.54) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (438.19,441.13) --
+	(441.20,441.13);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (439.75,438.18) --
+	(439.75,443.68);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (439.75,437.10) {$L$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (473.41,472.82) --
+	(474.81,472.82);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (474.13,472.59) --
+	(474.13,473.05);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.13,468.79) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (441.30,443.82) --
+	(448.98,443.82);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (445.53,439.42) --
+	(445.53,447.40);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (445.53,439.79) {$h$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (439.65,458.10) --
+	(451.95,458.10);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (446.77,453.81) --
+	(446.77,461.61);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (446.77,455.20) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (484.46,481.91) --
+	(485.86,481.91);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (485.17,481.83) --
+	(485.17,481.99);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (485.17,479.00) {$\kappa$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.99,478.97) --
+	(483.46,478.97);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (482.27,467.29) --
+	(482.27,486.16);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (482.27,475.74) {$p$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (469.91,465.38) --
+	(473.82,465.38);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (471.96,453.39) --
+	(471.96,472.69);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (471.96,461.35) {$L$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.74,482.47) --
+	(488.07,482.47);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (486.03,470.56) --
+	(486.03,489.76);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (486.03,478.44) {$r$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (466.94,464.45) --
+	(471.37,464.45);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (469.28,451.93) --
+	(469.28,471.95);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (469.28,460.42) {$h$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (473.52,474.07) --
+	(477.97,474.07);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (475.87,462.11) --
+	(475.87,481.38);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (475.87,471.17) {$\sigma$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (494.17,491.37) --
+	(498.25,491.37);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (496.32,479.32) --
+	(496.32,498.71);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (496.32,488.47) {$\kappa$};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00, 85.56) --
-	(286.65,372.21) --
-	(286.65,201.09) --
-	( 85.56,  0.00);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (  0.00, 57.04) --
-	(286.65,343.69) --
-	(286.65,229.61) --
-	( 57.04,  0.00);
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (  0.00, 28.52) --
-	(286.65,315.17) --
-	(286.65,258.13) --
-	( 28.52,  0.00);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (142.89, 53.23) {$\frac{1}{64} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,146.79) {$64\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (114.37, 53.23) {$\frac{1}{16} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,118.27) {$16\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 84.20, 53.23) {$\frac{1}{4} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92, 89.75) {$4\times$};
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] ( 49.80, 49.80) -- (239.28,239.28);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.29,108.94) --
-	(133.14,108.94);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (127.70, 93.05) --
-	(127.70,117.79);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (127.70,105.71) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.66,186.83) --
-	(188.08,186.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.38,185.99) --
-	(187.38,187.64);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.38,182.80) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.53,183.85) --
-	(185.71,183.85);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.13,179.87) --
-	(185.13,187.18);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.13,179.81) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.27,108.66) --
-	(131.51,108.66);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (127.02, 88.31) --
-	(127.02,118.69);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (127.02,104.63) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.54, 77.11) --
-	(101.64, 77.11);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 98.81, 68.10) --
-	( 98.81, 83.36);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 98.81, 74.21) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.17,194.24) --
-	(194.98,194.24);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.58,194.00) --
-	(194.58,194.48);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.58,191.34) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.57,162.72) --
-	(165.24,162.72);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.95,157.69) --
-	(163.95,166.76);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (163.95,159.49) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.42,190.76) --
-	(191.81,190.76);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.18,188.99) --
-	(190.18,192.40);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.18,186.73) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.42,194.78) --
-	(194.88,194.78);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.65,192.84) --
-	(194.65,196.56);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.65,190.75) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.10,160.08) --
-	(162.23,160.08);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.73,153.30) --
-	(160.73,165.16);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (160.73,156.04) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.18,159.04) --
-	(160.66,159.04);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.46,156.47) --
-	(159.46,161.34);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (159.46,156.14) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.50,198.95) --
-	(199.38,198.95);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.94,198.56) --
-	(198.94,199.33);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.94,196.04) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.01,134.92) --
-	(140.91,134.92);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (133.01,131.33) --
-	(133.01,137.97);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (133.01,131.69) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.89,185.49) --
-	(169.89,193.28);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.89,185.72) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.06,187.75) --
-	(189.03,187.75);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.07,187.20) --
-	(188.07,188.28);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.07,183.71) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.68,134.24) --
-	(141.00,134.24);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (132.48,131.91) --
-	(132.48,136.33);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (132.48,130.20) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (116.87,117.63) --
-	(124.27,117.63);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.90,115.52) --
-	(120.90,119.56);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (120.90,114.73) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.20,196.14) --
-	(196.81,196.14);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.02,196.01) --
-	(196.02,196.27);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.02,193.24) {$\kappa$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.10,146.87) --
-	(145.49,146.87);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (142.97,144.32) --
-	(142.97,149.14);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (142.97,143.64) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.55,193.77) --
-	(196.64,193.77);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.26,191.53) --
-	(194.26,195.79);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.26,189.74) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.99,193.77) --
-	(193.36,193.77);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.17,193.53) --
-	(193.17,194.01);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.17,189.74) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.74,161.33) --
-	(164.38,161.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.64,158.55) --
-	(162.64,163.78);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (162.64,157.30) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.74,151.01) --
-	(151.39,151.01);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.76,148.68) --
-	(148.76,153.10);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (148.76,148.10) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.97,198.53) --
-	(199.02,198.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.50,196.83) --
-	(198.50,200.10);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.50,195.63) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (167.86,180.58) --
-	(174.76,180.58);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.60,177.98) --
-	(171.60,182.88);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.60,177.35) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.67,192.44) --
-	(200.52,192.44);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.38,188.99) --
-	(197.38,195.39);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.38,188.40) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.49,198.71) --
-	(193.70,198.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.10,198.09) --
-	(193.10,199.32);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.10,194.68) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (147.86,159.75) --
-	(156.18,159.75);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (152.44,156.46) --
-	(152.44,162.58);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (152.44,155.72) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (170.24,181.29) --
-	(178.28,181.29);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.65,179.40) --
-	(174.65,183.02);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.65,178.39) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.69,210.83) --
-	(211.22,210.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.08,210.24) --
-	(209.08,211.41);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.08,207.93) {$\kappa$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.60,195.33) --
-	(185.11,195.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (183.43,193.67) --
-	(183.43,196.87);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.43,192.11) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.99,201.82) --
-	(203.98,201.82);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (202.54,201.65) --
-	(202.54,201.98);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.54,197.78) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.19,199.95) --
-	(194.01,199.95);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.60,198.75) --
-	(193.60,201.09);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.60,195.92) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.73,178.14) --
-	(171.51,178.14);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (170.17,173.53) --
-	(170.17,181.90);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (170.17,174.11) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.16,186.15) --
-	(180.87,186.15);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (178.21,182.17) --
-	(178.21,189.49);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (178.21,183.25) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.70,212.25) --
-	(212.86,212.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.28,211.79) --
-	(212.28,212.69);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.28,209.34) {$\kappa$};
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (  0.00, 79.57) --
+	(283.33,362.91) --
+	(283.33,203.76) --
+	( 79.57,  0.00);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00, 53.05) --
+	(283.33,336.38) --
+	(283.33,230.29) --
+	( 53.05,  0.00);
+
+\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round] (  0.00, 26.52) --
+	(283.33,309.86) --
+	(283.33,256.81) --
+	( 26.52,  0.00);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (136.90, 53.23) {$\frac{1}{64} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,140.80) {$64\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (110.38, 53.23) {$\frac{1}{16} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,114.28) {$16\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 82.20, 53.23) {$\frac{1}{4} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92, 87.76) {$4\times$};
+
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 49.80, 49.80) -- (239.28,239.28);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (119.22,133.74) --
+	(125.50,133.74);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (122.62,131.32) --
+	(122.62,135.89);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (122.62,130.51) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.08,163.49) --
+	(173.69,163.49);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.43,162.82) --
+	(172.43,164.14);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.43,159.46) {$L$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (163.79,157.59) --
+	(164.15,157.59);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (163.97,156.14) --
+	(163.97,158.94);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (163.97,153.56) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (111.15,129.44) --
+	(123.55,129.44);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (118.34,122.67) --
+	(118.34,134.44);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (118.34,125.41) {$h$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 86.01,141.72) --
+	(102.45,141.72);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 95.94,137.34) --
+	( 95.94,145.28);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 95.94,138.82) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.66,162.12) --
+	(170.44,162.12);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (170.06,160.75) --
+	(170.06,163.41);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (170.06,159.22) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.18,196.97) --
+	(198.17,196.97);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.99,191.89) --
+	(194.99,200.98);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.99,193.75) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.32,178.33) --
+	(183.38,178.33);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.77,174.91) --
+	(179.77,181.23);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.77,174.29) {$L$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (207.57,209.76) --
+	(213.43,209.76);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (210.72,206.00) --
+	(210.72,212.89);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.72,205.72) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.35,190.94) --
+	(192.25,190.94);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.96,186.45) --
+	(189.96,194.56);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (189.96,186.90) {$h$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.85,206.77) --
+	(195.62,206.77);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.38,201.30) --
+	(193.38,211.01);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.38,203.86) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (207.03,208.18) --
+	(213.16,208.18);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (210.34,204.65) --
+	(210.34,211.15);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.34,205.27) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (148.71,155.17) --
+	(152.25,155.17);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.56,150.44) --
+	(150.56,158.96);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (150.56,151.94) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.87,175.38) --
+	(178.05,175.38);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.53,174.47) --
+	(176.53,176.26);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.53,171.35) {$L$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.31,197.56) --
+	(197.08,197.56);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.70,197.01) --
+	(196.70,198.09);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.70,193.52) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (135.09,140.93) --
+	(139.35,140.93);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (137.34,135.37) --
+	(137.34,145.24);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (137.34,136.90) {$h$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.50,163.94) --
+	(157.69,163.94);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (154.84,159.82) --
+	(154.84,167.33);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (154.84,161.04) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.08,195.44) --
+	(196.86,195.44);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.47,194.67) --
+	(196.47,196.19);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.47,192.54) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.32,166.20) --
+	(172.54,166.20);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.94,164.42) --
+	(171.94,167.82);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.94,162.97) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.30,166.51) --
+	(173.74,166.51);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.65,164.69) --
+	(171.65,168.17);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.65,162.48) {$L$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.69,192.01) --
+	(197.11,192.01);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.90,191.61) --
+	(196.90,192.41);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.90,187.98) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (166.11,166.26) --
+	(169.53,166.26);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (167.90,164.04) --
+	(167.90,168.25);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (167.90,162.22) {$h$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (162.50,170.18) --
+	(165.57,170.18);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.10,167.85) --
+	(164.10,172.25);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (164.10,167.27) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.88,193.27) --
+	(199.80,193.27);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.35,192.90) --
+	(199.35,193.64);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.35,190.37) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (124.17,130.82) --
+	(135.05,130.82);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (130.37,129.32) --
+	(130.37,132.21);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (130.37,127.59) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.71,169.21) --
+	(175.99,169.21);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.69,167.03) --
+	(172.69,171.17);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.69,165.18) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.74,168.04) --
+	(176.78,168.04);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.18,167.56) --
+	(173.18,168.52);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.18,164.01) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (124.56,130.19) --
+	(135.79,130.19);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (130.99,128.38) --
+	(130.99,131.85);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (130.99,126.16) {$h$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (114.79,142.45) --
+	(124.44,142.45);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (120.21,139.32) --
+	(120.21,145.14);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (120.21,139.55) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.73,174.17) --
+	(181.56,174.17);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.04,173.92) --
+	(178.04,174.43);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (178.04,171.27) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.96,202.35) --
+	(197.98,202.35);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.39,199.26) --
+	(194.39,205.02);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.39,199.13) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.40,184.18) --
+	(186.62,184.18);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.35,180.38) --
+	(183.35,187.35);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.35,180.15) {$L$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (201.06,211.64) --
+	(206.65,211.64);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (204.06,208.60) --
+	(204.06,214.27);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (204.06,207.61) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.60,173.82) --
+	(178.09,173.82);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.31,170.50) --
+	(174.31,176.65);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.31,169.79) {$h$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.61,188.11) --
+	(188.46,188.11);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.16,184.94) --
+	(184.16,190.83);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.16,185.21) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.82,202.01) --
+	(205.71,202.01);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (202.99,199.20) --
+	(202.99,204.45);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.99,199.10) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (160.93,164.39) --
+	(166.31,164.39);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (163.81,160.23) --
+	(163.81,167.80);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (163.81,161.16) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.32,195.94) --
+	(194.68,195.94);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.07,194.12) --
+	(193.07,197.60);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.07,191.91) {$L$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (201.32,200.28) --
+	(201.99,200.28);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (201.66,199.87) --
+	(201.66,200.68);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (201.66,196.25) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.59,172.87) --
+	(177.80,172.87);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.26,167.27) --
+	(176.26,177.19);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.26,168.83) {$h$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (163.99,177.89) --
+	(166.93,177.89);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (165.51,174.55) --
+	(165.51,180.72);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (165.51,174.98) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (202.72,202.23) --
+	(205.01,202.23);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (203.90,200.86) --
+	(203.90,203.50);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (203.90,199.32) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.16,169.69) --
+	(170.04,169.69);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.12,167.16) --
+	(169.12,171.92);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.12,166.46) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (156.48,152.05) --
+	(163.33,152.05);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (160.21,149.10) --
+	(160.21,154.60);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (160.21,148.02) {$L$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.03,183.74) --
+	(182.29,183.74);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.16,183.51) --
+	(182.16,183.97);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.16,179.71) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.51,154.74) --
+	(161.49,154.74);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (156.77,150.34) --
+	(156.77,158.32);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (156.77,150.71) {$h$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.34,169.02) --
+	(169.01,169.02);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (166.82,164.73) --
+	(166.82,172.53);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (166.82,166.12) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.04,192.83) --
+	(196.98,192.83);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.04,192.75) --
+	(196.04,192.91);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.04,189.92) {$\kappa$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.69,189.89) --
+	(180.94,189.89);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.33,178.21) --
+	(180.33,197.08);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.33,186.66) {$p$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.68,176.30) --
+	(177.56,176.30);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.72,164.31) --
+	(175.72,183.61);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (175.72,172.27) {$L$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.95,193.39) --
+	(188.43,193.39);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.19,181.48) --
+	(188.19,200.68);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.19,189.36) {$r$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.03,175.37) --
+	(171.64,175.37);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (170.38,162.85) --
+	(170.38,182.87);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (170.38,171.34) {$h$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.72,184.99) --
+	(174.30,184.99);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.53,173.03) --
+	(173.53,192.30);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.53,182.09) {$\sigma$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (202.53,202.29) --
+	(203.85,202.29);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (203.20,190.24) --
+	(203.20,209.63);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (203.20,199.39) {$\kappa$};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.52,  0.00) --
-	(575.73,372.21) --
-	(575.73,201.09) --
-	(374.64,  0.00);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (232.04,  0.00) --
-	(575.73,343.69) --
-	(575.73,229.61) --
-	(346.12,  0.00);
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (260.56,  0.00) --
-	(575.73,315.17) --
-	(575.73,258.13) --
-	(317.60,  0.00);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (431.97, 53.23) {$\frac{1}{64} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,146.79) {$64\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (403.45, 53.23) {$\frac{1}{16} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,118.27) {$16\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (373.28, 53.23) {$\frac{1}{4} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.00, 89.75) {$4\times$};
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (338.88, 49.80) -- (528.36,239.28);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (369.53,100.95) --
-	(401.69,100.95);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (391.34, 96.83) --
-	(391.34,104.39);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (391.34, 97.73) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (469.11,180.21) --
-	(478.54,180.21);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.36,157.25) --
-	(474.36,190.79);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.36,176.18) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (378.71, 99.41) --
-	(392.60, 99.41);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (386.80, 95.00) --
-	(386.80,103.04);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (386.80, 95.37) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (379.87,102.83) --
-	(403.10,102.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (394.60,100.19) --
-	(394.60,105.17);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (394.60, 98.80) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (373.83, 90.46) --
-	(386.33, 90.46);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (381.02, 83.73) --
-	(381.02, 95.52);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (381.02, 87.56) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.33,194.78) --
-	(484.25,194.78);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.79,194.57) --
-	(483.79,194.99);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.79,191.87) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (403.60,109.49) --
-	(412.89,109.49);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (408.76, 99.61) --
-	(408.76,116.13);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (408.76,106.26) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.33,191.83) --
-	(481.58,191.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.56,190.07) --
-	(479.56,193.44);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (479.56,187.79) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (448.80,164.69) --
-	(449.61,164.69);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (449.21,164.54) --
-	(449.21,164.84);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (449.21,160.65) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (402.13,107.26) --
-	(410.13,107.26);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (406.52,100.97) --
-	(406.52,112.07);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (406.52,103.23) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (394.71,110.51) --
-	(411.65,110.51);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (404.88,103.25) --
-	(404.88,115.87);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (404.88,107.61) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.25,196.27) --
-	(485.92,196.27);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.59,196.12) --
-	(485.59,196.43);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (485.59,193.37) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.30,177.43) --
-	(465.23,177.43);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (460.48,172.15) --
-	(460.48,181.63);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (460.48,174.20) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.33,174.98) --
-	(474.75,174.98);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.90,158.21) --
-	(461.90,184.09);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (461.90,170.94) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (480.68,197.38) --
-	(482.70,197.38);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (481.71,196.98) --
-	(481.71,197.78);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (481.71,193.35) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (436.28,158.71) --
-	(449.09,158.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.66,150.24) --
-	(443.66,164.70);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (443.66,154.68) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.65,180.86) --
-	(466.79,180.86);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (465.75,178.58) --
-	(465.75,182.90);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (465.75,177.95) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.10,210.49) --
-	(500.73,210.49);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.93,208.48) --
-	(499.93,212.33);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (499.93,207.59) {$\kappa$};
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (209.51,  0.00) --
+	(572.41,362.91) --
+	(572.41,203.76) --
+	(368.65,  0.00);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (236.03,  0.00) --
+	(572.41,336.38) --
+	(572.41,230.29) --
+	(342.13,  0.00);
+
+\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round] (262.56,  0.00) --
+	(572.41,309.86) --
+	(572.41,256.81) --
+	(315.60,  0.00);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (425.98, 53.23) {$\frac{1}{64} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,140.80) {$64\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (399.46, 53.23) {$\frac{1}{16} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,114.28) {$16\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (371.28, 53.23) {$\frac{1}{4} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.00, 87.76) {$4\times$};
+
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (338.88, 49.80) -- (528.36,239.28);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (489.17,200.46) --
+	(494.14,200.46);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (491.81,198.61) --
+	(491.81,202.14);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (491.81,197.23) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (470.10,180.29) --
+	(473.13,180.29);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (471.67,178.14) --
+	(471.67,182.23);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (471.67,176.26) {$L$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (498.44,206.93) --
+	(499.98,206.93);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (499.23,203.91) --
+	(499.23,209.53);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (499.23,202.90) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (482.98,192.71) --
+	(485.77,192.71);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (484.43,188.53) --
+	(484.43,196.14);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (484.43,188.68) {$h$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (493.93,201.00) --
+	(496.01,201.00);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (495.00,197.45) --
+	(495.00,203.99);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (495.00,198.10) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (506.72,211.69) --
+	(508.78,211.69);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (507.78,208.42) --
+	(507.78,214.48);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (507.78,208.79) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (458.92,161.28) --
+	(462.02,161.28);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (460.53,159.29) --
+	(460.53,163.09);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (460.53,158.06) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (462.78,174.74) --
+	(466.69,174.74);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (464.84,172.43) --
+	(464.84,176.80);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (464.84,170.71) {$L$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (489.61,195.98) --
+	(490.75,195.98);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (490.19,194.87) --
+	(490.19,197.04);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (490.19,191.95) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (434.26,145.82) --
+	(443.18,145.82);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (439.23,140.13) --
+	(439.23,150.21);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (439.23,141.79) {$h$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (448.95,154.25) --
+	(455.49,154.25);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (452.50,150.54) --
+	(452.50,157.36);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (452.50,151.35) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (496.87,199.16) --
+	(497.33,199.16);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (497.10,198.20) --
+	(497.10,200.08);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (497.10,196.26) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (442.45,157.16) --
+	(443.45,157.16);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (442.96,156.23) --
+	(442.96,158.05);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (442.96,153.94) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (453.40,164.82) --
+	(457.57,164.82);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (455.60,162.22) --
+	(455.60,167.11);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (455.60,160.79) {$L$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.33,189.55) --
+	(482.60,189.55);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.50,188.39) --
+	(481.50,190.63);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (481.50,185.51) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (434.13,150.27) --
+	(440.56,150.27);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (437.62,145.43) --
+	(437.62,154.13);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (437.62,146.24) {$h$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (437.80,157.06) --
+	(446.05,157.06);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (442.37,132.82) --
+	(442.37,167.42);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (442.37,154.16) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (495.27,198.57) --
+	(495.84,198.57);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (495.56,198.44) --
+	(495.56,198.69);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (495.56,195.66) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (400.39,107.27) --
+	(406.95,107.27);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (403.95,102.23) --
+	(403.95,111.25);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (403.95,104.04) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (443.10,156.88) --
+	(457.34,156.88);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (451.51,151.53) --
+	(451.51,161.05);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (451.51,152.84) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (442.66,157.29) --
+	(443.37,157.29);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (443.02,155.91) --
+	(443.02,158.58);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (443.02,153.26) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (396.26,100.71) --
+	(404.45,100.71);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (400.79, 95.38) --
+	(400.79,104.88);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (400.79, 96.68) {$h$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (390.59,110.14) --
+	(407.20,110.14);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (400.64, 99.79) --
+	(400.64,116.82);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (400.64,107.24) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (475.76,185.81) --
+	(477.20,185.81);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (476.49,183.08) --
+	(476.49,188.19);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (476.49,182.90) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (495.31,205.27) --
+	(497.05,205.27);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (496.20,202.53) --
+	(496.20,207.67);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (496.20,202.04) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (475.59,185.89) --
+	(481.45,185.89);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (478.75,183.37) --
+	(478.75,188.12);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (478.75,181.86) {$L$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (507.78,215.25) --
+	(508.09,215.25);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (507.93,213.22) --
+	(507.93,217.09);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (507.93,211.22) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (467.06,177.27) --
+	(470.11,177.27);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (468.65,175.15) --
+	(468.65,179.18);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.65,173.24) {$h$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.64,191.87) --
+	(485.18,191.87);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.49,189.77) --
+	(483.49,193.75);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.49,188.96) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (502.08,205.65) --
+	(503.19,205.65);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (502.64,203.55) --
+	(502.64,207.55);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (502.64,202.75) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (439.99,151.08) --
+	(446.87,151.08);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (443.73,147.85) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (495.27,206.36) --
+	(500.59,206.36);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (498.12,202.33) {$L$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (477.15,191.68) --
+	(478.39,191.68);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (477.78,187.65) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (445.65,158.37) --
+	(448.05,158.37);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (446.89,154.33) {$h$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (452.96,153.51) --
+	(458.75,153.51);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (456.08,150.61) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (501.01,209.66) --
+	(503.73,209.66);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (502.42,206.76) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (451.32,173.38) --
+	(461.03,173.38);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (456.78,168.80) --
+	(456.78,177.08);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (456.78,170.16) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (427.92,150.89) --
+	(442.33,150.89);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (436.45,147.87) --
+	(436.45,153.50);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (436.45,146.85) {$L$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (473.66,189.57) --
+	(476.30,189.57);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (475.02,188.87) --
+	(475.02,190.24);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (475.02,185.53) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (435.82,153.94) --
+	(440.37,153.94);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (438.23,146.53) --
+	(438.23,159.26);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (438.23,149.90) {$h$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (438.10,161.88) --
+	(445.96,161.88);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (442.43,152.76) --
+	(442.43,168.03);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (442.43,158.98) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (491.96,202.04) --
+	(493.35,202.04);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (492.67,199.33) --
+	(492.67,204.41);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (492.67,199.14) {$\kappa$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.86,195.35) --
+	(483.18,195.35);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (482.05,194.39) --
+	(482.05,196.26);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (482.05,192.12) {$p$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (471.59,182.66) --
+	(475.02,182.66);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (473.38,181.83) --
+	(473.38,183.47);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (473.38,178.63) {$L$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (487.02,198.60) --
+	(487.89,198.60);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (487.46,197.76) --
+	(487.46,199.40);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (487.46,194.56) {$r$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (468.85,181.82) --
+	(472.24,181.82);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (470.62,180.12) --
+	(470.62,183.39);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (470.62,177.79) {$h$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (472.99,187.44) --
+	(476.41,187.44);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (474.77,186.86) --
+	(474.77,188.00);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.77,184.53) {$\sigma$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (503.25,208.38) --
+	(504.90,208.38);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (504.09,207.49) --
+	(504.09,209.23);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (504.09,205.48) {$\kappa$};
 \end{scope}

### 2020-08-26 benchmarking/benchmarkingVM/ESS_round1_real.tex
results update

--- 2020-08-07 benchmarking/benchmarkingVM/ESS_round1_real.tex
@@
-% Created by tikzDevice version 0.12.3 on 2020-08-07 14:28:24
+% Created by tikzDevice version 0.12.3.1 on 2020-08-25 15:32:33
 % !TEX encoding = UTF-8 Unicode
@@
 \definecolor{drawColor}{RGB}{0,0,0}
-\definecolor{fillColor}{gray}{0.91}
-
-\path[draw=drawColor,line width= 0.1pt,line join=round,line cap=round,fill=fillColor] (  0.00,365.38) --
-	(212.78,578.16) --
-	(281.53,578.16) --
-	(281.53,494.30) --
-	(  0.00,212.78) --
-	cycle;
-\definecolor{fillColor}{RGB}{190,190,190}
-
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] (  0.00,339.95) --
-	(238.21,578.16) --
-	(281.53,578.16) --
-	(281.53,519.74) --
-	(  0.00,238.21) --
-	cycle;
-\definecolor{fillColor}{RGB}{169,169,169}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (  0.00,314.51) --
-	(263.65,578.16) --
-	(281.53,578.16) --
-	(281.53,545.17) --
-	(  0.00,263.65) --
-	cycle;
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (133.64,342.31) {$\frac{1}{64} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,426.62) {$64\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (108.20,342.31) {$\frac{1}{16} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,401.18) {$16\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 81.11,342.31) {$\frac{1}{4} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92,375.75) {$4\times$};
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,528.36);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.14,457.67) --
-	(163.00,457.67);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.72,454.14) --
-	(158.72,460.63);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.72,454.44) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.97,498.27) --
-	(218.78,498.27);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.83,495.92) --
-	(212.83,500.36);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.83,494.24) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (178.45,498.59) --
-	(180.15,498.59);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.32,497.51) --
-	(179.32,499.62);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.32,494.56) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (146.49,453.46) --
-	(152.86,453.46);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (149.95,449.76) --
-	(149.95,456.55);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (149.95,449.43) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (156.64,437.17) --
-	(165.01,437.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.30,434.91) --
-	(161.30,439.18);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (161.30,434.26) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.32,508.76) --
-	(221.15,508.76);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.74,507.98) --
-	(220.74,509.51);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.74,505.85) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.30,494.32) --
-	(194.81,494.32);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.60,491.54) --
-	(193.60,496.74);
-\definecolor{drawColor}{RGB}{0,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.60,491.10) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (205.85,498.07) --
-	(214.19,498.07);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.49,494.17) --
-	(210.49,501.29);
-\definecolor{drawColor}{RGB}{0,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.49,494.04) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.48,503.25) --
-	(210.75,503.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.13,501.60) --
-	(210.13,504.76);
-\definecolor{drawColor}{RGB}{0,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.13,499.21) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.18,482.71) --
-	(198.08,482.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.79,479.66) --
-	(195.79,485.33);
-\definecolor{drawColor}{RGB}{0,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.79,478.68) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.48,485.22) --
-	(198.60,485.22);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.57,481.89) --
-	(197.57,488.04);
-\definecolor{drawColor}{RGB}{0,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.57,482.32) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.10,512.25) --
-	(223.18,512.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.65,510.74) --
-	(222.65,513.65);
-\definecolor{drawColor}{RGB}{0,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (222.65,509.35) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.17,469.31) --
-	(197.17,474.08);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.17,468.62) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (214.45,504.24) --
-	(220.93,504.24);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.97,503.56) --
-	(217.97,504.90);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (217.97,500.21) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.42,505.36) --
-	(222.61,505.36);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (216.85,505.09) --
-	(216.85,505.62);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (216.85,501.33) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.48,442.96) --
-	(169.48,453.47);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.48,444.93) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.56,462.82) --
-	(196.56,467.56);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.56,462.44) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.70,512.26) --
-	(223.15,512.26);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.93,512.04) --
-	(222.93,512.48);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (222.93,509.36) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.68,478.88) --
-	(192.68,485.07);
-\definecolor{drawColor}{RGB}{255,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.68,479.01) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.72,496.18) --
-	(218.04,496.18);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (205.74,494.03) --
-	(205.74,498.10);
-\definecolor{drawColor}{RGB}{255,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.74,492.14) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.70,503.25) --
-	(229.53,503.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (224.55,502.95) --
-	(224.55,503.55);
-\definecolor{drawColor}{RGB}{255,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (224.55,499.22) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.85,475.04) --
-	(211.32,475.04);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.84,472.97) --
-	(200.84,476.90);
-\definecolor{drawColor}{RGB}{255,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (200.84,471.00) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.62,480.49) --
-	(206.62,483.96);
-\definecolor{drawColor}{RGB}{255,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (206.62,479.40) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.33,511.89) --
-	(223.37,511.89);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.86,511.27) --
-	(222.86,512.49);
-\definecolor{drawColor}{RGB}{255,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (222.86,508.99) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.91,482.52) --
-	(221.91,491.18);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (221.91,484.13) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (202.65,482.61) --
-	(202.65,488.22);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.65,481.59) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (199.21,500.97) --
-	(230.61,500.97);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.94,500.31) --
-	(220.94,501.61);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.94,496.94) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.32,486.64) --
-	(193.67,486.64);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.26,482.99) --
-	(185.26,489.69);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.26,482.61) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (207.68,479.70) --
-	(207.68,488.91);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.68,481.98) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (119.95,439.54) --
-	(137.90,439.54);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (131.04,432.27) --
-	(131.04,444.73);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (131.04,436.31) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.56,498.07) --
-	(210.93,498.07);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.02,496.36) --
-	(208.02,499.62);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (208.02,494.03) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (125.81,497.45) --
-	(135.01,497.45);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (130.98,494.97) --
-	(130.98,499.64);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (130.98,493.42) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (119.66,452.88) --
-	(130.48,452.88);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (125.86,445.61) --
-	(125.86,458.08);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (125.86,448.85) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (119.40,419.55) --
-	(144.64,419.55);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (136.05,411.70) --
-	(136.05,425.03);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (136.05,416.65) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.17,512.87) --
-	(223.63,512.87);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.40,512.58) --
-	(223.40,513.16);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (223.40,509.97) {$\mu$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (165.32,492.59) --
-	(187.22,492.59);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.36,490.80) --
-	(179.36,494.22);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.36,489.37) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.77,494.95) --
-	(207.58,494.95);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (199.98,487.86) --
-	(199.98,500.06);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.98,490.92) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.10,499.92) --
-	(216.56,499.92);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.11,499.81) --
-	(210.11,500.04);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.11,495.89) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (156.75,463.31) --
-	(179.56,463.31);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.50,460.78) --
-	(171.50,465.53);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.50,459.27) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (165.37,483.34) --
-	(188.77,483.34);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.57,482.71) --
-	(180.57,483.94);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.57,480.43) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (216.41,512.30) --
-	(225.65,512.30);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.61,509.43) --
-	(221.61,514.78);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (221.61,509.40) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (164.18,476.03) --
-	(174.33,476.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.95,474.65) --
-	(169.95,477.32);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.95,472.81) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (213.06,503.10) --
-	(218.28,503.10);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.85,502.50) --
-	(215.85,503.67);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (215.85,499.06) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (202.88,502.51) --
-	(207.31,502.51);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (205.23,502.21) --
-	(205.23,502.80);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.23,498.47) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.71,468.73) --
-	(170.74,468.73);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (166.40,467.18) --
-	(166.40,470.16);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (166.40,464.70) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.55,467.47) --
-	(172.33,467.47);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (167.72,466.51) --
-	(167.72,468.39);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (167.72,464.57) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.84,507.62) --
-	(218.89,507.62);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.38,507.22) --
-	(218.38,508.01);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (218.38,504.71) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (137.20,493.15) --
-	(182.80,493.15);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.55,492.20) --
-	(171.55,494.06);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.55,489.93) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.57,502.64) --
-	(218.61,502.64);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (207.57,501.88) --
-	(207.57,503.37);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.57,498.61) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.92,502.35) --
-	(194.96,502.35);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.81,502.20) --
-	(187.81,502.49);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.81,498.31) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (165.35,472.33) --
-	(173.05,472.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.60,471.58) --
-	(169.60,473.05);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.60,468.29) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (134.07,470.24) --
-	(176.07,470.24);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (165.12,469.07) --
-	(165.12,471.33);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (165.12,467.33) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (  0.00,368.65) --
+	(209.51,578.16);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (283.33,578.16) --
+	(283.33,492.84) --
+	(  0.00,209.51);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,342.13) --
+	(236.03,578.16);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (283.33,578.16) --
+	(283.33,519.37) --
+	(  0.00,236.03);
+
+\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round] (  0.00,315.60) --
+	(262.56,578.16);
+
+\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round] (283.33,578.16) --
+	(283.33,545.89) --
+	(  0.00,262.56);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (136.90,342.31) {$\frac{1}{64} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,429.88) {$64\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (110.38,342.31) {$\frac{1}{16} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,403.36) {$16\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 82.20,342.31) {$\frac{1}{4} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92,376.84) {$4\times$};
+
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,528.36);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (120.87,491.63) --
+	(153.32,491.63);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (143.28,489.68) --
+	(143.28,493.39);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (143.28,488.40) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.77,470.99) --
+	(175.39,470.99);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (166.58,468.16) --
+	(166.58,473.45);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (166.58,466.95) {$L$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (206.16,500.74) --
+	(215.69,500.74);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.51,500.34) --
+	(211.51,501.13);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.51,496.70) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.45,479.76) --
+	(197.91,479.76);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.80,477.75) --
+	(189.80,481.58);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (189.80,475.72) {$h$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (134.12,482.07) --
+	(177.22,482.07);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (165.87,479.79) --
+	(165.87,484.11);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (165.87,479.17) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (222.16,504.36) --
+	(223.91,504.36);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (223.06,503.90) --
+	(223.06,504.81);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (223.06,501.45) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.77,450.33) --
+	(180.77,456.96);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.77,450.70) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (127.28,471.34) --
+	(186.05,471.34);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.66,470.84) --
+	(173.66,471.83);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.66,467.31) {$L$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.13,489.98) --
+	(211.57,489.98);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (204.21,489.60) --
+	(204.21,490.35);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (204.21,485.95) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (158.71,426.99) --
+	(158.71,436.27);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.71,428.15) {$h$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.28,442.01) --
+	(181.28,450.04);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.28,443.54) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (210.92,494.39) --
+	(211.41,494.39);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.17,494.00) --
+	(211.17,494.78);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.17,491.49) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (111.69,458.54) --
+	(151.89,458.54);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (140.84,457.29) --
+	(140.84,459.71);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (140.84,455.31) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (135.21,465.08) --
+	(177.74,465.08);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (166.44,464.31) --
+	(166.44,465.81);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (166.44,461.04) {$L$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.37,486.12) --
+	(198.07,486.12);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.42,485.75) --
+	(192.42,486.49);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.42,482.09) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (131.08,451.24) --
+	(158.21,451.24);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.10,449.98) --
+	(149.10,452.42);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (149.10,447.21) {$h$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (118.18,448.42) --
+	(157.07,448.42);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (146.16,445.27) --
+	(146.16,451.13);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (146.16,445.52) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (210.39,493.75) --
+	(211.29,493.75);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (210.85,493.47) --
+	(210.85,494.02);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.85,490.85) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (123.38,424.42) --
+	(130.68,424.42);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (127.38,421.26) --
+	(127.38,427.12);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (127.38,421.19) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (146.20,468.06) --
+	(169.06,468.06);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (160.86,465.26) --
+	(160.86,470.50);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (160.86,464.02) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.44,466.43) --
+	(152.81,466.43);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.13,465.29) --
+	(152.13,467.52);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (152.13,462.40) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (109.33,419.53) --
+	(117.33,419.53);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (113.75,415.02) --
+	(113.75,423.18);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (113.75,415.50) {$h$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (123.65,403.30) --
+	(135.78,403.30);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (130.66,401.93) --
+	(130.66,404.58);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (130.66,400.39) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.69,475.61) --
+	(192.26,475.61);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.98,474.76) --
+	(191.98,476.41);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.98,472.70) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.12,466.92) --
+	(187.12,473.64);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.12,467.35) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.14,476.78) --
+	(180.14,480.98);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.14,474.96) {$L$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (216.84,493.07) --
+	(230.43,493.07);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (224.81,492.69) --
+	(224.81,493.45);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (224.81,489.04) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.46,463.13) --
+	(211.65,463.13);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (200.82,460.82) --
+	(200.82,465.20);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (200.82,459.10) {$h$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (204.80,468.25) --
+	(204.80,471.97);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (204.80,467.30) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (219.49,498.64) --
+	(220.69,498.64);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (220.10,498.09) --
+	(220.10,499.17);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.10,495.73) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (128.17,481.37) --
+	(128.17,483.93);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (128.17,479.47) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (133.95,488.01) --
+	(133.95,491.15);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (133.95,485.61) {$L$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (157.10,491.91) --
+	(191.40,491.91);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.09,491.31) --
+	(181.09,492.50);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.09,487.88) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (166.81,460.10) --
+	(172.28,460.10);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.74,458.25) --
+	(169.74,461.79);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.74,456.07) {$h$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (139.80,456.53) --
+	(139.80,458.39);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (139.80,454.58) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (219.72,498.92) --
+	(223.33,498.92);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (221.61,498.04) --
+	(221.61,499.76);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (221.61,496.01) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 77.66,454.16) --
+	( 90.48,454.16);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 85.13,451.25) --
+	( 85.13,456.69);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 85.13,450.94) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 92.57,442.19) --
+	(113.59,442.19);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (105.83,425.62) --
+	(105.83,450.94);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (105.83,438.16) {$L$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.95,468.69) --
+	(185.12,468.69);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.70,468.48) --
+	(178.70,468.90);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (178.70,464.66) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (118.32,432.28) --
+	(139.71,432.28);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (131.86,429.85) --
+	(131.86,434.45);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (131.86,428.25) {$h$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 80.49,443.30) --
+	( 96.43,443.30);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 90.07,438.32) --
+	( 90.07,447.26);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 90.07,440.40) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (208.10,489.05) --
+	(210.28,489.05);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (209.22,487.17) --
+	(209.22,490.76);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.22,486.14) {$\kappa$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.14,461.92) --
+	(211.14,468.04);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.14,462.00) {$p$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (159.01,457.26) --
+	(159.01,467.68);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (159.01,459.14) {$L$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.24,477.77) --
+	(220.71,477.77);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (208.91,477.50) --
+	(208.91,478.04);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (208.91,473.74) {$r$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (157.73,460.39) --
+	(184.13,460.39);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.16,455.16) --
+	(175.16,464.50);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (175.16,456.36) {$h$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.46,458.99) --
+	(191.46,464.85);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.46,459.24) {$\sigma$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (224.99,499.53) --
+	(226.68,499.53);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (225.86,498.82) --
+	(225.86,500.21);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (225.86,496.62) {$\kappa$};
 \end{scope}
@@
 \definecolor{drawColor}{RGB}{0,0,0}
-\definecolor{fillColor}{gray}{0.91}
-
-\path[draw=drawColor,line width= 0.1pt,line join=round,line cap=round,fill=fillColor] (169.90,246.20) --
-	(501.86,578.16) --
-	(570.61,578.16) --
-	(570.61,494.30) --
-	(169.90, 93.59) --
-	cycle;
-\definecolor{fillColor}{RGB}{190,190,190}
-
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] (169.90,220.77) --
-	(527.29,578.16) --
-	(570.61,578.16) --
-	(570.61,519.74) --
-	(169.90,119.03) --
-	cycle;
-\definecolor{fillColor}{RGB}{169,169,169}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.90,195.33) --
-	(552.73,578.16) --
-	(570.61,578.16) --
-	(570.61,545.17) --
-	(169.90,144.46) --
-	cycle;
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (422.72,342.31) {$\frac{1}{64} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,426.62) {$64\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (397.28,342.31) {$\frac{1}{16} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,401.18) {$16\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (370.19,342.31) {$\frac{1}{4} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.00,375.75) {$4\times$};
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (338.88,338.88) -- (528.36,528.36);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (442.22,490.95) --
-	(452.08,490.95);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (447.80,488.50) --
-	(447.80,493.11);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (447.80,487.72) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (493.05,494.57) --
-	(507.86,494.57);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (501.91,492.61) --
-	(501.91,496.33);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (501.91,490.53) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (467.53,499.63) --
-	(469.23,499.63);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (468.40,499.53) --
-	(468.40,499.72);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.40,495.59) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (435.57,457.21) --
-	(441.94,457.21);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (439.03,453.71) --
-	(439.03,460.15);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (439.03,453.18) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (445.72,477.46) --
-	(454.09,477.46);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (450.38,473.15) --
-	(450.38,480.94);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (450.38,474.55) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (509.40,508.34) --
-	(510.23,508.34);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (509.82,507.96) --
-	(509.82,508.71);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (509.82,505.44) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.25,470.08) --
-	(486.25,474.05);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (486.25,468.95) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (503.53,505.74) --
-	(510.01,505.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (507.05,504.33) --
-	(507.05,507.05);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (507.05,501.71) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (497.50,509.15) --
-	(511.69,509.15);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (505.93,509.01) --
-	(505.93,509.30);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (505.93,505.12) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (458.56,441.48) --
-	(458.56,447.41);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (458.56,440.65) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.64,465.29) --
-	(485.64,470.85);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (485.64,465.37) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (511.78,512.39) --
-	(512.23,512.39);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (512.01,512.01) --
-	(512.01,512.77);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (512.01,509.49) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (510.99,489.74) --
-	(510.99,496.16);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (510.99,490.01) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (491.73,482.43) --
-	(491.73,487.46);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (491.73,481.08) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (488.29,509.74) --
-	(519.69,509.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (510.02,509.40) --
-	(510.02,510.06);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (510.02,505.70) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (458.40,493.13) --
-	(482.75,493.13);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.34,492.97) --
-	(474.34,493.29);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.34,489.10) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (496.76,491.95) --
-	(496.76,497.87);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (496.76,492.25) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (409.03,486.63) --
-	(426.98,486.63);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.12,480.59) --
-	(420.12,491.17);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (420.12,483.41) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (493.64,486.94) --
-	(500.01,486.94);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (497.10,484.78) --
-	(497.10,488.87);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (497.10,482.90) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (414.89,499.46) --
-	(424.09,499.46);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.06,498.34) --
-	(420.06,500.52);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (420.06,495.43) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (408.74,462.06) --
-	(419.56,462.06);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (414.94,452.46) --
-	(414.94,468.33);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (414.94,458.03) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (408.48,488.92) --
-	(433.72,488.92);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (425.13,483.95) --
-	(425.13,492.83);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (425.13,486.02) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (512.25,512.90) --
-	(512.71,512.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (512.48,512.69) --
-	(512.48,513.11);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (512.48,509.99) {$\mu$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.40,497.82) --
-	(476.30,497.82);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (468.44,494.86) --
-	(468.44,500.36);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.44,494.59) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (475.85,498.71) --
-	(496.66,498.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (489.06,489.13) --
-	(489.06,504.97);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (489.06,494.67) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (489.18,507.02) --
-	(505.64,507.02);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.19,506.47) --
-	(499.19,507.55);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (499.19,502.98) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (445.83,469.60) --
-	(468.64,469.60);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (460.58,463.71) --
-	(460.58,474.05);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (460.58,465.56) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.45,496.70) --
-	(477.85,496.70);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (469.65,491.56) --
-	(469.65,500.72);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (469.65,493.80) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (505.49,512.98) --
-	(514.73,512.98);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (510.69,511.49) --
-	(510.69,514.37);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (510.69,510.08) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (453.26,482.10) --
-	(463.41,482.10);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (459.03,480.23) --
-	(459.03,483.80);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (459.03,478.87) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (502.14,502.07) --
-	(507.36,502.07);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (504.93,500.38) --
-	(504.93,503.61);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (504.93,498.03) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (491.96,503.97) --
-	(496.39,503.97);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (494.31,503.61) --
-	(494.31,504.33);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (494.31,499.94) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (449.79,473.17) --
-	(459.82,473.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (455.48,470.48) --
-	(455.48,475.52);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (455.48,469.14) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (450.63,478.15) --
-	(461.41,478.15);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (456.80,476.59) --
-	(456.80,479.58);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (456.80,475.24) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (506.92,507.74) --
-	(507.97,507.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (507.46,507.42) --
-	(507.46,508.04);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (507.46,504.83) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.28,495.30) --
-	(471.88,495.30);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (460.63,494.52) --
-	(460.63,496.04);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (460.63,492.07) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.65,495.60) --
-	(507.69,495.60);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (496.65,494.08) --
-	(496.65,497.00);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (496.65,491.57) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (465.00,500.38) --
-	(484.04,500.38);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.89,500.12) --
-	(476.89,500.63);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (476.89,496.34) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.43,473.27) --
-	(462.13,473.27);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (458.68,472.16) --
-	(458.68,474.32);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (458.68,469.24) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.15,473.74) --
-	(465.15,473.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.20,471.09) --
-	(454.20,476.05);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (454.20,470.83) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (162.66,242.23) --
+	(498.59,578.16);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (572.41,578.16) --
+	(572.41,492.84) --
+	(162.66, 83.09) --
+	(162.66,242.23);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.66,215.71) --
+	(525.11,578.16);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (572.41,578.16) --
+	(572.41,519.37) --
+	(162.66,109.61) --
+	(162.66,215.71);
+
+\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round] (162.66,189.19) --
+	(551.64,578.16);
+
+\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round] (572.41,578.16) --
+	(572.41,545.89) --
+	(162.66,136.14) --
+	(162.66,189.19);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (425.98,342.31) {$\frac{1}{64} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,429.88) {$64\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (399.46,342.31) {$\frac{1}{16} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,403.36) {$16\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (371.28,342.31) {$\frac{1}{4} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.00,376.84) {$4\times$};
+
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (338.88,338.88) -- (528.36,528.36);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (409.95,498.53) --
+	(442.40,498.53);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (432.36,495.69) --
+	(432.36,501.00);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (432.36,495.30) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (438.85,477.19) --
+	(464.47,477.19);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (455.66,473.20) --
+	(455.66,480.49);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (455.66,473.16) {$L$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (495.24,507.29) --
+	(504.77,507.29);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (500.59,504.13) --
+	(500.59,510.00);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (500.59,503.26) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (464.53,488.44) --
+	(486.99,488.44);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (478.88,485.34) --
+	(478.88,491.10);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (478.88,484.40) {$h$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (423.20,500.32) --
+	(466.30,500.32);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (454.95,497.70) --
+	(454.95,502.63);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (454.95,497.42) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (511.24,508.32) --
+	(512.99,508.32);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (512.14,505.44) --
+	(512.14,510.82);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (512.14,505.41) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (469.85,459.47) --
+	(469.85,463.29);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (469.85,458.25) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (416.36,473.75) --
+	(475.13,473.75);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (462.74,467.42) --
+	(462.74,478.51);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (462.74,469.72) {$L$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.21,499.81) --
+	(500.65,499.81);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (493.29,499.49) --
+	(493.29,500.13);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (493.29,495.78) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (447.79,430.75) --
+	(447.79,435.51);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (447.79,429.24) {$h$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (470.36,453.95) --
+	(470.36,460.21);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (470.36,454.43) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (500.00,500.26) --
+	(500.49,500.26);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (500.25,500.10) --
+	(500.25,500.41);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (500.25,497.35) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (400.77,472.45) --
+	(440.97,472.45);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (429.92,469.05) --
+	(429.92,475.33);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (429.92,469.22) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (424.29,469.44) --
+	(466.82,469.44);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (455.52,468.18) --
+	(455.52,470.63);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (455.52,465.41) {$L$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (473.45,494.42) --
+	(487.15,494.42);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.50,494.08) --
+	(481.50,494.75);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (481.50,490.38) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (420.16,461.88) --
+	(447.29,461.88);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (438.18,458.33) --
+	(438.18,464.86);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (438.18,457.84) {$h$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (407.26,466.76) --
+	(446.15,466.76);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (435.24,464.72) --
+	(435.24,468.61);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (435.24,463.86) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (499.47,500.16) --
+	(500.37,500.16);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (499.93,499.71) --
+	(499.93,500.60);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (499.93,497.25) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (412.46,461.86) --
+	(419.76,461.86);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (416.46,457.98) --
+	(416.46,465.08);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (416.46,458.63) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (435.28,471.68) --
+	(458.14,471.68);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (449.94,467.85) --
+	(449.94,474.87);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (449.94,467.65) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (440.52,473.63) --
+	(441.89,473.63);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (441.21,473.45) --
+	(441.21,473.81);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (441.21,469.59) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (398.41,428.77) --
+	(406.41,428.77);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (402.83,424.39) --
+	(402.83,432.32);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (402.83,424.73) {$h$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (412.73,451.10) --
+	(424.86,451.10);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (419.74,444.27) --
+	(419.74,456.13);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (419.74,448.20) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.77,482.13) --
+	(481.34,482.13);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.06,481.71) --
+	(481.06,482.53);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (481.06,479.22) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (476.20,469.20) --
+	(476.20,486.87);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (476.20,476.78) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (469.22,479.54) --
+	(469.22,485.69);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (469.22,478.82) {$L$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (505.92,510.87) --
+	(519.51,510.87);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (513.89,508.22) --
+	(513.89,513.20);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (513.89,506.84) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (462.54,475.07) --
+	(500.73,475.07);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (489.90,471.46) --
+	(489.90,478.10);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (489.90,471.03) {$h$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (493.88,480.19) --
+	(493.88,486.83);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (493.88,480.89) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (508.57,502.56) --
+	(509.77,502.56);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (509.18,499.82) --
+	(509.18,504.96);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (509.18,499.66) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (417.25,495.96) --
+	(417.25,497.69);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (417.25,493.62) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (423.03,501.50) --
+	(423.03,504.37);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (423.03,498.95) {$L$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (446.18,502.51) --
+	(480.48,502.51);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (470.17,502.30) --
+	(470.17,502.71);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (470.17,498.47) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (455.89,473.26) --
+	(461.36,473.26);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (458.82,472.23) --
+	(458.82,474.23);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (458.82,469.22) {$h$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (428.88,471.94) --
+	(428.88,477.11);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (428.88,471.79) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (508.80,510.43) --
+	(512.41,510.43);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (510.69,509.55) --
+	(510.69,511.28);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (510.69,507.53) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (366.74,474.68) --
+	(379.56,474.68);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (374.21,470.11) --
+	(374.21,478.38);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (374.21,471.46) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (381.65,452.98) --
+	(402.67,452.98);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (394.91,449.28) --
+	(394.91,456.08);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (394.91,448.95) {$L$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (458.03,485.78) --
+	(474.20,485.78);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (467.78,485.35) --
+	(467.78,486.21);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (467.78,481.75) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (407.40,446.62) --
+	(428.79,446.62);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (420.94,441.01) --
+	(420.94,450.95);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (420.94,442.59) {$h$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (369.57,472.80) --
+	(385.51,472.80);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (379.15,467.90) --
+	(379.15,476.70);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (379.15,469.90) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (497.18,498.56) --
+	(499.36,498.56);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (498.30,497.16) --
+	(498.30,499.86);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (498.30,495.65) {$\kappa$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (500.22,478.54) --
+	(500.22,484.51);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (500.22,478.53) {$p$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (448.09,474.79) --
+	(448.09,481.27);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (448.09,474.27) {$L$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (461.32,500.43) --
+	(509.79,500.43);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (497.99,500.31) --
+	(497.99,500.55);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (497.99,496.40) {$r$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (446.81,480.91) --
+	(473.21,480.91);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (464.24,478.84) --
+	(464.24,482.78);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (464.24,476.88) {$h$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.54,484.34) --
+	(480.54,486.46);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (480.54,482.53) {$\sigma$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (514.07,512.69) --
+	(515.76,512.69);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (514.94,512.04) --
+	(514.94,513.32);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (514.94,509.78) {$\kappa$};
 \end{scope}
@@
 \definecolor{drawColor}{RGB}{0,0,0}
-\definecolor{fillColor}{gray}{0.91}
-
-\path[draw=drawColor,line width= 0.1pt,line join=round,line cap=round,fill=fillColor] (  0.00, 82.04) --
-	(284.70,366.75) --
-	(284.70,202.66) --
-	( 82.04,  0.00) --
-	(  0.00,  0.00) --
-	cycle;
-\definecolor{fillColor}{RGB}{190,190,190}
-
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round,fill=fillColor] (  0.00, 54.70) --
-	(284.70,339.40) --
-	(284.70,230.01) --
-	( 54.70,  0.00) --
-	(  0.00,  0.00) --
-	cycle;
-\definecolor{fillColor}{RGB}{169,169,169}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (  0.00, 27.35) --
-	(284.70,312.05) --
-	(284.70,257.36) --
-	( 27.35,  0.00) --
-	(  0.00,  0.00) --
-	cycle;
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (139.38, 53.23) {$\frac{1}{64} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,143.28) {$64\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (112.03, 53.23) {$\frac{1}{16} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,115.93) {$16\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 83.03, 53.23) {$\frac{1}{4} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92, 88.58) {$4\times$};
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 49.80, 49.80) -- (239.28,239.28);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.73,213.31) --
-	(180.71,213.31);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.53,210.67) --
-	(177.53,215.64);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.53,210.08) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.65,217.20) --
-	(223.43,217.20);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.18,215.09) --
-	(221.18,219.10);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (221.18,213.16) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.36,222.64) --
-	(222.63,222.64);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.53,222.53) --
-	(221.53,222.74);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (221.53,218.60) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.02,177.03) --
-	(176.32,177.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.00,173.27) --
-	(173.00,180.19);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.00,173.00) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.05,198.80) --
-	(157.65,198.80);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (155.48,194.17) --
-	(155.48,202.55);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (155.48,195.89) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.61,232.01) --
-	(233.26,232.01);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.46,231.60) --
-	(232.46,232.40);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (232.46,229.10) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.04,193.12) --
-	(195.17,193.12);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.77,190.87) --
-	(192.77,195.14);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.77,189.89) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.87,229.21) --
-	(228.31,229.21);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.60,227.70) --
-	(227.60,230.62);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (227.60,225.18) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.52,232.88) --
-	(229.09,232.88);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.80,232.72) --
-	(228.80,233.04);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (228.80,228.85) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.71,163.56) --
-	(173.01,163.56);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.16,160.12) --
-	(168.16,166.49);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (168.16,159.53) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (183.06,188.93) --
-	(188.16,188.93);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.77,185.72) --
-	(185.77,191.69);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.77,186.03) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.98,236.37) --
-	(236.46,236.37);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (236.22,235.95) --
-	(236.22,236.77);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (236.22,233.46) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.24,215.76) --
-	(213.56,215.76);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.45,212.01) --
-	(209.45,218.92);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.45,212.54) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.34,207.04) --
-	(210.37,207.04);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (207.59,204.14) --
-	(207.59,209.56);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.59,203.00) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (223.38,233.51) --
-	(224.77,233.51);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (224.09,233.15) --
-	(224.09,233.86);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (224.09,229.47) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.76,215.65) --
-	(211.95,215.65);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.68,215.48) --
-	(208.68,215.82);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (208.68,211.62) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (201.21,217.83) --
-	(211.12,217.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.78,214.39) --
-	(206.78,220.75);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (206.78,214.92) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (150.22,208.67) --
-	(163.61,208.67);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.03,202.16) --
-	(158.03,213.55);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.03,205.44) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (219.13,208.99) --
-	(222.64,208.99);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.96,206.67) --
-	(220.96,211.07);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.96,204.96) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.63,222.46) --
-	(222.65,222.46);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.30,221.26) --
-	(220.30,223.59);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.30,218.43) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (164.55,182.25) --
-	(177.96,182.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.38,171.93) --
-	(172.38,188.99);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.38,178.21) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (128.10,211.13) --
-	(142.44,211.13);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (136.54,205.79) --
-	(136.54,215.33);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (136.54,208.22) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (236.56,236.91) --
-	(237.19,236.91);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (236.88,236.68) --
-	(236.88,237.13);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (236.88,234.00) {$\mu$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (213.15,220.69) --
-	(216.83,220.69);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.07,217.51) --
-	(215.07,223.43);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (215.07,217.47) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.98,221.65) --
-	(223.10,221.65);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.61,211.36) --
-	(217.61,228.38);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (217.61,217.62) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.83,230.59) --
-	(223.08,230.59);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.96,230.00) --
-	(222.96,231.16);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (222.96,226.55) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.87,190.35) --
-	(185.98,190.35);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (183.59,184.02) --
-	(183.59,195.13);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.59,186.31) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.45,219.50) --
-	(205.78,219.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (205.12,213.97) --
-	(205.12,223.81);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.12,216.59) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (233.18,237.00) --
-	(238.93,237.00);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (236.27,235.39) --
-	(236.27,238.49);
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (236.27,234.10) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.79,203.79) --
-	(198.65,203.79);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.27,201.78) --
-	(197.27,205.62);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.27,200.56) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.73,225.26) --
-	(226.99,225.26);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.37,223.45) --
-	(226.37,226.92);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (226.37,221.23) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.42,227.31) --
-	(226.05,227.31);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.74,226.93) --
-	(225.74,227.69);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (225.74,223.28) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.75,194.19) --
-	(190.95,194.19);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.42,191.29) --
-	(189.42,196.72);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (189.42,190.16) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.03,199.54) --
-	(189.05,199.54);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.07,197.87) --
-	(188.07,201.08);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.07,196.64) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.81,231.36) --
-	(231.65,231.36);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.23,231.02) --
-	(231.23,231.69);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (231.23,228.45) {$\mu$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (214.65,217.98) --
-	(216.65,217.98);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.68,217.15) --
-	(215.68,218.78);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (215.68,214.76) {$p$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.06,218.31) --
-	(226.66,218.31);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.88,216.68) --
-	(225.88,219.81);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (225.88,214.28) {$L$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.41,223.44) --
-	(225.72,223.44);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.56,223.17) --
-	(225.56,223.71);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (225.56,219.41) {$r$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.48,194.30) --
-	(194.06,194.30);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.28,193.10) --
-	(193.28,195.43);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.28,190.27) {$h$};
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.79,194.80) --
-	(192.21,194.80);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.04,191.95) --
-	(191.04,197.29);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.04,191.90) {$\sigma$};
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (  0.00, 79.57) --
+	(283.33,362.91) --
+	(283.33,203.76) --
+	( 79.57,  0.00);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00, 53.05) --
+	(283.33,336.38) --
+	(283.33,230.29) --
+	( 53.05,  0.00);
+
+\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round] (  0.00, 26.52) --
+	(283.33,309.86) --
+	(283.33,256.81) --
+	( 26.52,  0.00);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (136.90, 53.23) {$\frac{1}{64} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,140.80) {$64\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (110.38, 53.23) {$\frac{1}{16} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,114.28) {$16\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 82.20, 53.23) {$\frac{1}{4} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92, 87.76) {$4\times$};
+
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 49.80, 49.80) -- (239.28,239.28);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (200.60,209.45) --
+	(204.31,209.45);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (202.55,206.61) --
+	(202.55,211.92);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.55,206.22) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.08,188.11) --
+	(184.37,188.11);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.91,184.12) --
+	(181.91,191.41);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.91,184.08) {$L$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.26,218.21) --
+	(212.05,218.21);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.66,215.05) --
+	(211.66,220.92);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.66,214.18) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.67,199.36) --
+	(192.50,199.36);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.68,196.26) --
+	(190.68,202.02);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.68,195.32) {$h$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.71,211.24) --
+	(195.03,211.24);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.99,208.62) --
+	(192.99,213.55);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.99,208.34) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (214.82,219.24) --
+	(215.73,219.24);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (215.28,216.36) --
+	(215.28,221.74);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (215.28,216.33) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.25,172.40) --
+	(167.88,172.40);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.85,170.39) --
+	(164.85,174.21);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (164.85,169.17) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.76,184.67) --
+	(182.75,184.67);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.26,178.34) --
+	(182.26,189.43);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.26,180.64) {$L$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (200.52,210.73) --
+	(201.27,210.73);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (200.90,210.41) --
+	(200.90,211.05);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (200.90,206.70) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (137.91,144.20) --
+	(147.19,144.20);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (143.11,141.67) --
+	(143.11,146.43);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (143.11,140.16) {$h$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.93,168.26) --
+	(160.96,168.26);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (157.36,164.87) --
+	(157.36,171.13);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (157.36,165.35) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (204.92,211.18) --
+	(205.70,211.18);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (205.31,211.02) --
+	(205.31,211.33);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.31,208.27) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.21,183.37) --
+	(170.63,183.37);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.46,179.97) --
+	(169.46,186.25);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.46,180.14) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.23,180.36) --
+	(176.73,180.36);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.00,179.10) --
+	(176.00,181.55);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.00,176.33) {$L$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.67,205.34) --
+	(197.41,205.34);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (197.04,205.00) --
+	(197.04,205.67);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.04,201.30) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (160.90,172.80) --
+	(163.34,172.80);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (162.16,169.25) --
+	(162.16,175.78);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (162.16,168.76) {$h$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (156.19,177.68) --
+	(162.05,177.68);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (159.34,175.64) --
+	(159.34,179.53);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (159.34,174.78) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (204.39,211.08) --
+	(204.94,211.08);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (204.67,210.63) --
+	(204.67,211.52);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (204.67,208.17) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (132.18,172.78) --
+	(138.04,172.78);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (135.34,168.90) --
+	(135.34,176.00);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (135.34,169.55) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.18,182.60) --
+	(181.42,182.60);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.98,178.77) --
+	(178.98,185.79);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (178.98,178.57) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.21,184.55) --
+	(178.44,184.55);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (177.35,184.37) --
+	(177.35,184.73);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.35,180.51) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (125.94,139.69) --
+	(134.10,139.69);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (130.45,135.31) --
+	(130.45,143.24);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (130.45,135.65) {$h$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (112.85,162.02) --
+	(115.50,162.02);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (114.22,155.19) --
+	(114.22,167.05);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (114.22,159.12) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.68,193.05) --
+	(187.33,193.05);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.53,192.63) --
+	(186.53,193.45);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (186.53,190.14) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (177.84,190.92) --
+	(184.56,190.92);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.49,180.12) --
+	(181.49,197.79);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.49,187.70) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.70,193.78) --
+	(191.90,193.78);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.91,190.46) --
+	(189.91,196.61);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (189.91,189.74) {$L$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (203.61,221.79) --
+	(204.37,221.79);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (203.99,219.14) --
+	(203.99,224.12);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (203.99,217.76) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.74,185.99) --
+	(176.12,185.99);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.05,182.38) --
+	(174.05,189.02);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.05,181.95) {$h$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.17,194.72) --
+	(182.89,194.72);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.12,191.11) --
+	(181.12,197.75);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.12,191.81) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (209.01,213.48) --
+	(210.09,213.48);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (209.56,210.74) --
+	(209.56,215.88);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.56,210.58) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.29,207.77) --
+	(194.85,207.77);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.61,206.88) --
+	(193.61,208.61);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.61,204.54) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.93,213.91) --
+	(202.07,213.91);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (200.57,212.42) --
+	(200.57,215.29);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (200.57,209.87) {$L$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (202.23,213.43) --
+	(203.42,213.43);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (202.83,213.22) --
+	(202.83,213.63);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.83,209.39) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.17,184.18) --
+	(172.71,184.18);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.02,183.15) --
+	(171.02,185.15);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.02,180.14) {$h$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (167.45,185.62) --
+	(169.31,185.62);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.40,182.86) --
+	(168.40,188.03);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (168.40,182.71) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (208.96,221.35) --
+	(210.68,221.35);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (209.84,220.47) --
+	(209.84,222.20);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.84,218.45) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (162.17,185.60) --
+	(167.61,185.60);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (165.08,181.03) --
+	(165.08,189.30);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (165.08,182.38) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (136.54,163.90) --
+	(161.86,163.90);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (153.11,160.20) --
+	(153.11,167.00);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (153.11,159.87) {$L$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.40,196.70) --
+	(179.82,196.70);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.61,196.27) --
+	(179.61,197.13);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.61,192.67) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (140.77,157.54) --
+	(145.37,157.54);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (143.20,151.93) --
+	(143.20,161.87);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (143.20,153.51) {$h$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.24,183.72) --
+	(158.18,183.72);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (154.22,178.82) --
+	(154.22,187.62);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (154.22,180.82) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.09,209.48) --
+	(201.68,209.48);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.97,208.08) --
+	(199.97,210.78);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.97,206.57) {$\kappa$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.84,192.68) --
+	(178.96,192.68);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.15,189.46) --
+	(176.15,195.43);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.15,189.45) {$p$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.18,189.23) --
+	(178.60,189.23);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.09,185.71) --
+	(174.09,192.19);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.09,185.19) {$L$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.42,211.35) --
+	(188.96,211.35);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.69,211.23) --
+	(188.69,211.47);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.69,207.32) {$r$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (166.08,191.83) --
+	(175.42,191.83);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.31,189.76) --
+	(171.31,193.70);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.31,187.80) {$h$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.91,196.35) --
+	(175.77,196.35);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.06,195.26) --
+	(173.06,197.38);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.06,193.45) {$\sigma$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (209.74,223.61) --
+	(211.13,223.61);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (210.45,222.96) --
+	(210.45,224.24);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.45,220.70) {$\kappa$};
 \end{scope}
@@
 \path[clip] (338.88, 49.80) rectangle (528.36,239.28);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.85, 89.35) -- (428.67, 81.11);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.57, 81.09) -- (516.39, 89.09);
-\definecolor{fillColor}{RGB}{255,0,0}
-
-\path[fill=fillColor] (345.90, 92.78) --
-	(348.41, 88.43) --
-	(343.38, 88.43) --
+\definecolor{fillColor}{RGB}{255,0,109}
+
+\path[fill=fillColor] (485.73,232.77) circle (  1.87);
+
+\path[fill=fillColor] (485.73, 55.06) --
+	(488.24, 50.70) --
+	(483.21, 50.70) --
 	cycle;
-
-\path[fill=fillColor] (433.62, 80.59) circle (  1.87);
-
-\path[fill=fillColor] (521.34, 89.60) circle (  1.87);
-\definecolor{drawColor}{RGB}{0,255,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.72,134.93) -- (428.80,114.73);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.48,114.58) -- (516.48,132.20);
-\definecolor{fillColor}{RGB}{0,255,0}
-
-\path[fill=fillColor] (345.90,139.09) --
-	(348.41,134.73) --
-	(343.38,134.73) --
+\definecolor{fillColor}{RGB}{0,0,0}
+
+\path[fill=fillColor] (435.32,150.27) circle (  2.15);
+
+\path[fill=fillColor] (435.32,142.15) --
+	(438.21,137.14) --
+	(432.42,137.14) --
 	cycle;
-
-\path[fill=fillColor] (433.62,113.49) circle (  1.87);
-
-\path[fill=fillColor] (521.34,133.30) circle (  1.87);
-\definecolor{drawColor}{RGB}{255,165,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (349.23,225.52) -- (430.29,135.59);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.56,132.54) -- (516.40,142.76);
-\definecolor{fillColor}{RGB}{255,165,0}
-
-\path[fill=fillColor] (345.90,232.13) --
-	(348.41,227.77) --
-	(343.38,227.77) --
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,146.98) {\texttt{ConstantDistance}};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
+\definecolor{fillColor}{RGB}{253,104,0}
+
+\path[fill=fillColor] (356.88,165.38) circle (  1.87);
+
+\path[fill=fillColor] (356.88, 80.00) --
+	(359.40, 75.65) --
+	(354.37, 75.65) --
 	cycle;
-
-\path[fill=fillColor] (433.62,131.89) circle (  1.87);
-
-\path[fill=fillColor] (521.34,143.41) circle (  1.87);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.88, 71.53) -- (428.64, 69.21);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.60, 69.22) -- (516.36, 71.77);
 \definecolor{fillColor}{RGB}{0,0,0}
 
-\path[fill=fillColor] (345.90, 71.68) circle (  1.87);
-
-\path[fill=fillColor] (433.62, 69.06) circle (  1.87);
-
-\path[fill=fillColor] (521.34, 74.84) --
-	(523.86, 70.48) --
-	(518.83, 70.48) --
+\path[fill=fillColor] (435.32,150.27) circle (  2.15);
+
+\path[fill=fillColor] (435.32,142.15) --
+	(438.21,137.14) --
+	(432.42,137.14) --
 	cycle;
-\definecolor{drawColor}{RGB}{160,32,240}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.48,143.02) -- (429.04,109.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.26,109.56) -- (516.70,139.97);
-\definecolor{fillColor}{RGB}{160,32,240}
-
-\path[fill=fillColor] (345.90,147.87) --
-	(348.41,143.51) --
-	(343.38,143.51) --
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,146.98) {\texttt{ConstantDistance}};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
+\definecolor{fillColor}{RGB}{143,161,0}
+
+\path[fill=fillColor] (394.78,149.36) circle (  1.87);
+
+\path[fill=fillColor] (394.78, 80.07) --
+	(397.29, 75.72) --
+	(392.26, 75.72) --
 	cycle;
-
-\path[fill=fillColor] (433.62,107.76) circle (  1.87);
-
-\path[fill=fillColor] (521.34,141.77) circle (  1.87);
-\definecolor{drawColor}{RGB}{0,100,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.70,132.99) -- (428.82,111.40);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.60,110.21) -- (516.36,112.45);
-\definecolor{fillColor}{RGB}{0,100,0}
-
-\path[fill=fillColor] (345.90,137.22) --
-	(348.41,132.86) --
-	(343.38,132.86) --
+\definecolor{fillColor}{RGB}{0,0,0}
+
+\path[fill=fillColor] (435.32,150.27) circle (  2.15);
+
+\path[fill=fillColor] (435.32,142.15) --
+	(438.21,137.14) --
+	(432.42,137.14) --
 	cycle;
 
-\path[fill=fillColor] (433.62,110.07) circle (  1.87);
-
-\path[fill=fillColor] (521.34,112.59) circle (  1.87);
-\definecolor{drawColor}{RGB}{0,255,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (349.79,196.49) -- (429.73,132.52);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (437.55,132.47) -- (517.41,194.71);
-\definecolor{fillColor}{RGB}{0,255,255}
-
-\path[fill=fillColor] (345.90,202.50) --
-	(348.41,198.15) --
-	(343.38,198.15) --
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,146.98) {\texttt{ConstantDistance}};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
+\definecolor{fillColor}{RGB}{0,195,0}
+
+\path[fill=fillColor] (390.04,184.14) circle (  1.87);
+
+\path[fill=fillColor] (390.04, 69.81) --
+	(392.55, 65.46) --
+	(387.52, 65.46) --
 	cycle;
-
-\path[fill=fillColor] (433.62,129.40) circle (  1.87);
-
-\path[fill=fillColor] (521.34,197.77) circle (  1.87);
+\definecolor{fillColor}{RGB}{0,0,0}
+
+\path[fill=fillColor] (435.32,150.27) circle (  2.15);
+
+\path[fill=fillColor] (435.32,142.15) --
+	(438.21,137.14) --
+	(432.42,137.14) --
+	cycle;
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,146.98) {\texttt{ConstantDistance}};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
+\definecolor{fillColor}{RGB}{0,219,171}
+
+\path[fill=fillColor] (404.25,211.12) circle (  1.87);
+
+\path[fill=fillColor] (404.25, 60.31) --
+	(406.77, 55.95) --
+	(401.74, 55.95) --
+	cycle;
+\definecolor{fillColor}{RGB}{0,0,0}
+
+\path[fill=fillColor] (435.32,150.27) circle (  2.15);
+
+\path[fill=fillColor] (435.32,142.15) --
+	(438.21,137.14) --
+	(432.42,137.14) --
+	cycle;
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,146.98) {\texttt{ConstantDistance}};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
+\definecolor{fillColor}{RGB}{0,216,255}
+
+\path[fill=fillColor] (359.72,111.61) circle (  1.87);
+
+\path[fill=fillColor] (359.72, 94.33) --
+	(362.24, 89.97) --
+	(357.21, 89.97) --
+	cycle;
+\definecolor{fillColor}{RGB}{0,0,0}
+
+\path[fill=fillColor] (435.32,150.27) circle (  2.15);
+
+\path[fill=fillColor] (435.32,142.15) --
+	(438.21,137.14) --
+	(432.42,137.14) --
+	cycle;
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,146.98) {\texttt{ConstantDistance}};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
+\definecolor{fillColor}{RGB}{151,0,255}
+
+\path[fill=fillColor] (433.62,198.59) circle (  1.87);
+
+\path[fill=fillColor] (433.62, 71.59) --
+	(436.14, 67.23) --
+	(431.10, 67.23) --
+	cycle;
+\definecolor{fillColor}{RGB}{0,0,0}
+
+\path[fill=fillColor] (435.32,150.27) circle (  2.15);
+
+\path[fill=fillColor] (435.32,142.15) --
+	(438.21,137.14) --
+	(432.42,137.14) --
+	cycle;
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,146.98) {\texttt{ConstantDistance}};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
+\definecolor{fillColor}{RGB}{255,0,255}
+
+\path[fill=fillColor] (359.72,131.32) circle (  1.87);
+
+\path[fill=fillColor] (359.72, 82.69) --
+	(362.24, 78.34) --
+	(357.21, 78.34) --
+	cycle;
+\definecolor{fillColor}{RGB}{0,0,0}
+
+\path[fill=fillColor] (435.32,150.27) circle (  2.15);
+
+\path[fill=fillColor] (435.32,142.15) --
+	(438.21,137.14) --
+	(432.42,137.14) --
+	cycle;
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,146.98) {\texttt{ConstantDistance}};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
+\definecolor{fillColor}{RGB}{68,68,68}
+
+\path[fill=fillColor] (346.46,125.73) circle (  1.87);
+
+\path[fill=fillColor] (346.46, 76.98) --
+	(348.97, 72.63) --
+	(343.94, 72.63) --
+	cycle;
+\definecolor{fillColor}{RGB}{0,0,0}
+
+\path[fill=fillColor] (435.32,150.27) circle (  2.15);
+
+\path[fill=fillColor] (435.32,142.15) --
+	(438.21,137.14) --
+	(432.42,137.14) --
+	cycle;
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,146.98) {\texttt{ConstantDistance}};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,115.46) --
+	(339.26,115.86) --
+	(339.64,116.25) --
+	(340.02,116.65) --
+	(340.40,117.05) --
+	(340.78,117.45) --
+	(341.16,117.85) --
+	(341.54,118.25) --
+	(341.92,118.65) --
+	(342.30,119.06) --
+	(342.68,119.46) --
+	(343.06,119.87) --
+	(343.44,120.27) --
+	(343.82,120.68) --
+	(344.20,121.09) --
+	(344.58,121.50) --
+	(344.96,121.91) --
+	(345.34,122.32) --
+	(345.71,122.73) --
+	(346.09,123.14) --
+	(346.47,123.56) --
+	(346.85,123.97) --
+	(347.23,124.39) --
+	(347.61,124.80) --
+	(347.99,125.22) --
+	(348.37,125.64) --
+	(348.75,126.06) --
+	(349.13,126.48) --
+	(349.51,126.90) --
+	(349.89,127.32) --
+	(350.27,127.74) --
+	(350.65,128.16) --
+	(351.03,128.58) --
+	(351.41,129.01) --
+	(351.79,129.43) --
+	(352.17,129.85) --
+	(352.55,130.28) --
+	(352.93,130.71) --
+	(353.31,131.13) --
+	(353.69,131.56) --
+	(354.07,131.99) --
+	(354.45,132.42) --
+	(354.83,132.84) --
+	(355.21,133.27) --
+	(355.59,133.70) --
+	(355.97,134.13) --
+	(356.35,134.56) --
+	(356.73,134.99) --
+	(357.11,135.43) --
+	(357.49,135.86) --
+	(357.87,136.29) --
+	(358.25,136.72) --
+	(358.63,137.15) --
+	(359.01,137.59) --
+	(359.38,138.02) --
+	(359.76,138.45) --
+	(360.14,138.89) --
+	(360.52,139.32) --
+	(360.90,139.76) --
+	(361.28,140.19) --
+	(361.66,140.63) --
+	(362.04,141.06) --
+	(362.42,141.50) --
+	(362.80,141.93) --
+	(363.18,142.37) --
+	(363.56,142.80) --
+	(363.94,143.24) --
+	(364.32,143.67) --
+	(364.70,144.11) --
+	(365.08,144.54) --
+	(365.46,144.98) --
+	(365.84,145.41) --
+	(366.22,145.85) --
+	(366.60,146.28) --
+	(366.98,146.72) --
+	(367.36,147.16) --
+	(367.74,147.59) --
+	(368.12,148.03) --
+	(368.50,148.46) --
+	(368.88,148.89) --
+	(369.26,149.33) --
+	(369.64,149.76) --
+	(370.02,150.20) --
+	(370.40,150.63) --
+	(370.78,151.07) --
+	(371.16,151.50) --
+	(371.54,151.93) --
+	(371.92,152.36) --
+	(372.30,152.80) --
+	(372.68,153.23) --
+	(373.05,153.66) --
+	(373.43,154.09) --
+	(373.81,154.52) --
+	(374.19,154.95) --
+	(374.57,155.38) --
+	(374.95,155.81) --
+	(375.33,156.24) --
+	(375.71,156.67) --
+	(376.09,157.10) --
+	(376.47,157.53) --
+	(376.85,157.95) --
+	(377.23,158.38) --
+	(377.61,158.81) --
+	(377.99,159.23) --
+	(378.37,159.66) --
+	(378.75,160.08) --
+	(379.13,160.50) --
+	(379.51,160.93) --
+	(379.89,161.35) --
+	(380.27,161.77) --
+	(380.65,162.19) --
+	(381.03,162.61) --
+	(381.41,163.03) --
+	(381.79,163.45) --
+	(382.17,163.87) --
+	(382.55,164.28) --
+	(382.93,164.70) --
+	(383.31,165.11) --
+	(383.69,165.53) --
+	(384.07,165.94) --
+	(384.45,166.36) --
+	(384.83,166.77) --
+	(385.21,167.18) --
+	(385.59,167.59) --
+	(385.97,168.00) --
+	(386.34,168.41) --
+	(386.72,168.81) --
+	(387.10,169.22) --
+	(387.48,169.63) --
+	(387.86,170.03) --
+	(388.24,170.43) --
+	(388.62,170.84) --
+	(389.00,171.24) --
+	(389.38,171.64) --
+	(389.76,172.04) --
+	(390.14,172.44) --
+	(390.52,172.83) --
+	(390.90,173.23) --
+	(391.28,173.62) --
+	(391.66,174.02) --
+	(392.04,174.41) --
+	(392.42,174.80) --
+	(392.80,175.19) --
+	(393.18,175.58) --
+	(393.56,175.97) --
+	(393.94,176.36) --
+	(394.32,176.74) --
+	(394.70,177.13) --
+	(395.08,177.51) --
+	(395.46,177.89) --
+	(395.84,178.27) --
+	(396.22,178.65) --
+	(396.60,179.03) --
+	(396.98,179.41) --
+	(397.36,179.79) --
+	(397.74,180.16) --
+	(398.12,180.53) --
+	(398.50,180.91) --
+	(398.88,181.28) --
+	(399.26,181.65) --
+	(399.64,182.01) --
+	(400.01,182.38) --
+	(400.39,182.75) --
+	(400.77,183.11) --
+	(401.15,183.47) --
+	(401.53,183.83) --
+	(401.91,184.19) --
+	(402.29,184.55) --
+	(402.67,184.91) --
+	(403.05,185.26) --
+	(403.43,185.62) --
+	(403.81,185.97) --
+	(404.19,186.32) --
+	(404.57,186.67) --
+	(404.95,187.02) --
+	(405.33,187.37) --
+	(405.71,187.71) --
+	(406.09,188.06) --
+	(406.47,188.40) --
+	(406.85,188.74) --
+	(407.23,189.08) --
+	(407.61,189.42) --
+	(407.99,189.76) --
+	(408.37,190.09) --
+	(408.75,190.43) --
+	(409.13,190.76) --
+	(409.51,191.09) --
+	(409.89,191.42) --
+	(410.27,191.75) --
+	(410.65,192.08) --
+	(411.03,192.40) --
+	(411.41,192.73) --
+	(411.79,193.05) --
+	(412.17,193.37) --
+	(412.55,193.69) --
+	(412.93,194.00) --
+	(413.31,194.32) --
+	(413.68,194.64) --
+	(414.06,194.95) --
+	(414.44,195.26) --
+	(414.82,195.57) --
+	(415.20,195.88) --
+	(415.58,196.18) --
+	(415.96,196.49) --
+	(416.34,196.79) --
+	(416.72,197.10) --
+	(417.10,197.40) --
+	(417.48,197.70) --
+	(417.86,197.99) --
+	(418.24,198.29) --
+	(418.62,198.58) --
+	(419.00,198.88) --
+	(419.38,199.17) --
+	(419.76,199.46) --
+	(420.14,199.75) --
+	(420.52,200.03) --
+	(420.90,200.32) --
+	(421.28,200.60) --
+	(421.66,200.89) --
+	(422.04,201.17) --
+	(422.42,201.45) --
+	(422.80,201.72) --
+	(423.18,202.00) --
+	(423.56,202.27) --
+	(423.94,202.55) --
+	(424.32,202.82) --
+	(424.70,203.09) --
+	(425.08,203.36) --
+	(425.46,203.62) --
+	(425.84,203.89) --
+	(426.22,204.15) --
+	(426.60,204.41) --
+	(426.97,204.68) --
+	(427.35,204.93) --
+	(427.73,205.19) --
+	(428.11,205.45) --
+	(428.49,205.70) --
+	(428.87,205.96) --
+	(429.25,206.21) --
+	(429.63,206.46) --
+	(430.01,206.71) --
+	(430.39,206.95) --
+	(430.77,207.20) --
+	(431.15,207.44) --
+	(431.53,207.69) --
+	(431.91,207.93) --
+	(432.29,208.17) --
+	(432.67,208.41) --
+	(433.05,208.64) --
+	(433.43,208.88) --
+	(433.81,209.11) --
+	(434.19,209.35) --
+	(434.57,209.58) --
+	(434.95,209.81) --
+	(435.33,210.03) --
+	(435.71,210.26) --
+	(436.09,210.49) --
+	(436.47,210.71) --
+	(436.85,210.93) --
+	(437.23,211.15) --
+	(437.61,211.37) --
+	(437.99,211.59) --
+	(438.37,211.81) --
+	(438.75,212.02) --
+	(439.13,212.24) --
+	(439.51,212.45) --
+	(439.89,212.66) --
+	(440.27,212.87) --
+	(440.64,213.08) --
+	(441.02,213.28) --
+	(441.40,213.49) --
+	(441.78,213.69) --
+	(442.16,213.90) --
+	(442.54,214.10) --
+	(442.92,214.30) --
+	(443.30,214.50) --
+	(443.68,214.69) --
+	(444.06,214.89) --
+	(444.44,215.09) --
+	(444.82,215.28) --
+	(445.20,215.47) --
+	(445.58,215.66) --
+	(445.96,215.85) --
+	(446.34,216.04) --
+	(446.72,216.23) --
+	(447.10,216.41) --
+	(447.48,216.60) --
+	(447.86,216.78) --
+	(448.24,216.96) --
+	(448.62,217.14) --
+	(449.00,217.32) --
+	(449.38,217.50) --
+	(449.76,217.67) --
+	(450.14,217.85) --
+	(450.52,218.02) --
+	(450.90,218.20) --
+	(451.28,218.37) --
+	(451.66,218.54) --
+	(452.04,218.71) --
+	(452.42,218.88) --
+	(452.80,219.04) --
+	(453.18,219.21) --
+	(453.56,219.37) --
+	(453.93,219.54) --
+	(454.31,219.70) --
+	(454.69,219.86) --
+	(455.07,220.02) --
+	(455.45,220.18) --
+	(455.83,220.33) --
+	(456.21,220.49) --
+	(456.59,220.65) --
+	(456.97,220.80) --
+	(457.35,220.95) --
+	(457.73,221.10) --
+	(458.11,221.25) --
+	(458.49,221.40) --
+	(458.87,221.55) --
+	(459.25,221.70) --
+	(459.63,221.85) --
+	(460.01,221.99) --
+	(460.39,222.13) --
+	(460.77,222.28) --
+	(461.15,222.42) --
+	(461.53,222.56) --
+	(461.91,222.70) --
+	(462.29,222.84) --
+	(462.67,222.98) --
+	(463.05,223.11) --
+	(463.43,223.25) --
+	(463.81,223.38) --
+	(464.19,223.52) --
+	(464.57,223.65) --
+	(464.95,223.78) --
+	(465.33,223.91) --
+	(465.71,224.04) --
+	(466.09,224.17) --
+	(466.47,224.29) --
+	(466.85,224.42) --
+	(467.23,224.55) --
+	(467.60,224.67) --
+	(467.98,224.79) --
+	(468.36,224.92) --
+	(468.74,225.04) --
+	(469.12,225.16) --
+	(469.50,225.28) --
+	(469.88,225.40) --
+	(470.26,225.51) --
+	(470.64,225.63) --
+	(471.02,225.75) --
+	(471.40,225.86) --
+	(471.78,225.98) --
+	(472.16,226.09) --
+	(472.54,226.20) --
+	(472.92,226.31) --
+	(473.30,226.42) --
+	(473.68,226.53) --
+	(474.06,226.64) --
+	(474.44,226.75) --
+	(474.82,226.86) --
+	(475.20,226.96) --
+	(475.58,227.07) --
+	(475.96,227.17) --
+	(476.34,227.28) --
+	(476.72,227.38) --
+	(477.10,227.48) --
+	(477.48,227.59) --
+	(477.86,227.69) --
+	(478.24,227.79) --
+	(478.62,227.88) --
+	(479.00,227.98) --
+	(479.38,228.08) --
+	(479.76,228.18) --
+	(480.14,228.27) --
+	(480.52,228.37) --
+	(480.90,228.46) --
+	(481.27,228.55) --
+	(481.65,228.65) --
+	(482.03,228.74) --
+	(482.41,228.83) --
+	(482.79,228.92) --
+	(483.17,229.01) --
+	(483.55,229.10) --
+	(483.93,229.19) --
+	(484.31,229.27) --
+	(484.69,229.36) --
+	(485.07,229.45) --
+	(485.45,229.53) --
+	(485.83,229.62) --
+	(486.21,229.70) --
+	(486.59,229.78) --
+	(486.97,229.87) --
+	(487.35,229.95) --
+	(487.73,230.03) --
+	(488.11,230.11) --
+	(488.49,230.19) --
+	(488.87,230.27) --
+	(489.25,230.35) --
+	(489.63,230.43) --
+	(490.01,230.50) --
+	(490.39,230.58) --
+	(490.77,230.66) --
+	(491.15,230.73) --
+	(491.53,230.81) --
+	(491.91,230.88) --
+	(492.29,230.95) --
+	(492.67,231.03) --
+	(493.05,231.10) --
+	(493.43,231.17) --
+	(493.81,231.24) --
+	(494.19,231.31) --
+	(494.56,231.38) --
+	(494.94,231.45) --
+	(495.32,231.52) --
+	(495.70,231.59) --
+	(496.08,231.66) --
+	(496.46,231.72) --
+	(496.84,231.79) --
+	(497.22,231.86) --
+	(497.60,231.92) --
+	(497.98,231.99) --
+	(498.36,232.05) --
+	(498.74,232.11) --
+	(499.12,232.18) --
+	(499.50,232.24) --
+	(499.88,232.30) --
+	(500.26,232.36) --
+	(500.64,232.42) --
+	(501.02,232.48) --
+	(501.40,232.54) --
+	(501.78,232.60) --
+	(502.16,232.66) --
+	(502.54,232.72) --
+	(502.92,232.78) --
+	(503.30,232.84) --
+	(503.68,232.89) --
+	(504.06,232.95) --
+	(504.44,233.01) --
+	(504.82,233.06) --
+	(505.20,233.12) --
+	(505.58,233.17) --
+	(505.96,233.23) --
+	(506.34,233.28) --
+	(506.72,233.33) --
+	(507.10,233.38) --
+	(507.48,233.44) --
+	(507.86,233.49) --
+	(508.23,233.54) --
+	(508.61,233.59) --
+	(508.99,233.64) --
+	(509.37,233.69) --
+	(509.75,233.74) --
+	(510.13,233.79) --
+	(510.51,233.84) --
+	(510.89,233.89) --
+	(511.27,233.94) --
+	(511.65,233.98) --
+	(512.03,234.03) --
+	(512.41,234.08) --
+	(512.79,234.12) --
+	(513.17,234.17) --
+	(513.55,234.21) --
+	(513.93,234.26) --
+	(514.31,234.30) --
+	(514.69,234.35) --
+	(515.07,234.39) --
+	(515.45,234.44) --
+	(515.83,234.48) --
+	(516.21,234.52) --
+	(516.59,234.57) --
+	(516.97,234.61) --
+	(517.35,234.65) --
+	(517.73,234.69) --
+	(518.11,234.73) --
+	(518.49,234.77) --
+	(518.87,234.81) --
+	(519.25,234.85) --
+	(519.63,234.89) --
+	(520.01,234.93) --
+	(520.39,234.97) --
+	(520.77,235.01) --
+	(521.15,235.05) --
+	(521.53,235.08) --
+	(521.90,235.12) --
+	(522.28,235.16) --
+	(522.66,235.20) --
+	(523.04,235.23) --
+	(523.42,235.27) --
+	(523.80,235.30) --
+	(524.18,235.34) --
+	(524.56,235.38) --
+	(524.94,235.41) --
+	(525.32,235.45) --
+	(525.70,235.48) --
+	(526.08,235.51) --
+	(526.46,235.55) --
+	(526.84,235.58) --
+	(527.22,235.61) --
+	(527.60,235.65) --
+	(527.98,235.68) --
+	(528.36,235.71);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 86.82) --
+	(339.26, 86.66) --
+	(339.64, 86.51) --
+	(340.02, 86.35) --
+	(340.40, 86.20) --
+	(340.78, 86.04) --
+	(341.16, 85.89) --
+	(341.54, 85.74) --
+	(341.92, 85.58) --
+	(342.30, 85.43) --
+	(342.68, 85.28) --
+	(343.06, 85.13) --
+	(343.44, 84.98) --
+	(343.82, 84.83) --
+	(344.20, 84.68) --
+	(344.58, 84.53) --
+	(344.96, 84.38) --
+	(345.34, 84.24) --
+	(345.71, 84.09) --
+	(346.09, 83.94) --
+	(346.47, 83.80) --
+	(346.85, 83.65) --
+	(347.23, 83.50) --
+	(347.61, 83.36) --
+	(347.99, 83.21) --
+	(348.37, 83.07) --
+	(348.75, 82.93) --
+	(349.13, 82.78) --
+	(349.51, 82.64) --
+	(349.89, 82.50) --
+	(350.27, 82.36) --
+	(350.65, 82.22) --
+	(351.03, 82.08) --
+	(351.41, 81.94) --
+	(351.79, 81.80) --
+	(352.17, 81.66) --
+	(352.55, 81.52) --
+	(352.93, 81.38) --
+	(353.31, 81.24) --
+	(353.69, 81.11) --
+	(354.07, 80.97) --
+	(354.45, 80.83) --
+	(354.83, 80.70) --
+	(355.21, 80.56) --
+	(355.59, 80.43) --
+	(355.97, 80.29) --
+	(356.35, 80.16) --
+	(356.73, 80.03) --
+	(357.11, 79.89) --
+	(357.49, 79.76) --
+	(357.87, 79.63) --
+	(358.25, 79.50) --
+	(358.63, 79.37) --
+	(359.01, 79.24) --
+	(359.38, 79.11) --
+	(359.76, 78.98) --
+	(360.14, 78.85) --
+	(360.52, 78.72) --
+	(360.90, 78.59) --
+	(361.28, 78.46) --
+	(361.66, 78.34) --
+	(362.04, 78.21) --
+	(362.42, 78.08) --
+	(362.80, 77.96) --
+	(363.18, 77.83) --
+	(363.56, 77.71) --
+	(363.94, 77.58) --
+	(364.32, 77.46) --
+	(364.70, 77.33) --
+	(365.08, 77.21) --
+	(365.46, 77.09) --
+	(365.84, 76.97) --
+	(366.22, 76.85) --
+	(366.60, 76.72) --
+	(366.98, 76.60) --
+	(367.36, 76.48) --
+	(367.74, 76.36) --
+	(368.12, 76.24) --
+	(368.50, 76.12) --
+	(368.88, 76.01) --
+	(369.26, 75.89) --
+	(369.64, 75.77) --
+	(370.02, 75.65) --
+	(370.40, 75.54) --
+	(370.78, 75.42) --
+	(371.16, 75.30) --
+	(371.54, 75.19) --
+	(371.92, 75.07) --
+	(372.30, 74.96) --
+	(372.68, 74.85) --
+	(373.05, 74.73) --
+	(373.43, 74.62) --
+	(373.81, 74.51) --
+	(374.19, 74.39) --
+	(374.57, 74.28) --
+	(374.95, 74.17) --
+	(375.33, 74.06) --
+	(375.71, 73.95) --
+	(376.09, 73.84) --
+	(376.47, 73.73) --
+	(376.85, 73.62) --
+	(377.23, 73.51) --
+	(377.61, 73.40) --
+	(377.99, 73.29) --
+	(378.37, 73.19) --
+	(378.75, 73.08) --
+	(379.13, 72.97) --
+	(379.51, 72.87) --
+	(379.89, 72.76) --
+	(380.27, 72.65) --
+	(380.65, 72.55) --
+	(381.03, 72.44) --
+	(381.41, 72.34) --
+	(381.79, 72.24) --
+	(382.17, 72.13) --
+	(382.55, 72.03) --
+	(382.93, 71.93) --
+	(383.31, 71.83) --
+	(383.69, 71.72) --
+	(384.07, 71.62) --
+	(384.45, 71.52) --
+	(384.83, 71.42) --
+	(385.21, 71.32) --
+	(385.59, 71.22) --
+	(385.97, 71.12) --
+	(386.34, 71.02) --
+	(386.72, 70.92) --
+	(387.10, 70.83) --
+	(387.48, 70.73) --
+	(387.86, 70.63) --
+	(388.24, 70.53) --
+	(388.62, 70.44) --
+	(389.00, 70.34) --
+	(389.38, 70.25) --
+	(389.76, 70.15) --
+	(390.14, 70.06) --
+	(390.52, 69.96) --
+	(390.90, 69.87) --
+	(391.28, 69.77) --
+	(391.66, 69.68) --
+	(392.04, 69.59) --
+	(392.42, 69.49) --
+	(392.80, 69.40) --
+	(393.18, 69.31) --
+	(393.56, 69.22) --
+	(393.94, 69.13) --
+	(394.32, 69.04) --
+	(394.70, 68.95) --
+	(395.08, 68.86) --
+	(395.46, 68.77) --
+	(395.84, 68.68) --
+	(396.22, 68.59) --
+	(396.60, 68.50) --
+	(396.98, 68.41) --
+	(397.36, 68.32) --
+	(397.74, 68.24) --
+	(398.12, 68.15) --
+	(398.50, 68.06) --
+	(398.88, 67.98) --
+	(399.26, 67.89) --
+	(399.64, 67.80) --
+	(400.01, 67.72) --
+	(400.39, 67.63) --
+	(400.77, 67.55) --
+	(401.15, 67.47) --
+	(401.53, 67.38) --
+	(401.91, 67.30) --
+	(402.29, 67.22) --
+	(402.67, 67.13) --
+	(403.05, 67.05) --
+	(403.43, 66.97) --
+	(403.81, 66.89) --
+	(404.19, 66.81) --
+	(404.57, 66.73) --
+	(404.95, 66.64) --
+	(405.33, 66.56) --
+	(405.71, 66.48) --
+	(406.09, 66.40) --
+	(406.47, 66.33) --
+	(406.85, 66.25) --
+	(407.23, 66.17) --
+	(407.61, 66.09) --
+	(407.99, 66.01) --
+	(408.37, 65.93) --
+	(408.75, 65.86) --
+	(409.13, 65.78) --
+	(409.51, 65.70) --
+	(409.89, 65.63) --
+	(410.27, 65.55) --
+	(410.65, 65.48) --
+	(411.03, 65.40) --
+	(411.41, 65.33) --
+	(411.79, 65.25) --
+	(412.17, 65.18) --
+	(412.55, 65.10) --
+	(412.93, 65.03) --
+	(413.31, 64.96) --
+	(413.68, 64.88) --
+	(414.06, 64.81) --
+	(414.44, 64.74) --
+	(414.82, 64.67) --
+	(415.20, 64.60) --
+	(415.58, 64.52) --
+	(415.96, 64.45) --
+	(416.34, 64.38) --
+	(416.72, 64.31) --
+	(417.10, 64.24) --
+	(417.48, 64.17) --
+	(417.86, 64.10) --
+	(418.24, 64.03) --
+	(418.62, 63.97) --
+	(419.00, 63.90) --
+	(419.38, 63.83) --
+	(419.76, 63.76) --
+	(420.14, 63.69) --
+	(420.52, 63.63) --
+	(420.90, 63.56) --
+	(421.28, 63.49) --
+	(421.66, 63.43) --
+	(422.04, 63.36) --
+	(422.42, 63.29) --
+	(422.80, 63.23) --
+	(423.18, 63.16) --
+	(423.56, 63.10) --
+	(423.94, 63.03) --
+	(424.32, 62.97) --
+	(424.70, 62.91) --
+	(425.08, 62.84) --
+	(425.46, 62.78) --
+	(425.84, 62.72) --
+	(426.22, 62.65) --
+	(426.60, 62.59) --
+	(426.97, 62.53) --
+	(427.35, 62.47) --
+	(427.73, 62.40) --
+	(428.11, 62.34) --
+	(428.49, 62.28) --
+	(428.87, 62.22) --
+	(429.25, 62.16) --
+	(429.63, 62.10) --
+	(430.01, 62.04) --
+	(430.39, 61.98) --
+	(430.77, 61.92) --
+	(431.15, 61.86) --
+	(431.53, 61.80) --
+	(431.91, 61.74) --
+	(432.29, 61.68) --
+	(432.67, 61.63) --
+	(433.05, 61.57) --
+	(433.43, 61.51) --
+	(433.81, 61.45) --
+	(434.19, 61.40) --
+	(434.57, 61.34) --
+	(434.95, 61.28) --
+	(435.33, 61.23) --
+	(435.71, 61.17) --
+	(436.09, 61.11) --
+	(436.47, 61.06) --
+	(436.85, 61.00) --
+	(437.23, 60.95) --
+	(437.61, 60.89) --
+	(437.99, 60.84) --
+	(438.37, 60.78) --
+	(438.75, 60.73) --
+	(439.13, 60.68) --
+	(439.51, 60.62) --
+	(439.89, 60.57) --
+	(440.27, 60.52) --
+	(440.64, 60.46) --
+	(441.02, 60.41) --
+	(441.40, 60.36) --
+	(441.78, 60.31) --
+	(442.16, 60.25) --
+	(442.54, 60.20) --
+	(442.92, 60.15) --
+	(443.30, 60.10) --
+	(443.68, 60.05) --
+	(444.06, 60.00) --
+	(444.44, 59.95) --
+	(444.82, 59.90) --
+	(445.20, 59.85) --
+	(445.58, 59.80) --
+	(445.96, 59.75) --
+	(446.34, 59.70) --
+	(446.72, 59.65) --
+	(447.10, 59.60) --
+	(447.48, 59.55) --
+	(447.86, 59.50) --
+	(448.24, 59.46) --
+	(448.62, 59.41) --
+	(449.00, 59.36) --
+	(449.38, 59.31) --
+	(449.76, 59.27) --
+	(450.14, 59.22) --
+	(450.52, 59.17) --
+	(450.90, 59.13) --
+	(451.28, 59.08) --
+	(451.66, 59.03) --
+	(452.04, 58.99) --
+	(452.42, 58.94) --
+	(452.80, 58.90) --
+	(453.18, 58.85) --
+	(453.56, 58.81) --
+	(453.93, 58.76) --
+	(454.31, 58.72) --
+	(454.69, 58.67) --
+	(455.07, 58.63) --
+	(455.45, 58.58) --
+	(455.83, 58.54) --
+	(456.21, 58.50) --
+	(456.59, 58.45) --
+	(456.97, 58.41) --
+	(457.35, 58.37) --
+	(457.73, 58.32) --
+	(458.11, 58.28) --
+	(458.49, 58.24) --
+	(458.87, 58.20) --
+	(459.25, 58.15) --
+	(459.63, 58.11) --
+	(460.01, 58.07) --
+	(460.39, 58.03) --
+	(460.77, 57.99) --
+	(461.15, 57.95) --
+	(461.53, 57.91) --
+	(461.91, 57.87) --
+	(462.29, 57.83) --
+	(462.67, 57.79) --
+	(463.05, 57.75) --
+	(463.43, 57.71) --
+	(463.81, 57.67) --
+	(464.19, 57.63) --
+	(464.57, 57.59) --
+	(464.95, 57.55) --
+	(465.33, 57.51) --
+	(465.71, 57.47) --
+	(466.09, 57.43) --
+	(466.47, 57.40) --
+	(466.85, 57.36) --
+	(467.23, 57.32) --
+	(467.60, 57.28) --
+	(467.98, 57.24) --
+	(468.36, 57.21) --
+	(468.74, 57.17) --
+	(469.12, 57.13) --
+	(469.50, 57.10) --
+	(469.88, 57.06) --
+	(470.26, 57.02) --
+	(470.64, 56.99) --
+	(471.02, 56.95) --
+	(471.40, 56.91) --
+	(471.78, 56.88) --
+	(472.16, 56.84) --
+	(472.54, 56.81) --
+	(472.92, 56.77) --
+	(473.30, 56.74) --
+	(473.68, 56.70) --
+	(474.06, 56.67) --
+	(474.44, 56.63) --
+	(474.82, 56.60) --
+	(475.20, 56.56) --
+	(475.58, 56.53) --
+	(475.96, 56.50) --
+	(476.34, 56.46) --
+	(476.72, 56.43) --
+	(477.10, 56.39) --
+	(477.48, 56.36) --
+	(477.86, 56.33) --
+	(478.24, 56.30) --
+	(478.62, 56.26) --
+	(479.00, 56.23) --
+	(479.38, 56.20) --
+	(479.76, 56.17) --
+	(480.14, 56.13) --
+	(480.52, 56.10) --
+	(480.90, 56.07) --
+	(481.27, 56.04) --
+	(481.65, 56.01) --
+	(482.03, 55.97) --
+	(482.41, 55.94) --
+	(482.79, 55.91) --
+	(483.17, 55.88) --
+	(483.55, 55.85) --
+	(483.93, 55.82) --
+	(484.31, 55.79) --
+	(484.69, 55.76) --
+	(485.07, 55.73) --
+	(485.45, 55.70) --
+	(485.83, 55.67) --
+	(486.21, 55.64) --
+	(486.59, 55.61) --
+	(486.97, 55.58) --
+	(487.35, 55.55) --
+	(487.73, 55.52) --
+	(488.11, 55.49) --
+	(488.49, 55.46) --
+	(488.87, 55.44) --
+	(489.25, 55.41) --
+	(489.63, 55.38) --
+	(490.01, 55.35) --
+	(490.39, 55.32) --
+	(490.77, 55.29) --
+	(491.15, 55.27) --
+	(491.53, 55.24) --
+	(491.91, 55.21) --
+	(492.29, 55.18) --
+	(492.67, 55.16) --
+	(493.05, 55.13) --
+	(493.43, 55.10) --
+	(493.81, 55.07) --
+	(494.19, 55.05) --
+	(494.56, 55.02) --
+	(494.94, 54.99) --
+	(495.32, 54.97) --
+	(495.70, 54.94) --
+	(496.08, 54.92) --
+	(496.46, 54.89) --
+	(496.84, 54.86) --
+	(497.22, 54.84) --
+	(497.60, 54.81) --
+	(497.98, 54.79) --
+	(498.36, 54.76) --
+	(498.74, 54.74) --
+	(499.12, 54.71) --
+	(499.50, 54.69) --
+	(499.88, 54.66) --
+	(500.26, 54.64) --
+	(500.64, 54.61) --
+	(501.02, 54.59) --
+	(501.40, 54.56) --
+	(501.78, 54.54) --
+	(502.16, 54.51) --
+	(502.54, 54.49) --
+	(502.92, 54.47) --
+	(503.30, 54.44) --
+	(503.68, 54.42) --
+	(504.06, 54.40) --
+	(504.44, 54.37) --
+	(504.82, 54.35) --
+	(505.20, 54.33) --
+	(505.58, 54.30) --
+	(505.96, 54.28) --
+	(506.34, 54.26) --
+	(506.72, 54.23) --
+	(507.10, 54.21) --
+	(507.48, 54.19) --
+	(507.86, 54.17) --
+	(508.23, 54.14) --
+	(508.61, 54.12) --
+	(508.99, 54.10) --
+	(509.37, 54.08) --
+	(509.75, 54.06) --
+	(510.13, 54.03) --
+	(510.51, 54.01) --
+	(510.89, 53.99) --
+	(511.27, 53.97) --
+	(511.65, 53.95) --
+	(512.03, 53.93) --
+	(512.41, 53.91) --
+	(512.79, 53.89) --
+	(513.17, 53.86) --
+	(513.55, 53.84) --
+	(513.93, 53.82) --
+	(514.31, 53.80) --
+	(514.69, 53.78) --
+	(515.07, 53.76) --
+	(515.45, 53.74) --
+	(515.83, 53.72) --
+	(516.21, 53.70) --
+	(516.59, 53.68) --
+	(516.97, 53.66) --
+	(517.35, 53.64) --
+	(517.73, 53.62) --
+	(518.11, 53.60) --
+	(518.49, 53.58) --
+	(518.87, 53.56) --
+	(519.25, 53.54) --
+	(519.63, 53.53) --
+	(520.01, 53.51) --
+	(520.39, 53.49) --
+	(520.77, 53.47) --
+	(521.15, 53.45) --
+	(521.53, 53.43) --
+	(521.90, 53.41) --
+	(522.28, 53.39) --
+	(522.66, 53.38) --
+	(523.04, 53.36) --
+	(523.42, 53.34) --
+	(523.80, 53.32) --
+	(524.18, 53.30) --
+	(524.56, 53.28) --
+	(524.94, 53.27) --
+	(525.32, 53.25) --
+	(525.70, 53.23) --
+	(526.08, 53.21) --
+	(526.46, 53.20) --
+	(526.84, 53.18) --
+	(527.22, 53.16) --
+	(527.60, 53.14) --
+	(527.98, 53.13) --
+	(528.36, 53.11);
 \end{scope}

### 2020-08-26 benchmarking/benchmarkingVM/ESS_round2.tex
results update

--- 2020-08-10 benchmarking/benchmarkingVM/ESS_round2.tex
@@
-% Created by tikzDevice version 0.12.3 on 2020-08-10 16:04:21
+% Created by tikzDevice version 0.12.3.1 on 2020-08-25 15:33:23
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,374.64) --
-	(203.52,578.16);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (286.65,578.16) --
-	(286.65,490.17) --
-	(  0.00,203.52);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (  0.00,346.12) --
-	(232.04,578.16);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (286.65,578.16) --
-	(286.65,518.69) --
-	(  0.00,232.04);
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (  0.00,317.60) --
-	(260.56,578.16);
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (286.65,578.16) --
-	(286.65,547.21) --
-	(  0.00,260.56);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (142.89,342.31) {$\frac{1}{64} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,435.87) {$64\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (114.37,342.31) {$\frac{1}{16} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,407.35) {$16\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 84.20,342.31) {$\frac{1}{4} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92,378.83) {$4\times$};
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,528.36);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 96.83,462.17) --
-	(104.39,462.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.95,455.39) --
-	(100.95,467.26);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (100.95,458.94) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (157.25,462.51) --
-	(190.79,462.51);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.21,460.09) --
-	(180.21,464.68);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.21,458.48) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.00,476.56) --
-	(103.04,476.56);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.41,475.30) --
-	( 99.41,477.74);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 99.41,472.52) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.19,434.62) --
-	(105.17,434.62);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (102.83,423.86) --
-	(102.83,441.65);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (102.83,430.59) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.73,464.74) --
-	( 95.52,464.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 90.46,459.17) --
-	( 90.46,469.12);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 90.46,461.83) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.57,483.53) --
-	(194.99,483.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.78,482.91) --
-	(194.78,484.13);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.78,480.62) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.61,467.01) --
-	(116.13,467.01);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.49,464.26) --
-	(109.49,469.44);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (109.49,463.79) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.07,471.07) --
-	(193.44,471.07);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.83,468.87) --
-	(191.83,473.05);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.83,467.03) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (164.54,476.74) --
-	(164.84,476.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (164.69,476.63) --
-	(164.69,476.85);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (164.69,472.71) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.97,429.18) --
-	(112.07,429.18);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (107.26,425.26) --
-	(107.26,432.48);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (107.26,425.15) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (103.25,451.88) --
-	(115.87,451.88);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (110.51,447.05) --
-	(110.51,455.79);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (110.51,448.98) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.12,485.74) --
-	(196.43,485.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.27,485.16) --
-	(196.27,486.31);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.27,482.84) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.15,474.71) --
-	(181.63,474.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.43,471.39) --
-	(177.43,477.57);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.43,471.49) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.21,475.71) --
-	(184.09,475.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.98,464.98) --
-	(174.98,482.73);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.98,471.68) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.98,485.03) --
-	(197.78,485.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.38,484.42) --
-	(197.38,485.62);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.38,481.00) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (150.24,443.07) --
-	(164.70,443.07);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.71,436.47) --
-	(158.71,448.06);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.71,439.03) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (178.58,473.47) --
-	(182.90,473.47);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.86,467.70) --
-	(180.86,477.96);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.86,470.56) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.48,498.31) --
-	(212.33,498.31);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.49,497.03) --
-	(210.49,499.52);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.49,495.41) {$\kappa$};
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (  0.00,368.65) --
+	(209.51,578.16);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (283.33,578.16) --
+	(283.33,492.84) --
+	(  0.00,209.51);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,342.13) --
+	(236.03,578.16);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (283.33,578.16) --
+	(283.33,519.37) --
+	(  0.00,236.03);
+
+\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round] (  0.00,315.60) --
+	(262.56,578.16);
+
+\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round] (283.33,578.16) --
+	(283.33,545.89) --
+	(  0.00,262.56);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (136.90,342.31) {$\frac{1}{64} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,429.88) {$64\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (110.38,342.31) {$\frac{1}{16} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,403.36) {$16\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 82.20,342.31) {$\frac{1}{4} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92,376.84) {$4\times$};
+
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,528.36);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 69.78,442.39) --
+	( 87.52,442.39);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 80.64,435.58) --
+	( 80.64,447.40);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 80.64,439.16) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (113.18,466.07) --
+	(139.72,466.07);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (130.72,464.03) --
+	(130.72,467.92);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (130.72,462.04) {$L$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 72.46,458.74) --
+	( 82.66,458.74);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 78.23,457.64) --
+	( 78.23,459.78);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 78.23,454.71) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 67.86,420.09) --
+	( 87.25,420.09);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 79.91,409.91) --
+	( 79.91,426.69);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 79.91,416.05) {$h$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 46.78,445.45) --
+	( 58.72,445.45);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 53.67,440.98) --
+	( 53.67,449.06);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 53.67,442.54) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.23,465.32) --
+	(172.50,465.32);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.36,464.91) --
+	(172.36,465.72);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.36,462.41) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.61,498.53) --
+	(202.14,498.53);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (200.46,495.69) --
+	(200.46,501.00);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (200.46,495.30) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.14,477.19) --
+	(182.23,477.19);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.29,473.20) --
+	(180.29,480.49);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.29,473.16) {$L$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (203.91,507.29) --
+	(209.53,507.29);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (206.93,504.13) --
+	(206.93,510.00);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (206.93,503.26) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.53,488.44) --
+	(196.14,488.44);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.71,485.34) --
+	(192.71,491.10);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.71,484.40) {$h$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (197.45,500.32) --
+	(203.99,500.32);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (201.00,497.70) --
+	(201.00,502.63);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (201.00,497.42) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (208.42,508.32) --
+	(214.48,508.32);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.69,505.44) --
+	(211.69,510.82);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.69,505.41) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (159.29,461.48) --
+	(163.09,461.48);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.28,459.47) --
+	(161.28,463.29);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (161.28,458.25) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.43,473.75) --
+	(176.80,473.75);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.74,467.42) --
+	(174.74,478.51);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.74,469.72) {$L$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.87,499.81) --
+	(197.04,499.81);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.98,499.49) --
+	(195.98,500.13);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.98,495.78) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (140.13,433.28) --
+	(150.21,433.28);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (145.82,430.75) --
+	(145.82,435.51);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (145.82,429.24) {$h$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.54,457.34) --
+	(157.36,457.34);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (154.25,453.95) --
+	(154.25,460.21);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (154.25,454.43) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.20,500.26) --
+	(200.08,500.26);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.16,500.10) --
+	(199.16,500.41);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.16,497.35) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (156.23,472.45) --
+	(158.05,472.45);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (157.16,469.05) --
+	(157.16,475.33);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (157.16,469.22) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (162.22,469.44) --
+	(167.11,469.44);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.82,468.18) --
+	(164.82,470.63);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (164.82,465.41) {$L$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.39,494.42) --
+	(190.63,494.42);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.55,494.08) --
+	(189.55,494.75);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (189.55,490.38) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (145.43,461.88) --
+	(154.13,461.88);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.27,458.33) --
+	(150.27,464.86);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (150.27,457.84) {$h$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (132.82,466.76) --
+	(167.42,466.76);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (157.06,464.72) --
+	(157.06,468.61);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (157.06,463.86) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.44,500.16) --
+	(198.69,500.16);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.57,499.71) --
+	(198.57,500.60);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.57,497.25) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (102.23,461.86) --
+	(111.25,461.86);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (107.27,457.98) --
+	(107.27,465.08);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (107.27,458.63) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.53,471.68) --
+	(161.05,471.68);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (156.88,467.85) --
+	(156.88,474.87);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (156.88,467.65) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (155.91,473.63) --
+	(158.58,473.63);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (157.29,473.45) --
+	(157.29,473.81);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (157.29,469.59) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 95.38,428.77) --
+	(104.88,428.77);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (100.71,424.39) --
+	(100.71,432.32);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (100.71,424.73) {$h$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 99.79,451.10) --
+	(116.82,451.10);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (110.14,444.27) --
+	(110.14,456.13);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (110.14,448.20) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.08,482.13) --
+	(188.19,482.13);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.81,481.71) --
+	(185.81,482.53);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.81,479.22) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (202.53,480.00) --
+	(207.67,480.00);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (205.27,469.20) --
+	(205.27,486.87);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.27,476.78) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.37,482.86) --
+	(188.12,482.86);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.89,479.54) --
+	(185.89,485.69);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.89,478.82) {$L$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (213.22,510.87) --
+	(217.09,510.87);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (215.25,508.22) --
+	(215.25,513.20);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (215.25,506.84) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.15,475.07) --
+	(179.18,475.07);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (177.27,471.46) --
+	(177.27,478.10);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.27,471.03) {$h$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.77,483.80) --
+	(193.75,483.80);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.87,480.19) --
+	(191.87,486.83);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.87,480.89) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (203.55,502.56) --
+	(207.55,502.56);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (205.65,499.82) --
+	(205.65,504.96);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.65,499.66) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.08,495.96) --
+	(151.08,497.69);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (151.08,493.62) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (206.36,501.50) --
+	(206.36,504.37);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (206.36,498.95) {$L$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.68,502.30) --
+	(191.68,502.71);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.68,498.47) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (158.37,472.23) --
+	(158.37,474.23);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.37,469.22) {$h$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (153.51,471.94) --
+	(153.51,477.11);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (153.51,471.79) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (209.66,509.55) --
+	(209.66,511.28);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.66,507.53) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.80,474.68) --
+	(177.08,474.68);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.38,470.11) --
+	(173.38,478.38);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.38,471.46) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (147.87,452.98) --
+	(153.50,452.98);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.89,449.28) --
+	(150.89,456.08);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (150.89,448.95) {$L$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.87,485.78) --
+	(190.24,485.78);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.57,485.35) --
+	(189.57,486.21);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (189.57,481.75) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (146.53,446.62) --
+	(159.26,446.62);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (153.94,441.01) --
+	(153.94,450.95);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (153.94,442.59) {$h$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.76,472.80) --
+	(168.03,472.80);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.88,467.90) --
+	(161.88,476.70);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (161.88,469.90) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.33,498.56) --
+	(204.41,498.56);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (202.04,497.16) --
+	(202.04,499.86);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.04,495.65) {$\kappa$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.39,481.76) --
+	(196.26,481.76);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.35,478.54) --
+	(195.35,484.51);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.35,478.53) {$p$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.83,478.31) --
+	(183.47,478.31);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.66,474.79) --
+	(182.66,481.27);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.66,474.27) {$L$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (197.76,500.43) --
+	(199.40,500.43);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.60,500.31) --
+	(198.60,500.55);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.60,496.40) {$r$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.12,480.91) --
+	(183.39,480.91);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.82,478.84) --
+	(181.82,482.78);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.82,476.88) {$h$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.86,485.43) --
+	(188.00,485.43);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.44,484.34) --
+	(187.44,486.46);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.44,482.53) {$\sigma$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (207.49,512.69) --
+	(209.23,512.69);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (208.38,512.04) --
+	(208.38,513.32);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (208.38,509.78) {$\kappa$};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (149.40,234.96) --
-	(492.60,578.16);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (575.73,578.16) --
-	(575.73,490.17) --
-	(149.40, 63.84) --
-	(149.40,234.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (149.40,206.44) --
-	(521.12,578.16);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (575.73,578.16) --
-	(575.73,518.69) --
-	(149.40, 92.36) --
-	(149.40,206.44);
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (149.40,177.92) --
-	(549.64,578.16);
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (575.73,578.16) --
-	(575.73,547.21) --
-	(149.40,120.88) --
-	(149.40,177.92);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (431.97,342.31) {$\frac{1}{64} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,435.87) {$64\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (403.45,342.31) {$\frac{1}{16} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,407.35) {$16\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (373.28,342.31) {$\frac{1}{4} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.00,378.83) {$4\times$};
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (338.88,338.88) -- (528.36,528.36);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (385.91,398.02) --
-	(393.47,398.02);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (390.03,382.13) --
-	(390.03,406.87);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (390.03,394.79) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (446.33,475.91) --
-	(479.87,475.91);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (469.29,475.07) --
-	(469.29,476.72);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (469.29,471.88) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (384.08,472.93) --
-	(392.12,472.93);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (388.49,468.95) --
-	(388.49,476.26);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (388.49,468.89) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.27,397.74) --
-	(394.25,397.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (391.91,377.39) --
-	(391.91,407.77);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (391.91,393.71) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (372.81,366.19) --
-	(384.60,366.19);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (379.54,357.18) --
-	(379.54,372.44);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (379.54,363.29) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.65,483.32) --
-	(484.07,483.32);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.86,483.08) --
-	(483.86,483.56);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.86,480.42) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (388.69,424.26) --
-	(405.21,424.26);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (398.57,421.10) --
-	(398.57,427.01);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (398.57,421.04) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.15,476.34) --
-	(482.52,476.34);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (480.91,473.72) --
-	(480.91,478.65);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (480.91,472.30) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (453.62,477.11) --
-	(453.92,477.11);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (453.77,476.35) --
-	(453.77,477.84);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (453.77,473.07) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (390.05,422.63) --
-	(401.15,422.63);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (396.34,419.69) --
-	(396.34,425.20);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (396.34,418.60) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (392.33,405.99) --
-	(404.95,405.99);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (399.59,404.44) --
-	(399.59,407.42);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (399.59,403.08) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.20,485.27) --
-	(485.51,485.27);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.35,485.11) --
-	(485.35,485.43);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (485.35,482.37) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.23,469.66) --
-	(470.71,469.66);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (466.51,467.06) --
-	(466.51,471.96);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (466.51,466.43) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (447.29,481.52) --
-	(473.17,481.52);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.06,478.07) --
-	(464.06,484.47);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (464.06,477.48) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.06,487.79) --
-	(486.86,487.79);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.46,487.17) --
-	(486.46,488.40);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (486.46,483.76) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (439.32,448.83) --
-	(453.78,448.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (447.79,445.54) --
-	(447.79,451.66);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (447.79,444.80) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (467.66,470.37) --
-	(471.98,470.37);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (469.94,468.48) --
-	(469.94,472.10);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (469.94,467.47) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (497.56,499.91) --
-	(501.41,499.91);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.57,499.32) --
-	(499.57,500.49);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (499.57,497.01) {$\kappa$};
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (162.66,242.23) --
+	(498.59,578.16);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (572.41,578.16) --
+	(572.41,492.84) --
+	(162.66, 83.09) --
+	(162.66,242.23);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.66,215.71) --
+	(525.11,578.16);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (572.41,578.16) --
+	(572.41,519.37) --
+	(162.66,109.61) --
+	(162.66,215.71);
+
+\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round] (162.66,189.19) --
+	(551.64,578.16);
+
+\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round] (572.41,578.16) --
+	(572.41,545.89) --
+	(162.66,136.14) --
+	(162.66,189.19);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (425.98,342.31) {$\frac{1}{64} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,429.88) {$64\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (399.46,342.31) {$\frac{1}{16} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,403.36) {$16\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (371.28,342.31) {$\frac{1}{4} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.00,376.84) {$4\times$};
+
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (338.88,338.88) -- (528.36,528.36);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (358.86,422.82) --
+	(376.60,422.82);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (369.72,420.40) --
+	(369.72,424.97);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (369.72,419.59) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (402.26,452.57) --
+	(428.80,452.57);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (419.80,451.90) --
+	(419.80,453.22);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (419.80,448.54) {$L$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (361.54,446.67) --
+	(371.74,446.67);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (367.31,445.22) --
+	(367.31,448.02);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (367.31,442.64) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (356.94,418.52) --
+	(376.33,418.52);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (368.99,411.75) --
+	(368.99,423.52);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (368.99,414.49) {$h$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (335.86,430.80) --
+	(347.80,430.80);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (342.75,426.42) --
+	(342.75,434.36);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (342.75,427.90) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (461.31,451.20) --
+	(461.58,451.20);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (461.44,449.83) --
+	(461.44,452.49);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (461.44,448.30) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (487.69,486.05) --
+	(491.22,486.05);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (489.54,480.97) --
+	(489.54,490.06);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (489.54,482.83) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (467.22,467.41) --
+	(471.31,467.41);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (469.37,463.99) --
+	(469.37,470.31);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (469.37,463.37) {$L$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (492.99,498.84) --
+	(498.61,498.84);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (496.01,495.08) --
+	(496.01,501.97);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (496.01,494.80) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (477.61,480.02) --
+	(485.22,480.02);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.79,475.53) --
+	(481.79,483.64);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (481.79,475.98) {$h$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (486.53,495.85) --
+	(493.07,495.85);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (490.08,490.38) --
+	(490.08,500.09);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (490.08,492.94) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (497.50,497.26) --
+	(503.56,497.26);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (500.77,493.73) --
+	(500.77,500.23);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (500.77,494.35) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (448.37,444.25) --
+	(452.17,444.25);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (450.36,439.52) --
+	(450.36,448.04);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (450.36,441.02) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (461.51,464.46) --
+	(465.88,464.46);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (463.82,463.55) --
+	(463.82,465.34);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (463.82,460.43) {$L$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.95,486.64) --
+	(486.12,486.64);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (485.06,486.09) --
+	(485.06,487.17);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (485.06,482.60) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (429.21,430.01) --
+	(439.29,430.01);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (434.90,424.45) --
+	(434.90,434.32);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (434.90,425.98) {$h$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (439.62,453.02) --
+	(446.44,453.02);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (443.33,448.90) --
+	(443.33,456.41);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (443.33,450.12) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (487.28,484.52) --
+	(489.16,484.52);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (488.24,483.75) --
+	(488.24,485.27);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (488.24,481.62) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (445.31,455.28) --
+	(447.13,455.28);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (446.24,453.50) --
+	(446.24,456.90);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (446.24,452.05) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (451.30,455.59) --
+	(456.19,455.59);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (453.90,453.77) --
+	(453.90,457.25);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (453.90,451.56) {$L$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (477.47,481.09) --
+	(479.71,481.09);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (478.63,480.69) --
+	(478.63,481.49);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (478.63,477.06) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (434.51,455.34) --
+	(443.21,455.34);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (439.35,453.12) --
+	(439.35,457.33);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (439.35,451.30) {$h$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (421.90,459.26) --
+	(456.50,459.26);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (446.14,456.93) --
+	(446.14,461.33);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (446.14,456.35) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (487.52,482.35) --
+	(487.77,482.35);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (487.65,481.98) --
+	(487.65,482.72);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (487.65,479.45) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (391.31,419.90) --
+	(400.33,419.90);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (396.35,418.40) --
+	(396.35,421.29);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (396.35,416.67) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (440.61,458.29) --
+	(450.13,458.29);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (445.96,456.11) --
+	(445.96,460.25);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (445.96,454.26) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (444.99,457.12) --
+	(447.66,457.12);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (446.37,456.64) --
+	(446.37,457.60);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (446.37,453.09) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (384.46,419.27) --
+	(393.96,419.27);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (389.79,417.46) --
+	(389.79,420.93);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (389.79,415.24) {$h$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (388.87,431.53) --
+	(405.90,431.53);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (399.22,428.40) --
+	(399.22,434.22);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (399.22,428.63) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (472.16,463.25) --
+	(477.27,463.25);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (474.89,463.00) --
+	(474.89,463.51);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.89,460.35) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (491.61,491.43) --
+	(496.75,491.43);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (494.35,488.34) --
+	(494.35,494.10);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (494.35,488.21) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (472.45,473.26) --
+	(477.20,473.26);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (474.97,469.46) --
+	(474.97,476.43);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.97,469.23) {$L$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (502.30,500.72) --
+	(506.17,500.72);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (504.33,497.68) --
+	(504.33,503.35);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (504.33,496.69) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (464.23,462.90) --
+	(468.26,462.90);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (466.35,459.58) --
+	(466.35,465.73);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (466.35,458.87) {$h$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (478.85,477.19) --
+	(482.83,477.19);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.95,474.02) --
+	(480.95,479.91);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (480.95,474.29) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (492.63,491.09) --
+	(496.63,491.09);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (494.73,488.28) --
+	(494.73,493.53);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (494.73,488.18) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (440.16,449.31) --
+	(440.16,456.88);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (440.16,450.24) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (495.44,483.20) --
+	(495.44,486.68);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (495.44,480.99) {$L$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.76,488.95) --
+	(480.76,489.76);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (480.76,485.33) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (447.45,456.35) --
+	(447.45,466.27);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (447.45,457.91) {$h$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (442.59,463.63) --
+	(442.59,469.80);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (442.59,464.06) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (498.74,489.94) --
+	(498.74,492.58);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (498.74,488.40) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (457.88,458.77) --
+	(466.16,458.77);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (462.46,456.24) --
+	(462.46,461.00);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (462.46,455.54) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (436.95,441.13) --
+	(442.58,441.13);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (439.97,438.18) --
+	(439.97,443.68);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (439.97,437.10) {$L$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (477.95,472.82) --
+	(479.32,472.82);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (478.65,472.59) --
+	(478.65,473.05);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (478.65,468.79) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (435.61,443.82) --
+	(448.34,443.82);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (443.02,439.42) --
+	(443.02,447.40);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (443.02,439.79) {$h$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (441.84,458.10) --
+	(457.11,458.10);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (450.96,453.81) --
+	(450.96,461.61);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (450.96,455.20) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (488.41,481.91) --
+	(493.49,481.91);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (491.12,481.83) --
+	(491.12,481.99);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (491.12,479.00) {$\kappa$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.47,478.97) --
+	(485.34,478.97);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (484.43,467.29) --
+	(484.43,486.16);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (484.43,475.74) {$p$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (470.91,465.38) --
+	(472.55,465.38);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (471.74,453.39) --
+	(471.74,472.69);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (471.74,461.35) {$L$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (486.84,482.47) --
+	(488.48,482.47);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (487.68,470.56) --
+	(487.68,489.76);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (487.68,478.44) {$r$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (469.20,464.45) --
+	(472.47,464.45);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (470.90,451.93) --
+	(470.90,471.95);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (470.90,460.42) {$h$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (475.94,474.07) --
+	(477.08,474.07);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (476.52,462.11) --
+	(476.52,481.38);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (476.52,471.17) {$\sigma$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (496.57,491.37) --
+	(498.31,491.37);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (497.46,479.32) --
+	(497.46,498.71);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (497.46,488.47) {$\kappa$};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00, 85.56) --
-	(286.65,372.21) --
-	(286.65,201.09) --
-	( 85.56,  0.00);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (  0.00, 57.04) --
-	(286.65,343.69) --
-	(286.65,229.61) --
-	( 57.04,  0.00);
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (  0.00, 28.52) --
-	(286.65,315.17) --
-	(286.65,258.13) --
-	( 28.52,  0.00);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (142.89, 53.23) {$\frac{1}{64} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,146.79) {$64\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (114.37, 53.23) {$\frac{1}{16} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,118.27) {$16\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 84.20, 53.23) {$\frac{1}{4} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92, 89.75) {$4\times$};
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] ( 49.80, 49.80) -- (239.28,239.28);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (166.31,108.94) --
-	(178.18,108.94);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.09, 93.05) --
-	(173.09,117.79);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.09,105.71) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.01,186.83) --
-	(175.60,186.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.43,185.99) --
-	(173.43,187.64);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.43,182.80) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.22,183.85) --
-	(188.66,183.85);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.48,179.87) --
-	(187.48,187.18);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.48,179.81) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (134.78,108.66) --
-	(152.57,108.66);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.54, 88.31) --
-	(145.54,118.69);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (145.54,104.63) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (170.09, 77.11) --
-	(180.04, 77.11);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.66, 68.10) --
-	(175.66, 83.36);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (175.66, 74.21) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.83,194.24) --
-	(195.05,194.24);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.45,194.00) --
-	(194.45,194.48);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.45,191.34) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (165.91,162.72) --
-	(169.91,162.72);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.01,157.69) --
-	(168.01,166.76);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (168.01,159.49) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.51,190.76) --
-	(192.13,190.76);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.40,188.99) --
-	(190.40,192.40);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.40,186.73) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.13,194.78) --
-	(192.93,194.78);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.54,192.84) --
-	(192.54,196.56);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.54,190.75) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (154.98,160.08) --
-	(160.63,160.08);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.00,153.30) --
-	(158.00,165.16);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.00,156.04) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.83,159.04) --
-	(165.18,159.04);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.57,156.47) --
-	(163.57,161.34);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (163.57,156.14) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.10,198.95) --
-	(199.15,198.95);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.63,198.56) --
-	(198.63,199.33);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.63,196.04) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.18,135.18) --
-	(180.36,135.18);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.93,132.02) --
-	(177.93,137.93);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.93,131.96) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.79,187.26) --
-	(183.97,187.26);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.99,184.64) --
-	(181.99,189.57);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.99,183.22) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.55,188.03) --
-	(187.77,188.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.66,187.27) --
-	(187.66,188.76);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.66,183.99) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (136.18,133.55) --
-	(143.40,133.55);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.10,130.61) --
-	(140.10,136.12);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (140.10,129.52) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (157.97,116.91) --
-	(166.71,116.91);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.80,115.36) --
-	(162.80,118.34);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (162.80,114.00) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.08,196.19) --
-	(197.23,196.19);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.66,196.03) --
-	(196.66,196.35);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.66,193.29) {$\kappa$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.94,146.87) --
-	(183.64,146.87);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.81,144.32) --
-	(182.81,149.14);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.81,143.64) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.45,193.77) --
-	(184.72,193.77);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (183.15,191.53) --
-	(183.15,195.79);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.15,189.74) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.22,193.77) --
-	(188.78,193.77);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.50,193.53) --
-	(188.50,194.01);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.50,189.74) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (156.86,161.33) --
-	(159.29,161.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.11,158.55) --
-	(158.11,163.78);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.11,157.30) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (155.66,151.01) --
-	(161.22,151.01);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.63,148.68) --
-	(158.63,153.10);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.63,148.10) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.03,198.53) --
-	(199.38,198.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.24,196.83) --
-	(198.24,200.10);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.24,195.63) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.31,180.58) --
-	(188.49,180.58);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.63,177.98) --
-	(185.63,182.88);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.63,177.35) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.90,192.44) --
-	(193.65,192.44);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.63,188.99) --
-	(186.63,195.39);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (186.63,188.40) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.34,198.71) --
-	(196.54,198.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.95,198.09) --
-	(195.95,199.32);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.95,194.68) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (147.39,159.75) --
-	(158.98,159.75);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.99,156.46) --
-	(153.99,162.58);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (153.99,155.72) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (178.62,181.29) --
-	(188.88,181.29);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.39,179.40) --
-	(184.39,183.02);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.39,178.39) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (207.95,210.83) --
-	(210.44,210.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.23,210.24) --
-	(209.23,211.41);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.23,207.93) {$\kappa$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.58,195.33) --
-	(183.78,195.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.49,193.67) --
-	(180.49,196.87);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.49,192.11) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.38,201.82) --
-	(174.02,201.82);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.39,201.65) --
-	(171.39,201.98);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.39,197.78) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.62,199.95) --
-	(199.37,199.95);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (199.00,198.75) --
-	(199.00,201.09);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.00,195.92) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.20,178.14) --
-	(180.56,178.14);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.38,173.53) --
-	(180.38,181.90);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.38,174.11) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.06,186.15) --
-	(185.69,186.15);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.64,182.17) --
-	(182.64,189.49);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.64,183.25) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.62,212.25) --
-	(213.79,212.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.74,211.79) --
-	(212.74,212.69);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.74,209.34) {$\kappa$};
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (  0.00, 79.57) --
+	(283.33,362.91) --
+	(283.33,203.76) --
+	( 79.57,  0.00);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00, 53.05) --
+	(283.33,336.38) --
+	(283.33,230.29) --
+	( 53.05,  0.00);
+
+\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round] (  0.00, 26.52) --
+	(283.33,309.86) --
+	(283.33,256.81) --
+	( 26.52,  0.00);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (136.90, 53.23) {$\frac{1}{64} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,140.80) {$64\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (110.38, 53.23) {$\frac{1}{16} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,114.28) {$16\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 82.20, 53.23) {$\frac{1}{4} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92, 87.76) {$4\times$};
+
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 49.80, 49.80) -- (239.28,239.28);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (146.50,133.74) --
+	(158.32,133.74);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (153.31,131.32) --
+	(153.31,135.89);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (153.31,130.51) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.95,163.49) --
+	(178.84,163.49);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.99,162.82) --
+	(176.99,164.14);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.99,159.46) {$L$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.56,157.59) --
+	(170.70,157.59);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.66,156.14) --
+	(169.66,158.94);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.66,153.56) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (120.83,129.44) --
+	(137.61,129.44);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (131.01,122.67) --
+	(131.01,134.44);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (131.01,125.41) {$h$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.90,141.72) --
+	(159.98,141.72);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (156.37,137.34) --
+	(156.37,145.28);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (156.37,138.82) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.83,162.12) --
+	(176.64,162.12);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.24,160.75) --
+	(176.24,163.41);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.24,159.22) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (206.61,196.97) --
+	(211.92,196.97);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (209.45,191.89) --
+	(209.45,200.98);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.45,193.75) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.12,178.33) --
+	(191.41,178.33);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.11,174.91) --
+	(188.11,181.23);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.11,174.29) {$L$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (215.05,209.76) --
+	(220.92,209.76);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (218.21,206.00) --
+	(218.21,212.89);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (218.21,205.72) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.26,190.94) --
+	(202.02,190.94);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.36,186.45) --
+	(199.36,194.56);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.36,186.90) {$h$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (208.62,206.77) --
+	(213.55,206.77);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.24,201.30) --
+	(211.24,211.01);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.24,203.86) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (216.36,208.18) --
+	(221.74,208.18);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (219.24,204.65) --
+	(219.24,211.15);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (219.24,205.27) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (170.39,155.17) --
+	(174.21,155.17);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.40,150.44) --
+	(172.40,158.96);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.40,151.94) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.34,175.38) --
+	(189.43,175.38);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.67,174.47) --
+	(184.67,176.26);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.67,171.35) {$L$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (210.41,197.56) --
+	(211.05,197.56);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (210.73,197.01) --
+	(210.73,198.09);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.73,193.52) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (141.67,140.93) --
+	(146.43,140.93);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (144.20,135.37) --
+	(144.20,145.24);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (144.20,136.90) {$h$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.87,163.94) --
+	(171.13,163.94);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.26,159.82) --
+	(168.26,167.33);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (168.26,161.04) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.02,195.44) --
+	(211.33,195.44);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.18,194.67) --
+	(211.18,196.19);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.18,192.54) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.97,166.20) --
+	(186.25,166.20);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.37,164.42) --
+	(183.37,167.82);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.37,162.97) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.10,166.51) --
+	(181.55,166.51);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.36,164.69) --
+	(180.36,168.17);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.36,162.48) {$L$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (205.00,192.01) --
+	(205.67,192.01);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (205.34,191.61) --
+	(205.34,192.41);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.34,187.98) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.25,166.26) --
+	(175.78,166.26);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.80,164.04) --
+	(172.80,168.25);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.80,162.22) {$h$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.64,170.18) --
+	(179.53,170.18);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (177.68,167.85) --
+	(177.68,172.25);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.68,167.27) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (210.63,193.27) --
+	(211.52,193.27);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.08,192.90) --
+	(211.08,193.64);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.08,190.37) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.90,130.82) --
+	(176.00,130.82);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.78,129.32) --
+	(172.78,132.21);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.78,127.59) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.77,169.21) --
+	(185.79,169.21);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.60,167.03) --
+	(182.60,171.17);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.60,165.18) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.37,168.04) --
+	(184.73,168.04);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.55,167.56) --
+	(184.55,168.52);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.55,164.01) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (135.31,130.19) --
+	(143.24,130.19);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (139.69,128.38) --
+	(139.69,131.85);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (139.69,126.16) {$h$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (155.19,142.45) --
+	(167.05,142.45);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (162.02,139.32) --
+	(162.02,145.14);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (162.02,139.55) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.63,174.17) --
+	(193.45,174.17);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.05,173.92) --
+	(193.05,174.43);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.05,171.27) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.12,202.35) --
+	(197.79,202.35);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.92,199.26) --
+	(190.92,205.02);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.92,199.13) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.46,184.18) --
+	(196.61,184.18);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.78,180.38) --
+	(193.78,187.35);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.78,180.15) {$L$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (219.14,211.64) --
+	(224.12,211.64);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (221.79,208.60) --
+	(221.79,214.27);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (221.79,207.61) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.38,173.82) --
+	(189.02,173.82);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.99,170.50) --
+	(185.99,176.65);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.99,169.79) {$h$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.11,188.11) --
+	(197.75,188.11);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.72,184.94) --
+	(194.72,190.83);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.72,185.21) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (210.74,202.01) --
+	(215.88,202.01);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (213.48,199.20) --
+	(213.48,204.45);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (213.48,199.10) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (206.88,164.39) --
+	(208.61,164.39);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (207.77,160.23) --
+	(207.77,167.80);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.77,161.16) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (212.42,195.94) --
+	(215.29,195.94);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (213.91,194.12) --
+	(213.91,197.60);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (213.91,191.91) {$L$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (213.22,200.28) --
+	(213.63,200.28);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (213.43,199.87) --
+	(213.43,200.68);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (213.43,196.25) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.15,172.87) --
+	(185.15,172.87);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.18,167.27) --
+	(184.18,177.19);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.18,168.83) {$h$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.86,177.89) --
+	(188.03,177.89);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.62,174.55) --
+	(185.62,180.72);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.62,174.98) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (220.47,202.23) --
+	(222.20,202.23);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (221.35,200.86) --
+	(221.35,203.50);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (221.35,199.32) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.03,169.69) --
+	(189.30,169.69);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.60,167.16) --
+	(185.60,171.92);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.60,166.46) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (160.20,152.05) --
+	(167.00,152.05);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (163.90,149.10) --
+	(163.90,154.60);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (163.90,148.02) {$L$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.27,183.74) --
+	(197.13,183.74);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.70,183.51) --
+	(196.70,183.97);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.70,179.71) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.93,154.74) --
+	(161.87,154.74);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (157.54,150.34) --
+	(157.54,158.32);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (157.54,150.71) {$h$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.82,169.02) --
+	(187.62,169.02);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.72,164.73) --
+	(183.72,172.53);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.72,166.12) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (208.08,192.83) --
+	(210.78,192.83);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (209.48,192.75) --
+	(209.48,192.91);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.48,189.92) {$\kappa$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.46,189.89) --
+	(195.43,189.89);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.68,178.21) --
+	(192.68,197.08);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.68,186.66) {$p$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.71,176.30) --
+	(192.19,176.30);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.23,164.31) --
+	(189.23,183.61);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (189.23,172.27) {$L$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.23,193.39) --
+	(211.47,193.39);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.35,181.48) --
+	(211.35,200.68);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.35,189.36) {$r$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.76,175.37) --
+	(193.70,175.37);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.83,162.85) --
+	(191.83,182.87);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.83,171.34) {$h$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.26,184.99) --
+	(197.38,184.99);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.35,173.03) --
+	(196.35,192.30);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.35,182.09) {$\sigma$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (222.96,202.29) --
+	(224.24,202.29);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (223.61,190.24) --
+	(223.61,209.63);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (223.61,199.39) {$\kappa$};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (485.73,205.86) --
-	(485.73, 51.84);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (485.73,126.77) {$77\times $};
-\definecolor{fillColor}{RGB}{0,140,186}
-
-\path[fill=fillColor] (485.73,205.86) circle (  1.87);
-\definecolor{fillColor}{RGB}{105,105,105}
-
-\path[fill=fillColor] (485.73, 51.84) circle (  1.87);
-\definecolor{fillColor}{gray}{0.64}
-
-\path[fill=fillColor] (485.73,199.70) circle (  1.87);
-\definecolor{fillColor}{RGB}{0,140,186}
-
-\path[fill=fillColor] (347.47, 84.16) circle (  2.15);
-\definecolor{fillColor}{RGB}{105,105,105}
-
-\path[fill=fillColor] (347.47, 72.71) circle (  2.15);
-\definecolor{fillColor}{gray}{0.64}
-
-\path[fill=fillColor] (347.47, 61.25) circle (  2.15);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 80.88) {adapt (\textit{real})};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 69.42) {adapt (\textit{cat})};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 57.97) {adapt (\textit{quant})};
-\definecolor{fillColor}{RGB}{0,140,186}
-
-\path[fill=fillColor] (347.47, 84.16) circle (  2.15);
-\definecolor{fillColor}{RGB}{105,105,105}
-
-\path[fill=fillColor] (347.47, 72.71) circle (  2.15);
-\definecolor{fillColor}{gray}{0.64}
-
-\path[fill=fillColor] (347.47, 61.25) circle (  2.15);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 80.88) {adapt (\textit{real})};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 69.42) {adapt (\textit{cat})};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 57.97) {adapt (\textit{quant})};
-\definecolor{fillColor}{RGB}{0,140,186}
-
-\path[fill=fillColor] (394.78,308.65) circle (  1.87);
-
-\path[fill=fillColor] (347.47, 84.16) circle (  2.15);
-\definecolor{fillColor}{RGB}{105,105,105}
-
-\path[fill=fillColor] (347.47, 72.71) circle (  2.15);
-\definecolor{fillColor}{gray}{0.64}
-
-\path[fill=fillColor] (347.47, 61.25) circle (  2.15);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 80.88) {adapt (\textit{real})};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 69.42) {adapt (\textit{cat})};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 57.97) {adapt (\textit{quant})};
-\definecolor{fillColor}{RGB}{0,140,186}
-
-\path[fill=fillColor] (390.04,246.75) circle (  1.87);
-\definecolor{fillColor}{gray}{0.64}
-
-\path[fill=fillColor] (390.04,277.75) circle (  1.87);
-\definecolor{fillColor}{RGB}{0,140,186}
-
-\path[fill=fillColor] (347.47, 84.16) circle (  2.15);
-\definecolor{fillColor}{RGB}{105,105,105}
-
-\path[fill=fillColor] (347.47, 72.71) circle (  2.15);
-\definecolor{fillColor}{gray}{0.64}
-
-\path[fill=fillColor] (347.47, 61.25) circle (  2.15);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 80.88) {adapt (\textit{real})};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 69.42) {adapt (\textit{cat})};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 57.97) {adapt (\textit{quant})};
-
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (404.25,204.65) --
-	(404.25,100.19);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (404.25,150.34) {$3.1\times $};
-\definecolor{fillColor}{RGB}{0,140,186}
-
-\path[fill=fillColor] (404.25,204.65) circle (  1.87);
-\definecolor{fillColor}{RGB}{105,105,105}
-
-\path[fill=fillColor] (404.25,100.19) circle (  1.87);
-\definecolor{fillColor}{gray}{0.64}
-
-\path[fill=fillColor] (404.25,210.63) circle (  1.87);
-\definecolor{fillColor}{RGB}{0,140,186}
-
-\path[fill=fillColor] (347.47, 84.16) circle (  2.15);
-\definecolor{fillColor}{RGB}{105,105,105}
-
-\path[fill=fillColor] (347.47, 72.71) circle (  2.15);
-\definecolor{fillColor}{gray}{0.64}
-
-\path[fill=fillColor] (347.47, 61.25) circle (  2.15);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 80.88) {adapt (\textit{real})};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 69.42) {adapt (\textit{cat})};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 57.97) {adapt (\textit{quant})};
-\definecolor{fillColor}{RGB}{0,140,186}
-
-\path[fill=fillColor] (347.47, 84.16) circle (  2.15);
-\definecolor{fillColor}{RGB}{105,105,105}
-
-\path[fill=fillColor] (347.47, 72.71) circle (  2.15);
-\definecolor{fillColor}{gray}{0.64}
-
-\path[fill=fillColor] (347.47, 61.25) circle (  2.15);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 80.88) {adapt (\textit{real})};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 69.42) {adapt (\textit{cat})};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 57.97) {adapt (\textit{quant})};
-\definecolor{fillColor}{RGB}{0,140,186}
-
-\path[fill=fillColor] (433.62,210.36) circle (  1.87);
-\definecolor{fillColor}{gray}{0.64}
-
-\path[fill=fillColor] (433.62,258.51) circle (  1.87);
-\definecolor{fillColor}{RGB}{0,140,186}
-
-\path[fill=fillColor] (347.47, 84.16) circle (  2.15);
-\definecolor{fillColor}{RGB}{105,105,105}
-
-\path[fill=fillColor] (347.47, 72.71) circle (  2.15);
-\definecolor{fillColor}{gray}{0.64}
-
-\path[fill=fillColor] (347.47, 61.25) circle (  2.15);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 80.88) {adapt (\textit{real})};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 69.42) {adapt (\textit{cat})};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 57.97) {adapt (\textit{quant})};
-
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (359.72,284.96) --
-	(359.72,295.15);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (359.72,287.98) {$0.96\times $};
-\definecolor{fillColor}{RGB}{0,140,186}
-
-\path[fill=fillColor] (359.72,284.96) circle (  1.87);
-\definecolor{fillColor}{RGB}{105,105,105}
-
-\path[fill=fillColor] (359.72,295.15) circle (  1.87);
-\definecolor{fillColor}{gray}{0.64}
-
-\path[fill=fillColor] (359.72,315.21) circle (  1.87);
-\definecolor{fillColor}{RGB}{0,140,186}
-
-\path[fill=fillColor] (347.47, 84.16) circle (  2.15);
-\definecolor{fillColor}{RGB}{105,105,105}
-
-\path[fill=fillColor] (347.47, 72.71) circle (  2.15);
-\definecolor{fillColor}{gray}{0.64}
-
-\path[fill=fillColor] (347.47, 61.25) circle (  2.15);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 80.88) {adapt (\textit{real})};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 69.42) {adapt (\textit{cat})};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 57.97) {adapt (\textit{quant})};
-\definecolor{fillColor}{RGB}{0,140,186}
-
-\path[fill=fillColor] (346.46,317.20) circle (  1.87);
-\definecolor{fillColor}{gray}{0.64}
-
-\path[fill=fillColor] (346.46,337.93) circle (  1.87);
-\definecolor{fillColor}{RGB}{0,140,186}
-
-\path[fill=fillColor] (347.47, 84.16) circle (  2.15);
-\definecolor{fillColor}{RGB}{105,105,105}
-
-\path[fill=fillColor] (347.47, 72.71) circle (  2.15);
-\definecolor{fillColor}{gray}{0.64}
-
-\path[fill=fillColor] (347.47, 61.25) circle (  2.15);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 80.88) {adapt (\textit{real})};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 69.42) {adapt (\textit{cat})};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 57.97) {adapt (\textit{quant})};
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (485.73,186.78) --
+	(485.73, 81.34);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (485.73,169.78) {$130\times $};
+\definecolor{fillColor}{RGB}{255,0,109}
+
+\path[fill=fillColor] (485.73,186.78) circle (  1.87);
+
+\path[fill=fillColor] (485.73, 84.24) --
+	(488.24, 79.89) --
+	(483.21, 79.89) --
+	cycle;
+
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (356.88,239.03) --
+	(356.88,234.24);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (356.88,234.69) {$1.2\times $};
+\definecolor{fillColor}{RGB}{253,104,0}
+
+\path[fill=fillColor] (356.88,239.03) circle (  1.87);
+
+\path[fill=fillColor] (356.88,237.15) --
+	(359.40,232.79) --
+	(354.37,232.79) --
+	cycle;
+\definecolor{fillColor}{RGB}{143,161,0}
+
+\path[fill=fillColor] (394.78,233.05) circle (  1.87);
+\definecolor{fillColor}{RGB}{0,195,0}
+
+\path[fill=fillColor] (390.04,227.01) circle (  1.87);
+
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (404.25,203.42) --
+	(404.25,173.39);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (404.25,191.14) {$4\times $};
+\definecolor{fillColor}{RGB}{0,219,171}
+
+\path[fill=fillColor] (404.25,203.42) circle (  1.87);
+
+\path[fill=fillColor] (404.25,176.30) --
+	(406.77,171.94) --
+	(401.74,171.94) --
+	cycle;
+
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (359.72,244.03) --
+	(359.72,242.10);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (359.72,241.01) {$1.1\times $};
+\definecolor{fillColor}{RGB}{0,216,255}
+
+\path[fill=fillColor] (359.72,244.03) circle (  1.87);
+
+\path[fill=fillColor] (359.72,245.01) --
+	(362.24,240.65) --
+	(357.21,240.65) --
+	cycle;
+\definecolor{fillColor}{RGB}{151,0,255}
+
+\path[fill=fillColor] (433.62,236.07) circle (  1.87);
+
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (359.72,217.25) --
+	(359.72,208.71);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (359.72,211.32) {$1.5\times $};
+\definecolor{fillColor}{RGB}{255,0,255}
+
+\path[fill=fillColor] (359.72,217.25) circle (  1.87);
+
+\path[fill=fillColor] (359.72,211.61) --
+	(362.24,207.26) --
+	(357.21,207.26) --
+	cycle;
+
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (346.46,233.81) --
+	(346.46,219.02);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (346.46,225.57) {$2\times $};
+\definecolor{fillColor}{RGB}{68,68,68}
+
+\path[fill=fillColor] (346.46,233.81) circle (  1.87);
+
+\path[fill=fillColor] (346.46,221.92) --
+	(348.97,217.56) --
+	(343.94,217.56) --
+	cycle;
+\definecolor{fillColor}{RGB}{0,0,0}
+
+\path[fill=fillColor] (465.27,227.83) circle (  2.15);
+
+\path[fill=fillColor] (465.27,219.71) --
+	(468.17,214.70) --
+	(462.38,214.70) --
+	cycle;
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (473.87,224.54) {adapt (\textit{real})};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (473.87,213.09) {adapt (\textit{cat})};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 49.80) -- (338.88,239.28);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 49.80) -- (338.88,235.31);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 87.70) -- (333.90, 87.70);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,125.59) -- (333.90,125.59);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,163.49) -- (333.90,163.49);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,201.38) -- (333.90,201.38);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,239.28) -- (333.90,239.28);
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92, 46.94) {0};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92, 84.84) {200};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,122.73) {400};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,160.63) {600};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,198.53) {800};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,236.42) {1000};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 84.85) -- (333.90, 84.85);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 99.95) -- (333.90, 99.95);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,135.01) -- (333.90,135.01);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,150.10) -- (333.90,150.10);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,185.16) -- (333.90,185.16);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,200.25) -- (333.90,200.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,235.31) -- (333.90,235.31);
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92, 46.94) {1};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92, 82.00) {5};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92, 97.09) {10};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,132.15) {50};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,147.24) {100};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,182.30) {500};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,197.40) {1000};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,232.45) {5000};
 \end{scope}

### 2020-08-26 benchmarking/benchmarkingVM/ESS_round3.tex
results update

--- 2020-08-10 benchmarking/benchmarkingVM/ESS_round3.tex
@@
-% Created by tikzDevice version 0.12.3 on 2020-08-10 15:55:24
+% Created by tikzDevice version 0.12.3.1 on 2020-08-25 15:33:46
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00, 76.35) --
-	(212.73,289.08);
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (  0.00, 71.00) --
+	(218.08,289.08);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.35,289.08) --
-	(271.35,195.00) --
-	( 76.35,  0.00);
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (268.39,289.08) --
+	(268.39,197.39) --
+	( 71.00,  0.00);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (  0.00, 50.90) --
-	(238.18,289.08);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00, 47.34) --
+	(241.74,289.08);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (271.35,289.08) --
-	(271.35,220.45) --
-	( 50.90,  0.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (268.39,289.08) --
+	(268.39,221.06) --
+	( 47.34,  0.00);
 
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (  0.00, 25.45) --
-	(263.63,289.08);
+\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round] (  0.00, 23.67) --
+	(265.41,289.08);
 
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (271.35,289.08) --
-	(271.35,245.90) --
-	( 25.45,  0.00);
+\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round] (268.39,289.08) --
+	(268.39,244.72) --
+	( 23.67,  0.00);
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (145.42, 64.13) {$\frac{1}{64} \times$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (140.08, 64.13) {$\frac{1}{64} \times$};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,150.12) {$64\times$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,144.78) {$64\times$};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (119.97, 64.13) {$\frac{1}{16} \times$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (116.41, 64.13) {$\frac{1}{16} \times$};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,124.67) {$16\times$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,121.11) {$16\times$};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 92.53, 64.13) {$\frac{1}{4} \times$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 90.75, 64.13) {$\frac{1}{4} \times$};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 62.56, 99.22) {$4\times$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 62.56, 97.44) {$4\times$};
 
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] ( 60.00, 60.00) -- (229.08,229.08);
-\definecolor{drawColor}{RGB}{255,0,109}
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 60.00, 60.00) -- (229.08,229.08);
+\definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.97,173.04) --
-	(174.56,173.04);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (200.17,196.99) --
+	(201.72,196.99);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (170.02,163.26) --
-	(170.02,179.39);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (200.96,196.43) --
+	(200.96,197.53);
+\definecolor{drawColor}{RGB}{151,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (170.02,169.15) {$p$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (200.96,193.10) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.16,172.12) --
-	(172.25,172.12);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (205.11,198.75) --
+	(207.67,198.75);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (170.32,170.07) --
-	(170.32,173.96);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (206.44,197.10) --
+	(206.44,200.25);
+\definecolor{drawColor}{RGB}{151,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (170.32,167.26) {$L$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (206.44,193.89) {$L$};
+\definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.73,184.48) --
-	(183.91,184.48);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (205.83,203.06) --
+	(206.19,203.06);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.85,183.02) --
-	(182.85,185.84);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (206.01,202.94) --
+	(206.01,203.18);
+\definecolor{drawColor}{RGB}{151,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (182.85,179.62) {$r$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (206.01,198.20) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (135.83,152.06) --
-	(151.70,152.06);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.99,182.32) --
+	(180.78,182.32);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.43,146.58) --
-	(145.43,156.28);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.91,181.55) --
+	(179.91,183.06);
+\definecolor{drawColor}{RGB}{151,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (145.43,147.20) {$h$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (179.91,177.46) {$h$};
+\definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (167.34,176.95) --
-	(176.22,176.95);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.73,181.94) --
+	(183.35,181.94);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.31,171.72) --
-	(172.31,181.01);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.20,181.15) --
+	(181.20,182.69);
+\definecolor{drawColor}{RGB}{151,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (172.31,173.45) {$\sigma$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (181.20,178.44) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.52,189.61) --
-	(189.61,189.61);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (212.29,207.61) --
+	(213.84,207.61);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.07,189.39) --
-	(189.07,189.83);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (213.08,206.84) --
+	(213.08,208.35);
+\definecolor{drawColor}{RGB}{151,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (189.07,186.11) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.89,177.49) --
-	(176.50,177.49);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.34,177.31) --
-	(174.34,177.66);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (174.34,173.60) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.00,179.60) --
-	(179.72,179.60);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.96,177.03) --
-	(177.96,181.87);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (177.96,174.74) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.92,182.73) --
-	(183.11,182.73);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (183.02,182.56) --
-	(183.02,182.90);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (183.02,177.87) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (137.08,144.73) --
-	(143.52,144.73);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.58,137.44) --
-	(140.58,149.93);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (140.58,139.87) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (156.53,157.68) --
-	(164.32,157.68);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.84,139.80) --
-	(160.84,166.56);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (160.84,154.18) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.53,191.09) --
-	(191.56,191.09);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.05,190.40) --
-	(191.05,191.75);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (191.05,187.59) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (178.25,170.79) --
-	(183.76,170.79);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.21,169.12) --
-	(181.21,172.32);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (181.21,166.90) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.52,175.16) --
-	(188.36,175.16);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.10,159.21) --
-	(182.10,183.57);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (182.10,170.30) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.87,190.74) --
-	(190.95,190.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.41,189.74) --
-	(190.41,191.69);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (190.41,185.88) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (147.08,153.71) --
-	(157.42,153.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (152.97,149.99) --
-	(152.97,156.80);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (152.97,148.85) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.95,170.40) --
-	(184.11,170.40);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.10,167.27) --
-	(180.10,173.07);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (180.10,166.90) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (201.12,201.71) --
-	(203.34,201.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (202.27,200.95) --
-	(202.27,202.44);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (202.27,198.21) {$\kappa$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (213.08,204.11) {$\kappa$};
 \end{scope}

### 2020-08-26 benchmarking/render.R

@@ -7,7 +7,7 @@ library(rjson)
 
 
 
-PER_CHAIN = TRUE
+PER_CHAIN = FALSE
 
 #settings = c("cat", "real", "quant", "bactrian95", "bactrian98")
 settings = c("cat",  "real_06", "quant_06", "real", "quant", "bactrian95", "bactrian98", "NER", "AVMN")
@@ -100,7 +100,8 @@ getDateTime = function(str){
 
 ESS.df = data.frame(batch = numeric(0), param = character(0), dataset = character(0), partition = numeric(0), setting = character(0), nstates = numeric(0),
 		ESS = numeric(0), hr = numeric(0), ESS.hr = numeric(0), Leff = numeric(0), L = numeric(0), N = numeric(0), mean.speed = numeric(0), 
-		CD_weight = numeric(0), RW_weight = numeric(0), SPP_weight = numeric(0), NER_weight = numeric(0), NER_acc = numeric(0), NE_acc = numeric(0))
+		CD_weight = numeric(0), RW_weight = numeric(0), SPP_weight = numeric(0), NER_weight = numeric(0), NER_acc = numeric(0), NE_acc = numeric(0),
+		correctBactrian = logical(0))
 
 
 
@@ -251,17 +252,21 @@ for (f in batchfolders){
 					NER_weight = -1
 					NER_acc = -1
 					NE_acc = -1
+					correctBactrian = TRUE
 					
 					state.in = paste0("benchmark_", s, ".xml.0state")
 					if (file.exists(state.in)) {
 						state.file = readLines(state.in)
-						if (length(grep("adaptive", s)) == 1){
-
-							if (length(grep("<!--", state.file)) == 1){
-
-								operator.lines = paste(state.file[(grep("<!--", state.file)+1):(grep("-->", state.file)-1)], collapse = " ")
-								json = fromJSON(operator.lines)
-								ops = json$operators
+						
+						
+						if (length(grep("<!--", state.file)) == 1){
+						
+							operator.lines = paste(state.file[(grep("<!--", state.file)+1):(grep("-->", state.file)-1)], collapse = " ")
+							json = fromJSON(operator.lines)
[…]

### 2020-08-26 clockSD.R

@@ -26,6 +26,8 @@ par(cex.main = 1.4)
 
 
 
+Scols = c("#c91f37", "#36e0c8")
+
 sigma = 0.4
 mu = -0.5*sigma^2
 sigma2 = 0.8
@@ -37,10 +39,10 @@ q2 = plnorm(r, mu2, sigma2)
 
 
 # $\\vec{\\mathcal{R}}$
-plot(r, q1, type = "l", xlab = "Rate", ylab = "Quantile", main = "$\\sigma$ scale operators", xaxs = "i", yaxs = "i", axes = F, lwd=2, xlim = c(0, 2), ylim = c(0,1))
-points(r, q2, type = "l", col = "red", lwd=2)
+plot(r, q1, type = "l", xlab = "Rate", ylab = "Quantile", main = "$\\sigma$ scale operators", xaxs = "i", yaxs = "i", axes = F, lwd=3, xlim = c(0, 2), ylim = c(0,1), col = Scols[1])
+points(r, q2, type = "l", col = Scols[2], lwd=3)
 
-legend("topleft", c(paste0("$\\sigma=", sigma, "$"), paste0("$\\sigma^\\prime=", sigma2, "$")), col = c("black", "red"), lwd = 2, bty = "n")
+legend("topleft", c(paste0("$\\sigma=", sigma, "$"), paste0("$\\sigma^\\prime=", sigma2, "$")), col = Scols, lwd = 3, bty = "n")
 
 
 # Scale
@@ -49,9 +51,9 @@ s_q0 = plnorm(s_r0, mu, sigma)
 s_q1 = plnorm(s_r0, mu2, sigma2)
 lines(c(s_r0, s_r0), c(0, max(s_q0, s_q1)), lwd = 2, col = "#696969", lty = "1515")
 
-lines(c(0, s_r0), c(s_q0, s_q0), lty = "1515", col = "black", lwd = 2)
-lines(c(0, s_r0), c(s_q1, s_q1), lty = "1515", col = "red", lwd = 2)
-points(c(s_r0, s_r0), c(s_q0, s_q1), pch = 16, col = c("black", "red"))
+lines(c(0, s_r0), c(s_q0, s_q0), lty = "1515", col = Scols[1], lwd = 2)
+lines(c(0, s_r0), c(s_q1, s_q1), lty = "1515", col = Scols[2], lwd = 2)
[…]

### 2020-08-28 benchmarking/benchmarkingVM/ESS_round1_catquant.tex
results update

--- 2020-08-10 benchmarking/benchmarkingVM/ESS_round1_catquant.tex
@@
-% Created by tikzDevice version 0.12.3 on 2020-08-10 13:51:28
+% Created by tikzDevice version 0.12.3.1 on 2020-08-28 13:29:15
 % !TEX encoding = UTF-8 Unicode
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,301.03) {ESS/hr [nocons (\textit{quant})]};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,433.62) {ESS/hr [cons (\textit{quant})]};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,301.03) {ESS/$10^6$ states [nocons (\textit{quant})]};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,433.62) {ESS/$10^6$ states [cons (\textit{quant})]};
 \end{scope}
@@
 \path[clip] ( 49.80,338.88) rectangle (239.28,528.36);
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (  0.00,403.16) --
+	(175.00,578.16);
+
+\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (302.44,578.16) --
+	(302.44,477.44) --
+	(  0.00,175.00);
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (  0.00,365.13) --
+	(213.03,578.16);
+
+\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (302.44,578.16) --
+	(302.44,515.47) --
+	(  0.00,213.03);
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (  0.00,327.11) --
+	(251.05,578.16);
+
+\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (302.44,578.16) --
+	(302.44,553.49) --
+	(  0.00,251.05);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,374.64) --
-	(203.52,578.16);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (286.65,578.16) --
-	(286.65,490.17) --
-	(  0.00,203.52);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (  0.00,346.12) --
-	(232.04,578.16);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (286.65,578.16) --
-	(286.65,518.69) --
-	(  0.00,232.04);
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (  0.00,317.60) --
-	(260.56,578.16);
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (286.65,578.16) --
-	(286.65,547.21) --
-	(  0.00,260.56);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (142.89,342.31) {$\frac{1}{64} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,435.87) {$64\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (114.37,342.31) {$\frac{1}{16} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,407.35) {$16\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 84.20,342.31) {$\frac{1}{4} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92,378.83) {$4\times$};
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,528.36);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 94.65,416.78) --
-	(103.65,416.78);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.64,409.37) --
-	( 99.64,422.22);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 99.64,413.56) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.25,476.46) --
-	(190.95,476.46);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.73,475.74) --
-	(188.73,477.16);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.73,472.43) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.21,474.21) --
-	(104.27,474.21);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (102.34,473.61) --
-	(102.34,474.79);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (102.34,470.18) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.11,416.10) --
-	(103.73,416.10);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.87,410.35) --
-	( 99.87,420.59);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 99.87,412.07) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.40,387.89) --
-	(115.90,387.89);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (106.65,384.62) --
-	(106.65,390.72);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (106.65,384.99) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.54,483.66) --
-	(195.01,483.66);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.29,483.25) --
-	(194.29,484.06);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.29,480.76) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.24,453.03) --
-	(151.45,453.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.58,451.65) --
-	(148.58,454.32);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (148.58,449.80) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.12,479.26) --
-	(197.83,479.26);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.99,477.50) --
-	(196.99,480.89);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.99,475.23) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.36,483.73) --
-	(188.58,483.73);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.98,483.50) --
-	(187.98,483.96);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.98,479.70) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.83,449.81) --
-	(142.53,449.81);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.76,448.18) --
-	(140.76,451.31);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (140.76,445.77) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.30,448.54) --
-	(152.66,448.54);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (149.31,447.26) --
-	(149.31,449.74);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (149.31,445.63) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.59,488.02) --
-	(199.40,488.02);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (199.00,487.58) --
-	(199.00,488.46);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.00,485.12) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.84,422.09) --
-	(126.52,422.09);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (122.64,409.09) --
-	(122.64,429.99);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (122.64,418.86) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.62,458.97) --
-	(195.24,458.97);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.51,454.93) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.66,477.15) --
-	(163.23,477.15);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.95,476.14) --
-	(162.95,478.11);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (162.95,473.11) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.91,421.56) --
-	(120.70,421.56);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.17,406.76) --
-	(117.17,430.08);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (117.17,417.53) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (124.20,409.98) --
-	(134.18,409.98);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.79,405.95) --
-	(129.79,413.35);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (129.79,407.07) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.21,485.10) --
-	(197.03,485.10);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.62,484.28) --
-	(196.62,485.89);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.62,482.19) {$\kappa$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.77,432.05) --
-	(140.26,432.05);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (135.68,429.18) --
-	(135.68,434.57);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (135.68,428.82) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.99,483.34) --
-	(200.70,483.34);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (199.86,480.63) --
-	(199.86,485.72);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.86,479.30) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.36,482.25) --
-	(177.58,482.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.47,482.07) --
-	(177.47,482.44);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.47,478.22) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (133.12,451.72) --
-	(147.88,451.72);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (141.79,449.82) --
-	(141.79,453.46);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (141.79,447.69) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (136.74,437.84) --
-	(147.60,437.84);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (142.88,434.82) --
-	(142.88,440.47);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (142.88,434.94) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.27,487.58) --
-	(198.98,487.58);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.14,487.05) --
-	(198.14,488.10);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.14,484.68) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.42,460.68) --
-	(181.15,460.68);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.37,456.94) --
-	(179.37,463.84);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.37,457.45) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.94,486.46) --
-	(184.37,486.46);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.33,482.75) --
-	(176.33,489.60);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.33,482.42) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.15,482.18) --
-	(197.23,482.18);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.69,481.57) --
-	(196.69,482.78);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.69,478.15) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.45,441.52) --
-	(161.00,441.52);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (157.57,436.94) --
-	(157.57,445.26);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (157.57,437.48) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.01,463.73) --
-	(184.30,463.73);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.82,459.32) --
-	(181.82,467.36);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.82,460.82) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.90,498.16) --
-	(211.56,498.16);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.27,495.77) --
-	(210.27,500.30);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.27,495.25) {$\kappa$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.64,472.51) --
-	(197.79,472.51);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.95,470.68) --
-	(194.95,474.19);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.95,469.28) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.60,491.62) --
-	(178.99,491.62);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.91,490.07) --
-	(176.91,493.06);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.91,487.58) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.25,482.68) --
-	(197.61,482.68);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.43,482.27) --
-	(197.43,483.09);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.43,478.65) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.17,459.25) --
-	(178.40,459.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.85,457.81) --
-	(176.85,460.59);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.85,455.21) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.79,467.29) --
-	(192.74,467.29);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.37,464.24) --
-	(185.37,469.95);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.37,464.39) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.72,501.36) --
-	(212.84,501.36);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.78,500.78) --
-	(212.78,501.94);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.78,498.46) {$\kappa$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (171.41,342.31) {$\frac{1}{64} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,464.39) {$64\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (133.38,342.31) {$\frac{1}{16} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,426.36) {$16\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 93.70,342.31) {$\frac{1}{4} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92,388.34) {$4\times$};
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,528.36);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 70.80,423.36) --
+	( 93.23,423.36);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 84.25,418.92) --
+	( 84.25,427.19);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 84.25,420.14) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (148.42,463.51) --
+	(187.31,463.51);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.24,460.11) --
+	(174.24,466.53);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.24,459.48) {$L$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 73.08,470.98) --
+	( 83.11,470.98);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 78.55,469.19) --
+	( 78.55,472.65);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 78.55,466.94) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 64.94,418.41) --
+	(105.90,418.41);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 92.45,409.17) --
+	( 92.45,425.31);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 92.45,414.38) {$h$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (  0.00,383.37) --
+	( 89.39,383.37);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 70.64,364.91) --
+	( 70.64,394.30);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 70.64,380.46) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.11,478.20) --
+	(192.04,478.20);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.62,477.22) --
+	(190.62,479.15);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.62,475.30) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.31,460.60) --
+	(178.05,460.60);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.71,458.59) --
+	(176.71,462.48);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.71,457.38) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.70,475.32) --
+	(192.51,475.32);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.14,473.33) --
+	(191.14,477.17);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.14,471.28) {$L$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.74,481.34) --
+	(184.36,481.34);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.05,481.07) --
+	(184.05,481.61);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.05,477.31) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (162.07,451.67) --
+	(165.83,451.67);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.01,449.52) --
+	(164.01,453.66);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (164.01,447.64) {$h$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.90,457.02) --
+	(176.90,457.02);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.44,455.90) --
+	(175.44,458.10);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (175.44,454.12) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.63,481.06) --
+	(191.86,481.06);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.26,480.49) --
+	(191.26,481.62);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.26,478.16) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (111.76,418.47) --
+	(118.07,418.47);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (115.09,416.16) --
+	(115.09,420.60);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (115.09,415.24) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.82,478.07) --
+	(195.49,478.07);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.67,476.87) --
+	(194.67,479.21);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.67,474.03) {$L$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.00,483.62) --
+	(190.59,483.62);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.30,483.50) --
+	(190.30,483.75);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.30,479.59) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 97.72,398.46) --
+	(103.70,398.46);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (100.88,395.62) --
+	(100.88,401.02);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (100.88,394.42) {$h$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (139.09,427.60) --
+	(144.44,427.60);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (141.90,423.74) --
+	(141.90,430.98);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (141.90,424.69) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.06,483.35) --
+	(195.09,483.35);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.58,483.08) --
+	(194.58,483.61);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.58,480.44) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (129.85,441.25) --
+	(135.49,441.25);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (132.82,438.28) --
+	(132.82,443.93);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (132.82,438.02) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.60,478.27) --
+	(196.71,478.27);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.68,477.02) --
+	(195.68,479.46);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.68,474.23) {$L$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.20,480.37) --
+	(183.91,480.37);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.06,479.98) --
+	(183.06,480.76);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.06,476.34) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (123.31,439.83) --
+	(129.99,439.83);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (126.85,438.03) --
+	(126.85,441.53);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (126.85,435.80) {$h$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (133.31,436.72) --
+	(141.06,436.72);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (137.46,434.86) --
+	(137.46,438.47);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (137.46,433.82) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.13,484.10) --
+	(196.02,484.10);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.09,483.74) --
+	(195.09,484.46);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.09,481.20) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 99.42,409.91) --
+	(113.41,409.91);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (107.30,400.41) --
+	(107.30,416.95);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (107.30,406.68) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.90,469.29) --
+	(192.29,469.29);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.73,467.51) --
+	(189.73,470.97);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (189.73,465.26) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.49,472.05) --
+	(150.55,472.05);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.03,471.80) --
+	(150.03,472.30);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (150.03,468.02) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 89.71,411.55) --
+	(110.93,411.55);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (102.32,410.26) --
+	(102.32,412.78);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (102.32,407.51) {$h$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (106.50,394.39) --
+	(115.04,394.39);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (111.10,388.67) --
+	(111.10,399.12);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (111.10,391.49) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.74,478.31) --
+	(191.06,478.31);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.41,477.22) --
+	(190.41,479.36);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.41,475.41) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.85,465.05) --
+	(185.79,465.05);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.84,463.70) --
+	(184.84,466.35);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.84,461.83) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.95,472.04) --
+	(193.32,472.04);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.64,470.64) --
+	(192.64,473.37);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.64,468.00) {$L$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (205.55,484.63) --
+	(205.79,484.63);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (205.67,484.50) --
+	(205.67,484.77);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.67,480.60) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.69,439.74) --
+	(153.31,439.74);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.56,436.87) --
+	(151.56,442.34);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (151.56,435.71) {$h$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.03,453.85) --
+	(173.21,453.85);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.20,451.51) --
+	(171.20,456.00);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.20,450.94) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.05,483.32) --
+	(194.70,483.32);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.38,482.91) --
+	(194.38,483.72);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.38,480.42) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (125.84,426.58) --
+	(133.48,426.58);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (129.93,424.06) --
+	(129.93,428.89);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (129.93,423.36) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.71,480.06) --
+	(201.09,480.06);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.93,479.25) --
+	(199.93,480.85);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.93,476.03) {$L$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.10,481.98) --
+	(174.44,481.98);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.30,481.32) --
+	(173.30,482.63);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.30,477.95) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (130.42,446.65) --
+	(136.31,446.65);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (133.52,443.11) --
+	(133.52,449.78);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (133.52,442.62) {$h$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (136.55,432.76) --
+	(142.96,432.76);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (139.94,430.69) --
+	(139.94,434.68);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (139.94,429.86) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.00,487.23) --
+	(198.91,487.23);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (197.49,486.45) --
+	(197.49,487.99);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.49,484.33) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (155.64,441.44) --
+	(160.72,441.44);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (158.30,439.73) --
+	(158.30,443.05);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.30,438.21) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (166.43,456.22) --
+	(176.68,456.22);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.03,455.20) --
+	(172.03,457.21);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.03,452.19) {$L$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (177.52,461.94) --
+	(178.35,461.94);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (177.93,461.63) --
+	(177.93,462.26);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.93,457.91) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (136.50,427.60) --
+	(144.46,427.60);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (140.77,423.63) --
+	(140.77,431.08);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (140.77,423.57) {$h$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.18,441.48) --
+	(163.87,441.48);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (162.56,439.63) --
+	(162.56,443.22);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (162.56,438.58) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.23,480.99) --
+	(193.16,480.99);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.70,480.18) --
+	(192.70,481.77);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.70,478.08) {$\kappa$};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 97.17,338.88) -- ( 97.17,333.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (144.54,338.88) -- (144.54,333.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.91,338.88) -- (191.91,333.90);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 93.95,338.88) -- ( 93.95,333.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.96,338.88) -- (112.96,333.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (157.11,338.88) -- (157.11,333.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.12,338.88) -- (176.12,333.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.27,338.88) -- (220.27,333.90);
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 97.17,320.95) {10};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (144.54,320.95) {100};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (191.91,320.95) {1000};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (239.28,320.95) {10000};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 93.95,320.95) {5};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (112.96,320.95) {10};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (157.11,320.95) {50};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (176.12,320.95) {100};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (220.27,320.95) {500};
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,386.25) -- ( 44.82,386.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,433.62) -- ( 44.82,433.62);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,480.99) -- ( 44.82,480.99);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,383.03) -- ( 44.82,383.03);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,402.04) -- ( 44.82,402.04);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,446.19) -- ( 44.82,446.19);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,465.20) -- ( 44.82,465.20);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,509.35) -- ( 44.82,509.35);
 
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,383.39) {10};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,430.76) {100};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,478.13) {1000};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,525.50) {10000};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,380.17) {5};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,399.18) {10};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,443.33) {50};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,462.34) {100};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,506.49) {500};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,525.50) {1000};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,301.03) {ESS/hr [nocons (\textit{quant})]};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (307.01,433.62) {ESS/hr [adapt (\textit{quant})]};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,301.03) {ESS/$10^6$ states [nocons (\textit{quant})]};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (307.01,433.62) {ESS/$10^6$ states [adapt (\textit{quant})]};
 \end{scope}
@@
 \path[clip] (338.88,338.88) rectangle (528.36,528.36);
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] ( 86.24,200.32) --
+	(464.08,578.16);
+
+\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (578.16,464.08) --
+	(114.08,  0.00);
+
+\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] ( 86.24,  0.00) --
+	( 86.24,200.32);
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] ( 86.24,162.29) --
+	(502.11,578.16);
+
+\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (578.16,502.11) --
+	( 86.24, 10.19) --
+	( 86.24,162.29);
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] ( 86.24,124.27) --
+	(540.13,578.16);
+
+\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (578.16,540.13) --
+	( 86.24, 48.21) --
+	( 86.24,124.27);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (149.40,234.96) --
-	(492.60,578.16);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (575.73,578.16) --
-	(575.73,490.17) --
-	(149.40, 63.84) --
-	(149.40,234.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (149.40,206.44) --
-	(521.12,578.16);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (575.73,578.16) --
-	(575.73,518.69) --
-	(149.40, 92.36) --
-	(149.40,206.44);
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (149.40,177.92) --
-	(549.64,578.16);
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (575.73,578.16) --
-	(575.73,547.21) --
-	(149.40,120.88) --
-	(149.40,177.92);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (431.97,342.31) {$\frac{1}{64} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,435.87) {$64\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (403.45,342.31) {$\frac{1}{16} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,407.35) {$16\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (373.28,342.31) {$\frac{1}{4} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.00,378.83) {$4\times$};
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (338.88,338.88) -- (528.36,528.36);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (383.73,398.02) --
-	(392.73,398.02);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (388.72,382.13) --
-	(388.72,406.87);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (388.72,394.79) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (475.33,475.91) --
-	(480.03,475.91);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.81,475.07) --
-	(477.81,476.72);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (477.81,471.88) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.29,472.93) --
-	(393.35,472.93);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (391.42,468.95) --
-	(391.42,476.26);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (391.42,468.89) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (384.19,397.74) --
-	(392.81,397.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (388.95,377.39) --
-	(388.95,407.77);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (388.95,393.71) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (378.48,366.19) --
-	(404.98,366.19);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (395.73,357.18) --
-	(395.73,372.44);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (395.73,363.29) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.62,483.32) --
-	(484.09,483.32);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.37,483.08) --
-	(483.37,483.56);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.37,480.42) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (434.32,451.80) --
-	(440.53,451.80);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (437.66,446.77) --
-	(437.66,455.84);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (437.66,448.57) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.20,479.84) --
-	(486.91,479.84);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.07,478.07) --
-	(486.07,481.48);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (486.07,475.81) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.44,483.86) --
-	(477.66,483.86);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.06,481.92) --
-	(477.06,485.64);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (477.06,479.83) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.91,449.16) --
-	(431.61,449.16);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (429.84,442.38) --
-	(429.84,454.24);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (429.84,445.12) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (434.38,448.12) --
-	(441.74,448.12);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.39,445.55) --
-	(438.39,450.42);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (438.39,445.22) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (487.67,488.03) --
-	(488.48,488.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (488.08,487.64) --
-	(488.08,488.41);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (488.08,485.12) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (406.92,424.00) --
-	(415.60,424.00);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (411.72,420.41) --
-	(411.72,427.05);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (411.72,420.77) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (480.70,478.83) --
-	(484.32,478.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.59,474.57) --
-	(482.59,482.36);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (482.59,474.80) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (451.74,476.83) --
-	(452.31,476.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (452.03,476.28) --
-	(452.03,477.36);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (452.03,472.79) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (401.99,423.32) --
-	(409.78,423.32);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (406.25,420.99) --
-	(406.25,425.41);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (406.25,419.28) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (413.28,406.71) --
-	(423.26,406.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.87,404.60) --
-	(418.87,408.64);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (418.87,403.81) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.29,485.22) --
-	(486.11,485.22);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.70,485.09) --
-	(485.70,485.35);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (485.70,482.32) {$\kappa$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.85,435.95) --
-	(429.34,435.95);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (424.76,433.40) --
-	(424.76,438.22);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (424.76,432.72) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (488.07,482.85) --
-	(489.78,482.85);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (488.94,480.61) --
-	(488.94,484.87);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (488.94,478.82) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (466.44,482.85) --
-	(466.66,482.85);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (466.55,482.61) --
-	(466.55,483.09);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (466.55,478.82) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (422.20,450.41) --
-	(436.96,450.41);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (430.87,447.63) --
-	(430.87,452.86);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (430.87,446.38) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (425.82,440.09) --
-	(436.68,440.09);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (431.96,437.76) --
-	(431.96,442.18);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (431.96,437.18) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.35,487.61) --
-	(488.06,487.61);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (487.22,485.91) --
-	(487.22,489.18);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (487.22,484.71) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (466.50,469.66) --
-	(470.23,469.66);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (468.45,467.06) --
-	(468.45,471.96);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.45,466.43) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (452.02,481.52) --
-	(473.45,481.52);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (465.41,478.07) --
-	(465.41,484.47);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (465.41,477.48) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.23,487.79) --
-	(486.31,487.79);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.77,487.17) --
-	(485.77,488.40);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (485.77,483.76) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (442.53,448.83) --
-	(450.08,448.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (446.65,445.54) --
-	(446.65,451.66);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (446.65,444.80) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (468.09,470.37) --
-	(473.38,470.37);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (470.90,468.48) --
-	(470.90,472.10);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (470.90,467.47) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (497.98,499.91) --
-	(500.64,499.91);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.35,499.32) --
-	(499.35,500.49);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (499.35,497.01) {$\kappa$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (480.72,484.41) --
-	(486.87,484.41);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (484.03,482.75) --
-	(484.03,485.95);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (484.03,481.19) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.68,490.90) --
-	(468.07,490.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (465.99,490.73) --
-	(465.99,491.06);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (465.99,486.86) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.33,489.03) --
-	(486.69,489.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.51,487.83) --
-	(486.51,490.17);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (486.51,485.00) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.25,467.22) --
-	(467.48,467.22);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (465.93,462.61) --
-	(465.93,470.98);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (465.93,463.19) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.87,475.23) --
-	(481.82,475.23);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.45,471.25) --
-	(474.45,478.57);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.45,472.33) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (501.80,501.33) --
-	(501.92,501.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (501.86,500.87) --
-	(501.86,501.77);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (501.86,498.42) {$\kappa$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (460.49,342.31) {$\frac{1}{64} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,464.39) {$64\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (422.46,342.31) {$\frac{1}{16} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,426.36) {$16\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (382.78,342.31) {$\frac{1}{4} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.00,388.34) {$4\times$};
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (338.88,338.88) -- (528.36,528.36);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (359.88,438.13) --
+	(382.31,438.13);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (373.33,433.43) --
+	(373.33,442.14);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (373.33,434.90) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (437.50,456.44) --
+	(476.39,456.44);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (463.32,453.88) --
+	(463.32,458.79);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (463.32,452.41) {$L$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (362.16,475.42) --
+	(372.19,475.42);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (367.63,474.25) --
+	(367.63,476.55);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (367.63,471.39) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (354.02,428.85) --
+	(394.98,428.85);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (381.53,416.26) --
+	(381.53,437.45);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (381.53,424.82) {$h$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (250.87,453.94) --
+	(378.47,453.94);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (359.72,449.40) --
+	(359.72,457.84);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (359.72,451.04) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (478.19,480.12) --
+	(481.12,480.12);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (479.70,479.30) --
+	(479.70,480.91);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (479.70,477.22) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (464.39,465.58) --
+	(467.13,465.58);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (465.79,463.97) --
+	(465.79,467.09);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (465.79,462.35) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (478.78,480.31) --
+	(481.59,480.31);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.22,479.55) --
+	(480.22,481.05);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (480.22,476.28) {$L$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (472.82,482.31) --
+	(473.44,482.31);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (473.13,482.08) --
+	(473.13,482.54);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (473.13,478.28) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (451.15,455.62) --
+	(454.91,455.62);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (453.09,454.14) --
+	(453.09,457.03);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (453.09,451.59) {$h$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (462.98,478.30) --
+	(465.98,478.30);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (464.52,477.07) --
+	(464.52,479.47);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (464.52,475.39) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (479.71,480.62) --
+	(480.94,480.62);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.34,480.18) --
+	(480.34,481.06);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (480.34,477.72) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (400.84,427.43) --
+	(407.15,427.43);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (404.17,424.99) --
+	(404.17,429.68);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (404.17,424.21) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (482.90,482.27) --
+	(484.57,482.27);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.75,481.56) --
+	(483.75,482.95);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.75,478.23) {$L$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (479.08,486.43) --
+	(479.67,486.43);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (479.38,486.21) --
+	(479.38,486.65);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (479.38,482.40) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (386.80,409.36) --
+	(392.78,409.36);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (389.96,407.67) --
+	(389.96,410.96);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (389.96,405.33) {$h$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (428.17,441.67) --
+	(433.52,441.67);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (430.98,439.92) --
+	(430.98,443.32);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (430.98,438.77) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.14,483.51) --
+	(484.17,483.51);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.66,483.13) --
+	(483.66,483.88);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.66,480.60) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (418.93,448.30) --
+	(424.57,448.30);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (421.90,445.38) --
+	(421.90,450.94);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (421.90,445.07) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.68,483.20) --
+	(485.79,483.20);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (484.76,482.06) --
+	(484.76,484.31);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (484.76,479.17) {$L$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (471.28,483.39) --
+	(472.99,483.39);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (472.14,482.50) --
+	(472.14,484.26);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (472.14,479.36) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (412.39,447.57) --
+	(419.07,447.57);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (415.93,444.38) --
+	(415.93,450.43);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (415.93,443.54) {$h$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (422.39,456.30) --
+	(430.14,456.30);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (426.54,453.54) --
+	(426.54,458.81);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (426.54,453.40) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.21,485.06) --
+	(485.10,485.06);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (484.17,483.93) --
+	(484.17,486.13);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (484.17,482.15) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (388.50,414.28) --
+	(402.49,414.28);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (396.38,410.38) --
+	(396.38,417.69);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (396.38,411.05) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (475.98,464.34) --
+	(481.37,464.34);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (478.81,461.59) --
+	(478.81,466.85);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (478.81,460.31) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (438.57,472.21) --
+	(439.63,472.21);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (439.11,471.57) --
+	(439.11,472.84);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (439.11,468.18) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (378.79,418.44) --
+	(400.01,418.44);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (391.40,413.15) --
+	(391.40,422.88);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (391.40,414.41) {$h$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (395.58,431.44) --
+	(404.12,431.44);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (400.18,417.90) --
+	(400.18,440.46);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (400.18,428.53) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (478.82,479.21) --
+	(480.14,479.21);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (479.49,478.51) --
+	(479.49,479.89);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (479.49,476.30) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (472.93,477.88) --
+	(474.87,477.88);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (473.92,476.37) --
+	(473.92,479.32);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (473.92,474.66) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.03,482.67) --
+	(482.40,482.67);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.72,481.72) --
+	(481.72,483.59);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (481.72,478.64) {$L$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (494.63,497.06) --
+	(494.87,497.06);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (494.75,496.96) --
+	(494.75,497.15);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (494.75,493.02) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (438.77,444.49) --
+	(442.39,444.49);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (440.64,442.00) --
+	(440.64,446.77);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (440.64,440.45) {$h$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (458.11,466.45) --
+	(462.29,466.45);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (460.28,465.18) --
+	(460.28,467.65);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (460.28,463.54) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.13,482.79) --
+	(483.78,482.79);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.46,482.51) --
+	(483.46,483.08);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.46,479.89) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (414.92,428.04) --
+	(422.56,428.04);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (419.01,424.63) --
+	(419.01,431.08);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (419.01,424.82) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (487.79,482.21) --
+	(490.17,482.21);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (489.01,481.06) --
+	(489.01,483.31);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (489.01,478.18) {$L$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (461.18,483.22) --
+	(463.52,483.22);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (462.38,482.71) --
+	(462.38,483.73);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (462.38,479.19) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (419.50,443.20) --
+	(425.39,443.20);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (422.60,439.70) --
+	(422.60,446.30);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (422.60,439.17) {$h$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (425.63,450.57) --
+	(432.04,450.57);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (429.02,448.28) --
+	(429.02,452.68);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (429.02,447.67) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (485.08,486.67) --
+	(487.99,486.67);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (486.57,485.68) --
+	(486.57,487.63);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (486.57,483.77) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (444.72,448.44) --
+	(449.80,448.44);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (447.38,445.70) --
+	(447.38,450.93);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (447.38,445.21) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (455.51,463.89) --
+	(465.76,463.89);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (461.11,462.95) --
+	(461.11,464.79);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (461.11,459.85) {$L$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (466.60,469.57) --
+	(467.43,469.57);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (467.01,469.18) --
+	(467.01,469.94);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (467.01,465.53) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (425.58,426.15) --
+	(433.54,426.15);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (429.85,423.97) --
+	(429.85,428.18);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (429.85,422.12) {$h$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (450.26,456.41) --
+	(452.95,456.41);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (451.64,454.54) --
+	(451.64,458.16);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (451.64,453.50) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.31,482.11) --
+	(482.24,482.11);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.78,481.47) --
+	(481.78,482.74);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (481.78,479.21) {$\kappa$};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (386.25,338.88) -- (386.25,333.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.62,338.88) -- (433.62,333.90);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (480.99,338.88) -- (480.99,333.90);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (383.03,338.88) -- (383.03,333.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (402.04,338.88) -- (402.04,333.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (446.19,338.88) -- (446.19,333.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (465.20,338.88) -- (465.20,333.90);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (509.35,338.88) -- (509.35,333.90);
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (386.25,320.95) {10};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (433.62,320.95) {100};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (480.99,320.95) {1000};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (528.36,320.95) {10000};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (383.03,320.95) {5};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (402.04,320.95) {10};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (446.19,320.95) {50};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (465.20,320.95) {100};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (509.35,320.95) {500};
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,386.25) -- (333.90,386.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,433.62) -- (333.90,433.62);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,480.99) -- (333.90,480.99);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,383.03) -- (333.90,383.03);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,402.04) -- (333.90,402.04);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,446.19) -- (333.90,446.19);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,465.20) -- (333.90,465.20);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,509.35) -- (333.90,509.35);
 
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,383.39) {10};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,430.76) {100};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,478.13) {1000};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,525.50) {10000};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,380.17) {5};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,399.18) {10};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,443.33) {50};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,462.34) {100};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,506.49) {500};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,525.50) {1000};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54, 11.95) {ESS/hr [cons (\textit{quant})]};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,144.54) {ESS/hr [adapt (\textit{quant})]};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54, 11.95) {ESS/$10^6$ states [cons (\textit{quant})]};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,144.54) {ESS/$10^6$ states [adapt (\textit{quant})]};
 \end{scope}
@@
 \path[clip] ( 49.80, 49.80) rectangle (239.28,239.28);
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (  0.00,114.08) --
+	(302.44,416.52) --
+	(302.44,188.36) --
+	(114.08,  0.00);
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (  0.00, 76.05) --
+	(302.44,378.49) --
+	(302.44,226.39) --
+	( 76.05,  0.00);
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (  0.00, 38.03) --
+	(302.44,340.47) --
+	(302.44,264.41) --
+	( 38.03,  0.00);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00, 85.56) --
-	(286.65,372.21) --
-	(286.65,201.09) --
-	( 85.56,  0.00);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (  0.00, 57.04) --
-	(286.65,343.69) --
-	(286.65,229.61) --
-	( 57.04,  0.00);
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (  0.00, 28.52) --
-	(286.65,315.17) --
-	(286.65,258.13) --
-	( 28.52,  0.00);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (142.89, 53.23) {$\frac{1}{64} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,146.79) {$64\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (114.37, 53.23) {$\frac{1}{16} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,118.27) {$16\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 84.20, 53.23) {$\frac{1}{4} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92, 89.75) {$4\times$};
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] ( 49.80, 49.80) -- (239.28,239.28);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.29,108.94) --
-	(133.14,108.94);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (127.70, 93.05) --
-	(127.70,117.79);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (127.70,105.71) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.66,186.83) --
-	(188.08,186.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.38,185.99) --
-	(187.38,187.64);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.38,182.80) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.53,183.85) --
-	(185.71,183.85);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.13,179.87) --
-	(185.13,187.18);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.13,179.81) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.27,108.66) --
-	(131.51,108.66);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (127.02, 88.31) --
-	(127.02,118.69);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (127.02,104.63) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.54, 77.11) --
-	(101.64, 77.11);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 98.81, 68.10) --
-	( 98.81, 83.36);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 98.81, 74.21) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.17,194.24) --
-	(194.98,194.24);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.58,194.00) --
-	(194.58,194.48);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.58,191.34) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.57,162.72) --
-	(165.24,162.72);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.95,157.69) --
-	(163.95,166.76);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (163.95,159.49) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.42,190.76) --
-	(191.81,190.76);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.18,188.99) --
-	(190.18,192.40);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.18,186.73) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.42,194.78) --
-	(194.88,194.78);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.65,192.84) --
-	(194.65,196.56);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.65,190.75) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.10,160.08) --
-	(162.23,160.08);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.73,153.30) --
-	(160.73,165.16);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (160.73,156.04) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.18,159.04) --
-	(160.66,159.04);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.46,156.47) --
-	(159.46,161.34);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (159.46,156.14) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.50,198.95) --
-	(199.38,198.95);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.94,198.56) --
-	(198.94,199.33);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.94,196.04) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.01,134.92) --
-	(140.91,134.92);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (133.01,131.33) --
-	(133.01,137.97);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (133.01,131.69) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.89,185.49) --
-	(169.89,193.28);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.89,185.72) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.06,187.75) --
-	(189.03,187.75);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.07,187.20) --
-	(188.07,188.28);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.07,183.71) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.68,134.24) --
-	(141.00,134.24);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (132.48,131.91) --
-	(132.48,136.33);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (132.48,130.20) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (116.87,117.63) --
-	(124.27,117.63);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.90,115.52) --
-	(120.90,119.56);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (120.90,114.73) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.20,196.14) --
-	(196.81,196.14);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.02,196.01) --
-	(196.02,196.27);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.02,193.24) {$\kappa$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.10,146.87) --
-	(145.49,146.87);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (142.97,144.32) --
-	(142.97,149.14);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (142.97,143.64) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.55,193.77) --
-	(196.64,193.77);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.26,191.53) --
-	(194.26,195.79);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.26,189.74) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.99,193.77) --
-	(193.36,193.77);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.17,193.53) --
-	(193.17,194.01);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.17,189.74) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.74,161.33) --
-	(164.38,161.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.64,158.55) --
-	(162.64,163.78);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (162.64,157.30) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.74,151.01) --
-	(151.39,151.01);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.76,148.68) --
-	(148.76,153.10);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (148.76,148.10) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.97,198.53) --
-	(199.02,198.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.50,196.83) --
-	(198.50,200.10);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.50,195.63) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (167.86,180.58) --
-	(174.76,180.58);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.60,177.98) --
-	(171.60,182.88);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.60,177.35) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.67,192.44) --
-	(200.52,192.44);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.38,188.99) --
-	(197.38,195.39);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.38,188.40) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.49,198.71) --
-	(193.70,198.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.10,198.09) --
-	(193.10,199.32);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.10,194.68) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (147.86,159.75) --
-	(156.18,159.75);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (152.44,156.46) --
-	(152.44,162.58);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (152.44,155.72) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (170.24,181.29) --
-	(178.28,181.29);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.65,179.40) --
-	(174.65,183.02);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.65,178.39) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.69,210.83) --
-	(211.22,210.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.08,210.24) --
-	(209.08,211.41);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.08,207.93) {$\kappa$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.60,195.33) --
-	(185.11,195.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (183.43,193.67) --
-	(183.43,196.87);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.43,192.11) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.99,201.82) --
-	(203.98,201.82);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (202.54,201.65) --
-	(202.54,201.98);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.54,197.78) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.19,199.95) --
-	(194.01,199.95);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.60,198.75) --
-	(193.60,201.09);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.60,195.92) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.73,178.14) --
-	(171.51,178.14);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (170.17,173.53) --
-	(170.17,181.90);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (170.17,174.11) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.16,186.15) --
-	(180.87,186.15);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (178.21,182.17) --
-	(178.21,189.49);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (178.21,183.25) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.70,212.25) --
-	(212.86,212.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.28,211.79) --
-	(212.28,212.69);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.28,209.34) {$\kappa$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (171.41, 53.23) {$\frac{1}{64} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,175.31) {$64\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (133.38, 53.23) {$\frac{1}{16} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,137.28) {$16\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 93.70, 53.23) {$\frac{1}{4} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92, 99.26) {$4\times$};
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 49.80, 49.80) -- (239.28,239.28);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (129.84,149.05) --
+	(138.11,149.05);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (134.28,144.35) --
+	(134.28,153.06);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (134.28,145.82) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.03,167.36) --
+	(177.45,167.36);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.43,164.80) --
+	(174.43,169.71);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.43,163.33) {$L$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.11,186.34) --
+	(183.57,186.34);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.90,185.17) --
+	(181.90,187.47);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.90,182.31) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (120.09,139.77) --
+	(136.23,139.77);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (129.33,127.18) --
+	(129.33,148.37);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (129.33,135.74) {$h$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 75.83,164.86) --
+	(105.22,164.86);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 94.29,160.32) --
+	( 94.29,168.76);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 94.29,161.96) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.14,191.04) --
+	(190.07,191.04);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.12,190.22) --
+	(189.12,191.83);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (189.12,188.14) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.51,176.50) --
+	(173.40,176.50);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.52,174.89) --
+	(171.52,178.01);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.52,173.27) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.25,191.23) --
+	(188.09,191.23);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.24,190.47) --
+	(186.24,191.97);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (186.24,187.20) {$L$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.99,193.23) --
+	(192.53,193.23);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.26,193.00) --
+	(192.26,193.46);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.26,189.20) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (160.44,166.54) --
+	(164.58,166.54);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (162.59,165.06) --
+	(162.59,167.95);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (162.59,162.51) {$h$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (166.82,189.22) --
+	(169.02,189.22);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (167.94,187.99) --
+	(167.94,190.39);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (167.94,186.31) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.41,191.54) --
+	(192.54,191.54);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.98,191.10) --
+	(191.98,191.98);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.98,188.64) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (127.08,138.35) --
+	(131.52,138.35);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (129.39,135.91) --
+	(129.39,140.60);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (129.39,135.13) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.79,193.19) --
+	(190.13,193.19);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.99,192.48) --
+	(188.99,193.87);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.99,189.15) {$L$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.42,197.35) --
+	(194.67,197.35);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.54,197.13) --
+	(194.54,197.57);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.54,193.32) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (106.54,120.28) --
+	(111.94,120.28);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (109.38,118.59) --
+	(109.38,121.88);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (109.38,116.25) {$h$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (134.66,152.59) --
+	(141.90,152.59);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (138.52,150.84) --
+	(138.52,154.24);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (138.52,149.69) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.00,194.43) --
+	(194.53,194.43);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.27,194.05) --
+	(194.27,194.80);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.27,191.52) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.20,159.22) --
+	(154.85,159.22);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.17,156.30) --
+	(152.17,161.86);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (152.17,155.99) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.94,194.12) --
+	(190.38,194.12);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.19,192.98) --
+	(189.19,195.23);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (189.19,190.09) {$L$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.90,194.31) --
+	(191.68,194.31);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.29,193.42) --
+	(191.29,195.18);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.29,190.28) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (148.95,158.49) --
+	(152.45,158.49);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.75,155.30) --
+	(150.75,161.35);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (150.75,154.46) {$h$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (145.78,167.22) --
+	(149.39,167.22);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (147.64,164.46) --
+	(147.64,169.73);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (147.64,164.32) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.66,195.98) --
+	(195.38,195.98);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.02,194.85) --
+	(195.02,197.05);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.02,193.07) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (111.33,125.20) --
+	(127.87,125.20);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (120.83,121.30) --
+	(120.83,128.61);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (120.83,121.97) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.43,175.26) --
+	(181.89,175.26);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.21,172.51) --
+	(180.21,177.77);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.21,171.23) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.72,183.13) --
+	(183.22,183.13);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.97,182.49) --
+	(182.97,183.76);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.97,179.10) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (121.18,129.36) --
+	(123.70,129.36);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (122.47,124.07) --
+	(122.47,133.80);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (122.47,125.33) {$h$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 99.59,142.36) --
+	(110.04,142.36);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (105.31,128.82) --
+	(105.31,151.38);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (105.31,139.45) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.14,190.13) --
+	(190.28,190.13);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.23,189.43) --
+	(189.23,190.81);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (189.23,187.22) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.62,188.80) --
+	(177.27,188.80);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.97,187.29) --
+	(175.97,190.24);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (175.97,185.58) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.56,193.59) --
+	(184.29,193.59);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.96,192.64) --
+	(182.96,194.51);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.96,189.56) {$L$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.42,207.98) --
+	(195.69,207.98);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.55,207.88) --
+	(195.55,208.07);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.55,203.94) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (147.79,155.41) --
+	(153.26,155.41);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.66,152.92) --
+	(150.66,157.69);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (150.66,151.37) {$h$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (162.43,177.37) --
+	(166.92,177.37);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.77,176.10) --
+	(164.77,178.57);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (164.77,174.46) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.83,193.71) --
+	(194.64,193.71);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.24,193.43) --
+	(194.24,194.00);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.24,190.81) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (134.98,138.96) --
+	(139.81,138.96);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (137.50,135.55) --
+	(137.50,142.00);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (137.50,135.74) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.17,193.13) --
+	(191.77,193.13);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.98,191.98) --
+	(190.98,194.23);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.98,189.10) {$L$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.24,194.14) --
+	(193.55,194.14);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.90,193.63) --
+	(192.90,194.65);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.90,190.11) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (154.03,154.12) --
+	(160.70,154.12);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (157.57,150.62) --
+	(157.57,157.22);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (157.57,150.09) {$h$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (141.61,161.49) --
+	(145.60,161.49);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (143.68,159.20) --
+	(143.68,163.60);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (143.68,158.59) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (197.37,197.59) --
+	(198.91,197.59);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.15,196.60) --
+	(198.15,198.55);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.15,194.69) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.65,159.36) --
+	(153.97,159.36);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.36,156.62) --
+	(152.36,161.85);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (152.36,156.13) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (166.12,174.81) --
+	(168.13,174.81);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (167.14,173.87) --
+	(167.14,175.71);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (167.14,170.77) {$L$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.55,180.49) --
+	(173.18,180.49);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.86,180.10) --
+	(172.86,180.86);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.86,176.45) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (134.55,137.07) --
+	(142.00,137.07);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (138.52,134.89) --
+	(138.52,139.10);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (138.52,133.04) {$h$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.55,167.33) --
+	(154.14,167.33);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.40,165.46) --
+	(152.40,169.08);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (152.40,164.42) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.10,193.03) --
+	(192.69,193.03);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.91,192.39) --
+	(191.91,193.66);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.91,190.13) {$\kappa$};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 97.17, 49.80) -- ( 97.17, 44.82);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (144.54, 49.80) -- (144.54, 44.82);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.91, 49.80) -- (191.91, 44.82);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 93.95, 49.80) -- ( 93.95, 44.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.96, 49.80) -- (112.96, 44.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (157.11, 49.80) -- (157.11, 44.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.12, 49.80) -- (176.12, 44.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.27, 49.80) -- (220.27, 44.82);
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 97.17, 31.87) {10};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (144.54, 31.87) {100};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (191.91, 31.87) {1000};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (239.28, 31.87) {10000};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 93.95, 31.87) {5};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (112.96, 31.87) {10};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (157.11, 31.87) {50};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (176.12, 31.87) {100};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (220.27, 31.87) {500};
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 97.17) -- ( 44.82, 97.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,144.54) -- ( 44.82,144.54);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,191.91) -- ( 44.82,191.91);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80, 93.95) -- ( 44.82, 93.95);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,112.96) -- ( 44.82,112.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,157.11) -- ( 44.82,157.11);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,176.12) -- ( 44.82,176.12);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,220.27) -- ( 44.82,220.27);
 
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84, 94.31) {10};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,141.68) {100};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,189.05) {1000};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,236.42) {10000};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84, 91.09) {5};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,110.10) {10};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,154.25) {50};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,173.26) {100};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,217.41) {500};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 39.84,236.42) {1000};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62, 11.95) {ESS/hr [\textit{cat}]};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (307.01,144.54) {ESS/hr [adapt (\textit{cat})]};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62, 11.95) {ESS/$10^6$ states [\textit{cat}]};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (307.01,144.54) {ESS/$10^6$ states [adapt (\textit{cat})]};
 \end{scope}
@@
 \path[clip] (338.88, 49.80) rectangle (528.36,239.28);
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (175.00,  0.00) --
+	(578.16,403.16);
+
+\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (578.16,175.00) --
+	(403.16,  0.00);
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (213.03,  0.00) --
+	(578.16,365.13);
+
+\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (578.16,213.03) --
+	(365.13,  0.00);
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (251.05,  0.00) --
+	(578.16,327.11);
+
+\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (578.16,251.05) --
+	(327.11,  0.00);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.52,  0.00) --
-	(575.73,372.21) --
-	(575.73,201.09) --
-	(374.64,  0.00);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (232.04,  0.00) --
-	(575.73,343.69) --
-	(575.73,229.61) --
-	(346.12,  0.00);
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (260.56,  0.00) --
-	(575.73,315.17) --
-	(575.73,258.13) --
-	(317.60,  0.00);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (431.97, 53.23) {$\frac{1}{64} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,146.79) {$64\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (403.45, 53.23) {$\frac{1}{16} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,118.27) {$16\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (373.28, 53.23) {$\frac{1}{4} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.00, 89.75) {$4\times$};
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (338.88, 49.80) -- (528.36,239.28);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (369.53,100.95) --
-	(401.69,100.95);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (391.34, 96.83) --
-	(391.34,104.39);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (391.34, 97.73) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (469.11,180.21) --
-	(478.54,180.21);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.36,157.25) --
-	(474.36,190.79);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.36,176.18) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (378.71, 99.41) --
-	(392.60, 99.41);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (386.80, 95.00) --
-	(386.80,103.04);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (386.80, 95.37) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (379.87,102.83) --
-	(403.10,102.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (394.60,100.19) --
-	(394.60,105.17);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (394.60, 98.80) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (373.83, 90.46) --
-	(386.33, 90.46);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (381.02, 83.73) --
-	(381.02, 95.52);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (381.02, 87.56) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.33,194.78) --
-	(484.25,194.78);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.79,194.57) --
-	(483.79,194.99);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.79,191.87) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (403.60,109.49) --
-	(412.89,109.49);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (408.76, 99.61) --
-	(408.76,116.13);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (408.76,106.26) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.33,191.83) --
-	(481.58,191.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.56,190.07) --
-	(479.56,193.44);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (479.56,187.79) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (448.80,164.69) --
-	(449.61,164.69);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (449.21,164.54) --
-	(449.21,164.84);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (449.21,160.65) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (402.13,107.26) --
-	(410.13,107.26);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (406.52,100.97) --
-	(406.52,112.07);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (406.52,103.23) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (394.71,110.51) --
-	(411.65,110.51);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (404.88,103.25) --
-	(404.88,115.87);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (404.88,107.61) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.25,196.27) --
-	(485.92,196.27);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.59,196.12) --
-	(485.59,196.43);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (485.59,193.37) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.30,177.43) --
-	(465.23,177.43);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (460.48,172.15) --
-	(460.48,181.63);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (460.48,174.20) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.33,174.98) --
-	(474.75,174.98);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.90,158.21) --
-	(461.90,184.09);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (461.90,170.94) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (480.68,197.38) --
-	(482.70,197.38);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (481.71,196.98) --
-	(481.71,197.78);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (481.71,193.35) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (436.28,158.71) --
-	(449.09,158.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.66,150.24) --
-	(443.66,164.70);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (443.66,154.68) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.65,180.86) --
-	(466.79,180.86);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (465.75,178.58) --
-	(465.75,182.90);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (465.75,177.95) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.10,210.49) --
-	(500.73,210.49);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.93,208.48) --
-	(499.93,212.33);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (499.93,207.59) {$\kappa$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (460.49, 53.23) {$\frac{1}{64} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,175.31) {$64\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (422.46, 53.23) {$\frac{1}{16} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,137.28) {$16\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (382.78, 53.23) {$\frac{1}{4} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.00, 99.26) {$4\times$};
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (338.88, 49.80) -- (528.36,239.28);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (334.61, 83.64) --
+	(372.72, 83.64);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (359.81, 65.57) --
+	(359.81, 94.44);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (359.81, 80.41) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (440.92,179.14) --
+	(467.98,179.14);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (457.66,176.43) --
+	(457.66,181.61);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (457.66,175.11) {$L$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (366.14, 82.04) --
+	(372.76, 82.04);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (369.65, 75.12) --
+	(369.65, 87.57);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (369.65, 78.01) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (359.02, 95.99) --
+	(386.82, 95.99);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (376.30, 72.91) --
+	(376.30,108.34);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (376.30, 91.95) {$h$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (281.67, 58.63) --
+	(366.93, 58.63);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (349.12, 33.73) --
+	(349.12, 71.46);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (349.12, 55.72) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (477.60,190.83) --
+	(479.43,190.83);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (478.53,190.10) --
+	(478.53,191.54);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (478.53,187.92) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (458.98,176.41) --
+	(461.56,176.41);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (460.30,175.58) --
+	(460.30,177.22);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (460.30,173.19) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (478.30,190.31) --
+	(480.49,190.31);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (479.42,188.37) --
+	(479.42,192.12);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (479.42,186.27) {$L$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (469.57,184.01) --
+	(469.93,184.01);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (469.75,183.74) --
+	(469.75,184.28);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (469.75,179.98) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (448.93,165.60) --
+	(451.61,165.60);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (450.30,163.78) --
+	(450.30,167.31);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (450.30,161.57) {$h$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (459.91,175.41) --
+	(463.16,175.41);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (461.58,173.43) --
+	(461.58,177.25);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (461.58,172.50) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.05,191.90) --
+	(480.87,191.90);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.47,191.32) --
+	(480.47,192.47);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (480.47,189.00) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (441.24,147.16) --
+	(444.46,147.16);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (442.90,143.30) --
+	(442.90,150.54);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (442.90,143.93) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.34,194.74) --
+	(483.37,194.74);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (482.37,193.44) --
+	(482.37,195.98);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (482.37,190.70) {$L$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (475.70,191.38) --
+	(476.47,191.38);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (476.09,190.94) --
+	(476.09,191.80);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (476.09,187.34) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (414.12,117.28) --
+	(419.19,117.28);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (416.77,113.09) --
+	(416.77,120.91);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (416.77,113.24) {$h$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (430.95,142.91) --
+	(436.78,142.91);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (434.02,139.37) --
+	(434.02,146.05);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (434.02,140.01) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (482.95,194.71) --
+	(483.77,194.71);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.36,194.43) --
+	(483.36,194.98);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.36,191.80) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (418.72,132.69) --
+	(423.45,132.69);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (421.19,129.75) --
+	(421.19,135.34);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (421.19,129.46) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (479.62,193.24) --
+	(482.28,193.24);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.98,191.98) --
+	(480.98,194.45);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (480.98,189.21) {$L$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (467.00,183.39) --
+	(467.83,183.39);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (467.42,182.80) --
+	(467.42,183.97);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (467.42,179.36) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (412.87,125.74) --
+	(417.56,125.74);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (415.31,122.57) --
+	(415.31,128.58);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (415.31,121.70) {$h$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (422.54,138.22) --
+	(425.51,138.22);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (424.06,134.00) --
+	(424.06,141.88);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (424.06,135.32) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.36,195.09) --
+	(484.08,195.09);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.72,194.56) --
+	(483.72,195.61);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.72,192.18) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (383.87,101.21) --
+	(388.61,101.21);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (386.34, 84.00) --
+	(386.34,111.71);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (386.34, 97.98) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (470.13,184.99) --
+	(480.49,184.99);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (475.80,179.70) --
+	(475.80,189.43);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (475.80,180.96) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (436.20,154.50) --
+	(438.24,154.50);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (437.24,153.50) --
+	(437.24,155.46);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (437.24,150.46) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (385.40, 93.05) --
+	(391.40, 93.05);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (388.56, 81.05) --
+	(388.56,101.36);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (388.56, 89.01) {$h$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (376.33, 98.28) --
+	(389.61, 98.28);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (383.76, 84.24) --
+	(383.76,107.51);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (383.76, 95.37) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.53,192.40) --
+	(482.50,192.40);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (482.02,191.03) --
+	(482.02,193.70);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (482.02,189.50) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (467.36,189.45) --
+	(471.39,189.45);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (469.45,187.84) --
+	(469.45,190.97);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (469.45,186.22) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (478.44,193.31) --
+	(480.96,193.31);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (479.73,191.90) --
+	(479.73,194.66);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (479.73,189.28) {$L$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (492.43,207.94) --
+	(492.86,207.94);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (492.65,207.74) --
+	(492.65,208.14);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (492.65,203.91) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (435.04,154.48) --
+	(441.46,154.48);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (438.44,152.85) --
+	(438.44,156.02);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (438.44,150.45) {$h$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (457.65,173.50) --
+	(461.23,173.50);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (459.50,171.08) --
+	(459.50,175.72);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (459.50,170.59) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (482.60,194.00) --
+	(483.66,194.00);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.14,193.44) --
+	(483.14,194.56);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.14,191.10) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (412.69,117.50) --
+	(418.50,117.50);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (415.75,111.56) --
+	(415.75,122.39);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (415.75,114.28) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.49,199.54) --
+	(486.60,199.54);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (485.09,198.30) --
+	(485.09,200.72);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (485.09,195.50) {$L$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (454.74,171.96) --
+	(456.90,171.96);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (455.84,171.07) --
+	(455.84,172.82);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (455.84,167.93) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (413.21,127.52) --
+	(419.93,127.52);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (416.78,122.36) --
+	(416.78,131.86);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (416.78,123.49) {$h$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (430.22,126.73) --
+	(433.18,126.73);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (431.74,119.73) --
+	(431.74,132.30);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (431.74,123.83) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (486.29,197.53) --
+	(487.57,197.53);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (486.94,196.03) --
+	(486.94,198.96);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (486.94,194.63) {$\kappa$};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (386.25, 49.80) -- (386.25, 44.82);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.62, 49.80) -- (433.62, 44.82);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (480.99, 49.80) -- (480.99, 44.82);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (383.03, 49.80) -- (383.03, 44.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (402.04, 49.80) -- (402.04, 44.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (446.19, 49.80) -- (446.19, 44.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (465.20, 49.80) -- (465.20, 44.82);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (509.35, 49.80) -- (509.35, 44.82);
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (386.25, 31.87) {10};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (433.62, 31.87) {100};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (480.99, 31.87) {1000};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (528.36, 31.87) {10000};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (383.03, 31.87) {5};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (402.04, 31.87) {10};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (446.19, 31.87) {50};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (465.20, 31.87) {100};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.83] at (509.35, 31.87) {500};
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 97.17) -- (333.90, 97.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,144.54) -- (333.90,144.54);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,191.91) -- (333.90,191.91);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 93.95) -- (333.90, 93.95);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,112.96) -- (333.90,112.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,157.11) -- (333.90,157.11);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,176.12) -- (333.90,176.12);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,220.27) -- (333.90,220.27);
 
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92, 94.31) {10};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,141.68) {100};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,189.05) {1000};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,236.42) {10000};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92, 91.09) {5};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,110.10) {10};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,154.25) {50};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,173.26) {100};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,217.41) {500};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,236.42) {1000};
 \end{scope}

### 2020-08-28 benchmarking/benchmarkingVM/ESS_round1_real.tex
results update

--- 2020-08-10 benchmarking/benchmarkingVM/ESS_round1_real.tex
@@
-% Created by tikzDevice version 0.12.3 on 2020-08-10 16:04:15
+% Created by tikzDevice version 0.12.3.1 on 2020-08-28 13:28:47
 % !TEX encoding = UTF-8 Unicode
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,301.03) {ESS/hr [nocons (\textit{real})]};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,433.62) {ESS/hr [cons (\textit{real})]};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,301.03) {ESS/$10^6$ states [nocons (\textit{real})]};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,433.62) {ESS/$10^6$ states [cons (\textit{real})]};
 \end{scope}
@@
 \path[clip] ( 49.80,338.88) rectangle (239.28,528.36);
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (  0.00,403.16) --
+	(175.00,578.16);
+
+\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (302.44,578.16) --
+	(302.44,477.44) --
+	(  0.00,175.00);
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (  0.00,365.13) --
+	(213.03,578.16);
+
+\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (302.44,578.16) --
+	(302.44,515.47) --
+	(  0.00,213.03);
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (  0.00,327.11) --
+	(251.05,578.16);
+
+\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (302.44,578.16) --
+	(302.44,553.49) --
+	(  0.00,251.05);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,374.64) --
-	(203.52,578.16);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (286.65,578.16) --
-	(286.65,490.17) --
-	(  0.00,203.52);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (  0.00,346.12) --
-	(232.04,578.16);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (286.65,578.16) --
-	(286.65,518.69) --
-	(  0.00,232.04);
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (  0.00,317.60) --
-	(260.56,578.16);
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (286.65,578.16) --
-	(286.65,547.21) --
-	(  0.00,260.56);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (142.89,342.31) {$\frac{1}{64} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,435.87) {$64\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (114.37,342.31) {$\frac{1}{16} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,407.35) {$16\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 84.20,342.31) {$\frac{1}{4} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92,378.83) {$4\times$};
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,528.36);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 86.08,409.37) --
-	(106.21,409.37);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 98.51,401.22) --
-	( 98.51,415.19);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 98.51,406.14) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.95,474.99) --
-	(188.09,474.99);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.83,473.08) --
-	(184.83,476.74);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.83,470.96) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.65,474.30) --
-	(102.96,474.30);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 98.44,471.52) --
-	( 98.44,476.75);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 98.44,470.27) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 85.75,424.33) --
-	( 97.88,424.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.70,416.17) --
-	( 92.70,430.15);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 92.70,420.29) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 85.46,386.96) --
-	(113.76,386.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (104.13,378.15) --
-	(104.13,393.10);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (104.13,384.05) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.32,483.57) --
-	(194.53,483.57);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.94,482.97) --
-	(193.94,484.15);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.94,480.66) {$\kappa$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (167.20,470.80) --
-	(170.02,470.80);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.66,467.68) --
-	(168.66,473.50);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (168.66,467.57) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.39,475.00) --
-	(191.75,475.00);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.60,470.62) --
-	(187.60,478.61);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.60,470.96) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.47,480.80) --
-	(187.89,480.80);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.19,478.95) --
-	(187.19,482.50);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.19,476.77) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.19,457.78) --
-	(173.69,457.78);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.12,454.35) --
-	(171.12,460.71);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.12,453.74) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.89,460.59) --
-	(174.27,460.59);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.11,456.85) --
-	(173.11,463.75);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.11,457.69) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.58,485.03) --
-	(197.77,485.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.24,483.39) --
-	(196.24,486.55);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.24,482.13) {$\kappa$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.67,442.74) --
-	(172.67,448.10);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.67,442.37) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.04,481.91) --
-	(199.30,481.91);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.99,481.15) --
-	(195.99,482.65);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.99,477.88) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.28,483.17) --
-	(201.19,483.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.73,482.87) --
-	(194.73,483.47);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.73,479.14) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (141.61,413.21) --
-	(141.61,424.99);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (141.61,415.90) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.98,435.47) --
-	(171.98,440.78);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.98,435.39) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.52,487.53) --
-	(197.96,487.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.74,487.09) --
-	(197.74,487.96);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.74,484.63) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (135.67,450.29) --
-	(147.06,450.29);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (142.14,448.74) --
-	(142.14,451.73);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (142.14,447.06) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.48,480.63) --
-	(196.33,480.63);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.61,479.97) --
-	(193.61,481.28);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.61,476.60) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.06,479.97) --
-	(184.03,479.97);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.70,479.64) --
-	(181.70,480.30);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.70,475.94) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (131.78,442.10) --
-	(143.02,442.10);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.16,440.36) --
-	(138.16,443.70);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (138.16,438.06) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (132.72,440.69) --
-	(144.81,440.69);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (139.64,439.60) --
-	(139.64,441.72);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (139.64,437.78) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.55,488.06) --
-	(198.21,488.06);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.88,487.69) --
-	(197.88,488.42);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.88,485.15) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (123.29,429.70) --
-	(134.35,429.70);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.55,425.74) --
-	(129.55,433.02);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (129.55,426.47) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.28,475.22) --
-	(196.89,475.22);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.22,472.58) --
-	(190.22,477.56);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.22,471.19) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.67,475.58) --
-	(153.58,475.58);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (152.65,474.36) --
-	(152.65,476.74);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (152.65,471.55) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (115.83,424.98) --
-	(122.98,424.98);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (119.72,420.83) --
-	(119.72,428.44);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (119.72,420.95) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (127.22,406.71) --
-	(136.61,406.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (132.44,404.17) --
-	(132.44,408.97);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (132.44,403.80) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.61,485.43) --
-	(196.23,485.43);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.92,484.44) --
-	(195.92,486.37);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.92,482.52) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (167.63,453.48) --
-	(167.63,460.42);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (167.63,454.02) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (118.33,472.88) --
-	(196.07,472.88);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.27,470.47) --
-	(182.27,475.03);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.27,468.84) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.68,480.81) --
-	(208.94,480.81);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.36,480.47) --
-	(203.36,481.14);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (203.36,476.77) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (146.51,449.17) --
-	(188.52,449.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.77,446.85) --
-	(176.77,451.26);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.77,445.14) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (183.26,455.28) --
-	(183.26,459.17);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.26,454.41) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.59,486.76) --
-	(197.77,486.76);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.19,486.27) --
-	(197.19,487.23);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.19,483.85) {$\kappa$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (105.42,469.49) --
-	(156.55,469.49);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (143.93,468.42) --
-	(143.93,470.50);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (143.93,466.26) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.45,480.12) --
-	(196.70,480.12);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.33,479.27) --
-	(184.33,480.94);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.33,476.09) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.84,479.79) --
-	(170.18,479.79);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.16,479.63) --
-	(162.16,479.96);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (162.16,475.76) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (136.98,446.13) --
-	(145.62,446.13);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (141.75,445.29) --
-	(141.75,446.94);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (141.75,442.10) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (101.91,443.79) --
-	(149.00,443.79);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (136.72,442.48) --
-	(136.72,445.01);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (136.72,440.88) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.72,487.93) --
-	(199.43,487.93);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.12,487.45) --
-	(198.12,488.39);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.12,485.02) {$\kappa$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (171.41,342.31) {$\frac{1}{64} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,464.39) {$64\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (133.38,342.31) {$\frac{1}{16} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,426.36) {$16\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 93.70,342.31) {$\frac{1}{4} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92,388.34) {$4\times$};
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,528.36);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 78.41,410.95) --
+	( 91.01,410.95);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 85.43,396.47) --
+	( 85.43,420.38);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 85.43,407.72) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.48,467.57) --
+	(182.33,467.57);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.56,466.01) --
+	(179.56,469.05);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.56,463.54) {$L$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 81.27,472.87) --
+	( 87.83,472.87);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 84.75,471.19) --
+	( 84.75,474.46);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 84.75,468.84) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 77.34,424.98) --
+	( 96.67,424.98);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 88.68,419.14) --
+	( 88.68,429.79);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 88.68,420.94) {$h$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 77.52,382.73) --
+	(108.13,382.73);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 96.89,359.01) --
+	( 96.89,395.26);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 96.89,379.83) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.26,478.14) --
+	(189.63,478.14);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.95,477.37) --
+	(188.95,478.88);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.95,475.23) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (141.10,467.30) --
+	(170.92,467.30);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (159.88,465.91) --
+	(159.88,468.61);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (159.88,464.07) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (177.80,474.02) --
+	(190.74,474.02);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.02,472.32) --
+	(185.02,475.62);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.02,469.99) {$L$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.73,476.99) --
+	(183.11,476.99);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.67,476.82) --
+	(179.67,477.16);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.67,472.96) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (139.34,449.32) --
+	(177.09,449.32);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.26,447.98) --
+	(164.26,450.60);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (164.26,445.29) {$h$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (117.89,454.32) --
+	(191.13,454.32);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.96,452.70) --
+	(173.96,455.85);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.96,451.42) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.24,481.37) --
+	(192.56,481.37);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.42,480.81) --
+	(191.42,481.92);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.42,478.46) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.68,424.45) --
+	(151.68,434.52);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (151.68,426.72) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.78,476.44) --
+	(192.59,476.44);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.44,475.09) --
+	(184.44,477.73);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.44,472.41) {$L$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.84,478.90) --
+	(189.05,478.90);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.62,478.65) --
+	(183.62,479.14);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.62,474.86) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (148.64,389.28) --
+	(148.64,395.86);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (148.64,388.74) {$h$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (159.92,416.68) --
+	(159.92,425.68);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (159.92,418.64) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.20,483.88) --
+	(195.50,483.88);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.86,483.48) --
+	(194.86,484.29);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.86,480.98) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (144.50,437.03) --
+	(144.50,441.13);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (144.50,435.93) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (166.76,476.35) --
+	(192.56,476.35);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.59,475.11) --
+	(182.59,477.54);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.59,472.32) {$L$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (157.54,475.45) --
+	(177.27,475.45);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.14,475.33) --
+	(169.14,475.58);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.14,471.42) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (142.49,430.50) --
+	(142.49,432.37);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (142.49,427.42) {$h$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (160.23,425.41) --
+	(160.23,429.48);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (160.23,424.62) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.33,484.64) --
+	(195.61,484.64);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.98,484.32) --
+	(194.98,484.95);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.98,481.73) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (101.54,432.34) --
+	(123.04,432.34);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (114.35,429.11) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.64,471.96) --
+	(192.30,471.96);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.87,467.92) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (132.95,472.27) --
+	(142.09,472.27);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (137.90,468.23) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 85.73,415.23) --
+	(106.54,415.23);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 98.06,411.19) {$h$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 98.15,400.30) --
+	(118.93,400.30);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (110.47,397.40) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.20,481.36) --
+	(193.74,481.36);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.56,478.45) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 32.48,444.50) --
+	(192.17,444.50);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.24,441.31) --
+	(173.24,447.36);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.24,441.28) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (132.20,463.69) --
+	(175.44,463.69);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.58,461.46) --
+	(161.58,465.75);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (161.58,459.66) {$L$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.89,474.60) --
+	(201.90,474.60);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.54,474.36) --
+	(196.54,474.83);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.54,470.56) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (146.45,434.24) --
+	(175.79,434.24);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.87,432.34) --
+	(164.87,436.02);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (164.87,430.21) {$h$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (138.81,444.30) --
+	(205.67,444.30);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.96,442.70) --
+	(188.96,445.81);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.96,441.39) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.98,483.57) --
+	(193.61,483.57);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.81,482.98) --
+	(192.81,484.15);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.81,480.67) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (139.00,463.79) --
+	(201.79,463.79);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.42,461.47) --
+	(185.42,465.93);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.42,460.57) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.22,472.84) --
+	(191.06,472.84);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.99,472.16) --
+	(186.99,473.50);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (186.99,468.81) {$L$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (158.42,475.45) --
+	(161.91,475.45);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (160.22,475.26) --
+	(160.22,475.63);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (160.22,471.41) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (127.39,437.43) --
+	(187.18,437.43);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.11,435.37) --
+	(171.11,439.35);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.11,433.40) {$h$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (131.09,432.16) --
+	(204.47,432.16);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.28,430.29) --
+	(187.28,433.90);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.28,429.25) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.52,484.51) --
+	(195.71,484.51);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.16,483.14) --
+	(194.16,485.82);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.16,481.61) {$\kappa$};
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (136.95,468.82) --
-	(161.50,468.82);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (152.69,467.28) --
-	(152.69,470.26);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (152.69,465.59) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.00,470.14) --
-	(184.33,470.14);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.81,462.83) --
-	(175.81,475.52);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (175.81,466.10) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.94,477.02) --
-	(194.40,477.02);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.18,476.87) --
-	(187.18,477.17);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.18,472.99) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (127.34,436.53) --
-	(152.92,436.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (143.88,434.15) --
-	(143.88,438.66);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (143.88,432.50) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (137.00,458.99) --
-	(163.24,458.99);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (154.05,457.82) --
-	(154.05,460.09);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (154.05,456.08) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.68,499.03) --
-	(209.42,499.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.05,497.42) --
-	(209.05,500.52);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.05,496.12) {$\kappa$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.40,457.56) --
-	(200.40,467.28);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (200.40,459.76) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (178.81,457.66) --
-	(178.81,463.95);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (178.81,457.01) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.96,478.25) --
-	(210.16,478.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (199.32,477.51) --
-	(199.32,478.96);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.32,474.22) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (141.43,462.19) --
-	(168.73,462.19);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.31,458.09) --
-	(159.31,465.60);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (159.31,458.15) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.44,454.40) --
-	(184.44,464.73);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.44,457.30) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.41,501.46) --
-	(213.31,501.46);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.38,500.63) --
-	(212.38,502.26);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.38,498.56) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 87.75,444.22) --
+	(129.17,444.22);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (115.63,442.73) --
+	(115.63,445.63);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (115.63,440.99) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (119.18,453.67) --
+	(160.39,453.67);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (146.89,450.11) --
+	(146.89,456.83);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (146.89,449.64) {$L$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (146.34,455.68) --
+	(169.74,455.68);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (160.47,455.40) --
+	(160.47,455.96);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (160.47,451.65) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 79.88,412.46) --
+	(117.32,412.46);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (104.54,406.29) --
+	(104.54,417.50);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (104.54,408.43) {$h$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 90.78,434.42) --
+	(132.68,434.42);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (119.05,432.86) --
+	(119.05,435.90);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (119.05,431.52) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.48,481.72) --
+	(193.39,481.72);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.50,481.16) --
+	(191.50,482.26);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.50,478.81) {$\kappa$};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,301.03) {ESS/hr [nocons (\textit{real})]};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (307.01,433.62) {ESS/hr [adapt (\textit{real})]};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,301.03) {ESS/$10^6$ states [nocons (\textit{real})]};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (307.01,433.62) {ESS/$10^6$ states [adapt (\textit{real})]};
 \end{scope}
@@
 \path[clip] (338.88,338.88) rectangle (528.36,528.36);
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] ( 86.24,200.32) --
+	(464.08,578.16);
+
+\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (578.16,464.08) --
+	(114.08,  0.00);
+
+\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] ( 86.24,  0.00) --
+	( 86.24,200.32);
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] ( 86.24,162.29) --
+	(502.11,578.16);
+
+\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (578.16,502.11) --
+	( 86.24, 10.19) --
+	( 86.24,162.29);
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] ( 86.24,124.27) --
+	(540.13,578.16);
+
+\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (578.16,540.13) --
+	( 86.24, 48.21) --
+	( 86.24,124.27);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (149.40,234.96) --
-	(492.60,578.16);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (575.73,578.16) --
-	(575.73,490.17) --
-	(149.40, 63.84) --
-	(149.40,234.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (149.40,206.44) --
-	(521.12,578.16);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (575.73,578.16) --
-	(575.73,518.69) --
-	(149.40, 92.36) --
-	(149.40,206.44);
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (149.40,177.92) --
-	(549.64,578.16);
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (575.73,578.16) --
-	(575.73,547.21) --
-	(149.40,120.88) --
-	(149.40,177.92);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (431.97,342.31) {$\frac{1}{64} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,435.87) {$64\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (403.45,342.31) {$\frac{1}{16} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,407.35) {$16\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (373.28,342.31) {$\frac{1}{4} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.00,378.83) {$4\times$};
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (338.88,338.88) -- (528.36,528.36);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (375.16,462.17) --
-	(395.29,462.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (387.59,455.39) --
-	(387.59,467.26);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (387.59,458.94) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (470.03,462.51) --
-	(477.17,462.51);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (473.91,460.09) --
-	(473.91,464.68);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (473.91,458.48) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (381.73,476.56) --
-	(392.04,476.56);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (387.52,475.30) --
-	(387.52,477.74);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (387.52,472.52) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (374.83,434.62) --
-	(386.96,434.62);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (381.78,423.86) --
-	(381.78,441.65);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (381.78,430.59) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (374.54,464.74) --
-	(402.84,464.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (393.21,459.17) --
-	(393.21,469.12);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (393.21,461.83) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.40,483.53) --
-	(483.61,483.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.02,482.91) --
-	(483.02,484.13);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.02,480.62) {$\kappa$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.75,443.62) --
-	(461.75,448.06);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (461.75,442.73) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (481.12,483.60) --
-	(488.38,483.60);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.07,482.02) --
-	(485.07,485.07);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (485.07,479.57) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.36,487.42) --
-	(490.27,487.42);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.81,487.26) --
-	(483.81,487.59);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.81,483.39) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (430.69,411.54) --
-	(430.69,418.19);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (430.69,411.10) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.06,438.24) --
-	(461.06,444.47);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (461.06,438.69) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.60,487.66) --
-	(487.04,487.66);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.82,487.45) --
-	(486.82,487.86);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (486.82,484.75) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (424.75,457.09) --
-	(436.14,457.09);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (431.22,454.99) --
-	(431.22,458.99);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (431.22,453.86) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.56,479.48) --
-	(485.41,479.48);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.69,477.59) --
-	(482.69,481.21);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (482.69,475.44) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (468.14,481.62) --
-	(473.11,481.62);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (470.78,481.21) --
-	(470.78,482.01);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (470.78,477.58) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.86,447.08) --
-	(432.10,447.08);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.24,444.06) --
-	(427.24,449.71);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (427.24,443.04) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,452.65) --
-	(433.89,452.65);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (428.72,450.91) --
-	(428.72,454.26);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (428.72,449.75) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.63,487.71) --
-	(487.29,487.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.96,487.18) --
-	(486.96,488.23);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (486.96,484.81) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.37,467.01) --
-	(423.43,467.01);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.63,464.26) --
-	(418.63,469.44);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (418.63,463.79) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (469.36,471.07) --
-	(485.97,471.07);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.30,468.87) --
-	(479.30,473.05);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (479.30,467.03) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (440.75,476.74) --
-	(442.66,476.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (441.73,476.63) --
-	(441.73,476.85);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (441.73,472.71) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (404.91,429.18) --
-	(412.06,429.18);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (408.80,425.26) --
-	(408.80,432.48);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (408.80,425.15) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (416.30,451.88) --
-	(425.69,451.88);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.52,447.05) --
-	(421.52,455.79);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (421.52,448.98) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (484.69,485.74) --
-	(485.31,485.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.00,485.16) --
-	(485.00,486.31);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (485.00,482.84) {$\kappa$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (394.50,471.89) --
-	(445.63,471.89);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.01,471.02) --
-	(433.01,472.72);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (433.01,468.66) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (437.53,472.23) --
-	(485.78,472.23);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (473.41,470.53) --
-	(473.41,473.80);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (473.41,468.19) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (437.92,477.58) --
-	(459.26,477.58);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (451.24,477.30) --
-	(451.24,477.86);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (451.24,473.55) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.06,447.19) --
-	(434.70,447.19);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (430.83,445.94) --
-	(430.83,448.37);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (430.83,443.16) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (390.99,447.71) --
-	(438.08,447.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (425.80,444.74) --
-	(425.80,450.30);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (425.80,444.81) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.80,487.32) --
-	(488.51,487.32);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (487.20,486.11) --
-	(487.20,488.46);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (487.20,484.42) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.03,474.71) --
-	(450.58,474.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (441.77,471.39) --
-	(441.77,477.57);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (441.77,471.49) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (450.08,475.71) --
-	(473.41,475.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.89,464.98) --
-	(464.89,482.73);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (464.89,471.68) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (465.02,485.03) --
-	(483.48,485.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.26,484.42) --
-	(476.26,485.62);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (476.26,481.00) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (416.42,443.07) --
-	(442.00,443.07);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (432.96,436.47) --
-	(432.96,448.06);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (432.96,439.03) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.08,473.47) --
-	(452.32,473.47);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (443.13,467.70) --
-	(443.13,477.96);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (443.13,470.56) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (497.76,498.31) --
-	(498.50,498.31);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (498.13,497.03) --
-	(498.13,499.52);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (498.13,495.41) {$\kappa$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (489.48,465.66) --
-	(489.48,472.86);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (489.48,466.35) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (467.89,457.46) --
-	(467.89,463.10);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (467.89,456.44) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.04,488.08) --
-	(499.24,488.08);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (488.40,487.70) --
-	(488.40,488.45);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (488.40,484.04) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (430.51,469.46) --
-	(457.81,469.46);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (448.39,469.28) --
-	(448.39,469.64);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (448.39,465.42) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (473.52,468.14) --
-	(473.52,474.77);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (473.52,468.82) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (500.49,501.82) --
-	(502.39,501.82);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (501.46,500.70) --
-	(501.46,502.87);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (501.46,498.91) {$\kappa$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (460.49,342.31) {$\frac{1}{64} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,464.39) {$64\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (422.46,342.31) {$\frac{1}{16} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,426.36) {$16\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (382.78,342.31) {$\frac{1}{4} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.00,388.34) {$4\times$};
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (338.88,338.88) -- (528.36,528.36);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (367.49,467.04) --
+	(380.09,467.04);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (374.51,464.05) --
+	(374.51,469.74);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (374.51,463.82) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (465.56,448.03) --
+	(471.41,448.03);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (468.64,444.87) --
+	(468.64,450.86);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.64,444.00) {$L$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (370.35,473.24) --
+	(376.91,473.24);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (373.83,472.46) --
+	(373.83,473.99);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (373.83,469.20) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (366.42,435.02) --
+	(385.75,435.02);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (377.76,431.48) --
+	(377.76,438.16);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (377.76,430.99) {$h$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (366.60,468.13) --
+	(397.21,468.13);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (385.97,465.86) --
+	(385.97,470.24);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (385.97,465.23) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (477.34,477.42) --
+	(478.71,477.42);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (478.03,476.86) --
+	(478.03,477.97);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (478.03,474.52) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (430.18,471.54) --
+	(460.00,471.54);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (448.96,470.69) --
+	(448.96,472.36);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (448.96,468.31) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (466.88,474.80) --
+	(479.82,474.80);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (474.10,472.77) --
+	(474.10,476.70);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.10,470.77) {$L$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (464.81,479.57) --
+	(472.19,479.57);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (468.75,479.29) --
+	(468.75,479.85);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.75,475.54) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (428.42,454.70) --
+	(466.17,454.70);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (453.34,453.16) --
+	(453.34,456.15);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (453.34,450.66) {$h$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (406.97,473.34) --
+	(480.21,473.34);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (463.04,472.63) --
+	(463.04,474.04);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (463.04,470.44) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (479.32,481.45) --
+	(481.64,481.45);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.50,480.91) --
+	(480.50,481.98);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (480.50,478.54) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (440.76,432.68) --
+	(440.76,439.12);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (440.76,432.86) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (461.86,479.26) --
+	(481.67,479.26);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (473.52,478.07) --
+	(473.52,480.41);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (473.52,475.23) {$L$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (465.92,482.87) --
+	(478.13,482.87);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (472.70,482.55) --
+	(472.70,483.18);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (472.70,478.84) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (437.72,397.21) --
+	(437.72,405.84);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (437.72,397.83) {$h$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (449.00,429.23) --
+	(449.00,436.09);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (449.00,429.97) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.28,484.21) --
+	(484.58,484.21);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.94,483.81) --
+	(483.94,484.61);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.94,481.31) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (433.58,448.44) --
+	(433.58,452.06);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (433.58,447.08) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (455.84,473.88) --
+	(481.64,473.88);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (471.67,472.84) --
+	(471.67,474.88);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (471.67,469.85) {$L$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (446.62,475.99) --
+	(466.35,475.99);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (458.22,475.70) --
+	(458.22,476.27);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (458.22,471.95) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (431.57,433.40) --
+	(431.57,438.03);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (431.57,431.78) {$h$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (449.31,443.26) --
+	(449.31,447.88);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (449.31,442.77) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.41,484.53) --
+	(484.69,484.53);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (484.06,484.08) --
+	(484.06,484.98);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (484.06,481.63) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (390.62,463.50) --
+	(412.12,463.50);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (403.43,460.57) --
+	(403.43,466.15);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (403.43,460.27) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (460.72,461.08) --
+	(481.38,461.08);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (472.95,460.33) --
+	(472.95,461.81);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (472.95,457.05) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (422.03,470.75) --
+	(431.17,470.75);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (426.98,470.01) --
+	(426.98,471.47);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (426.98,466.72) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (374.81,416.60) --
+	(395.62,416.60);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (387.14,412.44) --
+	(387.14,420.21);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (387.14,412.57) {$h$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (387.23,446.61) --
+	(408.01,446.61);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (399.55,444.30) --
+	(399.55,448.73);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (399.55,443.70) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (478.28,481.27) --
+	(482.82,481.27);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.64,480.85) --
+	(480.64,481.68);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (480.64,478.36) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (321.56,455.89) --
+	(481.25,455.89);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (462.32,452.11) --
+	(462.32,459.20);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (462.32,452.66) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (421.28,478.12) --
+	(464.52,478.12);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (450.66,477.19) --
+	(450.66,479.03);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (450.66,474.09) {$L$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (478.97,495.81) --
+	(490.98,495.81);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (485.62,495.66) --
+	(485.62,495.97);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (485.62,491.78) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (435.53,446.43) --
+	(464.87,446.43);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (453.95,444.35) --
+	(453.95,448.35);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (453.95,442.39) {$h$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (427.89,460.23) --
+	(494.75,460.23);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (478.04,459.37) --
+	(478.04,461.07);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (478.04,457.33) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.06,483.43) --
+	(482.69,483.43);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.89,483.01) --
+	(481.89,483.84);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (481.89,480.52) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (428.08,510.61) --
+	(490.87,510.61);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (474.50,506.59) --
+	(474.50,514.11);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.50,507.38) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (471.30,510.72) --
+	(480.14,510.72);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (476.07,507.87) --
+	(476.07,513.30);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (476.07,506.68) {$L$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (416.47,483.27) --
+	(476.26,483.27);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (460.19,480.40) --
+	(460.19,485.87);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (460.19,479.24) {$h$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (420.17,487.76) --
+	(493.55,487.76);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (476.36,484.08) --
+	(476.36,491.00);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (476.36,484.85) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.60,529.08) --
+	(484.79,529.08);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.24,525.48) --
+	(483.24,532.27);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.24,526.18) {$\kappa$};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54, 11.95) {ESS/hr [cons (\textit{real})]};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,144.54) {ESS/hr [adapt (\textit{real})]};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54, 11.95) {ESS/$10^6$ states [cons (\textit{real})]};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,144.54) {ESS/$10^6$ states [adapt (\textit{real})]};
 \end{scope}
@@
 \path[clip] ( 49.80, 49.80) rectangle (239.28,239.28);
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (  0.00,114.08) --
+	(302.44,416.52) --
+	(302.44,188.36) --
+	(114.08,  0.00);
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (  0.00, 76.05) --
+	(302.44,378.49) --
+	(302.44,226.39) --
+	( 76.05,  0.00);
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (  0.00, 38.03) --
+	(302.44,340.47) --
+	(302.44,264.41) --
+	( 38.03,  0.00);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00, 85.56) --
-	(286.65,372.21) --
-	(286.65,201.09) --
-	( 85.56,  0.00);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (  0.00, 57.04) --
-	(286.65,343.69) --
-	(286.65,229.61) --
-	( 57.04,  0.00);
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (  0.00, 28.52) --
-	(286.65,315.17) --
-	(286.65,258.13) --
-	( 28.52,  0.00);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (142.89, 53.23) {$\frac{1}{64} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,146.79) {$64\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (114.37, 53.23) {$\frac{1}{16} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,118.27) {$16\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 84.20, 53.23) {$\frac{1}{4} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92, 89.75) {$4\times$};
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] ( 49.80, 49.80) -- (239.28,239.28);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.14,173.09) --
-	(126.11,173.09);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.29,166.31) --
-	(120.29,178.18);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (120.29,169.86) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.00,173.43) --
-	(187.66,173.43);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.91,171.01) --
-	(185.91,175.60);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.91,169.40) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.44,187.48) --
-	(187.67,187.48);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.22,186.22) --
-	(185.22,188.66);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.22,183.44) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (127.09,145.54) --
-	(141.07,145.54);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (135.25,134.78) --
-	(135.25,152.57);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (135.25,141.51) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.07,175.66) --
-	(104.02,175.66);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 97.88,170.09) --
-	( 97.88,180.04);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 97.88,172.75) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.89,194.45) --
-	(195.07,194.45);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.49,193.83) --
-	(194.49,195.05);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.49,191.54) {$\kappa$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.66,156.88) --
-	(159.02,156.88);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (156.52,154.54) --
-	(156.52,158.98);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (156.52,153.65) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.07,194.52) --
-	(193.57,194.52);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.83,192.94) --
-	(192.83,195.99);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.83,190.49) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.79,198.34) --
-	(194.39,198.34);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.09,198.18) --
-	(194.09,198.51);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.09,194.31) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (124.13,126.05) --
-	(135.91,126.05);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (130.85,122.46) --
-	(130.85,129.11);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (130.85,122.02) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (146.39,152.51) --
-	(151.70,152.51);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (149.22,149.16) --
-	(149.22,155.39);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (149.22,149.61) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.01,198.58) --
-	(198.88,198.58);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.45,198.37) --
-	(198.45,198.78);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.45,195.67) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.66,168.01) --
-	(162.65,168.01);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.21,165.91) --
-	(161.21,169.91);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (161.21,164.78) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.89,190.40) --
-	(192.20,190.40);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.55,188.51) --
-	(191.55,192.13);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.55,186.36) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.56,192.54) --
-	(191.22,192.54);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.89,192.13) --
-	(190.89,192.93);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.89,188.50) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.28,158.00) --
-	(154.62,158.00);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.02,154.98) --
-	(153.02,160.63);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (153.02,153.96) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (150.52,163.57) --
-	(152.64,163.57);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.61,161.83) --
-	(151.61,165.18);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (151.61,160.67) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.61,198.63) --
-	(199.34,198.63);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.98,198.10) --
-	(198.98,199.15);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.98,195.73) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (136.66,177.93) --
-	(143.94,177.93);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.62,175.18) --
-	(140.62,180.36);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (140.62,174.71) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (183.50,181.99) --
-	(188.48,181.99);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.14,179.79) --
-	(186.14,183.97);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (186.14,177.95) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.28,187.66) --
-	(187.66,187.66);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.50,187.55) --
-	(186.50,187.77);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (186.50,183.63) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (131.75,140.10) --
-	(139.36,140.10);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (135.90,136.18) --
-	(135.90,143.40);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (135.90,136.07) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (115.09,162.80) --
-	(119.89,162.80);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.63,157.97) --
-	(117.63,166.71);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (117.63,159.90) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.36,196.66) --
-	(197.29,196.66);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.35,196.08) --
-	(196.35,197.23);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.35,193.76) {$\kappa$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.34,182.81) --
-	(181.42,182.81);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.41,181.94) --
-	(180.41,183.64);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.41,179.58) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.19,183.15) --
-	(191.86,183.15);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.04,181.45) --
-	(191.04,184.72);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.04,179.11) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.55,188.50) --
-	(190.88,188.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.71,188.22) --
-	(190.71,188.78);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.71,184.47) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (156.21,158.11) --
-	(157.86,158.11);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (157.05,156.86) --
-	(157.05,159.29);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (157.05,154.08) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.40,158.63) --
-	(155.93,158.63);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (154.71,155.66) --
-	(154.71,161.22);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (154.71,155.73) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.37,198.24) --
-	(199.31,198.24);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.85,197.03) --
-	(198.85,199.38);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.85,195.34) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (178.20,185.63) --
-	(181.18,185.63);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.74,182.31) --
-	(179.74,188.49);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.74,182.41) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.75,186.63) --
-	(186.44,186.63);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.06,175.90) --
-	(181.06,193.65);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.06,182.60) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.79,195.95) --
-	(188.09,195.95);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.94,195.34) --
-	(187.94,196.54);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.94,191.92) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.07,153.99) --
-	(149.58,153.99);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (147.45,147.39) --
-	(147.45,158.98);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (147.45,149.95) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.74,184.39) --
-	(171.01,184.39);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.91,178.62) --
-	(169.91,188.88);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.91,181.48) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.34,209.23) --
-	(211.44,209.23);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.95,207.95) --
-	(209.95,210.44);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.95,206.33) {$\kappa$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.48,180.49) --
-	(178.20,180.49);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.91,176.58) --
-	(173.91,183.78);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.91,177.27) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.58,171.39) --
-	(174.87,171.39);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.97,168.38) --
-	(171.97,174.02);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.97,167.36) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.43,199.00) --
-	(189.88,199.00);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.17,198.62) --
-	(189.17,199.37);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (189.17,194.96) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.01,180.38) --
-	(176.52,180.38);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.11,180.20) --
-	(173.11,180.56);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.11,176.34) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (165.32,182.64) --
-	(175.65,182.64);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.13,179.06) --
-	(171.13,185.69);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.13,179.74) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.55,212.74) --
-	(213.18,212.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.38,211.62) --
-	(212.38,213.79);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.38,209.83) {$\kappa$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (171.41, 53.23) {$\frac{1}{64} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,175.31) {$64\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (133.38, 53.23) {$\frac{1}{16} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,137.28) {$16\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 93.70, 53.23) {$\frac{1}{4} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92, 99.26) {$4\times$};
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 49.80, 49.80) -- (239.28,239.28);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (107.39,177.96) --
+	(131.30,177.96);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (121.87,174.97) --
+	(121.87,180.66);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (121.87,174.74) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.93,158.95) --
+	(179.97,158.95);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.49,155.79) --
+	(178.49,161.78);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (178.49,154.92) {$L$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.11,184.16) --
+	(185.38,184.16);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.79,183.38) --
+	(183.79,184.91);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.79,180.12) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (130.06,145.94) --
+	(140.71,145.94);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (135.90,142.40) --
+	(135.90,149.08);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (135.90,141.91) {$h$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 69.93,179.05) --
+	(106.18,179.05);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 93.65,176.78) --
+	( 93.65,181.16);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 93.65,176.15) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.29,188.34) --
+	(189.80,188.34);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.06,187.78) --
+	(189.06,188.89);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (189.06,185.44) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.83,182.46) --
+	(179.53,182.46);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.22,181.61) --
+	(178.22,183.28);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (178.22,179.23) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.24,185.72) --
+	(186.54,185.72);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.94,183.69) --
+	(184.94,187.62);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.94,181.69) {$L$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.74,190.49) --
+	(188.08,190.49);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.91,190.21) --
+	(187.91,190.77);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.91,186.46) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (158.90,165.62) --
+	(161.52,165.62);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (160.24,164.08) --
+	(160.24,167.07);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (160.24,161.58) {$h$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (163.62,184.26) --
+	(166.77,184.26);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (165.24,183.55) --
+	(165.24,184.96);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (165.24,181.36) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.73,192.37) --
+	(192.84,192.37);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.29,191.83) --
+	(192.29,192.90);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.29,189.46) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (135.37,147.01) --
+	(145.44,147.01);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (140.87,143.60) --
+	(140.87,150.04);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (140.87,143.78) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.01,190.18) --
+	(188.65,190.18);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.36,188.99) --
+	(187.36,191.33);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.36,186.15) {$L$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.57,193.79) --
+	(190.06,193.79);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.82,193.47) --
+	(189.82,194.10);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (189.82,189.76) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (100.20,112.78) --
+	(106.78,112.78);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (103.69,108.13) --
+	(103.69,116.76);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (103.69,108.75) {$h$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (127.60,143.80) --
+	(136.60,143.80);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (132.47,140.15) --
+	(132.47,147.01);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (132.47,140.89) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.40,195.13) --
+	(195.21,195.13);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.80,194.73) --
+	(194.80,195.53);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.80,192.23) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (147.95,161.23) --
+	(152.05,161.23);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.07,159.36) --
+	(150.07,162.98);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (150.07,158.00) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.03,184.80) --
+	(188.46,184.80);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.27,183.76) --
+	(187.27,185.80);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.27,180.77) {$L$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.25,186.91) --
+	(186.50,186.91);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.37,186.62) --
+	(186.37,187.19);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (186.37,182.87) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (141.42,146.73) --
+	(143.29,146.73);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (142.37,144.32) --
+	(142.37,148.95);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (142.37,142.70) {$h$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (136.33,156.59) --
+	(140.40,156.59);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (138.44,154.18) --
+	(138.44,158.80);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (138.44,153.69) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.24,195.45) --
+	(195.87,195.45);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.56,195.00) --
+	(195.56,195.90);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.56,192.55) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (143.26,171.49) --
+	(143.26,177.07);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (143.26,171.19) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.88,171.25) --
+	(182.88,172.73);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.88,167.97) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.19,180.93) --
+	(183.19,182.39);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.19,177.64) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (126.15,123.36) --
+	(126.15,131.13);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (126.15,123.49) {$h$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (111.22,155.22) --
+	(111.22,159.65);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (111.22,154.62) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.28,191.77) --
+	(192.28,192.60);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.28,189.28) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.23,166.81) --
+	(158.28,166.81);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (155.42,163.03) --
+	(155.42,170.12);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (155.42,163.58) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.38,189.04) --
+	(176.67,189.04);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.61,188.11) --
+	(174.61,189.95);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.61,185.01) {$L$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.28,206.73) --
+	(185.75,206.73);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.52,206.58) --
+	(185.52,206.89);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.52,202.70) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (143.26,157.35) --
+	(146.94,157.35);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (145.16,155.27) --
+	(145.16,159.27);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (145.16,153.31) {$h$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (153.62,171.15) --
+	(156.73,171.15);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (155.22,170.29) --
+	(155.22,171.99);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (155.22,168.25) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.90,194.35) --
+	(195.07,194.35);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.49,193.93) --
+	(194.49,194.76);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.49,191.44) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.39,221.53) --
+	(176.85,221.53);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.71,217.51) --
+	(174.71,225.03);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.71,218.30) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.08,221.64) --
+	(184.42,221.64);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.76,218.79) --
+	(183.76,224.22);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.76,217.60) {$L$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (146.29,194.19) --
+	(150.27,194.19);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (148.35,191.32) --
+	(148.35,196.79);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (148.35,190.16) {$h$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (141.21,198.68) --
+	(144.82,198.68);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (143.08,195.00) --
+	(143.08,201.92);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (143.08,195.77) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.06,240.00) --
+	(196.74,240.00);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.43,236.40) --
+	(195.43,243.19);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.43,237.10) {$\kappa$};
 \end{scope}
@@
 
-\path[fill=fillColor] (485.73,232.77) circle (  1.87);
-
-\path[fill=fillColor] (485.73, 55.06) --
-	(488.24, 50.70) --
-	(483.21, 50.70) --
+\path[fill=fillColor] (485.73,235.47) circle (  1.87);
+
+\path[fill=fillColor] (485.73, 54.16) --
+	(488.24, 49.81) --
+	(483.21, 49.81) --
 	cycle;
@@
 \node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
-\definecolor{fillColor}{RGB}{143,161,0}
-
-\path[fill=fillColor] (394.78,149.36) circle (  1.87);
-
-\path[fill=fillColor] (394.78, 80.07) --
-	(397.29, 75.72) --
-	(392.26, 75.72) --
+\definecolor{fillColor}{RGB}{253,104,0}
+
+\path[fill=fillColor] (356.88,164.91) circle (  1.87);
+
+\path[fill=fillColor] (356.88, 79.47) --
+	(359.40, 75.11) --
+	(354.37, 75.11) --
 	cycle;
@@
 \node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
-\definecolor{fillColor}{RGB}{0,195,0}
-
-\path[fill=fillColor] (390.04,184.14) circle (  1.87);
-
-\path[fill=fillColor] (390.04, 69.81) --
-	(392.55, 65.46) --
-	(387.52, 65.46) --
+\definecolor{fillColor}{RGB}{143,161,0}
+
+\path[fill=fillColor] (394.78,165.18) circle (  1.87);
+
+\path[fill=fillColor] (394.78, 79.59) --
+	(397.29, 75.23) --
+	(392.26, 75.23) --
 	cycle;
@@
 \node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
-\definecolor{fillColor}{RGB}{0,219,171}
-
-\path[fill=fillColor] (404.25,211.12) circle (  1.87);
-
-\path[fill=fillColor] (404.25, 60.31) --
-	(406.77, 55.95) --
-	(401.74, 55.95) --
+\definecolor{fillColor}{RGB}{0,195,0}
+
+\path[fill=fillColor] (390.04,192.04) circle (  1.87);
+
+\path[fill=fillColor] (390.04, 71.74) --
+	(392.55, 67.38) --
+	(387.52, 67.38) --
 	cycle;
@@
 \node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
-\definecolor{fillColor}{RGB}{151,0,255}
-
-\path[fill=fillColor] (433.62,198.59) circle (  1.87);
-
-\path[fill=fillColor] (433.62, 71.59) --
-	(436.14, 67.23) --
-	(431.10, 67.23) --
+\definecolor{fillColor}{RGB}{0,219,171}
+
+\path[fill=fillColor] (404.25,216.71) circle (  1.87);
+
+\path[fill=fillColor] (404.25, 59.65) --
+	(406.77, 55.29) --
+	(401.74, 55.29) --
 	cycle;
@@
 \node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
-\definecolor{fillColor}{RGB}{255,0,255}
-
-\path[fill=fillColor] (359.72,131.32) circle (  1.87);
-
-\path[fill=fillColor] (359.72, 82.69) --
-	(362.24, 78.34) --
-	(357.21, 78.34) --
+\definecolor{fillColor}{RGB}{0,216,255}
+
+\path[fill=fillColor] (359.72,107.30) circle (  1.87);
+
+\path[fill=fillColor] (359.72, 91.05) --
+	(362.24, 86.70) --
+	(357.21, 86.70) --
 	cycle;
@@
 \node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
-\definecolor{fillColor}{RGB}{68,68,68}
-
-\path[fill=fillColor] (346.46,125.02) circle (  1.87);
-
-\path[fill=fillColor] (346.46, 77.24) --
-	(348.97, 72.89) --
-	(343.94, 72.89) --
+\definecolor{fillColor}{RGB}{151,0,255}
+
+\path[fill=fillColor] (433.62,204.25) circle (  1.87);
+
+\path[fill=fillColor] (433.62, 68.39) --
+	(436.14, 64.04) --
+	(431.10, 64.04) --
 	cycle;
@@
 \node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,113.13) --
-	(339.26,113.54) --
-	(339.64,113.94) --
-	(340.02,114.34) --
-	(340.40,114.75) --
-	(340.78,115.15) --
-	(341.16,115.56) --
-	(341.54,115.97) --
-	(341.92,116.38) --
-	(342.30,116.79) --
-	(342.68,117.20) --
-	(343.06,117.61) --
-	(343.44,118.03) --
-	(343.82,118.44) --
-	(344.20,118.86) --
-	(344.58,119.27) --
-	(344.96,119.69) --
-	(345.34,120.11) --
-	(345.71,120.53) --
-	(346.09,120.95) --
-	(346.47,121.37) --
-	(346.85,121.80) --
-	(347.23,122.22) --
-	(347.61,122.65) --
-	(347.99,123.07) --
-	(348.37,123.50) --
-	(348.75,123.93) --
-	(349.13,124.36) --
-	(349.51,124.79) --
-	(349.89,125.22) --
-	(350.27,125.65) --
-	(350.65,126.08) --
-	(351.03,126.51) --
-	(351.41,126.95) --
-	(351.79,127.38) --
-	(352.17,127.82) --
-	(352.55,128.25) --
-	(352.93,128.69) --
-	(353.31,129.13) --
-	(353.69,129.57) --
-	(354.07,130.01) --
-	(354.45,130.44) --
-	(354.83,130.88) --
-	(355.21,131.33) --
-	(355.59,131.77) --
-	(355.97,132.21) --
-	(356.35,132.65) --
-	(356.73,133.09) --
-	(357.11,133.54) --
-	(357.49,133.98) --
-	(357.87,134.43) --
-	(358.25,134.87) --
-	(358.63,135.32) --
-	(359.01,135.76) --
-	(359.38,136.21) --
-	(359.76,136.65) --
-	(360.14,137.10) --
-	(360.52,137.55) --
-	(360.90,137.99) --
-	(361.28,138.44) --
-	(361.66,138.89) --
-	(362.04,139.34) --
-	(362.42,139.79) --
-	(362.80,140.24) --
-	(363.18,140.68) --
-	(363.56,141.13) --
-	(363.94,141.58) --
-	(364.32,142.03) --
-	(364.70,142.48) --
-	(365.08,142.93) --
-	(365.46,143.38) --
-	(365.84,143.83) --
-	(366.22,144.28) --
-	(366.60,144.73) --
-	(366.98,145.18) --
-	(367.36,145.63) --
-	(367.74,146.08) --
-	(368.12,146.53) --
-	(368.50,146.98) --
-	(368.88,147.43) --
-	(369.26,147.88) --
-	(369.64,148.32) --
-	(370.02,148.77) --
-	(370.40,149.22) --
-	(370.78,149.67) --
-	(371.16,150.12) --
-	(371.54,150.57) --
-	(371.92,151.01) --
-	(372.30,151.46) --
-	(372.68,151.91) --
-	(373.05,152.36) --
-	(373.43,152.80) --
-	(373.81,153.25) --
-	(374.19,153.69) --
-	(374.57,154.14) --
-	(374.95,154.58) --
-	(375.33,155.03) --
-	(375.71,155.47) --
-	(376.09,155.92) --
-	(376.47,156.36) --
-	(376.85,156.80) --
-	(377.23,157.24) --
-	(377.61,157.68) --
-	(377.99,158.13) --
-	(378.37,158.57) --
-	(378.75,159.01) --
-	(379.13,159.44) --
-	(379.51,159.88) --
-	(379.89,160.32) --
-	(380.27,160.76) --
-	(380.65,161.19) --
-	(381.03,161.63) --
-	(381.41,162.06) --
-	(381.79,162.50) --
-	(382.17,162.93) --
-	(382.55,163.36) --
-	(382.93,163.79) --
-	(383.31,164.22) --
-	(383.69,164.65) --
-	(384.07,165.08) --
-	(384.45,165.51) --
-	(384.83,165.94) --
-	(385.21,166.36) --
-	(385.59,166.79) --
-	(385.97,167.21) --
-	(386.34,167.64) --
-	(386.72,168.06) --
-	(387.10,168.48) --
-	(387.48,168.90) --
-	(387.86,169.32) --
-	(388.24,169.74) --
-	(388.62,170.16) --
-	(389.00,170.57) --
-	(389.38,170.99) --
-	(389.76,171.40) --
-	(390.14,171.82) --
-	(390.52,172.23) --
-	(390.90,172.64) --
-	(391.28,173.05) --
-	(391.66,173.46) --
-	(392.04,173.86) --
-	(392.42,174.27) --
-	(392.80,174.67) --
-	(393.18,175.08) --
-	(393.56,175.48) --
-	(393.94,175.88) --
-	(394.32,176.28) --
-	(394.70,176.68) --
-	(395.08,177.08) --
-	(395.46,177.47) --
-	(395.84,177.87) --
-	(396.22,178.26) --
-	(396.60,178.65) --
-	(396.98,179.04) --
-	(397.36,179.43) --
-	(397.74,179.82) --
-	(398.12,180.21) --
-	(398.50,180.59) --
-	(398.88,180.98) --
-	(399.26,181.36) --
-	(399.64,181.74) --
-	(400.01,182.12) --
-	(400.39,182.50) --
-	(400.77,182.88) --
-	(401.15,183.25) --
-	(401.53,183.62) --
-	(401.91,184.00) --
-	(402.29,184.37) --
-	(402.67,184.74) --
-	(403.05,185.11) --
-	(403.43,185.47) --
-	(403.81,185.84) --
-	(404.19,186.20) --
-	(404.57,186.56) --
-	(404.95,186.92) --
-	(405.33,187.28) --
-	(405.71,187.64) --
-	(406.09,188.00) --
-	(406.47,188.35) --
-	(406.85,188.70) --
-	(407.23,189.05) --
-	(407.61,189.40) --
-	(407.99,189.75) --
-	(408.37,190.10) --
-	(408.75,190.44) --
-	(409.13,190.79) --
-	(409.51,191.13) --
-	(409.89,191.47) --
-	(410.27,191.81) --
-	(410.65,192.14) --
-	(411.03,192.48) --
-	(411.41,192.81) --
-	(411.79,193.14) --
-	(412.17,193.48) --
-	(412.55,193.80) --
-	(412.93,194.13) --
-	(413.31,194.46) --
-	(413.68,194.78) --
-	(414.06,195.10) --
-	(414.44,195.42) --
-	(414.82,195.74) --
-	(415.20,196.06) --
-	(415.58,196.38) --
-	(415.96,196.69) --
-	(416.34,197.00) --
-	(416.72,197.31) --
-	(417.10,197.62) --
-	(417.48,197.93) --
-	(417.86,198.24) --
-	(418.24,198.54) --
-	(418.62,198.84) --
-	(419.00,199.15) --
-	(419.38,199.45) --
-	(419.76,199.74) --
-	(420.14,200.04) --
-	(420.52,200.33) --
-	(420.90,200.63) --
-	(421.28,200.92) --
-	(421.66,201.21) --
-	(422.04,201.50) --
-	(422.42,201.78) --
-	(422.80,202.07) --
-	(423.18,202.35) --
-	(423.56,202.63) --
-	(423.94,202.91) --
-	(424.32,203.19) --
-	(424.70,203.47) --
-	(425.08,203.74) --
-	(425.46,204.01) --
-	(425.84,204.29) --
-	(426.22,204.56) --
-	(426.60,204.82) --
-	(426.97,205.09) --
-	(427.35,205.36) --
-	(427.73,205.62) --
-	(428.11,205.88) --
-	(428.49,206.14) --
-	(428.87,206.40) --
-	(429.25,206.66) --
-	(429.63,206.91) --
-	(430.01,207.17) --
-	(430.39,207.42) --
-	(430.77,207.67) --
-	(431.15,207.92) --
-	(431.53,208.17) --
-	(431.91,208.41) --
-	(432.29,208.66) --
-	(432.67,208.90) --
-	(433.05,209.14) --
-	(433.43,209.38) --
-	(433.81,209.62) --
-	(434.19,209.86) --
-	(434.57,210.09) --
-	(434.95,210.33) --
-	(435.33,210.56) --
-	(435.71,210.79) --
-	(436.09,211.02) --
-	(436.47,211.25) --
-	(436.85,211.47) --
-	(437.23,211.70) --
-	(437.61,211.92) --
-	(437.99,212.14) --
-	(438.37,212.36) --
-	(438.75,212.58) --
-	(439.13,212.80) --
-	(439.51,213.01) --
-	(439.89,213.23) --
-	(440.27,213.44) --
-	(440.64,213.65) --
-	(441.02,213.86) --
-	(441.40,214.07) --
-	(441.78,214.27) --
-	(442.16,214.48) --
-	(442.54,214.68) --
-	(442.92,214.89) --
-	(443.30,215.09) --
-	(443.68,215.29) --
-	(444.06,215.48) --
-	(444.44,215.68) --
-	(444.82,215.88) --
-	(445.20,216.07) --
-	(445.58,216.26) --
-	(445.96,216.45) --
-	(446.34,216.64) --
-	(446.72,216.83) --
-	(447.10,217.02) --
-	(447.48,217.21) --
-	(447.86,217.39) --
-	(448.24,217.57) --
-	(448.62,217.76) --
-	(449.00,217.94) --
-	(449.38,218.11) --
-	(449.76,218.29) --
-	(450.14,218.47) --
-	(450.52,218.64) --
-	(450.90,218.82) --
-	(451.28,218.99) --
-	(451.66,219.16) --
-	(452.04,219.33) --
-	(452.42,219.50) --
-	(452.80,219.67) --
-	(453.18,219.84) --
-	(453.56,220.00) --
-	(453.93,220.16) --
-	(454.31,220.33) --
-	(454.69,220.49) --
-	(455.07,220.65) --
-	(455.45,220.81) --
-	(455.83,220.96) --
-	(456.21,221.12) --
-	(456.59,221.28) --
-	(456.97,221.43) --
-	(457.35,221.58) --
-	(457.73,221.73) --
-	(458.11,221.89) --
-	(458.49,222.03) --
-	(458.87,222.18) --
-	(459.25,222.33) --
-	(459.63,222.48) --
-	(460.01,222.62) --
-	(460.39,222.76) --
-	(460.77,222.91) --
-	(461.15,223.05) --
-	(461.53,223.19) --
-	(461.91,223.33) --
-	(462.29,223.47) --
-	(462.67,223.60) --
-	(463.05,223.74) --
-	(463.43,223.87) --
-	(463.81,224.01) --
-	(464.19,224.14) --
-	(464.57,224.27) --
-	(464.95,224.40) --
-	(465.33,224.53) --
-	(465.71,224.66) --
-	(466.09,224.79) --
-	(466.47,224.92) --
-	(466.85,225.04) --
-	(467.23,225.17) --
-	(467.60,225.29) --
-	(467.98,225.41) --
-	(468.36,225.53) --
-	(468.74,225.65) --
-	(469.12,225.77) --
-	(469.50,225.89) --
-	(469.88,226.01) --
-	(470.26,226.13) --
-	(470.64,226.24) --
-	(471.02,226.36) --
-	(471.40,226.47) --
-	(471.78,226.58) --
-	(472.16,226.70) --
-	(472.54,226.81) --
-	(472.92,226.92) --
-	(473.30,227.03) --
-	(473.68,227.13) --
-	(474.06,227.24) --
-	(474.44,227.35) --
-	(474.82,227.45) --
-	(475.20,227.56) --
-	(475.58,227.66) --
-	(475.96,227.77) --
-	(476.34,227.87) --
-	(476.72,227.97) --
-	(477.10,228.07) --
-	(477.48,228.17) --
-	(477.86,228.27) --
-	(478.24,228.37) --
-	(478.62,228.46) --
-	(479.00,228.56) --
-	(479.38,228.66) --
-	(479.76,228.75) --
-	(480.14,228.84) --
-	(480.52,228.94) --
-	(480.90,229.03) --
-	(481.27,229.12) --
-	(481.65,229.21) --
-	(482.03,229.30) --
-	(482.41,229.39) --
-	(482.79,229.48) --
-	(483.17,229.57) --
-	(483.55,229.66) --
-	(483.93,229.74) --
-	(484.31,229.83) --
-	(484.69,229.91) --
-	(485.07,230.00) --
-	(485.45,230.08) --
-	(485.83,230.16) --
-	(486.21,230.24) --
-	(486.59,230.33) --
-	(486.97,230.41) --
-	(487.35,230.49) --
-	(487.73,230.57) --
-	(488.11,230.64) --
-	(488.49,230.72) --
-	(488.87,230.80) --
-	(489.25,230.88) --
-	(489.63,230.95) --
-	(490.01,231.03) --
-	(490.39,231.10) --
-	(490.77,231.18) --
-	(491.15,231.25) --
-	(491.53,231.32) --
-	(491.91,231.39) --
-	(492.29,231.47) --
-	(492.67,231.54) --
-	(493.05,231.61) --
-	(493.43,231.68) --
-	(493.81,231.75) --
-	(494.19,231.81) --
-	(494.56,231.88) --
-	(494.94,231.95) --
-	(495.32,232.02) --
-	(495.70,232.08) --
-	(496.08,232.15) --
-	(496.46,232.21) --
-	(496.84,232.28) --
-	(497.22,232.34) --
-	(497.60,232.40) --
-	(497.98,232.47) --
-	(498.36,232.53) --
-	(498.74,232.59) --
-	(499.12,232.65) --
-	(499.50,232.71) --
-	(499.88,232.77) --
-	(500.26,232.83) --
-	(500.64,232.89) --
-	(501.02,232.95) --
-	(501.40,233.01) --
-	(501.78,233.06) --
-	(502.16,233.12) --
-	(502.54,233.18) --
-	(502.92,233.23) --
-	(503.30,233.29) --
-	(503.68,233.34) --
-	(504.06,233.40) --
-	(504.44,233.45) --
-	(504.82,233.50) --
-	(505.20,233.56) --
-	(505.58,233.61) --
-	(505.96,233.66) --
-	(506.34,233.71) --
-	(506.72,233.76) --
-	(507.10,233.81) --
-	(507.48,233.86) --
-	(507.86,233.91) --
-	(508.23,233.96) --
-	(508.61,234.01) --
-	(508.99,234.06) --
-	(509.37,234.11) --
-	(509.75,234.16) --
-	(510.13,234.20) --
-	(510.51,234.25) --
-	(510.89,234.30) --
-	(511.27,234.34) --
-	(511.65,234.39) --
-	(512.03,234.43) --
-	(512.41,234.48) --
-	(512.79,234.52) --
-	(513.17,234.56) --
-	(513.55,234.61) --
-	(513.93,234.65) --
-	(514.31,234.69) --
-	(514.69,234.74) --
-	(515.07,234.78) --
-	(515.45,234.82) --
-	(515.83,234.86) --
-	(516.21,234.90) --
-	(516.59,234.94) --
-	(516.97,234.98) --
-	(517.35,235.02) --
-	(517.73,235.06) --
-	(518.11,235.10) --
-	(518.49,235.14) --
-	(518.87,235.18) --
-	(519.25,235.22) --
-	(519.63,235.25) --
-	(520.01,235.29) --
-	(520.39,235.33) --
-	(520.77,235.36) --
-	(521.15,235.40) --
-	(521.53,235.44) --
-	(521.90,235.47) --
-	(522.28,235.51) --
-	(522.66,235.54) --
-	(523.04,235.58) --
-	(523.42,235.61) --
-	(523.80,235.64) --
-	(524.18,235.68) --
-	(524.56,235.71) --
-	(524.94,235.74) --
-	(525.32,235.78) --
-	(525.70,235.81) --
-	(526.08,235.84) --
-	(526.46,235.87) --
-	(526.84,235.91) --
-	(527.22,235.94) --
-	(527.60,235.97) --
-	(527.98,236.00) --
-	(528.36,236.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 82.52) --
-	(339.26, 82.40) --
-	(339.64, 82.27) --
-	(340.02, 82.15) --
-	(340.40, 82.02) --
-	(340.78, 81.90) --
-	(341.16, 81.77) --
-	(341.54, 81.65) --
-	(341.92, 81.53) --
-	(342.30, 81.40) --
-	(342.68, 81.28) --
-	(343.06, 81.16) --
-	(343.44, 81.04) --
-	(343.82, 80.92) --
-	(344.20, 80.80) --
-	(344.58, 80.68) --
-	(344.96, 80.56) --
-	(345.34, 80.44) --
-	(345.71, 80.32) --
-	(346.09, 80.20) --
-	(346.47, 80.08) --
-	(346.85, 79.96) --
-	(347.23, 79.84) --
-	(347.61, 79.73) --
-	(347.99, 79.61) --
-	(348.37, 79.49) --
-	(348.75, 79.37) --
-	(349.13, 79.26) --
-	(349.51, 79.14) --
-	(349.89, 79.03) --
-	(350.27, 78.91) --
-	(350.65, 78.80) --
-	(351.03, 78.68) --
-	(351.41, 78.57) --
-	(351.79, 78.46) --
-	(352.17, 78.34) --
-	(352.55, 78.23) --
-	(352.93, 78.12) --
-	(353.31, 78.01) --
-	(353.69, 77.90) --
-	(354.07, 77.78) --
-	(354.45, 77.67) --
-	(354.83, 77.56) --
-	(355.21, 77.45) --
-	(355.59, 77.34) --
-	(355.97, 77.23) --
-	(356.35, 77.12) --
-	(356.73, 77.02) --
-	(357.11, 76.91) --
-	(357.49, 76.80) --
-	(357.87, 76.69) --
-	(358.25, 76.58) --
-	(358.63, 76.48) --
-	(359.01, 76.37) --
-	(359.38, 76.26) --
-	(359.76, 76.16) --
-	(360.14, 76.05) --
-	(360.52, 75.95) --
-	(360.90, 75.84) --
-	(361.28, 75.74) --
-	(361.66, 75.63) --
-	(362.04, 75.53) --
-	(362.42, 75.43) --
-	(362.80, 75.32) --
-	(363.18, 75.22) --
-	(363.56, 75.12) --
-	(363.94, 75.02) --
-	(364.32, 74.92) --
-	(364.70, 74.81) --
-	(365.08, 74.71) --
-	(365.46, 74.61) --
-	(365.84, 74.51) --
-	(366.22, 74.41) --
-	(366.60, 74.31) --
-	(366.98, 74.21) --
-	(367.36, 74.12) --
-	(367.74, 74.02) --
-	(368.12, 73.92) --
-	(368.50, 73.82) --
-	(368.88, 73.72) --
-	(369.26, 73.63) --
-	(369.64, 73.53) --
-	(370.02, 73.43) --
-	(370.40, 73.34) --
-	(370.78, 73.24) --
-	(371.16, 73.15) --
-	(371.54, 73.05) --
-	(371.92, 72.96) --
-	(372.30, 72.86) --
-	(372.68, 72.77) --
-	(373.05, 72.67) --
-	(373.43, 72.58) --
-	(373.81, 72.49) --
-	(374.19, 72.39) --
-	(374.57, 72.30) --
-	(374.95, 72.21) --
-	(375.33, 72.12) --
-	(375.71, 72.03) --
-	(376.09, 71.93) --
-	(376.47, 71.84) --
-	(376.85, 71.75) --
-	(377.23, 71.66) --
-	(377.61, 71.57) --
-	(377.99, 71.48) --
-	(378.37, 71.39) --
-	(378.75, 71.30) --
-	(379.13, 71.22) --
-	(379.51, 71.13) --
-	(379.89, 71.04) --
-	(380.27, 70.95) --
-	(380.65, 70.86) --
-	(381.03, 70.78) --
-	(381.41, 70.69) --
-	(381.79, 70.60) --
-	(382.17, 70.52) --
-	(382.55, 70.43) --
-	(382.93, 70.35) --
-	(383.31, 70.26) --
-	(383.69, 70.18) --
-	(384.07, 70.09) --
-	(384.45, 70.01) --
-	(384.83, 69.92) --
-	(385.21, 69.84) --
-	(385.59, 69.76) --
-	(385.97, 69.67) --
-	(386.34, 69.59) --
-	(386.72, 69.51) --
-	(387.10, 69.43) --
-	(387.48, 69.35) --
-	(387.86, 69.26) --
-	(388.24, 69.18) --
-	(388.62, 69.10) --
-	(389.00, 69.02) --
-	(389.38, 68.94) --
-	(389.76, 68.86) --
-	(390.14, 68.78) --
-	(390.52, 68.70) --
-	(390.90, 68.62) --
-	(391.28, 68.54) --
-	(391.66, 68.47) --
-	(392.04, 68.39) --
-	(392.42, 68.31) --
-	(392.80, 68.23) --
-	(393.18, 68.15) --
-	(393.56, 68.08) --
-	(393.94, 68.00) --
-	(394.32, 67.92) --
-	(394.70, 67.85) --
-	(395.08, 67.77) --
-	(395.46, 67.70) --
-	(395.84, 67.62) --
-	(396.22, 67.55) --
-	(396.60, 67.47) --
-	(396.98, 67.40) --
-	(397.36, 67.32) --
-	(397.74, 67.25) --
-	(398.12, 67.18) --
-	(398.50, 67.10) --
-	(398.88, 67.03) --
-	(399.26, 66.96) --
-	(399.64, 66.88) --
-	(400.01, 66.81) --
-	(400.39, 66.74) --
-	(400.77, 66.67) --
-	(401.15, 66.60) --
-	(401.53, 66.53) --
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (338.88,114.47) --
+	(339.26,114.92) --
+	(339.64,115.37) --
+	(340.02,115.83) --
+	(340.40,116.28) --
+	(340.78,116.74) --
+	(341.16,117.20) --
+	(341.54,117.66) --
+	(341.92,118.12) --
+	(342.30,118.58) --
+	(342.68,119.05) --
+	(343.06,119.51) --
+	(343.44,119.98) --
+	(343.82,120.45) --
+	(344.20,120.92) --
+	(344.58,121.39) --
+	(344.96,121.86) --
+	(345.34,122.34) --
+	(345.71,122.81) --
+	(346.09,123.29) --
+	(346.47,123.76) --
+	(346.85,124.24) --
+	(347.23,124.72) --
+	(347.61,125.20) --
+	(347.99,125.68) --
+	(348.37,126.16) --
+	(348.75,126.65) --
+	(349.13,127.13) --
+	(349.51,127.62) --
+	(349.89,128.10) --
+	(350.27,128.59) --
+	(350.65,129.08) --
+	(351.03,129.56) --
+	(351.41,130.05) --
+	(351.79,130.54) --
+	(352.17,131.03) --
+	(352.55,131.53) --
+	(352.93,132.02) --
+	(353.31,132.51) --
+	(353.69,133.01) --
+	(354.07,133.50) --
+	(354.45,133.99) --
+	(354.83,134.49) --
+	(355.21,134.99) --
+	(355.59,135.48) --
+	(355.97,135.98) --
+	(356.35,136.48) --
+	(356.73,136.98) --
+	(357.11,137.47) --
+	(357.49,137.97) --
+	(357.87,138.47) --
+	(358.25,138.97) --
+	(358.63,139.47) --
+	(359.01,139.97) --
+	(359.38,140.47) --
+	(359.76,140.97) --
+	(360.14,141.47) --
+	(360.52,141.98) --
+	(360.90,142.48) --
+	(361.28,142.98) --
+	(361.66,143.48) --
+	(362.04,143.98) --
+	(362.42,144.48) --
+	(362.80,144.98) --
+	(363.18,145.49) --
+	(363.56,145.99) --
+	(363.94,146.49) --
+	(364.32,146.99) --
+	(364.70,147.49) --
+	(365.08,147.99) --
+	(365.46,148.49) --
+	(365.84,148.99) --
+	(366.22,149.49) --
+	(366.60,149.99) --
+	(366.98,150.49) --
+	(367.36,150.99) --
+	(367.74,151.49) --
+	(368.12,151.99) --
+	(368.50,152.49) --
+	(368.88,152.99) --
+	(369.26,153.48) --
+	(369.64,153.98) --
+	(370.02,154.48) --
+	(370.40,154.97) --
+	(370.78,155.47) --
+	(371.16,155.96) --
+	(371.54,156.45) --
+	(371.92,156.95) --
+	(372.30,157.44) --
+	(372.68,157.93) --
+	(373.05,158.42) --
+	(373.43,158.91) --
+	(373.81,159.40) --
+	(374.19,159.89) --
+	(374.57,160.38) --
+	(374.95,160.87) --
+	(375.33,161.35) --
+	(375.71,161.84) --
+	(376.09,162.32) --
+	(376.47,162.81) --
+	(376.85,163.29) --
+	(377.23,163.77) --
+	(377.61,164.25) --
+	(377.99,164.73) --
+	(378.37,165.21) --
+	(378.75,165.68) --
+	(379.13,166.16) --
+	(379.51,166.64) --
+	(379.89,167.11) --
+	(380.27,167.58) --
+	(380.65,168.05) --
+	(381.03,168.52) --
+	(381.41,168.99) --
+	(381.79,169.46) --
+	(382.17,169.92) --
+	(382.55,170.39) --
+	(382.93,170.85) --
+	(383.31,171.32) --
+	(383.69,171.78) --
+	(384.07,172.24) --
+	(384.45,172.69) --
+	(384.83,173.15) --
+	(385.21,173.60) --
+	(385.59,174.06) --
+	(385.97,174.51) --
+	(386.34,174.96) --
+	(386.72,175.41) --
+	(387.10,175.86) --
+	(387.48,176.30) --
+	(387.86,176.75) --
+	(388.24,177.19) --
+	(388.62,177.63) --
+	(389.00,178.07) --
+	(389.38,178.51) --
+	(389.76,178.94) --
+	(390.14,179.38) --
+	(390.52,179.81) --
+	(390.90,180.24) --
+	(391.28,180.67) --
+	(391.66,181.10) --
+	(392.04,181.53) --
+	(392.42,181.95) --
+	(392.80,182.37) --
+	(393.18,182.79) --
+	(393.56,183.21) --
+	(393.94,183.63) --
+	(394.32,184.04) --
+	(394.70,184.46) --
+	(395.08,184.87) --
+	(395.46,185.28) --
+	(395.84,185.69) --
+	(396.22,186.09) --
+	(396.60,186.50) --
+	(396.98,186.90) --
+	(397.36,187.30) --
+	(397.74,187.70) --
+	(398.12,188.09) --
+	(398.50,188.49) --
+	(398.88,188.88) --
+	(399.26,189.27) --
+	(399.64,189.66) --
+	(400.01,190.05) --
+	(400.39,190.43) --
+	(400.77,190.82) --
+	(401.15,191.20) --
+	(401.53,191.57) --
+	(401.91,191.95) --
+	(402.29,192.33) --
+	(402.67,192.70) --
+	(403.05,193.07) --
+	(403.43,193.44) --
+	(403.81,193.81) --
+	(404.19,194.17) --
+	(404.57,194.53) --
+	(404.95,194.89) --
+	(405.33,195.25) --
+	(405.71,195.61) --
+	(406.09,195.97) --
+	(406.47,196.32) --
+	(406.85,196.67) --
+	(407.23,197.02) --
+	(407.61,197.36) --
+	(407.99,197.71) --
+	(408.37,198.05) --
+	(408.75,198.39) --
+	(409.13,198.73) --
+	(409.51,199.07) --
+	(409.89,199.40) --
+	(410.27,199.73) --
+	(410.65,200.06) --
+	(411.03,200.39) --
+	(411.41,200.72) --
+	(411.79,201.04) --
+	(412.17,201.36) --
+	(412.55,201.68) --
+	(412.93,202.00) --
+	(413.31,202.32) --
+	(413.68,202.63) --
+	(414.06,202.94) --
+	(414.44,203.25) --
+	(414.82,203.56) --
+	(415.20,203.87) --
+	(415.58,204.17) --
+	(415.96,204.47) --
+	(416.34,204.77) --
+	(416.72,205.07) --
+	(417.10,205.37) --
+	(417.48,205.66) --
+	(417.86,205.95) --
+	(418.24,206.24) --
+	(418.62,206.53) --
+	(419.00,206.82) --
+	(419.38,207.10) --
+	(419.76,207.38) --
+	(420.14,207.66) --
+	(420.52,207.94) --
+	(420.90,208.21) --
+	(421.28,208.49) --
+	(421.66,208.76) --
+	(422.04,209.03) --
+	(422.42,209.30) --
+	(422.80,209.57) --
+	(423.18,209.83) --
+	(423.56,210.09) --
+	(423.94,210.35) --
+	(424.32,210.61) --
+	(424.70,210.87) --
+	(425.08,211.12) --
+	(425.46,211.37) --
+	(425.84,211.63) --
+	(426.22,211.87) --
+	(426.60,212.12) --
+	(426.97,212.37) --
+	(427.35,212.61) --
+	(427.73,212.85) --
+	(428.11,213.09) --
+	(428.49,213.33) --
+	(428.87,213.57) --
+	(429.25,213.80) --
+	(429.63,214.03) --
+	(430.01,214.26) --
+	(430.39,214.49) --
+	(430.77,214.72) --
+	(431.15,214.95) --
+	(431.53,215.17) --
+	(431.91,215.39) --
+	(432.29,215.61) --
+	(432.67,215.83) --
+	(433.05,216.05) --
+	(433.43,216.26) --
+	(433.81,216.47) --
+	(434.19,216.69) --
+	(434.57,216.90) --
+	(434.95,217.10) --
+	(435.33,217.31) --
+	(435.71,217.52) --
+	(436.09,217.72) --
+	(436.47,217.92) --
+	(436.85,218.12) --
+	(437.23,218.32) --
+	(437.61,218.51) --
+	(437.99,218.71) --
+	(438.37,218.90) --
+	(438.75,219.09) --
+	(439.13,219.28) --
+	(439.51,219.47) --
+	(439.89,219.66) --
+	(440.27,219.85) --
+	(440.64,220.03) --
+	(441.02,220.21) --
+	(441.40,220.39) --
+	(441.78,220.57) --
+	(442.16,220.75) --
+	(442.54,220.93) --
+	(442.92,221.10) --
+	(443.30,221.27) --
+	(443.68,221.45) --
+	(444.06,221.62) --
+	(444.44,221.78) --
+	(444.82,221.95) --
+	(445.20,222.12) --
+	(445.58,222.28) --
+	(445.96,222.45) --
+	(446.34,222.61) --
+	(446.72,222.77) --
+	(447.10,222.93) --
+	(447.48,223.08) --
+	(447.86,223.24) --
+	(448.24,223.40) --
+	(448.62,223.55) --
+	(449.00,223.70) --
+	(449.38,223.85) --
+	(449.76,224.00) --
+	(450.14,224.15) --
+	(450.52,224.30) --
+	(450.90,224.44) --
+	(451.28,224.58) --
+	(451.66,224.73) --
+	(452.04,224.87) --
+	(452.42,225.01) --
+	(452.80,225.15) --
+	(453.18,225.29) --
+	(453.56,225.42) --
+	(453.93,225.56) --
+	(454.31,225.69) --
+	(454.69,225.83) --
+	(455.07,225.96) --
+	(455.45,226.09) --
+	(455.83,226.22) --
+	(456.21,226.35) --
+	(456.59,226.47) --
+	(456.97,226.60) --
+	(457.35,226.72) --
+	(457.73,226.85) --
+	(458.11,226.97) --
+	(458.49,227.09) --
+	(458.87,227.21) --
+	(459.25,227.33) --
+	(459.63,227.45) --
+	(460.01,227.56) --
+	(460.39,227.68) --
+	(460.77,227.79) --
+	(461.15,227.91) --
+	(461.53,228.02) --
+	(461.91,228.13) --
+	(462.29,228.24) --
+	(462.67,228.35) --
+	(463.05,228.46) --
+	(463.43,228.57) --
+	(463.81,228.68) --
+	(464.19,228.78) --
+	(464.57,228.89) --
+	(464.95,228.99) --
+	(465.33,229.09) --
+	(465.71,229.19) --
+	(466.09,229.29) --
+	(466.47,229.39) --
+	(466.85,229.49) --
+	(467.23,229.59) --
+	(467.60,229.69) --
+	(467.98,229.78) --
+	(468.36,229.88) --
+	(468.74,229.97) --
+	(469.12,230.07) --
+	(469.50,230.16) --
+	(469.88,230.25) --
+	(470.26,230.34) --
+	(470.64,230.43) --
+	(471.02,230.52) --
+	(471.40,230.61) --
+	(471.78,230.69) --
+	(472.16,230.78) --
+	(472.54,230.87) --
+	(472.92,230.95) --
+	(473.30,231.03) --
+	(473.68,231.12) --
+	(474.06,231.20) --
+	(474.44,231.28) --
+	(474.82,231.36) --
+	(475.20,231.44) --
+	(475.58,231.52) --
+	(475.96,231.60) --
+	(476.34,231.68) --
+	(476.72,231.75) --
+	(477.10,231.83) --
+	(477.48,231.91) --
+	(477.86,231.98) --
+	(478.24,232.05) --
+	(478.62,232.13) --
+	(479.00,232.20) --
+	(479.38,232.27) --
+	(479.76,232.34) --
+	(480.14,232.41) --
+	(480.52,232.48) --
+	(480.90,232.55) --
+	(481.27,232.62) --
+	(481.65,232.69) --
+	(482.03,232.75) --
+	(482.41,232.82) --
+	(482.79,232.89) --
+	(483.17,232.95) --
+	(483.55,233.02) --
+	(483.93,233.08) --
+	(484.31,233.14) --
+	(484.69,233.21) --
+	(485.07,233.27) --
+	(485.45,233.33) --
+	(485.83,233.39) --
+	(486.21,233.45) --
+	(486.59,233.51) --
+	(486.97,233.57) --
+	(487.35,233.63) --
+	(487.73,233.68) --
+	(488.11,233.74) --
+	(488.49,233.80) --
+	(488.87,233.85) --
+	(489.25,233.91) --
+	(489.63,233.96) --
+	(490.01,234.02) --
+	(490.39,234.07) --
+	(490.77,234.13) --
+	(491.15,234.18) --
+	(491.53,234.23) --
+	(491.91,234.28) --
+	(492.29,234.33) --
+	(492.67,234.39) --
+	(493.05,234.44) --
+	(493.43,234.49) --
+	(493.81,234.53) --
+	(494.19,234.58) --
+	(494.56,234.63) --
+	(494.94,234.68) --
+	(495.32,234.73) --
+	(495.70,234.77) --
+	(496.08,234.82) --
+	(496.46,234.87) --
+	(496.84,234.91) --
+	(497.22,234.96) --
+	(497.60,235.00) --
+	(497.98,235.04) --
+	(498.36,235.09) --
+	(498.74,235.13) --
+	(499.12,235.17) --
+	(499.50,235.22) --
+	(499.88,235.26) --
+	(500.26,235.30) --
+	(500.64,235.34) --
+	(501.02,235.38) --
+	(501.40,235.42) --
+	(501.78,235.46) --
+	(502.16,235.50) --
+	(502.54,235.54) --
+	(502.92,235.58) --
+	(503.30,235.62) --
+	(503.68,235.65) --
+	(504.06,235.69) --
+	(504.44,235.73) --
+	(504.82,235.77) --
+	(505.20,235.80) --
+	(505.58,235.84) --
+	(505.96,235.87) --
+	(506.34,235.91) --
+	(506.72,235.94) --
+	(507.10,235.98) --
+	(507.48,236.01) --
+	(507.86,236.05) --
+	(508.23,236.08) --
+	(508.61,236.11) --
+	(508.99,236.15) --
+	(509.37,236.18) --
+	(509.75,236.21) --
+	(510.13,236.24) --
+	(510.51,236.27) --
+	(510.89,236.30) --
+	(511.27,236.34) --
+	(511.65,236.37) --
+	(512.03,236.40) --
+	(512.41,236.43) --
+	(512.79,236.46) --
+	(513.17,236.49) --
+	(513.55,236.51) --
+	(513.93,236.54) --
+	(514.31,236.57) --
+	(514.69,236.60) --
+	(515.07,236.63) --
+	(515.45,236.65) --
+	(515.83,236.68) --
+	(516.21,236.71) --
+	(516.59,236.74) --
+	(516.97,236.76) --
+	(517.35,236.79) --
+	(517.73,236.81) --
+	(518.11,236.84) --
+	(518.49,236.87) --
+	(518.87,236.89) --
+	(519.25,236.92) --
+	(519.63,236.94) --
+	(520.01,236.96) --
+	(520.39,236.99) --
+	(520.77,237.01) --
+	(521.15,237.04) --
+	(521.53,237.06) --
+	(521.90,237.08) --
+	(522.28,237.11) --
+	(522.66,237.13) --
+	(523.04,237.15) --
+	(523.42,237.17) --
+	(523.80,237.19) --
+	(524.18,237.22) --
+	(524.56,237.24) --
+	(524.94,237.26) --
+	(525.32,237.28) --
+	(525.70,237.30) --
+	(526.08,237.32) --
+	(526.46,237.34) --
+	(526.84,237.36) --
+	(527.22,237.38) --
+	(527.60,237.40) --
+	(527.98,237.42) --
+	(528.36,237.44);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (338.88, 93.87) --
+	(339.26, 93.64) --
+	(339.64, 93.40) --
+	(340.02, 93.17) --
+	(340.40, 92.94) --
+	(340.78, 92.71) --
+	(341.16, 92.48) --
+	(341.54, 92.26) --
+	(341.92, 92.03) --
+	(342.30, 91.80) --
+	(342.68, 91.58) --
+	(343.06, 91.35) --
+	(343.44, 91.13) --
+	(343.82, 90.91) --
+	(344.20, 90.69) --
+	(344.58, 90.46) --
+	(344.96, 90.24) --
+	(345.34, 90.02) --
+	(345.71, 89.81) --
+	(346.09, 89.59) --
+	(346.47, 89.37) --
+	(346.85, 89.16) --
+	(347.23, 88.94) --
+	(347.61, 88.73) --
+	(347.99, 88.51) --
+	(348.37, 88.30) --
+	(348.75, 88.09) --
+	(349.13, 87.88) --
+	(349.51, 87.67) --
+	(349.89, 87.46) --
+	(350.27, 87.25) --
+	(350.65, 87.05) --
+	(351.03, 86.84) --
+	(351.41, 86.64) --
+	(351.79, 86.43) --
+	(352.17, 86.23) --
+	(352.55, 86.02) --
+	(352.93, 85.82) --
+	(353.31, 85.62) --
+	(353.69, 85.42) --
+	(354.07, 85.22) --
+	(354.45, 85.02) --
+	(354.83, 84.83) --
+	(355.21, 84.63) --
+	(355.59, 84.43) --
+	(355.97, 84.24) --
+	(356.35, 84.04) --
+	(356.73, 83.85) --
+	(357.11, 83.66) --
+	(357.49, 83.47) --
+	(357.87, 83.28) --
+	(358.25, 83.09) --
+	(358.63, 82.90) --
+	(359.01, 82.71) --
+	(359.38, 82.52) --
+	(359.76, 82.33) --
+	(360.14, 82.15) --
+	(360.52, 81.96) --
+	(360.90, 81.78) --
+	(361.28, 81.60) --
+	(361.66, 81.41) --
+	(362.04, 81.23) --
+	(362.42, 81.05) --
+	(362.80, 80.87) --
+	(363.18, 80.69) --
+	(363.56, 80.52) --
+	(363.94, 80.34) --
+	(364.32, 80.16) --
+	(364.70, 79.99) --
+	(365.08, 79.81) --
+	(365.46, 79.64) --
+	(365.84, 79.46) --
+	(366.22, 79.29) --
+	(366.60, 79.12) --
+	(366.98, 78.95) --
+	(367.36, 78.78) --
+	(367.74, 78.61) --
+	(368.12, 78.44) --
+	(368.50, 78.27) --
+	(368.88, 78.11) --
+	(369.26, 77.94) --
+	(369.64, 77.78) --
+	(370.02, 77.61) --
+	(370.40, 77.45) --
+	(370.78, 77.29) --
+	(371.16, 77.13) --
+	(371.54, 76.96) --
+	(371.92, 76.80) --
+	(372.30, 76.64) --
+	(372.68, 76.49) --
+	(373.05, 76.33) --
+	(373.43, 76.17) --
+	(373.81, 76.01) --
+	(374.19, 75.86) --
+	(374.57, 75.70) --
+	(374.95, 75.55) --
+	(375.33, 75.40) --
+	(375.71, 75.24) --
+	(376.09, 75.09) --
+	(376.47, 74.94) --
+	(376.85, 74.79) --
+	(377.23, 74.64) --
+	(377.61, 74.49) --
+	(377.99, 74.34) --
+	(378.37, 74.20) --
+	(378.75, 74.05) --
+	(379.13, 73.91) --
+	(379.51, 73.76) --
+	(379.89, 73.62) --
+	(380.27, 73.47) --
+	(380.65, 73.33) --
+	(381.03, 73.19) --
+	(381.41, 73.05) --
+	(381.79, 72.91) --
+	(382.17, 72.77) --
+	(382.55, 72.63) --
+	(382.93, 72.49) --
+	(383.31, 72.35) --
+	(383.69, 72.22) --
+	(384.07, 72.08) --
+	(384.45, 71.94) --
+	(384.83, 71.81) --
+	(385.21, 71.68) --
+	(385.59, 71.54) --
+	(385.97, 71.41) --
+	(386.34, 71.28) --
+	(386.72, 71.15) --
+	(387.10, 71.02) --
+	(387.48, 70.89) --
+	(387.86, 70.76) --
+	(388.24, 70.63) --
+	(388.62, 70.50) --
+	(389.00, 70.37) --
+	(389.38, 70.25) --
+	(389.76, 70.12) --
+	(390.14, 70.00) --
+	(390.52, 69.87) --
+	(390.90, 69.75) --
+	(391.28, 69.63) --
+	(391.66, 69.50) --
+	(392.04, 69.38) --
+	(392.42, 69.26) --
+	(392.80, 69.14) --
+	(393.18, 69.02) --
+	(393.56, 68.90) --
+	(393.94, 68.78) --
+	(394.32, 68.67) --
+	(394.70, 68.55) --
+	(395.08, 68.43) --
+	(395.46, 68.32) --
+	(395.84, 68.20) --
+	(396.22, 68.09) --
+	(396.60, 67.97) --
+	(396.98, 67.86) --
+	(397.36, 67.75) --
+	(397.74, 67.64) --
+	(398.12, 67.53) --
+	(398.50, 67.42) --
+	(398.88, 67.31) --
+	(399.26, 67.20) --
+	(399.64, 67.09) --
+	(400.01, 66.98) --
+	(400.39, 66.87) --
+	(400.77, 66.76) --
+	(401.15, 66.66) --
+	(401.53, 66.55) --
 	(401.91, 66.45) --
-	(402.29, 66.38) --
-	(402.67, 66.31) --
-	(403.05, 66.24) --
-	(403.43, 66.17) --
-	(403.81, 66.10) --
-	(404.19, 66.03) --
-	(404.57, 65.97) --
-	(404.95, 65.90) --
-	(405.33, 65.83) --
-	(405.71, 65.76) --
-	(406.09, 65.69) --
-	(406.47, 65.62) --
-	(406.85, 65.56) --
-	(407.23, 65.49) --
-	(407.61, 65.42) --
-	(407.99, 65.36) --
-	(408.37, 65.29) --
-	(408.75, 65.22) --
-	(409.13, 65.16) --
-	(409.51, 65.09) --
-	(409.89, 65.03) --
-	(410.27, 64.96) --
-	(410.65, 64.90) --
-	(411.03, 64.83) --
-	(411.41, 64.77) --
-	(411.79, 64.70) --
-	(412.17, 64.64) --
-	(412.55, 64.58) --
-	(412.93, 64.51) --
-	(413.31, 64.45) --
-	(413.68, 64.39) --
-	(414.06, 64.33) --
-	(414.44, 64.26) --
-	(414.82, 64.20) --
-	(415.20, 64.14) --
-	(415.58, 64.08) --
-	(415.96, 64.02) --
-	(416.34, 63.96) --
-	(416.72, 63.89) --
-	(417.10, 63.83) --
-	(417.48, 63.77) --
-	(417.86, 63.71) --
-	(418.24, 63.65) --
-	(418.62, 63.59) --
-	(419.00, 63.53) --
-	(419.38, 63.47) --
-	(419.76, 63.42) --
-	(420.14, 63.36) --
-	(420.52, 63.30) --
-	(420.90, 63.24) --
-	(421.28, 63.18) --
-	(421.66, 63.12) --
-	(422.04, 63.07) --
-	(422.42, 63.01) --
-	(422.80, 62.95) --
-	(423.18, 62.90) --
-	(423.56, 62.84) --
-	(423.94, 62.78) --
-	(424.32, 62.73) --
-	(424.70, 62.67) --
-	(425.08, 62.61) --
-	(425.46, 62.56) --
-	(425.84, 62.50) --
-	(426.22, 62.45) --
-	(426.60, 62.39) --
-	(426.97, 62.34) --
-	(427.35, 62.28) --
-	(427.73, 62.23) --
-	(428.11, 62.18) --
-	(428.49, 62.12) --
-	(428.87, 62.07) --
-	(429.25, 62.02) --
-	(429.63, 61.96) --
-	(430.01, 61.91) --
-	(430.39, 61.86) --
-	(430.77, 61.80) --
-	(431.15, 61.75) --
-	(431.53, 61.70) --
-	(431.91, 61.65) --
-	(432.29, 61.60) --
-	(432.67, 61.55) --
-	(433.05, 61.49) --
-	(433.43, 61.44) --
-	(433.81, 61.39) --
-	(434.19, 61.34) --
-	(434.57, 61.29) --
-	(434.95, 61.24) --
-	(435.33, 61.19) --
-	(435.71, 61.14) --
-	(436.09, 61.09) --
-	(436.47, 61.04) --
-	(436.85, 60.99) --
-	(437.23, 60.94) --
-	(437.61, 60.90) --
-	(437.99, 60.85) --
-	(438.37, 60.80) --
-	(438.75, 60.75) --
-	(439.13, 60.70) --
-	(439.51, 60.66) --
-	(439.89, 60.61) --
-	(440.27, 60.56) --
-	(440.64, 60.51) --
-	(441.02, 60.47) --
-	(441.40, 60.42) --
-	(441.78, 60.37) --
-	(442.16, 60.33) --
-	(442.54, 60.28) --
-	(442.92, 60.23) --
-	(443.30, 60.19) --
-	(443.68, 60.14) --
-	(444.06, 60.10) --
-	(444.44, 60.05) --
-	(444.82, 60.01) --
-	(445.20, 59.96) --
-	(445.58, 59.92) --
-	(445.96, 59.87) --
-	(446.34, 59.83) --
-	(446.72, 59.78) --
-	(447.10, 59.74) --
-	(447.48, 59.70) --
-	(447.86, 59.65) --
-	(448.24, 59.61) --
-	(448.62, 59.57) --
-	(449.00, 59.52) --
-	(449.38, 59.48) --
-	(449.76, 59.44) --
-	(450.14, 59.40) --
-	(450.52, 59.35) --
-	(450.90, 59.31) --
-	(451.28, 59.27) --
-	(451.66, 59.23) --
-	(452.04, 59.19) --
-	(452.42, 59.14) --
-	(452.80, 59.10) --
-	(453.18, 59.06) --
-	(453.56, 59.02) --
-	(453.93, 58.98) --
-	(454.31, 58.94) --
-	(454.69, 58.90) --
-	(455.07, 58.86) --
-	(455.45, 58.82) --
-	(455.83, 58.78) --
-	(456.21, 58.74) --
-	(456.59, 58.70) --
-	(456.97, 58.66) --
-	(457.35, 58.62) --
-	(457.73, 58.58) --
-	(458.11, 58.54) --
-	(458.49, 58.50) --
-	(458.87, 58.47) --
-	(459.25, 58.43) --
-	(459.63, 58.39) --
-	(460.01, 58.35) --
-	(460.39, 58.31) --
-	(460.77, 58.27) --
-	(461.15, 58.24) --
-	(461.53, 58.20) --
-	(461.91, 58.16) --
-	(462.29, 58.13) --
-	(462.67, 58.09) --
-	(463.05, 58.05) --
-	(463.43, 58.01) --
-	(463.81, 57.98) --
-	(464.19, 57.94) --
-	(464.57, 57.91) --
-	(464.95, 57.87) --
-	(465.33, 57.83) --
-	(465.71, 57.80) --
-	(466.09, 57.76) --
-	(466.47, 57.73) --
-	(466.85, 57.69) --
-	(467.23, 57.66) --
-	(467.60, 57.62) --
-	(467.98, 57.59) --
-	(468.36, 57.55) --
-	(468.74, 57.52) --
-	(469.12, 57.48) --
-	(469.50, 57.45) --
-	(469.88, 57.41) --
-	(470.26, 57.38) --
-	(470.64, 57.35) --
-	(471.02, 57.31) --
-	(471.40, 57.28) --
-	(471.78, 57.25) --
-	(472.16, 57.21) --
-	(472.54, 57.18) --
-	(472.92, 57.15) --
-	(473.30, 57.11) --
-	(473.68, 57.08) --
-	(474.06, 57.05) --
-	(474.44, 57.02) --
-	(474.82, 56.98) --
-	(475.20, 56.95) --
-	(475.58, 56.92) --
-	(475.96, 56.89) --
-	(476.34, 56.86) --
-	(476.72, 56.83) --
-	(477.10, 56.79) --
-	(477.48, 56.76) --
-	(477.86, 56.73) --
-	(478.24, 56.70) --
-	(478.62, 56.67) --
-	(479.00, 56.64) --
-	(479.38, 56.61) --
-	(479.76, 56.58) --
-	(480.14, 56.55) --
-	(480.52, 56.52) --
-	(480.90, 56.49) --
-	(481.27, 56.46) --
-	(481.65, 56.43) --
-	(482.03, 56.40) --
-	(482.41, 56.37) --
-	(482.79, 56.34) --
-	(483.17, 56.31) --
-	(483.55, 56.28) --
-	(483.93, 56.25) --
-	(484.31, 56.22) --
-	(484.69, 56.19) --
-	(485.07, 56.16) --
-	(485.45, 56.14) --
-	(485.83, 56.11) --
-	(486.21, 56.08) --
-	(486.59, 56.05) --
-	(486.97, 56.02) --
-	(487.35, 55.99) --
-	(487.73, 55.97) --
-	(488.11, 55.94) --
-	(488.49, 55.91) --
-	(488.87, 55.88) --
-	(489.25, 55.86) --
-	(489.63, 55.83) --
-	(490.01, 55.80) --
-	(490.39, 55.78) --
-	(490.77, 55.75) --
-	(491.15, 55.72) --
-	(491.53, 55.69) --
-	(491.91, 55.67) --
-	(492.29, 55.64) --
-	(492.67, 55.62) --
-	(493.05, 55.59) --
-	(493.43, 55.56) --
-	(493.81, 55.54) --
-	(494.19, 55.51) --
-	(494.56, 55.49) --
-	(494.94, 55.46) --
-	(495.32, 55.43) --
-	(495.70, 55.41) --
-	(496.08, 55.38) --
-	(496.46, 55.36) --
-	(496.84, 55.33) --
-	(497.22, 55.31) --
-	(497.60, 55.28) --
-	(497.98, 55.26) --
-	(498.36, 55.23) --
-	(498.74, 55.21) --
-	(499.12, 55.19) --
-	(499.50, 55.16) --
-	(499.88, 55.14) --
-	(500.26, 55.11) --
-	(500.64, 55.09) --
-	(501.02, 55.06) --
-	(501.40, 55.04) --
-	(501.78, 55.02) --
-	(502.16, 54.99) --
-	(502.54, 54.97) --
-	(502.92, 54.95) --
-	(503.30, 54.92) --
-	(503.68, 54.90) --
-	(504.06, 54.88) --
-	(504.44, 54.85) --
-	(504.82, 54.83) --
-	(505.20, 54.81) --
-	(505.58, 54.79) --
-	(505.96, 54.76) --
-	(506.34, 54.74) --
-	(506.72, 54.72) --
-	(507.10, 54.70) --
-	(507.48, 54.67) --
-	(507.86, 54.65) --
-	(508.23, 54.63) --
-	(508.61, 54.61) --
-	(508.99, 54.59) --
-	(509.37, 54.57) --
-	(509.75, 54.54) --
-	(510.13, 54.52) --
-	(510.51, 54.50) --
-	(510.89, 54.48) --
-	(511.27, 54.46) --
-	(511.65, 54.44) --
-	(512.03, 54.42) --
-	(512.41, 54.40) --
-	(512.79, 54.37) --
-	(513.17, 54.35) --
-	(513.55, 54.33) --
-	(513.93, 54.31) --
-	(514.31, 54.29) --
-	(514.69, 54.27) --
-	(515.07, 54.25) --
-	(515.45, 54.23) --
-	(515.83, 54.21) --
-	(516.21, 54.19) --
-	(516.59, 54.17) --
-	(516.97, 54.15) --
-	(517.35, 54.13) --
-	(517.73, 54.11) --
-	(518.11, 54.09) --
-	(518.49, 54.07) --
-	(518.87, 54.05) --
-	(519.25, 54.03) --
-	(519.63, 54.01) --
-	(520.01, 54.00) --
-	(520.39, 53.98) --
-	(520.77, 53.96) --
-	(521.15, 53.94) --
-	(521.53, 53.92) --
-	(521.90, 53.90) --
-	(522.28, 53.88) --
-	(522.66, 53.86) --
-	(523.04, 53.85) --
-	(523.42, 53.83) --
-	(523.80, 53.81) --
-	(524.18, 53.79) --
-	(524.56, 53.77) --
-	(524.94, 53.75) --
-	(525.32, 53.74) --
-	(525.70, 53.72) --
-	(526.08, 53.70) --
-	(526.46, 53.68) --
-	(526.84, 53.67) --
-	(527.22, 53.65) --
-	(527.60, 53.63) --
-	(527.98, 53.61) --
-	(528.36, 53.60);
+	(402.29, 66.34) --
+	(402.67, 66.24) --
+	(403.05, 66.14) --
+	(403.43, 66.03) --
+	(403.81, 65.93) --
+	(404.19, 65.83) --
+	(404.57, 65.73) --
+	(404.95, 65.63) --
+	(405.33, 65.53) --
+	(405.71, 65.43) --
+	(406.09, 65.33) --
+	(406.47, 65.23) --
+	(406.85, 65.13) --
+	(407.23, 65.04) --
+	(407.61, 64.94) --
+	(407.99, 64.84) --
+	(408.37, 64.75) --
+	(408.75, 64.65) --
+	(409.13, 64.56) --
+	(409.51, 64.47) --
+	(409.89, 64.37) --
+	(410.27, 64.28) --
+	(410.65, 64.19) --
+	(411.03, 64.10) --
+	(411.41, 64.01) --
+	(411.79, 63.91) --
+	(412.17, 63.82) --
+	(412.55, 63.74) --
+	(412.93, 63.65) --
+	(413.31, 63.56) --
+	(413.68, 63.47) --
+	(414.06, 63.38) --
+	(414.44, 63.30) --
+	(414.82, 63.21) --
+	(415.20, 63.12) --
+	(415.58, 63.04) --
+	(415.96, 62.95) --
+	(416.34, 62.87) --
+	(416.72, 62.79) --
+	(417.10, 62.70) --
+	(417.48, 62.62) --
+	(417.86, 62.54) --
+	(418.24, 62.46) --
+	(418.62, 62.37) --
+	(419.00, 62.29) --
+	(419.38, 62.21) --
+	(419.76, 62.13) --
+	(420.14, 62.05) --
+	(420.52, 61.98) --
+	(420.90, 61.90) --
+	(421.28, 61.82) --
+	(421.66, 61.74) --
+	(422.04, 61.66) --
+	(422.42, 61.59) --
+	(422.80, 61.51) --
+	(423.18, 61.44) --
+	(423.56, 61.36) --
+	(423.94, 61.29) --
+	(424.32, 61.21) --
+	(424.70, 61.14) --
+	(425.08, 61.06) --
+	(425.46, 60.99) --
+	(425.84, 60.92) --
+	(426.22, 60.85) --
+	(426.60, 60.78) --
+	(426.97, 60.70) --
+	(427.35, 60.63) --
+	(427.73, 60.56) --
+	(428.11, 60.49) --
+	(428.49, 60.42) --
+	(428.87, 60.35) --
+	(429.25, 60.29) --
+	(429.63, 60.22) --
+	(430.01, 60.15) --
+	(430.39, 60.08) --
+	(430.77, 60.02) --
+	(431.15, 59.95) --
+	(431.53, 59.88) --
+	(431.91, 59.82) --
+	(432.29, 59.75) --
+	(432.67, 59.69) --
+	(433.05, 59.62) --
+	(433.43, 59.56) --
+	(433.81, 59.49) --
+	(434.19, 59.43) --
+	(434.57, 59.37) --
+	(434.95, 59.31) --
+	(435.33, 59.24) --
+	(435.71, 59.18) --
+	(436.09, 59.12) --
+	(436.47, 59.06) --
+	(436.85, 59.00) --
+	(437.23, 58.94) --
+	(437.61, 58.88) --
+	(437.99, 58.82) --
+	(438.37, 58.76) --
+	(438.75, 58.70) --
+	(439.13, 58.64) --
+	(439.51, 58.59) --
+	(439.89, 58.53) --
+	(440.27, 58.47) --
+	(440.64, 58.41) --
+	(441.02, 58.36) --
+	(441.40, 58.30) --
+	(441.78, 58.24) --
+	(442.16, 58.19) --
+	(442.54, 58.13) --
+	(442.92, 58.08) --
+	(443.30, 58.02) --
+	(443.68, 57.97) --
+	(444.06, 57.92) --
+	(444.44, 57.86) --
+	(444.82, 57.81) --
+	(445.20, 57.76) --
+	(445.58, 57.70) --
+	(445.96, 57.65) --
+	(446.34, 57.60) --
+	(446.72, 57.55) --
+	(447.10, 57.50) --
+	(447.48, 57.45) --
+	(447.86, 57.40) --
+	(448.24, 57.35) --
+	(448.62, 57.30) --
+	(449.00, 57.25) --
+	(449.38, 57.20) --
+	(449.76, 57.15) --
+	(450.14, 57.10) --
+	(450.52, 57.05) --
+	(450.90, 57.00) --
+	(451.28, 56.96) --
+	(451.66, 56.91) --
+	(452.04, 56.86) --
+	(452.42, 56.81) --
+	(452.80, 56.77) --
+	(453.18, 56.72) --
+	(453.56, 56.68) --
+	(453.93, 56.63) --
+	(454.31, 56.59) --
+	(454.69, 56.54) --
+	(455.07, 56.50) --
+	(455.45, 56.45) --
+	(455.83, 56.41) --
+	(456.21, 56.36) --
+	(456.59, 56.32) --
+	(456.97, 56.28) --
+	(457.35, 56.23) --
+	(457.73, 56.19) --
+	(458.11, 56.15) --
+	(458.49, 56.11) --
+	(458.87, 56.06) --
+	(459.25, 56.02) --
+	(459.63, 55.98) --
+	(460.01, 55.94) --
+	(460.39, 55.90) --
+	(460.77, 55.86) --
+	(461.15, 55.82) --
+	(461.53, 55.78) --
+	(461.91, 55.74) --
+	(462.29, 55.70) --
+	(462.67, 55.66) --
+	(463.05, 55.62) --
+	(463.43, 55.58) --
+	(463.81, 55.54) --
+	(464.19, 55.50) --
+	(464.57, 55.47) --
+	(464.95, 55.43) --
+	(465.33, 55.39) --
+	(465.71, 55.35) --
+	(466.09, 55.32) --
+	(466.47, 55.28) --
+	(466.85, 55.24) --
+	(467.23, 55.21) --
+	(467.60, 55.17) --
+	(467.98, 55.13) --
+	(468.36, 55.10) --
+	(468.74, 55.06) --
+	(469.12, 55.03) --
+	(469.50, 54.99) --
+	(469.88, 54.96) --
+	(470.26, 54.92) --
+	(470.64, 54.89) --
+	(471.02, 54.85) --
+	(471.40, 54.82) --
+	(471.78, 54.79) --
+	(472.16, 54.75) --
+	(472.54, 54.72) --
+	(472.92, 54.69) --
+	(473.30, 54.65) --
+	(473.68, 54.62) --
+	(474.06, 54.59) --
+	(474.44, 54.56) --
+	(474.82, 54.53) --
+	(475.20, 54.49) --
+	(475.58, 54.46) --
+	(475.96, 54.43) --
+	(476.34, 54.40) --
+	(476.72, 54.37) --
+	(477.10, 54.34) --
+	(477.48, 54.31) --
+	(477.86, 54.28) --
+	(478.24, 54.25) --
+	(478.62, 54.22) --
+	(479.00, 54.19) --
+	(479.38, 54.16) --
+	(479.76, 54.13) --
+	(480.14, 54.10) --
+	(480.52, 54.07) --
+	(480.90, 54.04) --
+	(481.27, 54.01) --
+	(481.65, 53.99) --
+	(482.03, 53.96) --
+	(482.41, 53.93) --
+	(482.79, 53.90) --
+	(483.17, 53.87) --
+	(483.55, 53.85) --
+	(483.93, 53.82) --
+	(484.31, 53.79) --
+	(484.69, 53.77) --
+	(485.07, 53.74) --
+	(485.45, 53.71) --
+	(485.83, 53.69) --
+	(486.21, 53.66) --
+	(486.59, 53.63) --
+	(486.97, 53.61) --
+	(487.35, 53.58) --
+	(487.73, 53.56) --
+	(488.11, 53.53) --
+	(488.49, 53.51) --
+	(488.87, 53.48) --
+	(489.25, 53.46) --
+	(489.63, 53.43) --
+	(490.01, 53.41) --
+	(490.39, 53.38) --
+	(490.77, 53.36) --
+	(491.15, 53.33) --
+	(491.53, 53.31) --
+	(491.91, 53.29) --
+	(492.29, 53.26) --
+	(492.67, 53.24) --
+	(493.05, 53.22) --
+	(493.43, 53.19) --
+	(493.81, 53.17) --
+	(494.19, 53.15) --
+	(494.56, 53.13) --
+	(494.94, 53.10) --
+	(495.32, 53.08) --
+	(495.70, 53.06) --
+	(496.08, 53.04) --
+	(496.46, 53.01) --
+	(496.84, 52.99) --
+	(497.22, 52.97) --
+	(497.60, 52.95) --
+	(497.98, 52.93) --
+	(498.36, 52.91) --
+	(498.74, 52.89) --
+	(499.12, 52.87) --
+	(499.50, 52.84) --
+	(499.88, 52.82) --
+	(500.26, 52.80) --
+	(500.64, 52.78) --
+	(501.02, 52.76) --
+	(501.40, 52.74) --
+	(501.78, 52.72) --
+	(502.16, 52.70) --
+	(502.54, 52.68) --
+	(502.92, 52.66) --
+	(503.30, 52.64) --
+	(503.68, 52.62) --
+	(504.06, 52.61) --
+	(504.44, 52.59) --
+	(504.82, 52.57) --
+	(505.20, 52.55) --
+	(505.58, 52.53) --
+	(505.96, 52.51) --
+	(506.34, 52.49) --
+	(506.72, 52.48) --
+	(507.10, 52.46) --
+	(507.48, 52.44) --
+	(507.86, 52.42) --
+	(508.23, 52.40) --
+	(508.61, 52.39) --
+	(508.99, 52.37) --
+	(509.37, 52.35) --
+	(509.75, 52.33) --
+	(510.13, 52.32) --
+	(510.51, 52.30) --
+	(510.89, 52.28) --
+	(511.27, 52.27) --
+	(511.65, 52.25) --
+	(512.03, 52.23) --
+	(512.41, 52.22) --
+	(512.79, 52.20) --
+	(513.17, 52.18) --
+	(513.55, 52.17) --
+	(513.93, 52.15) --
+	(514.31, 52.13) --
+	(514.69, 52.12) --
+	(515.07, 52.10) --
+	(515.45, 52.09) --
+	(515.83, 52.07) --
+	(516.21, 52.06) --
+	(516.59, 52.04) --
+	(516.97, 52.03) --
+	(517.35, 52.01) --
+	(517.73, 52.00) --
+	(518.11, 51.98) --
+	(518.49, 51.97) --
+	(518.87, 51.95) --
+	(519.25, 51.94) --
+	(519.63, 51.92) --
+	(520.01, 51.91) --
+	(520.39, 51.89) --
+	(520.77, 51.88) --
+	(521.15, 51.86) --
+	(521.53, 51.85) --
+	(521.90, 51.84) --
+	(522.28, 51.82) --
+	(522.66, 51.81) --
+	(523.04, 51.80) --
+	(523.42, 51.78) --
+	(523.80, 51.77) --
+	(524.18, 51.75) --
+	(524.56, 51.74) --
+	(524.94, 51.73) --
+	(525.32, 51.72) --
+	(525.70, 51.70) --
+	(526.08, 51.69) --
+	(526.46, 51.68) --
+	(526.84, 51.66) --
+	(527.22, 51.65) --
+	(527.60, 51.64) --
+	(527.98, 51.63) --
+	(528.36, 51.61);
 \end{scope}

### 2020-08-28 benchmarking/benchmarkingVM/ESS_round2.tex
results update

--- 2020-08-10 benchmarking/benchmarkingVM/ESS_round2.tex
@@
-% Created by tikzDevice version 0.12.3 on 2020-08-10 16:04:21
+% Created by tikzDevice version 0.12.3.1 on 2020-08-28 13:29:31
 % !TEX encoding = UTF-8 Unicode
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,301.03) {ESS/hr [adapt (\textit{cat})]};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,433.62) {ESS/hr [adapt (\textit{real})]};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,301.03) {ESS/$10^6$ states [adapt (\textit{cat})]};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,433.62) {ESS/$10^6$ states [adapt (\textit{real})]};
 \end{scope}
@@
 \path[clip] ( 49.80,338.88) rectangle (239.28,528.36);
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (  0.00,403.16) --
+	(175.00,578.16);
+
+\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (302.44,578.16) --
+	(302.44,477.44) --
+	(  0.00,175.00);
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (  0.00,365.13) --
+	(213.03,578.16);
+
+\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (302.44,578.16) --
+	(302.44,515.47) --
+	(  0.00,213.03);
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (  0.00,327.11) --
+	(251.05,578.16);
+
+\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (302.44,578.16) --
+	(302.44,553.49) --
+	(  0.00,251.05);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,374.64) --
-	(203.52,578.16);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (286.65,578.16) --
-	(286.65,490.17) --
-	(  0.00,203.52);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (  0.00,346.12) --
-	(232.04,578.16);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (286.65,578.16) --
-	(286.65,518.69) --
-	(  0.00,232.04);
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (  0.00,317.60) --
-	(260.56,578.16);
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (286.65,578.16) --
-	(286.65,547.21) --
-	(  0.00,260.56);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (142.89,342.31) {$\frac{1}{64} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,435.87) {$64\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (114.37,342.31) {$\frac{1}{16} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,407.35) {$16\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 84.20,342.31) {$\frac{1}{4} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92,378.83) {$4\times$};
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,528.36);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 96.83,462.17) --
-	(104.39,462.17);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.95,455.39) --
-	(100.95,467.26);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (100.95,458.94) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (157.25,462.51) --
-	(190.79,462.51);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.21,460.09) --
-	(180.21,464.68);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.21,458.48) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.00,476.56) --
-	(103.04,476.56);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.41,475.30) --
-	( 99.41,477.74);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 99.41,472.52) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.19,434.62) --
-	(105.17,434.62);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (102.83,423.86) --
-	(102.83,441.65);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (102.83,430.59) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.73,464.74) --
-	( 95.52,464.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 90.46,459.17) --
-	( 90.46,469.12);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 90.46,461.83) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.57,483.53) --
-	(194.99,483.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.78,482.91) --
-	(194.78,484.13);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.78,480.62) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.61,467.01) --
-	(116.13,467.01);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.49,464.26) --
-	(109.49,469.44);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (109.49,463.79) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.07,471.07) --
-	(193.44,471.07);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.83,468.87) --
-	(191.83,473.05);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.83,467.03) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (164.54,476.74) --
-	(164.84,476.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (164.69,476.63) --
-	(164.69,476.85);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (164.69,472.71) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.97,429.18) --
-	(112.07,429.18);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (107.26,425.26) --
-	(107.26,432.48);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (107.26,425.15) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (103.25,451.88) --
-	(115.87,451.88);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (110.51,447.05) --
-	(110.51,455.79);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (110.51,448.98) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.12,485.74) --
-	(196.43,485.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.27,485.16) --
-	(196.27,486.31);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.27,482.84) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.15,474.71) --
-	(181.63,474.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.43,471.39) --
-	(177.43,477.57);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.43,471.49) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.21,475.71) --
-	(184.09,475.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.98,464.98) --
-	(174.98,482.73);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.98,471.68) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.98,485.03) --
-	(197.78,485.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.38,484.42) --
-	(197.38,485.62);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.38,481.00) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (150.24,443.07) --
-	(164.70,443.07);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.71,436.47) --
-	(158.71,448.06);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.71,439.03) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (178.58,473.47) --
-	(182.90,473.47);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.86,467.70) --
-	(180.86,477.96);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.86,470.56) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.48,498.31) --
-	(212.33,498.31);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.49,497.03) --
-	(210.49,499.52);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.49,495.41) {$\kappa$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (171.41,342.31) {$\frac{1}{64} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,464.39) {$64\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (133.38,342.31) {$\frac{1}{16} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,426.36) {$16\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 93.70,342.31) {$\frac{1}{4} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92,388.34) {$4\times$};
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,528.36);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 65.57,467.04) --
+	( 94.44,467.04);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 83.64,464.05) --
+	( 83.64,469.74);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 83.64,463.82) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.43,448.03) --
+	(181.61,448.03);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.14,444.87) --
+	(179.14,450.86);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.14,444.00) {$L$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 75.12,473.24) --
+	( 87.57,473.24);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 82.04,472.46) --
+	( 82.04,473.99);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 82.04,469.20) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 72.91,435.02) --
+	(108.34,435.02);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 95.99,431.48) --
+	( 95.99,438.16);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 95.99,430.99) {$h$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 33.73,468.13) --
+	( 71.46,468.13);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 58.63,465.86) --
+	( 58.63,470.24);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 58.63,465.23) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.10,477.42) --
+	(191.54,477.42);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.83,476.86) --
+	(190.83,477.97);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.83,474.52) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.58,471.54) --
+	(177.22,471.54);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.41,470.69) --
+	(176.41,472.36);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.41,468.31) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.37,474.80) --
+	(192.12,474.80);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.31,472.77) --
+	(190.31,476.70);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.31,470.77) {$L$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.74,479.57) --
+	(184.28,479.57);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.01,479.29) --
+	(184.01,479.85);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.01,475.54) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (163.78,454.70) --
+	(167.31,454.70);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (165.60,453.16) --
+	(165.60,456.15);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (165.60,450.66) {$h$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.43,473.34) --
+	(177.25,473.34);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.41,472.63) --
+	(175.41,474.04);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (175.41,470.44) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.32,481.45) --
+	(192.47,481.45);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.90,480.91) --
+	(191.90,481.98);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.90,478.54) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (143.30,436.09) --
+	(150.54,436.09);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (147.16,432.68) --
+	(147.16,439.12);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (147.16,432.86) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.44,479.26) --
+	(195.98,479.26);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.74,478.07) --
+	(194.74,480.41);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.74,475.23) {$L$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.94,482.87) --
+	(191.80,482.87);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.38,482.55) --
+	(191.38,483.18);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.38,478.84) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (113.09,401.86) --
+	(120.91,401.86);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (117.28,397.21) --
+	(117.28,405.84);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (117.28,397.83) {$h$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (139.37,432.88) --
+	(146.05,432.88);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (142.91,429.23) --
+	(142.91,436.09);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (142.91,429.97) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.43,484.21) --
+	(194.98,484.21);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.71,483.81) --
+	(194.71,484.61);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.71,481.31) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (129.75,450.31) --
+	(135.34,450.31);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (132.69,448.44) --
+	(132.69,452.06);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (132.69,447.08) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.98,473.88) --
+	(194.45,473.88);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.24,472.84) --
+	(193.24,474.88);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.24,469.85) {$L$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.80,475.99) --
+	(183.97,475.99);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.39,475.70) --
+	(183.39,476.27);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.39,471.95) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (122.57,435.81) --
+	(128.58,435.81);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (125.74,433.40) --
+	(125.74,438.03);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (125.74,431.78) {$h$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (134.00,445.67) --
+	(141.88,445.67);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (138.22,443.26) --
+	(138.22,447.88);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (138.22,442.77) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.56,484.53) --
+	(195.61,484.53);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.09,484.08) --
+	(195.09,484.98);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.09,481.63) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 84.00,463.50) --
+	(111.71,463.50);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (101.21,460.57) --
+	(101.21,466.15);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (101.21,460.27) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.70,461.08) --
+	(189.43,461.08);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.99,460.33) --
+	(184.99,461.81);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.99,457.05) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (153.50,470.75) --
+	(155.46,470.75);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (154.50,470.01) --
+	(154.50,471.47);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (154.50,466.72) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 81.05,416.60) --
+	(101.36,416.60);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 93.05,412.44) --
+	( 93.05,420.21);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 93.05,412.57) {$h$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 84.24,446.61) --
+	(107.51,446.61);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 98.28,444.30) --
+	( 98.28,448.73);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 98.28,443.70) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.03,481.27) --
+	(193.70,481.27);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.40,480.85) --
+	(192.40,481.68);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.40,478.36) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.84,455.89) --
+	(190.97,455.89);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.45,452.11) --
+	(189.45,459.20);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (189.45,452.66) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.90,478.12) --
+	(194.66,478.12);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.31,477.19) --
+	(193.31,479.03);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.31,474.09) {$L$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (207.74,495.81) --
+	(208.14,495.81);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (207.94,495.66) --
+	(207.94,495.97);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.94,491.78) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.85,446.43) --
+	(156.02,446.43);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (154.48,444.35) --
+	(154.48,448.35);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (154.48,442.39) {$h$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.08,460.23) --
+	(175.72,460.23);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.50,459.37) --
+	(173.50,461.07);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.50,457.33) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.44,483.43) --
+	(194.56,483.43);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.00,483.01) --
+	(194.00,483.84);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.00,480.52) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (111.56,510.61) --
+	(122.39,510.61);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (117.50,506.59) --
+	(117.50,514.11);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (117.50,507.38) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.30,510.72) --
+	(200.72,510.72);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.54,507.87) --
+	(199.54,513.30);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.54,506.68) {$L$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (122.36,483.27) --
+	(131.86,483.27);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (127.52,480.40) --
+	(127.52,485.87);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (127.52,479.24) {$h$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (119.73,487.76) --
+	(132.30,487.76);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (126.73,484.08) --
+	(126.73,491.00);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (126.73,484.85) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.03,529.08) --
+	(198.96,529.08);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (197.53,525.48) --
+	(197.53,532.27);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.53,526.18) {$\kappa$};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,301.03) {ESS/hr [adapt (\textit{cat})]};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (307.01,433.62) {ESS/hr [adapt (\textit{quant})]};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,301.03) {ESS/$10^6$ states [adapt (\textit{cat})]};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (307.01,433.62) {ESS/$10^6$ states [adapt (\textit{quant})]};
 \end{scope}
@@
 \path[clip] (338.88,338.88) rectangle (528.36,528.36);
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] ( 86.24,200.32) --
+	(464.08,578.16);
+
+\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (578.16,464.08) --
+	(114.08,  0.00);
+
+\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] ( 86.24,  0.00) --
+	( 86.24,200.32);
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] ( 86.24,162.29) --
+	(502.11,578.16);
+
+\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (578.16,502.11) --
+	( 86.24, 10.19) --
+	( 86.24,162.29);
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] ( 86.24,124.27) --
+	(540.13,578.16);
+
+\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (578.16,540.13) --
+	( 86.24, 48.21) --
+	( 86.24,124.27);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (149.40,234.96) --
-	(492.60,578.16);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (575.73,578.16) --
-	(575.73,490.17) --
-	(149.40, 63.84) --
-	(149.40,234.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (149.40,206.44) --
-	(521.12,578.16);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (575.73,578.16) --
-	(575.73,518.69) --
-	(149.40, 92.36) --
-	(149.40,206.44);
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (149.40,177.92) --
-	(549.64,578.16);
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (575.73,578.16) --
-	(575.73,547.21) --
-	(149.40,120.88) --
-	(149.40,177.92);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (431.97,342.31) {$\frac{1}{64} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,435.87) {$64\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (403.45,342.31) {$\frac{1}{16} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,407.35) {$16\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (373.28,342.31) {$\frac{1}{4} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.00,378.83) {$4\times$};
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (338.88,338.88) -- (528.36,528.36);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (385.91,398.02) --
-	(393.47,398.02);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (390.03,382.13) --
-	(390.03,406.87);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (390.03,394.79) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (446.33,475.91) --
-	(479.87,475.91);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (469.29,475.07) --
-	(469.29,476.72);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (469.29,471.88) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (384.08,472.93) --
-	(392.12,472.93);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (388.49,468.95) --
-	(388.49,476.26);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (388.49,468.89) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.27,397.74) --
-	(394.25,397.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (391.91,377.39) --
-	(391.91,407.77);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (391.91,393.71) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (372.81,366.19) --
-	(384.60,366.19);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (379.54,357.18) --
-	(379.54,372.44);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (379.54,363.29) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.65,483.32) --
-	(484.07,483.32);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.86,483.08) --
-	(483.86,483.56);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.86,480.42) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (388.69,424.26) --
-	(405.21,424.26);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (398.57,421.10) --
-	(398.57,427.01);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (398.57,421.04) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.15,476.34) --
-	(482.52,476.34);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (480.91,473.72) --
-	(480.91,478.65);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (480.91,472.30) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (453.62,477.11) --
-	(453.92,477.11);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (453.77,476.35) --
-	(453.77,477.84);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (453.77,473.07) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (390.05,422.63) --
-	(401.15,422.63);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (396.34,419.69) --
-	(396.34,425.20);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (396.34,418.60) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (392.33,405.99) --
-	(404.95,405.99);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (399.59,404.44) --
-	(399.59,407.42);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (399.59,403.08) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.20,485.27) --
-	(485.51,485.27);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.35,485.11) --
-	(485.35,485.43);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (485.35,482.37) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.23,469.66) --
-	(470.71,469.66);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (466.51,467.06) --
-	(466.51,471.96);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (466.51,466.43) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (447.29,481.52) --
-	(473.17,481.52);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.06,478.07) --
-	(464.06,484.47);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (464.06,477.48) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.06,487.79) --
-	(486.86,487.79);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.46,487.17) --
-	(486.46,488.40);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (486.46,483.76) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (439.32,448.83) --
-	(453.78,448.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (447.79,445.54) --
-	(447.79,451.66);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (447.79,444.80) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (467.66,470.37) --
-	(471.98,470.37);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (469.94,468.48) --
-	(469.94,472.10);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (469.94,467.47) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (497.56,499.91) --
-	(501.41,499.91);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.57,499.32) --
-	(499.57,500.49);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (499.57,497.01) {$\kappa$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (460.49,342.31) {$\frac{1}{64} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,464.39) {$64\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (422.46,342.31) {$\frac{1}{16} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.83,426.36) {$16\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (382.78,342.31) {$\frac{1}{4} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.00,388.34) {$4\times$};
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (338.88,338.88) -- (528.36,528.36);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (354.65,438.13) --
+	(383.52,438.13);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (372.72,433.43) --
+	(372.72,442.14);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (372.72,434.90) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (465.51,456.44) --
+	(470.69,456.44);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (468.22,453.88) --
+	(468.22,458.79);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.22,452.41) {$L$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (364.20,475.42) --
+	(376.65,475.42);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (371.12,474.25) --
+	(371.12,476.55);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (371.12,471.39) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (361.99,428.85) --
+	(397.42,428.85);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (385.07,416.26) --
+	(385.07,437.45);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (385.07,424.82) {$h$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (322.81,453.94) --
+	(360.54,453.94);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (347.71,449.40) --
+	(347.71,457.84);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (347.71,451.04) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (479.18,480.12) --
+	(480.62,480.12);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (479.91,479.30) --
+	(479.91,480.91);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (479.91,477.22) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (464.66,465.58) --
+	(466.30,465.58);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (465.49,463.97) --
+	(465.49,467.09);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (465.49,462.35) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (477.45,480.31) --
+	(481.20,480.31);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (479.39,479.55) --
+	(479.39,481.05);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (479.39,476.28) {$L$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (472.82,482.31) --
+	(473.36,482.31);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (473.09,482.08) --
+	(473.09,482.54);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (473.09,478.28) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (452.86,455.62) --
+	(456.39,455.62);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (454.68,454.14) --
+	(454.68,457.03);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (454.68,451.59) {$h$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (462.51,478.30) --
+	(466.33,478.30);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (464.49,477.07) --
+	(464.49,479.47);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (464.49,475.39) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.40,480.62) --
+	(481.55,480.62);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.98,480.18) --
+	(480.98,481.06);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (480.98,477.72) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (432.38,427.43) --
+	(439.62,427.43);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (436.24,424.99) --
+	(436.24,429.68);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (436.24,424.21) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (482.52,482.27) --
+	(485.06,482.27);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.82,481.56) --
+	(483.82,482.95);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.82,478.23) {$L$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.02,486.43) --
+	(480.88,486.43);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.46,486.21) --
+	(480.46,486.65);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (480.46,482.40) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (402.17,409.36) --
+	(409.99,409.36);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (406.36,407.67) --
+	(406.36,410.96);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (406.36,405.33) {$h$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (428.45,441.67) --
+	(435.13,441.67);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (431.99,439.92) --
+	(431.99,443.32);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (431.99,438.77) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.51,483.51) --
+	(484.06,483.51);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.79,483.13) --
+	(483.79,483.88);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.79,480.60) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (418.83,448.30) --
+	(424.42,448.30);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (421.77,445.38) --
+	(421.77,450.94);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (421.77,445.07) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.06,483.20) --
+	(483.53,483.20);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (482.32,482.06) --
+	(482.32,484.31);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (482.32,479.17) {$L$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (471.88,483.39) --
+	(473.05,483.39);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (472.47,482.50) --
+	(472.47,484.26);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (472.47,479.36) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (411.65,447.57) --
+	(417.66,447.57);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (414.82,444.38) --
+	(414.82,450.43);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (414.82,443.54) {$h$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (423.08,456.30) --
+	(430.96,456.30);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (427.30,453.54) --
+	(427.30,458.81);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (427.30,453.40) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.64,485.06) --
+	(484.69,485.06);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (484.17,483.93) --
+	(484.17,486.13);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (484.17,482.15) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (373.08,414.28) --
+	(400.79,414.28);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (390.29,410.38) --
+	(390.29,417.69);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (390.29,411.05) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (468.78,464.34) --
+	(478.51,464.34);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (474.07,461.59) --
+	(474.07,466.85);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.07,460.31) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (442.58,472.21) --
+	(444.54,472.21);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (443.58,471.57) --
+	(443.58,472.84);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (443.58,468.18) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (370.13,418.44) --
+	(390.44,418.44);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (382.13,413.15) --
+	(382.13,422.88);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (382.13,414.41) {$h$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (373.32,431.44) --
+	(396.59,431.44);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (387.36,417.90) --
+	(387.36,440.46);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (387.36,428.53) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.11,479.21) --
+	(482.78,479.21);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.48,478.51) --
+	(481.48,479.89);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (481.48,476.30) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (476.92,477.88) --
+	(480.05,477.88);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (478.53,476.37) --
+	(478.53,479.32);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (478.53,474.66) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.98,482.67) --
+	(483.74,482.67);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (482.39,481.72) --
+	(482.39,483.59);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (482.39,478.64) {$L$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (496.82,497.06) --
+	(497.22,497.06);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (497.02,496.96) --
+	(497.02,497.15);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (497.02,493.02) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (441.93,444.49) --
+	(445.10,444.49);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (443.56,442.00) --
+	(443.56,446.77);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (443.56,440.45) {$h$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (460.16,466.45) --
+	(464.80,466.45);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (462.58,465.18) --
+	(462.58,467.65);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (462.58,463.54) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (482.52,482.79) --
+	(483.64,482.79);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.08,482.51) --
+	(483.08,483.08);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.08,479.89) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (400.64,428.04) --
+	(411.47,428.04);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (406.58,424.63) --
+	(406.58,431.08);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (406.58,424.82) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (487.38,482.21) --
+	(489.80,482.21);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (488.62,481.06) --
+	(488.62,483.31);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (488.62,478.18) {$L$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (460.15,483.22) --
+	(461.90,483.22);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (461.04,482.71) --
+	(461.04,483.73);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (461.04,479.19) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (411.44,443.20) --
+	(420.94,443.20);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (416.60,439.70) --
+	(416.60,446.30);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (416.60,439.17) {$h$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (408.81,450.57) --
+	(421.38,450.57);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (415.81,448.28) --
+	(415.81,452.68);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (415.81,447.67) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (485.11,486.67) --
+	(488.04,486.67);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (486.61,485.68) --
+	(486.61,487.63);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (486.61,483.77) {$\kappa$};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54, 11.95) {ESS/hr [adapt (\textit{real})]};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,144.54) {ESS/hr [adapt (\textit{quant})]};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54, 11.95) {ESS/$10^6$ states [adapt (\textit{real})]};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,144.54) {ESS/$10^6$ states [adapt (\textit{quant})]};
 \end{scope}
@@
 \path[clip] ( 49.80, 49.80) rectangle (239.28,239.28);
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (  0.00,114.08) --
+	(302.44,416.52) --
+	(302.44,188.36) --
+	(114.08,  0.00);
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (  0.00, 76.05) --
+	(302.44,378.49) --
+	(302.44,226.39) --
+	( 76.05,  0.00);
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (  0.00, 38.03) --
+	(302.44,340.47) --
+	(302.44,264.41) --
+	( 38.03,  0.00);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00, 85.56) --
-	(286.65,372.21) --
-	(286.65,201.09) --
-	( 85.56,  0.00);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (  0.00, 57.04) --
-	(286.65,343.69) --
-	(286.65,229.61) --
-	( 57.04,  0.00);
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (  0.00, 28.52) --
-	(286.65,315.17) --
-	(286.65,258.13) --
-	( 28.52,  0.00);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (142.89, 53.23) {$\frac{1}{64} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,146.79) {$64\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (114.37, 53.23) {$\frac{1}{16} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,118.27) {$16\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 84.20, 53.23) {$\frac{1}{4} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92, 89.75) {$4\times$};
-
-\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] ( 49.80, 49.80) -- (239.28,239.28);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (166.31,108.94) --
-	(178.18,108.94);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.09, 93.05) --
-	(173.09,117.79);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.09,105.71) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.01,186.83) --
-	(175.60,186.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.43,185.99) --
-	(173.43,187.64);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.43,182.80) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.22,183.85) --
-	(188.66,183.85);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.48,179.87) --
-	(187.48,187.18);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.48,179.81) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (134.78,108.66) --
-	(152.57,108.66);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.54, 88.31) --
-	(145.54,118.69);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (145.54,104.63) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (170.09, 77.11) --
-	(180.04, 77.11);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.66, 68.10) --
-	(175.66, 83.36);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (175.66, 74.21) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.83,194.24) --
-	(195.05,194.24);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.45,194.00) --
-	(194.45,194.48);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.45,191.34) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (165.91,162.72) --
-	(169.91,162.72);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.01,157.69) --
-	(168.01,166.76);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (168.01,159.49) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.51,190.76) --
-	(192.13,190.76);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.40,188.99) --
-	(190.40,192.40);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.40,186.73) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.13,194.78) --
-	(192.93,194.78);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.54,192.84) --
-	(192.54,196.56);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.54,190.75) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (154.98,160.08) --
-	(160.63,160.08);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.00,153.30) --
-	(158.00,165.16);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.00,156.04) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.83,159.04) --
-	(165.18,159.04);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.57,156.47) --
-	(163.57,161.34);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (163.57,156.14) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.10,198.95) --
-	(199.15,198.95);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.63,198.56) --
-	(198.63,199.33);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.63,196.04) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.18,135.18) --
-	(180.36,135.18);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.93,132.02) --
-	(177.93,137.93);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.93,131.96) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.79,187.26) --
-	(183.97,187.26);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.99,184.64) --
-	(181.99,189.57);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.99,183.22) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.55,188.03) --
-	(187.77,188.03);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.66,187.27) --
-	(187.66,188.76);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.66,183.99) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (136.18,133.55) --
-	(143.40,133.55);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.10,130.61) --
-	(140.10,136.12);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (140.10,129.52) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (157.97,116.91) --
-	(166.71,116.91);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.80,115.36) --
-	(162.80,118.34);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (162.80,114.00) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.08,196.19) --
-	(197.23,196.19);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.66,196.03) --
-	(196.66,196.35);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.66,193.29) {$\kappa$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.94,146.87) --
-	(183.64,146.87);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.81,144.32) --
-	(182.81,149.14);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.81,143.64) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.45,193.77) --
-	(184.72,193.77);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (183.15,191.53) --
-	(183.15,195.79);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.15,189.74) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.22,193.77) --
-	(188.78,193.77);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.50,193.53) --
-	(188.50,194.01);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.50,189.74) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (156.86,161.33) --
-	(159.29,161.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.11,158.55) --
-	(158.11,163.78);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.11,157.30) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (155.66,151.01) --
-	(161.22,151.01);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.63,148.68) --
-	(158.63,153.10);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.63,148.10) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.03,198.53) --
-	(199.38,198.53);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.24,196.83) --
-	(198.24,200.10);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.24,195.63) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.31,180.58) --
-	(188.49,180.58);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.63,177.98) --
-	(185.63,182.88);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.63,177.35) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.90,192.44) --
-	(193.65,192.44);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.63,188.99) --
-	(186.63,195.39);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (186.63,188.40) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.34,198.71) --
-	(196.54,198.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.95,198.09) --
-	(195.95,199.32);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.95,194.68) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (147.39,159.75) --
-	(158.98,159.75);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.99,156.46) --
-	(153.99,162.58);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (153.99,155.72) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (178.62,181.29) --
-	(188.88,181.29);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (184.39,179.40) --
-	(184.39,183.02);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.39,178.39) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (207.95,210.83) --
-	(210.44,210.83);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.23,210.24) --
-	(209.23,211.41);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.23,207.93) {$\kappa$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.58,195.33) --
-	(183.78,195.33);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.49,193.67) --
-	(180.49,196.87);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.49,192.11) {$p$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.38,201.82) --
-	(174.02,201.82);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.39,201.65) --
-	(171.39,201.98);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.39,197.78) {$L$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.62,199.95) --
-	(199.37,199.95);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (199.00,198.75) --
-	(199.00,201.09);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.00,195.92) {$r$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.20,178.14) --
-	(180.56,178.14);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (180.38,173.53) --
-	(180.38,181.90);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.38,174.11) {$h$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.06,186.15) --
-	(185.69,186.15);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.64,182.17) --
-	(182.64,189.49);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.64,183.25) {$\sigma$};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.62,212.25) --
-	(213.79,212.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.74,211.79) --
-	(212.74,212.69);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.74,209.34) {$\kappa$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (171.41, 53.23) {$\frac{1}{64} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,175.31) {$64\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (133.38, 53.23) {$\frac{1}{16} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,137.28) {$16\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 93.70, 53.23) {$\frac{1}{4} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92, 99.26) {$4\times$};
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 49.80, 49.80) -- (239.28,239.28);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.97,149.05) --
+	(180.66,149.05);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (177.96,144.35) --
+	(177.96,153.06);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.96,145.82) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (155.79,167.36) --
+	(161.78,167.36);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (158.95,164.80) --
+	(158.95,169.71);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.95,163.33) {$L$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.38,186.34) --
+	(184.91,186.34);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.16,185.17) --
+	(184.16,187.47);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.16,182.31) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (142.40,139.77) --
+	(149.08,139.77);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (145.94,127.18) --
+	(145.94,148.37);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (145.94,135.74) {$h$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.78,164.86) --
+	(181.16,164.86);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.05,160.32) --
+	(179.05,168.76);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.05,161.96) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.78,191.04) --
+	(188.89,191.04);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.34,190.22) --
+	(188.34,191.83);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.34,188.14) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.61,176.50) --
+	(183.28,176.50);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.46,174.89) --
+	(182.46,178.01);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.46,173.27) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.69,191.23) --
+	(187.62,191.23);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.72,190.47) --
+	(185.72,191.97);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.72,187.20) {$L$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.21,193.23) --
+	(190.77,193.23);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.49,193.00) --
+	(190.49,193.46);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.49,189.20) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.08,166.54) --
+	(167.07,166.54);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (165.62,165.06) --
+	(165.62,167.95);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (165.62,162.51) {$h$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.55,189.22) --
+	(184.96,189.22);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.26,187.99) --
+	(184.26,190.39);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.26,186.31) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.83,191.54) --
+	(192.90,191.54);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.37,191.10) --
+	(192.37,191.98);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.37,188.64) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (143.60,138.35) --
+	(150.04,138.35);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (147.01,135.91) --
+	(147.01,140.60);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (147.01,135.13) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.99,193.19) --
+	(191.33,193.19);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.18,192.48) --
+	(190.18,193.87);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.18,189.15) {$L$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.47,197.35) --
+	(194.10,197.35);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.79,197.13) --
+	(193.79,197.57);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.79,193.32) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (108.13,120.28) --
+	(116.76,120.28);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (112.78,118.59) --
+	(112.78,121.88);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (112.78,116.25) {$h$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (140.15,152.59) --
+	(147.01,152.59);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (143.80,150.84) --
+	(143.80,154.24);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (143.80,149.69) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.73,194.43) --
+	(195.53,194.43);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.13,194.05) --
+	(195.13,194.80);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.13,191.52) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (159.36,159.22) --
+	(162.98,159.22);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.23,156.30) --
+	(161.23,161.86);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (161.23,155.99) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.76,194.12) --
+	(185.80,194.12);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.80,192.98) --
+	(184.80,195.23);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.80,190.09) {$L$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.62,194.31) --
+	(187.19,194.31);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.91,193.42) --
+	(186.91,195.18);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (186.91,190.28) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (144.32,158.49) --
+	(148.95,158.49);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (146.73,155.30) --
+	(146.73,161.35);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (146.73,154.46) {$h$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (154.18,167.22) --
+	(158.80,167.22);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (156.59,164.46) --
+	(156.59,169.73);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (156.59,164.32) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.00,195.98) --
+	(195.90,195.98);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.45,194.85) --
+	(195.45,197.05);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.45,193.07) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.49,125.20) --
+	(177.07,125.20);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.42,121.30) --
+	(174.42,128.61);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.42,121.97) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.25,175.26) --
+	(172.73,175.26);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.00,172.51) --
+	(172.00,177.77);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.00,171.23) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.93,183.13) --
+	(182.39,183.13);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.67,182.49) --
+	(181.67,183.76);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.67,179.10) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (123.36,129.36) --
+	(131.13,129.36);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (127.52,124.07) --
+	(127.52,133.80);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (127.52,125.33) {$h$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (155.22,142.36) --
+	(159.65,142.36);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (157.53,128.82) --
+	(157.53,151.38);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (157.53,139.45) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.77,190.13) --
+	(192.60,190.13);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.19,189.43) --
+	(192.19,190.81);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.19,187.22) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (163.03,188.80) --
+	(170.12,188.80);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (166.81,187.29) --
+	(166.81,190.24);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (166.81,185.58) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.11,193.59) --
+	(189.95,193.59);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.04,192.64) --
+	(189.04,194.51);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (189.04,189.56) {$L$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (206.58,207.98) --
+	(206.89,207.98);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (206.73,207.88) --
+	(206.73,208.07);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (206.73,203.94) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (155.27,155.41) --
+	(159.27,155.41);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (157.35,152.92) --
+	(157.35,157.69);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (157.35,151.37) {$h$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (170.29,177.37) --
+	(171.99,177.37);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.15,176.10) --
+	(171.15,178.57);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.15,174.46) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.93,193.71) --
+	(194.76,193.71);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.35,193.43) --
+	(194.35,194.00);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.35,190.81) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (217.51,138.96) --
+	(225.03,138.96);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (221.53,135.55) --
+	(221.53,142.00);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (221.53,135.74) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (218.79,193.13) --
+	(224.22,193.13);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (221.64,191.98) --
+	(221.64,194.23);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (221.64,189.10) {$L$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.32,154.12) --
+	(196.79,154.12);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.19,150.62) --
+	(194.19,157.22);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.19,150.09) {$h$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.00,161.49) --
+	(201.92,161.49);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.68,159.20) --
+	(198.68,163.60);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.68,158.59) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (236.40,197.59) --
+	(243.19,197.59);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (240.00,196.60) --
+	(240.00,198.55);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (240.00,194.69) {$\kappa$};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (485.73,205.86) --
-	(485.73, 51.84);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (485.73,126.77) {$77\times $};
-\definecolor{fillColor}{RGB}{0,140,186}
-
-\path[fill=fillColor] (485.73,205.86) circle (  1.87);
-\definecolor{fillColor}{RGB}{105,105,105}
-
-\path[fill=fillColor] (485.73, 51.84) circle (  1.87);
-\definecolor{fillColor}{gray}{0.64}
-
-\path[fill=fillColor] (485.73,199.70) circle (  1.87);
-\definecolor{fillColor}{RGB}{0,140,186}
-
-\path[fill=fillColor] (347.47, 84.16) circle (  2.15);
-\definecolor{fillColor}{RGB}{105,105,105}
-
-\path[fill=fillColor] (347.47, 72.71) circle (  2.15);
-\definecolor{fillColor}{gray}{0.64}
-
-\path[fill=fillColor] (347.47, 61.25) circle (  2.15);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 80.88) {adapt (\textit{real})};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 69.42) {adapt (\textit{cat})};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 57.97) {adapt (\textit{quant})};
-\definecolor{fillColor}{RGB}{0,140,186}
-
-\path[fill=fillColor] (347.47, 84.16) circle (  2.15);
-\definecolor{fillColor}{RGB}{105,105,105}
-
-\path[fill=fillColor] (347.47, 72.71) circle (  2.15);
-\definecolor{fillColor}{gray}{0.64}
-
-\path[fill=fillColor] (347.47, 61.25) circle (  2.15);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 80.88) {adapt (\textit{real})};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 69.42) {adapt (\textit{cat})};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 57.97) {adapt (\textit{quant})};
-\definecolor{fillColor}{RGB}{0,140,186}
-
-\path[fill=fillColor] (394.78,308.65) circle (  1.87);
-
-\path[fill=fillColor] (347.47, 84.16) circle (  2.15);
-\definecolor{fillColor}{RGB}{105,105,105}
-
-\path[fill=fillColor] (347.47, 72.71) circle (  2.15);
-\definecolor{fillColor}{gray}{0.64}
-
-\path[fill=fillColor] (347.47, 61.25) circle (  2.15);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 80.88) {adapt (\textit{real})};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 69.42) {adapt (\textit{cat})};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 57.97) {adapt (\textit{quant})};
-\definecolor{fillColor}{RGB}{0,140,186}
-
-\path[fill=fillColor] (390.04,246.75) circle (  1.87);
-\definecolor{fillColor}{gray}{0.64}
-
-\path[fill=fillColor] (390.04,277.75) circle (  1.87);
-\definecolor{fillColor}{RGB}{0,140,186}
-
-\path[fill=fillColor] (347.47, 84.16) circle (  2.15);
-\definecolor{fillColor}{RGB}{105,105,105}
-
-\path[fill=fillColor] (347.47, 72.71) circle (  2.15);
-\definecolor{fillColor}{gray}{0.64}
-
-\path[fill=fillColor] (347.47, 61.25) circle (  2.15);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 80.88) {adapt (\textit{real})};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 69.42) {adapt (\textit{cat})};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 57.97) {adapt (\textit{quant})};
-
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (404.25,204.65) --
-	(404.25,100.19);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (404.25,150.34) {$3.1\times $};
-\definecolor{fillColor}{RGB}{0,140,186}
-
-\path[fill=fillColor] (404.25,204.65) circle (  1.87);
-\definecolor{fillColor}{RGB}{105,105,105}
-
-\path[fill=fillColor] (404.25,100.19) circle (  1.87);
-\definecolor{fillColor}{gray}{0.64}
-
-\path[fill=fillColor] (404.25,210.63) circle (  1.87);
-\definecolor{fillColor}{RGB}{0,140,186}
-
-\path[fill=fillColor] (347.47, 84.16) circle (  2.15);
-\definecolor{fillColor}{RGB}{105,105,105}
-
-\path[fill=fillColor] (347.47, 72.71) circle (  2.15);
-\definecolor{fillColor}{gray}{0.64}
-
-\path[fill=fillColor] (347.47, 61.25) circle (  2.15);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 80.88) {adapt (\textit{real})};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 69.42) {adapt (\textit{cat})};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 57.97) {adapt (\textit{quant})};
-\definecolor{fillColor}{RGB}{0,140,186}
-
-\path[fill=fillColor] (347.47, 84.16) circle (  2.15);
-\definecolor{fillColor}{RGB}{105,105,105}
-
-\path[fill=fillColor] (347.47, 72.71) circle (  2.15);
-\definecolor{fillColor}{gray}{0.64}
-
-\path[fill=fillColor] (347.47, 61.25) circle (  2.15);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 80.88) {adapt (\textit{real})};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 69.42) {adapt (\textit{cat})};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 57.97) {adapt (\textit{quant})};
-\definecolor{fillColor}{RGB}{0,140,186}
-
-\path[fill=fillColor] (433.62,210.36) circle (  1.87);
-\definecolor{fillColor}{gray}{0.64}
-
-\path[fill=fillColor] (433.62,258.51) circle (  1.87);
-\definecolor{fillColor}{RGB}{0,140,186}
-
-\path[fill=fillColor] (347.47, 84.16) circle (  2.15);
-\definecolor{fillColor}{RGB}{105,105,105}
-
-\path[fill=fillColor] (347.47, 72.71) circle (  2.15);
-\definecolor{fillColor}{gray}{0.64}
-
-\path[fill=fillColor] (347.47, 61.25) circle (  2.15);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 80.88) {adapt (\textit{real})};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 69.42) {adapt (\textit{cat})};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 57.97) {adapt (\textit{quant})};
-
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (359.72,284.96) --
-	(359.72,295.15);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (359.72,287.98) {$0.96\times $};
-\definecolor{fillColor}{RGB}{0,140,186}
-
-\path[fill=fillColor] (359.72,284.96) circle (  1.87);
-\definecolor{fillColor}{RGB}{105,105,105}
-
-\path[fill=fillColor] (359.72,295.15) circle (  1.87);
-\definecolor{fillColor}{gray}{0.64}
-
-\path[fill=fillColor] (359.72,315.21) circle (  1.87);
-\definecolor{fillColor}{RGB}{0,140,186}
-
-\path[fill=fillColor] (347.47, 84.16) circle (  2.15);
-\definecolor{fillColor}{RGB}{105,105,105}
-
-\path[fill=fillColor] (347.47, 72.71) circle (  2.15);
-\definecolor{fillColor}{gray}{0.64}
-
-\path[fill=fillColor] (347.47, 61.25) circle (  2.15);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 80.88) {adapt (\textit{real})};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 69.42) {adapt (\textit{cat})};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 57.97) {adapt (\textit{quant})};
-\definecolor{fillColor}{RGB}{0,140,186}
-
-\path[fill=fillColor] (346.46,317.20) circle (  1.87);
-\definecolor{fillColor}{gray}{0.64}
-
-\path[fill=fillColor] (346.46,337.93) circle (  1.87);
-\definecolor{fillColor}{RGB}{0,140,186}
-
-\path[fill=fillColor] (347.47, 84.16) circle (  2.15);
-\definecolor{fillColor}{RGB}{105,105,105}
-
-\path[fill=fillColor] (347.47, 72.71) circle (  2.15);
-\definecolor{fillColor}{gray}{0.64}
-
-\path[fill=fillColor] (347.47, 61.25) circle (  2.15);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 80.88) {adapt (\textit{real})};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 69.42) {adapt (\textit{cat})};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (356.06, 57.97) {adapt (\textit{quant})};
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (485.73,100.19) --
+	(485.73, 51.03);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (485.73, 73.54) {$41\times $};
+\definecolor{fillColor}{RGB}{255,0,109}
+
+\path[fill=fillColor] (485.73,100.19) circle (  1.87);
+
+\path[fill=fillColor] (485.73, 53.94) --
+	(488.24, 49.58) --
+	(483.21, 49.58) --
+	cycle;
+
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (356.88,114.21) --
+	(356.88,100.41);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (356.88,105.24) {$1.3\times $};
+\definecolor{fillColor}{RGB}{253,104,0}
+
+\path[fill=fillColor] (356.88,114.21) circle (  1.87);
+
+\path[fill=fillColor] (356.88,103.31) --
+	(359.40, 98.95) --
+	(354.37, 98.95) --
+	cycle;
+
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (394.78,121.88) --
+	(394.78,116.44);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (394.78,117.08) {$1.1\times $};
+\definecolor{fillColor}{RGB}{143,161,0}
+
+\path[fill=fillColor] (394.78,121.88) circle (  1.87);
+
+\path[fill=fillColor] (394.78,119.34) --
+	(397.29,114.98) --
+	(392.26,114.98) --
+	cycle;
+
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (390.04,105.56) --
+	(390.04, 99.20);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (390.04,100.30) {$1.1\times $};
+\definecolor{fillColor}{RGB}{0,195,0}
+
+\path[fill=fillColor] (390.04,105.56) circle (  1.87);
+
+\path[fill=fillColor] (390.04,102.10) --
+	(392.55, 97.75) --
+	(387.52, 97.75) --
+	cycle;
+
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (404.25, 96.11) --
+	(404.25, 66.68);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (404.25, 79.32) {$2.7\times $};
+\definecolor{fillColor}{RGB}{0,219,171}
+
+\path[fill=fillColor] (404.25, 96.11) circle (  1.87);
+
+\path[fill=fillColor] (404.25, 69.58) --
+	(406.77, 65.23) --
+	(401.74, 65.23) --
+	cycle;
+
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (359.72,165.72) --
+	(359.72,170.31);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (359.72,165.94) {$0.96\times $};
+\definecolor{fillColor}{RGB}{0,216,255}
+
+\path[fill=fillColor] (359.72,165.72) circle (  1.87);
+
+\path[fill=fillColor] (359.72,173.21) --
+	(362.24,168.86) --
+	(357.21,168.86) --
+	cycle;
+\definecolor{fillColor}{RGB}{0,0,0}
+
+\path[fill=fillColor] (465.27,227.83) circle (  2.15);
+
+\path[fill=fillColor] (465.27,219.71) --
+	(468.17,214.70) --
+	(462.38,214.70) --
+	cycle;
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (473.87,224.54) {adapt (\textit{real})};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (473.87,213.09) {adapt (\textit{cat})};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92, 84.84) {200};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,122.73) {400};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,160.63) {600};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,198.53) {800};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,236.42) {1000};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92, 84.84) {100};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,122.73) {200};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,160.63) {300};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,198.53) {400};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,236.42) {500};
 \end{scope}

### 2020-08-28 benchmarking/benchmarkingVM/ESS_round3.tex
results update

@@
-% Created by tikzDevice version 0.12.3.1 on 2020-08-25 15:33:46
+% Created by tikzDevice version 0.12.3.1 on 2020-08-28 13:29:50
 % !TEX encoding = UTF-8 Unicode
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at (144.54, 14.40) {ESS/hr [adapt (\textit{real})]};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at (144.54, 14.40) {ESS/$10^6$ states [adapt (\textit{real})]};
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at ( 21.60,144.54) {ESS/hr [Bactrian (\textit{real})]};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at ( 21.60,144.54) {ESS/$10^6$ states [Bactrian (\textit{real})]};
 \end{scope}
@@
 \path[clip] ( 60.00, 60.00) rectangle (229.08,229.08);
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (  0.00,101.80) --
+	(187.28,289.08);
+
+\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (285.44,289.08) --
+	(285.44,183.64) --
+	(101.80,  0.00);
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (  0.00, 67.86) --
+	(221.22,289.08);
+
+\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (285.44,289.08) --
+	(285.44,217.58) --
+	( 67.86,  0.00);
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (  0.00, 33.93) --
+	(255.15,289.08);
+
+\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (285.44,289.08) --
+	(285.44,251.51) --
+	( 33.93,  0.00);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (  0.00, 71.00) --
-	(218.08,289.08);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (170.87, 64.13) {$\frac{1}{64} \times$};
 
-\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (268.39,289.08) --
-	(268.39,197.39) --
-	( 71.00,  0.00);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,175.57) {$64\times$};
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00, 47.34) --
-	(241.74,289.08);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (136.94, 64.13) {$\frac{1}{16} \times$};
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (268.39,289.08) --
-	(268.39,221.06) --
-	( 47.34,  0.00);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,141.64) {$16\times$};
 
-\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round] (  0.00, 23.67) --
-	(265.41,289.08);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (101.01, 64.13) {$\frac{1}{4} \times$};
 
-\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round] (268.39,289.08) --
-	(268.39,244.72) --
-	( 23.67,  0.00);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (140.08, 64.13) {$\frac{1}{64} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,144.78) {$64\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (116.41, 64.13) {$\frac{1}{16} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,121.11) {$16\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 90.75, 64.13) {$\frac{1}{4} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 62.56, 97.44) {$4\times$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 62.56,107.71) {$4\times$};
+\definecolor{drawColor}{RGB}{105,105,105}
 
 \path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 60.00, 60.00) -- (229.08,229.08);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.70,173.17) --
+	(176.77,173.17);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.36,167.76) --
+	(174.36,177.59);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (174.36,169.28) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (154.58,161.72) --
+	(159.92,161.72);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (157.40,159.31) --
+	(157.40,163.92);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (157.40,156.86) {$L$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.20,180.79) --
+	(180.57,180.79);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.89,179.06) --
+	(179.89,182.41);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (179.89,175.93) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (142.63,150.92) --
+	(148.59,150.92);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (145.79,146.50) --
+	(145.79,154.66);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (145.79,146.06) {$h$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.30,174.88) --
+	(177.21,174.88);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.34,171.71) --
+	(175.34,177.68);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (175.34,171.38) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.13,184.12) --
+	(184.12,184.12);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.63,183.73) --
+	(183.63,184.51);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (183.63,180.62) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (177.62,168.18) --
+	(179.11,168.18);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.38,167.36) --
+	(178.38,168.98);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (178.38,164.30) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.47,182.59) --
+	(182.98,182.59);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.29,180.33) --
+	(181.29,184.66);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (181.29,177.73) {$L$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.29,189.87) --
+	(185.80,189.87);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.55,189.65) --
+	(185.55,190.09);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (185.55,185.01) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.98,162.27) --
+	(164.64,162.27);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (163.35,161.01) --
+	(163.35,163.46);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (163.35,157.41) {$h$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.35,170.47) --
+	(180.61,170.47);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.99,169.43) --
+	(179.99,171.47);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (179.99,166.97) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.74,187.47) --
+	(187.69,187.47);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.22,187.11) --
+	(187.22,187.84);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (187.22,183.97) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (143.70,144.02) --
+	(149.45,144.02);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (146.74,140.77) --
+	(146.74,146.89);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (146.74,140.13) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.20,185.47) --
+	(186.29,185.47);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.27,184.63) --
+	(185.27,186.28);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (185.27,180.61) {$L$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.21,191.45) --
+	(188.77,191.45);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.49,191.28) --
+	(188.49,191.62);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (188.49,186.59) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (112.05,118.53) --
+	(119.75,118.53);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (116.20,115.40) --
+	(116.20,121.31);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (116.20,113.67) {$h$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (140.62,141.70) --
+	(146.75,141.70);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (143.88,138.45) --
+	(143.88,144.56);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (143.88,138.20) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.32,189.85) --
+	(190.04,189.85);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.69,189.60) --
+	(189.69,190.10);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (189.69,186.35) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (157.76,155.09) --
+	(160.99,155.09);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (159.43,153.71) --
+	(159.43,156.41);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (159.43,151.21) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.54,183.59) --
+	(181.36,183.59);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.47,183.01) --
+	(180.47,184.16);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (180.47,178.73) {$L$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.09,185.46) --
+	(182.59,185.46);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.34,185.27) --
+	(182.34,185.64);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (182.34,180.60) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (144.34,151.89) --
+	(148.48,151.89);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (146.50,150.38) --
+	(146.50,153.32);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (146.50,147.03) {$h$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (153.15,151.61) --
+	(157.27,151.61);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (155.29,149.99) --
+	(155.29,153.12);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (155.29,148.11) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.57,189.80) --
+	(190.37,189.80);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.97,189.48) --
+	(189.97,190.12);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (189.97,186.30) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.58,170.89) --
+	(173.57,170.89);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.20,168.97) --
+	(171.20,172.66);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (171.20,167.00) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.38,171.25) --
+	(169.69,171.25);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.04,169.63) --
+	(169.04,172.76);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (169.04,166.39) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (177.01,179.51) --
+	(178.32,179.51);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (177.67,178.71) --
+	(177.67,180.29);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (177.67,174.65) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (125.64,135.61) --
+	(132.58,135.61);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (129.35,132.05) --
+	(129.35,138.72);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (129.35,130.75) {$h$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (154.07,156.42) --
+	(158.03,156.42);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (156.13,153.99) --
+	(156.13,158.62);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (156.13,152.92) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.69,187.61) --
+	(187.42,187.61);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.06,187.12) --
+	(187.06,188.09);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (187.06,184.11) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.04,140.38) --
+	(167.37,140.38);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.41,136.78) --
+	(164.41,143.51);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (164.41,136.49) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.42,173.94) --
+	(185.06,173.94);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.25,172.19) --
+	(184.25,175.57);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (184.25,169.08) {$L$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.90,199.27) --
+	(200.17,199.27);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (200.04,199.14) --
+	(200.04,199.39);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (200.04,194.41) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (154.12,151.45) --
+	(157.69,151.45);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (155.97,149.32) --
+	(155.97,153.40);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (155.97,146.59) {$h$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (167.51,145.17) --
+	(169.03,145.17);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.29,143.54) --
+	(168.29,146.70);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (168.29,141.67) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.61,188.95) --
+	(189.35,188.95);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.98,188.59) --
+	(188.98,189.30);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (188.98,185.45) {$\kappa$};
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (200.17,196.99) --
-	(201.72,196.99);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (209.65,210.38) --
+	(216.36,210.38);
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (200.96,196.43) --
-	(200.96,197.53);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (213.24,207.54) --
+	(213.24,212.93);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (200.96,193.10) {$p$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (213.24,206.50) {$p$};
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (205.11,198.75) --
-	(207.67,198.75);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (210.79,215.57) --
+	(215.64,215.57);
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (206.44,197.10) --
-	(206.44,200.25);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (213.34,211.97) --
+	(213.34,218.72);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (206.44,193.89) {$L$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (213.34,210.72) {$L$};
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (205.83,203.06) --
-	(206.19,203.06);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.28,192.12) --
+	(191.17,192.12);
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (206.01,202.94) --
-	(206.01,203.18);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.85,189.23) --
+	(188.85,194.70);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (206.01,198.20) {$r$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (188.85,187.26) {$h$};
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.99,182.32) --
-	(180.78,182.32);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.57,186.62) --
+	(195.74,186.62);
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.91,181.55) --
-	(179.91,183.06);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.85,182.41) --
+	(192.85,190.21);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (179.91,177.46) {$h$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (192.85,183.12) {$\sigma$};
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.73,181.94) --
-	(183.35,181.94);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (226.51,226.85) --
+	(232.57,226.85);
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.20,181.15) --
-	(181.20,182.69);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (229.72,223.68) --
+	(229.72,229.66);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (181.20,178.44) {$\sigma$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (212.29,207.61) --
-	(213.84,207.61);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (213.08,206.84) --
-	(213.08,208.35);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (213.08,204.11) {$\kappa$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (229.72,223.35) {$\kappa$};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- (217.25, 60.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- (229.08, 60.00);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.31, 60.00) -- ( 99.31, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.39, 60.00) -- ( 99.39, 54.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.62, 60.00) -- (138.62, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (116.36, 60.00) -- (116.36, 54.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.93, 60.00) -- (177.93, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (155.75, 60.00) -- (155.75, 54.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.25, 60.00) -- (217.25, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.72, 60.00) -- (172.72, 54.00);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.11, 60.00) -- (212.11, 54.00);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.08, 60.00) -- (229.08, 54.00);
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 99.31, 38.40) {10};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 99.39, 38.40) {5};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (138.62, 38.40) {100};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (116.36, 38.40) {10};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (177.93, 38.40) {1000};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (155.75, 38.40) {50};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (217.25, 38.40) {10000};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (212.11, 38.40) {500};
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- ( 60.00,217.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- ( 60.00,229.08);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 99.31) -- ( 54.00, 99.31);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 99.39) -- ( 54.00, 99.39);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,138.62) -- ( 54.00,138.62);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,116.36) -- ( 54.00,116.36);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,177.93) -- ( 54.00,177.93);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,155.75) -- ( 54.00,155.75);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,217.25) -- ( 54.00,217.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,172.72) -- ( 54.00,172.72);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,212.11) -- ( 54.00,212.11);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,229.08) -- ( 54.00,229.08);
 
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00, 95.87) {10};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00, 95.95) {5};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,135.18) {100};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,112.92) {10};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,174.49) {1000};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,152.31) {50};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,213.80) {10000};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,169.28) {100};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,208.67) {500};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,225.64) {1000};
 \end{scope}

### 2020-08-28 benchmarking/benchmarkingVM/ESS_round4b.tex
results update

% Created by tikzDevice version 0.12.3.1 on 2020-08-28 13:29:57
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (289.08,289.08);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at (144.54,253.90) {\bfseries NER (\textit{real}) vs. Bactrian (\textit{real})};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at (144.54, 14.40) {ESS/$10^6$ states [Bactrian (\textit{real})]};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at ( 21.60,144.54) {ESS/$10^6$ states [NER (\textit{real})]};
\end{scope}
\begin{scope}
\path[clip] ( 60.00, 60.00) rectangle (229.08,229.08);
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (  0.00,101.80) --
	(187.28,289.08);

\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (285.44,289.08) --
	(285.44,183.64) --
	(101.80,  0.00);
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (  0.00, 67.86) --
	(221.22,289.08);

\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (285.44,289.08) --
	(285.44,217.58) --
	( 67.86,  0.00);
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (  0.00, 33.93) --
	(255.15,289.08);

\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (285.44,289.08) --
	(285.44,251.51) --
	( 33.93,  0.00);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (170.87, 64.13) {$\frac{1}{64} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,175.57) {$64\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (136.94, 64.13) {$\frac{1}{16} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,141.64) {$16\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (101.01, 64.13) {$\frac{1}{4} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 62.56,107.71) {$4\times$};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 60.00, 60.00) -- (229.08,229.08);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (167.76,176.81) --
	(177.59,176.81);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.17,173.30) --
	(173.17,179.87);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (173.17,172.92) {$p$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (159.31,162.01) --
	(163.92,162.01);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.72,159.26) --
	(161.72,164.49);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (161.72,157.15) {$L$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.06,181.17) --
	(182.41,181.17);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.79,179.85) --
	(180.79,182.42);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (180.79,176.31) {$r$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (146.50,148.62) --
	(154.66,148.62);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.92,144.87) --
	(150.92,151.87);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (150.92,143.76) {$h$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.71,173.43) --
	(177.68,173.43);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.88,170.31) --
	(174.88,176.19);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (174.88,169.93) {$\sigma$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.73,184.14) --
	(184.51,184.14);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.12,183.29) --
	(184.12,184.97);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (184.12,180.65) {$\kappa$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (167.36,168.02) --
	(168.98,168.02);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.18,166.12) --
	(168.18,169.79);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (168.18,164.13) {$p$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.33,181.05) --
	(184.66,181.05);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.59,179.68) --
	(182.59,182.34);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (182.59,176.19) {$L$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.65,189.93) --
	(190.09,189.93);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.87,189.80) --
	(189.87,190.07);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (189.87,185.07) {$r$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.01,163.37) --
	(163.46,163.37);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (162.27,161.59) --
	(162.27,165.04);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (162.27,158.51) {$h$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.43,171.21) --
	(171.47,171.21);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (170.47,169.54) --
	(170.47,172.76);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (170.47,167.71) {$\sigma$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.11,186.84) --
	(187.84,186.84);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.47,186.09) --
	(187.47,187.56);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (187.47,183.34) {$\kappa$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (140.77,143.75) --
	(146.89,143.75);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (144.02,141.02) --
	(144.02,146.20);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (144.02,139.86) {$p$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.63,185.25) --
	(186.28,185.25);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.47,184.60) --
	(185.47,185.88);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (185.47,180.39) {$L$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.28,191.35) --
	(191.62,191.35);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.45,191.14) --
	(191.45,191.57);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (191.45,186.49) {$r$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (115.40,120.77) --
	(121.31,120.77);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (118.53,118.52) --
	(118.53,122.84);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (118.53,115.91) {$h$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (138.45,141.26) --
	(144.56,141.26);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (141.70,138.68) --
	(141.70,143.59);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (141.70,137.76) {$\sigma$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.60,189.69) --
	(190.10,189.69);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.85,189.37) --
	(189.85,190.01);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (189.85,186.19) {$\kappa$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (153.71,155.81) --
	(156.41,155.81);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (155.09,153.97) --
	(155.09,157.53);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (155.09,151.93) {$p$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.01,182.93) --
	(184.16,182.93);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.59,181.97) --
	(183.59,183.86);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (183.59,178.07) {$L$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.27,185.41) --
	(185.64,185.41);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.46,185.14) --
	(185.46,185.68);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (185.46,180.55) {$r$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.38,152.51) --
	(153.32,152.51);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.89,150.64) --
	(151.89,154.25);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (151.89,147.65) {$h$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.99,153.09) --
	(153.12,153.09);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.61,151.37) --
	(151.61,154.70);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (151.61,149.59) {$\sigma$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.48,189.88) --
	(190.12,189.88);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.80,189.64) --
	(189.80,190.12);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (189.80,186.38) {$\kappa$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.97,172.63) --
	(172.66,172.63);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (170.89,171.25) --
	(170.89,173.93);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (170.89,168.74) {$p$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.63,171.20) --
	(172.76,171.20);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.25,168.92) --
	(171.25,173.27);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (171.25,166.34) {$L$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.71,179.54) --
	(180.29,179.54);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.51,179.22) --
	(179.51,179.86);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (179.51,174.68) {$r$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (132.05,136.84) --
	(138.72,136.84);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (135.61,134.65) --
	(135.61,138.85);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (135.61,131.98) {$h$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (153.99,158.74) --
	(158.62,158.74);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (156.42,156.68) --
	(156.42,160.64);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (156.42,155.24) {$\sigma$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.12,187.39) --
	(188.09,187.39);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.61,187.21) --
	(187.61,187.56);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (187.61,183.89) {$\kappa$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (136.78,142.81) --
	(143.51,142.81);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (140.38,140.95) --
	(140.38,144.54);
\definecolor{drawColor}{RGB}{0,216,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (140.38,138.93) {$p$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.19,175.24) --
	(175.57,175.24);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.94,173.70) --
	(173.94,176.70);
\definecolor{drawColor}{RGB}{0,216,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (173.94,170.38) {$L$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.14,199.28) --
	(199.39,199.28);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.27,199.12) --
	(199.27,199.43);
\definecolor{drawColor}{RGB}{0,216,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (199.27,194.42) {$r$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.32,153.37) --
	(153.40,153.37);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.45,152.09) --
	(151.45,154.59);
\definecolor{drawColor}{RGB}{0,216,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (151.45,148.51) {$h$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (143.54,146.09) --
	(146.70,146.09);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (145.17,144.77) --
	(145.17,147.34);
\definecolor{drawColor}{RGB}{0,216,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (145.17,142.59) {$\sigma$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.59,188.58) --
	(189.30,188.58);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.95,188.00) --
	(188.95,189.16);
\definecolor{drawColor}{RGB}{0,216,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (188.95,185.09) {$\kappa$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (207.54,173.85) --
	(212.93,173.85);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (210.38,172.98) --
	(210.38,174.70);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (210.38,169.97) {$p$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.97,180.24) --
	(218.72,180.24);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (215.57,179.26) --
	(215.57,181.18);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (215.57,175.38) {$L$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.23,155.80) --
	(194.70,155.80);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.12,153.72) --
	(192.12,157.72);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (192.12,150.94) {$h$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.41,148.96) --
	(190.21,148.96);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.62,146.15) --
	(186.62,151.47);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (186.62,145.46) {$\sigma$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (223.68,189.99) --
	(229.66,189.99);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (226.85,189.40) --
	(226.85,190.57);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (226.85,186.49) {$\kappa$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (147.49,145.70) --
	(150.04,145.70);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (148.80,143.46) --
	(148.80,147.76);
\definecolor{drawColor}{RGB}{255,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (148.80,141.81) {$p$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (162.54,164.33) --
	(168.49,164.33);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (165.69,161.29) --
	(165.69,167.03);
\definecolor{drawColor}{RGB}{255,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (165.69,159.47) {$L$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.75,174.68) --
	(175.23,174.68);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.99,174.37) --
	(174.99,174.99);
\definecolor{drawColor}{RGB}{255,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (174.99,169.82) {$r$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (128.23,128.70) --
	(134.51,128.70);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (131.57,126.30) --
	(131.57,130.88);
\definecolor{drawColor}{RGB}{255,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (131.57,123.84) {$h$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.09,147.25) --
	(151.54,147.25);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.34,144.74) --
	(150.34,149.53);
\definecolor{drawColor}{RGB}{255,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (150.34,143.75) {$\sigma$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.90,187.34) --
	(187.94,187.34);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.43,186.74) --
	(187.43,187.93);
\definecolor{drawColor}{RGB}{255,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (187.43,183.84) {$\kappa$};
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (137.43,142.95) --
	(143.47,142.95);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (140.64,139.25) --
	(140.64,146.17);
\definecolor{drawColor}{RGB}{68,68,68}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (140.64,139.07) {$p$};
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (147.25,154.09) --
	(156.56,154.09);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.34,152.31) --
	(152.34,155.75);
\definecolor{drawColor}{RGB}{68,68,68}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (152.34,149.23) {$L$};
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.42,178.15) --
	(177.06,178.15);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.75,177.83) --
	(176.75,178.46);
\definecolor{drawColor}{RGB}{68,68,68}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (176.75,173.29) {$r$};
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.25,153.72) --
	(154.44,153.72);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.90,151.71) --
	(152.90,155.57);
\definecolor{drawColor}{RGB}{68,68,68}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (152.90,148.86) {$h$};
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (140.61,145.84) --
	(146.50,145.84);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (143.73,141.96) --
	(143.73,149.20);
\definecolor{drawColor}{RGB}{68,68,68}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (143.73,142.35) {$\sigma$};
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.41,188.98) --
	(189.20,188.98);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.32,187.71) --
	(188.32,190.20);
\definecolor{drawColor}{RGB}{68,68,68}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (188.32,185.48) {$\kappa$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- (229.08, 60.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- ( 60.00, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.39, 60.00) -- ( 99.39, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (116.36, 60.00) -- (116.36, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (155.75, 60.00) -- (155.75, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.72, 60.00) -- (172.72, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.11, 60.00) -- (212.11, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.08, 60.00) -- (229.08, 54.00);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 60.00, 38.40) {1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 99.39, 38.40) {5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (116.36, 38.40) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (155.75, 38.40) {50};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (212.11, 38.40) {500};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- ( 60.00,229.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- ( 54.00, 60.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 99.39) -- ( 54.00, 99.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,116.36) -- ( 54.00,116.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,155.75) -- ( 54.00,155.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,172.72) -- ( 54.00,172.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,212.11) -- ( 54.00,212.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,229.08) -- ( 54.00,229.08);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00, 56.56) {1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00, 95.95) {5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,112.92) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,152.31) {50};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,169.28) {100};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,208.67) {500};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,225.64) {1000};
\end{scope}
\begin{scope}
\path[clip] ( 60.00, 60.00) rectangle (229.08,229.08);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,171.00) rectangle (169.31,165.00);
\definecolor{fillColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,159.00) rectangle (169.31,153.00);
\definecolor{fillColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,147.00) rectangle (169.31,141.00);
\definecolor{fillColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,135.00) rectangle (169.31,129.00);
\definecolor{fillColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,123.00) rectangle (169.31,117.00);
\definecolor{fillColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,111.00) rectangle (169.31,105.00);
\definecolor{fillColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11, 99.00) rectangle (169.31, 93.00);
\definecolor{fillColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11, 87.00) rectangle (169.31, 81.00);
\definecolor{fillColor}{RGB}{68,68,68}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11, 75.00) rectangle (169.31, 69.00);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,164.56) {Ran};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,152.56) {Cognato};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,140.56) {Dornburg};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,128.56) {Sauquet};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,116.56) {Broughton};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,104.56) {Kawahara};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31, 92.56) {simulated};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31, 80.56) {Rightmyer};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31, 68.56) {Moyle};
\end{scope}
\end{tikzpicture}

\end{document}

### 2020-08-28 benchmarking/benchmarkingVM/real_quant.tex
results update

% Created by tikzDevice version 0.12.3.1 on 2020-08-28 13:28:29
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (289.08,289.08);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at (144.54,253.90) {\bfseries cons (\textit{real}) vs. cons (\textit{quant})};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at (144.54, 14.40) {ESS/$10^6$ states [cons (\textit{quant})]};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at ( 21.60,144.54) {ESS/$10^6$ states [cons (\textit{real})]};
\end{scope}
\begin{scope}
\path[clip] ( 60.00, 60.00) rectangle (229.08,229.08);
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (  0.00,101.80) --
	(187.28,289.08);

\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (285.44,289.08) --
	(285.44,183.64) --
	(101.80,  0.00);
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (  0.00, 67.86) --
	(221.22,289.08);

\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (285.44,289.08) --
	(285.44,217.58) --
	( 67.86,  0.00);
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (  0.00, 33.93) --
	(255.15,289.08);

\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (285.44,289.08) --
	(285.44,251.51) --
	( 33.93,  0.00);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (170.87, 64.13) {$\frac{1}{64} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,175.57) {$64\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (136.94, 64.13) {$\frac{1}{16} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,141.64) {$16\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (101.01, 64.13) {$\frac{1}{4} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 62.56,107.71) {$4\times$};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 60.00, 60.00) -- (229.08,229.08);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (131.42,124.31) --
	(138.80,124.31);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (135.39,111.39) --
	(135.39,132.72);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (135.39,120.42) {$p$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.18,174.84) --
	(173.91,174.84);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.21,173.44) --
	(171.21,176.16);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (171.21,169.98) {$L$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.28,179.57) --
	(179.37,179.57);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (177.88,178.07) --
	(177.88,180.98);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (177.88,174.71) {$r$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (122.73,136.83) --
	(137.12,136.83);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (130.97,131.62) --
	(130.97,141.12);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (130.97,131.97) {$h$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 83.23, 99.13) --
	(109.45, 99.13);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 99.70, 77.96) --
	( 99.70,110.31);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 99.70, 95.63) {$\sigma$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.45,184.26) --
	(185.17,184.26);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.32,183.58) --
	(184.32,184.93);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (184.32,180.76) {$\kappa$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (166.82,174.59) --
	(170.29,174.59);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.62,173.35) --
	(168.62,175.77);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (168.62,170.70) {$p$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.97,180.59) --
	(183.40,180.59);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.75,179.08) --
	(181.75,182.02);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (181.75,175.73) {$L$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.88,183.24) --
	(187.36,183.24);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.12,183.09) --
	(187.12,183.39);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (187.12,178.38) {$r$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (158.73,158.55) --
	(162.43,158.55);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (160.65,157.35) --
	(160.65,159.70);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (160.65,153.69) {$h$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.42,163.01) --
	(166.38,163.01);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (165.42,161.57) --
	(165.42,164.37);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (165.42,159.51) {$\sigma$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.37,187.15) --
	(187.37,187.15);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.88,186.65) --
	(186.88,187.64);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (186.88,183.65) {$\kappa$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (128.96,141.26) --
	(132.92,141.26);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (131.02,136.36) --
	(131.02,145.35);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (131.02,137.37) {$p$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.13,182.75) --
	(185.22,182.75);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.20,181.54) --
	(184.20,183.90);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (184.20,177.89) {$L$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.05,184.94) --
	(189.27,184.94);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.16,184.72) --
	(189.16,185.16);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (189.16,180.08) {$r$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (110.63,108.09) --
	(115.45,108.09);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (113.16,104.98) --
	(113.16,110.85);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (113.16,103.23) {$h$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (135.73,133.77) --
	(142.18,133.77);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (139.17,129.42) --
	(139.17,137.45);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (139.17,130.27) {$\sigma$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.68,189.39) --
	(189.15,189.39);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.91,189.03) --
	(188.91,189.75);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (188.91,185.89) {$\kappa$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (148.70,149.48) --
	(153.74,149.48);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.35,147.58) --
	(151.35,151.24);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (151.35,145.59) {$p$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.27,182.67) --
	(185.44,182.67);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.38,181.56) --
	(184.38,183.73);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (184.38,177.81) {$L$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.91,181.87) --
	(186.60,181.87);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.26,181.76) --
	(186.26,181.98);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (186.26,177.01) {$r$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (148.47,142.60) --
	(151.60,142.60);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.08,141.76) --
	(150.08,143.42);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (150.08,137.74) {$h$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (145.65,139.10) --
	(148.86,139.10);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (147.31,137.22) --
	(147.31,140.84);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (147.31,135.60) {$\sigma$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.26,190.07) --
	(189.90,190.07);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.59,189.78) --
	(189.59,190.34);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (189.59,186.57) {$\kappa$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (114.91,143.39) --
	(129.67,143.39);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (123.38,139.51) {$p$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.78,178.75) --
	(177.87,178.75);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (176.37,173.89) {$L$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.61,179.03) --
	(179.05,179.03);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (178.83,174.17) {$r$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (123.69,128.13) --
	(125.94,128.13);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (124.84,123.27) {$h$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (104.43,114.81) --
	(113.76,114.81);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (109.53,111.31) {$\sigma$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.44,187.14) --
	(185.36,187.14);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (184.42,183.64) {$\kappa$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.38,154.25) --
	(173.74,154.25);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.59,151.40) --
	(172.59,156.80);
\definecolor{drawColor}{RGB}{0,216,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (172.59,150.36) {$p$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (177.57,171.37) --
	(180.01,171.37);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.82,169.38) --
	(178.82,173.21);
\definecolor{drawColor}{RGB}{0,216,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (178.82,166.51) {$L$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.94,181.11) --
	(190.18,181.11);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.06,180.89) --
	(190.06,181.32);
\definecolor{drawColor}{RGB}{0,216,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (190.06,176.25) {$r$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (147.44,145.09) --
	(152.32,145.09);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.00,143.40) --
	(150.00,146.68);
\definecolor{drawColor}{RGB}{0,216,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (150.00,140.23) {$h$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (160.50,154.07) --
	(164.51,154.07);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (162.59,152.64) --
	(162.59,155.42);
\definecolor{drawColor}{RGB}{0,216,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (162.59,150.57) {$\sigma$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.53,189.11) --
	(189.25,189.11);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.89,188.58) --
	(188.89,189.63);
\definecolor{drawColor}{RGB}{0,216,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (188.89,185.61) {$\kappa$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (136.01,171.46) --
	(140.32,171.46);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (138.26,169.40) --
	(138.26,173.37);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (138.26,167.58) {$p$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.25,179.54) --
	(186.69,179.54);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.98,178.93) --
	(185.98,180.13);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (185.98,174.68) {$L$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.11,181.86) --
	(188.27,181.86);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.70,181.70) --
	(187.70,182.02);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (187.70,177.00) {$r$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (153.01,147.94) --
	(158.96,147.94);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (156.17,146.11) --
	(156.17,149.65);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (156.17,143.08) {$h$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (141.92,143.23) --
	(145.49,143.23);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (143.77,141.57) --
	(143.77,144.79);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (143.77,139.74) {$\sigma$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.68,189.95) --
	(193.06,189.95);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.38,188.73) --
	(192.38,191.12);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (192.38,186.45) {$\kappa$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.99,154.00) --
	(152.95,154.00);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.52,152.67) --
	(151.52,155.26);
\definecolor{drawColor}{RGB}{255,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (151.52,150.11) {$p$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (163.79,162.43) --
	(165.59,162.43);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.71,159.25) --
	(164.71,165.25);
\definecolor{drawColor}{RGB}{255,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (164.71,157.57) {$L$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.53,164.23) --
	(170.09,164.23);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.81,163.98) --
	(169.81,164.47);
\definecolor{drawColor}{RGB}{255,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (169.81,159.37) {$r$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (135.62,125.66) --
	(142.27,125.66);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (139.17,120.15) --
	(139.17,130.16);
\definecolor{drawColor}{RGB}{255,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (139.17,120.80) {$h$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.90,145.25) --
	(153.10,145.25);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.55,143.86) --
	(151.55,146.57);
\definecolor{drawColor}{RGB}{255,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (151.55,141.76) {$\sigma$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.09,187.46) --
	(187.51,187.46);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.81,186.96) --
	(186.81,187.95);
\definecolor{drawColor}{RGB}{255,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (186.81,183.96) {$\kappa$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- (229.08, 60.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- ( 60.00, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.39, 60.00) -- ( 99.39, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (116.36, 60.00) -- (116.36, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (155.75, 60.00) -- (155.75, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.72, 60.00) -- (172.72, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.11, 60.00) -- (212.11, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.08, 60.00) -- (229.08, 54.00);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 60.00, 38.40) {1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 99.39, 38.40) {5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (116.36, 38.40) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (155.75, 38.40) {50};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (212.11, 38.40) {500};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- ( 60.00,229.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- ( 54.00, 60.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 99.39) -- ( 54.00, 99.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,116.36) -- ( 54.00,116.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,155.75) -- ( 54.00,155.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,172.72) -- ( 54.00,172.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,212.11) -- ( 54.00,212.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,229.08) -- ( 54.00,229.08);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00, 56.56) {1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00, 95.95) {5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,112.92) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,152.31) {50};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,169.28) {100};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,208.67) {500};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,225.64) {1000};
\end{scope}
\begin{scope}
\path[clip] ( 60.00, 60.00) rectangle (229.08,229.08);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,171.00) rectangle (169.31,165.00);
\definecolor{fillColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,159.00) rectangle (169.31,153.00);
\definecolor{fillColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,147.00) rectangle (169.31,141.00);
\definecolor{fillColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,135.00) rectangle (169.31,129.00);
\definecolor{fillColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,123.00) rectangle (169.31,117.00);
\definecolor{fillColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,111.00) rectangle (169.31,105.00);
\definecolor{fillColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11, 99.00) rectangle (169.31, 93.00);
\definecolor{fillColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11, 87.00) rectangle (169.31, 81.00);
\definecolor{fillColor}{RGB}{68,68,68}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11, 75.00) rectangle (169.31, 69.00);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,164.56) {Ran};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,152.56) {Cognato};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,140.56) {Dornburg};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,128.56) {Sauquet};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,116.56) {Broughton};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,104.56) {Kawahara};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31, 92.56) {simulated};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31, 80.56) {Rightmyer};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31, 68.56) {Moyle};
\end{scope}
\end{tikzpicture}

\end{document}

### 2020-08-28 manuscript.tex
results update

@@
 Here, we present the \texttt{NarrowExchangeRate} (NER) operator. 
-Let $r_A$, $r_B$, $r_C$, and $r_D$ be the clock rates of nodes $A$, $B$, $C$, and $D$, respectively. 
-In addition to the modest topological change applied by \texttt{NarrowExchange}, NER also proposes new clock rates ${r_A}^\prime$, ${r_B}^\prime$, ${r_C}^\prime$, and ${r_D}^\prime$.
+Let $r_A$, $r_B$, $r_C$, and $r_D$ be the substitution rates of nodes $A$, $B$, $C$, and $D$, respectively. 
+In addition to the modest topological change applied by \texttt{NarrowExchange}, NER also proposes new branch rates ${r_A}^\prime$, ${r_B}^\prime$, ${r_C}^\prime$, and ${r_D}^\prime$.
 While NER does not alter $t_D$ (i.e.
@@
 \clearpage
-\subsection*{A guided adaptive leaf rate operator}
+\subsection*{An adaptive leaf rate operator}
 \label{AVMVN_sect}
 
-A \textit{guided} operator incorporates knowledge about neighbouring states, while an \textit{adaptive} operator undergoes a training process to improve its efficiency over time \cite{roberts2007coupling}.
-In previous work, parsimony scores and conditional clade probabilities of neighbouring trees have been employed by guided tree operators \cite{hohna2012guided,zhang2020using,meyer2019adaptive} and the latter has also been explored as the basis of  adaptive tree operators \cite{hohna2012guided,meyer2019adaptive}.
-The (adaptive) mirror kernel \cite{thawornwattana2018designing} learns a target distribution which acts as a `mirror image' of the current point $x$.
-The adaptable variance multivariate normal (AVMVN) kernel \cite{baele2017adaptive,suchard2018bayesian} learns correlations between parameters during MCMC.
+%, such as \texttt{AdaptiveOperatorSampler},
+Adaptive operators undergo a training process to improve their efficiency over time \cite{roberts2007coupling}. 
+For example, the conditional clade probabilities of neighbouring trees can serve as the basis of adaptive tree operators \cite{hohna2012guided,zhang2020using,meyer2019adaptive},
+and the mirror kernel learns a target distribution which acts as a `mirror image' of the current point $x$ \cite{thawornwattana2018designing}.  
+The \texttt{AdaptiveOperatorSampler} operator, introduced in this article, learns the weight of sub-operators.
+Finally, the adaptable variance multivariate normal (AVMVN) kernel  learns correlations between parameters during MCMC \cite{baele2017adaptive,suchard2018bayesian}.
 Baele et al.
-2017  observed a large increase ($\approx 5-10 \times$) in sampling efficiency from using the AVMVN kernel on clock rates and substitution model parameters across partitions \cite{baele2017adaptive}.
+2017  observed a large increase ($\approx 5-10 \times$) in sampling efficiency from using the AVMVN kernel on clock rates XXX(check)XXX and substitution model parameters across partitions \cite{baele2017adaptive}.
 
@@
 Furthermore, the adapt setup dramatically improved mixing for \textit{real} by finding the right balance between cons and nocons.
-This yielded an average ESS/hr of XXX times that of cons and YYY times that of nocons, with respect to leaf branch rates.   
-However adapt did not improve \textit{cat} or \textit{quant}, suggesting that the default operator weighting scheme was sufficient in either case.
+This yielded an ESS/hr (averaged across all 9 datasets) 80\% faster than cons and 120\% faster than nocons, with respect to leaf branch rates, and 250\% and 1800\% faster for $\sigma$.
+Similar results were observed with \textit{quant}.
+However adapt neither helped nor harmed \textit{cat}, suggesting that the default operator weighting scheme was sufficient.
 Overall, the \texttt{AdaptiveOperatorSampler} operator will be included in all subsequent rounds in the tournament.
@@
 \clearpage
-\subsection*{Round 2: The \textit{real} parameterisation yields the fastest mixing }
+\subsection*{Round 2: The \textit{real} parameterisation yielded the fastest mixing }
 
@@
 We benchmarked the adapt (\textit{real}) configuration with a) standard uniform proposal kernels, and b) Bactrian(0.95) kernels.
-These kernels applied to all clock rate related operators (\textbf{Table \ref{table:bactriankernels}}).
+These kernels applied to all clock model related operators (\textbf{Table \ref{table:bactriankernels}}).
 
@@
 In this round we benchmarked the adapt + Bactrian(0.95) (\textit{real})  setting with a) $\text{NER} \{\}$ only, and b) adaptive $\text{NER}$ (\textbf{Table \ref{table:operatorSchemes}}).
+
+Our experiments confirmed that $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ is indeed superior on larger datasets (where $L > 1$kb; \textbf{Fig. \ref{fig:round4Results}}).
+Whereas, on smaller datasets the standard \texttt{NarrowExchange} operator had a higher acceptance rate.
+Using an adaptive operator (\texttt{AdaptiveOperatorSampler}) removes the burden from the user in selecting which operator is the best pick.
+The average acceptance rate of
+
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{benchmarking/benchmarkingVM/ESS_round4.pdf}
+\caption{\textbf{Round 4: benchmarking the NER operators.} 
+The learned weights (left) behind the two NER operators ($\text{NER} \{\}$ and $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$), and the relative difference between their acceptance rates $\alpha$ (right), are presented as functions of sequence length.
+Logistic and linear regression models are shown, respectively. }
+\label{fig:round4Results}
+\end{figure}
 

### 2020-08-28 benchmarking/benchmarkingVM/CStemplate.sh

@@ -1,0 +1,24 @@
+#!/bin/bash -e
+
+#SBATCH --job-name   	 JOBID
+#SBATCH --account    	 nesi00390
+#SBATCH --time       	 TOTALTIME:00:00
+#SBATCH --ntasks     	 1
+#SBATCH --nodes	     	 1
+#SBATCH --mem		 	 MEMORY
+#SBATCH --cpus-per-task	 4
+#SBATCH --output    	 JOBID.txt
+#SBATCH --error      	 JOBID.err
+
+
+module load beagle-lib/3.0.1-gimkl-2017a
+module load Java/1.8.0_144
+
+
+~/beast/bin/beast -seed RANDOMSEED -overwrite -beagle_SSE tmp.xml
+rm tmp.xml
+
+
+
+
+

### 2020-08-28 benchmarking/benchmarkingVM/submit_Nesi.sh

@@ -1,0 +1,118 @@
+#!/bin/sh
+
+
+
+TEMPLATE="../../../../../CStemplate.sh"
+
+#settings=("real" "real_adaptive" "cat" "quant" "AVMN" "bactrian98" "bactrian95" "NER" "real_06" "quant_06")
+settings=("cat" "cat_adaptive" "real" "real_06" "real_adaptive" "quant_cached" "quant_cached_adaptive" "quant_06_cached" "bactrian95" "NER")
+
+datasets=("simulated" "Ran_2018_dna" "Rightmyer_2013" "Broughton_2013" "Sauquet_2011" "Moyle_2016" "Dornburg_2012" "Kawahara_2013" "Cognato_2001")
+
+
+
+
+# Randomly shuffle the datasets
+#datasets_shuffled=( $(shuf -e "${datasets[@]}") )
+
+for d in ${datasets[@]} ; do
+    echo "$d"
+    cd $d
+
+	dshort="${d:0:4}"
+
+    for e in */ ; do
+        echo "$e"
+        cd $e
+
+
+			eshort="${e%?}"
+
+          # Randomly shuffle the settings
+          settings_shuffled=( $(shuf -e "${settings[@]}") )
+          for s in "${settings_shuffled[@]}"
+          do
+		  
+			mkdir -p $s
+			rm -f Batch*
+			cd $s
+	  
+			for ((i=1;i<=20;i++)); do
+			
+				mkdir -p "Batch$i"
+				cd "Batch$i"
+				rand=$RANDOM
+				echo "Dispatching ${dshort}${i}_${s} with seed $rand"
+				sed "s/JOBID/${dshort}${i}_${s}/g" ${TEMPLATE} > temp.sl
+				sed "s/RANDOMSEED/$rand/g" temp.sl > temp2.sl
+				sed "s/DATASET/$d/g" temp2.sl > temp.sl
+				sed "s/SETTING/$s/g" temp.sl > temp2.sl
+				sed "s/PARTITION/${eshort}/g" temp2.sl > temp.sl
+				
+				
+				
+				if [ "$d" == "Ran_2018_dna" ] || [ "$d" == "Broughton_2013" ]  || [ "$d" == "Rightmyer_2013" ]; then
+					
+					echo "Big job"
+					sed "s/TOTALTIME/60/g" temp.sl > temp2.sl
+					sed "s/MEMORY/8000/g" temp2.sl > temp.sl
+					
+					
+				else
+				
+					echo "Small job"
[…]

### 2020-08-28 benchmarking/plotBenchmark.R

@@ -1,914 +1,0 @@
-
-library(tikzDevice)
-library(HDInterval)
-library(lubridate)
-
-
-
-
-#settings = c("cat",  "real_06", "quant_06", "real", "quant", "bactrian95", "bactrian98", "NER", "AVMN")
-settings = c("real", "real_adaptive", "real_06")
-
-benchmark = data.frame(batch = numeric(0), param = character(0), dataset = character(0), partition = numeric(0), setting = character(0), nstates = numeric(0), finalESS = numeric(0), finalMCD = numeric(0), done = logical(0),  error = logical(0))
-
-
-latex.table = read.table("/home/jdou557/Documents/Marsden2019/Months/January2020/fromVM/latex.table", sep = "&")
-colnames(latex.table) = c("ID", "N", "P", "L", "Leff", "ref")
-latex.table$ref = gsub(" ", "", gsub("[0-9].+", "", latex.table$ref))
-
-
-
-latex.table$completion = ""
-
-progress.df = read.csv("progress.csv", header = T)
-progress.df$batch = ifelse(progress.df$batch == 4, 5, ifelse(progress.df$batch == 5, 4, progress.df$batch))
-
-
-parameters = c("posterior", "likelihood", "prior", "treeLength", "height", "birthRate", "kappa",  "freqParameter", "ucldStdev", "clockRate", "TipRates", "RateStatLogger.mean", "RateStatLogger.variance")
-
-
-parameters.latex = lapply(parameters, function(x) x)
-names(parameters.latex) = parameters
-parameters.latex["posterior"] = "Posterior $P(\\theta|D)$"
-parameters.latex["likelihood"] = "Likelihood $P(D|\\theta)$"
-parameters.latex["prior"] = "Prior $P(\\theta)$"
-parameters.latex["birthRate"] = "Yule birth rate $\\lambda$"
-parameters.latex["gammaShape"] = "$\\Gamma$ shape"
-parameters.latex["kappa"] = "$\\kappa$"
-parameters.latex["freqParameter"] = "Nucleotide frequency $f$"
-parameters.latex["ucldStdev"] = "Clock SD $\\sigma$"
-parameters.latex["TipRates"] = "Mean tip rate $r$"
-parameters.latex["treeLength"] = "Tree length $l$"
-parameters.latex["height"] = "Tree height $h$"
-
-
-getDateTime = function(str){
-
[…]

### 2020-08-28 benchmarking/render.R

@@ -7,7 +7,7 @@ library(rjson)
 
 
 
-PER_CHAIN = FALSE
+PER_CHAIN = TRUE
 
 #settings = c("cat", "real", "quant", "bactrian95", "bactrian98")
 settings = c("cat",  "real_06", "quant_06", "real", "quant", "bactrian95", "bactrian98", "NER", "AVMN")
@@ -99,9 +99,9 @@ getDateTime = function(str){
 
 
 ESS.df = data.frame(batch = numeric(0), param = character(0), dataset = character(0), partition = numeric(0), setting = character(0), nstates = numeric(0),
-		ESS = numeric(0), hr = numeric(0), ESS.hr = numeric(0), Leff = numeric(0), L = numeric(0), N = numeric(0), mean.speed = numeric(0), 
+		ESS = numeric(0), hr = numeric(0), ESS.hr = numeric(0), Leff = numeric(0), L = numeric(0), N = numeric(0), sigma = numeric(0),
 		CD_weight = numeric(0), RW_weight = numeric(0), SPP_weight = numeric(0), NER_weight = numeric(0), NER_acc = numeric(0), NE_acc = numeric(0),
-		correctBactrian = logical(0))
+		 nsamples = numeric(0))
 
 
 
@@ -110,7 +110,7 @@ ESS.df = data.frame(batch = numeric(0), param = character(0), dataset = characte
 speed.df = data.frame(batch = numeric(0), dataset = character(0), setting = character(0), state = numeric(0), speed = numeric(0))
 
 # For each batch
-batchfolders = list.dirs(recursive = F)
+batchfolders = "BatchN" #list.dirs(recursive = F)
 for (f in batchfolders){
 
 	print(f)
@@ -127,9 +127,6 @@ for (f in batchfolders){
 
 		print(d)
 
-
-		#if (d == "./Fong_2012" | d == "./McCormack_2013") next
-		
 
 		dataset = substring(d, 3)
 		matching_row_num = sapply(latex.table$ref, function(pattern) length(grep(pattern, dataset)) > 0)
@@ -166,168 +163,137 @@ for (f in batchfolders){
 				for (s in settings) {
 
 
-
-
-
-				
-					# Read in output file
+					setwd(s)
 					
-					fileName = paste0("error_", s, ".err")
-					if (!file.exists(fileName)) {
-						#print("Error cannot file file")
-						#next
-					}
-					#output_in = readLines(fileName)
-
-
-					# Is it done?
[…]

### 2020-08-29 benchmarking/benchmarkingVM/ESS_round1_catquant.tex
results update

@@
-% Created by tikzDevice version 0.12.3.1 on 2020-08-28 13:29:15
+% Created by tikzDevice version 0.12.3.1 on 2020-08-29 17:34:20
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 70.80,423.36) --
-	( 93.23,423.36);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 84.25,418.92) --
-	( 84.25,427.19);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 84.25,420.14) {$p$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (148.42,463.51) --
-	(187.31,463.51);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.24,460.11) --
-	(174.24,466.53);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.24,459.48) {$L$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 73.08,470.98) --
-	( 83.11,470.98);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 78.55,469.19) --
-	( 78.55,472.65);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 78.55,466.94) {$r$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 64.94,418.41) --
-	(105.90,418.41);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 92.45,409.17) --
-	( 92.45,425.31);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 92.45,414.38) {$h$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (  0.00,383.37) --
-	( 89.39,383.37);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 70.64,364.91) --
-	( 70.64,394.30);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 70.64,380.46) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.11,478.20) --
-	(192.04,478.20);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.62,477.22) --
-	(190.62,479.15);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.62,475.30) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 82.42,418.44) --
+	(101.58,418.44);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 93.64,413.11) --
+	( 93.64,422.90);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 93.64,415.21) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (177.17,466.47) --
+	(183.46,466.47);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.49,463.51) --
+	(180.49,469.14);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.49,462.43) {$L$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 81.91,470.49) --
+	( 89.03,470.49);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 85.70,469.68) --
+	( 85.70,471.27);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 85.70,466.46) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 78.93,418.74) --
+	( 98.83,418.74);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 90.64,413.20) --
+	( 90.64,423.35);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 90.64,414.71) {$l$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 87.59,376.12) --
+	( 98.21,376.12);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 93.41,371.04) --
+	( 93.41,380.41);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 93.41,373.21) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.25,479.34) --
+	(191.96,479.34);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.12,478.87) --
+	(191.12,479.80);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.12,476.43) {$\kappa$};
 \definecolor{drawColor}{RGB}{253,104,0}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (162.07,451.67) --
-	(165.83,451.67);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.01,449.52) --
-	(164.01,453.66);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (164.01,447.64) {$h$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.29,456.73) --
+	(174.60,456.73);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.47,455.02) --
+	(173.47,458.33);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.47,452.69) {$l$};
 \definecolor{drawColor}{RGB}{253,104,0}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 97.72,398.46) --
-	(103.70,398.46);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (100.88,395.62) --
-	(100.88,401.02);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (100.88,394.42) {$h$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (106.92,412.94) --
+	(112.96,412.94);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (110.11,410.95) --
+	(110.11,414.80);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (110.11,408.91) {$l$};
 \definecolor{drawColor}{RGB}{143,161,0}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (123.31,439.83) --
-	(129.99,439.83);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (126.85,438.03) --
-	(126.85,441.53);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (126.85,435.80) {$h$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (127.67,440.72) --
+	(133.30,440.72);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (130.63,438.76) --
+	(130.63,442.54);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (130.63,436.68) {$l$};
 \definecolor{drawColor}{RGB}{0,195,0}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 99.42,409.91) --
-	(113.41,409.91);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (107.30,400.41) --
-	(107.30,416.95);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (107.30,406.68) {$p$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.90,469.29) --
-	(192.29,469.29);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.73,467.51) --
-	(189.73,470.97);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (189.73,465.26) {$L$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.49,472.05) --
-	(150.55,472.05);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.03,471.80) --
-	(150.03,472.30);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (150.03,468.02) {$r$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 89.71,411.55) --
-	(110.93,411.55);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (102.32,410.26) --
-	(102.32,412.78);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (102.32,407.51) {$h$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (106.50,394.39) --
-	(115.04,394.39);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (111.10,388.67) --
-	(111.10,399.12);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (111.10,391.49) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.74,478.31) --
-	(191.06,478.31);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.41,477.22) --
-	(190.41,479.36);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.41,475.41) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (105.48,413.51) --
+	(113.85,413.51);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (109.98,411.22) --
+	(109.98,415.63);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (109.98,410.29) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.73,472.93) --
+	(192.09,472.93);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.94,469.80) --
+	(190.94,475.74);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.94,468.90) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.70,473.83) --
+	(152.55,473.83);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.13,473.43) --
+	(152.13,474.22);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (152.13,469.80) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (104.58,414.60) --
+	(113.08,414.60);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (109.15,412.46) --
+	(109.15,416.59);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (109.15,410.57) {$l$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (106.80,396.71) --
+	(118.52,396.71);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (113.28,394.41) --
+	(113.28,398.84);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (113.28,393.81) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.38,480.86) --
+	(193.35,480.86);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.87,480.61) --
+	(192.87,481.11);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.87,477.96) {$\kappa$};
 \definecolor{drawColor}{RGB}{0,216,255}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.69,439.74) --
-	(153.31,439.74);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.56,436.87) --
-	(151.56,442.34);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (151.56,435.71) {$h$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.34,462.49) --
+	(183.19,462.49);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.80,461.19) --
+	(181.80,463.73);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.80,458.46) {$l$};
 \definecolor{drawColor}{RGB}{0,216,255}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (130.42,446.65) --
-	(136.31,446.65);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (133.52,443.11) --
-	(133.52,449.78);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (133.52,442.62) {$h$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (126.28,427.38) --
+	(133.41,427.38);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (130.08,424.75) --
+	(130.08,429.78);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (130.08,423.34) {$l$};
 \definecolor{drawColor}{RGB}{151,0,255}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (155.64,441.44) --
-	(160.72,441.44);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (158.30,439.73) --
-	(158.30,443.05);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.30,438.21) {$p$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (166.43,456.22) --
-	(176.68,456.22);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.03,455.20) --
-	(172.03,457.21);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.03,452.19) {$L$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (177.52,461.94) --
-	(178.35,461.94);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (177.93,461.63) --
-	(177.93,462.26);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.93,457.91) {$r$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (136.50,427.60) --
-	(144.46,427.60);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (140.77,423.63) --
-	(140.77,431.08);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (140.77,423.57) {$h$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.18,441.48) --
-	(163.87,441.48);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (162.56,439.63) --
-	(162.56,443.22);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (162.56,438.58) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.23,480.99) --
-	(193.16,480.99);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.70,480.18) --
-	(192.70,481.77);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.70,478.08) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (156.24,440.75) --
+	(160.08,440.75);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (158.23,438.87) --
+	(158.23,442.51);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.23,437.52) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (167.80,456.00) --
+	(175.12,456.00);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.71,455.05) --
+	(171.71,456.92);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.71,451.97) {$L$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (177.64,461.90) --
+	(178.22,461.90);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (177.93,461.64) --
+	(177.93,462.15);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.93,457.86) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (154.82,439.25) --
+	(158.45,439.25);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (156.70,437.53) --
+	(156.70,440.86);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (156.70,435.21) {$l$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (159.76,440.57) --
+	(163.69,440.57);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.79,438.58) --
+	(161.79,442.42);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (161.79,437.67) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.88,481.15) --
+	(192.99,481.15);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.44,480.48) --
+	(192.44,481.81);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.44,478.25) {$\kappa$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.05,449.43) --
+	(174.01,449.43);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.04,448.15) --
+	(173.04,450.65);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.04,446.20) {$p$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (153.68,442.46) --
+	(157.19,442.46);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (155.49,440.09) --
+	(155.49,444.64);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (155.49,438.42) {$L$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.66,462.32) --
+	(178.93,462.32);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.80,462.06) --
+	(178.80,462.58);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (178.80,458.29) {$r$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.95,448.96) --
+	(173.63,448.96);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.80,447.45) --
+	(172.80,450.38);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.80,444.92) {$l$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (162.14,442.09) --
+	(165.67,442.09);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (163.96,441.11) --
+	(163.96,443.04);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (163.96,439.19) {$\sigma$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.89,484.25) --
+	(196.26,484.25);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.59,483.78) --
+	(195.59,484.72);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.59,481.35) {$\kappa$};
 \end{scope}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (359.88,438.13) --
-	(382.31,438.13);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (373.33,433.43) --
-	(373.33,442.14);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (373.33,434.90) {$p$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (437.50,456.44) --
-	(476.39,456.44);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (463.32,453.88) --
-	(463.32,458.79);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (463.32,452.41) {$L$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (362.16,475.42) --
-	(372.19,475.42);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (367.63,474.25) --
-	(367.63,476.55);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (367.63,471.39) {$r$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (354.02,428.85) --
-	(394.98,428.85);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (381.53,416.26) --
-	(381.53,437.45);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (381.53,424.82) {$h$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (250.87,453.94) --
-	(378.47,453.94);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (359.72,449.40) --
-	(359.72,457.84);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (359.72,451.04) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (478.19,480.12) --
-	(481.12,480.12);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (479.70,479.30) --
-	(479.70,480.91);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (479.70,477.22) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (371.50,435.89) --
+	(390.66,435.89);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (382.72,433.60) --
+	(382.72,438.01);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (382.72,432.67) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (466.25,452.57) --
+	(472.54,452.57);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (469.57,448.91) --
+	(469.57,455.81);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (469.57,448.54) {$L$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (370.99,473.43) --
+	(378.11,473.43);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (374.78,472.65) --
+	(374.78,474.19);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (374.78,469.40) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (368.01,434.69) --
+	(387.91,434.69);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (379.72,432.46) --
+	(379.72,436.75);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (379.72,430.66) {$l$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (376.67,451.88) --
+	(387.29,451.88);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (382.49,448.72) --
+	(382.49,454.72);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (382.49,448.98) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (479.33,479.96) --
+	(481.04,479.96);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.20,479.17) --
+	(480.20,480.73);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (480.20,477.06) {$\kappa$};
 \definecolor{drawColor}{RGB}{253,104,0}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (451.15,455.62) --
-	(454.91,455.62);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (453.09,454.14) --
-	(453.09,457.03);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (453.09,451.59) {$h$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (461.37,462.46) --
+	(463.68,462.46);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (462.55,461.30) --
+	(462.55,463.57);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (462.55,458.43) {$l$};
 \definecolor{drawColor}{RGB}{253,104,0}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (386.80,409.36) --
-	(392.78,409.36);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (389.96,407.67) --
-	(389.96,410.96);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (389.96,405.33) {$h$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (396.00,421.79) --
+	(402.04,421.79);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (399.19,419.43) --
+	(399.19,423.96);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (399.19,417.76) {$l$};
 \definecolor{drawColor}{RGB}{143,161,0}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (418.93,448.30) --
-	(424.57,448.30);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (421.90,445.38) --
-	(421.90,450.94);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (421.90,445.07) {$p$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.68,483.20) --
-	(485.79,483.20);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (484.76,482.06) --
-	(484.76,484.31);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (484.76,479.17) {$L$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (471.28,483.39) --
-	(472.99,483.39);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (472.14,482.50) --
-	(472.14,484.26);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (472.14,479.36) {$r$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (412.39,447.57) --
-	(419.07,447.57);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (415.93,444.38) --
-	(415.93,450.43);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (415.93,443.54) {$h$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (422.39,456.30) --
-	(430.14,456.30);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (426.54,453.54) --
-	(426.54,458.81);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (426.54,453.40) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.21,485.06) --
-	(485.10,485.06);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (484.17,483.93) --
-	(484.17,486.13);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (484.17,482.15) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (388.50,414.28) --
-	(402.49,414.28);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (396.38,410.38) --
-	(396.38,417.69);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (396.38,411.05) {$p$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (475.98,464.34) --
-	(481.37,464.34);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (478.81,461.59) --
-	(478.81,466.85);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (478.81,460.31) {$L$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (438.57,472.21) --
-	(439.63,472.21);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (439.11,471.57) --
-	(439.11,472.84);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (439.11,468.18) {$r$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (378.79,418.44) --
-	(400.01,418.44);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (391.40,413.15) --
-	(391.40,422.88);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (391.40,414.41) {$h$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (395.58,431.44) --
-	(404.12,431.44);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (400.18,417.90) --
-	(400.18,440.46);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (400.18,428.53) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (478.82,479.21) --
-	(480.14,479.21);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (479.49,478.51) --
-	(479.49,479.89);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (479.49,476.30) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (418.93,448.69) --
+	(424.57,448.69);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (421.90,446.00) --
+	(421.90,451.13);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (421.90,445.46) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.68,483.39) --
+	(485.79,483.39);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (484.76,482.30) --
+	(484.76,484.44);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (484.76,479.36) {$L$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (471.28,483.68) --
+	(472.99,483.68);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (472.14,482.69) --
+	(472.14,484.64);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (472.14,479.65) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (416.75,446.99) --
+	(422.38,446.99);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (419.71,444.38) --
+	(419.71,449.37);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (419.71,442.96) {$l$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (422.39,456.86) --
+	(430.14,456.86);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (426.54,454.18) --
+	(426.54,459.31);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (426.54,453.96) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.21,485.34) --
+	(485.10,485.34);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (484.17,484.19) --
+	(484.17,486.45);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (484.17,482.44) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (394.56,415.59) --
+	(402.93,415.59);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (399.06,412.36) --
+	(399.06,418.49);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (399.06,412.37) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (478.81,465.76) --
+	(481.17,465.76);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.02,463.80) --
+	(480.02,467.60);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (480.02,461.73) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (440.78,472.94) --
+	(441.63,472.94);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (441.21,472.44) --
+	(441.21,473.42);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (441.21,468.90) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (393.66,415.20) --
+	(402.16,415.20);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (398.23,411.87) --
+	(398.23,418.17);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (398.23,411.17) {$l$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (395.88,435.27) --
+	(407.60,435.27);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (402.36,431.31) --
+	(402.36,438.72);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (402.36,432.36) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.46,481.15) --
+	(482.43,481.15);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.95,480.69) --
+	(481.95,481.60);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (481.95,478.25) {$\kappa$};
 \definecolor{drawColor}{RGB}{0,216,255}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (438.77,444.49) --
-	(442.39,444.49);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (440.64,442.00) --
-	(440.64,446.77);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (440.64,440.45) {$h$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (469.42,476.37) --
+	(472.27,476.37);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (470.88,475.07) --
+	(470.88,477.61);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (470.88,472.34) {$l$};
 \definecolor{drawColor}{RGB}{0,216,255}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (419.50,443.20) --
-	(425.39,443.20);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (422.60,439.70) --
-	(422.60,446.30);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (422.60,439.17) {$h$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (415.36,428.89) --
+	(422.49,428.89);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (419.16,425.48) --
+	(419.16,431.93);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (419.16,424.86) {$l$};
 \definecolor{drawColor}{RGB}{151,0,255}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (444.72,448.44) --
-	(449.80,448.44);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (447.38,445.70) --
-	(447.38,450.93);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (447.38,445.21) {$p$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (455.51,463.89) --
-	(465.76,463.89);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (461.11,462.95) --
-	(461.11,464.79);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (461.11,459.85) {$L$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (466.60,469.57) --
-	(467.43,469.57);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (467.01,469.18) --
-	(467.01,469.94);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (467.01,465.53) {$r$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (425.58,426.15) --
-	(433.54,426.15);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (429.85,423.97) --
-	(429.85,428.18);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (429.85,422.12) {$h$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (450.26,456.41) --
-	(452.95,456.41);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (451.64,454.54) --
-	(451.64,458.16);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (451.64,453.50) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.31,482.11) --
-	(482.24,482.11);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.78,481.47) --
-	(481.78,482.74);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (481.78,479.21) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (445.32,449.25) --
+	(449.16,449.25);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (447.31,446.87) --
+	(447.31,451.45);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (447.31,446.02) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (456.88,463.59) --
+	(464.20,463.59);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (460.79,462.04) --
+	(460.79,465.06);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (460.79,459.56) {$L$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (466.72,469.62) --
+	(467.30,469.62);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (467.01,469.33) --
+	(467.01,469.91);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (467.01,465.59) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (443.90,447.90) --
+	(447.53,447.90);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (445.78,445.62) --
+	(445.78,450.01);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (445.78,443.87) {$l$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (448.84,457.57) --
+	(452.77,457.57);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (450.87,455.71) --
+	(450.87,459.32);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (450.87,454.67) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.96,482.08) --
+	(482.07,482.08);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.52,481.63) --
+	(481.52,482.53);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (481.52,479.18) {$\kappa$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (461.13,464.79) --
+	(463.09,464.79);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (462.12,463.96) --
+	(462.12,465.60);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (462.12,461.57) {$p$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (442.76,443.46) --
+	(446.27,443.46);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (444.57,438.02) --
+	(444.57,448.00);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (444.57,439.43) {$L$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (467.74,468.50) --
+	(468.01,468.50);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (467.88,461.81) --
+	(467.88,473.87);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (467.88,464.47) {$r$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (461.03,462.06) --
+	(462.71,462.06);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (461.88,456.71) --
+	(461.88,466.54);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (461.88,458.03) {$l$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (451.22,455.57) --
+	(454.75,455.57);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (453.04,448.94) --
+	(453.04,460.90);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (453.04,452.67) {$\sigma$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.97,481.47) --
+	(485.34,481.47);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (484.67,475.14) --
+	(484.67,486.61);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (484.67,478.57) {$\kappa$};
 \end{scope}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (129.84,149.05) --
-	(138.11,149.05);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (134.28,144.35) --
-	(134.28,153.06);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (134.28,145.82) {$p$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.03,167.36) --
-	(177.45,167.36);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.43,164.80) --
-	(174.43,169.71);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.43,163.33) {$L$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.11,186.34) --
-	(183.57,186.34);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.90,185.17) --
-	(181.90,187.47);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.90,182.31) {$r$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (120.09,139.77) --
-	(136.23,139.77);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (129.33,127.18) --
-	(129.33,148.37);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (129.33,135.74) {$h$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 75.83,164.86) --
-	(105.22,164.86);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 94.29,160.32) --
-	( 94.29,168.76);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 94.29,161.96) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.14,191.04) --
-	(190.07,191.04);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.12,190.22) --
-	(189.12,191.83);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (189.12,188.14) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (124.03,146.81) --
+	(133.82,146.81);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (129.36,144.52) --
+	(129.36,148.93);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (129.36,143.59) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.43,163.49) --
+	(180.06,163.49);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (177.39,159.83) --
+	(177.39,166.73);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.39,159.46) {$L$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.60,184.35) --
+	(182.19,184.35);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.41,183.57) --
+	(181.41,185.11);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.41,180.32) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (124.12,145.61) --
+	(134.27,145.61);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (129.66,143.38) --
+	(129.66,147.67);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (129.66,141.58) {$l$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 81.96,162.80) --
+	( 91.33,162.80);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 87.04,159.64) --
+	( 87.04,165.64);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 87.04,159.90) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.79,190.88) --
+	(190.72,190.88);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.26,190.09) --
+	(190.26,191.65);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.26,187.98) {$\kappa$};
 \definecolor{drawColor}{RGB}{253,104,0}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (160.44,166.54) --
-	(164.58,166.54);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (162.59,165.06) --
-	(162.59,167.95);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (162.59,162.51) {$h$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (165.94,173.38) --
+	(169.25,173.38);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (167.65,172.22) --
+	(167.65,174.49);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (167.65,169.35) {$l$};
 \definecolor{drawColor}{RGB}{253,104,0}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (106.54,120.28) --
-	(111.94,120.28);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (109.38,118.59) --
-	(109.38,121.88);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (109.38,116.25) {$h$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (121.87,132.71) --
+	(125.72,132.71);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (123.86,130.35) --
+	(123.86,134.88);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (123.86,128.68) {$l$};
 \definecolor{drawColor}{RGB}{143,161,0}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.20,159.22) --
-	(154.85,159.22);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.17,156.30) --
-	(152.17,161.86);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (152.17,155.99) {$p$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.94,194.12) --
-	(190.38,194.12);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.19,192.98) --
-	(189.19,195.23);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (189.19,190.09) {$L$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.90,194.31) --
-	(191.68,194.31);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.29,193.42) --
-	(191.29,195.18);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.29,190.28) {$r$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (148.95,158.49) --
-	(152.45,158.49);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.75,155.30) --
-	(150.75,161.35);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (150.75,154.46) {$h$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (145.78,167.22) --
-	(149.39,167.22);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (147.64,164.46) --
-	(147.64,169.73);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (147.64,164.32) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.66,195.98) --
-	(195.38,195.98);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.02,194.85) --
-	(195.02,197.05);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.02,193.07) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (111.33,125.20) --
-	(127.87,125.20);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (120.83,121.30) --
-	(120.83,128.61);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (120.83,121.97) {$p$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.43,175.26) --
-	(181.89,175.26);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.21,172.51) --
-	(180.21,177.77);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.21,171.23) {$L$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.72,183.13) --
-	(183.22,183.13);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.97,182.49) --
-	(182.97,183.76);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.97,179.10) {$r$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (121.18,129.36) --
-	(123.70,129.36);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (122.47,124.07) --
-	(122.47,133.80);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (122.47,125.33) {$h$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 99.59,142.36) --
-	(110.04,142.36);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (105.31,128.82) --
-	(105.31,151.38);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (105.31,139.45) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.14,190.13) --
-	(190.28,190.13);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.23,189.43) --
-	(189.23,190.81);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (189.23,187.22) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.20,159.61) --
+	(154.85,159.61);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.17,156.92) --
+	(152.17,162.05);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (152.17,156.38) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.94,194.31) --
+	(190.38,194.31);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.19,193.22) --
+	(189.19,195.36);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (189.19,190.28) {$L$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.90,194.60) --
+	(191.68,194.60);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.29,193.61) --
+	(191.29,195.56);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.29,190.57) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.68,157.91) --
+	(153.46,157.91);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.64,155.30) --
+	(151.64,160.29);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (151.64,153.88) {$l$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (145.78,167.78) --
+	(149.39,167.78);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (147.64,165.10) --
+	(147.64,170.23);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (147.64,164.88) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.66,196.26) --
+	(195.38,196.26);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.02,195.11) --
+	(195.02,197.37);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.02,193.36) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (122.14,126.51) --
+	(126.55,126.51);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (124.43,123.28) --
+	(124.43,129.41);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (124.43,123.29) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.72,176.68) --
+	(186.66,176.68);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.85,174.72) --
+	(183.85,178.52);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.85,172.65) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.35,183.86) --
+	(185.14,183.86);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.75,183.36) --
+	(184.75,184.34);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.75,179.82) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (123.38,126.12) --
+	(127.51,126.12);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (125.52,122.79) --
+	(125.52,129.09);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (125.52,122.09) {$l$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (105.33,146.19) --
+	(109.76,146.19);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (107.63,142.23) --
+	(107.63,149.64);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (107.63,143.28) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.53,192.07) --
+	(192.03,192.07);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.78,191.61) --
+	(191.78,192.52);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.78,189.17) {$\kappa$};
 \definecolor{drawColor}{RGB}{0,216,255}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (147.79,155.41) --
-	(153.26,155.41);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.66,152.92) --
-	(150.66,157.69);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (150.66,151.37) {$h$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.11,187.29) --
+	(174.65,187.29);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.41,185.99) --
+	(173.41,188.53);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.41,183.26) {$l$};
 \definecolor{drawColor}{RGB}{0,216,255}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (154.03,154.12) --
-	(160.70,154.12);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (157.57,150.62) --
-	(157.57,157.22);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (157.57,150.09) {$h$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (135.67,139.81) --
+	(140.70,139.81);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (138.30,136.40) --
+	(138.30,142.85);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (138.30,135.78) {$l$};
 \definecolor{drawColor}{RGB}{151,0,255}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.65,159.36) --
-	(153.97,159.36);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.36,156.62) --
-	(152.36,161.85);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (152.36,156.13) {$p$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (166.12,174.81) --
-	(168.13,174.81);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (167.14,173.87) --
-	(167.14,175.71);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (167.14,170.77) {$L$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.55,180.49) --
-	(173.18,180.49);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.86,180.10) --
-	(172.86,180.86);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.86,176.45) {$r$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (134.55,137.07) --
-	(142.00,137.07);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (138.52,134.89) --
-	(138.52,139.10);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (138.52,133.04) {$h$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.55,167.33) --
-	(154.14,167.33);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.40,165.46) --
-	(152.40,169.08);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (152.40,164.42) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.10,193.03) --
-	(192.69,193.03);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.91,192.39) --
-	(191.91,193.66);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.91,190.13) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.79,160.17) --
+	(153.43,160.17);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.67,157.79) --
+	(151.67,162.37);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (151.67,156.94) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (165.97,174.51) --
+	(167.84,174.51);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (166.92,172.96) --
+	(166.92,175.98);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (166.92,170.48) {$L$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.56,180.54) --
+	(173.07,180.54);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.82,180.25) --
+	(172.82,180.83);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.82,176.51) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (148.45,158.82) --
+	(151.78,158.82);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.17,156.54) --
+	(150.17,160.93);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (150.17,154.79) {$l$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.50,168.49) --
+	(153.34,168.49);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.49,166.63) --
+	(151.49,170.24);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (151.49,165.59) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.40,193.00) --
+	(192.73,193.00);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.07,192.55) --
+	(192.07,193.45);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.07,190.10) {$\kappa$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (159.07,175.71) --
+	(161.57,175.71);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (160.35,174.88) --
+	(160.35,176.52);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (160.35,172.49) {$p$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.01,154.38) --
+	(155.56,154.38);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (153.38,148.94) --
+	(153.38,158.92);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (153.38,150.35) {$L$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.98,179.42) --
+	(173.50,179.42);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.24,172.73) --
+	(173.24,184.79);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.24,175.39) {$r$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (158.37,172.98) --
+	(161.30,172.98);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (159.88,167.63) --
+	(159.88,177.46);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (159.88,168.95) {$l$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.03,166.49) --
+	(153.96,166.49);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (153.01,159.86) --
+	(153.01,171.82);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (153.01,163.59) {$\sigma$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.70,192.39) --
+	(195.64,192.39);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.17,186.06) --
+	(195.17,197.53);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.17,189.49) {$\kappa$};
 \end{scope}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (334.61, 83.64) --
-	(372.72, 83.64);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (359.81, 65.57) --
-	(359.81, 94.44);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (359.81, 80.41) {$p$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (440.92,179.14) --
-	(467.98,179.14);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (457.66,176.43) --
-	(457.66,181.61);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (457.66,175.11) {$L$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (366.14, 82.04) --
-	(372.76, 82.04);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (369.65, 75.12) --
-	(369.65, 87.57);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (369.65, 78.01) {$r$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (359.02, 95.99) --
-	(386.82, 95.99);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (376.30, 72.91) --
-	(376.30,108.34);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (376.30, 91.95) {$h$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (281.67, 58.63) --
-	(366.93, 58.63);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (349.12, 33.73) --
-	(349.12, 71.46);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (349.12, 55.72) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (477.60,190.83) --
-	(479.43,190.83);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (478.53,190.10) --
-	(478.53,191.54);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (478.53,187.92) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (351.67, 75.92) --
+	(366.50, 75.92);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (360.08, 62.11) --
+	(360.08, 85.06);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (360.08, 72.69) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (465.30,181.30) --
+	(470.01,181.30);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (467.75,180.10) --
+	(467.75,182.45);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (467.75,177.27) {$L$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (364.69, 79.71) --
+	(370.86, 79.71);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (367.95, 75.59) --
+	(367.95, 83.28);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (367.95, 75.67) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (347.94, 72.23) --
+	(363.09, 72.23);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (356.55, 59.20) --
+	(356.55, 81.03);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (356.55, 68.19) {$l$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (357.53, 79.67) --
+	(372.18, 79.67);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (365.82, 65.98) --
+	(365.82, 88.76);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (365.82, 76.77) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (479.12,191.17) --
+	(479.79,191.17);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (479.46,190.77) --
+	(479.46,191.56);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (479.46,188.26) {$\kappa$};
 \definecolor{drawColor}{RGB}{253,104,0}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (448.93,165.60) --
-	(451.61,165.60);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (450.30,163.78) --
-	(450.30,167.31);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (450.30,161.57) {$h$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (454.92,172.72) --
+	(457.88,172.72);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (456.44,171.76) --
+	(456.44,173.64);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (456.44,168.68) {$l$};
 \definecolor{drawColor}{RGB}{253,104,0}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (414.12,117.28) --
-	(419.19,117.28);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (416.77,113.09) --
-	(416.77,120.91);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (416.77,113.24) {$h$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (433.89,137.53) --
+	(437.42,137.53);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (435.72,132.94) --
+	(435.72,141.47);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (435.72,133.50) {$l$};
 \definecolor{drawColor}{RGB}{143,161,0}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (412.87,125.74) --
-	(417.56,125.74);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (415.31,122.57) --
-	(415.31,128.58);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (415.31,121.70) {$h$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (416.18,129.41) --
+	(420.97,129.41);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (418.68,126.91) --
+	(418.68,131.70);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (418.68,125.38) {$l$};
 \definecolor{drawColor}{RGB}{0,195,0}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (383.87,101.21) --
-	(388.61,101.21);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (386.34, 84.00) --
-	(386.34,111.71);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (386.34, 97.98) {$p$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (470.13,184.99) --
-	(480.49,184.99);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (475.80,179.70) --
-	(475.80,189.43);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (475.80,180.96) {$L$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (436.20,154.50) --
-	(438.24,154.50);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (437.24,153.50) --
-	(437.24,155.46);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (437.24,150.46) {$r$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (385.40, 93.05) --
-	(391.40, 93.05);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (388.56, 81.05) --
-	(388.56,101.36);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (388.56, 89.01) {$h$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (376.33, 98.28) --
-	(389.61, 98.28);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (383.76, 84.24) --
-	(383.76,107.51);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (383.76, 95.37) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.53,192.40) --
-	(482.50,192.40);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (482.02,191.03) --
-	(482.02,193.70);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (482.02,189.50) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (385.83, 99.40) --
+	(392.31, 99.40);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (389.26, 95.81) --
+	(389.26,102.57);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (389.26, 96.17) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (473.69,188.73) --
+	(476.49,188.73);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (475.13,188.01) --
+	(475.13,189.43);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (475.13,184.70) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (436.76,155.25) --
+	(437.67,155.25);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (437.22,154.80) --
+	(437.22,155.68);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (437.22,151.21) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (385.41, 98.57) --
+	(391.78, 98.57);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (388.78, 95.11) --
+	(388.78,101.64);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (388.78, 94.54) {$l$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (387.89, 96.18) --
+	(397.47, 96.18);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (393.09, 90.44) --
+	(393.09,100.91);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (393.09, 93.27) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.18,192.76) --
+	(482.04,192.76);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.61,192.24) --
+	(481.61,193.26);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (481.61,189.85) {$\kappa$};
 \definecolor{drawColor}{RGB}{0,216,255}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (435.04,154.48) --
-	(441.46,154.48);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (438.44,152.85) --
-	(438.44,156.02);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (438.44,150.45) {$h$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (464.60,186.56) --
+	(468.77,186.56);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (466.76,185.04) --
+	(466.76,188.01);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (466.76,182.53) {$l$};
 \definecolor{drawColor}{RGB}{0,216,255}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (413.21,127.52) --
-	(419.93,127.52);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (416.78,122.36) --
-	(416.78,131.86);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (416.78,123.49) {$h$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (413.34,118.27) --
+	(419.01,118.27);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (416.32,112.36) --
+	(416.32,123.13);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (416.32,114.24) {$l$};
 \definecolor{drawColor}{RGB}{151,0,255}
@@
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (486.94,194.63) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (438.45,155.96) --
+	(442.00,155.96);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (440.28,154.10) --
+	(440.28,157.70);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (440.28,152.73) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (458.53,175.41) --
+	(464.64,175.41);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (461.75,173.27) --
+	(461.75,177.39);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (461.75,171.37) {$L$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (462.38,179.31) --
+	(462.82,179.31);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (462.60,178.99) --
+	(462.60,179.62);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (462.60,175.27) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (436.63,154.10) --
+	(440.02,154.10);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (438.38,152.17) --
+	(438.38,155.91);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (438.38,150.07) {$l$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (444.68,160.90) --
+	(447.75,160.90);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (446.26,158.54) --
+	(446.26,163.08);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (446.26,158.00) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.53,193.23) --
+	(482.54,193.23);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (482.04,192.54) --
+	(482.04,193.90);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (482.04,190.33) {$\kappa$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (452.90,174.58) --
+	(454.78,174.58);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (453.85,173.07) --
+	(453.85,176.00);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (453.85,171.35) {$p$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (440.24,156.40) --
+	(444.95,156.40);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (442.69,153.89) --
+	(442.69,158.71);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (442.69,152.37) {$L$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (463.72,180.84) --
+	(464.20,180.84);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (463.96,180.59) --
+	(463.96,181.10);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (463.96,176.81) {$r$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (452.87,174.56) --
+	(454.69,174.56);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (453.79,173.09) --
+	(453.79,175.96);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (453.79,170.53) {$l$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (446.17,165.32) --
+	(449.23,165.32);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (447.74,163.80) --
+	(447.74,166.75);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (447.74,162.41) {$\sigma$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.22,195.23) --
+	(484.60,195.23);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.92,194.48) --
+	(483.92,195.97);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.92,192.33) {$\kappa$};
 \end{scope}

### 2020-08-29 benchmarking/benchmarkingVM/ESS_round1_real.tex
results update

@@
-% Created by tikzDevice version 0.12.3.1 on 2020-08-28 13:28:47
+% Created by tikzDevice version 0.12.3.1 on 2020-08-29 17:33:51
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 78.41,410.95) --
-	( 91.01,410.95);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 85.43,396.47) --
-	( 85.43,420.38);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 85.43,407.72) {$p$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.48,467.57) --
-	(182.33,467.57);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.56,466.01) --
-	(179.56,469.05);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.56,463.54) {$L$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 81.27,472.87) --
-	( 87.83,472.87);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 84.75,471.19) --
-	( 84.75,474.46);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 84.75,468.84) {$r$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 77.34,424.98) --
-	( 96.67,424.98);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 88.68,419.14) --
-	( 88.68,429.79);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 88.68,420.94) {$h$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 77.52,382.73) --
-	(108.13,382.73);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 96.89,359.01) --
-	( 96.89,395.26);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 96.89,379.83) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.26,478.14) --
-	(189.63,478.14);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.95,477.37) --
-	(188.95,478.88);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.95,475.23) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 83.02,404.70) --
+	( 97.04,404.70);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 90.92,398.69) --
+	( 90.92,409.62);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 90.92,401.47) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.01,467.31) --
+	(183.45,467.31);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.98,465.30) --
+	(179.98,469.19);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.98,463.28) {$L$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 80.73,472.59) --
+	( 84.67,472.59);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 82.77,471.35) --
+	( 82.77,473.77);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 82.77,468.56) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 69.02,424.21) --
+	( 77.50,424.21);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 73.59,418.49) --
+	( 73.59,428.93);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 73.59,420.17) {$l$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 91.37,374.35) --
+	(105.23,374.35);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 99.16,369.99) --
+	( 99.16,378.12);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 99.16,371.45) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.87,480.03) --
+	(190.98,480.03);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.43,479.66) --
+	(190.43,480.40);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.43,477.13) {$\kappa$};
 \definecolor{drawColor}{RGB}{253,104,0}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (139.34,449.32) --
-	(177.09,449.32);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.26,447.98) --
-	(164.26,450.60);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (164.26,445.29) {$h$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (139.57,454.32) --
+	(189.04,454.32);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.21,453.15) --
+	(174.21,455.44);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.21,450.29) {$l$};
 \definecolor{drawColor}{RGB}{253,104,0}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (148.64,389.28) --
-	(148.64,395.86);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (148.64,388.74) {$h$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (155.04,402.37) --
+	(155.04,408.04);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (155.04,401.32) {$l$};
 \definecolor{drawColor}{RGB}{143,161,0}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (142.49,430.50) --
-	(142.49,432.37);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (142.49,427.42) {$h$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (148.29,435.17) --
+	(148.29,438.68);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (148.29,432.95) {$l$};
 \definecolor{drawColor}{RGB}{0,195,0}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (101.54,432.34) --
-	(123.04,432.34);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (114.35,429.11) {$p$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.64,471.96) --
-	(192.30,471.96);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.87,467.92) {$L$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (132.95,472.27) --
-	(142.09,472.27);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (137.90,468.23) {$r$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 85.73,415.23) --
-	(106.54,415.23);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 98.06,411.19) {$h$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 98.15,400.30) --
-	(118.93,400.30);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (110.47,397.40) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.20,481.36) --
-	(193.74,481.36);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.56,478.45) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (106.98,425.81) --
+	(121.30,425.81);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (115.07,420.45) --
+	(115.07,430.30);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (115.07,422.59) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.17,470.70) --
+	(191.58,470.70);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.68,470.14) --
+	(185.68,471.25);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.68,466.67) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (135.16,472.44) --
+	(141.55,472.44);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (138.54,472.04) --
+	(138.54,472.83);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (138.54,468.40) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 89.10,417.71) --
+	(103.63,417.71);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 97.32,415.03) --
+	( 97.32,420.16);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 97.32,413.68) {$l$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (104.73,394.81) --
+	(121.56,394.81);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (114.41,389.48) --
+	(114.41,399.26);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (114.41,391.90) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.32,481.31) --
+	(193.49,481.31);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.95,480.90) --
+	(191.95,481.72);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.95,478.41) {$\kappa$};
 \definecolor{drawColor}{RGB}{0,216,255}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (146.45,434.24) --
-	(175.79,434.24);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.87,432.34) --
-	(164.87,436.02);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (164.87,430.21) {$h$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.57,454.48) --
+	(205.36,454.48);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.68,453.18) --
+	(195.68,455.71);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.68,450.44) {$l$};
 \definecolor{drawColor}{RGB}{0,216,255}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (127.39,437.43) --
-	(187.18,437.43);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.11,435.37) --
-	(171.11,439.35);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.11,433.40) {$h$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (120.33,428.75) --
+	(203.84,428.75);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.10,426.86) --
+	(186.10,430.51);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (186.10,424.71) {$l$};
 \definecolor{drawColor}{RGB}{151,0,255}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 87.75,444.22) --
-	(129.17,444.22);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (115.63,442.73) --
-	(115.63,445.63);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (115.63,440.99) {$p$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (119.18,453.67) --
-	(160.39,453.67);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (146.89,450.11) --
-	(146.89,456.83);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (146.89,449.64) {$L$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (146.34,455.68) --
-	(169.74,455.68);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (160.47,455.40) --
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (133.67,442.76) --
+	(133.67,445.15);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (133.67,440.75) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (114.67,452.24) --
+	(158.12,452.24);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (144.22,448.41) --
+	(144.22,455.61);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (144.22,448.21) {$L$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (146.34,455.71) --
+	(169.74,455.71);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (160.47,455.45) --
 	(160.47,455.96);
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (160.47,451.65) {$r$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 79.88,412.46) --
-	(117.32,412.46);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (104.54,406.29) --
-	(104.54,417.50);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (104.54,408.43) {$h$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 90.78,434.42) --
-	(132.68,434.42);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (119.05,432.86) --
-	(119.05,435.90);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (119.05,431.52) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.48,481.72) --
-	(193.39,481.72);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.50,481.16) --
-	(191.50,482.26);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.50,478.81) {$\kappa$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (160.47,451.67) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (108.92,431.10) --
+	(154.18,431.10);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (139.99,427.06) --
+	(139.99,434.62);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (139.99,427.07) {$l$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (160.33,433.08) --
+	(160.33,435.62);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (160.33,431.48) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.30,481.70) --
+	(193.01,481.70);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.22,481.20) --
+	(191.22,482.19);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.22,478.80) {$\kappa$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.00,440.60) --
+	(176.00,444.07);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.00,439.16) {$p$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (100.89,439.35) --
+	(139.08,439.35);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (126.16,436.47) --
+	(126.16,441.96);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (126.16,435.32) {$L$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (144.61,456.39) --
+	(200.58,456.39);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.92,456.18) --
+	(184.92,456.60);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.92,452.36) {$r$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.08,440.70) --
+	(208.08,440.70);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (197.25,439.24) --
+	(197.25,442.09);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.25,436.67) {$l$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (134.06,438.18) --
+	(205.41,438.18);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.36,436.36) --
+	(188.36,439.88);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.36,435.27) {$\sigma$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.91,484.86) --
+	(195.41,484.86);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.19,484.41) --
+	(194.19,485.31);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.19,481.96) {$\kappa$};
 \end{scope}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (367.49,467.04) --
-	(380.09,467.04);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (374.51,464.05) --
-	(374.51,469.74);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (374.51,463.82) {$p$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (465.56,448.03) --
-	(471.41,448.03);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (468.64,444.87) --
-	(468.64,450.86);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.64,444.00) {$L$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (370.35,473.24) --
-	(376.91,473.24);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (373.83,472.46) --
-	(373.83,473.99);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (373.83,469.20) {$r$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (366.42,435.02) --
-	(385.75,435.02);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (377.76,431.48) --
-	(377.76,438.16);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (377.76,430.99) {$h$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (366.60,468.13) --
-	(397.21,468.13);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (385.97,465.86) --
-	(385.97,470.24);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (385.97,465.23) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (477.34,477.42) --
-	(478.71,477.42);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (478.03,476.86) --
-	(478.03,477.97);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (478.03,474.52) {$\kappa$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (430.18,471.54) --
-	(460.00,471.54);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (448.96,470.69) --
-	(448.96,472.36);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (448.96,468.31) {$p$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (466.88,474.80) --
-	(479.82,474.80);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (474.10,472.77) --
-	(474.10,476.70);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.10,470.77) {$L$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (464.81,479.57) --
-	(472.19,479.57);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (468.75,479.29) --
-	(468.75,479.85);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.75,475.54) {$r$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (428.42,454.70) --
-	(466.17,454.70);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (453.34,453.16) --
-	(453.34,456.15);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (453.34,450.66) {$h$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (406.97,473.34) --
-	(480.21,473.34);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (463.04,472.63) --
-	(463.04,474.04);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (463.04,470.44) {$\sigma$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (479.32,481.45) --
-	(481.64,481.45);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.50,480.91) --
-	(480.50,481.98);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (480.50,478.54) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (372.10,469.76) --
+	(386.12,469.76);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (380.00,467.35) --
+	(380.00,471.98);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (380.00,466.53) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (465.09,450.78) --
+	(472.53,450.78);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (469.06,448.97) --
+	(469.06,452.47);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (469.06,446.75) {$L$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (369.81,473.72) --
+	(373.75,473.72);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (371.85,473.22) --
+	(371.85,474.21);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (371.85,469.68) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (358.10,438.88) --
+	(366.58,438.88);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (362.67,436.62) --
+	(362.67,440.96);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (362.67,434.84) {$l$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (380.45,467.10) --
+	(394.31,467.10);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (388.24,465.29) --
+	(388.24,468.80);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (388.24,464.20) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (478.95,479.42) --
+	(480.06,479.42);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (479.51,478.97) --
+	(479.51,479.86);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (479.51,476.51) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (430.18,471.62) --
+	(460.00,471.62);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (448.96,470.85) --
+	(448.96,472.37);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (448.96,468.40) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (466.88,474.53) --
+	(479.82,474.53);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (474.10,472.61) --
+	(474.10,476.32);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.10,470.49) {$L$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (464.81,479.56) --
+	(472.19,479.56);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (468.75,479.31) --
+	(468.75,479.81);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.75,475.53) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (428.65,458.11) --
+	(478.12,458.11);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (463.29,457.04) --
+	(463.29,459.15);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (463.29,454.08) {$l$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (406.97,473.51) --
+	(480.21,473.51);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (463.04,472.79) --
+	(463.04,474.21);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (463.04,470.60) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (479.32,481.54) --
+	(481.64,481.54);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.50,481.02) --
+	(480.50,482.04);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (480.50,478.63) {$\kappa$};
 \definecolor{drawColor}{RGB}{143,161,0}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (437.72,397.21) --
-	(437.72,405.84);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (437.72,397.83) {$h$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (444.12,411.64) --
+	(444.12,421.72);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (444.12,413.11) {$l$};
 \definecolor{drawColor}{RGB}{143,161,0}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (431.57,433.40) --
-	(431.57,438.03);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (431.57,431.78) {$h$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (437.37,439.79) --
+	(437.37,442.98);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (437.37,437.39) {$l$};
 \definecolor{drawColor}{RGB}{0,195,0}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (390.62,463.50) --
-	(412.12,463.50);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (403.43,460.57) --
-	(403.43,466.15);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (403.43,460.27) {$p$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (460.72,461.08) --
-	(481.38,461.08);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (472.95,460.33) --
-	(472.95,461.81);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (472.95,457.05) {$L$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (422.03,470.75) --
-	(431.17,470.75);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (426.98,470.01) --
-	(426.98,471.47);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (426.98,466.72) {$r$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (374.81,416.60) --
-	(395.62,416.60);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (387.14,412.44) --
-	(387.14,420.21);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (387.14,412.57) {$h$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (387.23,446.61) --
-	(408.01,446.61);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (399.55,444.30) --
-	(399.55,448.73);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (399.55,443.70) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (478.28,481.27) --
-	(482.82,481.27);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.64,480.85) --
-	(480.64,481.68);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (480.64,478.36) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (396.06,463.48) --
+	(410.38,463.48);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (404.15,461.30) --
+	(404.15,465.50);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (404.15,460.25) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (467.25,461.16) --
+	(480.66,461.16);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (474.76,460.75) --
+	(474.76,461.56);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.76,457.13) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (424.24,470.95) --
+	(430.63,470.95);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (427.62,470.38) --
+	(427.62,471.51);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (427.62,466.92) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (378.18,422.68) --
+	(392.71,422.68);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (386.40,420.09) --
+	(386.40,425.05);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (386.40,418.65) {$l$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (393.81,445.42) --
+	(410.64,445.42);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (403.49,442.80) --
+	(403.49,447.81);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (403.49,442.52) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (479.40,481.50) --
+	(482.57,481.50);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.03,481.12) --
+	(481.03,481.86);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (481.03,478.59) {$\kappa$};
 \definecolor{drawColor}{RGB}{0,216,255}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (435.53,446.43) --
-	(464.87,446.43);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (453.95,444.35) --
-	(453.95,448.35);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (453.95,442.39) {$h$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (469.65,476.49) --
+	(494.44,476.49);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (484.76,475.16) --
+	(484.76,477.77);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (484.76,472.46) {$l$};
 \definecolor{drawColor}{RGB}{0,216,255}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (428.08,510.61) --
-	(490.87,510.61);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (474.50,506.59) --
-	(474.50,514.11);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.50,507.38) {$p$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (471.30,510.72) --
-	(480.14,510.72);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (476.07,507.87) --
-	(476.07,513.30);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (476.07,506.68) {$L$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (416.47,483.27) --
-	(476.26,483.27);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (460.19,480.40) --
-	(460.19,485.87);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (460.19,479.24) {$h$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (420.17,487.76) --
-	(493.55,487.76);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (476.36,484.08) --
-	(476.36,491.00);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (476.36,484.85) {$\sigma$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.60,529.08) --
-	(484.79,529.08);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.24,525.48) --
-	(483.24,532.27);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.24,526.18) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (428.08,467.23) --
+	(490.87,467.23);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (474.50,465.85) --
+	(474.50,468.55);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.50,464.01) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (471.30,464.98) --
+	(480.14,464.98);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (476.07,463.73) --
+	(476.07,466.18);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (476.07,460.95) {$L$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (447.50,472.08) --
+	(450.99,472.08);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (449.30,471.77) --
+	(449.30,472.39);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (449.30,468.05) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (409.41,426.58) --
+	(492.92,426.58);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (475.18,423.54) --
+	(475.18,429.32);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (475.18,422.55) {$l$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (420.17,444.15) --
+	(493.55,444.15);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (476.36,442.54) --
+	(476.36,445.67);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (476.36,441.24) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.60,485.16) --
+	(484.79,485.16);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.24,484.79) --
+	(483.24,485.52);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.24,482.25) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (422.75,450.99) --
+	(422.75,454.38);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (422.75,449.51) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (403.75,455.09) --
+	(447.20,455.09);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (433.30,448.17) --
+	(433.30,460.61);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (433.30,451.05) {$L$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (435.42,464.34) --
+	(458.82,464.34);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (449.55,463.86) --
+	(449.55,464.81);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (449.55,460.30) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (398.00,441.30) --
+	(443.26,441.30);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (429.07,439.87) --
+	(429.07,442.66);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (429.07,437.27) {$l$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (449.41,451.50) --
+	(449.41,454.19);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (449.41,449.97) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (478.38,482.14) --
+	(482.09,482.14);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.30,481.65) --
+	(480.30,482.62);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (480.30,479.23) {$\kappa$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (465.08,446.82) --
+	(465.08,451.65);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (465.08,446.11) {$p$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (389.97,443.85) --
+	(428.16,443.85);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (415.24,441.95) --
+	(415.24,445.64);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (415.24,439.82) {$L$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (433.69,468.32) --
+	(489.66,468.32);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (474.00,468.11) --
+	(474.00,468.53);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.00,464.29) {$r$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (468.16,461.78) --
+	(497.16,461.78);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (486.33,461.02) --
+	(486.33,462.52);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (486.33,457.75) {$l$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (423.14,452.09) --
+	(494.49,452.09);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (477.44,449.26) --
+	(477.44,454.65);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (477.44,449.18) {$\sigma$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.99,484.04) --
+	(484.49,484.04);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.27,483.19) --
+	(483.27,484.87);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.27,481.14) {$\kappa$};
 \end{scope}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (107.39,177.96) --
-	(131.30,177.96);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (121.87,174.97) --
-	(121.87,180.66);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (121.87,174.74) {$p$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.93,158.95) --
-	(179.97,158.95);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.49,155.79) --
-	(178.49,161.78);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (178.49,154.92) {$L$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.11,184.16) --
-	(185.38,184.16);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.79,183.38) --
-	(183.79,184.91);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.79,180.12) {$r$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (130.06,145.94) --
-	(140.71,145.94);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (135.90,142.40) --
-	(135.90,149.08);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (135.90,141.91) {$h$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 69.93,179.05) --
-	(106.18,179.05);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 93.65,176.78) --
-	( 93.65,181.16);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 93.65,176.15) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.29,188.34) --
-	(189.80,188.34);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.06,187.78) --
-	(189.06,188.89);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (189.06,185.44) {$\kappa$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.83,182.46) --
-	(179.53,182.46);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.22,181.61) --
-	(178.22,183.28);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (178.22,179.23) {$p$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.24,185.72) --
-	(186.54,185.72);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.94,183.69) --
-	(184.94,187.62);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.94,181.69) {$L$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.74,190.49) --
-	(188.08,190.49);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.91,190.21) --
-	(187.91,190.77);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.91,186.46) {$r$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (158.90,165.62) --
-	(161.52,165.62);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (160.24,164.08) --
-	(160.24,167.07);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (160.24,161.58) {$h$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (163.62,184.26) --
-	(166.77,184.26);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (165.24,183.55) --
-	(165.24,184.96);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (165.24,181.36) {$\sigma$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.73,192.37) --
-	(192.84,192.37);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.29,191.83) --
-	(192.29,192.90);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.29,189.46) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (109.61,180.68) --
+	(120.54,180.68);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (115.62,178.27) --
+	(115.62,182.90);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (115.62,177.45) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.22,161.70) --
+	(180.11,161.70);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.23,159.89) --
+	(178.23,163.39);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (178.23,157.67) {$L$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.27,184.64) --
+	(184.69,184.64);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.51,184.14) --
+	(183.51,185.13);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.51,180.60) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (129.41,149.80) --
+	(139.85,149.80);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (135.13,147.54) --
+	(135.13,151.88);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (135.13,145.76) {$l$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 80.91,178.02) --
+	( 89.04,178.02);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 85.27,176.21) --
+	( 85.27,179.72);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 85.27,175.12) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.58,190.34) --
+	(191.32,190.34);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.95,189.89) --
+	(190.95,190.78);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.95,187.43) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.83,182.54) --
+	(179.53,182.54);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.22,181.77) --
+	(178.22,183.29);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (178.22,179.32) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.24,185.45) --
+	(186.54,185.45);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.94,183.53) --
+	(184.94,187.24);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.94,181.41) {$L$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.74,190.48) --
+	(188.08,190.48);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.91,190.23) --
+	(187.91,190.73);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.91,186.45) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.07,169.03) --
+	(166.36,169.03);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (165.24,167.96) --
+	(165.24,170.07);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (165.24,165.00) {$l$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (163.62,184.43) --
+	(166.77,184.43);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (165.24,183.71) --
+	(165.24,185.13);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (165.24,181.52) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.73,192.46) --
+	(192.84,192.46);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.29,191.94) --
+	(192.29,192.96);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.29,189.55) {$\kappa$};
 \definecolor{drawColor}{RGB}{143,161,0}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (100.20,112.78) --
-	(106.78,112.78);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (103.69,108.13) --
-	(103.69,116.76);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (103.69,108.75) {$h$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (113.29,128.06) --
+	(118.96,128.06);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (116.27,122.56) --
+	(116.27,132.64);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (116.27,124.03) {$l$};
 \definecolor{drawColor}{RGB}{143,161,0}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (141.42,146.73) --
-	(143.29,146.73);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (142.37,144.32) --
-	(142.37,148.95);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (142.37,142.70) {$h$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (146.09,152.35) --
+	(149.60,152.35);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (147.90,150.71) --
+	(147.90,153.90);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (147.90,148.31) {$l$};
 \definecolor{drawColor}{RGB}{0,195,0}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (143.26,171.49) --
-	(143.26,177.07);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (143.26,171.19) {$p$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.88,171.25) --
-	(182.88,172.73);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.88,167.97) {$L$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.19,180.93) --
-	(183.19,182.39);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.19,177.64) {$r$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (126.15,123.36) --
-	(126.15,131.13);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (126.15,123.49) {$h$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (111.22,155.22) --
-	(111.22,159.65);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (111.22,154.62) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.28,191.77) --
-	(192.28,192.60);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.28,189.28) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (131.37,174.40) --
+	(141.22,174.40);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (136.73,172.22) --
+	(136.73,176.42);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (136.73,171.17) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.06,172.08) --
+	(182.17,172.08);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.62,171.67) --
+	(181.62,172.48);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.62,168.05) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.96,181.87) --
+	(183.75,181.87);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.36,181.30) --
+	(183.36,182.43);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.36,177.84) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (125.95,133.60) --
+	(131.08,133.60);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (128.63,131.01) --
+	(128.63,135.97);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (128.63,129.57) {$l$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (100.40,156.34) --
+	(110.18,156.34);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (105.73,153.72) --
+	(105.73,158.73);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (105.73,153.44) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.82,192.42) --
+	(192.64,192.42);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.23,192.04) --
+	(192.23,192.78);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.23,189.51) {$\kappa$};
 \definecolor{drawColor}{RGB}{0,216,255}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (143.26,157.35) --
-	(146.94,157.35);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (145.16,155.27) --
-	(145.16,159.27);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (145.16,153.31) {$h$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.10,187.41) --
+	(166.63,187.41);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (165.40,186.08) --
+	(165.40,188.69);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (165.40,183.38) {$l$};
 \definecolor{drawColor}{RGB}{0,216,255}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.39,221.53) --
-	(176.85,221.53);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.71,217.51) --
-	(174.71,225.03);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.71,218.30) {$p$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.08,221.64) --
-	(184.42,221.64);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.76,218.79) --
-	(183.76,224.22);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.76,217.60) {$L$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (146.29,194.19) --
-	(150.27,194.19);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (148.35,191.32) --
-	(148.35,196.79);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (148.35,190.16) {$h$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (141.21,198.68) --
-	(144.82,198.68);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (143.08,195.00) --
-	(143.08,201.92);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (143.08,195.77) {$\sigma$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.06,240.00) --
-	(196.74,240.00);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.43,236.40) --
-	(195.43,243.19);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.43,237.10) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.39,178.15) --
+	(176.85,178.15);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.71,176.77) --
+	(174.71,179.47);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.71,174.93) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.08,175.90) --
+	(184.42,175.90);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.76,174.65) --
+	(183.76,177.10);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.76,171.87) {$L$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.18,183.00) --
+	(186.55,183.00);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.37,182.69) --
+	(186.37,183.31);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (186.37,178.97) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (137.78,137.50) --
+	(141.43,137.50);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (139.67,134.46) --
+	(139.67,140.24);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (139.67,133.47) {$l$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (141.21,155.07) --
+	(144.82,155.07);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (143.08,153.46) --
+	(143.08,156.59);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (143.08,152.16) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.06,196.08) --
+	(196.74,196.08);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.43,195.71) --
+	(195.43,196.44);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.43,193.17) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (153.68,163.66) --
+	(156.07,163.66);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (154.90,161.91) --
+	(154.90,165.30);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (154.90,160.43) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (159.33,166.01) --
+	(166.53,166.01);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (163.16,159.09) --
+	(163.16,171.53);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (163.16,161.97) {$L$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (166.37,175.26) --
+	(166.88,175.26);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (166.63,174.78) --
+	(166.63,175.73);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (166.63,171.22) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (137.98,152.22) --
+	(145.54,152.22);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (142.02,150.79) --
+	(142.02,153.58);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (142.02,148.19) {$l$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (144.00,163.79) --
+	(146.54,163.79);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (145.30,162.42) --
+	(145.30,165.11);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (145.30,160.89) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.12,193.06) --
+	(193.11,193.06);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.62,192.57) --
+	(192.62,193.54);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.62,190.15) {$\kappa$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.52,160.26) --
+	(154.99,160.26);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (153.31,157.74) --
+	(153.31,162.57);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (153.31,157.03) {$p$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (147.39,154.77) --
+	(152.88,154.77);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.27,152.87) --
+	(150.27,156.56);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (150.27,150.74) {$L$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (167.10,179.24) --
+	(167.52,179.24);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (167.31,179.03) --
+	(167.31,179.45);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (167.31,175.21) {$r$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.16,172.70) --
+	(153.01,172.70);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.62,171.94) --
+	(151.62,173.44);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (151.62,168.67) {$l$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (147.28,163.01) --
+	(150.80,163.01);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.10,160.18) --
+	(149.10,165.57);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (149.10,160.10) {$\sigma$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.33,194.96) --
+	(196.23,194.96);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.78,194.11) --
+	(195.78,195.79);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.78,192.06) {$\kappa$};
 \end{scope}
@@
 
-\path[fill=fillColor] (485.73,235.47) circle (  1.87);
-
-\path[fill=fillColor] (485.73, 54.16) --
-	(488.24, 49.81) --
-	(483.21, 49.81) --
+\path[fill=fillColor] (485.73,235.38) circle (  1.87);
+
+\path[fill=fillColor] (485.73, 54.21) --
+	(488.24, 49.85) --
+	(483.21, 49.85) --
 	cycle;
@@
 
-\path[fill=fillColor] (404.25,216.71) circle (  1.87);
-
-\path[fill=fillColor] (404.25, 59.65) --
-	(406.77, 55.29) --
-	(401.74, 55.29) --
+\path[fill=fillColor] (404.25,216.69) circle (  1.87);
+
+\path[fill=fillColor] (404.25, 59.59) --
+	(406.77, 55.23) --
+	(401.74, 55.23) --
 	cycle;
@@
 
-\path[fill=fillColor] (433.62,204.25) circle (  1.87);
-
-\path[fill=fillColor] (433.62, 68.39) --
-	(436.14, 64.04) --
-	(431.10, 64.04) --
+\path[fill=fillColor] (433.62,203.93) circle (  1.87);
+
+\path[fill=fillColor] (433.62, 68.64) --
+	(436.14, 64.29) --
+	(431.10, 64.29) --
 	cycle;
@@
 \node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
+\definecolor{fillColor}{RGB}{255,0,255}
+
+\path[fill=fillColor] (359.72,138.32) circle (  1.87);
+
+\path[fill=fillColor] (359.72, 88.29) --
+	(362.24, 83.94) --
+	(357.21, 83.94) --
+	cycle;
+\definecolor{fillColor}{RGB}{0,0,0}
+
+\path[fill=fillColor] (435.32,150.27) circle (  2.15);
+
+\path[fill=fillColor] (435.32,142.15) --
+	(438.21,137.14) --
+	(432.42,137.14) --
+	cycle;
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,146.98) {\texttt{ConstantDistance}};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
+\definecolor{fillColor}{RGB}{68,68,68}
+
+\path[fill=fillColor] (346.46,129.20) circle (  1.87);
+
+\path[fill=fillColor] (346.46, 90.01) --
+	(348.97, 85.65) --
+	(343.94, 85.65) --
+	cycle;
+\definecolor{fillColor}{RGB}{0,0,0}
+
+\path[fill=fillColor] (435.32,150.27) circle (  2.15);
+
+\path[fill=fillColor] (435.32,142.15) --
+	(438.21,137.14) --
+	(432.42,137.14) --
+	cycle;
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,146.98) {\texttt{ConstantDistance}};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (338.88,114.47) --
-	(339.26,114.92) --
-	(339.64,115.37) --
-	(340.02,115.83) --
-	(340.40,116.28) --
-	(340.78,116.74) --
-	(341.16,117.20) --
-	(341.54,117.66) --
-	(341.92,118.12) --
-	(342.30,118.58) --
-	(342.68,119.05) --
-	(343.06,119.51) --
-	(343.44,119.98) --
-	(343.82,120.45) --
-	(344.20,120.92) --
-	(344.58,121.39) --
-	(344.96,121.86) --
-	(345.34,122.34) --
-	(345.71,122.81) --
-	(346.09,123.29) --
-	(346.47,123.76) --
-	(346.85,124.24) --
-	(347.23,124.72) --
-	(347.61,125.20) --
-	(347.99,125.68) --
-	(348.37,126.16) --
-	(348.75,126.65) --
-	(349.13,127.13) --
-	(349.51,127.62) --
-	(349.89,128.10) --
-	(350.27,128.59) --
-	(350.65,129.08) --
-	(351.03,129.56) --
-	(351.41,130.05) --
-	(351.79,130.54) --
-	(352.17,131.03) --
-	(352.55,131.53) --
-	(352.93,132.02) --
-	(353.31,132.51) --
-	(353.69,133.01) --
-	(354.07,133.50) --
-	(354.45,133.99) --
-	(354.83,134.49) --
-	(355.21,134.99) --
-	(355.59,135.48) --
-	(355.97,135.98) --
-	(356.35,136.48) --
-	(356.73,136.98) --
-	(357.11,137.47) --
-	(357.49,137.97) --
-	(357.87,138.47) --
-	(358.25,138.97) --
-	(358.63,139.47) --
-	(359.01,139.97) --
-	(359.38,140.47) --
-	(359.76,140.97) --
-	(360.14,141.47) --
-	(360.52,141.98) --
-	(360.90,142.48) --
-	(361.28,142.98) --
-	(361.66,143.48) --
-	(362.04,143.98) --
-	(362.42,144.48) --
-	(362.80,144.98) --
-	(363.18,145.49) --
-	(363.56,145.99) --
-	(363.94,146.49) --
-	(364.32,146.99) --
-	(364.70,147.49) --
-	(365.08,147.99) --
-	(365.46,148.49) --
-	(365.84,148.99) --
-	(366.22,149.49) --
-	(366.60,149.99) --
-	(366.98,150.49) --
-	(367.36,150.99) --
-	(367.74,151.49) --
-	(368.12,151.99) --
-	(368.50,152.49) --
-	(368.88,152.99) --
-	(369.26,153.48) --
-	(369.64,153.98) --
-	(370.02,154.48) --
-	(370.40,154.97) --
-	(370.78,155.47) --
-	(371.16,155.96) --
-	(371.54,156.45) --
-	(371.92,156.95) --
-	(372.30,157.44) --
-	(372.68,157.93) --
-	(373.05,158.42) --
-	(373.43,158.91) --
-	(373.81,159.40) --
-	(374.19,159.89) --
-	(374.57,160.38) --
-	(374.95,160.87) --
-	(375.33,161.35) --
-	(375.71,161.84) --
-	(376.09,162.32) --
-	(376.47,162.81) --
-	(376.85,163.29) --
-	(377.23,163.77) --
-	(377.61,164.25) --
-	(377.99,164.73) --
-	(378.37,165.21) --
-	(378.75,165.68) --
-	(379.13,166.16) --
-	(379.51,166.64) --
-	(379.89,167.11) --
-	(380.27,167.58) --
-	(380.65,168.05) --
-	(381.03,168.52) --
-	(381.41,168.99) --
-	(381.79,169.46) --
-	(382.17,169.92) --
-	(382.55,170.39) --
-	(382.93,170.85) --
-	(383.31,171.32) --
-	(383.69,171.78) --
-	(384.07,172.24) --
-	(384.45,172.69) --
-	(384.83,173.15) --
-	(385.21,173.60) --
-	(385.59,174.06) --
-	(385.97,174.51) --
-	(386.34,174.96) --
-	(386.72,175.41) --
-	(387.10,175.86) --
-	(387.48,176.30) --
-	(387.86,176.75) --
-	(388.24,177.19) --
-	(388.62,177.63) --
-	(389.00,178.07) --
-	(389.38,178.51) --
-	(389.76,178.94) --
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (338.88,115.69) --
+	(339.26,116.14) --
+	(339.64,116.59) --
+	(340.02,117.04) --
+	(340.40,117.49) --
+	(340.78,117.94) --
+	(341.16,118.39) --
+	(341.54,118.85) --
+	(341.92,119.30) --
+	(342.30,119.76) --
+	(342.68,120.22) --
+	(343.06,120.68) --
+	(343.44,121.14) --
+	(343.82,121.60) --
+	(344.20,122.07) --
+	(344.58,122.53) --
+	(344.96,123.00) --
+	(345.34,123.46) --
+	(345.71,123.93) --
+	(346.09,124.40) --
+	(346.47,124.87) --
+	(346.85,125.34) --
+	(347.23,125.81) --
+	(347.61,126.28) --
+	(347.99,126.76) --
+	(348.37,127.23) --
+	(348.75,127.71) --
+	(349.13,128.18) --
+	(349.51,128.66) --
+	(349.89,129.14) --
+	(350.27,129.62) --
+	(350.65,130.10) --
+	(351.03,130.58) --
+	(351.41,131.06) --
+	(351.79,131.54) --
+	(352.17,132.02) --
+	(352.55,132.51) --
+	(352.93,132.99) --
+	(353.31,133.47) --
+	(353.69,133.96) --
+	(354.07,134.45) --
+	(354.45,134.93) --
+	(354.83,135.42) --
+	(355.21,135.91) --
+	(355.59,136.39) --
+	(355.97,136.88) --
+	(356.35,137.37) --
+	(356.73,137.86) --
+	(357.11,138.35) --
+	(357.49,138.84) --
+	(357.87,139.33) --
+	(358.25,139.82) --
+	(358.63,140.31) --
+	(359.01,140.80) --
+	(359.38,141.29) --
+	(359.76,141.78) --
+	(360.14,142.27) --
+	(360.52,142.76) --
+	(360.90,143.25) --
+	(361.28,143.74) --
+	(361.66,144.24) --
+	(362.04,144.73) --
+	(362.42,145.22) --
+	(362.80,145.71) --
+	(363.18,146.20) --
+	(363.56,146.69) --
+	(363.94,147.18) --
+	(364.32,147.68) --
+	(364.70,148.17) --
+	(365.08,148.66) --
+	(365.46,149.15) --
+	(365.84,149.64) --
+	(366.22,150.13) --
+	(366.60,150.62) --
+	(366.98,151.11) --
+	(367.36,151.59) --
+	(367.74,152.08) --
+	(368.12,152.57) --
+	(368.50,153.06) --
+	(368.88,153.55) --
+	(369.26,154.03) --
+	(369.64,154.52) --
+	(370.02,155.01) --
+	(370.40,155.49) --
+	(370.78,155.97) --
+	(371.16,156.46) --
+	(371.54,156.94) --
+	(371.92,157.42) --
+	(372.30,157.91) --
+	(372.68,158.39) --
+	(373.05,158.87) --
+	(373.43,159.35) --
+	(373.81,159.83) --
+	(374.19,160.31) --
+	(374.57,160.78) --
+	(374.95,161.26) --
+	(375.33,161.74) --
+	(375.71,162.21) --
+	(376.09,162.68) --
+	(376.47,163.16) --
+	(376.85,163.63) --
+	(377.23,164.10) --
+	(377.61,164.57) --
+	(377.99,165.04) --
+	(378.37,165.51) --
+	(378.75,165.97) --
+	(379.13,166.44) --
+	(379.51,166.90) --
+	(379.89,167.37) --
+	(380.27,167.83) --
+	(380.65,168.29) --
+	(381.03,168.75) --
+	(381.41,169.21) --
+	(381.79,169.67) --
+	(382.17,170.12) --
+	(382.55,170.58) --
+	(382.93,171.03) --
+	(383.31,171.48) --
+	(383.69,171.94) --
+	(384.07,172.39) --
+	(384.45,172.83) --
+	(384.83,173.28) --
+	(385.21,173.73) --
+	(385.59,174.17) --
+	(385.97,174.61) --
+	(386.34,175.05) --
+	(386.72,175.49) --
+	(387.10,175.93) --
+	(387.48,176.37) --
+	(387.86,176.80) --
+	(388.24,177.24) --
+	(388.62,177.67) --
+	(389.00,178.10) --
+	(389.38,178.53) --
+	(389.76,178.96) --
 	(390.14,179.38) --
 	(390.52,179.81) --
-	(390.90,180.24) --
-	(391.28,180.67) --
-	(391.66,181.10) --
-	(392.04,181.53) --
-	(392.42,181.95) --
-	(392.80,182.37) --
-	(393.18,182.79) --
-	(393.56,183.21) --
-	(393.94,183.63) --
-	(394.32,184.04) --
-	(394.70,184.46) --
-	(395.08,184.87) --
-	(395.46,185.28) --
-	(395.84,185.69) --
-	(396.22,186.09) --
-	(396.60,186.50) --
-	(396.98,186.90) --
-	(397.36,187.30) --
-	(397.74,187.70) --
-	(398.12,188.09) --
-	(398.50,188.49) --
-	(398.88,188.88) --
-	(399.26,189.27) --
-	(399.64,189.66) --
-	(400.01,190.05) --
-	(400.39,190.43) --
-	(400.77,190.82) --
-	(401.15,191.20) --
-	(401.53,191.57) --
-	(401.91,191.95) --
-	(402.29,192.33) --
-	(402.67,192.70) --
-	(403.05,193.07) --
-	(403.43,193.44) --
-	(403.81,193.81) --
-	(404.19,194.17) --
-	(404.57,194.53) --
-	(404.95,194.89) --
-	(405.33,195.25) --
-	(405.71,195.61) --
-	(406.09,195.97) --
-	(406.47,196.32) --
-	(406.85,196.67) --
-	(407.23,197.02) --
-	(407.61,197.36) --
-	(407.99,197.71) --
-	(408.37,198.05) --
-	(408.75,198.39) --
-	(409.13,198.73) --
-	(409.51,199.07) --
-	(409.89,199.40) --
-	(410.27,199.73) --
-	(410.65,200.06) --
-	(411.03,200.39) --
-	(411.41,200.72) --
-	(411.79,201.04) --
-	(412.17,201.36) --
-	(412.55,201.68) --
-	(412.93,202.00) --
-	(413.31,202.32) --
-	(413.68,202.63) --
-	(414.06,202.94) --
-	(414.44,203.25) --
-	(414.82,203.56) --
-	(415.20,203.87) --
-	(415.58,204.17) --
-	(415.96,204.47) --
-	(416.34,204.77) --
-	(416.72,205.07) --
-	(417.10,205.37) --
-	(417.48,205.66) --
-	(417.86,205.95) --
-	(418.24,206.24) --
-	(418.62,206.53) --
-	(419.00,206.82) --
-	(419.38,207.10) --
-	(419.76,207.38) --
-	(420.14,207.66) --
-	(420.52,207.94) --
-	(420.90,208.21) --
-	(421.28,208.49) --
-	(421.66,208.76) --
-	(422.04,209.03) --
-	(422.42,209.30) --
-	(422.80,209.57) --
-	(423.18,209.83) --
-	(423.56,210.09) --
-	(423.94,210.35) --
-	(424.32,210.61) --
-	(424.70,210.87) --
-	(425.08,211.12) --
-	(425.46,211.37) --
-	(425.84,211.63) --
-	(426.22,211.87) --
-	(426.60,212.12) --
-	(426.97,212.37) --
-	(427.35,212.61) --
-	(427.73,212.85) --
-	(428.11,213.09) --
-	(428.49,213.33) --
-	(428.87,213.57) --
-	(429.25,213.80) --
-	(429.63,214.03) --
-	(430.01,214.26) --
-	(430.39,214.49) --
-	(430.77,214.72) --
-	(431.15,214.95) --
-	(431.53,215.17) --
-	(431.91,215.39) --
-	(432.29,215.61) --
-	(432.67,215.83) --
-	(433.05,216.05) --
-	(433.43,216.26) --
-	(433.81,216.47) --
-	(434.19,216.69) --
-	(434.57,216.90) --
-	(434.95,217.10) --
-	(435.33,217.31) --
-	(435.71,217.52) --
-	(436.09,217.72) --
-	(436.47,217.92) --
-	(436.85,218.12) --
-	(437.23,218.32) --
-	(437.61,218.51) --
-	(437.99,218.71) --
-	(438.37,218.90) --
-	(438.75,219.09) --
-	(439.13,219.28) --
-	(439.51,219.47) --
-	(439.89,219.66) --
-	(440.27,219.85) --
-	(440.64,220.03) --
-	(441.02,220.21) --
-	(441.40,220.39) --
-	(441.78,220.57) --
-	(442.16,220.75) --
-	(442.54,220.93) --
-	(442.92,221.10) --
-	(443.30,221.27) --
-	(443.68,221.45) --
-	(444.06,221.62) --
-	(444.44,221.78) --
-	(444.82,221.95) --
-	(445.20,222.12) --
-	(445.58,222.28) --
-	(445.96,222.45) --
-	(446.34,222.61) --
-	(446.72,222.77) --
-	(447.10,222.93) --
-	(447.48,223.08) --
-	(447.86,223.24) --
-	(448.24,223.40) --
-	(448.62,223.55) --
-	(449.00,223.70) --
-	(449.38,223.85) --
-	(449.76,224.00) --
-	(450.14,224.15) --
-	(450.52,224.30) --
-	(450.90,224.44) --
-	(451.28,224.58) --
-	(451.66,224.73) --
-	(452.04,224.87) --
-	(452.42,225.01) --
-	(452.80,225.15) --
-	(453.18,225.29) --
-	(453.56,225.42) --
-	(453.93,225.56) --
-	(454.31,225.69) --
-	(454.69,225.83) --
-	(455.07,225.96) --
-	(455.45,226.09) --
-	(455.83,226.22) --
-	(456.21,226.35) --
-	(456.59,226.47) --
-	(456.97,226.60) --
-	(457.35,226.72) --
-	(457.73,226.85) --
-	(458.11,226.97) --
-	(458.49,227.09) --
-	(458.87,227.21) --
-	(459.25,227.33) --
-	(459.63,227.45) --
-	(460.01,227.56) --
-	(460.39,227.68) --
-	(460.77,227.79) --
-	(461.15,227.91) --
-	(461.53,228.02) --
-	(461.91,228.13) --
-	(462.29,228.24) --
-	(462.67,228.35) --
-	(463.05,228.46) --
-	(463.43,228.57) --
-	(463.81,228.68) --
-	(464.19,228.78) --
-	(464.57,228.89) --
-	(464.95,228.99) --
-	(465.33,229.09) --
-	(465.71,229.19) --
-	(466.09,229.29) --
-	(466.47,229.39) --
-	(466.85,229.49) --
-	(467.23,229.59) --
-	(467.60,229.69) --
-	(467.98,229.78) --
-	(468.36,229.88) --
-	(468.74,229.97) --
-	(469.12,230.07) --
-	(469.50,230.16) --
-	(469.88,230.25) --
-	(470.26,230.34) --
-	(470.64,230.43) --
-	(471.02,230.52) --
-	(471.40,230.61) --
-	(471.78,230.69) --
-	(472.16,230.78) --
-	(472.54,230.87) --
-	(472.92,230.95) --
-	(473.30,231.03) --
-	(473.68,231.12) --
-	(474.06,231.20) --
-	(474.44,231.28) --
-	(474.82,231.36) --
-	(475.20,231.44) --
-	(475.58,231.52) --
-	(475.96,231.60) --
-	(476.34,231.68) --
-	(476.72,231.75) --
-	(477.10,231.83) --
-	(477.48,231.91) --
-	(477.86,231.98) --
-	(478.24,232.05) --
-	(478.62,232.13) --
-	(479.00,232.20) --
-	(479.38,232.27) --
-	(479.76,232.34) --
-	(480.14,232.41) --
-	(480.52,232.48) --
-	(480.90,232.55) --
-	(481.27,232.62) --
-	(481.65,232.69) --
-	(482.03,232.75) --
-	(482.41,232.82) --
-	(482.79,232.89) --
-	(483.17,232.95) --
-	(483.55,233.02) --
-	(483.93,233.08) --
-	(484.31,233.14) --
-	(484.69,233.21) --
-	(485.07,233.27) --
-	(485.45,233.33) --
-	(485.83,233.39) --
-	(486.21,233.45) --
-	(486.59,233.51) --
-	(486.97,233.57) --
-	(487.35,233.63) --
-	(487.73,233.68) --
-	(488.11,233.74) --
-	(488.49,233.80) --
-	(488.87,233.85) --
-	(489.25,233.91) --
-	(489.63,233.96) --
-	(490.01,234.02) --
-	(490.39,234.07) --
-	(490.77,234.13) --
-	(491.15,234.18) --
-	(491.53,234.23) --
-	(491.91,234.28) --
-	(492.29,234.33) --
-	(492.67,234.39) --
-	(493.05,234.44) --
-	(493.43,234.49) --
-	(493.81,234.53) --
-	(494.19,234.58) --
-	(494.56,234.63) --
-	(494.94,234.68) --
-	(495.32,234.73) --
-	(495.70,234.77) --
-	(496.08,234.82) --
-	(496.46,234.87) --
-	(496.84,234.91) --
-	(497.22,234.96) --
-	(497.60,235.00) --
-	(497.98,235.04) --
-	(498.36,235.09) --
-	(498.74,235.13) --
-	(499.12,235.17) --
-	(499.50,235.22) --
-	(499.88,235.26) --
-	(500.26,235.30) --
-	(500.64,235.34) --
-	(501.02,235.38) --
-	(501.40,235.42) --
-	(501.78,235.46) --
-	(502.16,235.50) --
-	(502.54,235.54) --
-	(502.92,235.58) --
-	(503.30,235.62) --
-	(503.68,235.65) --
-	(504.06,235.69) --
-	(504.44,235.73) --
-	(504.82,235.77) --
-	(505.20,235.80) --
-	(505.58,235.84) --
-	(505.96,235.87) --
-	(506.34,235.91) --
-	(506.72,235.94) --
-	(507.10,235.98) --
-	(507.48,236.01) --
-	(507.86,236.05) --
-	(508.23,236.08) --
-	(508.61,236.11) --
-	(508.99,236.15) --
-	(509.37,236.18) --
-	(509.75,236.21) --
-	(510.13,236.24) --
-	(510.51,236.27) --
-	(510.89,236.30) --
-	(511.27,236.34) --
-	(511.65,236.37) --
-	(512.03,236.40) --
-	(512.41,236.43) --
-	(512.79,236.46) --
-	(513.17,236.49) --
-	(513.55,236.51) --
-	(513.93,236.54) --
-	(514.31,236.57) --
-	(514.69,236.60) --
-	(515.07,236.63) --
-	(515.45,236.65) --
-	(515.83,236.68) --
-	(516.21,236.71) --
-	(516.59,236.74) --
-	(516.97,236.76) --
-	(517.35,236.79) --
-	(517.73,236.81) --
-	(518.11,236.84) --
-	(518.49,236.87) --
-	(518.87,236.89) --
-	(519.25,236.92) --
-	(519.63,236.94) --
-	(520.01,236.96) --
-	(520.39,236.99) --
-	(520.77,237.01) --
-	(521.15,237.04) --
-	(521.53,237.06) --
-	(521.90,237.08) --
-	(522.28,237.11) --
-	(522.66,237.13) --
-	(523.04,237.15) --
-	(523.42,237.17) --
-	(523.80,237.19) --
-	(524.18,237.22) --
-	(524.56,237.24) --
-	(524.94,237.26) --
-	(525.32,237.28) --
-	(525.70,237.30) --
-	(526.08,237.32) --
-	(526.46,237.34) --
-	(526.84,237.36) --
-	(527.22,237.38) --
-	(527.60,237.40) --
-	(527.98,237.42) --
-	(528.36,237.44);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (338.88, 93.87) --
-	(339.26, 93.64) --
-	(339.64, 93.40) --
-	(340.02, 93.17) --
-	(340.40, 92.94) --
-	(340.78, 92.71) --
-	(341.16, 92.48) --
-	(341.54, 92.26) --
-	(341.92, 92.03) --
-	(342.30, 91.80) --
-	(342.68, 91.58) --
-	(343.06, 91.35) --
-	(343.44, 91.13) --
-	(343.82, 90.91) --
-	(344.20, 90.69) --
-	(344.58, 90.46) --
-	(344.96, 90.24) --
-	(345.34, 90.02) --
-	(345.71, 89.81) --
-	(346.09, 89.59) --
-	(346.47, 89.37) --
-	(346.85, 89.16) --
-	(347.23, 88.94) --
-	(347.61, 88.73) --
-	(347.99, 88.51) --
-	(348.37, 88.30) --
-	(348.75, 88.09) --
-	(349.13, 87.88) --
-	(349.51, 87.67) --
-	(349.89, 87.46) --
+	(390.90,180.23) --
+	(391.28,180.65) --
+	(391.66,181.07) --
+	(392.04,181.49) --
+	(392.42,181.90) --
+	(392.80,182.32) --
+	(393.18,182.73) --
+	(393.56,183.14) --
+	(393.94,183.55) --
+	(394.32,183.96) --
+	(394.70,184.36) --
+	(395.08,184.77) --
+	(395.46,185.17) --
+	(395.84,185.57) --
+	(396.22,185.97) --
+	(396.60,186.36) --
+	(396.98,186.76) --
+	(397.36,187.15) --
+	(397.74,187.54) --
+	(398.12,187.93) --
+	(398.50,188.32) --
+	(398.88,188.70) --
+	(399.26,189.09) --
+	(399.64,189.47) --
+	(400.01,189.85) --
+	(400.39,190.23) --
+	(400.77,190.60) --
+	(401.15,190.98) --
+	(401.53,191.35) --
+	(401.91,191.72) --
+	(402.29,192.09) --
+	(402.67,192.46) --
+	(403.05,192.82) --
+	(403.43,193.18) --
+	(403.81,193.55) --
+	(404.19,193.90) --
+	(404.57,194.26) --
+	(404.95,194.62) --
+	(405.33,194.97) --
+	(405.71,195.32) --
+	(406.09,195.67) --
+	(406.47,196.02) --
+	(406.85,196.36) --
+	(407.23,196.71) --
+	(407.61,197.05) --
+	(407.99,197.39) --
+	(408.37,197.72) --
+	(408.75,198.06) --
+	(409.13,198.39) --
+	(409.51,198.73) --
+	(409.89,199.06) --
+	(410.27,199.38) --
+	(410.65,199.71) --
+	(411.03,200.03) --
+	(411.41,200.35) --
+	(411.79,200.67) --
+	(412.17,200.99) --
+	(412.55,201.31) --
+	(412.93,201.62) --
+	(413.31,201.93) --
+	(413.68,202.24) --
+	(414.06,202.55) --
+	(414.44,202.86) --
+	(414.82,203.16) --
+	(415.20,203.47) --
+	(415.58,203.77) --
+	(415.96,204.06) --
+	(416.34,204.36) --
+	(416.72,204.66) --
+	(417.10,204.95) --
+	(417.48,205.24) --
+	(417.86,205.53) --
+	(418.24,205.81) --
+	(418.62,206.10) --
+	(419.00,206.38) --
+	(419.38,206.66) --
+	(419.76,206.94) --
+	(420.14,207.22) --
+	(420.52,207.49) --
+	(420.90,207.77) --
+	(421.28,208.04) --
+	(421.66,208.31) --
+	(422.04,208.58) --
+	(422.42,208.84) --
+	(422.80,209.11) --
+	(423.18,209.37) --
+	(423.56,209.63) --
+	(423.94,209.89) --
+	(424.32,210.15) --
+	(424.70,210.40) --
+	(425.08,210.65) --
+	(425.46,210.90) --
+	(425.84,211.15) --
+	(426.22,211.40) --
+	(426.60,211.65) --
+	(426.97,211.89) --
+	(427.35,212.13) --
+	(427.73,212.37) --
+	(428.11,212.61) --
+	(428.49,212.85) --
+	(428.87,213.08) --
+	(429.25,213.32) --
+	(429.63,213.55) --
+	(430.01,213.78) --
+	(430.39,214.01) --
+	(430.77,214.23) --
+	(431.15,214.46) --
+	(431.53,214.68) --
+	(431.91,214.90) --
+	(432.29,215.12) --
+	(432.67,215.34) --
+	(433.05,215.56) --
+	(433.43,215.77) --
+	(433.81,215.98) --
+	(434.19,216.19) --
+	(434.57,216.40) --
+	(434.95,216.61) --
+	(435.33,216.82) --
+	(435.71,217.02) --
+	(436.09,217.23) --
+	(436.47,217.43) --
+	(436.85,217.63) --
+	(437.23,217.82) --
+	(437.61,218.02) --
+	(437.99,218.22) --
+	(438.37,218.41) --
+	(438.75,218.60) --
+	(439.13,218.79) --
+	(439.51,218.98) --
+	(439.89,219.17) --
+	(440.27,219.35) --
+	(440.64,219.54) --
+	(441.02,219.72) --
+	(441.40,219.90) --
+	(441.78,220.08) --
+	(442.16,220.26) --
+	(442.54,220.44) --
+	(442.92,220.61) --
+	(443.30,220.79) --
+	(443.68,220.96) --
+	(444.06,221.13) --
+	(444.44,221.30) --
+	(444.82,221.47) --
+	(445.20,221.63) --
+	(445.58,221.80) --
+	(445.96,221.96) --
+	(446.34,222.13) --
+	(446.72,222.29) --
+	(447.10,222.45) --
+	(447.48,222.61) --
+	(447.86,222.76) --
+	(448.24,222.92) --
+	(448.62,223.07) --
+	(449.00,223.23) --
+	(449.38,223.38) --
+	(449.76,223.53) --
+	(450.14,223.68) --
+	(450.52,223.83) --
+	(450.90,223.97) --
+	(451.28,224.12) --
+	(451.66,224.26) --
+	(452.04,224.40) --
+	(452.42,224.55) --
+	(452.80,224.69) --
+	(453.18,224.83) --
+	(453.56,224.96) --
+	(453.93,225.10) --
+	(454.31,225.24) --
+	(454.69,225.37) --
+	(455.07,225.50) --
+	(455.45,225.63) --
+	(455.83,225.77) --
+	(456.21,225.90) --
+	(456.59,226.02) --
+	(456.97,226.15) --
+	(457.35,226.28) --
+	(457.73,226.40) --
+	(458.11,226.53) --
+	(458.49,226.65) --
+	(458.87,226.77) --
+	(459.25,226.89) --
+	(459.63,227.01) --
+	(460.01,227.13) --
+	(460.39,227.25) --
+	(460.77,227.36) --
+	(461.15,227.48) --
+	(461.53,227.59) --
+	(461.91,227.71) --
+	(462.29,227.82) --
+	(462.67,227.93) --
+	(463.05,228.04) --
+	(463.43,228.15) --
+	(463.81,228.26) --
+	(464.19,228.36) --
+	(464.57,228.47) --
+	(464.95,228.58) --
+	(465.33,228.68) --
+	(465.71,228.78) --
+	(466.09,228.89) --
+	(466.47,228.99) --
+	(466.85,229.09) --
+	(467.23,229.19) --
+	(467.60,229.29) --
+	(467.98,229.38) --
+	(468.36,229.48) --
+	(468.74,229.58) --
+	(469.12,229.67) --
+	(469.50,229.77) --
+	(469.88,229.86) --
+	(470.26,229.95) --
+	(470.64,230.04) --
+	(471.02,230.13) --
+	(471.40,230.22) --
+	(471.78,230.31) --
+	(472.16,230.40) --
+	(472.54,230.49) --
+	(472.92,230.58) --
+	(473.30,230.66) --
+	(473.68,230.75) --
+	(474.06,230.83) --
+	(474.44,230.91) --
+	(474.82,231.00) --
+	(475.20,231.08) --
+	(475.58,231.16) --
+	(475.96,231.24) --
+	(476.34,231.32) --
+	(476.72,231.40) --
+	(477.10,231.48) --
+	(477.48,231.55) --
+	(477.86,231.63) --
+	(478.24,231.70) --
+	(478.62,231.78) --
+	(479.00,231.85) --
+	(479.38,231.93) --
+	(479.76,232.00) --
+	(480.14,232.07) --
+	(480.52,232.14) --
+	(480.90,232.22) --
+	(481.27,232.29) --
+	(481.65,232.36) --
+	(482.03,232.42) --
+	(482.41,232.49) --
+	(482.79,232.56) --
+	(483.17,232.63) --
+	(483.55,232.69) --
+	(483.93,232.76) --
+	(484.31,232.82) --
+	(484.69,232.89) --
+	(485.07,232.95) --
+	(485.45,233.02) --
+	(485.83,233.08) --
+	(486.21,233.14) --
+	(486.59,233.20) --
+	(486.97,233.26) --
+	(487.35,233.32) --
+	(487.73,233.38) --
+	(488.11,233.44) --
+	(488.49,233.50) --
+	(488.87,233.56) --
+	(489.25,233.61) --
+	(489.63,233.67) --
+	(490.01,233.73) --
+	(490.39,233.78) --
+	(490.77,233.84) --
+	(491.15,233.89) --
+	(491.53,233.95) --
+	(491.91,234.00) --
+	(492.29,234.05) --
+	(492.67,234.11) --
+	(493.05,234.16) --
+	(493.43,234.21) --
+	(493.81,234.26) --
+	(494.19,234.31) --
+	(494.56,234.36) --
+	(494.94,234.41) --
+	(495.32,234.46) --
+	(495.70,234.51) --
+	(496.08,234.56) --
+	(496.46,234.60) --
+	(496.84,234.65) --
+	(497.22,234.70) --
+	(497.60,234.74) --
+	(497.98,234.79) --
+	(498.36,234.83) --
+	(498.74,234.88) --
+	(499.12,234.92) --
+	(499.50,234.97) --
+	(499.88,235.01) --
+	(500.26,235.05) --
+	(500.64,235.10) --
+	(501.02,235.14) --
+	(501.40,235.18) --
+	(501.78,235.22) --
+	(502.16,235.26) --
+	(502.54,235.30) --
+	(502.92,235.34) --
+	(503.30,235.38) --
+	(503.68,235.42) --
+	(504.06,235.46) --
+	(504.44,235.50) --
+	(504.82,235.54) --
+	(505.20,235.58) --
+	(505.58,235.61) --
+	(505.96,235.65) --
+	(506.34,235.69) --
+	(506.72,235.72) --
+	(507.10,235.76) --
+	(507.48,235.80) --
+	(507.86,235.83) --
+	(508.23,235.87) --
+	(508.61,235.90) --
+	(508.99,235.93) --
+	(509.37,235.97) --
+	(509.75,236.00) --
+	(510.13,236.04) --
+	(510.51,236.07) --
+	(510.89,236.10) --
+	(511.27,236.13) --
+	(511.65,236.17) --
+	(512.03,236.20) --
+	(512.41,236.23) --
+	(512.79,236.26) --
+	(513.17,236.29) --
+	(513.55,236.32) --
+	(513.93,236.35) --
+	(514.31,236.38) --
+	(514.69,236.41) --
+	(515.07,236.44) --
+	(515.45,236.47) --
+	(515.83,236.50) --
+	(516.21,236.52) --
+	(516.59,236.55) --
+	(516.97,236.58) --
+	(517.35,236.61) --
+	(517.73,236.64) --
+	(518.11,236.66) --
+	(518.49,236.69) --
+	(518.87,236.72) --
+	(519.25,236.74) --
+	(519.63,236.77) --
+	(520.01,236.79) --
+	(520.39,236.82) --
+	(520.77,236.84) --
+	(521.15,236.87) --
+	(521.53,236.89) --
+	(521.90,236.92) --
+	(522.28,236.94) --
+	(522.66,236.96) --
+	(523.04,236.99) --
+	(523.42,237.01) --
+	(523.80,237.03) --
+	(524.18,237.06) --
+	(524.56,237.08) --
+	(524.94,237.10) --
+	(525.32,237.13) --
+	(525.70,237.15) --
+	(526.08,237.17) --
+	(526.46,237.19) --
+	(526.84,237.21) --
+	(527.22,237.23) --
+	(527.60,237.25) --
+	(527.98,237.27) --
+	(528.36,237.29);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (338.88, 93.77) --
+	(339.26, 93.54) --
+	(339.64, 93.31) --
+	(340.02, 93.08) --
+	(340.40, 92.85) --
+	(340.78, 92.63) --
+	(341.16, 92.40) --
+	(341.54, 92.18) --
+	(341.92, 91.95) --
+	(342.30, 91.73) --
+	(342.68, 91.51) --
+	(343.06, 91.29) --
+	(343.44, 91.07) --
+	(343.82, 90.85) --
+	(344.20, 90.63) --
+	(344.58, 90.41) --
+	(344.96, 90.19) --
+	(345.34, 89.98) --
+	(345.71, 89.76) --
+	(346.09, 89.55) --
+	(346.47, 89.33) --
+	(346.85, 89.12) --
+	(347.23, 88.91) --
+	(347.61, 88.70) --
+	(347.99, 88.49) --
+	(348.37, 88.28) --
+	(348.75, 88.07) --
+	(349.13, 87.86) --
+	(349.51, 87.66) --
+	(349.89, 87.45) --
 	(350.27, 87.25) --
-	(350.65, 87.05) --
+	(350.65, 87.04) --
 	(351.03, 86.84) --
@@
 	(352.17, 86.23) --
-	(352.55, 86.02) --
-	(352.93, 85.82) --
-	(353.31, 85.62) --
-	(353.69, 85.42) --
-	(354.07, 85.22) --
-	(354.45, 85.02) --
-	(354.83, 84.83) --
-	(355.21, 84.63) --
-	(355.59, 84.43) --
-	(355.97, 84.24) --
-	(356.35, 84.04) --
-	(356.73, 83.85) --
-	(357.11, 83.66) --
-	(357.49, 83.47) --
-	(357.87, 83.28) --
-	(358.25, 83.09) --
-	(358.63, 82.90) --
-	(359.01, 82.71) --
-	(359.38, 82.52) --
-	(359.76, 82.33) --
-	(360.14, 82.15) --
-	(360.52, 81.96) --
-	(360.90, 81.78) --
-	(361.28, 81.60) --
-	(361.66, 81.41) --
-	(362.04, 81.23) --
-	(362.42, 81.05) --
-	(362.80, 80.87) --
-	(363.18, 80.69) --
-	(363.56, 80.52) --
-	(363.94, 80.34) --
-	(364.32, 80.16) --
-	(364.70, 79.99) --
-	(365.08, 79.81) --
-	(365.46, 79.64) --
-	(365.84, 79.46) --
-	(366.22, 79.29) --
-	(366.60, 79.12) --
-	(366.98, 78.95) --
-	(367.36, 78.78) --
-	(367.74, 78.61) --
-	(368.12, 78.44) --
-	(368.50, 78.27) --
-	(368.88, 78.11) --
-	(369.26, 77.94) --
-	(369.64, 77.78) --
-	(370.02, 77.61) --
-	(370.40, 77.45) --
-	(370.78, 77.29) --
-	(371.16, 77.13) --
-	(371.54, 76.96) --
-	(371.92, 76.80) --
-	(372.30, 76.64) --
-	(372.68, 76.49) --
-	(373.05, 76.33) --
-	(373.43, 76.17) --
-	(373.81, 76.01) --
-	(374.19, 75.86) --
-	(374.57, 75.70) --
-	(374.95, 75.55) --
-	(375.33, 75.40) --
-	(375.71, 75.24) --
-	(376.09, 75.09) --
-	(376.47, 74.94) --
-	(376.85, 74.79) --
-	(377.23, 74.64) --
-	(377.61, 74.49) --
-	(377.99, 74.34) --
-	(378.37, 74.20) --
-	(378.75, 74.05) --
-	(379.13, 73.91) --
-	(379.51, 73.76) --
-	(379.89, 73.62) --
-	(380.27, 73.47) --
-	(380.65, 73.33) --
-	(381.03, 73.19) --
-	(381.41, 73.05) --
-	(381.79, 72.91) --
-	(382.17, 72.77) --
-	(382.55, 72.63) --
-	(382.93, 72.49) --
-	(383.31, 72.35) --
-	(383.69, 72.22) --
-	(384.07, 72.08) --
-	(384.45, 71.94) --
-	(384.83, 71.81) --
-	(385.21, 71.68) --
-	(385.59, 71.54) --
-	(385.97, 71.41) --
-	(386.34, 71.28) --
-	(386.72, 71.15) --
-	(387.10, 71.02) --
-	(387.48, 70.89) --
-	(387.86, 70.76) --
-	(388.24, 70.63) --
-	(388.62, 70.50) --
-	(389.00, 70.37) --
-	(389.38, 70.25) --
-	(389.76, 70.12) --
-	(390.14, 70.00) --
-	(390.52, 69.87) --
-	(390.90, 69.75) --
-	(391.28, 69.63) --
-	(391.66, 69.50) --
-	(392.04, 69.38) --
-	(392.42, 69.26) --
-	(392.80, 69.14) --
-	(393.18, 69.02) --
-	(393.56, 68.90) --
-	(393.94, 68.78) --
-	(394.32, 68.67) --
-	(394.70, 68.55) --
-	(395.08, 68.43) --
-	(395.46, 68.32) --
-	(395.84, 68.20) --
-	(396.22, 68.09) --
-	(396.60, 67.97) --
-	(396.98, 67.86) --
-	(397.36, 67.75) --
-	(397.74, 67.64) --
-	(398.12, 67.53) --
-	(398.50, 67.42) --
-	(398.88, 67.31) --
-	(399.26, 67.20) --
-	(399.64, 67.09) --
-	(400.01, 66.98) --
-	(400.39, 66.87) --
-	(400.77, 66.76) --
-	(401.15, 66.66) --
-	(401.53, 66.55) --
-	(401.91, 66.45) --
-	(402.29, 66.34) --
-	(402.67, 66.24) --
-	(403.05, 66.14) --
-	(403.43, 66.03) --
-	(403.81, 65.93) --
-	(404.19, 65.83) --
-	(404.57, 65.73) --
-	(404.95, 65.63) --
-	(405.33, 65.53) --
-	(405.71, 65.43) --
-	(406.09, 65.33) --
-	(406.47, 65.23) --
-	(406.85, 65.13) --
-	(407.23, 65.04) --
-	(407.61, 64.94) --
-	(407.99, 64.84) --
-	(408.37, 64.75) --
-	(408.75, 64.65) --
-	(409.13, 64.56) --
-	(409.51, 64.47) --
-	(409.89, 64.37) --
-	(410.27, 64.28) --
-	(410.65, 64.19) --
-	(411.03, 64.10) --
-	(411.41, 64.01) --
-	(411.79, 63.91) --
-	(412.17, 63.82) --
-	(412.55, 63.74) --
-	(412.93, 63.65) --
-	(413.31, 63.56) --
-	(413.68, 63.47) --
-	(414.06, 63.38) --
-	(414.44, 63.30) --
-	(414.82, 63.21) --
-	(415.20, 63.12) --
-	(415.58, 63.04) --
-	(415.96, 62.95) --
-	(416.34, 62.87) --
-	(416.72, 62.79) --
-	(417.10, 62.70) --
-	(417.48, 62.62) --
-	(417.86, 62.54) --
-	(418.24, 62.46) --
-	(418.62, 62.37) --
-	(419.00, 62.29) --
-	(419.38, 62.21) --
-	(419.76, 62.13) --
-	(420.14, 62.05) --
-	(420.52, 61.98) --
-	(420.90, 61.90) --
-	(421.28, 61.82) --
-	(421.66, 61.74) --
-	(422.04, 61.66) --
-	(422.42, 61.59) --
-	(422.80, 61.51) --
-	(423.18, 61.44) --
-	(423.56, 61.36) --
-	(423.94, 61.29) --
-	(424.32, 61.21) --
-	(424.70, 61.14) --
-	(425.08, 61.06) --
-	(425.46, 60.99) --
-	(425.84, 60.92) --
-	(426.22, 60.85) --
-	(426.60, 60.78) --
-	(426.97, 60.70) --
-	(427.35, 60.63) --
-	(427.73, 60.56) --
-	(428.11, 60.49) --
-	(428.49, 60.42) --
-	(428.87, 60.35) --
-	(429.25, 60.29) --
-	(429.63, 60.22) --
-	(430.01, 60.15) --
-	(430.39, 60.08) --
-	(430.77, 60.02) --
-	(431.15, 59.95) --
-	(431.53, 59.88) --
-	(431.91, 59.82) --
-	(432.29, 59.75) --
-	(432.67, 59.69) --
-	(433.05, 59.62) --
-	(433.43, 59.56) --
-	(433.81, 59.49) --
-	(434.19, 59.43) --
-	(434.57, 59.37) --
-	(434.95, 59.31) --
-	(435.33, 59.24) --
-	(435.71, 59.18) --
-	(436.09, 59.12) --
-	(436.47, 59.06) --
-	(436.85, 59.00) --
-	(437.23, 58.94) --
-	(437.61, 58.88) --
-	(437.99, 58.82) --
-	(438.37, 58.76) --
-	(438.75, 58.70) --
-	(439.13, 58.64) --
-	(439.51, 58.59) --
-	(439.89, 58.53) --
-	(440.27, 58.47) --
-	(440.64, 58.41) --
-	(441.02, 58.36) --
-	(441.40, 58.30) --
-	(441.78, 58.24) --
-	(442.16, 58.19) --
-	(442.54, 58.13) --
-	(442.92, 58.08) --
-	(443.30, 58.02) --
-	(443.68, 57.97) --
-	(444.06, 57.92) --
-	(444.44, 57.86) --
-	(444.82, 57.81) --
-	(445.20, 57.76) --
-	(445.58, 57.70) --
-	(445.96, 57.65) --
-	(446.34, 57.60) --
-	(446.72, 57.55) --
-	(447.10, 57.50) --
-	(447.48, 57.45) --
-	(447.86, 57.40) --
-	(448.24, 57.35) --
-	(448.62, 57.30) --
-	(449.00, 57.25) --
-	(449.38, 57.20) --
-	(449.76, 57.15) --
-	(450.14, 57.10) --
-	(450.52, 57.05) --
-	(450.90, 57.00) --
-	(451.28, 56.96) --
-	(451.66, 56.91) --
-	(452.04, 56.86) --
-	(452.42, 56.81) --
-	(452.80, 56.77) --
-	(453.18, 56.72) --
-	(453.56, 56.68) --
-	(453.93, 56.63) --
-	(454.31, 56.59) --
-	(454.69, 56.54) --
-	(455.07, 56.50) --
-	(455.45, 56.45) --
-	(455.83, 56.41) --
-	(456.21, 56.36) --
-	(456.59, 56.32) --
-	(456.97, 56.28) --
-	(457.35, 56.23) --
-	(457.73, 56.19) --
-	(458.11, 56.15) --
-	(458.49, 56.11) --
-	(458.87, 56.06) --
-	(459.25, 56.02) --
-	(459.63, 55.98) --
-	(460.01, 55.94) --
-	(460.39, 55.90) --
-	(460.77, 55.86) --
-	(461.15, 55.82) --
-	(461.53, 55.78) --
-	(461.91, 55.74) --
-	(462.29, 55.70) --
-	(462.67, 55.66) --
-	(463.05, 55.62) --
-	(463.43, 55.58) --
-	(463.81, 55.54) --
-	(464.19, 55.50) --
-	(464.57, 55.47) --
-	(464.95, 55.43) --
-	(465.33, 55.39) --
-	(465.71, 55.35) --
-	(466.09, 55.32) --
-	(466.47, 55.28) --
-	(466.85, 55.24) --
-	(467.23, 55.21) --
-	(467.60, 55.17) --
-	(467.98, 55.13) --
-	(468.36, 55.10) --
-	(468.74, 55.06) --
-	(469.12, 55.03) --
-	(469.50, 54.99) --
-	(469.88, 54.96) --
-	(470.26, 54.92) --
-	(470.64, 54.89) --
-	(471.02, 54.85) --
-	(471.40, 54.82) --
-	(471.78, 54.79) --
-	(472.16, 54.75) --
-	(472.54, 54.72) --
-	(472.92, 54.69) --
-	(473.30, 54.65) --
-	(473.68, 54.62) --
-	(474.06, 54.59) --
-	(474.44, 54.56) --
-	(474.82, 54.53) --
-	(475.20, 54.49) --
-	(475.58, 54.46) --
-	(475.96, 54.43) --
-	(476.34, 54.40) --
-	(476.72, 54.37) --
-	(477.10, 54.34) --
-	(477.48, 54.31) --
-	(477.86, 54.28) --
-	(478.24, 54.25) --
-	(478.62, 54.22) --
-	(479.00, 54.19) --
-	(479.38, 54.16) --
-	(479.76, 54.13) --
-	(480.14, 54.10) --
-	(480.52, 54.07) --
-	(480.90, 54.04) --
-	(481.27, 54.01) --
-	(481.65, 53.99) --
-	(482.03, 53.96) --
-	(482.41, 53.93) --
-	(482.79, 53.90) --
-	(483.17, 53.87) --
-	(483.55, 53.85) --
-	(483.93, 53.82) --
-	(484.31, 53.79) --
-	(484.69, 53.77) --
-	(485.07, 53.74) --
-	(485.45, 53.71) --
-	(485.83, 53.69) --
-	(486.21, 53.66) --
-	(486.59, 53.63) --
-	(486.97, 53.61) --
-	(487.35, 53.58) --
-	(487.73, 53.56) --
-	(488.11, 53.53) --
-	(488.49, 53.51) --
-	(488.87, 53.48) --
-	(489.25, 53.46) --
-	(489.63, 53.43) --
-	(490.01, 53.41) --
-	(490.39, 53.38) --
-	(490.77, 53.36) --
-	(491.15, 53.33) --
-	(491.53, 53.31) --
-	(491.91, 53.29) --
-	(492.29, 53.26) --
-	(492.67, 53.24) --
-	(493.05, 53.22) --
-	(493.43, 53.19) --
-	(493.81, 53.17) --
-	(494.19, 53.15) --
-	(494.56, 53.13) --
-	(494.94, 53.10) --
-	(495.32, 53.08) --
-	(495.70, 53.06) --
-	(496.08, 53.04) --
-	(496.46, 53.01) --
-	(496.84, 52.99) --
-	(497.22, 52.97) --
-	(497.60, 52.95) --
-	(497.98, 52.93) --
-	(498.36, 52.91) --
-	(498.74, 52.89) --
-	(499.12, 52.87) --
-	(499.50, 52.84) --
-	(499.88, 52.82) --
-	(500.26, 52.80) --
-	(500.64, 52.78) --
-	(501.02, 52.76) --
-	(501.40, 52.74) --
-	(501.78, 52.72) --
-	(502.16, 52.70) --
-	(502.54, 52.68) --
-	(502.92, 52.66) --
-	(503.30, 52.64) --
-	(503.68, 52.62) --
-	(504.06, 52.61) --
-	(504.44, 52.59) --
-	(504.82, 52.57) --
-	(505.20, 52.55) --
-	(505.58, 52.53) --
-	(505.96, 52.51) --
-	(506.34, 52.49) --
-	(506.72, 52.48) --
-	(507.10, 52.46) --
-	(507.48, 52.44) --
-	(507.86, 52.42) --
-	(508.23, 52.40) --
-	(508.61, 52.39) --
-	(508.99, 52.37) --
-	(509.37, 52.35) --
-	(509.75, 52.33) --
-	(510.13, 52.32) --
-	(510.51, 52.30) --
-	(510.89, 52.28) --
-	(511.27, 52.27) --
-	(511.65, 52.25) --
-	(512.03, 52.23) --
-	(512.41, 52.22) --
-	(512.79, 52.20) --
-	(513.17, 52.18) --
-	(513.55, 52.17) --
-	(513.93, 52.15) --
-	(514.31, 52.13) --
-	(514.69, 52.12) --
-	(515.07, 52.10) --
-	(515.45, 52.09) --
-	(515.83, 52.07) --
-	(516.21, 52.06) --
-	(516.59, 52.04) --
-	(516.97, 52.03) --
-	(517.35, 52.01) --
-	(517.73, 52.00) --
-	(518.11, 51.98) --
-	(518.49, 51.97) --
-	(518.87, 51.95) --
-	(519.25, 51.94) --
-	(519.63, 51.92) --
-	(520.01, 51.91) --
-	(520.39, 51.89) --
-	(520.77, 51.88) --
-	(521.15, 51.86) --
-	(521.53, 51.85) --
-	(521.90, 51.84) --
-	(522.28, 51.82) --
-	(522.66, 51.81) --
-	(523.04, 51.80) --
-	(523.42, 51.78) --
-	(523.80, 51.77) --
-	(524.18, 51.75) --
-	(524.56, 51.74) --
-	(524.94, 51.73) --
-	(525.32, 51.72) --
-	(525.70, 51.70) --
-	(526.08, 51.69) --
-	(526.46, 51.68) --
-	(526.84, 51.66) --
-	(527.22, 51.65) --
-	(527.60, 51.64) --
-	(527.98, 51.63) --
-	(528.36, 51.61);
+	(352.55, 86.03) --
+	(352.93, 85.83) --
+	(353.31, 85.64) --
+	(353.69, 85.44) --
+	(354.07, 85.24) --
+	(354.45, 85.05) --
+	(354.83, 84.85) --
+	(355.21, 84.66) --
+	(355.59, 84.46) --
+	(355.97, 84.27) --
+	(356.35, 84.08) --
+	(356.73, 83.89) --
+	(357.11, 83.70) --
+	(357.49, 83.51) --
+	(357.87, 83.32) --
+	(358.25, 83.13) --
+	(358.63, 82.95) --
+	(359.01, 82.76) --
+	(359.38, 82.58) --
+	(359.76, 82.39) --
+	(360.14, 82.21) --
+	(360.52, 82.03) --
+	(360.90, 81.84) --
+	(361.28, 81.66) --
+	(361.66, 81.48) --
+	(362.04, 81.30) --
+	(362.42, 81.13) --
+	(362.80, 80.95) --
+	(363.18, 80.77) --
+	(363.56, 80.60) --
+	(363.94, 80.42) --
+	(364.32, 80.25) --
+	(364.70, 80.07) --
+	(365.08, 79.90) --
+	(365.46, 79.73) --
+	(365.84, 79.56) --
+	(366.22, 79.39) --
+	(366.60, 79.22) --
+	(366.98, 79.05) --
+	(367.36, 78.88) --
+	(367.74, 78.71) --
+	(368.12, 78.55) --
+	(368.50, 78.38) --
+	(368.88, 78.21) --
+	(369.26, 78.05) --
+	(369.64, 77.89) --
+	(370.02, 77.72) --
+	(370.40, 77.56) --
+	(370.78, 77.40) --
+	(371.16, 77.24) --
+	(371.54, 77.08) --
+	(371.92, 76.92) --
+	(372.30, 76.77) --
+	(372.68, 76.61) --
+	(373.05, 76.45) --
+	(373.43, 76.30) --
+	(373.81, 76.14) --
+	(374.19, 75.99) --
+	(374.57, 75.83) --
+	(374.95, 75.68) --
+	(375.33, 75.53) --
+	(375.71, 75.38) --
+	(376.09, 75.23) --
+	(376.47, 75.08) --
+	(376.85, 74.93) --
+	(377.23, 74.78) --
+	(377.61, 74.63) --
+	(377.99, 74.49) --
+	(378.37, 74.34) --
+	(378.75, 74.20) --
+	(379.13, 74.05) --
+	(379.51, 73.91) --
+	(379.89, 73.77) --
+	(380.27, 73.62) --
+	(380.65, 73.48) --
+	(381.03, 73.34) --
+	(381.41, 73.20) --
+	(381.79, 73.06) --
+	(382.17, 72.92) --
+	(382.55, 72.79) --
+	(382.93, 72.65) --
+	(383.31, 72.51) --
+	(383.69, 72.38) --
+	(384.07, 72.24) --
+	(384.45, 72.11) --
+	(384.83, 71.97) --
+	(385.21, 71.84) --
+	(385.59, 71.71) --
+	(385.97, 71.58) --
+	(386.34, 71.45) --
+	(386.72, 71.31) --
+	(387.10, 71.19) --
+	(387.48, 71.06) --
+	(387.86, 70.93) --
+	(388.24, 70.80) --
+	(388.62, 70.67) --
+	(389.00, 70.55) --
+	(389.38, 70.42) --
+	(389.76, 70.30) --
+	(390.14, 70.17) --
+	(390.52, 70.05) --
+	(390.90, 69.93) --
+	(391.28, 69.80) --
+	(391.66, 69.68) --
+	(392.04, 69.56) --
+	(392.42, 69.44) --
+	(392.80, 69.32) --
+	(393.18, 69.20) --
+	(393.56, 69.09) --
+	(393.94, 68.97) --
+	(394.32, 68.85) --
+	(394.70, 68.73) --
+	(395.08, 68.62) --
+	(395.46, 68.50) --
+	(395.84, 68.39) --
+	(396.22, 68.28) --
+	(396.60, 68.16) --
+	(396.98, 68.05) --
+	(397.36, 67.94) --
+	(397.74, 67.83) --
+	(398.12, 67.71) --
+	(398.50, 67.60) --
+	(398.88, 67.50) --
+	(399.26, 67.39) --
+	(399.64, 67.28) --
+	(400.01, 67.17) --
+	(400.39, 67.06) --
+	(400.77, 66.96) --
+	(401.15, 66.85) --
+	(401.53, 66.75) --
+	(401.91, 66.64) --
+	(402.29, 66.54) --
+	(402.67, 66.43) --
+	(403.05, 66.33) --
+	(403.43, 66.23) --
+	(403.81, 66.13) --
+	(404.19, 66.02) --
+	(404.57, 65.92) --
+	(404.95, 65.82) --
+	(405.33, 65.72) --
+	(405.71, 65.62) --
+	(406.09, 65.53) --
+	(406.47, 65.43) --
+	(406.85, 65.33) --
+	(407.23, 65.23) --
+	(407.61, 65.14) --
+	(407.99, 65.04) --
+	(408.37, 64.95) --
+	(408.75, 64.85) --
+	(409.13, 64.76) --
+	(409.51, 64.66) --
+	(409.89, 64.57) --
+	(410.27, 64.48) --
+	(410.65, 64.39) --
+	(411.03, 64.30) --
+	(411.41, 64.20) --
+	(411.79, 64.11) --
+	(412.17, 64.02) --
+	(412.55, 63.93) --
+	(412.93, 63.85) --
+	(413.31, 63.76) --
+	(413.68, 63.67) --
+	(414.06, 63.58) --
+	(414.44, 63.50) --
+	(414.82, 63.41) --
+	(415.20, 63.32) --
+	(415.58, 63.24) --
+	(415.96, 63.15) --
+	(416.34, 63.07) --
+	(416.72, 62.99) --
+	(417.10, 62.90) --
+	(417.48, 62.82) --
+	(417.86, 62.74) --
+	(418.24, 62.66) --
+	(418.62, 62.57) --
+	(419.00, 62.49) --
+	(419.38, 62.41) --
+	(419.76, 62.33) --
+	(420.14, 62.25) --
+	(420.52, 62.17) --
+	(420.90, 62.10) --
+	(421.28, 62.02) --
+	(421.66, 61.94) --
+	(422.04, 61.86) --
+	(422.42, 61.79) --
+	(422.80, 61.71) --
+	(423.18, 61.63) --
+	(423.56, 61.56) --
+	(423.94, 61.48) --
+	(424.32, 61.41) --
+	(424.70, 61.34) --
+	(425.08, 61.26) --
+	(425.46, 61.19) --
+	(425.84, 61.12) --
+	(426.22, 61.04) --
+	(426.60, 60.97) --
+	(426.97, 60.90) --
+	(427.35, 60.83) --
+	(427.73, 60.76) --
+	(428.11, 60.69) --
+	(428.49, 60.62) --
+	(428.87, 60.55) --
+	(429.25, 60.48) --
+	(429.63, 60.41) --
+	(430.01, 60.34) --
+	(430.39, 60.28) --
+	(430.77, 60.21) --
+	(431.15, 60.14) --
+	(431.53, 60.08) --
+	(431.91, 60.01) --
+	(432.29, 59.94) --
+	(432.67, 59.88) --
+	(433.05, 59.81) --
+	(433.43, 59.75) --
+	(433.81, 59.69) --
+	(434.19, 59.62) --
+	(434.57, 59.56) --
+	(434.95, 59.50) --
+	(435.33, 59.43) --
+	(435.71, 59.37) --
+	(436.09, 59.31) --
+	(436.47, 59.25) --
+	(436.85, 59.19) --
+	(437.23, 59.13) --
+	(437.61, 59.07) --
+	(437.99, 59.01) --
+	(438.37, 58.95) --
+	(438.75, 58.89) --
+	(439.13, 58.83) --
+	(439.51, 58.77) --
+	(439.89, 58.71) --
+	(440.27, 58.66) --
+	(440.64, 58.60) --
+	(441.02, 58.54) --
+	(441.40, 58.49) --
+	(441.78, 58.43) --
+	(442.16, 58.37) --
+	(442.54, 58.32) --
+	(442.92, 58.26) --
+	(443.30, 58.21) --
+	(443.68, 58.15) --
+	(444.06, 58.10) --
+	(444.44, 58.04) --
+	(444.82, 57.99) --
+	(445.20, 57.94) --
+	(445.58, 57.89) --
+	(445.96, 57.83) --
+	(446.34, 57.78) --
+	(446.72, 57.73) --
+	(447.10, 57.68) --
+	(447.48, 57.63) --
+	(447.86, 57.57) --
+	(448.24, 57.52) --
+	(448.62, 57.47) --
+	(449.00, 57.42) --
+	(449.38, 57.37) --
+	(449.76, 57.32) --
+	(450.14, 57.28) --
+	(450.52, 57.23) --
+	(450.90, 57.18) --
+	(451.28, 57.13) --
+	(451.66, 57.08) --
+	(452.04, 57.03) --
+	(452.42, 56.99) --
+	(452.80, 56.94) --
+	(453.18, 56.89) --
+	(453.56, 56.85) --
+	(453.93, 56.80) --
+	(454.31, 56.76) --
+	(454.69, 56.71) --
+	(455.07, 56.67) --
+	(455.45, 56.62) --
+	(455.83, 56.58) --
+	(456.21, 56.53) --
+	(456.59, 56.49) --
+	(456.97, 56.44) --
+	(457.35, 56.40) --
+	(457.73, 56.36) --
+	(458.11, 56.31) --
+	(458.49, 56.27) --
+	(458.87, 56.23) --
+	(459.25, 56.19) --
+	(459.63, 56.14) --
+	(460.01, 56.10) --
+	(460.39, 56.06) --
+	(460.77, 56.02) --
+	(461.15, 55.98) --
+	(461.53, 55.94) --
+	(461.91, 55.90) --
+	(462.29, 55.86) --
+	(462.67, 55.82) --
+	(463.05, 55.78) --
+	(463.43, 55.74) --
+	(463.81, 55.70) --
+	(464.19, 55.66) --
+	(464.57, 55.62) --
+	(464.95, 55.59) --
+	(465.33, 55.55) --
+	(465.71, 55.51) --
+	(466.09, 55.47) --
+	(466.47, 55.43) --
+	(466.85, 55.40) --
+	(467.23, 55.36) --
+	(467.60, 55.32) --
+	(467.98, 55.29) --
+	(468.36, 55.25) --
+	(468.74, 55.22) --
+	(469.12, 55.18) --
+	(469.50, 55.14) --
+	(469.88, 55.11) --
+	(470.26, 55.07) --
+	(470.64, 55.04) --
+	(471.02, 55.00) --
+	(471.40, 54.97) --
+	(471.78, 54.94) --
+	(472.16, 54.90) --
+	(472.54, 54.87) --
+	(472.92, 54.83) --
+	(473.30, 54.80) --
+	(473.68, 54.77) --
+	(474.06, 54.74) --
+	(474.44, 54.70) --
+	(474.82, 54.67) --
+	(475.20, 54.64) --
+	(475.58, 54.61) --
+	(475.96, 54.57) --
+	(476.34, 54.54) --
+	(476.72, 54.51) --
+	(477.10, 54.48) --
+	(477.48, 54.45) --
+	(477.86, 54.42) --
+	(478.24, 54.39) --
+	(478.62, 54.36) --
+	(479.00, 54.33) --
+	(479.38, 54.30) --
+	(479.76, 54.27) --
+	(480.14, 54.24) --
+	(480.52, 54.21) --
+	(480.90, 54.18) --
+	(481.27, 54.15) --
+	(481.65, 54.12) --
+	(482.03, 54.09) --
+	(482.41, 54.06) --
+	(482.79, 54.04) --
+	(483.17, 54.01) --
+	(483.55, 53.98) --
+	(483.93, 53.95) --
+	(484.31, 53.92) --
+	(484.69, 53.90) --
+	(485.07, 53.87) --
+	(485.45, 53.84) --
+	(485.83, 53.82) --
+	(486.21, 53.79) --
+	(486.59, 53.76) --
+	(486.97, 53.74) --
+	(487.35, 53.71) --
+	(487.73, 53.68) --
+	(488.11, 53.66) --
+	(488.49, 53.63) --
+	(488.87, 53.61) --
+	(489.25, 53.58) --
+	(489.63, 53.56) --
+	(490.01, 53.53) --
+	(490.39, 53.51) --
+	(490.77, 53.48) --
+	(491.15, 53.46) --
+	(491.53, 53.43) --
+	(491.91, 53.41) --
+	(492.29, 53.39) --
+	(492.67, 53.36) --
+	(493.05, 53.34) --
+	(493.43, 53.31) --
+	(493.81, 53.29) --
+	(494.19, 53.27) --
+	(494.56, 53.24) --
+	(494.94, 53.22) --
+	(495.32, 53.20) --
+	(495.70, 53.18) --
+	(496.08, 53.15) --
+	(496.46, 53.13) --
+	(496.84, 53.11) --
+	(497.22, 53.09) --
+	(497.60, 53.06) --
+	(497.98, 53.04) --
+	(498.36, 53.02) --
+	(498.74, 53.00) --
+	(499.12, 52.98) --
+	(499.50, 52.96) --
+	(499.88, 52.94) --
+	(500.26, 52.92) --
+	(500.64, 52.89) --
+	(501.02, 52.87) --
+	(501.40, 52.85) --
+	(501.78, 52.83) --
+	(502.16, 52.81) --
+	(502.54, 52.79) --
+	(502.92, 52.77) --
+	(503.30, 52.75) --
+	(503.68, 52.73) --
+	(504.06, 52.71) --
+	(504.44, 52.69) --
+	(504.82, 52.67) --
+	(505.20, 52.66) --
+	(505.58, 52.64) --
+	(505.96, 52.62) --
+	(506.34, 52.60) --
+	(506.72, 52.58) --
+	(507.10, 52.56) --
+	(507.48, 52.54) --
+	(507.86, 52.52) --
+	(508.23, 52.51) --
+	(508.61, 52.49) --
+	(508.99, 52.47) --
+	(509.37, 52.45) --
+	(509.75, 52.43) --
+	(510.13, 52.42) --
+	(510.51, 52.40) --
+	(510.89, 52.38) --
+	(511.27, 52.36) --
+	(511.65, 52.35) --
+	(512.03, 52.33) --
+	(512.41, 52.31) --
+	(512.79, 52.30) --
+	(513.17, 52.28) --
+	(513.55, 52.26) --
+	(513.93, 52.25) --
+	(514.31, 52.23) --
+	(514.69, 52.21) --
+	(515.07, 52.20) --
+	(515.45, 52.18) --
+	(515.83, 52.17) --
+	(516.21, 52.15) --
+	(516.59, 52.13) --
+	(516.97, 52.12) --
+	(517.35, 52.10) --
+	(517.73, 52.09) --
+	(518.11, 52.07) --
+	(518.49, 52.06) --
+	(518.87, 52.04) --
+	(519.25, 52.03) --
+	(519.63, 52.01) --
+	(520.01, 52.00) --
+	(520.39, 51.98) --
+	(520.77, 51.97) --
+	(521.15, 51.95) --
+	(521.53, 51.94) --
+	(521.90, 51.92) --
+	(522.28, 51.91) --
+	(522.66, 51.90) --
+	(523.04, 51.88) --
+	(523.42, 51.87) --
+	(523.80, 51.85) --
+	(524.18, 51.84) --
+	(524.56, 51.83) --
+	(524.94, 51.81) --
+	(525.32, 51.80) --
+	(525.70, 51.79) --
+	(526.08, 51.77) --
+	(526.46, 51.76) --
+	(526.84, 51.75) --
+	(527.22, 51.73) --
+	(527.60, 51.72) --
+	(527.98, 51.71) --
+	(528.36, 51.69);
 \end{scope}

### 2020-08-29 benchmarking/benchmarkingVM/ESS_round2.tex
results update

@@
-% Created by tikzDevice version 0.12.3.1 on 2020-08-28 13:29:31
+% Created by tikzDevice version 0.12.3.1 on 2020-08-29 17:55:30
 % !TEX encoding = UTF-8 Unicode
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,548.96) {\bfseries adapt (\textit{real}) vs. adapt (\textit{cat})};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,301.03) {ESS/$10^6$ states [adapt (\textit{cat})]};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,433.62) {ESS/$10^6$ states [adapt (\textit{real})]};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,548.96) {\bfseries adapt(\textit{real}) vs. adapt(\textit{cat})};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,301.03) {ESS/$10^6$ states [adapt(\textit{cat})]};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,433.62) {ESS/$10^6$ states [adapt(\textit{real})]};
 \end{scope}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 65.57,467.04) --
-	( 94.44,467.04);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 83.64,464.05) --
-	( 83.64,469.74);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 83.64,463.82) {$p$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.43,448.03) --
-	(181.61,448.03);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.14,444.87) --
-	(179.14,450.86);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.14,444.00) {$L$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 75.12,473.24) --
-	( 87.57,473.24);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 82.04,472.46) --
-	( 82.04,473.99);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 82.04,469.20) {$r$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 72.91,435.02) --
-	(108.34,435.02);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 95.99,431.48) --
-	( 95.99,438.16);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 95.99,430.99) {$h$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 33.73,468.13) --
-	( 71.46,468.13);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 58.63,465.86) --
-	( 58.63,470.24);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 58.63,465.23) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.10,477.42) --
-	(191.54,477.42);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.83,476.86) --
-	(190.83,477.97);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.83,474.52) {$\kappa$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.58,471.54) --
-	(177.22,471.54);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.41,470.69) --
-	(176.41,472.36);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.41,468.31) {$p$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.37,474.80) --
-	(192.12,474.80);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.31,472.77) --
-	(190.31,476.70);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.31,470.77) {$L$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.74,479.57) --
-	(184.28,479.57);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.01,479.29) --
-	(184.01,479.85);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.01,475.54) {$r$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (163.78,454.70) --
-	(167.31,454.70);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (165.60,453.16) --
-	(165.60,456.15);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (165.60,450.66) {$h$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.43,473.34) --
-	(177.25,473.34);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.41,472.63) --
-	(175.41,474.04);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (175.41,470.44) {$\sigma$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.32,481.45) --
-	(192.47,481.45);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.90,480.91) --
-	(191.90,481.98);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.90,478.54) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 62.11,469.76) --
+	( 85.06,469.76);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 75.92,467.35) --
+	( 75.92,471.98);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 75.92,466.53) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.10,450.78) --
+	(182.45,450.78);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.30,448.97) --
+	(181.30,452.47);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.30,446.75) {$L$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 75.59,473.72) --
+	( 83.28,473.72);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 79.71,473.22) --
+	( 79.71,474.21);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 79.71,469.68) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 59.20,438.88) --
+	( 81.03,438.88);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 72.23,436.62) --
+	( 72.23,440.96);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 72.23,434.84) {$l$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 65.98,467.10) --
+	( 88.76,467.10);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 79.67,465.29) --
+	( 79.67,468.80);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 79.67,464.20) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.77,479.42) --
+	(191.56,479.42);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.17,478.97) --
+	(191.17,479.86);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.17,476.51) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.58,471.62) --
+	(177.22,471.62);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.41,470.85) --
+	(176.41,472.37);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.41,468.40) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.37,474.53) --
+	(192.12,474.53);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.31,472.61) --
+	(190.31,476.32);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.31,470.49) {$L$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.74,479.56) --
+	(184.28,479.56);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.01,479.31) --
+	(184.01,479.81);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.01,475.53) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.76,458.11) --
+	(173.64,458.11);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.72,457.04) --
+	(172.72,459.15);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.72,454.08) {$l$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.43,473.51) --
+	(177.25,473.51);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.41,472.79) --
+	(175.41,474.21);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (175.41,470.60) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.32,481.54) --
+	(192.47,481.54);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.90,481.02) --
+	(191.90,482.04);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.90,478.63) {$\kappa$};
 \definecolor{drawColor}{RGB}{143,161,0}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (113.09,401.86) --
-	(120.91,401.86);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (117.28,397.21) --
-	(117.28,405.84);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (117.28,397.83) {$h$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (132.94,417.14) --
+	(141.47,417.14);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (137.53,411.64) --
+	(137.53,421.72);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (137.53,413.11) {$l$};
 \definecolor{drawColor}{RGB}{143,161,0}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (122.57,435.81) --
-	(128.58,435.81);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (125.74,433.40) --
-	(125.74,438.03);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (125.74,431.78) {$h$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (126.91,441.43) --
+	(131.70,441.43);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (129.41,439.79) --
+	(129.41,442.98);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (129.41,437.39) {$l$};
 \definecolor{drawColor}{RGB}{0,195,0}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 84.00,463.50) --
-	(111.71,463.50);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (101.21,460.57) --
-	(101.21,466.15);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (101.21,460.27) {$p$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.70,461.08) --
-	(189.43,461.08);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.99,460.33) --
-	(184.99,461.81);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.99,457.05) {$L$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (153.50,470.75) --
-	(155.46,470.75);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (154.50,470.01) --
-	(154.50,471.47);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (154.50,466.72) {$r$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 81.05,416.60) --
-	(101.36,416.60);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 93.05,412.44) --
-	( 93.05,420.21);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 93.05,412.57) {$h$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 84.24,446.61) --
-	(107.51,446.61);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 98.28,444.30) --
-	( 98.28,448.73);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 98.28,443.70) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.03,481.27) --
-	(193.70,481.27);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.40,480.85) --
-	(192.40,481.68);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.40,478.36) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 95.81,463.48) --
+	(102.57,463.48);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 99.40,461.30) --
+	( 99.40,465.50);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 99.40,460.25) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.01,461.16) --
+	(189.43,461.16);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.73,460.75) --
+	(188.73,461.56);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.73,457.13) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (154.80,470.95) --
+	(155.68,470.95);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (155.25,470.38) --
+	(155.25,471.51);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (155.25,466.92) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 95.11,422.68) --
+	(101.64,422.68);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 98.57,420.09) --
+	( 98.57,425.05);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 98.57,418.65) {$l$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 90.44,445.42) --
+	(100.91,445.42);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 96.18,442.80) --
+	( 96.18,447.81);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 96.18,442.52) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.24,481.50) --
+	(193.26,481.50);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.76,481.12) --
+	(192.76,481.86);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.76,478.59) {$\kappa$};
 \definecolor{drawColor}{RGB}{0,216,255}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.85,446.43) --
-	(156.02,446.43);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (154.48,444.35) --
-	(154.48,448.35);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (154.48,442.39) {$h$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.04,476.49) --
+	(188.01,476.49);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.56,475.16) --
+	(186.56,477.77);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (186.56,472.46) {$l$};
 \definecolor{drawColor}{RGB}{0,216,255}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (111.56,510.61) --
-	(122.39,510.61);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (117.50,506.59) --
-	(117.50,514.11);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (117.50,507.38) {$p$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.30,510.72) --
-	(200.72,510.72);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.54,507.87) --
-	(199.54,513.30);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.54,506.68) {$L$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (122.36,483.27) --
-	(131.86,483.27);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (127.52,480.40) --
-	(127.52,485.87);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (127.52,479.24) {$h$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (119.73,487.76) --
-	(132.30,487.76);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (126.73,484.08) --
-	(126.73,491.00);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (126.73,484.85) {$\sigma$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.03,529.08) --
-	(198.96,529.08);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (197.53,525.48) --
-	(197.53,532.27);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.53,526.18) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (111.56,467.23) --
+	(122.39,467.23);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (117.50,465.85) --
+	(117.50,468.55);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (117.50,464.01) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.30,464.98) --
+	(200.72,464.98);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.54,463.73) --
+	(199.54,466.18);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.54,460.95) {$L$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.07,472.08) --
+	(172.82,472.08);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.96,471.77) --
+	(171.96,472.39);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.96,468.05) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (112.36,426.58) --
+	(123.13,426.58);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (118.27,423.54) --
+	(118.27,429.32);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (118.27,422.55) {$l$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (119.73,444.15) --
+	(132.30,444.15);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (126.73,442.54) --
+	(126.73,445.67);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (126.73,441.24) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.03,485.16) --
+	(198.96,485.16);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (197.53,484.79) --
+	(197.53,485.52);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.53,482.25) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (154.10,452.74) --
+	(157.70,452.74);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (155.96,450.99) --
+	(155.96,454.38);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (155.96,449.51) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.27,455.09) --
+	(177.39,455.09);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.41,448.17) --
+	(175.41,460.61);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (175.41,451.05) {$L$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.99,464.34) --
+	(179.62,464.34);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.31,463.86) --
+	(179.31,464.81);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.31,460.30) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.17,441.30) --
+	(155.91,441.30);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (154.10,439.87) --
+	(154.10,442.66);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (154.10,437.27) {$l$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (158.54,452.87) --
+	(163.08,452.87);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (160.90,451.50) --
+	(160.90,454.19);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (160.90,449.97) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.54,482.14) --
+	(193.90,482.14);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.23,481.65) --
+	(193.23,482.62);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.23,479.23) {$\kappa$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.07,449.34) --
+	(176.00,449.34);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.58,446.82) --
+	(174.58,451.65);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.58,446.11) {$p$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (153.89,443.85) --
+	(158.71,443.85);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (156.40,441.95) --
+	(156.40,445.64);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (156.40,439.82) {$L$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.59,468.32) --
+	(181.10,468.32);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.84,468.11) --
+	(180.84,468.53);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.84,464.29) {$r$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.09,461.78) --
+	(175.96,461.78);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.56,461.02) --
+	(174.56,462.52);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.56,457.75) {$l$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (163.80,452.09) --
+	(166.75,452.09);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (165.32,449.26) --
+	(165.32,454.65);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (165.32,449.18) {$\sigma$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.48,484.04) --
+	(195.97,484.04);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.23,483.19) --
+	(195.23,484.87);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.23,481.14) {$\kappa$};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,548.96) {\bfseries adapt (\textit{quant}) vs. adapt (\textit{cat})};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,301.03) {ESS/$10^6$ states [adapt (\textit{cat})]};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (307.01,433.62) {ESS/$10^6$ states [adapt (\textit{quant})]};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,548.96) {\bfseries adapt(\textit{quant}) vs. adapt(\textit{cat})};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,301.03) {ESS/$10^6$ states [adapt(\textit{cat})]};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (307.01,433.62) {ESS/$10^6$ states [adapt(\textit{quant})]};
 \end{scope}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (354.65,438.13) --
-	(383.52,438.13);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (372.72,433.43) --
-	(372.72,442.14);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (372.72,434.90) {$p$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (465.51,456.44) --
-	(470.69,456.44);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (468.22,453.88) --
-	(468.22,458.79);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.22,452.41) {$L$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (364.20,475.42) --
-	(376.65,475.42);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (371.12,474.25) --
-	(371.12,476.55);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (371.12,471.39) {$r$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (361.99,428.85) --
-	(397.42,428.85);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (385.07,416.26) --
-	(385.07,437.45);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (385.07,424.82) {$h$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (322.81,453.94) --
-	(360.54,453.94);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (347.71,449.40) --
-	(347.71,457.84);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (347.71,451.04) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (479.18,480.12) --
-	(480.62,480.12);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (479.91,479.30) --
-	(479.91,480.91);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (479.91,477.22) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (351.19,435.89) --
+	(374.14,435.89);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (365.00,433.60) --
+	(365.00,438.01);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (365.00,432.67) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (469.18,452.57) --
+	(471.53,452.57);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (470.38,448.91) --
+	(470.38,455.81);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (470.38,448.54) {$L$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (364.67,473.43) --
+	(372.36,473.43);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (368.79,472.65) --
+	(368.79,474.19);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (368.79,469.40) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (348.28,434.69) --
+	(370.11,434.69);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (361.31,432.46) --
+	(361.31,436.75);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (361.31,430.66) {$l$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (355.06,451.88) --
+	(377.84,451.88);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (368.75,448.72) --
+	(368.75,454.72);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (368.75,448.98) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (479.85,479.96) --
+	(480.64,479.96);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.25,479.17) --
+	(480.25,480.73);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (480.25,477.06) {$\kappa$};
 \definecolor{drawColor}{RGB}{253,104,0}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (452.86,455.62) --
-	(456.39,455.62);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (454.68,454.14) --
-	(454.68,457.03);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (454.68,451.59) {$h$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (460.84,462.46) --
+	(462.72,462.46);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (461.80,461.30) --
+	(461.80,463.57);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (461.80,458.43) {$l$};
 \definecolor{drawColor}{RGB}{253,104,0}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (402.17,409.36) --
-	(409.99,409.36);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (406.36,407.67) --
-	(406.36,410.96);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (406.36,405.33) {$h$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (422.02,421.79) --
+	(430.55,421.79);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (426.61,419.43) --
+	(426.61,423.96);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (426.61,417.76) {$l$};
 \definecolor{drawColor}{RGB}{143,161,0}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (418.83,448.30) --
-	(424.42,448.30);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (421.77,445.38) --
-	(421.77,450.94);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (421.77,445.07) {$p$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.06,483.20) --
-	(483.53,483.20);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (482.32,482.06) --
-	(482.32,484.31);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (482.32,479.17) {$L$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (471.88,483.39) --
-	(473.05,483.39);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (472.47,482.50) --
-	(472.47,484.26);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (472.47,479.36) {$r$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (411.65,447.57) --
-	(417.66,447.57);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (414.82,444.38) --
-	(414.82,450.43);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (414.82,443.54) {$h$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (423.08,456.30) --
-	(430.96,456.30);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (427.30,453.54) --
-	(427.30,458.81);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (427.30,453.40) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.64,485.06) --
-	(484.69,485.06);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (484.17,483.93) --
-	(484.17,486.13);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (484.17,482.15) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (373.08,414.28) --
-	(400.79,414.28);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (390.29,410.38) --
-	(390.29,417.69);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (390.29,411.05) {$p$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (468.78,464.34) --
-	(478.51,464.34);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (474.07,461.59) --
-	(474.07,466.85);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.07,460.31) {$L$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (442.58,472.21) --
-	(444.54,472.21);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (443.58,471.57) --
-	(443.58,472.84);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (443.58,468.18) {$r$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (370.13,418.44) --
-	(390.44,418.44);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (382.13,413.15) --
-	(382.13,422.88);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (382.13,414.41) {$h$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (373.32,431.44) --
-	(396.59,431.44);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (387.36,417.90) --
-	(387.36,440.46);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (387.36,428.53) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.11,479.21) --
-	(482.78,479.21);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.48,478.51) --
-	(481.48,479.89);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (481.48,476.30) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (418.83,448.69) --
+	(424.42,448.69);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (421.77,446.00) --
+	(421.77,451.13);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (421.77,445.46) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.06,483.39) --
+	(483.53,483.39);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (482.32,482.30) --
+	(482.32,484.44);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (482.32,479.36) {$L$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (471.88,483.68) --
+	(473.05,483.68);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (472.47,482.69) --
+	(472.47,484.64);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (472.47,479.65) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (415.99,446.99) --
+	(420.78,446.99);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (418.49,444.38) --
+	(418.49,449.37);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (418.49,442.96) {$l$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (423.08,456.86) --
+	(430.96,456.86);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (427.30,454.18) --
+	(427.30,459.31);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (427.30,453.96) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.64,485.34) --
+	(484.69,485.34);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (484.17,484.19) --
+	(484.17,486.45);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (484.17,482.44) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (384.89,415.59) --
+	(391.65,415.59);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (388.48,412.36) --
+	(388.48,418.49);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (388.48,412.37) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (477.09,465.76) --
+	(478.51,465.76);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (477.81,463.80) --
+	(477.81,467.60);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (477.81,461.73) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (443.88,472.94) --
+	(444.76,472.94);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (444.33,472.44) --
+	(444.33,473.42);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (444.33,468.90) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (384.19,415.20) --
+	(390.72,415.20);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (387.65,411.87) --
+	(387.65,418.17);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (387.65,411.17) {$l$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (379.52,435.27) --
+	(389.99,435.27);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (385.26,431.31) --
+	(385.26,438.72);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (385.26,432.36) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.32,481.15) --
+	(482.34,481.15);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.84,480.69) --
+	(481.84,481.60);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (481.84,478.25) {$\kappa$};
 \definecolor{drawColor}{RGB}{0,216,255}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (441.93,444.49) --
-	(445.10,444.49);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (443.56,442.00) --
-	(443.56,446.77);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (443.56,440.45) {$h$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (474.12,476.37) --
+	(477.09,476.37);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (475.64,475.07) --
+	(475.64,477.61);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (475.64,472.34) {$l$};
 \definecolor{drawColor}{RGB}{0,216,255}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (411.44,443.20) --
-	(420.94,443.20);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (416.60,439.70) --
-	(416.60,446.30);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (416.60,439.17) {$h$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (401.44,428.89) --
+	(412.21,428.89);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (407.35,425.48) --
+	(407.35,431.93);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (407.35,424.86) {$l$};
 \definecolor{drawColor}{RGB}{151,0,255}
@@
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (486.61,483.77) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (443.18,449.25) --
+	(446.78,449.25);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (445.04,446.87) --
+	(445.04,451.45);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (445.04,446.02) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (462.35,463.59) --
+	(466.47,463.59);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (464.49,462.04) --
+	(464.49,465.06);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (464.49,459.56) {$L$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (468.07,469.62) --
+	(468.70,469.62);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (468.39,469.33) --
+	(468.39,469.91);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.39,465.59) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (441.25,447.90) --
+	(444.99,447.90);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (443.18,445.62) --
+	(443.18,450.01);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (443.18,443.87) {$l$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (447.62,457.57) --
+	(452.16,457.57);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (449.98,455.71) --
+	(449.98,459.32);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (449.98,454.67) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.62,482.08) --
+	(482.98,482.08);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (482.31,481.63) --
+	(482.31,482.53);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (482.31,479.18) {$\kappa$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (462.15,464.79) --
+	(465.08,464.79);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (463.66,463.96) --
+	(463.66,465.60);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (463.66,461.57) {$p$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (442.97,443.46) --
+	(447.79,443.46);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (445.48,438.02) --
+	(445.48,448.00);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (445.48,439.43) {$L$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (469.67,468.50) --
+	(470.18,468.50);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (469.92,461.81) --
+	(469.92,473.87);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (469.92,464.47) {$r$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (462.17,462.06) --
+	(465.04,462.06);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (463.64,456.71) --
+	(463.64,466.54);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (463.64,458.03) {$l$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (452.88,455.57) --
+	(455.83,455.57);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (454.40,448.94) --
+	(454.40,460.90);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (454.40,452.67) {$\sigma$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.56,481.47) --
+	(485.05,481.47);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (484.31,475.14) --
+	(484.31,486.61);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (484.31,478.57) {$\kappa$};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,259.88) {\bfseries adapt (\textit{quant}) vs. adapt (\textit{real})};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54, 11.95) {ESS/$10^6$ states [adapt (\textit{real})]};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,144.54) {ESS/$10^6$ states [adapt (\textit{quant})]};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,259.88) {\bfseries adapt(\textit{quant}) vs. adapt(\textit{real})};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54, 11.95) {ESS/$10^6$ states [adapt(\textit{real})]};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,144.54) {ESS/$10^6$ states [adapt(\textit{quant})]};
 \end{scope}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.97,149.05) --
-	(180.66,149.05);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (177.96,144.35) --
-	(177.96,153.06);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.96,145.82) {$p$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (155.79,167.36) --
-	(161.78,167.36);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (158.95,164.80) --
-	(158.95,169.71);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.95,163.33) {$L$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.38,186.34) --
-	(184.91,186.34);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.16,185.17) --
-	(184.16,187.47);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.16,182.31) {$r$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (142.40,139.77) --
-	(149.08,139.77);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (145.94,127.18) --
-	(145.94,148.37);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (145.94,135.74) {$h$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.78,164.86) --
-	(181.16,164.86);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.05,160.32) --
-	(179.05,168.76);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.05,161.96) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.78,191.04) --
-	(188.89,191.04);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.34,190.22) --
-	(188.34,191.83);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.34,188.14) {$\kappa$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.61,176.50) --
-	(183.28,176.50);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.46,174.89) --
-	(182.46,178.01);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.46,173.27) {$p$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.69,191.23) --
-	(187.62,191.23);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.72,190.47) --
-	(185.72,191.97);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.72,187.20) {$L$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.21,193.23) --
-	(190.77,193.23);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.49,193.00) --
-	(190.49,193.46);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.49,189.20) {$r$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.08,166.54) --
-	(167.07,166.54);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (165.62,165.06) --
-	(165.62,167.95);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (165.62,162.51) {$h$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.55,189.22) --
-	(184.96,189.22);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.26,187.99) --
-	(184.26,190.39);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.26,186.31) {$\sigma$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.83,191.54) --
-	(192.90,191.54);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.37,191.10) --
-	(192.37,191.98);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.37,188.64) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.27,146.81) --
+	(182.90,146.81);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.68,144.52) --
+	(180.68,148.93);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.68,143.59) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (159.89,163.49) --
+	(163.39,163.49);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.70,159.83) --
+	(161.70,166.73);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (161.70,159.46) {$L$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.14,184.35) --
+	(185.13,184.35);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.64,183.57) --
+	(184.64,185.11);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.64,180.32) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (147.54,145.61) --
+	(151.88,145.61);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.80,143.38) --
+	(149.80,147.67);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (149.80,141.58) {$l$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.21,162.80) --
+	(179.72,162.80);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.02,159.64) --
+	(178.02,165.64);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (178.02,159.90) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.89,190.88) --
+	(190.78,190.88);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.34,190.09) --
+	(190.34,191.65);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.34,187.98) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.77,176.50) --
+	(183.29,176.50);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.54,174.89) --
+	(182.54,178.01);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.54,173.27) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.53,191.23) --
+	(187.24,191.23);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.45,190.47) --
+	(185.45,191.97);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.45,187.20) {$L$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.23,193.23) --
+	(190.73,193.23);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.48,193.00) --
+	(190.48,193.46);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.48,189.20) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (167.96,173.38) --
+	(170.07,173.38);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.03,172.22) --
+	(169.03,174.49);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.03,169.35) {$l$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.71,189.22) --
+	(185.13,189.22);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.43,187.99) --
+	(184.43,190.39);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.43,186.31) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.94,191.54) --
+	(192.96,191.54);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.46,191.10) --
+	(192.46,191.98);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.46,188.64) {$\kappa$};
 \definecolor{drawColor}{RGB}{143,161,0}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (108.13,120.28) --
-	(116.76,120.28);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (112.78,118.59) --
-	(112.78,121.88);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (112.78,116.25) {$h$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (122.56,132.71) --
+	(132.64,132.71);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (128.06,130.35) --
+	(128.06,134.88);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (128.06,128.68) {$l$};
 \definecolor{drawColor}{RGB}{143,161,0}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (159.36,159.22) --
-	(162.98,159.22);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.23,156.30) --
-	(161.23,161.86);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (161.23,155.99) {$p$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.76,194.12) --
-	(185.80,194.12);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.80,192.98) --
-	(184.80,195.23);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.80,190.09) {$L$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.62,194.31) --
-	(187.19,194.31);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.91,193.42) --
-	(186.91,195.18);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (186.91,190.28) {$r$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (144.32,158.49) --
-	(148.95,158.49);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (146.73,155.30) --
-	(146.73,161.35);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (146.73,154.46) {$h$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (154.18,167.22) --
-	(158.80,167.22);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (156.59,164.46) --
-	(156.59,169.73);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (156.59,164.32) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.00,195.98) --
-	(195.90,195.98);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.45,194.85) --
-	(195.45,197.05);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.45,193.07) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.49,125.20) --
-	(177.07,125.20);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.42,121.30) --
-	(174.42,128.61);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.42,121.97) {$p$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.25,175.26) --
-	(172.73,175.26);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.00,172.51) --
-	(172.00,177.77);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.00,171.23) {$L$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.93,183.13) --
-	(182.39,183.13);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.67,182.49) --
-	(181.67,183.76);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.67,179.10) {$r$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (123.36,129.36) --
-	(131.13,129.36);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (127.52,124.07) --
-	(127.52,133.80);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (127.52,125.33) {$h$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (155.22,142.36) --
-	(159.65,142.36);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (157.53,128.82) --
-	(157.53,151.38);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (157.53,139.45) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.77,190.13) --
-	(192.60,190.13);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.19,189.43) --
-	(192.19,190.81);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.19,187.22) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (159.36,159.61) --
+	(162.98,159.61);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.23,156.92) --
+	(161.23,162.05);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (161.23,156.38) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.76,194.31) --
+	(185.80,194.31);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.80,193.22) --
+	(184.80,195.36);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.80,190.28) {$L$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.62,194.60) --
+	(187.19,194.60);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.91,193.61) --
+	(186.91,195.56);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (186.91,190.57) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.71,157.91) --
+	(153.90,157.91);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.35,155.30) --
+	(152.35,160.29);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (152.35,153.88) {$l$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (154.18,167.78) --
+	(158.80,167.78);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (156.59,165.10) --
+	(156.59,170.23);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (156.59,164.88) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.00,196.26) --
+	(195.90,196.26);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.45,195.11) --
+	(195.45,197.37);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.45,193.36) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.22,126.51) --
+	(176.42,126.51);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.40,123.28) --
+	(174.40,129.41);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.40,123.29) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.67,176.68) --
+	(172.48,176.68);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.08,174.72) --
+	(172.08,178.52);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.08,172.65) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.30,183.86) --
+	(182.43,183.86);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.87,183.36) --
+	(181.87,184.34);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.87,179.82) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (131.01,126.12) --
+	(135.97,126.12);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (133.60,122.79) --
+	(133.60,129.09);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (133.60,122.09) {$l$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (153.72,146.19) --
+	(158.73,146.19);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (156.34,142.23) --
+	(156.34,149.64);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (156.34,143.28) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.04,192.07) --
+	(192.78,192.07);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.42,191.61) --
+	(192.42,192.52);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.42,189.17) {$\kappa$};
 \definecolor{drawColor}{RGB}{0,216,255}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (155.27,155.41) --
-	(159.27,155.41);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (157.35,152.92) --
-	(157.35,157.69);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (157.35,151.37) {$h$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.08,187.29) --
+	(188.69,187.29);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.41,185.99) --
+	(187.41,188.53);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.41,183.26) {$l$};
 \definecolor{drawColor}{RGB}{0,216,255}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (217.51,138.96) --
-	(225.03,138.96);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (221.53,135.55) --
-	(221.53,142.00);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (221.53,135.74) {$p$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (218.79,193.13) --
-	(224.22,193.13);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (221.64,191.98) --
-	(221.64,194.23);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (221.64,189.10) {$L$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.32,154.12) --
-	(196.79,154.12);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.19,150.62) --
-	(194.19,157.22);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.19,150.09) {$h$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.00,161.49) --
-	(201.92,161.49);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.68,159.20) --
-	(198.68,163.60);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.68,158.59) {$\sigma$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (236.40,197.59) --
-	(243.19,197.59);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (240.00,196.60) --
-	(240.00,198.55);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (240.00,194.69) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.77,138.96) --
+	(179.47,138.96);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.15,135.55) --
+	(178.15,142.00);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (178.15,135.74) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.65,193.13) --
+	(177.10,193.13);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.90,191.98) --
+	(175.90,194.23);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (175.90,189.10) {$L$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.69,194.14) --
+	(183.31,194.14);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.00,193.63) --
+	(183.00,194.65);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.00,190.11) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (134.46,139.81) --
+	(140.24,139.81);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (137.50,136.40) --
+	(137.50,142.85);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (137.50,135.78) {$l$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (153.46,161.49) --
+	(156.59,161.49);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (155.07,159.20) --
+	(155.07,163.60);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (155.07,158.59) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.71,197.59) --
+	(196.44,197.59);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.08,196.60) --
+	(196.08,198.55);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.08,194.69) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.91,160.17) --
+	(165.30,160.17);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (163.66,157.79) --
+	(163.66,162.37);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (163.66,156.94) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (159.09,174.51) --
+	(171.53,174.51);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (166.01,172.96) --
+	(166.01,175.98);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (166.01,170.48) {$L$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.78,180.54) --
+	(175.73,180.54);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.26,180.25) --
+	(175.26,180.83);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (175.26,176.51) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.79,158.82) --
+	(153.58,158.82);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.22,156.54) --
+	(152.22,160.93);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (152.22,154.79) {$l$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (162.42,168.49) --
+	(165.11,168.49);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (163.79,166.63) --
+	(163.79,170.24);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (163.79,165.59) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.57,193.00) --
+	(193.54,193.00);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.06,192.55) --
+	(193.06,193.45);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.06,190.10) {$\kappa$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (157.74,175.71) --
+	(162.57,175.71);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (160.26,174.88) --
+	(160.26,176.52);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (160.26,172.49) {$p$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.87,154.38) --
+	(156.56,154.38);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (154.77,148.94) --
+	(154.77,158.92);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (154.77,150.35) {$L$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.03,179.42) --
+	(179.45,179.42);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.24,172.73) --
+	(179.24,184.79);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.24,175.39) {$r$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.94,172.98) --
+	(173.44,172.98);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.70,167.63) --
+	(172.70,177.46);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.70,168.95) {$l$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (160.18,166.49) --
+	(165.57,166.49);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (163.01,159.86) --
+	(163.01,171.82);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (163.01,163.59) {$\sigma$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.11,192.39) --
+	(195.79,192.39);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.96,186.06) --
+	(194.96,197.53);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.96,189.49) {$\kappa$};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,259.88) {\bfseries Disparity as a function of sequence length};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,259.88) {\bfseries Leaf rate mixing vs sequence length};
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (485.73,100.19) --
-	(485.73, 51.03);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (485.73, 73.54) {$41\times $};
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (485.73,101.01) --
+	(485.73, 50.89);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (487.62, 73.88) {$47\times $};
 \definecolor{fillColor}{RGB}{255,0,109}
 
-\path[fill=fillColor] (485.73,100.19) circle (  1.87);
-
-\path[fill=fillColor] (485.73, 53.94) --
-	(488.24, 49.58) --
-	(483.21, 49.58) --
+\path[fill=fillColor] (485.73,101.01) circle (  1.87);
+
+\path[fill=fillColor] (485.73, 53.79) --
+	(488.24, 49.44) --
+	(483.21, 49.44) --
 	cycle;
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (356.88,105.24) {$1.3\times $};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (358.78,105.24) {$1.3\times $};
 \definecolor{fillColor}{RGB}{253,104,0}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (394.78,117.08) {$1.1\times $};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (396.67,117.08) {$1.1\times $};
 \definecolor{fillColor}{RGB}{143,161,0}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (390.04,100.30) {$1.1\times $};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (391.93,100.30) {$1.1\times $};
 \definecolor{fillColor}{RGB}{0,195,0}
@@
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (404.25, 96.11) --
-	(404.25, 66.68);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (404.25, 79.32) {$2.7\times $};
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (404.25, 96.46) --
+	(404.25, 67.23);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (406.15, 79.77) {$2.7\times $};
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[fill=fillColor] (404.25, 96.11) circle (  1.87);
-
-\path[fill=fillColor] (404.25, 69.58) --
-	(406.77, 65.23) --
-	(401.74, 65.23) --
+\path[fill=fillColor] (404.25, 96.46) circle (  1.87);
+
+\path[fill=fillColor] (404.25, 70.13) --
+	(406.77, 65.78) --
+	(401.74, 65.78) --
 	cycle;
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (359.72,165.94) {$0.96\times $};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (361.62,165.94) {$0.96\times $};
 \definecolor{fillColor}{RGB}{0,216,255}
@@
 	(357.21,168.86) --
+	cycle;
+
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (433.62, 98.44) --
+	(433.62, 82.47);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (435.51, 88.38) {$1.5\times $};
+\definecolor{fillColor}{RGB}{151,0,255}
+
+\path[fill=fillColor] (433.62, 98.44) circle (  1.87);
+
+\path[fill=fillColor] (433.62, 85.38) --
+	(436.14, 81.02) --
+	(431.10, 81.02) --
+	cycle;
+
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (359.72, 86.63) --
+	(359.72, 92.30);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (361.62, 87.39) {$0.87\times $};
+\definecolor{fillColor}{RGB}{255,0,255}
+
+\path[fill=fillColor] (359.72, 86.63) circle (  1.87);
+
+\path[fill=fillColor] (359.72, 95.21) --
+	(362.24, 90.85) --
+	(357.21, 90.85) --
+	cycle;
+
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (346.46, 92.26) --
+	(346.46, 94.63);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (348.35, 91.38) {$0.95\times $};
+\definecolor{fillColor}{RGB}{68,68,68}
+
+\path[fill=fillColor] (346.46, 92.26) circle (  1.87);
+
+\path[fill=fillColor] (346.46, 97.54) --
+	(348.97, 93.18) --
+	(343.94, 93.18) --
 	cycle;

### 2020-08-29 benchmarking/benchmarkingVM/ESS_round3.tex
results update

--- 2020-08-26 benchmarking/benchmarkingVM/ESS_round3.tex
@@
-% Created by tikzDevice version 0.12.3.1 on 2020-08-25 15:33:46
+% Created by tikzDevice version 0.12.3.1 on 2020-08-29 17:55:47
 % !TEX encoding = UTF-8 Unicode
@@
 \definecolor{fillColor}{RGB}{255,255,255}
-\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (289.08,289.08);
+\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (578.16,357.33);
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
+\path[clip] (  0.00,  0.00) rectangle (578.16,357.33);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at (144.54,253.90) {\bfseries Bactrian (\textit{real}) vs. adapt (\textit{real})};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at (289.08,323.19) {\bfseries Comparison of Bactrian+adapt(\textit{real}) and adapt(\textit{real})};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at (144.54, 14.40) {ESS/hr [adapt (\textit{real})]};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at ( 21.60,144.54) {ESS/hr [Bactrian (\textit{real})]};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 21.60,178.67) {Relative ESS/hr};
 \end{scope}
 \begin{scope}
-\path[clip] ( 60.00, 60.00) rectangle (229.08,229.08);
+\path[clip] ( 60.00, 60.00) rectangle (518.16,297.33);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (  0.00, 71.00) --
-	(218.08,289.08);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] ( 60.00,178.67) -- (518.16,178.67);
+\definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (268.39,289.08) --
-	(268.39,197.39) --
-	( 71.00,  0.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 65.87,202.09) --
+	( 65.87,159.61);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00, 47.34) --
-	(241.74,289.08);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 65.87,176.96) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (268.39,289.08) --
-	(268.39,221.06) --
-	( 47.34,  0.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 71.75,231.12) --
+	( 71.75,209.11);
 
-\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round] (  0.00, 23.67) --
-	(265.41,289.08);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 71.75,216.23) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round] (268.39,289.08) --
-	(268.39,244.72) --
-	( 23.67,  0.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 77.62,249.80) --
+	( 77.62,200.82);
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (140.08, 64.13) {$\frac{1}{64} \times$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 77.62,221.42) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,144.78) {$64\times$};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.50,224.99) --
+	( 83.50,200.16);
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (116.41, 64.13) {$\frac{1}{16} \times$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 83.50,208.69) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,121.11) {$16\times$};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.37,224.48) --
+	( 89.37,192.74);
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 90.75, 64.13) {$\frac{1}{4} \times$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 89.37,204.72) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 62.56, 97.44) {$4\times$};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.24,207.01) --
+	( 95.24,123.55);
 
-\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 60.00, 60.00) -- (229.08,229.08);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 95.24,161.39) {$p$};
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (200.17,196.99) --
-	(201.72,196.99);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (101.12,236.74) --
+	(101.12,217.60);
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (200.96,196.43) --
-	(200.96,197.53);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (101.12,223.28) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (106.99,229.52) --
+	(106.99,197.09);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (106.99,209.42) {$p$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.86,233.06) --
+	(112.86,194.42);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (112.86,209.85) {$p$};
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] ( 65.87,207.44) --
+	(118.74,207.44);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 92.31,275.05) {15\% faster};
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (124.61,  0.00) --
+	(124.61,357.33);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (130.49,217.05) --
+	(130.49,177.97);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (130.49,192.65) {$L$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (136.36,220.22) --
+	(136.36,200.25);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (136.36,205.38) {$L$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (142.23,210.52) --
+	(142.23,187.84);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (142.23,194.32) {$L$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.11,222.54) --
+	(148.11,210.07);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (148.11,211.44) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.98,220.42) --
+	(153.98,189.38);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (153.98,200.04) {$L$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.86,198.32) --
+	(159.86,154.77);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (159.86,171.69) {$L$};
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (200.96,193.10) {$p$};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (165.73,269.42) --
+	(165.73,249.68);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (165.73,254.69) {$L$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.60,275.92) --
+	(171.60,205.26);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (171.60,235.73) {$L$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.48,226.24) --
+	(177.48,191.14);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (177.48,203.83) {$L$};
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (130.49,212.61) --
+	(183.35,212.61);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (156.92,275.05) {17\% faster};
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (189.22,  0.00) --
+	(189.22,357.33);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.10,178.30) --
+	(195.10,162.97);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (195.10,165.78) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.97,225.97) --
+	(200.97,222.91);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (200.97,219.58) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.85,209.90) --
+	(206.85,206.82);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (206.85,203.50) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.72,212.52) --
+	(212.72,207.42);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (212.72,205.11) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.59,201.48) --
+	(218.59,190.01);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (218.59,190.88) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (224.47,183.69) --
+	(224.47,181.07);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (224.47,177.52) {$r$};
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (205.11,198.75) --
-	(207.67,198.75);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.34,232.00) --
+	(230.34,228.44);
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (206.44,197.10) --
-	(206.44,200.25);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (230.34,225.36) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (236.22,216.70) --
+	(236.22,209.13);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (236.22,208.06) {$r$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (242.09,207.92) --
+	(242.09,204.10);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (242.09,201.15) {$r$};
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (195.10,204.52) --
+	(247.96,204.52);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (221.53,275.05) {13\% faster};
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (253.84,  0.00) --
+	(253.84,357.33);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (259.71,186.76) --
+	(259.71,147.52);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (259.71,162.28) {$l$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (265.58,236.27) --
+	(265.58,214.49);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (265.58,220.52) {$l$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.46,228.65) --
+	(271.46,191.80);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (271.46,205.37) {$l$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (277.33,209.40) --
+	(277.33,184.40);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (277.33,192.04) {$l$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (283.21,235.74) --
+	(283.21,179.82);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (283.21,202.92) {$l$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (289.08,186.44) --
+	(289.08,176.00);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (289.08,176.36) {$l$};
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (206.44,193.89) {$L$};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (294.95,233.35) --
+	(294.95,192.74);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (294.95,208.18) {$l$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (300.83,240.79) --
+	(300.83,197.15);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (300.83,214.11) {$l$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (306.70,218.21) --
+	(306.70,200.68);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (306.70,204.59) {$l$};
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (259.71,203.35) --
+	(312.58,203.35);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (286.14,275.05) {12\% faster};
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (318.45,  0.00) --
+	(318.45,357.33);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (324.32,210.47) --
+	(324.32,163.89);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (324.32,183.68) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (330.20,227.66) --
+	(330.20,207.12);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (330.20,213.90) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (336.07,242.97) --
+	(336.07,185.19);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (336.07,210.58) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (341.94,212.68) --
+	(341.94,193.89);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (341.94,199.78) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (347.82,240.03) --
+	(347.82,183.17);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (347.82,208.10) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (353.69,199.69) --
+	(353.69,152.13);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (353.69,172.41) {$\sigma$};
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (205.83,203.06) --
-	(206.19,203.06);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (359.57,228.13) --
+	(359.57,189.17);
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (206.01,202.94) --
-	(206.01,203.18);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (359.57,205.15) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (365.44,207.98) --
+	(365.44,189.19);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (365.44,195.09) {$\sigma$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (371.31,231.52) --
+	(371.31,197.67);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (371.31,211.09) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (324.32,203.48) --
+	(377.19,203.48);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (350.76,275.05) {13\% faster};
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (383.06,  0.00) --
+	(383.06,357.33);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (388.94,152.83) --
+	(388.94,146.45);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (388.94,146.14) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (394.81,184.19) --
+	(394.81,175.55);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (394.81,176.37) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (400.68,183.42) --
+	(400.68,178.65);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (400.68,177.54) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (406.56,180.51) --
+	(406.56,174.75);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (406.56,174.13) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.43,183.54) --
+	(412.43,178.58);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (412.43,177.56) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.30,182.54) --
+	(418.30,177.64);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (418.30,176.59) {$\kappa$};
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (206.01,198.20) {$r$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (424.18,175.13) --
+	(424.18,167.83);
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.99,182.32) --
-	(180.78,182.32);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (424.18,167.98) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.91,181.55) --
-	(179.91,183.06);
-\definecolor{drawColor}{RGB}{151,0,255}
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (430.05,180.45) --
+	(430.05,170.64);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (179.91,177.46) {$h$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (430.05,172.05) {$\kappa$};
+\definecolor{drawColor}{RGB}{68,68,68}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.73,181.94) --
-	(183.35,181.94);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (435.93,190.03) --
+	(435.93,177.11);
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.20,181.15) --
-	(181.20,182.69);
-\definecolor{drawColor}{RGB}{151,0,255}
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (435.93,180.07) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (181.20,178.44) {$\sigma$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (388.94,175.55) --
+	(441.80,175.55);
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (212.29,207.61) --
-	(213.84,207.61);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (415.37,275.05) {-1.6\% faster};
+\definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (213.08,206.84) --
-	(213.08,208.35);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (213.08,204.11) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (447.67,  0.00) --
+	(447.67,357.33);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
+\path[clip] (  0.00,  0.00) rectangle (578.16,357.33);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- (217.25, 60.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- (518.16, 60.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- ( 60.00, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.31, 60.00) -- ( 92.31, 54.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.31, 60.00) -- ( 99.31, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (156.92, 60.00) -- (156.92, 54.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.62, 60.00) -- (138.62, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.53, 60.00) -- (221.53, 54.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.93, 60.00) -- (177.93, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (286.14, 60.00) -- (286.14, 54.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.25, 60.00) -- (217.25, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.76, 60.00) -- (350.76, 54.00);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 60.00, 38.40) {1};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (415.37, 60.00) -- (415.37, 54.00);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 99.31, 38.40) {10};
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.70] at ( 94.72, 48.00) {Prior};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (138.62, 38.40) {100};
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.70] at (159.33, 48.00) {Likelihood};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (177.93, 38.40) {1000};
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.70] at (223.94, 48.00) {Mean leaf rate};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (217.25, 38.40) {10000};
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.70] at (288.55, 48.00) {Tree length};
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- ( 60.00,217.25);
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.70] at (353.17, 48.00) {Clock SD $\sigma$};
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- ( 54.00, 60.00);
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.70] at (417.78, 48.00) {HKY model $\kappa$};
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 99.31) -- ( 54.00, 99.31);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 79.78) -- ( 60.00,277.55);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,138.62) -- ( 54.00,138.62);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 79.78) -- ( 54.00, 79.78);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,177.93) -- ( 54.00,177.93);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,129.22) -- ( 54.00,129.22);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,217.25) -- ( 54.00,217.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,178.67) -- ( 54.00,178.67);
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00, 56.56) {1};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,228.11) -- ( 54.00,228.11);
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00, 95.87) {10};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,277.55) -- ( 54.00,277.55);
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,135.18) {100};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00, 76.33) {0.50};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,174.49) {1000};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,125.78) {0.75};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,213.80) {10000};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,175.22) {1.00};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,224.67) {1.25};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,274.11) {1.50};
 \end{scope}
 \begin{scope}
-\path[clip] ( 60.00, 60.00) rectangle (229.08,229.08);
+\path[clip] ( 60.00, 60.00) rectangle (518.16,297.33);
 \definecolor{drawColor}{RGB}{0,0,0}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,171.00) rectangle (169.31,165.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (451.19,171.00) rectangle (458.39,165.00);
 \definecolor{fillColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,159.00) rectangle (169.31,153.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (451.19,159.00) rectangle (458.39,153.00);
 \definecolor{fillColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,147.00) rectangle (169.31,141.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (451.19,147.00) rectangle (458.39,141.00);
 \definecolor{fillColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,135.00) rectangle (169.31,129.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (451.19,135.00) rectangle (458.39,129.00);
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,123.00) rectangle (169.31,117.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (451.19,123.00) rectangle (458.39,117.00);
 \definecolor{fillColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,111.00) rectangle (169.31,105.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (451.19,111.00) rectangle (458.39,105.00);
 \definecolor{fillColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11, 99.00) rectangle (169.31, 93.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (451.19, 99.00) rectangle (458.39, 93.00);
 \definecolor{fillColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11, 87.00) rectangle (169.31, 81.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (451.19, 87.00) rectangle (458.39, 81.00);
 \definecolor{fillColor}{RGB}{68,68,68}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11, 75.00) rectangle (169.31, 69.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (451.19, 75.00) rectangle (458.39, 69.00);
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,164.56) {Ran};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (467.39,164.56) {Ran};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,152.56) {Cognato};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (467.39,152.56) {Cognato};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,140.56) {Dornburg};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (467.39,140.56) {Dornburg};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,128.56) {Sauquet};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (467.39,128.56) {Sauquet};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,116.56) {Broughton};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (467.39,116.56) {Broughton};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,104.56) {Kawahara};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (467.39,104.56) {Kawahara};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31, 92.56) {simulated};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (467.39, 92.56) {simulated};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31, 80.56) {Rightmyer};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (467.39, 80.56) {Rightmyer};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31, 68.56) {Moyle};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (467.39, 68.56) {Moyle};
 \end{scope}

### 2020-08-29 benchmarking/benchmarkingVM/ESS_round3b.tex
results update

% Created by tikzDevice version 0.12.3.1 on 2020-08-28 17:00:42
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (289.08,289.08);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at (144.54,253.90) {\bfseries NER (\textit{real}) vs. adapt (\textit{real})};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at (144.54, 14.40) {ESS/$10^6$ states [adapt (\textit{real})]};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at ( 21.60,144.54) {ESS/$10^6$ states [NER (\textit{real})]};
\end{scope}
\begin{scope}
\path[clip] ( 60.00, 60.00) rectangle (229.08,229.08);
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (  0.00,101.80) --
	(187.28,289.08);

\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (285.44,289.08) --
	(285.44,183.64) --
	(101.80,  0.00);
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (  0.00, 67.86) --
	(221.22,289.08);

\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (285.44,289.08) --
	(285.44,217.58) --
	( 67.86,  0.00);
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (  0.00, 33.93) --
	(255.15,289.08);

\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (285.44,289.08) --
	(285.44,251.51) --
	( 33.93,  0.00);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (170.87, 64.13) {$\frac{1}{64} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,175.57) {$64\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (136.94, 64.13) {$\frac{1}{16} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,141.64) {$16\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (101.01, 64.13) {$\frac{1}{4} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 62.56,107.71) {$4\times$};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 60.00, 60.00) -- (229.08,229.08);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.60,183.33) --
	(174.96,183.33);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.34,179.58) --
	(173.34,186.58);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (173.34,179.44) {$p$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (155.55,162.15) --
	(159.04,162.15);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (157.36,157.65) --
	(157.36,165.95);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (157.36,157.29) {$L$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.74,182.83) --
	(178.32,182.83);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (177.54,181.53) --
	(177.54,184.08);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (177.54,177.97) {$r$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (141.49,151.20) --
	(145.23,151.20);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (143.43,144.43) --
	(143.43,156.49);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (143.43,146.34) {$h$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.64,175.85) --
	(174.30,175.85);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.08,169.71) --
	(172.08,180.76);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (172.08,172.35) {$\sigma$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.44,182.54) --
	(183.14,182.54);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.30,181.23) --
	(182.30,183.78);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (182.30,179.04) {$\kappa$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (177.62,183.36) --
	(179.11,183.36);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.38,182.30) --
	(178.38,184.38);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (178.38,179.47) {$p$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.47,184.19) --
	(182.98,184.19);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.29,182.94) --
	(181.29,185.38);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (181.29,179.33) {$L$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.29,190.79) --
	(185.80,190.79);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.55,190.62) --
	(185.55,190.97);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (185.55,185.93) {$r$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.98,166.29) --
	(164.64,166.29);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (163.35,164.84) --
	(163.35,167.66);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (163.35,161.43) {$h$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.35,184.64) --
	(180.61,184.64);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.99,183.55) --
	(179.99,185.68);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (179.99,181.14) {$\sigma$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.74,187.65) --
	(187.69,187.65);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.22,187.38) --
	(187.22,187.91);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (187.22,184.15) {$\kappa$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (143.70,153.94) --
	(149.45,153.94);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (146.74,152.66) --
	(146.74,155.15);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (146.74,150.05) {$p$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.20,186.95) --
	(186.29,186.95);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.27,185.97) --
	(185.27,187.90);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (185.27,182.09) {$L$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.21,190.15) --
	(188.77,190.15);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.49,189.87) --
	(188.49,190.43);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (188.49,185.29) {$r$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (112.05,123.74) --
	(119.75,123.74);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (116.20,120.85) --
	(116.20,126.32);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (116.20,118.88) {$h$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (140.62,151.34) --
	(146.75,151.34);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (143.88,150.04) --
	(143.88,152.58);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (143.88,147.84) {$\sigma$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.32,187.89) --
	(190.04,187.89);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.69,187.47) --
	(189.69,188.30);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (189.69,184.39) {$\kappa$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (157.76,161.48) --
	(160.99,161.48);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (159.43,158.54) --
	(159.43,164.09);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (159.43,157.59) {$p$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.54,181.51) --
	(181.36,181.51);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.47,180.37) --
	(180.47,182.60);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (180.47,176.65) {$L$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.09,183.74) --
	(182.59,183.74);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.34,183.37) --
	(182.34,184.10);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (182.34,178.88) {$r$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (144.34,152.68) --
	(148.48,152.68);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (146.50,151.68) --
	(146.50,153.64);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (146.50,147.82) {$h$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (153.15,155.46) --
	(157.27,155.46);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (155.29,151.87) --
	(155.29,158.60);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (155.29,151.96) {$\sigma$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.57,186.94) --
	(190.37,186.94);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.97,186.50) --
	(189.97,187.37);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (189.97,183.44) {$\kappa$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.24,172.81) --
	(172.98,172.81);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.19,169.34) --
	(171.19,175.84);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (171.19,168.92) {$p$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.75,171.78) --
	(169.47,171.78);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.11,169.87) --
	(169.11,173.55);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (169.11,166.92) {$L$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (177.34,178.93) --
	(178.35,178.93);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (177.85,177.73) --
	(177.85,180.08);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (177.85,174.07) {$r$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (126.62,135.01) --
	(132.46,135.01);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (129.72,127.84) --
	(129.72,140.55);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (129.72,130.15) {$h$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.73,157.02) --
	(157.21,157.02);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (155.07,152.02) --
	(155.07,161.16);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (155.07,153.52) {$\sigma$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.93,184.10) --
	(187.59,184.10);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.26,183.27) --
	(187.26,184.91);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (187.26,180.60) {$\kappa$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.04,164.08) --
	(167.37,164.08);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.41,159.52) --
	(164.41,167.92);
\definecolor{drawColor}{RGB}{0,216,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (164.41,160.19) {$p$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.42,184.07) --
	(185.06,184.07);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.25,182.74) --
	(184.25,185.33);
\definecolor{drawColor}{RGB}{0,216,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (184.25,179.21) {$L$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.90,199.50) --
	(200.17,199.50);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (200.04,199.27) --
	(200.04,199.73);
\definecolor{drawColor}{RGB}{0,216,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (200.04,194.64) {$r$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (154.12,153.88) --
	(157.69,153.88);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (155.97,152.02) --
	(155.97,155.61);
\definecolor{drawColor}{RGB}{0,216,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (155.97,149.02) {$h$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (167.51,168.69) --
	(169.03,168.69);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.29,166.99) --
	(168.29,170.29);
\definecolor{drawColor}{RGB}{0,216,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (168.29,165.20) {$\sigma$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.61,187.66) --
	(189.35,187.66);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.98,187.26) --
	(188.98,188.06);
\definecolor{drawColor}{RGB}{0,216,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (188.98,184.17) {$\kappa$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.30,176.27) --
	(175.71,176.27);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.54,175.24) --
	(174.54,177.25);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (174.54,172.38) {$p$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.41,178.30) --
	(173.60,178.30);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.53,177.11) --
	(172.53,179.43);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (172.53,173.44) {$L$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.58,181.62) --
	(179.14,181.62);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.86,180.39) --
	(178.86,182.79);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (178.86,176.76) {$r$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (147.21,155.17) --
	(150.70,155.17);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.02,153.93) --
	(149.02,156.34);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (149.02,150.31) {$h$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.50,154.89) --
	(155.29,154.89);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (153.93,151.43) --
	(153.93,157.92);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (153.93,151.39) {$\sigma$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.20,186.29) --
	(190.85,186.29);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.53,184.54) --
	(190.53,187.93);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (190.53,182.79) {$\kappa$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (160.04,161.75) --
	(163.07,161.75);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.60,159.16) --
	(161.60,164.09);
\definecolor{drawColor}{RGB}{255,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (161.60,157.86) {$p$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (157.52,161.46) --
	(168.62,161.46);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (163.70,153.21) --
	(163.70,167.62);
\definecolor{drawColor}{RGB}{255,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (163.70,156.60) {$L$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.52,172.81) --
	(172.37,172.81);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.95,172.41) --
	(171.95,173.20);
\definecolor{drawColor}{RGB}{255,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (171.95,167.95) {$r$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (126.13,126.18) --
	(132.10,126.18);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (129.30,123.02) --
	(129.30,128.98);
\definecolor{drawColor}{RGB}{255,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (129.30,121.32) {$h$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (160.49,160.99) --
	(162.89,160.99);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.72,159.36) --
	(161.72,162.52);
\definecolor{drawColor}{RGB}{255,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (161.72,157.49) {$\sigma$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.40,184.15) --
	(188.26,184.15);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.83,183.10) --
	(187.83,185.16);
\definecolor{drawColor}{RGB}{255,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (187.83,180.65) {$\kappa$};
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (156.32,158.99) --
	(160.63,158.99);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (158.57,156.81) --
	(158.57,160.99);
\definecolor{drawColor}{RGB}{68,68,68}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (158.57,155.10) {$p$};
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.97,154.94) --
	(155.26,154.94);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (153.67,151.73) --
	(153.67,157.77);
\definecolor{drawColor}{RGB}{68,68,68}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (153.67,150.08) {$L$};
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.32,176.67) --
	(175.70,176.67);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.51,176.33) --
	(175.51,177.01);
\definecolor{drawColor}{RGB}{68,68,68}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (175.51,171.81) {$r$};
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.34,152.43) --
	(155.24,152.43);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (153.84,150.65) --
	(153.84,154.10);
\definecolor{drawColor}{RGB}{68,68,68}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (153.84,147.57) {$h$};
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (158.49,161.60) --
	(163.31,161.60);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.02,159.79) --
	(161.02,163.29);
\definecolor{drawColor}{RGB}{68,68,68}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (161.02,158.10) {$\sigma$};
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.77,186.37) --
	(190.27,186.37);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.53,185.57) --
	(189.53,187.15);
\definecolor{drawColor}{RGB}{68,68,68}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (189.53,182.87) {$\kappa$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- (229.08, 60.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- ( 60.00, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.39, 60.00) -- ( 99.39, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (116.36, 60.00) -- (116.36, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (155.75, 60.00) -- (155.75, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.72, 60.00) -- (172.72, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.11, 60.00) -- (212.11, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.08, 60.00) -- (229.08, 54.00);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 60.00, 38.40) {1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 99.39, 38.40) {5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (116.36, 38.40) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (155.75, 38.40) {50};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (212.11, 38.40) {500};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- ( 60.00,229.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- ( 54.00, 60.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 99.39) -- ( 54.00, 99.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,116.36) -- ( 54.00,116.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,155.75) -- ( 54.00,155.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,172.72) -- ( 54.00,172.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,212.11) -- ( 54.00,212.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,229.08) -- ( 54.00,229.08);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00, 56.56) {1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00, 95.95) {5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,112.92) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,152.31) {50};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,169.28) {100};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,208.67) {500};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,225.64) {1000};
\end{scope}
\begin{scope}
\path[clip] ( 60.00, 60.00) rectangle (229.08,229.08);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,171.00) rectangle (169.31,165.00);
\definecolor{fillColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,159.00) rectangle (169.31,153.00);
\definecolor{fillColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,147.00) rectangle (169.31,141.00);
\definecolor{fillColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,135.00) rectangle (169.31,129.00);
\definecolor{fillColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,123.00) rectangle (169.31,117.00);
\definecolor{fillColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,111.00) rectangle (169.31,105.00);
\definecolor{fillColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11, 99.00) rectangle (169.31, 93.00);
\definecolor{fillColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11, 87.00) rectangle (169.31, 81.00);
\definecolor{fillColor}{RGB}{68,68,68}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11, 75.00) rectangle (169.31, 69.00);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,164.56) {Ran};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,152.56) {Cognato};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,140.56) {Dornburg};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,128.56) {Sauquet};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,116.56) {Broughton};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,104.56) {Kawahara};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31, 92.56) {simulated};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31, 80.56) {Rightmyer};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31, 68.56) {Moyle};
\end{scope}
\end{tikzpicture}

\end{document}

### 2020-08-29 benchmarking/benchmarkingVM/ESS_round4b.tex
results update

@@
-% Created by tikzDevice version 0.12.3.1 on 2020-08-28 13:29:57
+% Created by tikzDevice version 0.12.3.1 on 2020-08-29 18:08:36
 % !TEX encoding = UTF-8 Unicode
@@
 \definecolor{fillColor}{RGB}{255,255,255}
-\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (289.08,289.08);
+\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (578.16,357.33);
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
+\path[clip] (  0.00,  0.00) rectangle (578.16,357.33);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at (144.54,253.90) {\bfseries NER (\textit{real}) vs. Bactrian (\textit{real})};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at (289.08,323.19) {\bfseries Comparison of Bactrian+adapt(\textit{real}) and NER+Bactrian+adapt(\textit{real})};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at (144.54, 14.40) {ESS/$10^6$ states [Bactrian (\textit{real})]};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at ( 21.60,144.54) {ESS/$10^6$ states [NER (\textit{real})]};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 21.60,178.67) {Relative ESS/hr};
 \end{scope}
 \begin{scope}
-\path[clip] ( 60.00, 60.00) rectangle (229.08,229.08);
+\path[clip] ( 60.00, 60.00) rectangle (518.16,297.33);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] ( 60.00,178.67) -- (518.16,178.67);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 65.87,195.96) --
+	( 65.87,154.65);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 65.87,171.42) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 71.75,185.67) --
+	( 71.75,167.66);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 71.75,172.78) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 77.62,173.36) --
+	( 77.62,138.30);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 77.62,151.94) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.50,175.80) --
+	( 83.50,155.97);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 83.50,162.00) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.37,193.05) --
+	( 89.37,165.41);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 89.37,175.34) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.24,200.05) --
+	( 95.24,119.16);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 95.24,155.71) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (101.12,188.48) --
+	(101.12,172.95);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (101.12,176.83) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (106.99,203.32) --
+	(106.99,174.31);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (106.99,184.93) {$p$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.86,196.91) --
+	(112.86,163.81);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (112.86,176.47) {$p$};
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] ( 65.87,173.60) --
+	(118.74,173.60);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 92.31,275.05) {-2.6\% faster};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (  0.00,101.80) --
-	(187.28,289.08);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (124.61,  0.00) --
+	(124.61,357.33);
+\definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (285.44,289.08) --
-	(285.44,183.64) --
-	(101.80,  0.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (130.49,207.17) --
+	(130.49,169.73);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (130.49,183.59) {$L$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (136.36,191.35) --
+	(136.36,173.79);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (136.36,177.71) {$L$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (142.23,189.52) --
+	(142.23,168.91);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (142.23,174.36) {$L$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.11,185.84) --
+	(148.11,175.26);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (148.11,175.69) {$L$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.98,205.79) --
+	(153.98,176.65);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (153.98,186.36) {$L$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.86,186.57) --
+	(159.86,145.37);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (159.86,161.11) {$L$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (165.73,188.29) --
+	(165.73,174.10);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (165.73,176.34) {$L$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.60,255.23) --
+	(171.60,189.53);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (171.60,217.52) {$L$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.48,205.81) --
+	(177.48,173.63);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (177.48,184.86) {$L$};
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (130.49,186.81) --
+	(183.35,186.81);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (156.92,275.05) {4.1\% faster};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (  0.00, 67.86) --
-	(221.22,289.08);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (189.22,  0.00) --
+	(189.22,357.33);
+\definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (285.44,289.08) --
-	(285.44,217.58) --
-	( 67.86,  0.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.10,177.59) --
+	(195.10,162.31);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (195.10,165.09) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.97,178.57) --
+	(200.97,176.11);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (200.97,172.48) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.85,180.77) --
+	(206.85,178.09);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (206.85,174.57) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.72,177.37) --
+	(212.72,173.05);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (212.72,170.35) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.59,187.32) --
+	(218.59,176.60);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (218.59,177.10) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (224.47,177.78) --
+	(224.47,175.24);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (224.47,171.65) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.34,177.98) --
+	(230.34,175.18);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (230.34,171.72) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (236.22,183.49) --
+	(236.22,176.98);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (236.22,175.37) {$r$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (242.09,178.34) --
+	(242.09,175.02);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (242.09,171.82) {$r$};
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (195.10,177.10) --
+	(247.96,177.10);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (221.53,275.05) {-0.79\% faster};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (  0.00, 33.93) --
-	(255.15,289.08);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (253.84,  0.00) --
+	(253.84,357.33);
+\definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (285.44,289.08) --
-	(285.44,251.51) --
-	( 33.93,  0.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (259.71,184.32) --
+	(259.71,145.55);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (259.71,160.07) {$l$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (265.58,183.13) --
+	(265.58,165.89);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (265.58,169.65) {$l$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.46,153.36) --
+	(271.46,127.71);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (271.46,135.68) {$l$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (277.33,171.14) --
+	(277.33,150.33);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (277.33,155.88) {$l$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (283.21,201.48) --
+	(283.21,153.08);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (283.21,172.42) {$l$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (289.08,184.86) --
+	(289.08,174.50);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (289.08,174.82) {$l$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (294.95,205.34) --
+	(294.95,169.23);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (294.95,182.42) {$l$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (300.83,213.14) --
+	(300.83,174.14);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (300.83,188.78) {$l$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (306.70,185.85) --
+	(306.70,170.71);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (306.70,173.42) {$l$};
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (170.87, 64.13) {$\frac{1}{64} \times$};
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (259.71,172.99) --
+	(312.58,172.99);
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,175.57) {$64\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (136.94, 64.13) {$\frac{1}{16} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,141.64) {$16\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (101.01, 64.13) {$\frac{1}{4} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 62.56,107.71) {$4\times$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (286.14,275.05) {-2.9\% faster};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 60.00, 60.00) -- (229.08,229.08);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (318.45,  0.00) --
+	(318.45,357.33);
 \definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (167.76,176.81) --
-	(177.59,176.81);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (324.32,225.48) --
+	(324.32,175.86);
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.17,173.30) --
-	(173.17,179.87);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (324.32,197.17) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (330.20,186.20) --
+	(330.20,169.11);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (330.20,174.16) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (336.07,167.03) --
+	(336.07,125.99);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (336.07,143.01) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (341.94,173.76) --
+	(341.94,158.13);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (341.94,162.44) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (347.82,191.65) --
+	(347.82,145.40);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (347.82,165.03) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (353.69,186.56) --
+	(353.69,141.86);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (353.69,160.71) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (359.57,189.65) --
+	(359.57,156.76);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (359.57,169.71) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (365.44,190.85) --
+	(365.44,173.48);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (365.44,178.66) {$\sigma$};
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (371.31,192.67) --
+	(371.31,164.07);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (371.31,174.87) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (324.32,173.03) --
+	(377.19,173.03);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (350.76,275.05) {-2.8\% faster};
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (383.06,  0.00) --
+	(383.06,357.33);
 \definecolor{drawColor}{RGB}{255,0,109}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (173.17,172.92) {$p$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (388.94,171.89) --
+	(388.94,164.81);
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (159.31,162.01) --
-	(163.92,162.01);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.72,159.26) --
-	(161.72,164.49);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (161.72,157.15) {$L$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.06,181.17) --
-	(182.41,181.17);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.79,179.85) --
-	(180.79,182.42);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (180.79,176.31) {$r$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (146.50,148.62) --
-	(154.66,148.62);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.92,144.87) --
-	(150.92,151.87);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (150.92,143.76) {$h$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.71,173.43) --
-	(177.68,173.43);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.88,170.31) --
-	(174.88,176.19);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (174.88,169.93) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.73,184.14) --
-	(184.51,184.14);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.12,183.29) --
-	(184.12,184.97);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (184.12,180.65) {$\kappa$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (388.94,164.85) {$\kappa$};
 \definecolor{drawColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (167.36,168.02) --
-	(168.98,168.02);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (394.81,181.31) --
+	(394.81,172.79);
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.18,166.12) --
-	(168.18,169.79);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (168.18,164.13) {$p$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.33,181.05) --
-	(184.66,181.05);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.59,179.68) --
-	(182.59,182.34);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (182.59,176.19) {$L$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.65,189.93) --
-	(190.09,189.93);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.87,189.80) --
-	(189.87,190.07);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (189.87,185.07) {$r$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.01,163.37) --
-	(163.46,163.37);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (162.27,161.59) --
-	(162.27,165.04);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (162.27,158.51) {$h$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.43,171.21) --
-	(171.47,171.21);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (170.47,169.54) --
-	(170.47,172.76);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (170.47,167.71) {$\sigma$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.11,186.84) --
-	(187.84,186.84);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.47,186.09) --
-	(187.47,187.56);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (187.47,183.34) {$\kappa$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (394.81,173.55) {$\kappa$};
 \definecolor{drawColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (140.77,143.75) --
-	(146.89,143.75);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (400.68,183.51) --
+	(400.68,178.73);
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (144.02,141.02) --
-	(144.02,146.20);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (144.02,139.86) {$p$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.63,185.25) --
-	(186.28,185.25);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.47,184.60) --
-	(185.47,185.88);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (185.47,180.39) {$L$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.28,191.35) --
-	(191.62,191.35);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.45,191.14) --
-	(191.45,191.57);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (191.45,186.49) {$r$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (115.40,120.77) --
-	(121.31,120.77);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (118.53,118.52) --
-	(118.53,122.84);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (118.53,115.91) {$h$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (138.45,141.26) --
-	(144.56,141.26);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (141.70,138.68) --
-	(141.70,143.59);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (141.70,137.76) {$\sigma$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.60,189.69) --
-	(190.10,189.69);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.85,189.37) --
-	(189.85,190.01);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (189.85,186.19) {$\kappa$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (400.68,177.62) {$\kappa$};
 \definecolor{drawColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (153.71,155.81) --
-	(156.41,155.81);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (406.56,182.01) --
+	(406.56,176.20);
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (155.09,153.97) --
-	(155.09,157.53);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (155.09,151.93) {$p$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.01,182.93) --
-	(184.16,182.93);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.59,181.97) --
-	(183.59,183.86);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (183.59,178.07) {$L$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.27,185.41) --
-	(185.64,185.41);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.46,185.14) --
-	(185.46,185.68);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (185.46,180.55) {$r$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.38,152.51) --
-	(153.32,152.51);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.89,150.64) --
-	(151.89,154.25);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (151.89,147.65) {$h$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.99,153.09) --
-	(153.12,153.09);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.61,151.37) --
-	(151.61,154.70);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (151.61,149.59) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.48,189.88) --
-	(190.12,189.88);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.80,189.64) --
-	(189.80,190.12);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (189.80,186.38) {$\kappa$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (406.56,175.60) {$\kappa$};
 \definecolor{drawColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.97,172.63) --
-	(172.66,172.63);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.43,182.69) --
+	(412.43,177.75);
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (170.89,171.25) --
-	(170.89,173.93);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (170.89,168.74) {$p$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.63,171.20) --
-	(172.76,171.20);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.25,168.92) --
-	(171.25,173.27);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (171.25,166.34) {$L$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.71,179.54) --
-	(180.29,179.54);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.51,179.22) --
-	(179.51,179.86);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (179.51,174.68) {$r$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (132.05,136.84) --
-	(138.72,136.84);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (135.61,134.65) --
-	(135.61,138.85);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (135.61,131.98) {$h$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (153.99,158.74) --
-	(158.62,158.74);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (156.42,156.68) --
-	(156.42,160.64);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (156.42,155.24) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.12,187.39) --
-	(188.09,187.39);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.61,187.21) --
-	(187.61,187.56);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (187.61,183.89) {$\kappa$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (412.43,176.72) {$\kappa$};
 \definecolor{drawColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (136.78,142.81) --
-	(143.51,142.81);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.30,182.42) --
+	(418.30,177.52);
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (140.38,140.95) --
-	(140.38,144.54);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (140.38,138.93) {$p$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.19,175.24) --
-	(175.57,175.24);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.94,173.70) --
-	(173.94,176.70);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (173.94,170.38) {$L$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.14,199.28) --
-	(199.39,199.28);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.27,199.12) --
-	(199.27,199.43);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (199.27,194.42) {$r$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.32,153.37) --
-	(153.40,153.37);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.45,152.09) --
-	(151.45,154.59);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (151.45,148.51) {$h$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (143.54,146.09) --
-	(146.70,146.09);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (145.17,144.77) --
-	(145.17,147.34);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (145.17,142.59) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.59,188.58) --
-	(189.30,188.58);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.95,188.00) --
-	(188.95,189.16);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (188.95,185.09) {$\kappa$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (418.30,176.47) {$\kappa$};
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (207.54,173.85) --
-	(212.93,173.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (424.18,181.51) --
+	(424.18,173.97);
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (210.38,172.98) --
-	(210.38,174.70);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (210.38,169.97) {$p$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.97,180.24) --
-	(218.72,180.24);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (215.57,179.26) --
-	(215.57,181.18);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (215.57,175.38) {$L$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.23,155.80) --
-	(194.70,155.80);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.12,153.72) --
-	(192.12,157.72);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (192.12,150.94) {$h$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.41,148.96) --
-	(190.21,148.96);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.62,146.15) --
-	(186.62,151.47);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (186.62,145.46) {$\sigma$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (223.68,189.99) --
-	(229.66,189.99);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (226.85,189.40) --
-	(226.85,190.57);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (226.85,186.49) {$\kappa$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (424.18,174.24) {$\kappa$};
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (147.49,145.70) --
-	(150.04,145.70);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (430.05,182.22) --
+	(430.05,172.32);
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (148.80,143.46) --
-	(148.80,147.76);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (148.80,141.81) {$p$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (162.54,164.33) --
-	(168.49,164.33);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (165.69,161.29) --
-	(165.69,167.03);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (165.69,159.47) {$L$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.75,174.68) --
-	(175.23,174.68);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.99,174.37) --
-	(174.99,174.99);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (174.99,169.82) {$r$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (128.23,128.70) --
-	(134.51,128.70);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (131.57,126.30) --
-	(131.57,130.88);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (131.57,123.84) {$h$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.09,147.25) --
-	(151.54,147.25);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.34,144.74) --
-	(150.34,149.53);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (150.34,143.75) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.90,187.34) --
-	(187.94,187.34);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.43,186.74) --
-	(187.43,187.93);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (187.43,183.84) {$\kappa$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (430.05,173.77) {$\kappa$};
 \definecolor{drawColor}{RGB}{68,68,68}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (137.43,142.95) --
-	(143.47,142.95);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (435.93,190.73) --
+	(435.93,177.77);
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (140.64,139.25) --
-	(140.64,146.17);
-\definecolor{drawColor}{RGB}{68,68,68}
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (435.93,180.75) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (140.64,139.07) {$p$};
-\definecolor{drawColor}{RGB}{68,68,68}
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (388.94,178.34) --
+	(441.80,178.34);
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (147.25,154.09) --
-	(156.56,154.09);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (415.37,275.05) {-0.16\% faster};
+\definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.34,152.31) --
-	(152.34,155.75);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (152.34,149.23) {$L$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.42,178.15) --
-	(177.06,178.15);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.75,177.83) --
-	(176.75,178.46);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (176.75,173.29) {$r$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.25,153.72) --
-	(154.44,153.72);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.90,151.71) --
-	(152.90,155.57);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (152.90,148.86) {$h$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (140.61,145.84) --
-	(146.50,145.84);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (143.73,141.96) --
-	(143.73,149.20);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (143.73,142.35) {$\sigma$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.41,188.98) --
-	(189.20,188.98);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.32,187.71) --
-	(188.32,190.20);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (188.32,185.48) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (447.67,  0.00) --
+	(447.67,357.33);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
+\path[clip] (  0.00,  0.00) rectangle (578.16,357.33);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- (229.08, 60.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- (518.16, 60.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- ( 60.00, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.31, 60.00) -- ( 92.31, 54.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.39, 60.00) -- ( 99.39, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (156.92, 60.00) -- (156.92, 54.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (116.36, 60.00) -- (116.36, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.53, 60.00) -- (221.53, 54.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (155.75, 60.00) -- (155.75, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (286.14, 60.00) -- (286.14, 54.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.72, 60.00) -- (172.72, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.76, 60.00) -- (350.76, 54.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.11, 60.00) -- (212.11, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (415.37, 60.00) -- (415.37, 54.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.08, 60.00) -- (229.08, 54.00);
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.70] at ( 94.72, 48.00) {Prior};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 60.00, 38.40) {1};
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.70] at (159.33, 48.00) {Likelihood};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 99.39, 38.40) {5};
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.70] at (223.94, 48.00) {Mean leaf rate};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (116.36, 38.40) {10};
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.70] at (288.55, 48.00) {Tree length};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (155.75, 38.40) {50};
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.70] at (353.17, 48.00) {Clock SD $\sigma$};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (212.11, 38.40) {500};
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.70] at (417.78, 48.00) {HKY model $\kappa$};
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- ( 60.00,229.08);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 79.78) -- ( 60.00,277.55);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- ( 54.00, 60.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 79.78) -- ( 54.00, 79.78);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 99.39) -- ( 54.00, 99.39);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,129.22) -- ( 54.00,129.22);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,116.36) -- ( 54.00,116.36);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,178.67) -- ( 54.00,178.67);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,155.75) -- ( 54.00,155.75);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,228.11) -- ( 54.00,228.11);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,172.72) -- ( 54.00,172.72);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,277.55) -- ( 54.00,277.55);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,212.11) -- ( 54.00,212.11);
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00, 76.33) {0.50};
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,229.08) -- ( 54.00,229.08);
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,125.78) {0.75};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00, 56.56) {1};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,175.22) {1.00};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00, 95.95) {5};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,224.67) {1.25};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,112.92) {10};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,152.31) {50};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,169.28) {100};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,208.67) {500};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,225.64) {1000};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,274.11) {1.50};
 \end{scope}
 \begin{scope}
-\path[clip] ( 60.00, 60.00) rectangle (229.08,229.08);
+\path[clip] ( 60.00, 60.00) rectangle (518.16,297.33);
 \definecolor{drawColor}{RGB}{0,0,0}

### 2020-08-29 benchmarking/benchmarkingVM/ESS_round5.tex
results update

% Created by tikzDevice version 0.12.3.1 on 2020-08-29 17:56:05
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (578.16,357.33);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,357.33);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at (289.08,323.19) {\bfseries Comparison of AVMVN+NER+Bactrian+adapt(\textit{real}) and NER+Bactrian+adapt(\textit{real})};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 21.60,178.67) {Relative ESS/hr};
\end{scope}
\begin{scope}
\path[clip] ( 60.00, 60.00) rectangle (518.16,297.33);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] ( 60.00,178.67) -- (518.16,178.67);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 65.87,182.29) --
	( 65.87,155.40);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 65.87,164.96) {$p$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 71.75,182.37) --
	( 71.75,172.85);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 71.75,173.72) {$p$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 77.62,206.63) --
	( 77.62,183.55);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 77.62,191.20) {$p$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.50,192.35) --
	( 83.50,184.14);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 83.50,184.36) {$p$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.37,198.03) --
	( 89.37,169.64);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 89.37,179.94) {$p$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.24,194.87) --
	( 95.24,123.63);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 95.24,155.36) {$p$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (101.12,195.10) --
	(101.12,177.27);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (101.12,182.29) {$p$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (106.99,193.21) --
	(106.99,172.45);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (106.99,178.95) {$p$};
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.86,199.27) --
	(112.86,173.64);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (112.86,182.57) {$p$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] ( 65.87,180.93) --
	(118.74,180.93);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 92.31,275.05) {1.1\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (124.61,  0.00) --
	(124.61,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (130.49,204.32) --
	(130.49,182.55);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (130.49,188.58) {$L$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (136.36,199.93) --
	(136.36,178.39);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (136.36,184.30) {$L$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (142.23,195.23) --
	(142.23,183.90);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (142.23,184.70) {$L$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.11,217.30) --
	(148.11,203.38);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (148.11,205.48) {$L$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.98,248.47) --
	(153.98,227.05);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (153.98,232.90) {$L$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.86,183.36) --
	(159.86,156.04);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (159.86,164.84) {$L$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (165.73,231.86) --
	(165.73,219.25);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (165.73,220.70) {$L$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.60,235.33) --
	(171.60,157.10);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (171.60,191.36) {$L$};
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.48,199.47) --
	(177.48,168.81);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (177.48,179.28) {$L$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (130.49,199.54) --
	(183.35,199.54);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (156.92,275.05) {11\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (189.22,  0.00) --
	(189.22,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.10,173.48) --
	(195.10,158.53);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (195.10,161.15) {$r$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.97,184.98) --
	(200.97,182.46);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (200.97,178.86) {$r$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.85,186.09) --
	(206.85,182.08);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (206.85,179.23) {$r$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.72,194.39) --
	(212.72,191.56);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (212.72,188.11) {$r$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.59,208.43) --
	(218.59,201.15);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (218.59,199.93) {$r$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (224.47,185.90) --
	(224.47,183.69);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (224.47,179.94) {$r$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.34,200.46) --
	(230.34,196.65);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (230.34,193.69) {$r$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (236.22,188.37) --
	(236.22,184.80);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (236.22,181.72) {$r$};
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (242.09,174.48) --
	(242.09,171.48);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (242.09,168.12) {$r$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (195.10,186.05) --
	(247.96,186.05);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (221.53,275.05) {3.7\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (253.84,  0.00) --
	(253.84,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (259.71,170.83) --
	(259.71,145.47);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (259.71,153.29) {$l$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (265.58,217.60) --
	(265.58,197.77);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (265.58,202.82) {$l$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.46,235.98) --
	(271.46,197.45);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (271.46,211.85) {$l$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (277.33,200.90) --
	(277.33,186.58);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (277.33,188.88) {$l$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (283.21,194.62) --
	(283.21,161.91);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (283.21,173.40) {$l$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (289.08,195.59) --
	(289.08,178.65);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (289.08,182.26) {$l$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (294.95,222.46) --
	(294.95,190.90);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (294.95,201.82) {$l$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (300.83,227.18) --
	(300.83,192.62);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (300.83,205.04) {$l$};
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (306.70,227.56) --
	(306.70,211.98);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (306.70,214.91) {$l$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (259.71,197.56) --
	(312.58,197.56);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (286.14,275.05) {9.6\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (318.45,  0.00) --
	(318.45,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (324.32,177.22) --
	(324.32,147.94);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (324.32,159.08) {$\sigma$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (330.20,189.14) --
	(330.20,175.54);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (330.20,178.84) {$\sigma$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (336.07,201.86) --
	(336.07,178.01);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (336.07,186.44) {$\sigma$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (341.94,197.85) --
	(341.94,176.63);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (341.94,183.74) {$\sigma$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (347.82,185.47) --
	(347.82,162.39);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (347.82,170.43) {$\sigma$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (353.69,171.36) --
	(353.69,145.10);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (353.69,154.73) {$\sigma$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (359.57,218.64) --
	(359.57,189.11);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (359.57,200.38) {$\sigma$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (365.44,197.28) --
	(365.44,169.92);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (365.44,180.10) {$\sigma$};
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (371.31,208.91) --
	(371.31,174.10);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (371.31,188.01) {$\sigma$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (324.32,181.47) --
	(377.19,181.47);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (350.76,275.05) {1.4\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (383.06,  0.00) --
	(383.06,357.33);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (388.94,173.56) --
	(388.94,166.63);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (388.94,166.59) {$\kappa$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (394.81,181.62) --
	(394.81,172.94);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (394.81,173.78) {$\kappa$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (400.68,182.02) --
	(400.68,177.17);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (400.68,176.10) {$\kappa$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (406.56,181.64) --
	(406.56,176.43);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (406.56,175.54) {$\kappa$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.43,181.68) --
	(412.43,177.34);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (412.43,176.01) {$\kappa$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.30,183.51) --
	(418.30,175.87);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (418.30,176.19) {$\kappa$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (424.18,188.86) --
	(424.18,177.28);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (424.18,179.57) {$\kappa$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (430.05,185.00) --
	(430.05,172.59);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (430.05,175.29) {$\kappa$};
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (435.93,187.04) --
	(435.93,177.74);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (435.93,178.89) {$\kappa$};
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (388.94,178.83) --
	(441.80,178.83);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (415.37,275.05) {0.082\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (447.67,  0.00) --
	(447.67,357.33);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,357.33);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- (518.16, 60.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.31, 60.00) -- ( 92.31, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (156.92, 60.00) -- (156.92, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.53, 60.00) -- (221.53, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (286.14, 60.00) -- (286.14, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.76, 60.00) -- (350.76, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (415.37, 60.00) -- (415.37, 54.00);

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.70] at ( 94.72, 48.00) {Prior};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.70] at (159.33, 48.00) {Likelihood};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.70] at (223.94, 48.00) {Mean leaf rate};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.70] at (288.55, 48.00) {Tree length};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.70] at (353.17, 48.00) {Clock SD $\sigma$};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.70] at (417.78, 48.00) {HKY model $\kappa$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 79.78) -- ( 60.00,277.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 79.78) -- ( 54.00, 79.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,129.22) -- ( 54.00,129.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,178.67) -- ( 54.00,178.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,228.11) -- ( 54.00,228.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,277.55) -- ( 54.00,277.55);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00, 76.33) {0.50};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,125.78) {0.75};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,175.22) {1.00};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,224.67) {1.25};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,274.11) {1.50};
\end{scope}
\begin{scope}
\path[clip] ( 60.00, 60.00) rectangle (518.16,297.33);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (451.19,171.00) rectangle (458.39,165.00);
\definecolor{fillColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (451.19,159.00) rectangle (458.39,153.00);
\definecolor{fillColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (451.19,147.00) rectangle (458.39,141.00);
\definecolor{fillColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (451.19,135.00) rectangle (458.39,129.00);
\definecolor{fillColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (451.19,123.00) rectangle (458.39,117.00);
\definecolor{fillColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (451.19,111.00) rectangle (458.39,105.00);
\definecolor{fillColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (451.19, 99.00) rectangle (458.39, 93.00);
\definecolor{fillColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (451.19, 87.00) rectangle (458.39, 81.00);
\definecolor{fillColor}{RGB}{68,68,68}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (451.19, 75.00) rectangle (458.39, 69.00);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (467.39,164.56) {Ran};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (467.39,152.56) {Cognato};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (467.39,140.56) {Dornburg};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (467.39,128.56) {Sauquet};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (467.39,116.56) {Broughton};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (467.39,104.56) {Kawahara};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (467.39, 92.56) {simulated};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (467.39, 80.56) {Rightmyer};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (467.39, 68.56) {Moyle};
\end{scope}
\end{tikzpicture}

\end{document}

### 2020-08-29 benchmarking/benchmarkingVM/ESS_round5b.tex
results update

% Created by tikzDevice version 0.12.3.1 on 2020-08-29 17:56:12
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (289.08,289.08);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at (144.54,253.90) {\bfseries AVMVN+NER+Bactrian+adapt(\textit{real}) vs. \textit{cat}};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at (144.54, 14.40) {ESS/$10^6$ states [\textit{cat}]};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at ( 21.60,144.54) {ESS/$10^6$ states [AVMVN+NER+Bactrian+adapt(\textit{real})]};
\end{scope}
\begin{scope}
\path[clip] ( 60.00, 60.00) rectangle (229.08,229.08);
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (  0.00,101.80) --
	(187.28,289.08);

\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (285.44,289.08) --
	(285.44,183.64) --
	(101.80,  0.00);
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (  0.00, 67.86) --
	(221.22,289.08);

\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (285.44,289.08) --
	(285.44,217.58) --
	( 67.86,  0.00);
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (  0.00, 33.93) --
	(255.15,289.08);

\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (285.44,289.08) --
	(285.44,251.51) --
	( 33.93,  0.00);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (170.87, 64.13) {$\frac{1}{64} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,175.57) {$64\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (136.94, 64.13) {$\frac{1}{16} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,141.64) {$16\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (101.01, 64.13) {$\frac{1}{4} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 62.56,107.71) {$4\times$};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 60.00, 60.00) -- (229.08,229.08);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 71.42,176.23) --
	( 84.65,176.23);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 78.92,174.41) --
	( 78.92,177.92);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 78.92,172.34) {$p$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.81,162.66) --
	(177.01,162.66);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.00,161.37) --
	(175.00,163.88);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (175.00,157.80) {$L$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 83.03,178.79) --
	( 88.54,178.79);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 85.94,177.78) --
	( 85.94,179.76);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 85.94,173.93) {$r$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 68.08,146.84) --
	( 81.61,146.84);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 75.77,145.03) --
	( 75.77,148.53);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 75.77,141.98) {$l$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 76.64,170.79) --
	( 89.72,170.79);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 84.04,168.73) --
	( 84.04,172.69);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 84.04,167.29) {$\sigma$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.14,181.75) --
	(185.74,181.75);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.44,181.29) --
	(185.44,182.19);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (185.44,178.25) {$\kappa$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (167.17,183.23) --
	(169.48,183.23);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.35,182.63) --
	(168.35,183.81);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (168.35,179.34) {$p$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.41,185.46) --
	(186.36,185.46);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.41,184.16) --
	(185.41,186.69);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (185.41,180.60) {$L$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.62,191.41) --
	(176.94,191.41);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.78,191.26) --
	(176.78,191.56);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (176.78,186.55) {$r$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (163.54,175.46) --
	(166.19,175.46);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.90,174.36) --
	(164.90,176.51);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (164.90,170.60) {$l$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.00,185.09) --
	(170.90,185.09);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.49,184.25) --
	(169.49,185.90);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (169.49,181.59) {$\sigma$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.97,187.48) --
	(186.70,187.48);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.34,186.93) --
	(186.34,188.01);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (186.34,183.98) {$\kappa$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.34,156.88) --
	(154.22,156.88);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.82,155.53) --
	(152.82,158.17);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (152.82,152.99) {$p$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.12,188.93) --
	(188.93,188.93);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.04,188.26) --
	(188.04,189.59);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (188.04,184.07) {$L$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.09,192.48) --
	(182.78,192.48);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.44,192.24) --
	(182.44,192.72);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (182.44,187.62) {$r$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (144.78,143.01) --
	(147.93,143.01);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (146.41,140.92) --
	(146.41,144.93);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (146.41,138.15) {$l$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (142.15,153.61) --
	(147.36,153.61);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (144.89,152.17) --
	(144.89,154.96);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (144.89,150.11) {$\sigma$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.56,189.79) --
	(189.29,189.79);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.93,189.49) --
	(188.93,190.09);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (188.93,186.29) {$\kappa$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (131.25,166.10) --
	(135.47,166.10);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (133.45,165.61) --
	(133.45,166.58);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (133.45,162.21) {$p$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.59,188.13) --
	(187.96,188.13);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.80,187.38) --
	(186.80,188.87);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (186.80,183.27) {$L$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.33,188.08) --
	(175.07,188.08);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.70,187.92) --
	(174.70,188.24);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (174.70,183.22) {$r$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (128.97,157.79) --
	(133.26,157.79);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (131.21,156.95) --
	(131.21,158.60);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (131.21,152.93) {$l$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (134.65,160.83) --
	(137.30,160.83);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (136.01,159.54) --
	(136.01,162.06);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (136.01,157.33) {$\sigma$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.92,189.83) --
	(189.56,189.83);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.25,189.51) --
	(189.25,190.15);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (189.25,186.34) {$\kappa$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (101.90,175.20) --
	(107.68,175.20);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (104.96,173.42) --
	(104.96,176.85);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (104.96,171.31) {$p$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.30,177.06) --
	(182.80,177.06);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.58,176.01) --
	(181.58,178.06);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (181.58,172.20) {$L$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (147.34,182.51) --
	(148.15,182.51);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (147.75,182.11) --
	(147.75,182.91);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (147.75,177.65) {$r$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (101.52,138.26) --
	(107.21,138.26);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (104.53,136.14) --
	(104.53,140.21);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (104.53,133.40) {$l$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (103.73,159.54) --
	(112.28,159.54);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (108.38,158.03) --
	(108.38,160.96);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (108.38,156.04) {$\sigma$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.98,187.47) --
	(187.75,187.47);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.37,187.20) --
	(187.37,187.74);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (187.37,183.97) {$\kappa$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.65,162.64) --
	(178.24,162.64);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.51,157.19) --
	(176.51,167.10);
\definecolor{drawColor}{RGB}{0,216,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (176.51,158.76) {$p$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.53,184.48) --
	(186.79,184.48);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.68,182.64) --
	(185.68,186.19);
\definecolor{drawColor}{RGB}{0,216,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (185.68,179.62) {$L$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (197.02,201.51) --
	(197.40,201.51);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (197.21,201.37) --
	(197.21,201.64);
\definecolor{drawColor}{RGB}{0,216,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (197.21,196.65) {$r$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.18,184.01) --
	(175.90,184.01);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.11,182.98) --
	(174.11,185.00);
\definecolor{drawColor}{RGB}{0,216,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (174.11,179.15) {$l$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (165.98,167.13) --
	(169.18,167.13);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (167.63,165.25) --
	(167.63,168.88);
\definecolor{drawColor}{RGB}{0,216,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (167.63,163.63) {$\sigma$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.25,189.13) --
	(189.20,189.13);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.73,188.65) --
	(188.73,189.59);
\definecolor{drawColor}{RGB}{0,216,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (188.73,185.63) {$\kappa$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (125.86,180.56) --
	(131.05,180.56);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (128.59,179.48) --
	(128.59,181.61);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (128.59,176.68) {$p$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.04,185.82) --
	(191.81,185.82);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.47,185.18) --
	(190.47,186.44);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (190.47,180.96) {$L$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (163.39,187.14) --
	(165.31,187.14);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.37,186.92) --
	(164.37,187.35);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (164.37,182.28) {$r$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (126.45,144.38) --
	(131.50,144.38);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (129.10,142.61) --
	(129.10,146.03);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (129.10,139.52) {$l$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (141.51,161.01) --
	(144.15,161.01);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (142.86,159.33) --
	(142.86,162.58);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (142.86,157.51) {$\sigma$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.54,190.27) --
	(192.68,190.27);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.12,189.56) --
	(192.12,190.97);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (192.12,186.78) {$\kappa$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (148.85,164.84) --
	(152.02,164.84);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.49,163.54) --
	(150.49,166.06);
\definecolor{drawColor}{RGB}{255,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (150.49,160.95) {$p$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (166.77,167.56) --
	(172.22,167.56);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.65,162.65) --
	(169.65,171.64);
\definecolor{drawColor}{RGB}{255,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (169.65,162.70) {$L$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (170.20,176.63) --
	(170.60,176.63);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (170.40,176.41) --
	(170.40,176.84);
\definecolor{drawColor}{RGB}{255,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (170.40,171.77) {$r$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (147.22,157.74) --
	(150.25,157.74);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (148.78,155.82) --
	(148.78,159.52);
\definecolor{drawColor}{RGB}{255,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (148.78,152.88) {$l$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (154.41,164.24) --
	(157.15,164.24);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (155.82,162.53) --
	(155.82,165.84);
\definecolor{drawColor}{RGB}{255,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (155.82,160.75) {$\sigma$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.29,187.63) --
	(188.19,187.63);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.74,186.85) --
	(187.74,188.39);
\definecolor{drawColor}{RGB}{255,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (187.74,184.13) {$\kappa$};
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.74,163.30) --
	(163.42,163.30);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (162.60,161.73) --
	(162.60,164.78);
\definecolor{drawColor}{RGB}{68,68,68}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (162.60,159.41) {$p$};
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.44,156.47) --
	(154.65,156.47);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.63,154.55) --
	(152.63,158.25);
\definecolor{drawColor}{RGB}{68,68,68}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (152.63,151.61) {$L$};
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.40,178.21) --
	(171.83,178.21);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.61,178.02) --
	(171.61,178.40);
\definecolor{drawColor}{RGB}{68,68,68}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (171.61,173.35) {$r$};
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.71,177.88) --
	(163.34,177.88);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (162.54,177.07) --
	(162.54,178.66);
\definecolor{drawColor}{RGB}{68,68,68}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (162.54,173.02) {$l$};
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (155.74,166.68) --
	(158.47,166.68);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (157.14,164.57) --
	(157.14,168.62);
\definecolor{drawColor}{RGB}{68,68,68}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (157.14,163.18) {$\sigma$};
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.80,189.91) --
	(190.03,189.91);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.42,189.34) --
	(189.42,190.47);
\definecolor{drawColor}{RGB}{68,68,68}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (189.42,186.41) {$\kappa$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- (229.08, 60.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- ( 60.00, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.39, 60.00) -- ( 99.39, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (116.36, 60.00) -- (116.36, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (155.75, 60.00) -- (155.75, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.72, 60.00) -- (172.72, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.11, 60.00) -- (212.11, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.08, 60.00) -- (229.08, 54.00);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 60.00, 38.40) {1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 99.39, 38.40) {5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (116.36, 38.40) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (155.75, 38.40) {50};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (212.11, 38.40) {500};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- ( 60.00,229.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- ( 54.00, 60.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 99.39) -- ( 54.00, 99.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,116.36) -- ( 54.00,116.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,155.75) -- ( 54.00,155.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,172.72) -- ( 54.00,172.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,212.11) -- ( 54.00,212.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,229.08) -- ( 54.00,229.08);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00, 56.56) {1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00, 95.95) {5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,112.92) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,152.31) {50};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,169.28) {100};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,208.67) {500};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,225.64) {1000};
\end{scope}
\begin{scope}
\path[clip] ( 60.00, 60.00) rectangle (229.08,229.08);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,171.00) rectangle (169.31,165.00);
\definecolor{fillColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,159.00) rectangle (169.31,153.00);
\definecolor{fillColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,147.00) rectangle (169.31,141.00);
\definecolor{fillColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,135.00) rectangle (169.31,129.00);
\definecolor{fillColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,123.00) rectangle (169.31,117.00);
\definecolor{fillColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,111.00) rectangle (169.31,105.00);
\definecolor{fillColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11, 99.00) rectangle (169.31, 93.00);
\definecolor{fillColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11, 87.00) rectangle (169.31, 81.00);
\definecolor{fillColor}{RGB}{68,68,68}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11, 75.00) rectangle (169.31, 69.00);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,164.56) {Ran};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,152.56) {Cognato};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,140.56) {Dornburg};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,128.56) {Sauquet};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,116.56) {Broughton};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,104.56) {Kawahara};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31, 92.56) {simulated};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31, 80.56) {Rightmyer};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31, 68.56) {Moyle};
\end{scope}
\end{tikzpicture}
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (289.08,289.08);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at (144.54,253.90) {\bfseries AVMVN+NER+Bactrian+adapt(\textit{real}) vs. cons(\textit{real})};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at (144.54, 14.40) {ESS/$10^6$ states [cons(\textit{real})]};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at ( 21.60,144.54) {ESS/$10^6$ states [AVMVN+NER+Bactrian+adapt(\textit{real})]};
\end{scope}
\begin{scope}
\path[clip] ( 60.00, 60.00) rectangle (229.08,229.08);
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (  0.00,101.80) --
	(187.28,289.08);

\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (285.44,289.08) --
	(285.44,183.64) --
	(101.80,  0.00);
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (  0.00, 67.86) --
	(221.22,289.08);

\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (285.44,289.08) --
	(285.44,217.58) --
	( 67.86,  0.00);
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (  0.00, 33.93) --
	(255.15,289.08);

\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (285.44,289.08) --
	(285.44,251.51) --
	( 33.93,  0.00);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (170.87, 64.13) {$\frac{1}{64} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,175.57) {$64\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (136.94, 64.13) {$\frac{1}{16} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,141.64) {$16\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (101.01, 64.13) {$\frac{1}{4} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 62.56,107.71) {$4\times$};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 60.00, 60.00) -- (229.08,229.08);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (113.37,176.23) --
	(123.12,176.23);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (118.73,174.41) --
	(118.73,177.92);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (118.73,172.34) {$p$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.81,162.66) --
	(176.28,162.66);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.61,161.37) --
	(174.61,163.88);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (174.61,157.80) {$L$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.21,178.79) --
	(180.37,178.79);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.31,177.78) --
	(179.31,179.76);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (179.31,173.93) {$r$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (131.04,146.84) --
	(140.36,146.84);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (136.14,145.03) --
	(136.14,148.53);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (136.14,141.98) {$l$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 87.76,170.79) --
	( 95.01,170.79);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 91.65,168.73) --
	( 91.65,172.69);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 91.65,167.29) {$\sigma$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.62,181.75) --
	(186.28,181.75);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.95,181.29) --
	(185.95,182.19);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (185.95,178.25) {$\kappa$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.35,183.23) --
	(175.77,183.23);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.59,182.63) --
	(174.59,183.81);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (174.59,179.34) {$p$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.08,185.46) --
	(182.02,185.46);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.59,184.16) --
	(180.59,186.69);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (180.59,180.60) {$L$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.09,191.41) --
	(183.39,191.41);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.24,191.26) --
	(183.24,191.56);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (183.24,186.55) {$r$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.97,175.46) --
	(164.02,175.46);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (163.01,174.36) --
	(163.01,176.51);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (163.01,170.60) {$l$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.57,185.09) --
	(164.37,185.09);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (163.01,184.25) --
	(163.01,185.90);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (163.01,181.59) {$\sigma$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.65,187.48) --
	(187.64,187.48);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.15,186.93) --
	(187.15,188.01);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (187.15,183.98) {$\kappa$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (136.36,156.88) --
	(145.35,156.88);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (141.26,155.53) --
	(141.26,158.17);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (141.26,152.99) {$p$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.54,188.93) --
	(183.90,188.93);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.75,188.26) --
	(182.75,189.59);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (182.75,184.07) {$L$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.72,192.48) --
	(185.16,192.48);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.94,192.24) --
	(184.94,192.72);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (184.94,187.62) {$r$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (116.65,143.01) --
	(121.72,143.01);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (119.32,140.92) --
	(119.32,144.93);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (119.32,138.15) {$l$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (129.42,153.61) --
	(137.45,153.61);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (133.77,152.17) --
	(133.77,154.96);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (133.77,150.11) {$\sigma$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.03,189.79) --
	(189.75,189.79);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.39,189.49) --
	(189.39,190.09);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (189.39,186.29) {$\kappa$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (147.58,166.10) --
	(151.24,166.10);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.48,165.61) --
	(149.48,166.58);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (149.48,162.21) {$p$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.56,188.13) --
	(183.73,188.13);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.67,187.38) --
	(182.67,188.87);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (182.67,183.27) {$L$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.76,188.08) --
	(181.98,188.08);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.87,187.92) --
	(181.87,188.24);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (181.87,183.22) {$r$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (145.93,157.79) --
	(149.06,157.79);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (147.54,156.95) --
	(147.54,158.60);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (147.54,152.93) {$l$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (137.22,160.83) --
	(140.84,160.83);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (139.10,159.54) --
	(139.10,162.06);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (139.10,157.33) {$\sigma$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.78,189.83) --
	(190.34,189.83);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.07,189.51) --
	(190.07,190.15);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (190.07,186.34) {$\kappa$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (132.78,175.20) --
	(141.58,175.20);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (137.57,173.42) --
	(137.57,176.85);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (137.57,171.31) {$p$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (177.13,177.06) --
	(178.12,177.06);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (177.63,176.01) --
	(177.63,178.06);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (177.63,172.20) {$L$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.82,182.51) --
	(179.53,182.51);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.18,182.11) --
	(179.18,182.91);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (179.18,177.65) {$r$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (127.95,138.26) --
	(132.53,138.26);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (130.34,136.14) --
	(130.34,140.21);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (130.34,133.40) {$l$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (105.15,159.54) --
	(113.88,159.54);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (109.90,158.03) --
	(109.90,160.96);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (109.90,156.04) {$\sigma$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.73,187.47) --
	(187.47,187.47);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.10,187.20) --
	(187.10,187.74);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (187.10,183.97) {$\kappa$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.40,162.64) --
	(156.80,162.64);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (154.25,157.19) --
	(154.25,167.10);
\definecolor{drawColor}{RGB}{0,216,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (154.25,158.76) {$p$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.38,184.48) --
	(173.21,184.48);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.37,182.64) --
	(171.37,186.19);
\definecolor{drawColor}{RGB}{0,216,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (171.37,179.62) {$L$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.89,201.51) --
	(181.32,201.51);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.11,201.37) --
	(181.11,201.64);
\definecolor{drawColor}{RGB}{0,216,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (181.11,196.65) {$r$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.99,184.01) --
	(164.25,184.01);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (163.15,182.98) --
	(163.15,185.00);
\definecolor{drawColor}{RGB}{0,216,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (163.15,179.15) {$l$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.64,167.13) --
	(155.42,167.13);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (154.07,165.25) --
	(154.07,168.88);
\definecolor{drawColor}{RGB}{0,216,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (154.07,163.63) {$\sigma$};
\definecolor{drawColor}{RGB}{0,216,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.58,189.13) --
	(189.63,189.13);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.11,188.65) --
	(189.11,189.59);
\definecolor{drawColor}{RGB}{0,216,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (189.11,185.63) {$\kappa$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.40,180.56) --
	(173.37,180.56);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.46,179.48) --
	(171.46,181.61);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (171.46,176.68) {$p$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.93,185.82) --
	(180.13,185.82);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.54,185.18) --
	(179.54,186.44);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (179.54,180.96) {$L$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.70,187.14) --
	(182.02,187.14);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.86,186.92) --
	(181.86,187.35);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (181.86,182.28) {$r$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (138.51,144.38) --
	(141.76,144.38);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (140.19,142.61) --
	(140.19,146.03);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (140.19,139.52) {$l$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (141.57,161.01) --
	(144.79,161.01);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (143.23,159.33) --
	(143.23,162.58);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (143.23,157.51) {$\sigma$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.73,190.27) --
	(191.12,190.27);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.95,189.56) --
	(189.95,190.97);
\definecolor{drawColor}{RGB}{151,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (189.95,186.78) {$\kappa$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.69,164.84) --
	(154.83,164.84);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (153.79,163.54) --
	(153.79,166.06);
\definecolor{drawColor}{RGB}{255,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (153.79,160.95) {$p$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (157.74,167.56) --
	(164.16,167.56);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.16,162.65) --
	(161.16,171.64);
\definecolor{drawColor}{RGB}{255,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (161.16,162.70) {$L$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.02,176.63) --
	(164.48,176.63);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.25,176.41) --
	(164.25,176.84);
\definecolor{drawColor}{RGB}{255,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (164.25,171.77) {$r$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (138.68,157.74) --
	(145.44,157.74);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (142.29,155.82) --
	(142.29,159.52);
\definecolor{drawColor}{RGB}{255,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (142.29,152.88) {$l$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (144.06,164.24) --
	(146.33,164.24);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (145.22,162.53) --
	(145.22,165.84);
\definecolor{drawColor}{RGB}{255,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (145.22,160.75) {$\sigma$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.00,187.63) --
	(187.88,187.63);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.44,186.85) --
	(187.44,188.39);
\definecolor{drawColor}{RGB}{255,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (187.44,184.13) {$\kappa$};
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.77,163.30) --
	(153.87,163.30);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.37,161.73) --
	(152.37,164.78);
\definecolor{drawColor}{RGB}{68,68,68}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (152.37,159.41) {$p$};
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (147.08,156.47) --
	(151.98,156.47);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.66,154.55) --
	(149.66,158.25);
\definecolor{drawColor}{RGB}{68,68,68}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (149.66,151.61) {$L$};
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.67,178.21) --
	(165.05,178.21);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.86,178.02) --
	(164.86,178.40);
\definecolor{drawColor}{RGB}{68,68,68}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (164.86,173.35) {$r$};
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.56,177.88) --
	(152.10,177.88);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.86,177.07) --
	(150.86,178.66);
\definecolor{drawColor}{RGB}{68,68,68}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (150.86,173.02) {$l$};
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (146.99,166.68) --
	(150.13,166.68);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (148.61,164.57) --
	(148.61,168.62);
\definecolor{drawColor}{RGB}{68,68,68}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (148.61,163.18) {$\sigma$};
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.86,189.91) --
	(190.66,189.91);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.26,189.34) --
	(190.26,190.47);
\definecolor{drawColor}{RGB}{68,68,68}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (190.26,186.41) {$\kappa$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- (229.08, 60.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- ( 60.00, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.39, 60.00) -- ( 99.39, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (116.36, 60.00) -- (116.36, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (155.75, 60.00) -- (155.75, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.72, 60.00) -- (172.72, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.11, 60.00) -- (212.11, 54.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.08, 60.00) -- (229.08, 54.00);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 60.00, 38.40) {1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 99.39, 38.40) {5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (116.36, 38.40) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (155.75, 38.40) {50};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (212.11, 38.40) {500};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- ( 60.00,229.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- ( 54.00, 60.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 99.39) -- ( 54.00, 99.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,116.36) -- ( 54.00,116.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,155.75) -- ( 54.00,155.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,172.72) -- ( 54.00,172.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,212.11) -- ( 54.00,212.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,229.08) -- ( 54.00,229.08);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00, 56.56) {1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00, 95.95) {5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,112.92) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,152.31) {50};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,169.28) {100};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,208.67) {500};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,225.64) {1000};
\end{scope}
\end{tikzpicture}

\end{document}

### 2020-08-29 benchmarking/render.R

@@ -11,7 +11,7 @@ PER_CHAIN = TRUE
 
 #settings = c("cat", "real", "quant", "bactrian95", "bactrian98")
 settings = c("cat",  "real_06", "quant_06", "real", "quant", "bactrian95", "bactrian98", "NER", "AVMN")
-settings = c("cat", "cat_adaptive",  "real_06", "real", "real_adaptive", "quant_06_cached", "quant_cached_adaptive", "quant_cached", "bactrian95", "NER")
+settings = c("cat", "cat_adaptive",  "real_06", "real", "real_adaptive", "quant_06_cached", "quant_cached_adaptive", "quant_cached", "bactrian95", "NER", "AVMVN")
 
 benchmark = data.frame(batch = numeric(0), param = character(0), dataset = character(0), partition = numeric(0), setting = character(0), nstates = numeric(0), finalESS = numeric(0), finalMCD = numeric(0), done = logical(0),  error = logical(0))
 
@@ -20,17 +20,18 @@ benchmark = data.frame(batch = numeric(0), param = character(0), dataset = chara
 
 settings.names = lapply(settings, function(x) x)
 settings.names["cat"] = "\\textit{cat}"
-settings.names["cat_adaptive"] = "adapt (\\textit{cat})"
+settings.names["cat_adaptive"] = "adapt(\\textit{cat})"
 
-settings.names["real"] = "cons (\\textit{real})"
-settings.names["real_06"] = "nocons (\\textit{real})"
-settings.names["real_adaptive"] = "adapt (\\textit{real})"
+settings.names["real"] = "cons(\\textit{real})"
+settings.names["real_06"] = "nocons(\\textit{real})"
+settings.names["real_adaptive"] = "adapt(\\textit{real})"
 
-settings.names["quant_cached"] = "cons (\\textit{quant})"
-settings.names["quant_06_cached"] = "nocons (\\textit{quant})"
-settings.names["quant_cached_adaptive"] = "adapt (\\textit{quant})"
-settings.names["bactrian95"] = "Bactrian (\\textit{real})"
-settings.names["NER"] = "NER (\\textit{real})"
+settings.names["quant_cached"] = "cons(\\textit{quant})"
[…]

### 2020-08-31 benchmarking/benchmarkingVM/ESS_round1_catquant.tex
Results update

--- 2020-08-26 benchmarking/benchmarkingVM/ESS_round1_catquant.tex
@@
-% Created by tikzDevice version 0.12.3.1 on 2020-08-25 15:33:04
+% Created by tikzDevice version 0.12.3.1 on 2020-08-31 17:26:11
 % !TEX encoding = UTF-8 Unicode
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,548.96) {\bfseries cons (\textit{quant}) vs. nocons (\textit{quant})};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,301.03) {ESS/hr [nocons (\textit{quant})]};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,433.62) {ESS/hr [cons (\textit{quant})]};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,548.96) {\bfseries cons(\textit{quant}) vs. nocons(\textit{quant})};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,301.03) {ESS/hr [nocons(\textit{quant})]};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,433.62) {ESS/hr [cons(\textit{quant})]};
 \end{scope}
@@
 \path[clip] ( 49.80,338.88) rectangle (239.28,528.36);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (  0.00,368.65) --
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (  0.00,368.65) --
 	(209.51,578.16);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (283.33,578.16) --
+\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (283.33,578.16) --
 	(283.33,492.84) --
 	(  0.00,209.51);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,342.13) --
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (  0.00,342.13) --
 	(236.03,578.16);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (283.33,578.16) --
+\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (283.33,578.16) --
 	(283.33,519.37) --
 	(  0.00,236.03);
-
-\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round] (  0.00,315.60) --
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (  0.00,315.60) --
 	(262.56,578.16);
 
-\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round] (283.33,578.16) --
+\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (283.33,578.16) --
 	(283.33,545.89) --
 	(  0.00,262.56);
+\definecolor{drawColor}{RGB}{0,0,0}
 
@@
 \node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92,376.84) {$4\times$};
+\definecolor{drawColor}{RGB}{105,105,105}
 
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 92.06,411.70) --
-	(103.71,411.70);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 98.76,408.30) --
-	( 98.76,414.58);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 98.76,408.47) {$p$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (127.75,461.51) --
-	(136.14,461.51);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (132.40,460.16) --
-	(132.40,462.77);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (132.40,457.48) {$L$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 86.72,453.05) --
-	( 91.82,453.05);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 89.44,452.87) --
-	( 89.44,453.23);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 89.44,449.02) {$r$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 86.78,407.42) --
-	( 95.88,407.42);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 91.87,400.23) --
-	( 91.87,412.63);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 91.87,403.39) {$h$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 53.22,385.02) --
-	( 67.16,385.02);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 61.43,375.09) --
-	( 61.43,391.53);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 61.43,382.12) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (170.05,459.14) --
-	(170.79,459.14);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (170.42,458.74) --
-	(170.42,459.52);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (170.42,456.23) {$\kappa$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.41,484.07) --
-	(203.29,484.07);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.75,480.26) --
-	(199.75,487.25);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.75,480.85) {$p$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.32,468.85) --
-	(182.12,468.85);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.02,464.40) --
-	(179.02,472.46);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.02,464.82) {$L$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (202.56,499.80) --
-	(209.12,499.80);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (206.12,496.65) --
-	(206.12,502.51);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (206.12,495.77) {$r$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.18,479.04) --
-	(195.29,479.04);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.66,476.43) --
-	(191.66,481.33);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.66,475.00) {$h$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (197.75,482.46) --
-	(204.87,482.46);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (201.64,479.93) --
-	(201.64,484.70);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (201.64,479.56) {$\sigma$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (207.07,499.42) --
-	(214.51,499.42);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.15,496.11) --
-	(211.15,502.24);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.15,496.51) {$\kappa$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (141.42,439.64) --
-	(145.39,439.64);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (143.51,437.79) --
-	(143.51,441.33);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (143.51,436.42) {$p$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.24,465.61) --
-	(175.56,465.61);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.52,463.95) --
-	(173.52,467.13);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.52,461.57) {$L$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.84,485.78) --
-	(195.64,485.78);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.76,485.39) --
-	(194.76,486.16);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.76,481.74) {$r$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (130.58,426.42) --
-	(135.71,426.42);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (133.32,424.17) --
-	(133.32,428.43);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (133.32,422.38) {$h$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.34,443.92) --
-	(161.79,443.92);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (156.91,440.58) --
-	(156.91,446.77);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (156.91,441.02) {$\sigma$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (197.72,485.55) --
-	(199.65,485.55);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.71,485.16) --
-	(198.71,485.94);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.71,482.65) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (159.25,461.02) --
-	(162.39,461.02);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (160.88,460.40) --
-	(160.88,461.62);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (160.88,457.79) {$p$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (162.17,460.73) --
-	(166.45,460.73);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.43,458.38) --
-	(164.43,462.82);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (164.43,456.70) {$L$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.93,485.98) --
-	(191.45,485.98);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.19,485.77) --
-	(191.19,486.19);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.19,481.95) {$r$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (147.67,456.98) --
-	(154.15,456.98);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.19,455.19) --
-	(151.19,458.61);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (151.19,452.94) {$h$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.17,453.18) --
-	(158.44,453.18);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (154.75,451.58) --
-	(154.75,454.65);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (154.75,450.27) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.83,488.43) --
-	(200.35,488.43);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (200.09,487.96) --
-	(200.09,488.88);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (200.09,485.52) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (119.54,419.45) --
-	(125.87,419.45);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (122.97,413.25) --
-	(122.97,424.13);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (122.97,416.23) {$p$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (156.29,461.77) --
-	(162.87,461.77);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (159.86,457.79) --
-	(159.86,465.07);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (159.86,457.74) {$L$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (154.77,462.26) --
-	(155.59,462.26);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (155.19,457.82) --
-	(155.19,465.86);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (155.19,458.22) {$r$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (111.36,420.07) --
-	(124.02,420.07);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (118.72,413.64) --
-	(118.72,424.87);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (118.72,416.04) {$h$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (125.89,409.29) --
-	(132.73,409.29);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (129.61,403.87) --
-	(129.61,413.52);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (129.61,406.39) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.91,467.12) --
-	(183.92,467.12);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.42,462.81) --
-	(183.42,470.64);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.42,464.22) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.12,483.47) --
-	(204.02,483.47);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (201.73,479.04) --
-	(201.73,487.06);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (201.73,480.24) {$p$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.89,472.43) --
-	(186.13,472.43);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.58,468.48) --
-	(184.58,475.70);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.58,468.39) {$L$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (210.72,493.14) --
-	(214.50,493.14);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (212.70,490.14) --
-	(212.70,495.73);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.70,489.11) {$r$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.99,463.39) --
-	(177.57,463.39);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.42,458.68) --
-	(175.42,467.17);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (175.42,459.36) {$h$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.79,473.24) --
-	(188.18,473.24);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.56,467.69) --
-	(186.56,477.54);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (186.56,470.34) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (202.34,492.07) --
-	(206.48,492.07);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (204.52,488.90) --
-	(204.52,494.79);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (204.52,489.16) {$\kappa$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (154.78,452.89) --
-	(160.59,452.89);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (157.90,450.01) --
-	(157.90,455.39);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (157.90,449.66) {$p$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.87,482.15) --
-	(200.95,482.15);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.93,480.40) --
-	(199.93,483.76);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.93,478.12) {$L$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.09,490.74) --
-	(188.57,490.74);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.37,490.40) --
-	(187.37,491.07);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.37,486.70) {$r$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (156.27,465.34) --
-	(163.66,465.34);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (160.32,463.67) --
-	(160.32,466.88);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (160.32,461.31) {$h$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (158.86,454.59) --
-	(164.47,454.59);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.87,453.07) --
-	(161.87,456.01);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (161.87,451.69) {$\sigma$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (203.38,492.98) --
-	(205.35,492.98);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (204.39,491.80) --
-	(204.39,494.09);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (204.39,490.07) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.62,458.20) --
-	(175.50,458.20);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.11,457.24) --
-	(174.11,459.12);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.11,454.97) {$p$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.11,449.29) --
-	(152.12,449.29);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.67,445.56) --
-	(150.67,452.41);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (150.67,445.26) {$L$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.33,471.24) --
-	(185.73,471.24);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.05,471.11) --
-	(185.05,471.37);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.05,467.21) {$r$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.22,445.85) --
-	(159.90,445.85);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (156.45,439.59) --
-	(156.45,450.57);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (156.45,441.82) {$h$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.57,455.90) --
-	(162.87,455.90);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (157.69,453.42) --
-	(157.69,458.09);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (157.69,452.99) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.38,485.12) --
-	(196.78,485.12);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.09,484.12) --
-	(196.09,486.06);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.09,482.21) {$\kappa$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.91,469.41) --
-	(194.38,469.41);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.19,468.77) --
-	(193.19,470.02);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.19,466.18) {$p$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.83,464.80) --
-	(184.74,464.80);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.88,462.76) --
-	(182.88,466.64);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.88,460.77) {$L$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.66,477.27) --
-	(198.99,477.27);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.95,477.03) --
-	(196.95,477.51);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.95,473.24) {$r$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (177.86,459.46) --
-	(182.29,459.46);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.20,458.11) --
-	(180.20,460.72);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.20,455.43) {$h$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.44,462.61) --
-	(188.89,462.61);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.79,461.80) --
-	(186.79,463.38);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (186.79,459.70) {$\sigma$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (205.09,492.28) --
-	(209.17,492.28);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (207.24,491.61) --
-	(207.24,492.93);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.24,489.37) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (202.85,487.92) --
+	(203.52,487.92);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (203.19,487.52) --
+	(203.19,488.31);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (203.19,484.69) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (213.88,498.22) --
+	(214.75,498.22);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (214.32,497.75) --
+	(214.32,498.68);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (214.32,495.32) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (208.51,502.46) --
+	(208.63,502.46);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (208.57,502.40) --
+	(208.57,502.51);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (208.57,498.42) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (198.87,483.08) --
+	(199.54,483.08);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (199.20,482.74) --
+	(199.20,483.41);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.20,480.17) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (200.58,485.24) --
+	(201.25,485.24);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (200.92,484.90) --
+	(200.92,485.57);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (200.92,481.20) {$l$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (202.85,484.76) --
+	(203.53,484.76);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (203.19,484.34) --
+	(203.19,485.17);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (203.19,481.86) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (213.60,502.14) --
+	(213.84,502.14);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (213.72,501.98) --
+	(213.72,502.29);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (213.72,499.23) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (147.47,446.68) --
+	(148.89,446.68);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (148.19,445.79) --
+	(148.19,447.53);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (148.19,443.45) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (203.71,488.48) --
+	(204.13,488.48);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (203.92,488.23) --
+	(203.92,488.73);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (203.92,485.58) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (200.49,492.12) --
+	(200.68,492.12);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (200.58,492.09) --
+	(200.58,492.16);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (200.58,488.09) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (141.94,439.96) --
+	(143.33,439.96);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (142.65,439.14) --
+	(142.65,440.75);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (142.65,437.06) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (144.03,442.75) --
+	(145.40,442.75);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (144.73,441.92) --
+	(144.73,443.56);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (144.73,438.72) {$l$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (163.36,453.61) --
+	(165.24,453.61);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (164.32,452.72) --
+	(164.32,454.46);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (164.32,450.71) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (203.54,491.89) --
+	(203.75,491.89);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (203.64,491.82) --
+	(203.64,491.97);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (203.64,488.99) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (159.69,460.73) --
+	(161.01,460.73);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (160.36,460.14) --
+	(160.36,461.31);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (160.36,457.51) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (202.82,486.84) --
+	(203.46,486.84);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (203.14,486.48) --
+	(203.14,487.19);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (203.14,483.93) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (194.57,488.60) --
+	(194.89,488.60);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (194.73,488.53) --
+	(194.73,488.67);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.73,484.56) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (155.28,458.37) --
+	(156.76,458.37);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (156.03,457.88) --
+	(156.03,458.86);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (156.03,455.47) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (158.01,460.12) --
+	(159.37,460.12);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (158.71,459.64) --
+	(158.71,460.59);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.71,456.09) {$l$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (162.76,457.73) --
+	(164.34,457.73);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (163.57,457.26) --
+	(163.57,458.19);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (163.57,454.83) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (202.97,491.19) --
+	(203.31,491.19);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (203.14,491.10) --
+	(203.14,491.27);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (203.14,488.28) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (127.56,426.45) --
+	(130.46,426.45);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (129.06,425.65) --
+	(129.06,427.21);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (129.06,423.22) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (185.11,469.37) --
+	(185.94,469.37);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (185.53,468.22) --
+	(185.53,470.46);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.53,466.47) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (158.31,469.19) --
+	(158.61,469.19);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (158.46,469.06) --
+	(158.46,469.32);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.46,465.16) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (126.07,427.08) --
+	(128.95,427.08);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (127.56,426.01) --
+	(127.56,428.09);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (127.56,424.17) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (126.96,427.07) --
+	(129.90,427.07);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (128.49,426.25) --
+	(128.49,427.85);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (128.49,423.04) {$l$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (129.24,415.67) --
+	(133.28,415.67);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (131.36,414.96) --
+	(131.36,416.36);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (131.36,412.77) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (186.71,474.31) --
+	(187.04,474.31);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (186.88,474.21) --
+	(186.88,474.40);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (186.88,471.40) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (202.99,484.20) --
+	(203.57,484.20);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (203.28,483.88) --
+	(203.28,484.52);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (203.28,480.98) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (208.88,489.56) --
+	(209.24,489.56);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (209.06,489.28) --
+	(209.06,489.83);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.06,486.65) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (218.03,498.02) --
+	(218.09,498.02);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (218.06,497.99) --
+	(218.06,498.06);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (218.06,493.99) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (194.86,475.48) --
+	(195.71,475.48);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (195.29,475.12) --
+	(195.29,475.84);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.29,472.58) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (200.72,482.40) --
+	(201.41,482.40);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (201.07,482.06) --
+	(201.07,482.74);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (201.07,478.37) {$l$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (193.35,477.75) --
+	(194.47,477.75);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (193.92,477.24) --
+	(193.92,478.25);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.92,474.85) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (209.99,497.02) --
+	(210.17,497.02);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (210.08,496.91) --
+	(210.08,497.12);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.08,494.11) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (166.57,459.35) --
+	(168.17,459.35);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (167.39,458.78) --
+	(167.39,459.90);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (167.39,456.12) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (215.97,496.38) --
+	(216.67,496.38);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (216.32,496.09) --
+	(216.32,496.67);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (216.32,493.48) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (197.46,498.08) --
+	(198.01,498.08);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (197.74,497.92) --
+	(197.74,498.23);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.74,494.04) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (165.11,458.03) --
+	(166.67,458.03);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (165.90,457.48) --
+	(165.90,458.56);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (165.90,455.13) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (166.96,459.93) --
+	(168.48,459.93);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (167.73,459.33) --
+	(167.73,460.51);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (167.73,455.90) {$l$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (172.54,463.17) --
+	(174.47,463.17);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (173.53,462.51) --
+	(173.53,463.80);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.53,460.26) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (214.25,501.66) --
+	(214.98,501.66);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (214.62,501.48) --
+	(214.62,501.84);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (214.62,498.76) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (177.43,461.34) --
+	(178.36,461.34);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (177.90,460.84) --
+	(177.90,461.83);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.90,458.11) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (188.18,473.35) --
+	(189.52,473.35);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (188.86,472.81) --
+	(188.86,473.87);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.86,470.44) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (191.84,476.83) --
+	(191.96,476.83);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (191.90,476.76) --
+	(191.90,476.90);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.90,472.80) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (178.74,458.52) --
+	(179.34,458.52);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (179.04,458.06) --
+	(179.04,458.96);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.04,455.61) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (176.19,460.22) --
+	(177.09,460.22);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (176.64,459.76) --
+	(176.64,460.68);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.64,456.19) {$l$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (179.97,462.52) --
+	(180.75,462.52);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (180.36,462.09) --
+	(180.36,462.94);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.36,459.62) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (202.15,490.39) --
+	(202.43,490.39);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (202.29,490.22) --
+	(202.29,490.56);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.29,487.49) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (198.72,476.32) --
+	(199.21,476.32);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (198.97,476.00) --
+	(198.97,476.64);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.97,473.10) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (186.89,471.92) --
+	(187.71,471.92);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (187.31,471.34) --
+	(187.31,472.48);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.31,469.01) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (203.12,485.97) --
+	(203.22,485.97);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (203.17,485.90) --
+	(203.17,486.03);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (203.17,481.93) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (192.95,469.97) --
+	(193.53,469.97);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (193.24,469.65) --
+	(193.24,470.29);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.24,467.07) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (198.73,476.08) --
+	(199.11,476.08);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (198.92,475.74) --
+	(198.92,476.42);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.92,472.05) {$l$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (191.83,472.12) --
+	(192.70,472.12);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (192.27,471.75) --
+	(192.27,472.48);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.27,469.21) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (214.50,501.05) --
+	(214.82,501.05);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (214.66,500.92) --
+	(214.66,501.17);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (214.66,498.14) {$\kappa$};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,431.01) rectangle (189.67,426.03);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,421.05) rectangle (189.67,416.07);
 \definecolor{fillColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,421.05) rectangle (189.67,416.07);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,411.09) rectangle (189.67,406.11);
 \definecolor{fillColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,411.09) rectangle (189.67,406.11);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,401.13) rectangle (189.67,396.15);
 \definecolor{fillColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,401.13) rectangle (189.67,396.15);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,391.17) rectangle (189.67,386.19);
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,391.17) rectangle (189.67,386.19);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,381.21) rectangle (189.67,376.23);
 \definecolor{fillColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,381.21) rectangle (189.67,376.23);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,371.25) rectangle (189.67,366.27);
 \definecolor{fillColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,371.25) rectangle (189.67,366.27);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,361.29) rectangle (189.67,356.31);
 \definecolor{fillColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,361.29) rectangle (189.67,356.31);
-\definecolor{fillColor}{RGB}{68,68,68}
-
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,351.33) rectangle (189.67,346.35);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,425.66) {Ran};
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,548.96) {\bfseries adapt (\textit{quant}) vs. nocons (\textit{quant})};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,301.03) {ESS/hr [nocons (\textit{quant})]};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (307.01,433.62) {ESS/hr [adapt (\textit{quant})]};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,548.96) {\bfseries adapt(\textit{quant}) vs. nocons(\textit{quant})};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,301.03) {ESS/hr [nocons(\textit{quant})]};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (307.01,433.62) {ESS/hr [adapt(\textit{quant})]};
 \end{scope}
@@
 \path[clip] (338.88,338.88) rectangle (528.36,528.36);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (162.66,242.23) --
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (162.66,242.23) --
 	(498.59,578.16);
 
-\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (572.41,578.16) --
+\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (572.41,578.16) --
 	(572.41,492.84) --
@@
 	(162.66,242.23);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.66,215.71) --
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (162.66,215.71) --
 	(525.11,578.16);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (572.41,578.16) --
+\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (572.41,578.16) --
 	(572.41,519.37) --
@@
 	(162.66,215.71);
-
-\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round] (162.66,189.19) --
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (162.66,189.19) --
 	(551.64,578.16);
 
-\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round] (572.41,578.16) --
+\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (572.41,578.16) --
 	(572.41,545.89) --
@@
 	(162.66,189.19);
+\definecolor{drawColor}{RGB}{0,0,0}
 
@@
 \node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.00,376.84) {$4\times$};
+\definecolor{drawColor}{RGB}{105,105,105}
 
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (381.14,422.82) --
-	(392.79,422.82);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (387.84,420.40) --
-	(387.84,424.97);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (387.84,419.59) {$p$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (416.83,452.57) --
-	(425.22,452.57);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (421.48,451.90) --
-	(421.48,453.22);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (421.48,448.54) {$L$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (375.80,446.67) --
-	(380.90,446.67);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (378.52,445.22) --
-	(378.52,448.02);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (378.52,442.64) {$r$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (375.86,418.52) --
-	(384.96,418.52);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (380.95,411.75) --
-	(380.95,423.52);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (380.95,414.49) {$h$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (342.30,430.80) --
-	(356.24,430.80);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (350.51,426.42) --
-	(350.51,434.36);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (350.51,427.90) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (459.13,451.20) --
-	(459.87,451.20);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (459.50,449.83) --
-	(459.50,452.49);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (459.50,448.30) {$\kappa$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (484.49,486.05) --
-	(492.37,486.05);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (488.83,480.97) --
-	(488.83,490.06);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (488.83,482.83) {$p$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (464.40,467.41) --
-	(471.20,467.41);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (468.10,463.99) --
-	(468.10,470.31);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.10,463.37) {$L$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (491.64,498.84) --
-	(498.20,498.84);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (495.20,495.08) --
-	(495.20,501.97);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (495.20,494.80) {$r$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (476.26,480.02) --
-	(484.37,480.02);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.74,475.53) --
-	(480.74,483.64);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (480.74,475.98) {$h$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (486.83,495.85) --
-	(493.95,495.85);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (490.72,490.38) --
-	(490.72,500.09);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (490.72,492.94) {$\sigma$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (496.15,497.26) --
-	(503.59,497.26);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (500.23,493.73) --
-	(500.23,500.23);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (500.23,494.35) {$\kappa$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (430.50,444.25) --
-	(434.47,444.25);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (432.59,439.52) --
-	(432.59,448.04);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (432.59,441.02) {$p$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (460.32,464.46) --
-	(464.64,464.46);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (462.60,463.55) --
-	(462.60,465.34);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (462.60,460.43) {$L$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (482.92,486.64) --
-	(484.72,486.64);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.84,486.09) --
-	(483.84,487.17);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.84,482.60) {$r$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (419.66,430.01) --
-	(424.79,430.01);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (422.40,424.45) --
-	(422.40,434.32);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (422.40,425.98) {$h$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (439.42,453.02) --
-	(450.87,453.02);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (445.99,448.90) --
-	(445.99,456.41);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (445.99,450.12) {$\sigma$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (486.80,484.52) --
-	(488.73,484.52);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (487.79,483.75) --
-	(487.79,485.27);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (487.79,481.62) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (448.33,455.28) --
-	(451.47,455.28);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (449.96,453.50) --
-	(449.96,456.90);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (449.96,452.05) {$p$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (451.25,455.59) --
-	(455.53,455.59);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (453.51,453.77) --
-	(453.51,457.25);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (453.51,451.56) {$L$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.01,481.09) --
-	(480.53,481.09);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.27,480.69) --
-	(480.27,481.49);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (480.27,477.06) {$r$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (436.75,455.34) --
-	(443.23,455.34);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (440.27,453.12) --
-	(440.27,457.33);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (440.27,451.30) {$h$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (439.25,459.26) --
-	(447.52,459.26);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (443.83,456.93) --
-	(443.83,461.33);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (443.83,456.35) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (488.91,482.35) --
-	(489.43,482.35);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (489.17,481.98) --
-	(489.17,482.72);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (489.17,479.45) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (408.62,419.90) --
-	(414.95,419.90);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (412.05,418.40) --
-	(412.05,421.29);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (412.05,416.67) {$p$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (445.37,458.29) --
-	(451.95,458.29);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (448.94,456.11) --
-	(448.94,460.25);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (448.94,454.26) {$L$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (443.85,457.12) --
-	(444.67,457.12);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (444.27,456.64) --
-	(444.27,457.60);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (444.27,453.09) {$r$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (400.44,419.27) --
-	(413.10,419.27);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (407.80,417.46) --
-	(407.80,420.93);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (407.80,415.24) {$h$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (414.97,431.53) --
-	(421.81,431.53);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (418.69,428.40) --
-	(418.69,434.22);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (418.69,428.63) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (471.99,463.25) --
-	(473.00,463.25);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (472.50,463.00) --
-	(472.50,463.51);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (472.50,460.35) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (488.20,491.43) --
-	(493.10,491.43);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (490.81,488.34) --
-	(490.81,494.10);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (490.81,488.21) {$p$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (471.97,473.26) --
-	(475.21,473.26);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (473.66,469.46) --
-	(473.66,476.43);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (473.66,469.23) {$L$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (499.80,500.72) --
-	(503.58,500.72);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (501.78,497.68) --
-	(501.78,503.35);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (501.78,496.69) {$r$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (462.07,462.90) --
-	(466.65,462.90);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (464.50,459.58) --
-	(464.50,465.73);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (464.50,458.87) {$h$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (473.87,477.19) --
-	(477.26,477.19);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (475.64,474.02) --
-	(475.64,479.91);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (475.64,474.29) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (491.42,491.09) --
-	(495.56,491.09);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (493.60,488.28) --
-	(493.60,493.53);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (493.60,488.18) {$\kappa$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (443.86,453.47) --
-	(449.67,453.47);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (446.98,449.31) --
-	(446.98,456.88);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (446.98,450.24) {$p$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (487.95,485.02) --
-	(490.03,485.02);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (489.01,483.20) --
-	(489.01,486.68);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (489.01,480.99) {$L$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (475.17,489.36) --
-	(477.65,489.36);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (476.45,488.95) --
-	(476.45,489.76);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (476.45,485.33) {$r$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (445.35,461.95) --
-	(452.74,461.95);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (449.40,456.35) --
-	(449.40,466.27);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (449.40,457.91) {$h$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (447.94,466.97) --
-	(453.55,466.97);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (450.95,463.63) --
-	(450.95,469.80);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (450.95,464.06) {$\sigma$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (492.46,491.31) --
-	(494.43,491.31);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (493.47,489.94) --
-	(493.47,492.58);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (493.47,488.40) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (461.70,458.77) --
-	(464.58,458.77);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (463.19,456.24) --
-	(463.19,461.00);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (463.19,455.54) {$p$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (438.19,441.13) --
-	(441.20,441.13);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (439.75,438.18) --
-	(439.75,443.68);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (439.75,437.10) {$L$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (473.41,472.82) --
-	(474.81,472.82);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (474.13,472.59) --
-	(474.13,473.05);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.13,468.79) {$r$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (441.30,443.82) --
-	(448.98,443.82);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (445.53,439.42) --
-	(445.53,447.40);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (445.53,439.79) {$h$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (439.65,458.10) --
-	(451.95,458.10);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (446.77,453.81) --
-	(446.77,461.61);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (446.77,455.20) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (484.46,481.91) --
-	(485.86,481.91);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (485.17,481.83) --
-	(485.17,481.99);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (485.17,479.00) {$\kappa$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.99,478.97) --
-	(483.46,478.97);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (482.27,467.29) --
-	(482.27,486.16);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (482.27,475.74) {$p$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (469.91,465.38) --
-	(473.82,465.38);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (471.96,453.39) --
-	(471.96,472.69);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (471.96,461.35) {$L$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.74,482.47) --
-	(488.07,482.47);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (486.03,470.56) --
-	(486.03,489.76);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (486.03,478.44) {$r$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (466.94,464.45) --
-	(471.37,464.45);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (469.28,451.93) --
-	(469.28,471.95);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (469.28,460.42) {$h$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (473.52,474.07) --
-	(477.97,474.07);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (475.87,462.11) --
-	(475.87,481.38);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (475.87,471.17) {$\sigma$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (494.17,491.37) --
-	(498.25,491.37);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (496.32,479.32) --
-	(496.32,498.71);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (496.32,488.47) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (491.93,489.87) --
+	(492.60,489.87);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (492.27,489.57) --
+	(492.27,490.16);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (492.27,486.64) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (502.96,499.95) --
+	(503.83,499.95);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (503.40,499.66) --
+	(503.40,500.24);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (503.40,497.05) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (497.59,501.75) --
+	(497.71,501.75);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (497.65,501.69) --
+	(497.65,501.80);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (497.65,497.71) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (487.95,485.79) --
+	(488.62,485.79);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (488.28,485.54) --
+	(488.28,486.03);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (488.28,482.88) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (489.66,487.50) --
+	(490.33,487.50);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (490.00,487.21) --
+	(490.00,487.80);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (490.00,483.47) {$l$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (491.93,499.04) --
+	(492.61,499.04);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (492.27,498.77) --
+	(492.27,499.32);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (492.27,496.14) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (502.68,500.55) --
+	(502.92,500.55);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (502.80,500.44) --
+	(502.80,500.66);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (502.80,497.65) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (436.55,451.79) --
+	(437.97,451.79);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (437.27,451.27) --
+	(437.27,452.29);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (437.27,448.56) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (492.79,489.99) --
+	(493.21,489.99);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (493.00,489.81) --
+	(493.00,490.18);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (493.00,487.09) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (489.57,492.80) --
+	(489.76,492.80);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (489.66,492.74) --
+	(489.66,492.85);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (489.66,488.76) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (431.02,445.43) --
+	(432.41,445.43);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (431.73,444.89) --
+	(431.73,445.95);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (431.73,442.52) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (433.11,448.01) --
+	(434.48,448.01);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (433.81,447.49) --
+	(433.81,448.51);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (433.81,443.97) {$l$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (452.44,462.20) --
+	(454.32,462.20);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (453.40,461.65) --
+	(453.40,462.73);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (453.40,459.29) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (492.62,490.73) --
+	(492.83,490.73);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (492.72,490.65) --
+	(492.72,490.82);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (492.72,487.83) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (448.77,464.66) --
+	(450.09,464.66);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (449.44,464.12) --
+	(449.44,465.18);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (449.44,461.43) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (491.90,489.34) --
+	(492.54,489.34);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (492.22,489.09) --
+	(492.22,489.58);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (492.22,486.43) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (483.65,489.35) --
+	(483.97,489.35);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (483.81,489.15) --
+	(483.81,489.55);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.81,485.32) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (444.36,461.69) --
+	(445.84,461.69);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (445.11,461.16) --
+	(445.11,462.22);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (445.11,458.79) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (447.09,463.55) --
+	(448.45,463.55);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (447.79,463.00) --
+	(447.79,464.08);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (447.79,459.51) {$l$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (451.84,470.31) --
+	(453.42,470.31);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (452.65,469.79) --
+	(452.65,470.82);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (452.65,467.41) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (492.05,490.35) --
+	(492.39,490.35);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (492.22,490.11) --
+	(492.22,490.60);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (492.22,487.45) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (416.64,427.41) --
+	(419.54,427.41);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (418.14,426.32) --
+	(418.14,428.45);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (418.14,424.19) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (474.19,462.41) --
+	(475.02,462.41);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (474.61,461.74) --
+	(474.61,463.06);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.61,459.50) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (447.39,467.41) --
+	(447.69,467.41);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (447.54,467.24) --
+	(447.54,467.58);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (447.54,463.38) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (415.15,426.94) --
+	(418.03,426.94);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (416.64,425.89) --
+	(416.64,427.93);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (416.64,424.03) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (416.04,427.14) --
+	(418.98,427.14);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (417.57,426.01) --
+	(417.57,428.20);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (417.57,423.11) {$l$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (418.32,441.14) --
+	(422.36,441.14);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (420.44,439.81) --
+	(420.44,442.38);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (420.44,438.23) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (475.79,473.14) --
+	(476.12,473.14);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (475.96,472.98) --
+	(475.96,473.30);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (475.96,470.24) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (492.07,491.90) --
+	(492.65,491.90);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (492.36,491.57) --
+	(492.36,492.23);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (492.36,488.68) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (497.96,494.94) --
+	(498.32,494.94);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (498.14,494.63) --
+	(498.14,495.24);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (498.14,492.04) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (507.11,505.18) --
+	(507.17,505.18);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (507.14,505.15) --
+	(507.14,505.21);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (507.14,501.15) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (483.94,485.14) --
+	(484.79,485.14);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (484.37,484.76) --
+	(484.37,485.50);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (484.37,482.23) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (489.80,490.54) --
+	(490.49,490.54);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (490.15,490.21) --
+	(490.15,490.85);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (490.15,486.50) {$l$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (482.43,483.52) --
+	(483.55,483.52);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (483.00,483.11) --
+	(483.00,483.93);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.00,480.62) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (499.07,495.41) --
+	(499.25,495.41);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (499.16,495.32) --
+	(499.16,495.49);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (499.16,492.50) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (455.65,459.08) --
+	(457.25,459.08);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (456.47,458.35) --
+	(456.47,459.79);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (456.47,455.85) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (505.05,495.76) --
+	(505.75,495.76);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (505.40,495.49) --
+	(505.40,496.03);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (505.40,492.85) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (486.54,496.08) --
+	(487.09,496.08);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (486.82,495.98) --
+	(486.82,496.19);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (486.82,492.05) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (454.19,457.54) --
+	(455.75,457.54);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (454.98,456.85) --
+	(454.98,458.21);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (454.98,454.64) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (456.04,459.53) --
+	(457.56,459.53);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (456.81,458.82) --
+	(456.81,460.21);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (456.81,455.50) {$l$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (461.62,474.65) --
+	(463.55,474.65);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (462.61,473.94) --
+	(462.61,475.33);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (462.61,471.74) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (503.33,498.52) --
+	(504.06,498.52);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (503.70,498.30) --
+	(503.70,498.73);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (503.70,495.61) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (466.51,466.02) --
+	(467.44,466.02);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (466.98,465.37) --
+	(466.98,466.64);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (466.98,462.79) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (477.26,476.12) --
+	(478.60,476.12);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (477.94,475.44) --
+	(477.94,476.77);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (477.94,473.22) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (480.92,480.75) --
+	(481.04,480.75);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (480.98,480.67) --
+	(480.98,480.84);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (480.98,476.72) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (467.82,466.41) --
+	(468.42,466.41);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (468.12,466.01) --
+	(468.12,466.81);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.12,463.51) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (465.27,464.95) --
+	(466.17,464.95);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (465.72,464.33) --
+	(465.72,465.56);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (465.72,460.92) {$l$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (469.05,472.46) --
+	(469.83,472.46);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (469.44,471.96) --
+	(469.44,472.95);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (469.44,469.56) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (491.23,489.31) --
+	(491.51,489.31);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (491.37,489.19) --
+	(491.37,489.43);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (491.37,486.41) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (487.80,486.27) --
+	(488.29,486.27);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (488.05,486.05) --
+	(488.05,486.50);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (488.05,483.05) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (475.97,473.16) --
+	(476.79,473.16);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (476.39,472.60) --
+	(476.39,473.70);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (476.39,470.25) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (492.20,490.92) --
+	(492.30,490.92);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (492.25,490.86) --
+	(492.25,490.98);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (492.25,486.89) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (482.03,480.77) --
+	(482.61,480.77);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (482.32,480.54) --
+	(482.32,481.00);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (482.32,477.86) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (487.81,486.02) --
+	(488.19,486.02);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (488.00,485.79) --
+	(488.00,486.26);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (488.00,481.99) {$l$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (480.91,481.81) --
+	(481.78,481.81);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (481.35,481.42) --
+	(481.35,482.20);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (481.35,478.91) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (503.58,499.85) --
+	(503.90,499.85);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (503.74,499.72) --
+	(503.74,499.97);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (503.74,496.94) {$\kappa$};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,259.88) {\bfseries adapt (\textit{quant}) vs. cons (\textit{quant})};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54, 11.95) {ESS/hr [cons (\textit{quant})]};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,144.54) {ESS/hr [adapt (\textit{quant})]};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,259.88) {\bfseries adapt(\textit{quant}) vs. cons(\textit{quant})};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54, 11.95) {ESS/hr [cons(\textit{quant})]};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,144.54) {ESS/hr [adapt(\textit{quant})]};
 \end{scope}
@@
 \path[clip] ( 49.80, 49.80) rectangle (239.28,239.28);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (  0.00, 79.57) --
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (  0.00, 79.57) --
 	(283.33,362.91) --
@@
 	( 79.57,  0.00);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00, 53.05) --
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (  0.00, 53.05) --
 	(283.33,336.38) --
@@
 	( 53.05,  0.00);
-
-\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round] (  0.00, 26.52) --
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (  0.00, 26.52) --
 	(283.33,309.86) --
@@
 	( 26.52,  0.00);
+\definecolor{drawColor}{RGB}{0,0,0}
 
@@
 \node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92, 87.76) {$4\times$};
+\definecolor{drawColor}{RGB}{105,105,105}
 
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (119.22,133.74) --
-	(125.50,133.74);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (122.62,131.32) --
-	(122.62,135.89);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (122.62,130.51) {$p$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.08,163.49) --
-	(173.69,163.49);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.43,162.82) --
-	(172.43,164.14);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.43,159.46) {$L$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (163.79,157.59) --
-	(164.15,157.59);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (163.97,156.14) --
-	(163.97,158.94);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (163.97,153.56) {$r$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (111.15,129.44) --
-	(123.55,129.44);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (118.34,122.67) --
-	(118.34,134.44);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (118.34,125.41) {$h$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 86.01,141.72) --
-	(102.45,141.72);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 95.94,137.34) --
-	( 95.94,145.28);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 95.94,138.82) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.66,162.12) --
-	(170.44,162.12);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (170.06,160.75) --
-	(170.06,163.41);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (170.06,159.22) {$\kappa$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.18,196.97) --
-	(198.17,196.97);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.99,191.89) --
-	(194.99,200.98);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.99,193.75) {$p$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.32,178.33) --
-	(183.38,178.33);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.77,174.91) --
-	(179.77,181.23);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.77,174.29) {$L$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (207.57,209.76) --
-	(213.43,209.76);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (210.72,206.00) --
-	(210.72,212.89);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.72,205.72) {$r$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.35,190.94) --
-	(192.25,190.94);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.96,186.45) --
-	(189.96,194.56);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (189.96,186.90) {$h$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.85,206.77) --
-	(195.62,206.77);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.38,201.30) --
-	(193.38,211.01);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.38,203.86) {$\sigma$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (207.03,208.18) --
-	(213.16,208.18);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (210.34,204.65) --
-	(210.34,211.15);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.34,205.27) {$\kappa$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (148.71,155.17) --
-	(152.25,155.17);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.56,150.44) --
-	(150.56,158.96);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (150.56,151.94) {$p$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.87,175.38) --
-	(178.05,175.38);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.53,174.47) --
-	(176.53,176.26);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.53,171.35) {$L$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.31,197.56) --
-	(197.08,197.56);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.70,197.01) --
-	(196.70,198.09);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.70,193.52) {$r$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (135.09,140.93) --
-	(139.35,140.93);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (137.34,135.37) --
-	(137.34,145.24);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (137.34,136.90) {$h$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.50,163.94) --
-	(157.69,163.94);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (154.84,159.82) --
-	(154.84,167.33);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (154.84,161.04) {$\sigma$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.08,195.44) --
-	(196.86,195.44);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.47,194.67) --
-	(196.47,196.19);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.47,192.54) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.32,166.20) --
-	(172.54,166.20);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.94,164.42) --
-	(171.94,167.82);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.94,162.97) {$p$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.30,166.51) --
-	(173.74,166.51);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.65,164.69) --
-	(171.65,168.17);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.65,162.48) {$L$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.69,192.01) --
-	(197.11,192.01);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.90,191.61) --
-	(196.90,192.41);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.90,187.98) {$r$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (166.11,166.26) --
-	(169.53,166.26);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (167.90,164.04) --
-	(167.90,168.25);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (167.90,162.22) {$h$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (162.50,170.18) --
-	(165.57,170.18);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.10,167.85) --
-	(164.10,172.25);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (164.10,167.27) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.88,193.27) --
-	(199.80,193.27);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.35,192.90) --
-	(199.35,193.64);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.35,190.37) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (124.17,130.82) --
-	(135.05,130.82);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (130.37,129.32) --
-	(130.37,132.21);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (130.37,127.59) {$p$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.71,169.21) --
-	(175.99,169.21);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.69,167.03) --
-	(172.69,171.17);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.69,165.18) {$L$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.74,168.04) --
-	(176.78,168.04);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.18,167.56) --
-	(173.18,168.52);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.18,164.01) {$r$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (124.56,130.19) --
-	(135.79,130.19);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (130.99,128.38) --
-	(130.99,131.85);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (130.99,126.16) {$h$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (114.79,142.45) --
-	(124.44,142.45);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (120.21,139.32) --
-	(120.21,145.14);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (120.21,139.55) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.73,174.17) --
-	(181.56,174.17);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.04,173.92) --
-	(178.04,174.43);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (178.04,171.27) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.96,202.35) --
-	(197.98,202.35);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.39,199.26) --
-	(194.39,205.02);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.39,199.13) {$p$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.40,184.18) --
-	(186.62,184.18);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.35,180.38) --
-	(183.35,187.35);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.35,180.15) {$L$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (201.06,211.64) --
-	(206.65,211.64);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (204.06,208.60) --
-	(204.06,214.27);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (204.06,207.61) {$r$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.60,173.82) --
-	(178.09,173.82);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.31,170.50) --
-	(174.31,176.65);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.31,169.79) {$h$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.61,188.11) --
-	(188.46,188.11);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.16,184.94) --
-	(184.16,190.83);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.16,185.21) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.82,202.01) --
-	(205.71,202.01);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (202.99,199.20) --
-	(202.99,204.45);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.99,199.10) {$\kappa$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (160.93,164.39) --
-	(166.31,164.39);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (163.81,160.23) --
-	(163.81,167.80);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (163.81,161.16) {$p$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.32,195.94) --
-	(194.68,195.94);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.07,194.12) --
-	(193.07,197.60);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.07,191.91) {$L$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (201.32,200.28) --
-	(201.99,200.28);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (201.66,199.87) --
-	(201.66,200.68);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (201.66,196.25) {$r$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.59,172.87) --
-	(177.80,172.87);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.26,167.27) --
-	(176.26,177.19);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.26,168.83) {$h$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (163.99,177.89) --
-	(166.93,177.89);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (165.51,174.55) --
-	(165.51,180.72);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (165.51,174.98) {$\sigma$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (202.72,202.23) --
-	(205.01,202.23);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (203.90,200.86) --
-	(203.90,203.50);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (203.90,199.32) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.16,169.69) --
-	(170.04,169.69);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.12,167.16) --
-	(169.12,171.92);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.12,166.46) {$p$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (156.48,152.05) --
-	(163.33,152.05);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (160.21,149.10) --
-	(160.21,154.60);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (160.21,148.02) {$L$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.03,183.74) --
-	(182.29,183.74);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.16,183.51) --
-	(182.16,183.97);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.16,179.71) {$r$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.51,154.74) --
-	(161.49,154.74);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (156.77,150.34) --
-	(156.77,158.32);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (156.77,150.71) {$h$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.34,169.02) --
-	(169.01,169.02);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (166.82,164.73) --
-	(166.82,172.53);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (166.82,166.12) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.04,192.83) --
-	(196.98,192.83);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.04,192.75) --
-	(196.04,192.91);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.04,189.92) {$\kappa$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.69,189.89) --
-	(180.94,189.89);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.33,178.21) --
-	(180.33,197.08);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.33,186.66) {$p$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.68,176.30) --
-	(177.56,176.30);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.72,164.31) --
-	(175.72,183.61);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (175.72,172.27) {$L$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.95,193.39) --
-	(188.43,193.39);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.19,181.48) --
-	(188.19,200.68);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.19,189.36) {$r$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.03,175.37) --
-	(171.64,175.37);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (170.38,162.85) --
-	(170.38,182.87);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (170.38,171.34) {$h$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.72,184.99) --
-	(174.30,184.99);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.53,173.03) --
-	(173.53,192.30);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.53,182.09) {$\sigma$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (202.53,202.29) --
-	(203.85,202.29);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (203.20,190.24) --
-	(203.20,209.63);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (203.20,199.39) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (198.44,200.79) --
+	(199.23,200.79);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (198.84,200.49) --
+	(198.84,201.08);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.84,197.56) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (208.67,210.87) --
+	(209.60,210.87);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (209.14,210.58) --
+	(209.14,211.16);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.14,207.97) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (213.32,212.67) --
+	(213.43,212.67);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (213.38,212.61) --
+	(213.38,212.72);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (213.38,208.63) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (193.66,196.71) --
+	(194.33,196.71);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (194.00,196.46) --
+	(194.00,196.95);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.00,193.80) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (195.82,198.42) --
+	(196.49,198.42);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (196.16,198.13) --
+	(196.16,198.72);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.16,194.39) {$l$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (195.26,209.96) --
+	(196.09,209.96);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (195.68,209.69) --
+	(195.68,210.24);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.68,207.06) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (212.90,211.47) --
+	(213.21,211.47);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (213.06,211.36) --
+	(213.06,211.58);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (213.06,208.57) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (156.71,162.71) --
+	(158.45,162.71);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (157.60,162.19) --
+	(157.60,163.21);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (157.60,159.48) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (199.15,200.91) --
+	(199.65,200.91);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (199.40,200.73) --
+	(199.40,201.10);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.40,198.01) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (203.01,203.72) --
+	(203.08,203.72);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (203.04,203.66) --
+	(203.04,203.77);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (203.04,199.68) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (150.06,156.35) --
+	(151.67,156.35);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (150.88,155.81) --
+	(150.88,156.87);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (150.88,153.44) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (152.84,158.93) --
+	(154.48,158.93);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (153.67,158.41) --
+	(153.67,159.43);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (153.67,154.89) {$l$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (163.64,173.12) --
+	(165.38,173.12);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (164.53,172.57) --
+	(164.53,173.65);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (164.53,170.21) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (202.74,201.65) --
+	(202.89,201.65);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (202.81,201.57) --
+	(202.81,201.74);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.81,198.75) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (171.06,175.58) --
+	(172.23,175.58);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (171.65,175.04) --
+	(171.65,176.10);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.65,172.35) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (197.40,200.26) --
+	(198.11,200.26);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (197.76,200.01) --
+	(197.76,200.50);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.76,197.35) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (199.45,200.27) --
+	(199.59,200.27);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (199.52,200.07) --
+	(199.52,200.47);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.52,196.24) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (168.80,172.61) --
+	(169.78,172.61);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (169.29,172.08) --
+	(169.29,173.14);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.29,169.71) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (170.56,174.47) --
+	(171.51,174.47);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (171.04,173.92) --
+	(171.04,175.00);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.04,170.43) {$l$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (168.18,181.23) --
+	(169.11,181.23);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (168.65,180.71) --
+	(168.65,181.74);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (168.65,178.33) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (202.02,201.27) --
+	(202.19,201.27);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (202.11,201.03) --
+	(202.11,201.52);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.11,198.37) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (136.57,138.33) --
+	(138.13,138.33);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (137.37,137.24) --
+	(137.37,139.37);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (137.37,135.11) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (179.14,173.33) --
+	(181.38,173.33);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (180.29,172.66) --
+	(180.29,173.98);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.29,170.42) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (179.98,178.33) --
+	(180.24,178.33);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (180.11,178.16) --
+	(180.11,178.50);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.11,174.30) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (136.93,137.86) --
+	(139.01,137.86);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (138.00,136.81) --
+	(138.00,138.85);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (138.00,134.95) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (137.17,138.06) --
+	(138.77,138.06);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (137.99,136.93) --
+	(137.99,139.12);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (137.99,134.03) {$l$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (125.88,152.06) --
+	(127.28,152.06);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (126.59,150.73) --
+	(126.59,153.30);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (126.59,149.15) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (185.13,184.06) --
+	(185.32,184.06);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (185.23,183.90) --
+	(185.23,184.22);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.23,181.16) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (194.80,202.82) --
+	(195.44,202.82);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (195.12,202.49) --
+	(195.12,203.15);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.12,199.60) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (200.20,205.86) --
+	(200.75,205.86);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (200.48,205.55) --
+	(200.48,206.16);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (200.48,202.96) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (208.91,216.10) --
+	(208.98,216.10);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (208.94,216.07) --
+	(208.94,216.13);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (208.94,212.07) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (186.04,196.06) --
+	(186.76,196.06);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (186.40,195.68) --
+	(186.40,196.42);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (186.40,193.15) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (192.98,201.46) --
+	(193.66,201.46);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (193.32,201.13) --
+	(193.32,201.77);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.32,197.42) {$l$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (188.16,194.44) --
+	(189.17,194.44);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (188.67,194.03) --
+	(188.67,194.85);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.67,191.54) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (207.83,206.33) --
+	(208.04,206.33);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (207.94,206.24) --
+	(207.94,206.41);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.94,203.42) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (169.70,170.00) --
+	(170.82,170.00);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (170.27,169.27) --
+	(170.27,170.71);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (170.27,166.77) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (207.01,206.68) --
+	(207.59,206.68);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (207.30,206.41) --
+	(207.30,206.95);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.30,203.77) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (208.84,207.00) --
+	(209.15,207.00);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (209.00,206.90) --
+	(209.00,207.11);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.00,202.97) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (168.40,168.46) --
+	(169.48,168.46);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (168.95,167.77) --
+	(168.95,169.13);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (168.95,165.56) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (170.25,170.45) --
+	(171.43,170.45);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (170.85,169.74) --
+	(170.85,171.13);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (170.85,166.42) {$l$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (173.43,185.57) --
+	(174.72,185.57);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (174.09,184.86) --
+	(174.09,186.25);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.09,182.66) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (212.40,209.44) --
+	(212.76,209.44);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (212.58,209.22) --
+	(212.58,209.65);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.58,206.53) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (171.76,176.94) --
+	(172.75,176.94);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (172.26,176.29) --
+	(172.26,177.56);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.26,173.71) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (183.73,187.04) --
+	(184.79,187.04);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (184.27,186.36) --
+	(184.27,187.69);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.27,184.14) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (187.68,191.67) --
+	(187.82,191.67);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (187.75,191.59) --
+	(187.75,191.76);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.75,187.64) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (168.98,177.33) --
+	(169.88,177.33);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (169.44,176.93) --
+	(169.44,177.73);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.44,174.43) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (170.68,175.87) --
+	(171.60,175.87);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (171.14,175.25) --
+	(171.14,176.48);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.14,171.84) {$l$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (173.01,183.38) --
+	(173.86,183.38);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (173.44,182.88) --
+	(173.44,183.87);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.44,180.48) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (201.14,200.23) --
+	(201.48,200.23);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (201.31,200.11) --
+	(201.31,200.35);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (201.31,197.33) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (186.92,197.19) --
+	(187.56,197.19);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (187.24,196.97) --
+	(187.24,197.42);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.24,193.97) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (182.26,184.08) --
+	(183.40,184.08);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (182.84,183.52) --
+	(182.84,184.62);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.84,181.17) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (196.82,201.84) --
+	(196.95,201.84);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (196.89,201.78) --
+	(196.89,201.90);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.89,197.81) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (180.57,191.69) --
+	(181.21,191.69);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (180.89,191.46) --
+	(180.89,191.92);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.89,188.78) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (186.66,196.94) --
+	(187.34,196.94);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (187.00,196.71) --
+	(187.00,197.18);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.00,192.91) {$l$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (182.67,192.73) --
+	(183.40,192.73);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (183.04,192.34) --
+	(183.04,193.12);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.04,189.83) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (211.84,210.77) --
+	(212.09,210.77);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (211.97,210.64) --
+	(211.97,210.89);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.97,207.86) {$\kappa$};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,259.88) {\bfseries adapt (\textit{cat}) vs. \textit{cat}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,259.88) {\bfseries adapt(\textit{cat}) vs. \textit{cat}};
 
@@
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (307.01,144.54) {ESS/hr [adapt (\textit{cat})]};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (307.01,144.54) {ESS/hr [adapt(\textit{cat})]};
 \end{scope}
@@
 \path[clip] (338.88, 49.80) rectangle (528.36,239.28);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (209.51,  0.00) --
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (209.51,  0.00) --
 	(572.41,362.91) --
@@
 	(368.65,  0.00);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (236.03,  0.00) --
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (236.03,  0.00) --
 	(572.41,336.38) --
@@
 	(342.13,  0.00);
-
-\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round] (262.56,  0.00) --
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (262.56,  0.00) --
 	(572.41,309.86) --
@@
 	(315.60,  0.00);
+\definecolor{drawColor}{RGB}{0,0,0}
 
@@
 \node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.00, 87.76) {$4\times$};
+\definecolor{drawColor}{RGB}{105,105,105}
 
 \path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (338.88, 49.80) -- (528.36,239.28);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (489.17,200.46) --
-	(494.14,200.46);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (491.81,198.61) --
-	(491.81,202.14);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (491.81,197.23) {$p$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (470.10,180.29) --
-	(473.13,180.29);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (471.67,178.14) --
-	(471.67,182.23);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (471.67,176.26) {$L$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (498.44,206.93) --
-	(499.98,206.93);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (499.23,203.91) --
-	(499.23,209.53);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (499.23,202.90) {$r$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (482.98,192.71) --
-	(485.77,192.71);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (484.43,188.53) --
-	(484.43,196.14);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (484.43,188.68) {$h$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (493.93,201.00) --
-	(496.01,201.00);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (495.00,197.45) --
-	(495.00,203.99);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (495.00,198.10) {$\sigma$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (506.72,211.69) --
-	(508.78,211.69);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (507.78,208.42) --
-	(507.78,214.48);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (507.78,208.79) {$\kappa$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (458.92,161.28) --
-	(462.02,161.28);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (460.53,159.29) --
-	(460.53,163.09);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (460.53,158.06) {$p$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (462.78,174.74) --
-	(466.69,174.74);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (464.84,172.43) --
-	(464.84,176.80);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (464.84,170.71) {$L$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (489.61,195.98) --
-	(490.75,195.98);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (490.19,194.87) --
-	(490.19,197.04);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (490.19,191.95) {$r$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (434.26,145.82) --
-	(443.18,145.82);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (439.23,140.13) --
-	(439.23,150.21);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (439.23,141.79) {$h$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (448.95,154.25) --
-	(455.49,154.25);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (452.50,150.54) --
-	(452.50,157.36);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (452.50,151.35) {$\sigma$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (496.87,199.16) --
-	(497.33,199.16);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (497.10,198.20) --
-	(497.10,200.08);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (497.10,196.26) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (442.45,157.16) --
-	(443.45,157.16);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (442.96,156.23) --
-	(442.96,158.05);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (442.96,153.94) {$p$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (453.40,164.82) --
-	(457.57,164.82);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (455.60,162.22) --
-	(455.60,167.11);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (455.60,160.79) {$L$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.33,189.55) --
-	(482.60,189.55);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.50,188.39) --
-	(481.50,190.63);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (481.50,185.51) {$r$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (434.13,150.27) --
-	(440.56,150.27);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (437.62,145.43) --
-	(437.62,154.13);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (437.62,146.24) {$h$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (437.80,157.06) --
-	(446.05,157.06);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (442.37,132.82) --
-	(442.37,167.42);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (442.37,154.16) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (495.27,198.57) --
-	(495.84,198.57);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (495.56,198.44) --
-	(495.56,198.69);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (495.56,195.66) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (400.39,107.27) --
-	(406.95,107.27);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (403.95,102.23) --
-	(403.95,111.25);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (403.95,104.04) {$p$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (443.10,156.88) --
-	(457.34,156.88);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (451.51,151.53) --
-	(451.51,161.05);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (451.51,152.84) {$L$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (442.66,157.29) --
-	(443.37,157.29);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (443.02,155.91) --
-	(443.02,158.58);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (443.02,153.26) {$r$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (396.26,100.71) --
-	(404.45,100.71);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (400.79, 95.38) --
-	(400.79,104.88);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (400.79, 96.68) {$h$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (390.59,110.14) --
-	(407.20,110.14);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (400.64, 99.79) --
-	(400.64,116.82);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (400.64,107.24) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (475.76,185.81) --
-	(477.20,185.81);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (476.49,183.08) --
-	(476.49,188.19);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (476.49,182.90) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (495.31,205.27) --
-	(497.05,205.27);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (496.20,202.53) --
-	(496.20,207.67);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (496.20,202.04) {$p$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (475.59,185.89) --
-	(481.45,185.89);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (478.75,183.37) --
-	(478.75,188.12);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (478.75,181.86) {$L$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (507.78,215.25) --
-	(508.09,215.25);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (507.93,213.22) --
-	(507.93,217.09);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (507.93,211.22) {$r$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (467.06,177.27) --
-	(470.11,177.27);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (468.65,175.15) --
-	(468.65,179.18);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.65,173.24) {$h$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.64,191.87) --
-	(485.18,191.87);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.49,189.77) --
-	(483.49,193.75);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.49,188.96) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (502.08,205.65) --
-	(503.19,205.65);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (502.64,203.55) --
-	(502.64,207.55);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (502.64,202.75) {$\kappa$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (439.99,151.08) --
-	(446.87,151.08);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (443.73,147.85) {$p$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (495.27,206.36) --
-	(500.59,206.36);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (498.12,202.33) {$L$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (477.15,191.68) --
-	(478.39,191.68);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (477.78,187.65) {$r$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (445.65,158.37) --
-	(448.05,158.37);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (446.89,154.33) {$h$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (452.96,153.51) --
-	(458.75,153.51);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (456.08,150.61) {$\sigma$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (501.01,209.66) --
-	(503.73,209.66);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (502.42,206.76) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (451.32,173.38) --
-	(461.03,173.38);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (456.78,168.80) --
-	(456.78,177.08);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (456.78,170.16) {$p$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (427.92,150.89) --
-	(442.33,150.89);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (436.45,147.87) --
-	(436.45,153.50);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (436.45,146.85) {$L$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (473.66,189.57) --
-	(476.30,189.57);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (475.02,188.87) --
-	(475.02,190.24);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (475.02,185.53) {$r$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (435.82,153.94) --
-	(440.37,153.94);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (438.23,146.53) --
-	(438.23,159.26);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (438.23,149.90) {$h$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (438.10,161.88) --
-	(445.96,161.88);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (442.43,152.76) --
-	(442.43,168.03);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (442.43,158.98) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (491.96,202.04) --
-	(493.35,202.04);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (492.67,199.33) --
-	(492.67,204.41);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (492.67,199.14) {$\kappa$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.86,195.35) --
-	(483.18,195.35);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (482.05,194.39) --
-	(482.05,196.26);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (482.05,192.12) {$p$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (471.59,182.66) --
-	(475.02,182.66);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (473.38,181.83) --
-	(473.38,183.47);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (473.38,178.63) {$L$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (487.02,198.60) --
-	(487.89,198.60);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (487.46,197.76) --
-	(487.46,199.40);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (487.46,194.56) {$r$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (468.85,181.82) --
-	(472.24,181.82);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (470.62,180.12) --
-	(470.62,183.39);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (470.62,177.79) {$h$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (472.99,187.44) --
-	(476.41,187.44);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (474.77,186.86) --
-	(474.77,188.00);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.77,184.53) {$\sigma$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (503.25,208.38) --
-	(504.90,208.38);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (504.09,207.49) --
-	(504.09,209.23);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (504.09,205.48) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (492.65,206.23) --
+	(493.27,206.23);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (492.96,205.92) --
+	(492.96,206.54);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (492.96,203.00) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (505.38,216.73) --
+	(506.11,216.73);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (505.75,216.33) --
+	(505.75,217.11);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (505.75,213.82) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (499.10,211.70) --
+	(499.21,211.70);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (499.16,211.62) --
+	(499.16,211.77);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (499.16,207.66) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (487.73,202.32) --
+	(488.29,202.32);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (488.01,201.95) --
+	(488.01,202.68);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (488.01,199.41) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (489.82,204.03) --
+	(490.42,204.03);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (490.12,203.67) --
+	(490.12,204.38);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (490.12,200.00) {$l$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (493.57,206.16) --
+	(494.25,206.16);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (493.92,205.75) --
+	(493.92,206.55);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (493.92,203.25) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (506.62,217.05) --
+	(506.80,217.05);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (506.71,216.87) --
+	(506.71,217.23);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (506.71,214.15) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (467.32,174.83) --
+	(468.23,174.83);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (467.78,173.90) --
+	(467.78,175.72);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (467.78,171.60) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (495.74,206.87) --
+	(496.14,206.87);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (495.94,206.59) --
+	(495.94,207.15);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (495.94,203.96) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (491.49,204.57) --
+	(491.65,204.57);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (491.57,204.49) --
+	(491.57,204.66);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (491.57,200.54) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (460.42,166.26) --
+	(461.37,166.26);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (460.90,165.17) --
+	(460.90,167.29);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (460.90,163.35) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (462.36,168.44) --
+	(463.31,168.44);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (462.84,167.36) --
+	(462.84,169.47);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (462.84,164.41) {$l$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (460.95,171.11) --
+	(462.32,171.11);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (461.64,170.32) --
+	(461.64,171.88);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (461.64,168.21) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (496.66,206.85) --
+	(496.88,206.85);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (496.77,206.77) --
+	(496.77,206.93);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (496.77,203.95) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (451.25,162.13) --
+	(452.20,162.13);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (451.73,161.26) --
+	(451.73,162.96);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (451.73,158.90) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (493.61,205.15) --
+	(494.19,205.15);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (493.90,204.84) --
+	(493.90,205.45);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (493.90,202.25) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (484.20,197.89) --
+	(484.46,197.89);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (484.33,197.75) --
+	(484.33,198.03);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (484.33,193.86) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (447.20,157.10) --
+	(448.18,157.10);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (447.70,156.31) --
+	(447.70,157.86);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (447.70,154.20) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (449.46,160.18) --
+	(450.41,160.18);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (449.94,159.33) --
+	(449.94,160.99);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (449.94,156.14) {$l$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (452.80,166.37) --
+	(453.76,166.37);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (453.28,165.56) --
+	(453.28,167.15);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (453.28,163.47) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (495.58,206.10) --
+	(495.88,206.10);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (495.73,205.93) --
+	(495.73,206.27);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (495.73,203.20) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (413.75,122.86) --
+	(416.46,122.86);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (415.15,121.64) --
+	(415.15,124.00);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (415.15,119.63) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (473.31,185.63) --
+	(474.12,185.63);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (473.72,185.34) --
+	(473.72,185.91);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (473.72,182.72) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (447.11,162.51) --
+	(447.38,162.51);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (447.24,162.37) --
+	(447.24,162.64);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (447.24,158.47) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (412.33,121.32) --
+	(415.08,121.32);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (413.76,120.02) --
+	(413.76,122.54);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (413.76,118.42) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (413.42,122.40) --
+	(416.04,122.40);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (414.77,121.22) --
+	(414.77,123.50);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (414.77,118.36) {$l$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (414.94,122.32) --
+	(417.75,122.32);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (416.40,120.43) --
+	(416.40,124.03);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (416.40,119.41) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (478.09,188.67) --
+	(478.40,188.67);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (478.25,188.53) --
+	(478.25,188.81);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (478.25,185.77) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (492.83,207.98) --
+	(493.61,207.98);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (493.23,207.64) --
+	(493.23,208.32);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (493.23,204.76) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (499.67,211.45) --
+	(500.38,211.45);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (500.03,211.16) --
+	(500.03,211.73);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (500.03,208.54) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (509.13,221.32) --
+	(509.22,221.32);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (509.18,221.28) --
+	(509.18,221.36);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (509.18,217.29) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (484.34,200.66) --
+	(485.28,200.66);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (484.82,200.31) --
+	(484.82,201.00);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (484.82,197.76) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (490.86,205.99) --
+	(491.69,205.99);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (491.28,205.63) --
+	(491.28,206.35);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (491.28,201.96) {$l$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (484.57,197.45) --
+	(485.81,197.45);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (485.20,197.03) --
+	(485.20,197.86);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (485.20,194.55) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (502.49,211.68) --
+	(502.76,211.68);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (502.63,211.55) --
+	(502.63,211.80);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (502.63,208.78) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (454.59,160.79) --
+	(456.16,160.79);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (455.39,159.54) --
+	(455.39,161.97);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (455.39,157.57) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (503.58,216.74) --
+	(504.30,216.74);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (503.95,216.44) --
+	(503.95,217.03);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (503.95,213.83) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (483.64,197.69) --
+	(484.08,197.69);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (483.86,197.48) --
+	(483.86,197.89);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.86,193.65) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (453.00,159.54) --
+	(454.63,159.54);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (453.83,158.30) --
+	(453.83,160.71);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (453.83,156.64) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (455.02,161.26) --
+	(456.59,161.26);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (455.83,160.01) --
+	(455.83,162.43);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (455.83,157.23) {$l$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (466.45,167.17) --
+	(467.37,167.17);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (466.92,165.78) --
+	(466.92,168.47);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (466.92,164.27) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (505.18,215.30) --
+	(505.54,215.30);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (505.36,215.03) --
+	(505.36,215.57);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (505.36,212.39) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (465.34,179.33) --
+	(466.37,179.33);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (465.86,178.82) --
+	(465.86,179.82);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (465.86,176.10) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (479.70,192.12) --
+	(481.20,192.12);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (480.47,191.50) --
+	(480.47,192.71);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (480.47,189.21) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (480.95,194.85) --
+	(481.08,194.85);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (481.02,194.77) --
+	(481.02,194.93);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (481.02,190.81) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (463.17,179.09) --
+	(464.27,179.09);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (463.72,178.61) --
+	(463.72,179.57);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (463.72,176.19) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (464.14,178.17) --
+	(465.19,178.17);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (464.67,177.63) --
+	(464.67,178.69);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (464.67,174.13) {$l$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (469.69,182.13) --
+	(470.41,182.13);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (470.05,181.69) --
+	(470.05,182.56);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (470.05,179.23) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (494.25,204.55) --
+	(494.48,204.55);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (494.37,204.37) --
+	(494.37,204.73);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (494.37,201.64) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (482.88,199.90) --
+	(483.40,199.90);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (483.14,199.59) --
+	(483.14,200.20);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.14,196.67) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (475.17,187.60) --
+	(476.30,187.60);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (475.74,187.13) --
+	(475.74,188.05);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (475.74,184.69) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (490.02,204.20) --
+	(490.14,204.20);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (490.08,204.12) --
+	(490.08,204.27);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (490.08,200.16) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (476.61,194.33) --
+	(477.26,194.33);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (476.94,194.04) --
+	(476.94,194.61);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (476.94,191.42) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (482.77,199.86) --
+	(483.29,199.86);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (483.03,199.55) --
+	(483.03,200.15);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.03,195.82) {$l$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (479.06,192.69) --
+	(479.81,192.69);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (479.44,192.32) --
+	(479.44,193.05);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (479.44,189.78) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (503.86,214.16) --
+	(504.20,214.16);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (504.03,213.97) --
+	(504.03,214.36);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (504.03,211.26) {$\kappa$};
 \end{scope}

### 2020-08-31 benchmarking/benchmarkingVM/ESS_round1_real.tex
Results update

--- 2020-08-26 benchmarking/benchmarkingVM/ESS_round1_real.tex
@@
-% Created by tikzDevice version 0.12.3.1 on 2020-08-25 15:32:33
+% Created by tikzDevice version 0.12.3.1 on 2020-08-31 17:25:39
 % !TEX encoding = UTF-8 Unicode
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,548.96) {\bfseries cons (\textit{real}) vs. nocons (\textit{real})};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,301.03) {ESS/hr [nocons (\textit{real})]};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,433.62) {ESS/hr [cons (\textit{real})]};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,548.96) {\bfseries cons(\textit{real}) vs. nocons(\textit{real})};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,301.03) {ESS/hr [nocons(\textit{real})]};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,433.62) {ESS/hr [cons(\textit{real})]};
 \end{scope}
@@
 \node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92,376.84) {$4\times$};
+\definecolor{drawColor}{RGB}{105,105,105}
 
 \path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,528.36);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (120.87,491.63) --
-	(153.32,491.63);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (143.28,489.68) --
-	(143.28,493.39);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (143.28,488.40) {$p$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.77,470.99) --
-	(175.39,470.99);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (166.58,468.16) --
-	(166.58,473.45);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (166.58,466.95) {$L$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (206.16,500.74) --
-	(215.69,500.74);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.51,500.34) --
-	(211.51,501.13);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.51,496.70) {$r$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.45,479.76) --
-	(197.91,479.76);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.80,477.75) --
-	(189.80,481.58);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (189.80,475.72) {$h$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (134.12,482.07) --
-	(177.22,482.07);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (165.87,479.79) --
-	(165.87,484.11);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (165.87,479.17) {$\sigma$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (222.16,504.36) --
-	(223.91,504.36);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (223.06,503.90) --
-	(223.06,504.81);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (223.06,501.45) {$\kappa$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.77,450.33) --
-	(180.77,456.96);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.77,450.70) {$p$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (127.28,471.34) --
-	(186.05,471.34);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.66,470.84) --
-	(173.66,471.83);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.66,467.31) {$L$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.13,489.98) --
-	(211.57,489.98);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (204.21,489.60) --
-	(204.21,490.35);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (204.21,485.95) {$r$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (158.71,426.99) --
-	(158.71,436.27);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.71,428.15) {$h$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.28,442.01) --
-	(181.28,450.04);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.28,443.54) {$\sigma$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (210.92,494.39) --
-	(211.41,494.39);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.17,494.00) --
-	(211.17,494.78);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.17,491.49) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (111.69,458.54) --
-	(151.89,458.54);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (140.84,457.29) --
-	(140.84,459.71);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (140.84,455.31) {$p$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (135.21,465.08) --
-	(177.74,465.08);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (166.44,464.31) --
-	(166.44,465.81);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (166.44,461.04) {$L$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.37,486.12) --
-	(198.07,486.12);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.42,485.75) --
-	(192.42,486.49);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.42,482.09) {$r$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (131.08,451.24) --
-	(158.21,451.24);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.10,449.98) --
-	(149.10,452.42);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (149.10,447.21) {$h$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (118.18,448.42) --
-	(157.07,448.42);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (146.16,445.27) --
-	(146.16,451.13);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (146.16,445.52) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (210.39,493.75) --
-	(211.29,493.75);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (210.85,493.47) --
-	(210.85,494.02);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.85,490.85) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (123.38,424.42) --
-	(130.68,424.42);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (127.38,421.26) --
-	(127.38,427.12);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (127.38,421.19) {$p$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (146.20,468.06) --
-	(169.06,468.06);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (160.86,465.26) --
-	(160.86,470.50);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (160.86,464.02) {$L$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.44,466.43) --
-	(152.81,466.43);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.13,465.29) --
-	(152.13,467.52);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (152.13,462.40) {$r$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (109.33,419.53) --
-	(117.33,419.53);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (113.75,415.02) --
-	(113.75,423.18);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (113.75,415.50) {$h$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (123.65,403.30) --
-	(135.78,403.30);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (130.66,401.93) --
-	(130.66,404.58);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (130.66,400.39) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.69,475.61) --
-	(192.26,475.61);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.98,474.76) --
-	(191.98,476.41);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.98,472.70) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.12,466.92) --
-	(187.12,473.64);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.12,467.35) {$p$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.14,476.78) --
-	(180.14,480.98);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.14,474.96) {$L$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (216.84,493.07) --
-	(230.43,493.07);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (224.81,492.69) --
-	(224.81,493.45);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (224.81,489.04) {$r$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.46,463.13) --
-	(211.65,463.13);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (200.82,460.82) --
-	(200.82,465.20);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (200.82,459.10) {$h$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (204.80,468.25) --
-	(204.80,471.97);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (204.80,467.30) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (219.49,498.64) --
-	(220.69,498.64);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (220.10,498.09) --
-	(220.10,499.17);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.10,495.73) {$\kappa$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (128.17,481.37) --
-	(128.17,483.93);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (128.17,479.47) {$p$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (133.95,488.01) --
-	(133.95,491.15);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (133.95,485.61) {$L$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (157.10,491.91) --
-	(191.40,491.91);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.09,491.31) --
-	(181.09,492.50);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.09,487.88) {$r$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (166.81,460.10) --
-	(172.28,460.10);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.74,458.25) --
-	(169.74,461.79);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.74,456.07) {$h$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (139.80,456.53) --
-	(139.80,458.39);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (139.80,454.58) {$\sigma$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (219.72,498.92) --
-	(223.33,498.92);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (221.61,498.04) --
-	(221.61,499.76);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (221.61,496.01) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 77.66,454.16) --
-	( 90.48,454.16);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 85.13,451.25) --
-	( 85.13,456.69);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 85.13,450.94) {$p$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 92.57,442.19) --
-	(113.59,442.19);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (105.83,425.62) --
-	(105.83,450.94);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (105.83,438.16) {$L$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.95,468.69) --
-	(185.12,468.69);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.70,468.48) --
-	(178.70,468.90);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (178.70,464.66) {$r$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (118.32,432.28) --
-	(139.71,432.28);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (131.86,429.85) --
-	(131.86,434.45);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (131.86,428.25) {$h$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 80.49,443.30) --
-	( 96.43,443.30);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 90.07,438.32) --
-	( 90.07,447.26);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 90.07,440.40) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (208.10,489.05) --
-	(210.28,489.05);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (209.22,487.17) --
-	(209.22,490.76);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.22,486.14) {$\kappa$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.14,461.92) --
-	(211.14,468.04);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.14,462.00) {$p$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (159.01,457.26) --
-	(159.01,467.68);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (159.01,459.14) {$L$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.24,477.77) --
-	(220.71,477.77);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (208.91,477.50) --
-	(208.91,478.04);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (208.91,473.74) {$r$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (157.73,460.39) --
-	(184.13,460.39);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.16,455.16) --
-	(175.16,464.50);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (175.16,456.36) {$h$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.46,458.99) --
-	(191.46,464.85);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.46,459.24) {$\sigma$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (224.99,499.53) --
-	(226.68,499.53);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (225.86,498.82) --
-	(225.86,500.21);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (225.86,496.62) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (198.28,494.66) --
+	(204.36,494.66);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (201.56,494.38) --
+	(201.56,494.93);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (201.56,491.43) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (218.52,499.39) --
+	(220.75,499.39);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (219.67,499.07) --
+	(219.67,499.70);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (219.67,496.48) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (215.91,501.59) --
+	(219.27,501.59);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (217.66,501.55) --
+	(217.66,501.62);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (217.66,497.55) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (199.70,482.86) --
+	(203.04,482.86);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (201.44,482.57) --
+	(201.44,483.15);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (201.44,479.96) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (209.98,485.79) --
+	(219.03,485.79);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (215.04,485.56) --
+	(215.04,486.02);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (215.04,481.76) {$l$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (204.84,485.65) --
+	(216.47,485.65);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (211.53,485.34) --
+	(211.53,485.96);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.53,482.75) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (223.18,504.72) --
+	(223.70,504.72);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (223.44,504.58) --
+	(223.44,504.85);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (223.44,501.81) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (171.15,457.84) --
+	(189.63,457.84);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (182.54,456.70) --
+	(182.54,458.92);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.54,454.61) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (206.33,490.22) --
+	(209.40,490.22);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (207.93,489.91) --
+	(207.93,490.52);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.93,487.31) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (204.72,491.74) --
+	(206.73,491.74);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (205.75,491.68) --
+	(205.75,491.80);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.75,487.70) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (151.21,440.14) --
+	(153.87,440.14);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (152.58,439.22) --
+	(152.58,441.01);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (152.58,437.23) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (169.17,441.93) --
+	(192.67,441.93);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (184.32,441.01) --
+	(184.32,442.81);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.32,437.90) {$l$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (174.07,451.54) --
+	(196.64,451.54);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (188.51,450.41) --
+	(188.51,452.61);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.51,448.64) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (212.19,495.41) --
+	(212.45,495.41);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (212.32,495.32) --
+	(212.32,495.49);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.32,492.50) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (167.41,462.49) --
+	(183.10,462.49);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (176.82,461.97) --
+	(176.82,462.99);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.82,459.26) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (201.58,488.87) --
+	(206.74,488.87);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (204.34,488.55) --
+	(204.34,489.19);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (204.34,485.97) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (193.01,488.24) --
+	(196.83,488.24);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (195.02,488.18) --
+	(195.02,488.29);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.02,484.20) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (161.20,460.37) --
+	(165.98,460.37);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (163.74,459.93) --
+	(163.74,460.81);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (163.74,457.47) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (170.46,461.23) --
+	(184.95,461.23);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (179.04,460.77) --
+	(179.04,461.68);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.04,457.20) {$l$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (173.29,454.48) --
+	(196.02,454.48);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (187.85,454.03) --
+	(187.85,454.92);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.85,451.57) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (211.76,494.45) --
+	(212.07,494.45);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (211.92,494.36) --
+	(211.92,494.55);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.92,491.55) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (139.82,437.49) --
+	(142.69,437.49);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (141.31,435.71) --
+	(141.31,439.11);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (141.31,434.26) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (188.50,469.39) --
+	(191.19,469.39);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (189.89,469.21) --
+	(189.89,469.56);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (189.89,466.49) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (156.82,470.66) --
+	(158.12,470.66);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (157.48,470.52) --
+	(157.48,470.79);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (157.48,466.62) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (128.56,432.56) --
+	(131.74,432.56);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (130.21,431.55) --
+	(130.21,433.52);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (130.21,429.66) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (128.30,432.21) --
+	(131.22,432.21);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (129.82,431.35) --
+	(129.82,433.04);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (129.82,428.18) {$l$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (140.69,415.66) --
+	(144.04,415.66);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (142.44,413.79) --
+	(142.44,417.37);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (142.44,412.76) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (194.07,476.87) --
+	(194.73,476.87);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (194.40,476.71) --
+	(194.40,477.02);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.40,473.96) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (202.41,472.87) --
+	(214.60,472.87);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (209.46,472.13) --
+	(209.46,473.58);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.46,469.64) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (197.07,486.45) --
+	(205.48,486.45);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (201.74,486.03) --
+	(201.74,486.85);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (201.74,483.54) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (220.79,493.62) --
+	(223.70,493.62);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (222.30,493.57) --
+	(222.30,493.68);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (222.30,489.59) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (203.05,472.03) --
+	(211.88,472.03);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (207.97,471.72) --
+	(207.97,472.32);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.97,469.12) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (220.70,479.63) --
+	(226.20,479.63);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (223.64,479.32) --
+	(223.64,479.93);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (223.64,475.59) {$l$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (212.79,472.59) --
+	(223.65,472.59);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (218.98,472.14) --
+	(218.98,473.03);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (218.98,469.68) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (220.29,499.77) --
+	(220.89,499.77);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (220.59,499.63) --
+	(220.59,499.92);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.59,496.87) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (205.55,484.09) --
+	(218.19,484.09);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (212.89,483.58) --
+	(212.89,484.58);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.89,480.86) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (214.90,490.53) --
+	(218.08,490.53);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (216.56,490.26) --
+	(216.56,490.80);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (216.56,487.63) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (197.42,491.99) --
+	(208.44,491.99);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (203.71,491.95) --
+	(203.71,492.04);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (203.71,487.96) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (173.25,458.16) --
+	(191.52,458.16);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (184.49,457.57) --
+	(184.49,458.73);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.49,455.25) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (209.50,458.69) --
+	(221.94,458.69);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (216.71,458.03) --
+	(216.71,459.32);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (216.71,454.65) {$l$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (206.78,461.44) --
+	(220.04,461.44);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (214.54,460.91) --
+	(214.54,461.96);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (214.54,458.54) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (221.97,498.57) --
+	(222.68,498.57);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (222.33,498.31) --
+	(222.33,498.83);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (222.33,495.67) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (159.51,466.05) --
+	(176.34,466.05);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (169.72,465.68) --
+	(169.72,466.40);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.72,462.82) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (168.65,471.60) --
+	(178.58,471.60);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (174.25,470.81) --
+	(174.25,472.36);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.25,468.70) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (188.28,473.47) --
+	(197.14,473.47);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (193.22,473.41) --
+	(193.22,473.54);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.22,469.44) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (163.90,455.11) --
+	(172.62,455.11);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (168.75,454.43) --
+	(168.75,455.77);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (168.75,452.21) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (171.98,456.65) --
+	(181.96,456.65);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (177.61,455.82) --
+	(177.61,457.45);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.61,452.62) {$l$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (172.32,459.17) --
+	(197.10,459.17);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (188.47,458.78) --
+	(188.47,459.55);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.47,456.27) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (210.15,491.65) --
+	(211.06,491.65);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (210.61,491.52) --
+	(210.61,491.78);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.61,488.74) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (205.13,470.57) --
+	(219.00,470.57);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (213.29,470.19) --
+	(213.29,470.95);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (213.29,467.35) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (174.44,469.22) --
+	(182.16,469.22);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (178.68,468.65) --
+	(178.68,469.78);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (178.68,466.32) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (213.32,480.03) --
+	(222.77,480.03);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (218.62,479.97) --
+	(218.62,480.08);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (218.62,475.99) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (186.37,463.32) --
+	(203.09,463.32);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (196.50,462.98) --
+	(196.50,463.66);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.50,460.42) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (224.68,469.61) --
+	(230.80,469.61);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (227.99,469.27) --
+	(227.99,469.95);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (227.99,465.58) {$l$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (213.23,467.52) --
+	(225.36,467.52);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (220.24,467.13) --
+	(220.24,467.89);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.24,464.61) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (224.79,499.66) --
+	(225.47,499.66);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (225.13,499.50) --
+	(225.13,499.81);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (225.13,496.75) {$\kappa$};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,548.96) {\bfseries adapt (\textit{real}) vs. nocons (\textit{real})};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,301.03) {ESS/hr [nocons (\textit{real})]};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (307.01,433.62) {ESS/hr [adapt (\textit{real})]};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,548.96) {\bfseries adapt(\textit{real}) vs. nocons(\textit{real})};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,301.03) {ESS/hr [nocons(\textit{real})]};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (307.01,433.62) {ESS/hr [adapt(\textit{real})]};
 \end{scope}
@@
 \node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (341.00,376.84) {$4\times$};
+\definecolor{drawColor}{RGB}{105,105,105}
 
 \path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (338.88,338.88) -- (528.36,528.36);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (409.95,498.53) --
-	(442.40,498.53);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (432.36,495.69) --
-	(432.36,501.00);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (432.36,495.30) {$p$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (438.85,477.19) --
-	(464.47,477.19);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (455.66,473.20) --
-	(455.66,480.49);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (455.66,473.16) {$L$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (495.24,507.29) --
-	(504.77,507.29);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (500.59,504.13) --
-	(500.59,510.00);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (500.59,503.26) {$r$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (464.53,488.44) --
-	(486.99,488.44);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (478.88,485.34) --
-	(478.88,491.10);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (478.88,484.40) {$h$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (423.20,500.32) --
-	(466.30,500.32);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (454.95,497.70) --
-	(454.95,502.63);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (454.95,497.42) {$\sigma$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (511.24,508.32) --
-	(512.99,508.32);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (512.14,505.44) --
-	(512.14,510.82);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (512.14,505.41) {$\kappa$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (469.85,459.47) --
-	(469.85,463.29);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (469.85,458.25) {$p$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (416.36,473.75) --
-	(475.13,473.75);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (462.74,467.42) --
-	(462.74,478.51);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (462.74,469.72) {$L$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.21,499.81) --
-	(500.65,499.81);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (493.29,499.49) --
-	(493.29,500.13);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (493.29,495.78) {$r$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (447.79,430.75) --
-	(447.79,435.51);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (447.79,429.24) {$h$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (470.36,453.95) --
-	(470.36,460.21);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (470.36,454.43) {$\sigma$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (500.00,500.26) --
-	(500.49,500.26);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (500.25,500.10) --
-	(500.25,500.41);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (500.25,497.35) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (400.77,472.45) --
-	(440.97,472.45);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (429.92,469.05) --
-	(429.92,475.33);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (429.92,469.22) {$p$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (424.29,469.44) --
-	(466.82,469.44);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (455.52,468.18) --
-	(455.52,470.63);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (455.52,465.41) {$L$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (473.45,494.42) --
-	(487.15,494.42);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.50,494.08) --
-	(481.50,494.75);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (481.50,490.38) {$r$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (420.16,461.88) --
-	(447.29,461.88);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (438.18,458.33) --
-	(438.18,464.86);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (438.18,457.84) {$h$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (407.26,466.76) --
-	(446.15,466.76);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (435.24,464.72) --
-	(435.24,468.61);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (435.24,463.86) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (499.47,500.16) --
-	(500.37,500.16);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (499.93,499.71) --
-	(499.93,500.60);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (499.93,497.25) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (412.46,461.86) --
-	(419.76,461.86);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (416.46,457.98) --
-	(416.46,465.08);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (416.46,458.63) {$p$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (435.28,471.68) --
-	(458.14,471.68);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (449.94,467.85) --
-	(449.94,474.87);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (449.94,467.65) {$L$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (440.52,473.63) --
-	(441.89,473.63);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (441.21,473.45) --
-	(441.21,473.81);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (441.21,469.59) {$r$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (398.41,428.77) --
-	(406.41,428.77);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (402.83,424.39) --
-	(402.83,432.32);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (402.83,424.73) {$h$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (412.73,451.10) --
-	(424.86,451.10);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (419.74,444.27) --
-	(419.74,456.13);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (419.74,448.20) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.77,482.13) --
-	(481.34,482.13);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.06,481.71) --
-	(481.06,482.53);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (481.06,479.22) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (476.20,469.20) --
-	(476.20,486.87);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (476.20,476.78) {$p$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (469.22,479.54) --
-	(469.22,485.69);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (469.22,478.82) {$L$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (505.92,510.87) --
-	(519.51,510.87);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (513.89,508.22) --
-	(513.89,513.20);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (513.89,506.84) {$r$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (462.54,475.07) --
-	(500.73,475.07);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (489.90,471.46) --
-	(489.90,478.10);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (489.90,471.03) {$h$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (493.88,480.19) --
-	(493.88,486.83);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (493.88,480.89) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (508.57,502.56) --
-	(509.77,502.56);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (509.18,499.82) --
-	(509.18,504.96);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (509.18,499.66) {$\kappa$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (417.25,495.96) --
-	(417.25,497.69);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (417.25,493.62) {$p$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (423.03,501.50) --
-	(423.03,504.37);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (423.03,498.95) {$L$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (446.18,502.51) --
-	(480.48,502.51);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (470.17,502.30) --
-	(470.17,502.71);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (470.17,498.47) {$r$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (455.89,473.26) --
-	(461.36,473.26);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (458.82,472.23) --
-	(458.82,474.23);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (458.82,469.22) {$h$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (428.88,471.94) --
-	(428.88,477.11);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (428.88,471.79) {$\sigma$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (508.80,510.43) --
-	(512.41,510.43);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (510.69,509.55) --
-	(510.69,511.28);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (510.69,507.53) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (366.74,474.68) --
-	(379.56,474.68);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (374.21,470.11) --
-	(374.21,478.38);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (374.21,471.46) {$p$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (381.65,452.98) --
-	(402.67,452.98);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (394.91,449.28) --
-	(394.91,456.08);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (394.91,448.95) {$L$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (458.03,485.78) --
-	(474.20,485.78);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (467.78,485.35) --
-	(467.78,486.21);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (467.78,481.75) {$r$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (407.40,446.62) --
-	(428.79,446.62);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (420.94,441.01) --
-	(420.94,450.95);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (420.94,442.59) {$h$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (369.57,472.80) --
-	(385.51,472.80);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (379.15,467.90) --
-	(379.15,476.70);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (379.15,469.90) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (497.18,498.56) --
-	(499.36,498.56);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (498.30,497.16) --
-	(498.30,499.86);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (498.30,495.65) {$\kappa$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (500.22,478.54) --
-	(500.22,484.51);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (500.22,478.53) {$p$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (448.09,474.79) --
-	(448.09,481.27);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (448.09,474.27) {$L$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (461.32,500.43) --
-	(509.79,500.43);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (497.99,500.31) --
-	(497.99,500.55);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (497.99,496.40) {$r$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (446.81,480.91) --
-	(473.21,480.91);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (464.24,478.84) --
-	(464.24,482.78);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (464.24,476.88) {$h$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.54,484.34) --
-	(480.54,486.46);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (480.54,482.53) {$\sigma$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (514.07,512.69) --
-	(515.76,512.69);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (514.94,512.04) --
-	(514.94,513.32);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (514.94,509.78) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (487.36,505.04) --
+	(493.44,505.04);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (490.64,504.79) --
+	(490.64,505.29);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (490.64,501.82) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (507.60,507.39) --
+	(509.83,507.39);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (508.75,506.95) --
+	(508.75,507.82);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (508.75,504.49) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (504.99,511.19) --
+	(508.35,511.19);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (506.74,511.13) --
+	(506.74,511.25);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (506.74,507.16) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (488.78,493.79) --
+	(492.12,493.79);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (490.52,493.47) --
+	(490.52,494.11);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (490.52,490.89) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (499.06,496.31) --
+	(508.11,496.31);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (504.12,495.98) --
+	(504.12,496.64);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (504.12,492.28) {$l$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (493.92,506.51) --
+	(505.55,506.51);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (500.61,506.28) --
+	(500.61,506.73);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (500.61,503.60) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (512.26,512.59) --
+	(512.78,512.59);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (512.52,512.47) --
+	(512.52,512.71);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (512.52,509.69) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (460.23,468.92) --
+	(478.71,468.92);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (471.62,468.08) --
+	(471.62,469.72);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (471.62,465.69) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (495.41,497.49) --
+	(498.48,497.49);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (497.01,497.22) --
+	(497.01,497.77);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (497.01,494.59) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (493.80,500.25) --
+	(495.81,500.25);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (494.83,500.18) --
+	(494.83,500.32);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (494.83,496.21) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (440.29,453.35) --
+	(442.95,453.35);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (441.66,452.41) --
+	(441.66,454.24);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (441.66,450.44) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (458.25,455.34) --
+	(481.75,455.34);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (473.40,454.39) --
+	(473.40,456.25);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (473.40,451.31) {$l$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (463.15,466.37) --
+	(485.72,466.37);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (477.59,465.53) --
+	(477.59,467.17);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (477.59,463.46) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (501.27,501.14) --
+	(501.53,501.14);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (501.40,501.05) --
+	(501.40,501.23);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (501.40,498.24) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (456.49,477.08) --
+	(472.18,477.08);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (465.90,476.61) --
+	(465.90,477.54);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (465.90,473.86) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (490.66,493.82) --
+	(495.82,493.82);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (493.42,493.57) --
+	(493.42,494.06);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (493.42,490.91) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (482.09,495.00) --
+	(485.91,495.00);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (484.10,494.93) --
+	(484.10,495.07);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (484.10,490.97) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (450.28,470.07) --
+	(455.06,470.07);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (452.82,469.69) --
+	(452.82,470.46);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (452.82,467.17) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (459.54,471.13) --
+	(474.03,471.13);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (468.12,470.73) --
+	(468.12,471.51);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.12,467.09) {$l$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (462.37,474.04) --
+	(485.10,474.04);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (476.93,473.55) --
+	(476.93,474.51);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (476.93,471.13) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (500.84,500.80) --
+	(501.15,500.80);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (501.00,500.70) --
+	(501.00,500.90);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (501.00,497.89) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (428.90,470.69) --
+	(431.77,470.69);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (430.39,470.18) --
+	(430.39,471.19);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (430.39,467.47) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (477.58,468.90) --
+	(480.27,468.90);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (478.97,468.61) --
+	(478.97,469.18);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (478.97,465.99) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (445.90,475.57) --
+	(447.20,475.57);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (446.56,475.45) --
+	(446.56,475.69);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (446.56,471.54) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (417.64,442.67) --
+	(420.82,442.67);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (419.29,442.05) --
+	(419.29,443.26);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (419.29,439.76) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (417.38,442.55) --
+	(420.30,442.55);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (418.90,441.89) --
+	(418.90,443.18);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (418.90,438.51) {$l$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (429.77,458.76) --
+	(433.12,458.76);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (431.52,457.98) --
+	(431.52,459.51);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (431.52,455.86) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (483.15,482.91) --
+	(483.81,482.91);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (483.48,482.83) --
+	(483.48,482.99);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.48,480.01) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (491.49,487.61) --
+	(503.68,487.61);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (498.54,486.33) --
+	(498.54,488.81);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (498.54,484.39) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (486.15,504.08) --
+	(494.56,504.08);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (490.82,503.75) --
+	(490.82,504.41);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (490.82,501.17) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (509.87,516.22) --
+	(512.78,516.22);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (511.38,516.18) --
+	(511.38,516.26);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (511.38,512.18) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (492.13,497.67) --
+	(500.96,497.67);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (497.05,497.33) --
+	(497.05,498.01);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (497.05,494.77) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (509.78,502.94) --
+	(515.28,502.94);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (512.72,502.68) --
+	(512.72,503.19);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (512.72,498.90) {$l$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (501.87,491.24) --
+	(512.73,491.24);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (508.06,490.94) --
+	(508.06,491.55);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (508.06,488.34) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (509.37,507.70) --
+	(509.97,507.70);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (509.67,507.59) --
+	(509.67,507.81);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (509.67,504.80) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (494.63,499.71) --
+	(507.27,499.71);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (501.97,499.35) --
+	(501.97,500.06);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (501.97,496.48) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (503.98,498.95) --
+	(507.16,498.95);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (505.64,498.66) --
+	(505.64,499.24);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (505.64,496.05) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (486.50,503.67) --
+	(497.52,503.67);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (492.79,503.61) --
+	(492.79,503.74);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (492.79,499.64) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (462.33,471.10) --
+	(480.60,471.10);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (473.57,470.46) --
+	(473.57,471.72);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (473.57,468.20) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (498.58,471.53) --
+	(511.02,471.53);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (505.79,470.90) --
+	(505.79,472.14);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (505.79,467.50) {$l$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (495.86,483.58) --
+	(509.12,483.58);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (503.62,483.12) --
+	(503.62,484.03);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (503.62,480.67) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (511.05,512.59) --
+	(511.76,512.59);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (511.41,512.42) --
+	(511.41,512.76);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (511.41,509.69) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (448.59,481.02) --
+	(465.42,481.02);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (458.80,480.59) --
+	(458.80,481.44);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (458.80,477.79) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (457.73,482.93) --
+	(467.66,482.93);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (463.33,481.27) --
+	(463.33,484.45);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (463.33,480.02) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (477.36,489.01) --
+	(486.22,489.01);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (482.30,488.92) --
+	(482.30,489.11);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (482.30,484.98) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (452.98,473.57) --
+	(461.70,473.57);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (457.83,473.24) --
+	(457.83,473.89);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (457.83,470.67) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (461.06,472.97) --
+	(471.04,472.97);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (466.69,472.65) --
+	(466.69,473.28);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (466.69,468.93) {$l$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (461.40,480.98) --
+	(486.18,480.98);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (477.55,480.59) --
+	(477.55,481.36);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (477.55,478.08) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (499.23,501.33) --
+	(500.14,501.33);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (499.69,501.22) --
+	(499.69,501.45);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (499.69,498.43) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (494.21,487.86) --
+	(508.08,487.86);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (502.37,487.42) --
+	(502.37,488.29);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (502.37,484.64) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (463.52,484.00) --
+	(471.24,484.00);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (467.76,483.35) --
+	(467.76,484.63);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (467.76,481.10) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (502.40,500.91) --
+	(511.85,500.91);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (507.70,500.84) --
+	(507.70,500.97);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (507.70,496.87) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (475.45,490.16) --
+	(492.17,490.16);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (485.58,489.94) --
+	(485.58,490.38);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (485.58,487.26) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (513.76,495.79) --
+	(519.88,495.79);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (517.07,495.53) --
+	(517.07,496.04);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (517.07,491.75) {$l$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (502.31,490.00) --
+	(514.44,490.00);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (509.32,489.48) --
+	(509.32,490.49);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (509.32,487.09) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (513.87,512.17) --
+	(514.55,512.17);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (514.21,511.97) --
+	(514.21,512.37);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (514.21,509.26) {$\kappa$};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,259.88) {\bfseries adapt (\textit{real}) vs. cons (\textit{real})};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54, 11.95) {ESS/hr [cons (\textit{real})]};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,144.54) {ESS/hr [adapt (\textit{real})]};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,259.88) {\bfseries adapt(\textit{real}) vs. cons(\textit{real})};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54, 11.95) {ESS/hr [cons(\textit{real})]};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,144.54) {ESS/hr [adapt(\textit{real})]};
 \end{scope}
@@
 \node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92, 87.76) {$4\times$};
+\definecolor{drawColor}{RGB}{105,105,105}
 
 \path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 49.80, 49.80) -- (239.28,239.28);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (200.60,209.45) --
-	(204.31,209.45);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (202.55,206.61) --
-	(202.55,211.92);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.55,206.22) {$p$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.08,188.11) --
-	(184.37,188.11);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.91,184.12) --
-	(181.91,191.41);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.91,184.08) {$L$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.26,218.21) --
-	(212.05,218.21);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.66,215.05) --
-	(211.66,220.92);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.66,214.18) {$r$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.67,199.36) --
-	(192.50,199.36);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.68,196.26) --
-	(190.68,202.02);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.68,195.32) {$h$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.71,211.24) --
-	(195.03,211.24);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.99,208.62) --
-	(192.99,213.55);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.99,208.34) {$\sigma$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (214.82,219.24) --
-	(215.73,219.24);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (215.28,216.36) --
-	(215.28,221.74);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (215.28,216.33) {$\kappa$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.25,172.40) --
-	(167.88,172.40);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.85,170.39) --
-	(164.85,174.21);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (164.85,169.17) {$p$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.76,184.67) --
-	(182.75,184.67);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.26,178.34) --
-	(182.26,189.43);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.26,180.64) {$L$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (200.52,210.73) --
-	(201.27,210.73);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (200.90,210.41) --
-	(200.90,211.05);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (200.90,206.70) {$r$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (137.91,144.20) --
-	(147.19,144.20);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (143.11,141.67) --
-	(143.11,146.43);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (143.11,140.16) {$h$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.93,168.26) --
-	(160.96,168.26);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (157.36,164.87) --
-	(157.36,171.13);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (157.36,165.35) {$\sigma$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (204.92,211.18) --
-	(205.70,211.18);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (205.31,211.02) --
-	(205.31,211.33);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.31,208.27) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.21,183.37) --
-	(170.63,183.37);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.46,179.97) --
-	(169.46,186.25);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.46,180.14) {$p$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.23,180.36) --
-	(176.73,180.36);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.00,179.10) --
-	(176.00,181.55);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.00,176.33) {$L$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.67,205.34) --
-	(197.41,205.34);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (197.04,205.00) --
-	(197.04,205.67);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.04,201.30) {$r$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (160.90,172.80) --
-	(163.34,172.80);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (162.16,169.25) --
-	(162.16,175.78);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (162.16,168.76) {$h$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (156.19,177.68) --
-	(162.05,177.68);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (159.34,175.64) --
-	(159.34,179.53);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (159.34,174.78) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (204.39,211.08) --
-	(204.94,211.08);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (204.67,210.63) --
-	(204.67,211.52);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (204.67,208.17) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (132.18,172.78) --
-	(138.04,172.78);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (135.34,168.90) --
-	(135.34,176.00);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (135.34,169.55) {$p$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.18,182.60) --
-	(181.42,182.60);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.98,178.77) --
-	(178.98,185.79);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (178.98,178.57) {$L$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.21,184.55) --
-	(178.44,184.55);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (177.35,184.37) --
-	(177.35,184.73);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.35,180.51) {$r$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (125.94,139.69) --
-	(134.10,139.69);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (130.45,135.31) --
-	(130.45,143.24);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (130.45,135.65) {$h$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (112.85,162.02) --
-	(115.50,162.02);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (114.22,155.19) --
-	(114.22,167.05);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (114.22,159.12) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.68,193.05) --
-	(187.33,193.05);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.53,192.63) --
-	(186.53,193.45);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (186.53,190.14) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (177.84,190.92) --
-	(184.56,190.92);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.49,180.12) --
-	(181.49,197.79);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.49,187.70) {$p$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.70,193.78) --
-	(191.90,193.78);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.91,190.46) --
-	(189.91,196.61);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (189.91,189.74) {$L$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (203.61,221.79) --
-	(204.37,221.79);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (203.99,219.14) --
-	(203.99,224.12);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (203.99,217.76) {$r$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.74,185.99) --
-	(176.12,185.99);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.05,182.38) --
-	(174.05,189.02);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.05,181.95) {$h$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.17,194.72) --
-	(182.89,194.72);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.12,191.11) --
-	(181.12,197.75);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.12,191.81) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (209.01,213.48) --
-	(210.09,213.48);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (209.56,210.74) --
-	(209.56,215.88);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.56,210.58) {$\kappa$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.29,207.77) --
-	(194.85,207.77);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.61,206.88) --
-	(193.61,208.61);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.61,204.54) {$p$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.93,213.91) --
-	(202.07,213.91);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (200.57,212.42) --
-	(200.57,215.29);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (200.57,209.87) {$L$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (202.23,213.43) --
-	(203.42,213.43);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (202.83,213.22) --
-	(202.83,213.63);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.83,209.39) {$r$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.17,184.18) --
-	(172.71,184.18);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.02,183.15) --
-	(171.02,185.15);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.02,180.14) {$h$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (167.45,185.62) --
-	(169.31,185.62);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.40,182.86) --
-	(168.40,188.03);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (168.40,182.71) {$\sigma$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (208.96,221.35) --
-	(210.68,221.35);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (209.84,220.47) --
-	(209.84,222.20);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.84,218.45) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (162.17,185.60) --
-	(167.61,185.60);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (165.08,181.03) --
-	(165.08,189.30);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (165.08,182.38) {$p$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (136.54,163.90) --
-	(161.86,163.90);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (153.11,160.20) --
-	(153.11,167.00);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (153.11,159.87) {$L$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.40,196.70) --
-	(179.82,196.70);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.61,196.27) --
-	(179.61,197.13);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.61,192.67) {$r$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (140.77,157.54) --
-	(145.37,157.54);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (143.20,151.93) --
-	(143.20,161.87);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (143.20,153.51) {$h$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.24,183.72) --
-	(158.18,183.72);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (154.22,178.82) --
-	(154.22,187.62);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (154.22,180.82) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.09,209.48) --
-	(201.68,209.48);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.97,208.08) --
-	(199.97,210.78);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.97,206.57) {$\kappa$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.84,192.68) --
-	(178.96,192.68);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.15,189.46) --
-	(176.15,195.43);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.15,189.45) {$p$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.18,189.23) --
-	(178.60,189.23);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.09,185.71) --
-	(174.09,192.19);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.09,185.19) {$L$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.42,211.35) --
-	(188.96,211.35);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.69,211.23) --
-	(188.69,211.47);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.69,207.32) {$r$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (166.08,191.83) --
-	(175.42,191.83);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.31,189.76) --
-	(171.31,193.70);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.31,187.80) {$h$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.91,196.35) --
-	(175.77,196.35);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.06,195.26) --
-	(173.06,197.38);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.06,193.45) {$\sigma$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (209.74,223.61) --
-	(211.13,223.61);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (210.45,222.96) --
-	(210.45,224.24);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.45,220.70) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (205.30,215.96) --
+	(205.85,215.96);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (205.58,215.71) --
+	(205.58,216.21);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.58,212.74) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (209.99,218.31) --
+	(210.62,218.31);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (210.31,217.87) --
+	(210.31,218.74);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.31,215.41) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (212.47,222.11) --
+	(212.54,222.11);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (212.51,222.05) --
+	(212.51,222.17);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.51,218.08) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (193.49,204.71) --
+	(194.07,204.71);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (193.78,204.39) --
+	(193.78,205.03);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.78,201.81) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (196.48,207.23) --
+	(196.94,207.23);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (196.71,206.90) --
+	(196.71,207.56);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.71,203.20) {$l$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (196.26,217.43) --
+	(196.88,217.43);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (196.57,217.20) --
+	(196.57,217.65);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.57,214.52) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (215.50,223.51) --
+	(215.77,223.51);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (215.64,223.39) --
+	(215.64,223.63);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (215.64,220.61) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (167.62,179.84) --
+	(169.84,179.84);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (168.76,179.00) --
+	(168.76,180.64);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (168.76,176.61) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (200.83,208.41) --
+	(201.44,208.41);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (201.14,208.14) --
+	(201.14,208.69);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (201.14,205.51) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (202.60,211.17) --
+	(202.72,211.17);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (202.66,211.10) --
+	(202.66,211.24);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.66,207.13) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (150.14,164.27) --
+	(151.93,164.27);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (151.06,163.33) --
+	(151.06,165.16);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (151.06,161.36) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (151.93,166.26) --
+	(153.73,166.26);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (152.85,165.31) --
+	(152.85,167.17);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (152.85,162.23) {$l$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (161.33,177.29) --
+	(163.53,177.29);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (162.46,176.45) --
+	(162.46,178.09);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (162.46,174.38) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (206.24,212.06) --
+	(206.41,212.06);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (206.33,211.97) --
+	(206.33,212.15);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (206.33,209.16) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (172.89,188.00) --
+	(173.91,188.00);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (173.41,187.53) --
+	(173.41,188.46);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.41,184.78) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (199.47,204.74) --
+	(200.11,204.74);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (199.79,204.49) --
+	(199.79,204.98);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.79,201.83) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (199.10,205.92) --
+	(199.21,205.92);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (199.16,205.85) --
+	(199.16,205.99);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.16,201.89) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (170.85,180.99) --
+	(171.73,180.99);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (171.29,180.61) --
+	(171.29,181.38);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.29,178.09) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (171.69,182.05) --
+	(172.60,182.05);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (172.15,181.65) --
+	(172.15,182.43);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.15,178.01) {$l$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (164.95,184.96) --
+	(165.84,184.96);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (165.40,184.47) --
+	(165.40,185.43);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (165.40,182.05) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (205.28,211.72) --
+	(205.47,211.72);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (205.37,211.62) --
+	(205.37,211.82);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.37,208.81) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (146.63,181.61) --
+	(150.03,181.61);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (148.41,181.10) --
+	(148.41,182.11);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (148.41,178.39) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (180.13,179.82) --
+	(180.48,179.82);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (180.31,179.53) --
+	(180.31,180.10);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.31,176.91) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (181.44,186.49) --
+	(181.71,186.49);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (181.58,186.37) --
+	(181.58,186.61);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.58,182.46) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (142.47,153.59) --
+	(144.44,153.59);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (143.48,152.97) --
+	(143.48,154.18);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (143.48,150.68) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (142.27,153.47) --
+	(143.96,153.47);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (143.13,152.81) --
+	(143.13,154.10);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (143.13,149.43) {$l$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (124.71,169.68) --
+	(128.29,169.68);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (126.58,168.90) --
+	(126.58,170.43);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (126.58,166.78) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (187.63,193.83) --
+	(187.94,193.83);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (187.79,193.75) --
+	(187.79,193.91);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.79,190.93) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (183.05,198.53) --
+	(184.50,198.53);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (183.79,197.25) --
+	(183.79,199.73);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.79,195.31) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (196.95,215.00) --
+	(197.77,215.00);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (197.37,214.67) --
+	(197.37,215.33);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.37,212.09) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (204.49,227.14) --
+	(204.60,227.14);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (204.54,227.10) --
+	(204.54,227.18);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (204.54,223.10) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (182.64,208.59) --
+	(183.24,208.59);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (182.95,208.25) --
+	(182.95,208.93);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.95,205.69) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (190.24,213.86) --
+	(190.85,213.86);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (190.55,213.60) --
+	(190.55,214.11);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.55,209.82) {$l$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (183.06,202.16) --
+	(183.95,202.16);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (183.51,201.86) --
+	(183.51,202.47);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.51,199.26) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (210.55,218.62) --
+	(210.84,218.62);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (210.69,218.51) --
+	(210.69,218.73);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.69,215.72) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (194.50,210.63) --
+	(195.50,210.63);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (195.01,210.27) --
+	(195.01,210.98);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.01,207.40) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (201.18,209.87) --
+	(201.72,209.87);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (201.45,209.58) --
+	(201.45,210.16);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (201.45,206.97) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (202.87,214.59) --
+	(202.96,214.59);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (202.91,214.53) --
+	(202.91,214.66);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.91,210.56) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (168.49,182.02) --
+	(169.65,182.02);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (169.08,181.38) --
+	(169.08,182.64);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.08,179.12) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (168.95,182.45) --
+	(170.24,182.45);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (169.61,181.82) --
+	(169.61,183.06);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.61,178.42) {$l$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (171.83,194.50) --
+	(172.88,194.50);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (172.36,194.04) --
+	(172.36,194.95);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.36,191.59) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (209.23,223.51) --
+	(209.75,223.51);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (209.49,223.34) --
+	(209.49,223.68);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.49,220.61) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (176.60,191.94) --
+	(177.32,191.94);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (176.97,191.51) --
+	(176.97,192.36);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.97,188.71) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (181.73,193.85) --
+	(183.28,193.85);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (182.52,192.19) --
+	(182.52,195.37);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.52,190.94) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (184.33,199.93) --
+	(184.46,199.93);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (184.39,199.84) --
+	(184.39,200.03);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.39,195.90) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (165.35,184.49) --
+	(166.69,184.49);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (166.03,184.16) --
+	(166.03,184.81);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (166.03,181.59) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (166.74,183.89) --
+	(168.37,183.89);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (167.57,183.57) --
+	(167.57,184.20);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (167.57,179.85) {$l$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (169.70,191.90) --
+	(170.47,191.90);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (170.09,191.51) --
+	(170.09,192.28);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (170.09,189.00) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (202.44,212.25) --
+	(202.70,212.25);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (202.57,212.14) --
+	(202.57,212.37);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.57,209.35) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (181.11,198.78) --
+	(181.87,198.78);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (181.49,198.34) --
+	(181.49,199.21);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.49,195.56) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (179.57,194.92) --
+	(180.70,194.92);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (180.14,194.27) --
+	(180.14,195.55);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.14,192.02) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (190.89,211.83) --
+	(191.00,211.83);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (190.95,211.76) --
+	(190.95,211.89);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.95,207.79) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (173.90,201.08) --
+	(174.58,201.08);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (174.24,200.86) --
+	(174.24,201.30);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.24,198.18) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (180.19,206.71) --
+	(180.87,206.71);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (180.53,206.45) --
+	(180.53,206.96);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.53,202.67) {$l$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (178.05,200.92) --
+	(178.81,200.92);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (178.44,200.40) --
+	(178.44,201.41);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (178.44,198.01) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (210.42,223.09) --
+	(210.73,223.09);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (210.58,222.89) --
+	(210.58,223.29);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.58,220.18) {$\kappa$};
 \end{scope}
@@
 
-\path[fill=fillColor] (485.73,232.77) circle (  1.87);
-
-\path[fill=fillColor] (485.73, 55.06) --
-	(488.24, 50.70) --
-	(483.21, 50.70) --
+\path[fill=fillColor] (356.88,165.22) circle (  1.87);
+
+\path[fill=fillColor] (356.88, 79.54) --
+	(359.40, 75.18) --
+	(354.37, 75.18) --
 	cycle;
@@
 
-\path[fill=fillColor] (356.88,165.38) circle (  1.87);
-
-\path[fill=fillColor] (356.88, 80.00) --
-	(359.40, 75.65) --
-	(354.37, 75.65) --
+\path[fill=fillColor] (394.78,165.34) circle (  1.87);
+
+\path[fill=fillColor] (394.78, 79.41) --
+	(397.29, 75.05) --
+	(392.26, 75.05) --
 	cycle;
@@
 
-\path[fill=fillColor] (394.78,149.36) circle (  1.87);
-
-\path[fill=fillColor] (394.78, 80.07) --
-	(397.29, 75.72) --
-	(392.26, 75.72) --
+\path[fill=fillColor] (390.04,192.10) circle (  1.87);
+
+\path[fill=fillColor] (390.04, 71.80) --
+	(392.55, 67.44) --
+	(387.52, 67.44) --
 	cycle;
@@
 
-\path[fill=fillColor] (390.04,184.14) circle (  1.87);
-
-\path[fill=fillColor] (390.04, 69.81) --
-	(392.55, 65.46) --
-	(387.52, 65.46) --
+\path[fill=fillColor] (404.25,216.47) circle (  1.87);
+
+\path[fill=fillColor] (404.25, 59.60) --
+	(406.77, 55.24) --
+	(401.74, 55.24) --
 	cycle;
@@
 
-\path[fill=fillColor] (404.25,211.12) circle (  1.87);
-
-\path[fill=fillColor] (404.25, 60.31) --
-	(406.77, 55.95) --
-	(401.74, 55.95) --
+\path[fill=fillColor] (359.72,107.37) circle (  1.87);
+
+\path[fill=fillColor] (359.72, 91.15) --
+	(362.24, 86.80) --
+	(357.21, 86.80) --
 	cycle;
@@
 
-\path[fill=fillColor] (359.72,111.61) circle (  1.87);
-
-\path[fill=fillColor] (359.72, 94.33) --
-	(362.24, 89.97) --
-	(357.21, 89.97) --
+\path[fill=fillColor] (433.62,203.66) circle (  1.87);
+
+\path[fill=fillColor] (433.62, 68.80) --
+	(436.14, 64.44) --
+	(431.10, 64.44) --
 	cycle;
@@
 
-\path[fill=fillColor] (433.62,198.59) circle (  1.87);
-
-\path[fill=fillColor] (433.62, 71.59) --
-	(436.14, 67.23) --
-	(431.10, 67.23) --
+\path[fill=fillColor] (359.72,137.48) circle (  1.87);
+
+\path[fill=fillColor] (359.72, 88.39) --
+	(362.24, 84.03) --
+	(357.21, 84.03) --
 	cycle;
@@
 
-\path[fill=fillColor] (359.72,131.32) circle (  1.87);
-
-\path[fill=fillColor] (359.72, 82.69) --
-	(362.24, 78.34) --
-	(357.21, 78.34) --
+\path[fill=fillColor] (346.46,129.05) circle (  1.87);
+
+\path[fill=fillColor] (346.46, 89.93) --
+	(348.97, 85.57) --
+	(343.94, 85.57) --
 	cycle;
@@
 \node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
-\definecolor{fillColor}{RGB}{68,68,68}
-
-\path[fill=fillColor] (346.46,125.73) circle (  1.87);
-
-\path[fill=fillColor] (346.46, 76.98) --
-	(348.97, 72.63) --
-	(343.94, 72.63) --
-	cycle;
-\definecolor{fillColor}{RGB}{0,0,0}
-
-\path[fill=fillColor] (435.32,150.27) circle (  2.15);
-
-\path[fill=fillColor] (435.32,142.15) --
-	(438.21,137.14) --
-	(432.42,137.14) --
-	cycle;
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,146.98) {\texttt{ConstantDistance}};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,115.46) --
-	(339.26,115.86) --
-	(339.64,116.25) --
-	(340.02,116.65) --
-	(340.40,117.05) --
-	(340.78,117.45) --
-	(341.16,117.85) --
-	(341.54,118.25) --
-	(341.92,118.65) --
-	(342.30,119.06) --
-	(342.68,119.46) --
-	(343.06,119.87) --
-	(343.44,120.27) --
-	(343.82,120.68) --
-	(344.20,121.09) --
-	(344.58,121.50) --
-	(344.96,121.91) --
-	(345.34,122.32) --
-	(345.71,122.73) --
-	(346.09,123.14) --
-	(346.47,123.56) --
-	(346.85,123.97) --
-	(347.23,124.39) --
-	(347.61,124.80) --
-	(347.99,125.22) --
-	(348.37,125.64) --
-	(348.75,126.06) --
-	(349.13,126.48) --
-	(349.51,126.90) --
-	(349.89,127.32) --
-	(350.27,127.74) --
-	(350.65,128.16) --
-	(351.03,128.58) --
-	(351.41,129.01) --
-	(351.79,129.43) --
-	(352.17,129.85) --
-	(352.55,130.28) --
-	(352.93,130.71) --
-	(353.31,131.13) --
-	(353.69,131.56) --
-	(354.07,131.99) --
-	(354.45,132.42) --
-	(354.83,132.84) --
-	(355.21,133.27) --
-	(355.59,133.70) --
-	(355.97,134.13) --
-	(356.35,134.56) --
-	(356.73,134.99) --
-	(357.11,135.43) --
-	(357.49,135.86) --
-	(357.87,136.29) --
-	(358.25,136.72) --
-	(358.63,137.15) --
-	(359.01,137.59) --
-	(359.38,138.02) --
-	(359.76,138.45) --
-	(360.14,138.89) --
-	(360.52,139.32) --
-	(360.90,139.76) --
-	(361.28,140.19) --
-	(361.66,140.63) --
-	(362.04,141.06) --
-	(362.42,141.50) --
-	(362.80,141.93) --
-	(363.18,142.37) --
-	(363.56,142.80) --
-	(363.94,143.24) --
-	(364.32,143.67) --
-	(364.70,144.11) --
-	(365.08,144.54) --
-	(365.46,144.98) --
-	(365.84,145.41) --
-	(366.22,145.85) --
-	(366.60,146.28) --
-	(366.98,146.72) --
-	(367.36,147.16) --
-	(367.74,147.59) --
-	(368.12,148.03) --
-	(368.50,148.46) --
-	(368.88,148.89) --
-	(369.26,149.33) --
-	(369.64,149.76) --
-	(370.02,150.20) --
-	(370.40,150.63) --
-	(370.78,151.07) --
-	(371.16,151.50) --
-	(371.54,151.93) --
-	(371.92,152.36) --
-	(372.30,152.80) --
-	(372.68,153.23) --
-	(373.05,153.66) --
-	(373.43,154.09) --
-	(373.81,154.52) --
-	(374.19,154.95) --
-	(374.57,155.38) --
-	(374.95,155.81) --
-	(375.33,156.24) --
-	(375.71,156.67) --
-	(376.09,157.10) --
-	(376.47,157.53) --
-	(376.85,157.95) --
-	(377.23,158.38) --
-	(377.61,158.81) --
-	(377.99,159.23) --
-	(378.37,159.66) --
-	(378.75,160.08) --
-	(379.13,160.50) --
-	(379.51,160.93) --
-	(379.89,161.35) --
-	(380.27,161.77) --
-	(380.65,162.19) --
-	(381.03,162.61) --
-	(381.41,163.03) --
-	(381.79,163.45) --
-	(382.17,163.87) --
-	(382.55,164.28) --
-	(382.93,164.70) --
-	(383.31,165.11) --
-	(383.69,165.53) --
-	(384.07,165.94) --
-	(384.45,166.36) --
-	(384.83,166.77) --
-	(385.21,167.18) --
-	(385.59,167.59) --
-	(385.97,168.00) --
-	(386.34,168.41) --
-	(386.72,168.81) --
-	(387.10,169.22) --
-	(387.48,169.63) --
-	(387.86,170.03) --
-	(388.24,170.43) --
-	(388.62,170.84) --
-	(389.00,171.24) --
-	(389.38,171.64) --
-	(389.76,172.04) --
-	(390.14,172.44) --
-	(390.52,172.83) --
-	(390.90,173.23) --
-	(391.28,173.62) --
-	(391.66,174.02) --
-	(392.04,174.41) --
-	(392.42,174.80) --
-	(392.80,175.19) --
-	(393.18,175.58) --
-	(393.56,175.97) --
-	(393.94,176.36) --
-	(394.32,176.74) --
-	(394.70,177.13) --
-	(395.08,177.51) --
-	(395.46,177.89) --
-	(395.84,178.27) --
-	(396.22,178.65) --
-	(396.60,179.03) --
-	(396.98,179.41) --
-	(397.36,179.79) --
-	(397.74,180.16) --
-	(398.12,180.53) --
-	(398.50,180.91) --
-	(398.88,181.28) --
-	(399.26,181.65) --
-	(399.64,182.01) --
-	(400.01,182.38) --
-	(400.39,182.75) --
-	(400.77,183.11) --
-	(401.15,183.47) --
-	(401.53,183.83) --
-	(401.91,184.19) --
-	(402.29,184.55) --
-	(402.67,184.91) --
-	(403.05,185.26) --
-	(403.43,185.62) --
-	(403.81,185.97) --
-	(404.19,186.32) --
-	(404.57,186.67) --
-	(404.95,187.02) --
-	(405.33,187.37) --
-	(405.71,187.71) --
-	(406.09,188.06) --
-	(406.47,188.40) --
-	(406.85,188.74) --
-	(407.23,189.08) --
-	(407.61,189.42) --
-	(407.99,189.76) --
-	(408.37,190.09) --
-	(408.75,190.43) --
-	(409.13,190.76) --
-	(409.51,191.09) --
-	(409.89,191.42) --
-	(410.27,191.75) --
-	(410.65,192.08) --
-	(411.03,192.40) --
-	(411.41,192.73) --
-	(411.79,193.05) --
-	(412.17,193.37) --
-	(412.55,193.69) --
-	(412.93,194.00) --
-	(413.31,194.32) --
-	(413.68,194.64) --
-	(414.06,194.95) --
-	(414.44,195.26) --
-	(414.82,195.57) --
-	(415.20,195.88) --
-	(415.58,196.18) --
-	(415.96,196.49) --
-	(416.34,196.79) --
-	(416.72,197.10) --
-	(417.10,197.40) --
-	(417.48,197.70) --
-	(417.86,197.99) --
-	(418.24,198.29) --
-	(418.62,198.58) --
-	(419.00,198.88) --
-	(419.38,199.17) --
-	(419.76,199.46) --
-	(420.14,199.75) --
-	(420.52,200.03) --
-	(420.90,200.32) --
-	(421.28,200.60) --
-	(421.66,200.89) --
-	(422.04,201.17) --
-	(422.42,201.45) --
-	(422.80,201.72) --
-	(423.18,202.00) --
-	(423.56,202.27) --
-	(423.94,202.55) --
-	(424.32,202.82) --
-	(424.70,203.09) --
-	(425.08,203.36) --
-	(425.46,203.62) --
-	(425.84,203.89) --
-	(426.22,204.15) --
-	(426.60,204.41) --
-	(426.97,204.68) --
-	(427.35,204.93) --
-	(427.73,205.19) --
-	(428.11,205.45) --
-	(428.49,205.70) --
-	(428.87,205.96) --
-	(429.25,206.21) --
-	(429.63,206.46) --
-	(430.01,206.71) --
-	(430.39,206.95) --
-	(430.77,207.20) --
-	(431.15,207.44) --
-	(431.53,207.69) --
-	(431.91,207.93) --
-	(432.29,208.17) --
-	(432.67,208.41) --
-	(433.05,208.64) --
-	(433.43,208.88) --
-	(433.81,209.11) --
-	(434.19,209.35) --
-	(434.57,209.58) --
-	(434.95,209.81) --
-	(435.33,210.03) --
-	(435.71,210.26) --
-	(436.09,210.49) --
-	(436.47,210.71) --
-	(436.85,210.93) --
-	(437.23,211.15) --
-	(437.61,211.37) --
-	(437.99,211.59) --
-	(438.37,211.81) --
-	(438.75,212.02) --
-	(439.13,212.24) --
-	(439.51,212.45) --
-	(439.89,212.66) --
-	(440.27,212.87) --
-	(440.64,213.08) --
-	(441.02,213.28) --
-	(441.40,213.49) --
-	(441.78,213.69) --
-	(442.16,213.90) --
-	(442.54,214.10) --
-	(442.92,214.30) --
-	(443.30,214.50) --
-	(443.68,214.69) --
-	(444.06,214.89) --
-	(444.44,215.09) --
-	(444.82,215.28) --
-	(445.20,215.47) --
-	(445.58,215.66) --
-	(445.96,215.85) --
-	(446.34,216.04) --
-	(446.72,216.23) --
-	(447.10,216.41) --
-	(447.48,216.60) --
-	(447.86,216.78) --
-	(448.24,216.96) --
-	(448.62,217.14) --
-	(449.00,217.32) --
-	(449.38,217.50) --
-	(449.76,217.67) --
-	(450.14,217.85) --
-	(450.52,218.02) --
-	(450.90,218.20) --
-	(451.28,218.37) --
-	(451.66,218.54) --
-	(452.04,218.71) --
-	(452.42,218.88) --
-	(452.80,219.04) --
-	(453.18,219.21) --
-	(453.56,219.37) --
-	(453.93,219.54) --
-	(454.31,219.70) --
-	(454.69,219.86) --
-	(455.07,220.02) --
-	(455.45,220.18) --
-	(455.83,220.33) --
-	(456.21,220.49) --
-	(456.59,220.65) --
-	(456.97,220.80) --
-	(457.35,220.95) --
-	(457.73,221.10) --
-	(458.11,221.25) --
-	(458.49,221.40) --
-	(458.87,221.55) --
-	(459.25,221.70) --
-	(459.63,221.85) --
-	(460.01,221.99) --
-	(460.39,222.13) --
-	(460.77,222.28) --
-	(461.15,222.42) --
-	(461.53,222.56) --
-	(461.91,222.70) --
-	(462.29,222.84) --
-	(462.67,222.98) --
-	(463.05,223.11) --
-	(463.43,223.25) --
-	(463.81,223.38) --
-	(464.19,223.52) --
-	(464.57,223.65) --
-	(464.95,223.78) --
-	(465.33,223.91) --
-	(465.71,224.04) --
-	(466.09,224.17) --
-	(466.47,224.29) --
-	(466.85,224.42) --
-	(467.23,224.55) --
-	(467.60,224.67) --
-	(467.98,224.79) --
-	(468.36,224.92) --
-	(468.74,225.04) --
-	(469.12,225.16) --
-	(469.50,225.28) --
-	(469.88,225.40) --
-	(470.26,225.51) --
-	(470.64,225.63) --
-	(471.02,225.75) --
-	(471.40,225.86) --
-	(471.78,225.98) --
-	(472.16,226.09) --
-	(472.54,226.20) --
-	(472.92,226.31) --
-	(473.30,226.42) --
-	(473.68,226.53) --
-	(474.06,226.64) --
-	(474.44,226.75) --
-	(474.82,226.86) --
-	(475.20,226.96) --
-	(475.58,227.07) --
-	(475.96,227.17) --
-	(476.34,227.28) --
-	(476.72,227.38) --
-	(477.10,227.48) --
-	(477.48,227.59) --
-	(477.86,227.69) --
-	(478.24,227.79) --
-	(478.62,227.88) --
-	(479.00,227.98) --
-	(479.38,228.08) --
-	(479.76,228.18) --
-	(480.14,228.27) --
-	(480.52,228.37) --
-	(480.90,228.46) --
-	(481.27,228.55) --
-	(481.65,228.65) --
-	(482.03,228.74) --
-	(482.41,228.83) --
-	(482.79,228.92) --
-	(483.17,229.01) --
-	(483.55,229.10) --
-	(483.93,229.19) --
-	(484.31,229.27) --
-	(484.69,229.36) --
-	(485.07,229.45) --
-	(485.45,229.53) --
-	(485.83,229.62) --
-	(486.21,229.70) --
-	(486.59,229.78) --
-	(486.97,229.87) --
-	(487.35,229.95) --
-	(487.73,230.03) --
-	(488.11,230.11) --
-	(488.49,230.19) --
-	(488.87,230.27) --
-	(489.25,230.35) --
-	(489.63,230.43) --
-	(490.01,230.50) --
-	(490.39,230.58) --
-	(490.77,230.66) --
-	(491.15,230.73) --
-	(491.53,230.81) --
-	(491.91,230.88) --
-	(492.29,230.95) --
-	(492.67,231.03) --
-	(493.05,231.10) --
-	(493.43,231.17) --
-	(493.81,231.24) --
-	(494.19,231.31) --
-	(494.56,231.38) --
-	(494.94,231.45) --
-	(495.32,231.52) --
-	(495.70,231.59) --
-	(496.08,231.66) --
-	(496.46,231.72) --
-	(496.84,231.79) --
-	(497.22,231.86) --
-	(497.60,231.92) --
-	(497.98,231.99) --
-	(498.36,232.05) --
-	(498.74,232.11) --
-	(499.12,232.18) --
-	(499.50,232.24) --
-	(499.88,232.30) --
-	(500.26,232.36) --
-	(500.64,232.42) --
-	(501.02,232.48) --
-	(501.40,232.54) --
-	(501.78,232.60) --
-	(502.16,232.66) --
-	(502.54,232.72) --
-	(502.92,232.78) --
-	(503.30,232.84) --
-	(503.68,232.89) --
-	(504.06,232.95) --
-	(504.44,233.01) --
-	(504.82,233.06) --
-	(505.20,233.12) --
-	(505.58,233.17) --
-	(505.96,233.23) --
-	(506.34,233.28) --
-	(506.72,233.33) --
-	(507.10,233.38) --
-	(507.48,233.44) --
-	(507.86,233.49) --
-	(508.23,233.54) --
-	(508.61,233.59) --
-	(508.99,233.64) --
-	(509.37,233.69) --
-	(509.75,233.74) --
-	(510.13,233.79) --
-	(510.51,233.84) --
-	(510.89,233.89) --
-	(511.27,233.94) --
-	(511.65,233.98) --
-	(512.03,234.03) --
-	(512.41,234.08) --
-	(512.79,234.12) --
-	(513.17,234.17) --
-	(513.55,234.21) --
-	(513.93,234.26) --
-	(514.31,234.30) --
-	(514.69,234.35) --
-	(515.07,234.39) --
-	(515.45,234.44) --
-	(515.83,234.48) --
-	(516.21,234.52) --
-	(516.59,234.57) --
-	(516.97,234.61) --
-	(517.35,234.65) --
-	(517.73,234.69) --
-	(518.11,234.73) --
-	(518.49,234.77) --
-	(518.87,234.81) --
-	(519.25,234.85) --
-	(519.63,234.89) --
-	(520.01,234.93) --
-	(520.39,234.97) --
-	(520.77,235.01) --
-	(521.15,235.05) --
-	(521.53,235.08) --
-	(521.90,235.12) --
-	(522.28,235.16) --
-	(522.66,235.20) --
-	(523.04,235.23) --
-	(523.42,235.27) --
-	(523.80,235.30) --
-	(524.18,235.34) --
-	(524.56,235.38) --
-	(524.94,235.41) --
-	(525.32,235.45) --
-	(525.70,235.48) --
-	(526.08,235.51) --
-	(526.46,235.55) --
-	(526.84,235.58) --
-	(527.22,235.61) --
-	(527.60,235.65) --
-	(527.98,235.68) --
-	(528.36,235.71);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 86.82) --
-	(339.26, 86.66) --
-	(339.64, 86.51) --
-	(340.02, 86.35) --
-	(340.40, 86.20) --
-	(340.78, 86.04) --
-	(341.16, 85.89) --
-	(341.54, 85.74) --
-	(341.92, 85.58) --
-	(342.30, 85.43) --
-	(342.68, 85.28) --
-	(343.06, 85.13) --
-	(343.44, 84.98) --
-	(343.82, 84.83) --
-	(344.20, 84.68) --
-	(344.58, 84.53) --
-	(344.96, 84.38) --
-	(345.34, 84.24) --
-	(345.71, 84.09) --
-	(346.09, 83.94) --
-	(346.47, 83.80) --
-	(346.85, 83.65) --
-	(347.23, 83.50) --
-	(347.61, 83.36) --
-	(347.99, 83.21) --
-	(348.37, 83.07) --
-	(348.75, 82.93) --
-	(349.13, 82.78) --
-	(349.51, 82.64) --
-	(349.89, 82.50) --
-	(350.27, 82.36) --
-	(350.65, 82.22) --
-	(351.03, 82.08) --
-	(351.41, 81.94) --
-	(351.79, 81.80) --
-	(352.17, 81.66) --
-	(352.55, 81.52) --
-	(352.93, 81.38) --
-	(353.31, 81.24) --
-	(353.69, 81.11) --
-	(354.07, 80.97) --
-	(354.45, 80.83) --
-	(354.83, 80.70) --
-	(355.21, 80.56) --
-	(355.59, 80.43) --
-	(355.97, 80.29) --
-	(356.35, 80.16) --
-	(356.73, 80.03) --
-	(357.11, 79.89) --
-	(357.49, 79.76) --
-	(357.87, 79.63) --
-	(358.25, 79.50) --
-	(358.63, 79.37) --
-	(359.01, 79.24) --
-	(359.38, 79.11) --
-	(359.76, 78.98) --
-	(360.14, 78.85) --
-	(360.52, 78.72) --
-	(360.90, 78.59) --
-	(361.28, 78.46) --
-	(361.66, 78.34) --
-	(362.04, 78.21) --
-	(362.42, 78.08) --
-	(362.80, 77.96) --
-	(363.18, 77.83) --
-	(363.56, 77.71) --
-	(363.94, 77.58) --
-	(364.32, 77.46) --
-	(364.70, 77.33) --
-	(365.08, 77.21) --
-	(365.46, 77.09) --
-	(365.84, 76.97) --
-	(366.22, 76.85) --
-	(366.60, 76.72) --
-	(366.98, 76.60) --
-	(367.36, 76.48) --
-	(367.74, 76.36) --
-	(368.12, 76.24) --
-	(368.50, 76.12) --
-	(368.88, 76.01) --
-	(369.26, 75.89) --
-	(369.64, 75.77) --
-	(370.02, 75.65) --
-	(370.40, 75.54) --
-	(370.78, 75.42) --
-	(371.16, 75.30) --
-	(371.54, 75.19) --
-	(371.92, 75.07) --
-	(372.30, 74.96) --
-	(372.68, 74.85) --
-	(373.05, 74.73) --
-	(373.43, 74.62) --
-	(373.81, 74.51) --
-	(374.19, 74.39) --
-	(374.57, 74.28) --
-	(374.95, 74.17) --
-	(375.33, 74.06) --
-	(375.71, 73.95) --
-	(376.09, 73.84) --
-	(376.47, 73.73) --
-	(376.85, 73.62) --
-	(377.23, 73.51) --
-	(377.61, 73.40) --
-	(377.99, 73.29) --
-	(378.37, 73.19) --
-	(378.75, 73.08) --
-	(379.13, 72.97) --
-	(379.51, 72.87) --
-	(379.89, 72.76) --
-	(380.27, 72.65) --
-	(380.65, 72.55) --
-	(381.03, 72.44) --
-	(381.41, 72.34) --
-	(381.79, 72.24) --
-	(382.17, 72.13) --
-	(382.55, 72.03) --
-	(382.93, 71.93) --
-	(383.31, 71.83) --
-	(383.69, 71.72) --
-	(384.07, 71.62) --
-	(384.45, 71.52) --
-	(384.83, 71.42) --
-	(385.21, 71.32) --
-	(385.59, 71.22) --
-	(385.97, 71.12) --
-	(386.34, 71.02) --
-	(386.72, 70.92) --
-	(387.10, 70.83) --
-	(387.48, 70.73) --
-	(387.86, 70.63) --
-	(388.24, 70.53) --
-	(388.62, 70.44) --
-	(389.00, 70.34) --
-	(389.38, 70.25) --
-	(389.76, 70.15) --
-	(390.14, 70.06) --
-	(390.52, 69.96) --
-	(390.90, 69.87) --
-	(391.28, 69.77) --
-	(391.66, 69.68) --
-	(392.04, 69.59) --
-	(392.42, 69.49) --
-	(392.80, 69.40) --
-	(393.18, 69.31) --
-	(393.56, 69.22) --
-	(393.94, 69.13) --
-	(394.32, 69.04) --
-	(394.70, 68.95) --
-	(395.08, 68.86) --
-	(395.46, 68.77) --
-	(395.84, 68.68) --
-	(396.22, 68.59) --
-	(396.60, 68.50) --
-	(396.98, 68.41) --
-	(397.36, 68.32) --
-	(397.74, 68.24) --
-	(398.12, 68.15) --
-	(398.50, 68.06) --
-	(398.88, 67.98) --
-	(399.26, 67.89) --
-	(399.64, 67.80) --
-	(400.01, 67.72) --
-	(400.39, 67.63) --
-	(400.77, 67.55) --
-	(401.15, 67.47) --
-	(401.53, 67.38) --
-	(401.91, 67.30) --
-	(402.29, 67.22) --
-	(402.67, 67.13) --
-	(403.05, 67.05) --
-	(403.43, 66.97) --
-	(403.81, 66.89) --
-	(404.19, 66.81) --
-	(404.57, 66.73) --
-	(404.95, 66.64) --
-	(405.33, 66.56) --
-	(405.71, 66.48) --
-	(406.09, 66.40) --
-	(406.47, 66.33) --
-	(406.85, 66.25) --
-	(407.23, 66.17) --
-	(407.61, 66.09) --
-	(407.99, 66.01) --
-	(408.37, 65.93) --
-	(408.75, 65.86) --
-	(409.13, 65.78) --
-	(409.51, 65.70) --
-	(409.89, 65.63) --
-	(410.27, 65.55) --
-	(410.65, 65.48) --
-	(411.03, 65.40) --
-	(411.41, 65.33) --
-	(411.79, 65.25) --
-	(412.17, 65.18) --
-	(412.55, 65.10) --
-	(412.93, 65.03) --
-	(413.31, 64.96) --
-	(413.68, 64.88) --
-	(414.06, 64.81) --
-	(414.44, 64.74) --
-	(414.82, 64.67) --
-	(415.20, 64.60) --
-	(415.58, 64.52) --
-	(415.96, 64.45) --
-	(416.34, 64.38) --
-	(416.72, 64.31) --
-	(417.10, 64.24) --
-	(417.48, 64.17) --
-	(417.86, 64.10) --
-	(418.24, 64.03) --
-	(418.62, 63.97) --
-	(419.00, 63.90) --
-	(419.38, 63.83) --
-	(419.76, 63.76) --
-	(420.14, 63.69) --
-	(420.52, 63.63) --
-	(420.90, 63.56) --
-	(421.28, 63.49) --
-	(421.66, 63.43) --
-	(422.04, 63.36) --
-	(422.42, 63.29) --
-	(422.80, 63.23) --
-	(423.18, 63.16) --
-	(423.56, 63.10) --
-	(423.94, 63.03) --
-	(424.32, 62.97) --
-	(424.70, 62.91) --
-	(425.08, 62.84) --
-	(425.46, 62.78) --
-	(425.84, 62.72) --
-	(426.22, 62.65) --
-	(426.60, 62.59) --
-	(426.97, 62.53) --
-	(427.35, 62.47) --
-	(427.73, 62.40) --
-	(428.11, 62.34) --
-	(428.49, 62.28) --
-	(428.87, 62.22) --
-	(429.25, 62.16) --
-	(429.63, 62.10) --
-	(430.01, 62.04) --
-	(430.39, 61.98) --
-	(430.77, 61.92) --
-	(431.15, 61.86) --
-	(431.53, 61.80) --
-	(431.91, 61.74) --
-	(432.29, 61.68) --
-	(432.67, 61.63) --
-	(433.05, 61.57) --
-	(433.43, 61.51) --
-	(433.81, 61.45) --
-	(434.19, 61.40) --
-	(434.57, 61.34) --
-	(434.95, 61.28) --
-	(435.33, 61.23) --
-	(435.71, 61.17) --
-	(436.09, 61.11) --
-	(436.47, 61.06) --
-	(436.85, 61.00) --
-	(437.23, 60.95) --
-	(437.61, 60.89) --
-	(437.99, 60.84) --
-	(438.37, 60.78) --
-	(438.75, 60.73) --
-	(439.13, 60.68) --
-	(439.51, 60.62) --
-	(439.89, 60.57) --
-	(440.27, 60.52) --
-	(440.64, 60.46) --
-	(441.02, 60.41) --
-	(441.40, 60.36) --
-	(441.78, 60.31) --
-	(442.16, 60.25) --
-	(442.54, 60.20) --
-	(442.92, 60.15) --
-	(443.30, 60.10) --
-	(443.68, 60.05) --
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (338.88,117.32) --
+	(339.26,117.75) --
+	(339.64,118.18) --
+	(340.02,118.61) --
+	(340.40,119.05) --
+	(340.78,119.48) --
+	(341.16,119.92) --
+	(341.54,120.35) --
+	(341.92,120.79) --
+	(342.30,121.23) --
+	(342.68,121.67) --
+	(343.06,122.11) --
+	(343.44,122.55) --
+	(343.82,123.00) --
+	(344.20,123.44) --
+	(344.58,123.89) --
+	(344.96,124.33) --
+	(345.34,124.78) --
+	(345.71,125.23) --
+	(346.09,125.68) --
+	(346.47,126.13) --
+	(346.85,126.58) --
+	(347.23,127.03) --
+	(347.61,127.48) --
+	(347.99,127.93) --
+	(348.37,128.39) --
+	(348.75,128.84) --
+	(349.13,129.30) --
+	(349.51,129.75) --
+	(349.89,130.21) --
+	(350.27,130.67) --
+	(350.65,131.13) --
+	(351.03,131.59) --
+	(351.41,132.05) --
+	(351.79,132.51) --
+	(352.17,132.97) --
+	(352.55,133.43) --
+	(352.93,133.89) --
+	(353.31,134.35) --
+	(353.69,134.81) --
+	(354.07,135.28) --
+	(354.45,135.74) --
+	(354.83,136.20) --
+	(355.21,136.67) --
+	(355.59,137.13) --
+	(355.97,137.60) --
+	(356.35,138.06) --
+	(356.73,138.53) --
+	(357.11,139.00) --
+	(357.49,139.46) --
+	(357.87,139.93) --
+	(358.25,140.40) --
+	(358.63,140.86) --
+	(359.01,141.33) --
+	(359.38,141.80) --
+	(359.76,142.27) --
+	(360.14,142.73) --
+	(360.52,143.20) --
+	(360.90,143.67) --
+	(361.28,144.14) --
+	(361.66,144.61) --
+	(362.04,145.07) --
+	(362.42,145.54) --
+	(362.80,146.01) --
+	(363.18,146.48) --
+	(363.56,146.94) --
+	(363.94,147.41) --
+	(364.32,147.88) --
+	(364.70,148.35) --
+	(365.08,148.81) --
+	(365.46,149.28) --
+	(365.84,149.75) --
+	(366.22,150.21) --
+	(366.60,150.68) --
+	(366.98,151.14) --
+	(367.36,151.61) --
+	(367.74,152.08) --
+	(368.12,152.54) --
+	(368.50,153.00) --
+	(368.88,153.47) --
+	(369.26,153.93) --
+	(369.64,154.40) --
+	(370.02,154.86) --
+	(370.40,155.32) --
+	(370.78,155.78) --
+	(371.16,156.24) --
+	(371.54,156.70) --
+	(371.92,157.16) --
+	(372.30,157.62) --
+	(372.68,158.08) --
+	(373.05,158.54) --
+	(373.43,159.00) --
+	(373.81,159.45) --
+	(374.19,159.91) --
+	(374.57,160.36) --
+	(374.95,160.82) --
+	(375.33,161.27) --
+	(375.71,161.73) --
+	(376.09,162.18) --
+	(376.47,162.63) --
+	(376.85,163.08) --
+	(377.23,163.53) --
+	(377.61,163.98) --
+	(377.99,164.42) --
+	(378.37,164.87) --
+	(378.75,165.32) --
+	(379.13,165.76) --
+	(379.51,166.21) --
+	(379.89,166.65) --
+	(380.27,167.09) --
+	(380.65,167.53) --
+	(381.03,167.97) --
+	(381.41,168.41) --
+	(381.79,168.85) --
+	(382.17,169.28) --
+	(382.55,169.72) --
+	(382.93,170.15) --
+	(383.31,170.59) --
+	(383.69,171.02) --
+	(384.07,171.45) --
+	(384.45,171.88) --
+	(384.83,172.31) --
+	(385.21,172.74) --
+	(385.59,173.16) --
+	(385.97,173.59) --
+	(386.34,174.01) --
+	(386.72,174.43) --
+	(387.10,174.85) --
+	(387.48,175.27) --
+	(387.86,175.69) --
+	(388.24,176.11) --
+	(388.62,176.52) --
+	(389.00,176.93) --
+	(389.38,177.35) --
+	(389.76,177.76) --
+	(390.14,178.17) --
+	(390.52,178.58) --
+	(390.90,178.98) --
+	(391.28,179.39) --
+	(391.66,179.79) --
+	(392.04,180.19) --
+	(392.42,180.60) --
+	(392.80,180.99) --
+	(393.18,181.39) --
+	(393.56,181.79) --
+	(393.94,182.18) --
+	(394.32,182.58) --
+	(394.70,182.97) --
+	(395.08,183.36) --
+	(395.46,183.75) --
+	(395.84,184.13) --
+	(396.22,184.52) --
+	(396.60,184.90) --
+	(396.98,185.29) --
+	(397.36,185.67) --
+	(397.74,186.04) --
+	(398.12,186.42) --
+	(398.50,186.80) --
+	(398.88,187.17) --
+	(399.26,187.54) --
+	(399.64,187.91) --
+	(400.01,188.28) --
+	(400.39,188.65) --
+	(400.77,189.02) --
+	(401.15,189.38) --
+	(401.53,189.74) --
+	(401.91,190.10) --
+	(402.29,190.46) --
+	(402.67,190.82) --
+	(403.05,191.17) --
+	(403.43,191.53) --
+	(403.81,191.88) --
+	(404.19,192.23) --
+	(404.57,192.58) --
+	(404.95,192.93) --
+	(405.33,193.27) --
+	(405.71,193.61) --
+	(406.09,193.96) --
+	(406.47,194.30) --
+	(406.85,194.63) --
+	(407.23,194.97) --
+	(407.61,195.30) --
+	(407.99,195.64) --
+	(408.37,195.97) --
+	(408.75,196.30) --
+	(409.13,196.62) --
+	(409.51,196.95) --
+	(409.89,197.27) --
+	(410.27,197.60) --
+	(410.65,197.92) --
+	(411.03,198.23) --
+	(411.41,198.55) --
+	(411.79,198.87) --
+	(412.17,199.18) --
+	(412.55,199.49) --
+	(412.93,199.80) --
+	(413.31,200.11) --
+	(413.68,200.41) --
+	(414.06,200.72) --
+	(414.44,201.02) --
+	(414.82,201.32) --
+	(415.20,201.62) --
+	(415.58,201.92) --
+	(415.96,202.21) --
+	(416.34,202.51) --
+	(416.72,202.80) --
+	(417.10,203.09) --
+	(417.48,203.38) --
+	(417.86,203.66) --
+	(418.24,203.95) --
+	(418.62,204.23) --
+	(419.00,204.51) --
+	(419.38,204.79) --
+	(419.76,205.07) --
+	(420.14,205.35) --
+	(420.52,205.62) --
+	(420.90,205.89) --
+	(421.28,206.16) --
+	(421.66,206.43) --
+	(422.04,206.70) --
+	(422.42,206.97) --
+	(422.80,207.23) --
+	(423.18,207.49) --
+	(423.56,207.75) --
+	(423.94,208.01) --
+	(424.32,208.27) --
+	(424.70,208.52) --
+	(425.08,208.78) --
+	(425.46,209.03) --
+	(425.84,209.28) --
+	(426.22,209.53) --
+	(426.60,209.77) --
+	(426.97,210.02) --
+	(427.35,210.26) --
+	(427.73,210.50) --
+	(428.11,210.75) --
+	(428.49,210.98) --
+	(428.87,211.22) --
+	(429.25,211.46) --
+	(429.63,211.69) --
+	(430.01,211.92) --
+	(430.39,212.15) --
+	(430.77,212.38) --
+	(431.15,212.61) --
+	(431.53,212.83) --
+	(431.91,213.06) --
+	(432.29,213.28) --
+	(432.67,213.50) --
+	(433.05,213.72) --
+	(433.43,213.94) --
+	(433.81,214.15) --
+	(434.19,214.37) --
+	(434.57,214.58) --
+	(434.95,214.79) --
+	(435.33,215.00) --
+	(435.71,215.21) --
+	(436.09,215.42) --
+	(436.47,215.62) --
+	(436.85,215.83) --
+	(437.23,216.03) --
+	(437.61,216.23) --
+	(437.99,216.43) --
+	(438.37,216.63) --
+	(438.75,216.82) --
+	(439.13,217.02) --
+	(439.51,217.21) --
+	(439.89,217.40) --
+	(440.27,217.59) --
+	(440.64,217.78) --
+	(441.02,217.97) --
+	(441.40,218.16) --
+	(441.78,218.34) --
+	(442.16,218.52) --
+	(442.54,218.71) --
+	(442.92,218.89) --
+	(443.30,219.06) --
+	(443.68,219.24) --
+	(444.06,219.42) --
+	(444.44,219.59) --
+	(444.82,219.77) --
+	(445.20,219.94) --
+	(445.58,220.11) --
+	(445.96,220.28) --
+	(446.34,220.45) --
+	(446.72,220.61) --
+	(447.10,220.78) --
+	(447.48,220.94) --
+	(447.86,221.11) --
+	(448.24,221.27) --
+	(448.62,221.43) --
+	(449.00,221.59) --
+	(449.38,221.75) --
+	(449.76,221.90) --
+	(450.14,222.06) --
+	(450.52,222.21) --
+	(450.90,222.37) --
+	(451.28,222.52) --
+	(451.66,222.67) --
+	(452.04,222.82) --
+	(452.42,222.96) --
+	(452.80,223.11) --
+	(453.18,223.26) --
+	(453.56,223.40) --
+	(453.93,223.54) --
+	(454.31,223.69) --
+	(454.69,223.83) --
+	(455.07,223.97) --
+	(455.45,224.10) --
+	(455.83,224.24) --
+	(456.21,224.38) --
+	(456.59,224.51) --
+	(456.97,224.65) --
+	(457.35,224.78) --
+	(457.73,224.91) --
+	(458.11,225.04) --
+	(458.49,225.17) --
+	(458.87,225.30) --
+	(459.25,225.43) --
+	(459.63,225.55) --
+	(460.01,225.68) --
+	(460.39,225.80) --
+	(460.77,225.93) --
+	(461.15,226.05) --
+	(461.53,226.17) --
+	(461.91,226.29) --
+	(462.29,226.41) --
+	(462.67,226.53) --
+	(463.05,226.64) --
+	(463.43,226.76) --
+	(463.81,226.87) --
+	(464.19,226.99) --
+	(464.57,227.10) --
+	(464.95,227.21) --
+	(465.33,227.32) --
+	(465.71,227.43) --
+	(466.09,227.54) --
+	(466.47,227.65) --
+	(466.85,227.76) --
+	(467.23,227.87) --
+	(467.60,227.97) --
+	(467.98,228.08) --
+	(468.36,228.18) --
+	(468.74,228.28) --
+	(469.12,228.38) --
+	(469.50,228.49) --
+	(469.88,228.59) --
+	(470.26,228.68) --
+	(470.64,228.78) --
+	(471.02,228.88) --
+	(471.40,228.98) --
+	(471.78,229.07) --
+	(472.16,229.17) --
+	(472.54,229.26) --
+	(472.92,229.36) --
+	(473.30,229.45) --
+	(473.68,229.54) --
+	(474.06,229.63) --
+	(474.44,229.72) --
+	(474.82,229.81) --
+	(475.20,229.90) --
+	(475.58,229.99) --
+	(475.96,230.07) --
+	(476.34,230.16) --
+	(476.72,230.24) --
+	(477.10,230.33) --
+	(477.48,230.41) --
+	(477.86,230.50) --
+	(478.24,230.58) --
+	(478.62,230.66) --
+	(479.00,230.74) --
+	(479.38,230.82) --
+	(479.76,230.90) --
+	(480.14,230.98) --
+	(480.52,231.06) --
+	(480.90,231.13) --
+	(481.27,231.21) --
+	(481.65,231.29) --
+	(482.03,231.36) --
+	(482.41,231.44) --
+	(482.79,231.51) --
+	(483.17,231.58) --
+	(483.55,231.66) --
+	(483.93,231.73) --
+	(484.31,231.80) --
+	(484.69,231.87) --
+	(485.07,231.94) --
+	(485.45,232.01) --
+	(485.83,232.08) --
+	(486.21,232.15) --
+	(486.59,232.21) --
+	(486.97,232.28) --
+	(487.35,232.35) --
+	(487.73,232.41) --
+	(488.11,232.48) --
+	(488.49,232.54) --
+	(488.87,232.61) --
+	(489.25,232.67) --
+	(489.63,232.73) --
+	(490.01,232.79) --
+	(490.39,232.86) --
+	(490.77,232.92) --
+	(491.15,232.98) --
+	(491.53,233.04) --
+	(491.91,233.10) --
+	(492.29,233.16) --
+	(492.67,233.21) --
+	(493.05,233.27) --
+	(493.43,233.33) --
+	(493.81,233.39) --
+	(494.19,233.44) --
+	(494.56,233.50) --
+	(494.94,233.55) --
+	(495.32,233.61) --
+	(495.70,233.66) --
+	(496.08,233.72) --
+	(496.46,233.77) --
+	(496.84,233.82) --
+	(497.22,233.87) --
+	(497.60,233.92) --
+	(497.98,233.98) --
+	(498.36,234.03) --
+	(498.74,234.08) --
+	(499.12,234.13) --
+	(499.50,234.18) --
+	(499.88,234.22) --
+	(500.26,234.27) --
+	(500.64,234.32) --
+	(501.02,234.37) --
+	(501.40,234.42) --
+	(501.78,234.46) --
+	(502.16,234.51) --
+	(502.54,234.55) --
+	(502.92,234.60) --
+	(503.30,234.64) --
+	(503.68,234.69) --
+	(504.06,234.73) --
+	(504.44,234.78) --
+	(504.82,234.82) --
+	(505.20,234.86) --
+	(505.58,234.90) --
+	(505.96,234.95) --
+	(506.34,234.99) --
+	(506.72,235.03) --
+	(507.10,235.07) --
+	(507.48,235.11) --
+	(507.86,235.15) --
+	(508.23,235.19) --
+	(508.61,235.23) --
+	(508.99,235.27) --
+	(509.37,235.31) --
+	(509.75,235.35) --
+	(510.13,235.38) --
+	(510.51,235.42) --
+	(510.89,235.46) --
+	(511.27,235.50) --
+	(511.65,235.53) --
+	(512.03,235.57) --
+	(512.41,235.60) --
+	(512.79,235.64) --
+	(513.17,235.67) --
+	(513.55,235.71) --
+	(513.93,235.74) --
+	(514.31,235.78) --
+	(514.69,235.81) --
+	(515.07,235.84) --
+	(515.45,235.88) --
+	(515.83,235.91) --
+	(516.21,235.94) --
+	(516.59,235.98) --
+	(516.97,236.01) --
+	(517.35,236.04) --
+	(517.73,236.07) --
+	(518.11,236.10) --
+	(518.49,236.13) --
+	(518.87,236.16) --
+	(519.25,236.19) --
+	(519.63,236.22) --
+	(520.01,236.25) --
+	(520.39,236.28) --
+	(520.77,236.31) --
+	(521.15,236.34) --
+	(521.53,236.37) --
+	(521.90,236.40) --
+	(522.28,236.42) --
+	(522.66,236.45) --
+	(523.04,236.48) --
+	(523.42,236.51) --
+	(523.80,236.53) --
+	(524.18,236.56) --
+	(524.56,236.59) --
+	(524.94,236.61) --
+	(525.32,236.64) --
+	(525.70,236.66) --
+	(526.08,236.69) --
+	(526.46,236.71) --
+	(526.84,236.74) --
+	(527.22,236.76) --
+	(527.60,236.79) --
+	(527.98,236.81) --
+	(528.36,236.84);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (338.88, 91.23) --
+	(339.26, 91.04) --
+	(339.64, 90.86) --
+	(340.02, 90.67) --
+	(340.40, 90.49) --
+	(340.78, 90.30) --
+	(341.16, 90.12) --
+	(341.54, 89.94) --
+	(341.92, 89.76) --
+	(342.30, 89.58) --
+	(342.68, 89.40) --
+	(343.06, 89.22) --
+	(343.44, 89.04) --
+	(343.82, 88.86) --
+	(344.20, 88.68) --
+	(344.58, 88.50) --
+	(344.96, 88.33) --
+	(345.34, 88.15) --
+	(345.71, 87.97) --
+	(346.09, 87.80) --
+	(346.47, 87.62) --
+	(346.85, 87.45) --
+	(347.23, 87.28) --
+	(347.61, 87.10) --
+	(347.99, 86.93) --
+	(348.37, 86.76) --
+	(348.75, 86.59) --
+	(349.13, 86.42) --
+	(349.51, 86.25) --
+	(349.89, 86.08) --
+	(350.27, 85.91) --
+	(350.65, 85.75) --
+	(351.03, 85.58) --
+	(351.41, 85.41) --
+	(351.79, 85.25) --
+	(352.17, 85.08) --
+	(352.55, 84.92) --
+	(352.93, 84.75) --
+	(353.31, 84.59) --
+	(353.69, 84.43) --
+	(354.07, 84.26) --
+	(354.45, 84.10) --
+	(354.83, 83.94) --
+	(355.21, 83.78) --
+	(355.59, 83.62) --
+	(355.97, 83.46) --
+	(356.35, 83.30) --
+	(356.73, 83.14) --
+	(357.11, 82.99) --
+	(357.49, 82.83) --
+	(357.87, 82.67) --
+	(358.25, 82.52) --
+	(358.63, 82.36) --
+	(359.01, 82.21) --
+	(359.38, 82.05) --
+	(359.76, 81.90) --
+	(360.14, 81.74) --
+	(360.52, 81.59) --
+	(360.90, 81.44) --
+	(361.28, 81.29) --
+	(361.66, 81.14) --
+	(362.04, 80.99) --
+	(362.42, 80.84) --
+	(362.80, 80.69) --
+	(363.18, 80.54) --
+	(363.56, 80.39) --
+	(363.94, 80.25) --
+	(364.32, 80.10) --
+	(364.70, 79.95) --
+	(365.08, 79.81) --
+	(365.46, 79.66) --
+	(365.84, 79.52) --
+	(366.22, 79.38) --
+	(366.60, 79.23) --
+	(366.98, 79.09) --
+	(367.36, 78.95) --
+	(367.74, 78.81) --
+	(368.12, 78.67) --
+	(368.50, 78.52) --
+	(368.88, 78.38) --
+	(369.26, 78.25) --
+	(369.64, 78.11) --
+	(370.02, 77.97) --
+	(370.40, 77.83) --
+	(370.78, 77.69) --
+	(371.16, 77.56) --
+	(371.54, 77.42) --
+	(371.92, 77.29) --
+	(372.30, 77.15) --
+	(372.68, 77.02) --
+	(373.05, 76.88) --
+	(373.43, 76.75) --
+	(373.81, 76.62) --
+	(374.19, 76.49) --
+	(374.57, 76.35) --
+	(374.95, 76.22) --
+	(375.33, 76.09) --
+	(375.71, 75.96) --
+	(376.09, 75.83) --
+	(376.47, 75.70) --
+	(376.85, 75.58) --
+	(377.23, 75.45) --
+	(377.61, 75.32) --
+	(377.99, 75.19) --
+	(378.37, 75.07) --
+	(378.75, 74.94) --
+	(379.13, 74.82) --
+	(379.51, 74.69) --
+	(379.89, 74.57) --
+	(380.27, 74.45) --
+	(380.65, 74.32) --
+	(381.03, 74.20) --
+	(381.41, 74.08) --
+	(381.79, 73.96) --
+	(382.17, 73.84) --
+	(382.55, 73.71) --
+	(382.93, 73.60) --
+	(383.31, 73.48) --
+	(383.69, 73.36) --
+	(384.07, 73.24) --
+	(384.45, 73.12) --
+	(384.83, 73.00) --
+	(385.21, 72.89) --
+	(385.59, 72.77) --
+	(385.97, 72.65) --
+	(386.34, 72.54) --
+	(386.72, 72.42) --
+	(387.10, 72.31) --
+	(387.48, 72.20) --
+	(387.86, 72.08) --
+	(388.24, 71.97) --
+	(388.62, 71.86) --
+	(389.00, 71.75) --
+	(389.38, 71.63) --
+	(389.76, 71.52) --
+	(390.14, 71.41) --
+	(390.52, 71.30) --
+	(390.90, 71.19) --
+	(391.28, 71.09) --
+	(391.66, 70.98) --
+	(392.04, 70.87) --
+	(392.42, 70.76) --
+	(392.80, 70.65) --
+	(393.18, 70.55) --
+	(393.56, 70.44) --
+	(393.94, 70.34) --
+	(394.32, 70.23) --
+	(394.70, 70.13) --
+	(395.08, 70.02) --
+	(395.46, 69.92) --
+	(395.84, 69.82) --
+	(396.22, 69.71) --
+	(396.60, 69.61) --
+	(396.98, 69.51) --
+	(397.36, 69.41) --
+	(397.74, 69.31) --
+	(398.12, 69.21) --
+	(398.50, 69.11) --
+	(398.88, 69.01) --
+	(399.26, 68.91) --
+	(399.64, 68.81) --
+	(400.01, 68.71) --
+	(400.39, 68.61) --
+	(400.77, 68.52) --
+	(401.15, 68.42) --
+	(401.53, 68.32) --
+	(401.91, 68.23) --
+	(402.29, 68.13) --
+	(402.67, 68.04) --
+	(403.05, 67.94) --
+	(403.43, 67.85) --
+	(403.81, 67.76) --
+	(404.19, 67.66) --
+	(404.57, 67.57) --
+	(404.95, 67.48) --
+	(405.33, 67.39) --
+	(405.71, 67.29) --
+	(406.09, 67.20) --
+	(406.47, 67.11) --
+	(406.85, 67.02) --
+	(407.23, 66.93) --
+	(407.61, 66.84) --
+	(407.99, 66.75) --
+	(408.37, 66.66) --
+	(408.75, 66.58) --
+	(409.13, 66.49) --
+	(409.51, 66.40) --
+	(409.89, 66.31) --
+	(410.27, 66.23) --
+	(410.65, 66.14) --
+	(411.03, 66.06) --
+	(411.41, 65.97) --
+	(411.79, 65.89) --
+	(412.17, 65.80) --
+	(412.55, 65.72) --
+	(412.93, 65.63) --
+	(413.31, 65.55) --
+	(413.68, 65.47) --
+	(414.06, 65.39) --
+	(414.44, 65.30) --
+	(414.82, 65.22) --
+	(415.20, 65.14) --
+	(415.58, 65.06) --
+	(415.96, 64.98) --
+	(416.34, 64.90) --
+	(416.72, 64.82) --
+	(417.10, 64.74) --
+	(417.48, 64.66) --
+	(417.86, 64.58) --
+	(418.24, 64.50) --
+	(418.62, 64.43) --
+	(419.00, 64.35) --
+	(419.38, 64.27) --
+	(419.76, 64.20) --
+	(420.14, 64.12) --
+	(420.52, 64.04) --
+	(420.90, 63.97) --
+	(421.28, 63.89) --
+	(421.66, 63.82) --
+	(422.04, 63.74) --
+	(422.42, 63.67) --
+	(422.80, 63.60) --
+	(423.18, 63.52) --
+	(423.56, 63.45) --
+	(423.94, 63.38) --
+	(424.32, 63.30) --
+	(424.70, 63.23) --
+	(425.08, 63.16) --
+	(425.46, 63.09) --
+	(425.84, 63.02) --
+	(426.22, 62.95) --
+	(426.60, 62.88) --
+	(426.97, 62.81) --
+	(427.35, 62.74) --
+	(427.73, 62.67) --
+	(428.11, 62.60) --
+	(428.49, 62.53) --
+	(428.87, 62.46) --
+	(429.25, 62.40) --
+	(429.63, 62.33) --
+	(430.01, 62.26) --
+	(430.39, 62.20) --
+	(430.77, 62.13) --
+	(431.15, 62.06) --
+	(431.53, 62.00) --
+	(431.91, 61.93) --
+	(432.29, 61.87) --
+	(432.67, 61.80) --
+	(433.05, 61.74) --
+	(433.43, 61.67) --
+	(433.81, 61.61) --
+	(434.19, 61.55) --
+	(434.57, 61.48) --
+	(434.95, 61.42) --
+	(435.33, 61.36) --
+	(435.71, 61.29) --
+	(436.09, 61.23) --
+	(436.47, 61.17) --
+	(436.85, 61.11) --
+	(437.23, 61.05) --
+	(437.61, 60.99) --
+	(437.99, 60.93) --
+	(438.37, 60.87) --
+	(438.75, 60.81) --
+	(439.13, 60.75) --
+	(439.51, 60.69) --
+	(439.89, 60.63) --
+	(440.27, 60.57) --
+	(440.64, 60.51) --
+	(441.02, 60.46) --
+	(441.40, 60.40) --
+	(441.78, 60.34) --
+	(442.16, 60.28) --
+	(442.54, 60.23) --
+	(442.92, 60.17) --
+	(443.30, 60.11) --
+	(443.68, 60.06) --
 	(444.06, 60.00) --
 	(444.44, 59.95) --
-	(444.82, 59.90) --
-	(445.20, 59.85) --
-	(445.58, 59.80) --
-	(445.96, 59.75) --
-	(446.34, 59.70) --
-	(446.72, 59.65) --
-	(447.10, 59.60) --
-	(447.48, 59.55) --
-	(447.86, 59.50) --
-	(448.24, 59.46) --
-	(448.62, 59.41) --
-	(449.00, 59.36) --
-	(449.38, 59.31) --
-	(449.76, 59.27) --
-	(450.14, 59.22) --
-	(450.52, 59.17) --
-	(450.90, 59.13) --
-	(451.28, 59.08) --
-	(451.66, 59.03) --
-	(452.04, 58.99) --
-	(452.42, 58.94) --
-	(452.80, 58.90) --
-	(453.18, 58.85) --
-	(453.56, 58.81) --
-	(453.93, 58.76) --
-	(454.31, 58.72) --
-	(454.69, 58.67) --
-	(455.07, 58.63) --
-	(455.45, 58.58) --
-	(455.83, 58.54) --
-	(456.21, 58.50) --
-	(456.59, 58.45) --
-	(456.97, 58.41) --
-	(457.35, 58.37) --
-	(457.73, 58.32) --
-	(458.11, 58.28) --
-	(458.49, 58.24) --
-	(458.87, 58.20) --
-	(459.25, 58.15) --
-	(459.63, 58.11) --
-	(460.01, 58.07) --
-	(460.39, 58.03) --
-	(460.77, 57.99) --
-	(461.15, 57.95) --
-	(461.53, 57.91) --
-	(461.91, 57.87) --
-	(462.29, 57.83) --
-	(462.67, 57.79) --
-	(463.05, 57.75) --
-	(463.43, 57.71) --
-	(463.81, 57.67) --
-	(464.19, 57.63) --
-	(464.57, 57.59) --
-	(464.95, 57.55) --
-	(465.33, 57.51) --
-	(465.71, 57.47) --
-	(466.09, 57.43) --
-	(466.47, 57.40) --
-	(466.85, 57.36) --
-	(467.23, 57.32) --
-	(467.60, 57.28) --
-	(467.98, 57.24) --
-	(468.36, 57.21) --
-	(468.74, 57.17) --
-	(469.12, 57.13) --
-	(469.50, 57.10) --
-	(469.88, 57.06) --
-	(470.26, 57.02) --
-	(470.64, 56.99) --
-	(471.02, 56.95) --
-	(471.40, 56.91) --
-	(471.78, 56.88) --
-	(472.16, 56.84) --
-	(472.54, 56.81) --
-	(472.92, 56.77) --
-	(473.30, 56.74) --
-	(473.68, 56.70) --
-	(474.06, 56.67) --
-	(474.44, 56.63) --
-	(474.82, 56.60) --
-	(475.20, 56.56) --
-	(475.58, 56.53) --
-	(475.96, 56.50) --
-	(476.34, 56.46) --
-	(476.72, 56.43) --
-	(477.10, 56.39) --
-	(477.48, 56.36) --
-	(477.86, 56.33) --
-	(478.24, 56.30) --
-	(478.62, 56.26) --
-	(479.00, 56.23) --
-	(479.38, 56.20) --
-	(479.76, 56.17) --
-	(480.14, 56.13) --
-	(480.52, 56.10) --
-	(480.90, 56.07) --
-	(481.27, 56.04) --
-	(481.65, 56.01) --
-	(482.03, 55.97) --
-	(482.41, 55.94) --
-	(482.79, 55.91) --
-	(483.17, 55.88) --
-	(483.55, 55.85) --
-	(483.93, 55.82) --
-	(484.31, 55.79) --
-	(484.69, 55.76) --
-	(485.07, 55.73) --
-	(485.45, 55.70) --
-	(485.83, 55.67) --
-	(486.21, 55.64) --
-	(486.59, 55.61) --
-	(486.97, 55.58) --
-	(487.35, 55.55) --
-	(487.73, 55.52) --
-	(488.11, 55.49) --
-	(488.49, 55.46) --
-	(488.87, 55.44) --
-	(489.25, 55.41) --
-	(489.63, 55.38) --
-	(490.01, 55.35) --
-	(490.39, 55.32) --
-	(490.77, 55.29) --
-	(491.15, 55.27) --
-	(491.53, 55.24) --
-	(491.91, 55.21) --
-	(492.29, 55.18) --
-	(492.67, 55.16) --
-	(493.05, 55.13) --
-	(493.43, 55.10) --
-	(493.81, 55.07) --
-	(494.19, 55.05) --
-	(494.56, 55.02) --
-	(494.94, 54.99) --
-	(495.32, 54.97) --
-	(495.70, 54.94) --
-	(496.08, 54.92) --
-	(496.46, 54.89) --
-	(496.84, 54.86) --
-	(497.22, 54.84) --
-	(497.60, 54.81) --
-	(497.98, 54.79) --
-	(498.36, 54.76) --
-	(498.74, 54.74) --
-	(499.12, 54.71) --
-	(499.50, 54.69) --
-	(499.88, 54.66) --
-	(500.26, 54.64) --
-	(500.64, 54.61) --
-	(501.02, 54.59) --
-	(501.40, 54.56) --
-	(501.78, 54.54) --
-	(502.16, 54.51) --
-	(502.54, 54.49) --
-	(502.92, 54.47) --
-	(503.30, 54.44) --
-	(503.68, 54.42) --
-	(504.06, 54.40) --
-	(504.44, 54.37) --
-	(504.82, 54.35) --
-	(505.20, 54.33) --
-	(505.58, 54.30) --
-	(505.96, 54.28) --
-	(506.34, 54.26) --
-	(506.72, 54.23) --
-	(507.10, 54.21) --
-	(507.48, 54.19) --
-	(507.86, 54.17) --
-	(508.23, 54.14) --
-	(508.61, 54.12) --
-	(508.99, 54.10) --
-	(509.37, 54.08) --
-	(509.75, 54.06) --
-	(510.13, 54.03) --
-	(510.51, 54.01) --
-	(510.89, 53.99) --
-	(511.27, 53.97) --
-	(511.65, 53.95) --
-	(512.03, 53.93) --
-	(512.41, 53.91) --
-	(512.79, 53.89) --
-	(513.17, 53.86) --
-	(513.55, 53.84) --
-	(513.93, 53.82) --
-	(514.31, 53.80) --
-	(514.69, 53.78) --
-	(515.07, 53.76) --
-	(515.45, 53.74) --
-	(515.83, 53.72) --
-	(516.21, 53.70) --
-	(516.59, 53.68) --
-	(516.97, 53.66) --
-	(517.35, 53.64) --
-	(517.73, 53.62) --
-	(518.11, 53.60) --
-	(518.49, 53.58) --
-	(518.87, 53.56) --
-	(519.25, 53.54) --
-	(519.63, 53.53) --
-	(520.01, 53.51) --
-	(520.39, 53.49) --
-	(520.77, 53.47) --
-	(521.15, 53.45) --
-	(521.53, 53.43) --
-	(521.90, 53.41) --
-	(522.28, 53.39) --
-	(522.66, 53.38) --
-	(523.04, 53.36) --
-	(523.42, 53.34) --
-	(523.80, 53.32) --
-	(524.18, 53.30) --
-	(524.56, 53.28) --
-	(524.94, 53.27) --
-	(525.32, 53.25) --
-	(525.70, 53.23) --
-	(526.08, 53.21) --
-	(526.46, 53.20) --
-	(526.84, 53.18) --
-	(527.22, 53.16) --
-	(527.60, 53.14) --
-	(527.98, 53.13) --
-	(528.36, 53.11);
+	(444.82, 59.89) --
+	(445.20, 59.84) --
+	(445.58, 59.78) --
+	(445.96, 59.73) --
+	(446.34, 59.67) --
+	(446.72, 59.62) --
+	(447.10, 59.57) --
+	(447.48, 59.51) --
+	(447.86, 59.46) --
+	(448.24, 59.41) --
+	(448.62, 59.36) --
+	(449.00, 59.30) --
+	(449.38, 59.25) --
+	(449.76, 59.20) --
+	(450.14, 59.15) --
+	(450.52, 59.10) --
+	(450.90, 59.05) --
+	(451.28, 59.00) --
+	(451.66, 58.95) --
+	(452.04, 58.90) --
+	(452.42, 58.85) --
+	(452.80, 58.80) --
+	(453.18, 58.75) --
+	(453.56, 58.70) --
+	(453.93, 58.65) --
+	(454.31, 58.60) --
+	(454.69, 58.56) --
+	(455.07, 58.51) --
+	(455.45, 58.46) --
+	(455.83, 58.41) --
+	(456.21, 58.37) --
+	(456.59, 58.32) --
+	(456.97, 58.27) --
+	(457.35, 58.23) --
+	(457.73, 58.18) --
+	(458.11, 58.13) --
+	(458.49, 58.09) --
+	(458.87, 58.04) --
+	(459.25, 58.00) --
+	(459.63, 57.95) --
+	(460.01, 57.91) --
+	(460.39, 57.86) --
+	(460.77, 57.82) --
+	(461.15, 57.77) --
+	(461.53, 57.73) --
+	(461.91, 57.69) --
+	(462.29, 57.64) --
+	(462.67, 57.60) --
+	(463.05, 57.56) --
+	(463.43, 57.52) --
+	(463.81, 57.47) --
+	(464.19, 57.43) --
+	(464.57, 57.39) --
+	(464.95, 57.35) --
+	(465.33, 57.31) --
+	(465.71, 57.26) --
+	(466.09, 57.22) --
+	(466.47, 57.18) --
+	(466.85, 57.14) --
+	(467.23, 57.10) --
+	(467.60, 57.06) --
+	(467.98, 57.02) --
+	(468.36, 56.98) --
+	(468.74, 56.94) --
+	(469.12, 56.90) --
+	(469.50, 56.86) --
+	(469.88, 56.82) --
+	(470.26, 56.78) --
+	(470.64, 56.75) --
+	(471.02, 56.71) --
+	(471.40, 56.67) --
+	(471.78, 56.63) --
+	(472.16, 56.59) --
+	(472.54, 56.56) --
+	(472.92, 56.52) --
+	(473.30, 56.48) --
+	(473.68, 56.44) --
+	(474.06, 56.41) --
+	(474.44, 56.37) --
+	(474.82, 56.34) --
+	(475.20, 56.30) --
+	(475.58, 56.26) --
+	(475.96, 56.23) --
+	(476.34, 56.19) --
+	(476.72, 56.16) --
+	(477.10, 56.12) --
+	(477.48, 56.09) --
+	(477.86, 56.05) --
+	(478.24, 56.02) --
+	(478.62, 55.98) --
+	(479.00, 55.95) --
+	(479.38, 55.91) --
+	(479.76, 55.88) --
+	(480.14, 55.85) --
+	(480.52, 55.81) --
+	(480.90, 55.78) --
+	(481.27, 55.75) --
+	(481.65, 55.71) --
+	(482.03, 55.68) --
+	(482.41, 55.65) --
+	(482.79, 55.61) --
+	(483.17, 55.58) --
+	(483.55, 55.55) --
+	(483.93, 55.52) --
+	(484.31, 55.49) --
+	(484.69, 55.45) --
+	(485.07, 55.42) --
+	(485.45, 55.39) --
+	(485.83, 55.36) --
+	(486.21, 55.33) --
+	(486.59, 55.30) --
+	(486.97, 55.27) --
+	(487.35, 55.24) --
+	(487.73, 55.21) --
+	(488.11, 55.18) --
+	(488.49, 55.15) --
+	(488.87, 55.12) --
+	(489.25, 55.09) --
+	(489.63, 55.06) --
+	(490.01, 55.03) --
+	(490.39, 55.00) --
+	(490.77, 54.97) --
+	(491.15, 54.94) --
+	(491.53, 54.91) --
+	(491.91, 54.89) --
+	(492.29, 54.86) --
+	(492.67, 54.83) --
+	(493.05, 54.80) --
+	(493.43, 54.77) --
+	(493.81, 54.75) --
+	(494.19, 54.72) --
+	(494.56, 54.69) --
+	(494.94, 54.66) --
+	(495.32, 54.64) --
+	(495.70, 54.61) --
+	(496.08, 54.58) --
+	(496.46, 54.55) --
+	(496.84, 54.53) --
+	(497.22, 54.50) --
+	(497.60, 54.48) --
+	(497.98, 54.45) --
+	(498.36, 54.42) --
+	(498.74, 54.40) --
+	(499.12, 54.37) --
+	(499.50, 54.35) --
+	(499.88, 54.32) --
+	(500.26, 54.30) --
+	(500.64, 54.27) --
+	(501.02, 54.25) --
+	(501.40, 54.22) --
+	(501.78, 54.20) --
+	(502.16, 54.17) --
+	(502.54, 54.15) --
+	(502.92, 54.12) --
+	(503.30, 54.10) --
+	(503.68, 54.07) --
+	(504.06, 54.05) --
+	(504.44, 54.03) --
+	(504.82, 54.00) --
+	(505.20, 53.98) --
+	(505.58, 53.96) --
+	(505.96, 53.93) --
+	(506.34, 53.91) --
+	(506.72, 53.89) --
+	(507.10, 53.86) --
+	(507.48, 53.84) --
+	(507.86, 53.82) --
+	(508.23, 53.79) --
+	(508.61, 53.77) --
+	(508.99, 53.75) --
+	(509.37, 53.73) --
+	(509.75, 53.71) --
+	(510.13, 53.68) --
+	(510.51, 53.66) --
+	(510.89, 53.64) --
+	(511.27, 53.62) --
+	(511.65, 53.60) --
+	(512.03, 53.58) --
+	(512.41, 53.55) --
+	(512.79, 53.53) --
+	(513.17, 53.51) --
+	(513.55, 53.49) --
+	(513.93, 53.47) --
+	(514.31, 53.45) --
+	(514.69, 53.43) --
+	(515.07, 53.41) --
+	(515.45, 53.39) --
+	(515.83, 53.37) --
+	(516.21, 53.35) --
+	(516.59, 53.33) --
+	(516.97, 53.31) --
+	(517.35, 53.29) --
+	(517.73, 53.27) --
+	(518.11, 53.25) --
+	(518.49, 53.23) --
+	(518.87, 53.21) --
+	(519.25, 53.19) --
+	(519.63, 53.17) --
+	(520.01, 53.15) --
+	(520.39, 53.14) --
+	(520.77, 53.12) --
+	(521.15, 53.10) --
+	(521.53, 53.08) --
+	(521.90, 53.06) --
+	(522.28, 53.04) --
+	(522.66, 53.02) --
+	(523.04, 53.01) --
+	(523.42, 52.99) --
+	(523.80, 52.97) --
+	(524.18, 52.95) --
+	(524.56, 52.93) --
+	(524.94, 52.92) --
+	(525.32, 52.90) --
+	(525.70, 52.88) --
+	(526.08, 52.86) --
+	(526.46, 52.85) --
+	(526.84, 52.83) --
+	(527.22, 52.81) --
+	(527.60, 52.80) --
+	(527.98, 52.78) --
+	(528.36, 52.76);
 \end{scope}

### 2020-08-31 benchmarking/benchmarkingVM/ESS_round2.tex
Results update

--- 2020-08-26 benchmarking/benchmarkingVM/ESS_round2.tex
@@
-% Created by tikzDevice version 0.12.3.1 on 2020-08-25 15:33:23
+% Created by tikzDevice version 0.12.3.1 on 2020-08-31 17:26:30
 % !TEX encoding = UTF-8 Unicode
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,548.96) {\bfseries adapt (\textit{real}) vs. adapt (\textit{cat})};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,301.03) {ESS/hr [adapt (\textit{cat})]};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,433.62) {ESS/hr [adapt (\textit{real})]};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,548.96) {\bfseries adapt(\textit{real}) vs. adapt(\textit{cat})};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,301.03) {ESS/hr [adapt(\textit{cat})]};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,433.62) {ESS/hr [adapt(\textit{real})]};
 \end{scope}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 69.78,442.39) --
-	( 87.52,442.39);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 80.64,435.58) --
-	( 80.64,447.40);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 80.64,439.16) {$p$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (113.18,466.07) --
-	(139.72,466.07);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (130.72,464.03) --
-	(130.72,467.92);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (130.72,462.04) {$L$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 72.46,458.74) --
-	( 82.66,458.74);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 78.23,457.64) --
-	( 78.23,459.78);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 78.23,454.71) {$r$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 67.86,420.09) --
-	( 87.25,420.09);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 79.91,409.91) --
-	( 79.91,426.69);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 79.91,416.05) {$h$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 46.78,445.45) --
-	( 58.72,445.45);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 53.67,440.98) --
-	( 53.67,449.06);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 53.67,442.54) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.23,465.32) --
-	(172.50,465.32);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.36,464.91) --
-	(172.36,465.72);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.36,462.41) {$\kappa$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.61,498.53) --
-	(202.14,498.53);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (200.46,495.69) --
-	(200.46,501.00);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (200.46,495.30) {$p$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.14,477.19) --
-	(182.23,477.19);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.29,473.20) --
-	(180.29,480.49);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.29,473.16) {$L$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (203.91,507.29) --
-	(209.53,507.29);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (206.93,504.13) --
-	(206.93,510.00);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (206.93,503.26) {$r$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.53,488.44) --
-	(196.14,488.44);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.71,485.34) --
-	(192.71,491.10);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.71,484.40) {$h$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (197.45,500.32) --
-	(203.99,500.32);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (201.00,497.70) --
-	(201.00,502.63);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (201.00,497.42) {$\sigma$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (208.42,508.32) --
-	(214.48,508.32);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.69,505.44) --
-	(211.69,510.82);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.69,505.41) {$\kappa$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (159.29,461.48) --
-	(163.09,461.48);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.28,459.47) --
-	(161.28,463.29);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (161.28,458.25) {$p$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.43,473.75) --
-	(176.80,473.75);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.74,467.42) --
-	(174.74,478.51);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.74,469.72) {$L$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.87,499.81) --
-	(197.04,499.81);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.98,499.49) --
-	(195.98,500.13);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.98,495.78) {$r$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (140.13,433.28) --
-	(150.21,433.28);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (145.82,430.75) --
-	(145.82,435.51);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (145.82,429.24) {$h$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.54,457.34) --
-	(157.36,457.34);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (154.25,453.95) --
-	(154.25,460.21);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (154.25,454.43) {$\sigma$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.20,500.26) --
-	(200.08,500.26);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.16,500.10) --
-	(199.16,500.41);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.16,497.35) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (156.23,472.45) --
-	(158.05,472.45);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (157.16,469.05) --
-	(157.16,475.33);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (157.16,469.22) {$p$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (162.22,469.44) --
-	(167.11,469.44);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.82,468.18) --
-	(164.82,470.63);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (164.82,465.41) {$L$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.39,494.42) --
-	(190.63,494.42);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.55,494.08) --
-	(189.55,494.75);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (189.55,490.38) {$r$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (145.43,461.88) --
-	(154.13,461.88);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.27,458.33) --
-	(150.27,464.86);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (150.27,457.84) {$h$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (132.82,466.76) --
-	(167.42,466.76);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (157.06,464.72) --
-	(157.06,468.61);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (157.06,463.86) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.44,500.16) --
-	(198.69,500.16);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.57,499.71) --
-	(198.57,500.60);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.57,497.25) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (102.23,461.86) --
-	(111.25,461.86);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (107.27,457.98) --
-	(107.27,465.08);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (107.27,458.63) {$p$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.53,471.68) --
-	(161.05,471.68);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (156.88,467.85) --
-	(156.88,474.87);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (156.88,467.65) {$L$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (155.91,473.63) --
-	(158.58,473.63);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (157.29,473.45) --
-	(157.29,473.81);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (157.29,469.59) {$r$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 95.38,428.77) --
-	(104.88,428.77);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (100.71,424.39) --
-	(100.71,432.32);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (100.71,424.73) {$h$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 99.79,451.10) --
-	(116.82,451.10);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (110.14,444.27) --
-	(110.14,456.13);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (110.14,448.20) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.08,482.13) --
-	(188.19,482.13);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.81,481.71) --
-	(185.81,482.53);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.81,479.22) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (202.53,480.00) --
-	(207.67,480.00);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (205.27,469.20) --
-	(205.27,486.87);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.27,476.78) {$p$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.37,482.86) --
-	(188.12,482.86);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.89,479.54) --
-	(185.89,485.69);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.89,478.82) {$L$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (213.22,510.87) --
-	(217.09,510.87);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (215.25,508.22) --
-	(215.25,513.20);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (215.25,506.84) {$r$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.15,475.07) --
-	(179.18,475.07);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (177.27,471.46) --
-	(177.27,478.10);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.27,471.03) {$h$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.77,483.80) --
-	(193.75,483.80);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.87,480.19) --
-	(191.87,486.83);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.87,480.89) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (203.55,502.56) --
-	(207.55,502.56);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (205.65,499.82) --
-	(205.65,504.96);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.65,499.66) {$\kappa$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.08,495.96) --
-	(151.08,497.69);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (151.08,493.62) {$p$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (206.36,501.50) --
-	(206.36,504.37);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (206.36,498.95) {$L$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.68,502.30) --
-	(191.68,502.71);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.68,498.47) {$r$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (158.37,472.23) --
-	(158.37,474.23);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.37,469.22) {$h$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (153.51,471.94) --
-	(153.51,477.11);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (153.51,471.79) {$\sigma$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (209.66,509.55) --
-	(209.66,511.28);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.66,507.53) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.80,474.68) --
-	(177.08,474.68);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.38,470.11) --
-	(173.38,478.38);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.38,471.46) {$p$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (147.87,452.98) --
-	(153.50,452.98);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.89,449.28) --
-	(150.89,456.08);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (150.89,448.95) {$L$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.87,485.78) --
-	(190.24,485.78);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.57,485.35) --
-	(189.57,486.21);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (189.57,481.75) {$r$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (146.53,446.62) --
-	(159.26,446.62);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (153.94,441.01) --
-	(153.94,450.95);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (153.94,442.59) {$h$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.76,472.80) --
-	(168.03,472.80);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.88,467.90) --
-	(161.88,476.70);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (161.88,469.90) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.33,498.56) --
-	(204.41,498.56);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (202.04,497.16) --
-	(202.04,499.86);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.04,495.65) {$\kappa$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.39,481.76) --
-	(196.26,481.76);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.35,478.54) --
-	(195.35,484.51);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.35,478.53) {$p$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.83,478.31) --
-	(183.47,478.31);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.66,474.79) --
-	(182.66,481.27);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.66,474.27) {$L$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (197.76,500.43) --
-	(199.40,500.43);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.60,500.31) --
-	(198.60,500.55);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.60,496.40) {$r$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.12,480.91) --
-	(183.39,480.91);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.82,478.84) --
-	(181.82,482.78);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.82,476.88) {$h$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.86,485.43) --
-	(188.00,485.43);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.44,484.34) --
-	(187.44,486.46);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.44,482.53) {$\sigma$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (207.49,512.69) --
-	(209.23,512.69);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (208.38,512.04) --
-	(208.38,513.32);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (208.38,509.78) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (205.92,505.04) --
+	(206.54,505.04);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (206.23,504.79) --
+	(206.23,505.29);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (206.23,501.82) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (216.33,507.39) --
+	(217.11,507.39);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (216.73,506.95) --
+	(216.73,507.82);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (216.73,504.49) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (211.62,511.19) --
+	(211.77,511.19);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (211.70,511.13) --
+	(211.70,511.25);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.70,507.16) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (201.95,493.79) --
+	(202.68,493.79);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (202.32,493.47) --
+	(202.32,494.11);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.32,490.89) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (203.67,496.31) --
+	(204.38,496.31);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (204.03,495.98) --
+	(204.03,496.64);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (204.03,492.28) {$l$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (205.75,506.51) --
+	(206.55,506.51);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (206.16,506.28) --
+	(206.16,506.73);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (206.16,503.60) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (216.87,512.59) --
+	(217.23,512.59);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (217.05,512.47) --
+	(217.05,512.71);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (217.05,509.69) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (173.90,468.92) --
+	(175.72,468.92);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (174.83,468.08) --
+	(174.83,469.72);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.83,465.69) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (206.59,497.49) --
+	(207.15,497.49);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (206.87,497.22) --
+	(206.87,497.77);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (206.87,494.59) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (204.49,500.25) --
+	(204.66,500.25);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (204.57,500.18) --
+	(204.57,500.32);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (204.57,496.21) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (165.17,453.35) --
+	(167.29,453.35);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (166.26,452.41) --
+	(166.26,454.24);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (166.26,450.44) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (167.36,455.34) --
+	(169.47,455.34);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (168.44,454.39) --
+	(168.44,456.25);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (168.44,451.31) {$l$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (170.32,466.37) --
+	(171.88,466.37);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (171.11,465.53) --
+	(171.11,467.17);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.11,463.46) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (206.77,501.14) --
+	(206.93,501.14);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (206.85,501.05) --
+	(206.85,501.23);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (206.85,498.24) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (161.26,477.08) --
+	(162.96,477.08);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (162.13,476.61) --
+	(162.13,477.54);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (162.13,473.86) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (204.84,493.82) --
+	(205.45,493.82);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (205.15,493.57) --
+	(205.15,494.06);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.15,490.91) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (197.75,495.00) --
+	(198.03,495.00);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (197.89,494.93) --
+	(197.89,495.07);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.89,490.97) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (156.31,470.07) --
+	(157.86,470.07);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (157.10,469.69) --
+	(157.10,470.46);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (157.10,467.17) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (159.33,471.13) --
+	(160.99,471.13);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (160.18,470.73) --
+	(160.18,471.51);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (160.18,467.09) {$l$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (165.56,474.04) --
+	(167.15,474.04);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (166.37,473.55) --
+	(166.37,474.51);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (166.37,471.13) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (205.93,500.80) --
+	(206.27,500.80);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (206.10,500.70) --
+	(206.10,500.90);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (206.10,497.89) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (121.64,470.69) --
+	(124.00,470.69);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (122.86,470.18) --
+	(122.86,471.19);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (122.86,467.47) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (185.34,468.90) --
+	(185.91,468.90);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (185.63,468.61) --
+	(185.63,469.18);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.63,465.99) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (162.37,475.57) --
+	(162.64,475.57);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (162.51,475.45) --
+	(162.51,475.69);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (162.51,471.54) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (120.02,442.67) --
+	(122.54,442.67);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (121.32,442.05) --
+	(121.32,443.26);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (121.32,439.76) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (121.22,442.55) --
+	(123.50,442.55);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (122.40,441.89) --
+	(122.40,443.18);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (122.40,438.51) {$l$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (120.43,458.76) --
+	(124.03,458.76);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (122.32,457.98) --
+	(122.32,459.51);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (122.32,455.86) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (188.53,482.91) --
+	(188.81,482.91);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (188.67,482.83) --
+	(188.67,482.99);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.67,480.01) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (207.64,487.61) --
+	(208.32,487.61);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (207.98,486.33) --
+	(207.98,488.81);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.98,484.39) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (211.16,504.08) --
+	(211.73,504.08);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (211.45,503.75) --
+	(211.45,504.41);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.45,501.17) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (221.28,516.22) --
+	(221.36,516.22);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (221.32,516.18) --
+	(221.32,516.26);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (221.32,512.18) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (200.31,497.67) --
+	(201.00,497.67);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (200.66,497.33) --
+	(200.66,498.01);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (200.66,494.77) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (205.63,502.94) --
+	(206.35,502.94);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (205.99,502.68) --
+	(205.99,503.19);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.99,498.90) {$l$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (197.03,491.24) --
+	(197.86,491.24);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (197.45,490.94) --
+	(197.45,491.55);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.45,488.34) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (211.55,507.70) --
+	(211.80,507.70);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (211.68,507.59) --
+	(211.68,507.81);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.68,504.80) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (159.54,499.71) --
+	(161.97,499.71);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (160.79,499.35) --
+	(160.79,500.06);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (160.79,496.48) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (216.44,498.95) --
+	(217.03,498.95);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (216.74,498.66) --
+	(216.74,499.24);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (216.74,496.05) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (197.48,503.67) --
+	(197.89,503.67);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (197.69,503.61) --
+	(197.69,503.74);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.69,499.64) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (158.30,471.10) --
+	(160.71,471.10);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (159.54,470.46) --
+	(159.54,471.72);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (159.54,468.20) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (160.01,471.53) --
+	(162.43,471.53);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (161.26,470.90) --
+	(161.26,472.14);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (161.26,467.50) {$l$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (165.78,483.58) --
+	(168.47,483.58);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (167.17,483.12) --
+	(167.17,484.03);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (167.17,480.67) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (215.03,512.59) --
+	(215.57,512.59);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (215.30,512.42) --
+	(215.30,512.76);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (215.30,509.69) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (178.82,481.02) --
+	(179.82,481.02);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (179.33,480.59) --
+	(179.33,481.44);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.33,477.79) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (191.50,482.93) --
+	(192.71,482.93);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (192.12,481.27) --
+	(192.12,484.45);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.12,480.02) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (194.77,489.01) --
+	(194.93,489.01);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (194.85,488.92) --
+	(194.85,489.11);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.85,484.98) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (178.61,473.57) --
+	(179.57,473.57);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (179.09,473.24) --
+	(179.09,473.89);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.09,470.67) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (177.63,472.97) --
+	(178.69,472.97);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (178.17,472.65) --
+	(178.17,473.28);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (178.17,468.93) {$l$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (181.69,480.98) --
+	(182.56,480.98);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (182.13,480.59) --
+	(182.13,481.36);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.13,478.08) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (204.37,501.33) --
+	(204.73,501.33);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (204.55,501.22) --
+	(204.55,501.45);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (204.55,498.43) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (199.59,487.86) --
+	(200.20,487.86);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (199.90,487.42) --
+	(199.90,488.29);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.90,484.64) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (187.13,484.00) --
+	(188.05,484.00);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (187.60,483.35) --
+	(187.60,484.63);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.60,481.10) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (204.12,500.91) --
+	(204.27,500.91);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (204.20,500.84) --
+	(204.20,500.97);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (204.20,496.87) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (194.04,490.16) --
+	(194.61,490.16);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (194.33,489.94) --
+	(194.33,490.38);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.33,487.26) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (199.55,495.79) --
+	(200.15,495.79);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (199.86,495.53) --
+	(199.86,496.04);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.86,491.75) {$l$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (192.32,490.00) --
+	(193.05,490.00);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (192.69,489.48) --
+	(192.69,490.49);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.69,487.09) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (213.97,512.17) --
+	(214.36,512.17);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (214.16,511.97) --
+	(214.16,512.37);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (214.16,509.26) {$\kappa$};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,548.96) {\bfseries adapt (\textit{quant}) vs. adapt (\textit{cat})};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,301.03) {ESS/hr [adapt (\textit{cat})]};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (307.01,433.62) {ESS/hr [adapt (\textit{quant})]};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,548.96) {\bfseries adapt(\textit{quant}) vs. adapt(\textit{cat})};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (433.62,301.03) {ESS/hr [adapt(\textit{cat})]};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (307.01,433.62) {ESS/hr [adapt(\textit{quant})]};
 \end{scope}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (358.86,422.82) --
-	(376.60,422.82);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (369.72,420.40) --
-	(369.72,424.97);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (369.72,419.59) {$p$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (402.26,452.57) --
-	(428.80,452.57);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (419.80,451.90) --
-	(419.80,453.22);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (419.80,448.54) {$L$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (361.54,446.67) --
-	(371.74,446.67);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (367.31,445.22) --
-	(367.31,448.02);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (367.31,442.64) {$r$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (356.94,418.52) --
-	(376.33,418.52);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (368.99,411.75) --
-	(368.99,423.52);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (368.99,414.49) {$h$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (335.86,430.80) --
-	(347.80,430.80);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (342.75,426.42) --
-	(342.75,434.36);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (342.75,427.90) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (461.31,451.20) --
-	(461.58,451.20);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (461.44,449.83) --
-	(461.44,452.49);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (461.44,448.30) {$\kappa$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (487.69,486.05) --
-	(491.22,486.05);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (489.54,480.97) --
-	(489.54,490.06);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (489.54,482.83) {$p$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (467.22,467.41) --
-	(471.31,467.41);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (469.37,463.99) --
-	(469.37,470.31);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (469.37,463.37) {$L$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (492.99,498.84) --
-	(498.61,498.84);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (496.01,495.08) --
-	(496.01,501.97);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (496.01,494.80) {$r$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (477.61,480.02) --
-	(485.22,480.02);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (481.79,475.53) --
-	(481.79,483.64);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (481.79,475.98) {$h$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (486.53,495.85) --
-	(493.07,495.85);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (490.08,490.38) --
-	(490.08,500.09);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (490.08,492.94) {$\sigma$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (497.50,497.26) --
-	(503.56,497.26);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (500.77,493.73) --
-	(500.77,500.23);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (500.77,494.35) {$\kappa$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (448.37,444.25) --
-	(452.17,444.25);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (450.36,439.52) --
-	(450.36,448.04);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (450.36,441.02) {$p$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (461.51,464.46) --
-	(465.88,464.46);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (463.82,463.55) --
-	(463.82,465.34);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (463.82,460.43) {$L$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.95,486.64) --
-	(486.12,486.64);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (485.06,486.09) --
-	(485.06,487.17);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (485.06,482.60) {$r$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (429.21,430.01) --
-	(439.29,430.01);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (434.90,424.45) --
-	(434.90,434.32);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (434.90,425.98) {$h$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (439.62,453.02) --
-	(446.44,453.02);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (443.33,448.90) --
-	(443.33,456.41);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (443.33,450.12) {$\sigma$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (487.28,484.52) --
-	(489.16,484.52);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (488.24,483.75) --
-	(488.24,485.27);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (488.24,481.62) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (445.31,455.28) --
-	(447.13,455.28);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (446.24,453.50) --
-	(446.24,456.90);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (446.24,452.05) {$p$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (451.30,455.59) --
-	(456.19,455.59);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (453.90,453.77) --
-	(453.90,457.25);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (453.90,451.56) {$L$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (477.47,481.09) --
-	(479.71,481.09);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (478.63,480.69) --
-	(478.63,481.49);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (478.63,477.06) {$r$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (434.51,455.34) --
-	(443.21,455.34);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (439.35,453.12) --
-	(439.35,457.33);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (439.35,451.30) {$h$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (421.90,459.26) --
-	(456.50,459.26);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (446.14,456.93) --
-	(446.14,461.33);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (446.14,456.35) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (487.52,482.35) --
-	(487.77,482.35);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (487.65,481.98) --
-	(487.65,482.72);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (487.65,479.45) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (391.31,419.90) --
-	(400.33,419.90);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (396.35,418.40) --
-	(396.35,421.29);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (396.35,416.67) {$p$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (440.61,458.29) --
-	(450.13,458.29);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (445.96,456.11) --
-	(445.96,460.25);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (445.96,454.26) {$L$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (444.99,457.12) --
-	(447.66,457.12);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (446.37,456.64) --
-	(446.37,457.60);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (446.37,453.09) {$r$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (384.46,419.27) --
-	(393.96,419.27);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (389.79,417.46) --
-	(389.79,420.93);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (389.79,415.24) {$h$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (388.87,431.53) --
-	(405.90,431.53);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (399.22,428.40) --
-	(399.22,434.22);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (399.22,428.63) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (472.16,463.25) --
-	(477.27,463.25);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (474.89,463.00) --
-	(474.89,463.51);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.89,460.35) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (491.61,491.43) --
-	(496.75,491.43);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (494.35,488.34) --
-	(494.35,494.10);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (494.35,488.21) {$p$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (472.45,473.26) --
-	(477.20,473.26);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (474.97,469.46) --
-	(474.97,476.43);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.97,469.23) {$L$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (502.30,500.72) --
-	(506.17,500.72);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (504.33,497.68) --
-	(504.33,503.35);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (504.33,496.69) {$r$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (464.23,462.90) --
-	(468.26,462.90);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (466.35,459.58) --
-	(466.35,465.73);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (466.35,458.87) {$h$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (478.85,477.19) --
-	(482.83,477.19);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.95,474.02) --
-	(480.95,479.91);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (480.95,474.29) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (492.63,491.09) --
-	(496.63,491.09);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (494.73,488.28) --
-	(494.73,493.53);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (494.73,488.18) {$\kappa$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (440.16,449.31) --
-	(440.16,456.88);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (440.16,450.24) {$p$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (495.44,483.20) --
-	(495.44,486.68);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (495.44,480.99) {$L$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (480.76,488.95) --
-	(480.76,489.76);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (480.76,485.33) {$r$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (447.45,456.35) --
-	(447.45,466.27);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (447.45,457.91) {$h$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (442.59,463.63) --
-	(442.59,469.80);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (442.59,464.06) {$\sigma$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (498.74,489.94) --
-	(498.74,492.58);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (498.74,488.40) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (457.88,458.77) --
-	(466.16,458.77);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (462.46,456.24) --
-	(462.46,461.00);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (462.46,455.54) {$p$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (436.95,441.13) --
-	(442.58,441.13);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (439.97,438.18) --
-	(439.97,443.68);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (439.97,437.10) {$L$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (477.95,472.82) --
-	(479.32,472.82);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (478.65,472.59) --
-	(478.65,473.05);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (478.65,468.79) {$r$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (435.61,443.82) --
-	(448.34,443.82);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (443.02,439.42) --
-	(443.02,447.40);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (443.02,439.79) {$h$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (441.84,458.10) --
-	(457.11,458.10);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (450.96,453.81) --
-	(450.96,461.61);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (450.96,455.20) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (488.41,481.91) --
-	(493.49,481.91);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (491.12,481.83) --
-	(491.12,481.99);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (491.12,479.00) {$\kappa$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (483.47,478.97) --
-	(485.34,478.97);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (484.43,467.29) --
-	(484.43,486.16);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (484.43,475.74) {$p$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (470.91,465.38) --
-	(472.55,465.38);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (471.74,453.39) --
-	(471.74,472.69);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (471.74,461.35) {$L$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (486.84,482.47) --
-	(488.48,482.47);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (487.68,470.56) --
-	(487.68,489.76);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (487.68,478.44) {$r$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (469.20,464.45) --
-	(472.47,464.45);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (470.90,451.93) --
-	(470.90,471.95);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (470.90,460.42) {$h$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (475.94,474.07) --
-	(477.08,474.07);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (476.52,462.11) --
-	(476.52,481.38);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (476.52,471.17) {$\sigma$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (496.57,491.37) --
-	(498.31,491.37);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (497.46,479.32) --
-	(497.46,498.71);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (497.46,488.47) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (495.00,489.87) --
+	(495.62,489.87);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (495.31,489.57) --
+	(495.31,490.16);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (495.31,486.64) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (505.41,499.95) --
+	(506.19,499.95);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (505.81,499.66) --
+	(505.81,500.24);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (505.81,497.05) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (500.70,501.75) --
+	(500.85,501.75);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (500.78,501.69) --
+	(500.78,501.80);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (500.78,497.71) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (491.03,485.79) --
+	(491.76,485.79);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (491.40,485.54) --
+	(491.40,486.03);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (491.40,482.88) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (492.75,487.50) --
+	(493.46,487.50);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (493.11,487.21) --
+	(493.11,487.80);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (493.11,483.47) {$l$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (494.83,499.04) --
+	(495.63,499.04);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (495.24,498.77) --
+	(495.24,499.32);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (495.24,496.14) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (505.95,500.55) --
+	(506.31,500.55);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (506.13,500.44) --
+	(506.13,500.66);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (506.13,497.65) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (462.98,451.79) --
+	(464.80,451.79);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (463.91,451.27) --
+	(463.91,452.29);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (463.91,448.56) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (495.67,489.99) --
+	(496.23,489.99);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (495.95,489.81) --
+	(495.95,490.18);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (495.95,487.09) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (493.57,492.80) --
+	(493.74,492.80);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (493.65,492.74) --
+	(493.65,492.85);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (493.65,488.76) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (454.25,445.43) --
+	(456.37,445.43);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (455.34,444.89) --
+	(455.34,445.95);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (455.34,442.52) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (456.44,448.01) --
+	(458.55,448.01);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (457.52,447.49) --
+	(457.52,448.51);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (457.52,443.97) {$l$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (459.40,462.20) --
+	(460.96,462.20);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (460.19,461.65) --
+	(460.19,462.73);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (460.19,459.29) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (495.85,490.73) --
+	(496.01,490.73);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (495.93,490.65) --
+	(495.93,490.82);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (495.93,487.83) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (450.34,464.66) --
+	(452.04,464.66);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (451.21,464.12) --
+	(451.21,465.18);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (451.21,461.43) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (493.92,489.34) --
+	(494.53,489.34);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (494.23,489.09) --
+	(494.23,489.58);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (494.23,486.43) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (486.83,489.35) --
+	(487.11,489.35);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (486.97,489.15) --
+	(486.97,489.55);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (486.97,485.32) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (445.39,461.69) --
+	(446.94,461.69);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (446.18,461.16) --
+	(446.18,462.22);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (446.18,458.79) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (448.41,463.55) --
+	(450.07,463.55);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (449.26,463.00) --
+	(449.26,464.08);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (449.26,459.51) {$l$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (454.64,470.31) --
+	(456.23,470.31);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (455.45,469.79) --
+	(455.45,470.82);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (455.45,467.41) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (495.01,490.35) --
+	(495.35,490.35);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (495.18,490.11) --
+	(495.18,490.60);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (495.18,487.45) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (410.72,427.41) --
+	(413.08,427.41);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (411.94,426.32) --
+	(411.94,428.45);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (411.94,424.19) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (474.42,462.41) --
+	(474.99,462.41);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (474.71,461.74) --
+	(474.71,463.06);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.71,459.50) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (451.45,467.41) --
+	(451.72,467.41);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (451.59,467.24) --
+	(451.59,467.58);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (451.59,463.38) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (409.10,426.94) --
+	(411.62,426.94);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (410.40,425.89) --
+	(410.40,427.93);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (410.40,424.03) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (410.30,427.14) --
+	(412.58,427.14);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (411.48,426.01) --
+	(411.48,428.20);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (411.48,423.11) {$l$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (409.51,441.14) --
+	(413.11,441.14);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (411.40,439.81) --
+	(411.40,442.38);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (411.40,438.23) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (477.61,473.14) --
+	(477.89,473.14);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (477.75,472.98) --
+	(477.75,473.30);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (477.75,470.24) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (496.72,491.90) --
+	(497.40,491.90);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (497.06,491.57) --
+	(497.06,492.23);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (497.06,488.68) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (500.24,494.94) --
+	(500.81,494.94);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (500.53,494.63) --
+	(500.53,495.24);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (500.53,492.04) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (510.36,505.18) --
+	(510.44,505.18);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (510.40,505.15) --
+	(510.40,505.21);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (510.40,501.15) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (489.39,485.14) --
+	(490.08,485.14);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (489.74,484.76) --
+	(489.74,485.50);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (489.74,482.23) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (494.71,490.54) --
+	(495.43,490.54);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (495.07,490.21) --
+	(495.07,490.85);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (495.07,486.50) {$l$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (486.11,483.52) --
+	(486.94,483.52);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (486.53,483.11) --
+	(486.53,483.93);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (486.53,480.62) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (500.63,495.41) --
+	(500.88,495.41);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (500.76,495.32) --
+	(500.76,495.49);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (500.76,492.50) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (448.62,459.08) --
+	(451.05,459.08);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (449.87,458.35) --
+	(449.87,459.79);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (449.87,455.85) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (505.52,495.76) --
+	(506.11,495.76);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (505.82,495.49) --
+	(505.82,496.03);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (505.82,492.85) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (486.56,496.08) --
+	(486.97,496.08);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (486.77,495.98) --
+	(486.77,496.19);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (486.77,492.05) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (447.38,457.54) --
+	(449.79,457.54);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (448.62,456.85) --
+	(448.62,458.21);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (448.62,454.64) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (449.09,459.53) --
+	(451.51,459.53);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (450.34,458.82) --
+	(450.34,460.21);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (450.34,455.50) {$l$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (454.86,474.65) --
+	(457.55,474.65);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (456.25,473.94) --
+	(456.25,475.33);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (456.25,471.74) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (504.11,498.52) --
+	(504.65,498.52);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (504.38,498.30) --
+	(504.38,498.73);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (504.38,495.61) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (467.90,466.02) --
+	(468.90,466.02);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (468.41,465.37) --
+	(468.41,466.64);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.41,462.79) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (480.58,476.12) --
+	(481.79,476.12);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (481.20,475.44) --
+	(481.20,476.77);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (481.20,473.22) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (483.85,480.75) --
+	(484.01,480.75);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (483.93,480.67) --
+	(483.93,480.84);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.93,476.72) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (467.69,466.41) --
+	(468.65,466.41);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (468.17,466.01) --
+	(468.17,466.81);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.17,463.51) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (466.71,464.95) --
+	(467.77,464.95);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (467.25,464.33) --
+	(467.25,465.56);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (467.25,460.92) {$l$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (470.77,472.46) --
+	(471.64,472.46);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (471.21,471.96) --
+	(471.21,472.95);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (471.21,469.56) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (493.45,489.31) --
+	(493.81,489.31);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (493.63,489.19) --
+	(493.63,489.43);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (493.63,486.41) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (488.67,486.27) --
+	(489.28,486.27);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (488.98,486.05) --
+	(488.98,486.50);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (488.98,483.05) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (476.21,473.16) --
+	(477.13,473.16);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (476.68,472.60) --
+	(476.68,473.70);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (476.68,470.25) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (493.20,490.92) --
+	(493.35,490.92);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (493.28,490.86) --
+	(493.28,490.98);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (493.28,486.89) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (483.12,480.77) --
+	(483.69,480.77);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (483.41,480.54) --
+	(483.41,481.00);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.41,477.86) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (488.63,486.02) --
+	(489.23,486.02);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (488.94,485.79) --
+	(488.94,486.26);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (488.94,481.99) {$l$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (481.40,481.81) --
+	(482.13,481.81);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (481.77,481.42) --
+	(481.77,482.20);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (481.77,478.91) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (503.05,499.85) --
+	(503.44,499.85);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (503.24,499.72) --
+	(503.24,499.97);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (503.24,496.94) {$\kappa$};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,259.88) {\bfseries adapt (\textit{quant}) vs. adapt (\textit{real})};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54, 11.95) {ESS/hr [adapt (\textit{real})]};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,144.54) {ESS/hr [adapt (\textit{quant})]};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54,259.88) {\bfseries adapt(\textit{quant}) vs. adapt(\textit{real})};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at (144.54, 11.95) {ESS/hr [adapt(\textit{real})]};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.24] at ( 17.93,144.54) {ESS/hr [adapt(\textit{quant})]};
 \end{scope}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (146.50,133.74) --
-	(158.32,133.74);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (153.31,131.32) --
-	(153.31,135.89);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (153.31,130.51) {$p$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.95,163.49) --
-	(178.84,163.49);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.99,162.82) --
-	(176.99,164.14);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.99,159.46) {$L$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.56,157.59) --
-	(170.70,157.59);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.66,156.14) --
-	(169.66,158.94);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.66,153.56) {$r$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (120.83,129.44) --
-	(137.61,129.44);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (131.01,122.67) --
-	(131.01,134.44);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (131.01,125.41) {$h$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.90,141.72) --
-	(159.98,141.72);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (156.37,137.34) --
-	(156.37,145.28);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (156.37,138.82) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.83,162.12) --
-	(176.64,162.12);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.24,160.75) --
-	(176.24,163.41);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.24,159.22) {$\kappa$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (206.61,196.97) --
-	(211.92,196.97);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (209.45,191.89) --
-	(209.45,200.98);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.45,193.75) {$p$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.12,178.33) --
-	(191.41,178.33);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.11,174.91) --
-	(188.11,181.23);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.11,174.29) {$L$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (215.05,209.76) --
-	(220.92,209.76);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (218.21,206.00) --
-	(218.21,212.89);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (218.21,205.72) {$r$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.26,190.94) --
-	(202.02,190.94);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.36,186.45) --
-	(199.36,194.56);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.36,186.90) {$h$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (208.62,206.77) --
-	(213.55,206.77);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.24,201.30) --
-	(211.24,211.01);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.24,203.86) {$\sigma$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (216.36,208.18) --
-	(221.74,208.18);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (219.24,204.65) --
-	(219.24,211.15);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (219.24,205.27) {$\kappa$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (170.39,155.17) --
-	(174.21,155.17);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.40,150.44) --
-	(172.40,158.96);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.40,151.94) {$p$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.34,175.38) --
-	(189.43,175.38);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.67,174.47) --
-	(184.67,176.26);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.67,171.35) {$L$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (210.41,197.56) --
-	(211.05,197.56);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (210.73,197.01) --
-	(210.73,198.09);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.73,193.52) {$r$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (141.67,140.93) --
-	(146.43,140.93);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (144.20,135.37) --
-	(144.20,145.24);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (144.20,136.90) {$h$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.87,163.94) --
-	(171.13,163.94);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.26,159.82) --
-	(168.26,167.33);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (168.26,161.04) {$\sigma$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.02,195.44) --
-	(211.33,195.44);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.18,194.67) --
-	(211.18,196.19);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.18,192.54) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.97,166.20) --
-	(186.25,166.20);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.37,164.42) --
-	(183.37,167.82);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.37,162.97) {$p$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.10,166.51) --
-	(181.55,166.51);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.36,164.69) --
-	(180.36,168.17);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.36,162.48) {$L$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (205.00,192.01) --
-	(205.67,192.01);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (205.34,191.61) --
-	(205.34,192.41);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.34,187.98) {$r$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.25,166.26) --
-	(175.78,166.26);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.80,164.04) --
-	(172.80,168.25);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.80,162.22) {$h$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.64,170.18) --
-	(179.53,170.18);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (177.68,167.85) --
-	(177.68,172.25);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.68,167.27) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (210.63,193.27) --
-	(211.52,193.27);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.08,192.90) --
-	(211.08,193.64);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.08,190.37) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.90,130.82) --
-	(176.00,130.82);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.78,129.32) --
-	(172.78,132.21);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.78,127.59) {$p$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.77,169.21) --
-	(185.79,169.21);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.60,167.03) --
-	(182.60,171.17);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.60,165.18) {$L$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.37,168.04) --
-	(184.73,168.04);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.55,167.56) --
-	(184.55,168.52);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.55,164.01) {$r$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (135.31,130.19) --
-	(143.24,130.19);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (139.69,128.38) --
-	(139.69,131.85);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (139.69,126.16) {$h$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (155.19,142.45) --
-	(167.05,142.45);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (162.02,139.32) --
-	(162.02,145.14);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (162.02,139.55) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.63,174.17) --
-	(193.45,174.17);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.05,173.92) --
-	(193.05,174.43);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.05,171.27) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.12,202.35) --
-	(197.79,202.35);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.92,199.26) --
-	(190.92,205.02);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.92,199.13) {$p$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.46,184.18) --
-	(196.61,184.18);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.78,180.38) --
-	(193.78,187.35);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.78,180.15) {$L$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (219.14,211.64) --
-	(224.12,211.64);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (221.79,208.60) --
-	(221.79,214.27);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (221.79,207.61) {$r$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.38,173.82) --
-	(189.02,173.82);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.99,170.50) --
-	(185.99,176.65);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.99,169.79) {$h$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.11,188.11) --
-	(197.75,188.11);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.72,184.94) --
-	(194.72,190.83);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.72,185.21) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (210.74,202.01) --
-	(215.88,202.01);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (213.48,199.20) --
-	(213.48,204.45);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (213.48,199.10) {$\kappa$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (206.88,164.39) --
-	(208.61,164.39);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (207.77,160.23) --
-	(207.77,167.80);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.77,161.16) {$p$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (212.42,195.94) --
-	(215.29,195.94);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (213.91,194.12) --
-	(213.91,197.60);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (213.91,191.91) {$L$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (213.22,200.28) --
-	(213.63,200.28);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (213.43,199.87) --
-	(213.43,200.68);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (213.43,196.25) {$r$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.15,172.87) --
-	(185.15,172.87);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.18,167.27) --
-	(184.18,177.19);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.18,168.83) {$h$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.86,177.89) --
-	(188.03,177.89);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.62,174.55) --
-	(185.62,180.72);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.62,174.98) {$\sigma$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (220.47,202.23) --
-	(222.20,202.23);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (221.35,200.86) --
-	(221.35,203.50);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (221.35,199.32) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.03,169.69) --
-	(189.30,169.69);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.60,167.16) --
-	(185.60,171.92);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.60,166.46) {$p$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (160.20,152.05) --
-	(167.00,152.05);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (163.90,149.10) --
-	(163.90,154.60);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (163.90,148.02) {$L$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.27,183.74) --
-	(197.13,183.74);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.70,183.51) --
-	(196.70,183.97);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.70,179.71) {$r$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.93,154.74) --
-	(161.87,154.74);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (157.54,150.34) --
-	(157.54,158.32);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (157.54,150.71) {$h$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.82,169.02) --
-	(187.62,169.02);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.72,164.73) --
-	(183.72,172.53);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.72,166.12) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (208.08,192.83) --
-	(210.78,192.83);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (209.48,192.75) --
-	(209.48,192.91);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.48,189.92) {$\kappa$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.46,189.89) --
-	(195.43,189.89);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.68,178.21) --
-	(192.68,197.08);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.68,186.66) {$p$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.71,176.30) --
-	(192.19,176.30);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.23,164.31) --
-	(189.23,183.61);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (189.23,172.27) {$L$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.23,193.39) --
-	(211.47,193.39);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.35,181.48) --
-	(211.35,200.68);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.35,189.36) {$r$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.76,175.37) --
-	(193.70,175.37);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.83,162.85) --
-	(191.83,182.87);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.83,171.34) {$h$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.26,184.99) --
-	(197.38,184.99);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (196.35,173.03) --
-	(196.35,192.30);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.35,182.09) {$\sigma$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (222.96,202.29) --
-	(224.24,202.29);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (223.61,190.24) --
-	(223.61,209.63);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (223.61,199.39) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (215.71,200.79) --
+	(216.21,200.79);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (215.96,200.49) --
+	(215.96,201.08);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (215.96,197.56) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (217.87,210.87) --
+	(218.74,210.87);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (218.31,210.58) --
+	(218.31,211.16);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (218.31,207.97) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (222.05,212.67) --
+	(222.17,212.67);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (222.11,212.61) --
+	(222.11,212.72);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (222.11,208.63) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (204.39,196.71) --
+	(205.03,196.71);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (204.71,196.46) --
+	(204.71,196.95);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (204.71,193.80) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (206.90,198.42) --
+	(207.56,198.42);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (207.23,198.13) --
+	(207.23,198.72);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.23,194.39) {$l$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (217.20,209.96) --
+	(217.65,209.96);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (217.43,209.69) --
+	(217.43,210.24);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (217.43,207.06) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (223.39,211.47) --
+	(223.63,211.47);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (223.51,211.36) --
+	(223.51,211.58);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (223.51,208.57) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (179.00,162.71) --
+	(180.64,162.71);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (179.84,162.19) --
+	(179.84,163.21);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.84,159.48) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (208.14,200.91) --
+	(208.69,200.91);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (208.41,200.73) --
+	(208.41,201.10);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (208.41,198.01) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (211.10,203.72) --
+	(211.24,203.72);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (211.17,203.66) --
+	(211.17,203.77);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.17,199.68) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (163.33,156.35) --
+	(165.16,156.35);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (164.27,155.81) --
+	(164.27,156.87);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (164.27,153.44) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (165.31,158.93) --
+	(167.17,158.93);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (166.26,158.41) --
+	(166.26,159.43);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (166.26,154.89) {$l$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (176.45,173.12) --
+	(178.09,173.12);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (177.29,172.57) --
+	(177.29,173.65);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.29,170.21) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (211.97,201.65) --
+	(212.15,201.65);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (212.06,201.57) --
+	(212.06,201.74);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.06,198.75) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (187.53,175.58) --
+	(188.46,175.58);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (188.00,175.04) --
+	(188.00,176.10);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.00,172.35) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (204.49,200.26) --
+	(204.98,200.26);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (204.74,200.01) --
+	(204.74,200.50);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (204.74,197.35) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (205.85,200.27) --
+	(205.99,200.27);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (205.92,200.07) --
+	(205.92,200.47);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.92,196.24) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (180.61,172.61) --
+	(181.38,172.61);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (180.99,172.08) --
+	(180.99,173.14);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.99,169.71) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (181.65,174.47) --
+	(182.43,174.47);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (182.05,173.92) --
+	(182.05,175.00);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.05,170.43) {$l$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (184.47,181.23) --
+	(185.43,181.23);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (184.96,180.71) --
+	(184.96,181.74);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.96,178.33) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (211.62,201.27) --
+	(211.82,201.27);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (211.72,201.03) --
+	(211.72,201.52);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.72,198.37) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (181.10,138.33) --
+	(182.11,138.33);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (181.61,137.24) --
+	(181.61,139.37);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.61,135.11) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (179.53,173.33) --
+	(180.10,173.33);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (179.82,172.66) --
+	(179.82,173.98);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.82,170.42) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (186.37,178.33) --
+	(186.61,178.33);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (186.49,178.16) --
+	(186.49,178.50);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (186.49,174.30) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (152.97,137.86) --
+	(154.18,137.86);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (153.59,136.81) --
+	(153.59,138.85);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (153.59,134.95) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (152.81,138.06) --
+	(154.10,138.06);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (153.47,136.93) --
+	(153.47,139.12);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (153.47,134.03) {$l$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (168.90,152.06) --
+	(170.43,152.06);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (169.68,150.73) --
+	(169.68,153.30);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.68,149.15) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (193.75,184.06) --
+	(193.91,184.06);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (193.83,183.90) --
+	(193.83,184.22);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.83,181.16) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (197.25,202.82) --
+	(199.73,202.82);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (198.53,202.49) --
+	(198.53,203.15);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.53,199.60) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (214.67,205.86) --
+	(215.33,205.86);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (215.00,205.55) --
+	(215.00,206.16);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (215.00,202.96) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (227.10,216.10) --
+	(227.18,216.10);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (227.14,216.07) --
+	(227.14,216.13);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (227.14,212.07) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (208.25,196.06) --
+	(208.93,196.06);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (208.59,195.68) --
+	(208.59,196.42);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (208.59,193.15) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (213.60,201.46) --
+	(214.11,201.46);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (213.86,201.13) --
+	(213.86,201.77);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (213.86,197.42) {$l$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (201.86,194.44) --
+	(202.47,194.44);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (202.16,194.03) --
+	(202.16,194.85);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.16,191.54) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (218.51,206.33) --
+	(218.73,206.33);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (218.62,206.24) --
+	(218.62,206.41);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (218.62,203.42) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (210.27,170.00) --
+	(210.98,170.00);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (210.63,169.27) --
+	(210.63,170.71);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.63,166.77) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (209.58,206.68) --
+	(210.16,206.68);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (209.87,206.41) --
+	(209.87,206.95);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.87,203.77) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (214.53,207.00) --
+	(214.66,207.00);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (214.59,206.90) --
+	(214.59,207.11);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (214.59,202.97) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (181.38,168.46) --
+	(182.64,168.46);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (182.02,167.77) --
+	(182.02,169.13);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.02,165.56) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (181.82,170.45) --
+	(183.06,170.45);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (182.45,169.74) --
+	(182.45,171.13);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.45,166.42) {$l$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (194.04,185.57) --
+	(194.95,185.57);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (194.50,184.86) --
+	(194.50,186.25);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.50,182.66) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (223.34,209.44) --
+	(223.68,209.44);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (223.51,209.22) --
+	(223.51,209.65);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (223.51,206.53) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (191.51,176.94) --
+	(192.36,176.94);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (191.94,176.29) --
+	(191.94,177.56);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.94,173.71) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (192.19,187.04) --
+	(195.37,187.04);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (193.85,186.36) --
+	(193.85,187.69);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.85,184.14) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (199.84,191.67) --
+	(200.03,191.67);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (199.93,191.59) --
+	(199.93,191.76);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.93,187.64) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (184.16,177.33) --
+	(184.81,177.33);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (184.49,176.93) --
+	(184.49,177.73);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.49,174.43) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (183.57,175.87) --
+	(184.20,175.87);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (183.89,175.25) --
+	(183.89,176.48);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.89,171.84) {$l$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (191.51,183.38) --
+	(192.28,183.38);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (191.90,182.88) --
+	(191.90,183.87);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.90,180.48) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (212.14,200.23) --
+	(212.37,200.23);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (212.25,200.11) --
+	(212.25,200.35);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.25,197.33) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (198.34,197.19) --
+	(199.21,197.19);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (198.78,196.97) --
+	(198.78,197.42);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.78,193.97) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (194.27,184.08) --
+	(195.55,184.08);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (194.92,183.52) --
+	(194.92,184.62);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.92,181.17) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (211.76,201.84) --
+	(211.89,201.84);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (211.83,201.78) --
+	(211.83,201.90);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.83,197.81) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (200.86,191.69) --
+	(201.30,191.69);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (201.08,191.46) --
+	(201.08,191.92);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (201.08,188.78) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (206.45,196.94) --
+	(206.96,196.94);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (206.71,196.71) --
+	(206.71,197.18);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (206.71,192.91) {$l$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (200.40,192.73) --
+	(201.41,192.73);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (200.92,192.34) --
+	(200.92,193.12);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (200.92,189.83) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (222.89,210.77) --
+	(223.29,210.77);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (223.09,210.64) --
+	(223.09,210.89);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (223.09,207.86) {$\kappa$};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (485.73,186.78) --
-	(485.73, 81.34);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (485.73,169.78) {$130\times $};
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (356.88,127.23) --
+	(356.88, 94.67);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (358.78,108.88) {$1.7\times $};
 \definecolor{fillColor}{RGB}{255,0,109}
 
-\path[fill=fillColor] (485.73,186.78) circle (  1.87);
-
-\path[fill=fillColor] (485.73, 84.24) --
-	(488.24, 79.89) --
-	(483.21, 79.89) --
+\path[fill=fillColor] (356.88,127.23) circle (  1.87);
+
+\path[fill=fillColor] (356.88, 97.58) --
+	(359.40, 93.22) --
+	(354.37, 93.22) --
 	cycle;
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (356.88,239.03) --
-	(356.88,234.24);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (356.88,234.69) {$1.2\times $};
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (394.78, 93.40) --
+	(394.78, 80.86);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (396.67, 85.06) {$1.4\times $};
 \definecolor{fillColor}{RGB}{253,104,0}
 
-\path[fill=fillColor] (356.88,239.03) circle (  1.87);
-
-\path[fill=fillColor] (356.88,237.15) --
-	(359.40,232.79) --
-	(354.37,232.79) --
+\path[fill=fillColor] (394.78, 93.40) circle (  1.87);
+
+\path[fill=fillColor] (394.78, 83.77) --
+	(397.29, 79.41) --
+	(392.26, 79.41) --
 	cycle;
+
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (390.04, 82.94) --
+	(390.04, 71.70);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (391.93, 75.24) {$1.5\times $};
 \definecolor{fillColor}{RGB}{143,161,0}
 
-\path[fill=fillColor] (394.78,233.05) circle (  1.87);
+\path[fill=fillColor] (390.04, 82.94) circle (  1.87);
+
+\path[fill=fillColor] (390.04, 74.60) --
+	(392.55, 70.24) --
+	(387.52, 70.24) --
+	cycle;
+
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (404.25, 61.80) --
+	(404.25, 53.19);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (406.15, 55.42) {$3.5\times $};
 \definecolor{fillColor}{RGB}{0,195,0}
 
-\path[fill=fillColor] (390.04,227.01) circle (  1.87);
-
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (404.25,203.42) --
-	(404.25,173.39);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (404.25,191.14) {$4\times $};
+\path[fill=fillColor] (404.25, 61.80) circle (  1.87);
+
+\path[fill=fillColor] (404.25, 56.09) --
+	(406.77, 51.74) --
+	(401.74, 51.74) --
+	cycle;
+
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (359.72,150.32) --
+	(359.72,123.79);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (361.62,134.98) {$1.4\times $};
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[fill=fillColor] (404.25,203.42) circle (  1.87);
-
-\path[fill=fillColor] (404.25,176.30) --
-	(406.77,171.94) --
-	(401.74,171.94) --
+\path[fill=fillColor] (359.72,150.32) circle (  1.87);
+
+\path[fill=fillColor] (359.72,126.70) --
+	(362.24,122.34) --
+	(357.21,122.34) --
 	cycle;
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (359.72,244.03) --
-	(359.72,242.10);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (359.72,241.01) {$1.1\times $};
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (433.62,101.96) --
+	(433.62, 71.34);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (435.51, 84.58) {$2.4\times $};
 \definecolor{fillColor}{RGB}{0,216,255}
 
-\path[fill=fillColor] (359.72,244.03) circle (  1.87);
-
-\path[fill=fillColor] (359.72,245.01) --
-	(362.24,240.65) --
-	(357.21,240.65) --
+\path[fill=fillColor] (433.62,101.96) circle (  1.87);
+
+\path[fill=fillColor] (433.62, 74.24) --
+	(436.14, 69.88) --
+	(431.10, 69.88) --
 	cycle;
+
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (359.72, 74.13) --
+	(359.72, 68.32);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (361.62, 69.15) {$1.3\times $};
 \definecolor{fillColor}{RGB}{151,0,255}
 
-\path[fill=fillColor] (433.62,236.07) circle (  1.87);
-
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (359.72,217.25) --
-	(359.72,208.71);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (359.72,211.32) {$1.5\times $};
+\path[fill=fillColor] (359.72, 74.13) circle (  1.87);
+
+\path[fill=fillColor] (359.72, 71.22) --
+	(362.24, 66.86) --
+	(357.21, 66.86) --
+	cycle;
+
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (346.46, 95.05) --
+	(346.46, 80.15);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (348.35, 85.52) {$1.5\times $};
 \definecolor{fillColor}{RGB}{255,0,255}
 
-\path[fill=fillColor] (359.72,217.25) circle (  1.87);
-
-\path[fill=fillColor] (359.72,211.61) --
-	(362.24,207.26) --
-	(357.21,207.26) --
-	cycle;
-
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (346.46,233.81) --
-	(346.46,219.02);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (346.46,225.57) {$2\times $};
-\definecolor{fillColor}{RGB}{68,68,68}
-
-\path[fill=fillColor] (346.46,233.81) circle (  1.87);
-
-\path[fill=fillColor] (346.46,221.92) --
-	(348.97,217.56) --
-	(343.94,217.56) --
+\path[fill=fillColor] (346.46, 95.05) circle (  1.87);
+
+\path[fill=fillColor] (346.46, 83.05) --
+	(348.97, 78.70) --
+	(343.94, 78.70) --
 	cycle;
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 49.80) -- (338.88,235.31);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 49.80) -- (338.88,239.28);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 84.85) -- (333.90, 84.85);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 99.95) -- (333.90, 99.95);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,135.01) -- (333.90,135.01);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,150.10) -- (333.90,150.10);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,185.16) -- (333.90,185.16);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,200.25) -- (333.90,200.25);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,235.31) -- (333.90,235.31);
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92, 46.94) {1};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92, 82.00) {5};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92, 97.09) {10};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,132.15) {50};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,147.24) {100};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,182.30) {500};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,197.40) {1000};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,232.45) {5000};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 97.17) -- (333.90, 97.17);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,144.54) -- (333.90,144.54);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,191.91) -- (333.90,191.91);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,239.28) -- (333.90,239.28);
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92, 46.94) {0};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92, 94.31) {5000};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,141.68) {10000};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,189.05) {15000};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,236.42) {20000};
 \end{scope}

### 2020-08-31 benchmarking/benchmarkingVM/ESS_round3.tex
Results update

--- 2020-08-26 benchmarking/benchmarkingVM/ESS_round3.tex
@@
-% Created by tikzDevice version 0.12.3.1 on 2020-08-25 15:33:46
+% Created by tikzDevice version 0.12.3.1 on 2020-08-31 17:26:53
 % !TEX encoding = UTF-8 Unicode
@@
 \definecolor{fillColor}{RGB}{255,255,255}
-\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (289.08,289.08);
+\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (578.16,357.33);
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
+\path[clip] (  0.00,  0.00) rectangle (578.16,357.33);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at (144.54,253.90) {\bfseries Bactrian (\textit{real}) vs. adapt (\textit{real})};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at (301.08,335.19) {\bfseries Comparison of Bactrian+adapt(\textit{real}) and adapt(\textit{real})};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at (144.54, 14.40) {ESS/hr [adapt (\textit{real})]};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at ( 21.60,144.54) {ESS/hr [Bactrian (\textit{real})]};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (  9.60,190.67) {Relative ESS/hr};
 \end{scope}
 \begin{scope}
-\path[clip] ( 60.00, 60.00) rectangle (229.08,229.08);
+\path[clip] ( 48.00, 60.00) rectangle (554.16,321.33);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (  0.00, 71.00) --
-	(218.08,289.08);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] ( 48.00,173.19) --
+	(474.88,173.19);
+\definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (268.39,289.08) --
-	(268.39,197.39) --
-	( 71.00,  0.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.10,246.09) --
+	( 54.10,233.67);
+\definecolor{fillColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00, 47.34) --
-	(241.74,289.08);
+\path[fill=fillColor] ( 54.10,239.88) circle (  2.25);
+\definecolor{drawColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (268.39,289.08) --
-	(268.39,221.06) --
-	( 47.34,  0.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.20,249.96) --
+	( 60.20,218.26);
+\definecolor{fillColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round] (  0.00, 23.67) --
-	(265.41,289.08);
+\path[fill=fillColor] ( 60.20,234.11) circle (  2.25);
+\definecolor{drawColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round] (268.39,289.08) --
-	(268.39,244.72) --
-	( 23.67,  0.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.29,226.82) --
+	( 66.29,207.10);
+\definecolor{fillColor}{RGB}{143,161,0}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (140.08, 64.13) {$\frac{1}{64} \times$};
+\path[fill=fillColor] ( 66.29,216.96) circle (  2.25);
+\definecolor{drawColor}{RGB}{0,195,0}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,144.78) {$64\times$};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 72.39,210.32) --
+	( 72.39,191.80);
+\definecolor{fillColor}{RGB}{0,195,0}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (116.41, 64.13) {$\frac{1}{16} \times$};
+\path[fill=fillColor] ( 72.39,201.06) circle (  2.25);
+\definecolor{drawColor}{RGB}{0,219,171}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,121.11) {$16\times$};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 78.49,205.70) --
+	( 78.49,138.28);
+\definecolor{fillColor}{RGB}{0,219,171}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 90.75, 64.13) {$\frac{1}{4} \times$};
+\path[fill=fillColor] ( 78.49,171.99) circle (  2.25);
+\definecolor{drawColor}{RGB}{0,216,255}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 62.56, 97.44) {$4\times$};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 84.59,250.06) --
+	( 84.59,239.46);
+\definecolor{fillColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 60.00, 60.00) -- (229.08,229.08);
+\path[fill=fillColor] ( 84.59,244.76) circle (  2.25);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (200.17,196.99) --
-	(201.72,196.99);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 90.69,223.96) --
+	( 90.69,209.76);
+\definecolor{fillColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (200.96,196.43) --
-	(200.96,197.53);
+\path[fill=fillColor] ( 90.69,216.86) circle (  2.25);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 96.79,229.79) --
+	( 96.79,207.30);
+\definecolor{fillColor}{RGB}{255,0,255}
+
+\path[fill=fillColor] ( 96.79,218.55) circle (  2.25);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] ( 54.10,218.87) --
+	(102.88,218.87);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 78.49,284.14) {18\% faster};
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (108.98,  0.00) --
+	(108.98,357.33);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (115.08,231.18) --
+	(115.08,216.59);
+\definecolor{fillColor}{RGB}{255,0,109}
+
+\path[fill=fillColor] (115.08,223.89) circle (  2.25);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.18,210.48) --
+	(121.18,196.00);
+\definecolor{fillColor}{RGB}{253,104,0}
+
+\path[fill=fillColor] (121.18,203.24) circle (  2.25);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (127.28,217.85) --
+	(127.28,208.48);
+\definecolor{fillColor}{RGB}{143,161,0}
+
+\path[fill=fillColor] (127.28,213.17) circle (  2.25);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (133.38,206.09) --
+	(133.38,189.08);
+\definecolor{fillColor}{RGB}{0,195,0}
+
+\path[fill=fillColor] (133.38,197.58) circle (  2.25);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (139.47,184.21) --
+	(139.47,163.53);
+\definecolor{fillColor}{RGB}{0,219,171}
+
+\path[fill=fillColor] (139.47,173.87) circle (  2.25);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.57,274.87) --
+	(145.57,264.59);
+\definecolor{fillColor}{RGB}{0,216,255}
+
+\path[fill=fillColor] (145.57,269.73) circle (  2.25);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (200.96,193.10) {$p$};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.67,345.05) --
+	(151.67,220.65);
+\definecolor{fillColor}{RGB}{151,0,255}
+
+\path[fill=fillColor] (151.67,282.85) circle (  2.25);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (157.77,222.89) --
+	(157.77,199.51);
+\definecolor{fillColor}{RGB}{255,0,255}
+
+\path[fill=fillColor] (157.77,211.20) circle (  2.25);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (115.08,224.11) --
+	(163.87,224.11);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (139.47,284.14) {20\% faster};
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (169.97,  0.00) --
+	(169.97,357.33);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.06,237.79) --
+	(176.06,235.79);
+\definecolor{fillColor}{RGB}{255,0,109}
+
+\path[fill=fillColor] (176.06,236.79) circle (  2.25);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.16,213.87) --
+	(182.16,210.98);
+\definecolor{fillColor}{RGB}{253,104,0}
+
+\path[fill=fillColor] (182.16,212.42) circle (  2.25);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.26,213.40) --
+	(188.26,210.38);
+\definecolor{fillColor}{RGB}{143,161,0}
+
+\path[fill=fillColor] (188.26,211.89) circle (  2.25);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.36,192.72) --
+	(194.36,185.58);
+\definecolor{fillColor}{RGB}{0,195,0}
+
+\path[fill=fillColor] (194.36,189.15) circle (  2.25);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.46,187.16) --
+	(200.46,185.57);
+\definecolor{fillColor}{RGB}{0,219,171}
+
+\path[fill=fillColor] (200.46,186.36) circle (  2.25);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.56,240.68) --
+	(206.56,238.19);
+\definecolor{fillColor}{RGB}{0,216,255}
+
+\path[fill=fillColor] (206.56,239.44) circle (  2.25);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (205.11,198.75) --
-	(207.67,198.75);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.65,223.05) --
+	(212.65,219.07);
+\definecolor{fillColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (206.44,197.10) --
-	(206.44,200.25);
+\path[fill=fillColor] (212.65,221.06) circle (  2.25);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.75,215.97) --
+	(218.75,213.85);
+\definecolor{fillColor}{RGB}{255,0,255}
+
+\path[fill=fillColor] (218.75,214.91) circle (  2.25);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (176.06,214.59) --
+	(224.85,214.59);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (200.46,284.14) {16\% faster};
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (230.95,  0.00) --
+	(230.95,357.33);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.05,250.44) --
+	(237.05,241.85);
+\definecolor{fillColor}{RGB}{255,0,109}
+
+\path[fill=fillColor] (237.05,246.14) circle (  2.25);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (243.15,239.13) --
+	(243.15,208.60);
+\definecolor{fillColor}{RGB}{253,104,0}
+
+\path[fill=fillColor] (243.15,223.86) circle (  2.25);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (249.24,213.14) --
+	(249.24,198.87);
+\definecolor{fillColor}{RGB}{143,161,0}
+
+\path[fill=fillColor] (249.24,206.01) circle (  2.25);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (255.34,219.07) --
+	(255.34,189.90);
+\definecolor{fillColor}{RGB}{0,195,0}
+
+\path[fill=fillColor] (255.34,204.48) circle (  2.25);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44,175.34) --
+	(261.44,160.05);
+\definecolor{fillColor}{RGB}{0,219,171}
+
+\path[fill=fillColor] (261.44,167.69) circle (  2.25);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (267.54,231.48) --
+	(267.54,205.22);
+\definecolor{fillColor}{RGB}{0,216,255}
+
+\path[fill=fillColor] (267.54,218.35) circle (  2.25);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (206.44,193.89) {$L$};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (273.64,253.96) --
+	(273.64,239.75);
+\definecolor{fillColor}{RGB}{151,0,255}
+
+\path[fill=fillColor] (273.64,246.86) circle (  2.25);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (279.74,236.72) --
+	(279.74,225.81);
+\definecolor{fillColor}{RGB}{255,0,255}
+
+\path[fill=fillColor] (279.74,231.26) circle (  2.25);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (237.05,219.11) --
+	(285.83,219.11);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (261.44,284.14) {18\% faster};
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (291.93,  0.00) --
+	(291.93,357.33);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.03,240.03) --
+	(298.03,230.01);
+\definecolor{fillColor}{RGB}{255,0,109}
+
+\path[fill=fillColor] (298.03,235.02) circle (  2.25);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (304.13,238.59) --
+	(304.13,208.20);
+\definecolor{fillColor}{RGB}{253,104,0}
+
+\path[fill=fillColor] (304.13,223.39) circle (  2.25);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (310.23,210.81) --
+	(310.23,195.70);
+\definecolor{fillColor}{RGB}{143,161,0}
+
+\path[fill=fillColor] (310.23,203.25) circle (  2.25);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (316.33,228.88) --
+	(316.33,202.54);
+\definecolor{fillColor}{RGB}{0,195,0}
+
+\path[fill=fillColor] (316.33,215.71) circle (  2.25);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (322.42,175.84) --
+	(322.42,163.67);
+\definecolor{fillColor}{RGB}{0,219,171}
+
+\path[fill=fillColor] (322.42,169.76) circle (  2.25);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (328.52,230.74) --
+	(328.52,204.43);
+\definecolor{fillColor}{RGB}{0,216,255}
+
+\path[fill=fillColor] (328.52,217.58) circle (  2.25);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (205.83,203.06) --
-	(206.19,203.06);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (334.62,232.28) --
+	(334.62,208.40);
+\definecolor{fillColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (206.01,202.94) --
-	(206.01,203.18);
+\path[fill=fillColor] (334.62,220.34) circle (  2.25);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (340.72,233.20) --
+	(340.72,221.37);
+\definecolor{fillColor}{RGB}{255,0,255}
+
+\path[fill=fillColor] (340.72,227.29) circle (  2.25);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (298.03,214.66) --
+	(346.82,214.66);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (322.42,284.14) {16\% faster};
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (352.92,  0.00) --
+	(352.92,357.33);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (359.01,237.99) --
+	(359.01,223.51);
+\definecolor{fillColor}{RGB}{255,0,109}
+
+\path[fill=fillColor] (359.01,230.75) circle (  2.25);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (365.11,244.31) --
+	(365.11,211.56);
+\definecolor{fillColor}{RGB}{253,104,0}
+
+\path[fill=fillColor] (365.11,227.93) circle (  2.25);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (371.21,216.84) --
+	(371.21,196.62);
+\definecolor{fillColor}{RGB}{143,161,0}
+
+\path[fill=fillColor] (371.21,206.73) circle (  2.25);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (377.31,225.85) --
+	(377.31,198.06);
+\definecolor{fillColor}{RGB}{0,195,0}
+
+\path[fill=fillColor] (377.31,211.95) circle (  2.25);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (383.41,197.62) --
+	(383.41,172.56);
+\definecolor{fillColor}{RGB}{0,219,171}
+
+\path[fill=fillColor] (383.41,185.09) circle (  2.25);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.51,237.58) --
+	(389.51,211.29);
+\definecolor{fillColor}{RGB}{0,216,255}
+
+\path[fill=fillColor] (389.51,224.44) circle (  2.25);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (206.01,198.20) {$r$};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (395.60,213.92) --
+	(395.60,200.71);
+\definecolor{fillColor}{RGB}{151,0,255}
+
+\path[fill=fillColor] (395.60,207.32) circle (  2.25);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (401.70,230.89) --
+	(401.70,207.97);
+\definecolor{fillColor}{RGB}{255,0,255}
+
+\path[fill=fillColor] (401.70,219.43) circle (  2.25);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (359.01,214.55) --
+	(407.80,214.55);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (383.41,284.14) {16\% faster};
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (413.90,  0.00) --
+	(413.90,357.33);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.00,182.77) --
+	(420.00,177.72);
+\definecolor{fillColor}{RGB}{255,0,109}
+
+\path[fill=fillColor] (420.00,180.25) circle (  2.25);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.10,177.03) --
+	(426.10,173.95);
+\definecolor{fillColor}{RGB}{253,104,0}
+
+\path[fill=fillColor] (426.10,175.49) circle (  2.25);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (432.19,175.37) --
+	(432.19,171.54);
+\definecolor{fillColor}{RGB}{143,161,0}
+
+\path[fill=fillColor] (432.19,173.45) circle (  2.25);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.29,175.65) --
+	(438.29,172.26);
+\definecolor{fillColor}{RGB}{0,195,0}
+
+\path[fill=fillColor] (438.29,173.95) circle (  2.25);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (444.39,182.05) --
+	(444.39,177.75);
+\definecolor{fillColor}{RGB}{0,219,171}
+
+\path[fill=fillColor] (444.39,179.90) circle (  2.25);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (450.49,176.59) --
+	(450.49,169.19);
+\definecolor{fillColor}{RGB}{0,216,255}
+
+\path[fill=fillColor] (450.49,172.89) circle (  2.25);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.99,182.32) --
-	(180.78,182.32);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (456.59,177.97) --
+	(456.59,173.15);
+\definecolor{fillColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.91,181.55) --
-	(179.91,183.06);
-\definecolor{drawColor}{RGB}{151,0,255}
+\path[fill=fillColor] (456.59,175.56) circle (  2.25);
+\definecolor{drawColor}{RGB}{255,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (179.91,177.46) {$h$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.69,183.83) --
+	(462.69,176.41);
+\definecolor{fillColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.73,181.94) --
-	(183.35,181.94);
+\path[fill=fillColor] (462.69,180.12) circle (  2.25);
+\definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.20,181.15) --
-	(181.20,182.69);
-\definecolor{drawColor}{RGB}{151,0,255}
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (420.00,176.47) --
+	(468.78,176.47);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (181.20,178.44) {$\sigma$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (444.39,284.14) {1.2\% faster};
+\definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (212.29,207.61) --
-	(213.84,207.61);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (213.08,206.84) --
-	(213.08,208.35);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (213.08,204.11) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (474.88,  0.00) --
+	(474.88,357.33);
 \end{scope}
 \begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (289.08,289.08);
+\path[clip] (  0.00,  0.00) rectangle (578.16,357.33);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- (217.25, 60.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 60.00) -- (554.16, 60.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- ( 60.00, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 78.49, 60.00) -- ( 78.49, 54.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.31, 60.00) -- ( 99.31, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (139.47, 60.00) -- (139.47, 54.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.62, 60.00) -- (138.62, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.46, 60.00) -- (200.46, 54.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.93, 60.00) -- (177.93, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44, 60.00) -- (261.44, 54.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.25, 60.00) -- (217.25, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (322.42, 60.00) -- (322.42, 54.00);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 60.00, 38.40) {1};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (383.41, 60.00) -- (383.41, 54.00);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 99.31, 38.40) {10};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (444.39, 60.00) -- (444.39, 54.00);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (138.62, 38.40) {100};
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at ( 80.56, 48.00) {Prior};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (177.93, 38.40) {1000};
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (141.54, 48.00) {Likelihood};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (217.25, 38.40) {10000};
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (202.52, 48.00) {Leaf rate};
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- ( 60.00,217.25);
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (263.51, 48.00) {Mean branch rate};
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- ( 54.00, 60.00);
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (324.49, 48.00) {Tree length};
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 99.31) -- ( 54.00, 99.31);
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (385.47, 48.00) {Clock SD $\sigma$};
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,138.62) -- ( 54.00,138.62);
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (446.46, 48.00) {HKY model $\kappa$};
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,177.93) -- ( 54.00,177.93);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 60.00) -- ( 48.00,286.39);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,217.25) -- ( 54.00,217.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 60.00) -- ( 42.00, 60.00);
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00, 56.56) {1};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 92.88) -- ( 42.00, 92.88);
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00, 95.87) {10};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,135.92) -- ( 42.00,135.92);
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,135.18) {100};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,173.19) -- ( 42.00,173.19);
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,174.49) {1000};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,210.47) -- ( 42.00,210.47);
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,213.80) {10000};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,253.51) -- ( 42.00,253.51);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,286.39) -- ( 42.00,286.39);
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 36.00, 56.56) {$\frac{2}{3}\times$};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 36.00, 89.44) {$\frac{3}{4}\times$};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 36.00,132.47) {$\frac{7}{8}\times$};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 36.00,169.75) {$1\times$};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 36.00,207.03) {$\frac{8}{7}\times$};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 36.00,250.06) {$\frac{4}{3}\times$};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 36.00,282.94) {$\frac{3}{2}\times$};
 \end{scope}
 \begin{scope}
-\path[clip] ( 60.00, 60.00) rectangle (229.08,229.08);
+\path[clip] ( 48.00, 60.00) rectangle (554.16,321.33);
 \definecolor{drawColor}{RGB}{0,0,0}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,171.00) rectangle (169.31,165.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.19,235.67) rectangle (494.39,229.67);
 \definecolor{fillColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,159.00) rectangle (169.31,153.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.19,223.67) rectangle (494.39,217.67);
 \definecolor{fillColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,147.00) rectangle (169.31,141.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.19,211.67) rectangle (494.39,205.67);
 \definecolor{fillColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,135.00) rectangle (169.31,129.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.19,199.67) rectangle (494.39,193.67);
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,123.00) rectangle (169.31,117.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.19,187.67) rectangle (494.39,181.67);
 \definecolor{fillColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,111.00) rectangle (169.31,105.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.19,175.67) rectangle (494.39,169.67);
 \definecolor{fillColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11, 99.00) rectangle (169.31, 93.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.19,163.67) rectangle (494.39,157.67);
 \definecolor{fillColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11, 87.00) rectangle (169.31, 81.00);
-\definecolor{fillColor}{RGB}{68,68,68}
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.19,151.67) rectangle (494.39,145.67);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11, 75.00) rectangle (169.31, 69.00);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (503.39,229.22) {Cognato};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,164.56) {Ran};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (503.39,217.22) {Dornburg};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,152.56) {Cognato};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (503.39,205.22) {Sauquet};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,140.56) {Dornburg};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (503.39,193.22) {Broughton};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,128.56) {Sauquet};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (503.39,181.22) {Kawahara};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,116.56) {Broughton};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (503.39,169.22) {simulated};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,104.56) {Kawahara};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (503.39,157.22) {Rightmyer};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31, 92.56) {simulated};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31, 80.56) {Rightmyer};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31, 68.56) {Moyle};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (503.39,145.22) {Moyle};
 \end{scope}

### 2020-08-31 benchmarking/benchmarkingVM/ESS_round4b.tex
Results update

@@
-% Created by tikzDevice version 0.12.3.1 on 2020-08-29 18:08:36
+% Created by tikzDevice version 0.12.3.1 on 2020-08-31 17:27:18
 % !TEX encoding = UTF-8 Unicode
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at (289.08,323.19) {\bfseries Comparison of Bactrian+adapt(\textit{real}) and NER+Bactrian+adapt(\textit{real})};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at (301.08,335.19) {\bfseries Comparison of Bactrian+adapt(\textit{real}) and NER+Bactrian+adapt(\textit{real})};
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 21.60,178.67) {Relative ESS/hr};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (  9.60,190.67) {Relative ESS/hr};
 \end{scope}
 \begin{scope}
-\path[clip] ( 60.00, 60.00) rectangle (518.16,297.33);
+\path[clip] ( 48.00, 60.00) rectangle (554.16,321.33);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] ( 60.00,178.67) -- (518.16,178.67);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] ( 48.00,173.19) --
+	(474.88,173.19);
 \definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 65.87,195.96) --
-	( 65.87,154.65);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.10,186.05) --
+	( 54.10,174.62);
+\definecolor{fillColor}{RGB}{255,0,109}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 65.87,171.42) {$p$};
+\path[fill=fillColor] ( 54.10,180.33) circle (  2.25);
 \definecolor{drawColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 71.75,185.67) --
-	( 71.75,167.66);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.20,164.25) --
+	( 60.20,141.62);
+\definecolor{fillColor}{RGB}{253,104,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 71.75,172.78) {$p$};
+\path[fill=fillColor] ( 60.20,152.94) circle (  2.25);
 \definecolor{drawColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 77.62,173.36) --
-	( 77.62,138.30);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.29,167.28) --
+	( 66.29,150.64);
+\definecolor{fillColor}{RGB}{143,161,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 77.62,151.94) {$p$};
+\path[fill=fillColor] ( 66.29,158.96) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.50,175.80) --
-	( 83.50,155.97);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 72.39,166.76) --
+	( 72.39,144.26);
+\definecolor{fillColor}{RGB}{0,195,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 83.50,162.00) {$p$};
+\path[fill=fillColor] ( 72.39,155.51) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.37,193.05) --
-	( 89.37,165.41);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 78.49,162.02) --
+	( 78.49, 98.30);
+\definecolor{fillColor}{RGB}{0,219,171}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 89.37,175.34) {$p$};
+\path[fill=fillColor] ( 78.49,130.16) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.24,200.05) --
-	( 95.24,119.16);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 84.59,202.23) --
+	( 84.59,189.46);
+\definecolor{fillColor}{RGB}{0,216,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 95.24,155.71) {$p$};
+\path[fill=fillColor] ( 84.59,195.84) circle (  2.25);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (101.12,188.48) --
-	(101.12,172.95);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 90.69,203.28) --
+	( 90.69,181.04);
+\definecolor{fillColor}{RGB}{151,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (101.12,176.83) {$p$};
+\path[fill=fillColor] ( 90.69,192.16) circle (  2.25);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (106.99,203.32) --
-	(106.99,174.31);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 96.79,240.71) --
+	( 96.79,222.93);
+\definecolor{fillColor}{RGB}{255,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (106.99,184.93) {$p$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.86,196.91) --
-	(112.86,163.81);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (112.86,176.47) {$p$};
+\path[fill=fillColor] ( 96.79,231.82) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] ( 65.87,173.60) --
-	(118.74,173.60);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] ( 54.10,176.33) --
+	(102.88,176.33);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 92.31,275.05) {-2.6\% faster};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 78.49,284.14) {1.1\% faster};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (124.61,  0.00) --
-	(124.61,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (108.98,  0.00) --
+	(108.98,357.33);
 \definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (130.49,207.17) --
-	(130.49,169.73);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (115.08,192.84) --
+	(115.08,179.45);
+\definecolor{fillColor}{RGB}{255,0,109}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (130.49,183.59) {$L$};
+\path[fill=fillColor] (115.08,186.14) circle (  2.25);
 \definecolor{drawColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (136.36,191.35) --
-	(136.36,173.79);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.18,182.97) --
+	(121.18,171.24);
+\definecolor{fillColor}{RGB}{253,104,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (136.36,177.71) {$L$};
+\path[fill=fillColor] (121.18,177.11) circle (  2.25);
 \definecolor{drawColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (142.23,189.52) --
-	(142.23,168.91);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (127.28,184.85) --
+	(127.28,171.12);
+\definecolor{fillColor}{RGB}{143,161,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (142.23,174.36) {$L$};
+\path[fill=fillColor] (127.28,177.99) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.11,185.84) --
-	(148.11,175.26);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (133.38,190.36) --
+	(133.38,166.22);
+\definecolor{fillColor}{RGB}{0,195,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (148.11,175.69) {$L$};
+\path[fill=fillColor] (133.38,178.29) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.98,205.79) --
-	(153.98,176.65);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (139.47,169.54) --
+	(139.47,147.07);
+\definecolor{fillColor}{RGB}{0,219,171}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (153.98,186.36) {$L$};
+\path[fill=fillColor] (139.47,158.31) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.86,186.57) --
-	(159.86,145.37);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.57,195.26) --
+	(145.57,186.84);
+\definecolor{fillColor}{RGB}{0,216,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (159.86,161.11) {$L$};
+\path[fill=fillColor] (145.57,191.05) circle (  2.25);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (165.73,188.29) --
-	(165.73,174.10);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.67,257.34) --
+	(151.67,213.88);
+\definecolor{fillColor}{RGB}{151,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (165.73,176.34) {$L$};
+\path[fill=fillColor] (151.67,235.61) circle (  2.25);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.60,255.23) --
-	(171.60,189.53);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (157.77,242.16) --
+	(157.77,219.28);
+\definecolor{fillColor}{RGB}{255,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (171.60,217.52) {$L$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.48,205.81) --
-	(177.48,173.63);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (177.48,184.86) {$L$};
+\path[fill=fillColor] (157.77,230.72) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (130.49,186.81) --
-	(183.35,186.81);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (115.08,193.08) --
+	(163.87,193.08);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (156.92,275.05) {4.1\% faster};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (139.47,284.14) {7.4\% faster};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (189.22,  0.00) --
-	(189.22,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (169.97,  0.00) --
+	(169.97,357.33);
 \definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.10,177.59) --
-	(195.10,162.31);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.06,183.40) --
+	(176.06,181.91);
+\definecolor{fillColor}{RGB}{255,0,109}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (195.10,165.09) {$r$};
+\path[fill=fillColor] (176.06,182.66) circle (  2.25);
 \definecolor{drawColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.97,178.57) --
-	(200.97,176.11);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.16,178.32) --
+	(182.16,176.29);
+\definecolor{fillColor}{RGB}{253,104,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (200.97,172.48) {$r$};
+\path[fill=fillColor] (182.16,177.30) circle (  2.25);
 \definecolor{drawColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.85,180.77) --
-	(206.85,178.09);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.26,173.36) --
+	(188.26,171.68);
+\definecolor{fillColor}{RGB}{143,161,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (206.85,174.57) {$r$};
+\path[fill=fillColor] (188.26,172.52) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.72,177.37) --
-	(212.72,173.05);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.36,167.30) --
+	(194.36,164.77);
+\definecolor{fillColor}{RGB}{0,195,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (212.72,170.35) {$r$};
+\path[fill=fillColor] (194.36,166.03) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.59,187.32) --
-	(218.59,176.60);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.46,175.58) --
+	(200.46,173.46);
+\definecolor{fillColor}{RGB}{0,219,171}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (218.59,177.10) {$r$};
+\path[fill=fillColor] (200.46,174.52) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (224.47,177.78) --
-	(224.47,175.24);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.56,188.62) --
+	(206.56,187.01);
+\definecolor{fillColor}{RGB}{0,216,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (224.47,171.65) {$r$};
+\path[fill=fillColor] (206.56,187.82) circle (  2.25);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.34,177.98) --
-	(230.34,175.18);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.65,191.38) --
+	(212.65,187.66);
+\definecolor{fillColor}{RGB}{151,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (230.34,171.72) {$r$};
+\path[fill=fillColor] (212.65,189.52) circle (  2.25);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (236.22,183.49) --
-	(236.22,176.98);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.75,221.94) --
+	(218.75,219.83);
+\definecolor{fillColor}{RGB}{255,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (236.22,175.37) {$r$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (242.09,178.34) --
-	(242.09,175.02);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (242.09,171.82) {$r$};
+\path[fill=fillColor] (218.75,220.89) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (195.10,177.10) --
-	(247.96,177.10);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (176.06,184.37) --
+	(224.85,184.37);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (221.53,275.05) {-0.79\% faster};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (200.46,284.14) {4.1\% faster};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (253.84,  0.00) --
-	(253.84,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (230.95,  0.00) --
+	(230.95,357.33);
 \definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (259.71,184.32) --
-	(259.71,145.55);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.05,181.65) --
+	(237.05,172.54);
+\definecolor{fillColor}{RGB}{255,0,109}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (259.71,160.07) {$l$};
+\path[fill=fillColor] (237.05,177.10) circle (  2.25);
 \definecolor{drawColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (265.58,183.13) --
-	(265.58,165.89);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (243.15,159.01) --
+	(243.15,132.62);
+\definecolor{fillColor}{RGB}{253,104,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (265.58,169.65) {$l$};
+\path[fill=fillColor] (243.15,145.81) circle (  2.25);
 \definecolor{drawColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.46,153.36) --
-	(271.46,127.71);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (249.24,177.17) --
+	(249.24,157.93);
+\definecolor{fillColor}{RGB}{143,161,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (271.46,135.68) {$l$};
+\path[fill=fillColor] (249.24,167.55) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (277.33,171.14) --
-	(277.33,150.33);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (255.34,189.97) --
+	(255.34,147.35);
+\definecolor{fillColor}{RGB}{0,195,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (277.33,155.88) {$l$};
+\path[fill=fillColor] (255.34,168.66) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (283.21,201.48) --
-	(283.21,153.08);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44,177.18) --
+	(261.44,164.80);
+\definecolor{fillColor}{RGB}{0,219,171}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (283.21,172.42) {$l$};
+\path[fill=fillColor] (261.44,170.99) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (289.08,184.86) --
-	(289.08,174.50);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (267.54,208.69) --
+	(267.54,185.32);
+\definecolor{fillColor}{RGB}{0,216,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (289.08,174.82) {$l$};
+\path[fill=fillColor] (267.54,197.01) circle (  2.25);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (294.95,205.34) --
-	(294.95,169.23);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (273.64,218.20) --
+	(273.64,198.25);
+\definecolor{fillColor}{RGB}{151,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (294.95,182.42) {$l$};
+\path[fill=fillColor] (273.64,208.22) circle (  2.25);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (300.83,213.14) --
-	(300.83,174.14);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (279.74,223.20) --
+	(279.74,214.78);
+\definecolor{fillColor}{RGB}{255,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (300.83,188.78) {$l$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (306.70,185.85) --
-	(306.70,170.71);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (306.70,173.42) {$l$};
+\path[fill=fillColor] (279.74,218.99) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (259.71,172.99) --
-	(312.58,172.99);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (237.05,182.72) --
+	(285.83,182.72);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (286.14,275.05) {-2.9\% faster};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (261.44,284.14) {3.5\% faster};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (318.45,  0.00) --
-	(318.45,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (291.93,  0.00) --
+	(291.93,357.33);
 \definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (324.32,225.48) --
-	(324.32,175.86);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.03,178.61) --
+	(298.03,167.68);
+\definecolor{fillColor}{RGB}{255,0,109}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (324.32,197.17) {$\sigma$};
+\path[fill=fillColor] (298.03,173.15) circle (  2.25);
 \definecolor{drawColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (330.20,186.20) --
-	(330.20,169.11);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (304.13,162.68) --
+	(304.13,139.42);
+\definecolor{fillColor}{RGB}{253,104,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (330.20,174.16) {$\sigma$};
+\path[fill=fillColor] (304.13,151.05) circle (  2.25);
 \definecolor{drawColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (336.07,167.03) --
-	(336.07,125.99);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (310.23,176.48) --
+	(310.23,158.35);
+\definecolor{fillColor}{RGB}{143,161,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (336.07,143.01) {$\sigma$};
+\path[fill=fillColor] (310.23,167.41) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (341.94,173.76) --
-	(341.94,158.13);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (316.33,195.13) --
+	(316.33,158.87);
+\definecolor{fillColor}{RGB}{0,195,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (341.94,162.44) {$\sigma$};
+\path[fill=fillColor] (316.33,177.00) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (347.82,191.65) --
-	(347.82,145.40);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (322.42,176.14) --
+	(322.42,165.55);
+\definecolor{fillColor}{RGB}{0,219,171}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (347.82,165.03) {$\sigma$};
+\path[fill=fillColor] (322.42,170.84) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (353.69,186.56) --
-	(353.69,141.86);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (328.52,208.50) --
+	(328.52,185.79);
+\definecolor{fillColor}{RGB}{0,216,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (353.69,160.71) {$\sigma$};
+\path[fill=fillColor] (328.52,197.14) circle (  2.25);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (359.57,189.65) --
-	(359.57,156.76);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (334.62,224.16) --
+	(334.62,192.88);
+\definecolor{fillColor}{RGB}{151,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (359.57,169.71) {$\sigma$};
+\path[fill=fillColor] (334.62,208.52) circle (  2.25);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (365.44,190.85) --
-	(365.44,173.48);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (340.72,226.54) --
+	(340.72,218.12);
+\definecolor{fillColor}{RGB}{255,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (365.44,178.66) {$\sigma$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (371.31,192.67) --
-	(371.31,164.07);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (371.31,174.87) {$\sigma$};
+\path[fill=fillColor] (340.72,222.33) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (324.32,173.03) --
-	(377.19,173.03);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (298.03,184.32) --
+	(346.82,184.32);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (350.76,275.05) {-2.8\% faster};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (322.42,284.14) {4.1\% faster};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (383.06,  0.00) --
-	(383.06,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (352.92,  0.00) --
+	(352.92,357.33);
 \definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (388.94,171.89) --
-	(388.94,164.81);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (359.01,182.24) --
+	(359.01,167.41);
+\definecolor{fillColor}{RGB}{255,0,109}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (388.94,164.85) {$\kappa$};
+\path[fill=fillColor] (359.01,174.82) circle (  2.25);
 \definecolor{drawColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (394.81,181.31) --
-	(394.81,172.79);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (365.11,157.24) --
+	(365.11,131.60);
+\definecolor{fillColor}{RGB}{253,104,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (394.81,173.55) {$\kappa$};
+\path[fill=fillColor] (365.11,144.42) circle (  2.25);
 \definecolor{drawColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (400.68,183.51) --
-	(400.68,178.73);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (371.21,169.99) --
+	(371.21,153.88);
+\definecolor{fillColor}{RGB}{143,161,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (400.68,177.62) {$\kappa$};
+\path[fill=fillColor] (371.21,161.94) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (406.56,182.01) --
-	(406.56,176.20);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (377.31,168.23) --
+	(377.31,146.43);
+\definecolor{fillColor}{RGB}{0,195,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (406.56,175.60) {$\kappa$};
+\path[fill=fillColor] (377.31,157.33) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.43,182.69) --
-	(412.43,177.75);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (383.41,174.11) --
+	(383.41,150.84);
+\definecolor{fillColor}{RGB}{0,219,171}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (412.43,176.72) {$\kappa$};
+\path[fill=fillColor] (383.41,162.48) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.30,182.42) --
-	(418.30,177.52);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.51,193.90) --
+	(389.51,166.47);
+\definecolor{fillColor}{RGB}{0,216,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (418.30,176.47) {$\kappa$};
+\path[fill=fillColor] (389.51,180.18) circle (  2.25);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (424.18,181.51) --
-	(424.18,173.97);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (395.60,203.16) --
+	(395.60,181.99);
+\definecolor{fillColor}{RGB}{151,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (424.18,174.24) {$\kappa$};
+\path[fill=fillColor] (395.60,192.57) circle (  2.25);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (430.05,182.22) --
-	(430.05,172.32);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (401.70,239.78) --
+	(401.70,221.53);
+\definecolor{fillColor}{RGB}{255,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (430.05,173.77) {$\kappa$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (435.93,190.73) --
-	(435.93,177.77);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (435.93,180.75) {$\kappa$};
+\path[fill=fillColor] (401.70,230.66) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (388.94,178.34) --
-	(441.80,178.34);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (359.01,176.71) --
+	(407.80,176.71);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (415.37,275.05) {-0.16\% faster};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (383.41,284.14) {1.3\% faster};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (447.67,  0.00) --
-	(447.67,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (413.90,  0.00) --
+	(413.90,357.33);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.00,189.40) --
+	(420.00,183.99);
+\definecolor{fillColor}{RGB}{255,0,109}
+
+\path[fill=fillColor] (420.00,186.70) circle (  2.25);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.10,179.73) --
+	(426.10,176.02);
+\definecolor{fillColor}{RGB}{253,104,0}
+
+\path[fill=fillColor] (426.10,177.87) circle (  2.25);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (432.19,178.20) --
+	(432.19,174.37);
+\definecolor{fillColor}{RGB}{143,161,0}
+
+\path[fill=fillColor] (432.19,176.28) circle (  2.25);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.29,173.45) --
+	(438.29,169.46);
+\definecolor{fillColor}{RGB}{0,195,0}
+
+\path[fill=fillColor] (438.29,171.45) circle (  2.25);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (444.39,177.55) --
+	(444.39,172.82);
+\definecolor{fillColor}{RGB}{0,219,171}
+
+\path[fill=fillColor] (444.39,175.18) circle (  2.25);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (450.49,198.72) --
+	(450.49,192.07);
+\definecolor{fillColor}{RGB}{0,216,255}
+
+\path[fill=fillColor] (450.49,195.40) circle (  2.25);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (456.59,191.62) --
+	(456.59,186.36);
+\definecolor{fillColor}{RGB}{151,0,255}
+
+\path[fill=fillColor] (456.59,188.99) circle (  2.25);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.69,229.29) --
+	(462.69,223.00);
+\definecolor{fillColor}{RGB}{255,0,255}
+
+\path[fill=fillColor] (462.69,226.15) circle (  2.25);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (420.00,187.76) --
+	(468.78,187.76);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (444.39,284.14) {5.4\% faster};
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (474.88,  0.00) --
+	(474.88,357.33);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- (518.16, 60.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 60.00) -- (554.16, 60.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.31, 60.00) -- ( 92.31, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 78.49, 60.00) -- ( 78.49, 54.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (156.92, 60.00) -- (156.92, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (139.47, 60.00) -- (139.47, 54.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.53, 60.00) -- (221.53, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.46, 60.00) -- (200.46, 54.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (286.14, 60.00) -- (286.14, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44, 60.00) -- (261.44, 54.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (350.76, 60.00) -- (350.76, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (322.42, 60.00) -- (322.42, 54.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (415.37, 60.00) -- (415.37, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (383.41, 60.00) -- (383.41, 54.00);
 
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.70] at ( 94.72, 48.00) {Prior};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (444.39, 60.00) -- (444.39, 54.00);
 
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.70] at (159.33, 48.00) {Likelihood};
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at ( 80.56, 48.00) {Prior};
 
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.70] at (223.94, 48.00) {Mean leaf rate};
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (141.54, 48.00) {Likelihood};
 
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.70] at (288.55, 48.00) {Tree length};
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (202.52, 48.00) {Leaf rate};
 
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.70] at (353.17, 48.00) {Clock SD $\sigma$};
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (263.51, 48.00) {Mean branch rate};
 
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.70] at (417.78, 48.00) {HKY model $\kappa$};
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (324.49, 48.00) {Tree length};
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 79.78) -- ( 60.00,277.55);
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (385.47, 48.00) {Clock SD $\sigma$};
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 79.78) -- ( 54.00, 79.78);
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (446.46, 48.00) {HKY model $\kappa$};
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,129.22) -- ( 54.00,129.22);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 60.00) -- ( 48.00,286.39);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,178.67) -- ( 54.00,178.67);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 60.00) -- ( 42.00, 60.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,228.11) -- ( 54.00,228.11);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 92.88) -- ( 42.00, 92.88);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,277.55) -- ( 54.00,277.55);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,135.92) -- ( 42.00,135.92);
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00, 76.33) {0.50};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,173.19) -- ( 42.00,173.19);
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,125.78) {0.75};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,210.47) -- ( 42.00,210.47);
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,175.22) {1.00};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,253.51) -- ( 42.00,253.51);
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,224.67) {1.25};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,286.39) -- ( 42.00,286.39);
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,274.11) {1.50};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 36.00, 56.56) {$\frac{2}{3}\times$};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 36.00, 89.44) {$\frac{3}{4}\times$};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 36.00,132.47) {$\frac{7}{8}\times$};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 36.00,169.75) {$1\times$};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 36.00,207.03) {$\frac{8}{7}\times$};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 36.00,250.06) {$\frac{4}{3}\times$};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 36.00,282.94) {$\frac{3}{2}\times$};
 \end{scope}
 \begin{scope}
-\path[clip] ( 60.00, 60.00) rectangle (518.16,297.33);
+\path[clip] ( 48.00, 60.00) rectangle (554.16,321.33);
 \definecolor{drawColor}{RGB}{0,0,0}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (451.19,171.00) rectangle (458.39,165.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.19,235.67) rectangle (494.39,229.67);
 \definecolor{fillColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (451.19,159.00) rectangle (458.39,153.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.19,223.67) rectangle (494.39,217.67);
 \definecolor{fillColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (451.19,147.00) rectangle (458.39,141.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.19,211.67) rectangle (494.39,205.67);
 \definecolor{fillColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (451.19,135.00) rectangle (458.39,129.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.19,199.67) rectangle (494.39,193.67);
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (451.19,123.00) rectangle (458.39,117.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.19,187.67) rectangle (494.39,181.67);
 \definecolor{fillColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (451.19,111.00) rectangle (458.39,105.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.19,175.67) rectangle (494.39,169.67);
 \definecolor{fillColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (451.19, 99.00) rectangle (458.39, 93.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.19,163.67) rectangle (494.39,157.67);
 \definecolor{fillColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (451.19, 87.00) rectangle (458.39, 81.00);
-\definecolor{fillColor}{RGB}{68,68,68}
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.19,151.67) rectangle (494.39,145.67);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (451.19, 75.00) rectangle (458.39, 69.00);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (503.39,229.22) {Cognato};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (467.39,164.56) {Ran};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (503.39,217.22) {Dornburg};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (467.39,152.56) {Cognato};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (503.39,205.22) {Sauquet};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (467.39,140.56) {Dornburg};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (503.39,193.22) {Broughton};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (467.39,128.56) {Sauquet};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (503.39,181.22) {Kawahara};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (467.39,116.56) {Broughton};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (503.39,169.22) {simulated};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (467.39,104.56) {Kawahara};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (503.39,157.22) {Rightmyer};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (467.39, 92.56) {simulated};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (467.39, 80.56) {Rightmyer};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (467.39, 68.56) {Moyle};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (503.39,145.22) {Moyle};
 \end{scope}

### 2020-08-31 benchmarking/benchmarkingVM/ESS_round5.tex
Results update

@@
-% Created by tikzDevice version 0.12.3.1 on 2020-08-29 17:56:05
+% Created by tikzDevice version 0.12.3.1 on 2020-08-31 17:27:26
 % !TEX encoding = UTF-8 Unicode
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at (289.08,323.19) {\bfseries Comparison of AVMVN+NER+Bactrian+adapt(\textit{real}) and NER+Bactrian+adapt(\textit{real})};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at (301.08,335.19) {\bfseries Comparison of AVMVN+NER+Bactrian+adapt(\textit{real}) and NER+Bactrian+adapt(\textit{real})};
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 21.60,178.67) {Relative ESS/hr};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (  9.60,190.67) {Relative ESS/hr};
 \end{scope}
 \begin{scope}
-\path[clip] ( 60.00, 60.00) rectangle (518.16,297.33);
+\path[clip] ( 48.00, 60.00) rectangle (554.16,321.33);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] ( 60.00,178.67) -- (518.16,178.67);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] ( 48.00,173.19) --
+	(474.88,173.19);
 \definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 65.87,182.29) --
-	( 65.87,155.40);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.10,170.57) --
+	( 54.10,160.89);
+\definecolor{fillColor}{RGB}{255,0,109}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 65.87,164.96) {$p$};
+\path[fill=fillColor] ( 54.10,165.73) circle (  2.25);
 \definecolor{drawColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 71.75,182.37) --
-	( 71.75,172.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.20,193.03) --
+	( 60.20,169.27);
+\definecolor{fillColor}{RGB}{253,104,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 71.75,173.72) {$p$};
+\path[fill=fillColor] ( 60.20,181.15) circle (  2.25);
 \definecolor{drawColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 77.62,206.63) --
-	( 77.62,183.55);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.29,191.40) --
+	( 66.29,174.61);
+\definecolor{fillColor}{RGB}{143,161,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 77.62,191.20) {$p$};
+\path[fill=fillColor] ( 66.29,183.01) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.50,192.35) --
-	( 83.50,184.14);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 72.39,196.48) --
+	( 72.39,170.97);
+\definecolor{fillColor}{RGB}{0,195,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 83.50,184.36) {$p$};
+\path[fill=fillColor] ( 72.39,183.73) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.37,198.03) --
-	( 89.37,169.64);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 78.49,141.00) --
+	( 78.49, 76.27);
+\definecolor{fillColor}{RGB}{0,219,171}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 89.37,179.94) {$p$};
+\path[fill=fillColor] ( 78.49,108.63) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.24,194.87) --
-	( 95.24,123.63);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 84.59,183.38) --
+	( 84.59,168.50);
+\definecolor{fillColor}{RGB}{0,216,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 95.24,155.36) {$p$};
+\path[fill=fillColor] ( 84.59,175.94) circle (  2.25);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (101.12,195.10) --
-	(101.12,177.27);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 90.69,170.18) --
+	( 90.69,143.82);
+\definecolor{fillColor}{RGB}{151,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (101.12,182.29) {$p$};
+\path[fill=fillColor] ( 90.69,157.00) circle (  2.25);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (106.99,193.21) --
-	(106.99,172.45);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 96.79,196.84) --
+	( 96.79,181.84);
+\definecolor{fillColor}{RGB}{255,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (106.99,178.95) {$p$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.86,199.27) --
-	(112.86,173.64);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (112.86,182.57) {$p$};
+\path[fill=fillColor] ( 96.79,189.34) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] ( 65.87,180.93) --
-	(118.74,180.93);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] ( 54.10,169.09) --
+	(102.88,169.09);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 92.31,275.05) {1.1\% faster};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 78.49,284.14) {-1.5\% faster};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (124.61,  0.00) --
-	(124.61,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (108.98,  0.00) --
+	(108.98,357.33);
 \definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (130.49,204.32) --
-	(130.49,182.55);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (115.08,194.11) --
+	(115.08,179.13);
+\definecolor{fillColor}{RGB}{255,0,109}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (130.49,188.58) {$L$};
+\path[fill=fillColor] (115.08,186.62) circle (  2.25);
 \definecolor{drawColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (136.36,199.93) --
-	(136.36,178.39);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.18,185.55) --
+	(121.18,175.29);
+\definecolor{fillColor}{RGB}{253,104,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (136.36,184.30) {$L$};
+\path[fill=fillColor] (121.18,180.42) circle (  2.25);
 \definecolor{drawColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (142.23,195.23) --
-	(142.23,183.90);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (127.28,214.73) --
+	(127.28,201.99);
+\definecolor{fillColor}{RGB}{143,161,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (142.23,184.70) {$L$};
+\path[fill=fillColor] (127.28,208.36) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.11,217.30) --
-	(148.11,203.38);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (133.38,249.42) --
+	(133.38,231.42);
+\definecolor{fillColor}{RGB}{0,195,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (148.11,205.48) {$L$};
+\path[fill=fillColor] (133.38,240.42) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.98,248.47) --
-	(153.98,227.05);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (139.47,159.92) --
+	(139.47,140.75);
+\definecolor{fillColor}{RGB}{0,219,171}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (153.98,232.90) {$L$};
+\path[fill=fillColor] (139.47,150.33) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.86,183.36) --
-	(159.86,156.04);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.57,214.01) --
+	(145.57,205.08);
+\definecolor{fillColor}{RGB}{0,216,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (159.86,164.84) {$L$};
+\path[fill=fillColor] (145.57,209.54) circle (  2.25);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (165.73,231.86) --
-	(165.73,219.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.67,200.10) --
+	(151.67,107.60);
+\definecolor{fillColor}{RGB}{151,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (165.73,220.70) {$L$};
+\path[fill=fillColor] (151.67,153.85) circle (  2.25);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.60,235.33) --
-	(171.60,157.10);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (157.77,178.44) --
+	(157.77,154.84);
+\definecolor{fillColor}{RGB}{255,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (171.60,191.36) {$L$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.48,199.47) --
-	(177.48,168.81);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (177.48,179.28) {$L$};
+\path[fill=fillColor] (157.77,166.64) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (130.49,199.54) --
-	(183.35,199.54);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (115.08,188.55) --
+	(163.87,188.55);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (156.92,275.05) {11\% faster};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (139.47,284.14) {5.7\% faster};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (189.22,  0.00) --
-	(189.22,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (169.97,  0.00) --
+	(169.97,357.33);
 \definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (195.10,173.48) --
-	(195.10,158.53);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.06,172.66) --
+	(176.06,170.84);
+\definecolor{fillColor}{RGB}{255,0,109}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (195.10,161.15) {$r$};
+\path[fill=fillColor] (176.06,171.75) circle (  2.25);
 \definecolor{drawColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.97,184.98) --
-	(200.97,182.46);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.16,169.79) --
+	(182.16,167.75);
+\definecolor{fillColor}{RGB}{253,104,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (200.97,178.86) {$r$};
+\path[fill=fillColor] (182.16,168.77) circle (  2.25);
 \definecolor{drawColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.85,186.09) --
-	(206.85,182.08);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.26,189.75) --
+	(188.26,187.44);
+\definecolor{fillColor}{RGB}{143,161,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (206.85,179.23) {$r$};
+\path[fill=fillColor] (188.26,188.59) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.72,194.39) --
-	(212.72,191.56);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.36,203.19) --
+	(194.36,199.69);
+\definecolor{fillColor}{RGB}{0,195,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (212.72,188.11) {$r$};
+\path[fill=fillColor] (194.36,201.44) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.59,208.43) --
-	(218.59,201.15);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.46,171.28) --
+	(200.46,169.79);
+\definecolor{fillColor}{RGB}{0,219,171}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (218.59,199.93) {$r$};
+\path[fill=fillColor] (200.46,170.53) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (224.47,185.90) --
-	(224.47,183.69);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.56,184.57) --
+	(206.56,182.27);
+\definecolor{fillColor}{RGB}{0,216,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (224.47,179.94) {$r$};
+\path[fill=fillColor] (206.56,183.42) circle (  2.25);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.34,200.46) --
-	(230.34,196.65);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.65,163.32) --
+	(212.65,160.43);
+\definecolor{fillColor}{RGB}{151,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (230.34,193.69) {$r$};
+\path[fill=fillColor] (212.65,161.87) circle (  2.25);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (236.22,188.37) --
-	(236.22,184.80);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.75,155.78) --
+	(218.75,154.17);
+\definecolor{fillColor}{RGB}{255,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (236.22,181.72) {$r$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (242.09,174.48) --
-	(242.09,171.48);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (242.09,168.12) {$r$};
+\path[fill=fillColor] (218.75,154.97) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (195.10,186.05) --
-	(247.96,186.05);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (176.06,175.53) --
+	(224.85,175.53);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (221.53,275.05) {3.7\% faster};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (200.46,284.14) {0.84\% faster};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (253.84,  0.00) --
-	(253.84,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (230.95,  0.00) --
+	(230.95,357.33);
 \definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (259.71,170.83) --
-	(259.71,145.47);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.05,218.83) --
+	(237.05,206.46);
+\definecolor{fillColor}{RGB}{255,0,109}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (259.71,153.29) {$l$};
+\path[fill=fillColor] (237.05,212.65) circle (  2.25);
 \definecolor{drawColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (265.58,217.60) --
-	(265.58,197.77);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (243.15,242.97) --
+	(243.15,220.02);
+\definecolor{fillColor}{RGB}{253,104,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (265.58,202.82) {$l$};
+\path[fill=fillColor] (243.15,231.49) circle (  2.25);
 \definecolor{drawColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.46,235.98) --
-	(271.46,197.45);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (249.24,208.35) --
+	(249.24,192.32);
+\definecolor{fillColor}{RGB}{143,161,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (271.46,211.85) {$l$};
+\path[fill=fillColor] (249.24,200.33) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (277.33,200.90) --
-	(277.33,186.58);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (255.34,176.56) --
+	(255.34,142.47);
+\definecolor{fillColor}{RGB}{0,195,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (277.33,188.88) {$l$};
+\path[fill=fillColor] (255.34,159.52) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (283.21,194.62) --
-	(283.21,161.91);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44,187.62) --
+	(261.44,174.61);
+\definecolor{fillColor}{RGB}{0,219,171}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (283.21,173.40) {$l$};
+\path[fill=fillColor] (261.44,181.12) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (289.08,195.59) --
-	(289.08,178.65);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (267.54,206.77) --
+	(267.54,181.77);
+\definecolor{fillColor}{RGB}{0,216,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (289.08,182.26) {$l$};
+\path[fill=fillColor] (267.54,194.27) circle (  2.25);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (294.95,222.46) --
-	(294.95,190.90);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (273.64,229.57) --
+	(273.64,209.79);
+\definecolor{fillColor}{RGB}{151,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (294.95,201.82) {$l$};
+\path[fill=fillColor] (273.64,219.68) circle (  2.25);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (300.83,227.18) --
-	(300.83,192.62);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (279.74,216.31) --
+	(279.74,206.19);
+\definecolor{fillColor}{RGB}{255,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (300.83,205.04) {$l$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (306.70,227.56) --
-	(306.70,211.98);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (306.70,214.91) {$l$};
+\path[fill=fillColor] (279.74,211.25) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (259.71,197.56) --
-	(312.58,197.56);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (237.05,202.10) --
+	(285.83,202.10);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (286.14,275.05) {9.6\% faster};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (261.44,284.14) {11\% faster};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (318.45,  0.00) --
-	(318.45,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (291.93,  0.00) --
+	(291.93,357.33);
 \definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (324.32,177.22) --
-	(324.32,147.94);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.03,209.96) --
+	(298.03,198.22);
+\definecolor{fillColor}{RGB}{255,0,109}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (324.32,159.08) {$\sigma$};
+\path[fill=fillColor] (298.03,204.09) circle (  2.25);
 \definecolor{drawColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (330.20,189.14) --
-	(330.20,175.54);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (304.13,238.47) --
+	(304.13,217.31);
+\definecolor{fillColor}{RGB}{253,104,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (330.20,178.84) {$\sigma$};
+\path[fill=fillColor] (304.13,227.89) circle (  2.25);
 \definecolor{drawColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (336.07,201.86) --
-	(336.07,178.01);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (310.23,204.06) --
+	(310.23,189.08);
+\definecolor{fillColor}{RGB}{143,161,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (336.07,186.44) {$\sigma$};
+\path[fill=fillColor] (310.23,196.57) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (341.94,197.85) --
-	(341.94,176.63);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (316.33,171.91) --
+	(316.33,144.86);
+\definecolor{fillColor}{RGB}{0,195,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (341.94,183.74) {$\sigma$};
+\path[fill=fillColor] (316.33,158.38) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (347.82,185.47) --
-	(347.82,162.39);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (322.42,183.17) --
+	(322.42,172.59);
+\definecolor{fillColor}{RGB}{0,219,171}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (347.82,170.43) {$\sigma$};
+\path[fill=fillColor] (322.42,177.88) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (353.69,171.36) --
-	(353.69,145.10);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (328.52,206.07) --
+	(328.52,181.21);
+\definecolor{fillColor}{RGB}{0,216,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (353.69,154.73) {$\sigma$};
+\path[fill=fillColor] (328.52,193.64) circle (  2.25);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (359.57,218.64) --
-	(359.57,189.11);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (334.62,210.76) --
+	(334.62,182.47);
+\definecolor{fillColor}{RGB}{151,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (359.57,200.38) {$\sigma$};
+\path[fill=fillColor] (334.62,196.61) circle (  2.25);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (365.44,197.28) --
-	(365.44,169.92);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (340.72,208.61) --
+	(340.72,197.60);
+\definecolor{fillColor}{RGB}{255,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (365.44,180.10) {$\sigma$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (371.31,208.91) --
-	(371.31,174.10);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (371.31,188.01) {$\sigma$};
+\path[fill=fillColor] (340.72,203.11) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (324.32,181.47) --
-	(377.19,181.47);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (298.03,195.41) --
+	(346.82,195.41);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (350.76,275.05) {1.4\% faster};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (322.42,284.14) {8.3\% faster};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (383.06,  0.00) --
-	(383.06,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (352.92,  0.00) --
+	(352.92,357.33);
 \definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (388.94,173.56) --
-	(388.94,166.63);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (359.01,174.36) --
+	(359.01,162.95);
+\definecolor{fillColor}{RGB}{255,0,109}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (388.94,166.59) {$\kappa$};
+\path[fill=fillColor] (359.01,168.66) circle (  2.25);
 \definecolor{drawColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (394.81,181.62) --
-	(394.81,172.94);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (365.11,189.08) --
+	(365.11,165.88);
+\definecolor{fillColor}{RGB}{253,104,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (394.81,173.78) {$\kappa$};
+\path[fill=fillColor] (365.11,177.48) circle (  2.25);
 \definecolor{drawColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (400.68,182.02) --
-	(400.68,177.17);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (371.21,190.22) --
+	(371.21,174.54);
+\definecolor{fillColor}{RGB}{143,161,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (400.68,176.10) {$\kappa$};
+\path[fill=fillColor] (371.21,182.38) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (406.56,181.64) --
-	(406.56,176.43);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (377.31,180.24) --
+	(377.31,143.99);
+\definecolor{fillColor}{RGB}{0,195,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (406.56,175.54) {$\kappa$};
+\path[fill=fillColor] (377.31,162.11) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (412.43,181.68) --
-	(412.43,177.34);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (383.41,146.90) --
+	(383.41,126.33);
+\definecolor{fillColor}{RGB}{0,219,171}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (412.43,176.01) {$\kappa$};
+\path[fill=fillColor] (383.41,136.61) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.30,183.51) --
-	(418.30,175.87);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.51,194.96) --
+	(389.51,169.70);
+\definecolor{fillColor}{RGB}{0,216,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (418.30,176.19) {$\kappa$};
+\path[fill=fillColor] (389.51,182.33) circle (  2.25);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (424.18,188.86) --
-	(424.18,177.28);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (395.60,175.08) --
+	(395.60,145.39);
+\definecolor{fillColor}{RGB}{151,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (424.18,179.57) {$\kappa$};
+\path[fill=fillColor] (395.60,160.24) circle (  2.25);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (430.05,185.00) --
-	(430.05,172.59);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (401.70,198.72) --
+	(401.70,181.55);
+\definecolor{fillColor}{RGB}{255,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (430.05,175.29) {$\kappa$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (435.93,187.04) --
-	(435.93,177.74);
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (435.93,178.89) {$\kappa$};
+\path[fill=fillColor] (401.70,190.14) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (388.94,178.83) --
-	(441.80,178.83);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (359.01,170.44) --
+	(407.80,170.44);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (415.37,275.05) {0.082\% faster};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (383.41,284.14) {-0.98\% faster};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (447.67,  0.00) --
-	(447.67,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (413.90,  0.00) --
+	(413.90,357.33);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.00,167.61) --
+	(420.00,161.93);
+\definecolor{fillColor}{RGB}{255,0,109}
+
+\path[fill=fillColor] (420.00,164.77) circle (  2.25);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.10,164.25) --
+	(426.10,160.41);
+\definecolor{fillColor}{RGB}{253,104,0}
+
+\path[fill=fillColor] (426.10,162.33) circle (  2.25);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (432.19,168.36) --
+	(432.19,165.25);
+\definecolor{fillColor}{RGB}{143,161,0}
+
+\path[fill=fillColor] (432.19,166.80) circle (  2.25);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.29,170.98) --
+	(438.29,165.44);
+\definecolor{fillColor}{RGB}{0,195,0}
+
+\path[fill=fillColor] (438.29,168.21) circle (  2.25);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (444.39,161.65) --
+	(444.39,156.22);
+\definecolor{fillColor}{RGB}{0,219,171}
+
+\path[fill=fillColor] (444.39,158.94) circle (  2.25);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (450.49,162.17) --
+	(450.49,154.52);
+\definecolor{fillColor}{RGB}{0,216,255}
+
+\path[fill=fillColor] (450.49,158.35) circle (  2.25);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (456.59,155.49) --
+	(456.59,149.68);
+\definecolor{fillColor}{RGB}{151,0,255}
+
+\path[fill=fillColor] (456.59,152.58) circle (  2.25);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.69,166.82) --
+	(462.69,162.55);
+\definecolor{fillColor}{RGB}{255,0,255}
+
+\path[fill=fillColor] (462.69,164.69) circle (  2.25);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (420.00,162.13) --
+	(468.78,162.13);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (444.39,284.14) {-3.9\% faster};
+\definecolor{drawColor}{RGB}{105,105,105}
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (474.88,  0.00) --
+	(474.88,357.33);
 \end{scope}

### 2020-08-31 benchmarking/benchmarkingVM/ESS_round5b.tex
Results update

@@
-% Created by tikzDevice version 0.12.3.1 on 2020-08-29 17:56:12
+% Created by tikzDevice version 0.12.3.1 on 2020-08-31 17:27:34
 % !TEX encoding = UTF-8 Unicode
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at (144.54, 14.40) {ESS/$10^6$ states [\textit{cat}]};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at ( 21.60,144.54) {ESS/$10^6$ states [AVMVN+NER+Bactrian+adapt(\textit{real})]};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at (144.54, 14.40) {ESS/hr [\textit{cat}]};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at ( 21.60,144.54) {ESS/hr [AVMVN+NER+Bactrian+adapt(\textit{real})]};
 \end{scope}
@@
 
-\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (  0.00,101.80) --
-	(187.28,289.08);
-
-\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (285.44,289.08) --
-	(285.44,183.64) --
-	(101.80,  0.00);
+\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (  0.00, 71.00) --
+	(218.08,289.08);
+
+\path[draw=drawColor,draw opacity=0.47,line width= 0.4pt,line join=round,line cap=round] (268.39,289.08) --
+	(268.39,197.39) --
+	( 71.00,  0.00);
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (  0.00, 67.86) --
-	(221.22,289.08);
-
-\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (285.44,289.08) --
-	(285.44,217.58) --
-	( 67.86,  0.00);
+\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (  0.00, 47.34) --
+	(241.74,289.08);
+
+\path[draw=drawColor,draw opacity=0.67,line width= 0.6pt,line join=round,line cap=round] (268.39,289.08) --
+	(268.39,221.06) --
+	( 47.34,  0.00);
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (  0.00, 33.93) --
-	(255.15,289.08);
-
-\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (285.44,289.08) --
-	(285.44,251.51) --
-	( 33.93,  0.00);
+\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (  0.00, 23.67) --
+	(265.41,289.08);
+
+\path[draw=drawColor,draw opacity=0.87,line width= 0.8pt,line join=round,line cap=round] (268.39,289.08) --
+	(268.39,244.72) --
+	( 23.67,  0.00);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (170.87, 64.13) {$\frac{1}{64} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,175.57) {$64\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (136.94, 64.13) {$\frac{1}{16} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,141.64) {$16\times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (101.01, 64.13) {$\frac{1}{4} \times$};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 62.56,107.71) {$4\times$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (140.08, 64.13) {$\frac{1}{64} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,144.78) {$64\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (116.41, 64.13) {$\frac{1}{16} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 63.56,121.11) {$16\times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 90.75, 64.13) {$\frac{1}{4} \times$};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 62.56, 97.44) {$4\times$};
 \definecolor{drawColor}{RGB}{105,105,105}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 71.42,176.23) --
-	( 84.65,176.23);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 78.92,174.41) --
-	( 78.92,177.92);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 78.92,172.34) {$p$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.81,162.66) --
-	(177.01,162.66);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.00,161.37) --
-	(175.00,163.88);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (175.00,157.80) {$L$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 83.03,178.79) --
-	( 88.54,178.79);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 85.94,177.78) --
-	( 85.94,179.76);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 85.94,173.93) {$r$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 68.08,146.84) --
-	( 81.61,146.84);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 75.77,145.03) --
-	( 75.77,148.53);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 75.77,141.98) {$l$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 76.64,170.79) --
-	( 89.72,170.79);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 84.04,168.73) --
-	( 84.04,172.69);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 84.04,167.29) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.14,181.75) --
-	(185.74,181.75);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.44,181.29) --
-	(185.44,182.19);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (185.44,178.25) {$\kappa$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (167.17,183.23) --
-	(169.48,183.23);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.35,182.63) --
-	(168.35,183.81);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (168.35,179.34) {$p$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.41,185.46) --
-	(186.36,185.46);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.41,184.16) --
-	(185.41,186.69);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (185.41,180.60) {$L$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.62,191.41) --
-	(176.94,191.41);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.78,191.26) --
-	(176.78,191.56);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (176.78,186.55) {$r$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (163.54,175.46) --
-	(166.19,175.46);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.90,174.36) --
-	(164.90,176.51);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (164.90,170.60) {$l$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (168.00,185.09) --
-	(170.90,185.09);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.49,184.25) --
-	(169.49,185.90);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (169.49,181.59) {$\sigma$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.97,187.48) --
-	(186.70,187.48);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.34,186.93) --
-	(186.34,188.01);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (186.34,183.98) {$\kappa$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.34,156.88) --
-	(154.22,156.88);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.82,155.53) --
-	(152.82,158.17);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (152.82,152.99) {$p$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.12,188.93) --
-	(188.93,188.93);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.04,188.26) --
-	(188.04,189.59);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (188.04,184.07) {$L$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.09,192.48) --
-	(182.78,192.48);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.44,192.24) --
-	(182.44,192.72);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (182.44,187.62) {$r$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (144.78,143.01) --
-	(147.93,143.01);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (146.41,140.92) --
-	(146.41,144.93);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (146.41,138.15) {$l$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (142.15,153.61) --
-	(147.36,153.61);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (144.89,152.17) --
-	(144.89,154.96);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (144.89,150.11) {$\sigma$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.56,189.79) --
-	(189.29,189.79);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.93,189.49) --
-	(188.93,190.09);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (188.93,186.29) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (131.25,166.10) --
-	(135.47,166.10);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (133.45,165.61) --
-	(133.45,166.58);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (133.45,162.21) {$p$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.59,188.13) --
-	(187.96,188.13);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.80,187.38) --
-	(186.80,188.87);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (186.80,183.27) {$L$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.33,188.08) --
-	(175.07,188.08);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.70,187.92) --
-	(174.70,188.24);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (174.70,183.22) {$r$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (128.97,157.79) --
-	(133.26,157.79);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (131.21,156.95) --
-	(131.21,158.60);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (131.21,152.93) {$l$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (134.65,160.83) --
-	(137.30,160.83);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (136.01,159.54) --
-	(136.01,162.06);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (136.01,157.33) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.92,189.83) --
-	(189.56,189.83);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.25,189.51) --
-	(189.25,190.15);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (189.25,186.34) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (101.90,175.20) --
-	(107.68,175.20);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (104.96,173.42) --
-	(104.96,176.85);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (104.96,171.31) {$p$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.30,177.06) --
-	(182.80,177.06);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.58,176.01) --
-	(181.58,178.06);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (181.58,172.20) {$L$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (147.34,182.51) --
-	(148.15,182.51);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (147.75,182.11) --
-	(147.75,182.91);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (147.75,177.65) {$r$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (101.52,138.26) --
-	(107.21,138.26);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (104.53,136.14) --
-	(104.53,140.21);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (104.53,133.40) {$l$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (103.73,159.54) --
-	(112.28,159.54);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (108.38,158.03) --
-	(108.38,160.96);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (108.38,156.04) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.98,187.47) --
-	(187.75,187.47);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.37,187.20) --
-	(187.37,187.74);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (187.37,183.97) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.65,162.64) --
-	(178.24,162.64);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (176.51,157.19) --
-	(176.51,167.10);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (176.51,158.76) {$p$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.53,184.48) --
-	(186.79,184.48);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.68,182.64) --
-	(185.68,186.19);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (185.68,179.62) {$L$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (197.02,201.51) --
-	(197.40,201.51);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (197.21,201.37) --
-	(197.21,201.64);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (197.21,196.65) {$r$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.18,184.01) --
-	(175.90,184.01);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.11,182.98) --
-	(174.11,185.00);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (174.11,179.15) {$l$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (165.98,167.13) --
-	(169.18,167.13);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (167.63,165.25) --
-	(167.63,168.88);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (167.63,163.63) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.25,189.13) --
-	(189.20,189.13);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.73,188.65) --
-	(188.73,189.59);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (188.73,185.63) {$\kappa$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (125.86,180.56) --
-	(131.05,180.56);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (128.59,179.48) --
-	(128.59,181.61);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (128.59,176.68) {$p$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.04,185.82) --
-	(191.81,185.82);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.47,185.18) --
-	(190.47,186.44);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (190.47,180.96) {$L$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (163.39,187.14) --
-	(165.31,187.14);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.37,186.92) --
-	(164.37,187.35);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (164.37,182.28) {$r$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (126.45,144.38) --
-	(131.50,144.38);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (129.10,142.61) --
-	(129.10,146.03);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (129.10,139.52) {$l$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (141.51,161.01) --
-	(144.15,161.01);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (142.86,159.33) --
-	(142.86,162.58);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (142.86,157.51) {$\sigma$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.54,190.27) --
-	(192.68,190.27);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (192.12,189.56) --
-	(192.12,190.97);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (192.12,186.78) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (148.85,164.84) --
-	(152.02,164.84);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.49,163.54) --
-	(150.49,166.06);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (150.49,160.95) {$p$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (166.77,167.56) --
-	(172.22,167.56);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.65,162.65) --
-	(169.65,171.64);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (169.65,162.70) {$L$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (170.20,176.63) --
-	(170.60,176.63);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (170.40,176.41) --
-	(170.40,176.84);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (170.40,171.77) {$r$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (147.22,157.74) --
-	(150.25,157.74);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (148.78,155.82) --
-	(148.78,159.52);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (148.78,152.88) {$l$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (154.41,164.24) --
-	(157.15,164.24);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (155.82,162.53) --
-	(155.82,165.84);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (155.82,160.75) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.29,187.63) --
-	(188.19,187.63);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.74,186.85) --
-	(187.74,188.39);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (187.74,184.13) {$\kappa$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.74,163.30) --
-	(163.42,163.30);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (162.60,161.73) --
-	(162.60,164.78);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (162.60,159.41) {$p$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.44,156.47) --
-	(154.65,156.47);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.63,154.55) --
-	(152.63,158.25);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (152.63,151.61) {$L$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.40,178.21) --
-	(171.83,178.21);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.61,178.02) --
-	(171.61,178.40);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (171.61,173.35) {$r$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.71,177.88) --
-	(163.34,177.88);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (162.54,177.07) --
-	(162.54,178.66);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (162.54,173.02) {$l$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (155.74,166.68) --
-	(158.47,166.68);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (157.14,164.57) --
-	(157.14,168.62);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (157.14,163.18) {$\sigma$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.80,189.91) --
-	(190.03,189.91);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.42,189.34) --
-	(189.42,190.47);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (189.42,186.41) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (197.21,211.39) --
+	(197.77,211.39);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (197.49,211.18) --
+	(197.49,211.61);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (197.49,207.50) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (208.57,213.51) --
+	(209.23,213.51);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (208.90,213.19) --
+	(208.90,213.82);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (208.90,210.01) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (202.97,216.96) --
+	(203.07,216.96);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (203.02,216.92) --
+	(203.02,217.00);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (203.02,212.10) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (192.82,204.83) --
+	(193.33,204.83);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (193.08,204.58) --
+	(193.08,205.07);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (193.08,201.33) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (194.69,206.11) --
+	(195.23,206.11);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (194.96,205.86) --
+	(194.96,206.34);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (194.96,201.25) {$l$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (198.04,212.64) --
+	(198.65,212.64);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (198.35,212.38) --
+	(198.35,212.90);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (198.35,209.14) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (209.68,214.13) --
+	(209.84,214.13);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (209.76,214.01) --
+	(209.76,214.24);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (209.76,210.63) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (174.61,181.29) --
+	(175.42,181.29);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (175.02,180.81) --
+	(175.02,181.76);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (175.02,177.40) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (199.97,203.57) --
+	(200.33,203.57);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (200.15,203.36) --
+	(200.15,203.77);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (200.15,200.07) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (196.18,205.87) --
+	(196.32,205.87);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (196.25,205.81) --
+	(196.25,205.93);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (196.25,201.01) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (168.45,170.16) --
+	(169.30,170.16);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (168.88,169.66) --
+	(168.88,170.65);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (168.88,166.66) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (170.19,171.34) --
+	(171.03,171.34);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (170.61,170.86) --
+	(170.61,171.80);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (170.61,166.48) {$l$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (168.92,178.96) --
+	(170.15,178.96);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (169.55,178.44) --
+	(169.55,179.47);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (169.55,175.46) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (200.80,203.98) --
+	(200.99,203.98);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (200.89,203.91) --
+	(200.89,204.05);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (200.89,200.48) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (160.27,187.40) --
+	(161.12,187.40);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (160.70,187.18) --
+	(160.70,187.62);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (160.70,183.51) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (198.07,202.56) --
+	(198.59,202.56);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (198.33,202.33) --
+	(198.33,202.79);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (198.33,199.06) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (189.68,202.66) --
+	(189.90,202.66);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (189.79,202.63) --
+	(189.79,202.70);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (189.79,197.80) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (156.66,181.05) --
+	(157.53,181.05);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (157.10,180.80) --
+	(157.10,181.30);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (157.10,177.55) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (158.68,181.59) --
+	(159.52,181.59);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (159.10,181.36) --
+	(159.10,181.82);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (159.10,176.73) {$l$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (161.65,183.86) --
+	(162.51,183.86);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (162.09,183.56) --
+	(162.09,184.15);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (162.09,180.36) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (199.83,203.92) --
+	(200.10,203.92);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (199.96,203.85) --
+	(199.96,203.99);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (199.96,200.42) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (126.81,179.89) --
+	(129.23,179.89);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (128.06,179.46) --
+	(128.06,180.31);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (128.06,176.00) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (179.96,181.14) --
+	(180.68,181.14);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (180.33,180.91) --
+	(180.33,181.37);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (180.33,177.64) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (156.58,184.80) --
+	(156.82,184.80);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (156.70,184.71) --
+	(156.70,184.89);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (156.70,179.94) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (125.55,153.57) --
+	(127.99,153.57);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (126.81,153.09) --
+	(126.81,154.03);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (126.81,150.07) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (126.51,153.65) --
+	(128.85,153.65);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (127.72,153.18) --
+	(127.72,154.11);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (127.72,148.79) {$l$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (127.87,168.66) --
+	(130.38,168.66);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (129.17,168.21) --
+	(129.17,169.09);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (129.17,165.16) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (184.23,188.29) --
+	(184.50,188.29);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (184.36,188.21) --
+	(184.36,188.36);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (184.36,184.79) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (197.38,191.90) --
+	(198.07,191.90);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (197.73,190.51) --
+	(197.73,193.20);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (197.73,188.02) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (203.48,207.05) --
+	(204.11,207.05);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (203.80,206.57) --
+	(203.80,207.51);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (203.80,203.55) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (211.92,218.81) --
+	(212.00,218.81);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (211.96,218.78) --
+	(211.96,218.84);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (211.96,213.95) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (189.80,201.95) --
+	(190.64,201.95);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (190.23,201.73) --
+	(190.23,202.18);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (190.23,198.46) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (195.62,206.61) --
+	(196.35,206.61);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (195.99,206.39) --
+	(195.99,206.84);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (195.99,201.76) {$l$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (190.00,195.23) --
+	(191.11,195.23);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (190.57,194.70) --
+	(190.57,195.74);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (190.57,191.73) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (206.00,210.07) --
+	(206.24,210.07);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (206.12,209.94) --
+	(206.12,210.20);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (206.12,206.57) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (163.25,206.66) --
+	(164.65,206.66);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (163.97,206.38) --
+	(163.97,206.95);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (163.97,202.78) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (206.97,209.86) --
+	(207.61,209.86);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (207.29,209.66) --
+	(207.29,210.05);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (207.29,206.36) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (189.17,210.83) --
+	(189.57,210.83);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (189.37,210.78) --
+	(189.37,210.89);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (189.37,205.97) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (161.84,180.53) --
+	(163.29,180.53);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (162.58,180.05) --
+	(162.58,180.99);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (162.58,177.03) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (163.64,180.82) --
+	(165.04,180.82);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (164.35,180.34) --
+	(164.35,181.30);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (164.35,175.96) {$l$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (173.84,192.40) --
+	(174.66,192.40);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (174.25,191.96) --
+	(174.25,192.82);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (174.25,188.90) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (208.40,212.74) --
+	(208.72,212.74);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (208.56,212.51) --
+	(208.56,212.97);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (208.56,209.24) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (172.84,187.37) --
+	(173.77,187.37);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (173.31,186.95) --
+	(173.31,187.78);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (173.31,183.49) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (185.66,188.36) --
+	(187.00,188.36);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (186.34,187.14) --
+	(186.34,189.50);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (186.34,184.86) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (186.78,195.21) --
+	(186.89,195.21);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (186.83,195.14) --
+	(186.83,195.27);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (186.83,190.35) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (170.90,185.42) --
+	(171.89,185.42);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (171.40,185.05) --
+	(171.40,185.78);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (171.40,181.92) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (171.78,181.93) --
+	(172.71,181.93);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (172.25,181.38) --
+	(172.25,182.46);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (172.25,177.07) {$l$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (176.73,186.97) --
+	(177.37,186.97);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (177.05,186.50) --
+	(177.05,187.44);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (177.05,183.48) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (198.65,202.89) --
+	(198.85,202.89);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (198.75,202.73) --
+	(198.75,203.05);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (198.75,199.39) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (188.50,193.08) --
+	(188.96,193.08);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (188.73,192.74) --
+	(188.73,193.42);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (188.73,189.20) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (181.61,187.90) --
+	(182.63,187.90);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (182.13,187.35) --
+	(182.13,188.43);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (182.13,184.40) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (194.87,203.10) --
+	(194.98,203.10);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (194.92,203.05) --
+	(194.92,203.15);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (194.92,198.24) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (182.90,198.09) --
+	(183.48,198.09);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (183.19,197.82) --
+	(183.19,198.35);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (183.19,194.59) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (188.40,202.17) --
+	(188.86,202.17);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (188.63,201.86) --
+	(188.63,202.48);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (188.63,197.31) {$l$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (185.09,195.15) --
+	(185.75,195.15);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (185.42,194.76) --
+	(185.42,195.53);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (185.42,191.65) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (207.21,211.29) --
+	(207.52,211.29);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (207.37,211.13) --
+	(207.37,211.45);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (207.37,207.79) {$\kappa$};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.39, 60.00) -- ( 99.39, 54.00);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (116.36, 60.00) -- (116.36, 54.00);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (155.75, 60.00) -- (155.75, 54.00);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.72, 60.00) -- (172.72, 54.00);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.11, 60.00) -- (212.11, 54.00);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.08, 60.00) -- (229.08, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.31, 60.00) -- ( 99.31, 54.00);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.62, 60.00) -- (138.62, 54.00);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.93, 60.00) -- (177.93, 54.00);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.25, 60.00) -- (217.25, 54.00);
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 99.39, 38.40) {5};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (116.36, 38.40) {10};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (155.75, 38.40) {50};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (212.11, 38.40) {500};
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- ( 60.00,229.08);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 99.31, 38.40) {10};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (138.62, 38.40) {100};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (177.93, 38.40) {1000};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (217.25, 38.40) {10000};
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 60.00) -- ( 60.00,217.25);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 99.39) -- ( 54.00, 99.39);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,116.36) -- ( 54.00,116.36);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,155.75) -- ( 54.00,155.75);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,172.72) -- ( 54.00,172.72);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,212.11) -- ( 54.00,212.11);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,229.08) -- ( 54.00,229.08);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00, 99.31) -- ( 54.00, 99.31);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,138.62) -- ( 54.00,138.62);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,177.93) -- ( 54.00,177.93);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.00,217.25) -- ( 54.00,217.25);
 
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00, 95.95) {5};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,112.92) {10};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,152.31) {50};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,169.28) {100};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,208.67) {500};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,225.64) {1000};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00, 95.87) {10};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,135.18) {100};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,174.49) {1000};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 48.00,213.80) {10000};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,171.00) rectangle (169.31,165.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,159.00) rectangle (169.31,153.00);
 \definecolor{fillColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,159.00) rectangle (169.31,153.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,147.00) rectangle (169.31,141.00);
 \definecolor{fillColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,147.00) rectangle (169.31,141.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,135.00) rectangle (169.31,129.00);
 \definecolor{fillColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,135.00) rectangle (169.31,129.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,123.00) rectangle (169.31,117.00);
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,123.00) rectangle (169.31,117.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,111.00) rectangle (169.31,105.00);
 \definecolor{fillColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,111.00) rectangle (169.31,105.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11, 99.00) rectangle (169.31, 93.00);
 \definecolor{fillColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11, 99.00) rectangle (169.31, 93.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11, 87.00) rectangle (169.31, 81.00);
 \definecolor{fillColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11, 87.00) rectangle (169.31, 81.00);
-\definecolor{fillColor}{RGB}{68,68,68}
-
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11, 75.00) rectangle (169.31, 69.00);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,164.56) {Ran};
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at (144.54, 14.40) {ESS/$10^6$ states [cons(\textit{real})]};
-
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at ( 21.60,144.54) {ESS/$10^6$ states [AVMVN+NER+Bactrian+adapt(\textit{real})]};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at (144.54, 14.40) {ESS/hr [cons(\textit{real})]};
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.50] at ( 21.60,144.54) {ESS/hr [AVMVN+NER+Bactrian+adapt(\textit{real})]};
 \end{scope}
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (113.37,176.23) --
-	(123.12,176.23);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (118.73,174.41) --
-	(118.73,177.92);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (118.73,172.34) {$p$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (172.81,162.66) --
-	(176.28,162.66);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.61,161.37) --
-	(174.61,163.88);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (174.61,157.80) {$L$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.21,178.79) --
-	(180.37,178.79);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.31,177.78) --
-	(179.31,179.76);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (179.31,173.93) {$r$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (131.04,146.84) --
-	(140.36,146.84);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (136.14,145.03) --
-	(136.14,148.53);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (136.14,141.98) {$l$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 87.76,170.79) --
-	( 95.01,170.79);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 91.65,168.73) --
-	( 91.65,172.69);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 91.65,167.29) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.62,181.75) --
-	(186.28,181.75);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (185.95,181.29) --
-	(185.95,182.19);
-\definecolor{drawColor}{RGB}{255,0,109}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (185.95,178.25) {$\kappa$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.35,183.23) --
-	(175.77,183.23);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (174.59,182.63) --
-	(174.59,183.81);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (174.59,179.34) {$p$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.08,185.46) --
-	(182.02,185.46);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.59,184.16) --
-	(180.59,186.69);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (180.59,180.60) {$L$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.09,191.41) --
-	(183.39,191.41);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (183.24,191.26) --
-	(183.24,191.56);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (183.24,186.55) {$r$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.97,175.46) --
-	(164.02,175.46);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (163.01,174.36) --
-	(163.01,176.51);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (163.01,170.60) {$l$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.57,185.09) --
-	(164.37,185.09);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (163.01,184.25) --
-	(163.01,185.90);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (163.01,181.59) {$\sigma$};
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.65,187.48) --
-	(187.64,187.48);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.15,186.93) --
-	(187.15,188.01);
-\definecolor{drawColor}{RGB}{253,104,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (187.15,183.98) {$\kappa$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (136.36,156.88) --
-	(145.35,156.88);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (141.26,155.53) --
-	(141.26,158.17);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (141.26,152.99) {$p$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.54,188.93) --
-	(183.90,188.93);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.75,188.26) --
-	(182.75,189.59);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (182.75,184.07) {$L$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.72,192.48) --
-	(185.16,192.48);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (184.94,192.24) --
-	(184.94,192.72);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (184.94,187.62) {$r$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (116.65,143.01) --
-	(121.72,143.01);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (119.32,140.92) --
-	(119.32,144.93);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (119.32,138.15) {$l$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (129.42,153.61) --
-	(137.45,153.61);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (133.77,152.17) --
-	(133.77,154.96);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (133.77,150.11) {$\sigma$};
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.03,189.79) --
-	(189.75,189.79);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.39,189.49) --
-	(189.39,190.09);
-\definecolor{drawColor}{RGB}{143,161,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (189.39,186.29) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (147.58,166.10) --
-	(151.24,166.10);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.48,165.61) --
-	(149.48,166.58);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (149.48,162.21) {$p$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.56,188.13) --
-	(183.73,188.13);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (182.67,187.38) --
-	(182.67,188.87);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (182.67,183.27) {$L$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.76,188.08) --
-	(181.98,188.08);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.87,187.92) --
-	(181.87,188.24);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (181.87,183.22) {$r$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (145.93,157.79) --
-	(149.06,157.79);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (147.54,156.95) --
-	(147.54,158.60);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (147.54,152.93) {$l$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (137.22,160.83) --
-	(140.84,160.83);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (139.10,159.54) --
-	(139.10,162.06);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (139.10,157.33) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.78,189.83) --
-	(190.34,189.83);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.07,189.51) --
-	(190.07,190.15);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (190.07,186.34) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (132.78,175.20) --
-	(141.58,175.20);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (137.57,173.42) --
-	(137.57,176.85);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (137.57,171.31) {$p$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (177.13,177.06) --
-	(178.12,177.06);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (177.63,176.01) --
-	(177.63,178.06);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (177.63,172.20) {$L$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.82,182.51) --
-	(179.53,182.51);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.18,182.11) --
-	(179.18,182.91);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (179.18,177.65) {$r$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (127.95,138.26) --
-	(132.53,138.26);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (130.34,136.14) --
-	(130.34,140.21);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (130.34,133.40) {$l$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (105.15,159.54) --
-	(113.88,159.54);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (109.90,158.03) --
-	(109.90,160.96);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (109.90,156.04) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (186.73,187.47) --
-	(187.47,187.47);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.10,187.20) --
-	(187.10,187.74);
-\definecolor{drawColor}{RGB}{0,219,171}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (187.10,183.97) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.40,162.64) --
-	(156.80,162.64);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (154.25,157.19) --
-	(154.25,167.10);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (154.25,158.76) {$p$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.38,184.48) --
-	(173.21,184.48);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.37,182.64) --
-	(171.37,186.19);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (171.37,179.62) {$L$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (180.89,201.51) --
-	(181.32,201.51);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.11,201.37) --
-	(181.11,201.64);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (181.11,196.65) {$r$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.99,184.01) --
-	(164.25,184.01);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (163.15,182.98) --
-	(163.15,185.00);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (163.15,179.15) {$l$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.64,167.13) --
-	(155.42,167.13);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (154.07,165.25) --
-	(154.07,168.88);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (154.07,163.63) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.58,189.13) --
-	(189.63,189.13);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.11,188.65) --
-	(189.11,189.59);
-\definecolor{drawColor}{RGB}{0,216,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (189.11,185.63) {$\kappa$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (169.40,180.56) --
-	(173.37,180.56);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.46,179.48) --
-	(171.46,181.61);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (171.46,176.68) {$p$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (178.93,185.82) --
-	(180.13,185.82);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.54,185.18) --
-	(179.54,186.44);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (179.54,180.96) {$L$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.70,187.14) --
-	(182.02,187.14);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (181.86,186.92) --
-	(181.86,187.35);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (181.86,182.28) {$r$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (138.51,144.38) --
-	(141.76,144.38);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (140.19,142.61) --
-	(140.19,146.03);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (140.19,139.52) {$l$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (141.57,161.01) --
-	(144.79,161.01);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (143.23,159.33) --
-	(143.23,162.58);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (143.23,157.51) {$\sigma$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (188.73,190.27) --
-	(191.12,190.27);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.95,189.56) --
-	(189.95,190.97);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (189.95,186.78) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.69,164.84) --
-	(154.83,164.84);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (153.79,163.54) --
-	(153.79,166.06);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (153.79,160.95) {$p$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (157.74,167.56) --
-	(164.16,167.56);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (161.16,162.65) --
-	(161.16,171.64);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (161.16,162.70) {$L$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.02,176.63) --
-	(164.48,176.63);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.25,176.41) --
-	(164.25,176.84);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (164.25,171.77) {$r$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (138.68,157.74) --
-	(145.44,157.74);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (142.29,155.82) --
-	(142.29,159.52);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (142.29,152.88) {$l$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (144.06,164.24) --
-	(146.33,164.24);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (145.22,162.53) --
-	(145.22,165.84);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (145.22,160.75) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.00,187.63) --
-	(187.88,187.63);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.44,186.85) --
-	(187.44,188.39);
-\definecolor{drawColor}{RGB}{255,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (187.44,184.13) {$\kappa$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.77,163.30) --
-	(153.87,163.30);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (152.37,161.73) --
-	(152.37,164.78);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (152.37,159.41) {$p$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (147.08,156.47) --
-	(151.98,156.47);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.66,154.55) --
-	(149.66,158.25);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (149.66,151.61) {$L$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.67,178.21) --
-	(165.05,178.21);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.86,178.02) --
-	(164.86,178.40);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (164.86,173.35) {$r$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (149.56,177.88) --
-	(152.10,177.88);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.86,177.07) --
-	(150.86,178.66);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (150.86,173.02) {$l$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (146.99,166.68) --
-	(150.13,166.68);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (148.61,164.57) --
-	(148.61,168.62);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (148.61,163.18) {$\sigma$};
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (189.86,189.91) --
-	(190.66,189.91);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.26,189.34) --
-	(190.26,190.47);
-\definecolor{drawColor}{RGB}{68,68,68}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (190.26,186.41) {$\kappa$};
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (198.76,211.39) --
+	(199.25,211.39);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (199.01,211.18) --
+	(199.01,211.61);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (199.01,207.50) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (202.95,213.51) --
+	(203.50,213.51);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (203.23,213.19) --
+	(203.23,213.82);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (203.23,210.01) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (205.16,216.96) --
+	(205.22,216.96);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (205.19,216.92) --
+	(205.19,217.00);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (205.19,212.10) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (188.22,204.83) --
+	(188.74,204.83);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (188.48,204.58) --
+	(188.48,205.07);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (188.48,201.33) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (190.89,206.11) --
+	(191.29,206.11);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (191.09,205.86) --
+	(191.09,206.34);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (191.09,201.25) {$l$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (190.69,212.64) --
+	(191.24,212.64);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (190.97,212.38) --
+	(190.97,212.90);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (190.97,209.14) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (207.86,214.13) --
+	(208.10,214.13);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (207.98,214.01) --
+	(207.98,214.24);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (207.98,210.63) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (165.13,181.29) --
+	(167.11,181.29);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (166.15,180.81) --
+	(166.15,181.76);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (166.15,177.40) {$p$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (194.77,203.57) --
+	(195.32,203.57);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (195.04,203.36) --
+	(195.04,203.77);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (195.04,200.07) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (196.35,205.87) --
+	(196.45,205.87);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (196.40,205.81) --
+	(196.40,205.93);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (196.40,201.01) {$r$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (149.54,170.16) --
+	(151.14,170.16);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (150.36,169.66) --
+	(150.36,170.65);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (150.36,166.66) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (151.14,171.34) --
+	(152.74,171.34);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (151.96,170.86) --
+	(151.96,171.80);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (151.96,166.48) {$l$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (159.52,178.96) --
+	(161.49,178.96);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (160.53,178.44) --
+	(160.53,179.47);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (160.53,175.46) {$\sigma$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (199.60,203.98) --
+	(199.75,203.98);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (199.67,203.91) --
+	(199.67,204.05);
+\definecolor{drawColor}{RGB}{253,104,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (199.67,200.48) {$\kappa$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (169.84,187.40) --
+	(170.74,187.40);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (170.30,187.18) --
+	(170.30,187.62);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (170.30,183.51) {$p$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (193.55,202.56) --
+	(194.13,202.56);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (193.84,202.33) --
+	(193.84,202.79);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (193.84,199.06) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (193.23,202.66) --
+	(193.32,202.66);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (193.28,202.63) --
+	(193.28,202.70);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (193.28,197.80) {$r$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (168.01,181.05) --
+	(168.81,181.05);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (168.41,180.80) --
+	(168.41,181.30);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (168.41,177.55) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (168.77,181.59) --
+	(169.58,181.59);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (169.18,181.36) --
+	(169.18,181.82);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (169.18,176.73) {$l$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (162.75,183.86) --
+	(163.55,183.86);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (163.15,183.56) --
+	(163.15,184.15);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (163.15,180.36) {$\sigma$};
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (198.74,203.92) --
+	(198.91,203.92);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (198.83,203.85) --
+	(198.83,203.99);
+\definecolor{drawColor}{RGB}{143,161,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (198.83,200.42) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (146.41,179.89) --
+	(149.44,179.89);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (147.99,179.46) --
+	(147.99,180.31);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (147.99,176.00) {$p$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (176.30,181.14) --
+	(176.61,181.14);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (176.46,180.91) --
+	(176.46,181.37);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (176.46,177.64) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (177.46,184.80) --
+	(177.71,184.80);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (177.59,184.71) --
+	(177.59,184.89);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (177.59,179.94) {$r$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (142.69,153.57) --
+	(144.45,153.57);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (143.59,153.09) --
+	(143.59,154.03);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (143.59,150.07) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (142.51,153.65) --
+	(144.02,153.65);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (143.28,153.18) --
+	(143.28,154.11);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (143.28,148.79) {$l$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (126.85,168.66) --
+	(130.04,168.66);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (128.52,168.21) --
+	(128.52,169.09);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (128.52,165.16) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (182.99,188.29) --
+	(183.27,188.29);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (183.13,188.21) --
+	(183.13,188.36);
+\definecolor{drawColor}{RGB}{0,195,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (183.13,184.79) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (178.90,191.90) --
+	(180.20,191.90);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (179.56,190.51) --
+	(179.56,193.20);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (179.56,188.02) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (191.31,207.05) --
+	(192.04,207.05);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (191.68,206.57) --
+	(191.68,207.51);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (191.68,203.55) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (198.03,218.81) --
+	(198.13,218.81);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (198.08,218.78) --
+	(198.08,218.84);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (198.08,213.95) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (178.54,201.95) --
+	(179.08,201.95);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (178.81,201.73) --
+	(178.81,202.18);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (178.81,198.46) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (185.32,206.61) --
+	(185.86,206.61);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (185.59,206.39) --
+	(185.59,206.84);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (185.59,201.76) {$l$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (178.91,195.23) --
+	(179.71,195.23);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (179.31,194.70) --
+	(179.31,195.74);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (179.31,191.73) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (203.45,210.07) --
+	(203.70,210.07);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (203.57,209.94) --
+	(203.57,210.20);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (203.57,206.57) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (189.13,206.66) --
+	(190.02,206.66);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (189.58,206.38) --
+	(189.58,206.95);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (189.58,202.78) {$p$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (195.08,209.86) --
+	(195.57,209.86);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (195.33,209.66) --
+	(195.33,210.05);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (195.33,206.36) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (196.59,210.83) --
+	(196.67,210.83);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (196.63,210.78) --
+	(196.63,210.89);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (196.63,205.97) {$r$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (165.91,180.53) --
+	(166.94,180.53);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (166.44,180.05) --
+	(166.44,180.99);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (166.44,177.03) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (166.32,180.82) --
+	(167.48,180.82);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (166.91,180.34) --
+	(166.91,181.30);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (166.91,175.96) {$l$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (168.90,192.40) --
+	(169.83,192.40);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (169.37,191.96) --
+	(169.37,192.82);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (169.37,188.90) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (202.27,212.74) --
+	(202.73,212.74);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (202.50,212.51) --
+	(202.50,212.97);
+\definecolor{drawColor}{RGB}{0,216,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (202.50,209.24) {$\kappa$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (173.15,187.37) --
+	(173.79,187.37);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (173.47,186.95) --
+	(173.47,187.78);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (173.47,183.49) {$p$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (177.72,188.36) --
+	(179.11,188.36);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (178.43,187.14) --
+	(178.43,189.50);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (178.43,184.86) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (180.05,195.21) --
+	(180.16,195.21);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (180.10,195.14) --
+	(180.10,195.27);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (180.10,190.35) {$r$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (163.11,185.42) --
+	(164.30,185.42);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (163.72,185.05) --
+	(163.72,185.78);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (163.72,181.92) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (164.35,181.93) --
+	(165.81,181.93);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (165.09,181.38) --
+	(165.09,182.46);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (165.09,177.07) {$l$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (167.00,186.97) --
+	(167.68,186.97);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (167.34,186.50) --
+	(167.34,187.44);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (167.34,183.48) {$\sigma$};
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (196.20,202.89) --
+	(196.44,202.89);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (196.32,202.73) --
+	(196.32,203.05);
+\definecolor{drawColor}{RGB}{151,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (196.32,199.39) {$\kappa$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (177.17,193.08) --
+	(177.85,193.08);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (177.51,192.74) --
+	(177.51,193.42);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (177.51,189.20) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (175.80,187.90) --
+	(176.81,187.90);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (176.31,187.35) --
+	(176.31,188.43);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (176.31,184.40) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (185.90,203.10) --
+	(186.00,203.10);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (185.95,203.05) --
+	(185.95,203.15);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (185.95,198.24) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (170.74,198.09) --
+	(171.34,198.09);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (171.05,197.82) --
+	(171.05,198.35);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (171.05,194.59) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (176.35,202.17) --
+	(176.96,202.17);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (176.66,201.86) --
+	(176.66,202.48);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (176.66,197.31) {$l$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (174.44,195.15) --
+	(175.12,195.15);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (174.79,194.76) --
+	(174.79,195.53);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (174.79,191.65) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (203.33,211.29) --
+	(203.60,211.29);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (203.47,211.13) --
+	(203.47,211.45);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (203.47,207.79) {$\kappa$};
 \end{scope}

### 2020-08-31 benchmarking/benchmarkingVM/ESS_timesettings.tex
Results update

% Created by tikzDevice version 0.12.3.1 on 2020-08-31 17:27:56
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (578.16,357.33);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,357.33);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at (301.08,328.59) {\bfseries Relative speed compared with \textit{cat}};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 10.80,184.67) {Relative samples/hr};
\end{scope}
\begin{scope}
\path[clip] ( 49.20, 61.20) rectangle (552.96,308.13);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] ( 49.20,184.67) --
	(458.76,184.67);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] ( 53.30,192.21) circle (  2.25);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] ( 57.39,192.33) circle (  2.25);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] ( 61.49,192.07) circle (  2.25);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] ( 65.58,189.41) circle (  2.25);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] ( 69.68,201.89) circle (  2.25);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] ( 73.77,192.33) circle (  2.25);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] ( 77.87,193.68) circle (  2.25);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] ( 81.96,194.75) circle (  2.25);

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] ( 53.30,193.62) --
	( 86.06,193.62);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at ( 69.68,297.24) {5.2\% slower};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] ( 90.16,  0.00) --
	( 90.16,357.33);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] ( 94.25,131.15) circle (  2.25);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] ( 98.35,142.51) circle (  2.25);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (102.44,137.12) circle (  2.25);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (106.54,133.51) circle (  2.25);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (110.63,115.30) circle (  2.25);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (114.73,104.29) circle (  2.25);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (118.83,121.85) circle (  2.25);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (122.92, 87.01) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] ( 94.25,122.43) --
	(127.02,122.43);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (110.63,297.24) {29\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (131.11,  0.00) --
	(131.11,357.33);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (135.21,210.25) circle (  2.25);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (139.30,199.78) circle (  2.25);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (143.40,200.44) circle (  2.25);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (147.49,195.49) circle (  2.25);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (151.59,212.96) circle (  2.25);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (155.69,234.21) circle (  2.25);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (159.78,210.45) circle (  2.25);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (163.88,228.46) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (135.21,211.98) --
	(167.97,211.98);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (151.59,297.24) {17\% slower};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (172.07,  0.00) --
	(172.07,357.33);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (176.16,137.47) circle (  2.25);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (180.26,147.34) circle (  2.25);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (184.36,140.19) circle (  2.25);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (188.45,140.07) circle (  2.25);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (192.55,140.34) circle (  2.25);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (196.64,103.65) circle (  2.25);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (200.74,122.50) circle (  2.25);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (204.83,113.14) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (176.16,131.17) --
	(208.93,131.17);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (192.55,297.24) {26\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (213.02,  0.00) --
	(213.02,357.33);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (217.12,221.94) circle (  2.25);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (221.22,222.13) circle (  2.25);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (225.31,218.65) circle (  2.25);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (229.41,207.34) circle (  2.25);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (233.50,217.59) circle (  2.25);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (237.60,198.68) circle (  2.25);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (241.69,213.67) circle (  2.25);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (245.79,189.78) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (217.12,211.56) --
	(249.88,211.56);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (233.50,297.24) {16\% slower};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (253.98,  0.00) --
	(253.98,357.33);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (258.08,229.80) circle (  2.25);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (262.17,227.84) circle (  2.25);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (266.27,228.47) circle (  2.25);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (270.36,216.45) circle (  2.25);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (274.46,237.37) circle (  2.25);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (278.55,221.39) circle (  2.25);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (282.65,219.64) circle (  2.25);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (286.75,212.76) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (258.08,224.38) --
	(290.84,224.38);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (274.46,297.24) {25\% slower};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (294.94,  0.00) --
	(294.94,357.33);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (299.03,243.36) circle (  2.25);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (303.13,239.88) circle (  2.25);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (307.22,240.25) circle (  2.25);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (311.32,228.38) circle (  2.25);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (315.41,250.89) circle (  2.25);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (319.51,247.98) circle (  2.25);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (323.61,232.84) circle (  2.25);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (327.70,224.69) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (299.03,238.74) --
	(331.80,238.74);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (315.41,297.24) {35\% slower};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (335.89,  0.00) --
	(335.89,357.33);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (339.99,133.85) circle (  2.25);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (344.08,146.75) circle (  2.25);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (348.18,141.24) circle (  2.25);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (352.28,140.02) circle (  2.25);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (356.37,135.64) circle (  2.25);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (360.47,103.87) circle (  2.25);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (364.56,119.49) circle (  2.25);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (368.66,109.12) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (339.99,129.36) --
	(372.75,129.36);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (356.37,297.24) {27\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (376.85,  0.00) --
	(376.85,357.33);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (380.94,141.02) circle (  2.25);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (385.04,149.13) circle (  2.25);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (389.14,142.97) circle (  2.25);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (393.23,139.61) circle (  2.25);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (397.33,137.57) circle (  2.25);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (401.42,114.39) circle (  2.25);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (405.52,129.13) circle (  2.25);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (409.61,140.48) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (380.94,137.06) --
	(413.71,137.06);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (397.33,297.24) {23\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (417.80,  0.00) --
	(417.80,357.33);
\definecolor{fillColor}{RGB}{255,0,109}

\path[fill=fillColor] (421.90,147.24) circle (  2.25);
\definecolor{fillColor}{RGB}{253,104,0}

\path[fill=fillColor] (426.00,156.87) circle (  2.25);
\definecolor{fillColor}{RGB}{143,161,0}

\path[fill=fillColor] (430.09,147.29) circle (  2.25);
\definecolor{fillColor}{RGB}{0,195,0}

\path[fill=fillColor] (434.19,143.53) circle (  2.25);
\definecolor{fillColor}{RGB}{0,219,171}

\path[fill=fillColor] (438.28,144.92) circle (  2.25);
\definecolor{fillColor}{RGB}{0,216,255}

\path[fill=fillColor] (442.38,124.70) circle (  2.25);
\definecolor{fillColor}{RGB}{151,0,255}

\path[fill=fillColor] (446.47,142.61) circle (  2.25);
\definecolor{fillColor}{RGB}{255,0,255}

\path[fill=fillColor] (450.57,147.18) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (421.90,144.49) --
	(454.67,144.49);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (438.28,297.24) {20\% faster};
\definecolor{drawColor}{RGB}{105,105,105}

\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (458.76,  0.00) --
	(458.76,357.33);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,357.33);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20, 61.20) -- (552.96, 61.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 69.68, 61.20) -- ( 69.68, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (110.63, 61.20) -- (110.63, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.59, 61.20) -- (151.59, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.55, 61.20) -- (192.55, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (233.50, 61.20) -- (233.50, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (274.46, 61.20) -- (274.46, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (315.41, 61.20) -- (315.41, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (356.37, 61.20) -- (356.37, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (397.33, 61.20) -- (397.33, 55.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.28, 61.20) -- (438.28, 55.20);

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at ( 71.74, 49.20) {adapt(\textit{cat})};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (112.70, 49.20) {nocons(\textit{real})};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (153.66, 49.20) {cons(\textit{real})};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (194.61, 49.20) {adapt(\textit{real})};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (235.57, 49.20) {nocons(\textit{quant})};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (276.52, 49.20) {cons(\textit{quant})};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (317.48, 49.20) {adapt(\textit{quant})};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (358.44, 49.20) {Bactrian};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (399.39, 49.20) {NER};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (440.35, 49.20) {AVMVN};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20, 61.20) -- ( 49.20,308.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20, 61.20) -- ( 43.20, 61.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20,133.42) -- ( 43.20,133.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20,184.67) -- ( 43.20,184.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20,235.91) -- ( 43.20,235.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.20,308.13) -- ( 43.20,308.13);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 37.20, 57.76) {$\frac{1}{2}\times$};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 37.20,129.98) {$\frac{3}{4}\times$};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 37.20,181.22) {$1\times$};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 37.20,232.46) {$\frac{4}{3}\times$};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 37.20,304.69) {$\frac{2}{1}\times$};
\end{scope}
\begin{scope}
\path[clip] ( 49.20, 61.20) rectangle (552.96,308.13);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (485.99,229.67) rectangle (493.19,223.67);
\definecolor{fillColor}{RGB}{253,104,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (485.99,217.67) rectangle (493.19,211.67);
\definecolor{fillColor}{RGB}{143,161,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (485.99,205.67) rectangle (493.19,199.67);
\definecolor{fillColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (485.99,193.67) rectangle (493.19,187.67);
\definecolor{fillColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (485.99,181.67) rectangle (493.19,175.67);
\definecolor{fillColor}{RGB}{0,216,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (485.99,169.67) rectangle (493.19,163.67);
\definecolor{fillColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (485.99,157.67) rectangle (493.19,151.67);
\definecolor{fillColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (485.99,145.67) rectangle (493.19,139.67);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (502.19,223.22) {Cognato};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (502.19,211.22) {Dornburg};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (502.19,199.22) {Sauquet};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (502.19,187.22) {Broughton};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (502.19,175.22) {Kawahara};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (502.19,163.22) {simulated};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (502.19,151.22) {Rightmyer};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (502.19,139.22) {Moyle};
\end{scope}
\end{tikzpicture}

\end{document}

### 2020-08-31 RatesWCSS/CStemplate.sh

@@ -1,0 +1,18 @@
+#!/bin/bash -e
+
+#SBATCH --job-name   	 quant_SIM
+#SBATCH --account    	 nesi00390
+#SBATCH --time       	 20:00:00
+#SBATCH --ntasks     	 1
+#SBATCH --nodes	     	 1
+#SBATCH --mem		 500
+#SBATCH --cpus-per-task	 1
+#SBATCH --output    	 O_SIM.out
+#SBATCH --error      	 E_SIM.err
+
+
+module load beagle-lib/3.0.1-gimkl-2017a
+module load Java/1.8.0_144
+
+
+~/beast/bin/beast -overwrite -seed RANDOMSEED -beagle_SSE runSIM.xml

### 2020-08-31 RatesWCSS/submit_CSjob.sh

@@ -1,0 +1,18 @@
+#!/bin/sh
+TEMPLATE=../../CStemplate.sh
+
+
+
+for sim in {1..100}
+do
+rand=$RANDOM
+sed "s/SIM/${sim}/g" ${TEMPLATE} > temp.sl
+sed "s/RANDOMSEED/$rand/g" temp.sl > temp2.sl 
+echo "run${sim}.xml with seed ${rand}"
+sbatch temp2.sl 
+rm -f temp.sl
+rm -f temp2.sl 
+sleep 2
+done
+
+

### 2020-08-31 RatesWCSS/templates/populateXMLTemplates.R

@@ -1,0 +1,115 @@
+library(ape)
+args = commandArgs(trailingOnly=TRUE)
+
+
+print(args)
+
+logfile.folder = args[1] 
+output.txt.folder  = args[2]
+
+
+logfile.folder = "../true/"
+output.txt.folder = "../sim/"
+
+benchmarking = FALSE
+
+#nsim = 100
+nsim = 100
+#ntaxa = 100
+ntaxa = 30
+#templates = c("cat", "real", "quant", "real_06", "quant_06")
+#templates = c("bactrian95")
+
+templates = c("cat_adaptive", "quant_cached_adaptive", "real_adaptive", "AVMVN")
+
+
+for (xx in 1:length(templates)) {
+	templ = templates[xx]
+
+	
+	
+	# Read the log file
+	L = read.table(file=paste0(logfile.folder, "/priorSamples_N", ntaxa, ".log"), sep="\t", header=T)
+
+	# Read the .xml template
+	template_file = paste0("simulate_", templ, ".xml")
+	xml_template = readLines(template_file) 
+
+	# Read species tree
+	trees = read.nexus(file=paste0(logfile.folder, "/priorSamples_N", ntaxa, ".trees"))
+
+
+
+	# String replace
+	sim = 1
+	for (i in 1:nrow(L)){
+
+
+		tree = trees[i]
+		tree = read.tree(text = write.tree(tree))
+
+		xml_populated = xml_template
+
+
+		# Sample	proportionInvariant	gammaShape	kappa	ucldStdev	rateCategories.1	rateCategories.2	...	rateCategories.199	birthRate	freqParameter.1	freqParameter.2	freqParameter.3	freqParameter.4
+
+
+		# Put tree in file
+ 		xml_populated = gsub("INSERT_TREE_HERE", write.tree(tree), xml_populated)
+
+
+		# Clock SD
+		xml_populated = gsub("INSERT_CLOCK_SD_HERE", L[i,"ucldStdev"], xml_populated)
+
+
+		# Frequencies 
+		xml_populated = gsub("INSERT_FREQUENCIES_HERE", paste(as.numeric(L[i, paste0("freqParameter.", 1:4)]), collapse = " "), xml_populated)
+
+
+		# Kappa
+		xml_populated = gsub("INSERT_KAPPA_HERE", L[i,"kappa"], xml_populated)
+
+
+
+		# Simualation number
[…]

### 2020-08-31 benchmarking/render.R

@@ -7,11 +7,11 @@ library(rjson)
 
 
 
-PER_CHAIN = TRUE
+PER_CHAIN = FALSE
 
 #settings = c("cat", "real", "quant", "bactrian95", "bactrian98")
 settings = c("cat",  "real_06", "quant_06", "real", "quant", "bactrian95", "bactrian98", "NER", "AVMN")
-settings = c("cat", "cat_adaptive",  "real_06", "real", "real_adaptive", "quant_06_cached", "quant_cached_adaptive", "quant_cached", "bactrian95", "NER", "AVMVN")
+settings = c("cat", "cat_adaptive",  "real_06", "real", "real_adaptive", "quant_06_cached", "quant_cached", "quant_cached_adaptive", "bactrian95", "NER", "AVMVN")
 
 benchmark = data.frame(batch = numeric(0), param = character(0), dataset = character(0), partition = numeric(0), setting = character(0), nstates = numeric(0), finalESS = numeric(0), finalMCD = numeric(0), done = logical(0),  error = logical(0))
 
@@ -34,6 +34,14 @@ settings.names["NER"] = "NER+Bactrian+adapt(\\textit{real})"
 settings.names["AVMVN"] = "AVMVN+NER+Bactrian+adapt(\\textit{real})"
 
 
+
+
+settings.names.short = settings.names
+settings.names.short["bactrian95"] = "Bactrian"
+settings.names.short["NER"] = "NER"
+settings.names.short["AVMVN"] = "AVMVN"
+
+
 latex.table = read.table("../latex.table", sep = "&")
 colnames(latex.table) = c("ID", "N", "P", "L", "Leff", "ref")
 latex.table$ref = gsub(" ", "", gsub("[0-9].+", "", latex.table$ref))
@@ -48,6 +56,7 @@ progress.df = read.csv("progressVM.csv", header = T)
 
 #parameters = c("posterior", "likelihood", "prior", "height", "birthRate", "kappa",  "ucldStdev", "clockRate", "TipRates", "RateStatLogger.mean", "RateStatLogger.variance")
 parameters = c("prior", "likelihood", "TipRates", "treeLength", "ucldStdev", "kappa")
[…]

### 2020-09-01 RatesWCSS/WCSS_AVMVN.tex
complete draft

% Created by tikzDevice version 0.12.3.1 on 2020-09-01 10:43:33
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (578.16,578.16);
\begin{scope}
\path[clip] (  0.00,385.44) rectangle (192.72,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.79] at (104.28,559.19) {\bfseries Tree height $h$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (104.28,395.74) {True value};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (  7.13,485.76) {Estimated value};
\end{scope}
\begin{scope}
\path[clip] ( 32.47,425.83) rectangle (176.09,545.69);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] ( 32.47,425.83) --
	(176.09,545.69);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 65.50,452.51) --
	( 65.50,455.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 42.05,431.38) --
	( 42.05,439.34);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.12,452.89) --
	( 66.12,455.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.24,447.06) --
	( 60.24,451.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 78.61,461.83) --
	( 78.61,465.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.79,442.39) --
	( 52.79,444.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 46.14,433.32) --
	( 46.14,441.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 38.48,430.31) --
	( 38.48,431.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 34.07,427.02) --
	( 34.07,427.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.14,434.49) --
	( 44.14,439.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 39.61,431.14) --
	( 39.61,432.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 47.43,436.82) --
	( 47.43,438.53);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.33,429.75) --
	( 37.33,430.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (128.22,483.96) --
	(128.22,523.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 46.70,437.65) --
	( 46.70,438.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 42.97,433.27) --
	( 42.97,435.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 62.46,442.55) --
	( 62.46,469.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.87,443.34) --
	( 54.87,449.34);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 36.97,429.18) --
	( 36.97,430.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 38.34,430.38) --
	( 38.34,431.27);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.56,441.34) --
	( 52.56,443.68);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 51.80,433.61) --
	( 51.80,438.31);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.44,447.20) --
	( 60.44,450.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 77.29,456.18) --
	( 77.29,473.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.08,443.45) --
	( 54.08,445.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.68,435.11) --
	( 44.68,436.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 39.95,431.17) --
	( 39.95,433.40);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 56.47,444.63) --
	( 56.47,447.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 76.90,462.65) --
	( 76.90,466.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 41.51,431.86) --
	( 41.51,433.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.22,438.12) --
	( 48.22,443.58);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 74.69,456.13) --
	( 74.69,462.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 34.27,427.08) --
	( 34.27,427.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 53.39,440.46) --
	( 53.39,444.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 41.21,432.77) --
	( 41.21,433.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.34,431.94) --
	( 40.34,432.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 46.55,433.22) --
	( 46.55,448.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 38.28,430.15) --
	( 38.28,430.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.51,454.21) --
	( 66.51,458.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.33,442.90) --
	( 54.33,444.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 69.08,455.12) --
	( 69.08,457.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.72,426.74) --
	( 33.72,427.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.02,441.49) --
	( 52.02,443.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 47.67,437.76) --
	( 47.67,439.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 77.25,460.87) --
	( 77.25,464.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 39.23,430.74) --
	( 39.23,432.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 42.69,433.38) --
	( 42.69,434.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.60,438.64) --
	( 48.60,440.30);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 46.71,437.34) --
	( 46.71,438.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 42.57,430.81) --
	( 42.57,435.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.32,431.71) --
	( 40.32,432.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.21,438.08) --
	( 48.21,440.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 43.64,431.69) --
	( 43.64,438.09);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.33,428.03) --
	( 35.33,429.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 36.32,428.82) --
	( 36.32,429.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 41.82,432.93) --
	( 41.82,434.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 86.77,468.35) --
	( 86.77,479.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 47.87,437.92) --
	( 47.87,445.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.72,429.85) --
	( 37.72,430.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 65.79,451.82) --
	( 65.79,454.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 38.12,430.15) --
	( 38.12,431.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 59.30,446.67) --
	( 59.30,448.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 47.93,437.19) --
	( 47.93,438.94);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.19,432.93) --
	( 44.19,435.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 96.98,477.76) --
	( 96.98,485.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 42.10,432.74) --
	( 42.10,461.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.15,431.78) --
	( 40.15,432.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 59.10,446.71) --
	( 59.10,449.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 51.93,441.54) --
	( 51.93,442.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.10,434.53) --
	( 44.10,436.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 41.92,433.02) --
	( 41.92,434.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.35,445.92) --
	( 60.35,451.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.27,427.66) --
	( 44.27,473.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.16,434.68) --
	( 44.16,435.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 74.86,457.86) --
	( 74.86,463.06);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.74,428.92) --
	( 35.74,430.63);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 46.93,431.40) --
	( 46.93,449.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 41.30,431.69) --
	( 41.30,433.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 36.15,428.25) --
	( 36.15,429.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.81,433.11) --
	( 44.81,439.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 45.80,436.40) --
	( 45.80,437.60);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 42.15,433.33) --
	( 42.15,434.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.82,443.24) --
	( 54.82,445.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 41.82,431.59) --
	( 41.82,436.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 38.92,431.04) --
	( 38.92,431.79);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 70.94,457.56) --
	( 70.94,465.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 45.35,435.12) --
	( 45.35,438.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 36.88,428.25) --
	( 36.88,431.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.49,443.61) --
	( 54.49,445.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 36.82,427.28) --
	( 36.82,430.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 43.84,432.89) --
	( 43.84,439.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 46.97,436.45) --
	( 46.97,440.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 39.46,431.48) --
	( 39.46,432.53);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.02,427.55) --
	( 35.02,428.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 42.33,433.76) --
	( 42.33,434.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.57,453.74) --
	( 68.57,458.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 72.58,458.93) --
	( 72.58,461.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 36.03,428.53) --
	( 36.03,429.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.61,429.73) --
	( 37.61,430.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 64.66,451.09) --
	( 64.66,488.18);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] ( 65.50,453.86) circle (  1.49);

\path[fill=fillColor] ( 42.05,434.83) circle (  1.49);

\path[fill=fillColor] ( 66.12,454.14) circle (  1.49);

\path[fill=fillColor] ( 60.24,449.13) circle (  1.49);

\path[fill=fillColor] ( 78.61,463.72) circle (  1.49);

\path[fill=fillColor] ( 52.79,443.26) circle (  1.49);

\path[fill=fillColor] ( 46.14,436.79) circle (  1.49);

\path[fill=fillColor] ( 38.48,430.75) circle (  1.49);

\path[fill=fillColor] ( 34.07,427.19) circle (  1.49);

\path[fill=fillColor] ( 44.14,436.70) circle (  1.49);

\path[fill=fillColor] ( 39.61,431.66) circle (  1.49);

\path[fill=fillColor] ( 47.43,437.65) circle (  1.49);

\path[fill=fillColor] ( 37.33,430.25) circle (  1.49);

\path[fill=fillColor] (128.22,503.09) circle (  1.49);

\path[fill=fillColor] ( 46.70,438.26) circle (  1.49);

\path[fill=fillColor] ( 42.97,434.25) circle (  1.49);

\path[fill=fillColor] ( 62.46,454.66) circle (  1.49);

\path[fill=fillColor] ( 54.87,446.28) circle (  1.49);

\path[fill=fillColor] ( 36.97,429.75) circle (  1.49);

\path[fill=fillColor] ( 38.34,430.81) circle (  1.49);

\path[fill=fillColor] ( 52.56,442.53) circle (  1.49);

\path[fill=fillColor] ( 51.80,435.63) circle (  1.49);

\path[fill=fillColor] ( 60.44,448.71) circle (  1.49);

\path[fill=fillColor] ( 77.29,464.54) circle (  1.49);

\path[fill=fillColor] ( 54.08,444.37) circle (  1.49);

\path[fill=fillColor] ( 44.68,435.98) circle (  1.49);

\path[fill=fillColor] ( 39.95,432.24) circle (  1.49);

\path[fill=fillColor] ( 56.47,446.00) circle (  1.49);

\path[fill=fillColor] ( 76.90,464.60) circle (  1.49);

\path[fill=fillColor] ( 41.51,432.93) circle (  1.49);

\path[fill=fillColor] ( 48.22,440.69) circle (  1.49);

\path[fill=fillColor] ( 74.69,459.51) circle (  1.49);

\path[fill=fillColor] ( 34.27,427.27) circle (  1.49);

\path[fill=fillColor] ( 53.39,442.70) circle (  1.49);

\path[fill=fillColor] ( 41.21,433.19) circle (  1.49);

\path[fill=fillColor] ( 40.34,432.36) circle (  1.49);

\path[fill=fillColor] ( 46.55,439.53) circle (  1.49);

\path[fill=fillColor] ( 38.28,430.45) circle (  1.49);

\path[fill=fillColor] ( 66.51,456.26) circle (  1.49);

\path[fill=fillColor] ( 54.33,443.72) circle (  1.49);

\path[fill=fillColor] ( 69.08,456.42) circle (  1.49);

\path[fill=fillColor] ( 33.72,426.93) circle (  1.49);

\path[fill=fillColor] ( 52.02,442.58) circle (  1.49);

\path[fill=fillColor] ( 47.67,438.43) circle (  1.49);

\path[fill=fillColor] ( 77.25,462.87) circle (  1.49);

\path[fill=fillColor] ( 39.23,431.63) circle (  1.49);

\path[fill=fillColor] ( 42.69,434.04) circle (  1.49);

\path[fill=fillColor] ( 48.60,439.49) circle (  1.49);

\path[fill=fillColor] ( 46.71,437.94) circle (  1.49);

\path[fill=fillColor] ( 42.57,432.95) circle (  1.49);

\path[fill=fillColor] ( 40.32,432.10) circle (  1.49);

\path[fill=fillColor] ( 48.21,439.11) circle (  1.49);

\path[fill=fillColor] ( 43.64,434.87) circle (  1.49);

\path[fill=fillColor] ( 35.33,428.62) circle (  1.49);

\path[fill=fillColor] ( 36.32,429.10) circle (  1.49);

\path[fill=fillColor] ( 41.82,433.57) circle (  1.49);

\path[fill=fillColor] ( 86.77,473.75) circle (  1.49);

\path[fill=fillColor] ( 47.87,441.73) circle (  1.49);

\path[fill=fillColor] ( 37.72,430.25) circle (  1.49);

\path[fill=fillColor] ( 65.79,453.08) circle (  1.49);

\path[fill=fillColor] ( 38.12,430.65) circle (  1.49);

\path[fill=fillColor] ( 59.30,447.69) circle (  1.49);

\path[fill=fillColor] ( 47.93,438.07) circle (  1.49);

\path[fill=fillColor] ( 44.19,434.20) circle (  1.49);

\path[fill=fillColor] ( 96.98,481.57) circle (  1.49);

\path[fill=fillColor] ( 42.10,444.28) circle (  1.49);

\path[fill=fillColor] ( 40.15,432.13) circle (  1.49);

\path[fill=fillColor] ( 59.10,448.27) circle (  1.49);

\path[fill=fillColor] ( 51.93,442.20) circle (  1.49);

\path[fill=fillColor] ( 44.10,435.42) circle (  1.49);

\path[fill=fillColor] ( 41.92,433.67) circle (  1.49);

\path[fill=fillColor] ( 60.35,448.74) circle (  1.49);

\path[fill=fillColor] ( 44.27,443.40) circle (  1.49);

\path[fill=fillColor] ( 44.16,435.17) circle (  1.49);

\path[fill=fillColor] ( 74.86,460.42) circle (  1.49);

\path[fill=fillColor] ( 35.74,429.73) circle (  1.49);

\path[fill=fillColor] ( 46.93,438.90) circle (  1.49);

\path[fill=fillColor] ( 41.30,432.63) circle (  1.49);

\path[fill=fillColor] ( 36.15,428.79) circle (  1.49);

\path[fill=fillColor] ( 44.81,436.15) circle (  1.49);

\path[fill=fillColor] ( 45.80,436.96) circle (  1.49);

\path[fill=fillColor] ( 42.15,433.89) circle (  1.49);

\path[fill=fillColor] ( 54.82,444.12) circle (  1.49);

\path[fill=fillColor] ( 41.82,434.14) circle (  1.49);

\path[fill=fillColor] ( 38.92,431.40) circle (  1.49);

\path[fill=fillColor] ( 70.94,461.51) circle (  1.49);

\path[fill=fillColor] ( 45.35,436.63) circle (  1.49);

\path[fill=fillColor] ( 36.88,429.85) circle (  1.49);

\path[fill=fillColor] ( 54.49,444.39) circle (  1.49);

\path[fill=fillColor] ( 36.82,428.89) circle (  1.49);

\path[fill=fillColor] ( 43.84,435.53) circle (  1.49);

\path[fill=fillColor] ( 46.97,438.48) circle (  1.49);

\path[fill=fillColor] ( 39.46,432.02) circle (  1.49);

\path[fill=fillColor] ( 35.02,427.78) circle (  1.49);

\path[fill=fillColor] ( 42.33,434.30) circle (  1.49);

\path[fill=fillColor] ( 68.57,455.97) circle (  1.49);

\path[fill=fillColor] ( 72.58,460.32) circle (  1.49);

\path[fill=fillColor] ( 36.03,428.89) circle (  1.49);

\path[fill=fillColor] ( 37.61,430.05) circle (  1.49);

\path[fill=fillColor] ( 64.66,467.58) circle (  1.49);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (104.28,547.27) {Coverage: 98\%};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,425.83) -- (151.38,425.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,425.83) -- ( 32.47,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 62.20,425.83) -- ( 62.20,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 91.93,425.83) -- ( 91.93,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.66,425.83) -- (121.66,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.38,425.83) -- (151.38,421.87);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 32.47,411.58) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 62.20,411.58) {0.5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 91.93,411.58) {1.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (121.66,411.58) {1.5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (151.38,411.58) {2.0};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,425.83) -- ( 32.47,525.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,425.83) -- ( 28.51,425.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,450.64) -- ( 28.51,450.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,475.45) -- ( 28.51,475.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,500.26) -- ( 28.51,500.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,525.07) -- ( 28.51,525.07);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,423.56) {0.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,448.37) {0.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,473.18) {1.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,497.99) {1.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,522.80) {2.0};
\end{scope}
\begin{scope}
\path[clip] (192.72,385.44) rectangle (385.44,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.79] at (297.00,559.19) {\bfseries Yule birth rate $\lambda$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (297.00,395.74) {True value};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (199.85,485.76) {Estimated value};
\end{scope}
\begin{scope}
\path[clip] (225.19,425.83) rectangle (368.81,545.69);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (225.19,425.83) --
	(368.81,545.69);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.99,428.72) --
	(232.99,431.90);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.04,432.04) --
	(240.04,441.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.81,427.89) --
	(228.81,430.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.44,428.91) --
	(231.44,432.38);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.85,427.16) --
	(228.85,428.63);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.73,430.21) --
	(232.73,435.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (238.11,432.04) --
	(238.11,439.79);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.85,435.06) --
	(240.85,445.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (288.03,462.02) --
	(288.03,504.58);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.45,431.73) --
	(237.45,438.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (241.16,434.47) --
	(241.16,444.22);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.10,431.55) --
	(240.10,438.10);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (245.37,440.20) --
	(245.37,456.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.76,426.73) --
	(226.76,427.79);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.39,429.79) --
	(231.39,434.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (241.67,434.51) --
	(241.67,444.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.17,427.70) --
	(230.17,431.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.31,429.11) --
	(232.31,432.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.41,441.94) --
	(264.41,460.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (247.04,434.90) --
	(247.04,445.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.93,430.13) --
	(234.93,435.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.37,430.83) --
	(234.37,436.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.76,428.43) --
	(229.76,431.36);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.27,427.87) --
	(231.27,430.36);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (233.99,429.86) --
	(233.99,434.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.44,430.24) --
	(234.44,435.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.82,435.46) --
	(239.82,446.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.16,429.71) --
	(231.16,434.06);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.50,427.32) --
	(228.50,428.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (242.13,435.95) --
	(242.13,447.79);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.68,428.96) --
	(230.68,432.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.86,428.45) --
	(229.86,431.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (309.02,465.14) --
	(309.02,512.34);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.18,429.17) --
	(232.18,432.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (238.93,433.15) --
	(238.93,441.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (242.28,433.05) --
	(242.28,441.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.91,428.98) --
	(231.91,436.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (246.63,436.42) --
	(246.63,448.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.43,428.44) --
	(230.43,431.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.62,429.37) --
	(231.62,433.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.70,427.84) --
	(229.70,430.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (289.02,475.95) --
	(289.02,537.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (233.36,430.61) --
	(233.36,436.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.50,431.04) --
	(235.50,436.94);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.96,427.32) --
	(227.96,428.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (253.25,439.53) --
	(253.25,455.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.30,433.52) --
	(240.30,442.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.47,430.53) --
	(235.47,435.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.84,431.18) --
	(235.84,437.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.15,434.44) --
	(240.15,445.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (244.67,434.85) --
	(244.67,445.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (233.58,430.02) --
	(233.58,434.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.06,431.76) --
	(237.06,439.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (258.46,444.77) --
	(258.46,468.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (262.31,444.97) --
	(262.31,466.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.53,432.75) --
	(237.53,440.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.94,427.60) --
	(228.94,429.54);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (236.30,429.38) --
	(236.30,433.83);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (243.67,437.92) --
	(243.67,451.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.85,427.98) --
	(228.85,430.34);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (247.82,438.99) --
	(247.82,454.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.79,428.14) --
	(230.79,430.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.52,430.02) --
	(232.52,434.70);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.71,432.36) --
	(234.71,439.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.74,426.93) --
	(227.74,428.15);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (246.13,427.89) --
	(246.13,438.03);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.95,433.06) --
	(237.95,441.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.89,428.40) --
	(229.89,431.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.75,428.87) --
	(231.75,432.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.49,431.67) --
	(239.49,438.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.38,431.37) --
	(234.38,437.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.71,428.62) --
	(231.71,431.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (241.28,426.42) --
	(241.28,448.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.45,432.03) --
	(240.45,439.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.76,427.30) --
	(227.76,428.94);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (255.65,442.89) --
	(255.65,463.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (238.61,428.68) --
	(238.61,438.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.31,433.41) --
	(239.31,442.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (257.83,447.95) --
	(257.83,475.70);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.62,431.50) --
	(235.62,439.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.37,431.16) --
	(237.37,437.04);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (241.47,432.40) --
	(241.47,439.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.24,428.93) --
	(232.24,432.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (243.72,433.33) --
	(243.72,443.56);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (241.72,435.31) --
	(241.72,445.94);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.86,427.40) --
	(227.86,429.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.59,430.94) --
	(235.59,436.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (253.44,438.37) --
	(253.44,460.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.18,428.22) --
	(229.18,430.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (255.07,439.11) --
	(255.07,476.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.28,430.29) --
	(234.28,435.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.10,429.99) --
	(235.10,434.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (249.06,436.73) --
	(249.06,449.34);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.87,452.20) --
	(261.87,483.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.19,432.42) --
	(240.19,439.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.99,428.72) --
	(228.99,431.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.48,427.43) --
	(228.48,429.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (276.45,448.04) --
	(276.45,474.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (243.17,439.06) --
	(243.17,453.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.40,427.25) --
	(229.40,429.76);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] (232.99,430.22) circle (  1.49);

\path[fill=fillColor] (240.04,436.82) circle (  1.49);

\path[fill=fillColor] (228.81,429.01) circle (  1.49);

\path[fill=fillColor] (231.44,430.58) circle (  1.49);

\path[fill=fillColor] (228.85,427.88) circle (  1.49);

\path[fill=fillColor] (232.73,432.64) circle (  1.49);

\path[fill=fillColor] (238.11,435.73) circle (  1.49);

\path[fill=fillColor] (240.85,440.38) circle (  1.49);

\path[fill=fillColor] (288.03,481.88) circle (  1.49);

\path[fill=fillColor] (237.45,435.22) circle (  1.49);

\path[fill=fillColor] (241.16,439.33) circle (  1.49);

\path[fill=fillColor] (240.10,434.80) circle (  1.49);

\path[fill=fillColor] (245.37,447.87) circle (  1.49);

\path[fill=fillColor] (226.76,427.24) circle (  1.49);

\path[fill=fillColor] (231.39,431.98) circle (  1.49);

\path[fill=fillColor] (241.67,439.47) circle (  1.49);

\path[fill=fillColor] (230.17,429.38) circle (  1.49);

\path[fill=fillColor] (232.31,430.93) circle (  1.49);

\path[fill=fillColor] (264.41,450.77) circle (  1.49);

\path[fill=fillColor] (247.04,439.76) circle (  1.49);

\path[fill=fillColor] (234.93,432.53) circle (  1.49);

\path[fill=fillColor] (234.37,433.69) circle (  1.49);

\path[fill=fillColor] (229.76,429.87) circle (  1.49);

\path[fill=fillColor] (231.27,429.11) circle (  1.49);

\path[fill=fillColor] (233.99,431.98) circle (  1.49);

\path[fill=fillColor] (234.44,432.76) circle (  1.49);

\path[fill=fillColor] (239.82,440.82) circle (  1.49);

\path[fill=fillColor] (231.16,431.83) circle (  1.49);

\path[fill=fillColor] (228.50,428.11) circle (  1.49);

\path[fill=fillColor] (242.13,441.70) circle (  1.49);

\path[fill=fillColor] (230.68,430.80) circle (  1.49);

\path[fill=fillColor] (229.86,429.88) circle (  1.49);

\path[fill=fillColor] (309.02,488.18) circle (  1.49);

\path[fill=fillColor] (232.18,431.05) circle (  1.49);

\path[fill=fillColor] (238.93,437.20) circle (  1.49);

\path[fill=fillColor] (242.28,437.13) circle (  1.49);

\path[fill=fillColor] (231.91,432.46) circle (  1.49);

\path[fill=fillColor] (246.63,442.08) circle (  1.49);

\path[fill=fillColor] (230.43,429.86) circle (  1.49);

\path[fill=fillColor] (231.62,431.31) circle (  1.49);

\path[fill=fillColor] (229.70,428.95) circle (  1.49);

\path[fill=fillColor] (289.02,505.74) circle (  1.49);

\path[fill=fillColor] (233.36,433.33) circle (  1.49);

\path[fill=fillColor] (235.50,433.93) circle (  1.49);

\path[fill=fillColor] (227.96,428.09) circle (  1.49);

\path[fill=fillColor] (253.25,447.54) circle (  1.49);

\path[fill=fillColor] (240.30,437.74) circle (  1.49);

\path[fill=fillColor] (235.47,432.98) circle (  1.49);

\path[fill=fillColor] (235.84,434.14) circle (  1.49);

\path[fill=fillColor] (240.15,439.70) circle (  1.49);

\path[fill=fillColor] (244.67,439.98) circle (  1.49);

\path[fill=fillColor] (233.58,432.23) circle (  1.49);

\path[fill=fillColor] (237.06,435.42) circle (  1.49);

\path[fill=fillColor] (258.46,455.82) circle (  1.49);

\path[fill=fillColor] (262.31,455.63) circle (  1.49);

\path[fill=fillColor] (237.53,436.63) circle (  1.49);

\path[fill=fillColor] (228.94,428.54) circle (  1.49);

\path[fill=fillColor] (236.30,431.58) circle (  1.49);

\path[fill=fillColor] (243.67,444.78) circle (  1.49);

\path[fill=fillColor] (228.85,429.13) circle (  1.49);

\path[fill=fillColor] (247.82,446.42) circle (  1.49);

\path[fill=fillColor] (230.79,429.38) circle (  1.49);

\path[fill=fillColor] (232.52,432.36) circle (  1.49);

\path[fill=fillColor] (234.71,435.87) circle (  1.49);

\path[fill=fillColor] (227.74,427.53) circle (  1.49);

\path[fill=fillColor] (246.13,432.64) circle (  1.49);

\path[fill=fillColor] (237.95,437.10) circle (  1.49);

\path[fill=fillColor] (229.89,429.69) circle (  1.49);

\path[fill=fillColor] (231.75,430.57) circle (  1.49);

\path[fill=fillColor] (239.49,434.71) circle (  1.49);

\path[fill=fillColor] (234.38,434.52) circle (  1.49);

\path[fill=fillColor] (231.71,430.03) circle (  1.49);

\path[fill=fillColor] (241.28,435.18) circle (  1.49);

\path[fill=fillColor] (240.45,435.37) circle (  1.49);

\path[fill=fillColor] (227.76,428.12) circle (  1.49);

\path[fill=fillColor] (255.65,453.20) circle (  1.49);

\path[fill=fillColor] (238.61,433.36) circle (  1.49);

\path[fill=fillColor] (239.31,437.66) circle (  1.49);

\path[fill=fillColor] (257.83,461.88) circle (  1.49);

\path[fill=fillColor] (235.62,435.12) circle (  1.49);

\path[fill=fillColor] (237.37,433.89) circle (  1.49);

\path[fill=fillColor] (241.47,436.01) circle (  1.49);

\path[fill=fillColor] (232.24,430.65) circle (  1.49);

\path[fill=fillColor] (243.72,438.26) circle (  1.49);

\path[fill=fillColor] (241.72,440.36) circle (  1.49);

\path[fill=fillColor] (227.86,428.22) circle (  1.49);

\path[fill=fillColor] (235.59,433.81) circle (  1.49);

\path[fill=fillColor] (253.44,449.44) circle (  1.49);

\path[fill=fillColor] (229.18,429.48) circle (  1.49);

\path[fill=fillColor] (255.07,456.90) circle (  1.49);

\path[fill=fillColor] (234.28,433.00) circle (  1.49);

\path[fill=fillColor] (235.10,432.38) circle (  1.49);

\path[fill=fillColor] (249.06,443.05) circle (  1.49);

\path[fill=fillColor] (261.87,466.59) circle (  1.49);

\path[fill=fillColor] (240.19,435.95) circle (  1.49);

\path[fill=fillColor] (228.99,430.24) circle (  1.49);

\path[fill=fillColor] (228.48,428.31) circle (  1.49);

\path[fill=fillColor] (276.45,460.85) circle (  1.49);

\path[fill=fillColor] (243.17,446.15) circle (  1.49);

\path[fill=fillColor] (229.40,428.47) circle (  1.49);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (297.00,547.27) {Coverage: 94\%};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,425.83) -- (343.12,425.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,425.83) -- (225.19,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.50,425.83) -- (264.50,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (303.81,425.83) -- (303.81,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (343.12,425.83) -- (343.12,421.87);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (225.19,411.58) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (264.50,411.58) {50};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (303.81,411.58) {100};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (343.12,411.58) {150};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,425.83) -- (225.19,524.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,425.83) -- (221.23,425.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,458.64) -- (221.23,458.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,491.45) -- (221.23,491.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,524.25) -- (221.23,524.25);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,423.56) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,456.37) {50};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,489.17) {100};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,521.98) {150};
\end{scope}
\begin{scope}
\path[clip] (385.44,385.44) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.79] at (489.72,559.19) {\bfseries HKY model $\kappa$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (489.72,395.74) {True value};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (392.57,485.76) {Estimated value};
\end{scope}
\begin{scope}
\path[clip] (417.91,425.83) rectangle (561.53,545.69);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (417.91,425.83) --
	(561.53,545.69);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.04,426.68) --
	(419.04,426.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (465.85,460.96) --
	(465.85,471.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.30,432.39) --
	(426.30,433.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.79,426.53) --
	(418.79,426.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.27,438.16) --
	(433.27,439.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.66,427.92) --
	(420.66,428.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (422.71,429.43) --
	(422.71,429.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.94,430.23) --
	(423.94,431.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (440.52,440.96) --
	(440.52,449.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.39,426.91) --
	(419.39,427.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.71,428.96) --
	(421.71,429.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.33,427.81) --
	(420.33,428.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (424.29,431.01) --
	(424.29,432.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.51,428.65) --
	(421.51,428.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.35,426.93) --
	(419.35,427.09);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.38,427.73) --
	(420.38,428.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (429.03,434.90) --
	(429.03,435.94);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.42,427.92) --
	(420.42,428.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (509.55,485.38) --
	(509.55,528.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.76,427.36) --
	(419.76,427.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.82,427.29) --
	(419.82,427.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.79,428.87) --
	(421.79,429.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (422.40,429.34) --
	(422.40,429.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (430.89,435.82) --
	(430.89,436.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.03,429.89) --
	(423.03,430.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.23,426.07) --
	(418.23,426.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.57,428.63) --
	(421.57,429.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (425.94,432.09) --
	(425.94,432.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.90,426.64) --
	(418.90,426.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.04,428.19) --
	(421.04,428.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.70,428.15) --
	(420.70,428.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.16,425.99) --
	(418.16,426.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.86,429.91) --
	(423.86,431.60);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (422.66,429.47) --
	(422.66,429.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (422.30,429.17) --
	(422.30,429.70);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.51,428.61) --
	(421.51,429.04);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.10,426.75) --
	(419.10,426.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.50,432.38) --
	(426.50,433.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (424.78,431.40) --
	(424.78,431.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.53,427.90) --
	(420.53,428.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (425.26,431.60) --
	(425.26,432.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.95,432.40) --
	(426.95,435.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.96,432.66) --
	(426.96,433.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.68,426.38) --
	(418.68,426.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (450.68,450.55) --
	(450.68,453.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.97,433.34) --
	(427.97,435.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (429.16,434.21) --
	(429.16,435.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.98,427.39) --
	(419.98,427.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.49,427.87) --
	(420.49,428.16);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (451.53,455.32) --
	(451.53,466.32);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.59,427.13) --
	(419.59,427.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (428.32,434.23) --
	(428.32,435.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.15,426.78) --
	(419.15,426.94);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (425.51,430.63) --
	(425.51,431.97);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.23,427.66) --
	(420.23,428.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (425.54,432.04) --
	(425.54,433.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (422.40,429.26) --
	(422.40,429.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.03,427.44) --
	(420.03,427.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.66,427.18) --
	(419.66,427.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.21,426.05) --
	(418.21,426.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.69,426.38) --
	(418.69,426.55);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.84,430.82) --
	(423.84,431.30);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (453.39,455.44) --
	(453.39,461.56);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.53,430.09) --
	(423.53,430.79);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (447.79,449.83) --
	(447.79,452.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.79,426.48) --
	(418.79,426.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.94,427.37) --
	(419.94,427.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.66,426.38) --
	(418.66,426.48);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.16,428.25) --
	(421.16,428.52);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.78,428.01) --
	(420.78,428.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (422.65,429.46) --
	(422.65,429.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.52,428.69) --
	(421.52,428.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (425.13,431.67) --
	(425.13,433.11);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (425.89,432.50) --
	(425.89,433.56);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.82,426.53) --
	(418.82,426.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (434.49,437.00) --
	(434.49,440.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.24,428.42) --
	(421.24,428.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (441.10,442.75) --
	(441.10,446.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (448.30,446.18) --
	(448.30,456.53);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.39,426.19) --
	(418.39,426.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (425.44,431.76) --
	(425.44,432.60);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (459.79,456.64) --
	(459.79,465.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.49,428.75) --
	(421.49,429.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.46,432.74) --
	(426.46,433.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.88,433.60) --
	(427.88,435.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.75,427.29) --
	(419.75,427.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.68,432.34) --
	(426.68,433.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.77,427.98) --
	(420.77,428.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (436.59,441.04) --
	(436.59,442.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.55,428.40) --
	(421.55,429.15);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (435.68,440.67) --
	(435.68,443.09);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.14,427.58) --
	(420.14,427.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.45,433.13) --
	(427.45,434.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (424.23,430.75) --
	(424.23,432.34);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.62,428.98) --
	(421.62,429.44);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.16,429.93) --
	(423.16,430.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.92,429.00) --
	(421.92,429.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (424.95,430.98) --
	(424.95,432.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.34,426.18) --
	(418.34,426.31);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (422.10,429.42) --
	(422.10,429.80);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] (419.04,426.74) circle (  1.49);

\path[fill=fillColor] (465.85,465.89) circle (  1.49);

\path[fill=fillColor] (426.30,432.71) circle (  1.49);

\path[fill=fillColor] (418.79,426.58) circle (  1.49);

\path[fill=fillColor] (433.27,438.84) circle (  1.49);

\path[fill=fillColor] (420.66,428.07) circle (  1.49);

\path[fill=fillColor] (422.71,429.70) circle (  1.49);

\path[fill=fillColor] (423.94,430.63) circle (  1.49);

\path[fill=fillColor] (440.52,445.29) circle (  1.49);

\path[fill=fillColor] (419.39,427.01) circle (  1.49);

\path[fill=fillColor] (421.71,429.24) circle (  1.49);

\path[fill=fillColor] (420.33,427.95) circle (  1.49);

\path[fill=fillColor] (424.29,431.60) circle (  1.49);

\path[fill=fillColor] (421.51,428.78) circle (  1.49);

\path[fill=fillColor] (419.35,427.01) circle (  1.49);

\path[fill=fillColor] (420.38,427.90) circle (  1.49);

\path[fill=fillColor] (429.03,435.41) circle (  1.49);

\path[fill=fillColor] (420.42,428.04) circle (  1.49);

\path[fill=fillColor] (509.55,505.74) circle (  1.49);

\path[fill=fillColor] (419.76,427.50) circle (  1.49);

\path[fill=fillColor] (419.82,427.39) circle (  1.49);

\path[fill=fillColor] (421.79,429.07) circle (  1.49);

\path[fill=fillColor] (422.40,429.52) circle (  1.49);

\path[fill=fillColor] (430.89,436.42) circle (  1.49);

\path[fill=fillColor] (423.03,430.13) circle (  1.49);

\path[fill=fillColor] (418.23,426.10) circle (  1.49);

\path[fill=fillColor] (421.57,428.89) circle (  1.49);

\path[fill=fillColor] (425.94,432.47) circle (  1.49);

\path[fill=fillColor] (418.90,426.70) circle (  1.49);

\path[fill=fillColor] (421.04,428.43) circle (  1.49);

\path[fill=fillColor] (420.70,428.28) circle (  1.49);

\path[fill=fillColor] (418.16,426.02) circle (  1.49);

\path[fill=fillColor] (423.86,430.71) circle (  1.49);

\path[fill=fillColor] (422.66,429.67) circle (  1.49);

\path[fill=fillColor] (422.30,429.44) circle (  1.49);

\path[fill=fillColor] (421.51,428.82) circle (  1.49);

\path[fill=fillColor] (419.10,426.83) circle (  1.49);

\path[fill=fillColor] (426.50,433.01) circle (  1.49);

\path[fill=fillColor] (424.78,431.70) circle (  1.49);

\path[fill=fillColor] (420.53,428.03) circle (  1.49);

\path[fill=fillColor] (425.26,431.87) circle (  1.49);

\path[fill=fillColor] (426.95,434.10) circle (  1.49);

\path[fill=fillColor] (426.96,433.13) circle (  1.49);

\path[fill=fillColor] (418.68,426.43) circle (  1.49);

\path[fill=fillColor] (450.68,452.01) circle (  1.49);

\path[fill=fillColor] (427.97,434.26) circle (  1.49);

\path[fill=fillColor] (429.16,434.96) circle (  1.49);

\path[fill=fillColor] (419.98,427.51) circle (  1.49);

\path[fill=fillColor] (420.49,428.02) circle (  1.49);

\path[fill=fillColor] (451.53,460.82) circle (  1.49);

\path[fill=fillColor] (419.59,427.25) circle (  1.49);

\path[fill=fillColor] (428.32,434.80) circle (  1.49);

\path[fill=fillColor] (419.15,426.86) circle (  1.49);

\path[fill=fillColor] (425.51,431.29) circle (  1.49);

\path[fill=fillColor] (420.23,427.90) circle (  1.49);

\path[fill=fillColor] (425.54,432.52) circle (  1.49);

\path[fill=fillColor] (422.40,429.42) circle (  1.49);

\path[fill=fillColor] (420.03,427.54) circle (  1.49);

\path[fill=fillColor] (419.66,427.32) circle (  1.49);

\path[fill=fillColor] (418.21,426.08) circle (  1.49);

\path[fill=fillColor] (418.69,426.47) circle (  1.49);

\path[fill=fillColor] (423.84,431.05) circle (  1.49);

\path[fill=fillColor] (453.39,458.41) circle (  1.49);

\path[fill=fillColor] (423.53,430.45) circle (  1.49);

\path[fill=fillColor] (447.79,451.13) circle (  1.49);

\path[fill=fillColor] (418.79,426.55) circle (  1.49);

\path[fill=fillColor] (419.94,427.50) circle (  1.49);

\path[fill=fillColor] (418.66,426.43) circle (  1.49);

\path[fill=fillColor] (421.16,428.39) circle (  1.49);

\path[fill=fillColor] (420.78,428.16) circle (  1.49);

\path[fill=fillColor] (422.65,429.73) circle (  1.49);

\path[fill=fillColor] (421.52,428.83) circle (  1.49);

\path[fill=fillColor] (425.13,432.38) circle (  1.49);

\path[fill=fillColor] (425.89,433.03) circle (  1.49);

\path[fill=fillColor] (418.82,426.57) circle (  1.49);

\path[fill=fillColor] (434.49,438.96) circle (  1.49);

\path[fill=fillColor] (421.24,428.61) circle (  1.49);

\path[fill=fillColor] (441.10,444.79) circle (  1.49);

\path[fill=fillColor] (448.30,451.20) circle (  1.49);

\path[fill=fillColor] (418.39,426.23) circle (  1.49);

\path[fill=fillColor] (425.44,432.18) circle (  1.49);

\path[fill=fillColor] (459.79,461.16) circle (  1.49);

\path[fill=fillColor] (421.49,428.91) circle (  1.49);

\path[fill=fillColor] (426.46,433.36) circle (  1.49);

\path[fill=fillColor] (427.88,434.38) circle (  1.49);

\path[fill=fillColor] (419.75,427.37) circle (  1.49);

\path[fill=fillColor] (426.68,432.81) circle (  1.49);

\path[fill=fillColor] (420.77,428.24) circle (  1.49);

\path[fill=fillColor] (436.59,441.94) circle (  1.49);

\path[fill=fillColor] (421.55,428.77) circle (  1.49);

\path[fill=fillColor] (435.68,441.82) circle (  1.49);

\path[fill=fillColor] (420.14,427.69) circle (  1.49);

\path[fill=fillColor] (427.45,433.95) circle (  1.49);

\path[fill=fillColor] (424.23,431.55) circle (  1.49);

\path[fill=fillColor] (421.62,429.21) circle (  1.49);

\path[fill=fillColor] (423.16,430.15) circle (  1.49);

\path[fill=fillColor] (421.92,429.15) circle (  1.49);

\path[fill=fillColor] (424.95,431.72) circle (  1.49);

\path[fill=fillColor] (418.34,426.24) circle (  1.49);

\path[fill=fillColor] (422.10,429.61) circle (  1.49);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (489.72,547.27) {Coverage: 92\%};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,425.83) -- (548.61,425.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,425.83) -- (417.91,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (436.58,425.83) -- (436.58,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (455.25,425.83) -- (455.25,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (473.93,425.83) -- (473.93,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (492.60,425.83) -- (492.60,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (511.27,425.83) -- (511.27,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (529.94,425.83) -- (529.94,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (548.61,425.83) -- (548.61,421.87);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (417.91,411.58) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (436.58,411.58) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (455.25,411.58) {20};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (473.93,411.58) {30};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (492.60,411.58) {40};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (511.27,411.58) {50};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (529.94,411.58) {60};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (548.61,411.58) {70};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,425.83) -- (417.91,534.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,425.83) -- (413.95,425.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,441.41) -- (413.95,441.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,457.00) -- (413.95,457.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,472.58) -- (413.95,472.58);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,488.16) -- (413.95,488.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,503.74) -- (413.95,503.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,519.33) -- (413.95,519.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,534.91) -- (413.95,534.91);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,423.56) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,439.14) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,454.72) {20};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,470.31) {30};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,485.89) {40};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,501.47) {50};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,517.05) {60};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,532.64) {70};
\end{scope}
\begin{scope}
\path[clip] (  0.00,192.72) rectangle (192.72,385.44);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.79] at (104.28,366.47) {\bfseries Nucleotide frequency $f$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (104.28,203.02) {True value};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (  7.13,293.04) {Estimated value};
\end{scope}
\begin{scope}
\path[clip] ( 32.47,233.11) rectangle (176.09,352.97);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] ( 32.47,233.11) --
	(176.09,352.97);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 59.52,254.87) --
	( 59.52,257.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 80.98,272.46) --
	( 80.98,276.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 73.46,265.70) --
	( 73.46,268.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (106.47,294.55) --
	(106.47,298.56);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 93.59,282.37) --
	( 93.59,284.79);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 85.32,276.04) --
	( 85.32,280.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (114.14,300.47) --
	(114.14,305.30);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (114.03,297.85) --
	(114.03,303.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.32,285.17) --
	( 99.32,291.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 85.70,275.49) --
	( 85.70,279.75);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (119.28,299.94) --
	(119.28,305.38);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 74.17,265.60) --
	( 74.17,269.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 86.64,273.68) --
	( 86.64,279.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 76.12,268.46) --
	( 76.12,270.56);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 81.26,271.34) --
	( 81.26,274.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.22,304.51) --
	(121.22,310.06);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.79,254.90) --
	( 60.79,257.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 88.73,278.22) --
	( 88.73,281.70);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (106.97,291.56) --
	(106.97,297.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (105.24,290.64) --
	(105.24,295.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 72.44,264.52) --
	( 72.44,267.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.86,279.95) --
	( 92.86,284.09);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.03,297.32) --
	(112.03,301.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 84.55,274.40) --
	( 84.55,277.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.64,279.36) --
	( 92.64,283.34);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 96.89,285.15) --
	( 96.89,289.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (108.82,294.57) --
	(108.82,300.15);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.57,260.01) --
	( 68.57,263.14);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 98.03,286.07) --
	( 98.03,288.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (104.02,291.50) --
	(104.02,297.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 90.85,280.06) --
	( 90.85,283.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (128.22,309.74) --
	(128.22,313.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.10,280.96) --
	( 95.10,287.47);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 61.15,254.13) --
	( 61.15,256.58);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.84,288.41) --
	(100.84,293.34);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (101.64,287.51) --
	(101.64,292.52);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 81.37,274.60) --
	( 81.37,278.39);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (108.47,295.10) --
	(108.47,300.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 76.02,269.10) --
	( 76.02,272.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.04,284.38) --
	( 95.04,288.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 82.97,273.68) --
	( 82.97,276.60);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.04,276.91) --
	( 89.04,283.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.13,287.34) --
	(100.13,291.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 86.15,276.01) --
	( 86.15,279.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.23,261.05) --
	( 66.23,263.30);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 84.83,274.47) --
	( 84.83,279.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (110.01,297.22) --
	(110.01,302.53);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 72.64,266.48) --
	( 72.64,269.93);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (103.63,288.63) --
	(103.63,293.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.17,265.66) --
	( 75.17,270.40);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.42,304.17) --
	(121.42,309.79);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.69,282.27) --
	( 95.69,286.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 73.56,266.91) --
	( 73.56,270.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (114.69,299.16) --
	(114.69,305.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.50,278.41) --
	( 92.50,284.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (101.37,287.82) --
	(101.37,292.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 86.95,277.19) --
	( 86.95,279.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 77.83,269.76) --
	( 77.83,273.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 86.72,276.88) --
	( 86.72,282.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (113.57,297.73) --
	(113.57,301.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.07,260.17) --
	( 66.07,264.53);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.56,286.72) --
	( 95.56,290.06);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (103.40,288.64) --
	(103.40,292.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 78.68,269.34) --
	( 78.68,273.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.18,283.62) --
	( 95.18,286.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 85.11,275.02) --
	( 85.11,279.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (107.03,292.61) --
	(107.03,297.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 70.85,264.58) --
	( 70.85,267.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 74.58,267.70) --
	( 74.58,270.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 96.56,283.44) --
	( 96.56,288.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.98,280.32) --
	( 89.98,284.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (104.98,292.03) --
	(104.98,295.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.19,266.15) --
	( 75.19,271.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (110.27,295.17) --
	(110.27,300.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 65.48,259.32) --
	( 65.48,261.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 72.91,263.41) --
	( 72.91,268.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 90.11,279.79) --
	( 90.11,284.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 94.00,280.95) --
	( 94.00,285.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (105.13,289.61) --
	(105.13,296.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 84.06,272.90) --
	( 84.06,276.85);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 96.09,286.33) --
	( 96.09,290.74);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.77,276.50) --
	( 89.77,281.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (114.41,298.37) --
	(114.41,302.47);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (103.74,286.31) --
	(103.74,291.71);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.57,296.29) --
	(112.57,301.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 79.47,271.54) --
	( 79.47,274.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 88.02,276.92) --
	( 88.02,280.94);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 74.94,265.50) --
	( 74.94,270.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 76.72,267.62) --
	( 76.72,270.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 81.57,269.12) --
	( 81.57,274.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 71.87,262.79) --
	( 71.87,266.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (110.18,296.09) --
	(110.18,300.46);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 73.41,267.45) --
	( 73.41,272.07);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 85.28,274.95) --
	( 85.28,280.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 86.24,276.17) --
	( 86.24,280.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.02,274.31) --
	( 83.02,277.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 72.89,266.12) --
	( 72.89,268.53);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 93.64,283.42) --
	( 93.64,289.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (103.83,289.09) --
	(103.83,294.79);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 64.27,258.93) --
	( 64.27,261.11);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] ( 59.52,256.08) circle (  1.49);

\path[fill=fillColor] ( 80.98,274.42) circle (  1.49);

\path[fill=fillColor] ( 73.46,267.06) circle (  1.49);

\path[fill=fillColor] (106.47,296.53) circle (  1.49);

\path[fill=fillColor] ( 93.59,283.58) circle (  1.49);

\path[fill=fillColor] ( 85.32,278.22) circle (  1.49);

\path[fill=fillColor] (114.14,302.96) circle (  1.49);

\path[fill=fillColor] (114.03,300.67) circle (  1.49);

\path[fill=fillColor] ( 99.32,288.43) circle (  1.49);

\path[fill=fillColor] ( 85.70,277.63) circle (  1.49);

\path[fill=fillColor] (119.28,302.67) circle (  1.49);

\path[fill=fillColor] ( 74.17,267.38) circle (  1.49);

\path[fill=fillColor] ( 86.64,276.23) circle (  1.49);

\path[fill=fillColor] ( 76.12,269.49) circle (  1.49);

\path[fill=fillColor] ( 81.26,273.01) circle (  1.49);

\path[fill=fillColor] (121.22,307.35) circle (  1.49);

\path[fill=fillColor] ( 60.79,255.95) circle (  1.49);

\path[fill=fillColor] ( 88.73,279.90) circle (  1.49);

\path[fill=fillColor] (106.97,294.75) circle (  1.49);

\path[fill=fillColor] (105.24,293.36) circle (  1.49);

\path[fill=fillColor] ( 72.44,266.10) circle (  1.49);

\path[fill=fillColor] ( 92.86,282.00) circle (  1.49);

\path[fill=fillColor] (112.03,299.31) circle (  1.49);

\path[fill=fillColor] ( 84.55,275.86) circle (  1.49);

\path[fill=fillColor] ( 92.64,281.37) circle (  1.49);

\path[fill=fillColor] ( 96.89,287.26) circle (  1.49);

\path[fill=fillColor] (108.82,297.40) circle (  1.49);

\path[fill=fillColor] ( 68.57,261.61) circle (  1.49);

\path[fill=fillColor] ( 98.03,287.50) circle (  1.49);

\path[fill=fillColor] (104.02,294.29) circle (  1.49);

\path[fill=fillColor] ( 90.85,281.82) circle (  1.49);

\path[fill=fillColor] (128.22,311.66) circle (  1.49);

\path[fill=fillColor] ( 95.10,284.08) circle (  1.49);

\path[fill=fillColor] ( 61.15,255.36) circle (  1.49);

\path[fill=fillColor] (100.84,290.95) circle (  1.49);

\path[fill=fillColor] (101.64,290.02) circle (  1.49);

\path[fill=fillColor] ( 81.37,276.47) circle (  1.49);

\path[fill=fillColor] (108.47,297.83) circle (  1.49);

\path[fill=fillColor] ( 76.02,270.51) circle (  1.49);

\path[fill=fillColor] ( 95.04,286.24) circle (  1.49);

\path[fill=fillColor] ( 82.97,275.11) circle (  1.49);

\path[fill=fillColor] ( 89.04,280.23) circle (  1.49);

\path[fill=fillColor] (100.13,289.52) circle (  1.49);

\path[fill=fillColor] ( 86.15,277.94) circle (  1.49);

\path[fill=fillColor] ( 66.23,262.22) circle (  1.49);

\path[fill=fillColor] ( 84.83,277.21) circle (  1.49);

\path[fill=fillColor] (110.01,300.00) circle (  1.49);

\path[fill=fillColor] ( 72.64,268.11) circle (  1.49);

\path[fill=fillColor] (103.63,290.97) circle (  1.49);

\path[fill=fillColor] ( 75.17,267.96) circle (  1.49);

\path[fill=fillColor] (121.42,307.05) circle (  1.49);

\path[fill=fillColor] ( 95.69,284.22) circle (  1.49);

\path[fill=fillColor] ( 73.56,268.84) circle (  1.49);

\path[fill=fillColor] (114.69,302.29) circle (  1.49);

\path[fill=fillColor] ( 92.50,281.45) circle (  1.49);

\path[fill=fillColor] (101.37,290.10) circle (  1.49);

\path[fill=fillColor] ( 86.95,278.47) circle (  1.49);

\path[fill=fillColor] ( 77.83,271.40) circle (  1.49);

\path[fill=fillColor] ( 86.72,279.64) circle (  1.49);

\path[fill=fillColor] (113.57,299.49) circle (  1.49);

\path[fill=fillColor] ( 66.07,262.34) circle (  1.49);

\path[fill=fillColor] ( 95.56,288.42) circle (  1.49);

\path[fill=fillColor] (103.40,290.82) circle (  1.49);

\path[fill=fillColor] ( 78.68,271.55) circle (  1.49);

\path[fill=fillColor] ( 95.18,284.99) circle (  1.49);

\path[fill=fillColor] ( 85.11,277.09) circle (  1.49);

\path[fill=fillColor] (107.03,295.09) circle (  1.49);

\path[fill=fillColor] ( 70.85,265.93) circle (  1.49);

\path[fill=fillColor] ( 74.58,269.21) circle (  1.49);

\path[fill=fillColor] ( 96.56,285.72) circle (  1.49);

\path[fill=fillColor] ( 89.98,282.42) circle (  1.49);

\path[fill=fillColor] (104.98,293.79) circle (  1.49);

\path[fill=fillColor] ( 75.19,268.66) circle (  1.49);

\path[fill=fillColor] (110.27,297.62) circle (  1.49);

\path[fill=fillColor] ( 65.48,260.37) circle (  1.49);

\path[fill=fillColor] ( 72.91,266.15) circle (  1.49);

\path[fill=fillColor] ( 90.11,282.11) circle (  1.49);

\path[fill=fillColor] ( 94.00,283.18) circle (  1.49);

\path[fill=fillColor] (105.13,292.88) circle (  1.49);

\path[fill=fillColor] ( 84.06,274.85) circle (  1.49);

\path[fill=fillColor] ( 96.09,288.56) circle (  1.49);

\path[fill=fillColor] ( 89.77,278.88) circle (  1.49);

\path[fill=fillColor] (114.41,300.41) circle (  1.49);

\path[fill=fillColor] (103.74,288.94) circle (  1.49);

\path[fill=fillColor] (112.57,298.92) circle (  1.49);

\path[fill=fillColor] ( 79.47,272.79) circle (  1.49);

\path[fill=fillColor] ( 88.02,278.90) circle (  1.49);

\path[fill=fillColor] ( 74.94,267.89) circle (  1.49);

\path[fill=fillColor] ( 76.72,268.95) circle (  1.49);

\path[fill=fillColor] ( 81.57,271.81) circle (  1.49);

\path[fill=fillColor] ( 71.87,264.41) circle (  1.49);

\path[fill=fillColor] (110.18,298.16) circle (  1.49);

\path[fill=fillColor] ( 73.41,269.77) circle (  1.49);

\path[fill=fillColor] ( 85.28,277.79) circle (  1.49);

\path[fill=fillColor] ( 86.24,278.43) circle (  1.49);

\path[fill=fillColor] ( 83.02,276.03) circle (  1.49);

\path[fill=fillColor] ( 72.89,267.31) circle (  1.49);

\path[fill=fillColor] ( 93.64,286.52) circle (  1.49);

\path[fill=fillColor] (103.83,291.88) circle (  1.49);

\path[fill=fillColor] ( 64.27,260.00) circle (  1.49);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (104.28,354.55) {Coverage: 92\%};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,233.11) -- (174.42,233.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,233.11) -- ( 32.47,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 56.13,233.11) -- ( 56.13,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 79.79,233.11) -- ( 79.79,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (103.45,233.11) -- (103.45,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (127.10,233.11) -- (127.10,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (150.76,233.11) -- (150.76,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.42,233.11) -- (174.42,229.15);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 32.47,218.86) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 56.13,218.86) {0.1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 79.79,218.86) {0.2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (103.45,218.86) {0.3};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (127.10,218.86) {0.4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (150.76,218.86) {0.5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (174.42,218.86) {0.6};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,233.11) -- ( 32.47,351.58);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,233.11) -- ( 28.51,233.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,252.86) -- ( 28.51,252.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,272.60) -- ( 28.51,272.60);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,292.34) -- ( 28.51,292.34);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,312.09) -- ( 28.51,312.09);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,331.83) -- ( 28.51,331.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,351.58) -- ( 28.51,351.58);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,230.84) {0.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,250.58) {0.1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,270.33) {0.2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,290.07) {0.3};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,309.82) {0.4};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,329.56) {0.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,349.30) {0.6};
\end{scope}
\begin{scope}
\path[clip] (192.72,192.72) rectangle (385.44,385.44);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.79] at (297.00,366.47) {\bfseries Clock standard deviation $\sigma$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (297.00,203.02) {True value};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (199.85,293.04) {Estimated value};
\end{scope}
\begin{scope}
\path[clip] (225.19,233.11) rectangle (368.81,352.97);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (225.19,233.11) --
	(368.81,352.97);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.20,233.11) --
	(225.20,235.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (252.54,250.68) --
	(252.54,263.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.46,233.11) --
	(225.46,234.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.28,234.67) --
	(230.28,239.27);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.12,233.11) --
	(227.12,236.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.84,233.11) --
	(226.84,234.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.84,241.54) --
	(239.84,249.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.94,234.48) --
	(231.94,240.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.80,233.11) --
	(232.80,242.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (236.96,240.38) --
	(236.96,247.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.47,233.11) --
	(225.47,236.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.15,233.11) --
	(226.15,235.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.67,233.11) --
	(229.67,241.30);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (238.67,241.82) --
	(238.67,249.58);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.42,233.11) --
	(225.42,234.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.75,234.76) --
	(227.75,240.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (257.31,255.18) --
	(257.31,273.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (236.78,238.23) --
	(236.78,243.67);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.11,236.33) --
	(228.11,243.76);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.65,235.35) --
	(231.65,240.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.58,234.14) --
	(231.58,238.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.03,242.62) --
	(239.03,250.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.90,233.11) --
	(227.90,236.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.39,241.09) --
	(237.39,248.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.13,233.11) --
	(227.13,234.94);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.62,236.38) --
	(231.62,240.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.01,239.57) --
	(240.01,246.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.94,233.11) --
	(225.94,235.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.22,233.11) --
	(225.22,234.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.84,235.84) --
	(229.84,242.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.69,242.99) --
	(237.69,250.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.18,233.11) --
	(229.18,237.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.29,233.11) --
	(230.29,238.24);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.16,234.94) --
	(227.16,239.08);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.62,233.11) --
	(225.62,236.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.55,233.11) --
	(226.55,236.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.99,260.46) --
	(264.99,279.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.87,233.11) --
	(227.87,236.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.20,233.11) --
	(226.20,235.27);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.35,233.11) --
	(226.35,234.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.32,233.11) --
	(225.32,234.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.82,233.11) --
	(225.82,241.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.46,233.11) --
	(226.46,235.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,233.11) --
	(225.19,235.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.00,233.11) --
	(226.00,235.94);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (233.67,236.65) --
	(233.67,243.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.46,233.11) --
	(226.46,235.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.04,233.11) --
	(226.04,234.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.50,233.11) --
	(225.50,236.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (244.16,245.02) --
	(244.16,254.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.77,233.11) --
	(225.77,235.34);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.90,233.11) --
	(226.90,235.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.26,243.97) --
	(240.26,252.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.84,240.19) --
	(239.84,249.40);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.58,233.11) --
	(230.58,236.76);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.19,234.25) --
	(230.19,239.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.09,235.39) --
	(229.09,239.70);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (243.99,243.88) --
	(243.99,251.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.40,233.11) --
	(225.40,238.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.33,233.11) --
	(226.33,236.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.07,233.11) --
	(229.07,236.91);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.48,233.91) --
	(231.48,237.57);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.83,233.11) --
	(227.83,237.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.35,237.38) --
	(232.35,242.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.03,233.11) --
	(226.03,235.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (273.27,272.09) --
	(273.27,299.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.19,233.11) --
	(226.19,235.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.02,234.13) --
	(227.02,237.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.62,233.11) --
	(225.62,235.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.07,234.49) --
	(229.07,239.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.11,236.10) --
	(230.11,240.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.03,236.70) --
	(230.03,240.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (310.25,292.90) --
	(310.25,333.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.76,233.11) --
	(226.76,235.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.92,235.75) --
	(231.92,239.20);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (247.47,238.48) --
	(247.47,246.73);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (273.97,265.96) --
	(273.97,289.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.21,237.30) --
	(232.21,242.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (238.52,237.46) --
	(238.52,247.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (245.63,247.33) --
	(245.63,260.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.94,233.11) --
	(226.94,235.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.69,233.11) --
	(226.69,238.49);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,233.11) --
	(225.19,235.30);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (247.76,246.43) --
	(247.76,257.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.18,233.11) --
	(226.18,236.60);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (233.38,238.30) --
	(233.38,242.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.86,239.20) --
	(234.86,244.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (252.26,253.90) --
	(252.26,268.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.26,233.11) --
	(225.26,235.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (280.01,261.06) --
	(280.01,284.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (241.33,244.96) --
	(241.33,255.04);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.61,238.17) --
	(234.61,243.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.28,233.11) --
	(226.28,236.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.30,233.11) --
	(226.30,240.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.37,233.11) --
	(227.37,237.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.20,233.11) --
	(225.20,235.70);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.43,233.11) --
	(229.43,235.87);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.43,233.11) --
	(226.43,237.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.66,233.11) --
	(226.66,236.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (259.60,256.24) --
	(259.60,272.00);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] (225.20,233.77) circle (  1.49);

\path[fill=fillColor] (252.54,256.86) circle (  1.49);

\path[fill=fillColor] (225.46,233.62) circle (  1.49);

\path[fill=fillColor] (230.28,236.84) circle (  1.49);

\path[fill=fillColor] (227.12,234.39) circle (  1.49);

\path[fill=fillColor] (226.84,233.65) circle (  1.49);

\path[fill=fillColor] (239.84,245.22) circle (  1.49);

\path[fill=fillColor] (231.94,237.39) circle (  1.49);

\path[fill=fillColor] (232.80,236.70) circle (  1.49);

\path[fill=fillColor] (236.96,243.86) circle (  1.49);

\path[fill=fillColor] (225.47,234.34) circle (  1.49);

\path[fill=fillColor] (226.15,233.85) circle (  1.49);

\path[fill=fillColor] (229.67,237.30) circle (  1.49);

\path[fill=fillColor] (238.67,245.53) circle (  1.49);

\path[fill=fillColor] (225.42,233.54) circle (  1.49);

\path[fill=fillColor] (227.75,237.73) circle (  1.49);

\path[fill=fillColor] (257.31,263.92) circle (  1.49);

\path[fill=fillColor] (236.78,240.86) circle (  1.49);

\path[fill=fillColor] (228.11,239.75) circle (  1.49);

\path[fill=fillColor] (231.65,237.99) circle (  1.49);

\path[fill=fillColor] (231.58,236.38) circle (  1.49);

\path[fill=fillColor] (239.03,246.25) circle (  1.49);

\path[fill=fillColor] (227.90,234.86) circle (  1.49);

\path[fill=fillColor] (237.39,244.68) circle (  1.49);

\path[fill=fillColor] (227.13,233.68) circle (  1.49);

\path[fill=fillColor] (231.62,238.48) circle (  1.49);

\path[fill=fillColor] (240.01,243.12) circle (  1.49);

\path[fill=fillColor] (225.94,234.01) circle (  1.49);

\path[fill=fillColor] (225.22,233.48) circle (  1.49);

\path[fill=fillColor] (229.84,239.19) circle (  1.49);

\path[fill=fillColor] (237.69,246.76) circle (  1.49);

\path[fill=fillColor] (229.18,235.86) circle (  1.49);

\path[fill=fillColor] (230.29,234.73) circle (  1.49);

\path[fill=fillColor] (227.16,236.96) circle (  1.49);

\path[fill=fillColor] (225.62,234.18) circle (  1.49);

\path[fill=fillColor] (226.55,234.26) circle (  1.49);

\path[fill=fillColor] (264.99,269.25) circle (  1.49);

\path[fill=fillColor] (227.87,234.25) circle (  1.49);

\path[fill=fillColor] (226.20,233.88) circle (  1.49);

\path[fill=fillColor] (226.35,233.67) circle (  1.49);

\path[fill=fillColor] (225.32,233.56) circle (  1.49);

\path[fill=fillColor] (225.82,235.93) circle (  1.49);

\path[fill=fillColor] (226.46,233.99) circle (  1.49);

\path[fill=fillColor] (225.19,233.78) circle (  1.49);

\path[fill=fillColor] (226.00,234.14) circle (  1.49);

\path[fill=fillColor] (233.67,239.87) circle (  1.49);

\path[fill=fillColor] (226.46,233.97) circle (  1.49);

\path[fill=fillColor] (226.04,233.68) circle (  1.49);

\path[fill=fillColor] (225.50,234.37) circle (  1.49);

\path[fill=fillColor] (244.16,249.71) circle (  1.49);

\path[fill=fillColor] (225.77,233.81) circle (  1.49);

\path[fill=fillColor] (226.90,234.06) circle (  1.49);

\path[fill=fillColor] (240.26,248.10) circle (  1.49);

\path[fill=fillColor] (239.84,244.62) circle (  1.49);

\path[fill=fillColor] (230.58,234.25) circle (  1.49);

\path[fill=fillColor] (230.19,236.90) circle (  1.49);

\path[fill=fillColor] (229.09,237.44) circle (  1.49);

\path[fill=fillColor] (243.99,247.69) circle (  1.49);

\path[fill=fillColor] (225.40,235.04) circle (  1.49);

\path[fill=fillColor] (226.33,234.49) circle (  1.49);

\path[fill=fillColor] (229.07,234.35) circle (  1.49);

\path[fill=fillColor] (231.48,235.69) circle (  1.49);

\path[fill=fillColor] (227.83,235.39) circle (  1.49);

\path[fill=fillColor] (232.35,239.75) circle (  1.49);

\path[fill=fillColor] (226.03,234.14) circle (  1.49);

\path[fill=fillColor] (273.27,285.26) circle (  1.49);

\path[fill=fillColor] (226.19,233.85) circle (  1.49);

\path[fill=fillColor] (227.02,235.81) circle (  1.49);

\path[fill=fillColor] (225.62,233.85) circle (  1.49);

\path[fill=fillColor] (229.07,237.09) circle (  1.49);

\path[fill=fillColor] (230.11,238.29) circle (  1.49);

\path[fill=fillColor] (230.03,238.60) circle (  1.49);

\path[fill=fillColor] (310.25,313.02) circle (  1.49);

\path[fill=fillColor] (226.76,233.91) circle (  1.49);

\path[fill=fillColor] (231.92,237.40) circle (  1.49);

\path[fill=fillColor] (247.47,242.53) circle (  1.49);

\path[fill=fillColor] (273.97,277.27) circle (  1.49);

\path[fill=fillColor] (232.21,239.84) circle (  1.49);

\path[fill=fillColor] (238.52,242.32) circle (  1.49);

\path[fill=fillColor] (245.63,253.43) circle (  1.49);

\path[fill=fillColor] (226.94,233.86) circle (  1.49);

\path[fill=fillColor] (226.69,235.88) circle (  1.49);

\path[fill=fillColor] (225.19,233.81) circle (  1.49);

\path[fill=fillColor] (247.76,251.83) circle (  1.49);

\path[fill=fillColor] (226.18,234.41) circle (  1.49);

\path[fill=fillColor] (233.38,240.50) circle (  1.49);

\path[fill=fillColor] (234.86,241.91) circle (  1.49);

\path[fill=fillColor] (252.26,261.14) circle (  1.49);

\path[fill=fillColor] (225.26,233.95) circle (  1.49);

\path[fill=fillColor] (280.01,271.74) circle (  1.49);

\path[fill=fillColor] (241.33,249.71) circle (  1.49);

\path[fill=fillColor] (234.61,240.53) circle (  1.49);

\path[fill=fillColor] (226.28,234.32) circle (  1.49);

\path[fill=fillColor] (226.30,235.76) circle (  1.49);

\path[fill=fillColor] (227.37,235.18) circle (  1.49);

\path[fill=fillColor] (225.20,234.02) circle (  1.49);

\path[fill=fillColor] (229.43,234.28) circle (  1.49);

\path[fill=fillColor] (226.43,234.43) circle (  1.49);

\path[fill=fillColor] (226.66,234.09) circle (  1.49);

\path[fill=fillColor] (259.60,263.79) circle (  1.49);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (297.00,354.55) {Coverage: 94\%};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,233.11) -- (360.93,233.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,233.11) -- (225.19,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (244.58,233.11) -- (244.58,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (263.97,233.11) -- (263.97,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (283.37,233.11) -- (283.37,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (302.76,233.11) -- (302.76,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (322.15,233.11) -- (322.15,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (341.54,233.11) -- (341.54,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (360.93,233.11) -- (360.93,229.15);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (225.19,218.86) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (244.58,218.86) {0.5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (263.97,218.86) {1.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (283.37,218.86) {1.5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (302.76,218.86) {2.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (322.15,218.86) {2.5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (341.54,218.86) {3.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (360.93,218.86) {3.5};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,233.11) -- (225.19,346.40);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,233.11) -- (221.23,233.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,249.30) -- (221.23,249.30);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,265.48) -- (221.23,265.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,281.66) -- (221.23,281.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,297.85) -- (221.23,297.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,314.03) -- (221.23,314.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,330.21) -- (221.23,330.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,346.40) -- (221.23,346.40);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,230.84) {0.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,247.02) {0.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,263.21) {1.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,279.39) {1.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,295.57) {2.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,311.76) {2.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,327.94) {3.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,344.12) {3.5};
\end{scope}
\begin{scope}
\path[clip] (385.44,192.72) rectangle (578.16,385.44);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.79] at (489.72,366.47) {\bfseries Branch rate mean};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (489.72,203.02) {True value};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (392.57,293.04) {Estimated value};
\end{scope}
\begin{scope}
\path[clip] (417.91,233.11) rectangle (561.53,352.97);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (417.91,233.11) --
	(561.53,352.97);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.04,270.31) --
	(463.04,271.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.63,265.99) --
	(474.63,289.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.10,270.45) --
	(463.10,271.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.95,268.74) --
	(462.95,272.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.00,270.01) --
	(463.00,271.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.23,270.45) --
	(463.23,271.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (465.19,267.32) --
	(465.19,278.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.88,269.09) --
	(462.88,272.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.18,268.19) --
	(462.18,272.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.24,265.35) --
	(462.24,274.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.05,269.88) --
	(463.05,271.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.06,270.22) --
	(463.06,271.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.81,268.94) --
	(463.81,272.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.19,265.12) --
	(462.19,274.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.01,270.48) --
	(463.01,271.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.16,268.90) --
	(463.16,273.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (465.32,258.61) --
	(465.32,286.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (465.35,267.57) --
	(465.35,273.79);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.88,267.60) --
	(463.88,272.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.38,268.43) --
	(463.38,272.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.39,269.10) --
	(462.39,272.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (459.65,265.76) --
	(459.65,276.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.78,269.84) --
	(462.78,271.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (466.68,265.65) --
	(466.68,275.44);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.80,270.42) --
	(463.80,271.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (465.46,268.55) --
	(465.46,272.73);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (465.44,267.65) --
	(465.44,276.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.29,270.15) --
	(463.29,271.40);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.04,270.50) --
	(463.04,271.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.92,268.48) --
	(462.92,273.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.28,264.21) --
	(462.28,273.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.18,269.62) --
	(462.18,272.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.54,269.68) --
	(462.54,271.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.75,269.44) --
	(462.75,273.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.95,270.12) --
	(462.95,271.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.77,270.02) --
	(462.77,271.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (468.80,254.45) --
	(468.80,283.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.75,269.89) --
	(462.75,271.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.09,270.32) --
	(463.09,271.35);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.63,270.47) --
	(462.63,271.15);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.05,270.43) --
	(463.05,271.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.82,268.80) --
	(462.82,272.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.43,270.02) --
	(463.43,271.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.04,270.28) --
	(463.04,271.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.17,270.13) --
	(463.17,271.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.92,267.63) --
	(461.92,273.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.13,270.18) --
	(463.13,271.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.82,270.37) --
	(462.82,271.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.93,270.07) --
	(462.93,271.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (458.97,262.01) --
	(458.97,274.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.06,270.28) --
	(463.06,271.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.82,270.25) --
	(462.82,271.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (459.76,264.65) --
	(459.76,275.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (467.55,266.02) --
	(467.55,276.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.27,269.86) --
	(463.27,271.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.77,269.30) --
	(462.77,272.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.17,269.01) --
	(463.17,272.74);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (473.83,264.90) --
	(473.83,275.74);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.06,269.45) --
	(463.06,271.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.71,269.83) --
	(462.71,271.34);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.25,269.92) --
	(463.25,271.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.84,269.89) --
	(463.84,272.04);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.88,269.95) --
	(462.88,272.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.53,267.45) --
	(461.53,272.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.79,270.27) --
	(462.79,271.43);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (513.66,245.32) --
	(513.66,290.35);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.17,270.26) --
	(463.17,271.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.15,269.59) --
	(463.15,271.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.91,270.34) --
	(462.91,271.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.65,269.11) --
	(463.65,272.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.36,268.91) --
	(463.36,272.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.12,268.79) --
	(463.12,273.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.54,234.11) --
	(438.54,270.40);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.48,270.29) --
	(462.48,271.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.88,268.62) --
	(462.88,271.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.80,267.87) --
	(463.80,276.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (457.61,247.98) --
	(457.61,282.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.83,267.91) --
	(463.83,272.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (459.14,265.97) --
	(459.14,274.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.79,263.33) --
	(463.79,280.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.59,270.28) --
	(463.59,271.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.90,269.37) --
	(462.90,272.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.04,270.33) --
	(463.04,271.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (460.71,262.95) --
	(460.71,278.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.21,269.96) --
	(463.21,271.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (465.07,267.10) --
	(465.07,272.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.70,266.15) --
	(461.70,272.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (471.39,260.59) --
	(471.39,286.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.04,270.17) --
	(463.04,271.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (453.60,250.44) --
	(453.60,283.34);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (467.58,265.11) --
	(467.58,278.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.40,267.47) --
	(464.40,274.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.15,269.84) --
	(463.15,271.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.87,269.04) --
	(462.87,272.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.62,269.47) --
	(462.62,271.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.04,270.08) --
	(463.04,271.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.51,270.17) --
	(463.51,271.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.92,269.85) --
	(462.92,271.60);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.13,270.03) --
	(463.13,271.29);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.56,258.52) --
	(483.56,284.78);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] (463.04,270.80) circle (  1.49);

\path[fill=fillColor] (474.63,278.14) circle (  1.49);

\path[fill=fillColor] (463.10,270.77) circle (  1.49);

\path[fill=fillColor] (462.95,270.53) circle (  1.49);

\path[fill=fillColor] (463.00,270.76) circle (  1.49);

\path[fill=fillColor] (463.23,270.79) circle (  1.49);

\path[fill=fillColor] (465.19,272.89) circle (  1.49);

\path[fill=fillColor] (462.88,270.78) circle (  1.49);

\path[fill=fillColor] (462.18,270.50) circle (  1.49);

\path[fill=fillColor] (462.24,269.80) circle (  1.49);

\path[fill=fillColor] (463.05,270.73) circle (  1.49);

\path[fill=fillColor] (463.06,270.76) circle (  1.49);

\path[fill=fillColor] (463.81,270.89) circle (  1.49);

\path[fill=fillColor] (462.19,269.92) circle (  1.49);

\path[fill=fillColor] (463.01,270.78) circle (  1.49);

\path[fill=fillColor] (463.16,270.95) circle (  1.49);

\path[fill=fillColor] (465.32,272.17) circle (  1.49);

\path[fill=fillColor] (465.35,270.68) circle (  1.49);

\path[fill=fillColor] (463.88,270.20) circle (  1.49);

\path[fill=fillColor] (463.38,270.47) circle (  1.49);

\path[fill=fillColor] (462.39,270.61) circle (  1.49);

\path[fill=fillColor] (459.65,271.15) circle (  1.49);

\path[fill=fillColor] (462.78,270.76) circle (  1.49);

\path[fill=fillColor] (466.68,270.41) circle (  1.49);

\path[fill=fillColor] (463.80,270.79) circle (  1.49);

\path[fill=fillColor] (465.46,270.63) circle (  1.49);

\path[fill=fillColor] (465.44,271.75) circle (  1.49);

\path[fill=fillColor] (463.29,270.79) circle (  1.49);

\path[fill=fillColor] (463.04,270.78) circle (  1.49);

\path[fill=fillColor] (462.92,270.87) circle (  1.49);

\path[fill=fillColor] (462.28,269.03) circle (  1.49);

\path[fill=fillColor] (462.18,271.00) circle (  1.49);

\path[fill=fillColor] (462.54,270.75) circle (  1.49);

\path[fill=fillColor] (462.75,271.15) circle (  1.49);

\path[fill=fillColor] (462.95,270.78) circle (  1.49);

\path[fill=fillColor] (462.77,270.73) circle (  1.49);

\path[fill=fillColor] (468.80,268.62) circle (  1.49);

\path[fill=fillColor] (462.75,270.72) circle (  1.49);

\path[fill=fillColor] (463.09,270.79) circle (  1.49);

\path[fill=fillColor] (462.63,270.79) circle (  1.49);

\path[fill=fillColor] (463.05,270.76) circle (  1.49);

\path[fill=fillColor] (462.82,270.70) circle (  1.49);

\path[fill=fillColor] (463.43,270.75) circle (  1.49);

\path[fill=fillColor] (463.04,270.75) circle (  1.49);

\path[fill=fillColor] (463.17,270.75) circle (  1.49);

\path[fill=fillColor] (461.92,270.63) circle (  1.49);

\path[fill=fillColor] (463.13,270.77) circle (  1.49);

\path[fill=fillColor] (462.82,270.77) circle (  1.49);

\path[fill=fillColor] (462.93,270.81) circle (  1.49);

\path[fill=fillColor] (458.97,268.35) circle (  1.49);

\path[fill=fillColor] (463.06,270.77) circle (  1.49);

\path[fill=fillColor] (462.82,270.81) circle (  1.49);

\path[fill=fillColor] (459.76,270.23) circle (  1.49);

\path[fill=fillColor] (467.55,271.17) circle (  1.49);

\path[fill=fillColor] (463.27,270.72) circle (  1.49);

\path[fill=fillColor] (462.77,270.95) circle (  1.49);

\path[fill=fillColor] (463.17,270.85) circle (  1.49);

\path[fill=fillColor] (473.83,270.44) circle (  1.49);

\path[fill=fillColor] (463.06,270.70) circle (  1.49);

\path[fill=fillColor] (462.71,270.66) circle (  1.49);

\path[fill=fillColor] (463.25,270.78) circle (  1.49);

\path[fill=fillColor] (463.84,270.95) circle (  1.49);

\path[fill=fillColor] (462.88,271.02) circle (  1.49);

\path[fill=fillColor] (461.53,270.19) circle (  1.49);

\path[fill=fillColor] (462.79,270.80) circle (  1.49);

\path[fill=fillColor] (513.66,267.09) circle (  1.49);

\path[fill=fillColor] (463.17,270.76) circle (  1.49);

\path[fill=fillColor] (463.15,270.76) circle (  1.49);

\path[fill=fillColor] (462.91,270.77) circle (  1.49);

\path[fill=fillColor] (463.65,270.84) circle (  1.49);

\path[fill=fillColor] (463.36,270.88) circle (  1.49);

\path[fill=fillColor] (463.12,270.98) circle (  1.49);

\path[fill=fillColor] (438.54,248.54) circle (  1.49);

\path[fill=fillColor] (462.48,270.78) circle (  1.49);

\path[fill=fillColor] (462.88,270.28) circle (  1.49);

\path[fill=fillColor] (463.80,271.81) circle (  1.49);

\path[fill=fillColor] (457.61,265.47) circle (  1.49);

\path[fill=fillColor] (463.83,270.47) circle (  1.49);

\path[fill=fillColor] (459.14,270.15) circle (  1.49);

\path[fill=fillColor] (463.79,271.75) circle (  1.49);

\path[fill=fillColor] (463.59,270.77) circle (  1.49);

\path[fill=fillColor] (462.90,270.72) circle (  1.49);

\path[fill=fillColor] (463.04,270.79) circle (  1.49);

\path[fill=fillColor] (460.71,270.63) circle (  1.49);

\path[fill=fillColor] (463.21,270.75) circle (  1.49);

\path[fill=fillColor] (465.07,269.90) circle (  1.49);

\path[fill=fillColor] (461.70,269.36) circle (  1.49);

\path[fill=fillColor] (471.39,273.40) circle (  1.49);

\path[fill=fillColor] (463.04,270.73) circle (  1.49);

\path[fill=fillColor] (453.60,266.85) circle (  1.49);

\path[fill=fillColor] (467.58,271.90) circle (  1.49);

\path[fill=fillColor] (464.40,270.82) circle (  1.49);

\path[fill=fillColor] (463.15,270.73) circle (  1.49);

\path[fill=fillColor] (462.87,270.68) circle (  1.49);

\path[fill=fillColor] (462.62,270.68) circle (  1.49);

\path[fill=fillColor] (463.04,270.76) circle (  1.49);

\path[fill=fillColor] (463.51,270.78) circle (  1.49);

\path[fill=fillColor] (462.92,270.77) circle (  1.49);

\path[fill=fillColor] (463.13,270.73) circle (  1.49);

\path[fill=fillColor] (483.56,272.10) circle (  1.49);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (489.72,354.55) {Coverage: 94\%};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,233.11) -- (553.30,233.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,233.11) -- (417.91,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (440.48,233.11) -- (440.48,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.04,233.11) -- (463.04,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.61,233.11) -- (485.61,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (508.17,233.11) -- (508.17,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (530.74,233.11) -- (530.74,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (553.30,233.11) -- (553.30,229.15);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (417.91,218.86) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (440.48,218.86) {0.5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (463.04,218.86) {1.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (485.61,218.86) {1.5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (508.17,218.86) {2.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (530.74,218.86) {2.5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (553.30,218.86) {3.0};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,233.11) -- (417.91,346.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,233.11) -- (413.95,233.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,251.94) -- (413.95,251.94);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,270.78) -- (413.95,270.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,289.61) -- (413.95,289.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,308.44) -- (413.95,308.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,327.27) -- (413.95,327.27);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,346.10) -- (413.95,346.10);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,230.84) {0.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,249.67) {0.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,268.50) {1.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,287.33) {1.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,306.17) {2.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,325.00) {2.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,343.83) {3.0};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (192.72,192.72);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.79] at (104.28,173.75) {\bfseries Branch rate variance};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (104.28, 10.30) {True value};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (  7.13,100.32) {Estimated value};
\end{scope}
\begin{scope}
\path[clip] ( 32.47, 40.39) rectangle (176.09,160.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] ( 32.47, 40.39) --
	(176.09,160.25);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.19, 41.56) --
	( 37.19, 46.27);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.40);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.55, 40.39) --
	( 32.55, 40.49);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.40);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.08, 40.63) --
	( 33.08, 41.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.57, 40.39) --
	( 32.57, 40.53);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.61, 40.39) --
	( 32.61, 40.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.95, 40.57) --
	( 32.95, 41.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.53, 40.39) --
	( 32.53, 40.60);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.93, 40.65) --
	( 32.93, 41.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.40);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.49, 40.39) --
	( 32.49, 40.56);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 36.68, 41.26) --
	( 36.68, 50.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.82, 40.48) --
	( 32.82, 40.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.50, 40.41) --
	( 32.50, 40.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.59, 40.40) --
	( 32.59, 40.57);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.58, 40.39) --
	( 32.58, 40.48);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.14, 40.69) --
	( 33.14, 41.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.49, 40.39) --
	( 32.49, 40.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.98, 40.60) --
	( 32.98, 41.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.40);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.60, 40.43) --
	( 32.60, 40.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.04, 40.53) --
	( 33.04, 41.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.40);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.53, 40.39) --
	( 32.53, 40.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.03, 40.71) --
	( 33.03, 41.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.51, 40.39) --
	( 32.51, 40.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.54, 40.39) --
	( 32.54, 40.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.40) --
	( 32.48, 40.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.58, 41.31) --
	( 35.58, 52.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.49, 40.39) --
	( 32.49, 40.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.40);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.40);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.64, 40.42) --
	( 32.64, 40.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.40);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.63, 40.84) --
	( 33.63, 42.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.04, 40.75) --
	( 33.04, 41.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.97, 40.54) --
	( 32.97, 41.26);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.54, 40.39) --
	( 32.54, 40.44);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.53, 40.39) --
	( 32.53, 40.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.52, 40.41) --
	( 32.52, 40.52);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 34.10, 40.78) --
	( 34.10, 41.55);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.50, 40.39) --
	( 32.50, 40.44);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.56, 40.39) --
	( 32.56, 40.44);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.49, 40.39) --
	( 32.49, 40.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.59, 40.45) --
	( 32.59, 40.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.42);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (128.22, 40.64) --
	(128.22, 78.11);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.51, 40.39) --
	( 32.51, 40.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.55, 40.42) --
	( 32.55, 40.56);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.53, 40.44) --
	( 32.53, 40.56);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 56.52, 40.39) --
	( 56.52,128.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.58, 40.42) --
	( 32.58, 40.50);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.74, 40.49) --
	( 33.74, 41.00);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.75, 41.16) --
	( 52.75, 87.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.64, 40.44) --
	( 32.64, 40.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.02, 40.44) --
	( 33.02, 41.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.45, 40.98) --
	( 33.45, 43.09);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.62, 40.97) --
	( 33.62, 42.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.74, 40.49) --
	( 32.74, 40.69);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.70, 40.52) --
	( 32.70, 40.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 46.82, 41.89) --
	( 46.82, 55.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 38.01, 41.33) --
	( 38.01, 70.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.51, 40.86) --
	( 33.51, 42.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.68, 40.49) --
	( 32.68, 40.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.56);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.49, 40.39) --
	( 32.49, 40.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.41);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.50, 40.39) --
	( 32.50, 40.42);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.42);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 47.89, 41.71) --
	( 47.89, 50.78);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] ( 32.47, 40.39) circle (  1.49);

\path[fill=fillColor] ( 37.19, 43.69) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.39) circle (  1.49);

\path[fill=fillColor] ( 32.55, 40.44) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.39) circle (  1.49);

\path[fill=fillColor] ( 33.08, 40.91) circle (  1.49);

\path[fill=fillColor] ( 32.57, 40.46) circle (  1.49);

\path[fill=fillColor] ( 32.61, 40.46) circle (  1.49);

\path[fill=fillColor] ( 32.95, 40.80) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.53, 40.47) circle (  1.49);

\path[fill=fillColor] ( 32.93, 40.95) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.39) circle (  1.49);

\path[fill=fillColor] ( 32.49, 40.47) circle (  1.49);

\path[fill=fillColor] ( 36.68, 44.68) circle (  1.49);

\path[fill=fillColor] ( 32.82, 40.59) circle (  1.49);

\path[fill=fillColor] ( 32.50, 40.55) circle (  1.49);

\path[fill=fillColor] ( 32.59, 40.48) circle (  1.49);

\path[fill=fillColor] ( 32.58, 40.43) circle (  1.49);

\path[fill=fillColor] ( 33.14, 40.98) circle (  1.49);

\path[fill=fillColor] ( 32.49, 40.41) circle (  1.49);

\path[fill=fillColor] ( 32.98, 40.86) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.39) circle (  1.49);

\path[fill=fillColor] ( 32.60, 40.49) circle (  1.49);

\path[fill=fillColor] ( 33.04, 40.74) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.39) circle (  1.49);

\path[fill=fillColor] ( 32.53, 40.52) circle (  1.49);

\path[fill=fillColor] ( 33.03, 41.02) circle (  1.49);

\path[fill=fillColor] ( 32.51, 40.42) circle (  1.49);

\path[fill=fillColor] ( 32.54, 40.41) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.44) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.40) circle (  1.49);

\path[fill=fillColor] ( 35.58, 45.96) circle (  1.49);

\path[fill=fillColor] ( 32.49, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.39) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.39) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.44) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.64, 40.55) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.39) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 33.63, 41.42) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.40) circle (  1.49);

\path[fill=fillColor] ( 33.04, 41.14) circle (  1.49);

\path[fill=fillColor] ( 32.97, 40.86) circle (  1.49);

\path[fill=fillColor] ( 32.54, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.53, 40.44) circle (  1.49);

\path[fill=fillColor] ( 32.52, 40.46) circle (  1.49);

\path[fill=fillColor] ( 34.10, 41.12) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.41) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.50, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.56, 40.42) circle (  1.49);

\path[fill=fillColor] ( 32.49, 40.41) circle (  1.49);

\path[fill=fillColor] ( 32.59, 40.54) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] (128.22, 53.78) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.42) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.51, 40.45) circle (  1.49);

\path[fill=fillColor] ( 32.55, 40.48) circle (  1.49);

\path[fill=fillColor] ( 32.53, 40.49) circle (  1.49);

\path[fill=fillColor] ( 56.52, 74.10) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.58, 40.45) circle (  1.49);

\path[fill=fillColor] ( 33.74, 40.72) circle (  1.49);

\path[fill=fillColor] ( 52.75, 56.50) circle (  1.49);

\path[fill=fillColor] ( 32.64, 40.55) circle (  1.49);

\path[fill=fillColor] ( 33.02, 40.70) circle (  1.49);

\path[fill=fillColor] ( 33.45, 41.85) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.42) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 33.62, 41.78) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.74, 40.58) circle (  1.49);

\path[fill=fillColor] ( 32.70, 40.66) circle (  1.49);

\path[fill=fillColor] ( 46.82, 47.45) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 38.01, 51.63) circle (  1.49);

\path[fill=fillColor] ( 33.51, 41.40) circle (  1.49);

\path[fill=fillColor] ( 32.68, 40.59) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.43) circle (  1.49);

\path[fill=fillColor] ( 32.49, 40.41) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.50, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.40) circle (  1.49);

\path[fill=fillColor] ( 47.89, 45.38) circle (  1.49);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (104.28,161.83) {Coverage: 92\%};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) -- (159.11, 40.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) -- ( 32.47, 36.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 53.58, 40.39) -- ( 53.58, 36.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 74.68, 40.39) -- ( 74.68, 36.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.79, 40.39) -- ( 95.79, 36.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (116.90, 40.39) -- (116.90, 36.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.00, 40.39) -- (138.00, 36.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.11, 40.39) -- (159.11, 36.43);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 32.47, 26.14) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 53.58, 26.14) {5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 74.68, 26.14) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 95.79, 26.14) {15};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (116.90, 26.14) {20};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (138.00, 26.14) {25};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (159.11, 26.14) {30};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) -- ( 32.47,146.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) -- ( 28.51, 40.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 58.01) -- ( 28.51, 58.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 75.62) -- ( 28.51, 75.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 93.23) -- ( 28.51, 93.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,110.85) -- ( 28.51,110.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,128.46) -- ( 28.51,128.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,146.08) -- ( 28.51,146.08);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55, 38.12) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55, 55.73) {5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55, 73.35) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55, 90.96) {15};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,108.58) {20};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,126.19) {25};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,143.80) {30};
\end{scope}
\end{tikzpicture}

\end{document}

### 2020-09-01 RatesWCSS/WCSS_cat_adaptive.tex
complete draft

% Created by tikzDevice version 0.12.3.1 on 2020-09-01 10:42:19
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (578.16,578.16);
\begin{scope}
\path[clip] (  0.00,385.44) rectangle (192.72,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.79] at (104.28,559.19) {\bfseries Tree height $h$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (104.28,395.74) {True value};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (  7.13,485.76) {Estimated value};
\end{scope}
\begin{scope}
\path[clip] ( 32.47,425.83) rectangle (176.09,545.69);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] ( 32.47,425.83) --
	(176.09,545.69);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 62.33,450.31) --
	( 62.33,452.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 41.13,431.81) --
	( 41.13,437.34);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 62.89,450.33) --
	( 62.89,452.70);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 57.58,445.50) --
	( 57.58,450.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 74.19,457.72) --
	( 74.19,462.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.84,440.45) --
	( 50.84,442.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.83,433.64) --
	( 44.83,439.58);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.91,430.04) --
	( 37.91,430.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.92,426.94) --
	( 33.92,427.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 43.02,433.88) --
	( 43.02,436.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 38.93,430.96) --
	( 38.93,432.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 46.00,436.10) --
	( 46.00,437.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 36.87,428.91) --
	( 36.87,429.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (119.03,484.29) --
	(119.03,529.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 45.34,436.05) --
	( 45.34,437.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 41.96,433.35) --
	( 41.96,434.53);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 59.58,439.80) --
	( 59.58,457.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.72,440.80) --
	( 52.72,447.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 36.54,428.92) --
	( 36.54,429.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.77,429.68) --
	( 37.77,430.58);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.63,439.54) --
	( 50.63,443.04);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.95,434.64) --
	( 49.95,440.19);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 57.75,445.13) --
	( 57.75,447.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 72.99,452.30) --
	( 72.99,464.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.01,440.84) --
	( 52.01,442.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 43.50,434.78) --
	( 43.50,436.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 39.23,430.05) --
	( 39.23,432.93);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.17,442.44) --
	( 54.17,445.51);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 72.64,459.66) --
	( 72.64,463.13);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.64,431.59) --
	( 40.64,433.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 46.71,436.56) --
	( 46.71,440.58);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 70.64,456.10) --
	( 70.64,462.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 34.10,427.08) --
	( 34.10,427.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 51.38,440.59) --
	( 51.38,443.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.37,432.08) --
	( 40.37,432.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 39.58,431.60) --
	( 39.58,432.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 45.20,431.96) --
	( 45.20,441.27);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.72,430.12) --
	( 37.72,431.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 63.25,450.86) --
	( 63.25,454.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.23,441.83) --
	( 52.23,443.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 65.57,451.95) --
	( 65.57,454.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.60,426.56) --
	( 33.60,426.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.15,438.74) --
	( 50.15,440.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 46.22,436.72) --
	( 46.22,437.90);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 72.95,459.87) --
	( 72.95,466.23);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 38.58,429.89) --
	( 38.58,430.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 41.71,432.91) --
	( 41.71,434.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 47.05,437.56) --
	( 47.05,439.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 45.34,435.60) --
	( 45.34,436.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 41.60,430.55) --
	( 41.60,434.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 39.57,431.62) --
	( 39.57,432.45);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 46.70,436.12) --
	( 46.70,437.61);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 42.57,431.85) --
	( 42.57,437.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.05,427.39) --
	( 35.05,428.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.95,428.59) --
	( 35.95,429.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.92,432.28) --
	( 40.92,433.34);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 81.56,460.81) --
	( 81.56,466.35);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 46.39,433.91) --
	( 46.39,438.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.22,429.64) --
	( 37.22,430.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 62.59,450.42) --
	( 62.59,453.57);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.58,428.98) --
	( 37.58,429.91);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 56.72,444.02) --
	( 56.72,447.09);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 46.45,437.13) --
	( 46.45,438.53);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 43.06,432.61) --
	( 43.06,434.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 90.79,471.66) --
	( 90.79,477.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 41.18,429.17) --
	( 41.18,434.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 39.41,431.38) --
	( 39.41,432.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 56.55,444.55) --
	( 56.55,446.34);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.06,440.09) --
	( 50.06,441.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 42.99,434.08) --
	( 42.99,434.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 41.01,432.74) --
	( 41.01,434.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 57.68,444.46) --
	( 57.68,447.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 43.14,429.51) --
	( 43.14,439.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 43.04,434.06) --
	( 43.04,434.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 70.80,453.73) --
	( 70.80,458.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.42,427.88) --
	( 35.42,429.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 45.54,432.36) --
	( 45.54,445.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.45,431.81) --
	( 40.45,433.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.80,428.09) --
	( 35.80,429.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 43.63,432.90) --
	( 43.63,440.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.52,435.21) --
	( 44.52,436.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 41.22,432.92) --
	( 41.22,433.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.67,442.21) --
	( 52.67,443.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.92,431.08) --
	( 40.92,434.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 38.30,430.49) --
	( 38.30,431.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 67.25,453.02) --
	( 67.25,459.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.11,434.00) --
	( 44.11,438.60);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 36.46,428.16) --
	( 36.46,431.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.38,442.33) --
	( 52.38,443.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 36.40,428.08) --
	( 36.40,435.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 42.74,431.95) --
	( 42.74,436.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 45.58,435.35) --
	( 45.58,438.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 38.79,430.81) --
	( 38.79,431.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 34.77,427.61) --
	( 34.77,428.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 41.38,432.62) --
	( 41.38,433.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 65.11,451.63) --
	( 65.11,455.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.73,454.66) --
	( 68.73,459.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.68,427.95) --
	( 35.68,428.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.11,429.41) --
	( 37.11,430.02);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 61.57,452.67) --
	( 61.57,509.88);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] ( 62.33,451.56) circle (  1.49);

\path[fill=fillColor] ( 41.13,434.39) circle (  1.49);

\path[fill=fillColor] ( 62.89,451.49) circle (  1.49);

\path[fill=fillColor] ( 57.58,447.80) circle (  1.49);

\path[fill=fillColor] ( 74.19,459.87) circle (  1.49);

\path[fill=fillColor] ( 50.84,441.25) circle (  1.49);

\path[fill=fillColor] ( 44.83,436.30) circle (  1.49);

\path[fill=fillColor] ( 37.91,430.49) circle (  1.49);

\path[fill=fillColor] ( 33.92,427.17) circle (  1.49);

\path[fill=fillColor] ( 43.02,435.33) circle (  1.49);

\path[fill=fillColor] ( 38.93,431.52) circle (  1.49);

\path[fill=fillColor] ( 46.00,436.85) circle (  1.49);

\path[fill=fillColor] ( 36.87,429.38) circle (  1.49);

\path[fill=fillColor] (119.03,505.74) circle (  1.49);

\path[fill=fillColor] ( 45.34,436.56) circle (  1.49);

\path[fill=fillColor] ( 41.96,433.93) circle (  1.49);

\path[fill=fillColor] ( 59.58,447.71) circle (  1.49);

\path[fill=fillColor] ( 52.72,443.85) circle (  1.49);

\path[fill=fillColor] ( 36.54,429.25) circle (  1.49);

\path[fill=fillColor] ( 37.77,430.12) circle (  1.49);

\path[fill=fillColor] ( 50.63,441.23) circle (  1.49);

\path[fill=fillColor] ( 49.95,437.25) circle (  1.49);

\path[fill=fillColor] ( 57.75,446.19) circle (  1.49);

\path[fill=fillColor] ( 72.99,458.25) circle (  1.49);

\path[fill=fillColor] ( 52.01,441.87) circle (  1.49);

\path[fill=fillColor] ( 43.50,435.62) circle (  1.49);

\path[fill=fillColor] ( 39.23,431.36) circle (  1.49);

\path[fill=fillColor] ( 54.17,444.00) circle (  1.49);

\path[fill=fillColor] ( 72.64,461.34) circle (  1.49);

\path[fill=fillColor] ( 40.64,432.39) circle (  1.49);

\path[fill=fillColor] ( 46.71,438.45) circle (  1.49);

\path[fill=fillColor] ( 70.64,459.50) circle (  1.49);

\path[fill=fillColor] ( 34.10,427.26) circle (  1.49);

\path[fill=fillColor] ( 51.38,442.07) circle (  1.49);

\path[fill=fillColor] ( 40.37,432.46) circle (  1.49);

\path[fill=fillColor] ( 39.58,432.19) circle (  1.49);

\path[fill=fillColor] ( 45.20,436.05) circle (  1.49);

\path[fill=fillColor] ( 37.72,430.56) circle (  1.49);

\path[fill=fillColor] ( 63.25,452.61) circle (  1.49);

\path[fill=fillColor] ( 52.23,442.66) circle (  1.49);

\path[fill=fillColor] ( 65.57,453.41) circle (  1.49);

\path[fill=fillColor] ( 33.60,426.71) circle (  1.49);

\path[fill=fillColor] ( 50.15,439.64) circle (  1.49);

\path[fill=fillColor] ( 46.22,437.31) circle (  1.49);

\path[fill=fillColor] ( 72.95,462.97) circle (  1.49);

\path[fill=fillColor] ( 38.58,430.43) circle (  1.49);

\path[fill=fillColor] ( 41.71,433.50) circle (  1.49);

\path[fill=fillColor] ( 47.05,438.32) circle (  1.49);

\path[fill=fillColor] ( 45.34,436.31) circle (  1.49);

\path[fill=fillColor] ( 41.60,432.28) circle (  1.49);

\path[fill=fillColor] ( 39.57,432.04) circle (  1.49);

\path[fill=fillColor] ( 46.70,436.87) circle (  1.49);

\path[fill=fillColor] ( 42.57,434.70) circle (  1.49);

\path[fill=fillColor] ( 35.05,427.71) circle (  1.49);

\path[fill=fillColor] ( 35.95,428.85) circle (  1.49);

\path[fill=fillColor] ( 40.92,432.80) circle (  1.49);

\path[fill=fillColor] ( 81.56,463.54) circle (  1.49);

\path[fill=fillColor] ( 46.39,435.92) circle (  1.49);

\path[fill=fillColor] ( 37.22,429.98) circle (  1.49);

\path[fill=fillColor] ( 62.59,451.93) circle (  1.49);

\path[fill=fillColor] ( 37.58,429.44) circle (  1.49);

\path[fill=fillColor] ( 56.72,445.53) circle (  1.49);

\path[fill=fillColor] ( 46.45,437.79) circle (  1.49);

\path[fill=fillColor] ( 43.06,433.73) circle (  1.49);

\path[fill=fillColor] ( 90.79,474.71) circle (  1.49);

\path[fill=fillColor] ( 41.18,431.49) circle (  1.49);

\path[fill=fillColor] ( 39.41,431.74) circle (  1.49);

\path[fill=fillColor] ( 56.55,445.44) circle (  1.49);

\path[fill=fillColor] ( 50.06,440.70) circle (  1.49);

\path[fill=fillColor] ( 42.99,434.51) circle (  1.49);

\path[fill=fillColor] ( 41.01,433.37) circle (  1.49);

\path[fill=fillColor] ( 57.68,446.01) circle (  1.49);

\path[fill=fillColor] ( 43.14,433.73) circle (  1.49);

\path[fill=fillColor] ( 43.04,434.51) circle (  1.49);

\path[fill=fillColor] ( 70.80,455.87) circle (  1.49);

\path[fill=fillColor] ( 35.42,428.77) circle (  1.49);

\path[fill=fillColor] ( 45.54,438.29) circle (  1.49);

\path[fill=fillColor] ( 40.45,432.71) circle (  1.49);

\path[fill=fillColor] ( 35.80,428.70) circle (  1.49);

\path[fill=fillColor] ( 43.63,436.43) circle (  1.49);

\path[fill=fillColor] ( 44.52,435.69) circle (  1.49);

\path[fill=fillColor] ( 41.22,433.33) circle (  1.49);

\path[fill=fillColor] ( 52.67,443.00) circle (  1.49);

\path[fill=fillColor] ( 40.92,432.84) circle (  1.49);

\path[fill=fillColor] ( 38.30,430.90) circle (  1.49);

\path[fill=fillColor] ( 67.25,456.24) circle (  1.49);

\path[fill=fillColor] ( 44.11,436.12) circle (  1.49);

\path[fill=fillColor] ( 36.46,429.46) circle (  1.49);

\path[fill=fillColor] ( 52.38,442.98) circle (  1.49);

\path[fill=fillColor] ( 36.40,430.65) circle (  1.49);

\path[fill=fillColor] ( 42.74,434.01) circle (  1.49);

\path[fill=fillColor] ( 45.58,437.01) circle (  1.49);

\path[fill=fillColor] ( 38.79,431.30) circle (  1.49);

\path[fill=fillColor] ( 34.77,427.86) circle (  1.49);

\path[fill=fillColor] ( 41.38,433.02) circle (  1.49);

\path[fill=fillColor] ( 65.11,453.84) circle (  1.49);

\path[fill=fillColor] ( 68.73,456.83) circle (  1.49);

\path[fill=fillColor] ( 35.68,428.23) circle (  1.49);

\path[fill=fillColor] ( 37.11,429.72) circle (  1.49);

\path[fill=fillColor] ( 61.57,476.51) circle (  1.49);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (104.28,547.27) {Coverage: 93\%};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,425.83) -- (166.85,425.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,425.83) -- ( 32.47,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 59.35,425.83) -- ( 59.35,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 86.22,425.83) -- ( 86.22,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (113.10,425.83) -- (113.10,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (139.97,425.83) -- (139.97,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (166.85,425.83) -- (166.85,421.87);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 32.47,411.58) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 59.35,411.58) {0.5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 86.22,411.58) {1.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (113.10,411.58) {1.5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (139.97,411.58) {2.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (166.85,411.58) {2.5};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,425.83) -- ( 32.47,537.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,425.83) -- ( 28.51,425.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,448.26) -- ( 28.51,448.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,470.69) -- ( 28.51,470.69);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,493.12) -- ( 28.51,493.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,515.55) -- ( 28.51,515.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,537.98) -- ( 28.51,537.98);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,423.56) {0.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,445.99) {0.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,468.42) {1.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,490.85) {1.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,513.28) {2.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,535.71) {2.5};
\end{scope}
\begin{scope}
\path[clip] (192.72,385.44) rectangle (385.44,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.79] at (297.00,559.19) {\bfseries Yule birth rate $\lambda$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (297.00,395.74) {True value};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (199.85,485.76) {Estimated value};
\end{scope}
\begin{scope}
\path[clip] (225.19,425.83) rectangle (368.81,545.69);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (225.19,425.83) --
	(368.81,545.69);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.87,428.62) --
	(232.87,431.65);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.82,431.94) --
	(239.82,440.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.76,427.94) --
	(228.76,430.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.34,428.91) --
	(231.34,432.38);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.80,427.16) --
	(228.80,428.58);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.62,430.12) --
	(232.62,435.04);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.92,431.89) --
	(237.92,438.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.62,434.43) --
	(240.62,444.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (287.09,459.31) --
	(287.09,500.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.27,431.85) --
	(237.27,439.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.93,434.73) --
	(240.93,444.96);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.88,431.60) --
	(239.88,437.89);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (245.07,440.70) --
	(245.07,458.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.73,426.73) --
	(226.73,427.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.30,429.78) --
	(231.30,434.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (241.42,434.30) --
	(241.42,443.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.10,428.60) --
	(230.10,432.40);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.21,429.18) --
	(232.21,433.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (263.83,441.37) --
	(263.83,459.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (246.71,435.55) --
	(246.71,446.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.78,430.11) --
	(234.78,434.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.23,430.40) --
	(234.23,435.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.69,428.44) --
	(229.69,431.33);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.18,428.08) --
	(231.18,430.71);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (233.85,429.87) --
	(233.85,434.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.30,430.44) --
	(234.30,435.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.60,434.57) --
	(239.60,446.27);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.07,429.62) --
	(231.07,433.93);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.45,427.30) --
	(228.45,428.93);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (241.87,435.67) --
	(241.87,446.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.60,429.05) --
	(230.60,432.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.79,428.33) --
	(229.79,431.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (307.77,460.47) --
	(307.77,501.79);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.08,429.19) --
	(232.08,432.93);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (238.73,433.14) --
	(238.73,441.34);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (242.02,432.94) --
	(242.02,441.04);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.81,429.93) --
	(231.81,437.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (246.32,435.42) --
	(246.32,446.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.35,428.42) --
	(230.35,431.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.52,429.32) --
	(231.52,433.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.63,427.82) --
	(229.63,430.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (288.07,475.68) --
	(288.07,536.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (233.24,430.72) --
	(233.24,436.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.34,431.00) --
	(235.34,436.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.92,427.23) --
	(227.92,428.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (252.83,439.91) --
	(252.83,456.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.07,433.12) --
	(240.07,441.60);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.32,430.28) --
	(235.32,435.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.68,431.44) --
	(235.68,437.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.93,434.93) --
	(239.93,446.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (244.38,434.52) --
	(244.38,444.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (233.45,429.98) --
	(233.45,434.60);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (236.88,431.31) --
	(236.88,438.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (257.96,448.04) --
	(257.96,475.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.76,445.08) --
	(261.76,467.69);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.35,432.66) --
	(237.35,440.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.88,427.66) --
	(228.88,429.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (236.13,430.54) --
	(236.13,436.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (243.40,436.86) --
	(243.40,449.60);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.79,427.87) --
	(228.79,430.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (247.49,439.90) --
	(247.49,455.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.70,428.14) --
	(230.70,430.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.41,430.02) --
	(232.41,434.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.57,432.15) --
	(234.57,439.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.70,426.93) --
	(227.70,428.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (245.82,434.39) --
	(245.82,451.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.76,433.11) --
	(237.76,441.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.82,428.28) --
	(229.82,430.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.66,428.83) --
	(231.66,432.23);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.27,431.30) --
	(239.27,437.43);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.25,431.23) --
	(234.25,437.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.61,428.49) --
	(231.61,431.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (241.04,430.65) --
	(241.04,448.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.22,431.78) --
	(240.22,438.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.72,427.33) --
	(227.72,429.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (255.20,440.97) --
	(255.20,462.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (238.41,429.32) --
	(238.41,436.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.10,433.43) --
	(239.10,442.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (257.34,446.41) --
	(257.34,472.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.46,431.29) --
	(235.46,439.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.19,431.03) --
	(237.19,436.86);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (241.23,432.08) --
	(241.23,439.21);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.14,428.82) --
	(232.14,432.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (243.44,433.34) --
	(243.44,443.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (241.47,434.91) --
	(241.47,445.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.82,427.41) --
	(227.82,429.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.43,430.47) --
	(235.43,436.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (253.02,440.04) --
	(253.02,463.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.12,428.06) --
	(229.12,430.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (254.63,433.06) --
	(254.63,462.27);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.15,430.76) --
	(234.15,436.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.95,430.26) --
	(234.95,435.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (248.71,436.87) --
	(248.71,449.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.33,452.04) --
	(261.33,483.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.97,432.35) --
	(239.97,439.58);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.93,428.61) --
	(228.93,431.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.43,427.44) --
	(228.43,429.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (275.69,449.17) --
	(275.69,476.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (242.90,438.65) --
	(242.90,453.61);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.33,426.77) --
	(229.33,429.03);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] (232.87,430.07) circle (  1.49);

\path[fill=fillColor] (239.82,436.13) circle (  1.49);

\path[fill=fillColor] (228.76,429.06) circle (  1.49);

\path[fill=fillColor] (231.34,430.58) circle (  1.49);

\path[fill=fillColor] (228.80,427.83) circle (  1.49);

\path[fill=fillColor] (232.62,432.59) circle (  1.49);

\path[fill=fillColor] (237.92,435.23) circle (  1.49);

\path[fill=fillColor] (240.62,439.39) circle (  1.49);

\path[fill=fillColor] (287.09,479.35) circle (  1.49);

\path[fill=fillColor] (237.27,435.38) circle (  1.49);

\path[fill=fillColor] (240.93,439.71) circle (  1.49);

\path[fill=fillColor] (239.88,434.53) circle (  1.49);

\path[fill=fillColor] (245.07,449.29) circle (  1.49);

\path[fill=fillColor] (226.73,427.23) circle (  1.49);

\path[fill=fillColor] (231.30,432.02) circle (  1.49);

\path[fill=fillColor] (241.42,438.88) circle (  1.49);

\path[fill=fillColor] (230.10,430.45) circle (  1.49);

\path[fill=fillColor] (232.21,431.01) circle (  1.49);

\path[fill=fillColor] (263.83,450.27) circle (  1.49);

\path[fill=fillColor] (246.71,440.60) circle (  1.49);

\path[fill=fillColor] (234.78,432.46) circle (  1.49);

\path[fill=fillColor] (234.23,432.99) circle (  1.49);

\path[fill=fillColor] (229.69,429.86) circle (  1.49);

\path[fill=fillColor] (231.18,429.36) circle (  1.49);

\path[fill=fillColor] (233.85,431.99) circle (  1.49);

\path[fill=fillColor] (234.30,432.98) circle (  1.49);

\path[fill=fillColor] (239.60,440.35) circle (  1.49);

\path[fill=fillColor] (231.07,431.74) circle (  1.49);

\path[fill=fillColor] (228.45,428.08) circle (  1.49);

\path[fill=fillColor] (241.87,441.11) circle (  1.49);

\path[fill=fillColor] (230.60,430.86) circle (  1.49);

\path[fill=fillColor] (229.79,429.72) circle (  1.49);

\path[fill=fillColor] (307.77,480.52) circle (  1.49);

\path[fill=fillColor] (232.08,430.99) circle (  1.49);

\path[fill=fillColor] (238.73,437.10) circle (  1.49);

\path[fill=fillColor] (242.02,436.88) circle (  1.49);

\path[fill=fillColor] (231.81,433.43) circle (  1.49);

\path[fill=fillColor] (246.32,440.76) circle (  1.49);

\path[fill=fillColor] (230.35,429.91) circle (  1.49);

\path[fill=fillColor] (231.52,431.16) circle (  1.49);

\path[fill=fillColor] (229.63,428.88) circle (  1.49);

\path[fill=fillColor] (288.07,505.74) circle (  1.49);

\path[fill=fillColor] (233.24,433.43) circle (  1.49);

\path[fill=fillColor] (235.34,433.73) circle (  1.49);

\path[fill=fillColor] (227.92,427.98) circle (  1.49);

\path[fill=fillColor] (252.83,447.80) circle (  1.49);

\path[fill=fillColor] (240.07,437.32) circle (  1.49);

\path[fill=fillColor] (235.32,432.75) circle (  1.49);

\path[fill=fillColor] (235.68,434.26) circle (  1.49);

\path[fill=fillColor] (239.93,440.20) circle (  1.49);

\path[fill=fillColor] (244.38,439.39) circle (  1.49);

\path[fill=fillColor] (233.45,432.19) circle (  1.49);

\path[fill=fillColor] (236.88,434.69) circle (  1.49);

\path[fill=fillColor] (257.96,461.02) circle (  1.49);

\path[fill=fillColor] (261.76,456.23) circle (  1.49);

\path[fill=fillColor] (237.35,436.38) circle (  1.49);

\path[fill=fillColor] (228.88,428.63) circle (  1.49);

\path[fill=fillColor] (236.13,433.32) circle (  1.49);

\path[fill=fillColor] (243.40,443.04) circle (  1.49);

\path[fill=fillColor] (228.79,428.96) circle (  1.49);

\path[fill=fillColor] (247.49,447.44) circle (  1.49);

\path[fill=fillColor] (230.70,429.41) circle (  1.49);

\path[fill=fillColor] (232.41,432.17) circle (  1.49);

\path[fill=fillColor] (234.57,435.54) circle (  1.49);

\path[fill=fillColor] (227.70,427.53) circle (  1.49);

\path[fill=fillColor] (245.82,442.60) circle (  1.49);

\path[fill=fillColor] (237.76,437.14) circle (  1.49);

\path[fill=fillColor] (229.82,429.60) circle (  1.49);

\path[fill=fillColor] (231.66,430.52) circle (  1.49);

\path[fill=fillColor] (239.27,434.29) circle (  1.49);

\path[fill=fillColor] (234.25,434.22) circle (  1.49);

\path[fill=fillColor] (231.61,429.93) circle (  1.49);

\path[fill=fillColor] (241.04,438.73) circle (  1.49);

\path[fill=fillColor] (240.22,435.02) circle (  1.49);

\path[fill=fillColor] (227.72,428.17) circle (  1.49);

\path[fill=fillColor] (255.20,451.35) circle (  1.49);

\path[fill=fillColor] (238.41,432.95) circle (  1.49);

\path[fill=fillColor] (239.10,437.53) circle (  1.49);

\path[fill=fillColor] (257.34,458.82) circle (  1.49);

\path[fill=fillColor] (235.46,435.25) circle (  1.49);

\path[fill=fillColor] (237.19,433.82) circle (  1.49);

\path[fill=fillColor] (241.23,435.57) circle (  1.49);

\path[fill=fillColor] (232.14,430.47) circle (  1.49);

\path[fill=fillColor] (243.44,437.99) circle (  1.49);

\path[fill=fillColor] (241.47,440.05) circle (  1.49);

\path[fill=fillColor] (227.82,428.27) circle (  1.49);

\path[fill=fillColor] (235.43,433.35) circle (  1.49);

\path[fill=fillColor] (253.02,451.41) circle (  1.49);

\path[fill=fillColor] (229.12,429.32) circle (  1.49);

\path[fill=fillColor] (254.63,447.41) circle (  1.49);

\path[fill=fillColor] (234.15,433.78) circle (  1.49);

\path[fill=fillColor] (234.95,432.57) circle (  1.49);

\path[fill=fillColor] (248.71,443.06) circle (  1.49);

\path[fill=fillColor] (261.33,467.22) circle (  1.49);

\path[fill=fillColor] (239.97,435.80) circle (  1.49);

\path[fill=fillColor] (228.93,430.14) circle (  1.49);

\path[fill=fillColor] (228.43,428.31) circle (  1.49);

\path[fill=fillColor] (275.69,462.26) circle (  1.49);

\path[fill=fillColor] (242.90,445.93) circle (  1.49);

\path[fill=fillColor] (229.33,427.82) circle (  1.49);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (297.00,547.27) {Coverage: 93\%};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,425.83) -- (341.37,425.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,425.83) -- (225.19,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (263.92,425.83) -- (263.92,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (302.64,425.83) -- (302.64,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (341.37,425.83) -- (341.37,421.87);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (225.19,411.58) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (263.92,411.58) {50};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (302.64,411.58) {100};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (341.37,411.58) {150};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,425.83) -- (225.19,522.79);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,425.83) -- (221.23,425.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,458.15) -- (221.23,458.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,490.47) -- (221.23,490.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,522.79) -- (221.23,522.79);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,423.56) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,455.88) {50};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,488.19) {100};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,520.51) {150};
\end{scope}
\begin{scope}
\path[clip] (385.44,385.44) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.79] at (489.72,559.19) {\bfseries HKY model $\kappa$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (489.72,395.74) {True value};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (392.57,485.76) {Estimated value};
\end{scope}
\begin{scope}
\path[clip] (417.91,425.83) rectangle (561.53,545.69);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (417.91,425.83) --
	(561.53,545.69);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.07,426.78) --
	(419.07,426.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (467.37,464.31) --
	(467.37,476.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.56,432.83) --
	(426.56,433.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.82,426.56) --
	(418.82,426.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.76,437.65) --
	(433.76,439.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.75,428.08) --
	(420.75,428.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (422.86,429.96) --
	(422.86,430.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (424.13,430.84) --
	(424.13,431.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (441.24,440.99) --
	(441.24,449.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.44,427.03) --
	(419.44,427.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.83,429.03) --
	(421.83,429.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.41,427.81) --
	(420.41,428.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (424.50,430.89) --
	(424.50,432.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.62,428.81) --
	(421.62,429.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.39,426.96) --
	(419.39,427.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.45,427.81) --
	(420.45,428.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (429.38,434.86) --
	(429.38,435.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.50,427.92) --
	(420.50,428.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (512.46,486.12) --
	(512.46,527.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.82,427.34) --
	(419.82,427.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.88,427.39) --
	(419.88,427.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.92,428.88) --
	(421.92,429.27);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (422.55,429.39) --
	(422.55,429.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (431.30,436.61) --
	(431.30,437.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.20,430.01) --
	(423.20,430.53);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.24,426.07) --
	(418.24,426.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.69,428.83) --
	(421.69,429.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.19,432.17) --
	(426.19,432.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.93,426.67) --
	(418.93,426.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.14,428.40) --
	(421.14,428.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.79,428.15) --
	(420.79,428.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.17,426.02) --
	(418.17,426.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (424.05,430.89) --
	(424.05,432.93);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (422.81,429.60) --
	(422.81,430.04);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (422.44,429.71) --
	(422.44,430.32);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.62,428.74) --
	(421.62,429.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.13,426.81) --
	(419.13,426.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.77,432.90) --
	(426.77,434.30);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (424.99,431.23) --
	(424.99,431.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.62,427.89) --
	(420.62,428.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (425.49,431.81) --
	(425.49,432.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.24,432.22) --
	(427.24,435.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.25,433.12) --
	(427.25,434.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.70,426.48) --
	(418.70,426.60);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (451.72,454.07) --
	(451.72,457.60);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (428.29,433.72) --
	(428.29,435.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (429.52,434.77) --
	(429.52,436.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.04,427.53) --
	(420.04,427.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.57,427.80) --
	(420.57,428.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (452.60,454.32) --
	(452.60,464.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.65,427.16) --
	(419.65,427.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (428.65,434.67) --
	(428.65,435.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.19,426.80) --
	(419.19,426.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (425.75,431.71) --
	(425.75,433.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.31,427.60) --
	(420.31,428.08);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (425.79,431.28) --
	(425.79,432.18);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (422.54,429.59) --
	(422.54,429.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.09,427.57) --
	(420.09,427.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.72,427.20) --
	(419.72,427.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.22,426.06) --
	(418.22,426.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.71,426.36) --
	(418.71,426.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (424.03,430.73) --
	(424.03,431.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.51,453.11) --
	(454.51,458.43);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.71,429.93) --
	(423.71,430.56);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (448.74,449.49) --
	(448.74,451.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.82,426.47) --
	(418.82,426.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.00,427.40) --
	(420.00,427.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.69,426.45) --
	(418.69,426.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.27,428.48) --
	(421.27,428.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.87,428.10) --
	(420.87,428.42);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (422.80,430.05) --
	(422.80,430.64);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.64,428.70) --
	(421.64,429.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (425.36,431.38) --
	(425.36,432.53);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.15,432.36) --
	(426.15,433.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.85,426.56) --
	(418.85,426.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (435.02,438.39) --
	(435.02,442.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.34,428.47) --
	(421.34,428.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (441.84,443.15) --
	(441.84,447.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (449.27,446.51) --
	(449.27,456.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.41,426.19) --
	(418.41,426.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (425.68,431.71) --
	(425.68,432.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.11,454.72) --
	(461.11,462.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.60,428.80) --
	(421.60,429.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.73,432.46) --
	(426.73,433.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (428.20,434.07) --
	(428.20,435.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.81,427.37) --
	(419.81,427.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.95,432.89) --
	(426.95,433.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.86,428.06) --
	(420.86,428.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (437.18,441.04) --
	(437.18,442.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.67,428.80) --
	(421.67,429.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (436.24,439.78) --
	(436.24,442.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.21,427.66) --
	(420.21,427.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.75,433.83) --
	(427.75,435.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (424.43,430.83) --
	(424.43,432.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.74,428.75) --
	(421.74,429.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.32,430.16) --
	(423.32,430.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (422.05,429.10) --
	(422.05,429.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (425.18,431.06) --
	(425.18,432.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.35,426.17) --
	(418.35,426.30);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (422.24,429.32) --
	(422.24,429.70);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] (419.07,426.85) circle (  1.49);

\path[fill=fillColor] (467.37,470.48) circle (  1.49);

\path[fill=fillColor] (426.56,433.17) circle (  1.49);

\path[fill=fillColor] (418.82,426.62) circle (  1.49);

\path[fill=fillColor] (433.76,438.35) circle (  1.49);

\path[fill=fillColor] (420.75,428.22) circle (  1.49);

\path[fill=fillColor] (422.86,430.27) circle (  1.49);

\path[fill=fillColor] (424.13,431.29) circle (  1.49);

\path[fill=fillColor] (441.24,444.75) circle (  1.49);

\path[fill=fillColor] (419.44,427.13) circle (  1.49);

\path[fill=fillColor] (421.83,429.32) circle (  1.49);

\path[fill=fillColor] (420.41,427.95) circle (  1.49);

\path[fill=fillColor] (424.50,431.50) circle (  1.49);

\path[fill=fillColor] (421.62,428.95) circle (  1.49);

\path[fill=fillColor] (419.39,427.04) circle (  1.49);

\path[fill=fillColor] (420.45,427.98) circle (  1.49);

\path[fill=fillColor] (429.38,435.38) circle (  1.49);

\path[fill=fillColor] (420.50,428.05) circle (  1.49);

\path[fill=fillColor] (512.46,505.74) circle (  1.49);

\path[fill=fillColor] (419.82,427.48) circle (  1.49);

\path[fill=fillColor] (419.88,427.50) circle (  1.49);

\path[fill=fillColor] (421.92,429.08) circle (  1.49);

\path[fill=fillColor] (422.55,429.58) circle (  1.49);

\path[fill=fillColor] (431.30,437.24) circle (  1.49);

\path[fill=fillColor] (423.20,430.27) circle (  1.49);

\path[fill=fillColor] (418.24,426.11) circle (  1.49);

\path[fill=fillColor] (421.69,429.12) circle (  1.49);

\path[fill=fillColor] (426.19,432.58) circle (  1.49);

\path[fill=fillColor] (418.93,426.72) circle (  1.49);

\path[fill=fillColor] (421.14,428.65) circle (  1.49);

\path[fill=fillColor] (420.79,428.28) circle (  1.49);

\path[fill=fillColor] (418.17,426.05) circle (  1.49);

\path[fill=fillColor] (424.05,431.91) circle (  1.49);

\path[fill=fillColor] (422.81,429.82) circle (  1.49);

\path[fill=fillColor] (422.44,430.01) circle (  1.49);

\path[fill=fillColor] (421.62,428.96) circle (  1.49);

\path[fill=fillColor] (419.13,426.90) circle (  1.49);

\path[fill=fillColor] (426.77,433.60) circle (  1.49);

\path[fill=fillColor] (424.99,431.51) circle (  1.49);

\path[fill=fillColor] (420.62,428.01) circle (  1.49);

\path[fill=fillColor] (425.49,432.11) circle (  1.49);

\path[fill=fillColor] (427.24,433.82) circle (  1.49);

\path[fill=fillColor] (427.25,433.63) circle (  1.49);

\path[fill=fillColor] (418.70,426.54) circle (  1.49);

\path[fill=fillColor] (451.72,455.83) circle (  1.49);

\path[fill=fillColor] (428.29,434.72) circle (  1.49);

\path[fill=fillColor] (429.52,435.59) circle (  1.49);

\path[fill=fillColor] (420.04,427.64) circle (  1.49);

\path[fill=fillColor] (420.57,427.94) circle (  1.49);

\path[fill=fillColor] (452.60,459.60) circle (  1.49);

\path[fill=fillColor] (419.65,427.29) circle (  1.49);

\path[fill=fillColor] (428.65,435.25) circle (  1.49);

\path[fill=fillColor] (419.19,426.88) circle (  1.49);

\path[fill=fillColor] (425.75,432.60) circle (  1.49);

\path[fill=fillColor] (420.31,427.83) circle (  1.49);

\path[fill=fillColor] (425.79,431.73) circle (  1.49);

\path[fill=fillColor] (422.54,429.78) circle (  1.49);

\path[fill=fillColor] (420.09,427.69) circle (  1.49);

\path[fill=fillColor] (419.72,427.35) circle (  1.49);

\path[fill=fillColor] (418.22,426.09) circle (  1.49);

\path[fill=fillColor] (418.71,426.45) circle (  1.49);

\path[fill=fillColor] (424.03,430.97) circle (  1.49);

\path[fill=fillColor] (454.51,455.68) circle (  1.49);

\path[fill=fillColor] (423.71,430.25) circle (  1.49);

\path[fill=fillColor] (448.74,450.73) circle (  1.49);

\path[fill=fillColor] (418.82,426.55) circle (  1.49);

\path[fill=fillColor] (420.00,427.53) circle (  1.49);

\path[fill=fillColor] (418.69,426.50) circle (  1.49);

\path[fill=fillColor] (421.27,428.62) circle (  1.49);

\path[fill=fillColor] (420.87,428.26) circle (  1.49);

\path[fill=fillColor] (422.80,430.34) circle (  1.49);

\path[fill=fillColor] (421.64,428.85) circle (  1.49);

\path[fill=fillColor] (425.36,431.94) circle (  1.49);

\path[fill=fillColor] (426.15,432.85) circle (  1.49);

\path[fill=fillColor] (418.85,426.61) circle (  1.49);

\path[fill=fillColor] (435.02,440.52) circle (  1.49);

\path[fill=fillColor] (421.34,428.66) circle (  1.49);

\path[fill=fillColor] (441.84,445.08) circle (  1.49);

\path[fill=fillColor] (449.27,451.13) circle (  1.49);

\path[fill=fillColor] (418.41,426.24) circle (  1.49);

\path[fill=fillColor] (425.68,432.14) circle (  1.49);

\path[fill=fillColor] (461.11,458.59) circle (  1.49);

\path[fill=fillColor] (421.60,428.96) circle (  1.49);

\path[fill=fillColor] (426.73,433.06) circle (  1.49);

\path[fill=fillColor] (428.20,434.85) circle (  1.49);

\path[fill=fillColor] (419.81,427.44) circle (  1.49);

\path[fill=fillColor] (426.95,433.41) circle (  1.49);

\path[fill=fillColor] (420.86,428.34) circle (  1.49);

\path[fill=fillColor] (437.18,441.87) circle (  1.49);

\path[fill=fillColor] (421.67,429.19) circle (  1.49);

\path[fill=fillColor] (436.24,440.96) circle (  1.49);

\path[fill=fillColor] (420.21,427.78) circle (  1.49);

\path[fill=fillColor] (427.75,434.68) circle (  1.49);

\path[fill=fillColor] (424.43,431.66) circle (  1.49);

\path[fill=fillColor] (421.74,428.97) circle (  1.49);

\path[fill=fillColor] (423.32,430.39) circle (  1.49);

\path[fill=fillColor] (422.05,429.25) circle (  1.49);

\path[fill=fillColor] (425.18,431.86) circle (  1.49);

\path[fill=fillColor] (418.35,426.23) circle (  1.49);

\path[fill=fillColor] (422.24,429.51) circle (  1.49);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (489.72,547.27) {Coverage: 95\%};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,425.83) -- (552.76,425.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,425.83) -- (417.91,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (437.18,425.83) -- (437.18,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (456.44,425.83) -- (456.44,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (475.70,425.83) -- (475.70,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (494.97,425.83) -- (494.97,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (514.23,425.83) -- (514.23,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (533.49,425.83) -- (533.49,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (552.76,425.83) -- (552.76,421.87);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (417.91,411.58) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (437.18,411.58) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (456.44,411.58) {20};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (475.70,411.58) {30};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (494.97,411.58) {40};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (514.23,411.58) {50};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (533.49,411.58) {60};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (552.76,411.58) {70};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,425.83) -- (417.91,538.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,425.83) -- (413.95,425.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,441.91) -- (413.95,441.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,457.98) -- (413.95,457.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,474.06) -- (413.95,474.06);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,490.14) -- (413.95,490.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,506.21) -- (413.95,506.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,522.29) -- (413.95,522.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,538.37) -- (413.95,538.37);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,423.56) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,439.64) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,455.71) {20};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,471.79) {30};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,487.87) {40};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,503.94) {50};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,520.02) {60};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,536.09) {70};
\end{scope}
\begin{scope}
\path[clip] (  0.00,192.72) rectangle (192.72,385.44);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.79] at (104.28,366.47) {\bfseries Nucleotide frequency $f$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (104.28,203.02) {True value};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (  7.13,293.04) {Estimated value};
\end{scope}
\begin{scope}
\path[clip] ( 32.47,233.11) rectangle (176.09,352.97);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] ( 32.47,233.11) --
	(176.09,352.97);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 59.52,253.76) --
	( 59.52,256.09);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 80.98,271.74) --
	( 80.98,275.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 73.46,265.67) --
	( 73.46,268.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (106.47,294.82) --
	(106.47,298.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 93.59,282.91) --
	( 93.59,285.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 85.32,275.30) --
	( 85.32,279.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (114.14,298.38) --
	(114.14,303.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (114.03,296.78) --
	(114.03,302.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.32,286.59) --
	( 99.32,293.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 85.70,275.05) --
	( 85.70,279.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (119.28,301.72) --
	(119.28,307.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 74.17,265.49) --
	( 74.17,269.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 86.64,276.28) --
	( 86.64,281.70);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 76.12,268.61) --
	( 76.12,270.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 81.26,272.24) --
	( 81.26,275.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.22,305.31) --
	(121.22,310.96);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.79,256.93) --
	( 60.79,259.35);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 88.73,277.88) --
	( 88.73,281.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (106.97,290.23) --
	(106.97,296.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (105.24,290.35) --
	(105.24,295.60);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 72.44,263.99) --
	( 72.44,267.34);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.86,281.52) --
	( 92.86,285.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.03,297.50) --
	(112.03,301.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 84.55,273.90) --
	( 84.55,276.87);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.64,279.31) --
	( 92.64,283.22);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 96.89,284.75) --
	( 96.89,288.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (108.82,292.09) --
	(108.82,297.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.57,261.09) --
	( 68.57,264.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 98.03,286.22) --
	( 98.03,289.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (104.02,290.76) --
	(104.02,296.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 90.85,281.54) --
	( 90.85,285.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (128.22,310.98) --
	(128.22,315.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.10,282.10) --
	( 95.10,288.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 61.15,256.58) --
	( 61.15,259.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.84,287.78) --
	(100.84,292.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (101.64,288.40) --
	(101.64,293.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 81.37,273.00) --
	( 81.37,277.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (108.47,292.87) --
	(108.47,298.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 76.02,267.71) --
	( 76.02,270.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.04,283.85) --
	( 95.04,287.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 82.97,275.05) --
	( 82.97,277.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.04,278.23) --
	( 89.04,284.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.13,288.33) --
	(100.13,292.79);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 86.15,277.50) --
	( 86.15,281.53);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.23,260.98) --
	( 66.23,263.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 84.83,275.12) --
	( 84.83,280.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (110.01,296.71) --
	(110.01,302.06);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 72.64,265.65) --
	( 72.64,269.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (103.63,290.31) --
	(103.63,294.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.17,264.75) --
	( 75.17,269.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.42,304.96) --
	(121.42,310.56);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.69,284.41) --
	( 95.69,288.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 73.56,266.10) --
	( 73.56,269.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (114.69,296.27) --
	(114.69,302.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.50,280.46) --
	( 92.50,286.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (101.37,288.76) --
	(101.37,293.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 86.95,276.20) --
	( 86.95,279.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 77.83,268.60) --
	( 77.83,272.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 86.72,275.11) --
	( 86.72,280.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (113.57,299.01) --
	(113.57,302.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.07,258.35) --
	( 66.07,262.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.56,284.63) --
	( 95.56,287.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (103.40,291.16) --
	(103.40,295.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 78.68,269.78) --
	( 78.68,274.06);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.18,284.30) --
	( 95.18,287.08);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 85.11,277.47) --
	( 85.11,282.66);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (107.03,293.66) --
	(107.03,298.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 70.85,263.16) --
	( 70.85,265.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 74.58,267.87) --
	( 74.58,270.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 96.56,282.90) --
	( 96.56,287.34);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.98,278.44) --
	( 89.98,282.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (104.98,291.20) --
	(104.98,294.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.19,267.27) --
	( 75.19,271.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (110.27,293.47) --
	(110.27,298.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 65.48,260.04) --
	( 65.48,262.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 72.91,264.08) --
	( 72.91,269.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 90.11,278.89) --
	( 90.11,283.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 94.00,280.99) --
	( 94.00,285.69);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (105.13,289.20) --
	(105.13,295.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 84.06,272.87) --
	( 84.06,276.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 96.09,283.64) --
	( 96.09,288.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.77,278.96) --
	( 89.77,284.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (114.41,300.31) --
	(114.41,304.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (103.74,292.13) --
	(103.74,297.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.57,295.70) --
	(112.57,301.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 79.47,271.45) --
	( 79.47,273.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 88.02,278.38) --
	( 88.02,282.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 74.94,264.32) --
	( 74.94,269.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 76.72,268.10) --
	( 76.72,270.87);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 81.57,274.20) --
	( 81.57,279.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 71.87,266.76) --
	( 71.87,270.48);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (110.18,296.67) --
	(110.18,301.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 73.41,264.83) --
	( 73.41,269.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 85.28,273.66) --
	( 85.28,279.58);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 86.24,274.87) --
	( 86.24,279.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.02,273.03) --
	( 83.02,276.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 72.89,264.97) --
	( 72.89,267.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 93.64,280.22) --
	( 93.64,286.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (103.83,289.66) --
	(103.83,295.48);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 64.27,260.24) --
	( 64.27,262.42);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] ( 59.52,254.96) circle (  1.49);

\path[fill=fillColor] ( 80.98,273.78) circle (  1.49);

\path[fill=fillColor] ( 73.46,266.95) circle (  1.49);

\path[fill=fillColor] (106.47,296.73) circle (  1.49);

\path[fill=fillColor] ( 93.59,284.10) circle (  1.49);

\path[fill=fillColor] ( 85.32,277.27) circle (  1.49);

\path[fill=fillColor] (114.14,300.94) circle (  1.49);

\path[fill=fillColor] (114.03,299.46) circle (  1.49);

\path[fill=fillColor] ( 99.32,289.90) circle (  1.49);

\path[fill=fillColor] ( 85.70,277.26) circle (  1.49);

\path[fill=fillColor] (119.28,304.42) circle (  1.49);

\path[fill=fillColor] ( 74.17,267.36) circle (  1.49);

\path[fill=fillColor] ( 86.64,278.83) circle (  1.49);

\path[fill=fillColor] ( 76.12,269.68) circle (  1.49);

\path[fill=fillColor] ( 81.26,273.96) circle (  1.49);

\path[fill=fillColor] (121.22,308.01) circle (  1.49);

\path[fill=fillColor] ( 60.79,258.18) circle (  1.49);

\path[fill=fillColor] ( 88.73,279.66) circle (  1.49);

\path[fill=fillColor] (106.97,293.56) circle (  1.49);

\path[fill=fillColor] (105.24,292.91) circle (  1.49);

\path[fill=fillColor] ( 72.44,265.72) circle (  1.49);

\path[fill=fillColor] ( 92.86,283.61) circle (  1.49);

\path[fill=fillColor] (112.03,299.44) circle (  1.49);

\path[fill=fillColor] ( 84.55,275.40) circle (  1.49);

\path[fill=fillColor] ( 92.64,281.33) circle (  1.49);

\path[fill=fillColor] ( 96.89,286.84) circle (  1.49);

\path[fill=fillColor] (108.82,295.08) circle (  1.49);

\path[fill=fillColor] ( 68.57,262.60) circle (  1.49);

\path[fill=fillColor] ( 98.03,287.67) circle (  1.49);

\path[fill=fillColor] (104.02,293.62) circle (  1.49);

\path[fill=fillColor] ( 90.85,283.31) circle (  1.49);

\path[fill=fillColor] (128.22,312.91) circle (  1.49);

\path[fill=fillColor] ( 95.10,285.47) circle (  1.49);

\path[fill=fillColor] ( 61.15,257.89) circle (  1.49);

\path[fill=fillColor] (100.84,290.29) circle (  1.49);

\path[fill=fillColor] (101.64,290.96) circle (  1.49);

\path[fill=fillColor] ( 81.37,275.07) circle (  1.49);

\path[fill=fillColor] (108.47,295.65) circle (  1.49);

\path[fill=fillColor] ( 76.02,269.27) circle (  1.49);

\path[fill=fillColor] ( 95.04,285.69) circle (  1.49);

\path[fill=fillColor] ( 82.97,276.49) circle (  1.49);

\path[fill=fillColor] ( 89.04,281.42) circle (  1.49);

\path[fill=fillColor] (100.13,290.62) circle (  1.49);

\path[fill=fillColor] ( 86.15,279.52) circle (  1.49);

\path[fill=fillColor] ( 66.23,262.06) circle (  1.49);

\path[fill=fillColor] ( 84.83,277.89) circle (  1.49);

\path[fill=fillColor] (110.01,299.35) circle (  1.49);

\path[fill=fillColor] ( 72.64,267.35) circle (  1.49);

\path[fill=fillColor] (103.63,292.60) circle (  1.49);

\path[fill=fillColor] ( 75.17,267.32) circle (  1.49);

\path[fill=fillColor] (121.42,307.80) circle (  1.49);

\path[fill=fillColor] ( 95.69,286.43) circle (  1.49);

\path[fill=fillColor] ( 73.56,268.02) circle (  1.49);

\path[fill=fillColor] (114.69,299.49) circle (  1.49);

\path[fill=fillColor] ( 92.50,283.21) circle (  1.49);

\path[fill=fillColor] (101.37,291.28) circle (  1.49);

\path[fill=fillColor] ( 86.95,277.61) circle (  1.49);

\path[fill=fillColor] ( 77.83,270.42) circle (  1.49);

\path[fill=fillColor] ( 86.72,277.66) circle (  1.49);

\path[fill=fillColor] (113.57,300.85) circle (  1.49);

\path[fill=fillColor] ( 66.07,260.59) circle (  1.49);

\path[fill=fillColor] ( 95.56,286.34) circle (  1.49);

\path[fill=fillColor] (103.40,293.50) circle (  1.49);

\path[fill=fillColor] ( 78.68,271.94) circle (  1.49);

\path[fill=fillColor] ( 95.18,285.68) circle (  1.49);

\path[fill=fillColor] ( 85.11,280.00) circle (  1.49);

\path[fill=fillColor] (107.03,296.17) circle (  1.49);

\path[fill=fillColor] ( 70.85,264.47) circle (  1.49);

\path[fill=fillColor] ( 74.58,269.31) circle (  1.49);

\path[fill=fillColor] ( 96.56,285.14) circle (  1.49);

\path[fill=fillColor] ( 89.98,280.50) circle (  1.49);

\path[fill=fillColor] (104.98,293.09) circle (  1.49);

\path[fill=fillColor] ( 75.19,269.40) circle (  1.49);

\path[fill=fillColor] (110.27,295.97) circle (  1.49);

\path[fill=fillColor] ( 65.48,261.04) circle (  1.49);

\path[fill=fillColor] ( 72.91,266.61) circle (  1.49);

\path[fill=fillColor] ( 90.11,280.93) circle (  1.49);

\path[fill=fillColor] ( 94.00,283.29) circle (  1.49);

\path[fill=fillColor] (105.13,292.43) circle (  1.49);

\path[fill=fillColor] ( 84.06,274.97) circle (  1.49);

\path[fill=fillColor] ( 96.09,285.76) circle (  1.49);

\path[fill=fillColor] ( 89.77,281.62) circle (  1.49);

\path[fill=fillColor] (114.41,302.30) circle (  1.49);

\path[fill=fillColor] (103.74,294.89) circle (  1.49);

\path[fill=fillColor] (112.57,298.41) circle (  1.49);

\path[fill=fillColor] ( 79.47,272.68) circle (  1.49);

\path[fill=fillColor] ( 88.02,280.35) circle (  1.49);

\path[fill=fillColor] ( 74.94,266.71) circle (  1.49);

\path[fill=fillColor] ( 76.72,269.54) circle (  1.49);

\path[fill=fillColor] ( 81.57,276.93) circle (  1.49);

\path[fill=fillColor] ( 71.87,268.65) circle (  1.49);

\path[fill=fillColor] (110.18,298.83) circle (  1.49);

\path[fill=fillColor] ( 73.41,267.06) circle (  1.49);

\path[fill=fillColor] ( 85.28,276.57) circle (  1.49);

\path[fill=fillColor] ( 86.24,276.98) circle (  1.49);

\path[fill=fillColor] ( 83.02,274.73) circle (  1.49);

\path[fill=fillColor] ( 72.89,266.19) circle (  1.49);

\path[fill=fillColor] ( 93.64,283.39) circle (  1.49);

\path[fill=fillColor] (103.83,292.68) circle (  1.49);

\path[fill=fillColor] ( 64.27,261.28) circle (  1.49);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (104.28,354.55) {Coverage: 94\%};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,233.11) -- (174.42,233.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,233.11) -- ( 32.47,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 56.13,233.11) -- ( 56.13,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 79.79,233.11) -- ( 79.79,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (103.45,233.11) -- (103.45,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (127.10,233.11) -- (127.10,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (150.76,233.11) -- (150.76,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.42,233.11) -- (174.42,229.15);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 32.47,218.86) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 56.13,218.86) {0.1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 79.79,218.86) {0.2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (103.45,218.86) {0.3};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (127.10,218.86) {0.4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (150.76,218.86) {0.5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (174.42,218.86) {0.6};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,233.11) -- ( 32.47,351.58);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,233.11) -- ( 28.51,233.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,252.86) -- ( 28.51,252.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,272.60) -- ( 28.51,272.60);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,292.34) -- ( 28.51,292.34);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,312.09) -- ( 28.51,312.09);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,331.83) -- ( 28.51,331.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,351.58) -- ( 28.51,351.58);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,230.84) {0.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,250.58) {0.1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,270.33) {0.2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,290.07) {0.3};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,309.82) {0.4};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,329.56) {0.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,349.30) {0.6};
\end{scope}
\begin{scope}
\path[clip] (192.72,192.72) rectangle (385.44,385.44);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.79] at (297.00,366.47) {\bfseries Clock standard deviation $\sigma$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (297.00,203.02) {True value};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (199.85,293.04) {Estimated value};
\end{scope}
\begin{scope}
\path[clip] (225.19,233.11) rectangle (368.81,352.97);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (225.19,233.11) --
	(368.81,352.97);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.20,233.11) --
	(225.20,235.53);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (255.97,249.69) --
	(255.97,264.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.49,233.11) --
	(225.49,235.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.92,235.92) --
	(230.92,241.30);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.36,233.11) --
	(227.36,238.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.05,233.11) --
	(227.05,235.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (241.68,240.30) --
	(241.68,247.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.79,237.31) --
	(232.79,243.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (233.76,233.11) --
	(233.76,243.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (238.43,239.68) --
	(238.43,246.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.51,233.11) --
	(225.51,237.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.28,233.11) --
	(226.28,235.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.23,236.27) --
	(230.23,244.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.36,242.13) --
	(240.36,250.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.44,233.11) --
	(225.44,234.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.07,233.11) --
	(228.07,237.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.35,248.54) --
	(261.35,263.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (238.24,240.64) --
	(238.24,247.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.48,233.11) --
	(228.48,239.06);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.46,237.06) --
	(232.46,243.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.38,237.51) --
	(232.38,242.79);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.77,240.05) --
	(240.77,247.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.24,233.11) --
	(228.24,236.49);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (238.92,240.29) --
	(238.92,247.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.37,233.11) --
	(227.37,237.70);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.43,235.84) --
	(232.43,240.53);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (241.87,244.94) --
	(241.87,256.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.04,233.11) --
	(226.04,237.30);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.22,233.11) --
	(225.22,234.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.42,233.11) --
	(230.42,241.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.26,240.39) --
	(239.26,246.58);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.68,233.11) --
	(229.68,237.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.93,233.11) --
	(230.93,242.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.41,233.11) --
	(227.41,237.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.67,233.11) --
	(225.67,236.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.72,233.11) --
	(226.72,238.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (269.99,264.24) --
	(269.99,281.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.21,233.11) --
	(228.21,240.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.33,233.11) --
	(226.33,235.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.49,233.11) --
	(226.49,236.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.33,233.11) --
	(225.33,237.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.90,233.11) --
	(225.90,244.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.62,233.11) --
	(226.62,237.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,233.11) --
	(225.19,235.06);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.10,234.04) --
	(226.10,239.52);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.74,233.11) --
	(234.74,242.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.62,233.11) --
	(226.62,235.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.14,233.11) --
	(226.14,235.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.54,233.11) --
	(225.54,239.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (246.54,244.57) --
	(246.54,254.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.84,233.11) --
	(225.84,237.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.12,233.11) --
	(227.12,235.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (242.15,243.78) --
	(242.15,251.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (241.68,240.21) --
	(241.68,249.78);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.26,233.11) --
	(231.26,237.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.82,233.11) --
	(230.82,237.77);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.58,233.11) --
	(229.58,238.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (246.35,243.90) --
	(246.35,252.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.43,233.11) --
	(225.43,237.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.47,233.11) --
	(226.47,238.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.55,233.11) --
	(229.55,239.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.27,237.36) --
	(232.27,241.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.16,233.11) --
	(228.16,236.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (233.25,235.52) --
	(233.25,241.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.14,233.11) --
	(226.14,235.79);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (279.31,262.88) --
	(279.31,283.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.32,233.11) --
	(226.32,235.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.25,233.11) --
	(227.25,235.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.67,233.11) --
	(225.67,235.49);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.55,233.11) --
	(229.55,236.48);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.73,236.00) --
	(230.73,240.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.64,234.18) --
	(230.64,238.84);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (320.94,273.05) --
	(320.94,305.28);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.95,233.11) --
	(226.95,236.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.77,236.79) --
	(232.77,240.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (250.27,247.98) --
	(250.27,263.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (280.09,268.05) --
	(280.09,286.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (233.09,236.27) --
	(233.09,242.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.20,240.59) --
	(240.20,251.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (248.20,250.94) --
	(248.20,265.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.16,233.11) --
	(227.16,235.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.87,233.11) --
	(226.87,235.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,233.11) --
	(225.19,235.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (250.60,246.49) --
	(250.60,257.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.30,233.11) --
	(226.30,239.94);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.41,239.03) --
	(234.41,243.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (236.08,241.50) --
	(236.08,248.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (255.66,254.20) --
	(255.66,271.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.27,233.11) --
	(225.27,235.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (286.90,274.73) --
	(286.90,304.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (243.36,243.88) --
	(243.36,252.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.80,239.51) --
	(235.80,245.79);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.41,233.11) --
	(226.41,237.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.44,233.11) --
	(226.44,240.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.65,233.11) --
	(227.65,235.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.20,233.11) --
	(225.20,236.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.96,235.43) --
	(229.96,239.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.58,233.11) --
	(226.58,238.70);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.84,233.11) --
	(226.84,236.46);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (263.92,269.00) --
	(263.92,292.59);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] (225.20,233.90) circle (  1.49);

\path[fill=fillColor] (255.97,256.77) circle (  1.49);

\path[fill=fillColor] (225.49,233.84) circle (  1.49);

\path[fill=fillColor] (230.92,238.53) circle (  1.49);

\path[fill=fillColor] (227.36,236.11) circle (  1.49);

\path[fill=fillColor] (227.05,234.01) circle (  1.49);

\path[fill=fillColor] (241.68,243.48) circle (  1.49);

\path[fill=fillColor] (232.79,240.07) circle (  1.49);

\path[fill=fillColor] (233.76,237.44) circle (  1.49);

\path[fill=fillColor] (238.43,242.92) circle (  1.49);

\path[fill=fillColor] (225.51,234.64) circle (  1.49);

\path[fill=fillColor] (226.28,233.75) circle (  1.49);

\path[fill=fillColor] (230.23,240.36) circle (  1.49);

\path[fill=fillColor] (240.36,246.15) circle (  1.49);

\path[fill=fillColor] (225.44,233.67) circle (  1.49);

\path[fill=fillColor] (228.07,234.66) circle (  1.49);

\path[fill=fillColor] (261.35,255.47) circle (  1.49);

\path[fill=fillColor] (238.24,243.83) circle (  1.49);

\path[fill=fillColor] (228.48,235.21) circle (  1.49);

\path[fill=fillColor] (232.46,240.22) circle (  1.49);

\path[fill=fillColor] (232.38,240.05) circle (  1.49);

\path[fill=fillColor] (240.77,243.35) circle (  1.49);

\path[fill=fillColor] (228.24,234.52) circle (  1.49);

\path[fill=fillColor] (238.92,243.53) circle (  1.49);

\path[fill=fillColor] (227.37,235.26) circle (  1.49);

\path[fill=fillColor] (232.43,238.09) circle (  1.49);

\path[fill=fillColor] (241.87,250.24) circle (  1.49);

\path[fill=fillColor] (226.04,234.96) circle (  1.49);

\path[fill=fillColor] (225.22,233.60) circle (  1.49);

\path[fill=fillColor] (230.42,237.99) circle (  1.49);

\path[fill=fillColor] (239.26,243.34) circle (  1.49);

\path[fill=fillColor] (229.68,235.91) circle (  1.49);

\path[fill=fillColor] (230.93,236.66) circle (  1.49);

\path[fill=fillColor] (227.41,235.08) circle (  1.49);

\path[fill=fillColor] (225.67,234.24) circle (  1.49);

\path[fill=fillColor] (226.72,235.40) circle (  1.49);

\path[fill=fillColor] (269.99,272.75) circle (  1.49);

\path[fill=fillColor] (228.21,237.55) circle (  1.49);

\path[fill=fillColor] (226.33,233.80) circle (  1.49);

\path[fill=fillColor] (226.49,234.55) circle (  1.49);

\path[fill=fillColor] (225.33,235.18) circle (  1.49);

\path[fill=fillColor] (225.90,237.00) circle (  1.49);

\path[fill=fillColor] (226.62,234.43) circle (  1.49);

\path[fill=fillColor] (225.19,233.72) circle (  1.49);

\path[fill=fillColor] (226.10,236.79) circle (  1.49);

\path[fill=fillColor] (234.74,238.21) circle (  1.49);

\path[fill=fillColor] (226.62,234.01) circle (  1.49);

\path[fill=fillColor] (226.14,233.74) circle (  1.49);

\path[fill=fillColor] (225.54,236.55) circle (  1.49);

\path[fill=fillColor] (246.54,249.40) circle (  1.49);

\path[fill=fillColor] (225.84,234.89) circle (  1.49);

\path[fill=fillColor] (227.12,233.78) circle (  1.49);

\path[fill=fillColor] (242.15,247.57) circle (  1.49);

\path[fill=fillColor] (241.68,244.71) circle (  1.49);

\path[fill=fillColor] (231.26,234.36) circle (  1.49);

\path[fill=fillColor] (230.82,235.22) circle (  1.49);

\path[fill=fillColor] (229.58,235.75) circle (  1.49);

\path[fill=fillColor] (246.35,247.96) circle (  1.49);

\path[fill=fillColor] (225.43,234.59) circle (  1.49);

\path[fill=fillColor] (226.47,236.00) circle (  1.49);

\path[fill=fillColor] (229.55,235.34) circle (  1.49);

\path[fill=fillColor] (232.27,239.45) circle (  1.49);

\path[fill=fillColor] (228.16,234.23) circle (  1.49);

\path[fill=fillColor] (233.25,238.42) circle (  1.49);

\path[fill=fillColor] (226.14,234.08) circle (  1.49);

\path[fill=fillColor] (279.31,272.70) circle (  1.49);

\path[fill=fillColor] (226.32,233.87) circle (  1.49);

\path[fill=fillColor] (227.25,234.28) circle (  1.49);

\path[fill=fillColor] (225.67,233.89) circle (  1.49);

\path[fill=fillColor] (229.55,234.26) circle (  1.49);

\path[fill=fillColor] (230.73,238.29) circle (  1.49);

\path[fill=fillColor] (230.64,236.42) circle (  1.49);

\path[fill=fillColor] (320.94,288.25) circle (  1.49);

\path[fill=fillColor] (226.95,234.18) circle (  1.49);

\path[fill=fillColor] (232.77,238.61) circle (  1.49);

\path[fill=fillColor] (250.27,255.51) circle (  1.49);

\path[fill=fillColor] (280.09,277.06) circle (  1.49);

\path[fill=fillColor] (233.09,239.11) circle (  1.49);

\path[fill=fillColor] (240.20,245.98) circle (  1.49);

\path[fill=fillColor] (248.20,257.65) circle (  1.49);

\path[fill=fillColor] (227.16,233.77) circle (  1.49);

\path[fill=fillColor] (226.87,233.80) circle (  1.49);

\path[fill=fillColor] (225.19,233.80) circle (  1.49);

\path[fill=fillColor] (250.60,251.75) circle (  1.49);

\path[fill=fillColor] (226.30,236.94) circle (  1.49);

\path[fill=fillColor] (234.41,241.03) circle (  1.49);

\path[fill=fillColor] (236.08,245.01) circle (  1.49);

\path[fill=fillColor] (255.66,262.18) circle (  1.49);

\path[fill=fillColor] (225.27,233.86) circle (  1.49);

\path[fill=fillColor] (286.90,289.39) circle (  1.49);

\path[fill=fillColor] (243.36,247.76) circle (  1.49);

\path[fill=fillColor] (235.80,242.53) circle (  1.49);

\path[fill=fillColor] (226.41,234.78) circle (  1.49);

\path[fill=fillColor] (226.44,235.87) circle (  1.49);

\path[fill=fillColor] (227.65,234.05) circle (  1.49);

\path[fill=fillColor] (225.20,234.26) circle (  1.49);

\path[fill=fillColor] (229.96,237.38) circle (  1.49);

\path[fill=fillColor] (226.58,234.93) circle (  1.49);

\path[fill=fillColor] (226.84,234.15) circle (  1.49);

\path[fill=fillColor] (263.92,280.15) circle (  1.49);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (297.00,354.55) {Coverage: 94\%};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,233.11) -- (356.16,233.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,233.11) -- (225.19,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (247.02,233.11) -- (247.02,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (268.85,233.11) -- (268.85,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (290.68,233.11) -- (290.68,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (312.51,233.11) -- (312.51,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (334.33,233.11) -- (334.33,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (356.16,233.11) -- (356.16,229.15);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (225.19,218.86) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (247.02,218.86) {0.5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (268.85,218.86) {1.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (290.68,218.86) {1.5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (312.51,218.86) {2.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (334.33,218.86) {2.5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (356.16,218.86) {3.0};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,233.11) -- (225.19,342.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,233.11) -- (221.23,233.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,251.33) -- (221.23,251.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,269.55) -- (221.23,269.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,287.76) -- (221.23,287.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,305.98) -- (221.23,305.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,324.20) -- (221.23,324.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,342.41) -- (221.23,342.41);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,230.84) {0.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,249.06) {0.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,267.27) {1.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,285.49) {1.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,303.71) {2.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,321.92) {2.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,340.14) {3.0};
\end{scope}
\begin{scope}
\path[clip] (385.44,192.72) rectangle (578.16,385.44);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.79] at (489.72,366.47) {\bfseries Branch rate mean};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (489.72,203.02) {True value};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (392.57,293.04) {Estimated value};
\end{scope}
\begin{scope}
\path[clip] (417.91,233.11) rectangle (561.53,352.97);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (417.91,233.11) --
	(561.53,352.97);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.90,286.57) --
	(482.90,288.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.90,270.72) --
	(479.90,293.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.01,286.75) --
	(483.01,287.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.67,283.37) --
	(482.67,289.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.26,285.72) --
	(483.26,289.53);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.10,286.57) --
	(483.10,288.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.42,281.19) --
	(479.42,292.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.59,283.60) --
	(486.59,290.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (484.74,283.70) --
	(484.74,289.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.32,283.47) --
	(482.32,293.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.78,286.07) --
	(482.78,288.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.06,286.75) --
	(483.06,287.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.90,282.80) --
	(482.90,290.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (481.99,279.76) --
	(481.99,293.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.85,286.83) --
	(482.85,287.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.17,285.91) --
	(483.17,288.51);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (466.60,276.38) --
	(466.60,299.58);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.23,282.36) --
	(485.23,293.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.03,285.65) --
	(483.03,288.70);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.66,282.97) --
	(479.66,290.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.80,283.49) --
	(482.80,290.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.18,282.88) --
	(485.18,294.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.38,285.95) --
	(482.38,288.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.26,281.18) --
	(483.26,292.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.27,285.42) --
	(482.27,288.40);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (484.20,285.06) --
	(484.20,290.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.01,273.96) --
	(479.01,290.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.01,286.13) --
	(483.01,288.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.90,286.90) --
	(482.90,287.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.76,284.49) --
	(482.76,289.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.11,282.31) --
	(483.11,292.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (481.24,285.70) --
	(481.24,289.51);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.74,283.81) --
	(485.74,289.42);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.08,285.66) --
	(482.08,288.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.02,286.43) --
	(483.02,288.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.62,285.99) --
	(482.62,288.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (470.60,262.81) --
	(470.60,290.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.32,284.01) --
	(483.32,289.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.98,286.89) --
	(482.98,288.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.04,286.46) --
	(483.04,288.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.97,285.86) --
	(482.97,288.53);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.86,284.14) --
	(482.86,290.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.36,286.00) --
	(482.36,288.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.90,286.84) --
	(482.90,287.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.30,285.55) --
	(482.30,289.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.48,284.00) --
	(479.48,290.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.16,286.58) --
	(482.16,288.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.94,286.80) --
	(482.94,287.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.78,285.24) --
	(482.78,289.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.27,278.35) --
	(477.27,293.93);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.18,285.84) --
	(483.18,288.60);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.24,286.79) --
	(482.24,287.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (484.28,280.51) --
	(484.28,294.06);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.90,281.01) --
	(476.90,292.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.16,286.00) --
	(482.16,288.24);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (480.87,285.88) --
	(480.87,288.79);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (481.15,285.73) --
	(481.15,289.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.93,278.54) --
	(476.93,292.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.95,286.07) --
	(482.95,288.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.93,285.79) --
	(482.93,289.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.45,285.32) --
	(482.45,288.93);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (481.59,284.31) --
	(481.59,290.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.56,286.46) --
	(483.56,288.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (481.55,283.92) --
	(481.55,289.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.69,286.48) --
	(482.69,287.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (478.35,266.86) --
	(478.35,308.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.82,286.74) --
	(482.82,288.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.95,286.32) --
	(482.95,288.09);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.80,286.65) --
	(482.80,287.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.62,286.40) --
	(482.62,288.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.28,284.36) --
	(483.28,289.58);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.36,285.37) --
	(482.36,288.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (464.27,253.57) --
	(464.27,308.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.17,286.41) --
	(483.17,288.09);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.66,284.46) --
	(482.66,289.60);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.20,273.15) --
	(486.20,296.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (489.89,268.29) --
	(489.89,311.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.23,284.01) --
	(482.23,289.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (480.22,279.98) --
	(480.22,294.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.07,274.18) --
	(482.07,299.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.47,286.67) --
	(482.47,287.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.26,286.75) --
	(483.26,287.93);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.90,286.76) --
	(482.90,287.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.38,276.94) --
	(479.38,295.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.46,285.08) --
	(483.46,289.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.63,283.61) --
	(483.63,291.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.80,280.43) --
	(482.80,291.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (480.75,269.66) --
	(480.75,300.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.89,286.77) --
	(482.89,287.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.51,250.72) --
	(486.51,303.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.43,280.71) --
	(479.43,295.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.58,283.04) --
	(483.58,292.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.99,285.82) --
	(482.99,288.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.91,285.16) --
	(482.91,289.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.33,286.64) --
	(483.33,288.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.90,286.23) --
	(482.90,288.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.03,284.68) --
	(482.03,289.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.80,285.73) --
	(482.80,288.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.23,286.49) --
	(483.23,288.26);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (513.66,258.51) --
	(513.66,299.82);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] (482.90,287.34) circle (  1.49);

\path[fill=fillColor] (479.90,282.04) circle (  1.49);

\path[fill=fillColor] (483.01,287.33) circle (  1.49);

\path[fill=fillColor] (482.67,286.46) circle (  1.49);

\path[fill=fillColor] (483.26,287.52) circle (  1.49);

\path[fill=fillColor] (483.10,287.34) circle (  1.49);

\path[fill=fillColor] (479.42,286.84) circle (  1.49);

\path[fill=fillColor] (486.59,287.13) circle (  1.49);

\path[fill=fillColor] (484.74,287.01) circle (  1.49);

\path[fill=fillColor] (482.32,288.55) circle (  1.49);

\path[fill=fillColor] (482.78,287.37) circle (  1.49);

\path[fill=fillColor] (483.06,287.36) circle (  1.49);

\path[fill=fillColor] (482.90,286.66) circle (  1.49);

\path[fill=fillColor] (481.99,286.67) circle (  1.49);

\path[fill=fillColor] (482.85,287.34) circle (  1.49);

\path[fill=fillColor] (483.17,287.28) circle (  1.49);

\path[fill=fillColor] (466.60,288.00) circle (  1.49);

\path[fill=fillColor] (485.23,287.81) circle (  1.49);

\path[fill=fillColor] (483.03,287.22) circle (  1.49);

\path[fill=fillColor] (479.66,286.59) circle (  1.49);

\path[fill=fillColor] (482.80,287.20) circle (  1.49);

\path[fill=fillColor] (485.18,288.78) circle (  1.49);

\path[fill=fillColor] (482.38,287.20) circle (  1.49);

\path[fill=fillColor] (483.26,286.93) circle (  1.49);

\path[fill=fillColor] (482.27,287.11) circle (  1.49);

\path[fill=fillColor] (484.20,287.60) circle (  1.49);

\path[fill=fillColor] (479.01,282.47) circle (  1.49);

\path[fill=fillColor] (483.01,287.41) circle (  1.49);

\path[fill=fillColor] (482.90,287.37) circle (  1.49);

\path[fill=fillColor] (482.76,287.14) circle (  1.49);

\path[fill=fillColor] (483.11,287.28) circle (  1.49);

\path[fill=fillColor] (481.24,287.56) circle (  1.49);

\path[fill=fillColor] (485.74,287.00) circle (  1.49);

\path[fill=fillColor] (482.08,287.28) circle (  1.49);

\path[fill=fillColor] (483.02,287.37) circle (  1.49);

\path[fill=fillColor] (482.62,287.38) circle (  1.49);

\path[fill=fillColor] (470.60,276.47) circle (  1.49);

\path[fill=fillColor] (483.32,286.83) circle (  1.49);

\path[fill=fillColor] (482.98,287.41) circle (  1.49);

\path[fill=fillColor] (483.04,287.40) circle (  1.49);

\path[fill=fillColor] (482.97,287.24) circle (  1.49);

\path[fill=fillColor] (482.86,287.20) circle (  1.49);

\path[fill=fillColor] (482.36,287.37) circle (  1.49);

\path[fill=fillColor] (482.90,287.35) circle (  1.49);

\path[fill=fillColor] (482.30,287.48) circle (  1.49);

\path[fill=fillColor] (479.48,287.21) circle (  1.49);

\path[fill=fillColor] (482.16,287.37) circle (  1.49);

\path[fill=fillColor] (482.94,287.35) circle (  1.49);

\path[fill=fillColor] (482.78,287.43) circle (  1.49);

\path[fill=fillColor] (477.27,285.98) circle (  1.49);

\path[fill=fillColor] (483.18,287.29) circle (  1.49);

\path[fill=fillColor] (482.24,287.36) circle (  1.49);

\path[fill=fillColor] (484.28,287.39) circle (  1.49);

\path[fill=fillColor] (476.90,286.55) circle (  1.49);

\path[fill=fillColor] (482.16,287.22) circle (  1.49);

\path[fill=fillColor] (480.87,287.33) circle (  1.49);

\path[fill=fillColor] (481.15,287.36) circle (  1.49);

\path[fill=fillColor] (476.93,285.56) circle (  1.49);

\path[fill=fillColor] (482.95,287.32) circle (  1.49);

\path[fill=fillColor] (482.93,287.52) circle (  1.49);

\path[fill=fillColor] (482.45,287.22) circle (  1.49);

\path[fill=fillColor] (481.59,287.19) circle (  1.49);

\path[fill=fillColor] (483.56,287.36) circle (  1.49);

\path[fill=fillColor] (481.55,286.74) circle (  1.49);

\path[fill=fillColor] (482.69,287.30) circle (  1.49);

\path[fill=fillColor] (478.35,287.73) circle (  1.49);

\path[fill=fillColor] (482.82,287.37) circle (  1.49);

\path[fill=fillColor] (482.95,287.29) circle (  1.49);

\path[fill=fillColor] (482.80,287.32) circle (  1.49);

\path[fill=fillColor] (482.62,287.35) circle (  1.49);

\path[fill=fillColor] (483.28,287.04) circle (  1.49);

\path[fill=fillColor] (482.36,287.16) circle (  1.49);

\path[fill=fillColor] (464.27,279.64) circle (  1.49);

\path[fill=fillColor] (483.17,287.31) circle (  1.49);

\path[fill=fillColor] (482.66,286.97) circle (  1.49);

\path[fill=fillColor] (486.20,284.80) circle (  1.49);

\path[fill=fillColor] (489.89,288.30) circle (  1.49);

\path[fill=fillColor] (482.23,287.12) circle (  1.49);

\path[fill=fillColor] (480.22,287.01) circle (  1.49);

\path[fill=fillColor] (482.07,287.18) circle (  1.49);

\path[fill=fillColor] (482.47,287.31) circle (  1.49);

\path[fill=fillColor] (483.26,287.36) circle (  1.49);

\path[fill=fillColor] (482.90,287.36) circle (  1.49);

\path[fill=fillColor] (479.38,286.13) circle (  1.49);

\path[fill=fillColor] (483.46,287.32) circle (  1.49);

\path[fill=fillColor] (483.63,287.35) circle (  1.49);

\path[fill=fillColor] (482.80,286.15) circle (  1.49);

\path[fill=fillColor] (480.75,285.06) circle (  1.49);

\path[fill=fillColor] (482.89,287.34) circle (  1.49);

\path[fill=fillColor] (486.51,278.64) circle (  1.49);

\path[fill=fillColor] (479.43,287.88) circle (  1.49);

\path[fill=fillColor] (483.58,288.05) circle (  1.49);

\path[fill=fillColor] (482.99,287.30) circle (  1.49);

\path[fill=fillColor] (482.91,287.29) circle (  1.49);

\path[fill=fillColor] (483.33,287.37) circle (  1.49);

\path[fill=fillColor] (482.90,287.37) circle (  1.49);

\path[fill=fillColor] (482.03,286.93) circle (  1.49);

\path[fill=fillColor] (482.80,287.26) circle (  1.49);

\path[fill=fillColor] (483.23,287.36) circle (  1.49);

\path[fill=fillColor] (513.66,277.98) circle (  1.49);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (489.72,354.55) {Coverage: 96\%};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,233.11) -- (547.89,233.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,233.11) -- (417.91,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (450.41,233.11) -- (450.41,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.90,233.11) -- (482.90,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (515.40,233.11) -- (515.40,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (547.89,233.11) -- (547.89,229.15);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (417.91,218.86) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (450.41,218.86) {0.5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (482.90,218.86) {1.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (515.40,218.86) {1.5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (547.89,218.86) {2.0};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,233.11) -- (417.91,341.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,233.11) -- (413.95,233.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,260.23) -- (413.95,260.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,287.35) -- (413.95,287.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,314.47) -- (413.95,314.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,341.59) -- (413.95,341.59);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,230.84) {0.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,257.96) {0.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,285.08) {1.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,312.20) {1.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,339.32) {2.0};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (192.72,192.72);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.79] at (104.28,173.75) {\bfseries Branch rate variance};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (104.28, 10.30) {True value};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (  7.13,100.32) {Estimated value};
\end{scope}
\begin{scope}
\path[clip] ( 32.47, 40.39) rectangle (176.09,160.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] ( 32.47, 40.39) --
	(176.09,160.25);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.92, 45.33) --
	( 49.92, 61.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.49);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.99, 40.53) --
	( 32.99, 41.60);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.55, 40.39) --
	( 32.55, 40.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.53, 40.39) --
	( 32.53, 40.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 36.02, 41.41) --
	( 36.02, 44.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.76, 40.74) --
	( 33.76, 42.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.80, 40.39) --
	( 33.80, 42.27);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.06, 41.26) --
	( 35.06, 43.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.49, 40.39) --
	( 32.49, 40.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.91, 40.51) --
	( 32.91, 42.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 36.74, 42.15) --
	( 36.74, 46.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.59, 40.39) --
	( 32.59, 40.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 51.13, 44.60) --
	( 51.13, 60.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 34.68, 41.55) --
	( 34.68, 44.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.64, 40.39) --
	( 32.64, 41.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.34, 40.64) --
	( 33.34, 42.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.54, 40.77) --
	( 33.54, 42.12);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 36.84, 41.37) --
	( 36.84, 43.88);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.60, 40.39) --
	( 32.60, 40.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.73, 41.49) --
	( 35.73, 44.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.54, 40.39) --
	( 32.54, 40.79);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.35, 40.51) --
	( 33.35, 41.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.29, 43.14) --
	( 37.29, 50.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.00, 40.39) --
	( 33.00, 41.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.94, 41.44) --
	( 35.94, 43.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.92, 40.39) --
	( 32.92, 40.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.92, 40.39) --
	( 32.92, 42.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.55, 40.39) --
	( 32.55, 40.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.60);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.51, 40.39) --
	( 32.51, 40.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 74.88, 48.38) --
	( 74.88, 88.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.63, 40.39) --
	( 32.63, 41.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.50, 40.39) --
	( 32.50, 40.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.50, 40.39) --
	( 32.50, 40.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 42.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.51, 40.39) --
	( 32.51, 40.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.49, 40.39) --
	( 32.49, 41.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.49, 40.39) --
	( 33.49, 42.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.50, 40.39) --
	( 32.50, 40.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.49, 40.39) --
	( 32.49, 40.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 41.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.42, 42.90) --
	( 40.42, 49.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.54, 40.39) --
	( 32.54, 40.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.69, 42.67) --
	( 35.69, 47.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 36.07, 41.26) --
	( 36.07, 45.52);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.01, 40.39) --
	( 33.01, 40.69);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.07, 40.39) --
	( 33.07, 40.80);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.74, 40.39) --
	( 32.74, 40.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.81, 42.69) --
	( 37.81, 47.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.50, 40.39) --
	( 32.50, 40.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.82, 40.39) --
	( 32.82, 41.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.46, 40.75) --
	( 33.46, 41.70);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.62, 40.39) --
	( 32.62, 40.58);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.79, 40.39) --
	( 33.79, 41.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.49, 40.39) --
	( 32.49, 40.53);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 96.58, 51.36) --
	( 96.58,117.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.49, 40.39) --
	( 32.49, 40.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.54, 40.39) --
	( 32.54, 40.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.50);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.75, 40.39) --
	( 32.75, 40.61);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.97, 40.52) --
	( 32.97, 41.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.84, 40.39) --
	( 32.84, 40.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 73.34, 46.98) --
	( 73.34,160.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.52, 40.39) --
	( 32.52, 40.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.47, 40.65) --
	( 33.47, 41.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.43, 44.33) --
	( 50.43, 59.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.92, 72.17) --
	( 92.92,138.60);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.39, 40.56) --
	( 33.39, 41.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 36.02, 41.27) --
	( 36.02, 46.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 47.90, 47.07) --
	( 47.90, 64.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.54, 40.39) --
	( 32.54, 40.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.52, 40.39) --
	( 32.52, 40.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.18, 43.71) --
	( 40.18, 52.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.49, 40.39) --
	( 32.49, 41.27);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.93, 41.08) --
	( 33.93, 42.30);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.39, 41.86) --
	( 35.39, 44.93);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 46.37, 46.72) --
	( 46.37, 69.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.49);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (128.22, 44.56) --
	(128.22,133.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.12, 42.73) --
	( 37.12, 47.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 34.10, 41.26) --
	( 34.10, 43.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.51, 40.39) --
	( 32.51, 40.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.49, 40.39) --
	( 32.49, 41.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.57, 40.39) --
	( 32.57, 40.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.79, 40.48) --
	( 32.79, 41.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.51, 40.39) --
	( 32.51, 40.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.52, 40.39) --
	( 32.52, 40.61);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 96.72, 47.66) --
	( 96.72, 90.93);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] ( 32.47, 40.42) circle (  1.49);

\path[fill=fillColor] ( 49.92, 52.19) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.41) circle (  1.49);

\path[fill=fillColor] ( 32.99, 41.00) circle (  1.49);

\path[fill=fillColor] ( 32.55, 40.61) circle (  1.49);

\path[fill=fillColor] ( 32.53, 40.42) circle (  1.49);

\path[fill=fillColor] ( 36.02, 42.64) circle (  1.49);

\path[fill=fillColor] ( 33.76, 41.39) circle (  1.49);

\path[fill=fillColor] ( 33.80, 40.95) circle (  1.49);

\path[fill=fillColor] ( 35.06, 42.33) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.48) circle (  1.49);

\path[fill=fillColor] ( 32.49, 40.41) circle (  1.49);

\path[fill=fillColor] ( 32.91, 41.49) circle (  1.49);

\path[fill=fillColor] ( 36.74, 43.90) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.59, 40.48) circle (  1.49);

\path[fill=fillColor] ( 51.13, 51.17) circle (  1.49);

\path[fill=fillColor] ( 34.68, 42.70) circle (  1.49);

\path[fill=fillColor] ( 32.64, 40.55) circle (  1.49);

\path[fill=fillColor] ( 33.34, 41.43) circle (  1.49);

\path[fill=fillColor] ( 33.54, 41.38) circle (  1.49);

\path[fill=fillColor] ( 36.84, 42.49) circle (  1.49);

\path[fill=fillColor] ( 32.60, 40.45) circle (  1.49);

\path[fill=fillColor] ( 35.73, 42.64) circle (  1.49);

\path[fill=fillColor] ( 32.54, 40.52) circle (  1.49);

\path[fill=fillColor] ( 33.35, 40.90) circle (  1.49);

\path[fill=fillColor] ( 37.29, 46.43) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.49) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 33.00, 40.92) circle (  1.49);

\path[fill=fillColor] ( 35.94, 42.42) circle (  1.49);

\path[fill=fillColor] ( 32.92, 40.57) circle (  1.49);

\path[fill=fillColor] ( 32.92, 40.83) circle (  1.49);

\path[fill=fillColor] ( 32.55, 40.50) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.44) circle (  1.49);

\path[fill=fillColor] ( 32.51, 40.54) circle (  1.49);

\path[fill=fillColor] ( 74.88, 64.10) circle (  1.49);

\path[fill=fillColor] ( 32.63, 40.85) circle (  1.49);

\path[fill=fillColor] ( 32.50, 40.41) circle (  1.49);

\path[fill=fillColor] ( 32.50, 40.46) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.50) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.94) circle (  1.49);

\path[fill=fillColor] ( 32.51, 40.46) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.41) circle (  1.49);

\path[fill=fillColor] ( 32.49, 40.69) circle (  1.49);

\path[fill=fillColor] ( 33.49, 41.02) circle (  1.49);

\path[fill=fillColor] ( 32.50, 40.43) circle (  1.49);

\path[fill=fillColor] ( 32.49, 40.41) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.67) circle (  1.49);

\path[fill=fillColor] ( 40.42, 45.98) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.50) circle (  1.49);

\path[fill=fillColor] ( 32.54, 40.41) circle (  1.49);

\path[fill=fillColor] ( 35.69, 44.68) circle (  1.49);

\path[fill=fillColor] ( 36.07, 43.16) circle (  1.49);

\path[fill=fillColor] ( 33.01, 40.46) circle (  1.49);

\path[fill=fillColor] ( 33.07, 40.52) circle (  1.49);

\path[fill=fillColor] ( 32.74, 40.56) circle (  1.49);

\path[fill=fillColor] ( 37.81, 44.88) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.47) circle (  1.49);

\path[fill=fillColor] ( 32.50, 40.58) circle (  1.49);

\path[fill=fillColor] ( 32.82, 40.56) circle (  1.49);

\path[fill=fillColor] ( 33.46, 41.18) circle (  1.49);

\path[fill=fillColor] ( 32.62, 40.44) circle (  1.49);

\path[fill=fillColor] ( 33.79, 40.99) circle (  1.49);

\path[fill=fillColor] ( 32.49, 40.43) circle (  1.49);

\path[fill=fillColor] ( 96.58, 81.28) circle (  1.49);

\path[fill=fillColor] ( 32.49, 40.42) circle (  1.49);

\path[fill=fillColor] ( 32.54, 40.43) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.42) circle (  1.49);

\path[fill=fillColor] ( 32.75, 40.44) circle (  1.49);

\path[fill=fillColor] ( 32.97, 40.94) circle (  1.49);

\path[fill=fillColor] ( 32.84, 40.63) circle (  1.49);

\path[fill=fillColor] ( 73.34, 93.86) circle (  1.49);

\path[fill=fillColor] ( 32.52, 40.44) circle (  1.49);

\path[fill=fillColor] ( 33.47, 40.99) circle (  1.49);

\path[fill=fillColor] ( 50.43, 50.54) circle (  1.49);

\path[fill=fillColor] ( 92.92,102.54) circle (  1.49);

\path[fill=fillColor] ( 33.39, 41.13) circle (  1.49);

\path[fill=fillColor] ( 36.02, 43.77) circle (  1.49);

\path[fill=fillColor] ( 47.90, 54.73) circle (  1.49);

\path[fill=fillColor] ( 32.54, 40.41) circle (  1.49);

\path[fill=fillColor] ( 32.52, 40.41) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.41) circle (  1.49);

\path[fill=fillColor] ( 40.18, 47.53) circle (  1.49);

\path[fill=fillColor] ( 32.49, 40.74) circle (  1.49);

\path[fill=fillColor] ( 33.93, 41.64) circle (  1.49);

\path[fill=fillColor] ( 35.39, 43.22) circle (  1.49);

\path[fill=fillColor] ( 46.37, 57.05) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.41) circle (  1.49);

\path[fill=fillColor] (128.22, 81.40) circle (  1.49);

\path[fill=fillColor] ( 37.12, 44.88) circle (  1.49);

\path[fill=fillColor] ( 34.10, 42.20) circle (  1.49);

\path[fill=fillColor] ( 32.51, 40.49) circle (  1.49);

\path[fill=fillColor] ( 32.49, 40.65) circle (  1.49);

\path[fill=fillColor] ( 32.57, 40.43) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.44) circle (  1.49);

\path[fill=fillColor] ( 32.79, 40.75) circle (  1.49);

\path[fill=fillColor] ( 32.51, 40.52) circle (  1.49);

\path[fill=fillColor] ( 32.52, 40.44) circle (  1.49);

\path[fill=fillColor] ( 96.72, 68.23) circle (  1.49);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (104.28,161.83) {Coverage: 95\%};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) -- (161.43, 40.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) -- ( 32.47, 36.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 64.71, 40.39) -- ( 64.71, 36.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 96.95, 40.39) -- ( 96.95, 36.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.19, 40.39) -- (129.19, 36.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.43, 40.39) -- (161.43, 36.43);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 32.47, 26.14) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 64.71, 26.14) {1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 96.95, 26.14) {2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (129.19, 26.14) {3};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (161.43, 26.14) {4};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) -- ( 32.47,148.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) -- ( 28.51, 40.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 67.30) -- ( 28.51, 67.30);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 94.20) -- ( 28.51, 94.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,121.11) -- ( 28.51,121.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,148.01) -- ( 28.51,148.01);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55, 38.12) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55, 65.02) {1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55, 91.93) {2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,118.83) {3};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,145.74) {4};
\end{scope}
\end{tikzpicture}

\end{document}

### 2020-09-01 RatesWCSS/WCSS_quant_cached_adaptive.tex
complete draft

% Created by tikzDevice version 0.12.3.1 on 2020-09-01 10:41:06
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (578.16,578.16);
\begin{scope}
\path[clip] (  0.00,385.44) rectangle (192.72,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.79] at (104.28,559.19) {\bfseries Tree height $h$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (104.28,395.74) {True value};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (  7.13,485.76) {Estimated value};
\end{scope}
\begin{scope}
\path[clip] ( 32.47,425.83) rectangle (176.09,545.69);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] ( 32.47,425.83) --
	(176.09,545.69);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 59.35,447.61) --
	( 59.35,449.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.26,431.45) --
	( 40.26,439.94);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 59.86,447.48) --
	( 59.86,449.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 55.07,442.95) --
	( 55.07,446.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 70.02,455.23) --
	( 70.02,458.34);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.00,438.40) --
	( 49.00,439.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 43.59,432.68) --
	( 43.59,439.94);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.36,429.42) --
	( 37.36,430.27);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.77,426.72) --
	( 33.77,427.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 41.97,432.02) --
	( 41.97,435.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 38.28,430.45) --
	( 38.28,431.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.65,435.18) --
	( 44.65,436.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 36.43,428.58) --
	( 36.43,429.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (110.38,481.82) --
	(110.38,532.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.05,434.69) --
	( 44.05,435.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 41.01,432.00) --
	( 41.01,433.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 56.87,439.72) --
	( 56.87,471.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.70,437.73) --
	( 50.70,443.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 36.13,428.66) --
	( 36.13,429.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.24,429.46) --
	( 37.24,430.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.82,438.18) --
	( 48.82,441.58);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.20,433.23) --
	( 48.20,440.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 55.23,443.59) --
	( 55.23,447.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.95,448.46) --
	( 68.95,460.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.06,439.06) --
	( 50.06,441.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 42.40,433.24) --
	( 42.40,434.60);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 38.55,430.30) --
	( 38.55,432.94);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.00,441.09) --
	( 52.00,443.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.63,454.83) --
	( 68.63,458.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 39.82,431.18) --
	( 39.82,433.04);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 45.29,437.39) --
	( 45.29,445.03);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.83,452.17) --
	( 66.83,459.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.94,426.91) --
	( 33.94,427.20);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.49,438.28) --
	( 49.49,439.95);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 39.58,431.61) --
	( 39.58,432.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 38.87,430.68) --
	( 38.87,431.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 43.93,432.40) --
	( 43.93,471.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.20,429.62) --
	( 37.20,430.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.17,446.43) --
	( 60.17,449.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.26,440.00) --
	( 50.26,441.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 62.26,450.64) --
	( 62.26,453.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.49,426.51) --
	( 33.49,426.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.38,439.07) --
	( 48.38,440.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.84,435.47) --
	( 44.84,436.53);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.91,454.56) --
	( 68.91,457.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.97,429.68) --
	( 37.97,431.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.79,431.70) --
	( 40.79,433.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 45.59,436.50) --
	( 45.59,437.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.05,435.02) --
	( 44.05,435.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.69,430.50) --
	( 40.69,434.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 38.86,430.86) --
	( 38.86,431.70);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 45.28,435.95) --
	( 45.28,437.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 41.56,431.52) --
	( 41.56,436.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 34.80,427.55) --
	( 34.80,428.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.60,428.22) --
	( 35.60,428.70);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.08,431.67) --
	( 40.08,433.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 76.66,458.91) --
	( 76.66,463.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 45.00,433.95) --
	( 45.00,440.60);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 36.74,429.00) --
	( 36.74,429.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 59.58,447.54) --
	( 59.58,449.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.07,429.17) --
	( 37.07,430.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.30,442.17) --
	( 54.30,445.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 45.05,435.79) --
	( 45.05,437.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 42.01,432.05) --
	( 42.01,435.15);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 84.96,464.12) --
	( 84.96,469.15);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.31,428.95) --
	( 40.31,439.58);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 38.72,430.74) --
	( 38.72,431.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.14,443.05) --
	( 54.14,445.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.31,438.42) --
	( 48.31,439.50);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 41.94,433.76) --
	( 41.94,434.70);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.16,432.06) --
	( 40.16,432.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 55.16,442.53) --
	( 55.16,445.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 42.07,427.02) --
	( 42.07,516.87);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 41.99,432.93) --
	( 41.99,433.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.97,449.77) --
	( 66.97,454.12);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.13,427.66) --
	( 35.13,429.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.24,434.88) --
	( 44.24,522.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 39.65,430.98) --
	( 39.65,432.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.47,428.28) --
	( 35.47,429.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 42.51,432.28) --
	( 42.51,440.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 43.32,434.47) --
	( 43.32,435.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.35,431.93) --
	( 40.35,432.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.65,441.00) --
	( 50.65,442.56);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.08,430.82) --
	( 40.08,433.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.72,429.92) --
	( 37.72,430.63);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 63.77,452.11) --
	( 63.77,460.87);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 42.95,433.55) --
	( 42.95,436.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 36.06,428.42) --
	( 36.06,432.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.39,440.44) --
	( 50.39,441.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 36.01,427.09) --
	( 36.01,439.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 41.72,431.57) --
	( 41.72,435.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.27,433.81) --
	( 44.27,441.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 38.16,429.94) --
	( 38.16,430.93);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 34.54,427.37) --
	( 34.54,427.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.49,432.39) --
	( 40.49,433.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 61.85,449.15) --
	( 61.85,452.69);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 65.11,451.25) --
	( 65.11,454.53);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.36,428.09) --
	( 35.36,428.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 36.65,429.00) --
	( 36.65,429.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.66,444.22) --
	( 58.66,490.90);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] ( 59.35,448.70) circle (  1.49);

\path[fill=fillColor] ( 40.26,435.31) circle (  1.49);

\path[fill=fillColor] ( 59.86,448.50) circle (  1.49);

\path[fill=fillColor] ( 55.07,444.62) circle (  1.49);

\path[fill=fillColor] ( 70.02,456.76) circle (  1.49);

\path[fill=fillColor] ( 49.00,439.10) circle (  1.49);

\path[fill=fillColor] ( 43.59,436.08) circle (  1.49);

\path[fill=fillColor] ( 37.36,429.83) circle (  1.49);

\path[fill=fillColor] ( 33.77,426.97) circle (  1.49);

\path[fill=fillColor] ( 41.97,433.61) circle (  1.49);

\path[fill=fillColor] ( 38.28,430.84) circle (  1.49);

\path[fill=fillColor] ( 44.65,436.04) circle (  1.49);

\path[fill=fillColor] ( 36.43,429.11) circle (  1.49);

\path[fill=fillColor] (110.38,505.74) circle (  1.49);

\path[fill=fillColor] ( 44.05,435.18) circle (  1.49);

\path[fill=fillColor] ( 41.01,432.74) circle (  1.49);

\path[fill=fillColor] ( 56.87,454.12) circle (  1.49);

\path[fill=fillColor] ( 50.70,440.25) circle (  1.49);

\path[fill=fillColor] ( 36.13,428.94) circle (  1.49);

\path[fill=fillColor] ( 37.24,429.80) circle (  1.49);

\path[fill=fillColor] ( 48.82,439.84) circle (  1.49);

\path[fill=fillColor] ( 48.20,436.62) circle (  1.49);

\path[fill=fillColor] ( 55.23,445.34) circle (  1.49);

\path[fill=fillColor] ( 68.95,454.44) circle (  1.49);

\path[fill=fillColor] ( 50.06,440.01) circle (  1.49);

\path[fill=fillColor] ( 42.40,433.92) circle (  1.49);

\path[fill=fillColor] ( 38.55,431.59) circle (  1.49);

\path[fill=fillColor] ( 52.00,442.25) circle (  1.49);

\path[fill=fillColor] ( 68.63,456.38) circle (  1.49);

\path[fill=fillColor] ( 39.82,432.10) circle (  1.49);

\path[fill=fillColor] ( 45.29,441.14) circle (  1.49);

\path[fill=fillColor] ( 66.83,455.56) circle (  1.49);

\path[fill=fillColor] ( 33.94,427.05) circle (  1.49);

\path[fill=fillColor] ( 49.49,439.12) circle (  1.49);

\path[fill=fillColor] ( 39.58,431.96) circle (  1.49);

\path[fill=fillColor] ( 38.87,431.04) circle (  1.49);

\path[fill=fillColor] ( 43.93,447.50) circle (  1.49);

\path[fill=fillColor] ( 37.20,429.95) circle (  1.49);

\path[fill=fillColor] ( 60.17,448.20) circle (  1.49);

\path[fill=fillColor] ( 50.26,440.66) circle (  1.49);

\path[fill=fillColor] ( 62.26,451.81) circle (  1.49);

\path[fill=fillColor] ( 33.49,426.69) circle (  1.49);

\path[fill=fillColor] ( 48.38,439.92) circle (  1.49);

\path[fill=fillColor] ( 44.84,436.00) circle (  1.49);

\path[fill=fillColor] ( 68.91,456.23) circle (  1.49);

\path[fill=fillColor] ( 37.97,430.50) circle (  1.49);

\path[fill=fillColor] ( 40.79,432.45) circle (  1.49);

\path[fill=fillColor] ( 45.59,437.20) circle (  1.49);

\path[fill=fillColor] ( 44.05,435.50) circle (  1.49);

\path[fill=fillColor] ( 40.69,432.29) circle (  1.49);

\path[fill=fillColor] ( 38.86,431.29) circle (  1.49);

\path[fill=fillColor] ( 45.28,436.72) circle (  1.49);

\path[fill=fillColor] ( 41.56,434.14) circle (  1.49);

\path[fill=fillColor] ( 34.80,428.12) circle (  1.49);

\path[fill=fillColor] ( 35.60,428.45) circle (  1.49);

\path[fill=fillColor] ( 40.08,432.35) circle (  1.49);

\path[fill=fillColor] ( 76.66,461.26) circle (  1.49);

\path[fill=fillColor] ( 45.00,437.05) circle (  1.49);

\path[fill=fillColor] ( 36.74,429.28) circle (  1.49);

\path[fill=fillColor] ( 59.58,448.64) circle (  1.49);

\path[fill=fillColor] ( 37.07,429.97) circle (  1.49);

\path[fill=fillColor] ( 54.30,443.78) circle (  1.49);

\path[fill=fillColor] ( 45.05,436.52) circle (  1.49);

\path[fill=fillColor] ( 42.01,433.61) circle (  1.49);

\path[fill=fillColor] ( 84.96,466.59) circle (  1.49);

\path[fill=fillColor] ( 40.31,433.27) circle (  1.49);

\path[fill=fillColor] ( 38.72,431.05) circle (  1.49);

\path[fill=fillColor] ( 54.14,444.01) circle (  1.49);

\path[fill=fillColor] ( 48.31,438.93) circle (  1.49);

\path[fill=fillColor] ( 41.94,434.21) circle (  1.49);

\path[fill=fillColor] ( 40.16,432.47) circle (  1.49);

\path[fill=fillColor] ( 55.16,444.15) circle (  1.49);

\path[fill=fillColor] ( 42.07,449.76) circle (  1.49);

\path[fill=fillColor] ( 41.99,433.33) circle (  1.49);

\path[fill=fillColor] ( 66.97,451.83) circle (  1.49);

\path[fill=fillColor] ( 35.13,428.66) circle (  1.49);

\path[fill=fillColor] ( 44.24,462.43) circle (  1.49);

\path[fill=fillColor] ( 39.65,431.99) circle (  1.49);

\path[fill=fillColor] ( 35.47,428.93) circle (  1.49);

\path[fill=fillColor] ( 42.51,435.99) circle (  1.49);

\path[fill=fillColor] ( 43.32,435.03) circle (  1.49);

\path[fill=fillColor] ( 40.35,432.36) circle (  1.49);

\path[fill=fillColor] ( 50.65,441.76) circle (  1.49);

\path[fill=fillColor] ( 40.08,432.22) circle (  1.49);

\path[fill=fillColor] ( 37.72,430.27) circle (  1.49);

\path[fill=fillColor] ( 63.77,456.18) circle (  1.49);

\path[fill=fillColor] ( 42.95,434.87) circle (  1.49);

\path[fill=fillColor] ( 36.06,430.27) circle (  1.49);

\path[fill=fillColor] ( 50.39,441.15) circle (  1.49);

\path[fill=fillColor] ( 36.01,431.04) circle (  1.49);

\path[fill=fillColor] ( 41.72,433.19) circle (  1.49);

\path[fill=fillColor] ( 44.27,437.05) circle (  1.49);

\path[fill=fillColor] ( 38.16,430.44) circle (  1.49);

\path[fill=fillColor] ( 34.54,427.61) circle (  1.49);

\path[fill=fillColor] ( 40.49,432.80) circle (  1.49);

\path[fill=fillColor] ( 61.85,450.88) circle (  1.49);

\path[fill=fillColor] ( 65.11,452.79) circle (  1.49);

\path[fill=fillColor] ( 35.36,428.40) circle (  1.49);

\path[fill=fillColor] ( 36.65,429.29) circle (  1.49);

\path[fill=fillColor] ( 58.66,463.72) circle (  1.49);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (104.28,547.27) {Coverage: 93\%};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,425.83) -- (153.43,425.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,425.83) -- ( 32.47,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 56.66,425.83) -- ( 56.66,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 80.85,425.83) -- ( 80.85,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (105.05,425.83) -- (105.05,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.24,425.83) -- (129.24,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.43,425.83) -- (153.43,421.87);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 32.47,411.58) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 56.66,411.58) {0.5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 80.85,411.58) {1.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (105.05,411.58) {1.5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (129.24,411.58) {2.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (153.43,411.58) {2.5};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,425.83) -- ( 32.47,526.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,425.83) -- ( 28.51,425.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,446.02) -- ( 28.51,446.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,466.21) -- ( 28.51,466.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,486.40) -- ( 28.51,486.40);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,506.59) -- ( 28.51,506.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,526.78) -- ( 28.51,526.78);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,423.56) {0.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,443.75) {0.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,463.94) {1.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,484.13) {1.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,504.32) {2.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,524.50) {2.5};
\end{scope}
\begin{scope}
\path[clip] (192.72,385.44) rectangle (385.44,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.79] at (297.00,559.19) {\bfseries Yule birth rate $\lambda$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (297.00,395.74) {True value};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (199.85,485.76) {Estimated value};
\end{scope}
\begin{scope}
\path[clip] (225.19,425.83) rectangle (368.81,545.69);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (225.19,425.83) --
	(368.81,545.69);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.80,428.58) --
	(232.80,431.61);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.69,430.84) --
	(239.69,439.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.72,427.88) --
	(228.72,430.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.29,428.97) --
	(231.29,432.35);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.77,427.13) --
	(228.77,428.57);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.55,430.33) --
	(232.55,435.40);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.81,431.00) --
	(237.81,437.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.48,435.07) --
	(240.48,445.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (286.53,459.37) --
	(286.53,501.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.16,431.90) --
	(237.16,439.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.78,434.54) --
	(240.78,444.34);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.75,431.62) --
	(239.75,438.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (244.89,440.41) --
	(244.89,457.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.72,426.66) --
	(226.72,427.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.24,429.79) --
	(231.24,434.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (241.27,434.21) --
	(241.27,443.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.06,427.64) --
	(230.06,431.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.15,429.17) --
	(232.15,433.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (263.48,441.65) --
	(263.48,460.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (246.52,434.44) --
	(246.52,444.53);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.70,430.15) --
	(234.70,434.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.15,430.37) --
	(234.15,435.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.65,428.36) --
	(229.65,431.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.12,428.20) --
	(231.12,431.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (233.78,429.86) --
	(233.78,434.34);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.22,430.77) --
	(234.22,436.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.47,435.28) --
	(239.47,447.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.02,429.65) --
	(231.02,433.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.42,427.33) --
	(228.42,428.94);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (241.72,435.52) --
	(241.72,446.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.55,428.87) --
	(230.55,432.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.75,428.25) --
	(229.75,430.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (307.02,461.00) --
	(307.02,502.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.02,429.10) --
	(232.02,432.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (238.61,432.87) --
	(238.61,440.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (241.87,433.15) --
	(241.87,441.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.75,427.01) --
	(231.75,434.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (246.12,435.62) --
	(246.12,446.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.31,428.46) --
	(230.31,431.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.46,429.26) --
	(231.46,433.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.59,427.76) --
	(229.59,429.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (287.50,476.24) --
	(287.50,538.58);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (233.17,430.48) --
	(233.17,435.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.25,431.04) --
	(235.25,436.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.89,427.24) --
	(227.89,428.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (252.58,438.69) --
	(252.58,454.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.94,433.23) --
	(239.94,441.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.23,430.23) --
	(235.23,435.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.59,431.20) --
	(235.59,437.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.79,434.51) --
	(239.79,445.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (244.20,434.68) --
	(244.20,444.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (233.38,429.78) --
	(233.38,434.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (236.78,431.29) --
	(236.78,437.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (257.67,446.53) --
	(257.67,472.60);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.43,445.20) --
	(261.43,468.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.24,432.36) --
	(237.24,439.94);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.85,427.64) --
	(228.85,429.61);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (236.03,429.68) --
	(236.03,434.60);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (243.23,437.65) --
	(243.23,450.93);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.76,427.90) --
	(228.76,430.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (247.28,439.07) --
	(247.28,454.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.65,428.11) --
	(230.65,430.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.34,429.93) --
	(232.34,434.49);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.48,431.58) --
	(234.48,438.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.68,426.91) --
	(227.68,428.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (245.63,431.17) --
	(245.63,451.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.64,432.94) --
	(237.64,440.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.78,428.24) --
	(229.78,430.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.60,428.93) --
	(231.60,432.36);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.15,431.06) --
	(239.15,436.96);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.17,431.09) --
	(234.17,437.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.55,428.44) --
	(231.55,431.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.89,425.99) --
	(240.89,446.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.09,431.81) --
	(240.09,438.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.70,427.38) --
	(227.70,429.06);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (254.93,442.02) --
	(254.93,465.45);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (238.29,426.27) --
	(238.29,431.74);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (238.98,433.23) --
	(238.98,441.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (257.05,444.18) --
	(257.05,467.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.37,430.60) --
	(235.37,437.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.08,430.93) --
	(237.08,436.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (241.09,432.05) --
	(241.09,439.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.08,428.83) --
	(232.08,432.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (243.28,433.04) --
	(243.28,442.04);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (241.33,434.97) --
	(241.33,445.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.80,427.31) --
	(227.80,429.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.34,430.55) --
	(235.34,435.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (252.77,437.42) --
	(252.77,457.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.09,428.07) --
	(229.09,430.56);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (254.36,428.83) --
	(254.36,469.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.07,430.58) --
	(234.07,436.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.87,429.90) --
	(234.87,434.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (248.50,437.32) --
	(248.50,450.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.00,453.45) --
	(261.00,485.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.83,432.03) --
	(239.83,439.09);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.90,428.69) --
	(228.90,431.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.40,427.44) --
	(228.40,429.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (275.24,447.48) --
	(275.24,472.58);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (242.74,438.13) --
	(242.74,452.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.30,427.04) --
	(229.30,430.28);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] (232.80,430.08) circle (  1.49);

\path[fill=fillColor] (239.69,434.81) circle (  1.49);

\path[fill=fillColor] (228.72,429.02) circle (  1.49);

\path[fill=fillColor] (231.29,430.56) circle (  1.49);

\path[fill=fillColor] (228.77,427.84) circle (  1.49);

\path[fill=fillColor] (232.55,432.73) circle (  1.49);

\path[fill=fillColor] (237.81,434.32) circle (  1.49);

\path[fill=fillColor] (240.48,440.35) circle (  1.49);

\path[fill=fillColor] (286.53,480.29) circle (  1.49);

\path[fill=fillColor] (237.16,435.43) circle (  1.49);

\path[fill=fillColor] (240.78,439.31) circle (  1.49);

\path[fill=fillColor] (239.75,434.77) circle (  1.49);

\path[fill=fillColor] (244.89,448.74) circle (  1.49);

\path[fill=fillColor] (226.72,427.11) circle (  1.49);

\path[fill=fillColor] (231.24,431.97) circle (  1.49);

\path[fill=fillColor] (241.27,438.94) circle (  1.49);

\path[fill=fillColor] (230.06,429.41) circle (  1.49);

\path[fill=fillColor] (232.15,431.10) circle (  1.49);

\path[fill=fillColor] (263.48,450.77) circle (  1.49);

\path[fill=fillColor] (246.52,439.49) circle (  1.49);

\path[fill=fillColor] (234.70,432.46) circle (  1.49);

\path[fill=fillColor] (234.15,432.93) circle (  1.49);

\path[fill=fillColor] (229.65,429.72) circle (  1.49);

\path[fill=fillColor] (231.12,429.62) circle (  1.49);

\path[fill=fillColor] (233.78,432.03) circle (  1.49);

\path[fill=fillColor] (234.22,433.33) circle (  1.49);

\path[fill=fillColor] (239.47,441.03) circle (  1.49);

\path[fill=fillColor] (231.02,431.72) circle (  1.49);

\path[fill=fillColor] (228.42,428.09) circle (  1.49);

\path[fill=fillColor] (241.72,440.72) circle (  1.49);

\path[fill=fillColor] (230.55,430.53) circle (  1.49);

\path[fill=fillColor] (229.75,429.61) circle (  1.49);

\path[fill=fillColor] (307.02,480.88) circle (  1.49);

\path[fill=fillColor] (232.02,430.91) circle (  1.49);

\path[fill=fillColor] (238.61,436.56) circle (  1.49);

\path[fill=fillColor] (241.87,437.10) circle (  1.49);

\path[fill=fillColor] (231.75,430.83) circle (  1.49);

\path[fill=fillColor] (246.12,440.99) circle (  1.49);

\path[fill=fillColor] (230.31,429.92) circle (  1.49);

\path[fill=fillColor] (231.46,431.16) circle (  1.49);

\path[fill=fillColor] (229.59,428.81) circle (  1.49);

\path[fill=fillColor] (287.50,505.74) circle (  1.49);

\path[fill=fillColor] (233.17,432.95) circle (  1.49);

\path[fill=fillColor] (235.25,433.80) circle (  1.49);

\path[fill=fillColor] (227.89,428.01) circle (  1.49);

\path[fill=fillColor] (252.58,446.23) circle (  1.49);

\path[fill=fillColor] (239.94,437.07) circle (  1.49);

\path[fill=fillColor] (235.23,432.67) circle (  1.49);

\path[fill=fillColor] (235.59,434.02) circle (  1.49);

\path[fill=fillColor] (239.79,439.68) circle (  1.49);

\path[fill=fillColor] (244.20,439.72) circle (  1.49);

\path[fill=fillColor] (233.38,431.90) circle (  1.49);

\path[fill=fillColor] (236.78,434.43) circle (  1.49);

\path[fill=fillColor] (257.67,458.82) circle (  1.49);

\path[fill=fillColor] (261.43,456.33) circle (  1.49);

\path[fill=fillColor] (237.24,436.07) circle (  1.49);

\path[fill=fillColor] (228.85,428.58) circle (  1.49);

\path[fill=fillColor] (236.03,432.01) circle (  1.49);

\path[fill=fillColor] (243.23,443.87) circle (  1.49);

\path[fill=fillColor] (228.76,429.00) circle (  1.49);

\path[fill=fillColor] (247.28,446.08) circle (  1.49);

\path[fill=fillColor] (230.65,429.38) circle (  1.49);

\path[fill=fillColor] (232.34,432.12) circle (  1.49);

\path[fill=fillColor] (234.48,434.80) circle (  1.49);

\path[fill=fillColor] (227.68,427.50) circle (  1.49);

\path[fill=fillColor] (245.63,441.15) circle (  1.49);

\path[fill=fillColor] (237.64,436.82) circle (  1.49);

\path[fill=fillColor] (229.78,429.51) circle (  1.49);

\path[fill=fillColor] (231.60,430.58) circle (  1.49);

\path[fill=fillColor] (239.15,433.95) circle (  1.49);

\path[fill=fillColor] (234.17,433.97) circle (  1.49);

\path[fill=fillColor] (231.55,429.88) circle (  1.49);

\path[fill=fillColor] (240.89,433.95) circle (  1.49);

\path[fill=fillColor] (240.09,435.05) circle (  1.49);

\path[fill=fillColor] (227.70,428.19) circle (  1.49);

\path[fill=fillColor] (254.93,453.15) circle (  1.49);

\path[fill=fillColor] (238.29,429.03) circle (  1.49);

\path[fill=fillColor] (238.98,437.29) circle (  1.49);

\path[fill=fillColor] (257.05,455.51) circle (  1.49);

\path[fill=fillColor] (235.37,434.05) circle (  1.49);

\path[fill=fillColor] (237.08,433.71) circle (  1.49);

\path[fill=fillColor] (241.09,435.66) circle (  1.49);

\path[fill=fillColor] (232.08,430.45) circle (  1.49);

\path[fill=fillColor] (243.28,437.44) circle (  1.49);

\path[fill=fillColor] (241.33,440.16) circle (  1.49);

\path[fill=fillColor] (227.80,428.15) circle (  1.49);

\path[fill=fillColor] (235.34,433.14) circle (  1.49);

\path[fill=fillColor] (252.77,446.89) circle (  1.49);

\path[fill=fillColor] (229.09,429.30) circle (  1.49);

\path[fill=fillColor] (254.36,449.14) circle (  1.49);

\path[fill=fillColor] (234.07,433.47) circle (  1.49);

\path[fill=fillColor] (234.87,432.23) circle (  1.49);

\path[fill=fillColor] (248.50,443.56) circle (  1.49);

\path[fill=fillColor] (261.00,468.81) circle (  1.49);

\path[fill=fillColor] (239.83,435.53) circle (  1.49);

\path[fill=fillColor] (228.90,430.20) circle (  1.49);

\path[fill=fillColor] (228.40,428.30) circle (  1.49);

\path[fill=fillColor] (275.24,459.57) circle (  1.49);

\path[fill=fillColor] (242.74,444.89) circle (  1.49);

\path[fill=fillColor] (229.30,428.64) circle (  1.49);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (297.00,547.27) {Coverage: 95\%};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,425.83) -- (340.32,425.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,425.83) -- (225.19,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (263.57,425.83) -- (263.57,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (301.94,425.83) -- (301.94,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (340.32,425.83) -- (340.32,421.87);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (225.19,411.58) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (263.57,411.58) {50};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (301.94,411.58) {100};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (340.32,411.58) {150};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,425.83) -- (225.19,521.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,425.83) -- (221.23,425.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,457.86) -- (221.23,457.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,489.88) -- (221.23,489.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,521.91) -- (221.23,521.91);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,423.56) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,455.59) {50};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,487.61) {100};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,519.64) {150};
\end{scope}
\begin{scope}
\path[clip] (385.44,385.44) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.79] at (489.72,559.19) {\bfseries HKY model $\kappa$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (489.72,395.74) {True value};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (392.57,485.76) {Estimated value};
\end{scope}
\begin{scope}
\path[clip] (417.91,425.83) rectangle (561.53,545.69);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (417.91,425.83) --
	(561.53,545.69);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.03,426.70) --
	(419.03,426.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (465.54,459.67) --
	(465.54,469.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.24,432.35) --
	(426.24,432.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.79,426.50) --
	(418.79,426.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.17,437.95) --
	(433.17,439.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.65,427.96) --
	(420.65,428.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (422.68,429.74) --
	(422.68,430.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.90,430.22) --
	(423.90,431.09);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (440.37,441.88) --
	(440.37,451.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.38,426.99) --
	(419.38,427.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.69,428.62) --
	(421.69,429.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.32,427.73) --
	(420.32,428.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (424.25,430.48) --
	(424.25,431.56);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.48,428.61) --
	(421.48,428.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.34,426.95) --
	(419.34,427.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.36,427.66) --
	(420.36,427.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (428.96,434.68) --
	(428.96,435.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.41,427.76) --
	(420.41,427.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (508.96,484.50) --
	(508.96,526.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.75,427.23) --
	(419.75,427.49);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.81,427.36) --
	(419.81,427.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.77,428.75) --
	(421.77,429.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (422.37,429.30) --
	(422.37,429.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (430.81,436.58) --
	(430.81,437.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.00,429.67) --
	(423.00,430.15);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.22,426.09) --
	(418.22,426.17);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.55,428.53) --
	(421.55,429.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (425.89,432.16) --
	(425.89,432.97);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.89,426.66) --
	(418.89,426.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.02,428.46) --
	(421.02,428.96);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.69,428.13) --
	(420.69,428.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.16,426.00) --
	(418.16,426.06);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.82,429.76) --
	(423.82,431.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (422.63,429.59) --
	(422.63,430.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (422.27,429.22) --
	(422.27,429.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.48,428.54) --
	(421.48,428.98);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.09,426.84) --
	(419.09,427.00);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.44,432.32) --
	(426.44,433.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (424.73,431.17) --
	(424.73,431.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.52,427.89) --
	(420.52,428.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (425.21,431.69) --
	(425.21,432.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.89,432.18) --
	(426.89,435.56);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.90,432.85) --
	(426.90,433.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.67,426.40) --
	(418.67,426.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (450.47,451.60) --
	(450.47,454.69);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.91,433.09) --
	(427.91,434.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (429.09,434.49) --
	(429.09,436.06);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.96,427.43) --
	(419.96,427.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.47,427.84) --
	(420.47,428.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (451.31,450.90) --
	(451.31,459.45);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.58,427.25) --
	(419.58,427.52);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (428.25,434.08) --
	(428.25,435.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.15,426.83) --
	(419.15,426.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (425.46,431.20) --
	(425.46,432.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.22,427.55) --
	(420.22,428.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (425.49,431.41) --
	(425.49,432.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (422.37,429.31) --
	(422.37,429.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.01,427.51) --
	(420.01,427.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.65,427.10) --
	(419.65,427.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.21,426.04) --
	(418.21,426.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.68,426.40) --
	(418.68,426.58);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.80,430.55) --
	(423.80,431.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (453.16,451.64) --
	(453.16,456.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.49,430.09) --
	(423.49,430.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (447.60,449.25) --
	(447.60,451.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.79,426.47) --
	(418.79,426.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.93,427.43) --
	(419.93,427.69);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.66,426.39) --
	(418.66,426.49);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.14,428.36) --
	(421.14,428.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.76,427.97) --
	(420.76,428.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (422.62,429.40) --
	(422.62,429.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.50,428.74) --
	(421.50,429.04);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (425.09,431.16) --
	(425.09,432.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (425.84,431.86) --
	(425.84,432.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.81,426.57) --
	(418.81,426.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (434.39,436.79) --
	(434.39,440.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.22,428.36) --
	(421.22,428.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (440.95,444.24) --
	(440.95,448.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (448.11,447.41) --
	(448.11,457.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.39,426.19) --
	(418.39,426.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (425.39,431.62) --
	(425.39,432.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (459.52,460.41) --
	(459.52,470.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.47,428.69) --
	(421.47,429.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.41,432.37) --
	(426.41,433.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.82,433.29) --
	(427.82,434.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.74,427.29) --
	(419.74,427.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.62,432.63) --
	(426.62,433.60);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.75,428.00) --
	(420.75,428.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (436.47,440.22) --
	(436.47,441.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.53,428.73) --
	(421.53,429.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (435.57,439.19) --
	(435.57,441.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.13,427.58) --
	(420.13,427.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.39,433.41) --
	(427.39,435.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (424.19,430.40) --
	(424.19,431.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.60,428.78) --
	(421.60,429.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.12,429.90) --
	(423.12,430.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.89,428.99) --
	(421.89,429.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (424.91,430.49) --
	(424.91,431.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.33,426.12) --
	(418.33,426.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (422.08,429.11) --
	(422.08,429.48);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] (419.03,426.76) circle (  1.49);

\path[fill=fillColor] (465.54,464.87) circle (  1.49);

\path[fill=fillColor] (426.24,432.65) circle (  1.49);

\path[fill=fillColor] (418.79,426.56) circle (  1.49);

\path[fill=fillColor] (433.17,438.64) circle (  1.49);

\path[fill=fillColor] (420.65,428.10) circle (  1.49);

\path[fill=fillColor] (422.68,430.03) circle (  1.49);

\path[fill=fillColor] (423.90,430.66) circle (  1.49);

\path[fill=fillColor] (440.37,446.76) circle (  1.49);

\path[fill=fillColor] (419.38,427.09) circle (  1.49);

\path[fill=fillColor] (421.69,428.87) circle (  1.49);

\path[fill=fillColor] (420.32,427.88) circle (  1.49);

\path[fill=fillColor] (424.25,431.02) circle (  1.49);

\path[fill=fillColor] (421.48,428.75) circle (  1.49);

\path[fill=fillColor] (419.34,427.03) circle (  1.49);

\path[fill=fillColor] (420.36,427.82) circle (  1.49);

\path[fill=fillColor] (428.96,435.22) circle (  1.49);

\path[fill=fillColor] (420.41,427.88) circle (  1.49);

\path[fill=fillColor] (508.96,505.74) circle (  1.49);

\path[fill=fillColor] (419.75,427.36) circle (  1.49);

\path[fill=fillColor] (419.81,427.46) circle (  1.49);

\path[fill=fillColor] (421.77,428.94) circle (  1.49);

\path[fill=fillColor] (422.37,429.48) circle (  1.49);

\path[fill=fillColor] (430.81,437.25) circle (  1.49);

\path[fill=fillColor] (423.00,429.91) circle (  1.49);

\path[fill=fillColor] (418.22,426.13) circle (  1.49);

\path[fill=fillColor] (421.55,428.79) circle (  1.49);

\path[fill=fillColor] (425.89,432.56) circle (  1.49);

\path[fill=fillColor] (418.89,426.71) circle (  1.49);

\path[fill=fillColor] (421.02,428.71) circle (  1.49);

\path[fill=fillColor] (420.69,428.25) circle (  1.49);

\path[fill=fillColor] (418.16,426.03) circle (  1.49);

\path[fill=fillColor] (423.82,430.51) circle (  1.49);

\path[fill=fillColor] (422.63,429.80) circle (  1.49);

\path[fill=fillColor] (422.27,429.48) circle (  1.49);

\path[fill=fillColor] (421.48,428.76) circle (  1.49);

\path[fill=fillColor] (419.09,426.92) circle (  1.49);

\path[fill=fillColor] (426.44,433.02) circle (  1.49);

\path[fill=fillColor] (424.73,431.46) circle (  1.49);

\path[fill=fillColor] (420.52,428.01) circle (  1.49);

\path[fill=fillColor] (425.21,431.97) circle (  1.49);

\path[fill=fillColor] (426.89,433.85) circle (  1.49);

\path[fill=fillColor] (426.90,433.36) circle (  1.49);

\path[fill=fillColor] (418.67,426.45) circle (  1.49);

\path[fill=fillColor] (450.47,453.15) circle (  1.49);

\path[fill=fillColor] (427.91,433.96) circle (  1.49);

\path[fill=fillColor] (429.09,435.23) circle (  1.49);

\path[fill=fillColor] (419.96,427.54) circle (  1.49);

\path[fill=fillColor] (420.47,427.97) circle (  1.49);

\path[fill=fillColor] (451.31,455.23) circle (  1.49);

\path[fill=fillColor] (419.58,427.39) circle (  1.49);

\path[fill=fillColor] (428.25,434.62) circle (  1.49);

\path[fill=fillColor] (419.15,426.91) circle (  1.49);

\path[fill=fillColor] (425.46,432.01) circle (  1.49);

\path[fill=fillColor] (420.22,427.78) circle (  1.49);

\path[fill=fillColor] (425.49,431.88) circle (  1.49);

\path[fill=fillColor] (422.37,429.48) circle (  1.49);

\path[fill=fillColor] (420.01,427.62) circle (  1.49);

\path[fill=fillColor] (419.65,427.24) circle (  1.49);

\path[fill=fillColor] (418.21,426.07) circle (  1.49);

\path[fill=fillColor] (418.68,426.49) circle (  1.49);

\path[fill=fillColor] (423.80,430.79) circle (  1.49);

\path[fill=fillColor] (453.16,454.16) circle (  1.49);

\path[fill=fillColor] (423.49,430.41) circle (  1.49);

\path[fill=fillColor] (447.60,450.46) circle (  1.49);

\path[fill=fillColor] (418.79,426.57) circle (  1.49);

\path[fill=fillColor] (419.93,427.56) circle (  1.49);

\path[fill=fillColor] (418.66,426.44) circle (  1.49);

\path[fill=fillColor] (421.14,428.49) circle (  1.49);

\path[fill=fillColor] (420.76,428.14) circle (  1.49);

\path[fill=fillColor] (422.62,429.66) circle (  1.49);

\path[fill=fillColor] (421.50,428.89) circle (  1.49);

\path[fill=fillColor] (425.09,431.79) circle (  1.49);

\path[fill=fillColor] (425.84,432.33) circle (  1.49);

\path[fill=fillColor] (418.81,426.61) circle (  1.49);

\path[fill=fillColor] (434.39,438.84) circle (  1.49);

\path[fill=fillColor] (421.22,428.51) circle (  1.49);

\path[fill=fillColor] (440.95,446.45) circle (  1.49);

\path[fill=fillColor] (448.11,452.30) circle (  1.49);

\path[fill=fillColor] (418.39,426.24) circle (  1.49);

\path[fill=fillColor] (425.39,432.03) circle (  1.49);

\path[fill=fillColor] (459.52,465.57) circle (  1.49);

\path[fill=fillColor] (421.47,428.84) circle (  1.49);

\path[fill=fillColor] (426.41,432.94) circle (  1.49);

\path[fill=fillColor] (427.82,434.05) circle (  1.49);

\path[fill=fillColor] (419.74,427.37) circle (  1.49);

\path[fill=fillColor] (426.62,433.12) circle (  1.49);

\path[fill=fillColor] (420.75,428.26) circle (  1.49);

\path[fill=fillColor] (436.47,441.04) circle (  1.49);

\path[fill=fillColor] (421.53,429.20) circle (  1.49);

\path[fill=fillColor] (435.57,440.31) circle (  1.49);

\path[fill=fillColor] (420.13,427.69) circle (  1.49);

\path[fill=fillColor] (427.39,434.26) circle (  1.49);

\path[fill=fillColor] (424.19,431.18) circle (  1.49);

\path[fill=fillColor] (421.60,429.00) circle (  1.49);

\path[fill=fillColor] (423.12,430.13) circle (  1.49);

\path[fill=fillColor] (421.89,429.13) circle (  1.49);

\path[fill=fillColor] (424.91,431.18) circle (  1.49);

\path[fill=fillColor] (418.33,426.18) circle (  1.49);

\path[fill=fillColor] (422.08,429.29) circle (  1.49);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (489.72,547.27) {Coverage: 95\%};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,425.83) -- (547.77,425.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,425.83) -- (417.91,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (436.46,425.83) -- (436.46,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (455.01,425.83) -- (455.01,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (473.56,425.83) -- (473.56,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (492.11,425.83) -- (492.11,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (510.67,425.83) -- (510.67,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (529.22,425.83) -- (529.22,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (547.77,425.83) -- (547.77,421.87);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (417.91,411.58) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (436.46,411.58) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (455.01,411.58) {20};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (473.56,411.58) {30};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (492.11,411.58) {40};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (510.67,411.58) {50};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (529.22,411.58) {60};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (547.77,411.58) {70};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,425.83) -- (417.91,534.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,425.83) -- (413.95,425.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,441.31) -- (413.95,441.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,456.80) -- (413.95,456.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,472.28) -- (413.95,472.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,487.76) -- (413.95,487.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,503.24) -- (413.95,503.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,518.72) -- (413.95,518.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,534.20) -- (413.95,534.20);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,423.56) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,439.04) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,454.52) {20};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,470.00) {30};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,485.49) {40};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,500.97) {50};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,516.45) {60};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,531.93) {70};
\end{scope}
\begin{scope}
\path[clip] (  0.00,192.72) rectangle (192.72,385.44);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.79] at (104.28,366.47) {\bfseries Nucleotide frequency $f$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (104.28,203.02) {True value};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (  7.13,293.04) {Estimated value};
\end{scope}
\begin{scope}
\path[clip] ( 32.47,233.11) rectangle (176.09,352.97);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] ( 32.47,233.11) --
	(176.09,352.97);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 59.33,254.08) --
	( 59.33,256.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 80.63,271.74) --
	( 80.63,275.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 73.17,266.71) --
	( 73.17,269.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (105.94,291.97) --
	(105.94,295.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 93.16,281.84) --
	( 93.16,284.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 84.94,275.30) --
	( 84.94,279.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (113.56,296.56) --
	(113.56,301.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (113.44,297.60) --
	(113.44,303.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 98.84,285.56) --
	( 98.84,292.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 85.32,275.04) --
	( 85.32,279.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (118.66,301.28) --
	(118.66,306.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 73.87,264.55) --
	( 73.87,268.22);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 86.25,271.76) --
	( 86.25,276.98);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.81,268.83) --
	( 75.81,270.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 80.91,272.07) --
	( 80.91,275.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.58,303.49) --
	(120.58,309.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.58,256.44) --
	( 60.58,258.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 88.33,277.33) --
	( 88.33,280.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (106.44,293.72) --
	(106.44,300.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (104.72,290.82) --
	(104.72,296.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 72.16,264.69) --
	( 72.16,267.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.42,282.20) --
	( 92.42,286.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (111.46,295.79) --
	(111.46,299.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 84.18,273.96) --
	( 84.18,277.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.21,280.57) --
	( 92.21,284.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 96.43,285.22) --
	( 96.43,289.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (108.28,291.45) --
	(108.28,297.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.31,261.26) --
	( 68.31,264.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 97.56,285.25) --
	( 97.56,288.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (103.51,290.19) --
	(103.51,295.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 90.43,280.32) --
	( 90.43,283.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (127.53,310.97) --
	(127.53,314.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 94.65,282.42) --
	( 94.65,288.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.94,255.34) --
	( 60.94,257.90);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.35,289.98) --
	(100.35,294.88);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (101.15,288.35) --
	(101.15,293.49);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 81.01,270.90) --
	( 81.01,274.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (107.92,292.85) --
	(107.92,298.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.71,267.54) --
	( 75.71,270.56);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 94.59,282.13) --
	( 94.59,285.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 82.61,272.60) --
	( 82.61,275.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 88.63,276.72) --
	( 88.63,283.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.65,286.81) --
	( 99.65,291.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 85.76,275.12) --
	( 85.76,279.06);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 65.99,259.09) --
	( 65.99,261.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 84.46,273.24) --
	( 84.46,278.49);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.45,293.44) --
	(109.45,298.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 72.35,263.72) --
	( 72.35,267.04);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (103.12,289.90) --
	(103.12,294.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 74.86,266.38) --
	( 74.86,271.24);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.79,300.74) --
	(120.79,306.24);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.24,283.37) --
	( 95.24,287.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 73.27,264.69) --
	( 73.27,268.22);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (114.10,294.78) --
	(114.10,301.21);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.07,279.75) --
	( 92.07,285.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.88,289.47) --
	(100.88,294.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 86.56,276.10) --
	( 86.56,278.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 77.50,269.33) --
	( 77.50,272.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 86.33,275.25) --
	( 86.33,280.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.99,298.27) --
	(112.99,301.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 65.83,258.04) --
	( 65.83,262.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.11,283.39) --
	( 95.11,286.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (102.89,290.21) --
	(102.89,294.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 78.35,268.59) --
	( 78.35,272.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 94.74,284.09) --
	( 94.74,286.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 84.73,273.90) --
	( 84.73,279.15);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (106.49,289.89) --
	(106.49,294.77);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 70.57,264.41) --
	( 70.57,267.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 74.28,266.55) --
	( 74.28,269.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 96.10,284.68) --
	( 96.10,289.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.57,278.04) --
	( 89.57,282.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (104.46,291.30) --
	(104.46,295.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 74.89,266.30) --
	( 74.89,270.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.71,294.80) --
	(109.71,299.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 65.25,260.21) --
	( 65.25,262.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 72.62,263.65) --
	( 72.62,269.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.70,279.70) --
	( 89.70,283.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 93.56,281.90) --
	( 93.56,286.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (104.61,290.60) --
	(104.61,296.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.69,274.56) --
	( 83.69,278.56);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.63,283.67) --
	( 95.63,288.09);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.36,277.96) --
	( 89.36,283.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (113.82,299.81) --
	(113.82,303.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (103.23,288.47) --
	(103.23,293.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (111.99,298.59) --
	(111.99,304.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 79.13,269.61) --
	( 79.13,272.09);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 87.62,277.54) --
	( 87.62,281.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 74.64,265.27) --
	( 74.64,270.06);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 76.40,268.70) --
	( 76.40,271.45);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 81.22,273.88) --
	( 81.22,279.93);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 71.59,264.18) --
	( 71.59,267.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.62,295.48) --
	(109.62,299.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 73.11,264.80) --
	( 73.11,269.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 84.90,274.47) --
	( 84.90,280.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 85.86,275.99) --
	( 85.86,280.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 82.66,273.44) --
	( 82.66,276.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 72.60,266.22) --
	( 72.60,268.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 93.20,281.16) --
	( 93.20,287.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (103.32,290.70) --
	(103.32,296.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 64.04,258.94) --
	( 64.04,261.45);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] ( 59.33,255.22) circle (  1.49);

\path[fill=fillColor] ( 80.63,273.70) circle (  1.49);

\path[fill=fillColor] ( 73.17,268.05) circle (  1.49);

\path[fill=fillColor] (105.94,293.98) circle (  1.49);

\path[fill=fillColor] ( 93.16,282.98) circle (  1.49);

\path[fill=fillColor] ( 84.94,277.19) circle (  1.49);

\path[fill=fillColor] (113.56,299.21) circle (  1.49);

\path[fill=fillColor] (113.44,300.47) circle (  1.49);

\path[fill=fillColor] ( 98.84,288.83) circle (  1.49);

\path[fill=fillColor] ( 85.32,277.06) circle (  1.49);

\path[fill=fillColor] (118.66,304.11) circle (  1.49);

\path[fill=fillColor] ( 73.87,266.38) circle (  1.49);

\path[fill=fillColor] ( 86.25,274.44) circle (  1.49);

\path[fill=fillColor] ( 75.81,269.77) circle (  1.49);

\path[fill=fillColor] ( 80.91,273.81) circle (  1.49);

\path[fill=fillColor] (120.58,306.20) circle (  1.49);

\path[fill=fillColor] ( 60.58,257.59) circle (  1.49);

\path[fill=fillColor] ( 88.33,279.15) circle (  1.49);

\path[fill=fillColor] (106.44,296.80) circle (  1.49);

\path[fill=fillColor] (104.72,293.47) circle (  1.49);

\path[fill=fillColor] ( 72.16,266.32) circle (  1.49);

\path[fill=fillColor] ( 92.42,284.17) circle (  1.49);

\path[fill=fillColor] (111.46,297.60) circle (  1.49);

\path[fill=fillColor] ( 84.18,275.50) circle (  1.49);

\path[fill=fillColor] ( 92.21,282.50) circle (  1.49);

\path[fill=fillColor] ( 96.43,287.31) circle (  1.49);

\path[fill=fillColor] (108.28,294.22) circle (  1.49);

\path[fill=fillColor] ( 68.31,262.72) circle (  1.49);

\path[fill=fillColor] ( 97.56,286.66) circle (  1.49);

\path[fill=fillColor] (103.51,292.77) circle (  1.49);

\path[fill=fillColor] ( 90.43,282.06) circle (  1.49);

\path[fill=fillColor] (127.53,313.02) circle (  1.49);

\path[fill=fillColor] ( 94.65,285.65) circle (  1.49);

\path[fill=fillColor] ( 60.94,256.66) circle (  1.49);

\path[fill=fillColor] (100.35,292.39) circle (  1.49);

\path[fill=fillColor] (101.15,290.82) circle (  1.49);

\path[fill=fillColor] ( 81.01,272.68) circle (  1.49);

\path[fill=fillColor] (107.92,295.57) circle (  1.49);

\path[fill=fillColor] ( 75.71,269.04) circle (  1.49);

\path[fill=fillColor] ( 94.59,283.98) circle (  1.49);

\path[fill=fillColor] ( 82.61,274.05) circle (  1.49);

\path[fill=fillColor] ( 88.63,279.95) circle (  1.49);

\path[fill=fillColor] ( 99.65,288.96) circle (  1.49);

\path[fill=fillColor] ( 85.76,277.07) circle (  1.49);

\path[fill=fillColor] ( 65.99,260.15) circle (  1.49);

\path[fill=fillColor] ( 84.46,275.80) circle (  1.49);

\path[fill=fillColor] (109.45,296.06) circle (  1.49);

\path[fill=fillColor] ( 72.35,265.31) circle (  1.49);

\path[fill=fillColor] (103.12,292.24) circle (  1.49);

\path[fill=fillColor] ( 74.86,268.86) circle (  1.49);

\path[fill=fillColor] (120.79,303.54) circle (  1.49);

\path[fill=fillColor] ( 95.24,285.31) circle (  1.49);

\path[fill=fillColor] ( 73.27,266.47) circle (  1.49);

\path[fill=fillColor] (114.10,298.07) circle (  1.49);

\path[fill=fillColor] ( 92.07,282.70) circle (  1.49);

\path[fill=fillColor] (100.88,291.71) circle (  1.49);

\path[fill=fillColor] ( 86.56,277.46) circle (  1.49);

\path[fill=fillColor] ( 77.50,271.05) circle (  1.49);

\path[fill=fillColor] ( 86.33,277.79) circle (  1.49);

\path[fill=fillColor] (112.99,300.12) circle (  1.49);

\path[fill=fillColor] ( 65.83,260.12) circle (  1.49);

\path[fill=fillColor] ( 95.11,285.13) circle (  1.49);

\path[fill=fillColor] (102.89,292.35) circle (  1.49);

\path[fill=fillColor] ( 78.35,270.69) circle (  1.49);

\path[fill=fillColor] ( 94.74,285.45) circle (  1.49);

\path[fill=fillColor] ( 84.73,276.37) circle (  1.49);

\path[fill=fillColor] (106.49,292.26) circle (  1.49);

\path[fill=fillColor] ( 70.57,265.77) circle (  1.49);

\path[fill=fillColor] ( 74.28,268.06) circle (  1.49);

\path[fill=fillColor] ( 96.10,286.96) circle (  1.49);

\path[fill=fillColor] ( 89.57,279.95) circle (  1.49);

\path[fill=fillColor] (104.46,293.11) circle (  1.49);

\path[fill=fillColor] ( 74.89,268.58) circle (  1.49);

\path[fill=fillColor] (109.71,297.28) circle (  1.49);

\path[fill=fillColor] ( 65.25,261.25) circle (  1.49);

\path[fill=fillColor] ( 72.62,266.42) circle (  1.49);

\path[fill=fillColor] ( 89.70,281.42) circle (  1.49);

\path[fill=fillColor] ( 93.56,284.18) circle (  1.49);

\path[fill=fillColor] (104.61,293.87) circle (  1.49);

\path[fill=fillColor] ( 83.69,276.64) circle (  1.49);

\path[fill=fillColor] ( 95.63,285.85) circle (  1.49);

\path[fill=fillColor] ( 89.36,280.58) circle (  1.49);

\path[fill=fillColor] (113.82,301.76) circle (  1.49);

\path[fill=fillColor] (103.23,291.03) circle (  1.49);

\path[fill=fillColor] (111.99,301.31) circle (  1.49);

\path[fill=fillColor] ( 79.13,270.89) circle (  1.49);

\path[fill=fillColor] ( 87.62,279.58) circle (  1.49);

\path[fill=fillColor] ( 74.64,267.74) circle (  1.49);

\path[fill=fillColor] ( 76.40,270.07) circle (  1.49);

\path[fill=fillColor] ( 81.22,276.89) circle (  1.49);

\path[fill=fillColor] ( 71.59,265.91) circle (  1.49);

\path[fill=fillColor] (109.62,297.52) circle (  1.49);

\path[fill=fillColor] ( 73.11,266.98) circle (  1.49);

\path[fill=fillColor] ( 84.90,277.48) circle (  1.49);

\path[fill=fillColor] ( 85.86,278.17) circle (  1.49);

\path[fill=fillColor] ( 82.66,275.14) circle (  1.49);

\path[fill=fillColor] ( 72.60,267.38) circle (  1.49);

\path[fill=fillColor] ( 93.20,284.39) circle (  1.49);

\path[fill=fillColor] (103.32,293.36) circle (  1.49);

\path[fill=fillColor] ( 64.04,260.17) circle (  1.49);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (104.28,354.55) {Coverage: 94\%};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,233.11) -- (173.40,233.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,233.11) -- ( 32.47,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 55.96,233.11) -- ( 55.96,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 79.45,233.11) -- ( 79.45,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (102.94,233.11) -- (102.94,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (126.43,233.11) -- (126.43,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (149.92,233.11) -- (149.92,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.40,233.11) -- (173.40,229.15);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 32.47,218.86) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 55.96,218.86) {0.1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 79.45,218.86) {0.2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (102.94,218.86) {0.3};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (126.43,218.86) {0.4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (149.92,218.86) {0.5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (173.40,218.86) {0.6};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,233.11) -- ( 32.47,350.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,233.11) -- ( 28.51,233.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,252.71) -- ( 28.51,252.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,272.32) -- ( 28.51,272.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,291.92) -- ( 28.51,291.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,311.52) -- ( 28.51,311.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,331.13) -- ( 28.51,331.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,350.73) -- ( 28.51,350.73);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,230.84) {0.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,250.44) {0.1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,270.04) {0.2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,289.65) {0.3};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,309.25) {0.4};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,328.85) {0.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,348.46) {0.6};
\end{scope}
\begin{scope}
\path[clip] (192.72,192.72) rectangle (385.44,385.44);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.79] at (297.00,366.47) {\bfseries Clock standard deviation $\sigma$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (297.00,203.02) {True value};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (199.85,293.04) {Estimated value};
\end{scope}
\begin{scope}
\path[clip] (225.19,233.11) rectangle (368.81,352.97);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (225.19,233.11) --
	(368.81,352.97);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.20,233.11) --
	(225.20,235.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (255.64,252.30) --
	(255.64,269.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.49,233.11) --
	(225.49,235.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.86,234.52) --
	(230.86,239.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.34,233.11) --
	(227.34,235.79);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.03,233.11) --
	(227.03,235.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (241.50,244.96) --
	(241.50,254.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.70,236.42) --
	(232.70,242.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (233.67,237.81) --
	(233.67,250.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (238.29,240.77) --
	(238.29,247.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.50,233.11) --
	(225.50,236.56);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.26,233.11) --
	(226.26,236.95);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.18,238.07) --
	(230.18,246.32);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.20,241.20) --
	(240.20,249.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.44,233.11) --
	(225.44,235.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.04,233.11) --
	(228.04,240.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (260.96,253.37) --
	(260.96,276.53);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (238.10,241.22) --
	(238.10,248.34);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.45,233.11) --
	(228.45,236.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.38,235.64) --
	(232.38,241.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.30,237.70) --
	(232.30,243.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.60,241.23) --
	(240.60,248.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.21,234.46) --
	(228.21,239.30);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (238.77,240.75) --
	(238.77,248.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.35,233.11) --
	(227.35,237.53);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.35,234.87) --
	(232.35,239.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (241.69,242.17) --
	(241.69,251.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.03,233.11) --
	(226.03,236.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.22,233.11) --
	(225.22,235.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.36,235.18) --
	(230.36,243.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.11,239.96) --
	(239.11,245.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.64,235.16) --
	(229.64,239.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.87,233.11) --
	(230.87,238.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.38,233.11) --
	(227.38,235.34);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.67,233.11) --
	(225.67,235.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.70,233.11) --
	(226.70,235.60);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (269.51,261.13) --
	(269.51,299.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.18,233.11) --
	(228.18,238.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.32,233.11) --
	(226.32,236.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.48,233.11) --
	(226.48,235.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.33,233.11) --
	(225.33,235.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.89,233.11) --
	(225.89,247.49);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.60,233.11) --
	(226.60,235.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,233.11) --
	(225.19,235.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.09,233.11) --
	(226.09,235.34);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.64,238.99) --
	(234.64,247.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.60,233.11) --
	(226.60,240.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.13,233.11) --
	(226.13,235.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.53,233.11) --
	(225.53,236.56);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (246.32,243.30) --
	(246.32,253.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.83,233.11) --
	(225.83,239.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.10,233.11) --
	(227.10,235.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (241.97,242.33) --
	(241.97,250.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (241.51,240.77) --
	(241.51,251.29);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.20,233.11) --
	(231.20,237.01);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.75,236.78) --
	(230.75,242.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.53,233.11) --
	(229.53,237.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (246.13,246.26) --
	(246.13,256.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.42,233.11) --
	(225.42,235.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.46,233.11) --
	(226.46,236.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.51,233.11) --
	(229.51,241.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.19,238.02) --
	(232.19,242.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.13,233.11) --
	(228.13,237.70);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (233.16,237.73) --
	(233.16,244.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.13,233.11) --
	(226.13,235.93);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (278.73,261.48) --
	(278.73,291.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.31,233.11) --
	(226.31,236.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.23,233.11) --
	(227.23,236.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.66,233.11) --
	(225.66,234.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.51,233.11) --
	(229.51,237.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.67,233.11) --
	(230.67,237.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.58,235.33) --
	(230.58,239.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (319.91,287.40) --
	(319.91,343.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.93,233.11) --
	(226.93,236.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.69,236.92) --
	(232.69,240.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (250.00,247.58) --
	(250.00,263.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (279.51,268.48) --
	(279.51,308.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (233.00,238.12) --
	(233.00,243.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.04,238.68) --
	(240.04,252.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (247.95,249.75) --
	(247.95,266.79);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.14,233.11) --
	(227.14,236.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.86,233.11) --
	(226.86,238.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,233.11) --
	(225.19,235.65);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (250.33,242.02) --
	(250.33,250.90);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.29,233.11) --
	(226.29,239.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.31,239.93) --
	(234.31,246.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.96,240.75) --
	(235.96,247.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (255.33,253.45) --
	(255.33,271.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.27,233.11) --
	(225.27,236.79);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (286.24,266.42) --
	(286.24,311.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (243.17,242.90) --
	(243.17,251.94);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.68,241.16) --
	(235.68,248.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.40,233.11) --
	(226.40,239.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.42,233.11) --
	(226.42,241.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.62,233.11) --
	(227.62,237.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.20,233.11) --
	(225.20,235.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.91,235.03) --
	(229.91,239.09);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.57,233.11) --
	(226.57,239.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.83,233.11) --
	(226.83,238.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (263.51,260.71) --
	(263.51,283.87);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] (225.20,233.82) circle (  1.49);

\path[fill=fillColor] (255.64,260.34) circle (  1.49);

\path[fill=fillColor] (225.49,233.97) circle (  1.49);

\path[fill=fillColor] (230.86,237.04) circle (  1.49);

\path[fill=fillColor] (227.34,234.01) circle (  1.49);

\path[fill=fillColor] (227.03,234.05) circle (  1.49);

\path[fill=fillColor] (241.50,249.64) circle (  1.49);

\path[fill=fillColor] (232.70,239.36) circle (  1.49);

\path[fill=fillColor] (233.67,243.87) circle (  1.49);

\path[fill=fillColor] (238.29,244.18) circle (  1.49);

\path[fill=fillColor] (225.50,234.28) circle (  1.49);

\path[fill=fillColor] (226.26,234.59) circle (  1.49);

\path[fill=fillColor] (230.18,242.08) circle (  1.49);

\path[fill=fillColor] (240.20,245.03) circle (  1.49);

\path[fill=fillColor] (225.44,234.08) circle (  1.49);

\path[fill=fillColor] (228.04,237.26) circle (  1.49);

\path[fill=fillColor] (260.96,264.06) circle (  1.49);

\path[fill=fillColor] (238.10,244.53) circle (  1.49);

\path[fill=fillColor] (228.45,234.28) circle (  1.49);

\path[fill=fillColor] (232.38,238.46) circle (  1.49);

\path[fill=fillColor] (232.30,240.49) circle (  1.49);

\path[fill=fillColor] (240.60,244.93) circle (  1.49);

\path[fill=fillColor] (228.21,236.75) circle (  1.49);

\path[fill=fillColor] (238.77,244.21) circle (  1.49);

\path[fill=fillColor] (227.35,235.33) circle (  1.49);

\path[fill=fillColor] (232.35,237.11) circle (  1.49);

\path[fill=fillColor] (241.69,246.45) circle (  1.49);

\path[fill=fillColor] (226.03,234.24) circle (  1.49);

\path[fill=fillColor] (225.22,234.39) circle (  1.49);

\path[fill=fillColor] (230.36,239.13) circle (  1.49);

\path[fill=fillColor] (239.11,242.67) circle (  1.49);

\path[fill=fillColor] (229.64,237.11) circle (  1.49);

\path[fill=fillColor] (230.87,234.90) circle (  1.49);

\path[fill=fillColor] (227.38,233.84) circle (  1.49);

\path[fill=fillColor] (225.67,233.84) circle (  1.49);

\path[fill=fillColor] (226.70,233.90) circle (  1.49);

\path[fill=fillColor] (269.51,277.42) circle (  1.49);

\path[fill=fillColor] (228.18,235.68) circle (  1.49);

\path[fill=fillColor] (226.32,234.96) circle (  1.49);

\path[fill=fillColor] (226.48,233.79) circle (  1.49);

\path[fill=fillColor] (225.33,233.86) circle (  1.49);

\path[fill=fillColor] (225.89,239.09) circle (  1.49);

\path[fill=fillColor] (226.60,233.96) circle (  1.49);

\path[fill=fillColor] (225.19,233.91) circle (  1.49);

\path[fill=fillColor] (226.09,233.82) circle (  1.49);

\path[fill=fillColor] (234.64,243.16) circle (  1.49);

\path[fill=fillColor] (226.60,237.34) circle (  1.49);

\path[fill=fillColor] (226.13,233.77) circle (  1.49);

\path[fill=fillColor] (225.53,234.38) circle (  1.49);

\path[fill=fillColor] (246.32,248.30) circle (  1.49);

\path[fill=fillColor] (225.83,235.98) circle (  1.49);

\path[fill=fillColor] (227.10,233.90) circle (  1.49);

\path[fill=fillColor] (241.97,245.90) circle (  1.49);

\path[fill=fillColor] (241.51,245.67) circle (  1.49);

\path[fill=fillColor] (231.20,234.33) circle (  1.49);

\path[fill=fillColor] (230.75,239.36) circle (  1.49);

\path[fill=fillColor] (229.53,235.04) circle (  1.49);

\path[fill=fillColor] (246.13,251.25) circle (  1.49);

\path[fill=fillColor] (225.42,233.84) circle (  1.49);

\path[fill=fillColor] (226.46,234.66) circle (  1.49);

\path[fill=fillColor] (229.51,237.59) circle (  1.49);

\path[fill=fillColor] (232.19,240.45) circle (  1.49);

\path[fill=fillColor] (228.13,235.36) circle (  1.49);

\path[fill=fillColor] (233.16,240.73) circle (  1.49);

\path[fill=fillColor] (226.13,234.11) circle (  1.49);

\path[fill=fillColor] (278.73,275.22) circle (  1.49);

\path[fill=fillColor] (226.31,234.20) circle (  1.49);

\path[fill=fillColor] (227.23,234.79) circle (  1.49);

\path[fill=fillColor] (225.66,233.70) circle (  1.49);

\path[fill=fillColor] (229.51,234.67) circle (  1.49);

\path[fill=fillColor] (230.67,235.69) circle (  1.49);

\path[fill=fillColor] (230.58,237.26) circle (  1.49);

\path[fill=fillColor] (319.91,313.02) circle (  1.49);

\path[fill=fillColor] (226.93,234.40) circle (  1.49);

\path[fill=fillColor] (232.69,238.84) circle (  1.49);

\path[fill=fillColor] (250.00,255.21) circle (  1.49);

\path[fill=fillColor] (279.51,286.04) circle (  1.49);

\path[fill=fillColor] (233.00,240.94) circle (  1.49);

\path[fill=fillColor] (240.04,245.33) circle (  1.49);

\path[fill=fillColor] (247.95,257.65) circle (  1.49);

\path[fill=fillColor] (227.14,234.62) circle (  1.49);

\path[fill=fillColor] (226.86,235.97) circle (  1.49);

\path[fill=fillColor] (225.19,234.01) circle (  1.49);

\path[fill=fillColor] (250.33,246.18) circle (  1.49);

\path[fill=fillColor] (226.29,236.53) circle (  1.49);

\path[fill=fillColor] (234.31,242.83) circle (  1.49);

\path[fill=fillColor] (235.96,244.19) circle (  1.49);

\path[fill=fillColor] (255.33,262.16) circle (  1.49);

\path[fill=fillColor] (225.27,234.89) circle (  1.49);

\path[fill=fillColor] (286.24,286.56) circle (  1.49);

\path[fill=fillColor] (243.17,247.23) circle (  1.49);

\path[fill=fillColor] (235.68,244.51) circle (  1.49);

\path[fill=fillColor] (226.40,235.72) circle (  1.49);

\path[fill=fillColor] (226.42,235.76) circle (  1.49);

\path[fill=fillColor] (227.62,234.85) circle (  1.49);

\path[fill=fillColor] (225.20,233.78) circle (  1.49);

\path[fill=fillColor] (229.91,236.98) circle (  1.49);

\path[fill=fillColor] (226.57,235.29) circle (  1.49);

\path[fill=fillColor] (226.83,234.91) circle (  1.49);

\path[fill=fillColor] (263.51,271.73) circle (  1.49);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (297.00,354.55) {Coverage: 97\%};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,233.11) -- (354.76,233.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,233.11) -- (225.19,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (246.79,233.11) -- (246.79,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (268.38,233.11) -- (268.38,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (289.98,233.11) -- (289.98,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (311.57,233.11) -- (311.57,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.17,233.11) -- (333.17,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (354.76,233.11) -- (354.76,229.15);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (225.19,218.86) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (246.79,218.86) {0.5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (268.38,218.86) {1.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (289.98,218.86) {1.5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (311.57,218.86) {2.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (333.17,218.86) {2.5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (354.76,218.86) {3.0};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,233.11) -- (225.19,341.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,233.11) -- (221.23,233.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,251.13) -- (221.23,251.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,269.16) -- (221.23,269.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,287.18) -- (221.23,287.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,305.20) -- (221.23,305.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,323.22) -- (221.23,323.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,341.25) -- (221.23,341.25);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,230.84) {0.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,248.86) {0.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,266.88) {1.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,284.91) {1.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,302.93) {2.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,320.95) {2.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,338.97) {3.0};
\end{scope}
\begin{scope}
\path[clip] (385.44,192.72) rectangle (578.16,385.44);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.79] at (489.72,366.47) {\bfseries Branch rate mean};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (489.72,203.02) {True value};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (392.57,293.04) {Estimated value};
\end{scope}
\begin{scope}
\path[clip] (417.91,233.11) rectangle (561.53,352.97);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (417.91,233.11) --
	(561.53,352.97);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.02,281.83) --
	(477.02,283.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (481.35,263.58) --
	(481.35,289.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.91,281.78) --
	(476.91,282.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (475.58,280.30) --
	(475.58,284.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.92,281.74) --
	(476.92,283.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.48,281.76) --
	(476.48,283.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.09,273.49) --
	(482.09,291.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.99,279.26) --
	(474.99,285.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (473.68,276.43) --
	(473.68,287.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (475.79,276.98) --
	(475.79,287.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.04,281.43) --
	(477.04,283.27);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.08,281.51) --
	(477.08,283.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (475.69,278.06) --
	(475.69,286.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.12,278.30) --
	(482.12,291.69);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.95,281.57) --
	(476.95,283.04);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.76,280.37) --
	(476.76,284.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (473.21,262.78) --
	(473.21,298.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (478.51,277.91) --
	(478.51,289.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.66,281.64) --
	(476.66,283.30);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (475.87,280.06) --
	(475.87,285.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (475.25,278.66) --
	(475.25,285.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.64,277.39) --
	(477.64,289.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.51,280.00) --
	(477.51,283.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (470.99,276.47) --
	(470.99,288.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.38,281.25) --
	(476.38,284.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.15,280.41) --
	(476.15,284.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (475.54,276.25) --
	(475.54,289.69);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.90,281.45) --
	(476.90,283.27);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.02,281.62) --
	(477.02,283.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.19,279.54) --
	(477.19,285.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (481.19,277.38) --
	(481.19,286.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.18,280.19) --
	(476.18,284.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (478.41,280.74) --
	(478.41,283.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.60,281.89) --
	(476.60,283.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.04,281.89) --
	(477.04,283.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.69,281.89) --
	(476.69,283.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (500.40,245.90) --
	(500.40,302.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.81,280.52) --
	(477.81,283.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.31,281.13) --
	(477.31,283.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.83,281.94) --
	(476.83,282.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.05,281.98) --
	(477.05,283.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.19,277.35) --
	(477.19,285.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.28,281.64) --
	(477.28,283.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.02,281.87) --
	(477.02,283.09);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.11,281.96) --
	(477.11,283.06);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.49,277.28) --
	(479.49,287.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.51,280.35) --
	(477.51,285.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.94,281.90) --
	(476.94,282.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.98,281.49) --
	(476.98,283.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.13,273.12) --
	(474.13,287.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.11,281.05) --
	(477.11,284.58);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.14,281.90) --
	(477.14,283.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.82,275.90) --
	(479.82,287.58);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (478.50,276.39) --
	(478.50,289.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.49,281.43) --
	(477.49,283.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (478.42,279.76) --
	(478.42,286.06);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (475.82,281.16) --
	(475.82,283.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.82,270.99) --
	(477.82,287.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.95,281.88) --
	(476.95,283.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.05,281.58) --
	(477.05,283.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (478.09,280.05) --
	(478.09,285.69);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (475.63,278.26) --
	(475.63,284.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.25,281.33) --
	(477.25,284.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (480.86,278.43) --
	(480.86,285.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.96,281.75) --
	(476.96,283.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (459.08,247.70) --
	(459.08,288.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.71,281.51) --
	(476.71,283.09);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.55,281.17) --
	(476.55,283.30);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.88,281.96) --
	(476.88,282.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.45,281.33) --
	(477.45,283.66);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (478.98,281.30) --
	(478.98,284.04);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.97,280.59) --
	(476.97,284.53);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (482.57,233.94) --
	(482.57,333.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.52,281.60) --
	(477.52,283.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.74,280.25) --
	(476.74,285.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (472.31,266.92) --
	(472.31,287.33);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (513.66,238.30) --
	(513.66,290.31);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.37,278.62) --
	(476.37,285.68);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (484.58,274.95) --
	(484.58,287.92);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.53,268.47) --
	(479.53,292.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.67,281.17) --
	(476.67,283.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.73,281.09) --
	(476.73,284.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.02,281.66) --
	(477.02,283.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (478.44,276.20) --
	(478.44,288.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.92,280.41) --
	(476.92,284.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (481.29,278.03) --
	(481.29,286.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.47,275.41) --
	(476.47,284.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.63,260.12) --
	(476.63,285.06);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.02,281.40) --
	(477.02,283.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (460.99,237.47) --
	(460.99,284.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (473.50,273.33) --
	(473.50,286.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.09,275.62) --
	(476.09,288.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.57,280.65) --
	(476.57,284.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.78,279.91) --
	(476.78,283.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.92,281.36) --
	(476.92,283.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.02,281.80) --
	(477.02,283.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.44,280.54) --
	(477.44,284.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.43,280.80) --
	(477.43,284.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.82,281.16) --
	(476.82,283.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (468.31,250.76) --
	(468.31,281.94);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] (477.02,282.44) circle (  1.49);

\path[fill=fillColor] (481.35,276.42) circle (  1.49);

\path[fill=fillColor] (476.91,282.41) circle (  1.49);

\path[fill=fillColor] (475.58,282.42) circle (  1.49);

\path[fill=fillColor] (476.92,282.45) circle (  1.49);

\path[fill=fillColor] (476.48,282.45) circle (  1.49);

\path[fill=fillColor] (482.09,282.31) circle (  1.49);

\path[fill=fillColor] (474.99,282.22) circle (  1.49);

\path[fill=fillColor] (473.68,281.96) circle (  1.49);

\path[fill=fillColor] (475.79,282.02) circle (  1.49);

\path[fill=fillColor] (477.04,282.40) circle (  1.49);

\path[fill=fillColor] (477.08,282.61) circle (  1.49);

\path[fill=fillColor] (475.69,282.30) circle (  1.49);

\path[fill=fillColor] (482.12,284.96) circle (  1.49);

\path[fill=fillColor] (476.95,282.38) circle (  1.49);

\path[fill=fillColor] (476.76,282.56) circle (  1.49);

\path[fill=fillColor] (473.21,280.45) circle (  1.49);

\path[fill=fillColor] (478.51,283.57) circle (  1.49);

\path[fill=fillColor] (476.66,282.44) circle (  1.49);

\path[fill=fillColor] (475.87,282.63) circle (  1.49);

\path[fill=fillColor] (475.25,282.17) circle (  1.49);

\path[fill=fillColor] (477.64,283.59) circle (  1.49);

\path[fill=fillColor] (477.51,281.98) circle (  1.49);

\path[fill=fillColor] (470.99,282.25) circle (  1.49);

\path[fill=fillColor] (476.38,282.57) circle (  1.49);

\path[fill=fillColor] (476.15,282.35) circle (  1.49);

\path[fill=fillColor] (475.54,282.91) circle (  1.49);

\path[fill=fillColor] (476.90,282.42) circle (  1.49);

\path[fill=fillColor] (477.02,282.50) circle (  1.49);

\path[fill=fillColor] (477.19,282.61) circle (  1.49);

\path[fill=fillColor] (481.19,281.96) circle (  1.49);

\path[fill=fillColor] (476.18,282.44) circle (  1.49);

\path[fill=fillColor] (478.41,282.37) circle (  1.49);

\path[fill=fillColor] (476.60,282.45) circle (  1.49);

\path[fill=fillColor] (477.04,282.45) circle (  1.49);

\path[fill=fillColor] (476.69,282.44) circle (  1.49);

\path[fill=fillColor] (500.40,276.39) circle (  1.49);

\path[fill=fillColor] (477.81,282.30) circle (  1.49);

\path[fill=fillColor] (477.31,282.35) circle (  1.49);

\path[fill=fillColor] (476.83,282.43) circle (  1.49);

\path[fill=fillColor] (477.05,282.52) circle (  1.49);

\path[fill=fillColor] (477.19,281.83) circle (  1.49);

\path[fill=fillColor] (477.28,282.43) circle (  1.49);

\path[fill=fillColor] (477.02,282.45) circle (  1.49);

\path[fill=fillColor] (477.11,282.46) circle (  1.49);

\path[fill=fillColor] (479.49,282.12) circle (  1.49);

\path[fill=fillColor] (477.51,282.73) circle (  1.49);

\path[fill=fillColor] (476.94,282.45) circle (  1.49);

\path[fill=fillColor] (476.98,282.43) circle (  1.49);

\path[fill=fillColor] (474.13,280.30) circle (  1.49);

\path[fill=fillColor] (477.11,282.73) circle (  1.49);

\path[fill=fillColor] (477.14,282.47) circle (  1.49);

\path[fill=fillColor] (479.82,282.04) circle (  1.49);

\path[fill=fillColor] (478.50,283.08) circle (  1.49);

\path[fill=fillColor] (477.49,282.45) circle (  1.49);

\path[fill=fillColor] (478.42,283.02) circle (  1.49);

\path[fill=fillColor] (475.82,282.43) circle (  1.49);

\path[fill=fillColor] (477.82,279.25) circle (  1.49);

\path[fill=fillColor] (476.95,282.45) circle (  1.49);

\path[fill=fillColor] (477.05,282.54) circle (  1.49);

\path[fill=fillColor] (478.09,282.85) circle (  1.49);

\path[fill=fillColor] (475.63,281.60) circle (  1.49);

\path[fill=fillColor] (477.25,282.67) circle (  1.49);

\path[fill=fillColor] (480.86,282.11) circle (  1.49);

\path[fill=fillColor] (476.96,282.46) circle (  1.49);

\path[fill=fillColor] (459.08,268.25) circle (  1.49);

\path[fill=fillColor] (476.71,282.38) circle (  1.49);

\path[fill=fillColor] (476.55,282.31) circle (  1.49);

\path[fill=fillColor] (476.88,282.43) circle (  1.49);

\path[fill=fillColor] (477.45,282.46) circle (  1.49);

\path[fill=fillColor] (478.98,282.59) circle (  1.49);

\path[fill=fillColor] (476.97,282.57) circle (  1.49);

\path[fill=fillColor] (482.57,273.83) circle (  1.49);

\path[fill=fillColor] (477.52,282.47) circle (  1.49);

\path[fill=fillColor] (476.74,282.74) circle (  1.49);

\path[fill=fillColor] (472.31,277.07) circle (  1.49);

\path[fill=fillColor] (513.66,265.80) circle (  1.49);

\path[fill=fillColor] (476.37,282.13) circle (  1.49);

\path[fill=fillColor] (484.58,281.67) circle (  1.49);

\path[fill=fillColor] (479.53,280.12) circle (  1.49);

\path[fill=fillColor] (476.67,282.32) circle (  1.49);

\path[fill=fillColor] (476.73,282.63) circle (  1.49);

\path[fill=fillColor] (477.02,282.42) circle (  1.49);

\path[fill=fillColor] (478.44,282.57) circle (  1.49);

\path[fill=fillColor] (476.92,282.34) circle (  1.49);

\path[fill=fillColor] (481.29,282.46) circle (  1.49);

\path[fill=fillColor] (476.47,280.13) circle (  1.49);

\path[fill=fillColor] (476.63,272.47) circle (  1.49);

\path[fill=fillColor] (477.02,282.41) circle (  1.49);

\path[fill=fillColor] (460.99,262.09) circle (  1.49);

\path[fill=fillColor] (473.50,279.78) circle (  1.49);

\path[fill=fillColor] (476.09,281.84) circle (  1.49);

\path[fill=fillColor] (476.57,282.42) circle (  1.49);

\path[fill=fillColor] (476.78,282.21) circle (  1.49);

\path[fill=fillColor] (476.92,282.43) circle (  1.49);

\path[fill=fillColor] (477.02,282.44) circle (  1.49);

\path[fill=fillColor] (477.44,282.36) circle (  1.49);

\path[fill=fillColor] (477.43,282.44) circle (  1.49);

\path[fill=fillColor] (476.82,282.49) circle (  1.49);

\path[fill=fillColor] (468.31,266.38) circle (  1.49);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (489.72,354.55) {Coverage: 97\%};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,233.11) -- (536.13,233.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,233.11) -- (417.91,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (447.47,233.11) -- (447.47,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.02,233.11) -- (477.02,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (506.58,233.11) -- (506.58,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (536.13,233.11) -- (536.13,229.15);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (417.91,218.86) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (447.47,218.86) {0.5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (477.02,218.86) {1.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (506.58,218.86) {1.5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (536.13,218.86) {2.0};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,233.11) -- (417.91,331.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,233.11) -- (413.95,233.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,257.78) -- (413.95,257.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,282.44) -- (413.95,282.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,307.11) -- (413.95,307.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,331.77) -- (413.95,331.77);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,230.84) {0.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,255.50) {0.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,280.17) {1.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,304.83) {1.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,329.50) {2.0};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (192.72,192.72);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.79] at (104.28,173.75) {\bfseries Branch rate variance};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (104.28, 10.30) {True value};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (  7.13,100.32) {Estimated value};
\end{scope}
\begin{scope}
\path[clip] ( 32.47, 40.39) rectangle (176.09,160.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] ( 32.47, 40.39) --
	(176.09,160.25);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 36.12, 41.21) --
	( 36.12, 44.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.55, 40.39) --
	( 32.55, 40.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.39, 40.88) --
	( 33.39, 42.04);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.60, 40.42) --
	( 32.60, 40.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.62, 40.43) --
	( 32.62, 41.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.93, 40.58) --
	( 32.93, 41.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.57, 40.47) --
	( 32.57, 40.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.09, 40.60) --
	( 33.09, 41.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.50, 40.39) --
	( 32.50, 40.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 34.84, 41.17) --
	( 34.84, 46.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.88, 40.61) --
	( 32.88, 41.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.51, 40.39) --
	( 32.51, 40.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.60, 40.41) --
	( 32.60, 40.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.59, 40.45) --
	( 32.59, 40.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.09, 40.62) --
	( 33.09, 41.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.50, 40.39) --
	( 32.50, 40.49);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.91, 40.58) --
	( 32.91, 41.06);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.58, 40.40) --
	( 32.58, 40.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.45, 40.67) --
	( 33.45, 41.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.54, 40.39) --
	( 32.54, 40.65);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.09, 40.55) --
	( 33.09, 40.88);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.52, 40.40) --
	( 32.52, 40.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.56, 40.39) --
	( 32.56, 40.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.49, 40.39) --
	( 32.49, 40.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 45.44, 40.48) --
	( 45.44, 58.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.49, 40.39) --
	( 32.49, 40.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 41.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.82, 40.50) --
	( 32.82, 41.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.40, 40.72) --
	( 33.40, 41.70);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.24, 40.67) --
	( 33.24, 41.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.10, 40.57) --
	( 33.10, 41.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.53, 40.39) --
	( 32.53, 40.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.53, 40.43) --
	( 32.53, 40.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.53, 40.39) --
	( 32.53, 40.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.83, 40.97) --
	( 33.83, 42.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.52, 40.39) --
	( 32.52, 40.60);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.60, 40.48) --
	( 32.60, 40.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.50, 40.39) --
	( 32.50, 40.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.71, 40.45) --
	( 32.71, 40.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.92, 40.62) --
	( 35.92, 55.34);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.40);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.53, 40.39) --
	( 32.53, 40.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.55, 40.39) --
	( 32.55, 40.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.56, 40.41) --
	( 32.56, 40.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.14, 40.40) --
	(121.14,316.06);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.59, 40.44) --
	( 32.59, 40.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.55, 40.91) --
	( 33.55, 43.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.81, 40.45) --
	( 48.81, 58.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.62, 40.48) --
	( 32.62, 40.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.96, 40.45) --
	( 32.96, 41.49);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 34.09, 41.13) --
	( 34.09, 44.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.49, 40.39) --
	( 32.49, 40.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.41);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.91, 40.65) --
	( 33.91, 41.38);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.75, 40.55) --
	( 32.75, 40.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.89, 40.58) --
	( 32.89, 41.06);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 53.60, 41.22) --
	( 53.60, 45.23);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.65, 40.40) --
	( 35.65, 65.30);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.07, 40.71) --
	( 33.07, 41.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.80, 40.63) --
	( 32.80, 41.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.49, 40.39) --
	( 32.49, 40.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.54, 40.40) --
	( 32.54, 40.49);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 41.22, 41.13) --
	( 41.22, 55.76);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 36.12, 42.75) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.55, 40.45) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.40) circle (  1.49);

\path[fill=fillColor] ( 33.39, 41.39) circle (  1.49);

\path[fill=fillColor] ( 32.60, 40.52) circle (  1.49);

\path[fill=fillColor] ( 32.62, 40.80) circle (  1.49);

\path[fill=fillColor] ( 32.93, 40.79) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.57, 40.66) circle (  1.49);

\path[fill=fillColor] ( 33.09, 40.88) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.50, 40.46) circle (  1.49);

\path[fill=fillColor] ( 34.84, 43.33) circle (  1.49);

\path[fill=fillColor] ( 32.88, 40.81) circle (  1.49);

\path[fill=fillColor] ( 32.51, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.60, 40.49) circle (  1.49);

\path[fill=fillColor] ( 32.59, 40.58) circle (  1.49);

\path[fill=fillColor] ( 33.09, 40.87) circle (  1.49);

\path[fill=fillColor] ( 32.50, 40.44) circle (  1.49);

\path[fill=fillColor] ( 32.91, 40.79) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.41) circle (  1.49);

\path[fill=fillColor] ( 32.58, 40.45) circle (  1.49);

\path[fill=fillColor] ( 33.45, 40.99) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.54, 40.52) circle (  1.49);

\path[fill=fillColor] ( 33.09, 40.70) circle (  1.49);

\path[fill=fillColor] ( 32.52, 40.45) circle (  1.49);

\path[fill=fillColor] ( 32.56, 40.41) circle (  1.49);

\path[fill=fillColor] ( 32.49, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.40) circle (  1.49);

\path[fill=fillColor] ( 45.44, 48.28) circle (  1.49);

\path[fill=fillColor] ( 32.49, 40.42) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.41) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.39) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.58) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.82, 40.73) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.46) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.39) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 33.40, 41.14) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.43) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.40) circle (  1.49);

\path[fill=fillColor] ( 33.24, 40.95) circle (  1.49);

\path[fill=fillColor] ( 33.10, 40.94) circle (  1.49);

\path[fill=fillColor] ( 32.53, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.53, 40.52) circle (  1.49);

\path[fill=fillColor] ( 32.53, 40.41) circle (  1.49);

\path[fill=fillColor] ( 33.83, 41.57) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.52, 40.47) circle (  1.49);

\path[fill=fillColor] ( 32.60, 40.57) circle (  1.49);

\path[fill=fillColor] ( 32.50, 40.41) circle (  1.49);

\path[fill=fillColor] ( 32.71, 40.59) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 35.92, 46.66) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.41) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.39) circle (  1.49);

\path[fill=fillColor] ( 32.53, 40.41) circle (  1.49);

\path[fill=fillColor] ( 32.55, 40.42) circle (  1.49);

\path[fill=fillColor] ( 32.56, 40.45) circle (  1.49);

\path[fill=fillColor] (121.14,120.30) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.59, 40.50) circle (  1.49);

\path[fill=fillColor] ( 33.55, 41.85) circle (  1.49);

\path[fill=fillColor] ( 48.81, 47.34) circle (  1.49);

\path[fill=fillColor] ( 32.62, 40.61) circle (  1.49);

\path[fill=fillColor] ( 32.96, 40.91) circle (  1.49);

\path[fill=fillColor] ( 34.09, 42.40) circle (  1.49);

\path[fill=fillColor] ( 32.49, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.42) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 33.91, 40.97) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.44) circle (  1.49);

\path[fill=fillColor] ( 32.75, 40.69) circle (  1.49);

\path[fill=fillColor] ( 32.89, 40.79) circle (  1.49);

\path[fill=fillColor] ( 53.60, 42.87) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.41) circle (  1.49);

\path[fill=fillColor] ( 35.65, 49.15) circle (  1.49);

\path[fill=fillColor] ( 33.07, 41.07) circle (  1.49);

\path[fill=fillColor] ( 32.80, 40.86) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.43) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.44) circle (  1.49);

\path[fill=fillColor] ( 32.49, 40.41) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.39) circle (  1.49);

\path[fill=fillColor] ( 32.54, 40.44) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.42) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.41) circle (  1.49);

\path[fill=fillColor] ( 41.22, 46.77) circle (  1.49);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (104.28,161.83) {Coverage: 97\%};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) -- (159.00, 40.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) -- ( 32.47, 36.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 57.78, 40.39) -- ( 57.78, 36.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.08, 40.39) -- ( 83.08, 36.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (108.39, 40.39) -- (108.39, 36.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (133.70, 40.39) -- (133.70, 36.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.00, 40.39) -- (159.00, 36.43);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 32.47, 26.14) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 57.78, 26.14) {5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 83.08, 26.14) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (108.39, 26.14) {15};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (133.70, 26.14) {20};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (159.00, 26.14) {25};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) -- ( 32.47,145.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) -- ( 28.51, 40.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 61.51) -- ( 28.51, 61.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 82.63) -- ( 28.51, 82.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,103.75) -- ( 28.51,103.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,124.87) -- ( 28.51,124.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,145.99) -- ( 28.51,145.99);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55, 38.12) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55, 59.24) {5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55, 80.36) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,101.48) {15};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,122.60) {20};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,143.72) {25};
\end{scope}
\end{tikzpicture}

\end{document}

### 2020-09-01 RatesWCSS/WCSS_real_adaptive.tex
complete draft

% Created by tikzDevice version 0.12.3.1 on 2020-09-01 10:39:43
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (578.16,578.16);
\begin{scope}
\path[clip] (  0.00,385.44) rectangle (192.72,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.79] at (104.28,559.19) {\bfseries Tree height $h$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (104.28,395.74) {True value};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (  7.13,485.76) {Estimated value};
\end{scope}
\begin{scope}
\path[clip] ( 32.47,425.83) rectangle (176.09,545.69);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] ( 32.47,425.83) --
	(176.09,545.69);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.62,447.90) --
	( 60.62,450.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.63,431.21) --
	( 40.63,436.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 61.15,448.77) --
	( 61.15,451.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 56.13,443.42) --
	( 56.13,446.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 71.79,457.11) --
	( 71.79,460.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.78,439.55) --
	( 49.78,440.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.12,433.88) --
	( 44.12,442.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.60,429.89) --
	( 37.60,430.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.83,426.82) --
	( 33.83,427.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 42.42,433.74) --
	( 42.42,436.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 38.56,430.24) --
	( 38.56,430.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 45.22,435.14) --
	( 45.22,436.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 36.61,429.07) --
	( 36.61,429.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (114.06,479.32) --
	(114.06,534.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.60,435.36) --
	( 44.60,436.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 41.42,432.57) --
	( 41.42,433.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 58.02,438.12) --
	( 58.02,455.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 51.55,439.71) --
	( 51.55,444.70);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 36.30,428.99) --
	( 36.30,429.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.47,429.36) --
	( 37.47,430.05);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.59,436.83) --
	( 49.59,438.93);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.94,433.47) --
	( 48.94,445.44);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 56.30,443.62) --
	( 56.30,445.44);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 70.67,451.52) --
	( 70.67,465.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.89,439.99) --
	( 50.89,441.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 42.87,433.77) --
	( 42.87,436.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 38.84,430.08) --
	( 38.84,432.07);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 52.92,442.96) --
	( 52.92,446.30);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 70.33,456.68) --
	( 70.33,459.93);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.17,431.83) --
	( 40.17,434.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 45.89,436.29) --
	( 45.89,445.30);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.45,452.95) --
	( 68.45,460.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 34.00,426.96) --
	( 34.00,427.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.29,439.94) --
	( 50.29,441.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 39.92,431.88) --
	( 39.92,432.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 39.17,430.85) --
	( 39.17,431.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.47,429.60) --
	( 44.47,437.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.42,429.86) --
	( 37.42,430.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 61.48,448.52) --
	( 61.48,452.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 51.09,440.96) --
	( 51.09,442.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 63.67,450.80) --
	( 63.67,452.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.54,426.68) --
	( 33.54,427.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.13,438.63) --
	( 49.13,440.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 45.43,436.37) --
	( 45.43,437.53);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 70.62,455.88) --
	( 70.62,459.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 38.23,429.96) --
	( 38.23,432.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 41.18,432.06) --
	( 41.18,433.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 46.21,436.78) --
	( 46.21,438.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.60,435.18) --
	( 44.60,436.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 41.08,430.11) --
	( 41.08,433.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 39.16,431.01) --
	( 39.16,431.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 45.88,436.62) --
	( 45.88,438.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 41.99,431.56) --
	( 41.99,436.09);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 34.91,427.24) --
	( 34.91,428.07);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.75,428.05) --
	( 35.75,428.51);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.44,432.45) --
	( 40.44,433.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 78.74,460.74) --
	( 78.74,466.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 45.59,435.56) --
	( 45.59,445.04);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 36.94,429.22) --
	( 36.94,429.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.86,449.07) --
	( 60.86,451.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.28,429.33) --
	( 37.28,430.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 55.33,443.78) --
	( 55.33,445.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 45.65,435.83) --
	( 45.65,437.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 42.45,432.03) --
	( 42.45,435.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 87.44,467.93) --
	( 87.44,473.74);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.68,427.84) --
	( 40.68,431.66);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 39.01,430.98) --
	( 39.01,431.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 55.16,444.15) --
	( 55.16,446.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.05,439.46) --
	( 49.05,440.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 42.38,433.66) --
	( 42.38,434.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.52,432.24) --
	( 40.52,433.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 56.23,444.08) --
	( 56.23,447.53);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 42.52,426.73) --
	( 42.52,438.70);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 42.44,433.94) --
	( 42.44,434.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.59,454.67) --
	( 68.59,460.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.25,427.65) --
	( 35.25,429.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.79,430.34) --
	( 44.79,443.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 39.99,431.45) --
	( 39.99,433.12);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.61,427.52) --
	( 35.61,428.31);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 42.98,432.73) --
	( 42.98,439.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 43.83,434.98) --
	( 43.83,436.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.72,432.35) --
	( 40.72,433.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 51.51,441.13) --
	( 51.51,442.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.43,431.36) --
	( 40.43,436.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.97,430.04) --
	( 37.97,430.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 65.25,450.84) --
	( 65.25,456.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 43.44,433.94) --
	( 43.44,437.94);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 36.23,428.14) --
	( 36.23,431.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 51.23,440.87) --
	( 51.23,442.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 36.18,426.82) --
	( 36.18,430.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 42.15,432.34) --
	( 42.15,438.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.83,434.97) --
	( 44.83,439.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 38.43,430.38) --
	( 38.43,431.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 34.64,427.43) --
	( 34.64,427.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.87,432.33) --
	( 40.87,433.09);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 63.23,449.54) --
	( 63.23,452.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.64,453.36) --
	( 66.64,456.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.50,428.09) --
	( 35.50,428.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 36.85,429.30) --
	( 36.85,429.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 59.90,440.19) --
	( 59.90,455.62);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] ( 60.62,448.95) circle (  1.49);

\path[fill=fillColor] ( 40.63,433.67) circle (  1.49);

\path[fill=fillColor] ( 61.15,449.89) circle (  1.49);

\path[fill=fillColor] ( 56.13,445.15) circle (  1.49);

\path[fill=fillColor] ( 71.79,458.70) circle (  1.49);

\path[fill=fillColor] ( 49.78,440.24) circle (  1.49);

\path[fill=fillColor] ( 44.12,438.26) circle (  1.49);

\path[fill=fillColor] ( 37.60,430.19) circle (  1.49);

\path[fill=fillColor] ( 33.83,427.01) circle (  1.49);

\path[fill=fillColor] ( 42.42,435.05) circle (  1.49);

\path[fill=fillColor] ( 38.56,430.58) circle (  1.49);

\path[fill=fillColor] ( 45.22,436.07) circle (  1.49);

\path[fill=fillColor] ( 36.61,429.35) circle (  1.49);

\path[fill=fillColor] (114.06,505.74) circle (  1.49);

\path[fill=fillColor] ( 44.60,435.86) circle (  1.49);

\path[fill=fillColor] ( 41.42,433.20) circle (  1.49);

\path[fill=fillColor] ( 58.02,445.65) circle (  1.49);

\path[fill=fillColor] ( 51.55,442.14) circle (  1.49);

\path[fill=fillColor] ( 36.30,429.31) circle (  1.49);

\path[fill=fillColor] ( 37.47,429.70) circle (  1.49);

\path[fill=fillColor] ( 49.59,437.86) circle (  1.49);

\path[fill=fillColor] ( 48.94,439.04) circle (  1.49);

\path[fill=fillColor] ( 56.30,444.51) circle (  1.49);

\path[fill=fillColor] ( 70.67,458.33) circle (  1.49);

\path[fill=fillColor] ( 50.89,440.77) circle (  1.49);

\path[fill=fillColor] ( 42.87,434.90) circle (  1.49);

\path[fill=fillColor] ( 38.84,431.03) circle (  1.49);

\path[fill=fillColor] ( 52.92,444.67) circle (  1.49);

\path[fill=fillColor] ( 70.33,458.30) circle (  1.49);

\path[fill=fillColor] ( 40.17,433.09) circle (  1.49);

\path[fill=fillColor] ( 45.89,440.68) circle (  1.49);

\path[fill=fillColor] ( 68.45,456.85) circle (  1.49);

\path[fill=fillColor] ( 34.00,427.15) circle (  1.49);

\path[fill=fillColor] ( 50.29,440.87) circle (  1.49);

\path[fill=fillColor] ( 39.92,432.28) circle (  1.49);

\path[fill=fillColor] ( 39.17,431.15) circle (  1.49);

\path[fill=fillColor] ( 44.47,433.00) circle (  1.49);

\path[fill=fillColor] ( 37.42,430.24) circle (  1.49);

\path[fill=fillColor] ( 61.48,450.45) circle (  1.49);

\path[fill=fillColor] ( 51.09,441.67) circle (  1.49);

\path[fill=fillColor] ( 63.67,451.93) circle (  1.49);

\path[fill=fillColor] ( 33.54,426.85) circle (  1.49);

\path[fill=fillColor] ( 49.13,439.44) circle (  1.49);

\path[fill=fillColor] ( 45.43,436.96) circle (  1.49);

\path[fill=fillColor] ( 70.62,457.57) circle (  1.49);

\path[fill=fillColor] ( 38.23,431.00) circle (  1.49);

\path[fill=fillColor] ( 41.18,432.60) circle (  1.49);

\path[fill=fillColor] ( 46.21,437.69) circle (  1.49);

\path[fill=fillColor] ( 44.60,435.64) circle (  1.49);

\path[fill=fillColor] ( 41.08,431.57) circle (  1.49);

\path[fill=fillColor] ( 39.16,431.37) circle (  1.49);

\path[fill=fillColor] ( 45.88,437.44) circle (  1.49);

\path[fill=fillColor] ( 41.99,433.90) circle (  1.49);

\path[fill=fillColor] ( 34.91,427.62) circle (  1.49);

\path[fill=fillColor] ( 35.75,428.28) circle (  1.49);

\path[fill=fillColor] ( 40.44,432.83) circle (  1.49);

\path[fill=fillColor] ( 78.74,463.74) circle (  1.49);

\path[fill=fillColor] ( 45.59,440.02) circle (  1.49);

\path[fill=fillColor] ( 36.94,429.56) circle (  1.49);

\path[fill=fillColor] ( 60.86,450.27) circle (  1.49);

\path[fill=fillColor] ( 37.28,429.85) circle (  1.49);

\path[fill=fillColor] ( 55.33,444.88) circle (  1.49);

\path[fill=fillColor] ( 45.65,436.65) circle (  1.49);

\path[fill=fillColor] ( 42.45,433.68) circle (  1.49);

\path[fill=fillColor] ( 87.44,470.83) circle (  1.49);

\path[fill=fillColor] ( 40.68,429.56) circle (  1.49);

\path[fill=fillColor] ( 39.01,431.36) circle (  1.49);

\path[fill=fillColor] ( 55.16,445.15) circle (  1.49);

\path[fill=fillColor] ( 49.05,440.06) circle (  1.49);

\path[fill=fillColor] ( 42.38,434.25) circle (  1.49);

\path[fill=fillColor] ( 40.52,432.70) circle (  1.49);

\path[fill=fillColor] ( 56.23,445.77) circle (  1.49);

\path[fill=fillColor] ( 42.52,430.91) circle (  1.49);

\path[fill=fillColor] ( 42.44,434.40) circle (  1.49);

\path[fill=fillColor] ( 68.59,457.59) circle (  1.49);

\path[fill=fillColor] ( 35.25,428.35) circle (  1.49);

\path[fill=fillColor] ( 44.79,435.83) circle (  1.49);

\path[fill=fillColor] ( 39.99,432.24) circle (  1.49);

\path[fill=fillColor] ( 35.61,427.87) circle (  1.49);

\path[fill=fillColor] ( 42.98,435.83) circle (  1.49);

\path[fill=fillColor] ( 43.83,435.51) circle (  1.49);

\path[fill=fillColor] ( 40.72,432.76) circle (  1.49);

\path[fill=fillColor] ( 51.51,441.88) circle (  1.49);

\path[fill=fillColor] ( 40.43,433.64) circle (  1.49);

\path[fill=fillColor] ( 37.97,430.32) circle (  1.49);

\path[fill=fillColor] ( 65.25,453.48) circle (  1.49);

\path[fill=fillColor] ( 43.44,435.84) circle (  1.49);

\path[fill=fillColor] ( 36.23,429.64) circle (  1.49);

\path[fill=fillColor] ( 51.23,441.61) circle (  1.49);

\path[fill=fillColor] ( 36.18,428.50) circle (  1.49);

\path[fill=fillColor] ( 42.15,434.94) circle (  1.49);

\path[fill=fillColor] ( 44.83,437.14) circle (  1.49);

\path[fill=fillColor] ( 38.43,430.79) circle (  1.49);

\path[fill=fillColor] ( 34.64,427.67) circle (  1.49);

\path[fill=fillColor] ( 40.87,432.71) circle (  1.49);

\path[fill=fillColor] ( 63.23,451.26) circle (  1.49);

\path[fill=fillColor] ( 66.64,454.92) circle (  1.49);

\path[fill=fillColor] ( 35.50,428.38) circle (  1.49);

\path[fill=fillColor] ( 36.85,429.58) circle (  1.49);

\path[fill=fillColor] ( 59.90,447.00) circle (  1.49);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (104.28,547.27) {Coverage: 94\%};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,425.83) -- (159.13,425.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,425.83) -- ( 32.47,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 57.80,425.83) -- ( 57.80,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.14,425.83) -- ( 83.14,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (108.47,425.83) -- (108.47,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (133.80,425.83) -- (133.80,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.13,425.83) -- (159.13,421.87);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 32.47,411.58) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 57.80,411.58) {0.5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 83.14,411.58) {1.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (108.47,411.58) {1.5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (133.80,411.58) {2.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (159.13,411.58) {2.5};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,425.83) -- ( 32.47,531.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,425.83) -- ( 28.51,425.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,446.97) -- ( 28.51,446.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,468.11) -- ( 28.51,468.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,489.25) -- ( 28.51,489.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,510.39) -- ( 28.51,510.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,531.54) -- ( 28.51,531.54);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,423.56) {0.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,444.70) {0.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,465.84) {1.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,486.98) {1.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,508.12) {2.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,529.26) {2.5};
\end{scope}
\begin{scope}
\path[clip] (192.72,385.44) rectangle (385.44,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.79] at (297.00,559.19) {\bfseries Yule birth rate $\lambda$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (297.00,395.74) {True value};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (199.85,485.76) {Estimated value};
\end{scope}
\begin{scope}
\path[clip] (225.19,425.83) rectangle (368.81,545.69);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (225.19,425.83) --
	(368.81,545.69);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (233.08,428.69) --
	(233.08,431.85);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.22,431.73) --
	(240.22,440.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.85,428.04) --
	(228.85,430.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.51,428.90) --
	(231.51,432.42);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.90,427.17) --
	(228.90,428.63);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.82,430.33) --
	(232.82,435.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (238.27,431.70) --
	(238.27,438.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (241.04,435.27) --
	(241.04,445.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (288.80,459.50) --
	(288.80,500.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.60,431.55) --
	(237.60,438.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (241.36,434.91) --
	(241.36,445.49);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.29,431.65) --
	(240.29,438.16);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (245.62,440.55) --
	(245.62,457.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.78,426.67) --
	(226.78,427.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.47,429.93) --
	(231.47,434.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (241.87,434.57) --
	(241.87,444.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.24,428.37) --
	(230.24,432.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.40,429.16) --
	(232.40,432.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.90,442.27) --
	(264.90,460.93);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (247.31,435.78) --
	(247.31,447.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.05,430.52) --
	(235.05,435.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.48,430.16) --
	(234.48,435.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.81,428.56) --
	(229.81,431.54);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.34,428.14) --
	(231.34,430.91);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.09,429.97) --
	(234.09,434.58);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.56,430.71) --
	(234.56,436.30);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.00,435.25) --
	(240.00,446.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.24,429.71) --
	(231.24,434.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.54,427.36) --
	(228.54,429.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (242.33,435.30) --
	(242.33,446.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.75,429.12) --
	(230.75,432.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.92,428.38) --
	(229.92,431.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (310.05,465.13) --
	(310.05,511.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.27,429.16) --
	(232.27,432.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.10,433.14) --
	(239.10,441.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (242.49,433.11) --
	(242.49,441.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.99,431.17) --
	(231.99,443.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (246.90,435.81) --
	(246.90,447.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.49,428.58) --
	(230.49,431.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.69,429.44) --
	(231.69,433.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.75,427.90) --
	(229.75,430.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (289.81,476.34) --
	(289.81,536.94);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (233.46,430.85) --
	(233.46,436.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.63,431.03) --
	(235.63,436.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.99,427.33) --
	(227.99,428.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (253.60,439.32) --
	(253.60,455.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.48,433.67) --
	(240.48,442.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.60,430.46) --
	(235.60,435.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.97,431.47) --
	(235.97,437.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.33,434.49) --
	(240.33,445.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (244.91,435.12) --
	(244.91,445.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (233.68,429.86) --
	(233.68,434.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.21,431.92) --
	(237.21,438.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (258.87,448.93) --
	(258.87,477.70);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (262.77,447.38) --
	(262.77,472.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.68,432.45) --
	(237.68,439.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.98,427.63) --
	(228.98,429.64);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (236.43,429.72) --
	(236.43,434.71);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (243.90,437.61) --
	(243.90,451.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.89,427.92) --
	(228.89,430.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (248.10,440.05) --
	(248.10,456.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.86,428.17) --
	(230.86,430.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.61,430.07) --
	(232.61,434.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.83,432.02) --
	(234.83,439.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.77,426.97) --
	(227.77,428.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (246.39,436.88) --
	(246.39,461.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (238.10,433.10) --
	(238.10,441.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.95,428.28) --
	(229.95,431.04);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.83,429.01) --
	(231.83,432.49);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.66,431.39) --
	(239.66,437.70);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.50,431.56) --
	(234.50,438.04);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.79,428.52) --
	(231.79,431.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (241.48,427.67) --
	(241.48,477.39);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.64,431.90) --
	(240.64,438.64);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.79,427.38) --
	(227.79,429.06);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (256.03,441.94) --
	(256.03,463.27);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (238.78,429.47) --
	(238.78,439.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.49,432.86) --
	(239.49,441.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (258.23,451.93) --
	(258.23,484.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.75,431.46) --
	(235.75,439.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.52,431.17) --
	(237.52,437.07);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (241.68,432.30) --
	(241.68,439.57);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.33,428.99) --
	(232.33,432.50);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (243.95,431.76) --
	(243.95,440.12);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (241.92,435.64) --
	(241.92,446.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.90,427.50) --
	(227.90,429.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.72,430.69) --
	(235.72,436.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (253.79,439.70) --
	(253.79,461.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.23,428.16) --
	(229.23,430.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (255.44,437.43) --
	(255.44,488.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.39,430.78) --
	(234.39,436.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.22,430.13) --
	(235.22,435.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (249.36,437.90) --
	(249.36,451.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (262.32,453.16) --
	(262.32,485.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.37,432.62) --
	(240.37,440.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.03,428.82) --
	(229.03,432.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.52,427.48) --
	(228.52,429.30);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (277.09,448.78) --
	(277.09,475.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (243.39,438.59) --
	(243.39,453.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.45,428.42) --
	(229.45,431.95);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] (233.08,430.24) circle (  1.49);

\path[fill=fillColor] (240.22,435.94) circle (  1.49);

\path[fill=fillColor] (228.85,429.19) circle (  1.49);

\path[fill=fillColor] (231.51,430.64) circle (  1.49);

\path[fill=fillColor] (228.90,427.89) circle (  1.49);

\path[fill=fillColor] (232.82,432.85) circle (  1.49);

\path[fill=fillColor] (238.27,435.17) circle (  1.49);

\path[fill=fillColor] (241.04,440.47) circle (  1.49);

\path[fill=fillColor] (288.80,479.45) circle (  1.49);

\path[fill=fillColor] (237.60,434.83) circle (  1.49);

\path[fill=fillColor] (241.36,440.20) circle (  1.49);

\path[fill=fillColor] (240.29,434.81) circle (  1.49);

\path[fill=fillColor] (245.62,448.40) circle (  1.49);

\path[fill=fillColor] (226.78,427.15) circle (  1.49);

\path[fill=fillColor] (231.47,432.14) circle (  1.49);

\path[fill=fillColor] (241.87,439.48) circle (  1.49);

\path[fill=fillColor] (230.24,430.33) circle (  1.49);

\path[fill=fillColor] (232.40,431.01) circle (  1.49);

\path[fill=fillColor] (264.90,450.98) circle (  1.49);

\path[fill=fillColor] (247.31,441.51) circle (  1.49);

\path[fill=fillColor] (235.05,433.13) circle (  1.49);

\path[fill=fillColor] (234.48,432.83) circle (  1.49);

\path[fill=fillColor] (229.81,430.00) circle (  1.49);

\path[fill=fillColor] (231.34,429.48) circle (  1.49);

\path[fill=fillColor] (234.09,432.21) circle (  1.49);

\path[fill=fillColor] (234.56,433.36) circle (  1.49);

\path[fill=fillColor] (240.00,440.67) circle (  1.49);

\path[fill=fillColor] (231.24,431.81) circle (  1.49);

\path[fill=fillColor] (228.54,428.14) circle (  1.49);

\path[fill=fillColor] (242.33,440.62) circle (  1.49);

\path[fill=fillColor] (230.75,430.95) circle (  1.49);

\path[fill=fillColor] (229.92,429.74) circle (  1.49);

\path[fill=fillColor] (310.05,486.51) circle (  1.49);

\path[fill=fillColor] (232.27,431.01) circle (  1.49);

\path[fill=fillColor] (239.10,437.30) circle (  1.49);

\path[fill=fillColor] (242.49,437.21) circle (  1.49);

\path[fill=fillColor] (231.99,436.81) circle (  1.49);

\path[fill=fillColor] (246.90,441.32) circle (  1.49);

\path[fill=fillColor] (230.49,430.03) circle (  1.49);

\path[fill=fillColor] (231.69,431.32) circle (  1.49);

\path[fill=fillColor] (229.75,428.97) circle (  1.49);

\path[fill=fillColor] (289.81,505.74) circle (  1.49);

\path[fill=fillColor] (233.46,433.62) circle (  1.49);

\path[fill=fillColor] (235.63,433.80) circle (  1.49);

\path[fill=fillColor] (227.99,428.12) circle (  1.49);

\path[fill=fillColor] (253.60,447.48) circle (  1.49);

\path[fill=fillColor] (240.48,437.95) circle (  1.49);

\path[fill=fillColor] (235.60,433.02) circle (  1.49);

\path[fill=fillColor] (235.97,434.58) circle (  1.49);

\path[fill=fillColor] (240.33,439.95) circle (  1.49);

\path[fill=fillColor] (244.91,440.52) circle (  1.49);

\path[fill=fillColor] (233.68,432.06) circle (  1.49);

\path[fill=fillColor] (237.21,435.22) circle (  1.49);

\path[fill=fillColor] (258.87,462.43) circle (  1.49);

\path[fill=fillColor] (262.77,459.44) circle (  1.49);

\path[fill=fillColor] (237.68,436.12) circle (  1.49);

\path[fill=fillColor] (228.98,428.62) circle (  1.49);

\path[fill=fillColor] (236.43,432.11) circle (  1.49);

\path[fill=fillColor] (243.90,444.12) circle (  1.49);

\path[fill=fillColor] (228.89,429.10) circle (  1.49);

\path[fill=fillColor] (248.10,447.68) circle (  1.49);

\path[fill=fillColor] (230.86,429.43) circle (  1.49);

\path[fill=fillColor] (232.61,432.43) circle (  1.49);

\path[fill=fillColor] (234.83,435.45) circle (  1.49);

\path[fill=fillColor] (227.77,427.56) circle (  1.49);

\path[fill=fillColor] (246.39,448.70) circle (  1.49);

\path[fill=fillColor] (238.10,437.33) circle (  1.49);

\path[fill=fillColor] (229.95,429.63) circle (  1.49);

\path[fill=fillColor] (231.83,430.65) circle (  1.49);

\path[fill=fillColor] (239.66,434.50) circle (  1.49);

\path[fill=fillColor] (234.50,434.71) circle (  1.49);

\path[fill=fillColor] (231.79,430.01) circle (  1.49);

\path[fill=fillColor] (241.48,450.07) circle (  1.49);

\path[fill=fillColor] (240.64,435.13) circle (  1.49);

\path[fill=fillColor] (227.79,428.18) circle (  1.49);

\path[fill=fillColor] (256.03,452.14) circle (  1.49);

\path[fill=fillColor] (238.78,434.37) circle (  1.49);

\path[fill=fillColor] (239.49,437.04) circle (  1.49);

\path[fill=fillColor] (258.23,467.75) circle (  1.49);

\path[fill=fillColor] (235.75,435.17) circle (  1.49);

\path[fill=fillColor] (237.52,433.95) circle (  1.49);

\path[fill=fillColor] (241.68,435.80) circle (  1.49);

\path[fill=fillColor] (232.33,430.71) circle (  1.49);

\path[fill=fillColor] (243.95,435.87) circle (  1.49);

\path[fill=fillColor] (241.92,441.03) circle (  1.49);

\path[fill=fillColor] (227.90,428.40) circle (  1.49);

\path[fill=fillColor] (235.72,433.54) circle (  1.49);

\path[fill=fillColor] (253.79,450.13) circle (  1.49);

\path[fill=fillColor] (229.23,429.46) circle (  1.49);

\path[fill=fillColor] (255.44,461.58) circle (  1.49);

\path[fill=fillColor] (234.39,433.74) circle (  1.49);

\path[fill=fillColor] (235.22,432.58) circle (  1.49);

\path[fill=fillColor] (249.36,444.28) circle (  1.49);

\path[fill=fillColor] (262.32,468.98) circle (  1.49);

\path[fill=fillColor] (240.37,436.16) circle (  1.49);

\path[fill=fillColor] (229.03,430.41) circle (  1.49);

\path[fill=fillColor] (228.52,428.36) circle (  1.49);

\path[fill=fillColor] (277.09,462.38) circle (  1.49);

\path[fill=fillColor] (243.39,445.61) circle (  1.49);

\path[fill=fillColor] (229.45,430.05) circle (  1.49);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (297.00,547.27) {Coverage: 91\%};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,425.83) -- (344.58,425.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,425.83) -- (225.19,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.99,425.83) -- (264.99,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (304.78,425.83) -- (304.78,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (344.58,425.83) -- (344.58,421.87);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (225.19,411.58) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (264.99,411.58) {50};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (304.78,411.58) {100};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (344.58,411.58) {150};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,425.83) -- (225.19,525.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,425.83) -- (221.23,425.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,459.04) -- (221.23,459.04);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,492.25) -- (221.23,492.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,525.47) -- (221.23,525.47);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,423.56) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,456.77) {50};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,489.98) {100};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,523.19) {150};
\end{scope}
\begin{scope}
\path[clip] (385.44,385.44) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.79] at (489.72,559.19) {\bfseries HKY model $\kappa$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (489.72,395.74) {True value};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (392.57,485.76) {Estimated value};
\end{scope}
\begin{scope}
\path[clip] (417.91,425.83) rectangle (561.53,545.69);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (417.91,425.83) --
	(561.53,545.69);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.09,426.81) --
	(419.09,426.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (468.00,461.66) --
	(468.00,472.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.67,432.69) --
	(426.67,433.36);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.83,426.48) --
	(418.83,426.59);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.96,438.30) --
	(433.96,439.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.79,428.09) --
	(420.79,428.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (422.93,429.73) --
	(422.93,430.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (424.21,430.73) --
	(424.21,431.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (441.53,443.53) --
	(441.53,453.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.46,427.01) --
	(419.46,427.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.88,428.85) --
	(421.88,429.40);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.44,427.90) --
	(420.44,428.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (424.58,430.69) --
	(424.58,431.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.67,428.88) --
	(421.67,429.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.41,427.07) --
	(419.41,427.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.49,427.92) --
	(420.49,428.30);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (429.53,435.11) --
	(429.53,436.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.54,427.93) --
	(420.54,428.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (513.66,482.60) --
	(513.66,519.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.84,427.18) --
	(419.84,427.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.91,427.49) --
	(419.91,427.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.97,429.05) --
	(421.97,429.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (422.60,429.67) --
	(422.60,430.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (431.47,436.80) --
	(431.47,438.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.26,430.18) --
	(423.26,430.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.24,426.09) --
	(418.24,426.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.74,428.82) --
	(421.74,429.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.30,432.49) --
	(426.30,433.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.94,426.61) --
	(418.94,426.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.18,428.42) --
	(421.18,428.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.83,428.09) --
	(420.83,428.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.18,426.02) --
	(418.18,426.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (424.12,430.07) --
	(424.12,431.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (422.88,429.73) --
	(422.88,430.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (422.49,429.34) --
	(422.49,429.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.67,428.70) --
	(421.67,429.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.15,426.70) --
	(419.15,426.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.88,432.79) --
	(426.88,434.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (425.08,431.67) --
	(425.08,432.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.65,428.04) --
	(420.65,428.31);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (425.59,431.67) --
	(425.59,432.23);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.36,432.05) --
	(427.36,435.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.37,432.86) --
	(427.37,433.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.71,426.44) --
	(418.71,426.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (452.15,452.12) --
	(452.15,455.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (428.42,433.32) --
	(428.42,435.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (429.67,434.33) --
	(429.67,435.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.07,427.53) --
	(420.07,427.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.60,427.87) --
	(420.60,428.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (453.04,453.13) --
	(453.04,462.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.67,427.22) --
	(419.67,427.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (428.78,434.36) --
	(428.78,435.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.21,426.83) --
	(419.21,427.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (425.85,431.89) --
	(425.85,433.84);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.34,427.96) --
	(420.34,428.56);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (425.89,432.10) --
	(425.89,433.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (422.60,429.61) --
	(422.60,429.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.12,427.59) --
	(420.12,427.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.74,427.14) --
	(419.74,427.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.23,426.06) --
	(418.23,426.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.72,426.40) --
	(418.72,426.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (424.10,430.95) --
	(424.10,431.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.98,455.10) --
	(454.98,461.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.78,430.36) --
	(423.78,431.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (449.13,450.43) --
	(449.13,453.04);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.83,426.42) --
	(418.83,426.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.03,427.41) --
	(420.03,427.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.70,426.42) --
	(418.70,426.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.31,428.58) --
	(421.31,428.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.90,428.33) --
	(420.90,428.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (422.87,429.69) --
	(422.87,430.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.69,428.78) --
	(421.69,429.09);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (425.46,431.23) --
	(425.46,432.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.25,432.68) --
	(426.25,433.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.86,426.53) --
	(418.86,426.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (435.24,439.25) --
	(435.24,444.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.39,428.51) --
	(421.39,428.94);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (442.14,444.64) --
	(442.14,449.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (449.66,445.65) --
	(449.66,456.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.42,426.20) --
	(418.42,426.30);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (425.78,432.27) --
	(425.78,433.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.66,456.10) --
	(461.66,464.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.65,428.94) --
	(421.65,429.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.85,433.20) --
	(426.85,434.40);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (428.33,434.04) --
	(428.33,435.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.83,427.38) --
	(419.83,427.53);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.07,432.86) --
	(427.07,433.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.90,428.13) --
	(420.90,428.70);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (437.42,441.23) --
	(437.42,443.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.71,428.62) --
	(421.71,429.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (436.48,439.16) --
	(436.48,441.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.24,427.73) --
	(420.24,427.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.88,433.32) --
	(427.88,434.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (424.52,430.31) --
	(424.52,431.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.79,429.00) --
	(421.79,429.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.39,430.26) --
	(423.39,430.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (422.10,429.17) --
	(422.10,429.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (425.27,431.27) --
	(425.27,432.93);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.36,426.19) --
	(418.36,426.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (422.29,429.28) --
	(422.29,429.68);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] (419.09,426.88) circle (  1.49);

\path[fill=fillColor] (468.00,466.98) circle (  1.49);

\path[fill=fillColor] (426.67,433.02) circle (  1.49);

\path[fill=fillColor] (418.83,426.54) circle (  1.49);

\path[fill=fillColor] (433.96,439.01) circle (  1.49);

\path[fill=fillColor] (420.79,428.24) circle (  1.49);

\path[fill=fillColor] (422.93,430.02) circle (  1.49);

\path[fill=fillColor] (424.21,431.20) circle (  1.49);

\path[fill=fillColor] (441.53,448.54) circle (  1.49);

\path[fill=fillColor] (419.46,427.11) circle (  1.49);

\path[fill=fillColor] (421.88,429.14) circle (  1.49);

\path[fill=fillColor] (420.44,428.06) circle (  1.49);

\path[fill=fillColor] (424.58,431.24) circle (  1.49);

\path[fill=fillColor] (421.67,429.01) circle (  1.49);

\path[fill=fillColor] (419.41,427.16) circle (  1.49);

\path[fill=fillColor] (420.49,428.12) circle (  1.49);

\path[fill=fillColor] (429.53,435.65) circle (  1.49);

\path[fill=fillColor] (420.54,428.05) circle (  1.49);

\path[fill=fillColor] (513.66,499.91) circle (  1.49);

\path[fill=fillColor] (419.84,427.32) circle (  1.49);

\path[fill=fillColor] (419.91,427.61) circle (  1.49);

\path[fill=fillColor] (421.97,429.25) circle (  1.49);

\path[fill=fillColor] (422.60,429.87) circle (  1.49);

\path[fill=fillColor] (431.47,437.46) circle (  1.49);

\path[fill=fillColor] (423.26,430.46) circle (  1.49);

\path[fill=fillColor] (418.24,426.13) circle (  1.49);

\path[fill=fillColor] (421.74,429.08) circle (  1.49);

\path[fill=fillColor] (426.30,432.93) circle (  1.49);

\path[fill=fillColor] (418.94,426.67) circle (  1.49);

\path[fill=fillColor] (421.18,428.66) circle (  1.49);

\path[fill=fillColor] (420.83,428.21) circle (  1.49);

\path[fill=fillColor] (418.18,426.05) circle (  1.49);

\path[fill=fillColor] (424.12,430.90) circle (  1.49);

\path[fill=fillColor] (422.88,429.95) circle (  1.49);

\path[fill=fillColor] (422.49,429.61) circle (  1.49);

\path[fill=fillColor] (421.67,428.93) circle (  1.49);

\path[fill=fillColor] (419.15,426.79) circle (  1.49);

\path[fill=fillColor] (426.88,433.50) circle (  1.49);

\path[fill=fillColor] (425.08,431.98) circle (  1.49);

\path[fill=fillColor] (420.65,428.17) circle (  1.49);

\path[fill=fillColor] (425.59,431.96) circle (  1.49);

\path[fill=fillColor] (427.36,433.57) circle (  1.49);

\path[fill=fillColor] (427.37,433.37) circle (  1.49);

\path[fill=fillColor] (418.71,426.49) circle (  1.49);

\path[fill=fillColor] (452.15,453.71) circle (  1.49);

\path[fill=fillColor] (428.42,434.19) circle (  1.49);

\path[fill=fillColor] (429.67,435.08) circle (  1.49);

\path[fill=fillColor] (420.07,427.65) circle (  1.49);

\path[fill=fillColor] (420.60,428.01) circle (  1.49);

\path[fill=fillColor] (453.04,457.49) circle (  1.49);

\path[fill=fillColor] (419.67,427.35) circle (  1.49);

\path[fill=fillColor] (428.78,434.93) circle (  1.49);

\path[fill=fillColor] (419.21,426.91) circle (  1.49);

\path[fill=fillColor] (425.85,432.83) circle (  1.49);

\path[fill=fillColor] (420.34,428.27) circle (  1.49);

\path[fill=fillColor] (425.89,432.59) circle (  1.49);

\path[fill=fillColor] (422.60,429.80) circle (  1.49);

\path[fill=fillColor] (420.12,427.71) circle (  1.49);

\path[fill=fillColor] (419.74,427.28) circle (  1.49);

\path[fill=fillColor] (418.23,426.09) circle (  1.49);

\path[fill=fillColor] (418.72,426.49) circle (  1.49);

\path[fill=fillColor] (424.10,431.19) circle (  1.49);

\path[fill=fillColor] (454.98,457.98) circle (  1.49);

\path[fill=fillColor] (423.78,430.68) circle (  1.49);

\path[fill=fillColor] (449.13,451.68) circle (  1.49);

\path[fill=fillColor] (418.83,426.51) circle (  1.49);

\path[fill=fillColor] (420.03,427.55) circle (  1.49);

\path[fill=fillColor] (418.70,426.47) circle (  1.49);

\path[fill=fillColor] (421.31,428.73) circle (  1.49);

\path[fill=fillColor] (420.90,428.51) circle (  1.49);

\path[fill=fillColor] (422.87,429.96) circle (  1.49);

\path[fill=fillColor] (421.69,428.94) circle (  1.49);

\path[fill=fillColor] (425.46,431.98) circle (  1.49);

\path[fill=fillColor] (426.25,433.23) circle (  1.49);

\path[fill=fillColor] (418.86,426.58) circle (  1.49);

\path[fill=fillColor] (435.24,441.66) circle (  1.49);

\path[fill=fillColor] (421.39,428.73) circle (  1.49);

\path[fill=fillColor] (442.14,446.77) circle (  1.49);

\path[fill=fillColor] (449.66,450.64) circle (  1.49);

\path[fill=fillColor] (418.42,426.25) circle (  1.49);

\path[fill=fillColor] (425.78,432.76) circle (  1.49);

\path[fill=fillColor] (461.66,460.20) circle (  1.49);

\path[fill=fillColor] (421.65,429.12) circle (  1.49);

\path[fill=fillColor] (426.85,433.79) circle (  1.49);

\path[fill=fillColor] (428.33,434.83) circle (  1.49);

\path[fill=fillColor] (419.83,427.45) circle (  1.49);

\path[fill=fillColor] (427.07,433.35) circle (  1.49);

\path[fill=fillColor] (420.90,428.40) circle (  1.49);

\path[fill=fillColor] (437.42,442.12) circle (  1.49);

\path[fill=fillColor] (421.71,429.08) circle (  1.49);

\path[fill=fillColor] (436.48,440.27) circle (  1.49);

\path[fill=fillColor] (420.24,427.86) circle (  1.49);

\path[fill=fillColor] (427.88,434.12) circle (  1.49);

\path[fill=fillColor] (424.52,430.96) circle (  1.49);

\path[fill=fillColor] (421.79,429.23) circle (  1.49);

\path[fill=fillColor] (423.39,430.51) circle (  1.49);

\path[fill=fillColor] (422.10,429.32) circle (  1.49);

\path[fill=fillColor] (425.27,432.09) circle (  1.49);

\path[fill=fillColor] (418.36,426.25) circle (  1.49);

\path[fill=fillColor] (422.29,429.48) circle (  1.49);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (489.72,547.27) {Coverage: 97\%};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,425.83) -- (554.47,425.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,425.83) -- (417.91,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (437.42,425.83) -- (437.42,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (456.93,425.83) -- (456.93,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.44,425.83) -- (476.44,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.94,425.83) -- (495.94,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (515.45,425.83) -- (515.45,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (534.96,425.83) -- (534.96,421.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (554.47,425.83) -- (554.47,421.87);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (417.91,411.58) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (437.42,411.58) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (456.93,411.58) {20};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (476.44,411.58) {30};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (495.94,411.58) {40};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (515.45,411.58) {50};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (534.96,411.58) {60};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (554.47,411.58) {70};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,425.83) -- (417.91,539.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,425.83) -- (413.95,425.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,442.11) -- (413.95,442.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,458.39) -- (413.95,458.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,474.67) -- (413.95,474.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,490.95) -- (413.95,490.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,507.23) -- (413.95,507.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,523.51) -- (413.95,523.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,539.80) -- (413.95,539.80);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,423.56) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,439.84) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,456.12) {20};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,472.40) {30};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,488.68) {40};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,504.96) {50};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,521.24) {60};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,537.52) {70};
\end{scope}
\begin{scope}
\path[clip] (  0.00,192.72) rectangle (192.72,385.44);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.79] at (104.28,366.47) {\bfseries Nucleotide frequency $f$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (104.28,203.02) {True value};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (  7.13,293.04) {Estimated value};
\end{scope}
\begin{scope}
\path[clip] ( 32.47,233.11) rectangle (176.09,352.97);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] ( 32.47,233.11) --
	(176.09,352.97);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 59.52,255.16) --
	( 59.52,257.56);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 80.98,270.03) --
	( 80.98,273.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 73.46,266.60) --
	( 73.46,269.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (106.47,294.56) --
	(106.47,298.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 93.59,283.32) --
	( 93.59,285.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 85.32,276.11) --
	( 85.32,280.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (114.14,298.49) --
	(114.14,303.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (114.03,298.18) --
	(114.03,303.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.32,285.43) --
	( 99.32,292.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 85.70,274.91) --
	( 85.70,279.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (119.28,303.70) --
	(119.28,309.53);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 74.17,267.05) --
	( 74.17,270.79);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 86.64,275.03) --
	( 86.64,280.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 76.12,268.00) --
	( 76.12,270.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 81.26,272.84) --
	( 81.26,276.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.22,303.64) --
	(121.22,309.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.79,255.94) --
	( 60.79,258.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 88.73,277.61) --
	( 88.73,281.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (106.97,292.34) --
	(106.97,298.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (105.24,291.74) --
	(105.24,297.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 72.44,266.29) --
	( 72.44,269.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.86,281.03) --
	( 92.86,285.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.03,298.03) --
	(112.03,301.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 84.55,275.25) --
	( 84.55,278.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.64,282.00) --
	( 92.64,286.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 96.89,284.83) --
	( 96.89,289.09);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (108.82,294.55) --
	(108.82,300.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.57,260.48) --
	( 68.57,263.53);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 98.03,286.40) --
	( 98.03,289.34);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (104.02,288.23) --
	(104.02,293.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 90.85,281.07) --
	( 90.85,284.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (128.22,310.00) --
	(128.22,314.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.10,283.26) --
	( 95.10,290.06);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 61.15,256.51) --
	( 61.15,259.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.84,288.09) --
	(100.84,293.04);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (101.64,288.34) --
	(101.64,293.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 81.37,271.57) --
	( 81.37,275.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (108.47,295.28) --
	(108.47,300.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 76.02,267.15) --
	( 76.02,270.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.04,282.68) --
	( 95.04,286.49);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 82.97,274.28) --
	( 82.97,277.23);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.04,272.19) --
	( 89.04,278.52);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.13,287.56) --
	(100.13,292.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 86.15,276.82) --
	( 86.15,280.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.23,260.73) --
	( 66.23,263.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 84.83,275.11) --
	( 84.83,280.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (110.01,293.67) --
	(110.01,298.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 72.64,265.07) --
	( 72.64,268.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (103.63,291.49) --
	(103.63,296.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.17,266.01) --
	( 75.17,270.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.42,302.97) --
	(121.42,308.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.69,283.77) --
	( 95.69,287.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 73.56,265.83) --
	( 73.56,269.49);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (114.69,299.29) --
	(114.69,306.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.50,281.02) --
	( 92.50,287.06);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (101.37,288.52) --
	(101.37,293.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 86.95,277.38) --
	( 86.95,280.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 77.83,269.50) --
	( 77.83,272.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 86.72,276.86) --
	( 86.72,282.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (113.57,299.06) --
	(113.57,302.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.07,259.65) --
	( 66.07,263.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.56,283.79) --
	( 95.56,287.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (103.40,291.16) --
	(103.40,295.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 78.68,270.79) --
	( 78.68,275.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.18,284.39) --
	( 95.18,287.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 85.11,276.10) --
	( 85.11,281.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (107.03,291.97) --
	(107.03,297.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 70.85,263.59) --
	( 70.85,266.34);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 74.58,265.02) --
	( 74.58,267.95);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 96.56,286.31) --
	( 96.56,290.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.98,280.60) --
	( 89.98,284.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (104.98,291.56) --
	(104.98,295.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.19,268.02) --
	( 75.19,273.30);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (110.27,292.49) --
	(110.27,297.27);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 65.48,260.42) --
	( 65.48,262.56);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 72.91,265.05) --
	( 72.91,270.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 90.11,278.33) --
	( 90.11,282.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 94.00,282.19) --
	( 94.00,286.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (105.13,292.19) --
	(105.13,298.79);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 84.06,273.37) --
	( 84.06,277.27);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 96.09,284.22) --
	( 96.09,288.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.77,278.41) --
	( 89.77,283.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (114.41,300.94) --
	(114.41,304.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (103.74,290.88) --
	(103.74,295.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.57,295.98) --
	(112.57,301.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 79.47,271.65) --
	( 79.47,274.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 88.02,278.41) --
	( 88.02,282.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 74.94,268.31) --
	( 74.94,273.27);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 76.72,268.06) --
	( 76.72,270.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 81.57,271.33) --
	( 81.57,277.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 71.87,264.63) --
	( 71.87,268.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (110.18,296.46) --
	(110.18,300.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 73.41,265.08) --
	( 73.41,269.64);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 85.28,270.76) --
	( 85.28,276.46);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 86.24,275.69) --
	( 86.24,280.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.02,272.68) --
	( 83.02,276.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 72.89,265.90) --
	( 72.89,268.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 93.64,281.36) --
	( 93.64,287.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (103.83,289.39) --
	(103.83,295.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 64.27,258.16) --
	( 64.27,260.60);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] ( 59.52,256.31) circle (  1.49);

\path[fill=fillColor] ( 80.98,271.97) circle (  1.49);

\path[fill=fillColor] ( 73.46,267.99) circle (  1.49);

\path[fill=fillColor] (106.47,296.47) circle (  1.49);

\path[fill=fillColor] ( 93.59,284.61) circle (  1.49);

\path[fill=fillColor] ( 85.32,278.07) circle (  1.49);

\path[fill=fillColor] (114.14,300.88) circle (  1.49);

\path[fill=fillColor] (114.03,300.80) circle (  1.49);

\path[fill=fillColor] ( 99.32,288.89) circle (  1.49);

\path[fill=fillColor] ( 85.70,276.90) circle (  1.49);

\path[fill=fillColor] (119.28,306.56) circle (  1.49);

\path[fill=fillColor] ( 74.17,268.90) circle (  1.49);

\path[fill=fillColor] ( 86.64,277.85) circle (  1.49);

\path[fill=fillColor] ( 76.12,269.00) circle (  1.49);

\path[fill=fillColor] ( 81.26,274.66) circle (  1.49);

\path[fill=fillColor] (121.22,306.42) circle (  1.49);

\path[fill=fillColor] ( 60.79,257.10) circle (  1.49);

\path[fill=fillColor] ( 88.73,279.39) circle (  1.49);

\path[fill=fillColor] (106.97,295.64) circle (  1.49);

\path[fill=fillColor] (105.24,294.46) circle (  1.49);

\path[fill=fillColor] ( 72.44,267.96) circle (  1.49);

\path[fill=fillColor] ( 92.86,283.14) circle (  1.49);

\path[fill=fillColor] (112.03,299.77) circle (  1.49);

\path[fill=fillColor] ( 84.55,276.80) circle (  1.49);

\path[fill=fillColor] ( 92.64,284.02) circle (  1.49);

\path[fill=fillColor] ( 96.89,286.92) circle (  1.49);

\path[fill=fillColor] (108.82,297.30) circle (  1.49);

\path[fill=fillColor] ( 68.57,262.05) circle (  1.49);

\path[fill=fillColor] ( 98.03,287.92) circle (  1.49);

\path[fill=fillColor] (104.02,290.80) circle (  1.49);

\path[fill=fillColor] ( 90.85,282.88) circle (  1.49);

\path[fill=fillColor] (128.22,312.01) circle (  1.49);

\path[fill=fillColor] ( 95.10,286.47) circle (  1.49);

\path[fill=fillColor] ( 61.15,257.76) circle (  1.49);

\path[fill=fillColor] (100.84,290.49) circle (  1.49);

\path[fill=fillColor] (101.64,290.96) circle (  1.49);

\path[fill=fillColor] ( 81.37,273.72) circle (  1.49);

\path[fill=fillColor] (108.47,298.20) circle (  1.49);

\path[fill=fillColor] ( 76.02,268.67) circle (  1.49);

\path[fill=fillColor] ( 95.04,284.57) circle (  1.49);

\path[fill=fillColor] ( 82.97,275.76) circle (  1.49);

\path[fill=fillColor] ( 89.04,275.52) circle (  1.49);

\path[fill=fillColor] (100.13,289.80) circle (  1.49);

\path[fill=fillColor] ( 86.15,278.76) circle (  1.49);

\path[fill=fillColor] ( 66.23,261.83) circle (  1.49);

\path[fill=fillColor] ( 84.83,277.83) circle (  1.49);

\path[fill=fillColor] (110.01,296.25) circle (  1.49);

\path[fill=fillColor] ( 72.64,266.61) circle (  1.49);

\path[fill=fillColor] (103.63,293.95) circle (  1.49);

\path[fill=fillColor] ( 75.17,268.24) circle (  1.49);

\path[fill=fillColor] (121.42,305.81) circle (  1.49);

\path[fill=fillColor] ( 95.69,285.73) circle (  1.49);

\path[fill=fillColor] ( 73.56,267.64) circle (  1.49);

\path[fill=fillColor] (114.69,302.69) circle (  1.49);

\path[fill=fillColor] ( 92.50,283.92) circle (  1.49);

\path[fill=fillColor] (101.37,290.87) circle (  1.49);

\path[fill=fillColor] ( 86.95,278.72) circle (  1.49);

\path[fill=fillColor] ( 77.83,271.17) circle (  1.49);

\path[fill=fillColor] ( 86.72,279.55) circle (  1.49);

\path[fill=fillColor] (113.57,300.94) circle (  1.49);

\path[fill=fillColor] ( 66.07,261.77) circle (  1.49);

\path[fill=fillColor] ( 95.56,285.41) circle (  1.49);

\path[fill=fillColor] (103.40,293.30) circle (  1.49);

\path[fill=fillColor] ( 78.68,272.94) circle (  1.49);

\path[fill=fillColor] ( 95.18,285.77) circle (  1.49);

\path[fill=fillColor] ( 85.11,278.89) circle (  1.49);

\path[fill=fillColor] (107.03,294.56) circle (  1.49);

\path[fill=fillColor] ( 70.85,264.94) circle (  1.49);

\path[fill=fillColor] ( 74.58,266.46) circle (  1.49);

\path[fill=fillColor] ( 96.56,288.61) circle (  1.49);

\path[fill=fillColor] ( 89.98,282.70) circle (  1.49);

\path[fill=fillColor] (104.98,293.46) circle (  1.49);

\path[fill=fillColor] ( 75.19,270.71) circle (  1.49);

\path[fill=fillColor] (110.27,294.94) circle (  1.49);

\path[fill=fillColor] ( 65.48,261.45) circle (  1.49);

\path[fill=fillColor] ( 72.91,267.74) circle (  1.49);

\path[fill=fillColor] ( 90.11,280.35) circle (  1.49);

\path[fill=fillColor] ( 94.00,284.47) circle (  1.49);

\path[fill=fillColor] (105.13,295.40) circle (  1.49);

\path[fill=fillColor] ( 84.06,275.35) circle (  1.49);

\path[fill=fillColor] ( 96.09,286.43) circle (  1.49);

\path[fill=fillColor] ( 89.77,280.90) circle (  1.49);

\path[fill=fillColor] (114.41,302.93) circle (  1.49);

\path[fill=fillColor] (103.74,293.51) circle (  1.49);

\path[fill=fillColor] (112.57,298.70) circle (  1.49);

\path[fill=fillColor] ( 79.47,272.94) circle (  1.49);

\path[fill=fillColor] ( 88.02,280.29) circle (  1.49);

\path[fill=fillColor] ( 74.94,270.80) circle (  1.49);

\path[fill=fillColor] ( 76.72,269.50) circle (  1.49);

\path[fill=fillColor] ( 81.57,274.16) circle (  1.49);

\path[fill=fillColor] ( 71.87,266.32) circle (  1.49);

\path[fill=fillColor] (110.18,298.57) circle (  1.49);

\path[fill=fillColor] ( 73.41,267.37) circle (  1.49);

\path[fill=fillColor] ( 85.28,273.71) circle (  1.49);

\path[fill=fillColor] ( 86.24,277.82) circle (  1.49);

\path[fill=fillColor] ( 83.02,274.45) circle (  1.49);

\path[fill=fillColor] ( 72.89,267.16) circle (  1.49);

\path[fill=fillColor] ( 93.64,284.46) circle (  1.49);

\path[fill=fillColor] (103.83,292.30) circle (  1.49);

\path[fill=fillColor] ( 64.27,259.36) circle (  1.49);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (104.28,354.55) {Coverage: 96\%};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,233.11) -- (174.42,233.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,233.11) -- ( 32.47,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 56.13,233.11) -- ( 56.13,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 79.79,233.11) -- ( 79.79,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (103.45,233.11) -- (103.45,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (127.10,233.11) -- (127.10,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (150.76,233.11) -- (150.76,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.42,233.11) -- (174.42,229.15);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 32.47,218.86) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 56.13,218.86) {0.1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 79.79,218.86) {0.2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (103.45,218.86) {0.3};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (127.10,218.86) {0.4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (150.76,218.86) {0.5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (174.42,218.86) {0.6};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,233.11) -- ( 32.47,351.58);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,233.11) -- ( 28.51,233.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,252.86) -- ( 28.51,252.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,272.60) -- ( 28.51,272.60);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,292.34) -- ( 28.51,292.34);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,312.09) -- ( 28.51,312.09);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,331.83) -- ( 28.51,331.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,351.58) -- ( 28.51,351.58);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,230.84) {0.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,250.58) {0.1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,270.33) {0.2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,290.07) {0.3};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,309.82) {0.4};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,329.56) {0.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,349.30) {0.6};
\end{scope}
\begin{scope}
\path[clip] (192.72,192.72) rectangle (385.44,385.44);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.79] at (297.00,366.47) {\bfseries Clock standard deviation $\sigma$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (297.00,203.02) {True value};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (199.85,293.04) {Estimated value};
\end{scope}
\begin{scope}
\path[clip] (225.19,233.11) rectangle (368.81,352.97);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (225.19,233.11) --
	(368.81,352.97);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.20,233.11) --
	(225.20,235.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (255.97,251.22) --
	(255.97,265.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.49,233.11) --
	(225.49,235.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.92,235.60) --
	(230.92,240.09);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.36,233.11) --
	(227.36,235.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.05,233.11) --
	(227.05,235.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (241.68,241.59) --
	(241.68,250.18);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.79,233.11) --
	(232.79,237.60);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (233.76,233.11) --
	(233.76,246.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (238.43,239.46) --
	(238.43,245.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.51,233.11) --
	(225.51,235.53);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.28,233.11) --
	(226.28,237.19);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.23,233.11) --
	(230.23,236.42);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.36,243.70) --
	(240.36,253.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.44,233.11) --
	(225.44,235.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.07,233.11) --
	(228.07,239.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.35,255.95) --
	(261.35,273.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (238.24,239.57) --
	(238.24,245.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.48,233.11) --
	(228.48,239.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.46,235.04) --
	(232.46,241.69);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.38,235.15) --
	(232.38,240.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.77,244.58) --
	(240.77,254.70);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.24,233.11) --
	(228.24,235.36);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (238.92,241.83) --
	(238.92,249.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.37,233.11) --
	(227.37,235.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.43,238.49) --
	(232.43,243.94);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (241.87,241.81) --
	(241.87,251.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.04,233.11) --
	(226.04,237.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.22,233.11) --
	(225.22,235.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.42,236.44) --
	(230.42,244.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.26,242.21) --
	(239.26,249.30);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.68,235.68) --
	(229.68,239.60);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.93,233.11) --
	(230.93,243.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.41,233.11) --
	(227.41,235.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.67,233.11) --
	(225.67,235.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.72,233.11) --
	(226.72,236.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (269.99,261.23) --
	(269.99,284.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.21,233.11) --
	(228.21,240.60);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.33,233.11) --
	(226.33,236.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.49,233.11) --
	(226.49,235.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.33,233.11) --
	(225.33,234.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.90,233.11) --
	(225.90,241.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.62,233.11) --
	(226.62,235.27);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,233.11) --
	(225.19,235.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.10,233.11) --
	(226.10,235.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.74,239.40) --
	(234.74,248.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.62,233.11) --
	(226.62,235.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.14,233.11) --
	(226.14,236.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.54,233.11) --
	(225.54,235.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (246.54,245.01) --
	(246.54,256.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.84,233.11) --
	(225.84,236.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.12,233.11) --
	(227.12,235.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (242.15,241.10) --
	(242.15,248.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (241.68,243.14) --
	(241.68,254.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.26,233.11) --
	(231.26,238.37);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.82,233.11) --
	(230.82,236.95);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.58,234.44) --
	(229.58,238.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (246.35,247.08) --
	(246.35,257.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.43,233.11) --
	(225.43,238.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.47,233.11) --
	(226.47,236.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.55,233.11) --
	(229.55,239.24);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.27,235.54) --
	(232.27,238.86);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.16,233.11) --
	(228.16,238.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (233.25,238.99) --
	(233.25,245.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.14,233.11) --
	(226.14,235.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (279.31,262.62) --
	(279.31,283.56);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.32,233.11) --
	(226.32,237.79);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.25,233.11) --
	(227.25,236.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.67,233.11) --
	(225.67,235.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.55,233.11) --
	(229.55,238.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.73,233.11) --
	(230.73,238.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (230.64,234.09) --
	(230.64,239.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (320.94,283.48) --
	(320.94,330.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.95,233.11) --
	(226.95,236.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (232.77,237.27) --
	(232.77,241.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (250.27,245.97) --
	(250.27,259.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (280.09,267.31) --
	(280.09,291.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (233.09,237.24) --
	(233.09,243.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (240.20,236.30) --
	(240.20,249.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (248.20,248.41) --
	(248.20,263.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.16,233.11) --
	(227.16,236.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.87,233.11) --
	(226.87,237.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,233.11) --
	(225.19,235.06);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (250.60,249.81) --
	(250.60,263.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.30,233.11) --
	(226.30,235.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (234.41,238.10) --
	(234.41,242.72);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (236.08,243.02) --
	(236.08,251.25);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (255.66,253.41) --
	(255.66,268.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.27,233.11) --
	(225.27,237.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (286.90,270.35) --
	(286.90,301.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (243.36,243.98) --
	(243.36,253.30);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (235.80,240.69) --
	(235.80,247.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.41,233.11) --
	(226.41,236.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.44,233.11) --
	(226.44,240.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (227.65,233.11) --
	(227.65,235.93);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.20,233.11) --
	(225.20,234.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.96,234.59) --
	(229.96,238.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.58,233.11) --
	(226.58,236.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (226.84,233.11) --
	(226.84,236.61);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (263.92,250.57) --
	(263.92,263.20);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] (225.20,233.78) circle (  1.49);

\path[fill=fillColor] (255.97,257.95) circle (  1.49);

\path[fill=fillColor] (225.49,233.86) circle (  1.49);

\path[fill=fillColor] (230.92,237.80) circle (  1.49);

\path[fill=fillColor] (227.36,233.95) circle (  1.49);

\path[fill=fillColor] (227.05,233.81) circle (  1.49);

\path[fill=fillColor] (241.68,245.65) circle (  1.49);

\path[fill=fillColor] (232.79,234.68) circle (  1.49);

\path[fill=fillColor] (233.76,240.98) circle (  1.49);

\path[fill=fillColor] (238.43,242.42) circle (  1.49);

\path[fill=fillColor] (225.51,233.87) circle (  1.49);

\path[fill=fillColor] (226.28,234.74) circle (  1.49);

\path[fill=fillColor] (230.23,234.16) circle (  1.49);

\path[fill=fillColor] (240.36,248.49) circle (  1.49);

\path[fill=fillColor] (225.44,233.86) circle (  1.49);

\path[fill=fillColor] (228.07,235.59) circle (  1.49);

\path[fill=fillColor] (261.35,264.37) circle (  1.49);

\path[fill=fillColor] (238.24,242.45) circle (  1.49);

\path[fill=fillColor] (228.48,235.22) circle (  1.49);

\path[fill=fillColor] (232.46,238.23) circle (  1.49);

\path[fill=fillColor] (232.38,237.99) circle (  1.49);

\path[fill=fillColor] (240.77,249.39) circle (  1.49);

\path[fill=fillColor] (228.24,233.85) circle (  1.49);

\path[fill=fillColor] (238.92,245.67) circle (  1.49);

\path[fill=fillColor] (227.37,234.01) circle (  1.49);

\path[fill=fillColor] (232.43,241.08) circle (  1.49);

\path[fill=fillColor] (241.87,246.46) circle (  1.49);

\path[fill=fillColor] (226.04,234.96) circle (  1.49);

\path[fill=fillColor] (225.22,233.75) circle (  1.49);

\path[fill=fillColor] (230.42,240.31) circle (  1.49);

\path[fill=fillColor] (239.26,245.58) circle (  1.49);

\path[fill=fillColor] (229.68,237.54) circle (  1.49);

\path[fill=fillColor] (230.93,237.30) circle (  1.49);

\path[fill=fillColor] (227.41,233.90) circle (  1.49);

\path[fill=fillColor] (225.67,233.92) circle (  1.49);

\path[fill=fillColor] (226.72,234.30) circle (  1.49);

\path[fill=fillColor] (269.99,272.39) circle (  1.49);

\path[fill=fillColor] (228.21,237.54) circle (  1.49);

\path[fill=fillColor] (226.33,234.98) circle (  1.49);

\path[fill=fillColor] (226.49,233.84) circle (  1.49);

\path[fill=fillColor] (225.33,233.64) circle (  1.49);

\path[fill=fillColor] (225.90,235.89) circle (  1.49);

\path[fill=fillColor] (226.62,233.78) circle (  1.49);

\path[fill=fillColor] (225.19,233.74) circle (  1.49);

\path[fill=fillColor] (226.10,234.10) circle (  1.49);

\path[fill=fillColor] (234.74,244.00) circle (  1.49);

\path[fill=fillColor] (226.62,233.89) circle (  1.49);

\path[fill=fillColor] (226.14,234.52) circle (  1.49);

\path[fill=fillColor] (225.54,233.93) circle (  1.49);

\path[fill=fillColor] (246.54,250.33) circle (  1.49);

\path[fill=fillColor] (225.84,234.35) circle (  1.49);

\path[fill=fillColor] (227.12,233.73) circle (  1.49);

\path[fill=fillColor] (242.15,244.37) circle (  1.49);

\path[fill=fillColor] (241.68,248.52) circle (  1.49);

\path[fill=fillColor] (231.26,234.80) circle (  1.49);

\path[fill=fillColor] (230.82,234.65) circle (  1.49);

\path[fill=fillColor] (229.58,236.46) circle (  1.49);

\path[fill=fillColor] (246.35,251.99) circle (  1.49);

\path[fill=fillColor] (225.43,235.18) circle (  1.49);

\path[fill=fillColor] (226.47,235.07) circle (  1.49);

\path[fill=fillColor] (229.55,235.50) circle (  1.49);

\path[fill=fillColor] (232.27,237.13) circle (  1.49);

\path[fill=fillColor] (228.16,236.11) circle (  1.49);

\path[fill=fillColor] (233.25,242.19) circle (  1.49);

\path[fill=fillColor] (226.14,234.13) circle (  1.49);

\path[fill=fillColor] (279.31,272.54) circle (  1.49);

\path[fill=fillColor] (226.32,235.04) circle (  1.49);

\path[fill=fillColor] (227.25,234.70) circle (  1.49);

\path[fill=fillColor] (225.67,233.77) circle (  1.49);

\path[fill=fillColor] (229.55,235.46) circle (  1.49);

\path[fill=fillColor] (230.73,236.23) circle (  1.49);

\path[fill=fillColor] (230.64,236.67) circle (  1.49);

\path[fill=fillColor] (320.94,306.02) circle (  1.49);

\path[fill=fillColor] (226.95,234.20) circle (  1.49);

\path[fill=fillColor] (232.77,239.15) circle (  1.49);

\path[fill=fillColor] (250.27,252.29) circle (  1.49);

\path[fill=fillColor] (280.09,278.51) circle (  1.49);

\path[fill=fillColor] (233.09,240.12) circle (  1.49);

\path[fill=fillColor] (240.20,242.37) circle (  1.49);

\path[fill=fillColor] (248.20,255.66) circle (  1.49);

\path[fill=fillColor] (227.16,234.13) circle (  1.49);

\path[fill=fillColor] (226.87,235.30) circle (  1.49);

\path[fill=fillColor] (225.19,233.73) circle (  1.49);

\path[fill=fillColor] (250.60,256.38) circle (  1.49);

\path[fill=fillColor] (226.30,233.89) circle (  1.49);

\path[fill=fillColor] (234.41,240.35) circle (  1.49);

\path[fill=fillColor] (236.08,246.93) circle (  1.49);

\path[fill=fillColor] (255.66,260.83) circle (  1.49);

\path[fill=fillColor] (225.27,235.26) circle (  1.49);

\path[fill=fillColor] (286.90,285.54) circle (  1.49);

\path[fill=fillColor] (243.36,248.40) circle (  1.49);

\path[fill=fillColor] (235.80,243.89) circle (  1.49);

\path[fill=fillColor] (226.41,234.10) circle (  1.49);

\path[fill=fillColor] (226.44,235.64) circle (  1.49);

\path[fill=fillColor] (227.65,234.04) circle (  1.49);

\path[fill=fillColor] (225.20,233.65) circle (  1.49);

\path[fill=fillColor] (229.96,236.31) circle (  1.49);

\path[fill=fillColor] (226.58,234.27) circle (  1.49);

\path[fill=fillColor] (226.84,234.21) circle (  1.49);

\path[fill=fillColor] (263.92,256.34) circle (  1.49);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (297.00,354.55) {Coverage: 93\%};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,233.11) -- (356.16,233.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,233.11) -- (225.19,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (247.02,233.11) -- (247.02,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (268.85,233.11) -- (268.85,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (290.68,233.11) -- (290.68,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (312.51,233.11) -- (312.51,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (334.33,233.11) -- (334.33,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (356.16,233.11) -- (356.16,229.15);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (225.19,218.86) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (247.02,218.86) {0.5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (268.85,218.86) {1.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (290.68,218.86) {1.5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (312.51,218.86) {2.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (334.33,218.86) {2.5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (356.16,218.86) {3.0};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,233.11) -- (225.19,342.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,233.11) -- (221.23,233.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,251.33) -- (221.23,251.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,269.55) -- (221.23,269.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,287.76) -- (221.23,287.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,305.98) -- (221.23,305.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,324.20) -- (221.23,324.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.19,342.41) -- (221.23,342.41);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,230.84) {0.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,249.06) {0.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,267.27) {1.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,285.49) {1.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,303.71) {2.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,321.92) {2.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (217.27,340.14) {3.0};
\end{scope}
\begin{scope}
\path[clip] (385.44,192.72) rectangle (578.16,385.44);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.79] at (489.72,366.47) {\bfseries Branch rate mean};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (489.72,203.02) {True value};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (392.57,293.04) {Estimated value};
\end{scope}
\begin{scope}
\path[clip] (417.91,233.11) rectangle (561.53,352.97);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (417.91,233.11) --
	(561.53,352.97);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.34,300.35) --
	(499.34,301.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (498.07,279.07) --
	(498.07,308.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.37,300.20) --
	(499.37,301.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.75,297.47) --
	(499.75,303.91);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (497.93,300.22) --
	(497.93,302.00);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.66,300.38) --
	(499.66,301.87);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (511.94,297.00) --
	(511.94,318.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.42,299.34) --
	(499.42,302.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (498.78,293.72) --
	(498.78,305.06);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (502.51,295.19) --
	(502.51,307.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.30,300.24) --
	(499.30,301.93);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.47,299.33) --
	(499.47,302.80);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (500.50,299.93) --
	(500.50,301.99);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (502.61,291.01) --
	(502.61,311.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.14,300.37) --
	(499.14,302.04);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.54,298.84) --
	(499.54,303.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (488.59,285.43) --
	(488.59,330.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (503.34,293.94) --
	(503.34,305.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (500.21,298.89) --
	(500.21,302.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.62,297.86) --
	(495.62,304.37);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (494.16,297.32) --
	(494.16,304.09);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (503.26,290.87) --
	(503.26,314.41);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (498.40,300.36) --
	(498.40,302.00);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (497.73,292.77) --
	(497.73,309.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.97,300.00) --
	(499.97,301.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.06,296.50) --
	(499.06,306.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (504.00,293.09) --
	(504.00,310.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.17,299.22) --
	(499.17,302.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.32,300.30) --
	(499.32,301.79);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (501.08,296.43) --
	(501.08,306.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (502.59,293.01) --
	(502.59,308.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (500.41,297.94) --
	(500.41,304.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (498.83,296.91) --
	(498.83,304.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (498.76,300.18) --
	(498.76,301.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.23,300.18) --
	(499.23,301.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.15,299.88) --
	(499.15,302.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (470.58,267.14) --
	(470.58,316.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (500.07,297.39) --
	(500.07,303.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (498.76,299.66) --
	(498.76,302.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.94,300.34) --
	(499.94,301.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.40,300.51) --
	(499.40,301.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.56,298.32) --
	(499.56,304.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.01,300.21) --
	(499.01,302.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.33,300.39) --
	(499.33,301.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.97,300.05) --
	(499.97,302.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.11,293.03) --
	(499.11,307.20);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (498.27,300.19) --
	(498.27,301.90);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.49,299.91) --
	(499.49,302.70);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.34,300.13) --
	(499.34,301.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.75,290.14) --
	(495.75,310.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.33,299.37) --
	(499.33,302.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (500.00,300.35) --
	(500.00,301.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (495.64,293.15) --
	(495.64,306.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (493.70,290.58) --
	(493.70,309.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (500.04,299.13) --
	(500.04,302.88);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (501.67,299.98) --
	(501.67,303.00);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (498.94,298.45) --
	(498.94,303.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (513.66,290.03) --
	(513.66,313.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.36,298.70) --
	(499.36,302.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (500.13,299.55) --
	(500.13,302.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.94,298.82) --
	(499.94,303.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (501.06,298.80) --
	(501.06,303.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (500.48,298.43) --
	(500.48,303.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.03,293.80) --
	(499.03,305.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.09,300.03) --
	(499.09,302.01);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (471.77,273.15) --
	(471.77,327.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.13,299.42) --
	(499.13,302.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.78,299.61) --
	(499.78,302.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.48,300.30) --
	(499.48,301.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (500.07,298.92) --
	(500.07,303.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (497.09,298.27) --
	(497.09,302.70);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.20,298.51) --
	(499.20,303.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (445.97,237.33) --
	(445.97,347.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.16,299.78) --
	(499.16,301.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (498.31,296.44) --
	(498.31,303.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (506.39,287.49) --
	(506.39,312.34);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (503.68,269.92) --
	(503.68,347.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.97,295.67) --
	(499.97,304.30);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (485.26,292.64) --
	(485.26,306.08);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (504.97,288.15) --
	(504.97,319.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.56,299.88) --
	(499.56,302.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (500.39,299.14) --
	(500.39,302.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.33,300.29) --
	(499.33,301.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (512.41,284.47) --
	(512.41,313.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.72,300.16) --
	(499.72,301.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (496.68,296.20) --
	(496.68,304.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (501.71,292.12) --
	(501.71,308.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (501.78,280.06) --
	(501.78,314.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.34,299.09) --
	(499.34,302.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.92,255.86) --
	(474.92,330.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (500.91,292.59) --
	(500.91,313.09);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (500.40,295.70) --
	(500.40,309.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.35,299.95) --
	(499.35,302.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (498.96,298.24) --
	(498.96,303.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (498.65,300.16) --
	(498.65,302.04);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.33,300.37) --
	(499.33,301.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (500.11,299.10) --
	(500.11,303.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.80,299.79) --
	(499.80,302.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (498.47,299.89) --
	(498.47,302.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (487.56,285.14) --
	(487.56,315.11);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] (499.34,301.11) circle (  1.49);

\path[fill=fillColor] (498.07,294.03) circle (  1.49);

\path[fill=fillColor] (499.37,301.02) circle (  1.49);

\path[fill=fillColor] (499.75,300.60) circle (  1.49);

\path[fill=fillColor] (497.93,301.08) circle (  1.49);

\path[fill=fillColor] (499.66,301.09) circle (  1.49);

\path[fill=fillColor] (511.94,307.52) circle (  1.49);

\path[fill=fillColor] (499.42,300.98) circle (  1.49);

\path[fill=fillColor] (498.78,299.70) circle (  1.49);

\path[fill=fillColor] (502.51,301.26) circle (  1.49);

\path[fill=fillColor] (499.30,301.06) circle (  1.49);

\path[fill=fillColor] (499.47,301.05) circle (  1.49);

\path[fill=fillColor] (500.50,301.03) circle (  1.49);

\path[fill=fillColor] (502.61,301.05) circle (  1.49);

\path[fill=fillColor] (499.14,301.12) circle (  1.49);

\path[fill=fillColor] (499.54,301.13) circle (  1.49);

\path[fill=fillColor] (488.59,307.43) circle (  1.49);

\path[fill=fillColor] (503.34,299.86) circle (  1.49);

\path[fill=fillColor] (500.21,300.95) circle (  1.49);

\path[fill=fillColor] (495.62,301.14) circle (  1.49);

\path[fill=fillColor] (494.16,300.82) circle (  1.49);

\path[fill=fillColor] (503.26,302.70) circle (  1.49);

\path[fill=fillColor] (498.40,301.12) circle (  1.49);

\path[fill=fillColor] (497.73,301.34) circle (  1.49);

\path[fill=fillColor] (499.97,301.01) circle (  1.49);

\path[fill=fillColor] (499.06,301.66) circle (  1.49);

\path[fill=fillColor] (504.00,301.70) circle (  1.49);

\path[fill=fillColor] (499.17,301.10) circle (  1.49);

\path[fill=fillColor] (499.32,301.07) circle (  1.49);

\path[fill=fillColor] (501.08,301.42) circle (  1.49);

\path[fill=fillColor] (502.59,300.86) circle (  1.49);

\path[fill=fillColor] (500.41,301.22) circle (  1.49);

\path[fill=fillColor] (498.83,300.84) circle (  1.49);

\path[fill=fillColor] (498.76,301.06) circle (  1.49);

\path[fill=fillColor] (499.23,301.05) circle (  1.49);

\path[fill=fillColor] (499.15,301.03) circle (  1.49);

\path[fill=fillColor] (470.58,292.44) circle (  1.49);

\path[fill=fillColor] (500.07,300.64) circle (  1.49);

\path[fill=fillColor] (498.76,301.18) circle (  1.49);

\path[fill=fillColor] (499.94,301.06) circle (  1.49);

\path[fill=fillColor] (499.40,301.08) circle (  1.49);

\path[fill=fillColor] (499.56,301.12) circle (  1.49);

\path[fill=fillColor] (499.01,301.09) circle (  1.49);

\path[fill=fillColor] (499.33,301.05) circle (  1.49);

\path[fill=fillColor] (499.97,301.07) circle (  1.49);

\path[fill=fillColor] (499.11,300.47) circle (  1.49);

\path[fill=fillColor] (498.27,301.07) circle (  1.49);

\path[fill=fillColor] (499.49,301.19) circle (  1.49);

\path[fill=fillColor] (499.34,301.05) circle (  1.49);

\path[fill=fillColor] (495.75,300.48) circle (  1.49);

\path[fill=fillColor] (499.33,300.90) circle (  1.49);

\path[fill=fillColor] (500.00,301.03) circle (  1.49);

\path[fill=fillColor] (495.64,300.14) circle (  1.49);

\path[fill=fillColor] (493.70,300.41) circle (  1.49);

\path[fill=fillColor] (500.04,301.04) circle (  1.49);

\path[fill=fillColor] (501.67,301.24) circle (  1.49);

\path[fill=fillColor] (498.94,300.79) circle (  1.49);

\path[fill=fillColor] (513.66,301.64) circle (  1.49);

\path[fill=fillColor] (499.36,300.92) circle (  1.49);

\path[fill=fillColor] (500.13,301.14) circle (  1.49);

\path[fill=fillColor] (499.94,301.19) circle (  1.49);

\path[fill=fillColor] (501.06,301.27) circle (  1.49);

\path[fill=fillColor] (500.48,300.82) circle (  1.49);

\path[fill=fillColor] (499.03,299.57) circle (  1.49);

\path[fill=fillColor] (499.09,301.05) circle (  1.49);

\path[fill=fillColor] (471.77,299.97) circle (  1.49);

\path[fill=fillColor] (499.13,301.11) circle (  1.49);

\path[fill=fillColor] (499.78,301.03) circle (  1.49);

\path[fill=fillColor] (499.48,301.04) circle (  1.49);

\path[fill=fillColor] (500.07,301.08) circle (  1.49);

\path[fill=fillColor] (497.09,300.67) circle (  1.49);

\path[fill=fillColor] (499.20,300.89) circle (  1.49);

\path[fill=fillColor] (445.97,288.93) circle (  1.49);

\path[fill=fillColor] (499.16,300.98) circle (  1.49);

\path[fill=fillColor] (498.31,300.00) circle (  1.49);

\path[fill=fillColor] (506.39,299.45) circle (  1.49);

\path[fill=fillColor] (503.68,310.30) circle (  1.49);

\path[fill=fillColor] (499.97,300.03) circle (  1.49);

\path[fill=fillColor] (485.26,299.86) circle (  1.49);

\path[fill=fillColor] (504.97,303.91) circle (  1.49);

\path[fill=fillColor] (499.56,301.02) circle (  1.49);

\path[fill=fillColor] (500.39,301.02) circle (  1.49);

\path[fill=fillColor] (499.33,301.04) circle (  1.49);

\path[fill=fillColor] (512.41,298.79) circle (  1.49);

\path[fill=fillColor] (499.72,301.01) circle (  1.49);

\path[fill=fillColor] (496.68,300.47) circle (  1.49);

\path[fill=fillColor] (501.71,300.36) circle (  1.49);

\path[fill=fillColor] (501.78,297.25) circle (  1.49);

\path[fill=fillColor] (499.34,300.76) circle (  1.49);

\path[fill=fillColor] (474.92,291.97) circle (  1.49);

\path[fill=fillColor] (500.91,303.14) circle (  1.49);

\path[fill=fillColor] (500.40,302.50) circle (  1.49);

\path[fill=fillColor] (499.35,301.06) circle (  1.49);

\path[fill=fillColor] (498.96,300.92) circle (  1.49);

\path[fill=fillColor] (498.65,301.08) circle (  1.49);

\path[fill=fillColor] (499.33,301.08) circle (  1.49);

\path[fill=fillColor] (500.11,301.24) circle (  1.49);

\path[fill=fillColor] (499.80,301.03) circle (  1.49);

\path[fill=fillColor] (498.47,301.07) circle (  1.49);

\path[fill=fillColor] (487.56,300.48) circle (  1.49);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (489.72,354.55) {Coverage: 93\%};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,233.11) -- (540.05,233.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,233.11) -- (417.91,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (458.62,233.11) -- (458.62,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (499.33,233.11) -- (499.33,229.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (540.05,233.11) -- (540.05,229.15);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (417.91,218.86) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (458.62,218.86) {0.5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (499.33,218.86) {1.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (540.05,218.86) {1.5};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,233.11) -- (417.91,335.04);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,233.11) -- (413.95,233.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,267.09) -- (413.95,267.09);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,301.06) -- (413.95,301.06);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (417.91,335.04) -- (413.95,335.04);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,230.84) {0.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,264.81) {0.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,298.79) {1.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at (409.99,332.77) {1.5};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (192.72,192.72);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.79] at (104.28,173.75) {\bfseries Branch rate variance};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (104.28, 10.30) {True value};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (  7.13,100.32) {Estimated value};
\end{scope}
\begin{scope}
\path[clip] ( 32.47, 40.39) rectangle (176.09,160.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] ( 32.47, 40.39) --
	(176.09,160.25);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 43.21, 42.42) --
	( 43.21, 50.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.67, 40.43) --
	( 32.67, 40.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.50, 40.39) --
	( 32.50, 40.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.50, 40.39) --
	( 32.50, 40.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 34.14, 40.91) --
	( 34.14, 42.59);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.81, 40.39) --
	( 32.81, 40.54);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.99, 40.39) --
	( 32.99, 41.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.37, 40.69) --
	( 33.37, 41.49);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.51);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.66, 40.39) --
	( 32.66, 40.47);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 34.20, 41.18) --
	( 34.20, 43.69);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.52, 40.39) --
	( 32.52, 40.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.76, 43.24) --
	( 48.76, 63.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.41, 40.71) --
	( 33.41, 41.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.56, 40.39) --
	( 32.56, 40.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.69, 40.39) --
	( 32.69, 40.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.77, 40.39) --
	( 32.77, 40.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 34.26, 41.41) --
	( 34.26, 44.88);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.54, 40.39) --
	( 32.54, 40.43);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.69, 40.99) --
	( 33.69, 42.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.51, 40.39) --
	( 32.51, 40.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.90, 40.62) --
	( 32.90, 41.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.95, 40.92) --
	( 33.95, 42.69);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.53);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.70, 40.44) --
	( 32.70, 41.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.69, 41.09) --
	( 33.69, 42.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.62, 40.44) --
	( 32.62, 40.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.72, 40.39) --
	( 32.72, 41.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.51, 40.39) --
	( 32.51, 40.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.49, 40.39) --
	( 32.49, 40.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 38.92, 43.50) --
	( 38.92, 88.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.53, 40.39) --
	( 32.53, 40.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.49);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.94, 40.66) --
	( 32.94, 42.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 34.77, 41.38) --
	( 34.77, 44.30);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.49);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.50, 40.39) --
	( 32.50, 40.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 34.13, 40.85) --
	( 34.13, 41.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 34.11, 41.10) --
	( 34.11, 43.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.61, 40.39) --
	( 32.61, 40.59);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.62, 40.39) --
	( 32.62, 40.50);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.60, 40.39) --
	( 32.60, 40.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 37.00, 41.70) --
	( 37.00, 45.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.50);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.55, 40.39) --
	( 32.55, 40.66);
\definecolor{drawColor}{RGB}{186,46,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.75, 40.43) --
	( 32.75, 40.61);
\definecolor{drawColor}{RGB}{0,140,186}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.56, 40.39) --
	( 32.56, 40.60);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.91, 40.66) --
	( 32.91, 41.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 46.10, 43.14) --
	( 46.10, 76.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.50, 40.39) --
	( 32.50, 40.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.59, 40.39) --
	( 32.59, 40.56);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.65, 40.39) --
	( 32.65, 40.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.62, 40.39) --
	( 32.62, 40.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 46.23, 40.44) --
	( 46.23,292.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.49, 40.39) --
	( 32.49, 40.47);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.81, 40.52) --
	( 32.81, 40.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.92, 41.43) --
	( 35.92, 45.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.73, 43.34) --
	( 49.73,120.56);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.88, 40.50) --
	( 32.88, 41.09);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.31, 40.39) --
	( 33.31, 42.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 35.73, 42.18) --
	( 35.73, 49.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.50, 40.39) --
	( 32.50, 40.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.49, 40.39) --
	( 32.49, 40.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 41.18, 42.66) --
	( 41.18, 52.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.01, 40.59) --
	( 33.01, 41.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.93, 41.21) --
	( 33.93, 43.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 38.21, 43.31) --
	( 38.21, 56.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 43.94, 41.55) --
	( 43.94,142.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 34.22, 41.27) --
	( 34.22, 43.32);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.42, 40.80) --
	( 33.42, 41.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.50, 40.39) --
	( 32.50, 40.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) --
	( 32.47, 40.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.59, 40.41) --
	( 32.59, 40.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.48, 40.39) --
	( 32.48, 40.49);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.49, 40.39) --
	( 32.49, 40.48);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 38.60, 42.52) --
	( 38.60, 49.84);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 43.21, 45.80) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.67, 40.56) circle (  1.49);

\path[fill=fillColor] ( 32.50, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.50, 40.40) circle (  1.49);

\path[fill=fillColor] ( 34.14, 41.67) circle (  1.49);

\path[fill=fillColor] ( 32.81, 40.43) circle (  1.49);

\path[fill=fillColor] ( 32.99, 40.92) circle (  1.49);

\path[fill=fillColor] ( 33.37, 41.05) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.42) circle (  1.49);

\path[fill=fillColor] ( 32.66, 40.41) circle (  1.49);

\path[fill=fillColor] ( 34.20, 42.23) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.52, 40.46) circle (  1.49);

\path[fill=fillColor] ( 48.76, 51.18) circle (  1.49);

\path[fill=fillColor] ( 33.41, 41.04) circle (  1.49);

\path[fill=fillColor] ( 32.56, 40.45) circle (  1.49);

\path[fill=fillColor] ( 32.69, 40.60) circle (  1.49);

\path[fill=fillColor] ( 32.77, 40.58) circle (  1.49);

\path[fill=fillColor] ( 34.26, 42.88) circle (  1.49);

\path[fill=fillColor] ( 32.54, 40.40) circle (  1.49);

\path[fill=fillColor] ( 33.69, 41.64) circle (  1.49);

\path[fill=fillColor] ( 32.51, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.90, 40.88) circle (  1.49);

\path[fill=fillColor] ( 33.95, 41.69) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.43) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.70, 40.80) circle (  1.49);

\path[fill=fillColor] ( 33.69, 41.64) circle (  1.49);

\path[fill=fillColor] ( 32.62, 40.54) circle (  1.49);

\path[fill=fillColor] ( 32.72, 40.60) circle (  1.49);

\path[fill=fillColor] ( 32.51, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.49, 40.41) circle (  1.49);

\path[fill=fillColor] ( 38.92, 60.72) circle (  1.49);

\path[fill=fillColor] ( 32.53, 40.56) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.43) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.51) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.41) circle (  1.49);

\path[fill=fillColor] ( 32.94, 41.31) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.42) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 34.77, 42.65) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.41) circle (  1.49);

\path[fill=fillColor] ( 32.50, 40.40) circle (  1.49);

\path[fill=fillColor] ( 34.13, 41.35) circle (  1.49);

\path[fill=fillColor] ( 34.11, 42.28) circle (  1.49);

\path[fill=fillColor] ( 32.61, 40.43) circle (  1.49);

\path[fill=fillColor] ( 32.62, 40.42) circle (  1.49);

\path[fill=fillColor] ( 32.60, 40.48) circle (  1.49);

\path[fill=fillColor] ( 37.00, 43.14) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.45) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.43) circle (  1.49);

\path[fill=fillColor] ( 32.55, 40.46) circle (  1.49);

\path[fill=fillColor] ( 32.75, 40.51) circle (  1.49);

\path[fill=fillColor] ( 32.56, 40.47) circle (  1.49);

\path[fill=fillColor] ( 32.91, 41.03) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.41) circle (  1.49);

\path[fill=fillColor] ( 46.10, 56.76) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.43) circle (  1.49);

\path[fill=fillColor] ( 32.50, 40.42) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.59, 40.45) circle (  1.49);

\path[fill=fillColor] ( 32.65, 40.48) circle (  1.49);

\path[fill=fillColor] ( 32.62, 40.49) circle (  1.49);

\path[fill=fillColor] ( 46.23,120.30) circle (  1.49);

\path[fill=fillColor] ( 32.49, 40.41) circle (  1.49);

\path[fill=fillColor] ( 32.81, 40.67) circle (  1.49);

\path[fill=fillColor] ( 35.92, 43.18) circle (  1.49);

\path[fill=fillColor] ( 49.73, 72.06) circle (  1.49);

\path[fill=fillColor] ( 32.88, 40.77) circle (  1.49);

\path[fill=fillColor] ( 33.31, 41.12) circle (  1.49);

\path[fill=fillColor] ( 35.73, 45.14) circle (  1.49);

\path[fill=fillColor] ( 32.50, 40.41) circle (  1.49);

\path[fill=fillColor] ( 32.49, 40.44) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 41.18, 46.58) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.40) circle (  1.49);

\path[fill=fillColor] ( 33.01, 40.79) circle (  1.49);

\path[fill=fillColor] ( 33.93, 42.01) circle (  1.49);

\path[fill=fillColor] ( 38.21, 48.65) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.44) circle (  1.49);

\path[fill=fillColor] ( 43.94, 76.74) circle (  1.49);

\path[fill=fillColor] ( 34.22, 42.20) circle (  1.49);

\path[fill=fillColor] ( 33.42, 41.24) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.41) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.48) circle (  1.49);

\path[fill=fillColor] ( 32.50, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.47, 40.40) circle (  1.49);

\path[fill=fillColor] ( 32.59, 40.47) circle (  1.49);

\path[fill=fillColor] ( 32.48, 40.41) circle (  1.49);

\path[fill=fillColor] ( 32.49, 40.41) circle (  1.49);

\path[fill=fillColor] ( 38.60, 45.75) circle (  1.49);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (104.28,161.83) {Coverage: 95\%};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) -- (174.17, 40.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) -- ( 32.47, 36.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 56.09, 40.39) -- ( 56.09, 36.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 79.70, 40.39) -- ( 79.70, 36.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (103.32, 40.39) -- (103.32, 36.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (126.93, 40.39) -- (126.93, 36.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (150.55, 40.39) -- (150.55, 36.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.17, 40.39) -- (174.17, 36.43);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 32.47, 26.14) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 56.09, 26.14) {2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 79.70, 26.14) {4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (103.32, 26.14) {6};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (126.93, 26.14) {8};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (150.55, 26.14) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.66] at (174.17, 26.14) {12};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) -- ( 32.47,158.64);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 40.39) -- ( 28.51, 40.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 60.10) -- ( 28.51, 60.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 79.81) -- ( 28.51, 79.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47, 99.52) -- ( 28.51, 99.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,119.23) -- ( 28.51,119.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,138.93) -- ( 28.51,138.93);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 32.47,158.64) -- ( 28.51,158.64);

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55, 38.12) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55, 57.83) {2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55, 77.54) {4};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55, 97.24) {6};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,116.95) {8};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,136.66) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.66] at ( 24.55,156.37) {12};
\end{scope}
\end{tikzpicture}

\end{document}

### 2020-09-01 S1_appendix.tex
complete draft

@@
 
-\section*{S1 Appendix: Tree operators for rate quantiles}
+\section*{S1 Appendix: Rate quantiles}
 
-Zhang and Drummond 2020 introduced several tree operators for the \textit{real} parameterisation -- including Constant Distance, Simple Distance, and Small Pulley \cite{zhang2020improving}.
-In this appendix, these three operators are extended to the  the \textit{quant} parameterisation.
-Following the notation presented in the main article, let $t_i$ be the time of node $i$, let $0 < q_i < 1$ be the rate quantile of node $i$, and let $r_i = F^{-1}(q_i)$ be the real rate of node $i$ where $F^{-1}$ is the inverse cumulative density function (i-CDF).
+\section{Piecewise linear approximation}
+
+In this article we introduced a linear piecewise approximation of the i-CDF (inverse cumulative distribution function) to improve the computational performance of the \textit{quant} parameterisation. 
+Let $\hat{F}^{-1}(\mathcal{R}_i)$ be the piecewise approximation of the i-CDF $F^{-1}(\mathcal{R}_i)$. 
+The approximation consists of $n$ pieces (where $n=100$ is fixed).
+Due to the nonlinear nature of small and large quantiles in a Log-normal distribution, the first and last pieces are not linear approximations but rather equal to the underlying distribution itself.
+
+%$\hat{F}(\mathcal{R}_i)$ be the piecewise approximation of $F(\mathcal{R}_i)$, and let  be its inverse function.
+
+\begin{align}
+\hat{F}^{-1}(q) = \begin{cases} 
+F^{-1}(q) &\text{ if } q \leq \frac{1}{n} \text{ or } q \geq \frac{n-1}{n} \\ 
+F^{-1}(\floor{v}) + \Big(F^{-1}(\floor{v}+1) - F^{-1}(\floor{v}) \Big) \Big( v - \floor{v} \Big)  &\text{ otherwise}. 
+\end{cases}
+\end{align}
+
+where $v = q(n-1)$ indexes quantile $q$ into piece number $\floor{v}$.
+Values from the underlying function $F^{-1}$ are cached, enabling rapid computation.
+
+\section{Tree operators for rate quantiles}
+
+Zhang and Drummond 2020 introduced several tree operators for the \textit{real} parameterisation -- including \texttt{ConstantDistance}, \texttt{SimpleDistance}, and \texttt{SmallPulley} \cite{zhang2020improving}.
+In this appendix, these three operators are extended to the \textit{quant} parameterisation.
+Following the notation presented in the main article, let $t_i$ be the time of node $i$, let $0 < q_i < 1$ be the rate quantile of node $i$, and let $r_i = \hat{F^{-1}}(q_i)$ be the real rate of node $i$ where $\hat{F^{-1}}$ is the linear approximation of the i-CDF.
 
@@
 \begin{align}
-	{q_\mathcal{X}}^\prime  \leftarrow & F\Big({r_\mathcal{X}}^\prime \Big) \nonumber\\
-				\leftarrow & F\Big(\frac{t_\mathcal{P} - t_\mathcal{X}}{t_\mathcal{P} - {t_\mathcal{X}}^\prime} r_X \Big)\nonumber \\
-				\leftarrow & F\Big(\frac{t_\mathcal{P} - t_\mathcal{X}}{t_\mathcal{P} - {t_\mathcal{X}}^\prime} F^{-1}(q_\mathcal{X}) \Big).
+	{q_\mathcal{X}}^\prime  \leftarrow & \hat{F}\Big({r_\mathcal{X}}^\prime \Big) \nonumber\\
+				\leftarrow & \hat{F}\Big(\frac{t_\mathcal{P} - t_\mathcal{X}}{t_\mathcal{P} - {t_\mathcal{X}}^\prime} r_X \Big)\nonumber \\
+				\leftarrow & \hat{F}\Big(\frac{t_\mathcal{P} - t_\mathcal{X}}{t_\mathcal{P} - {t_\mathcal{X}}^\prime} \hat{F^{-1}}(q_\mathcal{X}) \Big).
 \end{align}
@@
 \begin{align}
-	{q_\mathcal{C}}^\prime  \leftarrow & F\Big({r_\mathcal{C}}^\prime \Big) \nonumber\\
-				\leftarrow & F\Big(\frac{t_\mathcal{X} - t_\mathcal{C}}{{t_\mathcal{X}}^\prime - t_\mathcal{C}} \times r_\mathcal{C} \Big) \nonumber\\
-				\leftarrow & F\Big(\frac{t_\mathcal{X} - t_\mathcal{C}}{{t_\mathcal{X}}^\prime - t_\mathcal{C}} \times F^{-1}(q_\mathcal{C}) \Big).
+	{q_\mathcal{C}}^\prime  \leftarrow & \hat{F}\Big({r_\mathcal{C}}^\prime \Big) \nonumber\\
+				\leftarrow & \hat{F}\Big(\frac{t_\mathcal{X} - t_\mathcal{C}}{{t_\mathcal{X}}^\prime - t_\mathcal{C}} \times r_\mathcal{C} \Big) \nonumber\\
+				\leftarrow & \hat{F}\Big(\frac{t_\mathcal{X} - t_\mathcal{C}}{{t_\mathcal{X}}^\prime - t_\mathcal{C}} \times \hat{F^{-1}}(q_\mathcal{C}) \Big).
 \end{align}
@@
 	\ln |J| =&  \ln \{ \frac{\partial {t_\mathcal{X}}^\prime}{\partial t_\mathcal{X}} \times \frac{\partial {q_\mathcal{X}}^\prime}{\partial q_\mathcal{X}} \times \frac{\partial {q_\mathcal{L}}^\prime}{\partial q_\mathcal{L}} \times \frac{\partial {q_\mathcal{R}}^\prime}{\partial q_\mathcal{R}} \} \nonumber\\
-		=& \ln 1 + \ln \; D F\Big( \frac{t_\mathcal{P} - t_\mathcal{X}}{t_\mathcal{P} - {t_\mathcal{X}}^\prime} \times F^{-1}(q_\mathcal{X})  \Big) + \ln \frac{\partial}{\partial q_\mathcal{X}}  \frac{t_\mathcal{P} - t_\mathcal{X}}{t_\mathcal{P} - {t_\mathcal{X}}^\prime} F^{-1} \Big( q_\mathcal{X} \Big) \nonumber\\
-		& + \ln \; DF\Big( \frac{t_X - t_\mathcal{L}}{{t_\mathcal{X}}^\prime - t_\mathcal{L}} \times F^{-1}(q_\mathcal{L}) \Big) + \ln \frac{\partial}{\partial q_\mathcal{L}} \frac{t_\mathcal{X} - t_\mathcal{L}}{{t_\mathcal{X}}^\prime - t_\mathcal{L}} F^{-1} \Big( q_\mathcal{L} \Big) \nonumber\\
-		& + \ln \; D F\Big( \frac{t_\mathcal{X} - t_\mathcal{R}}{{t_\mathcal{X}}^\prime - t_\mathcal{R}} \times F^{-1}(q_\mathcal{R}) \Big) + \ln \frac{\partial}{\partial q_\mathcal{R}} \frac{t_\mathcal{X} - t_\mathcal{R}}{{t_\mathcal{X}}^\prime - t_\mathcal{R}} F^{-1} \Big( q_\mathcal{R} \Big) \nonumber\\
-		=& \ln \; D F\Big( \frac{t_\mathcal{P} - t_\mathcal{X}}{t_\mathcal{P} - {t_\mathcal{X}}^\prime} \times F^{-1}(q_\mathcal{X})  \Big) + \ln \; D  F^{-1} \Big( q_\mathcal{X} \Big) + \ln \frac{t_\mathcal{P} - t_\mathcal{X}}{t_\mathcal{P} - {t_\mathcal{X}}^\prime} \nonumber\\
-		& + \ln \; DF\Big( \frac{t_\mathcal{X} - t_\mathcal{L}}{{t_\mathcal{X}}^\prime - t_\mathcal{L}} \times F^{-1}(q_\mathcal{L}) \Big) + \ln \; D F^{-1} \Big( q_\mathcal{L} \Big) + \ln  \frac{t_\mathcal{X} - t_\mathcal{L}}{{t_\mathcal{X}}^\prime - t_\mathcal{L}} \nonumber \\
-		& + \ln \; D F\Big( \frac{t_\mathcal{X} - t_\mathcal{R}}{{t_\mathcal{X}}^\prime - t_\mathcal{R}} \times F^{-1}(q_\mathcal{R}) \Big) + \ln \; DF^{-1} \Big( q_\mathcal{R} \Big) + \ln \frac{t_\mathcal{X} - t_\mathcal{R}}{{t_\mathcal{X}}^\prime - t_\mathcal{R}} .
+		=& \ln 1 + \ln \; D \hat{F}\Big( \frac{t_\mathcal{P} - t_\mathcal{X}}{t_\mathcal{P} - {t_\mathcal{X}}^\prime} \times \hat{F^{-1}}(q_\mathcal{X})  \Big) + \ln \frac{\partial}{\partial q_\mathcal{X}}  \frac{t_\mathcal{P} - t_\mathcal{X}}{t_\mathcal{P} - {t_\mathcal{X}}^\prime} \hat{F^{-1}} \Big( q_\mathcal{X} \Big) \nonumber\\
+		& + \ln \; D\hat{F}\Big( \frac{t_X - t_\mathcal{L}}{{t_\mathcal{X}}^\prime - t_\mathcal{L}} \times \hat{F^{-1}}(q_\mathcal{L}) \Big) + \ln \frac{\partial}{\partial q_\mathcal{L}} \frac{t_\mathcal{X} - t_\mathcal{L}}{{t_\mathcal{X}}^\prime - t_\mathcal{L}} \hat{F^{-1}} \Big( q_\mathcal{L} \Big) \nonumber\\
+		& + \ln \; D \hat{F}\Big( \frac{t_\mathcal{X} - t_\mathcal{R}}{{t_\mathcal{X}}^\prime - t_\mathcal{R}} \times \hat{F^{-1}}(q_\mathcal{R}) \Big) + \ln \frac{\partial}{\partial q_\mathcal{R}} \frac{t_\mathcal{X} - t_\mathcal{R}}{{t_\mathcal{X}}^\prime - t_\mathcal{R}} \hat{F^{-1}} \Big( q_\mathcal{R} \Big) \nonumber\\
+		=& \ln \; D \hat{F}\Big( \frac{t_\mathcal{P} - t_\mathcal{X}}{t_\mathcal{P} - {t_\mathcal{X}}^\prime} \times \hat{F^{-1}}(q_\mathcal{X})  \Big) + \ln \; D  \hat{F^{-1}} \Big( q_\mathcal{X} \Big) + \ln \frac{t_\mathcal{P} - t_\mathcal{X}}{t_\mathcal{P} - {t_\mathcal{X}}^\prime} \nonumber\\
+		& + \ln \; D\hat{F}\Big( \frac{t_\mathcal{X} - t_\mathcal{L}}{{t_\mathcal{X}}^\prime - t_\mathcal{L}} \times \hat{F^{-1}}(q_\mathcal{L}) \Big) + \ln \; D \hat{F^{-1}} \Big( q_\mathcal{L} \Big) + \ln  \frac{t_\mathcal{X} - t_\mathcal{L}}{{t_\mathcal{X}}^\prime - t_\mathcal{L}} \nonumber \\
+		& + \ln \; D \hat{F}\Big( \frac{t_\mathcal{X} - t_\mathcal{R}}{{t_\mathcal{X}}^\prime - t_\mathcal{R}} \times \hat{F^{-1}}(q_\mathcal{R}) \Big) + \ln \; D\hat{F^{-1}} \Big( q_\mathcal{R} \Big) + \ln \frac{t_\mathcal{X} - t_\mathcal{R}}{{t_\mathcal{X}}^\prime - t_\mathcal{R}} .
 \end{align}
 
-The derivatives $DF$ and $DF^{-1}$ can be computed using numerical approximations.
+The derivatives $D\hat{F}$ and $D\hat{F^{-1}}$ are computed using numerical approximations for the first and last pieces, or as the gradient of the linear approximation for internal pieces.
 As its final step, the operator returns $\ln |J|$.
@@
 \begin{align}
-	{t_\mathcal{X}}^\prime \leftarrow t_\mathcal{X} + s\Sigma
+	{t_\mathcal{X}}^\prime \leftarrow t_\mathcal{X} + s\Sigma.
 \end{align}
@@
 \begin{align}
-	{q_\mathcal{C}}^\prime  \leftarrow & F\Big({r_\mathcal{C}}^\prime \Big)  \nonumber \\
-				\leftarrow & F \Big( \frac{t_\mathcal{X} - t_\mathcal{C}}{{t_\mathcal{X}}^\prime - t_\mathcal{C}} \times r_\mathcal{C} \Big) \nonumber \\
-				\leftarrow & F \Big( \frac{t_\mathcal{X} - t_\mathcal{C}}{{t_\mathcal{X}}^\prime - t_\mathcal{C}} \times F^{-1}(q_\mathcal{C}) \Big).
+	{q_\mathcal{C}}^\prime  \leftarrow & \hat{F}\Big({r_\mathcal{C}}^\prime \Big)  \nonumber \\
+				\leftarrow & \hat{F}\Big( \frac{t_\mathcal{X} - t_\mathcal{C}}{{t_\mathcal{X}}^\prime - t_\mathcal{C}} \times r_\mathcal{C} \Big) \nonumber \\
+				\leftarrow & \hat{F}\Big( \frac{t_\mathcal{X} - t_\mathcal{C}}{{t_\mathcal{X}}^\prime - t_\mathcal{C}} \times \hat{F^{-1}}(q_\mathcal{C}) \Big).
 \end{align}
@@
 			=& \ln 1  \nonumber\\
-			&+ \ln \; D F\Big( \frac{t_\mathcal{X} - t_\mathcal{L}}{{t_\mathcal{X}}^\prime - t_\mathcal{L}} \times F^{-1}(q_\mathcal{L}) \Big) + \ln \frac{\partial}{\partial q_\mathcal{L}} \frac{t_\mathcal{X} - t_\mathcal{L}}{{t_\mathcal{X}}^\prime - t_\mathcal{L}} F^{-1} \Big( q_\mathcal{L} \Big) \nonumber\\
-			&+ \ln \; D F\Big( \frac{t_\mathcal{X} - t_\mathcal{R}}{{t_\mathcal{X}}^\prime - t_\mathcal{R}}\times F^{-1}(q_\mathcal{R}) \Big) + \ln \frac{\partial}{\partial q_\mathcal{R}} \frac{t_\mathcal{X} - t_\mathcal{R}}{{t_\mathcal{X}}^\prime - t_\mathcal{R}} F^{-1} \Big( q_\mathcal{R} \Big) \nonumber\\
-			=& \ln \; D F\Big( \frac{t_\mathcal{X} - t_\mathcal{L}}{{t_\mathcal{X}}^\prime - t_\mathcal{L}} \times F^{-1}(q_\mathcal{L}) \Big) + \ln \; D F^{-1} \Big( q_\mathcal{L} \Big) + \ln \frac{t_\mathcal{X} - t_\mathcal{L}}{{t_\mathcal{X}}^\prime - t_\mathcal{L}}\nonumber \\
-			&+ \ln \; D F\Big( \frac{t_\mathcal{X} - t_\mathcal{R}}{{t_\mathcal{X}}^\prime - t_\mathcal{R}}\times F^{-1}(q_\mathcal{R}) \Big) + \ln \; D F^{-1} \Big( q_\mathcal{R} \Big) + \ln  \frac{t_\mathcal{X} - t_\mathcal{R}}{{t_\mathcal{X}}^\prime - t_\mathcal{R}}.
+			&+ \ln \; D \hat{F}\Big( \frac{t_\mathcal{X} - t_\mathcal{L}}{{t_\mathcal{X}}^\prime - t_\mathcal{L}} \times \hat{F^{-1}}(q_\mathcal{L}) \Big) + \ln \frac{\partial}{\partial q_\mathcal{L}} \frac{t_\mathcal{X} - t_\mathcal{L}}{{t_\mathcal{X}}^\prime - t_\mathcal{L}} \hat{F^{-1}} \Big( q_\mathcal{L} \Big) \nonumber\\
+			&+ \ln \; D \hat{F}\Big( \frac{t_\mathcal{X} - t_\mathcal{R}}{{t_\mathcal{X}}^\prime - t_\mathcal{R}}\times \hat{F^{-1}}(q_\mathcal{R}) \Big) + \ln \frac{\partial}{\partial q_\mathcal{R}} \frac{t_\mathcal{X} - t_\mathcal{R}}{{t_\mathcal{X}}^\prime - t_\mathcal{R}} \hat{F^{-1}} \Big( q_\mathcal{R} \Big) \nonumber\\
+			=& \ln \; D \hat{F}\Big( \frac{t_\mathcal{X} - t_\mathcal{L}}{{t_\mathcal{X}}^\prime - t_\mathcal{L}} \times \hat{F^{-1}}(q_\mathcal{L}) \Big) + \ln \; D \hat{F^{-1}} \Big( q_\mathcal{L} \Big) + \ln \frac{t_\mathcal{X} - t_\mathcal{L}}{{t_\mathcal{X}}^\prime - t_\mathcal{L}}\nonumber \\
+			&+ \ln \; D \hat{F}\Big( \frac{t_\mathcal{X} - t_\mathcal{R}}{{t_\mathcal{X}}^\prime - t_\mathcal{R}}\times \hat{F^{-1}}(q_\mathcal{R}) \Big) + \ln \; D \hat{F^{-1}} \Big( q_\mathcal{R} \Big) + \ln  \frac{t_\mathcal{X} - t_\mathcal{R}}{{t_\mathcal{X}}^\prime - t_\mathcal{R}}.
 \end{align}
@@
 Let $\mathcal{X}$ be the root node and let $\mathcal{L}$ and $\mathcal{R}$ be its two children.
-However, unlike \texttt{SimpleDistance}, this operator alters the two genetic distances $d_\mathcal{L} = r_\mathcal{L} (t_\mathcal{X} - t_\mathcal{L}) = F^{-1} (q_\mathcal{L}) (t_\mathcal{X} - t_\mathcal{L})$ and $d_\mathcal{R} = r_\mathcal{R} (t_\mathcal{X} - t_\mathcal{R}) = F^{-1} (q_\mathcal{R}) (t_\mathcal{X} - t_\mathcal{R})$, while conserving their sum $d_\mathcal{L} + d_\mathcal{R}$.
+However, unlike \texttt{SimpleDistance}, this operator alters the two genetic distances $d_\mathcal{L} = r_\mathcal{L} (t_\mathcal{X} - t_\mathcal{L}) = \hat{F^{-1}} (q_\mathcal{L}) (t_\mathcal{X} - t_\mathcal{L})$ and $d_\mathcal{R} = r_\mathcal{R} (t_\mathcal{X} - t_\mathcal{R}) = \hat{F^{-1}} (q_\mathcal{R}) (t_\mathcal{X} - t_\mathcal{R})$, while conserving their sum $d_\mathcal{L} + d_\mathcal{R}$.
 
@@
 \begin{align}
-	{q_\mathcal{L}}^\prime &\leftarrow F\big( \frac{{d_\mathcal{L}}^\prime}{t_\mathcal{X} - t_\mathcal{L}} \big) \nonumber\\
-				 &\leftarrow F\big( \frac{F^{-1} (q_\mathcal{L}) (t_\mathcal{X} - t_\mathcal{L}) + \Sigma}{t_\mathcal{X} - t_\mathcal{L}} \big) \\
-	{q_\mathcal{R}}^\prime &\leftarrow F\big( \frac{{d_\mathcal{R}}^\prime}{t_\mathcal{X} - t_\mathcal{R}} \big) \nonumber \\
-				 &\leftarrow F\big( \frac{F^{-1} (q_\mathcal{R}) (t_\mathcal{X} - t_\mathcal{R}) - \Sigma}{t_\mathcal{X} - t_\mathcal{R}} \big).
+	{q_\mathcal{L}}^\prime &\leftarrow \hat{F}\Big( \frac{{d_\mathcal{L}}^\prime}{t_\mathcal{X} - t_\mathcal{L}} \big) \nonumber\\
+				 &\leftarrow \hat{F}\Big( \frac{\hat{F^{-1}} (q_\mathcal{L}) (t_\mathcal{X} - t_\mathcal{L}) + \Sigma}{t_\mathcal{X} - t_\mathcal{L}} \big) \\
+	{q_\mathcal{R}}^\prime &\leftarrow \hat{F}\Big( \frac{{d_\mathcal{R}}^\prime}{t_\mathcal{X} - t_\mathcal{R}} \big) \nonumber \\
+				 &\leftarrow \hat{F}\Big( \frac{\hat{F^{-1}} (q_\mathcal{R}) (t_\mathcal{X} - t_\mathcal{R}) - \Sigma}{t_\mathcal{X} - t_\mathcal{R}} \big).
 \end{align}
@@
 	 &= \begin{bmatrix} \frac{\partial {q_\mathcal{L}}^\prime}{\partial q_\mathcal{L}} & 0 \\
-						 0 & \frac{\partial {q_\mathcal{R}}^\prime}{\partial q_\mathcal{R}} \end{bmatrix}
+						 0 & \frac{\partial {q_\mathcal{R}}^\prime}{\partial q_\mathcal{R}} \end{bmatrix}.
 \end{align}
@@
 			=& \ln  \frac{\partial {q_\mathcal{L}}^\prime}{\partial q_\mathcal{L}} + \ln \frac{\partial {q_\mathcal{R}}^\prime}{\partial q_\mathcal{R}}\nonumber \\
-			=& \ln \; D F\big( \frac{F^{-1} (q_\mathcal{L}) (t_\mathcal{X} - t_\mathcal{L}) + \Sigma}{t_\mathcal{X} - t_\mathcal{L}} \big) + \ln \frac{\partial {q_\mathcal{L}}^\prime}{\partial q_\mathcal{L}}  \frac{F^{-1} (q_\mathcal{L}) (t_\mathcal{X} - t_\mathcal{L}) + \Sigma}{t_\mathcal{X} - t_\mathcal{L}} \nonumber\\
-			&+ \ln \; D F\big( \frac{F^{-1} (q_\mathcal{R}) (t_\mathcal{X} - t_\mathcal{R}) - \Sigma}{t_\mathcal{X} - t_\mathcal{R}} \big) + \ln \frac{\partial {q_\mathcal{R}}^\prime}{\partial q_\mathcal{R}}  \frac{F^{-1} (q_\mathcal{R}) (t_\mathcal{X} - t_\mathcal{R}) - \Sigma}{t_\mathcal{X} - t_\mathcal{R}} \nonumber\\
-			=& \ln \; D F\big( \frac{F^{-1} (q_\mathcal{L}) (t_\mathcal{X} - t_\mathcal{L}) + \Sigma}{t_\mathcal{X} - t_\mathcal{L}} \big) + \ln \; D F^{-1} (q_\mathcal{L}) \nonumber \\
-			&+ \ln \; D F\big( \frac{F^{-1} (q_\mathcal{R}) (t_\mathcal{X} - t_\mathcal{R}) - \Sigma}{t_\mathcal{X} - t_\mathcal{R}} \big) + \ln \; DF^{-1} (q_\mathcal{R}) .
+			=& \ln \; D \hat{F}\Big( \frac{\hat{F^{-1}} (q_\mathcal{L}) (t_\mathcal{X} - t_\mathcal{L}) + \Sigma}{t_\mathcal{X} - t_\mathcal{L}} \big) + \ln \frac{\partial {q_\mathcal{L}}^\prime}{\partial q_\mathcal{L}}  \frac{\hat{F^{-1}} (q_\mathcal{L}) (t_\mathcal{X} - t_\mathcal{L}) + \Sigma}{t_\mathcal{X} - t_\mathcal{L}} \nonumber\\
+			&+ \ln \; D \hat{F}\Big( \frac{\hat{F^{-1}} (q_\mathcal{R}) (t_\mathcal{X} - t_\mathcal{R}) - \Sigma}{t_\mathcal{X} - t_\mathcal{R}} \big) + \ln \frac{\partial {q_\mathcal{R}}^\prime}{\partial q_\mathcal{R}}  \frac{\hat{F^{-1}} (q_\mathcal{R}) (t_\mathcal{X} - t_\mathcal{R}) - \Sigma}{t_\mathcal{X} - t_\mathcal{R}} \nonumber\\
+			=& \ln \; D \hat{F}\Big( \frac{\hat{F^{-1}} (q_\mathcal{L}) (t_\mathcal{X} - t_\mathcal{L}) + \Sigma}{t_\mathcal{X} - t_\mathcal{L}} \big) + \ln \; D \hat{F^{-1}} (q_\mathcal{L}) \nonumber \\
+			&+ \ln \; D \hat{F}\Big( \frac{\hat{F^{-1}} (q_\mathcal{R}) (t_\mathcal{X} - t_\mathcal{R}) - \Sigma}{t_\mathcal{X} - t_\mathcal{R}} \big) + \ln \; D\hat{F^{-1}} (q_\mathcal{R}) .
 \end{align}
@@
 
+\clearpage
+\section{CisScale operator}
+
+\texttt{CisScale} was originally introduced by Zhang and Drummond 2020 for the \textit{real} parameterisation (therein named ucldstdevScaleOperator).
+Under the \textit{quant} configuration, the \texttt{CisScale} operator works as follows. \\
+
+\textul{\textit{Step 1}}. Propose a new value for the relaxed clock standard deviation $\sigma$
+
+\begin{align}
+	\sigma^\prime \leftarrow \sigma \times e^{s\Sigma}.
+\end{align}
+
+\textul{\textit{Step 2}}. Recalculate all branch substitution rate quantiles $q$ such that their rates $r$ remain constant
+
+\begin{align}
+	\text{let } & r = \hat{F}^{-1}(q|\sigma) \\ 
+	\text{let } & r^\prime = r\\ 
+	& q^\prime \leftarrow \hat{F}( r^\prime|\sigma^\prime) = \hat{F}( \hat{F}^{-1}(q|\sigma)|\sigma^\prime).
+\end{align}
+
+\textul{\textit{Step 3}}. Return the log Hastings-Green ratio of this proposal. 
+If $\Sigma$ was drawn from a symmetric proposal kernel (such as the Bactrian distribution), this is equal to:
+
+\begin{align}
+	|J| &= \log(e^{s\Sigma}) + \log\Big( \frac{\delta }{\delta q} \hat{F}( \hat{F}^{-1}(q|\sigma)|\sigma^\prime) \Big) \\
+	&= s\Sigma + \log D\hat{F}( \hat{F}^{-1}(q|\sigma)|\sigma^\prime) + \log D\hat{F}^{-1}(q|\sigma),
+\end{align}
+
+where derivatives $D\hat{F}$ and $D\hat{F}^{-1}$ can be approximated using either the piecewise linear model or standard numerical libraries.
+
+\clearpage
+\section{Narrow exchange rates}
+
+The \texttt{NarrowExchangeRate} operator is also compatible with rate quantiles.
+This operator behaves the same as presented in the main article however the Hastings-Green ratio requires further augmentation due to changes in dimension throughout the proposal. \\
+
+\textul{\textit{Step 1}}. Apply \texttt{NarrowExchange} to the current tree topology as described in the main article. 
+This will return a Hastings ratio $H$ due to the asymmetry of this proposal.  \\
+
+\textul{\textit{Step 2}}. Compute the relevant branch rates $r_i$ for $r \in \{A,B,C,D \}$ of the current state from their respective quantile parameters.  \\
+
+\begin{align}
+	r_i = \hat{F}^{-1}(q_i).
+\end{align}
+
+\textul{\textit{Step 3}}. Propose new rates and node heights and compute the Hastings-Green ratio of the real-space component of the proposal (e.g. Algorithms 1-2 of the main article).    \\
+
+\begin{align}
+	(r_A^\prime, r_B^\prime, r_C^\prime, r_D^\prime, t_D^\prime, |J_r|) \leftarrow \texttt{PROPOSAL}(r_A, r_B, r_C, r_D, t_D).
+\end{align}
+
+\textul{\textit{Step 4}}. Transform the rates back into quantiles.
+
+\begin{align}
+	q_i^\prime = \hat{F}(r_i^\prime).
+\end{align}
+
+\textul{\textit{Step 5}}. Compute the log Hastings-Green ratio of the interconversion between rates and quantiles.
+
+\begin{align}
+	\log|J_q| = \log \hat{F}(q) + \log \hat{F}^{-1}(r^\prime).
+\end{align}
+
+% double logHR = Math.log(pld.getDerivativeAtQuantile(qOld));
+% logHR +=  Math.log(pld.getDerivativeAtQuantileInverse(rNew, qNew));
+
+\textul{\textit{Step 6}}. Return the total log Hastings-Green ratio of this proposal: $\log H + \log|J_r| + \log|J_q|$.
+
 \bibliography{references}

### 2020-09-01 benchmarking/benchmarkingVM/ESS_round1_catquant.tex
complete draft

@@
-% Created by tikzDevice version 0.12.3.1 on 2020-08-31 17:26:11
+% Created by tikzDevice version 0.12.3.1 on 2020-09-01 15:29:29
 % !TEX encoding = UTF-8 Unicode
@@
 
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (101.40,416.31) --
+	(105.84,416.31);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (103.75,414.85) --
+	(103.75,417.67);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (103.75,413.08) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (164.93,455.43) --
+	(166.37,455.43);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (165.66,452.83) --
+	(165.66,457.72);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (165.66,452.53) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] ( 98.70,455.42) --
+	(100.34,455.42);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] ( 99.54,455.24) --
+	( 99.54,455.60);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 99.54,451.39) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] ( 98.59,417.88) --
+	(102.92,417.88);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (100.88,416.33) --
+	(100.88,419.32);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (100.88,414.98) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] ( 99.42,417.16) --
+	(103.97,417.16);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (101.83,415.76) --
+	(101.83,418.47);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (101.83,413.13) {$l$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (100.91,389.37) --
+	(104.26,389.37);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (102.66,387.79) --
+	(102.66,390.82);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (102.66,386.46) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (172.65,461.52) --
+	(173.04,461.52);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (172.84,461.40) --
+	(172.84,461.65);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.84,458.62) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
 \path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (202.85,487.92) --
@@
 	(203.19,488.31);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (203.19,484.69) {$p$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(214.32,498.68);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (214.32,495.32) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(208.57,502.51);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (208.57,498.42) {$r$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(199.20,483.41);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.20,480.17) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(200.92,485.57);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (200.92,481.20) {$l$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(203.19,485.17);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (203.19,481.86) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(213.72,502.29);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (213.72,499.23) {$\kappa$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(148.19,447.53);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (148.19,443.45) {$p$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(203.92,488.73);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (203.92,485.58) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(200.58,492.16);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (200.58,488.09) {$r$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(142.65,440.75);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (142.65,437.06) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(144.73,443.56);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (144.73,438.72) {$l$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(164.32,454.46);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (164.32,450.71) {$\sigma$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(203.64,491.97);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (203.64,488.99) {$\kappa$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(160.36,461.31);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (160.36,457.51) {$p$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(203.14,487.19);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (203.14,483.93) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(194.73,488.67);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.73,484.56) {$r$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(156.03,458.86);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (156.03,455.47) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(158.71,460.59);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.71,456.09) {$l$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(163.57,458.19);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (163.57,454.83) {$\sigma$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(203.14,491.27);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (203.14,488.28) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (127.56,426.45) --
-	(130.46,426.45);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (129.06,425.65) --
-	(129.06,427.21);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (129.06,423.22) {$p$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (185.11,469.37) --
-	(185.94,469.37);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (185.53,468.22) --
-	(185.53,470.46);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.53,466.47) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (158.31,469.19) --
-	(158.61,469.19);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (158.46,469.06) --
-	(158.46,469.32);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.46,465.16) {$r$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (126.07,427.08) --
-	(128.95,427.08);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (127.56,426.01) --
-	(127.56,428.09);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (127.56,424.17) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (126.96,427.07) --
-	(129.90,427.07);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (128.49,426.25) --
-	(128.49,427.85);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (128.49,423.04) {$l$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (129.24,415.67) --
-	(133.28,415.67);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (131.36,414.96) --
-	(131.36,416.36);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (131.36,412.77) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (186.71,474.31) --
-	(187.04,474.31);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (186.88,474.21) --
-	(186.88,474.40);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (186.88,471.40) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (128.05,426.35) --
+	(129.99,426.35);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (129.05,425.61) --
+	(129.05,427.05);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (129.05,423.12) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (185.02,468.08) --
+	(185.62,468.08);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (185.32,467.17) --
+	(185.32,468.95);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.32,465.18) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (158.55,469.25) --
+	(158.73,469.25);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (158.64,469.16) --
+	(158.64,469.34);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (158.64,465.21) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (126.64,426.80) --
+	(128.54,426.80);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (127.62,425.95) --
+	(127.62,427.61);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (127.62,423.89) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (127.60,426.97) --
+	(129.61,426.97);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (128.63,426.20) --
+	(128.63,427.70);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (128.63,422.93) {$l$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (130.80,414.86) --
+	(133.23,414.86);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (132.05,414.22) --
+	(132.05,415.47);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (132.05,411.95) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (186.58,474.39) --
+	(186.82,474.39);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (186.70,474.31) --
+	(186.70,474.47);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (186.70,471.49) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(203.28,484.52);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (203.28,480.98) {$p$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(209.06,489.83);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.06,486.65) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(218.06,498.06);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (218.06,493.99) {$r$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(195.29,475.84);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.29,472.58) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(201.07,482.74);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (201.07,478.37) {$l$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(193.92,478.25);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.92,474.85) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(210.08,497.12);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.08,494.11) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(167.39,459.90);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (167.39,456.12) {$p$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(216.32,496.67);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (216.32,493.48) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(197.74,498.23);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.74,494.04) {$r$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(165.90,458.56);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (165.90,455.13) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(167.73,460.51);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (167.73,455.90) {$l$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(173.53,463.80);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.53,460.26) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(214.62,501.84);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (214.62,498.76) {$\kappa$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (177.43,461.34) --
-	(178.36,461.34);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (177.90,460.84) --
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (177.43,461.36) --
+	(178.36,461.36);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (177.90,460.89) --
 	(177.90,461.83);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.90,458.11) {$p$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (188.18,473.35) --
-	(189.52,473.35);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (188.86,472.81) --
-	(188.86,473.87);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.86,470.44) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (191.84,476.83) --
-	(191.96,476.83);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (191.90,476.76) --
-	(191.90,476.90);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.90,472.80) {$r$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.90,458.14) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (188.18,473.41) --
+	(189.52,473.41);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (188.86,472.89) --
+	(188.86,473.91);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.86,470.50) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (191.84,476.81) --
+	(191.96,476.81);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (191.90,476.74) --
+	(191.90,476.88);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.90,472.77) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (179.04,458.06) --
-	(179.04,458.96);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.04,455.61) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (176.19,460.22) --
-	(177.09,460.22);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (176.64,459.76) --
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (179.04,458.09) --
+	(179.04,458.95);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.04,455.62) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (176.19,460.25) --
+	(177.09,460.25);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (176.64,459.81) --
 	(176.64,460.68);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.64,456.19) {$l$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (179.97,462.52) --
-	(180.75,462.52);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (180.36,462.09) --
-	(180.36,462.94);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.36,459.62) {$\sigma$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (202.15,490.39) --
-	(202.43,490.39);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (202.29,490.22) --
-	(202.29,490.56);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.29,487.49) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.64,456.22) {$l$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (179.97,462.48) --
+	(180.75,462.48);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (180.36,462.06) --
+	(180.36,462.88);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.36,459.57) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (202.15,490.36) --
+	(202.43,490.36);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (202.29,490.19) --
+	(202.29,490.52);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.29,487.45) {$\kappa$};
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(198.97,476.64);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.97,473.10) {$p$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(187.31,472.48);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.31,469.01) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(203.17,486.03);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (203.17,481.93) {$r$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(193.24,470.29);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.24,467.07) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(198.92,476.42);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.92,472.05) {$l$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(192.27,472.48);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.27,469.21) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(214.66,501.17);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,431.01) rectangle (189.67,426.03);
+\definecolor{fillColor}{RGB}{253,104,0}
+
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,421.05) rectangle (189.67,416.07);
-\definecolor{fillColor}{RGB}{253,104,0}
+\definecolor{fillColor}{RGB}{143,161,0}
 
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,411.09) rectangle (189.67,406.11);
-\definecolor{fillColor}{RGB}{143,161,0}
+\definecolor{fillColor}{RGB}{0,195,0}
 
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,401.13) rectangle (189.67,396.15);
-\definecolor{fillColor}{RGB}{0,195,0}
+\definecolor{fillColor}{RGB}{0,219,171}
 
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,391.17) rectangle (189.67,386.19);
-\definecolor{fillColor}{RGB}{0,219,171}
+\definecolor{fillColor}{RGB}{0,216,255}
 
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,381.21) rectangle (189.67,376.23);
-\definecolor{fillColor}{RGB}{0,216,255}
+\definecolor{fillColor}{RGB}{151,0,255}
 
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,371.25) rectangle (189.67,366.27);
-\definecolor{fillColor}{RGB}{151,0,255}
+\definecolor{fillColor}{RGB}{255,0,255}
 
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,361.29) rectangle (189.67,356.31);
-\definecolor{fillColor}{RGB}{255,0,255}
+\definecolor{fillColor}{RGB}{68,68,68}
 
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.70,351.33) rectangle (189.67,346.35);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (197.14,425.66) {Ran};
 
@@
 
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (390.48,431.45) --
+	(394.92,431.45);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (392.83,430.87) --
+	(392.83,432.02);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (392.83,428.22) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (454.01,442.95) --
+	(455.45,442.95);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (454.74,442.17) --
+	(454.74,443.70);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (454.74,440.05) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (387.78,457.16) --
+	(389.42,457.16);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (388.62,456.95) --
+	(388.62,457.37);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (388.62,453.13) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (387.67,430.23) --
+	(392.00,430.23);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (389.96,429.68) --
+	(389.96,430.76);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (389.96,427.33) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (388.50,430.56) --
+	(393.05,430.56);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (390.91,430.01) --
+	(390.91,431.09);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (390.91,426.53) {$l$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (389.99,442.92) --
+	(393.34,442.92);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (391.74,442.11) --
+	(391.74,443.70);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (391.74,440.02) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (461.73,461.49) --
+	(462.12,461.49);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (461.92,461.30) --
+	(461.92,461.69);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (461.92,458.59) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
 \path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (491.93,489.87) --
@@
 	(492.27,490.16);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (492.27,486.64) {$p$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(503.40,500.24);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (503.40,497.05) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(497.65,501.80);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (497.65,497.71) {$r$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(488.28,486.03);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (488.28,482.88) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(490.00,487.80);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (490.00,483.47) {$l$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(492.27,499.32);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (492.27,496.14) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(502.80,500.66);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (502.80,497.65) {$\kappa$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(437.27,452.29);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (437.27,448.56) {$p$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(493.00,490.18);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (493.00,487.09) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(489.66,492.85);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (489.66,488.76) {$r$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(431.73,445.95);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (431.73,442.52) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(433.81,448.51);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (433.81,443.97) {$l$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(453.40,462.73);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (453.40,459.29) {$\sigma$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(492.72,490.82);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (492.72,487.83) {$\kappa$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(449.44,465.18);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (449.44,461.43) {$p$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(492.22,489.58);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (492.22,486.43) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(483.81,489.55);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.81,485.32) {$r$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(445.11,462.22);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (445.11,458.79) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(447.79,464.08);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (447.79,459.51) {$l$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(452.65,470.82);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (452.65,467.41) {$\sigma$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(492.22,490.60);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (492.22,487.45) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (416.64,427.41) --
-	(419.54,427.41);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (418.14,426.32) --
-	(418.14,428.45);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (418.14,424.19) {$p$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (474.19,462.41) --
-	(475.02,462.41);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (474.61,461.74) --
-	(474.61,463.06);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.61,459.50) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (447.39,467.41) --
-	(447.69,467.41);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (447.54,467.24) --
-	(447.54,467.58);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (447.54,463.38) {$r$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (415.15,426.94) --
-	(418.03,426.94);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (416.64,425.89) --
-	(416.64,427.93);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (416.64,424.03) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (416.04,427.14) --
-	(418.98,427.14);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (417.57,426.01) --
-	(417.57,428.20);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (417.57,423.11) {$l$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (418.32,441.14) --
-	(422.36,441.14);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (420.44,439.81) --
-	(420.44,442.38);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (420.44,438.23) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (475.79,473.14) --
-	(476.12,473.14);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (475.96,472.98) --
-	(475.96,473.30);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (475.96,470.24) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (417.13,427.87) --
+	(419.07,427.87);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (418.13,426.98) --
+	(418.13,428.71);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (418.13,424.64) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (474.10,462.71) --
+	(474.70,462.71);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (474.40,462.27) --
+	(474.40,463.13);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.40,459.80) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (447.63,467.63) --
+	(447.81,467.63);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (447.72,467.45) --
+	(447.72,467.81);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (447.72,463.60) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (415.72,427.36) --
+	(417.62,427.36);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (416.70,426.45) --
+	(416.70,428.22);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (416.70,424.45) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (416.68,427.67) --
+	(418.69,427.67);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (417.71,426.79) --
+	(417.71,428.52);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (417.71,423.64) {$l$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (419.88,440.73) --
+	(422.31,440.73);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (421.13,439.76) --
+	(421.13,441.65);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (421.13,437.83) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (475.66,473.25) --
+	(475.90,473.25);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (475.78,473.11) --
+	(475.78,473.38);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (475.78,470.34) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(492.36,492.23);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (492.36,488.68) {$p$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(498.14,495.24);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (498.14,492.04) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(507.14,505.21);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (507.14,501.15) {$r$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(484.37,485.50);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (484.37,482.23) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(490.15,490.85);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (490.15,486.50) {$l$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(483.00,483.93);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.00,480.62) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(499.16,495.49);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (499.16,492.50) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(456.47,459.79);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (456.47,455.85) {$p$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(505.40,496.03);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (505.40,492.85) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(486.82,496.19);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (486.82,492.05) {$r$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(454.98,458.21);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (454.98,454.64) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(456.81,460.21);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (456.81,455.50) {$l$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(462.61,475.33);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (462.61,471.74) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(503.70,498.73);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (503.70,495.61) {$\kappa$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (466.51,466.02) --
-	(467.44,466.02);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (466.98,465.37) --
-	(466.98,466.64);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (466.98,462.79) {$p$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (477.26,476.12) --
-	(478.60,476.12);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (477.94,475.44) --
-	(477.94,476.77);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (477.94,473.22) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (480.92,480.75) --
-	(481.04,480.75);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (480.98,480.67) --
-	(480.98,480.84);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (480.98,476.72) {$r$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (467.82,466.41) --
-	(468.42,466.41);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (468.12,466.01) --
-	(468.12,466.81);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.12,463.51) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (465.27,464.95) --
-	(466.17,464.95);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (465.72,464.33) --
-	(465.72,465.56);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (465.72,460.92) {$l$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (469.05,472.46) --
-	(469.83,472.46);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (469.44,471.96) --
-	(469.44,472.95);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (469.44,469.56) {$\sigma$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (491.23,489.31) --
-	(491.51,489.31);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (491.37,489.19) --
-	(491.37,489.43);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (491.37,486.41) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (466.51,466.23) --
+	(467.44,466.23);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (466.98,465.71) --
+	(466.98,466.73);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (466.98,463.00) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (477.26,476.59) --
+	(478.60,476.59);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (477.94,476.02) --
+	(477.94,477.15);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (477.94,473.69) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (480.92,480.72) --
+	(481.04,480.72);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (480.98,480.65) --
+	(480.98,480.79);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (480.98,476.69) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (467.82,466.23) --
+	(468.42,466.23);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (468.12,465.88) --
+	(468.12,466.57);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.12,463.32) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (465.27,465.11) --
+	(466.17,465.11);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (465.72,464.61) --
+	(465.72,465.60);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (465.72,461.08) {$l$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (469.05,472.32) --
+	(469.83,472.32);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (469.44,471.83) --
+	(469.44,472.80);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (469.44,469.42) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (491.23,489.32) --
+	(491.51,489.32);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (491.37,489.22) --
+	(491.37,489.42);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (491.37,486.42) {$\kappa$};
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(488.05,486.50);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (488.05,483.05) {$p$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(476.39,473.70);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (476.39,470.25) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(492.25,490.98);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (492.25,486.89) {$r$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(482.32,481.00);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (482.32,477.86) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(488.00,486.26);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (488.00,481.99) {$l$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(481.35,482.20);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (481.35,478.91) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(503.74,499.97);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (125.77,142.37) --
+	(128.59,142.37);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (127.23,141.79) --
+	(127.23,142.94);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (127.23,139.14) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (163.75,153.87) --
+	(168.64,153.87);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (166.35,153.09) --
+	(166.35,154.62);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (166.35,150.97) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (166.16,168.08) --
+	(166.52,168.08);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (166.34,167.87) --
+	(166.34,168.29);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (166.34,164.05) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (127.25,141.15) --
+	(130.24,141.15);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (128.80,140.60) --
+	(128.80,141.68);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (128.80,138.25) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (126.68,141.48) --
+	(129.39,141.48);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (128.08,140.93) --
+	(128.08,142.01);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (128.08,137.45) {$l$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] ( 98.71,153.84) --
+	(101.74,153.84);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (100.29,153.03) --
+	(100.29,154.62);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (100.29,150.94) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (172.32,172.41) --
+	(172.57,172.41);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (172.44,172.22) --
+	(172.44,172.61);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.44,169.51) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
 \path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (198.44,200.79) --
@@
 	(198.84,201.08);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.84,197.56) {$p$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(209.14,211.16);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.14,207.97) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(213.38,212.72);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (213.38,208.63) {$r$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(194.00,196.95);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.00,193.80) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(196.16,198.72);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.16,194.39) {$l$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(195.68,210.24);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.68,207.06) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(213.06,211.58);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (213.06,208.57) {$\kappa$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(157.60,163.21);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (157.60,159.48) {$p$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(199.40,201.10);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.40,198.01) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(203.04,203.77);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (203.04,199.68) {$r$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(150.88,156.87);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (150.88,153.44) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(153.67,159.43);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (153.67,154.89) {$l$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(164.53,173.65);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (164.53,170.21) {$\sigma$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(202.81,201.74);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.81,198.75) {$\kappa$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(171.65,176.10);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.65,172.35) {$p$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(197.76,200.50);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.76,197.35) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(199.52,200.47);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.52,196.24) {$r$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(169.29,173.14);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.29,169.71) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(171.04,175.00);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.04,170.43) {$l$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(168.65,181.74);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (168.65,178.33) {$\sigma$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(202.11,201.52);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.11,198.37) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (136.57,138.33) --
-	(138.13,138.33);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (137.37,137.24) --
-	(137.37,139.37);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (137.37,135.11) {$p$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (179.14,173.33) --
-	(181.38,173.33);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (180.29,172.66) --
-	(180.29,173.98);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.29,170.42) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (179.98,178.33) --
-	(180.24,178.33);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (180.11,178.16) --
-	(180.11,178.50);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.11,174.30) {$r$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (136.93,137.86) --
-	(139.01,137.86);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (138.00,136.81) --
-	(138.00,138.85);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (138.00,134.95) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (137.17,138.06) --
-	(138.77,138.06);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (137.99,136.93) --
-	(137.99,139.12);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (137.99,134.03) {$l$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (125.88,152.06) --
-	(127.28,152.06);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (126.59,150.73) --
-	(126.59,153.30);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (126.59,149.15) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (185.13,184.06) --
-	(185.32,184.06);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (185.23,183.90) --
-	(185.23,184.22);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.23,181.16) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (136.53,138.79) --
+	(137.97,138.79);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (137.27,137.90) --
+	(137.27,139.63);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (137.27,135.56) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (178.09,173.63) --
+	(179.87,173.63);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (179.00,173.19) --
+	(179.00,174.05);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.00,170.72) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (180.08,178.55) --
+	(180.26,178.55);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (180.17,178.37) --
+	(180.17,178.73);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.17,174.52) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (136.87,138.28) --
+	(138.53,138.28);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (137.72,137.37) --
+	(137.72,139.14);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (137.72,135.37) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (137.12,138.59) --
+	(138.62,138.59);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (137.89,137.71) --
+	(137.89,139.44);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (137.89,134.56) {$l$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (125.14,151.65) --
+	(126.39,151.65);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (125.78,150.68) --
+	(125.78,152.57);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (125.78,148.75) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (185.23,184.17) --
+	(185.39,184.17);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (185.31,184.03) --
+	(185.31,184.30);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.31,181.26) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(195.12,203.15);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.12,199.60) {$p$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(200.48,206.16);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (200.48,202.96) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(208.94,216.13);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (208.94,212.07) {$r$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(186.40,196.42);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (186.40,193.15) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(193.32,201.77);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.32,197.42) {$l$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(188.67,194.85);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.67,191.54) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(207.94,206.41);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.94,203.42) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(170.27,170.71);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (170.27,166.77) {$p$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(207.30,206.95);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.30,203.77) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(209.00,207.11);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.00,202.97) {$r$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(168.95,169.13);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (168.95,165.56) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(170.85,171.13);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (170.85,166.42) {$l$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(174.09,186.25);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.09,182.66) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(212.58,209.65);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.58,206.53) {$\kappa$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (171.76,176.94) --
-	(172.75,176.94);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (172.26,176.29) --
-	(172.26,177.56);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.26,173.71) {$p$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (183.73,187.04) --
-	(184.79,187.04);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (184.27,186.36) --
-	(184.27,187.69);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.27,184.14) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (187.68,191.67) --
-	(187.82,191.67);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (187.75,191.59) --
-	(187.75,191.76);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.75,187.64) {$r$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (168.98,177.33) --
-	(169.88,177.33);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (169.44,176.93) --
-	(169.44,177.73);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.44,174.43) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (170.68,175.87) --
-	(171.60,175.87);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (171.14,175.25) --
-	(171.14,176.48);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.14,171.84) {$l$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (173.01,183.38) --
-	(173.86,183.38);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (173.44,182.88) --
-	(173.44,183.87);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.44,180.48) {$\sigma$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (201.14,200.23) --
-	(201.48,200.23);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (201.31,200.11) --
-	(201.31,200.35);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (201.31,197.33) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (171.81,177.15) --
+	(172.75,177.15);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (172.28,176.63) --
+	(172.28,177.65);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.28,173.92) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (183.81,187.51) --
+	(184.83,187.51);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (184.33,186.94) --
+	(184.33,188.07);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.33,184.61) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (187.66,191.64) --
+	(187.80,191.64);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (187.73,191.57) --
+	(187.73,191.71);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.73,187.61) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (169.01,177.15) --
+	(169.87,177.15);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (169.44,176.80) --
+	(169.44,177.49);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.44,174.24) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (170.73,176.03) --
+	(171.60,176.03);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (171.17,175.53) --
+	(171.17,176.52);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.17,172.00) {$l$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (172.98,183.24) --
+	(173.80,183.24);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (173.40,182.75) --
+	(173.40,183.72);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.40,180.34) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (201.11,200.24) --
+	(201.44,200.24);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (201.28,200.14) --
+	(201.28,200.34);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (201.28,197.34) {$\kappa$};
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(187.24,197.42);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.24,193.97) {$p$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(182.84,184.62);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.84,181.17) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(196.89,201.90);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.89,197.81) {$r$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(180.89,191.92);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.89,188.78) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(187.00,197.18);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.00,192.91) {$l$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(183.04,193.12);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.04,189.83) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(211.97,210.89);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (379.31, 91.70) --
+	(383.29, 91.70);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (381.40, 88.87) --
+	(381.40, 94.17);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (381.40, 88.48) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (454.84,166.96) --
+	(455.88,166.96);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (455.37,166.48) --
+	(455.37,167.44);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (455.37,164.06) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (384.74, 97.03) --
+	(385.93, 97.03);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (385.35, 96.22) --
+	(385.35, 97.81);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (385.35, 93.00) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (376.50, 88.33) --
+	(380.54, 88.33);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (378.63, 85.62) --
+	(378.63, 90.70);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (378.63, 85.42) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (377.31, 89.39) --
+	(381.39, 89.39);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (379.46, 86.69) --
+	(379.46, 91.75);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (379.46, 85.35) {$l$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (380.60, 96.67) --
+	(384.50, 96.67);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (382.65, 93.94) --
+	(382.65, 99.06);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (382.65, 93.76) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (463.47,174.59) --
+	(463.67,174.59);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (463.57,174.48) --
+	(463.57,174.70);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (463.57,171.69) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
 \path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (492.65,206.23) --
@@
 	(492.96,206.54);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (492.96,203.00) {$p$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(505.75,217.11);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (505.75,213.82) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(499.16,211.77);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (499.16,207.66) {$r$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(488.01,202.68);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (488.01,199.41) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(490.12,204.38);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (490.12,200.00) {$l$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(493.92,206.55);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (493.92,203.25) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(506.71,217.23);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (506.71,214.15) {$\kappa$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(467.78,175.72);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (467.78,171.60) {$p$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(495.94,207.15);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (495.94,203.96) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(491.57,204.66);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (491.57,200.54) {$r$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(460.90,167.29);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (460.90,163.35) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(462.84,169.47);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (462.84,164.41) {$l$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(461.64,171.88);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (461.64,168.21) {$\sigma$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(496.77,206.93);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (496.77,203.95) {$\kappa$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(451.73,162.96);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (451.73,158.90) {$p$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(493.90,205.45);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (493.90,202.25) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(484.33,198.03);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (484.33,193.86) {$r$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(447.70,157.86);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (447.70,154.20) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(449.94,160.99);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (449.94,156.14) {$l$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(453.28,167.15);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (453.28,163.47) {$\sigma$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(495.73,206.27);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (495.73,203.20) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (413.75,122.86) --
-	(416.46,122.86);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (415.15,121.64) --
-	(415.15,124.00);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (415.15,119.63) {$p$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (473.31,185.63) --
-	(474.12,185.63);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (473.72,185.34) --
-	(473.72,185.91);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (473.72,182.72) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (447.11,162.51) --
-	(447.38,162.51);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (447.24,162.37) --
-	(447.24,162.64);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (447.24,158.47) {$r$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (412.33,121.32) --
-	(415.08,121.32);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (413.76,120.02) --
-	(413.76,122.54);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (413.76,118.42) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (413.42,122.40) --
-	(416.04,122.40);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (414.77,121.22) --
-	(414.77,123.50);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (414.77,118.36) {$l$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (414.94,122.32) --
-	(417.75,122.32);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (416.40,120.43) --
-	(416.40,124.03);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (416.40,119.41) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (478.09,188.67) --
-	(478.40,188.67);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (478.25,188.53) --
-	(478.25,188.81);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (478.25,185.77) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (413.46,123.40) --
+	(415.50,123.40);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (414.51,122.47) --
+	(414.51,124.29);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (414.51,120.17) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (473.37,185.58) --
+	(473.90,185.58);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (473.64,185.33) --
+	(473.64,185.82);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (473.64,182.67) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (447.26,162.55) --
+	(447.45,162.55);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (447.36,162.43) --
+	(447.36,162.66);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (447.36,158.51) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (412.44,122.17) --
+	(414.56,122.17);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (413.53,121.23) --
+	(413.53,123.08);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (413.53,119.27) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (413.41,122.96) --
+	(415.48,122.96);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (414.47,122.04) --
+	(414.47,123.84);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (414.47,118.93) {$l$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (415.71,123.38) --
+	(418.33,123.38);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (417.07,122.11) --
+	(417.07,124.58);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (417.07,120.48) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (478.23,188.65) --
+	(478.44,188.65);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (478.34,188.54) --
+	(478.34,188.76);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (478.34,185.75) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(493.23,208.32);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (493.23,204.76) {$p$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(500.03,211.73);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (500.03,208.54) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(509.18,221.36);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (509.18,217.29) {$r$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(484.82,201.00);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (484.82,197.76) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(491.28,206.35);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (491.28,201.96) {$l$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(485.20,197.86);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (485.20,194.55) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(502.63,211.80);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (502.63,208.78) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(455.39,161.97);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (455.39,157.57) {$p$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(503.95,217.03);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (503.95,213.83) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(483.86,197.89);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.86,193.65) {$r$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(453.83,160.71);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (453.83,156.64) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(455.83,162.43);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (455.83,157.23) {$l$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(466.92,168.47);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (466.92,164.27) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(505.36,215.57);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (505.36,212.39) {$\kappa$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(465.86,179.82);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (465.86,176.10) {$p$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(480.47,192.71);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (480.47,189.21) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(481.02,194.93);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (481.02,190.81) {$r$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(463.72,179.57);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (463.72,176.19) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(464.67,178.69);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (464.67,174.13) {$l$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(470.05,182.56);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (470.05,179.23) {$\sigma$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(494.37,204.73);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (494.37,201.64) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(483.14,200.20);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.14,196.67) {$p$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(475.74,188.05);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (475.74,184.69) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(490.08,204.27);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (490.08,200.16) {$r$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(476.94,194.61);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (476.94,191.42) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(483.03,200.15);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.03,195.82) {$l$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(479.44,193.05);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (479.44,189.78) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(504.03,214.36);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 

### 2020-09-01 benchmarking/benchmarkingVM/ESS_round1_real.tex
complete draft

@@
-% Created by tikzDevice version 0.12.3.1 on 2020-08-31 17:25:39
+% Created by tikzDevice version 0.12.3.1 on 2020-09-01 15:28:56
 % !TEX encoding = UTF-8 Unicode
@@
 
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (105.63,410.80) --
+	(108.95,410.80);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (107.36,409.18) --
+	(107.36,412.29);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (107.36,407.57) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (169.53,454.52) --
+	(171.08,454.52);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (170.32,454.03) --
+	(170.32,455.00);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (170.32,451.62) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (102.05,458.26) --
+	(102.89,458.26);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (102.47,457.97) --
+	(102.47,458.55);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (102.47,454.23) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] ( 97.39,425.16) --
+	(100.73,425.16);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] ( 99.13,423.93) --
+	( 99.13,426.30);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 99.13,422.25) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] ( 97.47,424.85) --
+	(100.84,424.85);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] ( 99.23,423.54) --
+	( 99.23,426.08);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 99.23,420.82) {$l$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (112.80,389.93) --
+	(116.35,389.93);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (114.66,388.52) --
+	(114.66,391.23);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (114.66,387.02) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (177.35,463.25) --
+	(177.59,463.25);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (177.47,463.13) --
+	(177.47,463.38);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.47,460.35) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
 \path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (198.28,494.66) --
@@
 	(201.56,494.93);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (201.56,491.43) {$p$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(219.67,499.70);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (219.67,496.48) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(217.66,501.62);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (217.66,497.55) {$r$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(201.44,483.15);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (201.44,479.96) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(215.04,486.02);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (215.04,481.76) {$l$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(211.53,485.96);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.53,482.75) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(223.44,504.85);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (223.44,501.81) {$\kappa$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(182.54,458.92);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.54,454.61) {$p$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(207.93,490.52);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.93,487.31) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(205.75,491.80);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.75,487.70) {$r$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(152.58,441.01);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (152.58,437.23) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(184.32,442.81);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.32,437.90) {$l$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(188.51,452.61);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.51,448.64) {$\sigma$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(212.32,495.49);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.32,492.50) {$\kappa$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(176.82,462.99);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.82,459.26) {$p$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(204.34,489.19);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (204.34,485.97) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(195.02,488.29);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.02,484.20) {$r$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(163.74,460.81);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (163.74,457.47) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(179.04,461.68);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.04,457.20) {$l$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(187.85,454.92);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.85,451.57) {$\sigma$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(211.92,494.55);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.92,491.55) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (139.82,437.49) --
-	(142.69,437.49);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (141.31,435.71) --
-	(141.31,439.11);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (141.31,434.26) {$p$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (188.50,469.39) --
-	(191.19,469.39);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (189.89,469.21) --
-	(189.89,469.56);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (189.89,466.49) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (156.82,470.66) --
-	(158.12,470.66);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (157.48,470.52) --
-	(157.48,470.79);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (157.48,466.62) {$r$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (128.56,432.56) --
-	(131.74,432.56);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (130.21,431.55) --
-	(130.21,433.52);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (130.21,429.66) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (128.30,432.21) --
-	(131.22,432.21);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (129.82,431.35) --
-	(129.82,433.04);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (129.82,428.18) {$l$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (140.69,415.66) --
-	(144.04,415.66);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (142.44,413.79) --
-	(142.44,417.37);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (142.44,412.76) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (194.07,476.87) --
-	(194.73,476.87);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (194.40,476.71) --
-	(194.40,477.02);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.40,473.96) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (139.86,437.29) --
+	(142.37,437.29);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (141.16,436.19) --
+	(141.16,438.33);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (141.16,434.06) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (189.30,469.40) --
+	(191.60,469.40);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (190.48,469.23) --
+	(190.48,469.57);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.48,466.49) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (156.91,470.49) --
+	(158.03,470.49);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (157.48,470.37) --
+	(157.48,470.60);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (157.48,466.45) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (128.83,432.21) --
+	(131.63,432.21);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (130.28,431.49) --
+	(130.28,432.91);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (130.28,429.31) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (128.53,431.93) --
+	(131.13,431.93);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (129.87,431.26) --
+	(129.87,432.57);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (129.87,427.89) {$l$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (141.20,416.02) --
+	(144.18,416.02);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (142.75,414.84) --
+	(142.75,417.12);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (142.75,413.11) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (194.17,476.91) --
+	(194.73,476.91);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (194.46,476.81) --
+	(194.46,477.01);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.46,474.01) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(209.46,473.58);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.46,469.64) {$p$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(201.74,486.85);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (201.74,483.54) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(222.30,493.68);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (222.30,489.59) {$r$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(207.97,472.32);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.97,469.12) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(223.64,479.93);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (223.64,475.59) {$l$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(218.98,473.03);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (218.98,469.68) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(220.59,499.92);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.59,496.87) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(212.89,484.58);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.89,480.86) {$p$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(216.56,490.80);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (216.56,487.63) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(203.71,492.04);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (203.71,487.96) {$r$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(184.49,458.73);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.49,455.25) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(216.71,459.32);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (216.71,454.65) {$l$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(214.54,461.96);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (214.54,458.54) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(222.33,498.83);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (222.33,495.67) {$\kappa$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(169.72,466.40);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.72,462.82) {$p$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(174.25,472.36);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.25,468.70) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(193.22,473.54);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.22,469.44) {$r$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(168.75,455.77);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (168.75,452.21) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(177.61,457.45);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.61,452.62) {$l$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(188.47,459.55);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.47,456.27) {$\sigma$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(210.61,491.78);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.61,488.74) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(213.29,470.95);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (213.29,467.35) {$p$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(178.68,469.78);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (178.68,466.32) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(218.62,480.08);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (218.62,475.99) {$r$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(196.50,463.66);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.50,460.42) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(227.99,469.95);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (227.99,465.58) {$l$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(220.24,467.89);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (220.24,464.61) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(225.13,499.81);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (394.71,459.09) --
+	(398.03,459.09);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (396.44,458.12) --
+	(396.44,460.01);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (396.44,455.86) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (458.61,446.71) --
+	(460.16,446.71);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (459.40,446.25) --
+	(459.40,447.16);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (459.40,443.81) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (391.13,462.99) --
+	(391.97,462.99);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (391.55,462.79) --
+	(391.55,463.20);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (391.55,458.96) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (386.47,438.93) --
+	(389.81,438.93);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (388.21,438.43) --
+	(388.21,439.41);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (388.21,436.02) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (386.55,439.02) --
+	(389.92,439.02);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (388.31,438.53) --
+	(388.31,439.50);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (388.31,434.99) {$l$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (401.88,458.26) --
+	(405.43,458.26);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (403.74,457.64) --
+	(403.74,458.86);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (403.74,455.36) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (466.43,467.13) --
+	(466.67,467.13);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (466.55,466.97) --
+	(466.55,467.28);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (466.55,464.22) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
 \path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (487.36,505.04) --
@@
 	(490.64,505.29);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (490.64,501.82) {$p$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(508.75,507.82);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (508.75,504.49) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(506.74,511.25);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (506.74,507.16) {$r$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(490.52,494.11);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (490.52,490.89) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(504.12,496.64);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (504.12,492.28) {$l$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(500.61,506.73);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (500.61,503.60) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(512.52,512.71);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (512.52,509.69) {$\kappa$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(471.62,469.72);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (471.62,465.69) {$p$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(497.01,497.77);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (497.01,494.59) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(494.83,500.32);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (494.83,496.21) {$r$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(441.66,454.24);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (441.66,450.44) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(473.40,456.25);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (473.40,451.31) {$l$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(477.59,467.17);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (477.59,463.46) {$\sigma$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(501.40,501.23);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (501.40,498.24) {$\kappa$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(465.90,477.54);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (465.90,473.86) {$p$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(493.42,494.06);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (493.42,490.91) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(484.10,495.07);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (484.10,490.97) {$r$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(452.82,470.46);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (452.82,467.17) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(468.12,471.51);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.12,467.09) {$l$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(476.93,474.51);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (476.93,471.13) {$\sigma$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(501.00,500.90);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (501.00,497.89) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (428.90,470.69) --
-	(431.77,470.69);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (430.39,470.18) --
-	(430.39,471.19);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (430.39,467.47) {$p$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (477.58,468.90) --
-	(480.27,468.90);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (478.97,468.61) --
-	(478.97,469.18);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (478.97,465.99) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (445.90,475.57) --
-	(447.20,475.57);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (446.56,475.45) --
-	(446.56,475.69);
-\definecolor{drawColor}{RGB}{0,195,0}
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (428.94,470.59) --
+	(431.45,470.59);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (430.24,470.12) --
+	(430.24,471.05);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (430.24,467.36) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (478.38,468.78) --
+	(480.68,468.78);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (479.56,468.50) --
+	(479.56,469.06);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (479.56,465.88) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (445.99,475.58) --
+	(447.11,475.58);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (446.56,475.47) --
+	(446.56,475.68);
+\definecolor{drawColor}{RGB}{0,219,171}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (446.56,471.54) {$r$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (417.64,442.67) --
-	(420.82,442.67);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (419.29,442.05) --
-	(419.29,443.26);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (419.29,439.76) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (417.38,442.55) --
-	(420.30,442.55);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (418.90,441.89) --
-	(418.90,443.18);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (418.90,438.51) {$l$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (429.77,458.76) --
-	(433.12,458.76);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (431.52,457.98) --
-	(431.52,459.51);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (431.52,455.86) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (483.15,482.91) --
-	(483.81,482.91);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (483.48,482.83) --
-	(483.48,482.99);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.48,480.01) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (417.91,442.44) --
+	(420.71,442.44);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (419.36,441.85) --
+	(419.36,443.01);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (419.36,439.54) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (417.61,442.33) --
+	(420.21,442.33);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (418.95,441.70) --
+	(418.95,442.93);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (418.95,438.29) {$l$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (430.28,458.40) --
+	(433.26,458.40);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (431.83,457.64) --
+	(431.83,459.13);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (431.83,455.50) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (483.25,482.96) --
+	(483.81,482.96);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (483.54,482.88) --
+	(483.54,483.03);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.54,480.05) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(498.54,488.81);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (498.54,484.39) {$p$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(490.82,504.41);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (490.82,501.17) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(511.38,516.26);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (511.38,512.18) {$r$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(497.05,498.01);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (497.05,494.77) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(512.72,503.19);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (512.72,498.90) {$l$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(508.06,491.55);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (508.06,488.34) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(509.67,507.81);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (509.67,504.80) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(501.97,500.06);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (501.97,496.48) {$p$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(505.64,499.24);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (505.64,496.05) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(492.79,503.74);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (492.79,499.64) {$r$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(473.57,471.72);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (473.57,468.20) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(505.79,472.14);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (505.79,467.50) {$l$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(503.62,484.03);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (503.62,480.67) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(511.41,512.76);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (511.41,509.69) {$\kappa$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(458.80,481.44);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (458.80,477.79) {$p$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(463.33,484.45);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (463.33,480.02) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(482.30,489.11);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (482.30,484.98) {$r$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(457.83,473.89);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (457.83,470.67) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(466.69,473.28);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (466.69,468.93) {$l$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(477.55,481.36);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (477.55,478.08) {$\sigma$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(499.69,501.45);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (499.69,498.43) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(502.37,488.29);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (502.37,484.64) {$p$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(467.76,484.63);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (467.76,481.10) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(507.70,500.97);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (507.70,496.87) {$r$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(485.58,490.38);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (485.58,487.26) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(517.07,496.04);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (517.07,491.75) {$l$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(509.32,490.49);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (509.32,487.09) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(514.21,512.37);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (120.10,170.01) --
+	(123.21,170.01);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (121.72,169.04) --
+	(121.72,170.93);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (121.72,166.78) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (164.95,157.63) --
+	(165.92,157.63);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (165.44,157.17) --
+	(165.44,158.08);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (165.44,154.73) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (168.89,173.91) --
+	(169.47,173.91);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (169.18,173.71) --
+	(169.18,174.12);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.18,169.88) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (134.85,149.85) --
+	(137.22,149.85);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (136.08,149.35) --
+	(136.08,150.33);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (136.08,146.94) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (134.46,149.94) --
+	(137.00,149.94);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (135.77,149.45) --
+	(135.77,150.42);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (135.77,145.91) {$l$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] ( 99.44,169.18) --
+	(102.15,169.18);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (100.85,168.56) --
+	(100.85,169.78);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (100.85,166.28) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (174.05,178.05) --
+	(174.30,178.05);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (174.17,177.89) --
+	(174.17,178.20);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.17,175.14) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
 \path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (205.30,215.96) --
@@
 	(205.58,216.21);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.58,212.74) {$p$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(210.31,218.74);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.31,215.41) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(212.51,222.17);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.51,218.08) {$r$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(193.78,205.03);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.78,201.81) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(196.71,207.56);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.71,203.20) {$l$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(196.57,217.65);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.57,214.52) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(215.64,223.63);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (215.64,220.61) {$\kappa$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(168.76,180.64);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (168.76,176.61) {$p$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(201.14,208.69);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (201.14,205.51) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(202.66,211.24);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.66,207.13) {$r$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(151.06,165.16);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (151.06,161.36) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(152.85,167.17);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (152.85,162.23) {$l$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(162.46,178.09);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (162.46,174.38) {$\sigma$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(206.33,212.15);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (206.33,209.16) {$\kappa$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(173.41,188.46);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.41,184.78) {$p$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(199.79,204.98);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.79,201.83) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(199.16,205.99);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.16,201.89) {$r$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(171.29,181.38);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.29,178.09) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(172.15,182.43);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.15,178.01) {$l$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(165.40,185.43);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (165.40,182.05) {$\sigma$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(205.37,211.82);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.37,208.81) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (146.63,181.61) --
-	(150.03,181.61);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (148.41,181.10) --
-	(148.41,182.11);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (148.41,178.39) {$p$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (180.13,179.82) --
-	(180.48,179.82);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (180.31,179.53) --
-	(180.31,180.10);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.31,176.91) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (181.44,186.49) --
-	(181.71,186.49);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (181.58,186.37) --
-	(181.58,186.61);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.58,182.46) {$r$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (142.47,153.59) --
-	(144.44,153.59);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (143.48,152.97) --
-	(143.48,154.18);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (143.48,150.68) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (142.27,153.47) --
-	(143.96,153.47);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (143.13,152.81) --
-	(143.13,154.10);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (143.13,149.43) {$l$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (124.71,169.68) --
-	(128.29,169.68);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (126.58,168.90) --
-	(126.58,170.43);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (126.58,166.78) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (187.63,193.83) --
-	(187.94,193.83);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (187.79,193.75) --
-	(187.79,193.91);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.79,190.93) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (147.11,181.51) --
+	(149.25,181.51);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (148.21,181.04) --
+	(148.21,181.97);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (148.21,178.28) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (180.15,179.70) --
+	(180.49,179.70);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (180.32,179.42) --
+	(180.32,179.98);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.32,176.80) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (181.29,186.50) --
+	(181.52,186.50);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (181.41,186.39) --
+	(181.41,186.60);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.41,182.46) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (142.41,153.36) --
+	(143.83,153.36);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (143.13,152.77) --
+	(143.13,153.93);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (143.13,150.46) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (142.18,153.25) --
+	(143.49,153.25);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (142.85,152.62) --
+	(142.85,153.85);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (142.85,149.21) {$l$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (125.76,169.32) --
+	(128.04,169.32);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (126.94,168.56) --
+	(126.94,170.05);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (126.94,166.42) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (187.73,193.88) --
+	(187.93,193.88);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (187.83,193.80) --
+	(187.83,193.95);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.83,190.97) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(183.79,199.73);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.79,195.31) {$p$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(197.37,215.33);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.37,212.09) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(204.54,227.18);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (204.54,223.10) {$r$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(182.95,208.93);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.95,205.69) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(190.55,214.11);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.55,209.82) {$l$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(183.51,202.47);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.51,199.26) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(210.69,218.73);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.69,215.72) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(195.01,210.98);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (195.01,207.40) {$p$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(201.45,210.16);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (201.45,206.97) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(202.91,214.66);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.91,210.56) {$r$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(169.08,182.64);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.08,179.12) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(169.61,183.06);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.61,178.42) {$l$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(172.36,194.95);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (172.36,191.59) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(209.49,223.68);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.49,220.61) {$\kappa$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(176.97,192.36);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.97,188.71) {$p$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(182.52,195.37);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.52,190.94) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(184.39,200.03);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.39,195.90) {$r$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(166.03,184.81);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (166.03,181.59) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(167.57,184.20);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (167.57,179.85) {$l$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(170.09,192.28);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (170.09,189.00) {$\sigma$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(202.57,212.37);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.57,209.35) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(181.49,199.21);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.49,195.56) {$p$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(180.14,195.55);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.14,192.02) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(190.95,211.89);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (190.95,207.79) {$r$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(174.24,201.30);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.24,198.18) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(180.53,206.96);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.53,202.67) {$l$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(178.44,201.41);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (178.44,198.01) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(210.58,223.29);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 
+\path[fill=fillColor] (485.73,235.24) circle (  1.87);
+
+\path[fill=fillColor] (485.73, 54.26) --
+	(488.24, 49.90) --
+	(483.21, 49.90) --
+	cycle;
+\definecolor{fillColor}{RGB}{0,0,0}
+
+\path[fill=fillColor] (435.32,150.27) circle (  2.15);
+
+\path[fill=fillColor] (435.32,142.15) --
+	(438.21,137.14) --
+	(432.42,137.14) --
+	cycle;
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,146.98) {\texttt{ConstantDistance}};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
+\definecolor{fillColor}{RGB}{253,104,0}
+
 \path[fill=fillColor] (356.88,165.22) circle (  1.87);
@@
 	cycle;
-\definecolor{drawColor}{RGB}{0,0,0}
 
@@
 \node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
-\definecolor{fillColor}{RGB}{253,104,0}
+\definecolor{fillColor}{RGB}{143,161,0}
 
@@
 \node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
-\definecolor{fillColor}{RGB}{143,161,0}
+\definecolor{fillColor}{RGB}{0,195,0}
 
@@
 \node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
-\definecolor{fillColor}{RGB}{0,195,0}
-
-\path[fill=fillColor] (404.25,216.47) circle (  1.87);
-
-\path[fill=fillColor] (404.25, 59.60) --
-	(406.77, 55.24) --
-	(401.74, 55.24) --
+\definecolor{fillColor}{RGB}{0,219,171}
+
+\path[fill=fillColor] (404.25,216.38) circle (  1.87);
+
+\path[fill=fillColor] (404.25, 59.59) --
+	(406.77, 55.23) --
+	(401.74, 55.23) --
 	cycle;
@@
 \node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
-\definecolor{fillColor}{RGB}{0,219,171}
+\definecolor{fillColor}{RGB}{0,216,255}
 
@@
 \node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
-\definecolor{fillColor}{RGB}{0,216,255}
+\definecolor{fillColor}{RGB}{151,0,255}
 
@@
 \node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
-\definecolor{fillColor}{RGB}{151,0,255}
+\definecolor{fillColor}{RGB}{255,0,255}
 
@@
 \node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.95] at (443.91,135.53) {\texttt{RandomWalk}};
-\definecolor{fillColor}{RGB}{255,0,255}
+\definecolor{fillColor}{RGB}{68,68,68}
 
@@
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (338.88,117.32) --
-	(339.26,117.75) --
-	(339.64,118.18) --
-	(340.02,118.61) --
-	(340.40,119.05) --
-	(340.78,119.48) --
-	(341.16,119.92) --
-	(341.54,120.35) --
-	(341.92,120.79) --
-	(342.30,121.23) --
-	(342.68,121.67) --
-	(343.06,122.11) --
-	(343.44,122.55) --
-	(343.82,123.00) --
-	(344.20,123.44) --
-	(344.58,123.89) --
-	(344.96,124.33) --
-	(345.34,124.78) --
-	(345.71,125.23) --
-	(346.09,125.68) --
-	(346.47,126.13) --
-	(346.85,126.58) --
-	(347.23,127.03) --
-	(347.61,127.48) --
-	(347.99,127.93) --
-	(348.37,128.39) --
-	(348.75,128.84) --
-	(349.13,129.30) --
-	(349.51,129.75) --
-	(349.89,130.21) --
-	(350.27,130.67) --
-	(350.65,131.13) --
-	(351.03,131.59) --
-	(351.41,132.05) --
-	(351.79,132.51) --
-	(352.17,132.97) --
-	(352.55,133.43) --
-	(352.93,133.89) --
-	(353.31,134.35) --
-	(353.69,134.81) --
-	(354.07,135.28) --
-	(354.45,135.74) --
-	(354.83,136.20) --
-	(355.21,136.67) --
-	(355.59,137.13) --
-	(355.97,137.60) --
-	(356.35,138.06) --
-	(356.73,138.53) --
-	(357.11,139.00) --
-	(357.49,139.46) --
-	(357.87,139.93) --
-	(358.25,140.40) --
-	(358.63,140.86) --
-	(359.01,141.33) --
-	(359.38,141.80) --
-	(359.76,142.27) --
-	(360.14,142.73) --
-	(360.52,143.20) --
-	(360.90,143.67) --
-	(361.28,144.14) --
-	(361.66,144.61) --
-	(362.04,145.07) --
-	(362.42,145.54) --
-	(362.80,146.01) --
-	(363.18,146.48) --
-	(363.56,146.94) --
-	(363.94,147.41) --
-	(364.32,147.88) --
-	(364.70,148.35) --
-	(365.08,148.81) --
-	(365.46,149.28) --
-	(365.84,149.75) --
-	(366.22,150.21) --
-	(366.60,150.68) --
-	(366.98,151.14) --
-	(367.36,151.61) --
-	(367.74,152.08) --
-	(368.12,152.54) --
-	(368.50,153.00) --
-	(368.88,153.47) --
-	(369.26,153.93) --
-	(369.64,154.40) --
-	(370.02,154.86) --
-	(370.40,155.32) --
-	(370.78,155.78) --
-	(371.16,156.24) --
-	(371.54,156.70) --
-	(371.92,157.16) --
-	(372.30,157.62) --
-	(372.68,158.08) --
-	(373.05,158.54) --
-	(373.43,159.00) --
-	(373.81,159.45) --
-	(374.19,159.91) --
-	(374.57,160.36) --
-	(374.95,160.82) --
-	(375.33,161.27) --
-	(375.71,161.73) --
-	(376.09,162.18) --
-	(376.47,162.63) --
-	(376.85,163.08) --
-	(377.23,163.53) --
-	(377.61,163.98) --
-	(377.99,164.42) --
-	(378.37,164.87) --
-	(378.75,165.32) --
-	(379.13,165.76) --
-	(379.51,166.21) --
-	(379.89,166.65) --
-	(380.27,167.09) --
-	(380.65,167.53) --
-	(381.03,167.97) --
-	(381.41,168.41) --
-	(381.79,168.85) --
-	(382.17,169.28) --
-	(382.55,169.72) --
-	(382.93,170.15) --
-	(383.31,170.59) --
-	(383.69,171.02) --
-	(384.07,171.45) --
-	(384.45,171.88) --
-	(384.83,172.31) --
-	(385.21,172.74) --
-	(385.59,173.16) --
-	(385.97,173.59) --
-	(386.34,174.01) --
-	(386.72,174.43) --
-	(387.10,174.85) --
-	(387.48,175.27) --
-	(387.86,175.69) --
-	(388.24,176.11) --
-	(388.62,176.52) --
-	(389.00,176.93) --
-	(389.38,177.35) --
-	(389.76,177.76) --
-	(390.14,178.17) --
-	(390.52,178.58) --
-	(390.90,178.98) --
-	(391.28,179.39) --
-	(391.66,179.79) --
-	(392.04,180.19) --
-	(392.42,180.60) --
-	(392.80,180.99) --
-	(393.18,181.39) --
-	(393.56,181.79) --
-	(393.94,182.18) --
-	(394.32,182.58) --
-	(394.70,182.97) --
-	(395.08,183.36) --
-	(395.46,183.75) --
-	(395.84,184.13) --
-	(396.22,184.52) --
-	(396.60,184.90) --
-	(396.98,185.29) --
-	(397.36,185.67) --
-	(397.74,186.04) --
-	(398.12,186.42) --
-	(398.50,186.80) --
-	(398.88,187.17) --
-	(399.26,187.54) --
-	(399.64,187.91) --
-	(400.01,188.28) --
-	(400.39,188.65) --
-	(400.77,189.02) --
-	(401.15,189.38) --
-	(401.53,189.74) --
-	(401.91,190.10) --
-	(402.29,190.46) --
-	(402.67,190.82) --
-	(403.05,191.17) --
-	(403.43,191.53) --
-	(403.81,191.88) --
-	(404.19,192.23) --
-	(404.57,192.58) --
-	(404.95,192.93) --
-	(405.33,193.27) --
-	(405.71,193.61) --
-	(406.09,193.96) --
-	(406.47,194.30) --
-	(406.85,194.63) --
-	(407.23,194.97) --
-	(407.61,195.30) --
-	(407.99,195.64) --
-	(408.37,195.97) --
-	(408.75,196.30) --
-	(409.13,196.62) --
-	(409.51,196.95) --
-	(409.89,197.27) --
-	(410.27,197.60) --
-	(410.65,197.92) --
-	(411.03,198.23) --
-	(411.41,198.55) --
-	(411.79,198.87) --
-	(412.17,199.18) --
-	(412.55,199.49) --
-	(412.93,199.80) --
-	(413.31,200.11) --
-	(413.68,200.41) --
-	(414.06,200.72) --
-	(414.44,201.02) --
-	(414.82,201.32) --
-	(415.20,201.62) --
-	(415.58,201.92) --
-	(415.96,202.21) --
-	(416.34,202.51) --
-	(416.72,202.80) --
-	(417.10,203.09) --
-	(417.48,203.38) --
-	(417.86,203.66) --
-	(418.24,203.95) --
-	(418.62,204.23) --
-	(419.00,204.51) --
-	(419.38,204.79) --
-	(419.76,205.07) --
-	(420.14,205.35) --
-	(420.52,205.62) --
-	(420.90,205.89) --
-	(421.28,206.16) --
-	(421.66,206.43) --
-	(422.04,206.70) --
-	(422.42,206.97) --
-	(422.80,207.23) --
-	(423.18,207.49) --
-	(423.56,207.75) --
-	(423.94,208.01) --
-	(424.32,208.27) --
-	(424.70,208.52) --
-	(425.08,208.78) --
-	(425.46,209.03) --
-	(425.84,209.28) --
-	(426.22,209.53) --
-	(426.60,209.77) --
-	(426.97,210.02) --
-	(427.35,210.26) --
-	(427.73,210.50) --
-	(428.11,210.75) --
-	(428.49,210.98) --
-	(428.87,211.22) --
-	(429.25,211.46) --
-	(429.63,211.69) --
-	(430.01,211.92) --
-	(430.39,212.15) --
-	(430.77,212.38) --
-	(431.15,212.61) --
-	(431.53,212.83) --
-	(431.91,213.06) --
-	(432.29,213.28) --
-	(432.67,213.50) --
-	(433.05,213.72) --
-	(433.43,213.94) --
-	(433.81,214.15) --
-	(434.19,214.37) --
-	(434.57,214.58) --
-	(434.95,214.79) --
-	(435.33,215.00) --
-	(435.71,215.21) --
-	(436.09,215.42) --
-	(436.47,215.62) --
-	(436.85,215.83) --
-	(437.23,216.03) --
-	(437.61,216.23) --
-	(437.99,216.43) --
-	(438.37,216.63) --
-	(438.75,216.82) --
-	(439.13,217.02) --
-	(439.51,217.21) --
-	(439.89,217.40) --
-	(440.27,217.59) --
-	(440.64,217.78) --
-	(441.02,217.97) --
-	(441.40,218.16) --
-	(441.78,218.34) --
-	(442.16,218.52) --
-	(442.54,218.71) --
-	(442.92,218.89) --
-	(443.30,219.06) --
-	(443.68,219.24) --
-	(444.06,219.42) --
-	(444.44,219.59) --
-	(444.82,219.77) --
-	(445.20,219.94) --
-	(445.58,220.11) --
-	(445.96,220.28) --
-	(446.34,220.45) --
-	(446.72,220.61) --
-	(447.10,220.78) --
-	(447.48,220.94) --
-	(447.86,221.11) --
-	(448.24,221.27) --
-	(448.62,221.43) --
-	(449.00,221.59) --
-	(449.38,221.75) --
-	(449.76,221.90) --
-	(450.14,222.06) --
-	(450.52,222.21) --
-	(450.90,222.37) --
-	(451.28,222.52) --
-	(451.66,222.67) --
-	(452.04,222.82) --
-	(452.42,222.96) --
-	(452.80,223.11) --
-	(453.18,223.26) --
-	(453.56,223.40) --
-	(453.93,223.54) --
-	(454.31,223.69) --
-	(454.69,223.83) --
-	(455.07,223.97) --
-	(455.45,224.10) --
-	(455.83,224.24) --
-	(456.21,224.38) --
-	(456.59,224.51) --
-	(456.97,224.65) --
-	(457.35,224.78) --
-	(457.73,224.91) --
-	(458.11,225.04) --
-	(458.49,225.17) --
-	(458.87,225.30) --
-	(459.25,225.43) --
-	(459.63,225.55) --
-	(460.01,225.68) --
-	(460.39,225.80) --
-	(460.77,225.93) --
-	(461.15,226.05) --
-	(461.53,226.17) --
-	(461.91,226.29) --
-	(462.29,226.41) --
-	(462.67,226.53) --
-	(463.05,226.64) --
-	(463.43,226.76) --
-	(463.81,226.87) --
-	(464.19,226.99) --
-	(464.57,227.10) --
-	(464.95,227.21) --
-	(465.33,227.32) --
-	(465.71,227.43) --
-	(466.09,227.54) --
-	(466.47,227.65) --
-	(466.85,227.76) --
-	(467.23,227.87) --
-	(467.60,227.97) --
-	(467.98,228.08) --
-	(468.36,228.18) --
-	(468.74,228.28) --
-	(469.12,228.38) --
-	(469.50,228.49) --
-	(469.88,228.59) --
-	(470.26,228.68) --
-	(470.64,228.78) --
-	(471.02,228.88) --
-	(471.40,228.98) --
-	(471.78,229.07) --
-	(472.16,229.17) --
-	(472.54,229.26) --
-	(472.92,229.36) --
-	(473.30,229.45) --
-	(473.68,229.54) --
-	(474.06,229.63) --
-	(474.44,229.72) --
-	(474.82,229.81) --
-	(475.20,229.90) --
-	(475.58,229.99) --
-	(475.96,230.07) --
-	(476.34,230.16) --
-	(476.72,230.24) --
-	(477.10,230.33) --
-	(477.48,230.41) --
-	(477.86,230.50) --
-	(478.24,230.58) --
-	(478.62,230.66) --
-	(479.00,230.74) --
-	(479.38,230.82) --
-	(479.76,230.90) --
-	(480.14,230.98) --
-	(480.52,231.06) --
-	(480.90,231.13) --
-	(481.27,231.21) --
-	(481.65,231.29) --
-	(482.03,231.36) --
-	(482.41,231.44) --
-	(482.79,231.51) --
-	(483.17,231.58) --
-	(483.55,231.66) --
-	(483.93,231.73) --
-	(484.31,231.80) --
-	(484.69,231.87) --
-	(485.07,231.94) --
-	(485.45,232.01) --
-	(485.83,232.08) --
-	(486.21,232.15) --
-	(486.59,232.21) --
-	(486.97,232.28) --
-	(487.35,232.35) --
-	(487.73,232.41) --
-	(488.11,232.48) --
-	(488.49,232.54) --
-	(488.87,232.61) --
-	(489.25,232.67) --
-	(489.63,232.73) --
-	(490.01,232.79) --
-	(490.39,232.86) --
-	(490.77,232.92) --
-	(491.15,232.98) --
-	(491.53,233.04) --
-	(491.91,233.10) --
-	(492.29,233.16) --
-	(492.67,233.21) --
-	(493.05,233.27) --
-	(493.43,233.33) --
-	(493.81,233.39) --
-	(494.19,233.44) --
-	(494.56,233.50) --
-	(494.94,233.55) --
-	(495.32,233.61) --
-	(495.70,233.66) --
-	(496.08,233.72) --
-	(496.46,233.77) --
-	(496.84,233.82) --
-	(497.22,233.87) --
-	(497.60,233.92) --
-	(497.98,233.98) --
-	(498.36,234.03) --
-	(498.74,234.08) --
-	(499.12,234.13) --
-	(499.50,234.18) --
-	(499.88,234.22) --
-	(500.26,234.27) --
-	(500.64,234.32) --
-	(501.02,234.37) --
-	(501.40,234.42) --
-	(501.78,234.46) --
-	(502.16,234.51) --
-	(502.54,234.55) --
-	(502.92,234.60) --
-	(503.30,234.64) --
-	(503.68,234.69) --
-	(504.06,234.73) --
-	(504.44,234.78) --
-	(504.82,234.82) --
-	(505.20,234.86) --
-	(505.58,234.90) --
-	(505.96,234.95) --
-	(506.34,234.99) --
-	(506.72,235.03) --
-	(507.10,235.07) --
-	(507.48,235.11) --
-	(507.86,235.15) --
-	(508.23,235.19) --
-	(508.61,235.23) --
-	(508.99,235.27) --
-	(509.37,235.31) --
-	(509.75,235.35) --
-	(510.13,235.38) --
-	(510.51,235.42) --
-	(510.89,235.46) --
-	(511.27,235.50) --
-	(511.65,235.53) --
-	(512.03,235.57) --
-	(512.41,235.60) --
-	(512.79,235.64) --
-	(513.17,235.67) --
-	(513.55,235.71) --
-	(513.93,235.74) --
-	(514.31,235.78) --
-	(514.69,235.81) --
-	(515.07,235.84) --
-	(515.45,235.88) --
-	(515.83,235.91) --
-	(516.21,235.94) --
-	(516.59,235.98) --
-	(516.97,236.01) --
-	(517.35,236.04) --
-	(517.73,236.07) --
-	(518.11,236.10) --
-	(518.49,236.13) --
-	(518.87,236.16) --
-	(519.25,236.19) --
-	(519.63,236.22) --
-	(520.01,236.25) --
-	(520.39,236.28) --
-	(520.77,236.31) --
-	(521.15,236.34) --
-	(521.53,236.37) --
-	(521.90,236.40) --
-	(522.28,236.42) --
-	(522.66,236.45) --
-	(523.04,236.48) --
-	(523.42,236.51) --
-	(523.80,236.53) --
-	(524.18,236.56) --
-	(524.56,236.59) --
-	(524.94,236.61) --
-	(525.32,236.64) --
-	(525.70,236.66) --
-	(526.08,236.69) --
-	(526.46,236.71) --
-	(526.84,236.74) --
-	(527.22,236.76) --
-	(527.60,236.79) --
-	(527.98,236.81) --
-	(528.36,236.84);
-
-\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (338.88, 91.23) --
-	(339.26, 91.04) --
-	(339.64, 90.86) --
-	(340.02, 90.67) --
-	(340.40, 90.49) --
-	(340.78, 90.30) --
-	(341.16, 90.12) --
-	(341.54, 89.94) --
-	(341.92, 89.76) --
-	(342.30, 89.58) --
-	(342.68, 89.40) --
-	(343.06, 89.22) --
-	(343.44, 89.04) --
-	(343.82, 88.86) --
-	(344.20, 88.68) --
-	(344.58, 88.50) --
-	(344.96, 88.33) --
-	(345.34, 88.15) --
-	(345.71, 87.97) --
-	(346.09, 87.80) --
-	(346.47, 87.62) --
-	(346.85, 87.45) --
-	(347.23, 87.28) --
-	(347.61, 87.10) --
-	(347.99, 86.93) --
-	(348.37, 86.76) --
-	(348.75, 86.59) --
-	(349.13, 86.42) --
-	(349.51, 86.25) --
-	(349.89, 86.08) --
-	(350.27, 85.91) --
-	(350.65, 85.75) --
-	(351.03, 85.58) --
-	(351.41, 85.41) --
-	(351.79, 85.25) --
-	(352.17, 85.08) --
-	(352.55, 84.92) --
-	(352.93, 84.75) --
-	(353.31, 84.59) --
-	(353.69, 84.43) --
-	(354.07, 84.26) --
-	(354.45, 84.10) --
-	(354.83, 83.94) --
-	(355.21, 83.78) --
-	(355.59, 83.62) --
-	(355.97, 83.46) --
-	(356.35, 83.30) --
-	(356.73, 83.14) --
-	(357.11, 82.99) --
-	(357.49, 82.83) --
-	(357.87, 82.67) --
-	(358.25, 82.52) --
-	(358.63, 82.36) --
-	(359.01, 82.21) --
-	(359.38, 82.05) --
-	(359.76, 81.90) --
-	(360.14, 81.74) --
-	(360.52, 81.59) --
-	(360.90, 81.44) --
-	(361.28, 81.29) --
-	(361.66, 81.14) --
-	(362.04, 80.99) --
-	(362.42, 80.84) --
-	(362.80, 80.69) --
-	(363.18, 80.54) --
-	(363.56, 80.39) --
-	(363.94, 80.25) --
-	(364.32, 80.10) --
-	(364.70, 79.95) --
-	(365.08, 79.81) --
-	(365.46, 79.66) --
-	(365.84, 79.52) --
-	(366.22, 79.38) --
-	(366.60, 79.23) --
-	(366.98, 79.09) --
-	(367.36, 78.95) --
-	(367.74, 78.81) --
-	(368.12, 78.67) --
-	(368.50, 78.52) --
-	(368.88, 78.38) --
-	(369.26, 78.25) --
-	(369.64, 78.11) --
-	(370.02, 77.97) --
-	(370.40, 77.83) --
-	(370.78, 77.69) --
-	(371.16, 77.56) --
-	(371.54, 77.42) --
-	(371.92, 77.29) --
-	(372.30, 77.15) --
-	(372.68, 77.02) --
-	(373.05, 76.88) --
-	(373.43, 76.75) --
-	(373.81, 76.62) --
-	(374.19, 76.49) --
-	(374.57, 76.35) --
-	(374.95, 76.22) --
-	(375.33, 76.09) --
-	(375.71, 75.96) --
-	(376.09, 75.83) --
-	(376.47, 75.70) --
-	(376.85, 75.58) --
-	(377.23, 75.45) --
-	(377.61, 75.32) --
-	(377.99, 75.19) --
-	(378.37, 75.07) --
-	(378.75, 74.94) --
-	(379.13, 74.82) --
-	(379.51, 74.69) --
-	(379.89, 74.57) --
-	(380.27, 74.45) --
-	(380.65, 74.32) --
-	(381.03, 74.20) --
-	(381.41, 74.08) --
-	(381.79, 73.96) --
-	(382.17, 73.84) --
-	(382.55, 73.71) --
-	(382.93, 73.60) --
-	(383.31, 73.48) --
-	(383.69, 73.36) --
-	(384.07, 73.24) --
-	(384.45, 73.12) --
-	(384.83, 73.00) --
-	(385.21, 72.89) --
-	(385.59, 72.77) --
-	(385.97, 72.65) --
-	(386.34, 72.54) --
-	(386.72, 72.42) --
-	(387.10, 72.31) --
-	(387.48, 72.20) --
-	(387.86, 72.08) --
-	(388.24, 71.97) --
-	(388.62, 71.86) --
-	(389.00, 71.75) --
-	(389.38, 71.63) --
-	(389.76, 71.52) --
-	(390.14, 71.41) --
-	(390.52, 71.30) --
-	(390.90, 71.19) --
-	(391.28, 71.09) --
-	(391.66, 70.98) --
-	(392.04, 70.87) --
-	(392.42, 70.76) --
-	(392.80, 70.65) --
-	(393.18, 70.55) --
-	(393.56, 70.44) --
-	(393.94, 70.34) --
-	(394.32, 70.23) --
-	(394.70, 70.13) --
-	(395.08, 70.02) --
-	(395.46, 69.92) --
-	(395.84, 69.82) --
-	(396.22, 69.71) --
-	(396.60, 69.61) --
-	(396.98, 69.51) --
-	(397.36, 69.41) --
-	(397.74, 69.31) --
-	(398.12, 69.21) --
-	(398.50, 69.11) --
-	(398.88, 69.01) --
-	(399.26, 68.91) --
-	(399.64, 68.81) --
-	(400.01, 68.71) --
-	(400.39, 68.61) --
-	(400.77, 68.52) --
-	(401.15, 68.42) --
-	(401.53, 68.32) --
-	(401.91, 68.23) --
-	(402.29, 68.13) --
-	(402.67, 68.04) --
-	(403.05, 67.94) --
-	(403.43, 67.85) --
-	(403.81, 67.76) --
-	(404.19, 67.66) --
-	(404.57, 67.57) --
-	(404.95, 67.48) --
-	(405.33, 67.39) --
-	(405.71, 67.29) --
-	(406.09, 67.20) --
-	(406.47, 67.11) --
-	(406.85, 67.02) --
-	(407.23, 66.93) --
-	(407.61, 66.84) --
-	(407.99, 66.75) --
-	(408.37, 66.66) --
-	(408.75, 66.58) --
-	(409.13, 66.49) --
-	(409.51, 66.40) --
-	(409.89, 66.31) --
-	(410.27, 66.23) --
-	(410.65, 66.14) --
-	(411.03, 66.06) --
-	(411.41, 65.97) --
-	(411.79, 65.89) --
-	(412.17, 65.80) --
-	(412.55, 65.72) --
-	(412.93, 65.63) --
-	(413.31, 65.55) --
-	(413.68, 65.47) --
-	(414.06, 65.39) --
-	(414.44, 65.30) --
-	(414.82, 65.22) --
-	(415.20, 65.14) --
-	(415.58, 65.06) --
-	(415.96, 64.98) --
-	(416.34, 64.90) --
-	(416.72, 64.82) --
-	(417.10, 64.74) --
-	(417.48, 64.66) --
-	(417.86, 64.58) --
-	(418.24, 64.50) --
-	(418.62, 64.43) --
-	(419.00, 64.35) --
-	(419.38, 64.27) --
-	(419.76, 64.20) --
-	(420.14, 64.12) --
-	(420.52, 64.04) --
-	(420.90, 63.97) --
-	(421.28, 63.89) --
-	(421.66, 63.82) --
-	(422.04, 63.74) --
-	(422.42, 63.67) --
-	(422.80, 63.60) --
-	(423.18, 63.52) --
-	(423.56, 63.45) --
-	(423.94, 63.38) --
-	(424.32, 63.30) --
-	(424.70, 63.23) --
-	(425.08, 63.16) --
-	(425.46, 63.09) --
-	(425.84, 63.02) --
-	(426.22, 62.95) --
-	(426.60, 62.88) --
-	(426.97, 62.81) --
-	(427.35, 62.74) --
-	(427.73, 62.67) --
-	(428.11, 62.60) --
-	(428.49, 62.53) --
-	(428.87, 62.46) --
-	(429.25, 62.40) --
-	(429.63, 62.33) --
-	(430.01, 62.26) --
-	(430.39, 62.20) --
-	(430.77, 62.13) --
-	(431.15, 62.06) --
-	(431.53, 62.00) --
-	(431.91, 61.93) --
-	(432.29, 61.87) --
-	(432.67, 61.80) --
-	(433.05, 61.74) --
-	(433.43, 61.67) --
-	(433.81, 61.61) --
-	(434.19, 61.55) --
-	(434.57, 61.48) --
-	(434.95, 61.42) --
-	(435.33, 61.36) --
-	(435.71, 61.29) --
-	(436.09, 61.23) --
-	(436.47, 61.17) --
-	(436.85, 61.11) --
-	(437.23, 61.05) --
-	(437.61, 60.99) --
-	(437.99, 60.93) --
-	(438.37, 60.87) --
-	(438.75, 60.81) --
-	(439.13, 60.75) --
-	(439.51, 60.69) --
-	(439.89, 60.63) --
-	(440.27, 60.57) --
-	(440.64, 60.51) --
-	(441.02, 60.46) --
-	(441.40, 60.40) --
-	(441.78, 60.34) --
-	(442.16, 60.28) --
-	(442.54, 60.23) --
-	(442.92, 60.17) --
-	(443.30, 60.11) --
-	(443.68, 60.06) --
-	(444.06, 60.00) --
-	(444.44, 59.95) --
-	(444.82, 59.89) --
-	(445.20, 59.84) --
-	(445.58, 59.78) --
-	(445.96, 59.73) --
-	(446.34, 59.67) --
-	(446.72, 59.62) --
-	(447.10, 59.57) --
-	(447.48, 59.51) --
-	(447.86, 59.46) --
-	(448.24, 59.41) --
-	(448.62, 59.36) --
-	(449.00, 59.30) --
-	(449.38, 59.25) --
-	(449.76, 59.20) --
-	(450.14, 59.15) --
-	(450.52, 59.10) --
-	(450.90, 59.05) --
-	(451.28, 59.00) --
-	(451.66, 58.95) --
-	(452.04, 58.90) --
-	(452.42, 58.85) --
-	(452.80, 58.80) --
-	(453.18, 58.75) --
-	(453.56, 58.70) --
-	(453.93, 58.65) --
-	(454.31, 58.60) --
-	(454.69, 58.56) --
-	(455.07, 58.51) --
-	(455.45, 58.46) --
-	(455.83, 58.41) --
-	(456.21, 58.37) --
-	(456.59, 58.32) --
-	(456.97, 58.27) --
-	(457.35, 58.23) --
-	(457.73, 58.18) --
-	(458.11, 58.13) --
-	(458.49, 58.09) --
-	(458.87, 58.04) --
-	(459.25, 58.00) --
-	(459.63, 57.95) --
-	(460.01, 57.91) --
-	(460.39, 57.86) --
-	(460.77, 57.82) --
-	(461.15, 57.77) --
-	(461.53, 57.73) --
-	(461.91, 57.69) --
-	(462.29, 57.64) --
-	(462.67, 57.60) --
-	(463.05, 57.56) --
-	(463.43, 57.52) --
-	(463.81, 57.47) --
-	(464.19, 57.43) --
-	(464.57, 57.39) --
-	(464.95, 57.35) --
-	(465.33, 57.31) --
-	(465.71, 57.26) --
-	(466.09, 57.22) --
-	(466.47, 57.18) --
-	(466.85, 57.14) --
-	(467.23, 57.10) --
-	(467.60, 57.06) --
-	(467.98, 57.02) --
-	(468.36, 56.98) --
-	(468.74, 56.94) --
-	(469.12, 56.90) --
-	(469.50, 56.86) --
-	(469.88, 56.82) --
-	(470.26, 56.78) --
-	(470.64, 56.75) --
-	(471.02, 56.71) --
-	(471.40, 56.67) --
-	(471.78, 56.63) --
-	(472.16, 56.59) --
-	(472.54, 56.56) --
-	(472.92, 56.52) --
-	(473.30, 56.48) --
-	(473.68, 56.44) --
-	(474.06, 56.41) --
-	(474.44, 56.37) --
-	(474.82, 56.34) --
-	(475.20, 56.30) --
-	(475.58, 56.26) --
-	(475.96, 56.23) --
-	(476.34, 56.19) --
-	(476.72, 56.16) --
-	(477.10, 56.12) --
-	(477.48, 56.09) --
-	(477.86, 56.05) --
-	(478.24, 56.02) --
-	(478.62, 55.98) --
-	(479.00, 55.95) --
-	(479.38, 55.91) --
-	(479.76, 55.88) --
-	(480.14, 55.85) --
-	(480.52, 55.81) --
-	(480.90, 55.78) --
-	(481.27, 55.75) --
-	(481.65, 55.71) --
-	(482.03, 55.68) --
-	(482.41, 55.65) --
-	(482.79, 55.61) --
-	(483.17, 55.58) --
-	(483.55, 55.55) --
-	(483.93, 55.52) --
-	(484.31, 55.49) --
-	(484.69, 55.45) --
-	(485.07, 55.42) --
-	(485.45, 55.39) --
-	(485.83, 55.36) --
-	(486.21, 55.33) --
-	(486.59, 55.30) --
-	(486.97, 55.27) --
-	(487.35, 55.24) --
-	(487.73, 55.21) --
-	(488.11, 55.18) --
-	(488.49, 55.15) --
-	(488.87, 55.12) --
-	(489.25, 55.09) --
-	(489.63, 55.06) --
-	(490.01, 55.03) --
-	(490.39, 55.00) --
-	(490.77, 54.97) --
-	(491.15, 54.94) --
-	(491.53, 54.91) --
-	(491.91, 54.89) --
-	(492.29, 54.86) --
-	(492.67, 54.83) --
-	(493.05, 54.80) --
-	(493.43, 54.77) --
-	(493.81, 54.75) --
-	(494.19, 54.72) --
-	(494.56, 54.69) --
-	(494.94, 54.66) --
-	(495.32, 54.64) --
-	(495.70, 54.61) --
-	(496.08, 54.58) --
-	(496.46, 54.55) --
-	(496.84, 54.53) --
-	(497.22, 54.50) --
-	(497.60, 54.48) --
-	(497.98, 54.45) --
-	(498.36, 54.42) --
-	(498.74, 54.40) --
-	(499.12, 54.37) --
-	(499.50, 54.35) --
-	(499.88, 54.32) --
-	(500.26, 54.30) --
-	(500.64, 54.27) --
-	(501.02, 54.25) --
-	(501.40, 54.22) --
-	(501.78, 54.20) --
-	(502.16, 54.17) --
-	(502.54, 54.15) --
-	(502.92, 54.12) --
-	(503.30, 54.10) --
-	(503.68, 54.07) --
-	(504.06, 54.05) --
-	(504.44, 54.03) --
-	(504.82, 54.00) --
-	(505.20, 53.98) --
-	(505.58, 53.96) --
-	(505.96, 53.93) --
-	(506.34, 53.91) --
-	(506.72, 53.89) --
-	(507.10, 53.86) --
-	(507.48, 53.84) --
-	(507.86, 53.82) --
-	(508.23, 53.79) --
-	(508.61, 53.77) --
-	(508.99, 53.75) --
-	(509.37, 53.73) --
-	(509.75, 53.71) --
-	(510.13, 53.68) --
-	(510.51, 53.66) --
-	(510.89, 53.64) --
-	(511.27, 53.62) --
-	(511.65, 53.60) --
-	(512.03, 53.58) --
-	(512.41, 53.55) --
-	(512.79, 53.53) --
-	(513.17, 53.51) --
-	(513.55, 53.49) --
-	(513.93, 53.47) --
-	(514.31, 53.45) --
-	(514.69, 53.43) --
-	(515.07, 53.41) --
-	(515.45, 53.39) --
-	(515.83, 53.37) --
-	(516.21, 53.35) --
-	(516.59, 53.33) --
-	(516.97, 53.31) --
-	(517.35, 53.29) --
-	(517.73, 53.27) --
-	(518.11, 53.25) --
-	(518.49, 53.23) --
-	(518.87, 53.21) --
-	(519.25, 53.19) --
-	(519.63, 53.17) --
-	(520.01, 53.15) --
-	(520.39, 53.14) --
-	(520.77, 53.12) --
-	(521.15, 53.10) --
-	(521.53, 53.08) --
-	(521.90, 53.06) --
-	(522.28, 53.04) --
-	(522.66, 53.02) --
-	(523.04, 53.01) --
-	(523.42, 52.99) --
-	(523.80, 52.97) --
-	(524.18, 52.95) --
-	(524.56, 52.93) --
-	(524.94, 52.92) --
-	(525.32, 52.90) --
-	(525.70, 52.88) --
-	(526.08, 52.86) --
-	(526.46, 52.85) --
-	(526.84, 52.83) --
-	(527.22, 52.81) --
-	(527.60, 52.80) --
-	(527.98, 52.78) --
-	(528.36, 52.76);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (338.88,115.69) --
+	(339.26,116.14) --
+	(339.64,116.58) --
+	(340.02,117.03) --
+	(340.40,117.48) --
+	(340.78,117.93) --
+	(341.16,118.38) --
+	(341.54,118.83) --
+	(341.92,119.29) --
+	(342.30,119.75) --
+	(342.68,120.20) --
+	(343.06,120.66) --
+	(343.44,121.12) --
+	(343.82,121.58) --
+	(344.20,122.04) --
+	(344.58,122.50) --
+	(344.96,122.97) --
+	(345.34,123.43) --
+	(345.71,123.90) --
+	(346.09,124.37) --
+	(346.47,124.83) --
+	(346.85,125.30) --
+	(347.23,125.77) --
+	(347.61,126.25) --
+	(347.99,126.72) --
+	(348.37,127.19) --
+	(348.75,127.66) --
+	(349.13,128.14) --
+	(349.51,128.61) --
+	(349.89,129.09) --
+	(350.27,129.57) --
+	(350.65,130.05) --
+	(351.03,130.53) --
+	(351.41,131.00) --
+	(351.79,131.49) --
+	(352.17,131.97) --
+	(352.55,132.45) --
+	(352.93,132.93) --
+	(353.31,133.41) --
+	(353.69,133.90) --
+	(354.07,134.38) --
+	(354.45,134.86) --
+	(354.83,135.35) --
+	(355.21,135.83) --
+	(355.59,136.32) --
+	(355.97,136.81) --
+	(356.35,137.29) --
+	(356.73,137.78) --
+	(357.11,138.27) --
+	(357.49,138.76) --
+	(357.87,139.25) --
+	(358.25,139.73) --
+	(358.63,140.22) --
+	(359.01,140.71) --
+	(359.38,141.20) --
+	(359.76,141.69) --
+	(360.14,142.18) --
+	(360.52,142.67) --
+	(360.90,143.16) --
+	(361.28,143.65) --
+	(361.66,144.14) --
+	(362.04,144.63) --
+	(362.42,145.12) --
+	(362.80,145.61) --
+	(363.18,146.10) --
+	(363.56,146.59) --
+	(363.94,147.08) --
+	(364.32,147.57) --
+	(364.70,148.06) --
+	(365.08,148.54) --
+	(365.46,149.03) --
+	(365.84,149.52) --
+	(366.22,150.01) --
+	(366.60,150.50) --
+	(366.98,150.99) --
+	(367.36,151.47) --
+	(367.74,151.96) --
+	(368.12,152.45) --
+	(368.50,152.93) --
+	(368.88,153.42) --
+	(369.26,153.91) --
+	(369.64,154.39) --
+	(370.02,154.87) --
+	(370.40,155.36) --
+	(370.78,155.84) --
+	(371.16,156.32) --
+	(371.54,156.81) --
+	(371.92,157.29) --
+	(372.30,157.77) --
+	(372.68,158.25) --
+	(373.05,158.73) --
+	(373.43,159.21) --
+	(373.81,159.68) --
+	(374.19,160.16) --
+	(374.57,160.64) --
+	(374.95,161.11) --
+	(375.33,161.59) --
+	(375.71,162.06) --
+	(376.09,162.53) --
+	(376.47,163.00) --
+	(376.85,163.48) --
+	(377.23,163.94) --
+	(377.61,164.41) --
+	(377.99,164.88) --
+	(378.37,165.35) --
+	(378.75,165.81) --
+	(379.13,166.28) --
+	(379.51,166.74) --
+	(379.89,167.20) --
+	(380.27,167.67) --
+	(380.65,168.13) --
+	(381.03,168.58) --
+	(381.41,169.04) --
+	(381.79,169.50) --
+	(382.17,169.95) --
+	(382.55,170.41) --
+	(382.93,170.86) --
+	(383.31,171.31) --
+	(383.69,171.76) --
+	(384.07,172.21) --
+	(384.45,172.66) --
+	(384.83,173.10) --
+	(385.21,173.55) --
+	(385.59,173.99) --
+	(385.97,174.43) --
+	(386.34,174.87) --
+	(386.72,175.31) --
+	(387.10,175.75) --
+	(387.48,176.19) --
+	(387.86,176.62) --
+	(388.24,177.05) --
+	(388.62,177.49) --
+	(389.00,177.92) --
+	(389.38,178.34) --
+	(389.76,178.77) --
+	(390.14,179.20) --
+	(390.52,179.62) --
+	(390.90,180.04) --
+	(391.28,180.46) --
+	(391.66,180.88) --
+	(392.04,181.30) --
+	(392.42,181.71) --
+	(392.80,182.13) --
+	(393.18,182.54) --
+	(393.56,182.95) --
+	(393.94,183.36) --
+	(394.32,183.76) --
+	(394.70,184.17) --
+	(395.08,184.57) --
+	(395.46,184.97) --
+	(395.84,185.37) --
+	(396.22,185.77) --
+	(396.60,186.17) --
+	(396.98,186.56) --
+	(397.36,186.95) --
+	(397.74,187.35) --
+	(398.12,187.73) --
+	(398.50,188.12) --
+	(398.88,188.51) --
+	(399.26,188.89) --
+	(399.64,189.27) --
+	(400.01,189.65) --
+	(400.39,190.03) --
+	(400.77,190.41) --
+	(401.15,190.78) --
+	(401.53,191.15) --
+	(401.91,191.52) --
+	(402.29,191.89) --
+	(402.67,192.26) --
+	(403.05,192.62) --
+	(403.43,192.98) --
+	(403.81,193.35) --
+	(404.19,193.70) --
+	(404.57,194.06) --
+	(404.95,194.42) --
+	(405.33,194.77) --
+	(405.71,195.12) --
+	(406.09,195.47) --
+	(406.47,195.82) --
+	(406.85,196.16) --
+	(407.23,196.51) --
+	(407.61,196.85) --
+	(407.99,197.19) --
+	(408.37,197.52) --
+	(408.75,197.86) --
+	(409.13,198.19) --
+	(409.51,198.53) --
+	(409.89,198.86) --
+	(410.27,199.18) --
+	(410.65,199.51) --
+	(411.03,199.83) --
+	(411.41,200.16) --
+	(411.79,200.48) --
+	(412.17,200.79) --
+	(412.55,201.11) --
+	(412.93,201.42) --
+	(413.31,201.74) --
+	(413.68,202.05) --
+	(414.06,202.36) --
+	(414.44,202.66) --
+	(414.82,202.97) --
+	(415.20,203.27) --
+	(415.58,203.57) --
+	(415.96,203.87) --
+	(416.34,204.17) --
+	(416.72,204.46) --
+	(417.10,204.75) --
+	(417.48,205.04) --
+	(417.86,205.33) --
+	(418.24,205.62) --
+	(418.62,205.91) --
+	(419.00,206.19) --
+	(419.38,206.47) --
+	(419.76,206.75) --
+	(420.14,207.03) --
+	(420.52,207.30) --
+	(420.90,207.58) --
+	(421.28,207.85) --
+	(421.66,208.12) --
+	(422.04,208.39) --
+	(422.42,208.65) --
+	(422.80,208.92) --
+	(423.18,209.18) --
+	(423.56,209.44) --
+	(423.94,209.70) --
+	(424.32,209.96) --
+	(424.70,210.21) --
+	(425.08,210.47) --
+	(425.46,210.72) --
+	(425.84,210.97) --
+	(426.22,211.22) --
+	(426.60,211.46) --
+	(426.97,211.71) --
+	(427.35,211.95) --
+	(427.73,212.19) --
+	(428.11,212.43) --
+	(428.49,212.67) --
+	(428.87,212.90) --
+	(429.25,213.14) --
+	(429.63,213.37) --
+	(430.01,213.60) --
+	(430.39,213.83) --
+	(430.77,214.06) --
+	(431.15,214.28) --
+	(431.53,214.51) --
+	(431.91,214.73) --
+	(432.29,214.95) --
+	(432.67,215.17) --
+	(433.05,215.38) --
+	(433.43,215.60) --
+	(433.81,215.81) --
+	(434.19,216.02) --
+	(434.57,216.23) --
+	(434.95,216.44) --
+	(435.33,216.65) --
+	(435.71,216.85) --
+	(436.09,217.06) --
+	(436.47,217.26) --
+	(436.85,217.46) --
+	(437.23,217.66) --
+	(437.61,217.86) --
+	(437.99,218.05) --
+	(438.37,218.25) --
+	(438.75,218.44) --
+	(439.13,218.63) --
+	(439.51,218.82) --
+	(439.89,219.01) --
+	(440.27,219.19) --
+	(440.64,219.38) --
+	(441.02,219.56) --
+	(441.40,219.74) --
+	(441.78,219.93) --
+	(442.16,220.10) --
+	(442.54,220.28) --
+	(442.92,220.46) --
+	(443.30,220.63) --
+	(443.68,220.81) --
+	(444.06,220.98) --
+	(444.44,221.15) --
+	(444.82,221.32) --
+	(445.20,221.48) --
+	(445.58,221.65) --
+	(445.96,221.81) --
+	(446.34,221.98) --
+	(446.72,222.14) --
+	(447.10,222.30) --
+	(447.48,222.46) --
+	(447.86,222.62) --
+	(448.24,222.77) --
+	(448.62,222.93) --
+	(449.00,223.08) --
+	(449.38,223.24) --
+	(449.76,223.39) --
+	(450.14,223.54) --
+	(450.52,223.68) --
+	(450.90,223.83) --
+	(451.28,223.98) --
+	(451.66,224.12) --
+	(452.04,224.27) --
+	(452.42,224.41) --
+	(452.80,224.55) --
+	(453.18,224.69) --
+	(453.56,224.83) --
+	(453.93,224.97) --
+	(454.31,225.10) --
+	(454.69,225.24) --
+	(455.07,225.37) --
+	(455.45,225.50) --
+	(455.83,225.64) --
+	(456.21,225.77) --
+	(456.59,225.90) --
+	(456.97,226.02) --
+	(457.35,226.15) --
+	(457.73,226.28) --
+	(458.11,226.40) --
+	(458.49,226.52) --
+	(458.87,226.65) --
+	(459.25,226.77) --
+	(459.63,226.89) --
+	(460.01,227.01) --
+	(460.39,227.13) --
+	(460.77,227.24) --
+	(461.15,227.36) --
+	(461.53,227.47) --
+	(461.91,227.59) --
+	(462.29,227.70) --
+	(462.67,227.81) --
+	(463.05,227.92) --
+	(463.43,228.03) --
+	(463.81,228.14) --
+	(464.19,228.25) --
+	(464.57,228.36) --
+	(464.95,228.46) --
+	(465.33,228.57) --
+	(465.71,228.67) --
+	(466.09,228.78) --
+	(466.47,228.88) --
+	(466.85,228.98) --
+	(467.23,229.08) --
+	(467.60,229.18) --
+	(467.98,229.28) --
+	(468.36,229.37) --
+	(468.74,229.47) --
+	(469.12,229.57) --
+	(469.50,229.66) --
+	(469.88,229.76) --
+	(470.26,229.85) --
+	(470.64,229.94) --
+	(471.02,230.03) --
+	(471.40,230.12) --
+	(471.78,230.21) --
+	(472.16,230.30) --
+	(472.54,230.39) --
+	(472.92,230.48) --
+	(473.30,230.56) --
+	(473.68,230.65) --
+	(474.06,230.73) --
+	(474.44,230.82) --
+	(474.82,230.90) --
+	(475.20,230.98) --
+	(475.58,231.06) --
+	(475.96,231.15) --
+	(476.34,231.23) --
+	(476.72,231.31) --
+	(477.10,231.38) --
+	(477.48,231.46) --
+	(477.86,231.54) --
+	(478.24,231.62) --
+	(478.62,231.69) --
+	(479.00,231.77) --
+	(479.38,231.84) --
+	(479.76,231.91) --
+	(480.14,231.99) --
+	(480.52,232.06) --
+	(480.90,232.13) --
+	(481.27,232.20) --
+	(481.65,232.27) --
+	(482.03,232.34) --
+	(482.41,232.41) --
+	(482.79,232.48) --
+	(483.17,232.55) --
+	(483.55,232.61) --
+	(483.93,232.68) --
+	(484.31,232.74) --
+	(484.69,232.81) --
+	(485.07,232.87) --
+	(485.45,232.94) --
+	(485.83,233.00) --
+	(486.21,233.06) --
+	(486.59,233.12) --
+	(486.97,233.19) --
+	(487.35,233.25) --
+	(487.73,233.31) --
+	(488.11,233.37) --
+	(488.49,233.42) --
+	(488.87,233.48) --
+	(489.25,233.54) --
+	(489.63,233.60) --
+	(490.01,233.66) --
+	(490.39,233.71) --
+	(490.77,233.77) --
+	(491.15,233.82) --
+	(491.53,233.88) --
+	(491.91,233.93) --
+	(492.29,233.98) --
+	(492.67,234.04) --
+	(493.05,234.09) --
+	(493.43,234.14) --
+	(493.81,234.19) --
+	(494.19,234.24) --
+	(494.56,234.29) --
+	(494.94,234.34) --
+	(495.32,234.39) --
+	(495.70,234.44) --
+	(496.08,234.49) --
+	(496.46,234.54) --
+	(496.84,234.59) --
+	(497.22,234.63) --
+	(497.60,234.68) --
+	(497.98,234.73) --
+	(498.36,234.77) --
+	(498.74,234.82) --
+	(499.12,234.86) --
+	(499.50,234.91) --
+	(499.88,234.95) --
+	(500.26,234.99) --
+	(500.64,235.04) --
+	(501.02,235.08) --
+	(501.40,235.12) --
+	(501.78,235.16) --
+	(502.16,235.21) --
+	(502.54,235.25) --
+	(502.92,235.29) --
+	(503.30,235.33) --
+	(503.68,235.37) --
+	(504.06,235.41) --
+	(504.44,235.45) --
+	(504.82,235.48) --
+	(505.20,235.52) --
+	(505.58,235.56) --
+	(505.96,235.60) --
+	(506.34,235.64) --
+	(506.72,235.67) --
+	(507.10,235.71) --
+	(507.48,235.74) --
+	(507.86,235.78) --
+	(508.23,235.82) --
+	(508.61,235.85) --
+	(508.99,235.89) --
+	(509.37,235.92) --
+	(509.75,235.95) --
+	(510.13,235.99) --
+	(510.51,236.02) --
+	(510.89,236.05) --
+	(511.27,236.09) --
+	(511.65,236.12) --
+	(512.03,236.15) --
+	(512.41,236.18) --
+	(512.79,236.21) --
+	(513.17,236.24) --
+	(513.55,236.28) --
+	(513.93,236.31) --
+	(514.31,236.34) --
+	(514.69,236.37) --
+	(515.07,236.40) --
+	(515.45,236.42) --
+	(515.83,236.45) --
+	(516.21,236.48) --
+	(516.59,236.51) --
+	(516.97,236.54) --
+	(517.35,236.57) --
+	(517.73,236.59) --
+	(518.11,236.62) --
+	(518.49,236.65) --
+	(518.87,236.67) --
+	(519.25,236.70) --
+	(519.63,236.73) --
+	(520.01,236.75) --
+	(520.39,236.78) --
+	(520.77,236.80) --
+	(521.15,236.83) --
+	(521.53,236.85) --
+	(521.90,236.88) --
+	(522.28,236.90) --
+	(522.66,236.93) --
+	(523.04,236.95) --
+	(523.42,236.98) --
+	(523.80,237.00) --
+	(524.18,237.02) --
+	(524.56,237.04) --
+	(524.94,237.07) --
+	(525.32,237.09) --
+	(525.70,237.11) --
+	(526.08,237.13) --
+	(526.46,237.16) --
+	(526.84,237.18) --
+	(527.22,237.20) --
+	(527.60,237.22) --
+	(527.98,237.24) --
+	(528.36,237.26);
+
+\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (338.88, 93.73) --
+	(339.26, 93.50) --
+	(339.64, 93.28) --
+	(340.02, 93.05) --
+	(340.40, 92.82) --
+	(340.78, 92.60) --
+	(341.16, 92.37) --
+	(341.54, 92.15) --
+	(341.92, 91.93) --
+	(342.30, 91.71) --
+	(342.68, 91.49) --
+	(343.06, 91.27) --
+	(343.44, 91.05) --
+	(343.82, 90.83) --
+	(344.20, 90.61) --
+	(344.58, 90.39) --
+	(344.96, 90.18) --
+	(345.34, 89.96) --
+	(345.71, 89.75) --
+	(346.09, 89.53) --
+	(346.47, 89.32) --
+	(346.85, 89.11) --
+	(347.23, 88.90) --
+	(347.61, 88.69) --
+	(347.99, 88.48) --
+	(348.37, 88.27) --
+	(348.75, 88.06) --
+	(349.13, 87.86) --
+	(349.51, 87.65) --
+	(349.89, 87.45) --
+	(350.27, 87.24) --
+	(350.65, 87.04) --
+	(351.03, 86.84) --
+	(351.41, 86.63) --
+	(351.79, 86.43) --
+	(352.17, 86.23) --
+	(352.55, 86.03) --
+	(352.93, 85.84) --
+	(353.31, 85.64) --
+	(353.69, 85.44) --
+	(354.07, 85.25) --
+	(354.45, 85.05) --
+	(354.83, 84.86) --
+	(355.21, 84.66) --
+	(355.59, 84.47) --
+	(355.97, 84.28) --
+	(356.35, 84.09) --
+	(356.73, 83.90) --
+	(357.11, 83.71) --
+	(357.49, 83.52) --
+	(357.87, 83.33) --
+	(358.25, 83.15) --
+	(358.63, 82.96) --
+	(359.01, 82.77) --
+	(359.38, 82.59) --
+	(359.76, 82.41) --
+	(360.14, 82.22) --
+	(360.52, 82.04) --
+	(360.90, 81.86) --
+	(361.28, 81.68) --
+	(361.66, 81.50) --
+	(362.04, 81.32) --
+	(362.42, 81.14) --
+	(362.80, 80.97) --
+	(363.18, 80.79) --
+	(363.56, 80.62) --
+	(363.94, 80.44) --
+	(364.32, 80.27) --
+	(364.70, 80.09) --
+	(365.08, 79.92) --
+	(365.46, 79.75) --
+	(365.84, 79.58) --
+	(366.22, 79.41) --
+	(366.60, 79.24) --
+	(366.98, 79.07) --
+	(367.36, 78.91) --
+	(367.74, 78.74) --
+	(368.12, 78.57) --
+	(368.50, 78.41) --
+	(368.88, 78.24) --
+	(369.26, 78.08) --
+	(369.64, 77.92) --
+	(370.02, 77.76) --
+	(370.40, 77.59) --
+	(370.78, 77.43) --
+	(371.16, 77.27) --
+	(371.54, 77.11) --
+	(371.92, 76.96) --
+	(372.30, 76.80) --
+	(372.68, 76.64) --
+	(373.05, 76.49) --
+	(373.43, 76.33) --
+	(373.81, 76.18) --
+	(374.19, 76.02) --
+	(374.57, 75.87) --
+	(374.95, 75.72) --
+	(375.33, 75.57) --
+	(375.71, 75.42) --
+	(376.09, 75.27) --
+	(376.47, 75.12) --
+	(376.85, 74.97) --
+	(377.23, 74.82) --
+	(377.61, 74.67) --
+	(377.99, 74.53) --
+	(378.37, 74.38) --
+	(378.75, 74.24) --
+	(379.13, 74.09) --
+	(379.51, 73.95) --
+	(379.89, 73.81) --
+	(380.27, 73.67) --
+	(380.65, 73.52) --
+	(381.03, 73.38) --
+	(381.41, 73.24) --
+	(381.79, 73.11) --
+	(382.17, 72.97) --
+	(382.55, 72.83) --
+	(382.93, 72.69) --
+	(383.31, 72.56) --
+	(383.69, 72.42) --
+	(384.07, 72.29) --
+	(384.45, 72.15) --
+	(384.83, 72.02) --
+	(385.21, 71.89) --
+	(385.59, 71.75) --
+	(385.97, 71.62) --
+	(386.34, 71.49) --
+	(386.72, 71.36) --
+	(387.10, 71.23) --
+	(387.48, 71.10) --
+	(387.86, 70.98) --
+	(388.24, 70.85) --
+	(388.62, 70.72) --
+	(389.00, 70.60) --
+	(389.38, 70.47) --
+	(389.76, 70.35) --
+	(390.14, 70.22) --
+	(390.52, 70.10) --
+	(390.90, 69.98) --
+	(391.28, 69.86) --
+	(391.66, 69.73) --
+	(392.04, 69.61) --
+	(392.42, 69.49) --
+	(392.80, 69.37) --
+	(393.18, 69.26) --
+	(393.56, 69.14) --
+	(393.94, 69.02) --
+	(394.32, 68.90) --
+	(394.70, 68.79) --
+	(395.08, 68.67) --
+	(395.46, 68.56) --
+	(395.84, 68.44) --
+	(396.22, 68.33) --
+	(396.60, 68.22) --
+	(396.98, 68.10) --
+	(397.36, 67.99) --
+	(397.74, 67.88) --
+	(398.12, 67.77) --
+	(398.50, 67.66) --
+	(398.88, 67.55) --
+	(399.26, 67.44) --
+	(399.64, 67.33) --
+	(400.01, 67.22) --
+	(400.39, 67.12) --
+	(400.77, 67.01) --
+	(401.15, 66.91) --
+	(401.53, 66.80) --
+	(401.91, 66.70) --
+	(402.29, 66.59) --
+	(402.67, 66.49) --
+	(403.05, 66.39) --
+	(403.43, 66.28) --
+	(403.81, 66.18) --
+	(404.19, 66.08) --
+	(404.57, 65.98) --
+	(404.95, 65.88) --
+	(405.33, 65.78) --
+	(405.71, 65.68) --
+	(406.09, 65.58) --
+	(406.47, 65.48) --
+	(406.85, 65.39) --
+	(407.23, 65.29) --
+	(407.61, 65.19) --
+	(407.99, 65.10) --
+	(408.37, 65.00) --
+	(408.75, 64.91) --
+	(409.13, 64.81) --
+	(409.51, 64.72) --
+	(409.89, 64.63) --
+	(410.27, 64.54) --
+	(410.65, 64.44) --
+	(411.03, 64.35) --
+	(411.41, 64.26) --
+	(411.79, 64.17) --
+	(412.17, 64.08) --
+	(412.55, 63.99) --
+	(412.93, 63.90) --
+	(413.31, 63.81) --
+	(413.68, 63.73) --
+	(414.06, 63.64) --
+	(414.44, 63.55) --
+	(414.82, 63.47) --
+	(415.20, 63.38) --
+	(415.58, 63.30) --
+	(415.96, 63.21) --
+	(416.34, 63.13) --
+	(416.72, 63.04) --
+	(417.10, 62.96) --
+	(417.48, 62.88) --
+	(417.86, 62.79) --
+	(418.24, 62.71) --
+	(418.62, 62.63) --
+	(419.00, 62.55) --
+	(419.38, 62.47) --
+	(419.76, 62.39) --
+	(420.14, 62.31) --
+	(420.52, 62.23) --
+	(420.90, 62.15) --
+	(421.28, 62.07) --
+	(421.66, 62.00) --
+	(422.04, 61.92) --
+	(422.42, 61.84) --
+	(422.80, 61.77) --
+	(423.18, 61.69) --
+	(423.56, 61.62) --
+	(423.94, 61.54) --
+	(424.32, 61.47) --
+	(424.70, 61.39) --
+	(425.08, 61.32) --
+	(425.46, 61.25) --
+	(425.84, 61.17) --
+	(426.22, 61.10) --
+	(426.60, 61.03) --
+	(426.97, 60.96) --
+	(427.35, 60.89) --
+	(427.73, 60.82) --
+	(428.11, 60.75) --
+	(428.49, 60.68) --
+	(428.87, 60.61) --
+	(429.25, 60.54) --
+	(429.63, 60.47) --
+	(430.01, 60.40) --
+	(430.39, 60.33) --
+	(430.77, 60.27) --
+	(431.15, 60.20) --
+	(431.53, 60.13) --
+	(431.91, 60.07) --
+	(432.29, 60.00) --
+	(432.67, 59.94) --
+	(433.05, 59.87) --
+	(433.43, 59.81) --
+	(433.81, 59.74) --
+	(434.19, 59.68) --
+	(434.57, 59.62) --
+	(434.95, 59.55) --
+	(435.33, 59.49) --
+	(435.71, 59.43) --
+	(436.09, 59.37) --
+	(436.47, 59.30) --
+	(436.85, 59.24) --
+	(437.23, 59.18) --
+	(437.61, 59.12) --
+	(437.99, 59.06) --
+	(438.37, 59.00) --
+	(438.75, 58.94) --
+	(439.13, 58.88) --
+	(439.51, 58.83) --
+	(439.89, 58.77) --
+	(440.27, 58.71) --
+	(440.64, 58.65) --
+	(441.02, 58.60) --
+	(441.40, 58.54) --
+	(441.78, 58.48) --
+	(442.16, 58.43) --
+	(442.54, 58.37) --
+	(442.92, 58.32) --
+	(443.30, 58.26) --
+	(443.68, 58.21) --
+	(444.06, 58.15) --
+	(444.44, 58.10) --
+	(444.82, 58.04) --
+	(445.20, 57.99) --
+	(445.58, 57.94) --
+	(445.96, 57.88) --
+	(446.34, 57.83) --
+	(446.72, 57.78) --
+	(447.10, 57.73) --
+	(447.48, 57.68) --
+	(447.86, 57.63) --
+	(448.24, 57.58) --
+	(448.62, 57.53) --
+	(449.00, 57.48) --
+	(449.38, 57.43) --
+	(449.76, 57.38) --
+	(450.14, 57.33) --
+	(450.52, 57.28) --
+	(450.90, 57.23) --
+	(451.28, 57.18) --
+	(451.66, 57.13) --
+	(452.04, 57.09) --
+	(452.42, 57.04) --
+	(452.80, 56.99) --
+	(453.18, 56.94) --
+	(453.56, 56.90) --
+	(453.93, 56.85) --
+	(454.31, 56.81) --
+	(454.69, 56.76) --
+	(455.07, 56.71) --
+	(455.45, 56.67) --
+	(455.83, 56.62) --
+	(456.21, 56.58) --
+	(456.59, 56.54) --
+	(456.97, 56.49) --
+	(457.35, 56.45) --
+	(457.73, 56.41) --
+	(458.11, 56.36) --
+	(458.49, 56.32) --
+	(458.87, 56.28) --
+	(459.25, 56.23) --
+	(459.63, 56.19) --
+	(460.01, 56.15) --
+	(460.39, 56.11) --
+	(460.77, 56.07) --
+	(461.15, 56.03) --
+	(461.53, 55.99) --
+	(461.91, 55.95) --
+	(462.29, 55.91) --
+	(462.67, 55.87) --
+	(463.05, 55.83) --
+	(463.43, 55.79) --
+	(463.81, 55.75) --
+	(464.19, 55.71) --
+	(464.57, 55.67) --
+	(464.95, 55.63) --
+	(465.33, 55.59) --
+	(465.71, 55.55) --
+	(466.09, 55.52) --
+	(466.47, 55.48) --
+	(466.85, 55.44) --
+	(467.23, 55.41) --
+	(467.60, 55.37) --
+	(467.98, 55.33) --
+	(468.36, 55.30) --
+	(468.74, 55.26) --
+	(469.12, 55.22) --
+	(469.50, 55.19) --
+	(469.88, 55.15) --
+	(470.26, 55.12) --
+	(470.64, 55.08) --
+	(471.02, 55.05) --
+	(471.40, 55.01) --
+	(471.78, 54.98) --
+	(472.16, 54.95) --
+	(472.54, 54.91) --
+	(472.92, 54.88) --
+	(473.30, 54.84) --
+	(473.68, 54.81) --
+	(474.06, 54.78) --
+	(474.44, 54.75) --
+	(474.82, 54.71) --
+	(475.20, 54.68) --
+	(475.58, 54.65) --
+	(475.96, 54.62) --
+	(476.34, 54.58) --
+	(476.72, 54.55) --
+	(477.10, 54.52) --
+	(477.48, 54.49) --
+	(477.86, 54.46) --
+	(478.24, 54.43) --
+	(478.62, 54.40) --
+	(479.00, 54.37) --
+	(479.38, 54.34) --
+	(479.76, 54.31) --
+	(480.14, 54.28) --
+	(480.52, 54.25) --
+	(480.90, 54.22) --
+	(481.27, 54.19) --
+	(481.65, 54.16) --
+	(482.03, 54.13) --
+	(482.41, 54.10) --
+	(482.79, 54.08) --
+	(483.17, 54.05) --
+	(483.55, 54.02) --
+	(483.93, 53.99) --
+	(484.31, 53.96) --
+	(484.69, 53.94) --
+	(485.07, 53.91) --
+	(485.45, 53.88) --
+	(485.83, 53.85) --
+	(486.21, 53.83) --
+	(486.59, 53.80) --
+	(486.97, 53.77) --
+	(487.35, 53.75) --
+	(487.73, 53.72) --
+	(488.11, 53.70) --
+	(488.49, 53.67) --
+	(488.87, 53.64) --
+	(489.25, 53.62) --
+	(489.63, 53.59) --
+	(490.01, 53.57) --
+	(490.39, 53.54) --
+	(490.77, 53.52) --
+	(491.15, 53.49) --
+	(491.53, 53.47) --
+	(491.91, 53.45) --
+	(492.29, 53.42) --
+	(492.67, 53.40) --
+	(493.05, 53.37) --
+	(493.43, 53.35) --
+	(493.81, 53.33) --
+	(494.19, 53.30) --
+	(494.56, 53.28) --
+	(494.94, 53.26) --
+	(495.32, 53.23) --
+	(495.70, 53.21) --
+	(496.08, 53.19) --
+	(496.46, 53.17) --
+	(496.84, 53.14) --
+	(497.22, 53.12) --
+	(497.60, 53.10) --
+	(497.98, 53.08) --
+	(498.36, 53.06) --
+	(498.74, 53.03) --
+	(499.12, 53.01) --
+	(499.50, 52.99) --
+	(499.88, 52.97) --
+	(500.26, 52.95) --
+	(500.64, 52.93) --
+	(501.02, 52.91) --
+	(501.40, 52.89) --
+	(501.78, 52.87) --
+	(502.16, 52.85) --
+	(502.54, 52.82) --
+	(502.92, 52.80) --
+	(503.30, 52.78) --
+	(503.68, 52.76) --
+	(504.06, 52.75) --
+	(504.44, 52.73) --
+	(504.82, 52.71) --
+	(505.20, 52.69) --
+	(505.58, 52.67) --
+	(505.96, 52.65) --
+	(506.34, 52.63) --
+	(506.72, 52.61) --
+	(507.10, 52.59) --
+	(507.48, 52.57) --
+	(507.86, 52.55) --
+	(508.23, 52.54) --
+	(508.61, 52.52) --
+	(508.99, 52.50) --
+	(509.37, 52.48) --
+	(509.75, 52.46) --
+	(510.13, 52.45) --
+	(510.51, 52.43) --
+	(510.89, 52.41) --
+	(511.27, 52.39) --
+	(511.65, 52.38) --
+	(512.03, 52.36) --
+	(512.41, 52.34) --
+	(512.79, 52.33) --
+	(513.17, 52.31) --
+	(513.55, 52.29) --
+	(513.93, 52.28) --
+	(514.31, 52.26) --
+	(514.69, 52.24) --
+	(515.07, 52.23) --
+	(515.45, 52.21) --
+	(515.83, 52.19) --
+	(516.21, 52.18) --
+	(516.59, 52.16) --
+	(516.97, 52.15) --
+	(517.35, 52.13) --
+	(517.73, 52.11) --
+	(518.11, 52.10) --
+	(518.49, 52.08) --
+	(518.87, 52.07) --
+	(519.25, 52.05) --
+	(519.63, 52.04) --
+	(520.01, 52.02) --
+	(520.39, 52.01) --
+	(520.77, 51.99) --
+	(521.15, 51.98) --
+	(521.53, 51.96) --
+	(521.90, 51.95) --
+	(522.28, 51.94) --
+	(522.66, 51.92) --
+	(523.04, 51.91) --
+	(523.42, 51.89) --
+	(523.80, 51.88) --
+	(524.18, 51.87) --
+	(524.56, 51.85) --
+	(524.94, 51.84) --
+	(525.32, 51.82) --
+	(525.70, 51.81) --
+	(526.08, 51.80) --
+	(526.46, 51.78) --
+	(526.84, 51.77) --
+	(527.22, 51.76) --
+	(527.60, 51.74) --
+	(527.98, 51.73) --
+	(528.36, 51.72);
 \end{scope}

### 2020-09-01 benchmarking/benchmarkingVM/ESS_round2.tex
complete draft

@@
-% Created by tikzDevice version 0.12.3.1 on 2020-08-31 17:26:30
+% Created by tikzDevice version 0.12.3.1 on 2020-09-01 15:29:50
 % !TEX encoding = UTF-8 Unicode
@@
 
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] ( 88.87,459.09) --
+	( 94.17,459.09);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] ( 91.70,458.12) --
+	( 91.70,460.01);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 91.70,455.86) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (166.48,446.71) --
+	(167.44,446.71);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (166.96,446.25) --
+	(166.96,447.16);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (166.96,443.81) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] ( 96.22,462.99) --
+	( 97.81,462.99);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] ( 97.03,462.79) --
+	( 97.03,463.20);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 97.03,458.96) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] ( 85.62,438.93) --
+	( 90.70,438.93);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] ( 88.33,438.43) --
+	( 88.33,439.41);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 88.33,436.02) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] ( 86.69,439.02) --
+	( 91.75,439.02);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] ( 89.39,438.53) --
+	( 89.39,439.50);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 89.39,434.99) {$l$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] ( 93.94,458.26) --
+	( 99.06,458.26);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] ( 96.67,457.64) --
+	( 96.67,458.86);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 96.67,455.36) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (174.48,467.13) --
+	(174.70,467.13);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (174.59,466.97) --
+	(174.59,467.28);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.59,464.22) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
 \path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (205.92,505.04) --
@@
 	(206.23,505.29);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (206.23,501.82) {$p$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(216.73,507.82);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (216.73,504.49) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(211.70,511.25);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.70,507.16) {$r$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(202.32,494.11);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.32,490.89) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(204.03,496.64);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (204.03,492.28) {$l$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(206.16,506.73);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (206.16,503.60) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(217.05,512.71);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (217.05,509.69) {$\kappa$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(174.83,469.72);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (174.83,465.69) {$p$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(206.87,497.77);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (206.87,494.59) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(204.57,500.32);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (204.57,496.21) {$r$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(166.26,454.24);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (166.26,450.44) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(168.44,456.25);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (168.44,451.31) {$l$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(171.11,467.17);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (171.11,463.46) {$\sigma$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(206.85,501.23);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (206.85,498.24) {$\kappa$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(162.13,477.54);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (162.13,473.86) {$p$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(205.15,494.06);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.15,490.91) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(197.89,495.07);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.89,490.97) {$r$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(157.10,470.46);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (157.10,467.17) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(160.18,471.51);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (160.18,467.09) {$l$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(166.37,474.51);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (166.37,471.13) {$\sigma$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(206.10,500.90);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (206.10,497.89) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (121.64,470.69) --
-	(124.00,470.69);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (122.86,470.18) --
-	(122.86,471.19);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (122.86,467.47) {$p$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (185.34,468.90) --
-	(185.91,468.90);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (185.63,468.61) --
-	(185.63,469.18);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.63,465.99) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (162.37,475.57) --
-	(162.64,475.57);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (162.51,475.45) --
-	(162.51,475.69);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (162.51,471.54) {$r$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (120.02,442.67) --
-	(122.54,442.67);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (121.32,442.05) --
-	(121.32,443.26);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (121.32,439.76) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (121.22,442.55) --
-	(123.50,442.55);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (122.40,441.89) --
-	(122.40,443.18);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (122.40,438.51) {$l$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (120.43,458.76) --
-	(124.03,458.76);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (122.32,457.98) --
-	(122.32,459.51);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (122.32,455.86) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (188.53,482.91) --
-	(188.81,482.91);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (188.67,482.83) --
-	(188.67,482.99);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.67,480.01) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (122.47,470.59) --
+	(124.29,470.59);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (123.40,470.12) --
+	(123.40,471.05);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (123.40,467.36) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (185.33,468.78) --
+	(185.82,468.78);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (185.58,468.50) --
+	(185.58,469.06);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.58,465.88) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (162.43,475.58) --
+	(162.66,475.58);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (162.55,475.47) --
+	(162.55,475.68);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (162.55,471.54) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (121.23,442.44) --
+	(123.08,442.44);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (122.17,441.85) --
+	(122.17,443.01);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (122.17,439.54) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (122.04,442.33) --
+	(123.84,442.33);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (122.96,441.70) --
+	(122.96,442.93);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (122.96,438.29) {$l$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (122.11,458.40) --
+	(124.58,458.40);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (123.38,457.64) --
+	(123.38,459.13);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (123.38,455.50) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (188.54,482.96) --
+	(188.76,482.96);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (188.65,482.88) --
+	(188.65,483.03);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.65,480.05) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(207.98,488.81);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.98,484.39) {$p$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(211.45,504.41);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.45,501.17) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(221.32,516.26);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (221.32,512.18) {$r$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(200.66,498.01);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (200.66,494.77) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(205.99,503.19);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.99,498.90) {$l$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(197.45,491.55);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.45,488.34) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(211.68,507.81);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.68,504.80) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(160.79,500.06);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (160.79,496.48) {$p$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(216.74,499.24);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (216.74,496.05) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(197.69,503.74);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.69,499.64) {$r$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(159.54,471.72);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (159.54,468.20) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(161.26,472.14);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (161.26,467.50) {$l$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(167.17,484.03);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (167.17,480.67) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(215.30,512.76);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (215.30,509.69) {$\kappa$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(179.33,481.44);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.33,477.79) {$p$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(192.12,484.45);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.12,480.02) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(194.85,489.11);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.85,484.98) {$r$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(179.09,473.89);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.09,470.67) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(178.17,473.28);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (178.17,468.93) {$l$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(182.13,481.36);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.13,478.08) {$\sigma$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(204.55,501.45);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (204.55,498.43) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(199.90,488.29);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.90,484.64) {$p$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(187.60,484.63);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.60,481.10) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(204.20,500.97);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (204.20,496.87) {$r$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(194.33,490.38);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.33,487.26) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(199.86,496.04);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.86,491.75) {$l$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(192.69,490.49);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (192.69,487.09) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(214.16,512.37);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (377.95,431.45) --
+	(383.25,431.45);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (380.78,430.87) --
+	(380.78,432.02);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (380.78,428.22) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (455.56,442.95) --
+	(456.52,442.95);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (456.04,442.17) --
+	(456.04,443.70);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (456.04,440.05) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (385.30,457.16) --
+	(386.89,457.16);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (386.11,456.95) --
+	(386.11,457.37);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (386.11,453.13) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (374.70,430.23) --
+	(379.78,430.23);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (377.41,429.68) --
+	(377.41,430.76);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (377.41,427.33) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (375.77,430.56) --
+	(380.83,430.56);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (378.47,430.01) --
+	(378.47,431.09);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (378.47,426.53) {$l$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (383.02,442.92) --
+	(388.14,442.92);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (385.75,442.11) --
+	(385.75,443.70);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (385.75,440.02) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (463.56,461.49) --
+	(463.78,461.49);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (463.67,461.30) --
+	(463.67,461.69);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (463.67,458.59) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
 \path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (495.00,489.87) --
@@
 	(495.31,490.16);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (495.31,486.64) {$p$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(505.81,500.24);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (505.81,497.05) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(500.78,501.80);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (500.78,497.71) {$r$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(491.40,486.03);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (491.40,482.88) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(493.11,487.80);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (493.11,483.47) {$l$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(495.24,499.32);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (495.24,496.14) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(506.13,500.66);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (506.13,497.65) {$\kappa$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(463.91,452.29);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (463.91,448.56) {$p$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(495.95,490.18);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (495.95,487.09) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(493.65,492.85);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (493.65,488.76) {$r$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(455.34,445.95);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (455.34,442.52) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(457.52,448.51);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (457.52,443.97) {$l$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(460.19,462.73);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (460.19,459.29) {$\sigma$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(495.93,490.82);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (495.93,487.83) {$\kappa$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(451.21,465.18);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (451.21,461.43) {$p$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(494.23,489.58);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (494.23,486.43) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(486.97,489.55);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (486.97,485.32) {$r$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(446.18,462.22);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (446.18,458.79) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(449.26,464.08);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (449.26,459.51) {$l$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(455.45,470.82);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (455.45,467.41) {$\sigma$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(495.18,490.60);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (495.18,487.45) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (410.72,427.41) --
-	(413.08,427.41);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (411.94,426.32) --
-	(411.94,428.45);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (411.94,424.19) {$p$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (474.42,462.41) --
-	(474.99,462.41);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (474.71,461.74) --
-	(474.71,463.06);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.71,459.50) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (451.45,467.41) --
-	(451.72,467.41);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (451.59,467.24) --
-	(451.59,467.58);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (451.59,463.38) {$r$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (409.10,426.94) --
-	(411.62,426.94);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (410.40,425.89) --
-	(410.40,427.93);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (410.40,424.03) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (410.30,427.14) --
-	(412.58,427.14);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (411.48,426.01) --
-	(411.48,428.20);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (411.48,423.11) {$l$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (409.51,441.14) --
-	(413.11,441.14);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (411.40,439.81) --
-	(411.40,442.38);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (411.40,438.23) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (477.61,473.14) --
-	(477.89,473.14);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (477.75,472.98) --
-	(477.75,473.30);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (477.75,470.24) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (411.55,427.87) --
+	(413.37,427.87);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (412.48,426.98) --
+	(412.48,428.71);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (412.48,424.64) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (474.41,462.71) --
+	(474.90,462.71);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (474.66,462.27) --
+	(474.66,463.13);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (474.66,459.80) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (451.51,467.63) --
+	(451.74,467.63);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (451.63,467.45) --
+	(451.63,467.81);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (451.63,463.60) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (410.31,427.36) --
+	(412.16,427.36);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (411.25,426.45) --
+	(411.25,428.22);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (411.25,424.45) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (411.12,427.67) --
+	(412.92,427.67);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (412.04,426.79) --
+	(412.04,428.52);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (412.04,423.64) {$l$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (411.19,440.73) --
+	(413.66,440.73);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (412.46,439.76) --
+	(412.46,441.65);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (412.46,437.83) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (477.62,473.25) --
+	(477.84,473.25);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (477.73,473.11) --
+	(477.73,473.38);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (477.73,470.34) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(497.06,492.23);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (497.06,488.68) {$p$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(500.53,495.24);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (500.53,492.04) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(510.40,505.21);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (510.40,501.15) {$r$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(489.74,485.50);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (489.74,482.23) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(495.07,490.85);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (495.07,486.50) {$l$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(486.53,483.93);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (486.53,480.62) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(500.76,495.49);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (500.76,492.50) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(449.87,459.79);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (449.87,455.85) {$p$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(505.82,496.03);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (505.82,492.85) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(486.77,496.19);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (486.77,492.05) {$r$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(448.62,458.21);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (448.62,454.64) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(450.34,460.21);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (450.34,455.50) {$l$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(456.25,475.33);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (456.25,471.74) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(504.38,498.73);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (504.38,495.61) {$\kappa$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (467.90,466.02) --
-	(468.90,466.02);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (468.41,465.37) --
-	(468.41,466.64);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.41,462.79) {$p$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (480.58,476.12) --
-	(481.79,476.12);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (481.20,475.44) --
-	(481.20,476.77);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (481.20,473.22) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (483.85,480.75) --
-	(484.01,480.75);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (483.93,480.67) --
-	(483.93,480.84);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.93,476.72) {$r$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (467.69,466.41) --
-	(468.65,466.41);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (468.17,466.01) --
-	(468.17,466.81);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.17,463.51) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (466.71,464.95) --
-	(467.77,464.95);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (467.25,464.33) --
-	(467.25,465.56);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (467.25,460.92) {$l$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (470.77,472.46) --
-	(471.64,472.46);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (471.21,471.96) --
-	(471.21,472.95);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (471.21,469.56) {$\sigma$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (493.45,489.31) --
-	(493.81,489.31);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (493.63,489.19) --
-	(493.63,489.43);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (493.63,486.41) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (467.90,466.23) --
+	(468.90,466.23);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (468.41,465.71) --
+	(468.41,466.73);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.41,463.00) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (480.58,476.59) --
+	(481.79,476.59);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (481.20,476.02) --
+	(481.20,477.15);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (481.20,473.69) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (483.85,480.72) --
+	(484.01,480.72);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (483.93,480.65) --
+	(483.93,480.79);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.93,476.69) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (467.69,466.23) --
+	(468.65,466.23);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (468.17,465.88) --
+	(468.17,466.57);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (468.17,463.32) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (466.71,465.11) --
+	(467.77,465.11);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (467.25,464.61) --
+	(467.25,465.60);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (467.25,461.08) {$l$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (470.77,472.32) --
+	(471.64,472.32);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (471.21,471.83) --
+	(471.21,472.80);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (471.21,469.42) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (493.45,489.32) --
+	(493.81,489.32);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (493.63,489.22) --
+	(493.63,489.42);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (493.63,486.42) {$\kappa$};
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(488.98,486.50);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (488.98,483.05) {$p$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(476.68,473.70);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (476.68,470.25) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(493.28,490.98);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (493.28,486.89) {$r$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(483.41,481.00);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (483.41,477.86) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(488.94,486.26);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (488.94,481.99) {$l$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(481.77,482.20);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (481.77,478.91) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(503.24,499.97);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (169.04,142.37) --
+	(170.93,142.37);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (170.01,141.79) --
+	(170.01,142.94);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (170.01,139.14) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (157.17,153.87) --
+	(158.08,153.87);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (157.63,153.09) --
+	(157.63,154.62);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (157.63,150.97) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (173.71,168.08) --
+	(174.12,168.08);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (173.91,167.87) --
+	(173.91,168.29);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.91,164.05) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (149.35,141.15) --
+	(150.33,141.15);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (149.85,140.60) --
+	(149.85,141.68);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (149.85,138.25) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (149.45,141.48) --
+	(150.42,141.48);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (149.94,140.93) --
+	(149.94,142.01);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (149.94,137.45) {$l$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (168.56,153.84) --
+	(169.78,153.84);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (169.18,153.03) --
+	(169.18,154.62);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.18,150.94) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (177.89,172.41) --
+	(178.20,172.41);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (178.05,172.22) --
+	(178.05,172.61);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (178.05,169.51) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
 \path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (215.71,200.79) --
@@
 	(215.96,201.08);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (215.96,197.56) {$p$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(218.31,211.16);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (218.31,207.97) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(222.11,212.72);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (222.11,208.63) {$r$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(204.71,196.95);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (204.71,193.80) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(207.23,198.72);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (207.23,194.39) {$l$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(217.43,210.24);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (217.43,207.06) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(223.51,211.58);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (223.51,208.57) {$\kappa$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(179.84,163.21);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.84,159.48) {$p$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(208.41,201.10);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (208.41,198.01) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(211.17,203.77);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.17,199.68) {$r$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(164.27,156.87);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (164.27,153.44) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(166.26,159.43);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (166.26,154.89) {$l$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(177.29,173.65);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.29,170.21) {$\sigma$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(212.06,201.74);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.06,198.75) {$\kappa$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(188.00,176.10);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.00,172.35) {$p$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(204.74,200.50);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (204.74,197.35) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(205.92,200.47);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (205.92,196.24) {$r$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(180.99,173.14);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (180.99,169.71) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(182.05,175.00);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.05,170.43) {$l$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(184.96,181.74);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.96,178.33) {$\sigma$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(211.72,201.52);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.72,198.37) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (181.10,138.33) --
-	(182.11,138.33);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (181.61,137.24) --
-	(181.61,139.37);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.61,135.11) {$p$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (179.53,173.33) --
-	(180.10,173.33);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (179.82,172.66) --
-	(179.82,173.98);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.82,170.42) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (186.37,178.33) --
-	(186.61,178.33);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (186.49,178.16) --
-	(186.49,178.50);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (186.49,174.30) {$r$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (152.97,137.86) --
-	(154.18,137.86);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (153.59,136.81) --
-	(153.59,138.85);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (153.59,134.95) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (152.81,138.06) --
-	(154.10,138.06);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (153.47,136.93) --
-	(153.47,139.12);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (153.47,134.03) {$l$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (168.90,152.06) --
-	(170.43,152.06);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (169.68,150.73) --
-	(169.68,153.30);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.68,149.15) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (193.75,184.06) --
-	(193.91,184.06);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (193.83,183.90) --
-	(193.83,184.22);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.83,181.16) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (181.04,138.79) --
+	(181.97,138.79);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (181.51,137.90) --
+	(181.51,139.63);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.51,135.56) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (179.42,173.63) --
+	(179.98,173.63);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (179.70,173.19) --
+	(179.70,174.05);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.70,170.72) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (186.39,178.55) --
+	(186.60,178.55);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (186.50,178.37) --
+	(186.50,178.73);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (186.50,174.52) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (152.77,138.28) --
+	(153.93,138.28);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (153.36,137.37) --
+	(153.36,139.14);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (153.36,135.37) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (152.62,138.59) --
+	(153.85,138.59);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (153.25,137.71) --
+	(153.25,139.44);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (153.25,134.56) {$l$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (168.56,151.65) --
+	(170.05,151.65);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (169.32,150.68) --
+	(169.32,152.57);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (169.32,148.75) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (193.80,184.17) --
+	(193.95,184.17);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (193.88,184.03) --
+	(193.88,184.30);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.88,181.26) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(198.53,203.15);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.53,199.60) {$p$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(215.00,206.16);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (215.00,202.96) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(227.14,216.13);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (227.14,212.07) {$r$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(208.59,196.42);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (208.59,193.15) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(213.86,201.77);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (213.86,197.42) {$l$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(202.16,194.85);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (202.16,191.54) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(218.62,206.41);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (218.62,203.42) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(210.63,170.71);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.63,166.77) {$p$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(209.87,206.95);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (209.87,203.77) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(214.59,207.11);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (214.59,202.97) {$r$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(182.02,169.13);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.02,165.56) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(182.45,171.13);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (182.45,166.42) {$l$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(194.50,186.25);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.50,182.66) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(223.51,209.65);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (223.51,206.53) {$\kappa$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (191.51,176.94) --
-	(192.36,176.94);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (191.94,176.29) --
-	(191.94,177.56);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.94,173.71) {$p$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (192.19,187.04) --
-	(195.37,187.04);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (193.85,186.36) --
-	(193.85,187.69);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.85,184.14) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (199.84,191.67) --
-	(200.03,191.67);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (199.93,191.59) --
-	(199.93,191.76);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.93,187.64) {$r$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (184.16,177.33) --
-	(184.81,177.33);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (184.49,176.93) --
-	(184.49,177.73);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.49,174.43) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (183.57,175.87) --
-	(184.20,175.87);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (183.89,175.25) --
-	(183.89,176.48);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.89,171.84) {$l$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (191.51,183.38) --
-	(192.28,183.38);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (191.90,182.88) --
-	(191.90,183.87);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.90,180.48) {$\sigma$};
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (212.14,200.23) --
-	(212.37,200.23);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (212.25,200.11) --
-	(212.25,200.35);
-\definecolor{drawColor}{RGB}{151,0,255}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.25,197.33) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (191.51,177.15) --
+	(192.36,177.15);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (191.94,176.63) --
+	(191.94,177.65);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.94,173.92) {$p$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (192.19,187.51) --
+	(195.37,187.51);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (193.85,186.94) --
+	(193.85,188.07);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.85,184.61) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (199.84,191.64) --
+	(200.03,191.64);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (199.93,191.57) --
+	(199.93,191.71);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.93,187.61) {$r$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (184.16,177.15) --
+	(184.81,177.15);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (184.49,176.80) --
+	(184.49,177.49);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (184.49,174.24) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (183.57,176.03) --
+	(184.20,176.03);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (183.89,175.53) --
+	(183.89,176.52);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (183.89,172.00) {$l$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (191.51,183.24) --
+	(192.28,183.24);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (191.90,182.75) --
+	(191.90,183.72);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.90,180.34) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (212.14,200.24) --
+	(212.37,200.24);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (212.25,200.14) --
+	(212.25,200.34);
+\definecolor{drawColor}{RGB}{255,0,255}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.25,197.34) {$\kappa$};
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(198.78,197.42);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.78,193.97) {$p$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(194.92,184.62);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.92,181.17) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(211.83,201.90);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.83,197.81) {$r$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(201.08,191.92);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (201.08,188.78) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(206.71,197.18);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (206.71,192.91) {$l$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(200.92,193.12);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (200.92,189.83) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(223.09,210.89);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (356.88,127.23) --
-	(356.88, 94.67);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (358.78,108.88) {$1.7\times $};
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (485.73, 60.10) --
+	(485.73, 49.99);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (487.62, 52.97) {$55\times $};
 \definecolor{fillColor}{RGB}{255,0,109}
 
-\path[fill=fillColor] (356.88,127.23) circle (  1.87);
-
-\path[fill=fillColor] (356.88, 97.58) --
-	(359.40, 93.22) --
-	(354.37, 93.22) --
+\path[fill=fillColor] (485.73, 60.10) circle (  1.87);
+
+\path[fill=fillColor] (485.73, 52.89) --
+	(488.24, 48.54) --
+	(483.21, 48.54) --
 	cycle;
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (394.78, 93.40) --
-	(394.78, 80.86);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (396.67, 85.06) {$1.4\times $};
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (356.88,178.85) --
+	(356.88,124.59);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (358.78,149.64) {$1.7\times $};
 \definecolor{fillColor}{RGB}{253,104,0}
 
-\path[fill=fillColor] (394.78, 93.40) circle (  1.87);
-
-\path[fill=fillColor] (394.78, 83.77) --
-	(397.29, 79.41) --
-	(392.26, 79.41) --
+\path[fill=fillColor] (356.88,178.85) circle (  1.87);
+
+\path[fill=fillColor] (356.88,127.49) --
+	(359.40,123.13) --
+	(354.37,123.13) --
 	cycle;
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (390.04, 82.94) --
-	(390.04, 71.70);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (391.93, 75.24) {$1.5\times $};
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (394.78,122.47) --
+	(394.78,101.57);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (396.67,109.95) {$1.4\times $};
 \definecolor{fillColor}{RGB}{143,161,0}
 
-\path[fill=fillColor] (390.04, 82.94) circle (  1.87);
-
-\path[fill=fillColor] (390.04, 74.60) --
-	(392.55, 70.24) --
-	(387.52, 70.24) --
+\path[fill=fillColor] (394.78,122.47) circle (  1.87);
+
+\path[fill=fillColor] (394.78,104.48) --
+	(397.29,100.12) --
+	(392.26,100.12) --
 	cycle;
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (404.25, 61.80) --
-	(404.25, 53.19);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (406.15, 55.42) {$3.5\times $};
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (390.04,105.03) --
+	(390.04, 86.29);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (391.93, 93.59) {$1.5\times $};
 \definecolor{fillColor}{RGB}{0,195,0}
 
-\path[fill=fillColor] (404.25, 61.80) circle (  1.87);
-
-\path[fill=fillColor] (404.25, 56.09) --
-	(406.77, 51.74) --
-	(401.74, 51.74) --
+\path[fill=fillColor] (390.04,105.03) circle (  1.87);
+
+\path[fill=fillColor] (390.04, 89.20) --
+	(392.55, 84.84) --
+	(387.52, 84.84) --
 	cycle;
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (359.72,150.32) --
-	(359.72,123.79);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (361.62,134.98) {$1.4\times $};
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (404.25, 69.81) --
+	(404.25, 55.47);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (406.15, 60.57) {$3.5\times $};
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[fill=fillColor] (359.72,150.32) circle (  1.87);
-
-\path[fill=fillColor] (359.72,126.70) --
-	(362.24,122.34) --
-	(357.21,122.34) --
+\path[fill=fillColor] (404.25, 69.81) circle (  1.87);
+
+\path[fill=fillColor] (404.25, 58.37) --
+	(406.77, 54.02) --
+	(401.74, 54.02) --
 	cycle;
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (433.62,101.96) --
-	(433.62, 71.34);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (435.51, 84.58) {$2.4\times $};
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (359.72,217.34) --
+	(359.72,173.12);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (361.62,193.15) {$1.4\times $};
 \definecolor{fillColor}{RGB}{0,216,255}
 
-\path[fill=fillColor] (433.62,101.96) circle (  1.87);
-
-\path[fill=fillColor] (433.62, 74.24) --
-	(436.14, 69.88) --
-	(431.10, 69.88) --
+\path[fill=fillColor] (359.72,217.34) circle (  1.87);
+
+\path[fill=fillColor] (359.72,176.03) --
+	(362.24,171.67) --
+	(357.21,171.67) --
 	cycle;
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (359.72, 74.13) --
-	(359.72, 68.32);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (361.62, 69.15) {$1.3\times $};
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (433.62,136.74) --
+	(433.62, 85.69);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (435.51,109.14) {$2.4\times $};
 \definecolor{fillColor}{RGB}{151,0,255}
 
-\path[fill=fillColor] (359.72, 74.13) circle (  1.87);
-
-\path[fill=fillColor] (359.72, 71.22) --
-	(362.24, 66.86) --
-	(357.21, 66.86) --
+\path[fill=fillColor] (433.62,136.74) circle (  1.87);
+
+\path[fill=fillColor] (433.62, 88.60) --
+	(436.14, 84.24) --
+	(431.10, 84.24) --
 	cycle;
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (346.46, 95.05) --
-	(346.46, 80.15);
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (348.35, 85.52) {$1.5\times $};
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (359.72, 90.35) --
+	(359.72, 80.66);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (361.62, 83.43) {$1.3\times $};
 \definecolor{fillColor}{RGB}{255,0,255}
 
-\path[fill=fillColor] (346.46, 95.05) circle (  1.87);
-
-\path[fill=fillColor] (346.46, 83.05) --
-	(348.97, 78.70) --
-	(343.94, 78.70) --
+\path[fill=fillColor] (359.72, 90.35) circle (  1.87);
+
+\path[fill=fillColor] (359.72, 83.56) --
+	(362.24, 79.21) --
+	(357.21, 79.21) --
+	cycle;
+
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] (346.46,125.22) --
+	(346.46,100.38);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (348.35,110.72) {$1.5\times $};
+\definecolor{fillColor}{RGB}{68,68,68}
+
+\path[fill=fillColor] (346.46,125.22) circle (  1.87);
+
+\path[fill=fillColor] (346.46,103.28) --
+	(348.97, 98.93) --
+	(343.94, 98.93) --
 	cycle;
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 97.17) -- (333.90, 97.17);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88, 81.38) -- (333.90, 81.38);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,112.96) -- (333.90,112.96);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,191.91) -- (333.90,191.91);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,176.12) -- (333.90,176.12);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (338.88,207.70) -- (333.90,207.70);
 
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92, 94.31) {5000};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,141.68) {10000};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,189.05) {15000};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,236.42) {20000};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92, 78.52) {2000};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,110.10) {4000};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,141.68) {6000};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,173.26) {8000};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,204.84) {10000};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.83] at (328.92,236.42) {12000};
 \end{scope}

### 2020-09-01 benchmarking/benchmarkingVM/ESS_round3.tex
complete draft

@@
-% Created by tikzDevice version 0.12.3.1 on 2020-08-31 17:26:53
+% Created by tikzDevice version 0.12.3.1 on 2020-09-01 15:30:15
 % !TEX encoding = UTF-8 Unicode
@@
 \path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] ( 48.00,173.19) --
-	(474.88,173.19);
+	(476.29,173.19);
 \definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.10,246.09) --
-	( 54.10,233.67);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 53.56,210.61) --
+	( 53.56,170.08);
 \definecolor{fillColor}{RGB}{255,0,109}
 
-\path[fill=fillColor] ( 54.10,239.88) circle (  2.25);
+\path[fill=fillColor] ( 53.56,190.34) circle (  2.25);
 \definecolor{drawColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.20,249.96) --
-	( 60.20,218.26);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 59.12,246.09) --
+	( 59.12,233.67);
 \definecolor{fillColor}{RGB}{253,104,0}
 
-\path[fill=fillColor] ( 60.20,234.11) circle (  2.25);
+\path[fill=fillColor] ( 59.12,239.88) circle (  2.25);
 \definecolor{drawColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.29,226.82) --
-	( 66.29,207.10);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 64.69,249.96) --
+	( 64.69,218.26);
 \definecolor{fillColor}{RGB}{143,161,0}
 
-\path[fill=fillColor] ( 66.29,216.96) circle (  2.25);
+\path[fill=fillColor] ( 64.69,234.11) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 72.39,210.32) --
-	( 72.39,191.80);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 70.25,226.82) --
+	( 70.25,207.10);
 \definecolor{fillColor}{RGB}{0,195,0}
 
-\path[fill=fillColor] ( 72.39,201.06) circle (  2.25);
+\path[fill=fillColor] ( 70.25,216.96) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 78.49,205.70) --
-	( 78.49,138.28);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.81,209.65) --
+	( 75.81,192.67);
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[fill=fillColor] ( 78.49,171.99) circle (  2.25);
+\path[fill=fillColor] ( 75.81,201.16) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 84.59,250.06) --
-	( 84.59,239.46);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 81.37,205.70) --
+	( 81.37,138.28);
 \definecolor{fillColor}{RGB}{0,216,255}
 
-\path[fill=fillColor] ( 84.59,244.76) circle (  2.25);
+\path[fill=fillColor] ( 81.37,171.99) circle (  2.25);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 90.69,223.96) --
-	( 90.69,209.76);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 86.94,250.06) --
+	( 86.94,239.46);
 \definecolor{fillColor}{RGB}{151,0,255}
 
-\path[fill=fillColor] ( 90.69,216.86) circle (  2.25);
+\path[fill=fillColor] ( 86.94,244.76) circle (  2.25);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 96.79,229.79) --
-	( 96.79,207.30);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.50,223.96) --
+	( 92.50,209.76);
 \definecolor{fillColor}{RGB}{255,0,255}
 
-\path[fill=fillColor] ( 96.79,218.55) circle (  2.25);
+\path[fill=fillColor] ( 92.50,216.86) circle (  2.25);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 98.06,229.79) --
+	( 98.06,207.30);
+\definecolor{fillColor}{RGB}{68,68,68}
+
+\path[fill=fillColor] ( 98.06,218.55) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] ( 54.10,218.87) --
-	(102.88,218.87);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] ( 53.56,215.85) --
+	(103.62,215.85);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 78.49,284.14) {18\% faster};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 78.59,284.14) {17\% faster};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (108.98,  0.00) --
-	(108.98,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (109.18,  0.00) --
+	(109.18,357.33);
 \definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (115.08,231.18) --
-	(115.08,216.59);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (114.75,234.94) --
+	(114.75,216.63);
 \definecolor{fillColor}{RGB}{255,0,109}
 
-\path[fill=fillColor] (115.08,223.89) circle (  2.25);
+\path[fill=fillColor] (114.75,225.78) circle (  2.25);
 \definecolor{drawColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.18,210.48) --
-	(121.18,196.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.31,231.18) --
+	(120.31,216.59);
 \definecolor{fillColor}{RGB}{253,104,0}
 
-\path[fill=fillColor] (121.18,203.24) circle (  2.25);
+\path[fill=fillColor] (120.31,223.89) circle (  2.25);
 \definecolor{drawColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (127.28,217.85) --
-	(127.28,208.48);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (125.87,210.48) --
+	(125.87,196.00);
 \definecolor{fillColor}{RGB}{143,161,0}
 
-\path[fill=fillColor] (127.28,213.17) circle (  2.25);
+\path[fill=fillColor] (125.87,203.24) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (133.38,206.09) --
-	(133.38,189.08);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (131.43,217.85) --
+	(131.43,208.48);
 \definecolor{fillColor}{RGB}{0,195,0}
 
-\path[fill=fillColor] (133.38,197.58) circle (  2.25);
+\path[fill=fillColor] (131.43,213.17) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (139.47,184.21) --
-	(139.47,163.53);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (137.00,207.88) --
+	(137.00,192.85);
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[fill=fillColor] (139.47,173.87) circle (  2.25);
+\path[fill=fillColor] (137.00,200.36) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.57,274.87) --
-	(145.57,264.59);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (142.56,184.21) --
+	(142.56,163.53);
 \definecolor{fillColor}{RGB}{0,216,255}
 
-\path[fill=fillColor] (145.57,269.73) circle (  2.25);
+\path[fill=fillColor] (142.56,173.87) circle (  2.25);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.67,345.05) --
-	(151.67,220.65);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.12,274.87) --
+	(148.12,264.59);
 \definecolor{fillColor}{RGB}{151,0,255}
 
-\path[fill=fillColor] (151.67,282.85) circle (  2.25);
+\path[fill=fillColor] (148.12,269.73) circle (  2.25);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (157.77,222.89) --
-	(157.77,199.51);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.68,345.05) --
+	(153.68,220.65);
 \definecolor{fillColor}{RGB}{255,0,255}
 
-\path[fill=fillColor] (157.77,211.20) circle (  2.25);
+\path[fill=fillColor] (153.68,282.85) circle (  2.25);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.24,222.89) --
+	(159.24,199.51);
+\definecolor{fillColor}{RGB}{68,68,68}
+
+\path[fill=fillColor] (159.24,211.20) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (115.08,224.11) --
-	(163.87,224.11);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (114.75,224.57) --
+	(164.81,224.57);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (139.47,284.14) {20\% faster};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (139.78,284.14) {20\% faster};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (169.97,  0.00) --
-	(169.97,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (170.37,  0.00) --
+	(170.37,357.33);
 \definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.06,237.79) --
-	(176.06,235.79);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.93,201.00) --
+	(175.93,192.97);
 \definecolor{fillColor}{RGB}{255,0,109}
 
-\path[fill=fillColor] (176.06,236.79) circle (  2.25);
+\path[fill=fillColor] (175.93,196.98) circle (  2.25);
 \definecolor{drawColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.16,213.87) --
-	(182.16,210.98);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.49,237.79) --
+	(181.49,235.79);
 \definecolor{fillColor}{RGB}{253,104,0}
 
-\path[fill=fillColor] (182.16,212.42) circle (  2.25);
+\path[fill=fillColor] (181.49,236.79) circle (  2.25);
 \definecolor{drawColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.26,213.40) --
-	(188.26,210.38);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.05,213.87) --
+	(187.05,210.98);
 \definecolor{fillColor}{RGB}{143,161,0}
 
-\path[fill=fillColor] (188.26,211.89) circle (  2.25);
+\path[fill=fillColor] (187.05,212.42) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.36,192.72) --
-	(194.36,185.58);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.62,213.40) --
+	(192.62,210.38);
 \definecolor{fillColor}{RGB}{0,195,0}
 
-\path[fill=fillColor] (194.36,189.15) circle (  2.25);
+\path[fill=fillColor] (192.62,211.89) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.46,187.16) --
-	(200.46,185.57);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.18,192.27) --
+	(198.18,187.06);
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[fill=fillColor] (200.46,186.36) circle (  2.25);
+\path[fill=fillColor] (198.18,189.67) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.56,240.68) --
-	(206.56,238.19);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.74,187.16) --
+	(203.74,185.57);
 \definecolor{fillColor}{RGB}{0,216,255}
 
-\path[fill=fillColor] (206.56,239.44) circle (  2.25);
+\path[fill=fillColor] (203.74,186.36) circle (  2.25);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.65,223.05) --
-	(212.65,219.07);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.30,240.68) --
+	(209.30,238.19);
 \definecolor{fillColor}{RGB}{151,0,255}
 
-\path[fill=fillColor] (212.65,221.06) circle (  2.25);
+\path[fill=fillColor] (209.30,239.44) circle (  2.25);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.75,215.97) --
-	(218.75,213.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (214.87,223.05) --
+	(214.87,219.07);
 \definecolor{fillColor}{RGB}{255,0,255}
 
-\path[fill=fillColor] (218.75,214.91) circle (  2.25);
+\path[fill=fillColor] (214.87,221.06) circle (  2.25);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.43,215.97) --
+	(220.43,213.85);
+\definecolor{fillColor}{RGB}{68,68,68}
+
+\path[fill=fillColor] (220.43,214.91) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (176.06,214.59) --
-	(224.85,214.59);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (175.93,212.74) --
+	(225.99,212.74);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (200.46,284.14) {16\% faster};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (200.96,284.14) {15\% faster};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (230.95,  0.00) --
-	(230.95,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (231.55,  0.00) --
+	(231.55,357.33);
 \definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.05,250.44) --
-	(237.05,241.85);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.11,198.51) --
+	(237.11,180.05);
 \definecolor{fillColor}{RGB}{255,0,109}
 
-\path[fill=fillColor] (237.05,246.14) circle (  2.25);
+\path[fill=fillColor] (237.11,189.28) circle (  2.25);
 \definecolor{drawColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (243.15,239.13) --
-	(243.15,208.60);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (242.68,250.44) --
+	(242.68,241.85);
 \definecolor{fillColor}{RGB}{253,104,0}
 
-\path[fill=fillColor] (243.15,223.86) circle (  2.25);
+\path[fill=fillColor] (242.68,246.14) circle (  2.25);
 \definecolor{drawColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (249.24,213.14) --
-	(249.24,198.87);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (248.24,239.13) --
+	(248.24,208.60);
 \definecolor{fillColor}{RGB}{143,161,0}
 
-\path[fill=fillColor] (249.24,206.01) circle (  2.25);
+\path[fill=fillColor] (248.24,223.86) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (255.34,219.07) --
-	(255.34,189.90);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (253.80,213.14) --
+	(253.80,198.87);
 \definecolor{fillColor}{RGB}{0,195,0}
 
-\path[fill=fillColor] (255.34,204.48) circle (  2.25);
+\path[fill=fillColor] (253.80,206.01) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44,175.34) --
-	(261.44,160.05);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (259.36,215.64) --
+	(259.36,185.82);
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[fill=fillColor] (261.44,167.69) circle (  2.25);
+\path[fill=fillColor] (259.36,200.73) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (267.54,231.48) --
-	(267.54,205.22);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.93,175.34) --
+	(264.93,160.05);
 \definecolor{fillColor}{RGB}{0,216,255}
 
-\path[fill=fillColor] (267.54,218.35) circle (  2.25);
+\path[fill=fillColor] (264.93,167.69) circle (  2.25);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (273.64,253.96) --
-	(273.64,239.75);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (270.49,231.48) --
+	(270.49,205.22);
 \definecolor{fillColor}{RGB}{151,0,255}
 
-\path[fill=fillColor] (273.64,246.86) circle (  2.25);
+\path[fill=fillColor] (270.49,218.35) circle (  2.25);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (279.74,236.72) --
-	(279.74,225.81);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (276.05,253.96) --
+	(276.05,239.75);
 \definecolor{fillColor}{RGB}{255,0,255}
 
-\path[fill=fillColor] (279.74,231.26) circle (  2.25);
+\path[fill=fillColor] (276.05,246.86) circle (  2.25);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (281.61,236.72) --
+	(281.61,225.81);
+\definecolor{fillColor}{RGB}{68,68,68}
+
+\path[fill=fillColor] (281.61,231.26) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (237.05,219.11) --
-	(285.83,219.11);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (237.11,215.55) --
+	(287.17,215.55);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (261.44,284.14) {18\% faster};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (262.14,284.14) {16\% faster};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (291.93,  0.00) --
-	(291.93,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (292.74,  0.00) --
+	(292.74,357.33);
 \definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.03,240.03) --
-	(298.03,230.01);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.30,199.13) --
+	(298.30,180.61);
 \definecolor{fillColor}{RGB}{255,0,109}
 
-\path[fill=fillColor] (298.03,235.02) circle (  2.25);
+\path[fill=fillColor] (298.30,189.87) circle (  2.25);
 \definecolor{drawColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (304.13,238.59) --
-	(304.13,208.20);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (303.86,240.03) --
+	(303.86,230.01);
 \definecolor{fillColor}{RGB}{253,104,0}
 
-\path[fill=fillColor] (304.13,223.39) circle (  2.25);
+\path[fill=fillColor] (303.86,235.02) circle (  2.25);
 \definecolor{drawColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (310.23,210.81) --
-	(310.23,195.70);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (309.42,238.59) --
+	(309.42,208.20);
 \definecolor{fillColor}{RGB}{143,161,0}
 
-\path[fill=fillColor] (310.23,203.25) circle (  2.25);
+\path[fill=fillColor] (309.42,223.39) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (316.33,228.88) --
-	(316.33,202.54);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (314.99,210.81) --
+	(314.99,195.70);
 \definecolor{fillColor}{RGB}{0,195,0}
 
-\path[fill=fillColor] (316.33,215.71) circle (  2.25);
+\path[fill=fillColor] (314.99,203.25) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (322.42,175.84) --
-	(322.42,163.67);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (320.55,225.30) --
+	(320.55,196.46);
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[fill=fillColor] (322.42,169.76) circle (  2.25);
+\path[fill=fillColor] (320.55,210.88) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (328.52,230.74) --
-	(328.52,204.43);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (326.11,175.84) --
+	(326.11,163.67);
 \definecolor{fillColor}{RGB}{0,216,255}
 
-\path[fill=fillColor] (328.52,217.58) circle (  2.25);
+\path[fill=fillColor] (326.11,169.76) circle (  2.25);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (334.62,232.28) --
-	(334.62,208.40);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (331.67,230.74) --
+	(331.67,204.43);
 \definecolor{fillColor}{RGB}{151,0,255}
 
-\path[fill=fillColor] (334.62,220.34) circle (  2.25);
+\path[fill=fillColor] (331.67,217.58) circle (  2.25);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (340.72,233.20) --
-	(340.72,221.37);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (337.23,232.28) --
+	(337.23,208.40);
 \definecolor{fillColor}{RGB}{255,0,255}
 
-\path[fill=fillColor] (340.72,227.29) circle (  2.25);
+\path[fill=fillColor] (337.23,220.34) circle (  2.25);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (342.80,233.20) --
+	(342.80,221.37);
+\definecolor{fillColor}{RGB}{68,68,68}
+
+\path[fill=fillColor] (342.80,227.29) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (298.03,214.66) --
-	(346.82,214.66);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (298.30,211.47) --
+	(348.36,211.47);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (322.42,284.14) {16\% faster};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (323.33,284.14) {15\% faster};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (352.92,  0.00) --
-	(352.92,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (353.92,  0.00) --
+	(353.92,357.33);
 \definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (359.01,237.99) --
-	(359.01,223.51);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (359.48,201.98) --
+	(359.48,175.41);
 \definecolor{fillColor}{RGB}{255,0,109}
 
-\path[fill=fillColor] (359.01,230.75) circle (  2.25);
+\path[fill=fillColor] (359.48,188.70) circle (  2.25);
 \definecolor{drawColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (365.11,244.31) --
-	(365.11,211.56);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (365.05,237.99) --
+	(365.05,223.51);
 \definecolor{fillColor}{RGB}{253,104,0}
 
-\path[fill=fillColor] (365.11,227.93) circle (  2.25);
+\path[fill=fillColor] (365.05,230.75) circle (  2.25);
 \definecolor{drawColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (371.21,216.84) --
-	(371.21,196.62);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (370.61,244.31) --
+	(370.61,211.56);
 \definecolor{fillColor}{RGB}{143,161,0}
 
-\path[fill=fillColor] (371.21,206.73) circle (  2.25);
+\path[fill=fillColor] (370.61,227.93) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (377.31,225.85) --
-	(377.31,198.06);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (376.17,216.84) --
+	(376.17,196.62);
 \definecolor{fillColor}{RGB}{0,195,0}
 
-\path[fill=fillColor] (377.31,211.95) circle (  2.25);
+\path[fill=fillColor] (376.17,206.73) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (383.41,197.62) --
-	(383.41,172.56);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (381.73,223.80) --
+	(381.73,193.65);
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[fill=fillColor] (383.41,185.09) circle (  2.25);
+\path[fill=fillColor] (381.73,208.73) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.51,237.58) --
-	(389.51,211.29);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (387.29,197.62) --
+	(387.29,172.56);
 \definecolor{fillColor}{RGB}{0,216,255}
 
-\path[fill=fillColor] (389.51,224.44) circle (  2.25);
+\path[fill=fillColor] (387.29,185.09) circle (  2.25);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (395.60,213.92) --
-	(395.60,200.71);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (392.86,237.58) --
+	(392.86,211.29);
 \definecolor{fillColor}{RGB}{151,0,255}
 
-\path[fill=fillColor] (395.60,207.32) circle (  2.25);
+\path[fill=fillColor] (392.86,224.44) circle (  2.25);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (401.70,230.89) --
-	(401.70,207.97);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (398.42,213.92) --
+	(398.42,200.71);
 \definecolor{fillColor}{RGB}{255,0,255}
 
-\path[fill=fillColor] (401.70,219.43) circle (  2.25);
+\path[fill=fillColor] (398.42,207.32) circle (  2.25);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (403.98,230.89) --
+	(403.98,207.97);
+\definecolor{fillColor}{RGB}{68,68,68}
+
+\path[fill=fillColor] (403.98,219.43) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (359.01,214.55) --
-	(407.80,214.55);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (359.48,211.43) --
+	(409.54,211.43);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (383.41,284.14) {16\% faster};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (384.51,284.14) {15\% faster};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (413.90,  0.00) --
-	(413.90,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (415.11,  0.00) --
+	(415.11,357.33);
 \definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.00,182.77) --
-	(420.00,177.72);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.67,179.14) --
+	(420.67,173.06);
 \definecolor{fillColor}{RGB}{255,0,109}
 
-\path[fill=fillColor] (420.00,180.25) circle (  2.25);
+\path[fill=fillColor] (420.67,176.10) circle (  2.25);
 \definecolor{drawColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.10,177.03) --
-	(426.10,173.95);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.23,182.77) --
+	(426.23,177.72);
 \definecolor{fillColor}{RGB}{253,104,0}
 
-\path[fill=fillColor] (426.10,175.49) circle (  2.25);
+\path[fill=fillColor] (426.23,180.25) circle (  2.25);
 \definecolor{drawColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (432.19,175.37) --
-	(432.19,171.54);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (431.79,177.03) --
+	(431.79,173.95);
 \definecolor{fillColor}{RGB}{143,161,0}
 
-\path[fill=fillColor] (432.19,173.45) circle (  2.25);
+\path[fill=fillColor] (431.79,175.49) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.29,175.65) --
-	(438.29,172.26);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (437.35,175.37) --
+	(437.35,171.54);
 \definecolor{fillColor}{RGB}{0,195,0}
 
-\path[fill=fillColor] (438.29,173.95) circle (  2.25);
+\path[fill=fillColor] (437.35,173.45) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (444.39,182.05) --
-	(444.39,177.75);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (442.92,175.20) --
+	(442.92,172.49);
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[fill=fillColor] (444.39,179.90) circle (  2.25);
+\path[fill=fillColor] (442.92,173.84) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (450.49,176.59) --
-	(450.49,169.19);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (448.48,182.05) --
+	(448.48,177.75);
 \definecolor{fillColor}{RGB}{0,216,255}
 
-\path[fill=fillColor] (450.49,172.89) circle (  2.25);
+\path[fill=fillColor] (448.48,179.90) circle (  2.25);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (456.59,177.97) --
-	(456.59,173.15);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.04,176.59) --
+	(454.04,169.19);
 \definecolor{fillColor}{RGB}{151,0,255}
 
-\path[fill=fillColor] (456.59,175.56) circle (  2.25);
+\path[fill=fillColor] (454.04,172.89) circle (  2.25);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.69,183.83) --
-	(462.69,176.41);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (459.60,177.97) --
+	(459.60,173.15);
 \definecolor{fillColor}{RGB}{255,0,255}
 
-\path[fill=fillColor] (462.69,180.12) circle (  2.25);
+\path[fill=fillColor] (459.60,175.56) circle (  2.25);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (465.16,183.83) --
+	(465.16,176.41);
+\definecolor{fillColor}{RGB}{68,68,68}
+
+\path[fill=fillColor] (465.16,180.12) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (420.00,176.47) --
-	(468.78,176.47);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (420.67,176.41) --
+	(470.73,176.41);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (444.39,284.14) {1.2\% faster};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (445.70,284.14) {1.2\% faster};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (474.88,  0.00) --
-	(474.88,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (476.29,  0.00) --
+	(476.29,357.33);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 78.49, 60.00) -- ( 78.49, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 78.59, 60.00) -- ( 78.59, 54.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (139.47, 60.00) -- (139.47, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (139.78, 60.00) -- (139.78, 54.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.46, 60.00) -- (200.46, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.96, 60.00) -- (200.96, 54.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44, 60.00) -- (261.44, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (262.14, 60.00) -- (262.14, 54.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (322.42, 60.00) -- (322.42, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (323.33, 60.00) -- (323.33, 54.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (383.41, 60.00) -- (383.41, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (384.51, 60.00) -- (384.51, 54.00);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (444.39, 60.00) -- (444.39, 54.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (445.70, 60.00) -- (445.70, 54.00);
 
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at ( 80.56, 48.00) {Prior};
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at ( 80.66, 48.00) {Prior};
 
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (141.54, 48.00) {Likelihood};
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (141.84, 48.00) {Likelihood};
 
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (202.52, 48.00) {Leaf rate};
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (203.03, 48.00) {Leaf rate};
 
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (263.51, 48.00) {Mean branch rate};
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (264.21, 48.00) {Mean branch rate};
 
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (324.49, 48.00) {Tree length};
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (325.39, 48.00) {Tree length};
 
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (385.47, 48.00) {Clock SD $\sigma$};
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (386.58, 48.00) {Clock SD $\sigma$};
 
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (446.46, 48.00) {HKY model $\kappa$};
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (447.76, 48.00) {HKY model $\kappa$};
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.19,235.67) rectangle (494.39,229.67);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.19,241.67) rectangle (494.39,235.67);
 \definecolor{fillColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.19,223.67) rectangle (494.39,217.67);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.19,229.67) rectangle (494.39,223.67);
 \definecolor{fillColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.19,211.67) rectangle (494.39,205.67);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.19,217.67) rectangle (494.39,211.67);
 \definecolor{fillColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.19,199.67) rectangle (494.39,193.67);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.19,205.67) rectangle (494.39,199.67);
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.19,187.67) rectangle (494.39,181.67);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.19,193.67) rectangle (494.39,187.67);
 \definecolor{fillColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.19,175.67) rectangle (494.39,169.67);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.19,181.67) rectangle (494.39,175.67);
 \definecolor{fillColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.19,163.67) rectangle (494.39,157.67);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.19,169.67) rectangle (494.39,163.67);
 \definecolor{fillColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.19,151.67) rectangle (494.39,145.67);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.19,157.67) rectangle (494.39,151.67);
+\definecolor{fillColor}{RGB}{68,68,68}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (503.39,229.22) {Cognato};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.19,145.67) rectangle (494.39,139.67);
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (503.39,217.22) {Dornburg};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (503.39,235.22) {Ran};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (503.39,205.22) {Sauquet};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (503.39,223.22) {Cognato};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (503.39,193.22) {Broughton};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (503.39,211.22) {Dornburg};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (503.39,181.22) {Kawahara};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (503.39,199.22) {Sauquet};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (503.39,169.22) {simulated};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (503.39,187.22) {Broughton};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (503.39,157.22) {Rightmyer};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (503.39,175.22) {Kawahara};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (503.39,145.22) {Moyle};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (503.39,163.22) {simulated};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (503.39,151.22) {Rightmyer};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (503.39,139.22) {Moyle};
 \end{scope}

### 2020-09-01 benchmarking/benchmarkingVM/ESS_round4b.tex
complete draft

@@
-% Created by tikzDevice version 0.12.3.1 on 2020-08-31 17:27:18
+% Created by tikzDevice version 0.12.3.1 on 2020-09-01 15:30:41
 % !TEX encoding = UTF-8 Unicode
@@
 \path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] ( 48.00,173.19) --
-	(474.88,173.19);
+	(476.29,173.19);
 \definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.10,186.05) --
-	( 54.10,174.62);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 53.56,175.23) --
+	( 53.56,146.36);
 \definecolor{fillColor}{RGB}{255,0,109}
 
-\path[fill=fillColor] ( 54.10,180.33) circle (  2.25);
+\path[fill=fillColor] ( 53.56,160.80) circle (  2.25);
 \definecolor{drawColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.20,164.25) --
-	( 60.20,141.62);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 59.12,186.05) --
+	( 59.12,174.62);
 \definecolor{fillColor}{RGB}{253,104,0}
 
-\path[fill=fillColor] ( 60.20,152.94) circle (  2.25);
+\path[fill=fillColor] ( 59.12,180.33) circle (  2.25);
 \definecolor{drawColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.29,167.28) --
-	( 66.29,150.64);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 64.69,164.25) --
+	( 64.69,141.62);
 \definecolor{fillColor}{RGB}{143,161,0}
 
-\path[fill=fillColor] ( 66.29,158.96) circle (  2.25);
+\path[fill=fillColor] ( 64.69,152.94) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 72.39,166.76) --
-	( 72.39,144.26);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 70.25,167.28) --
+	( 70.25,150.64);
 \definecolor{fillColor}{RGB}{0,195,0}
 
-\path[fill=fillColor] ( 72.39,155.51) circle (  2.25);
+\path[fill=fillColor] ( 70.25,158.96) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 78.49,162.02) --
-	( 78.49, 98.30);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.81,179.53) --
+	( 75.81,164.10);
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[fill=fillColor] ( 78.49,130.16) circle (  2.25);
+\path[fill=fillColor] ( 75.81,171.82) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 84.59,202.23) --
-	( 84.59,189.46);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 81.37,162.02) --
+	( 81.37, 98.30);
 \definecolor{fillColor}{RGB}{0,216,255}
 
-\path[fill=fillColor] ( 84.59,195.84) circle (  2.25);
+\path[fill=fillColor] ( 81.37,130.16) circle (  2.25);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 90.69,203.28) --
-	( 90.69,181.04);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 86.94,202.23) --
+	( 86.94,189.46);
 \definecolor{fillColor}{RGB}{151,0,255}
 
-\path[fill=fillColor] ( 90.69,192.16) circle (  2.25);
+\path[fill=fillColor] ( 86.94,195.84) circle (  2.25);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 96.79,240.71) --
-	( 96.79,222.93);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.50,203.28) --
+	( 92.50,181.04);
 \definecolor{fillColor}{RGB}{255,0,255}
 
-\path[fill=fillColor] ( 96.79,231.82) circle (  2.25);
+\path[fill=fillColor] ( 92.50,192.16) circle (  2.25);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 98.06,240.71) --
+	( 98.06,222.93);
+\definecolor{fillColor}{RGB}{68,68,68}
+
+\path[fill=fillColor] ( 98.06,231.82) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] ( 54.10,176.33) --
-	(102.88,176.33);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] ( 53.56,176.39) --
+	(103.62,176.39);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 78.49,284.14) {1.1\% faster};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 78.59,284.14) {1.1\% faster};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (108.98,  0.00) --
-	(108.98,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (109.18,  0.00) --
+	(109.18,357.33);
 \definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (115.08,192.84) --
-	(115.08,179.45);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (114.75,200.32) --
+	(114.75,179.86);
 \definecolor{fillColor}{RGB}{255,0,109}
 
-\path[fill=fillColor] (115.08,186.14) circle (  2.25);
+\path[fill=fillColor] (114.75,190.09) circle (  2.25);
 \definecolor{drawColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.18,182.97) --
-	(121.18,171.24);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.31,192.84) --
+	(120.31,179.45);
 \definecolor{fillColor}{RGB}{253,104,0}
 
-\path[fill=fillColor] (121.18,177.11) circle (  2.25);
+\path[fill=fillColor] (120.31,186.14) circle (  2.25);
 \definecolor{drawColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (127.28,184.85) --
-	(127.28,171.12);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (125.87,182.97) --
+	(125.87,171.24);
 \definecolor{fillColor}{RGB}{143,161,0}
 
-\path[fill=fillColor] (127.28,177.99) circle (  2.25);
+\path[fill=fillColor] (125.87,177.11) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (133.38,190.36) --
-	(133.38,166.22);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (131.43,184.85) --
+	(131.43,171.12);
 \definecolor{fillColor}{RGB}{0,195,0}
 
-\path[fill=fillColor] (133.38,178.29) circle (  2.25);
+\path[fill=fillColor] (131.43,177.99) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (139.47,169.54) --
-	(139.47,147.07);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (137.00,184.14) --
+	(137.00,167.55);
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[fill=fillColor] (139.47,158.31) circle (  2.25);
+\path[fill=fillColor] (137.00,175.84) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.57,195.26) --
-	(145.57,186.84);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (142.56,169.54) --
+	(142.56,147.07);
 \definecolor{fillColor}{RGB}{0,216,255}
 
-\path[fill=fillColor] (145.57,191.05) circle (  2.25);
+\path[fill=fillColor] (142.56,158.31) circle (  2.25);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.67,257.34) --
-	(151.67,213.88);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.12,195.26) --
+	(148.12,186.84);
 \definecolor{fillColor}{RGB}{151,0,255}
 
-\path[fill=fillColor] (151.67,235.61) circle (  2.25);
+\path[fill=fillColor] (148.12,191.05) circle (  2.25);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (157.77,242.16) --
-	(157.77,219.28);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.68,257.34) --
+	(153.68,213.88);
 \definecolor{fillColor}{RGB}{255,0,255}
 
-\path[fill=fillColor] (157.77,230.72) circle (  2.25);
+\path[fill=fillColor] (153.68,235.61) circle (  2.25);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.24,242.16) --
+	(159.24,219.28);
+\definecolor{fillColor}{RGB}{68,68,68}
+
+\path[fill=fillColor] (159.24,230.72) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (115.08,193.08) --
-	(163.87,193.08);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (114.75,192.50) --
+	(164.81,192.50);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (139.47,284.14) {7.4\% faster};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (139.78,284.14) {7.2\% faster};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (169.97,  0.00) --
-	(169.97,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (170.37,  0.00) --
+	(170.37,357.33);
 \definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.06,183.40) --
-	(176.06,181.91);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.93,178.18) --
+	(175.93,171.14);
 \definecolor{fillColor}{RGB}{255,0,109}
 
-\path[fill=fillColor] (176.06,182.66) circle (  2.25);
+\path[fill=fillColor] (175.93,174.66) circle (  2.25);
 \definecolor{drawColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.16,178.32) --
-	(182.16,176.29);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.49,183.40) --
+	(181.49,181.91);
 \definecolor{fillColor}{RGB}{253,104,0}
 
-\path[fill=fillColor] (182.16,177.30) circle (  2.25);
+\path[fill=fillColor] (181.49,182.66) circle (  2.25);
 \definecolor{drawColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.26,173.36) --
-	(188.26,171.68);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.05,178.32) --
+	(187.05,176.29);
 \definecolor{fillColor}{RGB}{143,161,0}
 
-\path[fill=fillColor] (188.26,172.52) circle (  2.25);
+\path[fill=fillColor] (187.05,177.30) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.36,167.30) --
-	(194.36,164.77);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.62,173.36) --
+	(192.62,171.68);
 \definecolor{fillColor}{RGB}{0,195,0}
 
-\path[fill=fillColor] (194.36,166.03) circle (  2.25);
+\path[fill=fillColor] (192.62,172.52) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.46,175.58) --
-	(200.46,173.46);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.18,173.13) --
+	(198.18,167.55);
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[fill=fillColor] (200.46,174.52) circle (  2.25);
+\path[fill=fillColor] (198.18,170.34) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.56,188.62) --
-	(206.56,187.01);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.74,175.58) --
+	(203.74,173.46);
 \definecolor{fillColor}{RGB}{0,216,255}
 
-\path[fill=fillColor] (206.56,187.82) circle (  2.25);
+\path[fill=fillColor] (203.74,174.52) circle (  2.25);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.65,191.38) --
-	(212.65,187.66);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.30,188.62) --
+	(209.30,187.01);
 \definecolor{fillColor}{RGB}{151,0,255}
 
-\path[fill=fillColor] (212.65,189.52) circle (  2.25);
+\path[fill=fillColor] (209.30,187.82) circle (  2.25);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.75,221.94) --
-	(218.75,219.83);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (214.87,191.38) --
+	(214.87,187.66);
 \definecolor{fillColor}{RGB}{255,0,255}
 
-\path[fill=fillColor] (218.75,220.89) circle (  2.25);
+\path[fill=fillColor] (214.87,189.52) circle (  2.25);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.43,221.94) --
+	(220.43,219.83);
+\definecolor{fillColor}{RGB}{68,68,68}
+
+\path[fill=fillColor] (220.43,220.89) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (176.06,184.37) --
-	(224.85,184.37);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (175.93,183.76) --
+	(225.99,183.76);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (200.46,284.14) {4.1\% faster};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (200.96,284.14) {3.9\% faster};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (230.95,  0.00) --
-	(230.95,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (231.55,  0.00) --
+	(231.55,357.33);
 \definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.05,181.65) --
-	(237.05,172.54);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.11,175.10) --
+	(237.11,147.62);
 \definecolor{fillColor}{RGB}{255,0,109}
 
-\path[fill=fillColor] (237.05,177.10) circle (  2.25);
+\path[fill=fillColor] (237.11,161.36) circle (  2.25);
 \definecolor{drawColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (243.15,159.01) --
-	(243.15,132.62);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (242.68,181.65) --
+	(242.68,172.54);
 \definecolor{fillColor}{RGB}{253,104,0}
 
-\path[fill=fillColor] (243.15,145.81) circle (  2.25);
+\path[fill=fillColor] (242.68,177.10) circle (  2.25);
 \definecolor{drawColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (249.24,177.17) --
-	(249.24,157.93);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (248.24,159.01) --
+	(248.24,132.62);
 \definecolor{fillColor}{RGB}{143,161,0}
 
-\path[fill=fillColor] (249.24,167.55) circle (  2.25);
+\path[fill=fillColor] (248.24,145.81) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (255.34,189.97) --
-	(255.34,147.35);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (253.80,177.17) --
+	(253.80,157.93);
 \definecolor{fillColor}{RGB}{0,195,0}
 
-\path[fill=fillColor] (255.34,168.66) circle (  2.25);
+\path[fill=fillColor] (253.80,167.55) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44,177.18) --
-	(261.44,164.80);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (259.36,184.40) --
+	(259.36,154.83);
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[fill=fillColor] (261.44,170.99) circle (  2.25);
+\path[fill=fillColor] (259.36,169.62) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (267.54,208.69) --
-	(267.54,185.32);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.93,177.18) --
+	(264.93,164.80);
 \definecolor{fillColor}{RGB}{0,216,255}
 
-\path[fill=fillColor] (267.54,197.01) circle (  2.25);
+\path[fill=fillColor] (264.93,170.99) circle (  2.25);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (273.64,218.20) --
-	(273.64,198.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (270.49,208.69) --
+	(270.49,185.32);
 \definecolor{fillColor}{RGB}{151,0,255}
 
-\path[fill=fillColor] (273.64,208.22) circle (  2.25);
+\path[fill=fillColor] (270.49,197.01) circle (  2.25);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (279.74,223.20) --
-	(279.74,214.78);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (276.05,218.20) --
+	(276.05,198.25);
 \definecolor{fillColor}{RGB}{255,0,255}
 
-\path[fill=fillColor] (279.74,218.99) circle (  2.25);
+\path[fill=fillColor] (276.05,208.22) circle (  2.25);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (281.61,223.20) --
+	(281.61,214.78);
+\definecolor{fillColor}{RGB}{68,68,68}
+
+\path[fill=fillColor] (281.61,218.99) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (237.05,182.72) --
-	(285.83,182.72);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (237.11,180.53) --
+	(287.17,180.53);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (261.44,284.14) {3.5\% faster};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (262.14,284.14) {2.7\% faster};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (291.93,  0.00) --
-	(291.93,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (292.74,  0.00) --
+	(292.74,357.33);
 \definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.03,178.61) --
-	(298.03,167.68);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.30,171.47) --
+	(298.30,146.80);
 \definecolor{fillColor}{RGB}{255,0,109}
 
-\path[fill=fillColor] (298.03,173.15) circle (  2.25);
+\path[fill=fillColor] (298.30,159.14) circle (  2.25);
 \definecolor{drawColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (304.13,162.68) --
-	(304.13,139.42);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (303.86,178.61) --
+	(303.86,167.68);
 \definecolor{fillColor}{RGB}{253,104,0}
 
-\path[fill=fillColor] (304.13,151.05) circle (  2.25);
+\path[fill=fillColor] (303.86,173.15) circle (  2.25);
 \definecolor{drawColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (310.23,176.48) --
-	(310.23,158.35);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (309.42,162.68) --
+	(309.42,139.42);
 \definecolor{fillColor}{RGB}{143,161,0}
 
-\path[fill=fillColor] (310.23,167.41) circle (  2.25);
+\path[fill=fillColor] (309.42,151.05) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (316.33,195.13) --
-	(316.33,158.87);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (314.99,176.48) --
+	(314.99,158.35);
 \definecolor{fillColor}{RGB}{0,195,0}
 
-\path[fill=fillColor] (316.33,177.00) circle (  2.25);
+\path[fill=fillColor] (314.99,167.41) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (322.42,176.14) --
-	(322.42,165.55);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (320.55,197.57) --
+	(320.55,164.96);
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[fill=fillColor] (322.42,170.84) circle (  2.25);
+\path[fill=fillColor] (320.55,181.26) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (328.52,208.50) --
-	(328.52,185.79);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (326.11,176.14) --
+	(326.11,165.55);
 \definecolor{fillColor}{RGB}{0,216,255}
 
-\path[fill=fillColor] (328.52,197.14) circle (  2.25);
+\path[fill=fillColor] (326.11,170.84) circle (  2.25);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (334.62,224.16) --
-	(334.62,192.88);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (331.67,208.50) --
+	(331.67,185.79);
 \definecolor{fillColor}{RGB}{151,0,255}
 
-\path[fill=fillColor] (334.62,208.52) circle (  2.25);
+\path[fill=fillColor] (331.67,197.14) circle (  2.25);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (340.72,226.54) --
-	(340.72,218.12);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (337.23,224.16) --
+	(337.23,192.88);
 \definecolor{fillColor}{RGB}{255,0,255}
 
-\path[fill=fillColor] (340.72,222.33) circle (  2.25);
+\path[fill=fillColor] (337.23,208.52) circle (  2.25);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (342.80,226.54) --
+	(342.80,218.12);
+\definecolor{fillColor}{RGB}{68,68,68}
+
+\path[fill=fillColor] (342.80,222.33) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (298.03,184.32) --
-	(346.82,184.32);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (298.30,182.10) --
+	(348.36,182.10);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (322.42,284.14) {4.1\% faster};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (323.33,284.14) {3.2\% faster};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (352.92,  0.00) --
-	(352.92,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (353.92,  0.00) --
+	(353.92,357.33);
 \definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (359.01,182.24) --
-	(359.01,167.41);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (359.48,183.45) --
+	(359.48,166.61);
 \definecolor{fillColor}{RGB}{255,0,109}
 
-\path[fill=fillColor] (359.01,174.82) circle (  2.25);
+\path[fill=fillColor] (359.48,175.03) circle (  2.25);
 \definecolor{drawColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (365.11,157.24) --
-	(365.11,131.60);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (365.05,182.24) --
+	(365.05,167.41);
 \definecolor{fillColor}{RGB}{253,104,0}
 
-\path[fill=fillColor] (365.11,144.42) circle (  2.25);
+\path[fill=fillColor] (365.05,174.82) circle (  2.25);
 \definecolor{drawColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (371.21,169.99) --
-	(371.21,153.88);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (370.61,157.24) --
+	(370.61,131.60);
 \definecolor{fillColor}{RGB}{143,161,0}
 
-\path[fill=fillColor] (371.21,161.94) circle (  2.25);
+\path[fill=fillColor] (370.61,144.42) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (377.31,168.23) --
-	(377.31,146.43);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (376.17,169.99) --
+	(376.17,153.88);
 \definecolor{fillColor}{RGB}{0,195,0}
 
-\path[fill=fillColor] (377.31,157.33) circle (  2.25);
+\path[fill=fillColor] (376.17,161.94) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (383.41,174.11) --
-	(383.41,150.84);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (381.73,185.79) --
+	(381.73,156.55);
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[fill=fillColor] (383.41,162.48) circle (  2.25);
+\path[fill=fillColor] (381.73,171.17) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.51,193.90) --
-	(389.51,166.47);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (387.29,174.11) --
+	(387.29,150.84);
 \definecolor{fillColor}{RGB}{0,216,255}
 
-\path[fill=fillColor] (389.51,180.18) circle (  2.25);
+\path[fill=fillColor] (387.29,162.48) circle (  2.25);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (395.60,203.16) --
-	(395.60,181.99);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (392.86,193.90) --
+	(392.86,166.47);
 \definecolor{fillColor}{RGB}{151,0,255}
 
-\path[fill=fillColor] (395.60,192.57) circle (  2.25);
+\path[fill=fillColor] (392.86,180.18) circle (  2.25);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (401.70,239.78) --
-	(401.70,221.53);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (398.42,203.16) --
+	(398.42,181.99);
 \definecolor{fillColor}{RGB}{255,0,255}
 
-\path[fill=fillColor] (401.70,230.66) circle (  2.25);
+\path[fill=fillColor] (398.42,192.57) circle (  2.25);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (403.98,239.78) --
+	(403.98,221.53);
+\definecolor{fillColor}{RGB}{68,68,68}
+
+\path[fill=fillColor] (403.98,230.66) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (359.01,176.71) --
-	(407.80,176.71);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (359.48,177.99) --
+	(409.54,177.99);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (383.41,284.14) {1.3\% faster};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (384.51,284.14) {1.7\% faster};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (413.90,  0.00) --
-	(413.90,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (415.11,  0.00) --
+	(415.11,357.33);
 \definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.00,189.40) --
-	(420.00,183.99);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.67,175.06) --
+	(420.67,169.51);
 \definecolor{fillColor}{RGB}{255,0,109}
 
-\path[fill=fillColor] (420.00,186.70) circle (  2.25);
+\path[fill=fillColor] (420.67,172.29) circle (  2.25);
 \definecolor{drawColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.10,179.73) --
-	(426.10,176.02);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.23,189.40) --
+	(426.23,183.99);
 \definecolor{fillColor}{RGB}{253,104,0}
 
-\path[fill=fillColor] (426.10,177.87) circle (  2.25);
+\path[fill=fillColor] (426.23,186.70) circle (  2.25);
 \definecolor{drawColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (432.19,178.20) --
-	(432.19,174.37);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (431.79,179.73) --
+	(431.79,176.02);
 \definecolor{fillColor}{RGB}{143,161,0}
 
-\path[fill=fillColor] (432.19,176.28) circle (  2.25);
+\path[fill=fillColor] (431.79,177.87) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.29,173.45) --
-	(438.29,169.46);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (437.35,178.20) --
+	(437.35,174.37);
 \definecolor{fillColor}{RGB}{0,195,0}
 
-\path[fill=fillColor] (438.29,171.45) circle (  2.25);
+\path[fill=fillColor] (437.35,176.28) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (444.39,177.55) --
-	(444.39,172.82);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (442.92,174.49) --
+	(442.92,171.77);
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[fill=fillColor] (444.39,175.18) circle (  2.25);
+\path[fill=fillColor] (442.92,173.13) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (450.49,198.72) --
-	(450.49,192.07);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (448.48,177.55) --
+	(448.48,172.82);
 \definecolor{fillColor}{RGB}{0,216,255}
 
-\path[fill=fillColor] (450.49,195.40) circle (  2.25);
+\path[fill=fillColor] (448.48,175.18) circle (  2.25);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (456.59,191.62) --
-	(456.59,186.36);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.04,198.72) --
+	(454.04,192.07);
 \definecolor{fillColor}{RGB}{151,0,255}
 
-\path[fill=fillColor] (456.59,188.99) circle (  2.25);
+\path[fill=fillColor] (454.04,195.40) circle (  2.25);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.69,229.29) --
-	(462.69,223.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (459.60,191.62) --
+	(459.60,186.36);
 \definecolor{fillColor}{RGB}{255,0,255}
 
-\path[fill=fillColor] (462.69,226.15) circle (  2.25);
+\path[fill=fillColor] (459.60,188.99) circle (  2.25);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (465.16,229.29) --
+	(465.16,223.00);
+\definecolor{fillColor}{RGB}{68,68,68}
+
+\path[fill=fillColor] (465.16,226.15) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (420.00,187.76) --
-	(468.78,187.76);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (420.67,186.26) --
+	(470.73,186.26);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (444.39,284.14) {5.4\% faster};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (445.70,284.14) {4.8\% faster};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (474.88,  0.00) --
-	(474.88,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (476.29,  0.00) --
+	(476.29,357.33);
 \end{scope}

### 2020-09-01 benchmarking/benchmarkingVM/ESS_round5.tex
complete draft

@@
-% Created by tikzDevice version 0.12.3.1 on 2020-08-31 17:27:26
+% Created by tikzDevice version 0.12.3.1 on 2020-09-01 15:30:48
 % !TEX encoding = UTF-8 Unicode
@@
 \path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] ( 48.00,173.19) --
-	(474.88,173.19);
+	(476.29,173.19);
 \definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 54.10,170.57) --
-	( 54.10,160.89);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 53.56,197.87) --
+	( 53.56,173.22);
 \definecolor{fillColor}{RGB}{255,0,109}
 
-\path[fill=fillColor] ( 54.10,165.73) circle (  2.25);
+\path[fill=fillColor] ( 53.56,185.54) circle (  2.25);
 \definecolor{drawColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 60.20,193.03) --
-	( 60.20,169.27);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 59.12,170.57) --
+	( 59.12,160.89);
 \definecolor{fillColor}{RGB}{253,104,0}
 
-\path[fill=fillColor] ( 60.20,181.15) circle (  2.25);
+\path[fill=fillColor] ( 59.12,165.73) circle (  2.25);
 \definecolor{drawColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.29,191.40) --
-	( 66.29,174.61);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 64.69,193.03) --
+	( 64.69,169.27);
 \definecolor{fillColor}{RGB}{143,161,0}
 
-\path[fill=fillColor] ( 66.29,183.01) circle (  2.25);
+\path[fill=fillColor] ( 64.69,181.15) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 72.39,196.48) --
-	( 72.39,170.97);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 70.25,191.40) --
+	( 70.25,174.61);
 \definecolor{fillColor}{RGB}{0,195,0}
 
-\path[fill=fillColor] ( 72.39,183.73) circle (  2.25);
+\path[fill=fillColor] ( 70.25,183.01) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 78.49,141.00) --
-	( 78.49, 76.27);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.81,194.06) --
+	( 75.81,177.12);
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[fill=fillColor] ( 78.49,108.63) circle (  2.25);
+\path[fill=fillColor] ( 75.81,185.59) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 84.59,183.38) --
-	( 84.59,168.50);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 81.37,141.00) --
+	( 81.37, 76.27);
 \definecolor{fillColor}{RGB}{0,216,255}
 
-\path[fill=fillColor] ( 84.59,175.94) circle (  2.25);
+\path[fill=fillColor] ( 81.37,108.63) circle (  2.25);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 90.69,170.18) --
-	( 90.69,143.82);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 86.94,183.38) --
+	( 86.94,168.50);
 \definecolor{fillColor}{RGB}{151,0,255}
 
-\path[fill=fillColor] ( 90.69,157.00) circle (  2.25);
+\path[fill=fillColor] ( 86.94,175.94) circle (  2.25);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 96.79,196.84) --
-	( 96.79,181.84);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.50,170.18) --
+	( 92.50,143.82);
 \definecolor{fillColor}{RGB}{255,0,255}
 
-\path[fill=fillColor] ( 96.79,189.34) circle (  2.25);
+\path[fill=fillColor] ( 92.50,157.00) circle (  2.25);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 98.06,196.84) --
+	( 98.06,181.84);
+\definecolor{fillColor}{RGB}{68,68,68}
+
+\path[fill=fillColor] ( 98.06,189.34) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] ( 54.10,169.09) --
-	(102.88,169.09);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] ( 53.56,171.19) --
+	(103.62,171.19);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 78.49,284.14) {-1.5\% faster};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 78.59,284.14) {0.72\% slower};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (108.98,  0.00) --
-	(108.98,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (109.18,  0.00) --
+	(109.18,357.33);
 \definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (115.08,194.11) --
-	(115.08,179.13);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (114.75,229.74) --
+	(114.75,203.57);
 \definecolor{fillColor}{RGB}{255,0,109}
 
-\path[fill=fillColor] (115.08,186.62) circle (  2.25);
+\path[fill=fillColor] (114.75,216.66) circle (  2.25);
 \definecolor{drawColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.18,185.55) --
-	(121.18,175.29);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (120.31,194.11) --
+	(120.31,179.13);
 \definecolor{fillColor}{RGB}{253,104,0}
 
-\path[fill=fillColor] (121.18,180.42) circle (  2.25);
+\path[fill=fillColor] (120.31,186.62) circle (  2.25);
 \definecolor{drawColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (127.28,214.73) --
-	(127.28,201.99);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (125.87,185.55) --
+	(125.87,175.29);
 \definecolor{fillColor}{RGB}{143,161,0}
 
-\path[fill=fillColor] (127.28,208.36) circle (  2.25);
+\path[fill=fillColor] (125.87,180.42) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (133.38,249.42) --
-	(133.38,231.42);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (131.43,214.73) --
+	(131.43,201.99);
 \definecolor{fillColor}{RGB}{0,195,0}
 
-\path[fill=fillColor] (133.38,240.42) circle (  2.25);
+\path[fill=fillColor] (131.43,208.36) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (139.47,159.92) --
-	(139.47,140.75);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (137.00,239.63) --
+	(137.00,227.48);
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[fill=fillColor] (139.47,150.33) circle (  2.25);
+\path[fill=fillColor] (137.00,233.56) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.57,214.01) --
-	(145.57,205.08);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (142.56,159.92) --
+	(142.56,140.75);
 \definecolor{fillColor}{RGB}{0,216,255}
 
-\path[fill=fillColor] (145.57,209.54) circle (  2.25);
+\path[fill=fillColor] (142.56,150.33) circle (  2.25);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.67,200.10) --
-	(151.67,107.60);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.12,214.01) --
+	(148.12,205.08);
 \definecolor{fillColor}{RGB}{151,0,255}
 
-\path[fill=fillColor] (151.67,153.85) circle (  2.25);
+\path[fill=fillColor] (148.12,209.54) circle (  2.25);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (157.77,178.44) --
-	(157.77,154.84);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.68,200.10) --
+	(153.68,107.60);
 \definecolor{fillColor}{RGB}{255,0,255}
 
-\path[fill=fillColor] (157.77,166.64) circle (  2.25);
+\path[fill=fillColor] (153.68,153.85) circle (  2.25);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.24,178.44) --
+	(159.24,154.84);
+\definecolor{fillColor}{RGB}{68,68,68}
+
+\path[fill=fillColor] (159.24,166.64) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (115.08,188.55) --
-	(163.87,188.55);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (114.75,190.92) --
+	(164.81,190.92);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (139.47,284.14) {5.7\% faster};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (139.78,284.14) {6.6\% faster};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (169.97,  0.00) --
-	(169.97,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (170.37,  0.00) --
+	(170.37,357.33);
 \definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.06,172.66) --
-	(176.06,170.84);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.93,168.43) --
+	(175.93,160.62);
 \definecolor{fillColor}{RGB}{255,0,109}
 
-\path[fill=fillColor] (176.06,171.75) circle (  2.25);
+\path[fill=fillColor] (175.93,164.53) circle (  2.25);
 \definecolor{drawColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.16,169.79) --
-	(182.16,167.75);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.49,172.66) --
+	(181.49,170.84);
 \definecolor{fillColor}{RGB}{253,104,0}
 
-\path[fill=fillColor] (182.16,168.77) circle (  2.25);
+\path[fill=fillColor] (181.49,171.75) circle (  2.25);
 \definecolor{drawColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.26,189.75) --
-	(188.26,187.44);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.05,169.79) --
+	(187.05,167.75);
 \definecolor{fillColor}{RGB}{143,161,0}
 
-\path[fill=fillColor] (188.26,188.59) circle (  2.25);
+\path[fill=fillColor] (187.05,168.77) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.36,203.19) --
-	(194.36,199.69);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.62,189.75) --
+	(192.62,187.44);
 \definecolor{fillColor}{RGB}{0,195,0}
 
-\path[fill=fillColor] (194.36,201.44) circle (  2.25);
+\path[fill=fillColor] (192.62,188.59) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.46,171.28) --
-	(200.46,169.79);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.18,201.95) --
+	(198.18,198.81);
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[fill=fillColor] (200.46,170.53) circle (  2.25);
+\path[fill=fillColor] (198.18,200.38) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.56,184.57) --
-	(206.56,182.27);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.74,171.28) --
+	(203.74,169.79);
 \definecolor{fillColor}{RGB}{0,216,255}
 
-\path[fill=fillColor] (206.56,183.42) circle (  2.25);
+\path[fill=fillColor] (203.74,170.53) circle (  2.25);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.65,163.32) --
-	(212.65,160.43);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (209.30,184.57) --
+	(209.30,182.27);
 \definecolor{fillColor}{RGB}{151,0,255}
 
-\path[fill=fillColor] (212.65,161.87) circle (  2.25);
+\path[fill=fillColor] (209.30,183.42) circle (  2.25);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (218.75,155.78) --
-	(218.75,154.17);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (214.87,163.32) --
+	(214.87,160.43);
 \definecolor{fillColor}{RGB}{255,0,255}
 
-\path[fill=fillColor] (218.75,154.97) circle (  2.25);
+\path[fill=fillColor] (214.87,161.87) circle (  2.25);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (220.43,155.78) --
+	(220.43,154.17);
+\definecolor{fillColor}{RGB}{68,68,68}
+
+\path[fill=fillColor] (220.43,154.97) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (176.06,175.53) --
-	(224.85,175.53);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (175.93,174.20) --
+	(225.99,174.20);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (200.46,284.14) {0.84\% faster};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (200.96,284.14) {0.36\% faster};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (230.95,  0.00) --
-	(230.95,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (231.55,  0.00) --
+	(231.55,357.33);
 \definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.05,218.83) --
-	(237.05,206.46);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (237.11,171.43) --
+	(237.11,152.78);
 \definecolor{fillColor}{RGB}{255,0,109}
 
-\path[fill=fillColor] (237.05,212.65) circle (  2.25);
+\path[fill=fillColor] (237.11,162.10) circle (  2.25);
 \definecolor{drawColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (243.15,242.97) --
-	(243.15,220.02);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (242.68,218.83) --
+	(242.68,206.46);
 \definecolor{fillColor}{RGB}{253,104,0}
 
-\path[fill=fillColor] (243.15,231.49) circle (  2.25);
+\path[fill=fillColor] (242.68,212.65) circle (  2.25);
 \definecolor{drawColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (249.24,208.35) --
-	(249.24,192.32);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (248.24,242.97) --
+	(248.24,220.02);
 \definecolor{fillColor}{RGB}{143,161,0}
 
-\path[fill=fillColor] (249.24,200.33) circle (  2.25);
+\path[fill=fillColor] (248.24,231.49) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (255.34,176.56) --
-	(255.34,142.47);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (253.80,208.35) --
+	(253.80,192.32);
 \definecolor{fillColor}{RGB}{0,195,0}
 
-\path[fill=fillColor] (255.34,159.52) circle (  2.25);
+\path[fill=fillColor] (253.80,200.33) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.44,187.62) --
-	(261.44,174.61);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (259.36,179.26) --
+	(259.36,152.83);
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[fill=fillColor] (261.44,181.12) circle (  2.25);
+\path[fill=fillColor] (259.36,166.04) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (267.54,206.77) --
-	(267.54,181.77);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.93,187.62) --
+	(264.93,174.61);
 \definecolor{fillColor}{RGB}{0,216,255}
 
-\path[fill=fillColor] (267.54,194.27) circle (  2.25);
+\path[fill=fillColor] (264.93,181.12) circle (  2.25);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (273.64,229.57) --
-	(273.64,209.79);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (270.49,206.77) --
+	(270.49,181.77);
 \definecolor{fillColor}{RGB}{151,0,255}
 
-\path[fill=fillColor] (273.64,219.68) circle (  2.25);
+\path[fill=fillColor] (270.49,194.27) circle (  2.25);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (279.74,216.31) --
-	(279.74,206.19);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (276.05,229.57) --
+	(276.05,209.79);
 \definecolor{fillColor}{RGB}{255,0,255}
 
-\path[fill=fillColor] (279.74,211.25) circle (  2.25);
+\path[fill=fillColor] (276.05,219.68) circle (  2.25);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (281.61,216.31) --
+	(281.61,206.19);
+\definecolor{fillColor}{RGB}{68,68,68}
+
+\path[fill=fillColor] (281.61,211.25) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (237.05,202.10) --
-	(285.83,202.10);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (237.11,198.57) --
+	(287.17,198.57);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (261.44,284.14) {11\% faster};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (262.14,284.14) {9.5\% faster};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (291.93,  0.00) --
-	(291.93,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (292.74,  0.00) --
+	(292.74,357.33);
 \definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.03,209.96) --
-	(298.03,198.22);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.30,166.69) --
+	(298.30,150.30);
 \definecolor{fillColor}{RGB}{255,0,109}
 
-\path[fill=fillColor] (298.03,204.09) circle (  2.25);
+\path[fill=fillColor] (298.30,158.50) circle (  2.25);
 \definecolor{drawColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (304.13,238.47) --
-	(304.13,217.31);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (303.86,209.96) --
+	(303.86,198.22);
 \definecolor{fillColor}{RGB}{253,104,0}
 
-\path[fill=fillColor] (304.13,227.89) circle (  2.25);
+\path[fill=fillColor] (303.86,204.09) circle (  2.25);
 \definecolor{drawColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (310.23,204.06) --
-	(310.23,189.08);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (309.42,238.47) --
+	(309.42,217.31);
 \definecolor{fillColor}{RGB}{143,161,0}
 
-\path[fill=fillColor] (310.23,196.57) circle (  2.25);
+\path[fill=fillColor] (309.42,227.89) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (316.33,171.91) --
-	(316.33,144.86);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (314.99,204.06) --
+	(314.99,189.08);
 \definecolor{fillColor}{RGB}{0,195,0}
 
-\path[fill=fillColor] (316.33,158.38) circle (  2.25);
+\path[fill=fillColor] (314.99,196.57) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (322.42,183.17) --
-	(322.42,172.59);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (320.55,183.38) --
+	(320.55,154.32);
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[fill=fillColor] (322.42,177.88) circle (  2.25);
+\path[fill=fillColor] (320.55,168.85) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (328.52,206.07) --
-	(328.52,181.21);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (326.11,183.17) --
+	(326.11,172.59);
 \definecolor{fillColor}{RGB}{0,216,255}
 
-\path[fill=fillColor] (328.52,193.64) circle (  2.25);
+\path[fill=fillColor] (326.11,177.88) circle (  2.25);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (334.62,210.76) --
-	(334.62,182.47);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (331.67,206.07) --
+	(331.67,181.21);
 \definecolor{fillColor}{RGB}{151,0,255}
 
-\path[fill=fillColor] (334.62,196.61) circle (  2.25);
+\path[fill=fillColor] (331.67,193.64) circle (  2.25);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (340.72,208.61) --
-	(340.72,197.60);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (337.23,210.76) --
+	(337.23,182.47);
 \definecolor{fillColor}{RGB}{255,0,255}
 
-\path[fill=fillColor] (340.72,203.11) circle (  2.25);
+\path[fill=fillColor] (337.23,196.61) circle (  2.25);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (342.80,208.61) --
+	(342.80,197.60);
+\definecolor{fillColor}{RGB}{68,68,68}
+
+\path[fill=fillColor] (342.80,203.11) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (298.03,195.41) --
-	(346.82,195.41);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (298.30,192.59) --
+	(348.36,192.59);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (322.42,284.14) {8.3\% faster};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (323.33,284.14) {7.2\% faster};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (352.92,  0.00) --
-	(352.92,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (353.92,  0.00) --
+	(353.92,357.33);
 \definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (359.01,174.36) --
-	(359.01,162.95);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (359.48,175.89) --
+	(359.48,161.24);
 \definecolor{fillColor}{RGB}{255,0,109}
 
-\path[fill=fillColor] (359.01,168.66) circle (  2.25);
+\path[fill=fillColor] (359.48,168.57) circle (  2.25);
 \definecolor{drawColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (365.11,189.08) --
-	(365.11,165.88);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (365.05,174.36) --
+	(365.05,162.95);
 \definecolor{fillColor}{RGB}{253,104,0}
 
-\path[fill=fillColor] (365.11,177.48) circle (  2.25);
+\path[fill=fillColor] (365.05,168.66) circle (  2.25);
 \definecolor{drawColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (371.21,190.22) --
-	(371.21,174.54);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (370.61,189.08) --
+	(370.61,165.88);
 \definecolor{fillColor}{RGB}{143,161,0}
 
-\path[fill=fillColor] (371.21,182.38) circle (  2.25);
+\path[fill=fillColor] (370.61,177.48) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (377.31,180.24) --
-	(377.31,143.99);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (376.17,190.22) --
+	(376.17,174.54);
 \definecolor{fillColor}{RGB}{0,195,0}
 
-\path[fill=fillColor] (377.31,162.11) circle (  2.25);
+\path[fill=fillColor] (376.17,182.38) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (383.41,146.90) --
-	(383.41,126.33);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (381.73,191.32) --
+	(381.73,161.99);
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[fill=fillColor] (383.41,136.61) circle (  2.25);
+\path[fill=fillColor] (381.73,176.66) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.51,194.96) --
-	(389.51,169.70);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (387.29,146.90) --
+	(387.29,126.33);
 \definecolor{fillColor}{RGB}{0,216,255}
 
-\path[fill=fillColor] (389.51,182.33) circle (  2.25);
+\path[fill=fillColor] (387.29,136.61) circle (  2.25);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (395.60,175.08) --
-	(395.60,145.39);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (392.86,194.96) --
+	(392.86,169.70);
 \definecolor{fillColor}{RGB}{151,0,255}
 
-\path[fill=fillColor] (395.60,160.24) circle (  2.25);
+\path[fill=fillColor] (392.86,182.33) circle (  2.25);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (401.70,198.72) --
-	(401.70,181.55);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (398.42,175.08) --
+	(398.42,145.39);
 \definecolor{fillColor}{RGB}{255,0,255}
 
-\path[fill=fillColor] (401.70,190.14) circle (  2.25);
+\path[fill=fillColor] (398.42,160.24) circle (  2.25);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (403.98,198.72) --
+	(403.98,181.55);
+\definecolor{fillColor}{RGB}{68,68,68}
+
+\path[fill=fillColor] (403.98,190.14) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (359.01,170.44) --
-	(407.80,170.44);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (359.48,171.84) --
+	(409.54,171.84);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (383.41,284.14) {-0.98\% faster};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (384.51,284.14) {0.48\% slower};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (413.90,  0.00) --
-	(413.90,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (415.11,  0.00) --
+	(415.11,357.33);
 \definecolor{drawColor}{RGB}{255,0,109}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.00,167.61) --
-	(420.00,161.93);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (420.67,166.71) --
+	(420.67,162.11);
 \definecolor{fillColor}{RGB}{255,0,109}
 
-\path[fill=fillColor] (420.00,164.77) circle (  2.25);
+\path[fill=fillColor] (420.67,164.41) circle (  2.25);
 \definecolor{drawColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.10,164.25) --
-	(426.10,160.41);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (426.23,167.61) --
+	(426.23,161.93);
 \definecolor{fillColor}{RGB}{253,104,0}
 
-\path[fill=fillColor] (426.10,162.33) circle (  2.25);
+\path[fill=fillColor] (426.23,164.77) circle (  2.25);
 \definecolor{drawColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (432.19,168.36) --
-	(432.19,165.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (431.79,164.25) --
+	(431.79,160.41);
 \definecolor{fillColor}{RGB}{143,161,0}
 
-\path[fill=fillColor] (432.19,166.80) circle (  2.25);
+\path[fill=fillColor] (431.79,162.33) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.29,170.98) --
-	(438.29,165.44);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (437.35,168.36) --
+	(437.35,165.25);
 \definecolor{fillColor}{RGB}{0,195,0}
 
-\path[fill=fillColor] (438.29,168.21) circle (  2.25);
+\path[fill=fillColor] (437.35,166.80) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (444.39,161.65) --
-	(444.39,156.22);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (442.92,169.61) --
+	(442.92,166.59);
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[fill=fillColor] (444.39,158.94) circle (  2.25);
+\path[fill=fillColor] (442.92,168.10) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (450.49,162.17) --
-	(450.49,154.52);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (448.48,161.65) --
+	(448.48,156.22);
 \definecolor{fillColor}{RGB}{0,216,255}
 
-\path[fill=fillColor] (450.49,158.35) circle (  2.25);
+\path[fill=fillColor] (448.48,158.94) circle (  2.25);
 \definecolor{drawColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (456.59,155.49) --
-	(456.59,149.68);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (454.04,162.17) --
+	(454.04,154.52);
 \definecolor{fillColor}{RGB}{151,0,255}
 
-\path[fill=fillColor] (456.59,152.58) circle (  2.25);
+\path[fill=fillColor] (454.04,158.35) circle (  2.25);
 \definecolor{drawColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (462.69,166.82) --
-	(462.69,162.55);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (459.60,155.49) --
+	(459.60,149.68);
 \definecolor{fillColor}{RGB}{255,0,255}
 
-\path[fill=fillColor] (462.69,164.69) circle (  2.25);
+\path[fill=fillColor] (459.60,152.58) circle (  2.25);
+\definecolor{drawColor}{RGB}{68,68,68}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (465.16,166.82) --
+	(465.16,162.55);
+\definecolor{fillColor}{RGB}{68,68,68}
+
+\path[fill=fillColor] (465.16,164.69) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (420.00,162.13) --
-	(468.78,162.13);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (420.67,162.37) --
+	(470.73,162.37);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (444.39,284.14) {-3.9\% faster};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (445.70,284.14) {3.8\% slower};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (474.88,  0.00) --
-	(474.88,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (476.29,  0.00) --
+	(476.29,357.33);
 \end{scope}

### 2020-09-01 benchmarking/benchmarkingVM/ESS_round5b.tex
complete draft

@@
-% Created by tikzDevice version 0.12.3.1 on 2020-08-31 17:27:34
+% Created by tikzDevice version 0.12.3.1 on 2020-09-01 15:30:54
 % !TEX encoding = UTF-8 Unicode
@@
 
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] ( 96.08,169.48) --
+	( 99.63,169.48);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] ( 97.95,168.94) --
+	( 97.95,170.00);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 97.95,165.59) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (163.48,161.07) --
+	(164.40,161.07);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (163.94,160.64) --
+	(163.94,161.48);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (163.94,157.57) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (100.92,171.59) --
+	(101.99,171.59);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (101.46,171.40) --
+	(101.46,171.78);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (101.46,166.73) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] ( 93.57,150.27) --
+	( 97.17,150.27);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] ( 95.47,149.92) --
+	( 95.47,150.61);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 95.47,146.77) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] ( 94.30,150.30) --
+	( 97.93,150.30);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] ( 96.21,149.96) --
+	( 96.21,150.63);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 96.21,145.44) {$l$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] ( 97.23,166.98) --
+	(100.71,166.98);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] ( 99.06,166.56) --
+	( 99.06,167.38);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 99.06,163.48) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (171.18,174.13) --
+	(171.36,174.13);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (171.27,174.02) --
+	(171.27,174.24);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (171.27,170.63) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
 \path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (197.21,211.39) --
@@
 	(197.49,211.61);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (197.49,207.50) {$p$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(208.90,213.82);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (208.90,210.01) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(203.02,217.00);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (203.02,212.10) {$r$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(193.08,205.07);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (193.08,201.33) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(194.96,206.34);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (194.96,201.25) {$l$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(198.35,212.90);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (198.35,209.14) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(209.76,214.24);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (209.76,210.63) {$\kappa$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(175.02,181.76);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (175.02,177.40) {$p$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(200.15,203.77);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (200.15,200.07) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(196.25,205.93);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (196.25,201.01) {$r$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(168.88,170.65);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (168.88,166.66) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(170.61,171.80);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (170.61,166.48) {$l$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(169.55,179.47);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (169.55,175.46) {$\sigma$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(200.89,204.05);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (200.89,200.48) {$\kappa$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(160.70,187.62);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (160.70,183.51) {$p$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(198.33,202.79);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (198.33,199.06) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(189.79,202.70);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (189.79,197.80) {$r$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(157.10,181.30);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (157.10,177.55) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(159.10,181.82);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (159.10,176.73) {$l$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(162.09,184.15);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (162.09,180.36) {$\sigma$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(199.96,203.99);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (199.96,200.42) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (126.81,179.89) --
-	(129.23,179.89);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (128.06,179.46) --
-	(128.06,180.31);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (128.06,176.00) {$p$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (179.96,181.14) --
-	(180.68,181.14);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (180.33,180.91) --
-	(180.33,181.37);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (180.33,177.64) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (156.58,184.80) --
-	(156.82,184.80);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (156.70,184.71) --
-	(156.70,184.89);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (156.70,179.94) {$r$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (125.55,153.57) --
-	(127.99,153.57);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (126.81,153.09) --
-	(126.81,154.03);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (126.81,150.07) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (126.51,153.65) --
-	(128.85,153.65);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (127.72,153.18) --
-	(127.72,154.11);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (127.72,148.79) {$l$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (127.87,168.66) --
-	(130.38,168.66);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (129.17,168.21) --
-	(129.17,169.09);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (129.17,165.16) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (184.23,188.29) --
-	(184.50,188.29);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (184.36,188.21) --
-	(184.36,188.36);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (184.36,184.79) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (126.55,180.07) --
+	(128.37,180.07);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (127.48,179.67) --
+	(127.48,180.47);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (127.48,176.19) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (180.01,181.10) --
+	(180.49,181.10);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (180.25,180.89) --
+	(180.25,181.31);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (180.25,177.60) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (156.71,184.82) --
+	(156.88,184.82);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (156.80,184.74) --
+	(156.80,184.91);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (156.80,179.96) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (125.64,153.88) --
+	(127.53,153.88);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (126.61,153.34) --
+	(126.61,154.40);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (126.61,150.38) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (126.51,153.82) --
+	(128.35,153.82);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (127.46,153.32) --
+	(127.46,154.30);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (127.46,148.96) {$l$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (128.56,169.08) --
+	(130.90,169.08);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (129.77,168.53) --
+	(129.77,169.61);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (129.77,165.58) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (184.35,188.30) --
+	(184.54,188.30);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (184.44,188.23) --
+	(184.44,188.36);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (184.44,184.80) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(197.73,193.20);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (197.73,188.02) {$p$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(203.80,207.51);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (203.80,203.55) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(211.96,218.84);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (211.96,213.95) {$r$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(190.23,202.18);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (190.23,198.46) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(195.99,206.84);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (195.99,201.76) {$l$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(190.57,195.74);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (190.57,191.73) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(206.12,210.20);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (206.12,206.57) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(163.97,206.95);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (163.97,202.78) {$p$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(207.29,210.05);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (207.29,206.36) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(189.37,210.89);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (189.37,205.97) {$r$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(162.58,180.99);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (162.58,177.03) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(164.35,181.30);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (164.35,175.96) {$l$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(174.25,192.82);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (174.25,188.90) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(208.56,212.97);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (208.56,209.24) {$\kappa$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(173.31,187.78);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (173.31,183.49) {$p$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(186.34,189.50);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (186.34,184.86) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(186.83,195.27);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (186.83,190.35) {$r$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(171.40,185.78);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (171.40,181.92) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(172.25,182.46);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (172.25,177.07) {$l$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(177.05,187.44);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (177.05,183.48) {$\sigma$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(198.75,203.05);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (198.75,199.39) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(188.73,193.42);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (188.73,189.20) {$p$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(182.13,188.43);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (182.13,184.40) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(194.92,203.15);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (194.92,198.24) {$r$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(183.19,198.35);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (183.19,194.59) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(188.63,202.48);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (188.63,197.31) {$l$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(185.42,195.53);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (185.42,191.65) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(207.37,211.45);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,171.00) rectangle (169.31,165.00);
+\definecolor{fillColor}{RGB}{253,104,0}
+
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,159.00) rectangle (169.31,153.00);
-\definecolor{fillColor}{RGB}{253,104,0}
+\definecolor{fillColor}{RGB}{143,161,0}
 
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,147.00) rectangle (169.31,141.00);
-\definecolor{fillColor}{RGB}{143,161,0}
+\definecolor{fillColor}{RGB}{0,195,0}
 
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,135.00) rectangle (169.31,129.00);
-\definecolor{fillColor}{RGB}{0,195,0}
+\definecolor{fillColor}{RGB}{0,219,171}
 
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,123.00) rectangle (169.31,117.00);
-\definecolor{fillColor}{RGB}{0,219,171}
+\definecolor{fillColor}{RGB}{0,216,255}
 
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11,111.00) rectangle (169.31,105.00);
-\definecolor{fillColor}{RGB}{0,216,255}
+\definecolor{fillColor}{RGB}{151,0,255}
 
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11, 99.00) rectangle (169.31, 93.00);
-\definecolor{fillColor}{RGB}{151,0,255}
+\definecolor{fillColor}{RGB}{255,0,255}
 
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11, 87.00) rectangle (169.31, 81.00);
-\definecolor{fillColor}{RGB}{255,0,255}
+\definecolor{fillColor}{RGB}{68,68,68}
 
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.11, 75.00) rectangle (169.31, 69.00);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (178.31,164.56) {Ran};
 
@@
 
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (122.73,169.48) --
+	(125.51,169.48);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (124.17,168.94) --
+	(124.17,170.00);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (124.17,165.59) {$p$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (162.75,161.07) --
+	(163.62,161.07);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (163.19,160.64) --
+	(163.19,161.48);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (163.19,157.57) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (166.27,171.59) --
+	(166.78,171.59);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (166.53,171.40) --
+	(166.53,171.78);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (166.53,166.73) {$r$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (135.90,150.27) --
+	(138.01,150.27);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (136.99,149.92) --
+	(136.99,150.61);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (136.99,146.77) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (135.55,150.30) --
+	(137.81,150.30);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (136.72,149.96) --
+	(136.72,150.63);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (136.72,145.44) {$l$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (104.30,166.98) --
+	(106.72,166.98);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (105.55,166.56) --
+	(105.55,167.38);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (105.55,163.48) {$\sigma$};
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (170.87,174.13) --
+	(171.09,174.13);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (170.98,174.02) --
+	(170.98,174.24);
+\definecolor{drawColor}{RGB}{255,0,109}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (170.98,170.63) {$\kappa$};
+\definecolor{drawColor}{RGB}{253,104,0}
+
 \path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (198.76,211.39) --
@@
 	(199.01,211.61);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (199.01,207.50) {$p$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(203.23,213.82);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (203.23,210.01) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(205.19,217.00);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (205.19,212.10) {$r$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(188.48,205.07);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (188.48,201.33) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(191.09,206.34);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (191.09,201.25) {$l$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(190.97,212.90);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (190.97,209.14) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
@@
 	(207.98,214.24);
-\definecolor{drawColor}{RGB}{255,0,109}
+\definecolor{drawColor}{RGB}{253,104,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (207.98,210.63) {$\kappa$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(166.15,181.76);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (166.15,177.40) {$p$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(195.04,203.77);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (195.04,200.07) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(196.40,205.93);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (196.40,201.01) {$r$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(150.36,170.65);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (150.36,166.66) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(151.96,171.80);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (151.96,166.48) {$l$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(160.53,179.47);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (160.53,175.46) {$\sigma$};
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
@@
 	(199.67,204.05);
-\definecolor{drawColor}{RGB}{253,104,0}
+\definecolor{drawColor}{RGB}{143,161,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (199.67,200.48) {$\kappa$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(170.30,187.62);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (170.30,183.51) {$p$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(193.84,202.79);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (193.84,199.06) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(193.28,202.70);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (193.28,197.80) {$r$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(168.41,181.30);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (168.41,177.55) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(169.18,181.82);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (169.18,176.73) {$l$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(163.15,184.15);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (163.15,180.36) {$\sigma$};
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
@@
 	(198.83,203.99);
-\definecolor{drawColor}{RGB}{143,161,0}
+\definecolor{drawColor}{RGB}{0,195,0}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (198.83,200.42) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (146.41,179.89) --
-	(149.44,179.89);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (147.99,179.46) --
-	(147.99,180.31);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (147.99,176.00) {$p$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (176.30,181.14) --
-	(176.61,181.14);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (176.46,180.91) --
-	(176.46,181.37);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (176.46,177.64) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (177.46,184.80) --
-	(177.71,184.80);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (177.59,184.71) --
-	(177.59,184.89);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (177.59,179.94) {$r$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (142.69,153.57) --
-	(144.45,153.57);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (143.59,153.09) --
-	(143.59,154.03);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (143.59,150.07) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (142.51,153.65) --
-	(144.02,153.65);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (143.28,153.18) --
-	(143.28,154.11);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (143.28,148.79) {$l$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (126.85,168.66) --
-	(130.04,168.66);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (128.52,168.21) --
-	(128.52,169.09);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (128.52,165.16) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (182.99,188.29) --
-	(183.27,188.29);
-
-\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (183.13,188.21) --
-	(183.13,188.36);
-\definecolor{drawColor}{RGB}{0,195,0}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (183.13,184.79) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (146.83,180.07) --
+	(148.74,180.07);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (147.81,179.67) --
+	(147.81,180.47);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (147.81,176.19) {$p$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (176.31,181.10) --
+	(176.62,181.10);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (176.46,180.89) --
+	(176.46,181.31);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (176.46,177.60) {$\mathcal{L}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (177.33,184.82) --
+	(177.54,184.82);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (177.44,184.74) --
+	(177.44,184.91);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (177.44,179.96) {$r$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (142.64,153.88) --
+	(143.90,153.88);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (143.28,153.34) --
+	(143.28,154.40);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (143.28,150.38) {$\bar{r}$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (142.44,153.82) --
+	(143.60,153.82);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (143.03,153.32) --
+	(143.03,154.30);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (143.03,148.96) {$l$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (127.78,169.08) --
+	(129.82,169.08);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (128.83,168.53) --
+	(128.83,169.61);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (128.83,165.58) {$\sigma$};
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (183.08,188.30) --
+	(183.26,188.30);
+
+\path[draw=drawColor,draw opacity=0.33,line width= 0.4pt,line join=round,line cap=round] (183.17,188.23) --
+	(183.17,188.36);
+\definecolor{drawColor}{RGB}{0,219,171}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (183.17,184.80) {$\kappa$};
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(179.56,193.20);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (179.56,188.02) {$p$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(191.68,207.51);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (191.68,203.55) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(198.08,218.84);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (198.08,213.95) {$r$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(178.81,202.18);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (178.81,198.46) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(185.59,206.84);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (185.59,201.76) {$l$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(179.31,195.74);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (179.31,191.73) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
@@
 	(203.57,210.20);
-\definecolor{drawColor}{RGB}{0,219,171}
+\definecolor{drawColor}{RGB}{0,216,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (203.57,206.57) {$\kappa$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(189.58,206.95);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (189.58,202.78) {$p$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(195.33,210.05);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (195.33,206.36) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(196.63,210.89);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (196.63,205.97) {$r$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(166.44,180.99);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (166.44,177.03) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(166.91,181.30);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (166.91,175.96) {$l$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(169.37,192.82);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (169.37,188.90) {$\sigma$};
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
@@
 	(202.50,212.97);
-\definecolor{drawColor}{RGB}{0,216,255}
+\definecolor{drawColor}{RGB}{151,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (202.50,209.24) {$\kappa$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(173.47,187.78);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (173.47,183.49) {$p$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(178.43,189.50);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (178.43,184.86) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(180.10,195.27);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (180.10,190.35) {$r$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(163.72,185.78);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (163.72,181.92) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(165.09,182.46);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (165.09,177.07) {$l$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(167.34,187.44);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (167.34,183.48) {$\sigma$};
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
@@
 	(196.32,203.05);
-\definecolor{drawColor}{RGB}{151,0,255}
+\definecolor{drawColor}{RGB}{255,0,255}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (196.32,199.39) {$\kappa$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(177.51,193.42);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (177.51,189.20) {$p$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(176.31,188.43);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (176.31,184.40) {$\mathcal{L}$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(185.95,203.15);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (185.95,198.24) {$r$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(171.05,198.35);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (171.05,194.59) {$\bar{r}$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(176.66,202.48);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (176.66,197.31) {$l$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(174.79,195.53);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.40] at (174.79,191.65) {$\sigma$};
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 
@@
 	(203.47,211.45);
-\definecolor{drawColor}{RGB}{255,0,255}
+\definecolor{drawColor}{RGB}{68,68,68}
 

### 2020-09-01 benchmarking/benchmarkingVM/ESS_timesettings.tex
complete draft

@@
-% Created by tikzDevice version 0.12.3.1 on 2020-08-31 17:27:56
+% Created by tikzDevice version 0.12.3.1 on 2020-09-01 15:31:18
 % !TEX encoding = UTF-8 Unicode
@@
 \path[draw=drawColor,line width= 0.4pt,dash pattern=on 2pt off 5pt on 2pt off 5pt ,line join=round,line cap=round] ( 49.20,184.67) --
-	(458.76,184.67);
+	(459.67,184.67);
 \definecolor{fillColor}{RGB}{255,0,109}
 
-\path[fill=fillColor] ( 53.30,192.21) circle (  2.25);
+\path[fill=fillColor] ( 52.93,182.48) circle (  2.25);
 \definecolor{fillColor}{RGB}{253,104,0}
 
-\path[fill=fillColor] ( 57.39,192.33) circle (  2.25);
+\path[fill=fillColor] ( 56.66,177.12) circle (  2.25);
 \definecolor{fillColor}{RGB}{143,161,0}
 
-\path[fill=fillColor] ( 61.49,192.07) circle (  2.25);
+\path[fill=fillColor] ( 60.39,177.00) circle (  2.25);
 \definecolor{fillColor}{RGB}{0,195,0}
 
-\path[fill=fillColor] ( 65.58,189.41) circle (  2.25);
+\path[fill=fillColor] ( 64.13,177.26) circle (  2.25);
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[fill=fillColor] ( 69.68,201.89) circle (  2.25);
+\path[fill=fillColor] ( 67.86,179.92) circle (  2.25);
 \definecolor{fillColor}{RGB}{0,216,255}
 
-\path[fill=fillColor] ( 73.77,192.33) circle (  2.25);
+\path[fill=fillColor] ( 71.59,167.44) circle (  2.25);
 \definecolor{fillColor}{RGB}{151,0,255}
 
-\path[fill=fillColor] ( 77.87,193.68) circle (  2.25);
+\path[fill=fillColor] ( 75.32,177.00) circle (  2.25);
 \definecolor{fillColor}{RGB}{255,0,255}
 
-\path[fill=fillColor] ( 81.96,194.75) circle (  2.25);
+\path[fill=fillColor] ( 79.05,175.65) circle (  2.25);
+\definecolor{fillColor}{RGB}{68,68,68}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] ( 53.30,193.62) --
-	( 86.06,193.62);
+\path[fill=fillColor] ( 82.78,174.58) circle (  2.25);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at ( 69.68,297.24) {5.2\% slower};
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] ( 52.93,176.54) --
+	( 86.52,176.54);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at ( 69.72,297.24) {4.5\% slower};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] ( 90.16,  0.00) --
-	( 90.16,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] ( 90.25,  0.00) --
+	( 90.25,357.33);
 \definecolor{fillColor}{RGB}{255,0,109}
 
-\path[fill=fillColor] ( 94.25,131.15) circle (  2.25);
+\path[fill=fillColor] ( 93.98,212.46) circle (  2.25);
 \definecolor{fillColor}{RGB}{253,104,0}
 
-\path[fill=fillColor] ( 98.35,142.51) circle (  2.25);
+\path[fill=fillColor] ( 97.71,238.18) circle (  2.25);
 \definecolor{fillColor}{RGB}{143,161,0}
 
-\path[fill=fillColor] (102.44,137.12) circle (  2.25);
+\path[fill=fillColor] (101.44,226.82) circle (  2.25);
 \definecolor{fillColor}{RGB}{0,195,0}
 
-\path[fill=fillColor] (106.54,133.51) circle (  2.25);
+\path[fill=fillColor] (105.17,232.21) circle (  2.25);
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[fill=fillColor] (110.63,115.30) circle (  2.25);
+\path[fill=fillColor] (108.90,235.82) circle (  2.25);
 \definecolor{fillColor}{RGB}{0,216,255}
 
-\path[fill=fillColor] (114.73,104.29) circle (  2.25);
+\path[fill=fillColor] (112.64,254.03) circle (  2.25);
 \definecolor{fillColor}{RGB}{151,0,255}
 
-\path[fill=fillColor] (118.83,121.85) circle (  2.25);
+\path[fill=fillColor] (116.37,265.04) circle (  2.25);
 \definecolor{fillColor}{RGB}{255,0,255}
 
-\path[fill=fillColor] (122.92, 87.01) circle (  2.25);
+\path[fill=fillColor] (120.10,247.48) circle (  2.25);
+\definecolor{fillColor}{RGB}{68,68,68}
+
+\path[fill=fillColor] (123.83,282.32) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] ( 94.25,122.43) --
-	(127.02,122.43);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] ( 93.98,244.94) --
+	(127.56,244.94);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (110.63,297.24) {29\% faster};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (110.77,297.24) {40\% faster};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (131.11,  0.00) --
-	(131.11,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (131.29,  0.00) --
+	(131.29,357.33);
 \definecolor{fillColor}{RGB}{255,0,109}
 
-\path[fill=fillColor] (135.21,210.25) circle (  2.25);
+\path[fill=fillColor] (135.03,179.49) circle (  2.25);
 \definecolor{fillColor}{RGB}{253,104,0}
 
-\path[fill=fillColor] (139.30,199.78) circle (  2.25);
+\path[fill=fillColor] (138.76,159.08) circle (  2.25);
 \definecolor{fillColor}{RGB}{143,161,0}
 
-\path[fill=fillColor] (143.40,200.44) circle (  2.25);
+\path[fill=fillColor] (142.49,169.55) circle (  2.25);
 \definecolor{fillColor}{RGB}{0,195,0}
 
-\path[fill=fillColor] (147.49,195.49) circle (  2.25);
+\path[fill=fillColor] (146.22,168.89) circle (  2.25);
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[fill=fillColor] (151.59,212.96) circle (  2.25);
+\path[fill=fillColor] (149.95,173.84) circle (  2.25);
 \definecolor{fillColor}{RGB}{0,216,255}
 
-\path[fill=fillColor] (155.69,234.21) circle (  2.25);
+\path[fill=fillColor] (153.68,156.37) circle (  2.25);
 \definecolor{fillColor}{RGB}{151,0,255}
 
-\path[fill=fillColor] (159.78,210.45) circle (  2.25);
+\path[fill=fillColor] (157.42,135.12) circle (  2.25);
 \definecolor{fillColor}{RGB}{255,0,255}
 
-\path[fill=fillColor] (163.88,228.46) circle (  2.25);
+\path[fill=fillColor] (161.15,158.88) circle (  2.25);
+\definecolor{fillColor}{RGB}{68,68,68}
+
+\path[fill=fillColor] (164.88,140.87) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (135.21,211.98) --
-	(167.97,211.98);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (135.03,160.77) --
+	(168.61,160.77);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (151.59,297.24) {17\% slower};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (151.82,297.24) {13\% slower};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (172.07,  0.00) --
-	(172.07,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (172.34,  0.00) --
+	(172.34,357.33);
 \definecolor{fillColor}{RGB}{255,0,109}
 
-\path[fill=fillColor] (176.16,137.47) circle (  2.25);
+\path[fill=fillColor] (176.07,216.47) circle (  2.25);
 \definecolor{fillColor}{RGB}{253,104,0}
 
-\path[fill=fillColor] (180.26,147.34) circle (  2.25);
+\path[fill=fillColor] (179.80,231.86) circle (  2.25);
 \definecolor{fillColor}{RGB}{143,161,0}
 
-\path[fill=fillColor] (184.36,140.19) circle (  2.25);
+\path[fill=fillColor] (183.54,221.99) circle (  2.25);
 \definecolor{fillColor}{RGB}{0,195,0}
 
-\path[fill=fillColor] (188.45,140.07) circle (  2.25);
+\path[fill=fillColor] (187.27,229.14) circle (  2.25);
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[fill=fillColor] (192.55,140.34) circle (  2.25);
+\path[fill=fillColor] (191.00,229.26) circle (  2.25);
 \definecolor{fillColor}{RGB}{0,216,255}
 
-\path[fill=fillColor] (196.64,103.65) circle (  2.25);
+\path[fill=fillColor] (194.73,228.99) circle (  2.25);
 \definecolor{fillColor}{RGB}{151,0,255}
 
-\path[fill=fillColor] (200.74,122.50) circle (  2.25);
+\path[fill=fillColor] (198.46,265.68) circle (  2.25);
 \definecolor{fillColor}{RGB}{255,0,255}
 
-\path[fill=fillColor] (204.83,113.14) circle (  2.25);
+\path[fill=fillColor] (202.19,246.83) circle (  2.25);
+\definecolor{fillColor}{RGB}{68,68,68}
+
+\path[fill=fillColor] (205.93,256.19) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (176.16,131.17) --
-	(208.93,131.17);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (176.07,236.95) --
+	(209.66,236.95);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (192.55,297.24) {26\% faster};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (192.86,297.24) {34\% faster};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (213.02,  0.00) --
-	(213.02,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (213.39,  0.00) --
+	(213.39,357.33);
 \definecolor{fillColor}{RGB}{255,0,109}
 
-\path[fill=fillColor] (217.12,221.94) circle (  2.25);
+\path[fill=fillColor] (217.12,166.67) circle (  2.25);
 \definecolor{fillColor}{RGB}{253,104,0}
 
-\path[fill=fillColor] (221.22,222.13) circle (  2.25);
+\path[fill=fillColor] (220.85,147.39) circle (  2.25);
 \definecolor{fillColor}{RGB}{143,161,0}
 
-\path[fill=fillColor] (225.31,218.65) circle (  2.25);
+\path[fill=fillColor] (224.58,147.20) circle (  2.25);
 \definecolor{fillColor}{RGB}{0,195,0}
 
-\path[fill=fillColor] (229.41,207.34) circle (  2.25);
+\path[fill=fillColor] (228.31,150.68) circle (  2.25);
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[fill=fillColor] (233.50,217.59) circle (  2.25);
+\path[fill=fillColor] (232.05,161.99) circle (  2.25);
 \definecolor{fillColor}{RGB}{0,216,255}
 
-\path[fill=fillColor] (237.60,198.68) circle (  2.25);
+\path[fill=fillColor] (235.78,151.74) circle (  2.25);
 \definecolor{fillColor}{RGB}{151,0,255}
 
-\path[fill=fillColor] (241.69,213.67) circle (  2.25);
+\path[fill=fillColor] (239.51,170.65) circle (  2.25);
 \definecolor{fillColor}{RGB}{255,0,255}
 
-\path[fill=fillColor] (245.79,189.78) circle (  2.25);
+\path[fill=fillColor] (243.24,155.66) circle (  2.25);
+\definecolor{fillColor}{RGB}{68,68,68}
+
+\path[fill=fillColor] (246.97,179.55) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (217.12,211.56) --
-	(249.88,211.56);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (217.12,159.38) --
+	(250.70,159.38);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (233.50,297.24) {16\% slower};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (233.91,297.24) {13\% slower};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (253.98,  0.00) --
-	(253.98,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (254.44,  0.00) --
+	(254.44,357.33);
 \definecolor{fillColor}{RGB}{255,0,109}
 
-\path[fill=fillColor] (258.08,229.80) circle (  2.25);
+\path[fill=fillColor] (258.17,167.17) circle (  2.25);
 \definecolor{fillColor}{RGB}{253,104,0}
 
-\path[fill=fillColor] (262.17,227.84) circle (  2.25);
+\path[fill=fillColor] (261.90,139.53) circle (  2.25);
 \definecolor{fillColor}{RGB}{143,161,0}
 
-\path[fill=fillColor] (266.27,228.47) circle (  2.25);
+\path[fill=fillColor] (265.63,141.49) circle (  2.25);
 \definecolor{fillColor}{RGB}{0,195,0}
 
-\path[fill=fillColor] (270.36,216.45) circle (  2.25);
+\path[fill=fillColor] (269.36,140.86) circle (  2.25);
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[fill=fillColor] (274.46,237.37) circle (  2.25);
+\path[fill=fillColor] (273.09,152.88) circle (  2.25);
 \definecolor{fillColor}{RGB}{0,216,255}
 
-\path[fill=fillColor] (278.55,221.39) circle (  2.25);
+\path[fill=fillColor] (276.82,131.96) circle (  2.25);
 \definecolor{fillColor}{RGB}{151,0,255}
 
-\path[fill=fillColor] (282.65,219.64) circle (  2.25);
+\path[fill=fillColor] (280.56,147.94) circle (  2.25);
 \definecolor{fillColor}{RGB}{255,0,255}
 
-\path[fill=fillColor] (286.75,212.76) circle (  2.25);
+\path[fill=fillColor] (284.29,149.69) circle (  2.25);
+\definecolor{fillColor}{RGB}{68,68,68}
+
+\path[fill=fillColor] (288.02,156.57) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (258.08,224.38) --
-	(290.84,224.38);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (258.17,147.85) --
+	(291.75,147.85);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (274.46,297.24) {25\% slower};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (274.96,297.24) {19\% slower};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (294.94,  0.00) --
-	(294.94,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (295.48,  0.00) --
+	(295.48,357.33);
 \definecolor{fillColor}{RGB}{255,0,109}
 
-\path[fill=fillColor] (299.03,243.36) circle (  2.25);
+\path[fill=fillColor] (299.21,164.07) circle (  2.25);
 \definecolor{fillColor}{RGB}{253,104,0}
 
-\path[fill=fillColor] (303.13,239.88) circle (  2.25);
+\path[fill=fillColor] (302.95,125.97) circle (  2.25);
 \definecolor{fillColor}{RGB}{143,161,0}
 
-\path[fill=fillColor] (307.22,240.25) circle (  2.25);
+\path[fill=fillColor] (306.68,129.45) circle (  2.25);
 \definecolor{fillColor}{RGB}{0,195,0}
 
-\path[fill=fillColor] (311.32,228.38) circle (  2.25);
+\path[fill=fillColor] (310.41,129.08) circle (  2.25);
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[fill=fillColor] (315.41,250.89) circle (  2.25);
+\path[fill=fillColor] (314.14,140.95) circle (  2.25);
 \definecolor{fillColor}{RGB}{0,216,255}
 
-\path[fill=fillColor] (319.51,247.98) circle (  2.25);
+\path[fill=fillColor] (317.87,118.44) circle (  2.25);
 \definecolor{fillColor}{RGB}{151,0,255}
 
-\path[fill=fillColor] (323.61,232.84) circle (  2.25);
+\path[fill=fillColor] (321.60,121.35) circle (  2.25);
 \definecolor{fillColor}{RGB}{255,0,255}
 
-\path[fill=fillColor] (327.70,224.69) circle (  2.25);
+\path[fill=fillColor] (325.34,136.49) circle (  2.25);
+\definecolor{fillColor}{RGB}{68,68,68}
+
+\path[fill=fillColor] (329.07,144.64) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (299.03,238.74) --
-	(331.80,238.74);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (299.21,135.00) --
+	(332.80,135.00);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (315.41,297.24) {35\% slower};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (316.01,297.24) {24\% slower};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (335.89,  0.00) --
-	(335.89,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (336.53,  0.00) --
+	(336.53,357.33);
 \definecolor{fillColor}{RGB}{255,0,109}
 
-\path[fill=fillColor] (339.99,133.85) circle (  2.25);
+\path[fill=fillColor] (340.26,216.42) circle (  2.25);
 \definecolor{fillColor}{RGB}{253,104,0}
 
-\path[fill=fillColor] (344.08,146.75) circle (  2.25);
+\path[fill=fillColor] (343.99,235.48) circle (  2.25);
 \definecolor{fillColor}{RGB}{143,161,0}
 
-\path[fill=fillColor] (348.18,141.24) circle (  2.25);
+\path[fill=fillColor] (347.72,222.58) circle (  2.25);
 \definecolor{fillColor}{RGB}{0,195,0}
 
-\path[fill=fillColor] (352.28,140.02) circle (  2.25);
+\path[fill=fillColor] (351.46,228.09) circle (  2.25);
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[fill=fillColor] (356.37,135.64) circle (  2.25);
+\path[fill=fillColor] (355.19,229.31) circle (  2.25);
 \definecolor{fillColor}{RGB}{0,216,255}
 
-\path[fill=fillColor] (360.47,103.87) circle (  2.25);
+\path[fill=fillColor] (358.92,233.69) circle (  2.25);
 \definecolor{fillColor}{RGB}{151,0,255}
 
-\path[fill=fillColor] (364.56,119.49) circle (  2.25);
+\path[fill=fillColor] (362.65,265.46) circle (  2.25);
 \definecolor{fillColor}{RGB}{255,0,255}
 
-\path[fill=fillColor] (368.66,109.12) circle (  2.25);
+\path[fill=fillColor] (366.38,249.84) circle (  2.25);
+\definecolor{fillColor}{RGB}{68,68,68}
+
+\path[fill=fillColor] (370.11,260.21) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (339.99,129.36) --
-	(372.75,129.36);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (340.26,238.62) --
+	(373.85,238.62);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (356.37,297.24) {27\% faster};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (357.05,297.24) {35\% faster};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (376.85,  0.00) --
-	(376.85,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (377.58,  0.00) --
+	(377.58,357.33);
 \definecolor{fillColor}{RGB}{255,0,109}
 
-\path[fill=fillColor] (380.94,141.02) circle (  2.25);
+\path[fill=fillColor] (381.31,218.13) circle (  2.25);
 \definecolor{fillColor}{RGB}{253,104,0}
 
-\path[fill=fillColor] (385.04,149.13) circle (  2.25);
+\path[fill=fillColor] (385.04,228.31) circle (  2.25);
 \definecolor{fillColor}{RGB}{143,161,0}
 
-\path[fill=fillColor] (389.14,142.97) circle (  2.25);
+\path[fill=fillColor] (388.77,220.20) circle (  2.25);
 \definecolor{fillColor}{RGB}{0,195,0}
 
-\path[fill=fillColor] (393.23,139.61) circle (  2.25);
+\path[fill=fillColor] (392.50,226.36) circle (  2.25);
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[fill=fillColor] (397.33,137.57) circle (  2.25);
+\path[fill=fillColor] (396.23,229.72) circle (  2.25);
 \definecolor{fillColor}{RGB}{0,216,255}
 
-\path[fill=fillColor] (401.42,114.39) circle (  2.25);
+\path[fill=fillColor] (399.97,231.76) circle (  2.25);
 \definecolor{fillColor}{RGB}{151,0,255}
 
-\path[fill=fillColor] (405.52,129.13) circle (  2.25);
+\path[fill=fillColor] (403.70,254.94) circle (  2.25);
 \definecolor{fillColor}{RGB}{255,0,255}
 
-\path[fill=fillColor] (409.61,140.48) circle (  2.25);
+\path[fill=fillColor] (407.43,240.20) circle (  2.25);
+\definecolor{fillColor}{RGB}{68,68,68}
+
+\path[fill=fillColor] (411.16,228.85) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (380.94,137.06) --
-	(413.71,137.06);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (381.31,231.25) --
+	(414.89,231.25);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (397.33,297.24) {23\% faster};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (398.10,297.24) {30\% faster};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (417.80,  0.00) --
-	(417.80,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (418.62,  0.00) --
+	(418.62,357.33);
 \definecolor{fillColor}{RGB}{255,0,109}
 
-\path[fill=fillColor] (421.90,147.24) circle (  2.25);
+\path[fill=fillColor] (422.36,214.96) circle (  2.25);
 \definecolor{fillColor}{RGB}{253,104,0}
 
-\path[fill=fillColor] (426.00,156.87) circle (  2.25);
+\path[fill=fillColor] (426.09,222.09) circle (  2.25);
 \definecolor{fillColor}{RGB}{143,161,0}
 
-\path[fill=fillColor] (430.09,147.29) circle (  2.25);
+\path[fill=fillColor] (429.82,212.46) circle (  2.25);
 \definecolor{fillColor}{RGB}{0,195,0}
 
-\path[fill=fillColor] (434.19,143.53) circle (  2.25);
+\path[fill=fillColor] (433.55,222.04) circle (  2.25);
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[fill=fillColor] (438.28,144.92) circle (  2.25);
+\path[fill=fillColor] (437.28,225.80) circle (  2.25);
 \definecolor{fillColor}{RGB}{0,216,255}
 
-\path[fill=fillColor] (442.38,124.70) circle (  2.25);
+\path[fill=fillColor] (441.01,224.41) circle (  2.25);
 \definecolor{fillColor}{RGB}{151,0,255}
 
-\path[fill=fillColor] (446.47,142.61) circle (  2.25);
+\path[fill=fillColor] (444.74,244.63) circle (  2.25);
 \definecolor{fillColor}{RGB}{255,0,255}
 
-\path[fill=fillColor] (450.57,147.18) circle (  2.25);
+\path[fill=fillColor] (448.48,226.72) circle (  2.25);
+\definecolor{fillColor}{RGB}{68,68,68}
+
+\path[fill=fillColor] (452.21,222.15) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (421.90,144.49) --
-	(454.67,144.49);
+\path[draw=drawColor,line width= 0.2pt,line join=round,line cap=round] (422.36,224.13) --
+	(455.94,224.13);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (438.28,297.24) {20\% faster};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.70] at (439.15,297.24) {25\% faster};
 \definecolor{drawColor}{RGB}{105,105,105}
 
-\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (458.76,  0.00) --
-	(458.76,357.33);
+\path[draw=drawColor,draw opacity=0.60,line width= 0.2pt,line join=round,line cap=round] (459.67,  0.00) --
+	(459.67,357.33);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 69.68, 61.20) -- ( 69.68, 55.20);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 69.72, 61.20) -- ( 69.72, 55.20);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (110.63, 61.20) -- (110.63, 55.20);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (110.77, 61.20) -- (110.77, 55.20);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.59, 61.20) -- (151.59, 55.20);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.82, 61.20) -- (151.82, 55.20);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.55, 61.20) -- (192.55, 55.20);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (192.86, 61.20) -- (192.86, 55.20);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (233.50, 61.20) -- (233.50, 55.20);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (233.91, 61.20) -- (233.91, 55.20);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (274.46, 61.20) -- (274.46, 55.20);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (274.96, 61.20) -- (274.96, 55.20);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (315.41, 61.20) -- (315.41, 55.20);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (316.01, 61.20) -- (316.01, 55.20);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (356.37, 61.20) -- (356.37, 55.20);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (357.05, 61.20) -- (357.05, 55.20);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (397.33, 61.20) -- (397.33, 55.20);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (398.10, 61.20) -- (398.10, 55.20);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.28, 61.20) -- (438.28, 55.20);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (439.15, 61.20) -- (439.15, 55.20);
 
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at ( 71.74, 49.20) {adapt(\textit{cat})};
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at ( 71.79, 49.20) {adapt(\textit{cat})};
 
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (112.70, 49.20) {nocons(\textit{real})};
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (112.84, 49.20) {nocons(\textit{real})};
 
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (153.66, 49.20) {cons(\textit{real})};
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (153.88, 49.20) {cons(\textit{real})};
 
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (194.61, 49.20) {adapt(\textit{real})};
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (194.93, 49.20) {adapt(\textit{real})};
 
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (235.57, 49.20) {nocons(\textit{quant})};
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (235.98, 49.20) {nocons(\textit{quant})};
 
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (276.52, 49.20) {cons(\textit{quant})};
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (277.03, 49.20) {cons(\textit{quant})};
 
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (317.48, 49.20) {adapt(\textit{quant})};
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (318.07, 49.20) {adapt(\textit{quant})};
 
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (358.44, 49.20) {Bactrian};
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (359.12, 49.20) {Bactrian};
 
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (399.39, 49.20) {NER};
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (400.17, 49.20) {NER};
 
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (440.35, 49.20) {AVMVN};
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.60] at (441.21, 49.20) {AVMVN};
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (485.99,229.67) rectangle (493.19,223.67);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (485.99,235.67) rectangle (493.19,229.67);
 \definecolor{fillColor}{RGB}{253,104,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (485.99,217.67) rectangle (493.19,211.67);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (485.99,223.67) rectangle (493.19,217.67);
 \definecolor{fillColor}{RGB}{143,161,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (485.99,205.67) rectangle (493.19,199.67);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (485.99,211.67) rectangle (493.19,205.67);
 \definecolor{fillColor}{RGB}{0,195,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (485.99,193.67) rectangle (493.19,187.67);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (485.99,199.67) rectangle (493.19,193.67);
 \definecolor{fillColor}{RGB}{0,219,171}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (485.99,181.67) rectangle (493.19,175.67);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (485.99,187.67) rectangle (493.19,181.67);
 \definecolor{fillColor}{RGB}{0,216,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (485.99,169.67) rectangle (493.19,163.67);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (485.99,175.67) rectangle (493.19,169.67);
 \definecolor{fillColor}{RGB}{151,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (485.99,157.67) rectangle (493.19,151.67);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (485.99,163.67) rectangle (493.19,157.67);
 \definecolor{fillColor}{RGB}{255,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (485.99,145.67) rectangle (493.19,139.67);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (485.99,151.67) rectangle (493.19,145.67);
+\definecolor{fillColor}{RGB}{68,68,68}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (502.19,223.22) {Cognato};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (485.99,139.67) rectangle (493.19,133.67);
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (502.19,211.22) {Dornburg};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (502.19,229.22) {Ran};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (502.19,199.22) {Sauquet};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (502.19,217.22) {Cognato};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (502.19,187.22) {Broughton};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (502.19,205.22) {Dornburg};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (502.19,175.22) {Kawahara};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (502.19,193.22) {Sauquet};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (502.19,163.22) {simulated};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (502.19,181.22) {Broughton};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (502.19,151.22) {Rightmyer};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (502.19,169.22) {Kawahara};
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (502.19,139.22) {Moyle};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (502.19,157.22) {simulated};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (502.19,145.22) {Rightmyer};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (502.19,133.22) {Moyle};
 \end{scope}

### 2020-09-01 manuscript.tex
complete draft

@@
 % to minimize problems and delays during our production
-% process. Please follow the template instructions
+% process. Please follow the template instructionssum 
 % whenever possible.
@@
 This assumption forms the basis of phylogenetics, under which the evolutionary trees and divergence dates of life forms are inferred from biological sequences, such as nucleic and amino acids \cite{douzery2003local, drummond2006relaxed}.
-In Bayesian phylogenetics, these trees and their associated parameters are estimated as probabilitiy distributions \cite{kuhner1995estimating, larget1999markov, mau1999bayesian}. 
+In Bayesian phylogenetics, these trees and their associated parameters are estimated as probability distributions \cite{kuhner1995estimating, larget1999markov, mau1999bayesian}. 
 Statistical inference can be performed by the Markov chain Monte Carlo (MCMC) algorithm \cite{metropolis53, hastings70} using platforms such as BEAST \cite{drummond2012bayesian}, BEAST2 \cite{bouckaert2019beast}, MrBayes \cite{ronquist2012mrbayes}, and RevBayes \cite{hohna2016revbayes}.
 
-The simplest phylogenetic clock model -- the strick clock -- makes the mathematically convenient assumption that the evolutionary rate is constant across all lineages \cite{zuckerkandl1965evolutionary, kuhner1995estimating, larget1999markov}.
+The simplest phylogenetic clock model -- the strict clock -- makes the mathematically convenient assumption that the evolutionary rate is constant across all lineages \cite{zuckerkandl1965evolutionary, kuhner1995estimating, larget1999markov}.
 % Early examples?
@@
 
-With the overwhelming availabilty of biological sequence data, the development of efficient Bayesian phylogenetic methods is more important than ever. 
+With the overwhelming availability of biological sequence data, the development of efficient Bayesian phylogenetic methods is more important than ever. 
 The performance of MCMC is dependent not only on computational runtime but also the efficacy of an
@@
 The weight of an operator determines the probability of the operator being selected and is typically fixed throughout MCMC.
-In BEAST2, operators can have its own tunable parameter $s$ which determines the step size of the operator, and this term is learned over the course of the MCMC \cite{bouckaert2019beast}. 
+In BEAST2, operators can have their own tunable parameter $s$ which determines the step size of the operator, and this term is learned over the course of the MCMC \cite{bouckaert2019beast}. 
 Here, we define clock model operators as those which generate proposals for either $\vec{\mathcal{R}}^{\,}$ or $\sigma$.
@@
 \begin{tabular}{l p{4.2cm} l l} 
- \hline
  Operator & Description & Parameters & Parameterisations  \\
@@
 & $\vec{\mathcal{R}}^{\,}, \sigma$ & \textit{real}, \textit{quant} \\
- \hline
 \end{tabular}
@@
 
-The family of constant distance operators (\texttt{ConstantDistance}, \texttt{SimpleDistance}, and \texttt{SmallPulley} \cite{zhang2020improving}) are best suited for larger datasets (or datasets with strong signal) where the likelihood distribution is peaked (\textbf{Fig.
-\ref{fig:rateparams}}).
+The family of constant distance operators (\texttt{ConstantDistance}, \texttt{SimpleDistance}, and \texttt{SmallPulley} \cite{zhang2020improving}) are best suited for larger datasets (or datasets with strong signal) where the likelihood distribution is peaked (\textbf{Fig \ref{fig:rateparams}}).
 While simple one dimensional operators such as \texttt{RandomWalk} or \texttt{Scale} must make small steps in order to stay ``on the ridge'' of the likelihood function, the constant distance operators ``wander along the ridge''  by ensuring that genetic distances are constant after the proposal.
@@
  This discrepancy is even stronger for larger datasets and thus necessitates the use of operators such as \texttt{ConstantDistance} which account for correlations between branch lengths and rates. }
-\label{fig:rateparams}
+\label{fig:landscape}
 \end{figure}
 
- \texttt{Scale} and \texttt{CisScale} both operate on the clock model standard deviation $\sigma$ however they behave differently in the \textit{real} and \textit{quant} parameterisations (\textbf{Fig.
-\ref{fig:clockSDoperators}}).
+ \texttt{Scale} and \texttt{CisScale} both operate on the clock model standard deviation $\sigma$ however they behave differently in the \textit{real} and \textit{quant} parameterisations (\textbf{Fig \ref{fig:clockSDoperators}}).
 In \textit{real}, large proposals of $\sigma \rightarrow \sigma^\prime$ made by  \texttt{Scale} are likely to be rejected due to large penalties in clock model prior $p(\vec{\mathcal{R}}^{\,}|\sigma^\prime)$.
@@
 $r(\vec{\mathcal{R}}^{\,}) = r(\vec{\mathcal{R}}^{\,\prime})$.
-Overall, \texttt{Scale} and \texttt{CisScale} propose rates/quantiles in the opposite (trans) or same (cis) space that the clock model is parameterised under (\textbf{Fig.
-\ref{fig:clockSDoperators}}).
+In summary, \texttt{Scale} and \texttt{CisScale} propose rates/quantiles in the opposite (trans) or same (cis) space that the clock model is parameterised under (\textbf{Fig \ref{fig:clockSDoperators}}).
 
@@
 where \texttt{RF} is the Robinson-Foulds tree distance \cite{robinson1981comparison}, and $|p|$ is the number of dimensions of numerical parameter $p$ (1 for $\sigma$, $2N-2$ for $\vec{\mathcal{R}}^{\,}$, and $2N-1$ for node heights $t$).
-The remaining terms are trained during the second and third phases: the cumulative computational runtime spent on each operator $\mathbb{T}(\omega_i)$, the sample standard deviation $\sigma_p$ of each numerical parameter $p$, and the sum distances $\sum_x \mathbb{D}(x_p, x_p^\prime)$.
+The remaining terms are trained during the second and third phases: the cumulative computational runtime spent on each operator $\mathbb{T}(\omega_i)$, the sample standard deviation $\sigma_p$ of each numerical parameter $p$, and the summed distances $\sum_x \mathbb{D}(x_p, x_p^\prime)$.
 
@@
 
-Datasets with strong signal (or large $L$) are likely to achieve faster convergence when the more precise and meticulous kinds of operators are employed, such as those informed by correlations within the posterior distribution (\textbf{Fig.
-\ref{fig:rateparams}}).
+Datasets with strong signal (or large $L$) are likely to achieve faster convergence when the more precise and meticulous kinds of operators are employed, such as those informed by correlations within the posterior distribution (\textbf{Fig \ref{fig:landscape}}).
 Whereas, datasets which contain very poor signal (or small $L$) are likely to mix faster when more weight is placed on bold operators. 
@@
 
-The step size of a proposal kernal $q(x^\prime|x)$ should be such that the proposed state $x^\prime$ is sufficiently far from the current state $x$ to explore vast areas of parameter space, but not so large that the proposal is rejected too often \cite{roberts1997weak}.
+The step size of a proposal kernel $q(x^\prime|x)$ should be such that the proposed state $x^\prime$ is sufficiently far from the current state $x$ to explore vast areas of parameter space, but not so large that the proposal is rejected too often \cite{roberts1997weak}.
 Operators which attain an acceptance probability of 0.234 are often considered to have arrived at a suitable midpoint between these two extremes \cite{bouckaert2019beast, roberts1997weak}.
@@
 When $m=0$, the Bactrian distribution is equivalent to a $\text{Normal}(0, 1)$ distribution.
-As $m \rightarrow 1$, the distribution becomes increasingly bimodal (\textbf{Fig.
-\ref{fig:bactrian}}).
+As $m \rightarrow 1$, the distribution becomes increasingly bimodal (\textbf{Fig \ref{fig:bactrian}}).
 Yang et al.
@@
 
-% Give the equation of the Uniform + Bactrian kernals
+% Give the equation of the Uniform + Bactrian kernels
 % Fig: Bactrian m=0, 0.92, 0.95, 0.98, + Uniform(-1,1)
@@
 
-The \texttt{NarrowExchange} operator \cite{drummond2002estimating}, used widely in BEAST \cite{drummond2012bayesian,suchard2018bayesian} and BEAST2 \cite{bouckaert2019beast}, is similar to nearest-neighbour-interchange \cite{semple2003phylogenetics}, and works as follows (\textbf{Fig.
-\ref{fig:narrowexchange}}):
+The \texttt{NarrowExchange} operator \cite{drummond2002estimating}, used widely in BEAST \cite{drummond2012bayesian,suchard2018bayesian} and BEAST2 \cite{bouckaert2019beast}, is similar to nearest-neighbour-interchange \cite{semple2003phylogenetics}, and works as follows (\textbf{Fig \ref{fig:narrowexchange}}):
 
@@
 
-Lakner et al.
-2008 \cite{lakner2008efficiency} found that tree operators which perterb topology (such as nearest-neighbour-interchange and subtree-prune-and-regraft \cite{semple2003phylogenetics}) consistently perform better than those which also change branch lengths (such as LOCAL \cite{simon1998local} and Continuous Change \cite{jow2002bayesian}).
-If \texttt{NarrowExchange} was adapted the relaxed clock model by ensuring that genetic distances remain constant after the proposal (akin to the constant distance operators \cite{zhang2020improving}), then its ability to traverse the state space may improve.
-This may in turn permit proposing a new node height $t_D$ and therefore changing branch lengths.
+We hypothesised that if \texttt{NarrowExchange} was adapted to the relaxed clock model by ensuring that genetic distances remain constant after the proposal (akin to the constant distance operators \cite{zhang2020improving}), then its ability to traverse the state space may improve.
 
@@
 NER (and NERw) are compatible with both the \textit{real} and \textit{quant} parameterisations.
-Analagous to the \texttt{ConstantDistance} operator, the proposed rates ensure that the genetic distances between nodes $A$, $B$, $C$, and $E$ are constant. 
+Analogous to the \texttt{ConstantDistance} operator, the proposed rates ensure that the genetic distances between nodes $A$, $B$, $C$, and $E$ are constant. 
 There are six pairwise distance between these four nodes and therefore six constraints:
@@
 
-\paragraph{2. Solving Jacobian determinants.} The determinant of the Jacobian matrix $J$ is required for computng the Green ratio of the proposal. $J$ is defined as
+\paragraph{2. Solving Jacobian determinants.} The determinant of the Jacobian matrix $J$ is required for computing the Green ratio of the proposal. $J$ is defined as
 
@@
 Automated generation of BEAST2 operators.} Java class files are generated using string processing.
-Each class corresponds to a single operator, extends the class of a meta-NER-operator, and is comprised of the solutions found in \textbf{1} and the Jacobian determinant found in \textbf{2}.
+Each class corresponds to a single operator, extends the class of a meta-NER-operator, and consists of the solutions found in \textbf{1} and the Jacobian determinant found in \textbf{2}.
 $|J|$ is further augmented if the \textit{quant} parameterisation is employed (\textbf{\nameref{sect:S1Appendix}}).
@@
 $\mathcal{D}_{AB}$) or between $B$ and $C$ (i.e.
-$\mathcal{D}_{BC}$) usually performed worse than the standard \texttt{NarrowExchange} operator (\textbf{Fig.
-\ref{fig:acceptanceRateScreening}}).
+$\mathcal{D}_{BC}$) usually performed worse than the standard \texttt{NarrowExchange} operator (\textbf{Fig \ref{fig:acceptanceRateScreening}}).
 This is an intuitive result. 
@@
 
-\textbf{Fig.
-\ref{fig:acceptanceRateScreening}} also reveals a cluster of NER variants which -- under the conditions of the simulation --  performed better than the null operator $\text{NER}\{\}$ around 25\% of the time and performed worse around 10\% of the time.
+\textbf{Fig \ref{fig:acceptanceRateScreening}} also reveals a cluster of NER variants which -- under the conditions of the simulation --  performed better than the null operator $\text{NER}\{\}$ around 25\% of the time and performed worse around 10\% of the time.
 One such operator is  $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$  (\textbf{Algorithm \ref{alg:NER2}}). 
@@
 %, such as \texttt{AdaptiveOperatorSampler},
-Adaptive operators undergo a training process to improve their efficiency over time \cite{roberts2007coupling}. 
-For example, the conditional clade probabilities of neighbouring trees can serve as the basis of adaptive tree operators \cite{hohna2012guided,zhang2020using,meyer2019adaptive},
-and the mirror kernel learns a target distribution which acts as a `mirror image' of the current point $x$ \cite{thawornwattana2018designing}.  
-The \texttt{AdaptiveOperatorSampler} operator, introduced in this article, learns the weight of sub-operators.
-Finally, the adaptable variance multivariate normal (AVMVN) kernel  learns correlations between parameters during MCMC \cite{baele2017adaptive,suchard2018bayesian}.
-Baele et al.
-2017  observed a large increase ($\approx 5-10 \times$) in sampling efficiency from using the AVMVN kernel on clock rates XXX(check)XXX and substitution model parameters across partitions \cite{baele2017adaptive}.
-
-In this article we consider application of the AVMVN kernel to the branch rates of leaf nodes. 
+The adaptable variance multivariate normal (AVMVN) kernel  learns correlations between parameters during MCMC \cite{baele2017adaptive,suchard2018bayesian}. 
+Baele et al. 2017  observed a large increase ($\approx 5-10 \times$) in sampling efficiency from using the AVMVN kernel substitution model parameters \cite{baele2017adaptive}.  
+Here, we consider application of the AVMVN kernel to the branch rates of leaf nodes. 
 This operator, referred to as \texttt{LeafAVMVN}, is not readily applicable to internal node branch rates due to their dependencies on tree topology.
 
-\subsubsection*{AVMVN kernel}
+\subsubsection*{Leaf rate AVMVN kernel}
 
@@
 $\beta \; (= 0.05)$ is a constant which determines the fraction of the proposal determined by the identity matrix $\mathbb{I}_N$, as opposed to the covariance matrix $\Sigma_D$ which is trained during MCMC.
-
-The AVMVN proposal kernel is computed as
-
-\begin{align}
-	x^\prime &\leftarrow x + \sum\limits_{i=1}^N \sum\limits_{j=i}^N c_{i,j} \times s\Sigma \\
-	\text {where }  c &= \text{cholesky} \left( (1-\beta) \frac{\Sigma_N}{N} + \beta \frac{\mathbb{I}_N}{N} \right).
-\end{align}
-
-The cholesky$(Y)$ decomposition returns a lower diagonal matrix $L$, with positive real diagonal entries, such that $Y = LL^\prime$ \cite{lindstrom1988newton, pourahmadi2007cholesky}.
+Our BEAST2 implementation of the AVMVN kernel is adapted from that of BEAST \cite{suchard2018bayesian}.
+
+%The AVMVN proposal kernel is computed as
+
+%\begin{align}
+%	x^\prime &\leftarrow x + \sum\limits_{i=1}^N \sum\limits_{j=i}^N c_{i,j} \times s\Sigma \\
+%	\text {where }  c &= \text{cholesky} \left( (1-\beta) \frac{\Sigma_N}{N} + \beta \frac{\mathbb{I}_N}{N} \right).
+%\end{align}
+
+%The cholesky$(Y)$ decomposition returns a lower diagonal matrix $L$, with positive real diagonal entries, such that $Y = LL^\prime$ \cite{lindstrom1988newton, pourahmadi2007cholesky}.
 $s$ is a tunable step size parameter and $\Sigma$ is a random variable drawn from a proposal kernel (uniform or Bactrian for instance).
-Our BEAST2 implementation of the AVMVN kernel is adapted from that of BEAST \cite{suchard2018bayesian}.
-
-In \nameref{sect:results}, we evaluate the \texttt{LeafAVMVN} operator for its ability to estimate leaf rates. 
-As the size of the covariance matrix $\Sigma_N$ grows with the number of taxa $N$, AVMVN is hypothesised to work well on small trees but become less efficient with larger taxon sets.
+
+\texttt{LeafAVMVN} has the advantage of operating on all $N$ leaf rates simultaneously (as well as learning their correlations), as opposed to \texttt{ConstantDistance} which operates on at most 2, or \texttt{Scale} which operates on at most 1 leaf rate at a time.
+As the size of the covariance matrix $\Sigma_N$ grows with the number of taxa $N$, \texttt{LeafAVMVN} is likely to be less efficient with larger taxon sets.
+Therefore, we learn the weight behind this operator using \texttt{AdaptiveOperatorSampler}.
+
+To avoid the learned weight behind \texttt{LeafAVMVN} dominating the \texttt{AdaptiveOperatorSampler} weighting scheme and therefore inhibiting the mixing of internal node rates, we 
+introduce the \texttt{AdaptiveOperatorSampler(leaf)} and \texttt{AdaptiveOperatorSampler(internal)} meta-operators which operate exclusively on leaf node rates $\vec{\mathcal{R}}^{\,}_\text{leaf}$ and internal node rates $\vec{\mathcal{R}}^{\,}_\text{int}$ respectively  (\textbf{Table \ref{table:AVMVNoperators}}).
+The former employs the \texttt{LeafAVMVN} operator and learns its weight during MCMC (after providing it sufficient time to learn $\Sigma_N$).
+
+\begin{table}[h!]
+\centering
+\begin{tabular}{l l l} 
+ Meta-operator & POI & Operators \\
+\hline
+ \multirow{7}{*}{\texttt{AdaptiveOperatorSampler(leaf)}} & \multirow{7}{*}{$\vec{\mathcal{R}}^{\,}_\text{leaf}, t$} & \texttt{ConstantDistance($\vec{\mathcal{R}}^{\,}_\text{leaf}, \mathcal{T}$)}   \\ 
+&& \texttt{LeafAVMVN($\vec{\mathcal{R}}^{\,}_\text{leaf}$)}  \\
+&& \texttt{RandomWalk($\vec{\mathcal{R}}^{\,}_\text{leaf}$)}  \\
+&& \texttt{Scale($\vec{\mathcal{R}}^{\,}_\text{leaf}$)}   \\
+&& \texttt{Interval($\vec{\mathcal{R}}^{\,}_\text{leaf}$)}   \\
+&& \texttt{Swap($\vec{\mathcal{R}}^{\,}_\text{leaf}$)}  \\
+&& \texttt{SampleFromPrior($\vec{\mathcal{R}}^{\,}_\text{leaf}$)} \\
+\hline
+ \multirow{6}{*}{\texttt{AdaptiveOperatorSampler(internal)}} & \multirow{6}{*}{$\vec{\mathcal{R}}^{\,}_\text{int}, t$} & \texttt{ConstantDistance($\vec{\mathcal{R}}^{\,}_\text{int}, \mathcal{T}$)}   \\
+&& \texttt{RandomWalk($\vec{\mathcal{R}}^{\,}_\text{int}$)}  \\
+&& \texttt{Scale($\vec{\mathcal{R}}^{\,}_\text{int}$)}   \\
+&& \texttt{Interval($\vec{\mathcal{R}}^{\,}_\text{int}$)}   \\
+&& \texttt{Swap($\vec{\mathcal{R}}^{\,}_\text{int}$)}  \\
+&& \texttt{SampleFromPrior($\vec{\mathcal{R}}^{\,}_\text{int}$)} \\
+\end{tabular}
+\caption{Leaf rate $\vec{\mathcal{R}}^{\,}_\text{leaf}$ and internal node rate $\vec{\mathcal{R}}^{\,}_\text{int}$ operators. 
+This division enables the two meta-operators to be weighted proportionally to the number of nodes (leaves or internal) which it applies to.
+This facilitates incorporation of the  \texttt{LeafAVMVN} operator, which is only applicable to leaf nodes.
+In this setup, the \texttt{RandomWalk($x$)}, \texttt{Scale($x$)}, and \texttt{SampleFromPrior($x$)} operators apply to the corresponding set of branch rates $x$, whereas \texttt{ConstantDistance($x, \mathcal{T}$)} is only applicable to internal nodes which have at least one child of type $x \in \{\vec{\mathcal{R}}^{\,}_\text{leaf}, \vec{\mathcal{R}}^{\,}_\text{int}\}$.}
+\label{table:AVMVNoperators}
+\end{table}
 
@@
  	 \hline
+ 	 \multirow{4}{*}{AVMVN} & \texttt{AdaptiveOperatorSampler($\sigma$)} & $10$ & \checkmark &  & \checkmark  \\
+ 	& \texttt{AdaptiveOperatorSampler(leaf)} & $30 \times \frac{N}{2N-1}$ & \checkmark & & \checkmark  \\
+ 	& \texttt{AdaptiveOperatorSampler(internal)} & $30 \times \frac{N-2}{2N-1}$ &  \checkmark &  & \checkmark \\
+ 	 & \texttt{AdaptiveOperatorSampler(root)} & $30 \times \frac{1}{2N-1}$ & \checkmark & & \checkmark  \\
+ 	 \hline
  	 \hline
@@
 Operators which apply to either internal nodes or the root (but not both) are weighted according to leaf count $N$.
-The adapt operators are further broken down in \textbf{Table \ref{table:adaptiveSampling}}.
+The adaptive operators are further broken down in \textbf{Tables \ref{table:adaptiveSampling}, \ref{table:adaptiveNER}, and \ref{table:AVMVNoperators}}.
 All other operators (i.e. those which apply to which apply to other terms in the state such as the nucleotide substitution model) are held constant within each dataset.
@@
 The four operators introduced in these sections are summarised in \textbf{Table \ref{table:newOperators}}.
-The setting which is considered to be the best in each step is then incorporated into the following step. This protocol and its outcomes are summarised in \textbf{Fig. \ref{fig:tournament}}.
+The setting which is considered to be the best in each step is then incorporated into the following step. This protocol and its outcomes are summarised in \textbf{Fig \ref{fig:tournament}}.
 
@@
 \textbf{2. Mixing of parameters}. Key parameters are evaluated for the number of effective samples generated per hour (ESS/hr).
-This calculation is performed by BEAST2 \cite{bouckaert2019beast}. \\
-
-%\textbf{3.
-Time to convergence}.
-Two independent MCMC chains are run and the time is measured until: a) the absolute difference in clade posterior probability between the two chains is less than 0.05 for all clades, b) the Rubin-Gelman statistic $\hat{R}$ \cite{gelman1992inference} of every estimated parameter is less than 1.05, and c) the effective sample size \cite{rambaut2018posterior} of every estimated parameter is greater than 200 in each chain.
-\\
+These key parameters are the likelihood $\mathcal{L}$ and prior $p$ densities,  tree length $l$ (i.e.
+the sum of all branch lengths), mean branch rate $\bar{r}$, branch rate of all leaf nodes $r$, and relaxed clock standard deviation $\sigma$.
+We also include the HKY substitution model term $\kappa$. 
+The mixing of $\kappa$ should not be strongly affected by any of the clock model operators, and thus it serves as a positive control in each experiment. \\
 
 Methodologies are benchmarked using one simulated and eight empirical datasets.
-The latter were compiled \cite{lanfear2019Github} and partitioned \cite{lanfear2016partitionfinder} by Lanfear et al. as ``benchmark alignments'' (\textbf{Table \ref{table:datasets}}).
-Each methodology is benchmarked across 5 replicates on each dataset, using the Intel Xeon Gold 6138 CPU (2.00 GHz).
+The latter were compiled \cite{lanfear2019Github} and partitioned \cite{lanfear2016partitionfinder} by Lanfear as ``benchmark alignments'' (\textbf{Table \ref{table:datasets}}).
+Each methodology is benchmarked for million-states-per-hour using the Intel Xeon Gold 6138 CPU (2.00 GHz).
+These terms are multiplied by the ESS-per-state across 20 replicates on the New Zealand eScience Infrastructure (NeSI) cluster to compute the total ESS/hr of each dataset under each setting.
 All methodologies use identical models and operator configurations, except where a difference is specified.
@@
 
-This experiment revealed that nocons performed better than cons on datasets with small $L$ while cons performed better on larger datasets (\textbf{Fig.
-\ref{fig:round1Results}} and \textbf{\nameref{sect:SR_appendix}}).
-This result is unsurprising (\textbf{Fig. \ref{fig:rateparams}}).
+This experiment revealed that nocons usually performed better than cons on smaller datasets (i.e.
+small $L$) while cons consistently performed better on larger datasets (\textbf{Fig \ref{fig:round1Results}} and \textbf{\nameref{sect:SR_appendix}}).
+This result is unsurprising (\textbf{Fig \ref{fig:landscape}}).
 Furthermore, the adapt setup dramatically improved mixing for \textit{real} by finding the right balance between cons and nocons.
-This yielded an ESS/hr (averaged across all 9 datasets) 80\% faster than cons and 120\% faster than nocons, with respect to leaf branch rates, and 250\% and 1800\% faster for $\sigma$.
+This yielded an ESS/hr (averaged across all 9 datasets) 95\% faster than cons and 520\% faster than nocons, with respect to leaf branch rates, and 620\% and 190\% faster for $\sigma$.
 Similar results were observed with \textit{quant}.
-However adapt neither helped nor harmed \textit{cat}, suggesting that the default operator weighting scheme was sufficient.
+However, adapt neither helped nor harmed \textit{cat}, suggesting that the default operator weighting scheme was sufficient.
+
+This experiment also revealed that the standard \texttt{Scale} operator was preferred over \texttt{CisScale} for the \textit{real} configuration.
+Averaged across all datasets, the learned weights behind these two operators were 0.47 and 0.03.
+This is due to the computationally demanding nature of \texttt{CisScale} which invokes the i-CDF function.
+In contrast, the performance of \texttt{Scale} and \texttt{CisScale} were more similar under the \texttt{quant} configuration and were weighted at 0.28 and 0.45.
+For both \textit{real} and \textit{quant}, proposals which altered quantiles, while leaving the rates constant (\texttt{Scale} and \texttt{CisScale} respectively), were preferred.
+
 Overall, the \texttt{AdaptiveOperatorSampler} operator will be included in all subsequent rounds in the tournament.
@@
 \includegraphics[width=\textwidth]{benchmarking/benchmarkingVM/ESS_round1_real.pdf}
-\caption{\textbf{Round 1: benchmarking the \texttt{AdaptiveOperatorSampler} operator.} Top left, top right, bottom left: each plot compares the ESS/hr ($\pm 2$ standard errors) across two operator configurations with respect to relevant terms -- $L$: log likelihood, $p$: log prior density, $r$: substitution rate ESS averaged across all leaves, $\sigma$: clock standard deviation, $h$: tree height, and $\kappa$: HKY model transition-transversion ratio.
+\caption{\textbf{Round 1: benchmarking the \texttt{AdaptiveOperatorSampler} operator.} Top left, top right, bottom left: each plot compares the ESS/hr ($\pm 1$ standard error) across two operator configurations.
 Bottom right: the effect of sequence length $L$ on operator weights learned by \texttt{AdaptiveOperatorSampler}. Both sets of results are fit by a logistic regression curve.
@@
 
-This experiment showed that the \textit{real} parameterisation greatly outperformed both \textit{cat} and \textit{quant} on most datasets (\textbf{Fig. \ref{fig:round2Results}}).
+This experiment showed that the \textit{real} parameterisation greatly outperformed \textit{cat} on most datasets and most parameters (\textbf{Fig \ref{fig:round2Results}}).
 This disparity is strongest for long alignments.
-In the most extreme case, leaf substitution rates $r$ and clock standard deviation $\sigma$ both mixed around $70 \times$ faster on the 15.5 kb seed plant dataset \cite{Ran_2018} for \textit{real} than they did for \textit{cat}.
+In the most extreme case, leaf substitution rates $r$ and clock standard deviation $\sigma$ both mixed around 50 $\times$ faster on the 15.5 kb seed plant dataset \cite{Ran_2018} for \textit{real} than they did for \textit{cat}.
 The advantages in using constant distance operators would likely be even stronger for larger $L$.
+Furthermore, \textit{real} outperformed \textit{quant} on most datasets, but this is mostly due to the slow computational performance of \textit{quant} compared with real, as opposed to differences in mixing prowess (\textbf{\nameref{sect:SR_appendix}}).
+
 Overall, we have determined that \textit{real}, and its associated operators, makes the best parameterisation covered here and will proceed to the next rounds of the benchmarking.
@@
 \caption{\textbf{Round 2: benchmarking substitution rate parameterisations.} Top left, top right, bottom left: the adapt (\textit{real}), adapt (\textit{cat}), and adapt (\textit{quant}) configurations were compared.
-See \textbf{Fig.
-\ref{fig:round1Results}} caption for figure notation.
-Bottom right: comparison of the mean tip substitution rate ESS/hr as a function of sequence length.
+Bottom right: comparison of the mean tip substitution rate ESS/hr as a function of alignment length $L$.
 }
@@
 
-\subsection*{Round 3: Bactrian proposal kernels are 10\% more efficient than uniform kernels}
-
-We benchmarked the adapt (\textit{real}) configuration with a) standard uniform proposal kernels, and b) Bactrian(0.95) kernels.
+\subsection*{Round 3: Bactrian proposal kernels are around 15\% more efficient than uniform kernels}
+
+We benchmarked the adapt (\textit{real}) configuration with a) standard uniform proposal kernels, and b) Bactrian(0.95) kernels \cite{yang2013searching}.
 These kernels applied to all clock model related operators (\textbf{Table \ref{table:bactriankernels}}).
-
-\subsection*{Round 4: Evaluating adaptive NER}
-
-Our initial screening of the \texttt{NarrowExchangeRate} (NER) operators revealed that the $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ operator outperformed the standard $\text{NER} \{\}$ / \texttt{NarrowExchange} operator about 25\% of the time on simulated data, however it was also very sensitive to the dataset.
+These results confirmed that the Bactrian kernel yields faster mixing than the standard uniform kernel (\textbf{Fig \ref{fig:round3Results}}).
+All relevant continuous parameters considered had an ESS/hr, averaged across the 9 datasets, between 15 and 20\% faster compared to with the standard uniform kernel.
+Although the Bactrian proposal made little-to-no difference to the caterpillar dataset (Kawahara et al. 2013 \cite{Kawahara_2013}), every other dataset did in fact benefit.
+Bactrian proposal kernels will proceed to round 4 of the relaxed clock model optimisation protocol.
+
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{benchmarking/benchmarkingVM/ESS_round3.pdf}
+\caption{\textbf{Round 3: benchmarking the Bactrian kernel.}
+The ESS/hr ($\pm 1$ s.e.) under the Bactrian configuration, divided by that under the uniform kernel, is shown in the y-axis for each dataset and relevant parameter.
+Horizontal bars show the geometric mean under each parameter.
+ }
+\label{fig:round3Results}
+\end{figure}
+
+\subsection*{Round 4: NER operators outperform on larger datasets}
+
+Our initial screening of the \texttt{NarrowExchangeRate} (NER) operators revealed that the $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ operator outperformed the standard  \texttt{NarrowExchange} / $\text{NER} \{\}$ operator about 25\% of the time on simulated data, however it was also very sensitive to the dataset.
 Therefore we wrapped up the two operators ($\text{NER} \{\}$ and $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$) within an \texttt{AdaptiveOperatorSampler} operator so that the appropriate weights can be learned, using the Robinson-Foulds metric.
-In this round we benchmarked the adapt + Bactrian(0.95) (\textit{real})  setting with a) $\text{NER} \{\}$ only, and b) adaptive $\text{NER}$ (\textbf{Table \ref{table:operatorSchemes}}).
-
-Our experiments confirmed that $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ is indeed superior on larger datasets (where $L > 1$kb; \textbf{Fig. \ref{fig:round4Results}}).
-Whereas, on smaller datasets the standard \texttt{NarrowExchange} operator had a higher acceptance rate.
-Using an adaptive operator (\texttt{AdaptiveOperatorSampler}) removes the burden from the user in selecting which operator is the best pick.
-The average acceptance rate of
+In this round we benchmarked the Bactrian + adapt (\textit{real}) setting with the adaptive $\text{NER}$ operator (\textbf{Table \ref{table:operatorSchemes}}).
+
+Our experiments confirmed that $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ was indeed superior on larger datasets (where $L > 2$kb; \textbf{Fig \ref{fig:round4Results}}).
+While there was no significant difference in the ESS/hr of continuous parameters, $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ did have an acceptance rate 41\% higher than that of the standard \texttt{NarrowExchange} operator in the most extreme case (the 7kb alignment by Broughton et al.\cite{Broughton_2013}).
+Every proposal acceptance yields a new tree topology and thus facilitates traversal of tree space.
+
+In contrast, the standard \texttt{NarrowExchange} operator outperformed on smaller datasets.
+Thus, the new operator is not always helpful and sometimes it even hinders performance.
+Using an adaptive operator (\texttt{AdaptiveOperatorSampler}) removes the burden from the user in making the decision of which operator to use.
+The \texttt{AdaptiveOperatorSampler(NER)} operator will proceed to the final round of the tournament.
 
@@
 The learned weights (left) behind the two NER operators ($\text{NER} \{\}$ and $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$), and the relative difference between their acceptance rates $\alpha$ (right), are presented as functions of sequence length.
-Logistic and linear regression models are shown, respectively. }
+Logistic and logarithmic regression models are shown, respectively. }
 \label{fig:round4Results}
@@
 
-\subsection*{Round 5: The AVMVN leaf rate operator works well for small taxon sets}
-
+\subsection*{Round 5: The AVMVN leaf rate operator is computationally demanding and improves mixing slightly}
+
+We wanted to test the applicability of the adaptive AVMVN kernel to leaf rate proposals.
+This would operate by exploiting any correlations which occur between leaf branch substitution rates.
+To do this, we wrapped the \texttt{LeafAVMVN} operator within an \texttt{AdaptiveOperatorSampler} (\textbf{Table \ref{table:AVMVNoperators}}).
+The two configurations compared here were a) adapt + Bactrian + NER (\textit{real}) and b) AVMVN + NER + Bactrian + adapt (\textit{real})  (\textbf{Table \ref{table:operatorSchemes}}).
+
+These results showed that the AVMVN operator yielded slightly better mixing (around 6\% faster) for the tree likelihood, the tree length and the mean branch rate (\textbf{Table \ref{fig:round5Results}}).
+However, it also produced slightly slower mixing for $\kappa$, reflecting the high computational costs associated with the \texttt{LeafAVMVN} operator (\textbf{\nameref{sect:SR_appendix}}).
+The learned weight of the \texttt{LeafAVMVN} operator was quite small (ranging from 1 to 8\% across all datasets), again reflecting its high computational costs, but also reinforcing the value in having an adaptive weight operator which penalises slow operators.
+Overall, the \texttt{LeafAVMVN} operator provided some, but not much, benefit in its current form.
+
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{benchmarking/benchmarkingVM/ESS_round5.pdf}
+\caption{\textbf{Round 5: benchmarking the \texttt{LeafAVMVN} operator.} See \textbf{Fig \ref{fig:round3Results}} caption for figure notation.  }
+\label{fig:round5Results}
+\end{figure}
+
+Overall, this operator configuration is the final winner in the tournament.
+
+\subsection*{Tournament conclusion}
+ In conjunction with all settings which came before it, the tournament winner  outperformed both the historical \textit{cat} configuration \cite{drummond2006relaxed} as well as the recently developed cons (\textit{real}) scheme \cite{zhang2020improving} .
+Averaged across all datasets, this configuration yielded a relaxed clock  mixing rate between 1.2 and 13 times as fast as \textit{cat} and between 1.8 and 7.8 times as fast as cons (\textit{real}), depending on the parameter.
+For the largest dataset considered (Ran et al. 2018 \cite{Ran_2018}), the new settings were up to 66 and 37 times as fast respectively.
+This is likely to be even more extreme for larger alignments.
+
+\newpage
 \section*{Discussion} \label{sect:discussion}
 
-% Points to cover
-
-% - Dont change branch lengths and topology at the same time.
-This result is unfortunate however not unexpected, and is consistent with Lakner et al.
-2008 \cite{lakner2008efficiency}, who observed that tree operators perform best when they change either topology, or branch lengths, but not both.
+In this article, we delved into the highly correlated structure of relaxed clock models, in order to develop MCMC operators which traverse its posterior space efficiently.
+We introduced a range of relaxed clock model operators and compared three molecular substitution rate parameterisations.
+These methodologies were compared by constructing phylogenetic models from several empirical datasets (\textbf{Fig \ref{fig:parameterisationResults}}) and comparing their abilities to converge in a tournament-like protocol (\textbf{Fig \ref{fig:tournament}}).
+This work has produced an operator configuration which explores relaxed clock model space up to an order of magnitude more efficiently than previous setups.
 
@@
 \includegraphics[width=\textwidth]{Figures/broughton.pdf}
-\caption{\textbf{Maximum clade credibility trees.} 
-Phylogenetic trees of bark beetles (Cognato et al. 2001 \cite{Cognato_2001}; top) and bony fishes (Broughton et al. 2013 \cite{Broughton_2013}; bottom) are presented. 
+\caption{\textbf{Relaxed clock phylogenies.} 
+Maximum clade credibility trees of bark beetles (Cognato et al. 2001 \cite{Cognato_2001}; top) and bony fishes (Broughton et al. 2013 \cite{Broughton_2013}; bottom) are presented. 
 Branches are coloured by substitution rate (units: substitutions per site per unit of time) and the y-axis shows time, such that there is on average 1 substitution per unit of time.
@@
 
-\section*{Conclusion}
+% Points to cover
+
+\subsection*{Modern operator design}
+
+Adaptability and advanced proposal kernels, such as Bactrian kernels, are increasingly prevalent in MCMC operator design \cite{haario2001adaptive,vihola2012robust,benson2018adaptive,davis2020blocking}.
+
+Adaptive operators undergo training to improve their efficiency over time \cite{roberts2007coupling}. 
+In previous work, the conditional clade probabilities of neighbouring trees have served as the basis of adaptive tree operators \cite{hohna2012guided,meyer2019adaptive}.
+The mirror kernel learns a target distribution which acts as a ``mirror image'' of the current point \cite{thawornwattana2018designing}.
+The AVMVN operator learns correlations between numerical parameters in order to traverse the joint posterior distribution efficiently \cite{baele2017adaptive}.
+
+Here, we introduced an adaptive operator which learns the weights of other operators, by using a target function that rewards operators which bring about large changes to the state and penalises operators which exhibit poor computational runtime (\textbf{Equation \ref{eqn:adaptiveSampler}}).
+We demonstrated how learning the operator weightings, on a dataset-by-dataset basis, can improve mixing by up to an order of magnitude.
+We also demonstrated the versatility of this operator by applying it to a variety of settings.
+Assigning operator weights is an important task in Bayesian MCMC inference and the use of such an operator can relieve some of the burden from the person making this decision.
+However, this operator is no silver bullet and it must be used in a way that maintains ergodicity within the search space \cite{roberts2007coupling}.
+
+We also found that Bactrian proposal kernels quite reliably increased mixing efficiency by 15--20\% (\textbf{Fig \ref{fig:round3Results}}).
+Similar observations were made by Yang et al. \cite{yang2013searching}.
+While this may only be a modest improvement, incorporation of the Bactrian kernel into pre-existing operators is a computationally straightforward task and should be routinely implemented in Bayesian MCMC software packages.
+
+\subsection*{Traversing tree space}
+
+In this article we introduced the family of narrow exchange rate operators (\textbf{Fig \ref{fig:narrowexchange}}).
+These operators are built on top of the narrow exchange operator and are specifically designed for the relaxed clock model, by accounting for the correlation which exists between branch lengths and branch substitution rates.
+This family consists of 48 variants, each of which conserves a unique subset of genetic distances before and after the proposal. 
+Most of these operators turned out to be worse than narrow exchange, however a small subset of these were more efficient but only on larger datasets.
+
+Lakner et al. categorised tree operators into two classes.
+``Branch-rearrangement'' operators relocate a branch and thus alter tree topology. 
+Members of this class include narrow exchange, nearest neighbour interchange, and subtree-prune-and-regraft \cite{semple2003phylogenetics}.
+Whereas ``branch-length'' operators propose branch lengths, but can potentially alter the tree topology as a side-effect.
+ Such operators include subtree slide \cite{hohna2008clock}, LOCAL \cite{simon1998local}, and continuous change \cite{jow2002bayesian}.
+Lakner et al. observed that topological proposals made by the former class consistently outperformed topological changes invoked by the latter class \cite{lakner2008efficiency}.
+
+%found that tree operators which perturb topology consistently perform better than those which also change branch lengths as well as topology .
+
+We hypothesised that the increased efficiency behind narrow exchange rate operators could facilitate proposing internal node heights in conjunction with branch rearrangements.
+This would enable the efficient exploration of both topology and branch length spaces with a single proposal.
+Unfortunately, by incorporating a random walk on the height of the node being relocated, the acceptance rate of the operator declined dramatically  (\textbf{Fig \ref{fig:acceptanceRateScreening}}). 
+This decline was greater when more genetic distances were conserved.
+
+The design of operators which are able to efficiently traverse topological and branch length spaces simultaneously remains an open problem.
+
+\subsection*{Larger datasets require smarter operators}
+
+As signal within the dataset becomes stronger, the posterior distribution becomes increasingly peaked (\textbf{Fig \ref{fig:landscape}}).
+This topological change in the landscape necessitates the use of operators which exploit known correlations in the posterior density, such as AVMVN \cite{baele2017adaptive}, constant distance operators \cite{zhang2020improving}, and the narrow exchange rate operators introduced in this article.
+
+We have shown that while the latter two operators are efficient on large alignments, they are also quite frequently outperformed by simple random walk operators on small alignments.
+For instance, constant distance operators outperformed standard operator configurations by up to an order of magnitude on larger datasets but they were up to three times slower on smaller ones (\textbf{Fig \ref{fig:round1Results}}).
+Similarly, our narrow exchange rate operators were up to 40\% more efficient on large datasets but up to 10\% less efficient on smaller ones (\textbf{Fig \ref{fig:round4Results}}).
+
+This emphasises the value in our adaptive operator weighting scheme, which can ensure that operator weights are suitable for the size of the alignment.
+Given the immense availability of sequence data, and the increased computational cost required to process it, high performance on large datasets is a desirable property.
 
@@
 \label{sect:WCSS_appendix}
-{\textbf{Well-calibated simulation studies.} Methodologies are validated using well-calibated simulation studies.
+{\textbf{Well-calibrated simulation studies.} Methodologies are validated using well-calibrated simulation studies.
 

### 2020-09-01 RatesWCSS/WCSS.R

@@ -1,0 +1,167 @@
+
+library(tikzDevice)
+library(HDInterval)
+
+
+
+parameters = c("TreeHeight", "birthRate", "kappa", "freqParameter.1", "ucldStdev",  "RateStatLogger.mean", "RateStatLogger.variance")
+
+
+parameters.latex = lapply(parameters, function(x) x)
+names(parameters.latex) = parameters
+parameters.latex["birthRate"] = "Yule birth rate $\\lambda$"
+parameters.latex["TreeHeight"] = "Tree height $h$"
+parameters.latex["kappa"] = "HKY model $\\kappa$"
+parameters.latex["freqParameter.1"] = "Nucleotide frequency $f$"
+parameters.latex["ucldStdev"] = "Clock standard deviation $\\sigma$"
+parameters.latex["RateStatLogger.mean"] = "Branch rate mean"
+parameters.latex["RateStatLogger.variance"] = "Branch rate variance"
+
+
+BURNIN = 0.1
+
+
+settings = rev(list.dirs("sim", recursive = F))
+nsim = 100
+N = 30
+
+# True values
+true.df = read.table(paste0("true/", "priorSamples_N", N, ".log"), sep = "\t", header = T)
+true.df[,"RateStatLogger.mean"] = numeric(0)
+true.df[,"RateStatLogger.variance"] = numeric(0)
+true.df = true.df[1:nsim,parameters]
+
+
+
+for (sett in settings){
+
+
+	s = gsub("[.]", "", gsub("sim/", "", sett))
+	filename = paste0("WCSS_", s)
+	cat(paste(s, "\n"))
+
+	# Estimated values
+	means.df = true.df
+	for (col in colnames(means.df)) means.df[,col] = NA
+	lower.df = means.df
+	upper.df = means.df
+
+
+
+	for (sim in 1:nsim){
+	
+
+		cat(paste(sim, "\n"))
+
+		# Estimated values
+		sim.df = read.table(paste0(sett, "/logfile_", sim, ".log"), sep = "\t", header = T)
+		sim.df = sim.df[floor(BURNIN*nrow(sim.df)):nrow(sim.df),]
+
+		# Put the true rates/variances in the true df
+		true.df[sim,"RateStatLogger.mean"] = sim.df[1,"RateStatLogger.true.mean"]
[…]

### 2020-09-01 benchmarking/render.R

@@ -137,7 +137,6 @@ for (f in batchfolders){
 	for (d in datasetFolders) {
 
 		
-		if (length(grep("Ran_", d)) > 0) next
 		print(d)
 
 		dataset = substring(d, 3)
@@ -344,7 +343,7 @@ for (f in batchfolders){
 							
 							ESS.df2 = data.frame(batch = bb, param = p, setting = s, dataset = dataset, ESS = ESS, hr = runtime.hr, partition = P, Leff = Leff, L = L, N = N, sigma = sigma,
 									 CD_weight = CD_weight, RW_weight = RW_weight, SPP_weight = SPP_weight, NER_weight = NER_weight, NER_acc = NER_acc, NE_acc = NE_acc, leafCD_weight = leafCD_weight,
-									 leafCD_weight = leafCD_weight, cis_weight = cis_weight, trans_weight = trans_weight, nsamples = nsamples)
+									 leafCD_weight = leafCD_weight, cis_weight = cis_weight, trans_weight = trans_weight, leafAVMVN_weight = leafAVMVN_weight, nsamples = nsamples)
 							ESS.df = rbind(ESS.df, ESS.df2)
 
 							
@@ -410,7 +409,7 @@ plotRealCat = function(){
 
 
 	maxL = 20#max(ESS.df$L) + 2
-	plot(0, 0, type = "n", xlim = c(0,maxL), ylim = c(0, 20000), xlab = "Sequence length $L$ (kb)", ylab = "ESS/hr of tip rates $r$", axes = F, xaxs = "i", yaxs = "i", 
+	plot(0, 0, type = "n", xlim = c(0,maxL), ylim = c(0, 12000), xlab = "Sequence length $L$ (kb)", ylab = "ESS/hr of tip rates $r$", axes = F, xaxs = "i", yaxs = "i", 
 					main ="Leaf rate mixing vs sequence length", cex.main = 1.5, cex.lab = 1.5)
 
 
@@ -594,7 +593,7 @@ plotNERWeights = function(rates = FALSE) {
 			points(mean(sub.df$L), NER, col = data.cols[dataNum], pch = 18)
 			
 			
-			if (NER > 1) cat(paste("For", d, "NER has an acceptance rate", signif(100*(NER-1), 2), "% higher than NarrowExchange\n"))
[…]

### 2020-09-02 S2_appendix.tex
Complete draft

@@
 Rong Zhang\textsuperscript{1,2},
-Alexei J. Drummond\textsuperscript{1,2,3},
 Remco Bouckaert\textsuperscript{1,2}
@@
 \textbf{2} School of Computer Science, University of Auckland, Auckland, New Zealand\\
-\textbf{3} School of Biological Sciences, University of Auckland, Auckland, New Zealand
-\\
 \bigskip
@@
 In each plot, blue and red vertical lines are 95\% HPD intervals, where blue intervals contain the true value and red intervals do not.
-The number in the bottom right corner of each plot is the coverage; that is the percentage of simulations where the `true' parameter value is within the 95\% HPD interval. 
+The number at the top of each plot is the coverage; that is the percentage of simulations where the `true' parameter value is within the 95\% HPD interval. 
 If all parameters have coverage close to 95\%, then this suggests correctness of both methodology and implementation.
@@
 \begin{figure}[!htb]
-\includegraphics[width=\textwidth]{Figures/N30_cat_adaptive.pdf}
+\includegraphics[width=\textwidth]{RatesWCSS/WCSS_cat_adaptive.pdf}
 \caption{\textbf{The adapt (\textit{cat}) configuration.} }
@@
 \begin{figure}[!htb]
-\includegraphics[width=\textwidth]{Figures/N30_real_adaptive.pdf}
+\includegraphics[width=\textwidth]{RatesWCSS/WCSS_real_adaptive.pdf}
 \caption{\textbf{The adapt (\textit{real}) configuration.} }
@@
 \begin{figure}[!htb]
-\includegraphics[width=\textwidth]{Figures/N30_quant_cached_adaptive.pdf}
+\includegraphics[width=\textwidth]{RatesWCSS/WCSS_quant_cached_adaptive.pdf}
 \caption{\textbf{The adapt (\textit{quant}) configuration.} The constant distance operators were extended from \emph{real} to \emph{quant} as described in \textbf{S1 Appendix}.}
@@
 \begin{figure}[!htb]
-%\includegraphics[width=\textwidth]{Figures/CalSim_NER_real.pdf}
-\caption{\textbf{The Narrow Exchange Rate operators under the \textit{real} parameterisation.} The 48 NER and 48 NERw operators, including \texttt{NarrowExchange}, are tested in the same MCMC session.}
-\end{figure}
-
-\begin{figure}[!htb]
-%\includegraphics[width=\textwidth]{Figures/CalSim_NER_quant.pdf}
-\caption{\textbf{The \texttt{LeafAVMVN} configuration.} The adaptive NER operator, Bactrian proposals, and the \emph{real} configuration are included.}
+\includegraphics[width=\textwidth]{RatesWCSS/WCSS_AVMVN.pdf}
+\caption{\textbf{The AVMVN configuration.} The adaptive NER operator, Bactrian proposals, and the \emph{real} configuration are also included.}
 \end{figure}

### 2020-09-02 manuscript.tex
Complete draft

@@
 \section*{Abstract}
+
+% What is the relaxed clock
+% It is widely used
+% We delve deep into its complexities to develop efficient operators
+% Weight learning adaptive operator
+% Rate parameterisations
+% Other modern methods Bactrian and AVMVN kernels applied to the relaxed clock
+% Overall, up to 2 orders of magnitude faster at exploring continuous relaxed clock parameters 
+% Topological operators for the relaxed clock -> up to 40%
+% Methods are best for long alignments
+
+%Molecular clock models are used for dating evolutionary divergence times. 
+Relaxed clock models enable estimation of molecular substitution rates across lineages and are widely used in phylogenetics.
+This can be used for dating evolutionary divergence times.
+In this article we delved into the internal complexities of the relaxed clock model in order to develop efficient MCMC operators for Bayesian phylogenetic inference.
+We compared three substitution rate parameterisations, we introduced an adaptive operator which learns the weights of other operators during MCMC and, we explored how relaxed clock model estimation can benefit from two cutting-edge proposal kernels: the AVMVN and Bactrian kernels.
+This work has produced an operator scheme that is up to 65 times more efficient at exploring continuous relaxed clock parameters compared with previous setups, depending on the dataset.
+Finally, we explored variants of the standard narrow exchange operator which are specifically designed for the relaxed clock model.
+In the most extreme case, this new operator traversed tree space 40\% more efficiently than narrow exchange.
+The methodologies introduced are adaptive and highly effective on long alignments.
 
@@
 
+Biological sequences, such as DNA, accumulate mutations over generations. 
+By comparing such sequences in a phylogenetic framework, the evolutionary tree of lifeforms can be inferred.
+With the overwhelming availability of biological sequence data, and the increasing affordability of collecting new data, the development of fast and efficient phylogenetic algorithms is more important than ever.
+In this article we focus on the relaxed clock model, which is widely used in phylogenetics.
+We explored how a range of optimisations can improve the statistical inference of the relaxed clock.
+This work has produced a phylogenetic setup which can infer parameters related to the relaxed clock up to 65 times faster than previous setups, depending on the dataset.
+The methods introduced adapt to the dataset during computation and are highly efficient when processing long biological sequences.
+
 \linenumbers
 
+\clearpage
 % Use "Eq" instead of "Equation" for equation citations.
@@
 However, molecular substitution rates are known to vary over time, over population sizes, over evolutionary pressures, and over nucleic acid replicative machineries \cite{gillespie1994causes, woolfit2009effective, loh2010optimization}.
-Moreover, any given dataset may be clock-like (where the substitution rates have a small variance across lineages) or non clock-like (a large variance). 
+Moreover, any given dataset could be clock-like (where substitution rates have a small variance across lineages) or non clock-like (a large variance). 
 In the latter case, a strict clock is probably not suitable.
@@
 Finally, although not the focus of this article, the class of correlated clock models assumes some form of auto-correlation between rates over time. 
-The correlation itself can invoke a range of stochastic models, including compound Poisson \cite{huelsenbeck2000compound} and CIR processes \cite{lepage2007general}, or it can exist as a series of local relaxed clocks \cite{drummond2010bayesian}.
-However, due to the correlated and discrete nature of such models, the time until MCMC convergence may be cumbersome, particularly for larger datasets \cite{drummond2010bayesian}.
+The correlation itself can invoke a range of stochastic models, including compound Poisson \cite{huelsenbeck2000compound} and CIR processes \cite{lepage2007general}, or it can exist as a series of local clocks \cite{drummond2010bayesian}.
+However, due to the correlated and discrete nature of such models, the time required for MCMC to achieve convergence can be cumbersome, particularly for larger datasets \cite{drummond2010bayesian}.
 
 With the overwhelming availability of biological sequence data, the development of efficient Bayesian phylogenetic methods is more important than ever. 
-The performance of MCMC is dependent not only on computational runtime but also the efficacy of an
+The performance of MCMC is dependent not only on computational performance but also the efficacy of an
 MCMC setup to achieve its convergence.
@@
 and other explorative proposal kernels such as the Bactrian and mirror kernels \cite{yang2013searching, thawornwattana2018designing}.
-In the case of clock models, informed tree proposals can account for correlations between substitution rates and divergence times \cite{zhang2020improving}. 
+In the case of relaxed clocks, informed tree proposals can account for correlations between substitution rates and divergence times \cite{zhang2020improving}. 
 The rate parameterisation itself can also affect the ability to ``mix'' during MCMC \cite{drummond2006relaxed, li2012model, zhang2020improving}.
@@
 While a range of advanced operators and other MCMC optimisation methods have arisen over the years, there has yet to be a widescale performance benchmarking of such methods as applied to the relaxed clock model.
-In this article, we systematically evaluate how the relaxed clock model can benefit from i) adaptive operator weighting, ii) different substitution rate parameterisations,  iii) the use of Bactrian proposal kernels \cite{yang2013searching}, iv) tree operators which account for correlations between substitution rates and times, and v) adaptive multivariate operators \cite{baele2017adaptive}.
+In this article, we systematically evaluate how the relaxed clock model can benefit from i) adaptive operator weighting, ii) substitution rate parameterisation,  iii) Bactrian proposal kernels \cite{yang2013searching}, iv) tree operators which account for correlations between substitution rates and times, and v) adaptive multivariate operators \cite{baele2017adaptive}.
 The discussed methods are implemented in and compared using BEAST2 \cite{bouckaert2019beast}.
@@
 $\sigma$ represents clock model related parameters, and $p(\mathcal{T}|\theta)$ is the tree prior where $\theta$ describes further unspecified parameters. 
-The tree likelihood $p(D|\mathcal{T}, r(\vec{\mathcal{R}}^{\,}), \mu_C)$ is computed using the tree-peeling algorithm \cite{felsenstein1981evolutionary}, where $\mu_C$ is the overall clock rate and
-$\vec{\mathcal{R}}^{\,}$ is a vector of abstracted branch rates which is transformed into real rates by function $r(\vec{\mathcal{R}}^{\,})$. 
+The tree likelihood $p(D|\mathcal{T}, r(\vec{\mathcal{R}}^{\,}), \mu_C)$ is
+calculated by the tree-peeling algorithm \cite{felsenstein1981evolutionary}, where $\mu_C$ is the overall clock rate and
+$\vec{\mathcal{R}}^{\,}$ is an abstracted vector of branch molecular substitution rates which is transformed into real rates by function $r(\vec{\mathcal{R}}^{\,})$. 
 Branch rates have a mean of 1 under the prior to avoid non-identifiability with node heights and the clock rate $\mu_C$.
@@
 $q(a|b)$ is the transition kernel: the probability of proposing state $b$ from state $a$.
-The ratio between the two $\frac{q(x|x^\prime)}{q(x^\prime|x)}$ is also known as the Hastings ratio \cite{hastings70}.
+The ratio between the two $\frac{q(x|x^\prime)}{q(x^\prime|x)}$ is known as the Hastings ratio \cite{hastings70}.
 The determinant of the Jacobian matrix $|J|$ solves the dimension-matching problem for proposals which operate on multiple terms across one or more spaces \cite{green1995reversible, geyer2003metropolis}.
@@
 The natural (and unabstracted) parameterisation of a substitution rate is a real number $\mathcal{R}_i \in \mathbb{R}, \mathcal{R}_i > 0$ which is equal to the rate itself. 
-Thus, under the \textit{real} parameterisation:
+Under the \textit{real} parameterisation:
 
@@
 
-Under the Log-Normal clock prior $p(\vec{\mathcal{R}}^{\,} | \sigma)$, rates are distributed with a mean of 1:
+Under a Log-Normal clock prior $p(\vec{\mathcal{R}}^{\,} | \sigma)$, rates are distributed with a mean of 1:
 
@@
 
-where $\mu = -0.5\sigma^2$ is set such that the expected value of the Log-Normal distribution is 1.
+where $\mu = -0.5\sigma^2$ is set such that the expected value is 1.
 In this article we only consider Log-Normal clock priors, however the methods discussed are general.
@@
 \subsubsection*{2. Categories}
-The category parameterisation (\textit{cat}) is an abstraction of the \textit{real} parameterisation. 
+The category parameterisation \textit{cat} is an abstraction of the \textit{real} parameterisation. 
 Each of the $2N-2$ branches are assigned an integer from $0$ to $n-1$:
@@
 These integers correspond to $n$ rate categories (\textbf{Fig. \ref{fig:rateparams}}).
+Let $f(x|\sigma)$ be the probability density function (PDF) and let $F(x|\sigma) = \int\limits_{0}^{x} f(t|\sigma) \; dt$ be the cumulative distribution function (CDF) of the prior distribution used by the underlying \textit{real} clock model (a Log-Normal distribution for the purposes of this article).
+In the \textit{cat} parameterisation, $f(x|\sigma)$ is discretised into $n$ bins and each element within $\vec{\mathcal{R}}^{\,}$ points to one such bin.
+The rate of each bin is equal to its median value:
+
+\begin{align}
+r(\mathcal{R}_i) =& \; F^{-1}\big(\frac{\mathcal{R}_i + 0.5}{n}\big),
+\end{align}
+
+where $F^{-1}$ is the inverse cumulative distribution function (i-CDF).
 The domain of $\vec{\mathcal{R}}^{\,}$ is uniformly distributed under the prior:
@@
 
-Let $f(x|\sigma)$ be the probability density function (PDF) and let $F(x|\sigma) = \int\limits_{0}^{x} f(t|\sigma) \; dt$ be the cumulative distribution function (CDF) of the prior distribution used by the underlying \textit{real} clock model (a Log-Normal distribution in this project).
-Then, in the \textit{cat} parameterisation, $f(x|\sigma)$ is discretised into $n$ bins and each element within $\vec{\mathcal{R}}^{\,}$ points to one such bin,
-where each bin has uniform prior density.
- The rate of each bin is equal to the median value within the bin
-
-\begin{align}
-r(\mathcal{R}_i) =& \; F^{-1}\big(\frac{\mathcal{R}_i + 0.5}{n}\big),
-\end{align}
-
-where $F^{-1}$ is the inverse cumulative distribution function (i-CDF).
-
-The key advantage of the \textit{cat} parameterisation is the removal of a term from the posterior density (Equation \ref{eq:bayesian}), or more accurately the replacement of a non-trivial $p(\vec{\mathcal{R}}^{\,} | \sigma)$ term with that of a uniform prior.
-This may facilitate efficient traversal of the parameter space by MCMC.
+The key advantage of the \textit{cat} parameterisation is the removal of a term from the posterior density (\textbf{Equation \ref{eq:bayesian}}), or more accurately the replacement of a non-trivial $p(\vec{\mathcal{R}}^{\,} | \sigma)$ term with that of a uniform prior.
+This may facilitate efficient exploration of the posterior distribution by MCMC.
 
@@
 
-Finally, rates can be parameterised as real numbers $0 < \mathcal{R}_i < 1$ which describe the rate's quantile with respect to some underlying clock model distribution.
+Finally, rates can be parameterised as real numbers describing the rate's quantile with respect to some underlying clock model distribution.
 Under the  \textit{quant} parameterisation, each of the $2N-2$ elements in $\vec{\mathcal{R}}^{\,}$ are uniformly distributed.
@@
 Transforming these quantiles into rates invokes the i-CDF of the underlying \textit{real} clock model distribution.
-However, this function is computationally demanding to evaluate and therefore an approximation of the i-CDF is used:
+Evaluation of the Log-Normal i-CDF is has high computational costs and
+therefore an approximation is used instead.
 
@@
 
-The weight of an operator determines the probability of the operator being selected and is typically fixed throughout MCMC.
-In BEAST2, operators can have their own tunable parameter $s$ which determines the step size of the operator, and this term is learned over the course of the MCMC \cite{bouckaert2019beast}. 
-Here, we define clock model operators as those which generate proposals for either $\vec{\mathcal{R}}^{\,}$ or $\sigma$.
-Pre-existing BEAST2 clock model operators are summarised in \textbf{Table \ref{table:kernels}}, and further operators are introduced throughout the paper.
+The weight of an operator determines the probability of the operator being selected.
+Weights are typically fixed throughout MCMC.
+In BEAST2, operators can have their own tunable parameter $s$ which determine the step size of the operator.
+This term is learned over the course of the MCMC \cite{rosenthal2011optimal, bouckaert2019beast}. 
+We define clock model operators as those which generate proposals for either $\vec{\mathcal{R}}^{\,}$ or $\sigma$.
+Pre-existing BEAST2 clock model operators are summarised in \textbf{Table \ref{table:kernels}}, and further operators are introduced throughout this paper.
 
@@
   \hline
-\texttt{Scale} & Applies \texttt{RandomWalk} on the log-transformation (suitable for parameters with positive domains). & $\vec{\mathcal{R}}^{\,}, \sigma$ & \textit{real}, \textit{quant}  \\
+\texttt{Scale} & Applies \texttt{RandomWalk} on the log-transformation (suitable for parameters with positive domains).
+& $\vec{\mathcal{R}}^{\,}, \sigma$ & \textit{cat}, \textit{real}, \textit{quant}  \\
   \hline
@@
   \hline
- \texttt{Swap} & Swaps two random elements in the vector \cite{drummond2006relaxed}. & $\vec{\mathcal{R}}^{\,}$  & \textit{cat}, \textit{real}, \textit{quant}  \\
+ \texttt{Swap} & Swaps two random elements within the vector \cite{drummond2006relaxed}. & $\vec{\mathcal{R}}^{\,}$  & \textit{cat}, \textit{real}, \textit{quant}  \\
  \hline
@@
  \texttt{Scale} and \texttt{CisScale} both operate on the clock model standard deviation $\sigma$ however they behave differently in the \textit{real} and \textit{quant} parameterisations (\textbf{Fig \ref{fig:clockSDoperators}}).
-In \textit{real}, large proposals of $\sigma \rightarrow \sigma^\prime$ made by  \texttt{Scale} are likely to be rejected due to large penalties in clock model prior $p(\vec{\mathcal{R}}^{\,}|\sigma^\prime)$.
-This led to the development of the fast clock scaler \cite{zhang2020improving} (herein referred to as \texttt{CisScale}), which recomputes all branch rates $\vec{\mathcal{R}}^{\,} \rightarrow \vec{\mathcal{R}}^{\, \prime}$ such that their quantiles under the new clock model prior remain constant $p(\vec{\mathcal{R}}^{\,}|\sigma) = p(\vec{\mathcal{R}}^{\, \prime}|\sigma^\prime)$.
+In \textit{real}, large proposals of $\sigma \rightarrow \sigma^\prime$ made by  \texttt{Scale} could incur large penalties in the clock model prior density $p(\vec{\mathcal{R}}^{\,}|\sigma^\prime)$ and thus may be rejected quite often.
+This led to the development of the fast clock scaler \cite{zhang2020improving} (herein referred to as \texttt{CisScale}).
+This operator recomputes all branch rates $\vec{\mathcal{R}}^{\,} \rightarrow \vec{\mathcal{R}}^{\, \prime}$ such that their quantiles under the new clock model prior remain constant $p(\vec{\mathcal{R}}^{\,}|\sigma) = p(\vec{\mathcal{R}}^{\, \prime}|\sigma^\prime)$.
 In contrast, a proposal made by \texttt{Scale} $\sigma \rightarrow \sigma^\prime$ under the \textit{quant} parameterisation implicitly alters all branch rates $r(\vec{\mathcal{R}}^{\,})$ while leaving the quantiles $\vec{\mathcal{R}}^{\,}$ themselves constant.
@@
 \caption{\textbf{Clock standard deviation scale operators.}
-The two operators above propose a clock standard deviation $\sigma^\prime \leftarrow \sigma \times e^{s\Sigma}$ for some step size $s \Sigma$. 
+The two operators above propose a clock standard deviation $\sigma \rightarrow \sigma^\prime$. 
 Then, either the new quantiles are such that the rates remain constant (``New quantiles'', above) or the new rates are  such that the quantiles remain constant (``New rates''). 
@@
 
-% Section intro
-% Give some examples of this operator working better on this dataset but not that one, where both operators apply to the same parameter eg. Constant Distance? Any others?
-% Bring up theme that this can be related to signal.
-Sampling from the prior may give better results when there is poor signal, whereas random-walk based operators may do better in the other case.
-Any general theoretical examples of this?
-
-It is not always clear which mixture of operators is best for a given dataset.
-In this article we introduce \texttt{AdaptiveOperatorSampler} -- a meta-operator which learns operator weights during MCMC and samples operators according to these weights.
-The meta-operator undergoes three phases.
+It is not always clear which operators weighting scheme is best for a given dataset.
+In this article we introduce \texttt{AdaptiveOperatorSampler} -- a meta-operator which learns the weights of other operators during MCMC and then samples these operators according to their learned weights.
+This meta-operator undergoes three phases.
 In the first phase (burn-in), \texttt{AdaptiveOperatorSampler} samples from its set of sub-operators uniformly at random.
@@
 \label{eqn:adaptiveSampler}
-	p(\omega_i) \propto \begin{cases} 1 & \text{ with probability } \Omega \\ \frac{1}{\mathbb{T}(\omega_i)} \sum\limits_{p \in \text{POI}}  \sum\limits_{x \in \text{accepts}(\omega_i)}  \mathbb{D}(x_p, x_p^\prime) & \text{ with probability } 1-\Omega \end{cases}
+	p(\omega) \propto \begin{cases} 1 & \text{ with probability } \Omega \\ \frac{1}{\mathbb{T}(\omega)} \sum\limits_{p \in \text{POI}}  \sum\limits_{x \in \text{accepts}(\omega)}  \mathbb{D}(x_p, x_p^\prime) & \text{ with probability } 1-\Omega \end{cases}
 \end{align}
@@
 where $\Omega = 0.01$ allows any sub-operator to be sampled regardless of its performance.
-The parameters of interest (POI) may be either a set of numerical parameters (such as branch rates or node heights), or it may be the tree itself, but it cannot be both.
-The distance between states $x_p$ and its (accepted) proposal $x_p^\prime$ with respect to parameter $p$ is determined by
+The parameters of interest (POI) may be either a set of numerical parameters (such as branch rates or node heights), or it may be the tree itself, but it cannot be both in its current form.
+The distance between state $x_p$ and its (accepted) proposal $x_p^\prime$ with respect to parameter $p$ is determined by
 
@@
 where \texttt{RF} is the Robinson-Foulds tree distance \cite{robinson1981comparison}, and $|p|$ is the number of dimensions of numerical parameter $p$ (1 for $\sigma$, $2N-2$ for $\vec{\mathcal{R}}^{\,}$, and $2N-1$ for node heights $t$).
-The remaining terms are trained during the second and third phases: the cumulative computational runtime spent on each operator $\mathbb{T}(\omega_i)$, the sample standard deviation $\sigma_p$ of each numerical parameter $p$, and the summed distances $\sum_x \mathbb{D}(x_p, x_p^\prime)$.
+The remaining terms are trained during the second and third phases: the cumulative computational runtime spent on each operator $\mathbb{T}(\omega)$, the sample standard deviation $\sigma_p$ of each numerical parameter $p$, and the summed distances $\sum_x \mathbb{D}(x_p, x_p^\prime)$.
 
@@
 
-Datasets with strong signal (or large $L$) are likely to achieve faster convergence when the more precise and meticulous kinds of operators are employed, such as those informed by correlations within the posterior distribution (\textbf{Fig \ref{fig:landscape}}).
-Whereas, datasets which contain very poor signal (or small $L$) are likely to mix faster when more weight is placed on bold operators. 
+Datasets which contain very poor signal (or small $L$) are likely to mix better when more weight is placed on bold operators (\textbf{Fig \ref{fig:landscape}}). 
 We therefore introduce the \texttt{SampleFromPrior($\vec{x}^{\,}$)} operator.
@@
 %The \texttt{Uniform} operator is a special case of \texttt{SampleFromPrior}.
-\texttt{SampleFromPrior} is always included among the mixture of operators under \texttt{AdaptiveOperatorSampler} and serves to make the boldest proposals for datasets with poor signal.
-Ideally, an operator to the likes of \texttt{AdaptiveOperatorSampler} would learn the combination of weights behind these classes of operators best suited for any given dataset.
+\texttt{SampleFromPrior} is included among the set of operators under \texttt{AdaptiveOperatorSampler} and serves to make the boldest proposals for datasets with poor signal.
 
@@
 Operators which attain an acceptance probability of 0.234 are often considered to have arrived at a suitable midpoint between these two extremes \cite{bouckaert2019beast, roberts1997weak}.
-The standard uniform distribution kernel has recently been challenged by the Bactrian kernel \cite{yang2013searching, thawornwattana2018designing}.
-The $\text{Bactrian}(m)$ distribution is defined as the sum of two Normal distributions:
+The standard uniform distribution kernel has recently been challenged by the Bactrian kernels \cite{yang2013searching, thawornwattana2018designing}.
+The (Gaussian) $\text{Bactrian}(m)$ distribution is defined as the sum of two Normal distributions:
 
@@
 
-where $0 \leq m < 1$ describes the modality of the Bactrian distribution.
-When $m=0$, the Bactrian distribution is equivalent to a $\text{Normal}(0, 1)$ distribution.
-As $m \rightarrow 1$, the distribution becomes increasingly bimodal (\textbf{Fig \ref{fig:bactrian}}).
+where $0 \leq m < 1$ describes the modality of the Bactrian distribution. When $m=0$, the Bactrian distribution is equivalent to a $\text{Normal}(0, 1)$ distribution. 
+As $m$ approaches 1, the distribution becomes increasingly bimodal (\textbf{Fig \ref{fig:bactrian}}). 
 Yang et al.
@@
 
-In this article we compare the performance of uniform and Bactrian(0.95) proposal kernels with respect to estimating clock model parameters $\vec{\mathcal{R}}^{\,}$ and $\sigma$. 
+In this article we compare the abilities of uniform and Bactrian(0.95) proposal kernels at estimating clock model parameters. 
 The clock model operators which these proposal kernels apply to are described in \textbf{Table \ref{table:bactriankernels}}.
@@
 
-\textul{\textit{Step 4}}. Relocate the $B-D$ branch onto the $C-E$ branch, so that $B$ and $C$ become siblings and their parent is $D$. All node heights are unchanged.
+\textul{\textit{Step 4}}. Relocate the $B-D$ branch onto the $C-E$ branch, so that $B$ and $C$ become siblings and their parent is $D$. All node heights remain constant.
 
@@
 The vertical axis corresponds to node height $t$.
-In the bottom figure, branch rates $r$ are indicated by line thickness.
+In the bottom figure, branch rates $r$ are indicated by line width and therefore genetic distances are equal to the width of each branch multiplied by its length.
 In this example, the $\mathcal{D}_{AE}$ and $\mathcal{D}_{CE}$ constraints are satisfied.}
@@
 
-We hypothesised that if \texttt{NarrowExchange} was adapted to the relaxed clock model by ensuring that genetic distances remain constant after the proposal (akin to the constant distance operators \cite{zhang2020improving}), then its ability to traverse the state space may improve.
+We hypothesised that if \texttt{NarrowExchange} was adapted to the relaxed clock model by ensuring that genetic distances remain constant after the proposal (parallel to the constant distance operators \cite{zhang2020improving}), then its ability to traverse the state space may improve.
 
@@
 
-for random walk step size $s\Sigma$ where $s$ is a tunable scaler parameter and $\Sigma$ is drawn from a uniform or \textbf{\nameref{sect:randomwalks}}.
+for random walk step size $s\Sigma$ where $s$ is tunable and $\Sigma$ is drawn from a Uniform or Bactrian distribution.
 NER (and NERw) are compatible with both the \textit{real} and \textit{quant} parameterisations.
 Analogous to the \texttt{ConstantDistance} operator, the proposed rates ensure that the genetic distances between nodes $A$, $B$, $C$, and $E$ are constant. 
-There are six pairwise distance between these four nodes and therefore six constraints:
+Let $\mathcal{D}_{ij}$ be the constraint defined by a constant genetic distance between nodes $i$ and $j$ before and after the proposal.
+There are six pairwise distances between these four nodes and therefore there are six such constraints:
 
@@
 Unfortunately, there is no solution to all six $\mathcal{D}_{ij}$ constraints unless non-positive rates or illegal trees are permitted.
- Therefore rather than conserving all six pairwise distances, NER conserves a \textit{subset} of distances. It is not immediately clear which subset should be conserved.
+ Therefore instead of conserving all six pairwise distances, NER conserves a subset of distances. It is not immediately clear which subset should be conserved.
 
@@
 \begin{align}
-	J &= \begin{bmatrix} \frac{\partial {r_A}^\prime}{\partial r_A} & \frac{\partial {r_A}^\prime}{\partial r_B} & \frac{\partial {r_A}^\prime}{\partial r_C} & \frac{\partial {r_A}^\prime}{\partial r_D} \\
-	\frac{\partial {r_B}^\prime}{\partial r_A} & \frac{\partial {r_B}^\prime}{\partial r_B} & \frac{\partial {r_B}^\prime}{\partial r_C} & \frac{\partial {r_B}^\prime}{\partial r_D} \\
-	\frac{\partial {r_C}^\prime}{\partial r_A} & \frac{\partial {r_C}^\prime}{\partial r_B} & \frac{\partial {r_C}^\prime}{\partial r_C} & \frac{\partial {r_C}^\prime}{\partial r_D} \\
-	\frac{\partial {r_D}^\prime}{\partial r_A} & \frac{\partial {r_D}^\prime}{\partial r_B} & \frac{\partial {r_D}^\prime}{\partial r_C} & \frac{\partial {r_D}^\prime}{\partial r_D} \end{bmatrix}.
+	J &= \begin{bmatrix} \frac{\partial {r_A}^\prime}{\partial r_A} & \frac{\partial {r_A}^\prime}{\partial r_B} & \frac{\partial {r_A}^\prime}{\partial r_C} & \frac{\partial {r_A}^\prime}{\partial r_D} & \frac{\partial {r_A}^\prime}{\partial t_D} \\
+	\frac{\partial {r_B}^\prime}{\partial r_A} & \frac{\partial {r_B}^\prime}{\partial r_B} & \frac{\partial {r_B}^\prime}{\partial r_C} & \frac{\partial {r_B}^\prime}{\partial r_D} & \frac{\partial {r_B}^\prime}{\partial t_D} \\
+	\frac{\partial {r_C}^\prime}{\partial r_A} & \frac{\partial {r_C}^\prime}{\partial r_B} & \frac{\partial {r_C}^\prime}{\partial r_C} & \frac{\partial {r_C}^\prime}{\partial r_D} & \frac{\partial {r_C}^\prime}{\partial t_D} \\
+	\frac{\partial {r_D}^\prime}{\partial r_A} & \frac{\partial {r_D}^\prime}{\partial r_B} & \frac{\partial {r_D}^\prime}{\partial r_C} & \frac{\partial {r_D}^\prime}{\partial r_D} & \frac{\partial {r_D}^\prime}{\partial t_D} \\
+\frac{\partial {t_D}^\prime}{\partial r_A} & \frac{\partial {t_D}^\prime}{\partial r_B} & \frac{\partial {t_D}^\prime}{\partial r_C} & \frac{\partial {t_D}^\prime}{\partial r_D} & \frac{\partial {t_D}^\prime}{\partial t_D}\end{bmatrix}.
 \nonumber  \\
@@
 
-\paragraph{3.
-Automated generation of BEAST2 operators.} Java class files are generated using string processing.
-Each class corresponds to a single operator, extends the class of a meta-NER-operator, and consists of the solutions found in \textbf{1} and the Jacobian determinant found in \textbf{2}.
+\paragraph{3. Automated generation of BEAST2 operators.} Java class files were generated using string processing. 
+Each class corresponded to a single operator, extended the class of a meta-NER-operator, and consisted of the solutions found in \textbf{1} and the Jacobian determinant found in \textbf{2}. 
 $|J|$ is further augmented if the \textit{quant} parameterisation is employed (\textbf{\nameref{sect:S1Appendix}}).
@@
 
-The best NER operator variant to proceed to benchmarking on empirical data (\textbf{\nameref{sect:results}}) was selected by  performing MCMC on simulated data, measuring the acceptance rates of each of the 96 NER/NERw variants, and comparing them with the null operator $\text{NER}\{\}$ / \texttt{NarrowExchange}.
+Selecting the best NER variant to proceed to benchmarking on empirical data (\textbf{\nameref{sect:results}}) was determined by performing MCMC on simulated data, measuring the acceptance rates of each of the 96 NER/NERw variants, and comparing them with the null operator $\text{NER}\{\}$ / \texttt{NarrowExchange}.
 In total, there were 300 simulated datasets each with $N=30$ taxa and varying alignment lengths.
@@
 
-These experiments showed that NER variants which satisfy the genetic distances between nodes $B$ and $A$ (i.e.
+These experiments showed that NER variants which satisfied the genetic distances between nodes $B$ and $A$ (i.e.
 $\mathcal{D}_{AB}$) or between $B$ and $C$ (i.e.
@@
 This is an intuitive result. 
-If there is high uncertainty in the positioning of $B$ with respect to $A$ and $C$, then there is no value in respecting either of these distance constraints, and the proposals made to the rates may often be too bold or the Green ratio $|J|$ too small for the proposal to be accepted.
+If there is high uncertainty in the positioning of $B$ with respect to $A$ and $C$, then there is no value in respecting either of these distance constraints, and the proposals made to the rates may often be too extreme or the Green ratio $|J|$ too small for the proposal to be accepted.
 
@@
 
-\textbf{Fig \ref{fig:acceptanceRateScreening}} also reveals a cluster of NER variants which -- under the conditions of the simulation --  performed better than the null operator $\text{NER}\{\}$ around 25\% of the time and performed worse around 10\% of the time.
-One such operator is  $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$  (\textbf{Algorithm \ref{alg:NER2}}). 
+\textbf{Fig \ref{fig:acceptanceRateScreening}} also revealed a cluster of NER variants which -- under the conditions of the simulation --  performed better than the null operator $\text{NER}\{\}$ around 25\% of the time and performed worse around 10\% of the time.
+One such operator was  $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$  (\textbf{Algorithm \ref{alg:NER2}}). 
 This variant conserves the genetic distance between nodes $A$, $B$, $C$ and their grandparent $E$. 
-Moreover, this operator performs well when branch rates have a large variance ($\sigma > 0.5$), corresponding to data which is not clock-like. 
-On the other hand, the null operator $\text{NER}\{\}$ performs better on shorter sequences ($L < 1$kb) and therefore weaker signal.  
-Overall, $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ outperforms the standard \texttt{NarrowExchange} operator when the data is not clock-like and contains enough signal.
+Moreover, this operator performed well when branch rates have a large variance ($\sigma > 0.5$), corresponding to non clock-like data. 
+On the other hand, the null operator $\text{NER}\{\}$ performed better on shorter sequences ($L < 1$kb) with weaker signal.  
+Overall, $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ outperformed the standard \texttt{NarrowExchange} operator when the data was not clock-like and contained enough signal.
 
 Finally, this initial screening showed that applying a (Bactrian) random walk to the node height $t_D$ made the operator worse.
-This effect was most dominant for the NER variants which satisfy distance constraints (i.e. the operators which are not $\text{NER}\{\}$).
+This effect was most dominant for the NER variants which satisfied distance constraints (i.e. the operators which are not $\text{NER}\{\}$).
 
@@
 
-The AVMVN kernel assumes its parameters live in $x \in \mathbb{R}^N$ and that these parameters follow a Multivariate Normal distribution with covariance matrix $\Sigma_N$.
+The AVMVN kernel assumes its parameters live in $x \in \mathbb{R}^N$ for taxon count $N$ and that these parameters follow a Multivariate Normal distribution with covariance matrix $\Sigma_N$.
 Hence, the kernel operates on the logarithmic or logistic transformation of the $N$ leaf branch rates, depending on the rate parameterisation:
@@
 where $\mathcal{MVN}$ is the Multivariate Normal probability density.
-$\beta \; (= 0.05)$ is a constant which determines the fraction of the proposal determined by the identity matrix $\mathbb{I}_N$, as opposed to the covariance matrix $\Sigma_D$ which is trained during MCMC.
+$\beta  = 0.05$ is a constant which determines the fraction of the proposal determined by the identity matrix $\mathbb{I}_N$, as opposed to the covariance matrix $\Sigma_D$ which is trained during MCMC.
 Our BEAST2 implementation of the AVMVN kernel is adapted from that of BEAST \cite{suchard2018bayesian}.
@@
 As the size of the covariance matrix $\Sigma_N$ grows with the number of taxa $N$, \texttt{LeafAVMVN} is likely to be less efficient with larger taxon sets.
-Therefore, we learn the weight behind this operator using \texttt{AdaptiveOperatorSampler}.
-
-To avoid the learned weight behind \texttt{LeafAVMVN} dominating the \texttt{AdaptiveOperatorSampler} weighting scheme and therefore inhibiting the mixing of internal node rates, we 
+Therefore, the weight behind this operator is learned by \texttt{AdaptiveOperatorSampler}.
+
+To prevent the learned weight behind \texttt{LeafAVMVN} from dominating the \texttt{AdaptiveOperatorSampler} weighting scheme and therefore inhibiting the mixing of internal node rates, we 
 introduce the \texttt{AdaptiveOperatorSampler(leaf)} and \texttt{AdaptiveOperatorSampler(internal)} meta-operators which operate exclusively on leaf node rates $\vec{\mathcal{R}}^{\,}_\text{leaf}$ and internal node rates $\vec{\mathcal{R}}^{\,}_\text{int}$ respectively  (\textbf{Table \ref{table:AVMVNoperators}}).
@@
 \caption{Leaf rate $\vec{\mathcal{R}}^{\,}_\text{leaf}$ and internal node rate $\vec{\mathcal{R}}^{\,}_\text{int}$ operators. 
-This division enables the two meta-operators to be weighted proportionally to the number of nodes (leaves or internal) which it applies to.
+This division enables the two meta-operators to be weighted proportionally to the number of nodes (leaves or internal) which they apply to.
 This facilitates incorporation of the  \texttt{LeafAVMVN} operator, which is only applicable to leaf nodes.
@@
 Datasets are partitioned into subsequences, where each partition is associated with a distinct HKY substitution model \cite{hasegawa1985dating}.
-The transition-transversion ratio $\kappa \sim \text{Log-Normal}(1, 1.25)$, the four nucleotide frequencies $(f_A, f_C, f_G, f_T) \sim \text{Dirichlet}(10,10,10,10)$, and the relative clock rate $\mu_C \sim \text{Log-Normal}(1, 0.6)$ are estimated independently for each partition.
+The transition-transversion ratio $\kappa \sim \text{Log-Normal}(1, 1.25)$, the four nucleotide frequencies $(f_A, f_C, f_G, f_T) \sim \text{Dirichlet}(10,10,10,10)$, and the relative clock rate $\mu_C \sim \text{Log-Normal}(-0.18, 0.6)$ are estimated independently for each partition.
 The operator scheme ensures that the clock rates $\mu_C$ have a mean of 1 across all partitions. 
+This avoids non-identifiability with branch substitution rates.
 To enable the rapid benchmarking of larger datasets we use BEAGLE for high-performance tree likelihood calculations \cite{ayres2012beagle} and coupled MCMC with four chains for efficient mixing \cite{muller2019coupled}.
@@
   \hline
- \texttt{NarrowExchangeRate} & Moves a branch and recomputes branch rates so that genetic distances are constant (see \nameref{sect:NER}). & $\vec{\mathcal{R}}^{\,}, \mathcal{T}$\\
-  \hline
- \texttt{LeafAVMVN}  & Proposals new rates for all leaves in one move (see \nameref{AVMVN_sect}) \cite{baele2017adaptive}. & $\vec{\mathcal{R}}^{\,}$ \\
+ \texttt{NarrowExchangeRate} & Moves a branch and recomputes branch rates so that their genetic distances are constant (see \nameref{sect:NER}). & $\vec{\mathcal{R}}^{\,}, \mathcal{T}$\\
+  \hline
+ \texttt{LeafAVMVN}  & Proposes new rates for all leaves in one move (see \nameref{AVMVN_sect}) \cite{baele2017adaptive}. & $\vec{\mathcal{R}}^{\,}$ \\
 \end{tabular}
@@
   \hline
- \multirow{6}{*}{nocons} & \texttt{RandomWalk($\mathcal{R}$)} & $10$ & \checkmark &&  \\
+ \multirow{6}{*}{nocons} & \texttt{RandomWalk($\vec{\mathcal{R}}^{\,}$)} & $10$ & \checkmark & \checkmark &  \\
  	& \texttt{Scale($\vec{\mathcal{R}}^{\,}$)} & $10$ & \checkmark && \\ 
@@
    & \texttt{ConstantDistance($\vec{\mathcal{R}}^{\,}, \mathcal{T}$)} & $20 \times \frac{2N-2}{2N-1}$ & \checkmark & & \checkmark  \\
-   & \texttt{SimpleDistance($\vec{\mathcal{R}}^{\,}, \mathcal{T}$)} & $10 \times \frac{2N-2}{2N-1}$ & \checkmark & & \checkmark  \\
-   & \texttt{SmallPulley($\vec{\mathcal{R}}^{\,}$)} & $10 \times \frac{2N-2}{2N-1}$ & \checkmark & & \checkmark  \\
+   & \texttt{SimpleDistance($\vec{\mathcal{R}}^{\,}, \mathcal{T}$)} & $\frac{20}{2} \times \frac{1}{2N-1}$ & \checkmark & & \checkmark  \\
+   & \texttt{SmallPulley($\vec{\mathcal{R}}^{\,}$)} & $\frac{20}{2} \times \frac{1}{2N-1}$ & \checkmark & & \checkmark  \\
    & \texttt{RandomWalk($\vec{\mathcal{R}}^{\,}$)} & $5$ & \checkmark &&  \\
@@
  	& \texttt{Swap($\vec{\mathcal{R}}^{\,}$)} & $2.5$ & \checkmark & & \checkmark  \\ 
- 	& \texttt{CisScale($\sigma, \vec{\mathcal{R}}^{\,}$)} & $10$ & \checkmark  && \checkmark \\ 
+ 	& \texttt{CisScale($\sigma, \vec{\mathcal{R}}^{\,}$)} & $10$ & \checkmark  &&  \\ 
  	& \texttt{Scale($\sigma$)} & $10$ &  &&\checkmark \\ 
@@
 \end{tabular}
-\caption{Operator configurations and the substitution rate parameterisations which each operator are applicable to.
-Within each configuration (and substitution rate parameterisation), the weight behind $\mathcal{R}$ sums to 30, the weight of $\sigma$ is equal to 10, and the weight of NER is equal to 15.
+\caption{Operator configurations and the substitution rate parameterisations which each operator is applicable to.
+Within each configuration (and substitution rate parameterisation), the weight behind $\vec{\mathcal{R}}^{\,}$ sums to 30, the weight of $\sigma$ is equal to 10, and the weight of NER is equal to 15.
 %There is no cons (\textit{cat}) configuration because the parameterisation is not compatible the constant distance operators.
-Operators which apply to either internal nodes or the root (but not both) are weighted according to leaf count $N$.
-The adaptive operators are further broken down in \textbf{Tables \ref{table:adaptiveSampling}, \ref{table:adaptiveNER}, and \ref{table:AVMVNoperators}}.
+Operators which apply to specific node sets (root, internal, leaf, or all)
+ are weighted according to leaf count $N$. The adaptive operators are further broken down in \textbf{Tables \ref{table:adaptiveSampling}, \ref{table:adaptiveNER}, and \ref{table:AVMVNoperators}}.
 All other operators (i.e. those which apply to which apply to other terms in the state such as the nucleotide substitution model) are held constant within each dataset.
@@
 \centering
-\begin{tabular}{l l l l l l} 
-  & $N$ & $P$ & $L$ (kb) & $L_\text{unq}$ (kb) & \textbf{Description} \\
-  \hline
-
- 1  &  38  &  16  &  15.5  &  10.5  &  Seed plants (Ran 2018 \cite{Ran_2018}) \\
-
-2  &  44  &  7  &  5.9  &  1.8  &  Squirrel Fishes (Dornburg 2012 \cite{Dornburg_2012}) \\
-
-3  &  44  &  3  &  1.9  &  0.8  &  Bark beetles (Cognato 2001 \cite{Cognato_2001}) \\
-
-4  &  51  &  6  &  5.4  &  1.8  &  Southern beeches (Sauquet 2011 \cite{Sauquet_2011}) \\
-
-5  &  61  &  8  &  6.9  &  4.3  &  Bony fishes (Broughton 2013 \cite{Broughton_2013}) \\
-
-6  &  70  &  3  &  2.2  &  0.9  &  Caterpillars (Kawahara 2013 \cite{Kawahara_2013}) \\
-
-7  &  80  &  1 &  10.0  &  0.9  &  \textit{Simulated data}  \\
-
-8  &  94  &  4  &  2.2  &  1  &  Bees (Rightmyer 2013 \cite{Rightmyer_2013}) \\
-
-9  &  106  &  1  &  0.8  &  0.5  &  Songbirds (Moyle 2016 \cite{Moyle_2016}) \\
+\begin{tabular}{l l l l l l l} 
+  & $N$ & $P$ & $L$ (kb) & $L_\text{unq}$ (kb) & $\hat{\sigma}$ & \textbf{Description} \\
+  \hline
+
+ 1  &  38  &  16  &  15.5  &  10.5 &  0.44 &  Seed plants (Ran 2018 \cite{Ran_2018}) \\
+
+2  &  44  &  7  &  5.9  &  1.8& 0.30 &  Squirrel Fishes (Dornburg 2012 \cite{Dornburg_2012}) \\
+
+3  &  44  &  3  &  1.9  &  0.8& 0.27  &  Bark beetles (Cognato 2001 \cite{Cognato_2001}) \\
+
+4  &  51  &  6  &  5.4  &  1.8 & 0.52 &  Southern beeches (Sauquet 2011 \cite{Sauquet_2011}) \\
+
+5  &  61  &  8  &  6.9  &  4.3 & 0.53 &  Bony fishes (Broughton 2013 \cite{Broughton_2013}) \\
+
+6  &  70  &  3  &  2.2  &  0.9  & 0.19 &  Caterpillars (Kawahara 2013 \cite{Kawahara_2013}) \\
+
+7  &  80  &  1 &  10.0  &  0.9 & 0.82 &  \textit{Simulated data}  \\
+
+8  &  94  &  4  &  2.2  &  1 & 0.34 &  Bees (Rightmyer 2013 \cite{Rightmyer_2013}) \\
+
+9  &  106  &  1  &  0.8  &  0.5 & 0.37 &  Songbirds (Moyle 2016 \cite{Moyle_2016}) \\
 
@@
 Number of partitions $P$, total alignment length $L$, and number of unique site patterns $L_\text{unq}$ in the alignment are also specified.
+Clock standard deviation estimates $\hat\sigma$ are of moderate magnitude, suggesting that most of these datasets are not clock-like.
 }
@@
 \caption{\textbf{Round 1: benchmarking the \texttt{AdaptiveOperatorSampler} operator.} Top left, top right, bottom left: each plot compares the ESS/hr ($\pm 1$ standard error) across two operator configurations.
-Bottom right: the effect of sequence length $L$ on operator weights learned by \texttt{AdaptiveOperatorSampler}. Both sets of results are fit by a logistic regression curve.
+Bottom right: the effect of sequence length $L$ on operator weights learned by \texttt{AdaptiveOperatorSampler}. Both sets of observations are fit by logistic regression models.
  The benchmark datasets are displayed in \textbf{Table \ref{table:datasets}}. The \emph{cat} and \emph{quant} settings are evaluated in \textbf{\nameref{sect:SR_appendix}}.  }
@@
 This experiment showed that the \textit{real} parameterisation greatly outperformed \textit{cat} on most datasets and most parameters (\textbf{Fig \ref{fig:round2Results}}).
-This disparity is strongest for long alignments.
-In the most extreme case, leaf substitution rates $r$ and clock standard deviation $\sigma$ both mixed around 50 $\times$ faster on the 15.5 kb seed plant dataset \cite{Ran_2018} for \textit{real} than they did for \textit{cat}.
+This disparity was strongest for long alignments.
+In the most extreme case, leaf substitution rates $r$ and clock standard deviation $\sigma$ both mixed around $50\times$ faster on the 15.5 kb seed plant dataset (Ran et al.
+2018 \cite{Ran_2018}) for \textit{real} than they did for \textit{cat}.
 The advantages in using constant distance operators would likely be even stronger for larger $L$.
-Furthermore, \textit{real} outperformed \textit{quant} on most datasets, but this is mostly due to the slow computational performance of \textit{quant} compared with real, as opposed to differences in mixing prowess (\textbf{\nameref{sect:SR_appendix}}).
+Furthermore, \textit{real} outperformed \textit{quant} on most datasets, but this was mostly due to the slow computational performance of \textit{quant} compared with real, as opposed to differences in mixing prowess (\textbf{Fig \ref{fig:round2Resultsb}}).
+Irrespective of mixing ability, the adapt (\textit{real}) configuration had the best computation performance and generated samples 40\% faster than adapt (\textit{cat}) and 60\% faster than adapt (\textit{quant}).
 
@@
 \label{fig:round2Results}
+\end{figure}
+
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{benchmarking/benchmarkingVM/ESS_timesettings.pdf}
+\caption{\textbf{Comparison of runtimes across methodologies.} 
+The computational time required for a setting to sample a single state is divided by that of the nocons (\textit{cat}) configuration.
+The geometric mean under each congifuration, averaged across all 9 datasets, is displayed as a horizontal bar.}
+\label{fig:round2Resultsb}
 \end{figure}
@@
 In this round we benchmarked the Bactrian + adapt (\textit{real}) setting with the adaptive $\text{NER}$ operator (\textbf{Table \ref{table:operatorSchemes}}).
+The benchmark datasets are fairly non clock-like and therefore could benefit from NER (\textbf{Table \ref{table:datasets}}).
 
 Our experiments confirmed that $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ was indeed superior on larger datasets (where $L > 2$kb; \textbf{Fig \ref{fig:round4Results}}).
-While there was no significant difference in the ESS/hr of continuous parameters, $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ did have an acceptance rate 41\% higher than that of the standard \texttt{NarrowExchange} operator in the most extreme case (the 7kb alignment by Broughton et al.\cite{Broughton_2013}).
+While there was no significant difference in the ESS/hr of continuous parameters, $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ did have an acceptance rate 41\% higher than that of the standard \texttt{NarrowExchange} operator in the most extreme case (the bony fish alignment by Broughton et al.\cite{Broughton_2013}).
+The moderate variance in branch substitution rates ($\hat{\sigma} = 0.5$), coupled with a long alignment (7kb), and high topological uncertainty (\textbf{Fig \ref{fig:parameterisationResults}}) make this dataset the perfect canidate for the NER operator.
 Every proposal acceptance yields a new tree topology and thus facilitates traversal of tree space.
@@
 
+\begin{figure}[!h]
+%\includegraphics[width=\textwidth]{Figures/cognato.pdf}
+\includegraphics[width=\textwidth]{Figures/broughton.pdf}
+\caption{\textbf{Maximum clade credibility tree of bony fishes.} 
+Branches are coloured by substitution rate (units: substitutions per site per unit of time) and the y-axis shows time, such that there is on average 1 substitution per unit of time.
+Internal nodes are labelled with posterior clade support. 
+This alignment (Broughton et al.
+2013 \cite{Broughton_2013}) received the strongest boost from the $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ operator, likely due to its high topological uncertainty and branch rate variance.
+Tree generated by UglyTrees \cite{uglytrees}.  }
+\label{fig:parameterisationResults}
+\end{figure}
+
 \subsection*{Round 5: The AVMVN leaf rate operator is computationally demanding and improves mixing slightly}
 
-We wanted to test the applicability of the adaptive AVMVN kernel to leaf rate proposals.
-This would operate by exploiting any correlations which occur between leaf branch substitution rates.
+We tested the applicability of the AVMVN kernel to leaf rate proposals.
+This operates by exploiting any correlations which occur between leaf branch substitution rates.
 To do this, we wrapped the \texttt{LeafAVMVN} operator within an \texttt{AdaptiveOperatorSampler} (\textbf{Table \ref{table:AVMVNoperators}}).
@@
 
-These results showed that the AVMVN operator yielded slightly better mixing (around 6\% faster) for the tree likelihood, the tree length and the mean branch rate (\textbf{Table \ref{fig:round5Results}}).
-However, it also produced slightly slower mixing for $\kappa$, reflecting the high computational costs associated with the \texttt{LeafAVMVN} operator (\textbf{\nameref{sect:SR_appendix}}).
+These results showed that the AVMVN operator yielded slightly better mixing (around 6\% faster) for the tree likelihood, the tree length, and the mean branch rate (\textbf{Fig \ref{fig:round5Results}}).
+However, it also produced slightly slower mixing for $\kappa$, reflecting the high computational costs associated with the \texttt{LeafAVMVN} operator (\textbf{Fig \ref{fig:round2Resultsb}}).
 The learned weight of the \texttt{LeafAVMVN} operator was quite small (ranging from 1 to 8\% across all datasets), again reflecting its high computational costs, but also reinforcing the value in having an adaptive weight operator which penalises slow operators.
@@
 Averaged across all datasets, this configuration yielded a relaxed clock  mixing rate between 1.2 and 13 times as fast as \textit{cat} and between 1.8 and 7.8 times as fast as cons (\textit{real}), depending on the parameter.
-For the largest dataset considered (Ran et al. 2018 \cite{Ran_2018}), the new settings were up to 66 and 37 times as fast respectively.
+For the largest dataset considered (seed plants by Ran et al. 2018 \cite{Ran_2018}), the new settings were up to 66 and 37 times as fast respectively.
 This is likely to be even more extreme for larger alignments.
 
-\newpage
 \section*{Discussion} \label{sect:discussion}
 
-In this article, we delved into the highly correlated structure of relaxed clock models, in order to develop MCMC operators which traverse its posterior space efficiently.
-We introduced a range of relaxed clock model operators and compared three molecular substitution rate parameterisations.
-These methodologies were compared by constructing phylogenetic models from several empirical datasets (\textbf{Fig \ref{fig:parameterisationResults}}) and comparing their abilities to converge in a tournament-like protocol (\textbf{Fig \ref{fig:tournament}}).
-This work has produced an operator configuration which explores relaxed clock model space up to an order of magnitude more efficiently than previous setups.
-
-\begin{figure}[!h]
-\includegraphics[width=\textwidth]{Figures/cognato.pdf}
-\includegraphics[width=\textwidth]{Figures/broughton.pdf}
-\caption{\textbf{Relaxed clock phylogenies.} 
-Maximum clade credibility trees of bark beetles (Cognato et al. 2001 \cite{Cognato_2001}; top) and bony fishes (Broughton et al. 2013 \cite{Broughton_2013}; bottom) are presented. 
-Branches are coloured by substitution rate (units: substitutions per site per unit of time) and the y-axis shows time, such that there is on average 1 substitution per unit of time.
- Internal nodes are labelled with posterior clade support. Figures generated by UglyTrees \cite{uglytrees}.  }
-\label{fig:parameterisationResults}
-\end{figure}
-
 % Points to cover
@@
 Adaptability and advanced proposal kernels, such as Bactrian kernels, are increasingly prevalent in MCMC operator design \cite{haario2001adaptive,vihola2012robust,benson2018adaptive,davis2020blocking}.
-
 Adaptive operators undergo training to improve their efficiency over time \cite{roberts2007coupling}. 
 In previous work, the conditional clade probabilities of neighbouring trees have served as the basis of adaptive tree operators \cite{hohna2012guided,meyer2019adaptive}.
+Proposal step sizes can be tuned during MCMC \cite{rosenthal2011optimal}.
 The mirror kernel learns a target distribution which acts as a ``mirror image'' of the current point \cite{thawornwattana2018designing}.
@@
 
-We also found that Bactrian proposal kernels quite reliably increased mixing efficiency by 15--20\% (\textbf{Fig \ref{fig:round3Results}}).
+We also found that a Bactrian proposal kernel quite reliably increased mixing efficiency by 15--20\% (\textbf{Fig \ref{fig:round3Results}}).
 Similar observations were made by Yang et al. \cite{yang2013searching}.
-While this may only be a modest improvement, incorporation of the Bactrian kernel into pre-existing operators is a computationally straightforward task and should be routinely implemented in Bayesian MCMC software packages.
+While this may only be a modest improvement, incorporation of the Bactrian kernels into pre-existing operators is a computationally straightforward task and we recommend implementing them in Bayesian MCMC software packages.
 
@@
 
-Lakner et al. categorised tree operators into two classes.
+Lakner et al. 2008 categorised tree operators into two classes.
 ``Branch-rearrangement'' operators relocate a branch and thus alter tree topology. 
@@
  Such operators include subtree slide \cite{hohna2008clock}, LOCAL \cite{simon1998local}, and continuous change \cite{jow2002bayesian}.
-Lakner et al. observed that topological proposals made by the former class consistently outperformed topological changes invoked by the latter class \cite{lakner2008efficiency}.
+Lakner et al. 2008 observed that topological proposals made by the former class consistently outperformed topological changes invoked by the latter class \cite{lakner2008efficiency}.
 
@@
 
+These findings support Lakner's hypothesis.
 The design of operators which are able to efficiently traverse topological and branch length spaces simultaneously remains an open problem.
@@
 As signal within the dataset becomes stronger, the posterior distribution becomes increasingly peaked (\textbf{Fig \ref{fig:landscape}}).
-This topological change in the landscape necessitates the use of operators which exploit known correlations in the posterior density, such as AVMVN \cite{baele2017adaptive}, constant distance operators \cite{zhang2020improving}, and the narrow exchange rate operators introduced in this article.
+This change in the posterior topology necessitates the use of operators which exploit known correlations in the posterior density; operators such as AVMVN \cite{baele2017adaptive}, constant distance \cite{zhang2020improving}, and the narrow exchange rate operators introduced in this article.
 
 We have shown that while the latter two operators are efficient on large alignments, they are also quite frequently outperformed by simple random walk operators on small alignments.
-For instance, constant distance operators outperformed standard operator configurations by up to an order of magnitude on larger datasets but they were up to three times slower on smaller ones (\textbf{Fig \ref{fig:round1Results}}).
+For instance, we found that constant distance operators outperformed standard operator configurations by up to two orders of magnitude on larger datasets but they were up to three times slower on smaller ones (\textbf{Fig \ref{fig:round1Results}}).
 Similarly, our narrow exchange rate operators were up to 40\% more efficient on large datasets but up to 10\% less efficient on smaller ones (\textbf{Fig \ref{fig:round4Results}}).
@@
 This emphasises the value in our adaptive operator weighting scheme, which can ensure that operator weights are suitable for the size of the alignment.
-Given the immense availability of sequence data, and the increased computational cost required to process it, high performance on large datasets is a desirable property.
-
-\newpage
+Given the overwhelming availability of sequence data, high performance on large datasets is more important than ever.
+
+\section*{Conclusion}
+
+In this article, we delved into the highly correlated structure between substitution rates and divergence times of relaxed clock models, in order to develop MCMC operators which traverse its posterior space efficiently.
+We introduced a range of relaxed clock model operators and compared three molecular substitution rate parameterisations.
+These methodologies were compared by constructing phylogenetic models from several empirical datasets and comparing their abilities to converge in a tournament-like protocol (\textbf{Fig \ref{fig:tournament}}).
+The methods introduced are adaptive and treat each dataset differently.
+This work has produced an operator configuration which is highly effective  on large alignments and can explore relaxed clock model space up to two orders of magnitude more efficiently than previous setups.
+
+%Averaged across all datasets, this configuration yielded a relaxed clock  mixing rate between 1.2 and 13 times as fast as \textit{cat} and between 1.8 and 7.8 times as fast as cons (\textit{real}), depending on the parameter.
+%For the largest dataset considered (seed plants by Ran et al. 2018 \cite{Ran_2018}), the new settings were up to 66 and 37 times as fast respectively.
+%This is likely to be even more extreme for larger alignments.
+
+\section*{Software availability}
+
+The work presented in this article was implemented as a BEAST2 package.
+Instructions for using and installing this package can be found at \href{https://github.com/jordandouglas/ADFP}{https://github.com/jordandouglas/ADFP}.
+
+\section*{Acknowledgements}
+
+We wish to thank Alexei J. Drummond for his help during conception of the narrow exchange rate operators.
+
 \section*{Supporting information}
@@
 {\textbf{Rate quantiles.} The linear piecewise approximation used in the \textit{quant} parameterisation is described. 
-\texttt{Constant distance} tree operators \cite{zhang2020improving} are extended to the \textit{quant} parameterisation.
+Constant distance tree operators, \texttt{CisScale}, and  \texttt{NarrowExchangeRate} are extended to the \textit{quant} parameterisation.
 

### 2020-09-02 manuscript.tex
typo

@@
 While there was no significant difference in the ESS/hr of continuous parameters, $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ did have an acceptance rate 41\% higher than that of the standard \texttt{NarrowExchange} operator in the most extreme case (the bony fish alignment by Broughton et al.\cite{Broughton_2013}).
-The moderate variance in branch substitution rates ($\hat{\sigma} = 0.5$), coupled with a long alignment (7kb), and high topological uncertainty (\textbf{Fig \ref{fig:parameterisationResults}}) make this dataset the perfect canidate for the NER operator.
+The moderate variance in branch substitution rates ($\hat{\sigma} = 0.5$), coupled with a long alignment (7kb), and high topological uncertainty (\textbf{Fig \ref{fig:parameterisationResults}}) make this dataset the perfect candidate for the NER operator.
 Every proposal acceptance yields a new tree topology and thus facilitates traversal of tree space.

### 2020-09-02 benchmarking/benchmarkingVM/ORC.sh
Update xmls so they work with ORC package

@@ -1,0 +1,63 @@
+#!/bin/sh
+
+
+
+
+#settings=("real" "real_adaptive" "cat" "quant" "AVMN" "bactrian98" "bactrian95" "NER" "real_06" "quant_06")
+settings=("cat" "cat_adaptive" "real" "real_06" "real_adaptive" "quant_cached" "quant_cached_adaptive" "quant_06_cached" "bactrian95" "NER" "AVMVN")
+
+datasets=("simulated" "Ran_2018_dna" "Rightmyer_2013" "Broughton_2013" "Sauquet_2011" "Moyle_2016" "Dornburg_2012" "Kawahara_2013" "Cognato_2001")
+
+
+
+
+# Randomly shuffle the datasets
+#datasets_shuffled=( $(shuf -e "${datasets[@]}") )
+
+for d in ${datasets[@]} ; do
+    echo "$d"
+    cd $d
+
+	dshort="${d:0:4}"
+
+    for e in */ ; do
+        echo "$e"
+        cd $e
+
+
+		rm -f temp*.xml
+
+          # Randomly shuffle the settings
+          settings_shuffled=( $(shuf -e "${settings[@]}") )
+          #for s in "${settings_shuffled[@]}"
+         # do
+		  
+			
+		
+			
+			#xml="benchmark_${s}.xml"
+			#echo "Modifying ${xml}"
+			#sed "s/inference.TipRateLogger/orc.inference.TipRateLogger/g" ${xml} > temp.xml
+			#sed "s/NERVariants/orc.ner/g" temp.xml > temp2.xml
+			#sed "s/AdaptableOperatorSampler/orc.operators.AdaptableOperatorSampler/g" temp2.xml > temp.xml
+			#sed "s/SampleFromPriorOperator/orc.operators.SampleFromPriorOperator/g" temp.xml > temp2.xml
+			
+			#rm temp.xml
+
+			#mv temp2.xml ${xml}
+
+
+		#done
+
+        cd ../
+    done
+
+
+    cd ../
+
+
+done
+
+
+
+

### 2020-09-03 S3_appendix.tex
polishing

@@
 Rong Zhang\textsuperscript{1,2},
-Alexei J. Drummond\textsuperscript{1,2,3},
-Remco Bouckaert\textsuperscript{1,2}
+Remco Bouckaert\textsuperscript{1,2,3}
 \\
@@
 \textbf{2} School of Computer Science, University of Auckland, Auckland, New Zealand\\
-\textbf{3} School of Biological Sciences, University of Auckland, Auckland, New Zealand
-\\
+\textbf{3} Max Planck Institute for the Science of Human History, Jena, Germany\\
 \bigskip
@@
 \caption{\textbf{Round 1: Performance evaluation of \texttt{AdaptiveOperatorSampler} under the \emph{quant} and \emph{cat} parameterisations.}
-These results show that neither \emph{cat} nor \emph{quant} benefit strongly from adaptive weight sampling.
-The constant distance operators (cons) greatly improves the \emph{quant} parameterisation for most datasets, as expected.
-}
+These results show that \emph{cat} does not benefit from adaptive weight sampling. Whereas, adapt and cons both greatly improve the \emph{quant} parameterisation for most datasets, as expected. }
 \end{figure}

### 2020-09-03 manuscript.tex
polishing

@@
 Rong Zhang\textsuperscript{1,2},
-Remco Bouckaert\textsuperscript{1,2}
+Remco Bouckaert\textsuperscript{1,2,3}
 \\
@@
 \textbf{2} School of Computer Science, University of Auckland, Auckland, New Zealand\\
+\textbf{3} Max Planck Institute for the Science of Human History, Jena, Germany\\
 \bigskip
@@
 %Molecular clock models are used for dating evolutionary divergence times. 
-Relaxed clock models enable estimation of molecular substitution rates across lineages and are widely used in phylogenetics.
-This can be used for dating evolutionary divergence times.
+Uncorrelated relaxed clock models enable estimation of molecular substitution rates across lineages and are widely used in phylogenetics for dating evolutionary divergence times.
 In this article we delved into the internal complexities of the relaxed clock model in order to develop efficient MCMC operators for Bayesian phylogenetic inference.
-We compared three substitution rate parameterisations, we introduced an adaptive operator which learns the weights of other operators during MCMC and, we explored how relaxed clock model estimation can benefit from two cutting-edge proposal kernels: the AVMVN and Bactrian kernels.
+We compared three substitution rate parameterisations,  introduced an adaptive operator which learns the weights of other operators during MCMC and, we explored how relaxed clock model estimation can benefit from two cutting-edge proposal kernels: the AVMVN and Bactrian kernels.
 This work has produced an operator scheme that is up to 65 times more efficient at exploring continuous relaxed clock parameters compared with previous setups, depending on the dataset.
+%RB: 65 or 66 mentioned later?
 Finally, we explored variants of the standard narrow exchange operator which are specifically designed for the relaxed clock model.
 In the most extreme case, this new operator traversed tree space 40\% more efficiently than narrow exchange.
-The methodologies introduced are adaptive and highly effective on long alignments.
+The methodologies introduced are adaptive and highly effective on short as well as long alignments.
+The results are available via the open source optimised relaxed clock (ORC) package for BEAST 2 under the LGPL 2(?) licence (\url{https://github.com/jordandouglas/ORC}).
 
@@
 With the overwhelming availability of biological sequence data, and the increasing affordability of collecting new data, the development of fast and efficient phylogenetic algorithms is more important than ever.
-In this article we focus on the relaxed clock model, which is widely used in phylogenetics.
+In this article we focus on the relaxed clock model, which is very popular in phylogenetics.
 We explored how a range of optimisations can improve the statistical inference of the relaxed clock.
-This work has produced a phylogenetic setup which can infer parameters related to the relaxed clock up to 65 times faster than previous setups, depending on the dataset.
+This work has produced a phylogenetic setup which can infer parameters related to the relaxed clock up to 65 times faster than previous setups, depending on the dataset. %RB: 65 or 66 mentioned later?
 The methods introduced adapt to the dataset during computation and are highly efficient when processing long biological sequences.
@@
 In Bayesian phylogenetics, these trees and their associated parameters are estimated as probability distributions \cite{kuhner1995estimating, larget1999markov, mau1999bayesian}. 
-Statistical inference can be performed by the Markov chain Monte Carlo (MCMC) algorithm \cite{metropolis53, hastings70} using platforms such as BEAST \cite{drummond2012bayesian}, BEAST2 \cite{bouckaert2019beast}, MrBayes \cite{ronquist2012mrbayes}, and RevBayes \cite{hohna2016revbayes}.
+Statistical inference can be performed by the Markov chain Monte Carlo (MCMC) algorithm \cite{metropolis53, hastings70} using platforms such as BEAST \cite{drummond2012bayesian}, BEAST 2 \cite{bouckaert2019beast}, MrBayes \cite{ronquist2012mrbayes}, and RevBayes \cite{hohna2016revbayes}.
 
@@
 In the latter case, a strict clock is probably not suitable. 
+In the remainder of this paper %RB: "article" and "paper" are used a few times -- should we keep things consistent to either "paper" or "article"?
+we will only consider uncorrelated relaxed clock models.
 
 This led to the development of relaxed (uncorrelated) clock models, under which each branch in the phylogenetic tree has its own molecular substitution rate  \cite{drummond2006relaxed}.
-Branch rates can be drawn from a range of probability distributions including Log-Normal, Exponential, Gamma, and Inverse-Gamma distributions \cite{drummond2006relaxed, lepage2007general, li2012model}.
+Branch rates can be drawn from a range of probability distributions including log-normal, exponential, gamma, and inverse-gamma distributions \cite{drummond2006relaxed, lepage2007general, li2012model}.
 This class of models is widely used, and has aided insight into many recent biological problems, including the 2016 Zika virus outbreak \cite{faria2017establishment} and the COVID-19 pandemic \cite{giovanetti2020first}.
-% is compatible with increasingly prominent multispecies coalescent models \cite{ogilvie2017starbeast2},
+% is compatible with increasingly prominent multispecies coalescent models \cite{ogilvie2017starBEAST 2},
 
@@
 
-While a range of advanced operators and other MCMC optimisation methods have arisen over the years, there has yet to be a widescale performance benchmarking of such methods as applied to the relaxed clock model.
+While a range of advanced operators and other MCMC optimisation methods have arisen over the years, there has yet to be a large scale performance benchmarking of such methods as applied to the relaxed clock model.
 In this article, we systematically evaluate how the relaxed clock model can benefit from i) adaptive operator weighting, ii) substitution rate parameterisation,  iii) Bactrian proposal kernels \cite{yang2013searching}, iv) tree operators which account for correlations between substitution rates and times, and v) adaptive multivariate operators \cite{baele2017adaptive}.
-The discussed methods are implemented in and compared using BEAST2 \cite{bouckaert2019beast}.
+The discussed methods are implemented in the ORC package and compared using BEAST 2 \cite{bouckaert2019beast}.
 
@@
 
-Let $\mathcal{T}$ be a binary rooted time tree with $N$ taxa. Let $L$ be the number of sites within the multiple sequence alignment $D$. 
+Let $\mathcal{T}$ be a binary rooted time tree with $N$ taxa, and %. Let $L$ be the number of sites within the multiple sequence alignment $D$. 
+$D$ data associated with the tips, like a multiple sequence alignment with $L$ sites, morphological data or geographic locations. 
 The posterior density of a phylogenetic model is described by
@@
 \label{eq:bayesian}
-p(\mathcal{T}, \vec{\mathcal{R}}^{\,}, \sigma, \mu_C, \theta|D) \propto  p(D|\mathcal{T}, r(\vec{\mathcal{R}}^{\,}), \mu_C) \; p(\mathcal{T}|\theta) \;  p(\vec{\mathcal{R}}^{\,} | \sigma) \; p(\sigma) \; p(\mu_C) \; p(\theta).
+p(\mathcal{T}, \vec{\mathcal{R}}^{\,}, \sigma, \mu_C, \theta|D) \propto  p(D|\mathcal{T}, r(\vec{\mathcal{R}}^{\,}), \mu_C, \theta) \; p(\mathcal{T}|\theta) \;  p(\vec{\mathcal{R}}^{\,} | \sigma) \; p(\sigma) \; p(\mu_C) \; p(\theta).
 \end{eqnarray}
 
-$\sigma$ represents clock model related parameters, and $p(\mathcal{T}|\theta)$ is the tree prior where $\theta$ describes further unspecified parameters. 
-The tree likelihood $p(D|\mathcal{T}, r(\vec{\mathcal{R}}^{\,}), \mu_C)$ is
-calculated by the tree-peeling algorithm \cite{felsenstein1981evolutionary}, where $\mu_C$ is the overall clock rate and
-$\vec{\mathcal{R}}^{\,}$ is an abstracted vector of branch molecular substitution rates which is transformed into real rates by function $r(\vec{\mathcal{R}}^{\,})$. 
+\noindent
+where $\sigma$ and $\mu_C$ represent clock model related parameters, and $p(\mathcal{T}|\theta)$ is the tree prior where $\theta$ describes further unspecified parameters. 
+The tree likelihood $p(D|\mathcal{T}, r(\vec{\mathcal{R}}^{\,}), \mu_C,\theta)$ %is calculated by the tree-pruning algorithm \cite{felsenstein1981evolutionary}, where
+has $\mu_C$ as the overall clock rate and
+$\vec{\mathcal{R}}^{\,}$ is an abstracted vector of branch rates which is transformed into real rates by function $r(\vec{\mathcal{R}}^{\,})$. 
 Branch rates have a mean of 1 under the prior to avoid non-identifiability with node heights and the clock rate $\mu_C$.
@@
 
-$q(a|b)$ is the transition kernel: the probability of proposing state $b$ from state $a$.
+\noindent
+where $q(a|b)$ is the transition kernel: the probability of proposing state $b$ from state $a$.
 The ratio between the two $\frac{q(x|x^\prime)}{q(x^\prime|x)}$ is known as the Hastings ratio \cite{hastings70}.
-The determinant of the Jacobian matrix $|J|$ solves the dimension-matching problem for proposals which operate on multiple terms across one or more spaces \cite{green1995reversible, geyer2003metropolis}.
-This term is known as the Green ratio.
+The determinant of the Jacobian matrix $|J|$, known as the Green ratio, solves the dimension-matching problem for proposals which operate on multiple terms across one or more spaces \cite{green1995reversible, geyer2003metropolis}.
+%This term is known as the Green ratio.
 
 \clearpage
-\subsection*{Substitution rate parameterisations}
+\subsection*{Branch rate parameterisations}
 \label{sect:rateparams}
@@
 The function for transforming $\mathcal{R}$ into branch rates $r(\mathcal{R})$ is depicted for \textit{real} (top right), \textit{cat} (bottom left), and \textit{quant} (bottom right).
-For visualisation purposes, there are only 10 bins/pieces displayed, however in practice there are $2N-2$ bins for \textit{cat} and 100 pieces for \textit{quant}.
+For visualisation purposes, there are only 10 bins/pieces displayed, however in practice we use $2N-2$ bins for \textit{cat} and 100 pieces for \textit{quant}.
 The first and final \textit{quant} pieces are equal to the underlying function however the pieces in between use linear approximations of this function. }
@@
 
-Under a Log-Normal clock prior $p(\vec{\mathcal{R}}^{\,} | \sigma)$, rates are distributed with a mean of 1:
+Under a log-normal clock prior $p(\vec{\mathcal{R}}^{\,} | \sigma)$, rates are distributed with a mean of 1:
 
@@
 
+\noindent
 where $\mu = -0.5\sigma^2$ is set such that the expected value is 1.
-In this article we only consider Log-Normal clock priors, however the methods discussed are general.
+In this article we only consider log-normal clock priors, however the methods discussed are general.
 
@@
 These integers correspond to $n$ rate categories (\textbf{Fig. \ref{fig:rateparams}}).
-Let $f(x|\sigma)$ be the probability density function (PDF) and let $F(x|\sigma) = \int\limits_{0}^{x} f(t|\sigma) \; dt$ be the cumulative distribution function (CDF) of the prior distribution used by the underlying \textit{real} clock model (a Log-Normal distribution for the purposes of this article).
+Let $f(x|\sigma)$ be the probability density function (PDF) and let $F(x|\sigma) = \int\limits_{0}^{x} f(t|\sigma) \; dt$ be the cumulative distribution function (CDF) of the prior distribution used by the underlying \textit{real} clock model (a log-normal distribution for the purposes of this article).
 In the \textit{cat} parameterisation, $f(x|\sigma)$ is discretised into $n$ bins and each element within $\vec{\mathcal{R}}^{\,}$ points to one such bin.
@@
 
+\noindent
 where $F^{-1}$ is the inverse cumulative distribution function (i-CDF).
@@
 
-This parameterisation has been widely used in BEAST and BEAST2 analyses \cite{drummond2006relaxed}. 
+This parameterisation has been widely used in BEAST and BEAST 2 analyses \cite{drummond2006relaxed}. 
 However, the recently developed constant distance operators  -- which are incompatible with the \textit{cat} parameterisation -- can yield an increase in mixing rate under \textit{real} by up to an order of magnitude over that of \textit{cat}, depending on the dataset \cite{zhang2020improving}.
@@
 Transforming these quantiles into rates invokes the i-CDF of the underlying \textit{real} clock model distribution.
-Evaluation of the Log-Normal i-CDF is has high computational costs and
+Evaluation of the log-normal i-CDF is has high computational costs and
 therefore an approximation is used instead.
@@
 
+\noindent
 where $\hat{F}^{-1}$ is a linear piecewise approximation with 100 pieces.
@@
 Weights are typically fixed throughout MCMC.
-In BEAST2, operators can have their own tunable parameter $s$ which determine the step size of the operator.
+In BEAST 2, operators can have their own tunable parameter $s$, which determines the step size of the operator.
 This term is learned over the course of the MCMC \cite{rosenthal2011optimal, bouckaert2019beast}. 
 We define clock model operators as those which generate proposals for either $\vec{\mathcal{R}}^{\,}$ or $\sigma$.
-Pre-existing BEAST2 clock model operators are summarised in \textbf{Table \ref{table:kernels}}, and further operators are introduced throughout this paper.
+Pre-existing BEAST 2 clock model operators are summarised in \textbf{Table \ref{table:kernels}}, and further operators are introduced throughout this paper.
 
@@
 \end{tabular}
-\caption{Summary of pre-existing BEAST2 operators, which apply to either branch rates $\vec{\mathcal{R}}^{\,}$ or the clock standard deviation $\sigma$, and the substitution rate parameterisation they apply to.
+\caption{Summary of pre-existing BEAST 2 operators, which apply to either branch rates $\vec{\mathcal{R}}^{\,}$ or the clock standard deviation $\sigma$, and the substitution rate parameterisation they apply to.
  \texttt{ConstantDistance} and \texttt{SimpleDistance} also adjust node heights in the tree $\mathcal{T}$. }
@@
 In contrast, a proposal made by \texttt{Scale} $\sigma \rightarrow \sigma^\prime$ under the \textit{quant} parameterisation implicitly alters all branch rates $r(\vec{\mathcal{R}}^{\,})$ while leaving the quantiles $\vec{\mathcal{R}}^{\,}$ themselves constant.
-But by applying \texttt{CisScale} under \textit{quant},
-all quantiles are recomputed $\vec{\mathcal{R}} \rightarrow \vec{\mathcal{R}}^\prime$  such that the respective branch rates are constant i.e.
+In contrast, by applying \texttt{CisScale} under \textit{quant}
+all quantiles are recomputed $\vec{\mathcal{R}} \rightarrow \vec{\mathcal{R}}^\prime$  such that the respective branch rates are constant, i.e.
 $r(\vec{\mathcal{R}}^{\,}) = r(\vec{\mathcal{R}}^{\,\prime})$.
@@
 
-where $\Omega = 0.01$ allows any sub-operator to be sampled regardless of its performance.
+\noindent
+where  $\mathbb{T}(\omega)$ the cumulative computational time spent on each operator, $\mathbb{D}(.)$ a distance function and we use $\Omega = 0.01$ to allow any sub-operator to be sampled regardless of its performance.
 The parameters of interest (POI) may be either a set of numerical parameters (such as branch rates or node heights), or it may be the tree itself, but it cannot be both in its current form.
@@
 
+\noindent
 where \texttt{RF} is the Robinson-Foulds tree distance \cite{robinson1981comparison}, and $|p|$ is the number of dimensions of numerical parameter $p$ (1 for $\sigma$, $2N-2$ for $\vec{\mathcal{R}}^{\,}$, and $2N-1$ for node heights $t$).
@@
 
+%RRB: should the root operator include a tree root scaler?
+
 %\texttt{AdaptiveOperatorSampler($\sigma$)} samples the clock standard deviation, 
@@
 The standard uniform distribution kernel has recently been challenged by the Bactrian kernels \cite{yang2013searching, thawornwattana2018designing}.
-The (Gaussian) $\text{Bactrian}(m)$ distribution is defined as the sum of two Normal distributions:
+The (Gaussian) $\text{Bactrian}(m)$ distribution is defined as the sum of two normal distributions:
 
@@
 
+\noindent
 where $0 \leq m < 1$ describes the modality of the Bactrian distribution. When $m=0$, the Bactrian distribution is equivalent to a $\text{Normal}(0, 1)$ distribution. 
@@
 Yang et al.
-2013 \cite{yang2013searching} suggest that $\text{Bactrian}(m=0.95)$ yields a proposal kernel which traverses the posterior distribution more efficiently that the standard uniform kernel, by placing minimal probability on steps which are too small or too large.
+2013 \cite{yang2013searching} demonstrate that $\text{Bactrian}(m=0.95)$ yields a proposal kernel which traverses the posterior distribution more efficiently that the standard uniform kernel, by placing minimal probability on steps which are too small or too large.
 In this case, a target acceptance probability of around 0.3 is optimal.
@@
 \caption{Proposal kernels $q(x^\prime|x)$ of clock model operators.
- In each operator, $\Sigma$ is drawn from either a $\text{Bactrian}(m)$ or $\text{Uniform}$ distribution. 
+ In each operator, $\Sigma$ is drawn from either a $\text{Bactrian}(m)$ or $\text{Uniform}$ distribution.  %RB: Uniform on which interval? (-1,1)?
  The scale size $s$ is tunable.
@@
 
+% RB: Perhaps add Hastings ratios to the table?
+
 % Give the equation of the Uniform + Bactrian kernels
@@
 
-The \texttt{NarrowExchange} operator \cite{drummond2002estimating}, used widely in BEAST \cite{drummond2012bayesian,suchard2018bayesian} and BEAST2 \cite{bouckaert2019beast}, is similar to nearest-neighbour-interchange \cite{semple2003phylogenetics}, and works as follows (\textbf{Fig \ref{fig:narrowexchange}}):
+The \texttt{NarrowExchange} operator \cite{drummond2002estimating}, used widely in BEAST \cite{drummond2012bayesian,suchard2018bayesian} and BEAST 2 \cite{bouckaert2019beast}, is similar to nearest-neighbour-interchange \cite{semple2003phylogenetics}, and works as follows (\textbf{Fig \ref{fig:narrowexchange}}):
 
@@
 \textul{\textit{Step 2}}. Identify the child of $E$ with the greater height. Denote this child as $D$ and its sibling as $C$ (i.e. $t_D > t_C$).
+ %RB: C must not be internal, right? If C is leaf, abort?
 
@@
 In the bottom figure, branch rates $r$ are indicated by line width and therefore genetic distances are equal to the width of each branch multiplied by its length.
-In this example, the $\mathcal{D}_{AE}$ and $\mathcal{D}_{CE}$ constraints are satisfied.}
+In this example, the $\mathcal{D}_{AE}$ and $\mathcal{D}_{CE}$ constraints are satisfied.
+%RB: at this stage, D_AE and D_CE constraints have not been defined yet. Remove or reformulate or move to after definition?
+}
 \label{fig:narrowexchange}
@@
 
+\noindent
 for random walk step size $s\Sigma$ where $s$ is tunable and $\Sigma$ is drawn from a Uniform or Bactrian distribution.
@@
 The total space of NER operators is comprised of all possible subsets of distance constraints (i.e.
-$\{\},\{\mathcal{D}_{AB}\}, \{\mathcal{D}_{AC}\}, \dotso , \{\mathcal{D}_{AB}, \mathcal{D}_{AC}, \mathcal{D}_{AE}, \mathcal{D}_{BC}, \mathcal{D}_{BE}, \mathcal{D}_{CE} \}$) which are solvable.
-The simplest NER -- the null operator denoted by NER$\{\}$ -- does not satisfy any distance constraints. 
-This is equivalent to \texttt{NarrowExchange}. 
+$\{\},\{\mathcal{D}_{AB}\}, \{\mathcal{D}_{AC}\}, \dotso , \{\mathcal{D}_{AB}, \mathcal{D}_{AC}, \mathcal{D}_{AE}, \mathcal{D}_{BC}, \mathcal{D}_{BE}, \mathcal{D}_{CE} \}$) that are solvable.
+The simplest NER kernel -- the null operator denoted by NER$\{\}$ -- does not satisfy any distance constraints and is equivalent to \texttt{NarrowExchange}. 
 To determine which NER variants have the best performance, we developed an automated pipeline for generating and testing these operators.
@@
 
-\paragraph{3. Automated generation of BEAST2 operators.} Java class files were generated using string processing. 
+\paragraph{3. Automated generation of BEAST 2 operators.} Java class files were generated using string processing. 
 Each class corresponded to a single operator, extended the class of a meta-NER-operator, and consisted of the solutions found in \textbf{1} and the Jacobian determinant found in \textbf{2}. 
@@
 Two such operators are expressed in \textbf{Algorithms \ref{alg:NER1} and \ref{alg:NER2}}.
+%RB: what is the purpose of having 2 algorithms -- one (the second one, since that is the one performing well) is enough, no?
 
@@
 \includegraphics[width=\textwidth]{Figures/acceptanceRates.pdf}
-\caption{\textbf{Screening of NER and NERw variants by acceptance rate.} Top left: comparison of NER variants with the null operator $\text{NER}\{\}$ / \texttt{NarrowExchange}. 
+\caption{\textbf{Screening of NER and NERw variants by acceptance rate.} Top left: comparison of NER variants with the null operator $\text{NER}\{\}$ = \texttt{NarrowExchange}. 
 Each operator is represented by a single point, uniquely encoded by the point stylings. 
@@
 On the other hand, the null operator $\text{NER}\{\}$ performed better on shorter sequences ($L < 1$kb) with weaker signal.  
-Overall, $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ outperformed the standard \texttt{NarrowExchange} operator when the data was not clock-like and contained enough signal.
+Overall, $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ outperformed the standard \texttt{NarrowExchange} operator when the data was not clock-like and contained sufficient signal.
 
@@
 
-The AVMVN kernel assumes its parameters live in $x \in \mathbb{R}^N$ for taxon count $N$ and that these parameters follow a Multivariate Normal distribution with covariance matrix $\Sigma_N$.
+The AVMVN kernel assumes its parameters live in $x \in \mathbb{R}^N$ for taxon count $N$ and that these parameters follow a multivariate normal distribution with covariance matrix $\Sigma_N$.
 Hence, the kernel operates on the logarithmic or logistic transformation of the $N$ leaf branch rates, depending on the rate parameterisation:
@@
 
+\noindent
 where $r_i$ is a real rate and $q_i$ is a rate quantile. The AVMVN probability density is defined by
@@
 
-where $\mathcal{MVN}$ is the Multivariate Normal probability density.
+\noindent
+where $\mathcal{MVN}$ is the multivariate normal probability density.
 $\beta  = 0.05$ is a constant which determines the fraction of the proposal determined by the identity matrix $\mathbb{I}_N$, as opposed to the covariance matrix $\Sigma_D$ which is trained during MCMC.
-Our BEAST2 implementation of the AVMVN kernel is adapted from that of BEAST \cite{suchard2018bayesian}.
+Our BEAST 2 implementation of the AVMVN kernel is adapted from that of BEAST \cite{suchard2018bayesian}.
 
@@
 In all phylogenetic analyses presented here, we use a Yule \cite{yule1925ii} tree prior $p(\mathcal{T}|\lambda)$ with birth rate $\lambda \sim \text{Log-Normal}(1,1.25)$.
+%RB: mean in real space?
+This is not the traditional parameterisation in the literature, and it was also mentioned earlier that the mean parameter is set such that the mean=1
 The clock standard deviation has a $\sigma \sim \text{Gamma}(0.5396,0.3819)$ prior.
@@
 The transition-transversion ratio $\kappa \sim \text{Log-Normal}(1, 1.25)$, the four nucleotide frequencies $(f_A, f_C, f_G, f_T) \sim \text{Dirichlet}(10,10,10,10)$, and the relative clock rate $\mu_C \sim \text{Log-Normal}(-0.18, 0.6)$ are estimated independently for each partition.
+%RB: again mean in real space for Log-Normal?
 The operator scheme ensures that the clock rates $\mu_C$ have a mean of 1 across all partitions. 
@@
 
-\textbf{1. Validation}. This is assessed by measuring the coverage of all estimated parameters in well-calibrated simulation studies. These are presented in \textbf{\nameref{sect:WCSS_appendix}}. \\
+\textbf{1.
+Validation}.
+This is assessed by measuring the coverage of all estimated parameters in well-calibrated simulation studies.
+These are presented in \textbf{\nameref{sect:WCSS_appendix}} and give confidence operators are implemented correctly.
+\\
 
@@
 %All 25 datasets presented in \textbf{Table \ref{table:datasets}} are benchmarked together $1 \times$ each at the end of the protocol.
-Datasets and BEAST2 .xml templates are provided in the GitHub repository accompanying this article.
+Datasets and BEAST 2 .xml templates are provided in the GitHub repository accompanying this article.
 
@@
 We compared the nocons, cons, and adapt operator configurations (\textbf{Table \ref{table:operatorSchemes}}).
-nocons contained all of the standard BEAST2 operator configurations and weightings for \textit{real}, \textit{cat}, and \textit{quant}.
+nocons contained all of the standard BEAST 2 operator configurations and weightings for \textit{real}, \textit{cat}, and \textit{quant}.
 cons additionally contained (cons)tant distance operators and employed the same operator weighting scheme used previously \cite{zhang2020improving} (\textit{real} and \textit{quant} only). 
@@
 The computational time required for a setting to sample a single state is divided by that of the nocons (\textit{cat}) configuration.
-The geometric mean under each congifuration, averaged across all 9 datasets, is displayed as a horizontal bar.}
+The geometric mean under each configuration, averaged across all 9 datasets, is displayed as a horizontal bar.}
 \label{fig:round2Resultsb}
@@
 
-Overall, this operator configuration is the final winner in the tournament.
+Overall, this operator configuration is the final winner in the tournament. %RB: which configuration are you referring to?
 
 \subsection*{Tournament conclusion}
- In conjunction with all settings which came before it, the tournament winner  outperformed both the historical \textit{cat} configuration \cite{drummond2006relaxed} as well as the recently developed cons (\textit{real}) scheme \cite{zhang2020improving} .
+ In conjunction with all settings which came before it, the tournament winner  outperformed both the historical \textit{cat} configuration \cite{drummond2006relaxed} as well as the recently developed cons (\textit{real}) scheme \cite{zhang2020improving}.
 Averaged across all datasets, this configuration yielded a relaxed clock  mixing rate between 1.2 and 13 times as fast as \textit{cat} and between 1.8 and 7.8 times as fast as cons (\textit{real}), depending on the parameter.
@@
 These methodologies were compared by constructing phylogenetic models from several empirical datasets and comparing their abilities to converge in a tournament-like protocol (\textbf{Fig \ref{fig:tournament}}).
-The methods introduced are adaptive and treat each dataset differently.
+The methods introduced are adaptive and treat each dataset differently, and perform never worse than without adaptation. %RB: is the part after the comma true?
 This work has produced an operator configuration which is highly effective  on large alignments and can explore relaxed clock model space up to two orders of magnitude more efficiently than previous setups.
@@
 
-The work presented in this article was implemented as a BEAST2 package.
-Instructions for using and installing this package can be found at \href{https://github.com/jordandouglas/ADFP}{https://github.com/jordandouglas/ADFP}.
+The work presented in this article was implemented as a user friendly open source BEAST 2 package with GUI support via BEAUti making it easy to set up an analysis.
+Instructions for using and installing this package can be found at \href{https://github.com/jordandouglas/ORC}{https://github.com/jordandouglas/ORC}.
 

### 2020-09-03 clockSD.R
Paper fixes

@@ -51,11 +51,11 @@ s_q0 = plnorm(s_r0, mu, sigma)
 s_q1 = plnorm(s_r0, mu2, sigma2)
 lines(c(s_r0, s_r0), c(0, max(s_q0, s_q1)), lwd = 2, col = "#696969", lty = "1515")
 
-lines(c(0, s_r0), c(s_q0, s_q0), lty = "1515", col = Scols[1], lwd = 2)
-lines(c(0, s_r0), c(s_q1, s_q1), lty = "1515", col = Scols[2], lwd = 2)
+lines(c(0, s_r0), c(s_q0, s_q0), lty = "1515", col = "#696969", lwd = 2)
+lines(c(0, s_r0), c(s_q1, s_q1), lty = "1515", col = "#696969", lwd = 2)
 points(c(s_r0, s_r0), c(s_q0, s_q1), pch = 16, col = Scols)
 
-text(s_r0/2, max(s_q0, s_q1) + 0.01, "New quantiles", adj = c(0.5, 0))
+text(s_r0/2, max(s_q0, s_q1) + 0.02, "New quantiles", adj = c(0.5, 0))
 
 
 
@@ -65,11 +65,11 @@ c_q0 = plnorm(c_r0, mu, sigma)
 c_r1 = qlnorm(c_q0, mu2, sigma2)
 lines(c(0, max(c_r0, c_r1)), c(c_q0, c_q0), lwd = 2, col = "#696969", lty = "1515")
 
-lines(c(c_r0, c_r0), c(0, c_q0), lty = "1515", col = "black", lwd = 2)
-lines(c(c_r1, c_r1), c(0, c_q0), lty = "1515", col = "red", lwd = 2)
-points(c(c_r0, c_r1), c(c_q0, c_q0), pch = 16, col = c("black", "red"))
+lines(c(c_r0, c_r0), c(0, c_q0), lty = "1515", col = "#696969", lwd = 2)
+lines(c(c_r1, c_r1), c(0, c_q0), lty = "1515", col = "#696969", lwd = 2)
+points(c(c_r0, c_r1), c(c_q0, c_q0), pch = 16, col = Scols)
 
-text(max(c_r0, c_r1)/2, c_q0 + 0.01, "New rates", adj = c(0.5, 0))
+text(max(c_r0, c_r1)/2, c_q0 + 0.02, "New rates", adj = c(0.5, 0))
 
 
 

### 2020-09-04 S1_appendix.tex
polishing
Final touches

@@
 The approximation consists of $n$ pieces (where $n=100$ is fixed).
-Due to the nonlinear nature of small and large quantiles in a Log-normal distribution, the first and last pieces are not linear approximations but rather equal to the underlying distribution itself.
+Due to the nonlinear nature of small and large quantiles in a log-normal distribution, the first and last pieces are not linear approximations but rather equal to the underlying distribution itself.
 

### 2020-09-04 submission.tex
Final touches

--- 2020-09-03 manuscript.tex
@@
 % to minimize problems and delays during our production
-% process. Please follow the template instructionssum 
+% process. Please follow the template instructions 
 % whenever possible.
@@
 In this article we delved into the internal complexities of the relaxed clock model in order to develop efficient MCMC operators for Bayesian phylogenetic inference.
-We compared three substitution rate parameterisations,  introduced an adaptive operator which learns the weights of other operators during MCMC and, we explored how relaxed clock model estimation can benefit from two cutting-edge proposal kernels: the AVMVN and Bactrian kernels.
+We compared three substitution rate parameterisations, introduced an adaptive operator which learns the weights of other operators during MCMC, and we explored how relaxed clock model estimation can benefit from two cutting-edge proposal kernels: the AVMVN and Bactrian kernels.
 This work has produced an operator scheme that is up to 65 times more efficient at exploring continuous relaxed clock parameters compared with previous setups, depending on the dataset. 
-%RB: 65 or 66 mentioned later?
 Finally, we explored variants of the standard narrow exchange operator which are specifically designed for the relaxed clock model.
@@
 The methodologies introduced are adaptive and highly effective on short as well as long alignments.
-The results are available via the open source optimised relaxed clock (ORC) package for BEAST 2 under the LGPL 2(?) licence (\url{https://github.com/jordandouglas/ORC}).
+The results are available via the open source optimised relaxed clock (ORC) package for BEAST 2 under a GNU licence (\url{https://github.com/jordandouglas/ORC}).
 
@@
 We explored how a range of optimisations can improve the statistical inference of the relaxed clock.
-This work has produced a phylogenetic setup which can infer parameters related to the relaxed clock up to 65 times faster than previous setups, depending on the dataset. %RB: 65 or 66 mentioned later?
+This work has produced a phylogenetic setup which can infer parameters related to the relaxed clock up to 65 times faster than previous setups, depending on the dataset. 
 The methods introduced adapt to the dataset during computation and are highly efficient when processing long biological sequences.
@@
 In the latter case, a strict clock is probably not suitable.
-In the remainder of this paper %RB: "article" and "paper" are used a few times -- should we keep things consistent to either "paper" or "article"?
-we will only consider uncorrelated relaxed clock models.
 
@@
 This class of models is widely used, and has aided insight into many recent biological problems, including the 2016 Zika virus outbreak \cite{faria2017establishment} and the COVID-19 pandemic \cite{giovanetti2020first}.
+In the remainder of this paper we will only consider uncorrelated relaxed clock models.
 % is compatible with increasingly prominent multispecies coalescent models \cite{ogilvie2017starBEAST 2},
@@
 Let $\mathcal{T}$ be a binary rooted time tree with $N$ taxa, and %. Let $L$ be the number of sites within the multiple sequence alignment $D$. 
-$D$ data associated with the tips, like a multiple sequence alignment with $L$ sites, morphological data or geographic locations. 
+data $D$ associated with the tips, such as a multiple sequence alignment with $L$ sites, morphological data or geographic locations. 
 The posterior density of a phylogenetic model is described by
@@
 \label{eq:bayesian}
-p(\mathcal{T}, \vec{\mathcal{R}}^{\,}, \sigma, \mu_C, \theta|D) \propto  p(D|\mathcal{T}, r(\vec{\mathcal{R}}^{\,}), \mu_C, \theta) \; p(\mathcal{T}|\theta) \;  p(\vec{\mathcal{R}}^{\,} | \sigma) \; p(\sigma) \; p(\mu_C) \; p(\theta).
+p(\mathcal{T}, \vec{\mathcal{R}}^{\,}, \sigma, \mu_C, \theta|D) \propto  p(D|\mathcal{T}, r(\vec{\mathcal{R}}^{\,}), \mu_C, \theta) \; p(\mathcal{T}|\theta) \;  p(\vec{\mathcal{R}}^{\,} | \sigma) \; p(\sigma) \; p(\mu_C) \; p(\theta)
 \end{eqnarray}
@@
 \label{eq:MCMC}
-\alpha(x^\prime|x) =  \min\left( 1, \frac{p(x^\prime|D)}{p(x|D)} \; \frac{q(x|x^\prime)}{q(x^\prime|x)} \; |J| \right).
+\alpha(x^\prime|x) =  \min\left( 1, \frac{p(x^\prime|D)}{p(x|D)} \; \frac{q(x|x^\prime)}{q(x^\prime|x)} \; |J| \right)
 \end{eqnarray}
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{Figures/rateparameterisation.pdf}
+%%%%% \includegraphics[width=\textwidth]{Figures/rateparameterisation.pdf}
 \caption{\textbf{Branch rate parameterisations.} Top left: the prior density of a branch rate $r$ under a Log-Normal($-0.5\sigma^2, \sigma$) distribution (with its mean fixed at 1). 
@@
 
-The key advantage of the \textit{cat} parameterisation is the removal of a term from the posterior density (\textbf{Equation \ref{eq:bayesian}}), or more accurately the replacement of a non-trivial $p(\vec{\mathcal{R}}^{\,} | \sigma)$ term with that of a uniform prior.
+The key advantage of the \textit{cat} parameterisation is the removal of a term from the posterior density (\textbf{Eq \ref{eq:bayesian}}), or more accurately the replacement of a non-trivial $p(\vec{\mathcal{R}}^{\,} | \sigma)$ term with that of a uniform prior.
 This may facilitate efficient exploration of the posterior distribution by MCMC.
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{Figures/correlations.pdf}
+%%%%% \includegraphics[width=\textwidth]{Figures/correlations.pdf}
 \caption{\textbf{Traversing likelihood space.}
@@
 \centering
-\includegraphics[width=\textwidth]{Figures/clockSD.pdf}
+%%%%% \includegraphics[width=\textwidth]{Figures/clockSD.pdf}
 \caption{\textbf{Clock standard deviation scale operators.}
@@
 
-It is not always clear which operators weighting scheme is best for a given dataset.
+It is not always clear which operator weighting scheme is best for a given dataset.
 In this article we introduce \texttt{AdaptiveOperatorSampler} -- a meta-operator which learns the weights of other operators during MCMC and then samples these operators according to their learned weights.
@@
 In the first phase (burn-in), \texttt{AdaptiveOperatorSampler} samples from its set of sub-operators uniformly at random.
-In the second phase (learn-in), the meta-operator continues to sample operators uniformly at random however it begins learning several terms detailed below.
+In the second phase (learn-in), the meta-operator starts learning several terms detailed below whilst continuing to sample operators uniformly at random.
 In its final phase, \texttt{AdaptiveOperatorSampler} samples operators (denoted by $\omega$) using the following distribution:
@@
 \noindent
-where  $\mathbb{T}(\omega)$ the cumulative computational time spent on each operator, $\mathbb{D}(.)$ a distance function and we use $\Omega = 0.01$ to allow any sub-operator to be sampled regardless of its performance.
+where $\mathbb{T}(\omega)$ is the cumulative computational time spent on each operator, $\mathbb{D}$ is a distance function, and we use $\Omega = 0.01$ to allow any sub-operator to be sampled regardless of its performance.
 The parameters of interest (POI) may be either a set of numerical parameters (such as branch rates or node heights), or it may be the tree itself, but it cannot be both in its current form.
@@
 Under \textbf{Equations \ref{eqn:adaptiveSampler} and \ref{eqn:distanceFunctions}}, operators which effect larger changes on the parameters of interest, in shorter runtime, are sampled with greater probabilities.
-Division of the squared distance by a parameters variance $\sigma^2_p$ enables comparison between different numerical parameters.
+Division of the squared distance by a parameter's sample variance $\sigma^2_p$ enables comparison between different numerical parameters.
 
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{Figures/bactrian.pdf}
+%%%%% \includegraphics[width=\textwidth]{Figures/bactrian.pdf}
 \caption{\textbf{The Bactrian proposal kernel.} The step size made under a Bactrian proposal kernel is equal to $s \Sigma$ where $\Sigma$ is drawn from the above distribution and $s$ is tunable.   }
@@
 \caption{Proposal kernels $q(x^\prime|x)$ of clock model operators.
- In each operator, $\Sigma$ is drawn from either a $\text{Bactrian}(m)$ or $\text{Uniform}$ distribution.  %RB: Uniform on which interval? (-1,1)?
+ In each operator, $\Sigma$ is drawn from either a $\text{Bactrian}(m)$ or $\text{uniform}$ distribution.  %RB: Uniform on which interval? (-1,1)?
  The scale size $s$ is tunable.
@@
 
-% BRIEFLY describe three operators: random walk, scale, uniform + where the proposal kernal comes in + which parameters in the clock model it applies to
+% BRIEFLY describe three operators: random walk, scale, uniform + where the proposal kernel comes in + which parameters in the clock model it applies to
 
@@
 
-The \texttt{NarrowExchange} operator \cite{drummond2002estimating}, used widely in BEAST \cite{drummond2012bayesian,suchard2018bayesian} and BEAST 2 \cite{bouckaert2019beast}, is similar to nearest-neighbour-interchange \cite{semple2003phylogenetics}, and works as follows (\textbf{Fig \ref{fig:narrowexchange}}):
+The \texttt{NarrowExchange} operator \cite{drummond2002estimating}, used widely in BEAST \cite{drummond2012bayesian,suchard2018bayesian} and BEAST 2 \cite{bouckaert2019beast}, is similar to nearest neighbour interchange \cite{semple2003phylogenetics}, and works as follows (\textbf{Fig \ref{fig:narrowexchange}}):
 
@@
 
-\textul{\textit{Step 2}}. Identify the child of $E$ with the greater height. Denote this child as $D$ and its sibling as $C$ (i.e. $t_D > t_C$).
- %RB: C must not be internal, right? If C is leaf, abort?
+\textul{\textit{Step 2}}. Identify the child of $E$ with the greater height. Denote this child as $D$ and its sibling as $C$ (i.e. $t_D > t_C$). If $D$ is a leaf node, then reject the proposal.
 
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{Figures/NarrowExchange.pdf}
+%%%%% \includegraphics[width=\textwidth]{Figures/NarrowExchange.pdf}
 \caption{\textbf{Depiction of \texttt{NarrowExchange} and \texttt{NarrowExchangeRate} operators.} Proposals are denoted by $\mathcal{T} \rightarrow \mathcal{T}^\prime$.
-The vertical axis corresponds to node height $t$.
+The vertical axes correspond to node heights $t$.
 In the bottom figure, branch rates $r$ are indicated by line width and therefore genetic distances are equal to the width of each branch multiplied by its length.
@@
 While NER does not alter $t_D$ (i.e.
-${t_D}^\prime \leftarrow t_D$), we also consider NERw - a special case of the NER operator which embarks $t_D$ on a random walk:
+${t_D}^\prime \leftarrow t_D$), we also consider NERw -- a special case of the NER operator which embarks $t_D$ on a random walk:
 
@@
 \noindent
-for random walk step size $s\Sigma$ where $s$ is tunable and $\Sigma$ is drawn from a Uniform or Bactrian distribution.
+for random walk step size $s\Sigma$ where $s$ is tunable and $\Sigma$ is drawn from a uniform or Bactrian distribution.
 NER (and NERw) are compatible with both the \textit{real} and \textit{quant} parameterisations.
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{Figures/acceptanceRates.pdf}
+%%%%% \includegraphics[width=\textwidth]{Figures/acceptanceRates.pdf}
 \caption{\textbf{Screening of NER and NERw variants by acceptance rate.} Top left: comparison of NER variants with the null operator $\text{NER}\{\}$ = \texttt{NarrowExchange}. 
@@
 This variant conserves the genetic distance between nodes $A$, $B$, $C$ and their grandparent $E$. 
-Moreover, this operator performed well when branch rates have a large variance ($\sigma > 0.5$), corresponding to non clock-like data. 
+Moreover, this operator performed well when branch rates had a large variance ($\sigma > 0.5$), corresponding to non clock-like data. 
 On the other hand, the null operator $\text{NER}\{\}$ performed better on shorter sequences ($L < 1$kb) with weaker signal.  
@@
 
-In all phylogenetic analyses presented here, we use a Yule \cite{yule1925ii} tree prior $p(\mathcal{T}|\lambda)$ with birth rate $\lambda \sim \text{Log-Normal}(1,1.25)$.
-%RB: mean in real space?
-This is not the traditional parameterisation in the literature, and it was also mentioned earlier that the mean parameter is set such that the mean=1
+In all phylogenetic analyses presented here, we use a Yule \cite{yule1925ii} tree prior $p(\mathcal{T}|\lambda)$ with birth rate $\lambda \sim \text{Log-normal}(1,1.25)$.
+Here and throughout the article, a $\text{Log-normal}(a,b)$ distribution is parameterised such that $a$ and $b$ are the mean and standard deviation in log-space.
 The clock standard deviation has a $\sigma \sim \text{Gamma}(0.5396,0.3819)$ prior.
 Datasets are partitioned into subsequences, where each partition is associated with a distinct HKY substitution model \cite{hasegawa1985dating}.
-The transition-transversion ratio $\kappa \sim \text{Log-Normal}(1, 1.25)$, the four nucleotide frequencies $(f_A, f_C, f_G, f_T) \sim \text{Dirichlet}(10,10,10,10)$, and the relative clock rate $\mu_C \sim \text{Log-Normal}(-0.18, 0.6)$ are estimated independently for each partition.
+The transition-transversion ratio $\kappa \sim \text{Log-normal}(1, 1.25)$, the four nucleotide frequencies $(f_A, f_C, f_G, f_T) \sim \text{Dirichlet}(10,10,10,10)$, and the relative clock rate $\mu_C \sim \text{Log-normal}(-0.18, 0.6)$ are estimated independently for each partition.
 %RB: again mean in real space for Log-Normal?
@@
 The neighbour joining tree \cite{saitou1987neighbor} is used as the initial state in each MCMC chain.
-
-\subsection*{Operator configurations} \label{sect:operatorSchemes}
 
@@
 
-\subsection*{Assessment criteria and datasets}
-
-% Cite HKY somewhere hasegawa1985dating
-
-To avoid a cross-product explosion, the five targets for clock model improvement are evaluated sequentially in the following order: \textbf{\nameref{sect:adaptiveSampling}}, \textbf{\nameref{sect:rateparams}}, \textbf{\nameref{sect:randomwalks}}, \textbf{\nameref{sect:NER}}, and \textbf{\nameref{AVMVN_sect}}.
+To avoid a cross-product explosion, the five targets for clock model improvement were evaluated sequentially in the following order: \textbf{\nameref{sect:adaptiveSampling}}, \textbf{\nameref{sect:rateparams}}, \textbf{\nameref{sect:randomwalks}}, \textbf{\nameref{sect:NER}}, and \textbf{\nameref{AVMVN_sect}}.
 The four operators introduced in these sections are summarised in \textbf{Table \ref{table:newOperators}}.
-The setting which is considered to be the best in each step is then incorporated into the following step. This protocol and its outcomes are summarised in \textbf{Fig \ref{fig:tournament}}.
+The setting which was considered to be the best in each step was then incorporated into the following step. 
+This protocol and its outcomes are summarised in \textbf{Fig \ref{fig:tournament}}.
 
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{Figures/tournament.pdf}
+%%%%% \includegraphics[width=\textwidth]{Figures/tournament.pdf}
 \caption{\textbf{Protocol for optimising clock model methodologies.} Each area (detailed in \textbf{\nameref{sect:models}}) is optimised sequentially, and the best setting from each step is used when optimising the following step.}
@@
 
-Methodologies are assessed according to the following criteria.
-
-\textbf{1.
-Validation}.
-This is assessed by measuring the coverage of all estimated parameters in well-calibrated simulation studies.
-These are presented in \textbf{\nameref{sect:WCSS_appendix}} and give confidence operators are implemented correctly.
-\\
-
-\textbf{2. Mixing of parameters}. Key parameters are evaluated for the number of effective samples generated per hour (ESS/hr).
-These key parameters are the likelihood $\mathcal{L}$ and prior $p$ densities,  tree length $l$ (i.e.
+Methodologies were assessed according to the following criteria.
+
+\textbf{1. Validation}. This was assessed by measuring the coverage of all estimated parameters in well-calibrated simulation studies. 
+These are presented in \textbf{\nameref{sect:WCSS_appendix}} and give confidence operators are implemented correctly. \\
+
+\textbf{2. Mixing of parameters}. Key parameters were evaluated for the number of effective samples generated per hour (ESS/hr).
+These key parameters were the likelihood $\mathcal{L}$ and prior $p$ densities,  tree length $l$ (i.e.
 the sum of all branch lengths), mean branch rate $\bar{r}$, branch rate of all leaf nodes $r$, and relaxed clock standard deviation $\sigma$.
-We also include the HKY substitution model term $\kappa$. 
-The mixing of $\kappa$ should not be strongly affected by any of the clock model operators, and thus it serves as a positive control in each experiment. \\
-
-Methodologies are benchmarked using one simulated and eight empirical datasets.
+We also included the HKY substitution model term $\kappa$. 
+The mixing of $\kappa$ should not be strongly affected by any of the clock model operators, and thus it served as a positive control in each experiment. \\
+
+Methodologies were benchmarked using one simulated and eight empirical datasets.
 The latter were compiled \cite{lanfear2019Github} and partitioned \cite{lanfear2016partitionfinder} by Lanfear as ``benchmark alignments'' (\textbf{Table \ref{table:datasets}}).
-Each methodology is benchmarked for million-states-per-hour using the Intel Xeon Gold 6138 CPU (2.00 GHz).
-These terms are multiplied by the ESS-per-state across 20 replicates on the New Zealand eScience Infrastructure (NeSI) cluster to compute the total ESS/hr of each dataset under each setting.
-All methodologies use identical models and operator configurations, except where a difference is specified.
+Each methodology was benchmarked for million-states-per-hour using the Intel Xeon Gold 6138 CPU (2.00 GHz).
+These terms were multiplied by the ESS-per-state across 20 replicates on the New Zealand eScience Infrastructure (NeSI) cluster to compute the total ESS/hr of each dataset under each setting.
+All methodologies used identical models and operator configurations, except where a difference is specified.
 
@@
 \end{tabular}
-\caption{Benchmark datasets, sorted in increasing order of taxa count $N$.
+\caption{Benchmark datasets, sorted in increasing order of taxon count $N$.
 Number of partitions $P$, total alignment length $L$, and number of unique site patterns $L_\text{unq}$ in the alignment are also specified.
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{benchmarking/benchmarkingVM/ESS_round1_real.pdf}
+%%%%% \includegraphics[width=\textwidth]{benchmarking/benchmarkingVM/ESS_round1_real.pdf}
 \caption{\textbf{Round 1: benchmarking the \texttt{AdaptiveOperatorSampler} operator.} Top left, top right, bottom left: each plot compares the ESS/hr ($\pm 1$ standard error) across two operator configurations.
@@
 Furthermore, \textit{real} outperformed \textit{quant} on most datasets, but this was mostly due to the slow computational performance of \textit{quant} compared with real, as opposed to differences in mixing prowess (\textbf{Fig \ref{fig:round2Resultsb}}).
-Irrespective of mixing ability, the adapt (\textit{real}) configuration had the best computation performance and generated samples 40\% faster than adapt (\textit{cat}) and 60\% faster than adapt (\textit{quant}).
+Irrespective of mixing ability, the adapt (\textit{real}) configuration had the best computational performance and generated samples 40\% faster than adapt (\textit{cat}) and 60\% faster than adapt (\textit{quant}).
 
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{benchmarking/benchmarkingVM/ESS_round2.pdf}
+%%%%% \includegraphics[width=\textwidth]{benchmarking/benchmarkingVM/ESS_round2.pdf}
 \caption{\textbf{Round 2: benchmarking substitution rate parameterisations.} Top left, top right, bottom left: the adapt (\textit{real}), adapt (\textit{cat}), and adapt (\textit{quant}) configurations were compared.
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{benchmarking/benchmarkingVM/ESS_timesettings.pdf}
+%%%%% \includegraphics[width=\textwidth]{benchmarking/benchmarkingVM/ESS_timesettings.pdf}
 \caption{\textbf{Comparison of runtimes across methodologies.} 
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{benchmarking/benchmarkingVM/ESS_round3.pdf}
+%%%%% \includegraphics[width=\textwidth]{benchmarking/benchmarkingVM/ESS_round3.pdf}
 \caption{\textbf{Round 3: benchmarking the Bactrian kernel.}
@@
 
-Our experiments confirmed that $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ was indeed superior on larger datasets (where $L > 2$kb; \textbf{Fig \ref{fig:round4Results}}).
+Our experiments confirmed that $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ was indeed superior on larger datasets (where $L > 5$kb; \textbf{Fig \ref{fig:round4Results}}).
 While there was no significant difference in the ESS/hr of continuous parameters, $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ did have an acceptance rate 41\% higher than that of the standard \texttt{NarrowExchange} operator in the most extreme case (the bony fish alignment by Broughton et al.\cite{Broughton_2013}).
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{benchmarking/benchmarkingVM/ESS_round4.pdf}
+%%%%% \includegraphics[width=\textwidth]{benchmarking/benchmarkingVM/ESS_round4.pdf}
 \caption{\textbf{Round 4: benchmarking the NER operators.} 
@@
 \begin{figure}[!h]
-%\includegraphics[width=\textwidth]{Figures/cognato.pdf}
-\includegraphics[width=\textwidth]{Figures/broughton.pdf}
+%%%%% %\includegraphics[width=\textwidth]{Figures/cognato.pdf}
+%%%%% \includegraphics[width=\textwidth]{Figures/broughton.pdf}
 \caption{\textbf{Maximum clade credibility tree of bony fishes.} 
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{benchmarking/benchmarkingVM/ESS_round5.pdf}
+%%%%% \includegraphics[width=\textwidth]{benchmarking/benchmarkingVM/ESS_round5.pdf}
 \caption{\textbf{Round 5: benchmarking the \texttt{LeafAVMVN} operator.} See \textbf{Fig \ref{fig:round3Results}} caption for figure notation.  }
@@
 
-Overall, this operator configuration is the final winner in the tournament. %RB: which configuration are you referring to?
+Overall, we have shown that the AVMVN operator configuration is the final winner in the tournament, however its performance benefits are minor and therefore the computational complexities introduced by the \texttt{LeafAVMVN} operator may not be worth the trouble.
 
@@
 
-Here, we introduced an adaptive operator which learns the weights of other operators, by using a target function that rewards operators which bring about large changes to the state and penalises operators which exhibit poor computational runtime (\textbf{Equation \ref{eqn:adaptiveSampler}}).
+Here, we introduced an adaptive operator which learns the weights of other operators, by using a target function that rewards operators which bring about large changes to the state and penalises operators which exhibit poor computational runtime (\textbf{Eq \ref{eqn:adaptiveSampler}}).
 We demonstrated how learning the operator weightings, on a dataset-by-dataset basis, can improve mixing by up to an order of magnitude.
@@
 These methodologies were compared by constructing phylogenetic models from several empirical datasets and comparing their abilities to converge in a tournament-like protocol (\textbf{Fig \ref{fig:tournament}}).
-The methods introduced are adaptive and treat each dataset differently, and perform never worse than without adaptation. %RB: is the part after the comma true?
+The methods introduced are adaptive, treat each dataset differently, and rarely perform worse than without adaptation. 
 This work has produced an operator configuration which is highly effective  on large alignments and can explore relaxed clock model space up to two orders of magnitude more efficiently than previous setups.
@@
 
-\paragraph*{S3 Appendix.}
+\paragraph*{S1 Fig.}
 \label{sect:SR_appendix}
-{\textbf{Supplementary results.} Presentation and interpretation of further benchmarking results.
+{\textbf{Round 1: benchmarking adapt under the \textit{quant} and \textit{cat} parameterisations.} These results show that \textit{cat} does not benefit
+from adaptive weight sampling. Whereas, adapt and cons both greatly improve the \textit{quant}
+parameterisation for most datasets, as expected.
 

### 2020-09-04 Submission/prepareSubmission.R

@@ -1,0 +1,40 @@
+library(pdftools)
+library(tikzDevice)
+library(raster)
+library(rgdal)
+
+manuscript = readLines("../manuscript.tex")
+out.manuscript = "../submission.tex"
+
+# Get figure directories
+figlines = grep("includegraphics", manuscript)
+fig.dir = gsub("[}]*", "", gsub(".+[{]", "", manuscript[figlines]))
+figlines = figlines[fig.dir != "PLOS-submission.eps"]
+fig.dir = fig.dir[fig.dir != "PLOS-submission.eps"]
+fig.dir  = paste0("../", fig.dir)
+
+
+# Comment out figures
+manuscript[figlines] = paste("%%%%%", manuscript[figlines])
+write(paste(manuscript, collapse = "\n"), out.manuscript)
+
+
+# Convert to tiff and compress it
+tifoptions = c("COMPRESS=DEFLATE", "PREDICTOR=2", "ZLEVEL=6")
+for (i in 1:length(fig.dir)) {
+
+
+	filename = paste0("Figures/Fig", i, ".tif")
+	pdf_convert(fig.dir[i], format="tiff", filenames=filename, dpi = 500, antialias = FALSE)
+
+
+	# Compress
+	x = raster(filename)
+	writeRaster(x, filename, options = tifoptions, overwrite = TRUE)
+
+}
+
+tools::texi2pdf(out.manuscript)
+
+
+

### 2020-09-04 lognormal.R

@@ -37,7 +37,7 @@ par(cex.main = 1.5)
 x = seq(from = 0, to = xmax, by = 0.01)
 
 plot(0, 0, type = "n", lwd = 3, yaxs = "i", axes = F, xlab = "Branch rate $r$", ylab = "$p(r|\\sigma)$",
-main = "Probability density function (Log-Normal)", xlim = c(0, xmax), ylim=c(0, 5))
+main = "Probability density function (log-normal)", xlim = c(0, xmax), ylim=c(0, 5))
 
 
 
@@ -82,7 +82,7 @@ b = 0:(nbins-1)
 
 
 for (i in 1:length(b)) {
-	lines(c(b[i], b[i]), c(0, xmax), lty = "1818", lwd = 0.5)
+	#lines(c(b[i], b[i]), c(0, xmax), lty = "1818", lwd = 0.5)
 }
 
 
@@ -131,7 +131,7 @@ for (i in 1:length(Svals)){
 		
 			r0 = qlnorm(q0, M, S)
 			r1 = qlnorm(q1, M, S)
-			lines(c(q0, q1), c(r0, r1), lwd = 0.6, col = Scols[i], lty = "22")
+			lines(c(q0, q1), c(r0, r1), lwd = 1, col = Scols[i], lty = "22")
 			points(q0, r0, pch = 16, col = Scols[i])
 		
 		}

### 2020-09-04 cover_letter.tex
cover letter

\documentclass[12pt,a4paper]{article}
\usepackage[top=2.5cm,bottom=2.5cm,left=2.5cm,right=2.5cm]{geometry}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage{setspace}

\setlength\parindent{0pt}

\begin{document}
\onehalfspacing
%\begin{flushright}
4 September 2020
%\end{flushright}

\vspace{.25cm}
To the editor,

\vspace{.5cm}

Please find attached our manuscript titled ``\emph{Adaptive dating and fast proposals: revisiting the
phylogenetic relaxed clock model}'' for consideration as a
research article in PLOS Computational Biology.

\vspace{.5cm}

In this paper we thoroughly explored the uncorrelated relaxed clock model, which is widely used in phylogenetic inference.
The objective of this analysis was to produce new MCMC operators for doing Bayesian phylogenetic inference under the relaxed clock model.
With the overwhelming availability of genomic data, fast and efficient phylogenetic methods are more important than ever.

\vspace{.5cm}
We explored three parameterisation methods and two cutting-edge proposal kernels, introduced an adaptive operator which learns the weights of other operators, and we introduced a family of tree operators which are specifically designed to work in a relaxed clock model setting. 
These methodologies were systematically benchmarked on a range of empirical datasets to assess their abilities at achieving convergence.

\vspace{.5cm}
This work has produced a setup which can explore relaxed clock space up to 65 times faster than previous setups, depending on the dataset.
The methods produced are very effective on large datasets.
Our results are open source and accessible via a user-friendly interface.

\vspace{2cm}

%\begin{flushright}
Thank you for your consideration.

J. Douglas, R. Zhang, R. Bouckaert

\end{document}

### 2020-09-07 manuscript.tex
typo

@@
 The performance of MCMC is dependent not only on computational performance but also the efficacy of an
-MCMC setup to achieve its convergence.
+MCMC setup to achieve convergence.
 A critical task therein lies the further advancement of MCMC operators.
@@
 $\vec{\mathcal{R}}^{\,}$ is an abstracted vector of branch rates which is transformed into real rates by function $r(\vec{\mathcal{R}}^{\,})$. 
-Branch rates have a mean of 1 under the prior to avoid non-identifiability with node heights and the clock rate $\mu_C$.
+Branch rates have a mean of 1 under the prior to avoid non-identifiability with the clock rate $\mu_C$.
 Three methods of representing rates as $\vec{\mathcal{R}}^{\,}$ are presented in \textbf{\nameref{sect:rateparams}}.
@@
 \includegraphics[width=\textwidth]{Figures/rateparameterisation.pdf}
-\caption{\textbf{Branch rate parameterisations.} Top left: the prior density of a branch rate $r$ under a Log-Normal($-0.5\sigma^2, \sigma$) distribution (with its mean fixed at 1). 
+\caption{\textbf{Branch rate parameterisations.} Top left: the prior density of a branch rate $r$ under a Log-normal($-0.5\sigma^2, \sigma$) distribution (with its mean fixed at 1). 
 The function for transforming $\mathcal{R}$ into branch rates $r(\mathcal{R})$ is depicted for \textit{real} (top right), \textit{cat} (bottom left), and \textit{quant} (bottom right).
 For visualisation purposes, there are only 10 bins/pieces displayed, however in practice we use $2N-2$ bins for \textit{cat} and 100 pieces for \textit{quant}.
-The first and final \textit{quant} pieces are equal to the underlying function however the pieces in between use linear approximations of this function. }
+The first and final \textit{quant} pieces are equal to the underlying function (solid lines) however the pieces in between use linear approximations of this function (dashed lines).}
 \label{fig:rateparams}
@@
 The family of constant distance operators (\texttt{ConstantDistance}, \texttt{SimpleDistance}, and \texttt{SmallPulley} \cite{zhang2020improving}) are best suited for larger datasets (or datasets with strong signal) where the likelihood distribution is peaked (\textbf{Fig \ref{fig:rateparams}}).
-While simple one dimensional operators such as \texttt{RandomWalk} or \texttt{Scale} must make small steps in order to stay ``on the ridge'' of the likelihood function, the constant distance operators ``wander along the ridge''  by ensuring that genetic distances are constant after the proposal.
+While simple one dimensional operators such as \texttt{RandomWalk} or \texttt{Scale} must take small steps in order to stay ``on the ridge'' of the likelihood function, the constant distance operators ``wander along the ridge''  by ensuring that genetic distances are constant after the proposal.
 
@@
 In contrast, a proposal made by \texttt{Scale} $\sigma \rightarrow \sigma^\prime$ under the \textit{quant} parameterisation implicitly alters all branch rates $r(\vec{\mathcal{R}}^{\,})$ while leaving the quantiles $\vec{\mathcal{R}}^{\,}$ themselves constant.
-In contrast, by applying \texttt{CisScale} under \textit{quant}
-all quantiles are recomputed $\vec{\mathcal{R}} \rightarrow \vec{\mathcal{R}}^\prime$  such that the respective branch rates are constant, i.e.
+Whereas, application of \texttt{CisScale} under \textit{quant} results in all quantiles being recomputed $\vec{\mathcal{R}} \rightarrow \vec{\mathcal{R}}^\prime$  such that their rates are constant, i.e.
 $r(\vec{\mathcal{R}}^{\,}) = r(\vec{\mathcal{R}}^{\,\prime})$.
@@
 where \texttt{RF} is the Robinson-Foulds tree distance \cite{robinson1981comparison}, and $|p|$ is the number of dimensions of numerical parameter $p$ (1 for $\sigma$, $2N-2$ for $\vec{\mathcal{R}}^{\,}$, and $2N-1$ for node heights $t$).
-The remaining terms are trained during the second and third phases: the cumulative computational runtime spent on each operator $\mathbb{T}(\omega)$, the sample standard deviation $\sigma_p$ of each numerical parameter $p$, and the summed distances $\sum_x \mathbb{D}(x_p, x_p^\prime)$.
+The remaining terms are trained during the second and third phases: 
+the sample standard deviation $\sigma_p$ of each numerical parameter of interest $p$,
+the cumulative computational runtime spent on each operator $\mathbb{T}(\omega)$,  and the summed distances $\sum_x \mathbb{D}(x_p, x_p^\prime)$.
 
@@
 Under \textbf{Equations \ref{eqn:adaptiveSampler} and \ref{eqn:distanceFunctions}}, operators which effect larger changes on the parameters of interest, in shorter runtime, are sampled with greater probabilities.
-Division of the squared distance by a parameters variance $\sigma^2_p$ enables comparison between different numerical parameters.
+Division of the squared distance by a parameter's sample variance $\sigma^2_p$ enables comparison between numerical parameters which exist in different spaces.
 
@@
 Operators which attain an acceptance probability of 0.234 are often considered to have arrived at a suitable midpoint between these two extremes \cite{bouckaert2019beast, roberts1997weak}.
-The standard uniform distribution kernel has recently been challenged by the Bactrian kernels \cite{yang2013searching, thawornwattana2018designing}.
+The standard uniform distribution kernel has recently been challenged by the family of Bactrian kernels \cite{yang2013searching, thawornwattana2018designing}.
 The (Gaussian) $\text{Bactrian}(m)$ distribution is defined as the sum of two normal distributions:
@@
 \noindent
-where $0 \leq m < 1$ describes the modality of the Bactrian distribution. When $m=0$, the Bactrian distribution is equivalent to a $\text{Normal}(0, 1)$ distribution. 
+where $0 \leq m < 1$ describes modality. 
+When $m=0$, the Bactrian distribution is equivalent to $\text{Normal}(0, 1)$. 
 As $m$ approaches 1, the distribution becomes increasingly bimodal (\textbf{Fig \ref{fig:bactrian}}). 
 Yang et al.
-2013 \cite{yang2013searching} demonstrate that $\text{Bactrian}(m=0.95)$ yields a proposal kernel which traverses the posterior distribution more efficiently that the standard uniform kernel, by placing minimal probability on steps which are too small or too large.
+2013 \cite{yang2013searching} demonstrate that $\text{Bactrian}(m=0.95)$ yields a proposal kernel which traverses the posterior distribution more efficiently than the standard uniform kernel, by placing minimal probability on steps which are too small or too large.
 In this case, a target acceptance probability of around 0.3 is optimal.
@@
 \caption{\textbf{Depiction of \texttt{NarrowExchange} and \texttt{NarrowExchangeRate} operators.} Proposals are denoted by $\mathcal{T} \rightarrow \mathcal{T}^\prime$.
-The vertical axis corresponds to node height $t$.
+The vertical axes correspond to node heights $t$.
 In the bottom figure, branch rates $r$ are indicated by line width and therefore genetic distances are equal to the width of each branch multiplied by its length.
@@
 
-We hypothesised that if \texttt{NarrowExchange} was adapted to the relaxed clock model by ensuring that genetic distances remain constant after the proposal (parallel to the constant distance operators \cite{zhang2020improving}), then its ability to traverse the state space may improve.
+We hypothesised that if \texttt{NarrowExchange} was adapted to the relaxed clock model by ensuring that genetic distances remain constant after the proposal (analogous to constant distance operators \cite{zhang2020improving}), then its ability to traverse the state space may improve.
 
@@
 \begin{align}
-	r_i > 0 \text{ and } {r_i}^\prime > 0 \text { for } i \in \{A,B,C,D\} \\
-	\max\{t_B, t_C \} < {t_D}^\prime < t_E.
+	r_i, {r_i}^\prime > 0 \text { for } i \in \{A,B,C,D\} \\
+	t_B, t_C  < {t_D}^\prime < t_E.
 \end{align}
@@
 
-The total space of NER operators is comprised of all possible subsets of distance constraints (i.e.
+The total space of NER operators consists of all possible subsets of distance constraints (i.e.
 $\{\},\{\mathcal{D}_{AB}\}, \{\mathcal{D}_{AC}\}, \dotso , \{\mathcal{D}_{AB}, \mathcal{D}_{AC}, \mathcal{D}_{AE}, \mathcal{D}_{BC}, \mathcal{D}_{BE}, \mathcal{D}_{CE} \}$) that are solvable.
@@
 
-\paragraph{2. Solving Jacobian determinants.} The determinant of the Jacobian matrix $J$ is required for computing the Green ratio of the proposal. $J$ is defined as
+\paragraph{2. Solving Jacobian determinants.} The determinant of the Jacobian matrix $J$ is required for computing the Green ratio of this proposal. $J$ is defined as
 
@@
 
-Computing the determinant $|J|$ invokes standard analytical differentiation and linear algebra libraries of MATLAB. 
+Solving the determinant $|J|$ invokes standard analytical differentiation and linear algebra libraries of MATLAB. 
 6 of the 54 solvable operators were found to have $|J|=0$, corresponding to irreversible proposals, and were discarded.
@@
 This variant conserves the genetic distance between nodes $A$, $B$, $C$ and their grandparent $E$. 
-Moreover, this operator performed well when branch rates have a large variance ($\sigma > 0.5$), corresponding to non clock-like data. 
+This operator performed well when branch rates had a large variance ($\sigma > 0.5$), corresponding to non clock-like data. 
 On the other hand, the null operator $\text{NER}\{\}$ performed better on shorter sequences ($L < 1$kb) with weaker signal.  
@@
 \begin{align}
-	x_i = \begin{cases} \log r_i \text{ for } \textit{real} \\
-						\log \frac{q_i}{1 - q_i} \text{ for } \textit{quant}  \end{cases}
+	x = \begin{cases} \log r \text{ for } \textit{real} \\
+						\log \frac{q}{1 - q} \text{ for } \textit{quant}  \end{cases}
 \end{align}
@@
 \noindent
-where $r_i$ is a real rate and $q_i$ is a rate quantile. The AVMVN probability density is defined by
-
-\begin{align}
-	\mathcal{AVMVN}(x) =  \mathcal{MVN}\big(x, (1-\beta) \frac{\Sigma_N}{N} + \beta \frac{\mathbb{I}_N}{N} \big) ,
+where $r$ is a real rate and $q$ is a rate quantile. The AVMVN probability density is defined by
+
+\begin{align}
+	\mathcal{AVMVN}(\vec{x}) =  \mathcal{MVN}\big(\vec{x}, (1-\beta) \frac{\Sigma_N}{N} + \beta \frac{\mathbb{I}_N}{N} \big) ,
 \end{align}
@@
 
-In all phylogenetic analyses presented here, we use a Yule \cite{yule1925ii} tree prior $p(\mathcal{T}|\lambda)$ with birth rate $\lambda \sim \text{Log-Normal}(1,1.25)$.
-%RB: mean in real space?
-This is not the traditional parameterisation in the literature, and it was also mentioned earlier that the mean parameter is set such that the mean=1
+In all phylogenetic analyses presented here, we use a Yule \cite{yule1925ii} tree prior $p(\mathcal{T}|\lambda)$ with birth rate $\lambda \sim \text{Log-normal}(1,1.25)$.
+Here and throughout the article, a $\text{Log-normal}(a,b)$ distribution is parameterised such that $a$ and $b$ are the mean and standard deviation in log-space.
 The clock standard deviation has a $\sigma \sim \text{Gamma}(0.5396,0.3819)$ prior.
 Datasets are partitioned into subsequences, where each partition is associated with a distinct HKY substitution model \cite{hasegawa1985dating}.
-The transition-transversion ratio $\kappa \sim \text{Log-Normal}(1, 1.25)$, the four nucleotide frequencies $(f_A, f_C, f_G, f_T) \sim \text{Dirichlet}(10,10,10,10)$, and the relative clock rate $\mu_C \sim \text{Log-Normal}(-0.18, 0.6)$ are estimated independently for each partition.
-%RB: again mean in real space for Log-Normal?
+The transition-transversion ratio $\kappa \sim \text{Log-normal}(1, 1.25)$, the four nucleotide frequencies $(f_A, f_C, f_G, f_T) \sim \text{Dirichlet}(10,10,10,10)$, and the relative clock rate $\mu_C \sim \text{Log-normal}(-0.18, 0.6)$ are estimated independently for each partition.
 The operator scheme ensures that the clock rates $\mu_C$ have a mean of 1 across all partitions. 
 This avoids non-identifiability with branch substitution rates.
-To enable the rapid benchmarking of larger datasets we use BEAGLE for high-performance tree likelihood calculations \cite{ayres2012beagle} and coupled MCMC with four chains for efficient mixing \cite{muller2019coupled}.
+To enable rapid benchmarking of larger datasets we use BEAGLE for high-performance tree likelihood calculations \cite{ayres2012beagle} and coupled MCMC with four chains for efficient mixing \cite{muller2019coupled}.
 The neighbour joining tree \cite{saitou1987neighbor} is used as the initial state in each MCMC chain.
-
-\subsection*{Operator configurations} \label{sect:operatorSchemes}
 
@@
 
-\subsection*{Assessment criteria and datasets}
-
-% Cite HKY somewhere hasegawa1985dating
-
-To avoid a cross-product explosion, the five targets for clock model improvement are evaluated sequentially in the following order: \textbf{\nameref{sect:adaptiveSampling}}, \textbf{\nameref{sect:rateparams}}, \textbf{\nameref{sect:randomwalks}}, \textbf{\nameref{sect:NER}}, and \textbf{\nameref{AVMVN_sect}}.
+To avoid a cross-product explosion, the five targets for clock model improvement were evaluated sequentially in the following order: \textbf{\nameref{sect:adaptiveSampling}}, \textbf{\nameref{sect:rateparams}}, \textbf{\nameref{sect:randomwalks}}, \textbf{\nameref{sect:NER}}, and \textbf{\nameref{AVMVN_sect}}.
 The four operators introduced in these sections are summarised in \textbf{Table \ref{table:newOperators}}.
-The setting which is considered to be the best in each step is then incorporated into the following step. This protocol and its outcomes are summarised in \textbf{Fig \ref{fig:tournament}}.
+The setting which was considered to be the best in each step was then incorporated into the following step. 
+This protocol and its outcomes are summarised in \textbf{Fig \ref{fig:tournament}}.
 
@@
 
-7  &  80  &  1 &  10.0  &  0.9 & 0.82 &  \textit{Simulated data}  \\
+7  &  80  &  1 &  10.0  &  0.9 & 0.82 &  Simulated data  \\
 
@@
 \clearpage
-\subsection*{Round 1: A simple operator-weight learning algorithm can improve performance}
+\subsection*{Round 1: A simple operator-weight learning algorithm greatly improved performance}
 
@@
 Averaged across all datasets, the learned weights behind these two operators were 0.47 and 0.03.
-This is due to the computationally demanding nature of \texttt{CisScale} which invokes the i-CDF function.
-In contrast, the performance of \texttt{Scale} and \texttt{CisScale} were more similar under the \texttt{quant} configuration and were weighted at 0.28 and 0.45.
+This was due to the computationally demanding nature of \texttt{CisScale} which invokes the i-CDF function.
+In contrast, the performance of \texttt{Scale} and \texttt{CisScale} were more similar under the \textit{quant} configuration and were weighted at 0.28 and 0.45.
 For both \textit{real} and \textit{quant}, proposals which altered quantiles, while leaving the rates constant (\texttt{Scale} and \texttt{CisScale} respectively), were preferred.
 
-Overall, the \texttt{AdaptiveOperatorSampler} operator will be included in all subsequent rounds in the tournament.
+Overall, the \texttt{AdaptiveOperatorSampler} operator was included in all subsequent rounds in the tournament.
 
@@
 Furthermore, \textit{real} outperformed \textit{quant} on most datasets, but this was mostly due to the slow computational performance of \textit{quant} compared with real, as opposed to differences in mixing prowess (\textbf{Fig \ref{fig:round2Resultsb}}).
-Irrespective of mixing ability, the adapt (\textit{real}) configuration had the best computation performance and generated samples 40\% faster than adapt (\textit{cat}) and 60\% faster than adapt (\textit{quant}).
-
-Overall, we have determined that \textit{real}, and its associated operators, makes the best parameterisation covered here and will proceed to the next rounds of the benchmarking.
+Irrespective of mixing ability, the adapt (\textit{real}) configuration had the best computational performance and generated samples 40\% faster than adapt (\textit{cat}) and 60\% faster than adapt (\textit{quant}).
+
+Overall, we determined that \textit{real}, and its associated operators, made the best parameterisation covered here and it proceeded to the following rounds of benchmarking.
 
@@
 
-\subsection*{Round 3: Bactrian proposal kernels are around 15\% more efficient than uniform kernels}
+\subsection*{Round 3: Bactrian proposal kernels were around 15\% more efficient than uniform kernels}
 
 We benchmarked the adapt (\textit{real}) configuration with a) standard uniform proposal kernels, and b) Bactrian(0.95) kernels \cite{yang2013searching}.
-These kernels applied to all clock model related operators (\textbf{Table \ref{table:bactriankernels}}).
+These kernels applied to all clock model operators (\textbf{Table \ref{table:bactriankernels}}).
 These results confirmed that the Bactrian kernel yields faster mixing than the standard uniform kernel (\textbf{Fig \ref{fig:round3Results}}).
-All relevant continuous parameters considered had an ESS/hr, averaged across the 9 datasets, between 15 and 20\% faster compared to with the standard uniform kernel.
+All relevant continuous parameters considered had an ESS/hr, averaged across the 9 datasets, between 15\% and 20\% faster compared with the standard uniform kernel.
 Although the Bactrian proposal made little-to-no difference to the caterpillar dataset (Kawahara et al. 2013 \cite{Kawahara_2013}), every other dataset did in fact benefit.
-Bactrian proposal kernels will proceed to round 4 of the relaxed clock model optimisation protocol.
+Bactrian proposal kernels proceeded to round 4 of the relaxed clock model optimisation protocol.
 
@@
 
-\subsection*{Round 4: NER operators outperform on larger datasets}
+\subsection*{Round 4: NER operators outperformed on larger datasets}
 
 Our initial screening of the \texttt{NarrowExchangeRate} (NER) operators revealed that the $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ operator outperformed the standard  \texttt{NarrowExchange} / $\text{NER} \{\}$ operator about 25\% of the time on simulated data, however it was also very sensitive to the dataset.
-Therefore we wrapped up the two operators ($\text{NER} \{\}$ and $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$) within an \texttt{AdaptiveOperatorSampler} operator so that the appropriate weights can be learned, using the Robinson-Foulds metric.
+Therefore we wrapped up the two operators ($\text{NER} \{\}$ and $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$) within an \texttt{AdaptiveOperatorSampler} operator so that the appropriate weights could be learned.
 In this round we benchmarked the Bactrian + adapt (\textit{real}) setting with the adaptive $\text{NER}$ operator (\textbf{Table \ref{table:operatorSchemes}}).
-The benchmark datasets are fairly non clock-like and therefore could benefit from NER (\textbf{Table \ref{table:datasets}}).
-
-Our experiments confirmed that $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ was indeed superior on larger datasets (where $L > 2$kb; \textbf{Fig \ref{fig:round4Results}}).
+The benchmark datasets are fairly non clock-like and therefore could potentially benefit from NER (\textbf{Table \ref{table:datasets}}).
+
+Our experiments confirmed that $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ was indeed superior on larger datasets (where $L > 5$kb; \textbf{Fig \ref{fig:round4Results}}).
 While there was no significant difference in the ESS/hr of continuous parameters, $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ did have an acceptance rate 41\% higher than that of the standard \texttt{NarrowExchange} operator in the most extreme case (the bony fish alignment by Broughton et al.\cite{Broughton_2013}).
-The moderate variance in branch substitution rates ($\hat{\sigma} = 0.5$), coupled with a long alignment (7kb), and high topological uncertainty (\textbf{Fig \ref{fig:parameterisationResults}}) make this dataset the perfect candidate for the NER operator.
-Every proposal acceptance yields a new tree topology and thus facilitates traversal of tree space.
+The moderate variance in branch substitution rates ($\hat{\sigma} = 0.5$), coupled with a long alignment (7kb), and high topological uncertainty (\textbf{Fig \ref{fig:parameterisationResults}}) made this dataset the perfect target.
+Every acceptance of a branch rearrangement proposal yields a new topology and thus facilitates traversal of tree space.
 
 In contrast, the standard \texttt{NarrowExchange} operator outperformed on smaller datasets.
-Thus, the new operator is not always helpful and sometimes it even hinders performance.
-Using an adaptive operator (\texttt{AdaptiveOperatorSampler}) removes the burden from the user in making the decision of which operator to use.
-The \texttt{AdaptiveOperatorSampler(NER)} operator will proceed to the final round of the tournament.
+The new operator was not always helpful and sometimes it even hindered performance.
+Use of an adaptive operator (\texttt{AdaptiveOperatorSampler}) removes the burden from the user in making the decision of which operator to use.
+The \texttt{AdaptiveOperatorSampler(NER)} operator proceeded into the final round of the tournament.
 
@@
 
-\subsection*{Round 5: The AVMVN leaf rate operator is computationally demanding and improves mixing slightly}
+\subsection*{Round 5: The AVMVN leaf rate operator was computationally demanding and improved mixing very slightly}
 
 We tested the applicability of the AVMVN kernel to leaf rate proposals.
-This operates by exploiting any correlations which occur between leaf branch substitution rates.
+This operator exploits any correlations which exist between leaf branch substitution rates.
 To do this, we wrapped the \texttt{LeafAVMVN} operator within an \texttt{AdaptiveOperatorSampler} (\textbf{Table \ref{table:AVMVNoperators}}).
@@
 However, it also produced slightly slower mixing for $\kappa$, reflecting the high computational costs associated with the \texttt{LeafAVMVN} operator (\textbf{Fig \ref{fig:round2Resultsb}}).
-The learned weight of the \texttt{LeafAVMVN} operator was quite small (ranging from 1 to 8\% across all datasets), again reflecting its high computational costs, but also reinforcing the value in having an adaptive weight operator which penalises slow operators.
-Overall, the \texttt{LeafAVMVN} operator provided some, but not much, benefit in its current form.
+The learned weight of the \texttt{LeafAVMVN} operator was quite small (ranging from 1 to 8\% across all datasets), again reflecting its costly nature, but also reinforcing the value in having an adaptive weight operator which penalises slow operators.
+The \texttt{LeafAVMVN} operator provided some, but not much, benefit in its current form.
 
@@
 
-Overall, this operator configuration is the final winner in the tournament. %RB: which configuration are you referring to?
+Overall, we determined that the AVMVN operator configuration was the final winner of the tournament, however its performance benefits were minor and therefore the computational complexities introduced by the \texttt{LeafAVMVN} operator may not be worth the trouble.
 
@@
 This family consists of 48 variants, each of which conserves a unique subset of genetic distances before and after the proposal. 
-Most of these operators turned out to be worse than narrow exchange, however a small subset of these were more efficient but only on larger datasets.
+While most of these operators turned out to be worse than narrow exchange, a small subset were more efficient, but only on large datasets.
 
@@
  Such operators include subtree slide \cite{hohna2008clock}, LOCAL \cite{simon1998local}, and continuous change \cite{jow2002bayesian}.
-Lakner et al. 2008 observed that topological proposals made by the former class consistently outperformed topological changes invoked by the latter class \cite{lakner2008efficiency}.
+Lakner et al. 2008 observed that topological proposals made by the former class consistently outperformed topological changes invoked by the latter  \cite{lakner2008efficiency}.
 

### 2020-11-02 S1_appendix.tex
revisions

@@
 \usepackage{mathtools}
+\usepackage{algorithm}
+\usepackage[noend]{algpseudocode}
 
@@
 
-\section*{S1 Appendix: Rate quantiles}
+\section*{S1 Appendix: Rate quantiles and operators }
 
@@
 
+\clearpage
+\section{Summary of proposal kernels}
+
+Operators whose proposal kernels are affected by the decision to use a Bactrian kernel, as opposed to a uniform kernel, are specified below.
+
+\begin{table}[h!]
+\centering
+\begin{tabular}{l p{3cm} l l}
+
+ & Operator(s) & Proposal & Parameter $x$   \\
+   \hline
+ 1 & \texttt{RandomWalk}  & $x^\prime \leftarrow x + s\Sigma$ & $\vec{\mathcal{R}}^{\,}, \sigma$  \\
+  \hline
+ 2 & \texttt{Scale} & $x^\prime \leftarrow x \times e^{s\Sigma}$ & $\vec{\mathcal{R}}^{\,}, \sigma$   \\
+  \hline
+ 3 & \texttt{Interval} & $\begin{array} {rl} &y \leftarrow \frac{1 - x}{x} \times e^{s\Sigma} \\ &x^\prime \leftarrow \frac{y}{y + 1}  \end{array}$ & $\vec{\mathcal{R}}^{\,}$  \\
+  \hline
+ 4 & \texttt{ConstantDistance} \texttt{SimpleDistance} & $x^\prime \leftarrow x + s\Sigma$ & $t$ \\
+ \hline
+ 5 & \texttt{SmallPulley} & $x^\prime \leftarrow x + s\Sigma$ & $\vec{\mathcal{R}}^{\,}$  \\
+ \hline
+6 & \texttt{CisScale}  & $x^\prime \leftarrow x \times e^{s\Sigma}$ & $\sigma$   \\
+\end{tabular}
+\caption{Proposal kernels $q(x^\prime|x)$ of clock model operators.
+ In each operator, $\Sigma$ is drawn from either a $\text{Bactrian}(m)$ or $\text{uniform}$ distribution.  %RB: Uniform on which interval? (-1,1)?
+ The scale size $s$ is tunable.
+ \texttt{ConstantDistance} and \texttt{SimpleDistance} propose tree heights $t$.
+  The \texttt{Interval} operator applies to rate quantiles and respects its domain i.e. $0 < x, x^\prime < 1$. }
+\label{table:bactriankernels}
+\end{table}
+
+\clearpage
+\section{Supplementary NER Algorithm}
+
+A second NER algorithm is presented below. This operator was rejected by the screening protocol on simulated data.
+
+\begin{algorithm}
+\caption{The NER$\{ \mathcal{D}_{BC}, \mathcal{D}_{CE} \}$ operator.}
+\begin{algorithmic}[1]
+
+\Procedure{proposal}{$t_A$, $t_B$, $t_C$, $t_D$, $t_E$, $r_A$, $r_B$, $r_C$, $r_D$}
+
+	\State
+    \State $s\Sigma \leftarrow $ getRandomWalkSize() \Comment{Random walk size is 0 unless this is NERw}
+    \State $t_D^\prime \leftarrow t_D + s\Sigma$ \Comment{Propose new node height for $D$}
+    \State
+    \State $r_A^\prime \leftarrow r_A$ \Comment{Propose new rates}
+    \State $r_B^\prime \leftarrow \frac{r_B(t_D - t_B) + r_D(t_E - t_D) + r_D(t_E - t_D^\prime)}{t_D^\prime - t_B}$
+    \State $r_C^\prime \leftarrow \frac{r_C(t_E - t_C) - r_D(t_E - t_D^\prime)}{t_D^\prime - t_C}$
+    \State $r_D^\prime \leftarrow r_D$
+    \State
+    \State $|J| \leftarrow \frac{(t_D - t_B)(t_E - t_C)}{(t_D^\prime - t_B)(t_D^\prime - t_C)}$ \Comment{Calculate Jacobian determinant}
+    \State \Return $(r_A^\prime, r_B^\prime, r_C^\prime, r_D^\prime, t_D^\prime, |J|)$
+
+\EndProcedure
+
+\end{algorithmic}
+\label{alg:NER1}
+\end{algorithm}
+
 \bibliography{references}

### 2020-11-02 lognormal.R

@@ -36,7 +36,7 @@ par(cex.main = 1.5)
 # 1) pdf
 x = seq(from = 0, to = xmax, by = 0.01)
 
-plot(0, 0, type = "n", lwd = 3, yaxs = "i", axes = F, xlab = "Branch rate $r$", ylab = "$p(r|\\sigma)$",
+plot(0, 0, type = "n", lwd = 3, yaxs = "i", axes = F, xlab = "Branch rate $r = r(\\mathcal{R})$", ylab = "$p(r|\\sigma)$",
 main = "Probability density function (log-normal)", xlim = c(0, xmax), ylim=c(0, 5))
 
 

### 2020-11-03 manuscript.tex
citation fix

@@
 %Molecular clock models are used for dating evolutionary divergence times. 
-Uncorrelated relaxed clock models enable estimation of molecular substitution rates across lineages and are widely used in phylogenetics for dating evolutionary divergence times.
+Relaxed clock models enable estimation of molecular substitution rates across lineages and are widely used in phylogenetics for dating evolutionary divergence times.
+Under the (uncorrelated) relaxed clock model, tree branches are associated with molecular substitution rates which are independently and identically distributed.
 In this article we delved into the internal complexities of the relaxed clock model in order to develop efficient MCMC operators for Bayesian phylogenetic inference.
@@
 Biological sequences, such as DNA, accumulate mutations over generations. 
-By comparing such sequences in a phylogenetic framework, the evolutionary tree of lifeforms can be inferred.
+By comparing such sequences in a phylogenetic framework, the evolutionary tree of lifeforms can be inferred and historic divergence dates can be estimated.
 With the overwhelming availability of biological sequence data, and the increasing affordability of collecting new data, the development of fast and efficient phylogenetic algorithms is more important than ever.
@@
 The molecular clock hypothesis states that the evolutionary rates of biological sequences are approximately constant through time \cite{zuckerkandl1962molecular}.
-This assumption forms the basis of phylogenetics, under which the evolutionary trees and divergence dates of life forms are inferred from biological sequences, such as nucleic and amino acids \cite{douzery2003local, drummond2006relaxed}.
+This assumption forms the basis of clock-model-based phylogenetics, under which the evolutionary trees and divergence dates of life forms are inferred from biological sequences, such as nucleic and amino acids \cite{douzery2003local, drummond2006relaxed}.
 In Bayesian phylogenetics, these trees and their associated parameters are estimated as probability distributions \cite{kuhner1995estimating, larget1999markov, mau1999bayesian}. 
@@
 This class of models is widely used, and has aided insight into many recent biological problems, including the 2016 Zika virus outbreak \cite{faria2017establishment} and the COVID-19 pandemic \cite{giovanetti2020first}.
-In the remainder of this paper we will only consider uncorrelated relaxed clock models.
-% is compatible with increasingly prominent multispecies coalescent models \cite{ogilvie2017starBEAST 2},
 
 Finally, although not the focus of this article, the class of correlated clock models assumes some form of auto-correlation between rates over time. 
-The correlation itself can invoke a range of stochastic models, including compound Poisson \cite{huelsenbeck2000compound} and CIR processes \cite{lepage2007general}, or it can exist as a series of local clocks \cite{drummond2010bayesian}.
-However, due to the correlated and discrete nature of such models, the time required for MCMC to achieve convergence can be cumbersome, particularly for larger datasets \cite{drummond2010bayesian}.
+The correlation itself can invoke a range of stochastic models, including compound Poisson \cite{huelsenbeck2000compound} and CIR processes \cite{lepage2007general}, Bayesian parametric models \cite{thorne1998estimating}, or it can exist as a series of local clocks \cite{yoder2000estimation, drummond2010bayesian}.
+While these models may be more biologically realistic than uncorrelated models \cite{lepage2007general}, due to their correlated and discrete natures the time required for MCMC to achieve convergence can be cumbersome, particularly for larger datasets \cite{drummond2010bayesian}.
+In the remainder of this paper we only consider uncorrelated relaxed clock models.
 
@@
 Let $\mathcal{T}$ be a binary rooted time tree with $N$ taxa, and %. Let $L$ be the number of sites within the multiple sequence alignment $D$. 
-data $D$ associated with the tips, such as a multiple sequence alignment with $L$ sites, morphological data or geographic locations. 
+data $D$ associated with the tips, such as a multiple sequence alignment with $L$ sites, morphological data, or geographic locations. 
 The posterior density of a phylogenetic model is described by
@@
 \noindent
-where $\sigma$ and $\mu_C$ represent clock model related parameters, and $p(\mathcal{T}|\theta)$ is the tree prior where $\theta$ describes further unspecified parameters. 
+where $\sigma$ and $\mu_C$ represent clock model related parameters, and $p(\mathcal{T}|\theta)$ is the tree prior where $\theta$ describes parameters related to the tree branching or coalescent process.
 The tree likelihood $p(D|\mathcal{T}, r(\vec{\mathcal{R}}^{\,}), \mu_C,\theta)$ %is calculated by the tree-pruning algorithm \cite{felsenstein1981evolutionary}, where
@@
 Each node $i$ in $\mathcal{T}$, except for the root, is associated with a parental branch length $\tau_i$ (the height difference between $i$ and its parent)  and a parental branch substitution rate $r_i = r(\mathcal{R}_i)$.
-In a relaxed clock model, each of the $2N-2$ elements in $\vec{\mathcal{R}}^{\,}$ are independently distributed under the prior $p(\vec{\mathcal{R}}^{\,} | \sigma)$.
+In an uncorrelated relaxed clock model, each of the $2N-2$ elements in $\vec{\mathcal{R}}^{\,}$ are independently distributed under the prior $p(\vec{\mathcal{R}}^{\,} | \sigma)$.
 
@@
 \noindent
-where $q(a|b)$ is the transition kernel: the probability of proposing state $b$ from state $a$.
+where $q(x^\prime|x)$ is the transition kernel: the probability of proposing state $x^\prime$ from state $x$.
 The ratio between the two $\frac{q(x|x^\prime)}{q(x^\prime|x)}$ is known as the Hastings ratio \cite{hastings70}.
@@
 
-Finally, rates can be parameterised as real numbers describing the rate's quantile with respect to some underlying clock model distribution.
+Finally, rates can be parameterised as real numbers describing the rate's quantile with respect to some underlying clock model distribution \cite{li2012model}.
  Under the  \textit{quant} parameterisation, each of the $2N-2$ elements in $\vec{\mathcal{R}}^{\,}$ are uniformly distributed.
@@
 
-\clearpage
 \subsection*{Clock model operators}
@@
 In BEAST 2, operators can have their own tunable parameter $s$, which determines the step size of the operator.
-This term is learned over the course of the MCMC \cite{rosenthal2011optimal, bouckaert2019beast}. 
+This term is tuned over the course of MCMC by achieving a target acceptance rate, typically 0.234 \cite{roberts1997weak, rosenthal2011optimal, bouckaert2019beast}.
 We define clock model operators as those which generate proposals for either $\vec{\mathcal{R}}^{\,}$ or $\sigma$.
@@
 \centering
+\caption{\textbf{Summary of pre-existing BEAST 2 operators.}}
 \begin{tabular}{l p{4.2cm} l l} 
@@
 \texttt{ConstantDistance} & Adjusts an internal node height and recalculates all incident branch rates such that the genetic distances remain constant \cite{zhang2020improving}.
-& $\vec{\mathcal{R}}^{\,}, \mathcal{T}$ & \textit{real}, \textit{quant} \\
- \hline
-\texttt{SimpleDistance} & Applies \texttt{ConstantDistance} to the root node \cite{zhang2020improving}.  & $\vec{\mathcal{R}}^{\,}, \mathcal{T}$ & \textit{real}, \textit{quant} \\
+& $\vec{\mathcal{R}}^{\,}, t$ & \textit{real}, \textit{quant} \\
+ \hline
+\texttt{SimpleDistance} & Applies \texttt{ConstantDistance} to the root node \cite{zhang2020improving}.  & $\vec{\mathcal{R}}^{\,}, t$ & \textit{real}, \textit{quant} \\
  \hline
@@
 \end{tabular}
-\caption{Summary of pre-existing BEAST 2 operators, which apply to either branch rates $\vec{\mathcal{R}}^{\,}$ or the clock standard deviation $\sigma$, and the substitution rate parameterisation they apply to.
- \texttt{ConstantDistance} and \texttt{SimpleDistance} also adjust node heights in the tree $\mathcal{T}$. }
+\begin{flushleft} Summary of pre-existing BEAST 2 operators, which apply to either branch rates $\vec{\mathcal{R}}^{\,}$ or the clock standard deviation $\sigma$, and the substitution rate parameterisation they apply to.
+ \texttt{ConstantDistance} and \texttt{SimpleDistance} also adjust node heights $t$.
+ \end{flushleft}
 \label{table:kernels}
@@
 \centering
+\caption{\bf{Summary of \texttt{AdaptiveOperatorSampler} operators and their parameters of interest (POI).}}
 \begin{tabular}{l l l} 
@@
 &&  \texttt{SmallPulley($\vec{\mathcal{R}}^{\,}, t$)}  \\
+\hline
+\hline
+ \multirow{7}{*}{\texttt{AdaptiveOperatorSampler(leaf)}} & \multirow{7}{*}{$\vec{\mathcal{R}}^{\,}_\text{leaf}, t$} & \texttt{ConstantDistance($\vec{\mathcal{R}}^{\,}_\text{leaf}, \mathcal{T}$)}   \\ 
+&& \texttt{LeafAVMVN($\vec{\mathcal{R}}^{\,}_\text{leaf}$)}  \\
+&& \texttt{RandomWalk($\vec{\mathcal{R}}^{\,}_\text{leaf}$)}  \\
+&& \texttt{Scale($\vec{\mathcal{R}}^{\,}_\text{leaf}$)}   \\
+&& \texttt{Interval($\vec{\mathcal{R}}^{\,}_\text{leaf}$)}   \\
+&& \texttt{Swap($\vec{\mathcal{R}}^{\,}_\text{leaf}$)}  \\
+&& \texttt{SampleFromPrior($\vec{\mathcal{R}}^{\,}_\text{leaf}$)} \\
+\hline
+ \multirow{6}{*}{\texttt{AdaptiveOperatorSampler(internal)}} & \multirow{6}{*}{$\vec{\mathcal{R}}^{\,}_\text{int}, t$} & \texttt{ConstantDistance($\vec{\mathcal{R}}^{\,}_\text{int}, \mathcal{T}$)}   \\
+&& \texttt{RandomWalk($\vec{\mathcal{R}}^{\,}_\text{int}$)}  \\
+&& \texttt{Scale($\vec{\mathcal{R}}^{\,}_\text{int}$)}   \\
+&& \texttt{Interval($\vec{\mathcal{R}}^{\,}_\text{int}$)}   \\
+&& \texttt{Swap($\vec{\mathcal{R}}^{\,}_\text{int}$)}  \\
+&& \texttt{SampleFromPrior($\vec{\mathcal{R}}^{\,}_\text{int}$)} \\
+\hline
+\hline
+ \multirow{2}{*}{\texttt{AdaptiveOperatorSampler(NER)}} & \multirow{2}{*}{$\mathcal{T}$} & NER$\{  \}$ \\ 
+ && NER$\{ \mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE} \}$ \\
 \end{tabular}
-\caption{Summary of \texttt{AdaptiveOperatorSampler} operators and their parameters of interest (POI).
+\begin{flushleft}
 Different operators are applicable to different substitution rate parameterisations (\textbf{Table \ref{table:kernels}}).
+Nodes are broken down into regions to enable operators to be weighted according to their dimension.  
 \texttt{AdaptiveOperatorSampler(root)} applies the root-targeting constant distance operators only \cite{zhang2020improving} while \texttt{AdaptiveOperatorSampler($\vec{\mathcal{R}}^{\,}$)} targets all rates and all nodes heights $t$.
-These two operators are weighted proportionally to the contribution of the root node to the total node count. }
+Nodes are further broken down into leaf rate $\vec{\mathcal{R}}^{\,}_\text{leaf}$ and internal node rate $\vec{\mathcal{R}}^{\,}_\text{int}$ operators.
+This facilitates suitable weighting of the \texttt{LeafAVMVN} operator, which is only applicable to leaf nodes (\textbf{\nameref{AVMVN_sect}}).
+In this setup, the \texttt{RandomWalk($x$)}, \texttt{Scale($x$)}, and \texttt{SampleFromPrior($x$)} operators apply to the corresponding set of branch rates $x$, whereas \texttt{ConstantDistance($x, \mathcal{T}$)} is only applicable to internal nodes which have at least one child of type $x \in \{\vec{\mathcal{R}}^{\,}_\text{leaf}, \vec{\mathcal{R}}^{\,}_\text{int}\}$.
+Finally, the Robinson-Foulds distance between trees before and after every proposal accept is used to train the weights behind \texttt{AdaptiveOperatorSampler(NER)} (see \textbf{\nameref{sect:NER}}).
+In the special case of NER proposals, the \texttt{RF} distance is always equal to 1.
+\end{flushleft}
 \label{table:adaptiveSampling}
 \end{table}
-
-%RRB: should the root operator include a tree root scaler?
-
-%\texttt{AdaptiveOperatorSampler($\sigma$)} samples the clock standard deviation, 
-%\texttt{AdaptiveOperatorSampler($\mathcal{R}$)} samples branch rates and internal node heights,
-%and \texttt{AdaptiveOperatorSampler(root)} samples
 
@@
 In this article we compare the abilities of uniform and Bactrian(0.95) proposal kernels at estimating clock model parameters. 
-The clock model operators which these proposal kernels apply to are described in \textbf{Table \ref{table:bactriankernels}}.
-
-\begin{table}[h!]
-\centering
-\begin{tabular}{l p{3cm} l l}
-
- & Operator(s) & Proposal & Parameter $x$   \\
-   \hline
- 1 & \texttt{RandomWalk}  & $x^\prime \leftarrow x + s\Sigma$ & $\vec{\mathcal{R}}^{\,}, \sigma$  \\
-  \hline
- 2 & \texttt{Scale} & $x^\prime \leftarrow x \times e^{s\Sigma}$ & $\vec{\mathcal{R}}^{\,}, \sigma$   \\
-  \hline
- 3 & \texttt{Interval} & $\begin{array} {rl} &y \leftarrow \frac{1 - x}{x} \times e^{s\Sigma} \\ &x^\prime \leftarrow \frac{y}{y + 1}  \end{array}$ & $\vec{\mathcal{R}}^{\,}$  \\
-  \hline
- 4 & \texttt{ConstantDistance} \texttt{SimpleDistance} & $x^\prime \leftarrow x + s\Sigma$ & $t$ \\
- \hline
- 5 & \texttt{SmallPulley} & $x^\prime \leftarrow x + s\Sigma$ & $\vec{\mathcal{R}}^{\,}$  \\
- \hline
-6 & \texttt{CisScale}  & $x^\prime \leftarrow x \times e^{s\Sigma}$ & $\sigma$   \\
-\end{tabular}
-\caption{Proposal kernels $q(x^\prime|x)$ of clock model operators.
- In each operator, $\Sigma$ is drawn from either a $\text{Bactrian}(m)$ or $\text{uniform}$ distribution.  %RB: Uniform on which interval? (-1,1)?
- The scale size $s$ is tunable.
- \texttt{ConstantDistance} and \texttt{SimpleDistance} propose tree heights $t$.
-  The \texttt{Interval} operator applies to rate quantiles and respects its domain i.e. $0 < x, x^\prime < 1$. }
-\label{table:bactriankernels}
-\end{table}
-
-% RB: Perhaps add Hastings ratios to the table?
+The clock model operators which these proposal kernels apply to are described in \textbf{\nameref{sect:S1Appendix}}.
 
@@
 \clearpage
-% REMEMBER to define NNI and SPR acronyms in introduction preferably
 \subsection*{Narrow Exchange Rate} \label{sect:NER}
@@
 $|J|$ is further augmented if the \textit{quant} parameterisation is employed (\textbf{\nameref{sect:S1Appendix}}).
-Two such operators are expressed in \textbf{Algorithms \ref{alg:NER1} and \ref{alg:NER2}}.
+One such operator is expressed in \textbf{Algorithm \ref{alg:NER2}} and a second in the appendix.
 %RB: what is the purpose of having 2 algorithms -- one (the second one, since that is the one performing well) is enough, no?
-
-\begin{algorithm}
-\caption{The NER$\{ \mathcal{D}_{BC}, \mathcal{D}_{CE} \}$ operator.}
-\begin{algorithmic}[1]
-
-\Procedure{proposal}{$t_A$, $t_B$, $t_C$, $t_D$, $t_E$, $r_A$, $r_B$, $r_C$, $r_D$}
-
-	\State
-    \State $s\Sigma \leftarrow $ getRandomWalkSize() \Comment{Random walk size is 0 unless this is NERw}
-    \State $t_D^\prime \leftarrow t_D + s\Sigma$ \Comment{Propose new node height for $D$}
-    \State
-    \State $r_A^\prime \leftarrow r_A$ \Comment{Propose new rates}
-    \State $r_B^\prime \leftarrow \frac{r_B(t_D - t_B) + r_D(t_E - t_D) + r_D(t_E - t_D^\prime)}{t_D^\prime - t_B}$
-    \State $r_C^\prime \leftarrow \frac{r_C(t_E - t_C) - r_D(t_E - t_D^\prime)}{t_D^\prime - t_C}$
-    \State $r_D^\prime \leftarrow r_D$
-    \State
-    \State $|J| \leftarrow \frac{(t_D - t_B)(t_E - t_C)}{(t_D^\prime - t_B)(t_D^\prime - t_C)}$ \Comment{Calculate Jacobian determinant}
-    \State \Return $(r_A^\prime, r_B^\prime, r_C^\prime, r_D^\prime, t_D^\prime, |J|)$
-
-\EndProcedure
-
-\end{algorithmic}
-\label{alg:NER1}
-\end{algorithm}
 
@@
 Although there were several operators which behaved equivalently during this initial screening process, we selected $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ to proceed to benchmarking (\textbf{\nameref{sect:results}}).
-Due to the apparent sensitivity of NER operators to the data, we introduce the adaptive operator \texttt{AdaptiveOperatorSampler(NER)} which allows the operator scheme to fall back on the standard \texttt{NarrowExchange} in the event of $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ performing poorly (\textbf{Table \ref{table:adaptiveNER}}).
-
-\begin{table}[h!]
-\centering
-\begin{tabular}{l l l} 
- Meta-operator & POI & Operators \\
-\hline
- \multirow{2}{*}{\texttt{AdaptiveOperatorSampler(NER)}} & \multirow{2}{*}{$\mathcal{T}$} & NER$\{  \}$ \\ 
- && NER$\{ \mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE} \}$ \\
-\end{tabular}
-\caption{The adaptive NER operator. 
-The Robinson-Foulds distance between trees before and after every proposal accept is used to train the operator weights.
-In the special case of NER proposals, the \texttt{RF} distance is always equal to 1.
-}
-\label{table:adaptiveNER}
-\end{table}
-
-\clearpage
+Due to the apparent sensitivity of NER operators to the data, we introduce the adaptive operator \texttt{AdaptiveOperatorSampler(NER)} which allows the operator scheme to fall back on the standard \texttt{NarrowExchange} in the event of $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ performing poorly (\textbf{Table \ref{table:adaptiveSampling}}).
+
 \subsection*{An adaptive leaf rate operator}
@@
 The former employs the \texttt{LeafAVMVN} operator and learns its weight during MCMC (after providing it sufficient time to learn $\Sigma_N$).
-
-\begin{table}[h!]
-\centering
-\begin{tabular}{l l l} 
- Meta-operator & POI & Operators \\
-\hline
- \multirow{7}{*}{\texttt{AdaptiveOperatorSampler(leaf)}} & \multirow{7}{*}{$\vec{\mathcal{R}}^{\,}_\text{leaf}, t$} & \texttt{ConstantDistance($\vec{\mathcal{R}}^{\,}_\text{leaf}, \mathcal{T}$)}   \\ 
-&& \texttt{LeafAVMVN($\vec{\mathcal{R}}^{\,}_\text{leaf}$)}  \\
-&& \texttt{RandomWalk($\vec{\mathcal{R}}^{\,}_\text{leaf}$)}  \\
-&& \texttt{Scale($\vec{\mathcal{R}}^{\,}_\text{leaf}$)}   \\
-&& \texttt{Interval($\vec{\mathcal{R}}^{\,}_\text{leaf}$)}   \\
-&& \texttt{Swap($\vec{\mathcal{R}}^{\,}_\text{leaf}$)}  \\
-&& \texttt{SampleFromPrior($\vec{\mathcal{R}}^{\,}_\text{leaf}$)} \\
-\hline
- \multirow{6}{*}{\texttt{AdaptiveOperatorSampler(internal)}} & \multirow{6}{*}{$\vec{\mathcal{R}}^{\,}_\text{int}, t$} & \texttt{ConstantDistance($\vec{\mathcal{R}}^{\,}_\text{int}, \mathcal{T}$)}   \\
-&& \texttt{RandomWalk($\vec{\mathcal{R}}^{\,}_\text{int}$)}  \\
-&& \texttt{Scale($\vec{\mathcal{R}}^{\,}_\text{int}$)}   \\
-&& \texttt{Interval($\vec{\mathcal{R}}^{\,}_\text{int}$)}   \\
-&& \texttt{Swap($\vec{\mathcal{R}}^{\,}_\text{int}$)}  \\
-&& \texttt{SampleFromPrior($\vec{\mathcal{R}}^{\,}_\text{int}$)} \\
-\end{tabular}
-\caption{Leaf rate $\vec{\mathcal{R}}^{\,}_\text{leaf}$ and internal node rate $\vec{\mathcal{R}}^{\,}_\text{int}$ operators. 
-This division enables the two meta-operators to be weighted proportionally to the number of nodes (leaves or internal) which they apply to.
-This facilitates incorporation of the  \texttt{LeafAVMVN} operator, which is only applicable to leaf nodes.
-In this setup, the \texttt{RandomWalk($x$)}, \texttt{Scale($x$)}, and \texttt{SampleFromPrior($x$)} operators apply to the corresponding set of branch rates $x$, whereas \texttt{ConstantDistance($x, \mathcal{T}$)} is only applicable to internal nodes which have at least one child of type $x \in \{\vec{\mathcal{R}}^{\,}_\text{leaf}, \vec{\mathcal{R}}^{\,}_\text{int}\}$.}
-\label{table:AVMVNoperators}
-\end{table}
 
@@
 \centering
+\caption{\bf{Summary of clock model operators introduced throughout this article. }}
 \begin{tabular}{l p{4cm} l} 
@@
 \end{tabular}
-\caption{Summary of clock model operators introduced throughout this article. Pre-existing clock model operators are summarised in \textbf{Table \ref{table:kernels}}}
+\begin{flushleft}
+Pre-existing clock model operators are summarised in \textbf{Table \ref{table:kernels}}
+\end{flushleft}
 \label{table:newOperators}
@@
 \centering
+\caption{\bf{Operator configurations and the substitution rate parameterisations which each operator is applicable to.}}
 \begin{tabular}{l l l l l l} 
@@
 \end{tabular}
-\caption{Operator configurations and the substitution rate parameterisations which each operator is applicable to.
+\begin{flushleft}
 Within each configuration (and substitution rate parameterisation), the weight behind $\vec{\mathcal{R}}^{\,}$ sums to 30, the weight of $\sigma$ is equal to 10, and the weight of NER is equal to 15.
@@
 Operators which apply to specific node sets (root, internal, leaf, or all)
- are weighted according to leaf count $N$. The adaptive operators are further broken down in \textbf{Tables \ref{table:adaptiveSampling}, \ref{table:adaptiveNER}, and \ref{table:AVMVNoperators}}.
+ are weighted according to leaf count $N$. The adaptive operators are further broken down in \textbf{Table \ref{table:adaptiveSampling}}.
 All other operators (i.e. those which apply to which apply to other terms in the state such as the nucleotide substitution model) are held constant within each dataset.
-}
-
+\end{flushleft}
 %The total weight of all operators across all parameters was 116 in each MCMC setup.
@@
 
-To avoid a cross-product explosion, the five targets for clock model improvement were evaluated sequentially in the following order: \textbf{\nameref{sect:adaptiveSampling}}, \textbf{\nameref{sect:rateparams}}, \textbf{\nameref{sect:randomwalks}}, \textbf{\nameref{sect:NER}}, and \textbf{\nameref{AVMVN_sect}}.
+To avoid an intractably large search space, the five targets for clock model improvement were evaluated sequentially in the following order: \textbf{\nameref{sect:adaptiveSampling}}, \textbf{\nameref{sect:rateparams}}, \textbf{\nameref{sect:randomwalks}}, \textbf{\nameref{sect:NER}}, and \textbf{\nameref{AVMVN_sect}}.
 The four operators introduced in these sections are summarised in \textbf{Table \ref{table:newOperators}}.
@@
 Methodologies were benchmarked using one simulated and eight empirical datasets.
-The latter were compiled \cite{lanfear2019Github} and partitioned \cite{lanfear2016partitionfinder} by Lanfear as ``benchmark alignments'' (\textbf{Table \ref{table:datasets}}).
+The latter were compiled by Lanfear as ``benchmark alignments'' (\textbf{Table \ref{table:datasets}}) \cite{lanfear2019Github, lanfear2016partitionfinder}.
 Each methodology was benchmarked for million-states-per-hour using the Intel Xeon Gold 6138 CPU (2.00 GHz).
@@
 \centering
+\caption{\bf{Benchmark datasets, sorted in increasing order of taxon count $N$.}}
 \begin{tabular}{l l l l l l l} 
@@
 \end{tabular}
-\caption{Benchmark datasets, sorted in increasing order of taxon count $N$.
-Number of partitions $P$, total alignment length $L$, and number of unique site patterns $L_\text{unq}$ in the alignment are also specified.
+\begin{flushleft}
+Number of partitions $P$, total alignment length $L$, and number of unique site patterns $L_\text{unq}$ in the alignment are specified.
 Clock standard deviation estimates $\hat\sigma$ are of moderate magnitude, suggesting that most of these datasets are not clock-like.
-}
+\end{flushleft}
 \label{table:datasets}
@@
 
-We compared the three rate parameterisations described in \textbf{\nameref{sect:rateparams}}. 
+In Round 1 we selected the best configuration for each of the three rate parameterisations described in \textbf{\nameref{sect:rateparams}},  and in Round 2 we compared the three to each other.
 adapt (\textit{real}) and adapt (\textit{quant}) both employed constant distance tree operators \cite{zhang2020improving} and both used the \texttt{AdaptiveOperatorSampler} operator to learn clock model operator weights.
@@
 Overall, we determined that \textit{real}, and its associated operators, made the best parameterisation covered here and it proceeded to the following rounds of benchmarking.
+This outcome allowed Rounds 3, 4, and 5 to commence. 
+If \textit{cat} dominated in this round, then the operators benchmarked in Rounds 4 and 5 would not be applicable to the parameterisation and the Bactrian proposal kernel benchmarked in Round 3 would not be applicable to branch rate categories in its present form.
 
@@
 We benchmarked the adapt (\textit{real}) configuration with a) standard uniform proposal kernels, and b) Bactrian(0.95) kernels \cite{yang2013searching}.
-These kernels applied to all clock model operators (\textbf{Table \ref{table:bactriankernels}}).
+These kernels applied to all clock model operators.
 These results confirmed that the Bactrian kernel yields faster mixing than the standard uniform kernel (\textbf{Fig \ref{fig:round3Results}}).
 All relevant continuous parameters considered had an ESS/hr, averaged across the 9 datasets, between 15\% and 20\% faster compared with the standard uniform kernel.
-Although the Bactrian proposal made little-to-no difference to the caterpillar dataset (Kawahara et al. 2013 \cite{Kawahara_2013}), every other dataset did in fact benefit.
+Although the Bactrian proposal made little-to-no difference to the caterpillar dataset (Kawahara and Rubinoff 2013 \cite{Kawahara_2013}), every other dataset did in fact benefit.
 Bactrian proposal kernels proceeded to round 4 of the relaxed clock model optimisation protocol.
@@
 While there was no significant difference in the ESS/hr of continuous parameters, $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ did have an acceptance rate 41\% higher than that of the standard \texttt{NarrowExchange} operator in the most extreme case (the bony fish alignment by Broughton et al.\cite{Broughton_2013}).
-The moderate variance in branch substitution rates ($\hat{\sigma} = 0.5$), coupled with a long alignment (7kb), and high topological uncertainty (\textbf{Fig \ref{fig:parameterisationResults}}) made this dataset the perfect target.
+The moderate variance in branch substitution rates ($\hat{\sigma} = 0.5$), coupled with a long alignment (7kb), and high topological uncertainty (\textbf{Fig \ref{fig:round4Results}}) made this dataset the perfect target.
 Every acceptance of a branch rearrangement proposal yields a new topology and thus facilitates traversal of tree space.
@@
 \includegraphics[width=\textwidth]{benchmarking/benchmarkingVM/ESS_round4.pdf}
+\includegraphics[width=\textwidth]{Figures/broughton.pdf}
 \caption{\textbf{Round 4: benchmarking the NER operators.} 
-The learned weights (left) behind the two NER operators ($\text{NER} \{\}$ and $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$), and the relative difference between their acceptance rates $\alpha$ (right), are presented as functions of sequence length.
-Logistic and logarithmic regression models are shown, respectively. }
+Top: the learned weights (left) behind the two NER operators ($\text{NER} \{\}$ and $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$), and the relative difference between their acceptance rates $\alpha$ (right), are presented as functions of sequence length.
+Logistic and logarithmic regression models are shown, respectively.
+Bottom: maximum clade credibility tree of the bony fish dataset by Broughton et al. 2013 \cite{Broughton_2013}.
+This alignment received the strongest boost from NER, likely due to its high topological uncertainty and branch rate variance.  
+Branches are coloured by substitution rate, the y-axis shows time units, and internal nodes are labelled with posterior clade support.  
+Tree visualised using UglyTrees \cite{uglytrees}.}
 \label{fig:round4Results}
@@
 
-\begin{figure}[!h]
-%\includegraphics[width=\textwidth]{Figures/cognato.pdf}
-\includegraphics[width=\textwidth]{Figures/broughton.pdf}
-\caption{\textbf{Maximum clade credibility tree of bony fishes.} 
-Branches are coloured by substitution rate (units: substitutions per site per unit of time) and the y-axis shows time, such that there is on average 1 substitution per unit of time.
-Internal nodes are labelled with posterior clade support. 
-This alignment (Broughton et al.
-2013 \cite{Broughton_2013}) received the strongest boost from the $\text{NER}\{\mathcal{D}_{AE}, \mathcal{D}_{BE}, \mathcal{D}_{CE}\}$ operator, likely due to its high topological uncertainty and branch rate variance.
-Tree generated by UglyTrees \cite{uglytrees}.  }
-\label{fig:parameterisationResults}
-\end{figure}
-
+\clearpage
 \subsection*{Round 5: The AVMVN leaf rate operator was computationally demanding and improved mixing very slightly}
@@
 This operator exploits any correlations which exist between leaf branch substitution rates.
-To do this, we wrapped the \texttt{LeafAVMVN} operator within an \texttt{AdaptiveOperatorSampler} (\textbf{Table \ref{table:AVMVNoperators}}).
+To do this, we wrapped the \texttt{LeafAVMVN} operator within an \texttt{AdaptiveOperatorSampler} (\textbf{Table \ref{table:adaptiveSampling}}).
 The two configurations compared here were a) adapt + Bactrian + NER (\textit{real}) and b) AVMVN + NER + Bactrian + adapt (\textit{real})  (\textbf{Table \ref{table:operatorSchemes}}).
@@
 In this article we introduced the family of narrow exchange rate operators (\textbf{Fig \ref{fig:narrowexchange}}).
-These operators are built on top of the narrow exchange operator and are specifically designed for the relaxed clock model, by accounting for the correlation which exists between branch lengths and branch substitution rates.
+These operators are built on top of the narrow exchange operator and are specifically designed for the (uncorrelated) relaxed clock model, by accounting for the correlation which exists between branch lengths and branch substitution rates.
 This family consists of 48 variants, each of which conserves a unique subset of genetic distances before and after the proposal. 
@@
 
+\subsection*{Future outlook}
+
+Based on these experiments, we have corroborated the results of Zhang and Drummond 2020 \cite{zhang2020improving} by showing that the relaxed clock rate parameterisation can be greatly superior to the categories parameterisation.
+However this is conditional on the use of operators. 
+Standard scale operators are ineffective in the real rate space on large datasets and constant distance operators tend to be the same on smaller ones.
+As the categories configuration is the current relaxed clock model default in both BEAST as well as BEAST 2, we therefore recommend researchers make the transition to the real rate parameterisation and employ an operator setup similar to that described in this article.
+
+However, there remain several avenues for improvement.
+First, the use of a Weibull clock model prior, as opposed to a log-normal, could further decrease calculation time due to its closed-form inverse cumulative distribution function.
+Second, the leaf rate AVMVN operator presented in this article could be improved by proposing rates for only a small subset of correlated branch rates per proposal, as opposed to all at once. 
+This would mitigate the computational burden associated with a covariance matrix which grows with the tree size (\textbf{\nameref{AVMVN_sect}}).
+Finally, while our adaptive weighting operator can learn operator weights within parameter spaces, it is not clear how to best assign weights between spaces; the relative weighting between clock model operators and tree topology operators for instance.
+
+\newpage
 \section*{Conclusion}
@@
 \label{sect:S1Appendix}
-{\textbf{Rate quantiles.} The linear piecewise approximation used in the \textit{quant} parameterisation is described. 
+{\textbf{Rate quantiles and operators.} The linear piecewise approximation used in the \textit{quant} parameterisation is described. 
 Constant distance tree operators, \texttt{CisScale}, and  \texttt{NarrowExchangeRate} are extended to the \textit{quant} parameterisation. 
+A second NER algorithm is specified.
 

### 2020-11-04 tiff/toTiff.R
tiff file conversion

@@ -1,0 +1,27 @@
+library(pdftools)
+
+
+files = c("../Figures/rateparameterisation.pdf", "../Figures/correlations.pdf", "../Figures/clockSD.pdf", 
+		"../Figures/bactrian.pdf", "../Figures/NarrowExchange.pdf",  "../Figures/acceptanceRates.pdf", "../Figures/tournament.pdf",
+		"../benchmarking/benchmarkingVM/ESS_round1_real.pdf",
+		"../benchmarking/benchmarkingVM/ESS_round2.pdf",
+		"../benchmarking/benchmarkingVM/ESS_timesettings.pdf",
+		"../benchmarking/benchmarkingVM/ESS_round3.pdf",
+		"../Figures/Fig12.pdf",
+		"../benchmarking/benchmarkingVM/ESS_round5.pdf")
+for (i in 1:length(files)){
+
+
+	f = files[i]
+	o = paste0("ig", i, ".tiff")
+	pdf_convert(f, "tiff", dpi=600, filenames = o)
+
+
+	#tiff(o, compression = "lzw")
+
+
+
+	#dev.off()
+
+}
+

### 2020-11-04 tiff/toTiff.sh

@@ -1,0 +1,20 @@
+#!/bin/sh
+
+
+rm *.tiff
+Rscript toTiff.R
+
+# Real data   
+for t in *.tiff;
+do
+
+	echo "$t"
+	tiffcp $t "F$t" -c lzw
+	rm $t
+done
+
+
+
+
+#cd benchmarkingVM
+#Rscript ../render.R

### 2020-12-17 manuscript.tex
manuscript tidyups

@@
 
-\clearpage
 \subsection*{Branch rate parameterisations}
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{Figures/rateparameterisation.pdf}
+%\includegraphics[width=\textwidth]{Figures/rateparameterisation.pdf}
 \caption{\textbf{Branch rate parameterisations.} Top left: the prior density of a branch rate $r$ under a Log-normal($-0.5\sigma^2, \sigma$) distribution (with its mean fixed at 1). 
@@
 
-\clearpage
 \subsubsection*{1. Real rates}
@@
 
+ \texttt{Scale} and \texttt{CisScale} both operate on the clock model standard deviation $\sigma$ however they behave differently in the \textit{real} and \textit{quant} parameterisations (\textbf{Fig \ref{fig:clockSDoperators}}).
+In \textit{real}, large proposals of $\sigma \rightarrow \sigma^\prime$ made by  \texttt{Scale} could incur large penalties in the clock model prior density $p(\vec{\mathcal{R}}^{\,}|\sigma^\prime)$ and thus may be rejected quite often.
+This led to the development of the fast clock scaler \cite{zhang2020improving} (herein referred to as \texttt{CisScale}).
+This operator recomputes all branch rates $\vec{\mathcal{R}}^{\,} \rightarrow \vec{\mathcal{R}}^{\, \prime}$ such that their quantiles under the new clock model prior remain constant $p(\vec{\mathcal{R}}^{\,}|\sigma) = p(\vec{\mathcal{R}}^{\, \prime}|\sigma^\prime)$.
+In contrast, a proposal made by \texttt{Scale} $\sigma \rightarrow \sigma^\prime$ under the \textit{quant} parameterisation implicitly alters all branch rates $r(\vec{\mathcal{R}}^{\,})$ while leaving the quantiles $\vec{\mathcal{R}}^{\,}$ themselves constant.
+Whereas, application of \texttt{CisScale} under \textit{quant} results in all quantiles being recomputed $\vec{\mathcal{R}} \rightarrow \vec{\mathcal{R}}^\prime$  such that their rates are constant, i.e.
+$r(\vec{\mathcal{R}}^{\,}) = r(\vec{\mathcal{R}}^{\,\prime})$.
+In summary, \texttt{Scale} and \texttt{CisScale} propose rates/quantiles in the opposite (trans) or same (cis) space that the clock model is parameterised under (\textbf{Fig \ref{fig:clockSDoperators}}).
+
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{Figures/correlations.pdf}
+\centering
+%\includegraphics[width=\textwidth]{Figures/clockSD.pdf}
+\caption{\textbf{Clock standard deviation scale operators.}
+The two operators above propose a clock standard deviation $\sigma \rightarrow \sigma^\prime$. 
+Then, either the new quantiles are such that the rates remain constant (``New quantiles'', above) or the new rates are  such that the quantiles remain constant (``New rates''). 
+In the \textit{real} parameterisation, these two operators are known as \texttt{Scale} and \texttt{CisScale}, respectively.
+Whereas, in \textit{quant}, they are known as \texttt{CisScale} and \texttt{Scale}.    }
+\label{fig:clockSDoperators}
+\end{figure}
+
+\subsection*{Adaptive operator weighting}
+\label{sect:adaptiveSampling}
+
+It is not always clear which operator weighting scheme is best for a given dataset.
+In this article we introduce \texttt{AdaptiveOperatorSampler} -- a meta-operator which learns the weights of other operators during MCMC and then samples these operators according to their learned weights.
+This meta-operator undergoes three phases.
+In the first phase (burn-in), \texttt{AdaptiveOperatorSampler} samples from its set of sub-operators uniformly at random.
+In the second phase (learn-in), the meta-operator starts learning several terms detailed below whilst continuing to sample operators uniformly at random.
+In its final phase, \texttt{AdaptiveOperatorSampler} samples operators (denoted by $\omega$) using the following distribution:
+
+\begin{align}
+\label{eqn:adaptiveSampler}
+	p(\omega) \propto \begin{cases} 1 & \text{ with probability } \Omega \\ \frac{1}{\mathbb{T}(\omega)} \sum\limits_{p \in \text{POI}}  \sum\limits_{x \in \text{accepts}(\omega)}  \mathbb{D}(x_p, x_p^\prime) & \text{ with probability } 1-\Omega \end{cases}
+\end{align}
+
+\noindent
+where $\mathbb{T}(\omega)$ is the cumulative computational time spent on each operator, $\mathbb{D}$ is a distance function, and we use $\Omega = 0.01$ to allow any sub-operator to be sampled regardless of its performance.
+The parameters of interest (POI) may be either a set of numerical parameters (such as branch rates or node heights), or it may be the tree itself, but it cannot be both in its current form.
+The distance between state $x_p$ and its (accepted) proposal $x_p^\prime$ with respect to parameter $p$ is determined by
+
+\begin{align}
+\label{eqn:distanceFunctions} 
+	\mathbb{D}(x_p, x_p^\prime) = \begin{cases} \texttt{RF}(x_p, x_p^\prime)^2 & \text{ if } p \text{ is a tree} \\ 
+	\frac{1}{|p|} \Big[ \frac{\norm{x_p - x_p^\prime}}{\sigma_p} \Big]^2    & \text{ if } p \text{ is numerical}  \end{cases}
+\end{align}
+
+\noindent
+where \texttt{RF} is the Robinson-Foulds tree distance \cite{robinson1981comparison}, and $|p|$ is the number of dimensions of numerical parameter $p$ (1 for $\sigma$, $2N-2$ for $\vec{\mathcal{R}}^{\,}$, and $2N-1$ for node heights $t$).
+The remaining terms are trained during the second and third phases: 
+the sample standard deviation $\sigma_p$ of each numerical parameter of interest $p$,
+the cumulative computational runtime spent on each operator $\mathbb{T}(\omega)$,  and the summed distances $\sum_x \mathbb{D}(x_p, x_p^\prime)$.
+
+%The terms which are learned during the second and third phases are: ,
+
+Under \textbf{Equations \ref{eqn:adaptiveSampler} and \ref{eqn:distanceFunctions}}, operators which effect larger changes on the parameters of interest, in shorter runtime, are sampled with greater probabilities.
+Division of the squared distance by a parameter's sample variance $\sigma^2_p$ enables comparison between numerical parameters which exist in different spaces.
+
+Datasets which contain very poor signal (or small $L$) are likely to mix better when more weight is placed on bold operators (\textbf{Fig \ref{fig:landscape}}). 
+We therefore introduce the \texttt{SampleFromPrior($\vec{x}^{\,}$)} operator.
+This operator resamples $\psi$ randomly selected elements within vector $\vec{x}^{\,}$ from their prior distributions, where $\psi \sim \text{Binomial}(n=|\vec{x}^{\,}|, p=\frac{s}{|\vec{x}^{\,}|})$ for tunable term $s$.
+%The \texttt{Uniform} operator is a special case of \texttt{SampleFromPrior}.
+\texttt{SampleFromPrior} is included among the set of operators under \texttt{AdaptiveOperatorSampler} and serves to make the boldest proposals for datasets with poor signal.
+
+\begin{figure}[!h]
+%\includegraphics[width=\textwidth]{Figures/correlations.pdf}
 \caption{\textbf{Traversing likelihood space.}
@@
 
- \texttt{Scale} and \texttt{CisScale} both operate on the clock model standard deviation $\sigma$ however they behave differently in the \textit{real} and \textit{quant} parameterisations (\textbf{Fig \ref{fig:clockSDoperators}}).
-In \textit{real}, large proposals of $\sigma \rightarrow \sigma^\prime$ made by  \texttt{Scale} could incur large penalties in the clock model prior density $p(\vec{\mathcal{R}}^{\,}|\sigma^\prime)$ and thus may be rejected quite often.
-This led to the development of the fast clock scaler \cite{zhang2020improving} (herein referred to as \texttt{CisScale}).
-This operator recomputes all branch rates $\vec{\mathcal{R}}^{\,} \rightarrow \vec{\mathcal{R}}^{\, \prime}$ such that their quantiles under the new clock model prior remain constant $p(\vec{\mathcal{R}}^{\,}|\sigma) = p(\vec{\mathcal{R}}^{\, \prime}|\sigma^\prime)$.
-In contrast, a proposal made by \texttt{Scale} $\sigma \rightarrow \sigma^\prime$ under the \textit{quant} parameterisation implicitly alters all branch rates $r(\vec{\mathcal{R}}^{\,})$ while leaving the quantiles $\vec{\mathcal{R}}^{\,}$ themselves constant.
-Whereas, application of \texttt{CisScale} under \textit{quant} results in all quantiles being recomputed $\vec{\mathcal{R}} \rightarrow \vec{\mathcal{R}}^\prime$  such that their rates are constant, i.e.
-$r(\vec{\mathcal{R}}^{\,}) = r(\vec{\mathcal{R}}^{\,\prime})$.
-In summary, \texttt{Scale} and \texttt{CisScale} propose rates/quantiles in the opposite (trans) or same (cis) space that the clock model is parameterised under (\textbf{Fig \ref{fig:clockSDoperators}}).
-
-\begin{figure}[!h]
-\centering
-\includegraphics[width=\textwidth]{Figures/clockSD.pdf}
-\caption{\textbf{Clock standard deviation scale operators.}
-The two operators above propose a clock standard deviation $\sigma \rightarrow \sigma^\prime$. 
-Then, either the new quantiles are such that the rates remain constant (``New quantiles'', above) or the new rates are  such that the quantiles remain constant (``New rates''). 
-In the \textit{real} parameterisation, these two operators are known as \texttt{Scale} and \texttt{CisScale}, respectively.
-Whereas, in \textit{quant}, they are known as \texttt{CisScale} and \texttt{Scale}.    }
-\label{fig:clockSDoperators}
-\end{figure}
-
-\clearpage
-\subsection*{Adaptive operator weighting}
-\label{sect:adaptiveSampling}
-
-It is not always clear which operator weighting scheme is best for a given dataset.
-In this article we introduce \texttt{AdaptiveOperatorSampler} -- a meta-operator which learns the weights of other operators during MCMC and then samples these operators according to their learned weights.
-This meta-operator undergoes three phases.
-In the first phase (burn-in), \texttt{AdaptiveOperatorSampler} samples from its set of sub-operators uniformly at random.
-In the second phase (learn-in), the meta-operator starts learning several terms detailed below whilst continuing to sample operators uniformly at random.
-In its final phase, \texttt{AdaptiveOperatorSampler} samples operators (denoted by $\omega$) using the following distribution:
-
-\begin{align}
-\label{eqn:adaptiveSampler}
-	p(\omega) \propto \begin{cases} 1 & \text{ with probability } \Omega \\ \frac{1}{\mathbb{T}(\omega)} \sum\limits_{p \in \text{POI}}  \sum\limits_{x \in \text{accepts}(\omega)}  \mathbb{D}(x_p, x_p^\prime) & \text{ with probability } 1-\Omega \end{cases}
-\end{align}
-
-\noindent
-where $\mathbb{T}(\omega)$ is the cumulative computational time spent on each operator, $\mathbb{D}$ is a distance function, and we use $\Omega = 0.01$ to allow any sub-operator to be sampled regardless of its performance.
-The parameters of interest (POI) may be either a set of numerical parameters (such as branch rates or node heights), or it may be the tree itself, but it cannot be both in its current form.
-The distance between state $x_p$ and its (accepted) proposal $x_p^\prime$ with respect to parameter $p$ is determined by
-
-\begin{align}
-\label{eqn:distanceFunctions} 
-	\mathbb{D}(x_p, x_p^\prime) = \begin{cases} \texttt{RF}(x_p, x_p^\prime)^2 & \text{ if } p \text{ is a tree} \\ 
-	\frac{1}{|p|} \Big[ \frac{\norm{x_p - x_p^\prime}}{\sigma_p} \Big]^2    & \text{ if } p \text{ is numerical}  \end{cases}
-\end{align}
-
-\noindent
-where \texttt{RF} is the Robinson-Foulds tree distance \cite{robinson1981comparison}, and $|p|$ is the number of dimensions of numerical parameter $p$ (1 for $\sigma$, $2N-2$ for $\vec{\mathcal{R}}^{\,}$, and $2N-1$ for node heights $t$).
-The remaining terms are trained during the second and third phases: 
-the sample standard deviation $\sigma_p$ of each numerical parameter of interest $p$,
-the cumulative computational runtime spent on each operator $\mathbb{T}(\omega)$,  and the summed distances $\sum_x \mathbb{D}(x_p, x_p^\prime)$.
-
-%The terms which are learned during the second and third phases are: ,
-
-Under \textbf{Equations \ref{eqn:adaptiveSampler} and \ref{eqn:distanceFunctions}}, operators which effect larger changes on the parameters of interest, in shorter runtime, are sampled with greater probabilities.
-Division of the squared distance by a parameter's sample variance $\sigma^2_p$ enables comparison between numerical parameters which exist in different spaces.
-
-Datasets which contain very poor signal (or small $L$) are likely to mix better when more weight is placed on bold operators (\textbf{Fig \ref{fig:landscape}}). 
-We therefore introduce the \texttt{SampleFromPrior($\vec{x}^{\,}$)} operator.
-This operator resamples $\psi$ randomly selected elements within vector $\vec{x}^{\,}$ from their prior distributions, where $\psi \sim \text{Binomial}(n=|\vec{x}^{\,}|, p=\frac{s}{|\vec{x}^{\,}|})$ for tunable term $s$.
-%The \texttt{Uniform} operator is a special case of \texttt{SampleFromPrior}.
-\texttt{SampleFromPrior} is included among the set of operators under \texttt{AdaptiveOperatorSampler} and serves to make the boldest proposals for datasets with poor signal.
-
 In this article we apply three instances of the \texttt{AdaptiveOperatorSampler} meta-operator to the \textit{real}, \textit{cat}, and \textit{quant} parameterisations. 
@@
  \hline
-  \multirow{6}{*}{\texttt{AdaptiveOperatorSampler($\vec{\mathcal{R}}^{\,}$)}} & \multirow{6}{*}{$\vec{\mathcal{R}}^{\,}, t$} & \texttt{ConstantDistance($\vec{\mathcal{R}}^{\,}, \mathcal{T}$)}   \\ 
+  \multirow{6}{*}{\texttt{AdaptiveOperatorSampler($\vec{\mathcal{R}}^{\,}$)}} & \multirow{6}{*}{$\vec{\mathcal{R}}^{\,}, t$} & \texttt{ConstantDistance($\vec{\mathcal{R}}^{\,}, t$)}   \\ 
 && \texttt{RandomWalk($\vec{\mathcal{R}}^{\,}$)}  \\
@@
  \hline
-   \multirow{2}{*}{\texttt{AdaptiveOperatorSampler(root)}} & \multirow{2}{*}{$\vec{\mathcal{R}}^{\,}, t$} & \texttt{SimpleDistance($\vec{\mathcal{R}}^{\,}, \mathcal{T}$)}  \\ 
+   \multirow{2}{*}{\texttt{AdaptiveOperatorSampler(root)}} & \multirow{2}{*}{$\vec{\mathcal{R}}^{\,}, t$} & \texttt{SimpleDistance($\vec{\mathcal{R}}^{\,}, t$)}  \\ 
 &&  \texttt{SmallPulley($\vec{\mathcal{R}}^{\,}, t$)}  \\
@@
 \hline
- \multirow{7}{*}{\texttt{AdaptiveOperatorSampler(leaf)}} & \multirow{7}{*}{$\vec{\mathcal{R}}^{\,}_\text{leaf}, t$} & \texttt{ConstantDistance($\vec{\mathcal{R}}^{\,}_\text{leaf}, \mathcal{T}$)}   \\ 
+ \multirow{7}{*}{\texttt{AdaptiveOperatorSampler(leaf)}} & \multirow{7}{*}{$\vec{\mathcal{R}}^{\,}_\text{leaf}, t$} & \texttt{ConstantDistance($\vec{\mathcal{R}}^{\,}_\text{leaf}, t$)}   \\ 
 && \texttt{LeafAVMVN($\vec{\mathcal{R}}^{\,}_\text{leaf}$)}  \\
@@
 \hline
- \multirow{6}{*}{\texttt{AdaptiveOperatorSampler(internal)}} & \multirow{6}{*}{$\vec{\mathcal{R}}^{\,}_\text{int}, t$} & \texttt{ConstantDistance($\vec{\mathcal{R}}^{\,}_\text{int}, \mathcal{T}$)}   \\
+ \multirow{6}{*}{\texttt{AdaptiveOperatorSampler(internal)}} & \multirow{6}{*}{$\vec{\mathcal{R}}^{\,}_\text{int}, t$} & \texttt{ConstantDistance($\vec{\mathcal{R}}^{\,}_\text{int}, t$)}   \\ 
 && \texttt{RandomWalk($\vec{\mathcal{R}}^{\,}_\text{int}$)}  \\
@@
 This facilitates suitable weighting of the \texttt{LeafAVMVN} operator, which is only applicable to leaf nodes (\textbf{\nameref{AVMVN_sect}}).
-In this setup, the \texttt{RandomWalk($x$)}, \texttt{Scale($x$)}, and \texttt{SampleFromPrior($x$)} operators apply to the corresponding set of branch rates $x$, whereas \texttt{ConstantDistance($x, \mathcal{T}$)} is only applicable to internal nodes which have at least one child of type $x \in \{\vec{\mathcal{R}}^{\,}_\text{leaf}, \vec{\mathcal{R}}^{\,}_\text{int}\}$.
+In this setup, the \texttt{RandomWalk($x$)}, \texttt{Scale($x$)}, and \texttt{SampleFromPrior($x$)} operators apply to the corresponding set of branch rates $x$, whereas \texttt{ConstantDistance($x, t$)} is only applicable to internal nodes which have at least one child of type $x \in \{\vec{\mathcal{R}}^{\,}_\text{leaf}, \vec{\mathcal{R}}^{\,}_\text{int}\}$.
 Finally, the Robinson-Foulds distance between trees before and after every proposal accept is used to train the weights behind \texttt{AdaptiveOperatorSampler(NER)} (see \textbf{\nameref{sect:NER}}).
@@
 
-\clearpage
 \subsection*{Bactrian proposal kernel} \label{sect:randomwalks}
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{Figures/bactrian.pdf}
+%\includegraphics[width=\textwidth]{Figures/bactrian.pdf}
 \caption{\textbf{The Bactrian proposal kernel.} The step size made under a Bactrian proposal kernel is equal to $s \Sigma$ where $\Sigma$ is drawn from the above distribution and $s$ is tunable.   }
@@
 
-\clearpage
 \subsection*{Narrow Exchange Rate} \label{sect:NER}
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{Figures/NarrowExchange.pdf}
+%\includegraphics[width=\textwidth]{Figures/NarrowExchange.pdf}
 \caption{\textbf{Depiction of \texttt{NarrowExchange} and \texttt{NarrowExchangeRate} operators.} Proposals are denoted by $\mathcal{T} \rightarrow \mathcal{T}^\prime$.
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{Figures/acceptanceRates.pdf}
+%\includegraphics[width=\textwidth]{Figures/acceptanceRates.pdf}
 \caption{\textbf{Screening of NER and NERw variants by acceptance rate.} Top left: comparison of NER variants with the null operator $\text{NER}\{\}$ = \texttt{NarrowExchange}. 
@@
 To prevent the learned weight behind \texttt{LeafAVMVN} from dominating the \texttt{AdaptiveOperatorSampler} weighting scheme and therefore inhibiting the mixing of internal node rates, we 
-introduce the \texttt{AdaptiveOperatorSampler(leaf)} and \texttt{AdaptiveOperatorSampler(internal)} meta-operators which operate exclusively on leaf node rates $\vec{\mathcal{R}}^{\,}_\text{leaf}$ and internal node rates $\vec{\mathcal{R}}^{\,}_\text{int}$ respectively  (\textbf{Table \ref{table:AVMVNoperators}}).
+introduce the \texttt{AdaptiveOperatorSampler(leaf)} and \texttt{AdaptiveOperatorSampler(internal)} meta-operators which operate exclusively on leaf node rates $\vec{\mathcal{R}}^{\,}_\text{leaf}$ and internal node rates $\vec{\mathcal{R}}^{\,}_\text{int}$ respectively  (\textbf{Table \ref{table:adaptiveSampling}}).
 The former employs the \texttt{LeafAVMVN} operator and learns its weight during MCMC (after providing it sufficient time to learn $\Sigma_N$).
 
-\clearpage
 \subsection*{Model specification and MCMC settings} \label{sect:methods}
@@
   \hline
- \texttt{AdaptiveOperatorSampler} & Samples sub-operators proportionally to their weights, which are learned (see \nameref{sect:adaptiveSampling}). & $\vec{\mathcal{R}}^{\,}, \sigma, \mathcal{T}$ \\
+ \texttt{AdaptiveOperatorSampler} & Samples sub-operators proportionally to their weights, which are learned (see \nameref{sect:adaptiveSampling}). & $\vec{\mathcal{R}}^{\,}, \sigma, t \mathcal{T}$ \\
   \hline
@@
 \begin{flushleft}
-Pre-existing clock model operators are summarised in \textbf{Table \ref{table:kernels}}
+Pre-existing clock model operators are summarised in \textbf{Table \ref{table:kernels}}. $t$ denotes node heights while $\mathcal{T}$ denotes the whole tree, including topology.
 \end{flushleft}
@@
    \multirow{10}{*}{cons} 
-   & \texttt{ConstantDistance($\vec{\mathcal{R}}^{\,}, \mathcal{T}$)} & $20 \times \frac{2N-2}{2N-1}$ & \checkmark & & \checkmark  \\
-   & \texttt{SimpleDistance($\vec{\mathcal{R}}^{\,}, \mathcal{T}$)} & $\frac{20}{2} \times \frac{1}{2N-1}$ & \checkmark & & \checkmark  \\
+   & \texttt{ConstantDistance($\vec{\mathcal{R}}^{\,}, t$)} & $20 \times \frac{2N-2}{2N-1}$ & \checkmark & & \checkmark  \\
+   & \texttt{SimpleDistance($\vec{\mathcal{R}}^{\,}, t$)} & $\frac{20}{2} \times \frac{1}{2N-1}$ & \checkmark & & \checkmark  \\
    & \texttt{SmallPulley($\vec{\mathcal{R}}^{\,}$)} & $\frac{20}{2} \times \frac{1}{2N-1}$ & \checkmark & & \checkmark  \\
@@
 
-\clearpage
 \section*{Results} \label{sect:results}
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{Figures/tournament.pdf}
+%\includegraphics[width=\textwidth]{Figures/tournament.pdf}
 \caption{\textbf{Protocol for optimising clock model methodologies.} Each area (detailed in \textbf{\nameref{sect:models}}) is optimised sequentially, and the best setting from each step is used when optimising the following step.}
@@
 
-Methodologies were benchmarked using one simulated and eight empirical datasets.
+Methodologies were benchmarked using one simulated and eight empirical datasets \cite{Ran_2018,Dornburg_2012,Cognato_2001,Sauquet_2011,Broughton_2013,Kawahara_2013,Rightmyer_2013,Moyle_2016}.
 The latter were compiled by Lanfear as ``benchmark alignments'' (\textbf{Table \ref{table:datasets}}) \cite{lanfear2019Github, lanfear2016partitionfinder}.
@@
 All methodologies used identical models and operator configurations, except where a difference is specified.
-
-%All 25 datasets presented in \textbf{Table \ref{table:datasets}} are benchmarked together $1 \times$ each at the end of the protocol.
-Datasets and BEAST 2 .xml templates are provided in the GitHub repository accompanying this article.
 
@@
 
-\clearpage
 \subsection*{Round 1: A simple operator-weight learning algorithm greatly improved performance}
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{benchmarking/benchmarkingVM/ESS_round1_real.pdf}
+%\includegraphics[width=\textwidth]{benchmarking/benchmarkingVM/ESS_round1_real.pdf}
 \caption{\textbf{Round 1: benchmarking the \texttt{AdaptiveOperatorSampler} operator.} Top left, top right, bottom left: each plot compares the ESS/hr ($\pm 1$ standard error) across two operator configurations.
@@
 
-\clearpage
 \subsection*{Round 2: The \textit{real} parameterisation yielded the fastest mixing }
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{benchmarking/benchmarkingVM/ESS_round2.pdf}
+%\includegraphics[width=\textwidth]{benchmarking/benchmarkingVM/ESS_round2.pdf}
 \caption{\textbf{Round 2: benchmarking substitution rate parameterisations.} Top left, top right, bottom left: the adapt (\textit{real}), adapt (\textit{cat}), and adapt (\textit{quant}) configurations were compared.
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{benchmarking/benchmarkingVM/ESS_timesettings.pdf}
+%\includegraphics[width=\textwidth]{benchmarking/benchmarkingVM/ESS_timesettings.pdf}
 \caption{\textbf{Comparison of runtimes across methodologies.} 
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{benchmarking/benchmarkingVM/ESS_round3.pdf}
+%\includegraphics[width=\textwidth]{benchmarking/benchmarkingVM/ESS_round3.pdf}
 \caption{\textbf{Round 3: benchmarking the Bactrian kernel.}
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{benchmarking/benchmarkingVM/ESS_round4.pdf}
-\includegraphics[width=\textwidth]{Figures/broughton.pdf}
+%\includegraphics[width=\textwidth]{Figures/Fig12.pdf}
 \caption{\textbf{Round 4: benchmarking the NER operators.} 
@@
 
-\clearpage
 \subsection*{Round 5: The AVMVN leaf rate operator was computationally demanding and improved mixing very slightly}
@@
 \begin{figure}[!h]
-\includegraphics[width=\textwidth]{benchmarking/benchmarkingVM/ESS_round5.pdf}
+%\includegraphics[width=\textwidth]{benchmarking/benchmarkingVM/ESS_round5.pdf}
 \caption{\textbf{Round 5: benchmarking the \texttt{LeafAVMVN} operator.} See \textbf{Fig \ref{fig:round3Results}} caption for figure notation.  }
@@
 
-\newpage
 \section*{Conclusion}
@@
 
-\section*{Software availability}
-
-The work presented in this article was implemented as a user friendly open source BEAST 2 package with GUI support via BEAUti making it easy to set up an analysis.
-Instructions for using and installing this package can be found at \href{https://github.com/jordandouglas/ORC}{https://github.com/jordandouglas/ORC}.
-
 \section*{Acknowledgements}
@@
 
-\newpage
-\bibliography{references}
+%\bibliography{references}
+
+\begin{thebibliography}{10}
+
+\bibitem{zuckerkandl1962molecular}
+Zuckerkandl E.
+\newblock Molecular disease, evolution, and genetic heterogeneity.
+\newblock Horizons in biochemistry. 1962; p. 189--225.
+
+\bibitem{douzery2003local}
+Douzery EJ, Delsuc F, Stanhope MJ, Huchon D.
+\newblock Local molecular clocks in three nuclear genes: divergence times for
+  rodents and other mammals and incompatibility among fossil calibrations.
+\newblock Journal of Molecular Evolution. 2003;57(1):S201--S213.
+
+\bibitem{drummond2006relaxed}
+Drummond AJ, Ho SY, Phillips MJ, Rambaut A.
+\newblock Relaxed phylogenetics and dating with confidence.
+\newblock PLoS biology. 2006;4(5):e88.
+
+\bibitem{kuhner1995estimating}
+Kuhner MK, Yamato J, Felsenstein J.
+\newblock Estimating effective population size and mutation rate from sequence
+  data using Metropolis-Hastings sampling.
+\newblock Genetics. 1995;140(4):1421--1430.
+
+\bibitem{larget1999markov}
+Larget B, Simon DL.
+\newblock Markov chain Monte Carlo algorithms for the Bayesian analysis of
+  phylogenetic trees.
+\newblock Molecular biology and evolution. 1999;16(6):750--759.
+
+\bibitem{mau1999bayesian}
+Mau B, Newton MA, Larget B.
+\newblock Bayesian phylogenetic inference via Markov chain Monte Carlo methods.
+\newblock Biometrics. 1999;55(1):1--12.
+
+\bibitem{metropolis53}
+Metropolis N.
+\newblock Equation of state calculations by fast computing machines.
+\newblock {J Chem Phys}. 1953;21:1087--1092.
+
+\bibitem{hastings70}
+Hastings W.
+\newblock {Monte-Carlo} sampling methods using {Markov} chains and their
+  applications.
+\newblock Biometrika. 1970;57:97--109.
+
+\bibitem{drummond2012bayesian}
+Drummond AJ, Suchard MA, Xie D, Rambaut A.
+\newblock Bayesian phylogenetics with BEAUti and the BEAST 1.7.
+\newblock Molecular biology and evolution. 2012;29(8):1969--1973.
+
+\bibitem{bouckaert2019beast}
+Bouckaert R, Vaughan TG, Barido-Sottani J, Duch{\^e}ne S, Fourment M,
+  Gavryushkina A, et~al.
+\newblock BEAST 2.5: An advanced software platform for Bayesian evolutionary
+  analysis.
+\newblock PLoS computational biology. 2019;15(4):e1006650.
+
+\bibitem{ronquist2012mrbayes}
+Ronquist F, Teslenko M, Van Der~Mark P, Ayres DL, Darling A, H{\"o}hna S,
+  et~al.
+\newblock MrBayes 3.2: efficient Bayesian phylogenetic inference and model
+  choice across a large model space.
+\newblock Systematic biology. 2012;61(3):539--542.
+
+\bibitem{hohna2016revbayes}
+H{\"o}hna S, Landis MJ, Heath TA, Boussau B, Lartillot N, Moore BR, et~al.
+\newblock RevBayes: Bayesian phylogenetic inference using graphical models and
+  an interactive model-specification language.
+\newblock Systematic biology. 2016;65(4):726--736.
+
+\bibitem{zuckerkandl1965evolutionary}
+Zuckerkandl E, Pauling L.
+\newblock Evolutionary divergence and convergence in proteins.
+\newblock In: Evolving genes and proteins. Elsevier; 1965. p. 97--166.
+
+\bibitem{gillespie1994causes}
+Gillespie JH.
+\newblock The causes of molecular evolution. vol.~2.
+\newblock Oxford University Press On Demand; 1994.
+
+\bibitem{woolfit2009effective}
+Woolfit M.
+\newblock Effective population size and the rate and pattern of nucleotide
+  substitutions.
+\newblock Biology letters. 2009;5(3):417--420.
+
+\bibitem{loh2010optimization}
+Loh E, Salk JJ, Loeb LA.
+\newblock Optimization of DNA polymerase mutation rates during bacterial
+  evolution.
+\newblock Proceedings of the National Academy of Sciences.
+  2010;107(3):1154--1159.
+
+\bibitem{lepage2007general}
+Lepage T, Bryant D, Philippe H, Lartillot N.
+\newblock A general comparison of relaxed molecular clock models.
+\newblock Molecular biology and evolution. 2007;24(12):2669--2680.
+
+\bibitem{li2012model}
+Li WLS, Drummond AJ.
+\newblock Model averaging and Bayes factor calculation of relaxed molecular
+  clocks in Bayesian phylogenetics.
+\newblock Molecular biology and evolution. 2012;29(2):751--761.
+
+\bibitem{faria2017establishment}
+Faria NR, Quick J, Claro I, Theze J, de~Jesus JG, Giovanetti M, et~al.
+\newblock Establishment and cryptic transmission of Zika virus in Brazil and
+  the Americas.
+\newblock Nature. 2017;546(7658):406--410.
+
+\bibitem{giovanetti2020first}
+Giovanetti M, Benvenuto D, Angeletti S, Ciccozzi M.
+\newblock The first two cases of 2019-nCoV in Italy: Where they come from?
+\newblock Journal of medical virology. 2020;92(5):518--521.
+
+\bibitem{huelsenbeck2000compound}
+Huelsenbeck JP, Larget B, Swofford D.
+\newblock A compound Poisson process for relaxing the molecular clock.
+\newblock Genetics. 2000;154(4):1879--1892.
+
+\bibitem{thorne1998estimating}
+Thorne JL, Kishino H, Painter IS.
+\newblock Estimating the rate of evolution of the rate of molecular evolution.
+\newblock Molecular biology and evolution. 1998;15(12):1647--1657.
+
+\bibitem{yoder2000estimation}
+Yoder AD, Yang Z.
+\newblock Estimation of primate speciation dates using local molecular clocks.
+\newblock Molecular Biology and Evolution. 2000;17(7):1081--1090.
+
+\bibitem{drummond2010bayesian}
+Drummond AJ, Suchard MA.
+\newblock Bayesian random local clocks, or one rate to rule them all.
+\newblock BMC biology. 2010;8(1):1--12.
+
+\bibitem{zhang2020using}
+Zhang C, Huelsenbeck JP, Ronquist F.
+\newblock Using parsimony-guided tree proposals to accelerate convergence in
+  Bayesian phylogenetic inference.
+\newblock Systematic Biology. 2020;.
+
+\bibitem{meyer2019adaptive}
+Meyer X.
+\newblock Adaptive Tree Proposals for Bayesian Phylogenetic Inference.
+\newblock BioRxiv. 2019; p. 783597.
+
+\bibitem{hohna2012guided}
+H{\"o}hna S, Drummond AJ.
+\newblock Guided tree topology proposals for Bayesian phylogenetic inference.
+\newblock Systematic biology. 2012;61(1):1--11.
+
+\bibitem{altekar2004parallel}
+Altekar G, Dwarkadas S, Huelsenbeck JP, Ronquist F.
+\newblock Parallel metropolis coupled Markov chain Monte Carlo for Bayesian
+  phylogenetic inference.
+\newblock Bioinformatics. 2004;20(3):407--415.
+
+\bibitem{muller2019coupled}
+M{\"u}ller NF, Bouckaert R.
+\newblock Adaptive Metropolis-coupled MCMC for BEAST 2.
+\newblock PeerJ. 2020;.
+
+\bibitem{baele2017adaptive}
+Baele G, Lemey P, Rambaut A, Suchard MA.
+\newblock Adaptive MCMC in Bayesian phylogenetics: an application to analyzing
+  partitioned data in BEAST.
+\newblock Bioinformatics. 2017;33(12):1798--1805.
+
+\bibitem{yang2013searching}
+Yang Z, Rodr{\'\i}guez CE.
+\newblock Searching for efficient Markov chain Monte Carlo proposal kernels.
+\newblock Proceedings of the National Academy of Sciences.
+  2013;110(48):19307--19312.
+
+\bibitem{thawornwattana2018designing}
+Thawornwattana Y, Dalquen D, Yang Z, et~al.
+\newblock Designing simple and efficient Markov chain Monte Carlo proposal
+  kernels.
+\newblock Bayesian Analysis. 2018;13(4):1037--1063.
+
+\bibitem{zhang2020improving}
+Zhang R, Drummond A.
+\newblock Improving the performance of Bayesian phylogenetic inference under
+  relaxed clock models.
+\newblock BMC Evolutionary Biology. 2020;20:1--28.
+
+\bibitem{green1995reversible}
+Green PJ.
+\newblock Reversible jump Markov chain Monte Carlo computation and Bayesian
+  model determination.
+\newblock Biometrika. 1995;82(4):711--732.
+
+\bibitem{geyer2003metropolis}
+Geyer CJ. The metropolis-hastings-green algorithm; 2003.
+
+\bibitem{gelman2004parameterization}
+Gelman A.
+\newblock Parameterization and Bayesian modeling.
+\newblock Journal of the American Statistical Association.
+  2004;99(466):537--545.
+
+\bibitem{roberts1997weak}
+Roberts GO, Gelman A, Gilks WR, et~al.
+\newblock Weak convergence and optimal scaling of random walk Metropolis
+  algorithms.
+\newblock The annals of applied probability. 1997;7(1):110--120.
+
+\bibitem{rosenthal2011optimal}
+Rosenthal JS, et~al.
+\newblock Optimal proposal distributions and adaptive MCMC.
+\newblock Handbook of Markov Chain Monte Carlo. 2011;4(10.1201).
+
+\bibitem{robinson1981comparison}
+Robinson DF, Foulds LR.
+\newblock Comparison of phylogenetic trees.
+\newblock Mathematical biosciences. 1981;53(1-2):131--147.
+
+\bibitem{jukes1969evolution}
+Jukes TH, Cantor CR, et~al.
+\newblock Evolution of protein molecules.
+\newblock Mammalian protein metabolism. 1969;3:21--132.
+
+\bibitem{drummond2002estimating}
+Drummond AJ, Nicholls GK, Rodrigo AG, Solomon W.
+\newblock Estimating mutation parameters, population history and genealogy
+  simultaneously from temporally spaced sequence data.
+\newblock Genetics. 2002;161(3):1307--1320.
+
+\bibitem{suchard2018bayesian}
+Suchard MA, Lemey P, Baele G, Ayres DL, Drummond AJ, Rambaut A.
+\newblock Bayesian phylogenetic and phylodynamic data integration using BEAST
+  1.10.
+\newblock Virus evolution. 2018;4(1):vey016.
+
+\bibitem{semple2003phylogenetics}
+Semple C, Steel M, et~al.
+\newblock Phylogenetics. vol.~24.
+\newblock Oxford University Press on Demand; 2003.
+
+\bibitem{higham2016matlab}
+Higham DJ, Higham NJ.
+\newblock MATLAB guide.
+\newblock SIAM; 2016.
+
+\bibitem{yule1925ii}
+Yule GU.
+\newblock II.—A mathematical theory of evolution, based on the conclusions of
+  Dr. JC Willis, FR S.
+\newblock Philosophical transactions of the Royal Society of London Series B,
+  containing papers of a biological character. 1925;213(402-410):21--87.
+
+\bibitem{hasegawa1985dating}
+Hasegawa M, Kishino H, Yano Ta.
+\newblock Dating of the human-ape splitting by a molecular clock of
+  mitochondrial DNA.
+\newblock Journal of molecular evolution. 1985;22(2):160--174.
+
+\bibitem{ayres2012beagle}
+Ayres DL, Darling A, Zwickl DJ, Beerli P, Holder MT, Lewis PO, et~al.
+\newblock BEAGLE: an application programming interface and high-performance
+  computing library for statistical phylogenetics.
+\newblock Systematic biology. 2012;61(1):170--173.
+
+\bibitem{saitou1987neighbor}
+Saitou N, Nei M.
+\newblock The neighbor-joining method: a new method for reconstructing
+  phylogenetic trees.
+\newblock Molecular biology and evolution. 1987;4(4):406--425.
+
+\bibitem{Ran_2018}
+Ran JH, Shen TT, Wang MM, Wang XQ.
+\newblock Phylogenomics resolves the deep phylogeny of seed plants and
+  indicates partial convergent or homoplastic evolution between Gnetales and
+  angiosperms.
+\newblock Proceedings of the Royal Society B: Biological Sciences.
+  2018;285(1881):20181012.
+\newblock doi:{10.1098/rspb.2018.1012}.
+
+\bibitem{Dornburg_2012}
+Dornburg A, Moore JA, Webster R, Warren DL, Brandley MC, Iglesias TL, et~al.
+\newblock Molecular phylogenetics of squirrelfishes and soldierfishes
+  (Teleostei: Beryciformes: Holocentridae): Reconciling more than 100 years of
+  taxonomic confusion.
+\newblock Molecular Phylogenetics and Evolution. 2012;65(2):727--738.
+\newblock doi:{10.1016/j.ympev.2012.07.020}.
+
+\bibitem{Cognato_2001}
+Cognato AI, Vogler AP.
+\newblock Exploring Data Interaction and Nucleotide Alignment in a Multiple
+  Gene Analysis of Ips (Coleoptera: Scolytinae).
+\newblock Systematic Biology. 2001;50(6):758--780.
+\newblock doi:{10.1080/106351501753462803}.
+
+\bibitem{Sauquet_2011}
+Sauquet H, Ho SYW, Gandolfo MA, Jordan GJ, Wilf P, Cantrill DJ, et~al.
+\newblock Testing the Impact of Calibration on Molecular Divergence Times Using
+  a Fossil-Rich Group: The Case of Nothofagus (Fagales).
+\newblock Systematic Biology. 2011;61(2):289--313.
+\newblock doi:{10.1093/sysbio/syr116}.
+
+\bibitem{Broughton_2013}
+Broughton RE, Betancur-R R, Li C, Arratia G, Ort{\'{\i}} G.
+\newblock Multi-locus phylogenetic analysis reveals the pattern and tempo of
+  bony fish evolution.
+\newblock {PLoS} Currents.
+  2013;doi:{10.1371/currents.tol.2ca8041495ffafd0c92756e75247483e}.
+
+\bibitem{Kawahara_2013}
+Kawahara AY, Rubinoff D.
+\newblock Convergent evolution of morphology and habitat use in the explosive
+  Hawaiian fancy case caterpillar radiation.
+\newblock Journal of Evolutionary Biology. 2013;26(8):1763--1773.
+\newblock doi:{10.1111/jeb.12176}.
+
+\bibitem{Rightmyer_2013}
+Rightmyer MG, Griswold T, Brady SG.
+\newblock Phylogeny and systematics of the bee genus Osmia (Hymenoptera:
+  Megachilidae) with emphasis on North American Melanosmia: subgenera,
+  synonymies and nesting biology revisited.
+\newblock Systematic Entomology. 2013;38(3):561--576.
+
+\bibitem{Moyle_2016}
+Moyle RG, Oliveros CH, Andersen MJ, Hosner PA, Benz BW, Manthey JD, et~al.
+\newblock Tectonic collision and uplift of Wallacea triggered the global
+  songbird radiation.
+\newblock Nature Communications. 2016;7(1).
+\newblock doi:{10.1038/ncomms12709}.
+
+\bibitem{lanfear2019Github}
+Lanfear R.
+\newblock BenchmarkAlignments https://github.com/roblanf/BenchmarkAlignments.
+\newblock GitHub. 2019;.
+
+\bibitem{lanfear2016partitionfinder}
+Lanfear R, Frandsen PB, Wright AM, Senfeld T, Calcott B.
+\newblock PartitionFinder 2: new methods for selecting partitioned models of
+  evolution for molecular and morphological phylogenetic analyses.
+\newblock Molecular biology and evolution. 2016;34(3):772--773.
+
+\bibitem{uglytrees}
+Douglas J.
+\newblock {UglyTrees: a browser-based multispecies coalescent tree visualiser}.
+\newblock Bioinformatics. 2020;doi:{10.1093/bioinformatics/btaa679}.
+
+\bibitem{haario2001adaptive}
+Haario H, Saksman E, Tamminen J, et~al.
+\newblock An adaptive Metropolis algorithm.
+\newblock Bernoulli. 2001;7(2):223--242.
+
+\bibitem{vihola2012robust}
+Vihola M.
+\newblock Robust adaptive Metropolis algorithm with coerced acceptance rate.
+\newblock Statistics and Computing. 2012;22(5):997--1008.
+
+\bibitem{benson2018adaptive}
+Benson A, Friel N, et~al.
+\newblock Adaptive MCMC for multiple changepoint analysis with applications to
+  large datasets.
+\newblock Electronic Journal of Statistics. 2018;12(2):3365--3396.
+
+\bibitem{davis2020blocking}
+Davis A, Hauser J.
+\newblock Blocking borehole conductivity logs at the resolution of above-ground
+  electromagnetic systems.
+\newblock Geophysics. 2020;85(2):E67--E77.
+
+\bibitem{roberts2007coupling}
+Roberts GO, Rosenthal JS.
+\newblock Coupling and ergodicity of adaptive Markov chain Monte Carlo
+  algorithms.
+\newblock Journal of applied probability. 2007;44(2):458--475.
+
+\bibitem{hohna2008clock}
+Hohna S, Defoin-Platel M, Drummond AJ.
+\newblock Clock-constrained tree proposal operators in Bayesian phylogenetic
+  inference.
+\newblock In: 2008 8th IEEE International Conference on BioInformatics and
+  BioEngineering. IEEE; 2008. p. 1--7.
+
+\bibitem{simon1998local}
+Simon D, Larget B.
+\newblock Bayesian analysis in molecular biology and evolution (BAMBE)
+  http://www.mathcs.duq.edu/larget/bambe.html.
+\newblock Pittsburgh, Pennsylvania. 1998;.
+
+\bibitem{jow2002bayesian}
+Jow H, Hudelot C, Rattray M, Higgs P.
+\newblock Bayesian phylogenetics using an RNA substitution model applied to
+  early mammalian evolution.
+\newblock Molecular Biology and Evolution. 2002;19(9):1591--1601.
+
+\bibitem{lakner2008efficiency}
+Lakner C, Van Der~Mark P, Huelsenbeck JP, Larget B, Ronquist F.
+\newblock Efficiency of Markov chain Monte Carlo tree proposals in Bayesian
+  phylogenetics.
+\newblock Systematic biology. 2008;57(1):86--103.
+
+\end{thebibliography}
 
